### 2018-11-26 draft.tex
various fixes

\documentclass[12pt]{article}
\usepackage[top=2cm, bottom=2cm, left=2cm, right=2cm]{geometry}
\geometry{a4paper}
%\usepackage{authblk}

\usepackage{graphicx}
\usepackage{amsmath,amssymb,theorem,enumerate}
\usepackage{hyperref}
\usepackage{mathrsfs}

\newcommand{\email}[1]{\href{mailto:#1}{#1}}
\newcommand{\denselist}{\itemsep -2pt\topsep-6pt\partopsep-6pt}

%\newcommand{\rank}{\text{rank}}
\newcommand{\rank}{v}
\newcommand{\preflarge}{\boldsymbol{\succeq}^\textbf{r}}%real, complete pref
%\newcommand{\pref}{\boldsymbol{\succ}^\textbf{r}}%real, connected pref, strict
\newcommand{\pref}{{\succ}}%real, connected pref, strict
\newcommand{\prefr}{{\succ}^{r}}%real, connected pref, strict
\newcommand{\ppreflarge}{\succeq^\text{p}}%partial pref
\newcommand{\ppref}{\succ^\text{p}}%partial pref

\newcommand{\profile}{\textbf{v}}%(complete) prorile
\newcommand{\pprofile}{\textbf{p}}%partial prorile
\newcommand{\w}{\textbf{w}}%partial prorile

\DeclareMathOperator{\PMR}{PMR}
\DeclareMathOperator{\MR}{MR}
\DeclareMathOperator{\MMR}{MMR}

\title{Robust Winner Determination and Simultaneous Elicitation of Scoring Rules and Preferences}
\author{}
%\author{Paolo Viappiani} \affil{LIP6\\\email{paolo.viappiani@lip6.fr}}
%\author{Olivier Cailloux} 
%\author{Stefano Moretti}\affil{LAMSADE}

\begin{document}
\maketitle

%$\preflarge, \pref, \ppreflarge, \ppref$
% aggregate different opinions

%Minimax regret
%Given a full profile: use linear programming to maximize regret
%Given a partial profile: use techniques of Lu and Boutilier (2011).
Social choice deals with the problem of determining a consensus choice from the preferences of different agents (voters).
In the classical setting, the social choice rule is fixed beforehand; indeed many works analyze the properties of different rules (including axiomatic treatments) in order to justify the choice of specific social choice functions. 
Moreover, it is usually assumed that the preferences of the voters are completely known.

%We argue that it is possible that the committee wants to precise some preferences about the aggregation.
%We assume that obtaining information about them has a coast. 
%We  therefore aim at asking as few questions as possible.
In this draft we depart from the classic view by considering that both preferences and the social choice rule can be only partially specified.
We note that previous works have considered either partial preferences or a partially specified aggregation, but we do not know of any work considering both sources of uncertainty at the same time.
%We consider that the committee wants to express preferences for some voting rules
We provide a method for approximate winner determination and an incremental elicitation protocol based on minimax regret.

\section*{Background}

We assume that there is a set $A$ of $m$ alternatives and $n$ agents (voters); each agent is associated to a preference order.
%The set of preference orders is called profile and it is denoted by $v$.
The preferences of the agents are supposed to be linear orders (connected, transitive, asymmetric relations) involving the alternatives;
$\pref_i$ denotes the ``real'' preference relation of agent $i$. 
The set $(\pref_1,\ldots,\pref_n)$ is known in the social choice literature as the {\em preference  profile}.
The profile is equivalently represented by $\textbf{v}=(v_1,\ldots,v_n)$ where $v_i(j)$ denotes the rank (position) of alternative $j$ in the preference order $\pref_i$. 
With a little abuse of notation, we will use the term profile to refer to either $\textbf{v}$ or to the preference relations, depending on the context.
Let $V$ the set of possible preference profiles (the cartesian product of $n$ linear orders).

A social choice funtion $f : V \rightarrow A$ associates a profile with one winner (or multiple winners in some cases).
Among the many possible social choice functions, we consider those rules that are based on a numerical score that is decomposable voter-wise.
%the score $s(a; v)$ of alternative $a$ is additive decomposable if it can be computed as $s(a; v) = \sum_{i} s(a; v_{i})$.
In particular positional scoring rules attach weights to positions;
an alternative obtains a score that depends on the rank obtained in each of the preference orders:

\[ s(x) = \sum_{i=1}^{n} w_{v_i(x)}. \]

where the vector $(w_1,\ldots,w_m)$ is called the scoring vector;
%A positional scoring rule attach weights to positions; 
 it is usually assumed that the weights constitute a monotonic sequence: $w_{1} \geq w_{2} \geq \ldots \geq w_{n}$.

\medskip
We want to reason about partial preference information.
A partial preference  is encoded by a partial order $\ppref_k$  of voter $k$;
we assume that preference information is truthful, i.e. $a \ppref_k b \implies a \pref_k b$.

A completion of $\ppref_k$ is any linear order $\pref_k$ that extends $\ppref_k$.
Let $C(\ppref_k)$ be the set of completions of $\ppref_k$, that is the set of all complete rankings that extend $\ppref_k$.
An incomplete profile is a set of partial votes %$\textbf{p}=(p_1,\ldots,p_n)$.
$\textbf{p}=(\ppref_1,\ldots,\ppref_n)$.

We let $C(\textbf{p})=C(\ppref_1)\times \ldots \times C(\ppref_n)$ be the set of complete profiles extending $p$.

\medskip
We also assume that the weights of the scoring rules are only partially specified.
We use $W$ to denote the set of feasible weight vector.
Without loss of generality, we assume $w_1=0$ and $w_m=0$.
The preferences of the chair are incoded with linear constraints, for instance one may state
that $w_2>0.5$.
A specific kind of preference may that of requiring the sequence of the weights to be convex, that means
that the difference of between the weight of the first position and the weight of the second position is at least as much as the difference between the weights of the second and third position, etc. 
\[ \forall i \in \{1,\ldots,n\} \;\; w_i - w_{i+1} \geq w_{i+1}-w_{i+2} \iff  w_i - 2 w_{i+1} + w_{i+2} \geq 0 \]
This is a constraint often used when aggregating rankings in sport competitions.

\section*{Related works}

\paragraph{Uncertain scoring rules}
A number of works have dealt with the problem of reasoning with incompletely specified aggregation functions.
In particular, when considering positional scoring rules, it is possible to derive dominance relations (akin to sthochastic dominance) that allow to eliminate some alternatives since they will be less preferred than another one for any instantiation of the weights \cite{Stein1994}.
More recently the characterization of methods for aggregating the uncertainty over the scoring vectors has been studied in \cite{Viappiani2018}.
We also note that the elicitation methods based on minimax regret described in \cite{Boutilier2006} (and in many other recent papers), while not specifically targeted to scoring rules, can be easily adapted (from a technical point of view) to elicit the scoring vector from a committee.

\paragraph{Incomplete profiles}
%In this setting, the system knows a partial preference profile $\ppref$ 
%The partial preference relation $\ppref_i$ represents our knowledge about the preferences of agent $i$.

Lu and Boutilier \cite{Lu2011} assume that the preferences of the voters are only partially known (while the social choice function is known and fixed in advance; it is assumed to be decomposable) and 
 propose to use minimax regret to produce a robust approximation.
Each alternative is associated with a max regret value that measures how far from optimal it could be in the worst case given any completion of the partial profile.
The computation of max regret is facilitated by the fact the score is decomposable.
% We are given  $\ppref_i $,  a partial preference.
% The maximum regret is considered by assuming an adversary can choose the profile
% \begin{align*}
% \PMR(a,b; p) & = \max_{v \in C(p)} s(b; v) - s(a; v) \\
% \MR(a; p) & = \max_{b} \PMR(a,b) 
% \end{align*}
% 
% We then choose the minimax regret optimal alternative:
% \begin{align*}
% \MMR(p) & = \min \PMR(a,b) \\
% a^{*}(p) & \in \arg\min \PMR(a,b) 
% \end{align*}
%Max regret and minimax regret can be computed using independent completion of partial votes for non-decomposable scoring rules.

\section*{Incomplete profiles and partial information about the scoring rule}

{\bf Perhaps it could me made more general considering not only scoring rules, but all rules based on a score (as in Boutilier's paper)}

In this draft, we consider a setting where both the voters' preferences and the preferences of the chair about the voting rule are incomplete.
We write the score as $s(x; v,w)$ to underline the depency of the score on the preference profile and on the weight vector. Let $s(x;v,w)$ denote the score of alternative $x$ in profile $\textbf{v}$ with weights $\textbf{w}$:
\[ s(x;\textbf{v},\textbf{w}) = \sum_{i=1}^{m} w_{\rank_i(x)} \]

%By using decomposition, we can compute the vote-wise regret...

The quality of an alternative can be quantified by considering the maximum regret with respect to an adversary that can choose the instantiation of both a complete profile (extending the known preferences of the agents) and of the scoring vectors (associated to the preferences of the committee).

%The adversary can choose the instantiation of the weights and preferences of the agents so to maximize the loss.

We propose to use minimax regret to identify the alternative to declare as the approximate winner, extending the work of \cite{Lu2011} to the simultaneous presence of uncertainty in the agents' preferences and uncertainty in the weights.
The maximum regret is considered by assuming an adversary can choose both 1) to extend the partial profile into a complete profile 2) can instantiate the weights choosing among any feasible weight vector in $W$.

%We consider the pairwise max regret of alternative $x$  against alternative $y$ assuming that the weight vector belongs to $W$:

\begin{align*}
\PMR(x,y; \pprofile, W) &= \max_{\w \in W} \max_{\profile \in C(p)} s(y; \profile,\w) - s(x; \profile,\w)\\
\MR(x; \pprofile, W) &= \max_{y \in A} \PMR(x,y; \pprofile, W) \\
\MMR(\pprofile,W) & = \min_{x \in A} \MR(x;\pprofile,W) \\
x^{*}(\pprofile,W) & \in \arg\min_{x \in A} \MR(x;\pprofile,W) 
\end{align*}

\begin{itemize}
 \item $\PMR(x,y;\pprofile,W)$ denotes the pairwise max regret of $x$ relative to $y$ given partial profile $\pprofile$ and the space of weights $W$, that is the worst-case loss under all possible realizations of the full profile {\em and} all possible instantiations of the weights.
 \item Max regret $\MR(x;\pprofile,W)$ is the worst-case loss of $x$. It is the loss occured by an adversarial selection of a complete profile $\profile$ extending $\pprofile$ and a selection of $\w \in W$ to maximize the loss between $x$ and the true winner under $\profile$ and $w$.
 \item Minimax regret $\MMR(\pprofile,W)$ is the minimum of max regret obtained when choosing $x^*$
\end{itemize}
By recommending the alternative associated with minimax regret, we can provide a recommendation that gives worst-case guarantees, giving some robustness in face of uncertainty (due to both not knowing the agents' preferences and the weights used in the aggregation).

\paragraph{Computation of minimax regret}

We will adapt the reasoning from \cite{Lu2011} combined with linear programming optimization.

Exploiting the decomposition of the score in terms of votes we cam rewrite $\PMR$ as follows:

\begin{align*}
\PMR(x,y; \pprofile, W) &= \max_{\w \in W} \max_{\profile \in C(\pprofile)} [ s(y; \profile,\w) - s(x; \profile,\w) ] = \\
&=  \max_{\w \in W} \sum_{j=1}^{n} \max_{v_j \in C(\succ_j^p)} [s(y; v_j,\w) - s(x; v_j,\w)]=\\
&=  \max_{\w \in W} \sum_{j=1}^{n} \max_{v_j \in C(\succ_j^p)} [w_{v_j(y)} - w_{v_j(x)}] \\
\end{align*}

{\bf \em This is just sketchy TODO: reason about the optimization and complete section}

In many cases the inner maximization can be made regardless of the outer max.
Part of the optimization can be made voter-wise: for each of the agent,s we compute the extend the partial preference into a linear order that makes the gap between y and x as wide as possible.
However, in some cases the choice of how to complete the profiles may depend on the choice of weights, therefore it may be quite complicated...  (need to use integer variables???)
\medskip
 {\em Explain why convex sequences do not pose any problem}
In the case of convex sequences, the optimization can be done without integer variables.
Let $\hat{v}_k$ be the linear order extending $p_k$ according to the procedure descibed in \cite{Lu2011}.
\begin{align*}
\max_{\w \in W} \sum_{j=1}^{n}  [w_{\hat{v}_j(y)} - w_{\hat{v}_j(x)}]
\end{align*}
Therefore the pairwsie maximum regret can be computed with a linear program.

\paragraph{Interactive Elicitation}
Srtarting from some intial partial knowledge, our goal is to learn both the scoring rule function and the agents' preferences.
While this is of course possible by doing one elicitation after another one, we propose an interleaved approach.
We adopt an interactive  protocol for simultaneously eliciting the preferences of the chair about the voting rule and the voters' preferences about the alternatives.
Indeed, it can be beneficial to interleave questions asked to the committee and questions asked to voters, depending on which is estimated to be more informative.

Answers given by the committee about the scoring rule refines our knowledge of the weights $w_1,\ldots,w_n$.
Answers given by one of the agents refine our knowledge about the agent's preferences

\begin{itemize}
\item At each step we need to decide whether we want to ask a question to the committee or to one of the agents (and to which agent in particular).

\item We can consider different types of questions: asking to compare a pair of alternatives, asking about top-k alternatives.

Type of questions that we can ask to the chair:
bound queries, comparison queries.

\item In the experiments we want to compare the interleaved approach with a baseline challenger, a method  that elicits the preferences of the voters first and then the voting rule (or the other way around)
\end{itemize}

{\em Some ideas: decompose the regret into two components, one due to $\w$ and one due to $\pprofile$, and ask a question to the chair / or to one of the agens depending on which is highest}

%{\small
\bibliography{biblio}
\bibliographystyle{plain} 
%}

\end{document}

### 2018-11-26 draft.tex
spelling

@@
 Without loss of generality, we assume $w_1=0$ and $w_m=0$.
-The preferences of the chair are incoded with linear constraints, for instance one may state
+The preferences of the chair are encoded with linear constraints, for instance one may state
 that $w_2>0.5$.
-A specific kind of preference may that of requiring the sequence of the weights to be convex, that means
+A specific kind of preference may require the sequence of the weights to be convex, that means
 that the difference of between the weight of the first position and the weight of the second position is at least as much as the difference between the weights of the second and third position, etc. 

### 2018-12-04 draft.tex
spelling, typos, summation indices

@@
 With a little abuse of notation, we will use the term profile to refer to either $\textbf{v}$ or to the preference relations, depending on the context.
-Let $V$ the set of possible preference profiles (the cartesian product of $n$ linear orders).
+Let $V$ be the set of possible preference profiles (the cartesian product of $n$ linear orders).
 
-A social choice funtion $f : V \rightarrow A$ associates a profile with one winner (or multiple winners in some cases).
+A social choice function $f : V \rightarrow A$ associates a profile with one winner (or multiple winners in some cases).
 Among the many possible social choice functions, we consider those rules that are based on a numerical score that is decomposable voter-wise.
@@
 %A positional scoring rule attach weights to positions; 
- it is usually assumed that the weights constitute a monotonic sequence: $w_{1} \geq w_{2} \geq \ldots \geq w_{n}$.
+ it is usually assumed that the weights constitute a monotonic sequence: $w_{1} \geq w_{2} \geq \ldots \geq w_{m}$.
 
@@
 that $w_2>0.5$.
-A specific kind of preference may require the sequence of the weights to be convex, that means
-that the difference of between the weight of the first position and the weight of the second position is at least as much as the difference between the weights of the second and third position, etc. 
+A specific kind of preference may require the weights sequence to be convex, that means
+that the difference between the weight of the first position and the weight of the second position is at least as much as the difference between the weights of the second and third positions, etc. 
 \[ \forall i \in \{1,\ldots,n\} \;\; w_i - w_{i+1} \geq w_{i+1}-w_{i+2} \iff  w_i - 2 w_{i+1} + w_{i+2} \geq 0 \]
@@
 A number of works have dealt with the problem of reasoning with incompletely specified aggregation functions.
-In particular, when considering positional scoring rules, it is possible to derive dominance relations (akin to sthochastic dominance) that allow to eliminate some alternatives since they will be less preferred than another one for any instantiation of the weights \cite{Stein1994}.
+In particular, when considering positional scoring rules, it is possible to derive dominance relations (akin to stochastic dominance) that allow to eliminate some alternatives since they will be less preferred than another one for any instantiation of the weights \cite{Stein1994}.
 More recently the characterization of methods for aggregating the uncertainty over the scoring vectors has been studied in \cite{Viappiani2018}.
@@
 In this draft, we consider a setting where both the voters' preferences and the preferences of the chair about the voting rule are incomplete.
-We write the score as $s(x; v,w)$ to underline the depency of the score on the preference profile and on the weight vector.
+We write the score as $s(x; v,w)$ to underline the dependency of the score on the preference profile and on the weight vector.
 Let $s(x;v,w)$ denote the score of alternative $x$ in profile $\textbf{v}$ with weights $\textbf{w}$:
-\[ s(x;\textbf{v},\textbf{w}) = \sum_{i=1}^{m} w_{\rank_i(x)} \]
+\[ s(x;\textbf{v},\textbf{w}) = \sum_{i=1}^{n} w_{\rank_i(x)} \]
 
@@
  \item Max regret $\MR(x;\pprofile,W)$ is the worst-case loss of $x$.
-It is the loss occured by an adversarial selection of a complete profile $\profile$ extending $\pprofile$ and a selection of $\w \in W$ to maximize the loss between $x$ and the true winner under $\profile$ and $w$.
+It is the loss occurred by an adversarial selection of a complete profile $\profile$ extending $\pprofile$ and a selection of $\w \in W$ to maximize the loss between $x$ and the true winner under $\profile$ and $w$.
  \item Minimax regret $\MMR(\pprofile,W)$ is the minimum of max regret obtained when choosing $x^*$
@@
 In many cases the inner maximization can be made regardless of the outer max.
-Part of the optimization can be made voter-wise: for each of the agent,s we compute the extend the partial preference into a linear order that makes the gap between y and x as wide as possible.
+Part of the optimization can be made voter-wise: for each agent we extend the partial preference into a linear order that makes the gap between y and x as wide as possible.
 However, in some cases the choice of how to complete the profiles may depend on the choice of weights, therefore it may be quite complicated...  (need to use integer variables???)
@@
 In the case of convex sequences, the optimization can be done without integer variables.
-Let $\hat{v}_k$ be the linear order extending $p_k$ according to the procedure descibed in \cite{Lu2011}.
+Let $\hat{v}_k$ be the linear order extending $p_k$ according to the procedure described in \cite{Lu2011}.
 \begin{align*}
@@
 \end{align*}
-Therefore the pairwsie maximum regret can be computed with a linear program.
+Therefore the pairwise maximum regret can be computed with a linear program.
 
 \paragraph{Interactive Elicitation}
-Srtarting from some intial partial knowledge, our goal is to learn both the scoring rule function and the agents' preferences.
+Starting from some initial partial knowledge, our goal is to learn both the scoring rule function and the agents' preferences.
 While this is of course possible by doing one elicitation after another one, we propose an interleaved approach.
@@
 
-{\em Some ideas: decompose the regret into two components, one due to $\w$ and one due to $\pprofile$, and ask a question to the chair / or to one of the agens depending on which is highest}
+{\em Some ideas: decompose the regret into two components, one due to $\w$ and one due to $\pprofile$, and ask a question to the chair / or to one of the agents depending on which is highest}
 

### 2018-12-05 draft.tex
improved optimization section (plus small changes)

@@
 
+\DeclareMathOperator{\SCORE}{Score}
 \DeclareMathOperator{\PMR}{PMR}
@@
 \title{Robust Winner Determination and Simultaneous Elicitation of Scoring Rules and Preferences}
-\author{}
+%\author{}
 %\author{Paolo Viappiani} \affil{LIP6\\\email{paolo.viappiani@lip6.fr}}
 %\author{Olivier Cailloux} 
-%\author{Stefano Moretti}\affil{LAMSADE}
+%\author{Stefano Moretti}%\affil{LAMSADE}
+%\author{Beatrice Napolitano}\affil{LAMSADE}
 
@@
 \maketitle
-
-%$\preflarge, \pref, \ppreflarge, \ppref$
 % aggregate different opinions
 
-%Minimax regret
 %Given a full profile: use linear programming to maximize regret
@@
 %We argue that it is possible that the committee wants to precise some preferences about the aggregation.
-%We assume that obtaining information about them has a coast. 
-%We  therefore aim at asking as few questions as possible.
 In this draft we depart from the classic view by considering that both preferences and the social choice rule can be only partially specified.
@@
 %We consider that the committee wants to express preferences for some voting rules
-We provide a method for approximate winner determination and an incremental elicitation protocol based on minimax regret.
+In this draft we provide a method for approximate winner determination and an incremental elicitation protocol based on minimax regret.
 
-\section*{Background}
+\section{Background}
+
+{\bf We have to decide whether we want to focus only scoring rules, or on a larger class of rules based on a score.}
 
@@
 The set $(\pref_1,\ldots,\pref_n)$ is known in the social choice literature as the {\em preference  profile}.
-The profile is equivalently represented by $\textbf{v}=(v_1,\ldots,v_n)$ where $v_i(j)$ denotes the rank (position) of alternative $j$ in the preference order $\pref_i$. 
-With a little abuse of notation, we will use the term profile to refer to either $\textbf{v}$ or to the preference relations, depending on the context.
+The profile is equivalently represented by $\profile=(v_1,\ldots,v_n)$ where $v_i(j)$ denotes the rank (position) of alternative $j$ in the preference order $\pref_i$. 
+With a little abuse of notation, we will use the term profile to refer to either $\profile$ or to the preference relations, depending on the context.
 Let $V$ be the set of possible preference profiles (the cartesian product of $n$ linear orders).
@@
 %the score $s(a; v)$ of alternative $a$ is additive decomposable if it can be computed as $s(a; v) = \sum_{i} s(a; v_{i})$.
-In particular positional scoring rules attach weights to positions;
-an alternative obtains a score that depends on the rank obtained in each of the preference orders:
+In particular {\em positional scoring rules} attach weights to positions; an alternative obtains a score that depends on the rank obtained in each of the preference orders:
 
@@
 that $w_2>0.5$.
-A specific kind of preference may require the weights sequence to be convex, that means
-that the difference between the weight of the first position and the weight of the second position is at least as much as the difference between the weights of the second and third positions, etc. 
+A specific kind of preference may require the weight sequence to be convex, that means that the difference between the weight of the first position and the weight of the second position is at least as much as the difference between the weights of the second and third positions, etc.
 \[ \forall i \in \{1,\ldots,n\} \;\; w_i - w_{i+1} \geq w_{i+1}-w_{i+2} \iff  w_i - 2 w_{i+1} + w_{i+2} \geq 0 \]
@@
 
-\section*{Related works}
+\section{Related works}
 
@@
 The computation of max regret is facilitated by the fact the score is decomposable.
+
 % We are given  $\ppref_i $,  a partial preference.
@@
 
-\section*{Incomplete profiles and partial information about the scoring rule}
+\section{Incomplete profiles and partial information about the scoring rule}
+In this draft, we consider a setting where both the voters' preferences and the preferences of the chair about the voting rule are incomplete.
+Let $s(x;\profile,\w)$ denote the score of alternative $x$ in profile $\profile$ with weights $\w$.
+Assuming positional scoring rules, the score of alternative $x$ is the sum of the points obtained 
+\[ s(x;\profile,\w) = \sum_{i=1}^{n} w_{\rank_i(x)}. \]
+We write the score as $s(x;\profile,\textbf{w})$ to underline the dependency of the score on the preference profile and on the weight vector.
 
-{\bf Perhaps it could me made more general considering not only scoring rules, but all rules based on a score (as in Boutilier's paper)}
-
-In this draft, we consider a setting where both the voters' preferences and the preferences of the chair about the voting rule are incomplete.
-We write the score as $s(x; v,w)$ to underline the dependency of the score on the preference profile and on the weight vector.
-Let $s(x;v,w)$ denote the score of alternative $x$ in profile $\textbf{v}$ with weights $\textbf{w}$:
-\[ s(x;\textbf{v},\textbf{w}) = \sum_{i=1}^{n} w_{\rank_i(x)} \]
-
-%By using decomposition, we can compute the vote-wise regret...
+The weights of a scoring rule can model different preferences for the committee; However in general it can be difficult to set the weights in an appropriate way.
 
@@
 The maximum regret is considered by assuming an adversary can choose both 1) to extend the partial profile into a complete profile 2) can instantiate the weights choosing among any feasible weight vector in $W$.
-
-%We consider the pairwise max regret of alternative $x$  against alternative $y$ assuming that the weight vector belongs to $W$:
 
@@
 
-\paragraph{Computation of minimax regret}
+\subsection{Computation of minimax regret}
+{\bf \em TODO: reason about the optimization and complete section}
 
-We will adapt the reasoning from \cite{Lu2011} combined with linear programming optimization.
+In order to compute pairwise maximum regret and therefore minimax regret, we adapt the reasoning from \cite{Lu2011} so that we decompose the PMR into the contributions that is associated to each agent.
+The settings is however more challenging due to the presence of uncertainty in the weights.
 
+Let $s(x; v_j,\w)=w_{v_j(x)}$ be the number of points $x$ obtains in the ranking $v_j$, that is the weight of the position $v_j(x)$.
 Exploiting the decomposition of the score in terms of votes we cam rewrite $\PMR$ as follows:
-
 \begin{align*}
@@
 \end{align*}
+%Computing PMR may be challenging since in principle the inner maximization can depend on the outer maximization.
+Let $A^+$ be the set of agents for which we know that $y$ is preferred to $x$ (positive contribution to pairwise regret), $A^+$ 
+be the set of agents for wich we  know that $x$ is preferred to $y$ (negative contribution) and $A^?$ the remaining case, where the preference between $x$ and $y$ is not known.
+Consider how the adversary will complete the partial orders:
+\begin{itemize}
+ \item $j \in A^+$: If we know that agent $j$ prefers $y$ to $x$ then the adversary will complete the partial order of agent $j$ by placing as many as possible alternatives between $y$ and $x$.
+ The way the partial order is completed in independent on the choice of the weights.
 
-{\bf \em This is just sketchy TODO: reason about the optimization and complete section}
+ \item $j \in A^-$: If we know that agent $j$ prefers $x$ to $y$ then the adversary will place as few as possible alternatives between $x$ and $y$.
+ There is some dependecy between the weights and the completion of the partial order.
+ This concerns the set of alternatives $U$ that are currently incomparable with $x$ and $y$.
 
-In many cases the inner maximization can be made regardless of the outer max.
-Part of the optimization can be made voter-wise: for each agent we extend the partial preference into a linear order that makes the gap between y and x as wide as possible.
-However, in some cases the choice of how to complete the profiles may depend on the choice of weights, therefore it may be quite complicated...  (need to use integer variables???)
-\medskip
- {\em Explain why convex sequences do not pose any problem}
-In the case of convex sequences, the optimization can be done without integer variables.
-Let $\hat{v}_k$ be the linear order extending $p_k$ according to the procedure described in \cite{Lu2011}.
+ \item $j \in A^?$: If we do not know whether $x$ or $y$ is preferred by agent $j$ then the adversary will place $y$ before $x$ in the linear order and this case reduce to the first case; therefore also in this case the completion of the partial order can be done independently of the choice of $w$.
+\end{itemize}
+
+Let $\hat{v}_k$ be the linear order extending $p_k$ according to the above procedure (described in \cite{Lu2011}).
+
+Then PMR can be written as follows:
+\[ \PMR(x,y; \pprofile, W) = \max_{\w \in W} \Big \{ \max_{v_j \in C(\succ_j^p)} [w_{v_j(y)} - w_{v_j(x)}]  + \sum_{j \in A^+, j \in A^?} [w_{\hat{v}_j(y)} - w_{\hat{v}_j(x)}] \Big \} \]
+
+\begin{itemize}
+ \item Case of convex sequences:
+  %{\em Explain why convex sequences do not pose any problem}
+In the case of convex sequences, the optimization can be done without integer variables, since the case $A^-$ can be easily dealt with, and alternatives in $U$ can be indifferently be placed either to the top or to the bottom.
 \begin{align*}
-\max_{\w \in W} \sum_{j=1}^{n}  [w_{\hat{v}_j(y)} - w_{\hat{v}_j(x)}]
+\max_{\w} & \sum_{j=1}^{n}  [w_{\hat{v}_j(y)} - w_{\hat{v}_j(x)}] \\
+\text{s.t.} & \w \in W
 \end{align*}
+The space of feasible weights $W$ is encoded with linear constraints.
 Therefore the pairwise maximum regret can be computed with a linear program.
 
-\paragraph{Interactive Elicitation}
+ \item General case:
+{\bf \em TODO: still have to find out exactly how to do it}
+We introduce a set integer variables $I^i$, one for each position $i$.
+ Let $U^j$ be, for the agents in $A^-$, the alternatives that, in the partial order $\succ^p_j$ of some agent $j \in A^-$, are incomparable with $x$ and $y$.
+ \[ \sum_{l=1}^n I^j_l w_l \]
+  Variable $I^j$ associated with the constraint $0 \leq I \leq |U^j|$.
+
+  Use linearization techniques to handle the multiplication...
+\end{itemize}
+
+\subsection{Interactive Elicitation}
 Starting from some initial partial knowledge, our goal is to learn both the scoring rule function and the agents' preferences.
-While this is of course possible by doing one elicitation after another one, we propose an interleaved approach.
-We adopt an interactive  protocol for simultaneously eliciting the preferences of the chair about the voting rule and the voters' preferences about the alternatives.
+While it is of course possible doing full elicitation of the weights and afterwards elicit the agents' preferences (or the other way around) we propose an interleaved approach.
+In our interactive  protocol for simultaneously eliciting the preferences of the chair about the voting rule and the voters' preferences about the alternatives.
 Indeed, it can be beneficial to interleave questions asked to the committee and questions asked to voters, depending on which is estimated to be more informative.
 
-Answers given by the committee about the scoring rule refines our knowledge of the weights $w_1,\ldots,w_n$.
-Answers given by one of the agents refine our knowledge about the agent's preferences
+Answers given by the committee about the scoring rule refine our knowledge of the weights $w_1,\ldots,w_n$, while
+answers given by one of the agents refine our knowledge about the agent's preferences.
 
@@
 Type of questions that we can ask to the chair:
-bound queries, comparison queries.
+bound queries (Is this alternative among your top-k most preferred items?), comparison queries (do you prefer alternative x or alternative y?).
 
@@
 
+\paragraph{Query methods}
+
 {\em Some ideas: decompose the regret into two components, one due to $\w$ and one due to $\pprofile$, and ask a question to the chair / or to one of the agents depending on which is highest}
+
+%We consider strategies of the following form
+%{\em if} condition {\em then} ask comparison query {\em else} ask a committee query
+%Define a score associated to each potential query that we may ask.
+
+\begin{itemize}
+\item Current solution strategy:
+%Assume $x$ is the minimax regret optimal alternative $y$ the adversarial choice
+
+\item Non-iterleaved regret method:
+
+ \item One possibility is to consider the MMR {\em a posteriori}.
+Assume that the different answers to a query induce the possible sets to be $(\pprofile_1,W_1)$ and $(\pprofile_2,W_2)$, then the score according to worst-case maximum regret is:
+\[\SCORE(x)= \max_{i=1,2} \MMR(\pprofile_i,W_i) \]
+In this case, the query with least value is chosen.
+\end{itemize}
+
+\section{Empirical Evaluation}
+
+We evaluate the proposed method using the following simulated protocol.
+
+\begin{itemize}
+ \item Randomly generate the true preferences of the users (i.e. the linear orders) and the weights associated with the committee's preferences on the scoring rule
+ \item For each of the elicitation strategy, simulate the elicitation by asking the queries selected by the strategy.
+
+ \item Compare performance with respect to decrement in max regret, real loss
+\end{itemize}
+
+Test with different values of $m$ (number of alternatives) and $n$ (number of agents).
+
+Test with different population sizes, different number of alternatives, etc.
+
+Make one test assuming convex sequences of weights, and others without this assumption.
+
+Comparison between our interleaved strategy and a strategy, still based on minimax regret  but that is not interleaved; also compare to some heuristic baselines.
 

### 2018-12-05 draft.tex
small changes

@@
 \end{align*}
-The space of feasible weights $W$ is encoded with linear constraints.
+The space of feasible weights $W$ is encoded with linear constraints that model the preferences of the committee.
 Therefore the pairwise maximum regret can be computed with a linear program.
@@
 \begin{itemize}
-\item Current solution strategy:
-%Assume $x$ is the minimax regret optimal alternative $y$ the adversarial choice
+\item Current solution strategy: consider the solution of the minimax regret game, 
+ $(x,y,w^{a},\profile^{a})$, where $x$ is the minimax regret optimal alternative, $y$ the adversarial choice, $w^{a}$ the weights, and $\profile^{a}$ the profile completed by the adversary.
 
-\item Non-iterleaved regret method:
+\item Non-iterleaved regret method: comparison with a method based on minimax regret, but not interleaved.
 

### 2018-12-07 draft.tex
Added sections 3.1.1 and 3.1.2

@@
 \usepackage{mathrsfs}
+\usepackage{algorithm, algpseudocode}
 
@@
 \DeclareMathOperator{\MMR}{MMR}
+
+\algrenewcommand\algorithmicrequire{\textbf{Input:}}
+\algrenewcommand\algorithmicensure{\textbf{Output:}}
 
@@
 
+\subsubsection{Minimax Computation under Convex Assumption \cite{Lu2011}}
+The goal is to choose as a winner the alternative $x^*$ whose worst case loss is minimal under all possible realizations of the full profile and all possible choices of weights.
+Assume hereinafter the selected weights sequence $\w \in W$ to be convex.
+In order to compute the minimal max regret $\MMR(\pprofile)$ under partial profile $\pprofile$ we need to compute the pairwise max regret between all pairs of alternatives $(x,y)$, where $x$ is a proposed winner and $y$ is the ``adversary'' alternative.
+Indeed, the construction of $\PMR(x,y,\pprofile,\w)$ can be viewed as an adversary's attempt to maximize the regret of choosing $x$ instead of $y$.
+For doing this, he can choose a completion $\profile_k \in C(\pprofile_k)$ of the partial profile and a (feasible) scoring vector $\w$ that maximize the contribution of the voter $k$ to $\PMR(x,y,\pprofile,\w)$.
+Let us now analyze how it could be done depending on the relation between alternatives $x$ and $y$ in $\pprofile_k$.
+\begin{itemize}
+	\item $x \succ_k^\pprofile y$
+	\newline If we know $x$ is preferred to $y$ and we choose $x$ as a winner, $\pprofile_k$ contribution to $\PMR(x,y,\pprofile,\w)$ must be negative.
+In this situation, our adversary can only try to minimize this advantage by minimizing the positional gap between the two alternatives.
+To achieve that, he can arbitrary place all the alternatives preferred to $x$ above $x$, together with all the ones with unknown relation to $x$.
+Moreover, he can place all the alternatives less preferred to $x$ and with unknown relation to $y$ below $y$.
+We can summarize it for each $q \in A$ as follows:
+	\begin{align*}
+	q \succ_k^\pprofile x \vee q \ ?_k^\pprofile \ x \ & \Rightarrow \ \uparrow_x \\
+	x \succ_k^\pprofile q \wedge q \ ?_k^\pprofile \ y \ & \Rightarrow \ \downarrow_y \\
+	x \succ_k^\pprofile q \succ_k^\pprofile y \ & \Rightarrow \ \text{in between} \\
+	\end{align*}
+	It is worth noting that when the relation between $q$ and $x$ is not known in the partial profile, the adversary takes advantage by placing $q$ above $x$ only under the assumption of convex weight sequences.
+	\item $y \succ_k^\pprofile x$
+	\newline If $y$ is preferred to $x$ the construction proceeds similarly to the previous case, but now the adversary takes advantage by maximizing the gap between $x$ and $y$ placing as much alternatives as he can between the two.
+We can summarize the procedure for each $q \in A$ as follows:
+	\begin{align*}
+	q \succ_k^\pprofile y \ & \Rightarrow \ \uparrow_y \\
+	x \succ_k^\pprofile q \ & \Rightarrow \ \downarrow_x \\
+	(y \succ_k^\pprofile q \vee y \ ?_k^\pprofile \ q) \wedge (q \succ_k^\pprofile x \vee q \ ?_k^\pprofile \ x) \ & \Rightarrow \ \text{in between} \\
+	\end{align*}
+	\item $x \ ?_k^\pprofile \ y$
+	\newline If the partial profile $\pprofile_k$ does not specify the relation between $x$ and $y$, the advantage is maximized by ordering $y$ over $x$ and maximizing the gap between them following the procedure for the case $y \succ_k^\pprofile x$.
+\end{itemize}
+
+\subsubsection{Dropping the Convex Assumption}
+What if the sequence of weights is not convex?
+When $y \succ_k^\pprofile x$ or $x \ ?_k^\pprofile \ y$ weights do not influence the arbitrary placement of alternatives.
+Please remind we are working under the assumption that weights constitute a monotonic non-increasing sequence.
+Thus, there is no way for the adversary to take advantage from the weights distribution in order to increase the gap between $y$ and $x$ besides placing as much alternatives as he can between the two.
+The only case in which weights can influence the positional gap between $x$ and $y$ is when $x \succ_k^\pprofile y$ and $q \ ?_k^\pprofile \ x$.
+For convex sequences we place such alternatives $q$ above $x$, but it is not obvious that this is the best option for other sequences.
+For example, suppose $x$ and $y$ are ranked respectively in first and second position in the partial profile and we wonder where to place an alternative $q$ with unknown relation to $x$ (and thus to $y$).
+Suppose also that in the weight sequence the distance between the first and second positions is much lower than the one between the second and the third ones.
+In this case, placing $q$ above $x$ does not minimize the gap between $x$ and $y$ but we want, instead, to place $q$ below $y$.
+\newline Since weights are not totally specified, one solution could rely on choosing a completion for them so as to have a convex sequence and then reason under the convex assumption as described before.
+Nevertheless, this is not always possible because of the constraints existence.
+Indeed, may be the case that no feasible scoring vector forms a convex sequence.
+In this case we need to analyze the particular sequence of weights in order to decide how to maximize the adversary advantage.
+Before going into details, let us define $A$ as the set of alternatives (if any) preferred to $x$, $B$ as the set of alternatives preferred to $y$ but not to $x$, and $U$ the set of those with unknown relation to both $x$ and $y$.
+The idea is to determine the positions that minimize $x$'s advantage over $y$ and then place some of the alternatives in $U$ above $x$ and some below $y$ in order to get that desired ranking.
+Since we cannot change the order of the alternatives in the set $B$ we know that $x$ and $y$ are separated exactly by $|B|$ positions (the adversary would not take any advantage by adding alternatives between them).
+So, starting from the position of $x$ in the partial completion of $\pprofile_k$ computed so far ($\hat{\profile}_k$), we find the two positions separated by $|B|$ alternatives whose weights difference is the lowest.
+Note that we can only add $|U|$ alternatives so we can check only until the position $\hat{\profile}_k(x)+|U|$.
+Algorithm \ref{alg:splittingU} shows the procedure described.
+
+It is easy to see that we check at most $|U|$ positions.
+In the worst case the size of $U$ is equal to $m-2$, thus the procedure can be computed in $O(m)$ time.
+This cost does not affect the minimax regret computation time complexity that remains $O(nm^3)$.
+
+\begin{algorithm}[h] 
+	\caption{Placing alternatives in $U$ without Convex Assumption}
+	\label{alg:splittingU} 
+	\begin{algorithmic}
+		\Require $x$, $y$, $\hat{\profile}_k$, $\w$, $U$, $B$
+		\Ensure $\profile_k \in C(\pprofile)$
+		\Statex
+		\State $ j \gets 0$;
+		\State $ i \gets \hat{\profile}_k(x)$;
+		\State $ \mathit{posmin} \gets i$;
+		\State $ \mathit{min} \gets \w(i) - \w(i+1+|B|)$;
+		\While {$( j \leq |U| )$}
+		\If{ $(\w(i+j)-\w(i+1+|B|+j) < \mathit{min})$ }
+		\State $ \mathit{min} \gets \w(i+j) - \w(i+1+|B|+j)$;
+		\State $ \mathit{posmin} \gets i+j$;
+		\EndIf
+		\EndWhile
+
+		\State $U_{\mathit{abovex}} \gets (i-\mathit{posmin}) \text{ alternatives} \in U $;
+		\State $U_{\mathit{belowy}} \gets U \setminus U_{\mathit{above}}$;
+		\Statex
+		\State $\profile_k \gets place(\pprofile_k,U_{\mathit{abovex}},U_{\mathit{belowy}})$;
+		\Statex \Return $\profile_k$
+
+	\end{algorithmic}
+\end{algorithm}
+
+\subsubsection{Nondecomposable rules} 
+TODO ?
+
+\pagebreak
 \subsection{Interactive Elicitation}

### 2018-12-11 draft.tex
more organized draft assuming convex weihts

@@
 
-{\bf We have to decide whether we want to focus only scoring rules, or on a larger class of rules based on a score.}
-
 We assume that there is a set $A$ of $m$ alternatives and $n$ agents (voters); each agent is associated to a preference order.
@@
 
-A social choice function $f : V \rightarrow A$ associates a profile with one winner (or multiple winners in some cases).
-Among the many possible social choice functions, we consider those rules that are based on a numerical score that is decomposable voter-wise.
-%the score $s(a; v)$ of alternative $a$ is additive decomposable if it can be computed as $s(a; v) = \sum_{i} s(a; v_{i})$.
-In particular {\em positional scoring rules} attach weights to positions; an alternative obtains a score that depends on the rank obtained in each of the preference orders:
+A social choice function $f : V \rightarrow 2^A$ associates a profile with a set of winners.
+Among the many possible social choice functions, we consider {\em positional scoring rules}, which attach weights to positions; an alternative obtains a score that depends on the rank obtained in each of the preference orders:
 
-\[ s(x) = \sum_{i=1}^{n} w_{v_i(x)}. \]
+\[ s(x; \profile, \w) = \sum_{i=1}^{n} w_{v_i(x)}. \]
 
-where the vector $(w_1,\ldots,w_m)$ is called the scoring vector;
-%A positional scoring rule attach weights to positions; 
- it is usually assumed that the weights constitute a monotonic sequence: $w_{1} \geq w_{2} \geq \ldots \geq w_{m}$.
+where the vector $(w_1,\ldots,w_m)$ is called the scoring vector. We assume that the weights constitute a monotonic sequence: $w_{1} \geq w_{2} \geq \ldots \geq w_{m}$.
 
@@
 We want to reason about partial preference information.
-A partial preference  is encoded by a partial order $\ppref_k$  of voter $k$;
-we assume that preference information is truthful, i.e. $a \ppref_k b \implies a \pref_k b$.
+A partial preference  is encoded by a partial order $\ppref_i$  of voter $i$;
+we assume that preference information is truthful, i.e. $a \ppref_i b \implies a \pref_i b$.
 
-A completion of $\ppref_k$ is any linear order $\pref_k$ that extends $\ppref_k$.
-Let $C(\ppref_k)$ be the set of completions of $\ppref_k$, that is the set of all complete rankings that extend $\ppref_k$.
+A completion of $\ppref_i$ is any linear order $\pref_i$ that extends $\ppref_i$.
+Let $C(\ppref_i)$ be the set of completions of $\ppref_i$, that is the set of all complete rankings that extend $\ppref_i$.
 An incomplete profile is a set of partial votes %$\textbf{p}=(p_1,\ldots,p_n)$.
@@
 \medskip
-We also assume that the weights of the scoring rules are only partially specified.
-We use $W$ to denote the set of feasible weight vector.
-Without loss of generality, we assume $w_1=0$ and $w_m=0$.
+We also assume that the weights of the scoring rule are only partially specified.
+Without loss of generality, we assume $w_1=1$ and $w_m=0$.
 The preferences of the chair are encoded with linear constraints, for instance one may state
 that $w_2>0.5$.
-A specific kind of preference may require the weight sequence to be convex, that means that the difference between the weight of the first position and the weight of the second position is at least as much as the difference between the weights of the second and third positions, etc.
+We assume the weight sequence to be convex, that means that the difference between the weight of the first position and the weight of the second position is at least as much as the difference between the weights of the second and third positions, etc.
 \[ \forall i \in \{1,\ldots,n\} \;\; w_i - w_{i+1} \geq w_{i+1}-w_{i+2} \iff  w_i - 2 w_{i+1} + w_{i+2} \geq 0 \]
 This is a constraint often used when aggregating rankings in sport competitions.
+We use $\mathcal{W}$ to denote the set of convex weight vectors.
 
@@
 
-\section{Incomplete profiles and partial information about the scoring rule}
+\section{Minimax regret under partial profile and weight information}
 In this draft, we consider a setting where both the voters' preferences and the preferences of the chair about the voting rule are incomplete.
-Let $s(x;\profile,\w)$ denote the score of alternative $x$ in profile $\profile$ with weights $\w$.
-Assuming positional scoring rules, the score of alternative $x$ is the sum of the points obtained 
-\[ s(x;\profile,\w) = \sum_{i=1}^{n} w_{\rank_i(x)}. \]
-We write the score as $s(x;\profile,\textbf{w})$ to underline the dependency of the score on the preference profile and on the weight vector.
 
-The weights of a scoring rule can model different preferences for the committee; However in general it can be difficult to set the weights in an appropriate way.
+The weights of a scoring rule can model different preferences for the committee; however in general it can be difficult to set the weights in an appropriate way.
 
@@
 We propose to use minimax regret to identify the alternative to declare as the approximate winner, extending the work of \cite{Lu2011} to the simultaneous presence of uncertainty in the agents' preferences and uncertainty in the weights.
-The maximum regret is considered by assuming an adversary can choose both 1) to extend the partial profile into a complete profile 2) can instantiate the weights choosing among any feasible weight vector in $W$.
+The maximum regret is considered by assuming an adversary can choose both 1) to extend the partial profile into a complete profile 2) can instantiate the weights choosing among any feasible weight vector in $W \subseteq \mathcal{W}$.
 
@@
 
+We want to design a questioning strategy to minimize the worst regret in the long run.
+A questioning strategy indicates, given a partial profile and a set of feasible weights, which question to ask next.
+A question is either a query to the voter $i$ about her preference relation $\succ_i$ or a query to the committee about the feasible weights.
+
+In order to design this strategy we first evaluate how to compute the current regret.
+
 \subsection{Computation of minimax regret}
-{\bf \em TODO: reason about the optimization and complete section}
 
-In order to compute pairwise maximum regret and therefore minimax regret, we adapt the reasoning from \cite{Lu2011} so that we decompose the PMR into the contributions that is associated to each agent.
+In order to compute pairwise maximum regret and therefore minimax regret, we adapt the reasoning from \cite{Lu2011} so that we decompose the $\PMR$ into the contributions that is associated to each agent.
 The settings is however more challenging due to the presence of uncertainty in the weights.
@@
 Let $s(x; v_j,\w)=w_{v_j(x)}$ be the number of points $x$ obtains in the ranking $v_j$, that is the weight of the position $v_j(x)$.
-Exploiting the decomposition of the score in terms of votes we cam rewrite $\PMR$ as follows:
+Exploiting the decomposition of the score in terms of votes we can rewrite $\PMR$ as follows:
 \begin{align*}
@@
 %Computing PMR may be challenging since in principle the inner maximization can depend on the outer maximization.
-Let $A^+$ be the set of agents for which we know that $y$ is preferred to $x$ (positive contribution to pairwise regret), $A^+$ 
-be the set of agents for wich we  know that $x$ is preferred to $y$ (negative contribution) and $A^?$ the remaining case, where the preference between $x$ and $y$ is not known.
+Let $A^+=\{ i \ | \ y \succ_i^\pprofile x\}$ be the set of agents for which we know that $y$ is preferred to $x$ (positive contribution to pairwise regret), $A^-=\{ i \ | \ x \succ_i^\pprofile y\}$ 
+be the set of agents for wich we  know that $x$ is preferred to $y$ (negative contribution) and $A^?=\{ i \ | \ x \ T_i^\pprofile \ y\}$ the remaining case, where the preference between $x$ and $y$ is not known.
 Consider how the adversary will complete the partial orders:
 \begin{itemize}
- \item $j \in A^+$: If we know that agent $j$ prefers $y$ to $x$ then the adversary will complete the partial order of agent $j$ by placing as many as possible alternatives between $y$ and $x$.
- The way the partial order is completed in independent on the choice of the weights.
+ \item $j \in A^+$: If we know that agent $j$ prefers $y$ to $x$ then the adversary will complete the partial order of agent $j$ by placing as many alternatives as possible between $y$ and $x$.
+ The way the partial order is completed does not depend on the weights.
 
- \item $j \in A^-$: If we know that agent $j$ prefers $x$ to $y$ then the adversary will place as few as possible alternatives between $x$ and $y$.
- There is some dependecy between the weights and the completion of the partial order.
- This concerns the set of alternatives $U$ that are currently incomparable with $x$ and $y$.
+ \item $j \in A^?$: If we do not know whether $x$ or $y$ is preferred by agent $j$ then the adversary will place $y$ before $x$ in the linear order and this case reduce to the first one; therefore also in this case the completion of the partial order can be done independently of the choice of $w$.
 
- \item $j \in A^?$: If we do not know whether $x$ or $y$ is preferred by agent $j$ then the adversary will place $y$ before $x$ in the linear order and this case reduce to the first case; therefore also in this case the completion of the partial order can be done independently of the choice of $w$.
+ \item $j \in A^-$: If we know that agent $j$ prefers $x$ to $y$ then the adversary will place as few alternatives as possible between $x$ and $y$.
+ We define $U$ as the set of alternatives that are incomparable with $x$ and $y$ according to $\ppref_i$.
+Since weights are assumed to be convex, the adversary will place all alternatives in $U$ as better than $x$.
 \end{itemize}
 
-Let $\hat{v}_k$ be the linear order extending $p_k$ according to the above procedure (described in \cite{Lu2011}).
-
-Then PMR can be written as follows:
-\[ \PMR(x,y; \pprofile, W) = \max_{\w \in W} \Big \{ \max_{v_j \in C(\succ_j^p)} [w_{v_j(y)} - w_{v_j(x)}]  + \sum_{j \in A^+, j \in A^?} [w_{\hat{v}_j(y)} - w_{\hat{v}_j(x)}] \Big \} \]
-
-\begin{itemize}
- \item Case of convex sequences:
-  %{\em Explain why convex sequences do not pose any problem}
-In the case of convex sequences, the optimization can be done without integer variables, since the case $A^-$ can be easily dealt with, and alternatives in $U$ can be indifferently be placed either to the top or to the bottom.
-\begin{align*}
-\max_{\w} & \sum_{j=1}^{n}  [w_{\hat{v}_j(y)} - w_{\hat{v}_j(x)}] \\
-\text{s.t.} & \w \in W
-\end{align*}
 The space of feasible weights $W$ is encoded with linear constraints that model the preferences of the committee.
@@
 
- \item General case:
-{\bf \em TODO: still have to find out exactly how to do it}
-We introduce a set integer variables $I^i$, one for each position $i$.
- Let $U^j$ be, for the agents in $A^-$, the alternatives that, in the partial order $\succ^p_j$ of some agent $j \in A^-$, are incomparable with $x$ and $y$.
- \[ \sum_{l=1}^n I^j_l w_l \]
-  Variable $I^j$ associated with the constraint $0 \leq I \leq |U^j|$.
-
-  Use linearization techniques to handle the multiplication...
-\end{itemize}
-
-\subsubsection{Minimax Computation under Convex Assumption \cite{Lu2011}}
-The goal is to choose as a winner the alternative $x^*$ whose worst case loss is minimal under all possible realizations of the full profile and all possible choices of weights.
-Assume hereinafter the selected weights sequence $\w \in W$ to be convex.
-In order to compute the minimal max regret $\MMR(\pprofile)$ under partial profile $\pprofile$ we need to compute the pairwise max regret between all pairs of alternatives $(x,y)$, where $x$ is a proposed winner and $y$ is the ``adversary'' alternative.
-Indeed, the construction of $\PMR(x,y,\pprofile,\w)$ can be viewed as an adversary's attempt to maximize the regret of choosing $x$ instead of $y$.
-For doing this, he can choose a completion $\profile_k \in C(\pprofile_k)$ of the partial profile and a (feasible) scoring vector $\w$ that maximize the contribution of the voter $k$ to $\PMR(x,y,\pprofile,\w)$.
-Let us now analyze how it could be done depending on the relation between alternatives $x$ and $y$ in $\pprofile_k$.
-\begin{itemize}
-	\item $x \succ_k^\pprofile y$
-	\newline If we know $x$ is preferred to $y$ and we choose $x$ as a winner, $\pprofile_k$ contribution to $\PMR(x,y,\pprofile,\w)$ must be negative.
-In this situation, our adversary can only try to minimize this advantage by minimizing the positional gap between the two alternatives.
-To achieve that, he can arbitrary place all the alternatives preferred to $x$ above $x$, together with all the ones with unknown relation to $x$.
-Moreover, he can place all the alternatives less preferred to $x$ and with unknown relation to $y$ below $y$.
-We can summarize it for each $q \in A$ as follows:
-	\begin{align*}
-	q \succ_k^\pprofile x \vee q \ ?_k^\pprofile \ x \ & \Rightarrow \ \uparrow_x \\
-	x \succ_k^\pprofile q \wedge q \ ?_k^\pprofile \ y \ & \Rightarrow \ \downarrow_y \\
-	x \succ_k^\pprofile q \succ_k^\pprofile y \ & \Rightarrow \ \text{in between} \\
-	\end{align*}
-	It is worth noting that when the relation between $q$ and $x$ is not known in the partial profile, the adversary takes advantage by placing $q$ above $x$ only under the assumption of convex weight sequences.
-	\item $y \succ_k^\pprofile x$
-	\newline If $y$ is preferred to $x$ the construction proceeds similarly to the previous case, but now the adversary takes advantage by maximizing the gap between $x$ and $y$ placing as much alternatives as he can between the two.
-We can summarize the procedure for each $q \in A$ as follows:
-	\begin{align*}
-	q \succ_k^\pprofile y \ & \Rightarrow \ \uparrow_y \\
-	x \succ_k^\pprofile q \ & \Rightarrow \ \downarrow_x \\
-	(y \succ_k^\pprofile q \vee y \ ?_k^\pprofile \ q) \wedge (q \succ_k^\pprofile x \vee q \ ?_k^\pprofile \ x) \ & \Rightarrow \ \text{in between} \\
-	\end{align*}
-	\item $x \ ?_k^\pprofile \ y$
-	\newline If the partial profile $\pprofile_k$ does not specify the relation between $x$ and $y$, the advantage is maximized by ordering $y$ over $x$ and maximizing the gap between them following the procedure for the case $y \succ_k^\pprofile x$.
-\end{itemize}
-
-\subsubsection{Dropping the Convex Assumption}
-What if the sequence of weights is not convex?
-When $y \succ_k^\pprofile x$ or $x \ ?_k^\pprofile \ y$ weights do not influence the arbitrary placement of alternatives.
-Please remind we are working under the assumption that weights constitute a monotonic non-increasing sequence.
-Thus, there is no way for the adversary to take advantage from the weights distribution in order to increase the gap between $y$ and $x$ besides placing as much alternatives as he can between the two.
-The only case in which weights can influence the positional gap between $x$ and $y$ is when $x \succ_k^\pprofile y$ and $q \ ?_k^\pprofile \ x$.
-For convex sequences we place such alternatives $q$ above $x$, but it is not obvious that this is the best option for other sequences.
-For example, suppose $x$ and $y$ are ranked respectively in first and second position in the partial profile and we wonder where to place an alternative $q$ with unknown relation to $x$ (and thus to $y$).
-Suppose also that in the weight sequence the distance between the first and second positions is much lower than the one between the second and the third ones.
-In this case, placing $q$ above $x$ does not minimize the gap between $x$ and $y$ but we want, instead, to place $q$ below $y$.
-\newline Since weights are not totally specified, one solution could rely on choosing a completion for them so as to have a convex sequence and then reason under the convex assumption as described before.
-Nevertheless, this is not always possible because of the constraints existence.
-Indeed, may be the case that no feasible scoring vector forms a convex sequence.
-In this case we need to analyze the particular sequence of weights in order to decide how to maximize the adversary advantage.
-Before going into details, let us define $A$ as the set of alternatives (if any) preferred to $x$, $B$ as the set of alternatives preferred to $y$ but not to $x$, and $U$ the set of those with unknown relation to both $x$ and $y$.
-The idea is to determine the positions that minimize $x$'s advantage over $y$ and then place some of the alternatives in $U$ above $x$ and some below $y$ in order to get that desired ranking.
-Since we cannot change the order of the alternatives in the set $B$ we know that $x$ and $y$ are separated exactly by $|B|$ positions (the adversary would not take any advantage by adding alternatives between them).
-So, starting from the position of $x$ in the partial completion of $\pprofile_k$ computed so far ($\hat{\profile}_k$), we find the two positions separated by $|B|$ alternatives whose weights difference is the lowest.
-Note that we can only add $|U|$ alternatives so we can check only until the position $\hat{\profile}_k(x)+|U|$.
-Algorithm \ref{alg:splittingU} shows the procedure described.
-
-It is easy to see that we check at most $|U|$ positions.
-In the worst case the size of $U$ is equal to $m-2$, thus the procedure can be computed in $O(m)$ time.
-This cost does not affect the minimax regret computation time complexity that remains $O(nm^3)$.
-
-\begin{algorithm}[h] 
-	\caption{Placing alternatives in $U$ without Convex Assumption}
-	\label{alg:splittingU} 
-	\begin{algorithmic}
-		\Require $x$, $y$, $\hat{\profile}_k$, $\w$, $U$, $B$
-		\Ensure $\profile_k \in C(\pprofile)$
-		\Statex
-		\State $ j \gets 0$;
-		\State $ i \gets \hat{\profile}_k(x)$;
-		\State $ \mathit{posmin} \gets i$;
-		\State $ \mathit{min} \gets \w(i) - \w(i+1+|B|)$;
-		\While {$( j \leq |U| )$}
-		\If{ $(\w(i+j)-\w(i+1+|B|+j) < \mathit{min})$ }
-		\State $ \mathit{min} \gets \w(i+j) - \w(i+1+|B|+j)$;
-		\State $ \mathit{posmin} \gets i+j$;
-		\EndIf
-		\EndWhile
-
-		\State $U_{\mathit{abovex}} \gets (i-\mathit{posmin}) \text{ alternatives} \in U $;
-		\State $U_{\mathit{belowy}} \gets U \setminus U_{\mathit{above}}$;
-		\Statex
-		\State $\profile_k \gets place(\pprofile_k,U_{\mathit{abovex}},U_{\mathit{belowy}})$;
-		\Statex \Return $\profile_k$
-
-	\end{algorithmic}
-\end{algorithm}
-
-\subsubsection{Nondecomposable rules} 
-TODO ?
-
-\pagebreak
-\subsection{Interactive Elicitation}
+\section{Interactive Elicitation}
 Starting from some initial partial knowledge, our goal is to learn both the scoring rule function and the agents' preferences.
@@
 
-\begin{itemize}
-\item At each step we need to decide whether we want to ask a question to the committee or to one of the agents (and to which agent in particular).
+At each step we need to decide whether we want to ask a question to the committee or to one of the agents (and to which agent in particular).
+We can ask comparison queries to the agents and questions comparing the differences of weights to the committee.
 
-\item We can consider different types of questions: asking to compare a pair of alternatives, asking about top-k alternatives.
-
-Type of questions that we can ask to the chair:
-bound queries (Is this alternative among your top-k most preferred items?), comparison queries (do you prefer alternative x or alternative y?).
-
-\item In the experiments we want to compare the interleaved approach with a baseline challenger, a method  that elicits the preferences of the voters first and then the voting rule (or the other way around)
-\end{itemize}
+In the experiments we want to compare the interleaved approach with a baseline challenger, a method  that elicits the preferences of the voters first and then the voting rule (or the other way around)
 
@@
 
+\pagebreak
+\appendix
+\section{Minimax Computation under Convex Assumption \cite{Lu2011}}
+The goal is to choose as a winner the alternative $x^*$ whose worst case loss is minimal under all possible realizations of the full profile and all possible choices of weights.
+Assume hereinafter the selected weights sequence $\w \in W$ to be convex.
+In order to compute the minimal max regret $\MMR(\pprofile)$ under partial profile $\pprofile$ we need to compute the pairwise max regret between all pairs of alternatives $(x,y)$, where $x$ is a proposed winner and $y$ is the ``adversary'' alternative.
+Indeed, the construction of $\PMR(x,y,\pprofile,\w)$ can be viewed as an adversary's attempt to maximize the regret of choosing $x$ instead of $y$.
+For doing this, he can choose a completion $\profile_i \in C(\pprofile_i)$ of the partial profile and a (feasible) scoring vector $\w$ that maximize the contribution of the voter $i$ to $\PMR(x,y,\pprofile,\w)$.
+Let us now analyze how it could be done depending on the relation between alternatives $x$ and $y$ in $\pprofile_i$.
+\begin{itemize}
+	\item $x \succ_i^\pprofile y$
+	\newline If we know $x$ is preferred to $y$ and we choose $x$ as a winner, $\pprofile_i$ contribution to $\PMR(x,y,\pprofile,\w)$ must be negative.
+In this situation, our adversary can only try to minimize this advantage by minimizing the positional gap between the two alternatives.
+To achieve that, he can arbitrary place all the alternatives preferred to $x$ above $x$, together with all the ones with unknown relation to $x$.
+Moreover, he can place all the alternatives less preferred to $x$ and with unknown relation to $y$ below $y$.
+We can summarize it for each $q \in A$ as follows:
+	\begin{align*}
+	q \succ_i^\pprofile x \vee q \ ?_i^\pprofile \ x \ & \Rightarrow \ \uparrow_x \\
+	x \succ_i^\pprofile q \wedge ( q \ ?_i^\pprofile \ y \vee y \succ_i^\pprofile q) \ & \Rightarrow \ \downarrow_y \\
+	x \succ_i^\pprofile q \succ_i^\pprofile y \ & \Rightarrow \ \text{in between} \\
+	\end{align*}
+	It is worth noting that when the relation between $q$ and $x$ is not known in the partial profile, the adversary takes advantage by placing $q$ above $x$ only under the assumption of convex weight sequences.
+	\item $y \succ_i^\pprofile x$
+	\newline If $y$ is preferred to $x$ the construction proceeds similarly to the previous case, but now the adversary takes advantage by maximizing the gap between $x$ and $y$ placing as much alternatives as he can between the two.
+We can summarize the procedure for each $q \in A$ as follows:
+	\begin{align*}
+	q \succ_i^\pprofile y \ & \Rightarrow \ \uparrow_y \\
+	x \succ_i^\pprofile q \ & \Rightarrow \ \downarrow_x \\
+	(y \succ_i^\pprofile q \vee y \ ?_i^\pprofile \ q) \wedge (q \succ_i^\pprofile x \vee q \ ?_i^\pprofile \ x) \ & \Rightarrow \ \text{in between} \\
+	\end{align*}
+	\item $x \ ?_i^\pprofile \ y$
+	\newline If the partial profile $\pprofile_i$ does not specify the relation between $x$ and $y$, the advantage is maximized by ordering $y$ over $x$ and maximizing the gap between them following the procedure for the case $y \succ_i^\pprofile x$.
+\end{itemize}
+
+\section{Dropping the Convex Assumption}
+\subsection{Profile completion}
+What if the sequence of weights is not convex?
+When $y \succ_i^\pprofile x$ or $x \ ?_i^\pprofile \ y$ weights do not influence the arbitrary placement of alternatives.
+Please remind we are working under the assumption that weights constitute a monotonic non-increasing sequence.
+Thus, there is no way for the adversary to take advantage from the weights distribution in order to increase the gap between $y$ and $x$ besides placing as much alternatives as he can between the two.
+The only case in which weights can influence the positional gap between $x$ and $y$ is when $x \succ_i^\pprofile y$ and $q \ ?_i^\pprofile \ x$.
+For convex sequences we place such alternatives $q$ above $x$, but it is not obvious that this is the best option for other sequences.
+For example, suppose $x$ and $y$ are ranked respectively in first and second position in the partial profile and we wonder where to place an alternative $q$ with unknown relation to $x$ (and thus to $y$).
+Suppose also that in the weight sequence the distance between the first and second positions is much lower than the one between the second and the third ones.
+In this case, placing $q$ above $x$ does not minimize the gap between $x$ and $y$ but we want, instead, to place $q$ below $y$.
+\newline The constraints expressed by the chair may result in a set of feasible vectors such that none of them forms a convex sequence.
+In this case we need to analyze the particular sequence of weights in order to decide how to maximize the adversary advantage.
+Before going into details, let us define $A$ as the set of alternatives (if any) preferred to $x$, $B$ as the set of alternatives preferred to $y$ but not to $x$, and $U$ the set of those with unknown relation to both $x$ and $y$.
+The idea is to determine the positions that minimize $x$'s advantage over $y$ and then place some of the alternatives in $U$ above $x$ and some below $y$ in order to get that desired ranking.
+Since we cannot change the order of the alternatives in the set $B$ we know that $x$ and $y$ are separated exactly by $|B|$ positions (the adversary would not take any advantage by adding alternatives between them).
+So, starting from the position of $x$ in the partial completion of $\pprofile_i$ computed so far ($\hat{\profile}_i$), we find the two positions separated by $|B|$ alternatives whose weights difference is the lowest.
+Note that we can only add $|U|$ alternatives so we can check only until the position $\hat{\profile}_i(x)+|U|$.
+Algorithm \ref{alg:splittingU} shows the procedure described.
+
+It is easy to see that we check at most $|U|$ positions.
+In the worst case the size of $U$ is equal to $m-2$, thus the procedure can be computed in $O(m)$ time.
+This cost does not affect the minimax regret computation time complexity that remains $O(nm^3)$.
+
+\begin{algorithm}[h] 
+	\caption{Placing alternatives in $U$ without Convex Assumption}
+	\label{alg:splittingU} 
+	\begin{algorithmic}
+		\Require $x$, $y$, $\hat{\profile}_i$, $\w$, $U$, $B$
+		\Ensure $\profile_i \in C(\pprofile)$
+		\Statex
+		\State $ j \gets 0$;
+		\State $ i \gets \hat{\profile}_i(x)$;
+		\State $ \mathit{posmin} \gets i$;
+		\State $ \mathit{min} \gets \w(i) - \w(i+1+|B|)$;
+		\While {$( j \leq |U| )$}
+		\If{ $(\w(i+j)-\w(i+1+|B|+j) < \mathit{min})$ }
+		\State $ \mathit{min} \gets \w(i+j) - \w(i+1+|B|+j)$;
+		\State $ \mathit{posmin} \gets i+j$;
+		\EndIf
+		\EndWhile
+
+		\State $U_{\mathit{abovex}} \gets (i-\mathit{posmin}) \text{ alternatives} \in U $;
+		\State $U_{\mathit{belowy}} \gets U \setminus U_{\mathit{above}}$;
+		\Statex
+		\State $\profile_i \gets place(\pprofile_i,U_{\mathit{abovex}},U_{\mathit{belowy}})$;
+		\Statex \Return $\profile_i$
+
+	\end{algorithmic}
+\end{algorithm}
+
+\subsection{Profile completion, again}
+ {\bf \em TODO: still have to find out exactly how to do it}
+ We introduce a set integer variables $I^i$, one for each position $i$.
+ Let $U^j$ be, for the agents in $A^-$, the alternatives that, in the partial order $\succ^p_j$ of some agent $j \in A^-$, are incomparable with $x$ and $y$.
+ \[ \sum_{l=1}^n I^j_l w_l \]
+ Variable $I^j$ associated with the constraint $0 \leq I \leq |U^j|$.
+
+ Use linearization techniques to handle the multiplication...
+
+\section{To discuss}
+Let $\hat{v}_i$ be the linear order extending $p_i$ according to the above procedure (described in \cite{Lu2011}).
+
+Then PMR can be written as follows:
+\[ \PMR(x,y; \pprofile, W) = \max_{\w \in W} \Big \{ \max_{v_j \in C(\succ_j^p)} [w_{v_j(y)} - w_{v_j(x)}]  + \sum_{j \in A^+, j \in A^?} [w_{\hat{v}_j(y)} - w_{\hat{v}_j(x)}] \Big \} \]
+
+\section{Even more fun}
+We can consider different types of questions: asking to compare a pair of alternatives, asking about top-k alternatives.
+
+Type of questions that we can ask to the chair:
+bound queries (Is this alternative among your top-k most preferred items?), comparison queries (do you prefer alternative x or alternative y?).
+
 \end{document}

### 2018-12-12 draft.tex
minors

@@
 \begin{itemize}
-\item Current solution strategy: consider the solution of the minimax regret game, 
+\item \textbf{Current solution strategy}: consider the solution of the minimax regret game, 
  $(x,y,w^{a},\profile^{a})$, where $x$ is the minimax regret optimal alternative, $y$ the adversarial choice, $w^{a}$ the weights, and $\profile^{a}$ the profile completed by the adversary.
-
-\item Non-iterleaved regret method: comparison with a method based on minimax regret, but not interleaved.
 
@@
 In this case, the query with least value is chosen.
+
+What is the complexity of this strategy?
+Let's define $Q$ as the set of all possible queries we can address to the agents and to the committee.
+The worst case is represented by the situation in which we do not have any information about both the agents' preferences and the weights constraints.
+In this case we can address $\binom{m}{2}=\frac{m(m-1)}{2}$ questions to each agent.
+Moreover, we need to ask at least $m$ questions to the committee.
+Then, each question induces two possible pairs of $(\pprofile,W)$ for each of which we compute the $\MMR$, whose worst case complexity is $O(nm^3)$.
+Thus, the cardinality of $Q$ in the worst case is $\approx n \cdot \frac{m(m-1)}{2} + \lambda m$, and the worst case time complexity of the strategy is $O(n^2m^5)$.
+
+\item Non-interleaved regret method: comparison with a method based on minimax regret, but not interleaved.
+
+\item Non-interleaved non-regret strategies (useful as benchmarks).	
+	\begin{itemize}
+		\item Random strategy: randomly chooses an agent $i$ and a comparison query such that $x \ T_i^\pprofile \ y$.
+		\item Volumetric strategy: chooses an agent $i$ and a query that maximizes the number of new pairwise preferences revealed given the worst response.
+	\end{itemize}
 \end{itemize}

### 2018-12-14 draft.tex
Summary completion procedure

@@
 \usepackage{algorithm, algpseudocode}
+\usepackage{bm}
+\usepackage{cleveref}
+\usepackage{xcolor}
 
@@
 \newcommand{\denselist}{\itemsep -2pt\topsep-6pt\partopsep-6pt}
+\newcommand{\commentOC}[1]{\textcolor{blue}{\small$\big[$OC: #1$\big]$}}
 
@@
 %\newcommand{\pref}{\boldsymbol{\succ}^\textbf{r}}%real, connected pref, strict
-\newcommand{\pref}{{\succ}}%real, connected pref, strict
-\newcommand{\prefr}{{\succ}^{r}}%real, connected pref, strict
+\newcommand{\pref}{\succ}%real, connected pref, strict
+\newcommand{\prefr}{{\succ}^\text{r}}%real, connected pref, strict
 \newcommand{\ppreflarge}{\succeq^\text{p}}%partial pref
 \newcommand{\ppref}{\succ^\text{p}}%partial pref
+%Thanks to https://tex.stackexchange.com/q/154549
+\makeatletter
+\newcommand{\newrelation}[2]{% #1 = control sequence, #2 = replacement text
+  \@ifdefinable{#1}{%
+    \def#1{%
+    \@ifnextchar_{\csname\string#1\endcsname}{\mathrel{#2}}%
+    }%
+    \@namedef{\string#1}##1##2{\mathrel{#2_{##2}}}%
+  }%
+}
+\makeatother
 
-\newcommand{\profile}{\textbf{v}}%(complete) prorile
-\newcommand{\pprofile}{\textbf{p}}%partial prorile
-\newcommand{\w}{\textbf{w}}%partial prorile
+\newrelation{\myRgood}{R^X}
+\newrelation{\pinc}{Q^\text{p}}%partial pref, complement (incomparable)
+
+\newcommand{\profile}{\textbf{v}}%(complete) profile
+\newcommand{\pprofile}{\textbf{p}}%partial profile
+\newcommand{\w}{\textbf{w}}%partial profile
 
@@
 \end{align*}
-%Computing PMR may be challenging since in principle the inner maximization can depend on the outer maximization.
-Let $A^+=\{ i \ | \ y \succ_i^\pprofile x\}$ be the set of agents for which we know that $y$ is preferred to $x$ (positive contribution to pairwise regret), $A^-=\{ i \ | \ x \succ_i^\pprofile y\}$ 
-be the set of agents for wich we  know that $x$ is preferred to $y$ (negative contribution) and $A^?=\{ i \ | \ x \ T_i^\pprofile \ y\}$ the remaining case, where the preference between $x$ and $y$ is not known.
+
+Given our hypothesis, for all pairs of alternatives, there exists completions of the partial preferences $\ppref$ that maximize the PMR and that do not depend on the weights.
+That is, we can exhibit, for each voter $j$, a completion $v_j$ such that $\forall \w, \forall v'_j \in C(\ppref_j): [w_{v_j(y)} - w_{v_j(x)}] \geq [w_{v'_j(y)} - w_{v'_j(x)}]$.
+
+Let $A^+=\{ i \ | \ y \ppref_i x\}$ be the set of agents for which we know that $y$ is preferred to $x$ (positive contribution to pairwise regret), $A^-=\{ i \mid x \ppref_i y\}$ 
+be the set of agents for wich we  know that $x$ is preferred to $y$ (negative contribution) and $A^?=\{ i \mid x \pinc_i y\}$ the remaining case, where the preference between $x$ and $y$ is not known.
 Consider how the adversary will complete the partial orders:
@@
 \end{itemize}
+In summary, some best completion $\pref$ satisfies two properties: (1) for all $c \pinc x$, $c \pref x$; and (2) for all $c \pinc y$, if not $c \pref x \pref y$ then $y \pref c$.
+These two properties are intuitively understandable by observing that maximizing the PMR requires placing $x$ as low as possible (hence the first property) and $y$ as high as possible (hence the second property, with the exception that sometimes it is not possible to satisfy both desires and noting that the first desire is more important by convexity of the weights).
+A proof that this reasoning is correct is in \cref{sec:prfCompl}.
 
@@
 	\begin{itemize}
-		\item Random strategy: randomly chooses an agent $i$ and a comparison query such that $x \ T_i^\pprofile \ y$.
+		\item Random strategy: randomly chooses an agent $i$ and a comparison query such that $x \pinc_i y$.
 		\item Volumetric strategy: chooses an agent $i$ and a query that maximizes the number of new pairwise preferences revealed given the worst response.
@@
 
+\section{Proof of completion}
+\label{sec:prfCompl}
+Given $w$ and ${\pref} \in C(\ppref)$, let $w[\pref]$ denote $w_{|\pref(y)|} - w_{|\pref(x)|}$.
+\commentOC{Changing the notation to slightly to reduce the number of symbols, to be discussed.} Define ${\pref} \in m_w$ iff ${\pref} \in C(\ppref)$ and $\forall {\pref'} \in C(\ppref): w[\pref] \geq w[\pref']$.
+
+Given $w$ and $\pref$ an element of $C(\ppref)$.
+Consider $C = \{c \pinc x \land x \pref c\}$.
+Define $\pref^1$ as $\pref$ except that the elements in $C$ come just above $x$ in $\pref^1$, respecting in $\pref^1$ their internal ordering in $\pref$.
+We show that $\pref^1$ is an element of $C(\ppref)$; and that $w[\pref^1] \geq w[\pref]$.
+
+It is an element of $C(\ppref)$ as it does not contradict $\ppref$.
+To show this, recall first that $\pref$ does not contradict $\ppref$.
+Left to show is that $\forall c \in C, d \notin C: x \pref d \pref c \Rightarrow d \pinc c$ (thus any element $d$ whose relation with $c$ has changed from $\pref$ to $\pref^1$ were incomparable with $c$ in $\ppref$).
+Consider any such pair $c, d$.
+As $d \notin C$, $\lnot(d \pinc x)$ or $d \pref x$.
+From the hypothesis, $d \pref x$ is excluded.
+As $\pref$ extends $\ppref$, $\lnot(d \ppref x)$ and $\lnot (c \ppref d)$.
+Because $\lnot (d \pinc x)$, $x \ppref d$.
+Thus, $\lnot (d \ppref c)$, otherwise by transitivity $x \ppref c$.
+The conclusion now follows from $\lnot (c \ppref d)$ and $\lnot (d \ppref c)$.
+
+In $\pref^1$, compared to $\pref$, $x$ is $|C|$ positions lower, and $y$ is at most $|C|$ positions lower, depending on where $y$ was in $\pref$.
+Hence, by convexity of the weights, $w[\pref^1] \geq w[\pref]$.
+
+Now define $\pref^2$ as $\pref^1$ except that the elements from $C' = \{c \pinc y \land \lnot (c \pref^1 x \pref^1 y) \land c \pref^1 y\}$ move just below $y$, respecting in $\pref^2$ their internal ordering in $\pref^1$.
+Observe that this move keeps property (1), that was satisfied by construction in $\pref^1$, intact, and satisfies property (2).
+The rest of the reasoning is similar to the previous move, as the situations are symmetric.
+(To be checked?) Hence, $\pref^2 \in C(\pref)$ and it satisfies both properties.
+
+Given any $x, y, w$, as $C(\pref)$ has an element maximizing $w[.]$ (by finiteness of the set), the above reasoning shows that some element in $C(\pref)$ satisfies both properties and maximizes $w[.]$.
+And any element in $C(\pref)$ satisfying both properties attribute the same positions to $x$ and $y$, thus, maximizes $w[.]$.
 \end{document}

### 2019-01-07 draft.tex
Cosmetic

@@
 \label{sec:prfCompl}
-Given $w$ and ${\pref} \in C(\ppref)$, let $w[\pref]$ denote $w_{|\pref(y)|} - w_{|\pref(x)|}$.
-\commentOC{Changing the notation to slightly to reduce the number of symbols, to be discussed.} Define ${\pref} \in m_w$ iff ${\pref} \in C(\ppref)$ and $\forall {\pref'} \in C(\ppref): w[\pref] \geq w[\pref']$.
+Given $w$ and ${\pref} \in C(\ppref)$, let $w[\pref]$ denote $w_{|\pref(y)|} - w_{|\pref(x)|}$. \commentOC{Changing the notation to slightly reduce the number of symbols, to be discussed.}
 
-Given $w$ and $\pref$ an element of $C(\ppref)$.
-Consider $C = \{c \pinc x \land x \pref c\}$.
-Define $\pref^1$ as $\pref$ except that the elements in $C$ come just above $x$ in $\pref^1$, respecting in $\pref^1$ their internal ordering in $\pref$.
-We show that $\pref^1$ is an element of $C(\ppref)$; and that $w[\pref^1] \geq w[\pref]$.
+Given ${\pref} \in C(\ppref)$, define $\pref^1$ as $\pref$ except that the elements in $C = \{c \pinc x \land x \pref c\}$ come just above $x$ in $\pref^1$, respecting in $\pref^1$ their internal ordering in $\pref$.
+We show first that $\pref^1$ is an element of $C(\ppref)$; and second that $\forall w: w[\pref^1] \geq w[\pref]$.
 
-It is an element of $C(\ppref)$ as it does not contradict $\ppref$.
+First, it is an element of $C(\ppref)$ as it does not contradict $\ppref$.
 To show this, recall first that $\pref$ does not contradict $\ppref$.
@@
 
-In $\pref^1$, compared to $\pref$, $x$ is $|C|$ positions lower, and $y$ is at most $|C|$ positions lower, depending on where $y$ was in $\pref$.
+Second, in $\pref^1$, compared to $\pref$, $x$ is $|C|$ positions lower, and $y$ is at most $|C|$ positions lower, depending on where $y$ was in $\pref$.
 Hence, by convexity of the weights, $w[\pref^1] \geq w[\pref]$.
@@
 The rest of the reasoning is similar to the previous move, as the situations are symmetric.
-(To be checked?) Hence, $\pref^2 \in C(\pref)$ and it satisfies both properties.
+(To be checked?) Hence, ${\pref^2} \in C(\pref)$ and it satisfies both properties.
 

### 2019-01-29 draft.tex
linear optimization

@@
 
+\DeclareMathOperator{\Regret}{Regret}
 \DeclareMathOperator{\SCORE}{Score}
@@
 %Given a partial profile: use techniques of Lu and Boutilier (2011).
+\begin{abstract}
 Social choice deals with the problem of determining a consensus choice from the preferences of different agents (voters).
 In the classical setting, the social choice rule is fixed beforehand; indeed many works analyze the properties of different rules (including axiomatic treatments) in order to justify the choice of specific social choice functions.
-Moreover, it is usually assumed that the preferences of the voters are completely known.
+Moreover, it is usually assumed that the preferences of the voters are known completely.
 
@@
 In this draft we provide a method for approximate winner determination and an incremental elicitation protocol based on minimax regret. 
+\end{abstract}
+
+\section{Introduction}
+
+\begin{itemize}
+\item General motivation: need to deal with partially specified preferences and as well partially specified voting rules
+\item Focus on positional scoring rules
+\item Robust decision criterion: minimax regret
+\item Incremental elicitation of preferences can help mitigating the cognitive and communication costs
+\item Novelty of the proposed method
+\item Structure of the paper
+\end{itemize}
+
+Aggregation of preference information is a central task in many computer systems (recommender systems, search engines, etc).
+In many situations, such as in group recommender systems, the goal is to find a consensus choice.
+
+In this paper we propose an interactive adaptive protocol for eliciting both the voters preferences and the voting rule.
+At each step we need to decide whether we want to ask a question to the committee or to one of the agents (and to which agent in particular).
+%We want to design a questioning strategy to minimize the worst regret in the long run.
+A questioning strategy indicates, given a partial profile and a set of feasible weights, which question to ask next.
+A question is either a query to the voter $i$ about her preference relation $\succ_i$ or a query to the committee about the feasible weights.
+
+%The voting scheme selects the winner (a consensus option).
+%Incremental elicitation 
+% The paper is organized as follows.
+
+\subsection{Related works}
+
+\paragraph{Uncertain scoring rules}
+A number of works have dealt with the problem of reasoning with incompletely specified aggregation functions.
+In particular, when considering positional scoring rules, it is possible to derive dominance relations (akin to stochastic dominance) that allow to eliminate some alternatives since they will be less preferred than another one for any instantiation of the weights \cite{Stein1994}.
+More recently the characterization of methods for aggregating the uncertainty over the scoring vectors has been studied in \cite{Viappiani2018}.
+We also note that the elicitation methods based on minimax regret described in \cite{Boutilier2006} (and in many other recent papers), while not specifically targeted to scoring rules, can be easily adapted (from a technical point of view) to elicit the scoring vector from a committee.
+
+\paragraph{Incomplete profiles}
+%In this setting, the system knows a partial preference profile $\ppref$ 
+%The partial preference relation $\ppref_i$ represents our knowledge about the preferences of agent $i$.
+
+Lu and Boutilier \cite{Lu2011} assume that the preferences of the voters are only partially known (while the social choice function is known and fixed in advance; it is assumed to be decomposable) and
+ propose to use minimax regret to produce a robust approximation.
+Each alternative is associated with a max regret value that measures how far from optimal it could be in the worst case given any completion of the partial profile.
+The computation of max regret is facilitated by the fact the score is decomposable.
 
@@
 
-We assume that there is a set $A$ of $m$ alternatives and $n$ agents (voters); each agent is associated to a preference order.
+We assume that there is a set $A$ of $m$ alternatives (for instance products, restaurants, movies, public projects, job candidates, etc.) and $n$ agents (voters); each agent is associated to a preference order.
+The goal of the voters is to make a consensus choice, that is to select a ``winner'' given voter rankings.
+
 %The set of preference orders is called profile and it is denoted by $v$.
@@
 Among the many possible social choice functions, we consider {\em positional scoring rules}, which attach weights to positions; an alternative obtains a score that depends on the rank obtained in each of the preference orders:
-
-\[ s(x; \profile, \w) = \sum_{i=1}^{n} w_{v_i(x)}. \]
-
-where the vector $(w_1,\ldots,w_m)$ is called the scoring vector. We assume that the weights constitute a monotonic sequence: $w_{1} \geq w_{2} \geq \ldots \geq w_{m}$.
+\begin{align}
+s(x; \profile, \w) = \sum_{j=1}^{n} w_{v_j(x)}
+= \sum_{i=1}^{m} \alpha_i w_i . \label{eq:srule}
+\end{align}
+where $\alpha_i$ is the number of times that alternative $x$ was ranked in the $i$-th position.
+The vector $(w_1,\ldots,w_m)$ is called the scoring vector. We assume that the weights constitute a monotonic sequence: $w_{1} \geq w_{2} \geq \ldots \geq w_{m}$.
 
 \medskip
-We want to reason about partial preference information.
+In this work we want to reason about partial preference information.
 A partial preference  is encoded by a partial order $\ppref_i$  of voter $i$;
@@
 
-\section{Related works}
-
-\paragraph{Uncertain scoring rules}
-A number of works have dealt with the problem of reasoning with incompletely specified aggregation functions.
-In particular, when considering positional scoring rules, it is possible to derive dominance relations (akin to stochastic dominance) that allow to eliminate some alternatives since they will be less preferred than another one for any instantiation of the weights \cite{Stein1994}.
-More recently the characterization of methods for aggregating the uncertainty over the scoring vectors has been studied in \cite{Viappiani2018}.
-We also note that the elicitation methods based on minimax regret described in \cite{Boutilier2006} (and in many other recent papers), while not specifically targeted to scoring rules, can be easily adapted (from a technical point of view) to elicit the scoring vector from a committee.
-
-\paragraph{Incomplete profiles}
-%In this setting, the system knows a partial preference profile $\ppref$ 
-%The partial preference relation $\ppref_i$ represents our knowledge about the preferences of agent $i$.
-
-Lu and Boutilier \cite{Lu2011} assume that the preferences of the voters are only partially known (while the social choice function is known and fixed in advance; it is assumed to be decomposable) and
- propose to use minimax regret to produce a robust approximation.
-Each alternative is associated with a max regret value that measures how far from optimal it could be in the worst case given any completion of the partial profile.
-The computation of max regret is facilitated by the fact the score is decomposable.
-
 % We are given  $\ppref_i $,  a partial preference.
@@
 \section{Minimax regret under partial profile and weight information}
-In this draft, we consider a setting where both the voters' preferences and the preferences of the chair about the voting rule are incomplete.
 
-The weights of a scoring rule can model different preferences for the committee; however in general it can be difficult to set the weights in an appropriate way.
+%The regret-minimizing alternative may not be a possible winner for some voting rules.
+The weights of a scoring rule can model different preferences of the committee. 
+For instance, the weights can control the inclination to favour ``extreme'' alternatives (often at either the top or the bottom of the rankings) at the expenses of ``moderate'' alternatives (that are more consistently in the middle part of the rankings).
 
+However in general it can be difficult to set the weights in an appropriate way.
+
+In this paper, we consider a setting where both the voters' preferences and the preferences of the chair about the voting rule are incomplete.
+
+\medskip
 The quality of an alternative can be quantified by considering the maximum regret with respect to an adversary that can choose the instantiation of both a complete profile (extending the known preferences of the agents) and of the scoring vectors (associated to the preferences of the committee).
 
-%The adversary can choose the instantiation of the weights and preferences of the agents so to maximize the loss.
+We propose to use the minimax regret as a decision criterion to determine a winner.
+Minimax regret [ref] has been used for making decisions under utility uncertainty and for preference elicitation [ref].
+Lu and Boutilier \cite{Lu2011} have adopted minimax regret ;
 
-We propose to use minimax regret to identify the alternative to declare as the approximate winner, extending the work of \cite{Lu2011} to the simultaneous presence of uncertainty in the agents' preferences and uncertainty in the weights.
+This paper extends the work of  to the simultaneous presence of uncertainty in the agents' preferences and uncertainty in the weights.
+
 The maximum regret is considered by assuming an adversary can choose both 1) to extend the partial profile into a complete profile 2) can instantiate the weights choosing among any feasible weight vector in $W \subseteq \mathcal{W}$.
 
+We formalize the notion of minimax regret in multiple steps.
+First of all, $\Regret(x, \profile, \w)$ is the loss or ``actual'' regret  of selecting $x$ as a winner instead of choosing the optimal alternative under $\profile$ and $\w$:
+\[\Regret(x, \profile, \w) = \max_{y} s(y; \profile,\w) - s(x; \profile, \w).\]
+
+The pairwise max regret of $x$ relative to $y$ given partial profile $\pprofile$ and the space of weights $W$
+$\PMR(x,y;\pprofile,W)$ is the worst-case loss under all possible realizations of the full profile {\em and} all possible instantiations of the weights:
+\begin{align}
+\PMR(x,y; \pprofile, W) & = \max_{\w \in W} \max_{\profile \in C(p)} s(y; \profile,\w) - s(x; \profile,\w).
+\end{align}
+
+Max regret $\MR(x;\pprofile,W)$ is the worst-case loss of $x$.
+It is the loss occurred by an adversarial selection of a complete profile $\profile$ extending $\pprofile$ and a selection of $\w \in W$ to maximize the loss between $x$ and the true winner under $\profile$ and $w$.
+\begin{align}
+\MR(x; \pprofile, W) & = \max_{y \in A} \PMR(x,y; \pprofile, W)\\
+& = \max_{\w \in W} \max_{\profile \in C(p)} \Regret(x, \profile, \w).
+\end{align}
+
+Finally,  $\MMR(\pprofile,W)$ is the value of minimax regret under $\pprofile$ and $W$, obtained when recommending the minimax optimal alternative $x^*$:
 \begin{align*}
-\PMR(x,y; \pprofile, W) &= \max_{\w \in W} \max_{\profile \in C(p)} s(y; \profile,\w) - s(x; \profile,\w)\\
-\MR(x; \pprofile, W) &= \max_{y \in A} \PMR(x,y; \pprofile, W) \\
 \MMR(\pprofile,W) & = \min_{x \in A} \MR(x;\pprofile,W) \\
@@
 \end{align*}
-
-\begin{itemize}
- \item $\PMR(x,y;\pprofile,W)$ denotes the pairwise max regret of $x$ relative to $y$ given partial profile $\pprofile$ and the space of weights $W$, that is the worst-case loss under all possible realizations of the full profile {\em and} all possible instantiations of the weights.
- \item Max regret $\MR(x;\pprofile,W)$ is the worst-case loss of $x$.
-It is the loss occurred by an adversarial selection of a complete profile $\profile$ extending $\pprofile$ and a selection of $\w \in W$ to maximize the loss between $x$ and the true winner under $\profile$ and $w$.
- \item Minimax regret $\MMR(\pprofile,W)$ is the minimum of max regret obtained when choosing $x^*$
-\end{itemize}
 By recommending the alternative associated with minimax regret, we can provide a recommendation that gives worst-case guarantees, giving some robustness in face of uncertainty (due to both not knowing the agents' preferences and the weights used in the aggregation).
 
-We want to design a questioning strategy to minimize the worst regret in the long run.
-A questioning strategy indicates, given a partial profile and a set of feasible weights, which question to ask next.
-A question is either a query to the voter $i$ about her preference relation $\succ_i$ or a query to the committee about the feasible weights.
-
-In order to design this strategy we first evaluate how to compute the current regret.
+% Add some general remarks about using minimax regret
 
 \subsection{Computation of minimax regret}
-
 In order to compute pairwise maximum regret and therefore minimax regret, we adapt the reasoning from \cite{Lu2011} so that we decompose the $\PMR$ into the contributions that is associated to each agent.
@@
 
-Let $s(x; v_j,\w)=w_{v_j(x)}$ be the number of points $x$ obtains in the ranking $v_j$, that is the weight of the position $v_j(x)$.
-Exploiting the decomposition of the score in terms of votes we can rewrite $\PMR$ as follows:
+A scoring rule associates each alternative to a score that is given by the sum of points obtained for each voter.
+
+Let $s(x; v_j,\w)=w_{v_j(x)}$ be the number of points that $x$ obtains in the ranking $v_j$ (see Equation \ref{eq:srule}), that is the weight of position $v_j(x)$.
+Obviously we have 
+\[ s(x; \profile, \w) = \sum_{j=1}^n s(x; v_j,\w). \]
+
+We now  exploit the decomposition of the score in terms of votes.
+The actual regret of choosing $x$ instead of $y$ can be written as:
+\[
+s(y; \profile,\w) - s(x; \profile, \w) = [\sum_{j=1}^n s(y; v_j,\w) - s(x; v_j,\w)]
+\]
+and  can rewrite $\PMR$ as follows:
 \begin{align*}
@@
 \end{align*}
-
 Given our hypothesis, for all pairs of alternatives, there exists completions of the partial preferences $\ppref$ that maximize the PMR and that do not depend on the weights. 
@@
 
+\subsection{Linear program under the convex assumption}
+
+By solving a sequence of pairwise max regret computation is possible to determine the minimax regret solution.
+Each PMR is computed using a linear program.
+The decision variables correspond to the weights attached to the different positions.
+Constraints are on the feasible parameters (the ``weights'' of the scoring rules); contraints represent the preferences of the chair about the scoring rule.
+
+Let $\hat{v}$ be the compute profile computed according to the above procedure, and  $\hat{v}_j$ the $j$-th element (the linear order extending the partial order $p_j$ of the $j$-th voter).
+The PMR can be written as:
+\[ \PMR(x,y) = \sum_{j=1}^n w_{\hat{v}_i(y)} - w_{\hat{v}_i(x)} 
+= \sum_{i=1}^m \alpha_i w_i \]
+where the coefficient $\alpha_i$ is the number of times $y$ is in the $i-th$ position minus the number of times $x$ is the in the $i$-th position in the rankings of the completed profile $\hat{v}$:
+\[ \alpha_{i} = \sum_{j=1}^{n}  I[\hat{v}_{j}(y)=i] - I[\hat{v}_{j}(x)=i]\]
+where $I$ is the indicator function.
+The linear program is then the following:
+\begin{align}
+\max & \sum_{i=1}^m \alpha_i w_{i}\\
+\text{ s.t. } & w \in W
+\end{align}
+
+\subsection{Minimax regret without the convex assumption}
+
+\begin{itemize}
+ 	\item Mixed integer program to solve minimax regret without the convexity
+ 	\item Approximations ?
+\end{itemize}
+
+Let $\hat{v}_i$ be the linear order extending $p_i$ according to the above procedure (described in \cite{Lu2011}).
+Then PMR can be written as follows:
+\[ \PMR(x,y; \pprofile, W) = \max_{\w \in W} \Big \{ \max_{v_j \in C(\succ_j^p)} [w_{v_j(y)} - w_{v_j(x)}]  + \sum_{j \in A^+, j \in A^?} [w_{\hat{v}_j(y)} - w_{\hat{v}_j(x)}] \Big \} \]
+
+We compute pairwise maximum regret by considering binary variables to represent optimization choices related to where to position the alternatives.
+We also have numerical variables to represent the weights of the scoring rule.
+
+Since the objective is to maximize pairwise regret
+
+ The objective function can be written as:
+ \[ \max \sum_{l=1}^n I^j_l w_l -  I^j_l w_l \]
+
+ We replace the multiplicative terms by new variables..
+\[ V_{l}^{j} \sim I^j_l w_l  \]
+
+To impose the desired behavior:
+\begin{align*} 
+V_{l}^{j} \leq I^j \\
+V_{l}^{j} \leq w_l
+\end{align*}
+The expression $I^j_l w_l$ evaluates to $w_l$ if $I^j_l = 1$, and to $0$ otherwise.
+
+We write $w \in W$ as a shourtcut to represent the constraints that the weights are chosen to be in the feasible set.
+%Variable $I^j$ associated with the constraint $0 \leq I \leq |U^j|$.
+
+\begin{align}
+\max & \sum_{l=1}^m  V_{l}^{j,+} - V_{l}^{j,-}\\
+\text{ s.t. } & \\
+& V_{l}^{j} \leq I^j \\
+& V_{l}^{j} \leq w_l \\
+& V_{l}^{j} \leq I^j \\
+& V_{l}^{j} \leq w_l 
+\end{align}
+
 \section{Interactive Elicitation}
+
+\begin{itemize}
+	\item Minimax regret can be used to guide the elicitation process
+	\item As termination condition of elicitation, we can check whether minimax regret is lower than a threshold. If optimality is derived, we can perform elicitation until minimax regret drops to zero.
+	\item At each step, the system need to decide whether to ask a question to one of the agents or ask a question to the chair about the voting rule
+	\item Type of questions that we can ask to the chair:
+	bound queries (Is this alternative among your top-k most preferred items?), comparison queries (do you prefer alternative x or alternative y?).
+\end{itemize}
+
 Starting from some initial partial knowledge, our goal is to learn both the scoring rule function and the agents' preferences.
@@
 
-{\em Some ideas: decompose the regret into two components, one due to $\w$ and one due to $\pprofile$, and ask a question to the chair / or to one of the agents depending on which is highest}
+%{\em Some ideas: decompose the regret into two components, one due to $\w$ and one due to $\pprofile$, and ask a question to the chair / or to one of the agents depending on which is highest}
 
@@
 \begin{itemize}
-\item \textbf{Current solution strategy}: consider the solution of the minimax regret game, 
- $(x,y,w^{a},\profile^{a})$, where $x$ is the minimax regret optimal alternative, $y$ the adversarial choice, $w^{a}$ the weights, and $\profile^{a}$ the profile completed by the adversary.
+\item {\em Current solution strategy}: consider the solution of the minimax regret game, 
+ $(x,y,\w^{a},\profile^{a})$, where $x$ is the minimax regret optimal alternative, $y$ the adversarial choice, $\w^{a}$ the weights, and $\profile^{a}$ the profile completed by the adversary.
+
+Ask a question to compare $x$ with $y$ to an agent.
 
@@
 
-\item Non-interleaved regret method: comparison with a method based on minimax regret, but not interleaved.
+\item Two phase method.
+Ask a predefined (non adaptive) sequence of questions in order to learn the weights $w$ of the scoring rule).
+Then use minimax regret as in Lu and Boutilier.
+
+%\item Non-interleaved regret method: comparison with a method based on minimax regret, but not interleaved.
 
@@
 
+% We can stop elicitation when minimax regret is sufficiently small.
 We evaluate the proposed method using the following simulated protocol.
+
+We test the elicitation protocols in randomly generated datasets and real datasets (sushi and iris).
 
@@
 
-Test with different values of $m$ (number of alternatives) and $n$ (number of agents).
-
-Test with different population sizes, different number of alternatives, etc.
+Test with different values of $m$ (number of alternatives) and $n$ (number of agents); test with different population sizes, different number of alternatives, etc.
 
@@
 Comparison between our interleaved strategy and a strategy, still based on minimax regret  but that is not interleaved; also compare to some heuristic baselines.
+
+% Conclusions
+% summary of contribution, more comments, future works.
 
@@
 \appendix
-\section{Minimax Computation under Convex Assumption \cite{Lu2011}}
+\section{Minimax Computation under Convex Assumption}
+
+Refer to \cite{Lu2011}
 The goal is to choose as a winner the alternative $x^*$ whose worst case loss is minimal under all possible realizations of the full profile and all possible choices of weights. 
@@
 \subsection{Profile completion, again}
- {\bf \em TODO: still have to find out exactly how to do it}
+ %{\bf \em TODO: still have to find out exactly how to do it}
+
  We introduce a set integer variables $I^i$, one for each position $i$.
@@
 
- Use linearization techniques to handle the multiplication...
+ We provide the following MIP (mixed integer linear program).
 
-\section{To discuss}
-Let $\hat{v}_i$ be the linear order extending $p_i$ according to the above procedure (described in \cite{Lu2011}).
+% Use linearization techniques to handle the multiplications...
 
-Then PMR can be written as follows:
-\[ \PMR(x,y; \pprofile, W) = \max_{\w \in W} \Big \{ \max_{v_j \in C(\succ_j^p)} [w_{v_j(y)} - w_{v_j(x)}]  + \sum_{j \in A^+, j \in A^?} [w_{\hat{v}_j(y)} - w_{\hat{v}_j(x)}] \Big \} \]
-
-\section{Even more fun}
-We can consider different types of questions: asking to compare a pair of alternatives, asking about top-k alternatives.
-
-Type of questions that we can ask to the chair:
-bound queries (Is this alternative among your top-k most preferred items?), comparison queries (do you prefer alternative x or alternative y?).
+%\section{Even more fun}
+%We can consider different types of questions: asking to compare a pair of alternatives, asking about top-k alternatives.
+%
 

### 2019-01-29 draft.tex
Phrasing

@@
 In summary, some best completion $\pref$ satisfies two properties: (1) for all $c \pinc x$, $c \pref x$; and (2) for all $c \pinc y$, if not $c \pref x \pref y$ then $y \pref c$.
-These two properties are intuitively understandable by observing that maximizing the PMR requires placing $x$ as low as possible (hence the first property) and $y$ as high as possible (hence the second property, with the exception that sometimes it is not possible to satisfy both desires and noting that the first desire is more important by convexity of the weights).
+These two properties are intuitively understandable by observing that maximizing the PMR requires placing $x$ as low as possible, hence the first property; and $y$ as high as possible, hence the second property, with the exception that sometimes it is not possible to satisfy both desires and noting that the first desire is more important by convexity of the weights.
 A proof that this reasoning is correct is in \cref{sec:prfCompl}.

### 2019-01-29 draft.tex
Querying the committee

@@
 \usepackage{graphicx}
-\usepackage{amsmath,amssymb,theorem,enumerate}
+\usepackage{amsmath,amssymb,enumerate,amsthm}
 \usepackage{hyperref}
@@
 \usepackage{xcolor}
+\usepackage{booktabs}
 
@@
 \algrenewcommand\algorithmicensure{\textbf{Output:}}
+\newtheorem{claim}{Claim}
+\newtheorem{corollary}{Corollary}
+\newtheorem{definition}{Definition}
 
@@
 
-\section{Minimax regret under partial profile and weight information}
+\section[Minimax regret under partial profile and weight information]{Minimax regret under partial profile and weight \\ information}
 
@@
 And any element in $C(\pref)$ satisfying both properties attribute the same positions to $x$ and $y$, thus, maximizes $w[.]$.
+
+\section{Considerations on weights}
+\label{sec:weights}
+Let us consider a monotonic non-increasing sequence of weights: $w_{1} \geq w_{2} \geq \ldots \geq w_{m}$. Without loss of generality, we can assume $w_1=1$ and $w_m=0$.
+
+\begin{claim}
+	\label{clm:wsequence}
+	If the weight sequence is convex then $w_{1} > w_{2}$.
+	\[\forall i \in \{1,\ldots,m\} \;\; w_i - w_{i+1} \geq w_{i+1}-w_{i+2} \Rightarrow w_{1} > w_{2} \geq \ldots \geq w_{m}\] 
+\end{claim}
+\begin{proof}
+	By contradiction let assume $w_{1} = w_{2}$ then 
+	\begin{align*}
+	w_{1} - w_{2} \geq w_{2} - w_{3} &\geq \dots \geq w_{m-1} - w_{m} \\
+	1 - 1 \geq 1 - w_{3} &\geq \dots \geq w_{m-1} - 0 \\
+	0 \geq 1 - w_{3} &\geq \dots \geq w_{m-1}
+	\end{align*}
+	At this point either $0\leq w_{3}<1$ or $w_{3}=1$. In the first case 
+	\[0 \ngeq 1 - w_{3}\]
+	This breaks the convexity assumption so it is impossible.
+	In the second case, by definition there is a $w_{i} \neq 1$ where $2 < i \leq m$. So it would be 
+	\[0 \ngeq 1 - w_{i}\]
+	for some $i$. Again, the convexity is not satisfied.
+\end{proof}
+
+\begin{corollary}
+	\label{cor:weq}
+	If the weight sequence is convex and $w_{i} = w_{i+1}$ for some $i$, then $w_{j}=0 \ \forall \
+	j=i, \dots m$.
+\end{corollary}
+
+\section{Querying the committee}
+Suppose our query strategy suggests us to ask the committee the following query:
+\[ w_{2} - w_{3} \geq 2(w_{3} - w_{4}) \]
+Then we can transform it in:
+\begin{align}
+\label{eqn:juryquery}
+w_{2} - w_{3} &\geq 2 \cdot w_{3} - 2 \cdot w_{4} \notag \\
+w_{2} + 2 \cdot w_{4} &\geq 3 \cdot w_{3} 
+\end{align}
+and ask the committee if they would prefer as a winner an alternative ranked first one time and third three times rather than an alternative ranked second four times.
+
+Another way to query the committee, a more concrete one, is to present them a profile representing the situation described by the query and then deduce its answer from the selected winner.
+Obviously we have to be sure to choose a profile where only the alternatives we are interested in could be pick as winners.
+Therefore, we need a systematic way to construct a profile that reflects the situation outlined by the query for two alternatives and the others are not better than them.
+
+Assume we have a profile of $3$ voters ranking $4$ alternatives. We can represent it by columns where each of them represents the preference ordering of one voter.
+\[
+\begin{array}{ccc}
+v_1
+& v_2
+& v_3 \\
+\midrule 
+c
+& d
+& c \\
+a
+& c
+& d \\
+b
+& b
+& b \\
+d
+& a
+& a \\
+\end{array}
+\]
+
+Assuming anonymity, we can also write the profile expressing for each alternative $i \in A$ the number of voters placing it at a given rank.
+
+\[
+\begin{array}{ccccc}
+& 1^\circ
+& 2^\circ
+& 3^\circ
+& 4^\circ \\
+\cmidrule{2-5}
+a 
+& 0
+& 1
+& 0
+& 2 \\
+b
+& 0
+& 0
+& 3
+& 0 \\
+c
+& 2
+& 1
+& 0
+& 0 \\
+d
+& 0
+& 1
+& 1
+& 1 \\
+\end{array}
+\]
+
+Recalling the query (\ref{eqn:juryquery}) we are considering as an example, it is easy to see that in the current profile alternatives $a$ and $b$ represent the situation as described by the query.
+Therefore, if after proposing this profile to the committee the winning alternative turns out to be $a$ then we know that $w_{2} - w_{3} > 2(w_{3} - w_{4})$; if, instead, the winner is $b$ we know that $w_{2} - w_{3} < 2(w_{3} - w_{4})$ and if both alternatives are picked as winners then $w_{2} - w_{3} = 2(w_{3} - w_{4})$.
+
+Nevertheless, in this example it is clear that $c$ will always be preferred to other alternatives (see Claim \ref{clm:wsequence} in Section \ref{sec:weights}).
+To see it we can express for each alternative the number of voters placing it at a given rank or at a higher one.
+
+\[
+\begin{array}{ccccc}
+& \geq 1^\circ
+& \geq 2^\circ
+& \geq 3^\circ
+& \geq 4^\circ \\
+\cmidrule{2-5}
+a 
+& 0
+& 1
+& 1
+& 3 \\
+b
+& 0
+& 0
+& 3
+& 3 \\
+c
+& 2
+& 3
+& 3
+& 3 \\
+d
+& 0
+& 1
+& 2
+& 3 \\
+\end{array}
+\]
+
+\begin{claim}
+	Consider a set $A$ of $m$ alternatives and let $r_k(i)$ be the number of times the alternative $i$ obtains a rank $k$ or a higher one.
+Consider two alternatives $ i,j \in A$, if $\forall \ k=2, \dots,m \ r_k(i)\geq r_k(j)$ and $r_1(i) > r_1(j)$ then $i$ is always preferred to $j$ for any choice of weights.
+\end{claim}
+
+\begin{proof}
+	For our assumptions we know the sequence of weights is monotonic non-increasing and convex.
+Moreover, for the Claim \ref{clm:wsequence} in Section \ref{sec:weights}, we know that $w_1 > w_2$.
+Therefore, even in the worst case where $r_k(i) = r_k(j) \ forall \ k=2, \dots,m$ the sum of weights for alternative $i$ cannot be lower than the one for $j$.
+It is worth noting that we cannot say anything when $r_1(i) = r_1(j)$.
+Indeed, as said in Corollary \ref{cor:weq}, all the weights for other position but the first one can be equal, thus the number of voters ranking the alternatives at a certain position does not matter anymore.
+\end{proof}
+
+So the strategy for querying the committee is to use two alternatives $i$ and $j$ to represent the query and complete the profile such that the other alternatives are all dominated by them.
+An algorithmic approach is to start from the initial profile and then add as many voters as needed that rank $i$ and $j$ as their top choices and the other alternatives afterwards.
+As an example let consider again the query \ref*{eqn:juryquery}.
+We want the committee to choose between $a$ or $b$:
+
+\[
+\begin{array}{ccccc}
+& 1^\circ
+& 2^\circ
+& 3^\circ
+& 4^\circ \\
+\cmidrule{2-5}
+a 
+& 0
+& 1
+& 0
+& 2 \\
+b
+& 0
+& 0
+& 3
+& 0 \\
+\end{array}
+\]
+
+We add voters in order to increase the number of times $a$ and $b$ are ranked at first position.
+Please note we must maintain these scheme, so every add of a position to the ranking of $a$ must correspond to the same in the ranking of $b$.
+
+\[
+\begin{array}{cccccc}
+v_1
+& v_2
+& v_3 
+& v_4
+& v_5
+& v_6 \\
+\midrule 
+a
+& b
+& c 
+& d
+& a
+& b \\
+c
+& a
+& d
+& c
+& b
+& a \\
+b
+& d
+& b
+& b
+& d
+& c \\
+d
+& c
+& a
+& a
+& c
+& d \\
+\end{array}
+\]
+
+\[
+\begin{array}{ccccc}
+& 1^\circ
+& 2^\circ
+& 3^\circ
+& 4^\circ \\
+\cmidrule{2-5}
+a 
+& 2
+& 2
+& 0
+& 2 \\
+b
+& 2
+& 1
+& 3
+& 0 \\
+c
+& 1
+& 2
+& 1
+& 2 \\
+d
+& 1
+& 1
+& 2
+& 2 \\
+\end{array}
+\]
+
+\[
+\begin{array}{ccccc}
+& \geq 1^\circ
+& \geq 2^\circ
+& \geq 3^\circ
+& \geq 4^\circ \\
+\cmidrule{2-5}
+a 
+& 2
+& 4
+& 4
+& 6 \\
+b
+& 2
+& 3
+& 6
+& 6 \\
+c
+& 1
+& 3
+& 4
+& 6 \\
+d
+& 1
+& 2
+& 4
+& 6 \\
+\end{array}
+\]
+\textbf{Remarks:}
+\begin{itemize}
+	\item We are considering $\lambda \in \mathbb{N} \setminus \{0\}$ but we could be interested in a real number. \textit{Solution}: we can multiply both sides.
+\end{itemize}
+
 \end{document}

### 2019-02-05 draft.tex
additional references
yet more preferences
a rouugh and messy introduction

@@
 %\author{}
-%\author{Paolo Viappiani} \affil{LIP6\\\email{paolo.viappiani@lip6.fr}}
+\author{Olivier Cailloux \and Stefano Moretti \and Beatrice Napolitano \and Paolo Viappiani} %\affil{LIP6\\\email{paolo.viappiani@lip6.fr}
 %\author{Olivier Cailloux} 
@@
 \item Structure of the paper
+\item References: \cite{Cailloux2014}, \cite{Llamazares2013}, \cite{Konczak05}, \cite{Kalech2011}, \cite{Pini2009}
 \end{itemize}
@@
 In many situations, such as in group recommender systems, the goal is to find a consensus choice.
+
+The traditional approach to social choice assumes that both the social function and the full preference orderings of the voters are expressed beforehand. 
+As noted by several authors requiring voters to express full preference orderings can be onerous (especially for large sets of alternatives)
+
+% Given partial information about voter preferences, how does one choose a suitable approximate winner? 
+Scoring rules are a particularly common methods used to aggregate rankings and determine  a winner.
+The score can be seen as a utility for the society...
+
+%and often captures more information than is needed to determine the winner
+We develop methods for computing the minimax- optimal alternative for scoring rules with partial preference information and partial information about the weights.
+
+%which queries to ask of which voters. 
+We discuss  heuristics that allow us to determine queries that quickly allow one to reduce minimax regret.
+
+ Our experimental results on randomly generated and real world data sets show...
 
@@
 %Incremental elicitation 
-% The paper is organized as follows.
+\medskip
+The paper is organized as follows.
+In Section \ref{sec:background} we provide the necessary background.
+We introduce the minimax criterion and in Section \ref{sec:mmr}.
+In Section \ref{sec:elicit} we provide an interactive elicitation protocol based on minima regret; finally in Section 
+\ref{sec:conclusions} we provide some final thoughts.
 
@@
 
-\section{Background}
+\section{Background}\label{sec:background}
 
+We introduce the basic concepts.
 We assume that there is a set $A$ of $m$ alternatives (for instance products, restaurants, movies, public projects, job candidates, etc.) and $n$ agents (voters); each agent is associated to a preference order.
@@
 \section[Minimax regret under partial profile and weight information]{Minimax regret under partial profile and weight \\ information}
+\label{sec:mmr}
 
@@
 
+Scoring rules are additively decomposable.
 Let $s(x; v_j,\w)=w_{v_j(x)}$ be the number of points that $x$ obtains in the ranking $v_j$ (see Equation \ref{eq:srule}), that is the weight of position $v_j(x)$.
@@
 
-\section{Interactive Elicitation}
+\section{Interactive Elicitation} \label{sec:elicit}
 
@@
 
-\section{Empirical Evaluation}
+\section{Empirical Evaluation} \label{sec:experiments}
 
@@
 
-% Conclusions
-% summary of contribution, more comments, future works.
+\section{Conclusions}  \label{sec:conclusions}
+%  Possible future works: manipulation,
 
+This is an awesome paper, it should be accepted right away and win a prize.
+
+% Acknowledgements: We thank the reviewers for comments helping to improve the paper. 
 %{\small

### 2019-02-05 draft.tex
1 more reference; improve MILP

@@
 \item Structure of the paper
-\item References: \cite{Cailloux2014}, \cite{Llamazares2013}, \cite{Konczak05}, \cite{Kalech2011}, \cite{Pini2009}
+\item References: \cite{Cailloux2014}, \cite{Llamazares2013}, \cite{Konczak05}, \cite{Kalech2011}, \cite{Pini2009}, \cite{Xia2008}
 \end{itemize}
@@
 % Add some general remarks about using minimax regret
-
 \subsection{Computation of minimax regret}
@@
 
-We now  exploit the decomposition of the score in terms of votes.
-The actual regret of choosing $x$ instead of $y$ can be written as:
+By exploiting the decomposition of the score in terms of votes, we write the actual regret of choosing $x$ instead of $y$ as:
 \[
@@
 \end{align*}
-Given our hypothesis, for all pairs of alternatives, there exists completions of the partial preferences $\ppref$ that maximize the PMR and that do not depend on the weights. 
+Given our hypothesis, for all pairs of alternatives, there exist completions of the partial preferences $\ppref$ that maximize the PMR and that do not depend on the weights. 
 That is, we can exhibit, for each voter $j$, a completion $v_j$ such that $\forall \w, \forall v'_j \in C(\ppref_j): [w_{v_j(y)} - w_{v_j(x)}] \geq [w_{v'_j(y)} - w_{v'_j(x)}]$.
@@
 
-By solving a sequence of pairwise max regret computation is possible to determine the minimax regret solution.
+By solving a sequence of pairwise max regret computations is possible to determine the minimax regret solution.
 Each PMR is computed using a linear program.
@@
 \begin{itemize}	
+	\item (will probably go to a later section, or to the appendix)
 	\item Mixed integer program to solve minimax regret without the convexity
@@
 
-Since the objective is to maximize pairwise regret
+Since the objective is to maximize pairwise regret...
 
@@
 %Variable $I^j$ associated with the constraint $0 \leq I \leq |U^j|$.
-
+ Finally, the following is the optimization problem that compute the value $\PMR$.
+ The variables are $w$, $V$, $I$,...
 \begin{align}
 \max & \sum_{l=1}^m  V_{l}^{j,+} - V_{l}^{j,-}\\
-\text{ s.t. } & \\
-& V_{l}^{j} \leq I^j \\
-& V_{l}^{j} \leq w_l \\
-& V_{l}^{j} \leq I^j \\
-& V_{l}^{j} \leq w_l 
+\text{ s.t. } & w \in W  \\
+& \sum_{l} I^{j}_{l} = 1 & \forall j \\
+& V_{l}^{j,+} \leq I^j  & \forall l,j \\
+& V_{l}^{j,+} \leq w_l & \forall l,j \\
+& V_{l}^{j,-} \geq w + I^j - 1 & \forall l,j \\
+& V_{l}^{j,-} \geq 0 & \forall l,j\\
 \end{align} 
+The optimization program can be solved by any suitable MILP solver.
 
@@
 
+%regret-based incremental elicitation method
 \begin{itemize}

### 2019-02-08 draft.tex
more mess into the tex

@@
 %\author{}
-\author{Olivier Cailloux \and Stefano Moretti \and Beatrice Napolitano \and Paolo Viappiani} %\affil{LIP6\\\email{paolo.viappiani@lip6.fr}
+\author{Olivier Cailloux  \and Beatrice Napolitano \and Paolo Viappiani} %\affil{LIP6\\\email{paolo.viappiani@lip6.fr}
 %\author{Olivier Cailloux} 
@@
 \item Novelty of the proposed method
-\item Structure of the paper
-\item References: \cite{Cailloux2014}, \cite{Llamazares2013}, \cite{Konczak05}, \cite{Kalech2011}, \cite{Pini2009}, \cite{Xia2008}
+\item References: \cite{Cailloux2014}, \cite{Llamazares2013}, \cite{Konczak05}, \cite{Kalech2011}, \cite{Pini2009}, relation to necessary and possible winners \cite{Xia2008}
 \end{itemize}
@@
 The traditional approach to social choice assumes that both the social function and the full preference orderings of the voters are expressed beforehand. 
-As noted by several authors requiring voters to express full preference orderings can be onerous (especially for large sets of alternatives)
+As noted by several authors requiring voters to express full preference orderings can be onerous (especially for 
+large sets of alternatives).
+Acquiring the necessary preference information may require a high cognitive and communication cost.
 
-% Given partial information about voter preferences, how does one choose a suitable approximate winner? 
-Scoring rules are a particularly common methods used to aggregate rankings and determine  a winner.
-The score can be seen as a utility for the society...
+ In many real situations, however, it may be necessary to reason with partial preferences, as some prefer- ences are not available and too expensive to obtain (with respect to a cognitive or economic cost).
+This observation has motivated a number of recent works on
 
-%and often captures more information than is needed to determine the winner
+In this paper we relax the traditional assumptions.
 We develop methods for computing the minimax- optimal alternative for scoring rules with partial preference information and partial information about the weights.
 
-%which queries to ask of which voters. 
-We discuss  heuristics that allow us to determine queries that quickly allow one to reduce minimax regret.
+We an adaptive utility elicitation
 
- Our experimental results on randomly generated and real world data sets show...
+We focus on positional scoring rules, that  are a particularly common methods used to aggregate rankings and determine  a winner.
+We also address the problem of elicitation, providing incremental elicitation methods to acquire relevant preference information.%The score can be seen as a utility for the society.
+%and often captures more information than is needed to determine the winner
+We discuss  heuristics that allow us to determine queries that quickly allow to reduce minimax regret.
 
-In this paper we propose an interactive adaptive protocol for eliciting both the voters preferences and the voting rule.
-At each step we need to decide whether we want to ask a question to the committee or to one of the agents (and to which agent in particular).
+%In this paper we propose an interactive adaptive protocol for eliciting both the voters preferences and the voting rule.
+%At each step we need to decide whether we want to ask a question to the committee or to one of the agents (and to which agent in particular).
+
 %We want to design a questioning strategy to minimize the worst regret in the long run.
@@
 
-\subsection{Related works}
-
+%\subsection{Related works}
 \paragraph{Uncertain scoring rules}
@@
 A social choice function $f : V \rightarrow 2^A$ associates a profile with a set of winners.
-Among the many possible social choice functions, we consider {\em positional scoring rules}, which attach weights to positions; an alternative obtains a score that depends on the rank obtained in each of the preference orders:
+Among the many possible social choice functions, we consider {\em positional scoring rules}, which attach weights to positions; 
+%A scoring rule associates each alternative to a score that is given by the sum of points obtained for each voter.
+an alternative obtains a score that depends on the rank obtained in each of the preference orders:
 \begin{align}
@@
 For instance, the weights can control the inclination to favour ``extreme'' alternatives (often at either the top or the bottom of the rankings) at the expenses of ``moderate'' alternatives (that are more consistently in the middle part of the rankings).
-
 However in general it can be difficult to set the weights in an appropriate way.
@@
 We propose to use the minimax regret as a decision criterion to determine a winner.
-Minimax regret [ref] has been used for making decisions under utility uncertainty and for preference elicitation [ref].
-Lu and Boutilier \cite{Lu2011} have adopted minimax regret ;
+Minimax regret \cite{Boutilier2006} has been used for making decisions under utility uncertainty and for preference elicitation.
+%Lu and Boutilier \cite{Lu2011} have adopted minimax regret.
 
@@
 
-A scoring rule associates each alternative to a score that is given by the sum of points obtained for each voter.
-
 Scoring rules are additively decomposable.
+%A scoring rule associates each alternative to a score that is given by the sum of points obtained for each voter.
 Let $s(x; v_j,\w)=w_{v_j(x)}$ be the number of points that $x$ obtains in the ranking $v_j$ (see Equation \ref{eq:srule}), that is the weight of position $v_j(x)$.
@@
 We also have numerical variables to represent the weights of the scoring rule.
-
-Since the objective is to maximize pairwise regret...
+%Since the objective is to maximize pairwise regret...
 
  The objective function can be written as:
- \[ \max \sum_{l=1}^n I^j_l w_l -  I^j_l w_l \]
+ \[ \max \sum_{l=1}^n B^j_l w_l -  B^j_l w_l \]
 
- We replace the multiplicative terms by new variables..
-\[ V_{l}^{j} \sim I^j_l w_l  \]
+We use enconding trick in order to solve the problem.
+We replace the multiplicative terms by new variables.
+\[ V_{l}^{j} \sim B^j_l w_l  \]
 
@@
 \begin{align*} 
-V_{l}^{j} \leq I^j \\
+V_{l}^{j} \leq B^j \\
 V_{l}^{j} \leq w_l
@@
  Finally, the following is the optimization problem that compute the value $\PMR$.
- The variables are $w$, $V$, $I$,...
+ The variables are $w$, $V$, $B$,...
 \begin{align}
-\max & \sum_{l=1}^m  V_{l}^{j,+} - V_{l}^{j,-}\\
+Z := \max & \sum_{l=1}^m  V_{l}^{j,+} - V_{l}^{j,-}\\
 \text{ s.t. } & w \in W  \\
-& \sum_{l} I^{j}_{l} = 1 & \forall j \\
-& V_{l}^{j,+} \leq I^j  & \forall l,j \\
+& \sum_{B=i_{1}}^{i_{2}} I^{j}_{l} = 1 & \forall j \\
+& V_{l}^{j,+} \leq B^j_{l}  & \forall l,j \\
 & V_{l}^{j,+} \leq w_l & \forall l,j \\
-& V_{l}^{j,-} \geq w + I^j - 1 & \forall l,j \\
+& V_{l}^{j,-} \geq w + B_{l}^j - 1 & \forall l,j \\
 & V_{l}^{j,-} \geq 0 & \forall l,j\\
@@
 The optimization program can be solved by any suitable MILP solver.
+
+\begin{claim}
+The $\PMR$ is computed using the above optimization problem.
+\end{claim}
 
@@
 	\item Minimax regret can be used to guide the elicitation process
-	\item As termination condition of elicitation, we can check whether minimax regret is lower than a threshold. If optimality is derived, we can perform elicitation until minimax regret drops to zero.
-	\item At each step, the system need to decide whether to ask a question to one of the agents or ask a question to the chair about the voting rule
+	\item As termination condition of elicitation, we can check whether minimax regret is lower than a threshold. If we wish optimality, we can perform elicitation until minimax regret drops to zero.
+	\item At each step, the system needs to decide whether to ask a question to one of the agents or ask a question to the chair about the voting rule
 	\item Type of questions that we can ask to the chair:
@@
 
+\paragraph{Query types}
+
+Questions to the voters: it is natural to consider comparison queries asking to compare two alternatives
+
+Questions to the committee: we consider questions that refine our knowledge about the weighting vectors $w$.
+
 \paragraph{Query methods}
-
+We consider different strategies to determine the next question to ask given the current information.
 %{\em Some ideas: decompose the regret into two components, one due to $\w$ and one due to $\pprofile$, and ask a question to the chair / or to one of the agents depending on which is highest}
@@
 Ask a question to compare $x$ with $y$ to an agent.
+
+% Determine the part of ``regret'' due to uncertainty in $w$
+% Determine the part of ``regret' due to uncertainty in $p$
 
@@
 % We can stop elicitation when minimax regret is sufficiently small.
+We test the elicitation protocols in randomly generated datasets and real datasets. % (sushi and iris).
 We evaluate the proposed method using the following simulated protocol.
-
-We test the elicitation protocols in randomly generated datasets and real datasets (sushi and iris).
 
@@
 %  Possible future works: manipulation, 
+We have proposed the use of minimax regret as a way to determine a winner in a robust way when considering uncertainty on both the voting rule and the voters' preferences.
 
-This is an awesome paper, it should be accepted right away and win a prize.
+Our experimental results on randomly generated and real world data sets show that regret-based elicitation is effective and allow to find a near optimal consensus choice in a limited number of steps.
+%Our interactive elicitation methods are shown to be effective in simulations.
 
@@
 
-\subsection{Profile completion, again}
- %{\bf \em TODO: still have to find out exactly how to do it}
-
- We introduce a set integer variables $I^i$, one for each position $i$.
- Let $U^j$ be, for the agents in $A^-$, the alternatives that, in the partial order $\succ^p_j$ of some agent $j \in A^-$, are incomparable with $x$ and $y$.
- \[ \sum_{l=1}^n I^j_l w_l \]
- Variable $I^j$ associated with the constraint $0 \leq I \leq |U^j|$.
-
- We provide the following MIP (mixed integer linear program).
-
-% Use linearization techniques to handle the multiplications...
-
-%\section{Even more fun}
-%We can consider different types of questions: asking to compare a pair of alternatives, asking about top-k alternatives.
+%\subsection{Profile completion, again}
+% %{\bf \em TODO: still have to find out exactly how to do it}
+% 
+% We introduce a set integer variables $I^i$, one for each position $i$.
+% Let $U^j$ be, for the agents in $A^-$, the alternatives that, in the partial order $\succ^p_j$ of some agent $j \in A^-$, are incomparable with $x$ and $y$.
+% \[ \sum_{l=1}^n I^j_l w_l \]
+% Variable $I^j$ associated with the constraint $0 \leq I \leq |U^j|$.
+% 
+% We provide the following MIP (mixed integer linear program).
+% 
+%% Use linearization techniques to handle the multiplications...
+%
+%
+%%\section{Even more fun}
+%%We can consider different types of questions: asking to compare a pair of alternatives, asking about top-k alternatives.
 %

### 2019-02-09 draft.tex
a bit of cleanup

@@
 \begin{itemize}
-\item General motivation: need to deal with partially specified preferences and as well partially specified voting rules
-\item Focus on positional scoring rules
-\item Robust decision criterion: minimax regret
-\item Incremental elicitation of preferences can help mitigating the cognitive and communication costs
-\item Novelty of the proposed method
 \item References: \cite{Cailloux2014}, \cite{Llamazares2013}, \cite{Konczak05}, \cite{Kalech2011}, \cite{Pini2009}, relation to necessary and possible winners \cite{Xia2008}
@@
 
+%General motivation: need to deal with partially specified preferences and as well partially specified voting rules
 Aggregation of preference information is a central task in many computer systems (recommender systems, search engines, etc).
@@
 In this paper we relax the traditional assumptions.
+
+%Robust decision criterion: minimax regret
 We develop methods for computing the minimax- optimal alternative for scoring rules with partial preference information and partial information about the weights.
 
-We an adaptive utility elicitation
+%Incremental elicitation of preferences can help mitigating the cognitive and communication costs
+We adopt an adaptive utility elicitation framrwork
 
+%Focus on positional scoring rules
 We focus on positional scoring rules, that  are a particularly common methods used to aggregate rankings and determine  a winner.
@@
 We have proposed the use of minimax regret as a way to determine a winner in a robust way when considering uncertainty on both the voting rule and the voters' preferences.
+Our experimental results on randomly generated and real world data sets show that regret-based elicitation is effective and allow to find a near optimal consensus choice in a limited number of steps.
 
-Our experimental results on randomly generated and real world data sets show that regret-based elicitation is effective and allow to find a near optimal consensus choice in a limited number of steps.
-%Our interactive elicitation methods are shown to be effective in simulations.
-
+Future works include considering the effect of strategic agents, and considering probabilistic methods.
 % Acknowledgements: We thank the reviewers for comments helping to improve the paper. 

### 2019-02-11 draft.tex
adding conclusions

@@
 Social choice deals with the problem of determining a consensus choice from the preferences of different agents (voters).
-In the classical setting, the social choice rule is fixed beforehand; indeed many works analyze the properties of different rules (including axiomatic treatments) in order to justify the choice of specific social choice functions.
-Moreover, it is usually assumed that the preferences of the voters are known completely.
+In the classical setting, the voting rule is fixed beforehand, and the full preference information is provided by the voters.
 
-%We argue that it is possible that the committee wants to precise some preferences about the aggregation.
-In this draft we depart from the classic view by considering that both preferences and the social choice rule can be only partially specified.
-We note that previous works have considered either partial preferences or a partially specified aggregation, but we do not know of any work considering both sources of uncertainty at the same time.
+As social choice moves to the web, the
+
+the need for relaxing the assumptions
+
+In this paper we provide a method for approximate winner determination and an incremental elicitation protocol based on minimax regret.
+
+We then show how minimax regret can be used to drive the elicitation
+
+We develop several query strategies that  focus simultaneously on reduction of relevant preference and voting rule uncertainty.
+
 %We consider that the committee wants to express preferences for some voting rules
-In this draft we provide a method for approximate winner determination and an incremental elicitation protocol based on minimax regret. 
+
 \end{abstract}
@@
 \section{Introduction}
-
-\begin{itemize}
-\item References: \cite{Cailloux2014}, \cite{Llamazares2013}, \cite{Konczak05}, \cite{Kalech2011}, \cite{Pini2009}, relation to necessary and possible winners \cite{Xia2008}
-\end{itemize}
+% indeed many works analyze the properties of different rules (including axiomatic treatments) in order to justify the choice of specific social choice functions. 
+%Moreover, it is usually assumed that the preferences of the voters are known completely.
 
@@
 
- In many real situations, however, it may be necessary to reason with partial preferences, as some prefer- ences are not available and too expensive to obtain (with respect to a cognitive or economic cost).
-This observation has motivated a number of recent works on
+In many real situations, however, it may be necessary to reason with partial preferences, as some preferences are not available and too expensive to obtain (with respect to a cognitive or economic cost).
 
-In this paper we relax the traditional assumptions.
+In this paper we depart from the classic view by considering that both preferences and the social choice rule can be only partially specified.
 
-%Robust decision criterion: minimax regret
+This observation has motivated a number of recent works on preference elicitation, including several works on social choice with partial profiles.
+
 We develop methods for computing the minimax- optimal alternative for scoring rules with partial preference information and partial information about the weights.
 
+%We argue that it is possible that the committee wants to precise some preferences about the aggregation.s
+% Incremental elicitation of preferences is critical to easing the cognitive and communication cost for users 
+%In this paper we provide a method for approximate winner determination and an incremental elicitation protocol based on minimax regret. 
+%In this paper we relax the traditional assumptions.
+
 %Incremental elicitation of preferences can help mitigating the cognitive and communication costs
-We adopt an adaptive utility elicitation framrwork
+%We adopt an adaptive utility elicitation framrwork
 
@@
 We discuss  heuristics that allow us to determine queries that quickly allow to reduce minimax regret.
+
+Possible and necessary winner determination: in typical settings, there will be no necessary winner and too many possible winners.
+
+While previous works have considered either partial preferences or a partially specified aggregation, but we do not know of any work considering both sources of uncertainty at the same time.
+
+% We must engage in simultaneous elictation of the rule and of the preferences.
 
@@
 \ref{sec:conclusions} we provide some final thoughts.
+
+\begin{itemize}
+\item References: \cite{Cailloux2014}, \cite{Llamazares2013}, \cite{Konczak05}, \cite{Kalech2011}, \cite{Pini2009}, relation to necessary and possible winners \cite{Xia2008}.
+Also this reference: \cite{Naamani-Dery2015}.
+\end{itemize}
 
@@
 
+% Theoretical complexity of partial completition
+
 % We are given  $\ppref_i $,  a partial preference.
@@
 
-\section[Minimax regret under partial profile and weight information]{Minimax regret under partial profile and weight \\ information}
+\section[Minimax regret under partial profile and weight information]{Minimax regret under partial profile and weight information}
 \label{sec:mmr}
 
+%Robust decision criterion: minimax regret
+Minimax regret \cite{Savage1954} is a decision criterion that has been used for robust optimization under data uncertainty \cite{Kouvelis1997} and as well in decision-making with uncertain utility values  \cite{Salo2001,Boutilier2006}.
+
+% we use max regret to measure the quality
+
+% This leads to interesting tradeoffs in elicitation
 %The regret-minimizing alternative may not be a possible winner for some voting rules.
+% the value of certain preference information is often not worth the cost of obtaining it.
 The weights of a scoring rule can model different preferences of the committee. 
@@
 This paper extends the work of  to the simultaneous presence of uncertainty in the agents' preferences and uncertainty in the weights.
+
+Intuitively, the quality of a proposed alternative $a$ is how far from optimal $a$  could be in the worst case, given the current knowledge about the voting rule and about the voters' preferences.
 
@@
 By recommending the alternative associated with minimax regret, we can provide a recommendation that gives worst-case guarantees, giving some robustness in face of uncertainty (due to both not knowing the agents' preferences and the weights used in the aggregation).
+
+Notice that if $MMR(\pprofile, W)=0$, then $x^{*}(\pprofile,W)$  is a necessary co-winner.
 
@@
 
-%regret-based incremental elicitation method
-\begin{itemize}
-	\item Minimax regret can be used to guide the elicitation process
-	\item As termination condition of elicitation, we can check whether minimax regret is lower than a threshold. If we wish optimality, we can perform elicitation until minimax regret drops to zero.
-	\item At each step, the system needs to decide whether to ask a question to one of the agents or ask a question to the chair about the voting rule
-	\item Type of questions that we can ask to the chair:
-	bound queries (Is this alternative among your top-k most preferred items?), comparison queries (do you prefer alternative x or alternative y?).
-\end{itemize}
+If the available information is too limited, the potential error associated with the robust winner (i.e., its max regret) may be unacceptable.
 
+Minimax regret can be used to guide the elicitation process.
+As termination condition of elicitation, we can check whether minimax regret is lower than a threshold. If we wish optimality, we can perform elicitation until minimax regret drops to zero.
+
+At each step, the system needs to decide whether to ask a question to one of the agents or ask a question to the chair about the voting rule
+
+In this Section, we describe different strategies to determine informative queries to ask next, with the goal of reducing $\MMR(\pprofile,W)$ quickly.
+
+We propose an regret-based incremental elicitation method...
+
+\paragraph{Query types}
+
+\paragraph{Strategies}
+
+We develop some elicitation strategies for simultaneous elicitation of voters' preferences and of the scoring rule.
 Starting from some initial partial knowledge, our goal is to learn both the scoring rule function and the agents' preferences.
@@
 
+%Type of questions that we can ask to the chair:	bound queries (Is this alternative among your top-k most preferred items?), comparison queries (do you prefer alternative x or alternative y?).
+
+% we discuss the different forms of queries and develop several query strategies 
 \paragraph{Query types}
@@
 \section{Conclusions}  \label{sec:conclusions}
-%  Possible future works: manipulation, 
-We have proposed the use of minimax regret as a way to determine a winner in a robust way when considering uncertainty on both the voting rule and the voters' preferences.
-Our experimental results on randomly generated and real world data sets show that regret-based elicitation is effective and allow to find a near optimal consensus choice in a limited number of steps.
+%  We have proposed the use of minimax regret as a means of robust winner determination to support the informational approximation of voting rules, as well as to guide the process of incremental elicitation of voter preferences.
+%In this paper we have proposed the use of minimax regret as a way to determine a winner in a robust way when considering uncertainty on both the voting rule and the voters' preferences.
 
-Future works include considering the effect of strategic agents, and considering probabilistic methods.
+In this paper we have considered a  social choice setting with partial  information about the voter's  
+preferences and as well a partially specified voting rule.
+We have proposed the use of minimax regret as a means of robust winner determination in this setting, and as well as to guide the process of incremental elicitation of voter preferences.
+Our experimental results on randomly generated and real world data sets show that regret-based elicitation is effective and allow to find a near-optimal consensus choice in a limited number of steps.
+%Regret-based elicitation allows to determine near-optimal winners using only few information about the voters' preferences.
+We mention some  important directions for future works.
+First of all, further development of elicitation strategies, considering alternative heuristics, is an important direction. 
+Second, we are interested in extending elicitation of voting rules going beyond scoring rules.
+A third direction is that of considering probabilistic methods for elicitation.
+Finally, we are interested in studying the effect of strategic agents, that may not report their true preferences.
+% distribution-free heuristics
+
 % Acknowledgements: We thank the reviewers for comments helping to improve the paper. 

### 2019-02-11 draft.tex
yet more bibliography; some minor edits

@@
 
-As social choice moves to the web, the
-
-the need for relaxing the assumptions
+%As social choice moves to the web, the
+%the need for relaxing the assumptions of classical social choice
 
@@
 
-We then show how minimax regret can be used to drive the elicitation
+We then show how minimax regret can be used to drive the elicitation in order to ask informative queries in order to
 
@@
 \paragraph{Query types}
+We distinguish between queries asked to the voters and questions asked to the chair.
 
-\paragraph{Strategies}
+Questions to the voters: it is natural to consider comparison queries asking to compare two alternatives
+
+Another common type or queries are {\em top-k}, asking to each voter his $k$ most alternatives.
+
+Questions to the committee: we consider questions that refine our knowledge about the weighting vectors $w$.
+
+In particular, we want to acquire constraints of the type:
+\[ w_{i} - w_{+1i} \geq \lambda (w_{i+1} - w_{i+2}) \]
+
+\paragraph{Elicitation strategies}
 
@@
 % we discuss the different forms of queries and develop several query strategies
-\paragraph{Query types}
-
-Questions to the voters: it is natural to consider comparison queries asking to compare two alternatives
-
-Questions to the committee: we consider questions that refine our knowledge about the weighting vectors $w$.
 

### 2019-02-11 draft.tex
various edits

@@
 Social choice deals with the problem of determining a consensus choice from the preferences of different agents (voters).
-In the classical setting, the voting rule is fixed beforehand, and the full preference information is provided by the voters.
+In the classical setting, the voting rule is fixed beforehand and full preference information is provided by the voters. 
+Recently, the assumption of full preference information has been questioned by a number of researchers and 
+number of frameworks for vote elicitation have been proposed.
 
-%As social choice moves to the web, the
-%the need for relaxing the assumptions of classical social choice
+In this paper we go one step further and we assume that both the voting rule and the voters preferences are partially specified.
+Focusing on positional scoring rules, we assume that the chair %is not able to give the definition of the rule but 
+is able to answer simple questions  requiring to pick a winner from a specific  example profile.
+Moreover, the preferences of the voters are incrementally acquired by asking comparison queries.
 
-In this paper we provide a method for approximate winner determination and an incremental elicitation protocol based on minimax regret.
-
-We then show how minimax regret can be used to drive the elicitation in order to ask informative queries in order to
-
-We develop several query strategies that  focus simultaneously on reduction of relevant preference and voting rule uncertainty.
-
-%We consider that the committee wants to express preferences for some voting rules
-
+We propose a method  for robust approximate winner determination in this setting with minimax regret. 
+We then provide an interactive elicitation protocol based on minimax regret
+%We then show how minimax regret can be used to drive the elicitation in order to ask informative queries in order to a
+and develop several query strategies that interleave questions to the chair and questions to the voters in order to acquire the most relevant information about the preferences and voting rule.
 \end{abstract}
@@
 
+%Recently, the assumption of full a has been questioned by a number of researchers
 In many real situations, however, it may be necessary to reason with partial preferences, as some preferences are not available and too expensive to obtain (with respect to a cognitive or economic cost).
+This observation has motivated a number of recent works on preference elicitation, including several works on social choice with partial profiles.
+
+We argue that it is possible that the committee wants to precise some preferences about the aggregation.s
 
@@
 
-This observation has motivated a number of recent works on preference elicitation, including several works on social choice with partial profiles.
+We develop methods for computing the minimax-optimal alternative for scoring rules with partial preference information and partial information about the weights.
 
-We develop methods for computing the minimax- optimal alternative for scoring rules with partial preference information and partial information about the weights.
-
-%We argue that it is possible that the committee wants to precise some preferences about the aggregation.s
+%
 % Incremental elicitation of preferences is critical to easing the cognitive and communication cost for users 
@@
 
+%We consider that the committee wants to express preferences for some voting rules
+
+We develop several query strategies that  focus simultaneously on reduction of relevant preference and voting rule uncertainty.
 % We must engage in simultaneous elictation of the rule and of the preferences.
@@
 %Incremental elicitation 
-\medskip
 The paper is organized as follows.
@@
 We assume that there is a set $A$ of $m$ alternatives (for instance products, restaurants, movies, public projects, job candidates, etc.) and $n$ agents (voters); each agent is associated to a preference order.
-The goal of the voters is to make a consensus choice, that is to select a ``winner'' given voter rankings.
+The goal of the voters is to make a consensus choice, to select a ``winner'' given voter rankings.
 

### 2019-02-11 draft.tex
edits in introduction

@@
 In many situations, such as in group recommender systems, the goal is to find a consensus choice.
+It is natural to look at methods from social choice and see how they can be adapted for group decision-making in a computerized setting.
 
 The traditional approach to social choice assumes that both the social function and the full preference orderings of the voters are expressed beforehand. 
-As noted by several authors requiring voters to express full preference orderings can be onerous (especially for 
-large sets of alternatives).
-Acquiring the necessary preference information may require a high cognitive and communication cost.
+As noted by several authors requiring voters to express full preference orderings can be prohibitively costly (in term of cognitive and communication cost), especially for  large sets of alternatives.
+This observation has motivated a number of recent works \cite{Xia2008,Kalech2011,Lu2011,Naamani-Dery2015} on preference elicitation in a voting context.
+% including several works on social choice with partial profiles.
 
 %Recently, the assumption of full a has been questioned by a number of researchers
-In many real situations, however, it may be necessary to reason with partial preferences, as some preferences are not available and too expensive to obtain (with respect to a cognitive or economic cost).
-This observation has motivated a number of recent works on preference elicitation, including several works on social choice with partial profiles.
+%In many real situations, however, it may be necessary to reason with partial preferences, as some preferences are not available and too expensive to obtain (with respect to a cognitive or economic cost).
 
-We argue that it is possible that the committee wants to precise some preferences about the aggregation.s
+In a similar way,  Cailloux and Endriss \cite{Cailloux2014} have argued that it might not always be realistic to assume that a voting rule is known precisely.
+Indeed, it is possible that the chair may have some preferences over the desired aggregation method, but may still be not able to formalize the voting rule upfront.
 
+%We argue that it is possible that the committee wants to precise some preferences about the aggregations.
 In this paper we depart from the classic view by considering that both preferences and the social choice rule can be only partially specified.
-
 We develop methods for computing the minimax-optimal alternative for scoring rules with partial preference information and partial information about the weights.

### 2019-02-13 draft.tex
ijcai formatting

@@
 In many situations, such as in group recommender systems, the goal is to find a consensus choice.
-It is natural to look at methods from social choice and see how they can be adapted for group decision-making in a computerized setting.
+It is therefore natural to look at methods from social choice and see how they can be adapted for group decision-making in a computerized setting.
 
@@
 As noted by several authors requiring voters to express full preference orderings can be prohibitively costly (in term of cognitive and communication cost), especially for  large sets of alternatives.
-This observation has motivated a number of recent works \cite{Xia2008,Kalech2011,Lu2011,Naamani-Dery2015} on preference elicitation in a voting context.
+This observation has motivated a number of recent works \cite{Xia2008,Kalech2011,Lu2011,Naamani-Dery2015} have considered social choice with partially specified preferences and incremental elicitation of voters preferences.
 % including several works on social choice with partial profiles.
@@
 %In many real situations, however, it may be necessary to reason with partial preferences, as some preferences are not available and too expensive to obtain (with respect to a cognitive or economic cost).
-
-In a similar way,  Cailloux and Endriss \cite{Cailloux2014} have argued that it might not always be realistic to assume that a voting rule is known precisely.
+On the other hand, in several situations it may not be easy to precisely define the voting rule.
+In particular, when considering positional scoring rules, it is possible to derive dominance relations (akin to stochastic dominance) that allow to eliminate some alternatives since they will be less preferred than another one for any instantiation of the weights \cite{Stein1994}.Among others, Llamazares and Pe{\~{n}}a \cite{Llamazares2013} have considered  the problem of dealing with underspecified weights in positional scoring rules.
+Cailloux and Endriss \cite{Cailloux2014} have proposed elicitation methods for based on partial orders.
 Indeed, it is possible that the chair may have some preferences over the desired aggregation method, but may still be not able to formalize the voting rule upfront.
+%argued that it might not always be realistic to assume that a voting rule is known precisely.
 
 %We argue that it is possible that the committee wants to precise some preferences about the aggregations.
-In this paper we depart from the classic view by considering that both preferences and the social choice rule can be only partially specified.
+In this paper we consider that both preferences and the social choice rule can be only partially specified.
 We develop methods for computing the minimax-optimal alternative for scoring rules with partial preference information and partial information about the weights.
+While previous works have considered either partial preferences or a partially specified aggregation, but we do not know of any work considering both sources of uncertainty at the same time.
 
-%
 % Incremental elicitation of preferences is critical to easing the cognitive and communication cost for users 
@@
 %In this paper we relax the traditional assumptions.
+%Incremental elicitation of preferences can help mitigating the cognitive and communication costs
 
-%Incremental elicitation of preferences can help mitigating the cognitive and communication costs
-%We adopt an adaptive utility elicitation framrwork
-
-%Focus on positional scoring rules
 We focus on positional scoring rules, that  are a particularly common methods used to aggregate rankings and determine  a winner.
@@
 
-Possible and necessary winner determination: in typical settings, there will be no necessary winner and too many possible winners.
-
-While previous works have considered either partial preferences or a partially specified aggregation, but we do not know of any work considering both sources of uncertainty at the same time.
+% the value of certain preference information is often not worth the cost of obtaining it.
 
 %We consider that the committee wants to express preferences for some voting rules
-
 We develop several query strategies that  focus simultaneously on reduction of relevant preference and voting rule uncertainty.
@@
 
+Possible and necessary winner determination: in typical settings, there will be no necessary winner and too many possible winners.
+
 %\subsection{Related works}
@@
 A number of works have dealt with the problem of reasoning with incompletely specified aggregation functions.
-In particular, when considering positional scoring rules, it is possible to derive dominance relations (akin to stochastic dominance) that allow to eliminate some alternatives since they will be less preferred than another one for any instantiation of the weights \cite{Stein1994}.
+%In particular, when considering positional scoring rules, it is possible to derive dominance relations (akin to stochastic dominance) that allow to eliminate some alternatives since they will be less preferred than another one for any instantiation of the weights \cite{Stein1994}.
 More recently the characterization of methods for aggregating the uncertainty over the scoring vectors has been studied in \cite{Viappiani2018}.
-We also note that the elicitation methods based on minimax regret described in \cite{Boutilier2006} (and in many other recent papers), while not specifically targeted to scoring rules, can be easily adapted (from a technical point of view) to elicit the scoring vector from a committee.
 
-\paragraph{Incomplete profiles}
+%We also note that the elicitation methods based on minimax regret described in \cite{Boutilier2006} (and in many other recent papers), while not specifically targeted to scoring rules, can be easily adapted (from a technical point of view) to elicit the scoring vector from a committee.
+
+%\paragraph{Incomplete profiles}
 %In this setting, the system knows a partial preference profile $\ppref$ 
@@
 
-Lu and Boutilier \cite{Lu2011} assume that the preferences of the voters are only partially known (while the social choice function is known and fixed in advance; it is assumed to be decomposable) and
- propose to use minimax regret to produce a robust approximation.
-Each alternative is associated with a max regret value that measures how far from optimal it could be in the worst case given any completion of the partial profile.
-The computation of max regret is facilitated by the fact the score is decomposable.
+%Lu and Boutilier \cite{Lu2011} assume that the preferences of the voters are only partially known (while the social choice function is known and fixed in advance; it is assumed to be decomposable) and
+% propose to use minimax regret to produce a robust approximation.
+%Each alternative is associated with a max regret value that measures how far from optimal it could be in the worst case given any completion of the partial profile.
+%The computation of max regret is facilitated by the fact the score is decomposable.
 
@@
 We also assume that the weights of the scoring rule are only partially specified.
-Without loss of generality, we assume $w_1=1$ and $w_m=0$.
+We consider a monotonic non-increasing sequence of weights: $w_{1} \geq w_{2} \geq \ldots \geq w_{m}$. Without loss of generality, we assume $w_1=1$ and $w_m=0$
+%Without loss of generality, we assume $w_1=1$ and $w_m=0$.
 The preferences of the chair are encoded with linear constraints, for instance one may state
@@
 
-%Robust decision criterion: minimax regret
-Minimax regret \cite{Savage1954} is a decision criterion that has been used for robust optimization under data uncertainty \cite{Kouvelis1997} and as well in decision-making with uncertain utility values  \cite{Salo2001,Boutilier2006}.
-
-% we use max regret to measure the quality
-
 % This leads to interesting tradeoffs in elicitation
 %The regret-minimizing alternative may not be a possible winner for some voting rules.
-% the value of certain preference information is often not worth the cost of obtaining it.
 The weights of a scoring rule can model different preferences of the committee. 
@@
 
-\medskip
-The quality of an alternative can be quantified by considering the maximum regret with respect to an adversary that can choose the instantiation of both a complete profile (extending the known preferences of the agents) and of the scoring vectors (associated to the preferences of the committee).
+%\medskip
+%The quality of an alternative can be quantified by considering the maximum regret with respect to an adversary that can choose the instantiation of both a complete profile (extending the known preferences of the agents) and of the scoring vectors (associated to the preferences of the committee).
 
 We propose to use the minimax regret as a decision criterion to determine a winner.
+Minimax regret \cite{Savage1954} is a decision criterion that has been used for robust optimization under data uncertainty \cite{Kouvelis1997} and as well in decision-making with uncertain utility values  \cite{Salo2001,Boutilier2006}.
 Minimax regret \cite{Boutilier2006} has been used for making decisions under utility uncertainty and for preference elicitation.
-%Lu and Boutilier \cite{Lu2011} have adopted minimax regret.
+Lu and Boutilier \cite{Lu2011} have adopted minimax regret for winner determination in social choice with
+the preferences of the voters that are only partially known (while the social choice function is known and fixed in advance; it is assumed to be decomposable).
 
 This paper extends the work of  to the simultaneous presence of uncertainty in the agents' preferences and uncertainty in the weights.
-
 Intuitively, the quality of a proposed alternative $a$ is how far from optimal $a$  could be in the worst case, given the current knowledge about the voting rule and about the voters' preferences.
@@
 	\item (will probably go to a later section, or to the appendix)
-	\item Mixed integer program to solve minimax regret without the convexity
- 	\item Approximations ?
 \end{itemize}
@@
 
-Questions to the voters: it is natural to consider comparison queries asking to compare two alternatives
-
+Questions to the voters: it is natural to consider comparison queries asking to compare two alternatives.
 Another common type or queries are {\em top-k}, asking to each voter his $k$ most alternatives.
@@
 % we discuss the different forms of queries and develop several query strategies 
-
-\paragraph{Query methods}
+%\paragraph{Query methods}
 We consider different strategies to determine the next question to ask given the current information.
@@
 We test the elicitation protocols in randomly generated datasets and real datasets. % (sushi and iris).
+
 We evaluate the proposed method using the following simulated protocol.
+First of all, we randomly generate the true preferences of the users (i.e. the linear orders) and the weights associated with the committee's scoring rule.
+For each of the elicitation strategy, we simulate an elicitation session.
+We compare the performance  of the different strategies of Section \ref{sec:elicit} with respect to decrement in max regret and with respect to the real loss.
 
-\begin{itemize}
- \item Randomly generate the true preferences of the users (i.e. the linear orders) and the weights associated with the committee's preferences on the scoring rule
- \item For each of the elicitation strategy, simulate the elicitation by asking the queries selected by the strategy.
+%For each of the elicitation strategy, we simulate the elicitation by asking the queries selected by the strategy.
+ %\item 
+%\%end{itemize}
+We performed tests with different values of $m$ (number of alternatives) and $n$ (number of agents); test with different population sizes, different number of alternatives, etc.
 
- \item Compare performance with respect to decrement in max regret, real loss
-\end{itemize}
+We experimented with both settings that assume a convex sequences of weights, and others without this assumption.
 
-Test with different values of $m$ (number of alternatives) and $n$ (number of agents); test with different population sizes, different number of alternatives, etc.
-
-Make one test assuming convex sequences of weights, and others without this assumption.
-
-Comparison between our interleaved strategy and a strategy, still based on minimax regret  but that is not interleaved; also compare to some heuristic baselines.
+%Comparison between our interleaved strategy and a strategy, still based on minimax regret  but that is not interleaved; also compare to some heuristic baselines.
 

### 2019-02-15 draft.tex
improving MIP optimization

@@
+\newif\ifijcai
+ \ijcaitrue  %UNCOMMENT this to have the ijcai formatting / COMMENT for draft format
+
+\newif\ifappendix
+%\appendixtrue %COMMENT to remove appendix
+\ifijcai
+ 	\input{ijcai_preamble} 
+	\author{Olivier Cailloux$^1$	\and Beatrice Napolitano$^1$\and Paolo Viappiani$^{2}$
+	\affiliations $^1$ LAMSADE, CNRS and Dauphine University, PSL, Paris, France\\ $^2$ LIP6, UMR 7606, CNRS and Sorbonne Universit\'e, Paris, France
+	\emails \{first, second\}@lamsade.fr, paolo.viappiani@lip6.fr
+}
+\else
 	\documentclass[12pt]{article}
@@
 	\geometry{a4paper}
+	\usepackage{graphicx}
 	%\usepackage{authblk}
+	\usepackage{booktabs}
+	\usepackage{algorithm, algpseudocode}
+	\algrenewcommand\algorithmicrequire{\textbf{Input:}}
+	\algrenewcommand\algorithmicensure{\textbf{Output:}}
+	\author{Various Authors}
+\fi
 
-\usepackage{graphicx}
+\usepackage{algorithm, algpseudocode}
 \usepackage{amsmath,amssymb,enumerate,amsthm}
@@
 \usepackage{mathrsfs}
-\usepackage{algorithm, algpseudocode}
+
 \usepackage{bm}
@@
 \usepackage{xcolor}
-\usepackage{booktabs}
 
@@
 
-\algrenewcommand\algorithmicrequire{\textbf{Input:}}
-\algrenewcommand\algorithmicensure{\textbf{Output:}}
 \newtheorem{claim}{Claim}
@@
 \newtheorem{definition}{Definition}
+\newtheorem{example}{Example}
 
 \title{Robust Winner Determination and Simultaneous Elicitation of Scoring Rules and Preferences}
-%\author{}
-\author{Olivier Cailloux  \and Beatrice Napolitano \and Paolo Viappiani} %\affil{LIP6\\\email{paolo.viappiani@lip6.fr}
+%\author{Olivier Cailloux  \and Beatrice Napolitano \and Paolo Viappiani}
+
+%\affil{LIP6\\\email{paolo.viappiani@lip6.fr}
 %\author{Olivier Cailloux} 
@@
 On the other hand, in several situations it may not be easy to precisely define the voting rule.
-In particular, when considering positional scoring rules, it is possible to derive dominance relations (akin to stochastic dominance) that allow to eliminate some alternatives since they will be less preferred than another one for any instantiation of the weights \cite{Stein1994}.Among others, Llamazares and Pe{\~{n}}a \cite{Llamazares2013} have considered  the problem of dealing with underspecified weights in positional scoring rules.
+In particular, when considering positional scoring rules, it is possible to derive dominance relations (akin to stochastic dominance) that allow to eliminate some alternatives since they will be less preferred than another one for any instantiation of the weights \cite{Stein1994}.
+Among others, Llamazares and Pe{\~{n}}a \cite{Llamazares2013} have considered  the problem of dealing with underspecified weights in positional scoring rules.
 Cailloux and Endriss \cite{Cailloux2014} have proposed elicitation methods for based on partial orders.
@@
 We develop methods for computing the minimax-optimal alternative for scoring rules with partial preference information and partial information about the weights.
-While previous works have considered either partial preferences or a partially specified aggregation, but we do not know of any work considering both sources of uncertainty at the same time.
+While previous works have considered either partial preferences or a partially specified aggregation, we do not know of any work considering both sources of uncertainty at the same time.
 
@@
 We focus on positional scoring rules, that  are a particularly common methods used to aggregate rankings and determine  a winner.
-We also address the problem of elicitation, providing incremental elicitation methods to acquire relevant preference information.%The score can be seen as a utility for the society.
+We also address the problem of elicitation, providing incremental elicitation methods to acquire relevant preference information. 
+%The score can be seen as a utility for the society.
 %and often captures more information than is needed to determine the winner
 We discuss  heuristics that allow us to determine queries that quickly allow to reduce minimax regret.
-
+We develop several query strategies that  focus simultaneously on reduction of relevant preference and voting rule uncertainty.
 % the value of certain preference information is often not worth the cost of obtaining it.
@@
 %We consider that the committee wants to express preferences for some voting rules
-We develop several query strategies that  focus simultaneously on reduction of relevant preference and voting rule uncertainty.
+
 % We must engage in simultaneous elictation of the rule and of the preferences.
@@
 
-%We want to design a questioning strategy to minimize the worst regret in the long run.
-A questioning strategy indicates, given a partial profile and a set of feasible weights, which question to ask next.
+%We want to design a questioning strategy to minimize the worst regret in the long run
+% A questioning strategy indicates, given a partial profile and a set of feasible weights, which question to ask next.
 A question is either a query to the voter $i$ about her preference relation $\succ_i$ or a query to the committee about the feasible weights.
@@
 
-Possible and necessary winner determination: in typical settings, there will be no necessary winner and too many possible winners.
+% we define a model that allows simultaneous elicitation of the voting rule and user preferences, making appropriate tradeoffs be- tween the two types of information
 
 %\subsection{Related works}
-\paragraph{Uncertain scoring rules}
-A number of works have dealt with the problem of reasoning with incompletely specified aggregation functions.
+\paragraph{Text to be placed somewhere:}
+%A number of works have dealt with the problem of reasoning with incompletely specified aggregation functions.
 %In particular, when considering positional scoring rules, it is possible to derive dominance relations (akin to stochastic dominance) that allow to eliminate some alternatives since they will be less preferred than another one for any instantiation of the weights \cite{Stein1994}.
 More recently the characterization of methods for aggregating the uncertainty over the scoring vectors has been studied in \cite{Viappiani2018}.
+
+\medskip
+Using {\em maximum regret} to quantify the worst-case error, the alternative that minimize this error is selected as winner, providing us with a form of robust optimization.
+
+\medskip
+Possible and necessary winner determination \cite{Xia2008}: in typical settings, there will be no necessary winner and too many possible winners.
 
@@
 
-\section{Background}\label{sec:background}
+\section{Social choice with partial information}\label{sec:background}
 
-We introduce the basic concepts.
+In this Section we introduce some basic concepts.
 We assume that there is a set $A$ of $m$ alternatives (for instance products, restaurants, movies, public projects, job candidates, etc.) and $n$ agents (voters); each agent is associated to a preference order.
-The goal of the voters is to make a consensus choice, to select a ``winner'' given voter rankings.
+The goal of the voters is to make a consensus choice, in order to select a ``winner'' given voter rankings.
 
@@
 With a little abuse of notation, we will use the term profile to refer to either $\profile$ or to the preference relations, depending on the context.
+
 Let $V$ be the set of possible preference profiles (the cartesian product of $n$ linear orders).
-
 A social choice function $f : V \rightarrow 2^A$ associates a profile with a set of winners.
@@
 s(x; \profile, \w) = \sum_{j=1}^{n} w_{v_j(x)}
-= \sum_{i=1}^{m} \alpha_i w_i . \label{eq:srule}
+= \sum_{i=1}^{m} \alpha^{x}_i w_i . \label{eq:srule}
 \end{align}
-where $\alpha_i$ is the number of times that alternative $x$ was ranked in the $i$-th position.
-The vector $(w_1,\ldots,w_m)$ is called the scoring vector. We assume that the weights constitute a monotonic sequence: $w_{1} \geq w_{2} \geq \ldots \geq w_{m}$.
-
-\medskip
+where $\alpha^{x}_i$ is the number of times that alternative $x$ was ranked in the $i$-th position.
+The winner is the alternative with highest score.
+The vector $(w_1,\ldots,w_m)$ is called the scoring vector.
+%We assume that the weights constitute a monotonic sequence: $w_{1} \geq w_{2} \geq \ldots \geq w_{m}$.
 In this work we want to reason about partial preference information.
-A partial preference  is encoded by a partial order $\ppref_i$  of voter $i$;
-we assume that preference information is truthful, i.e. $a \ppref_i b \implies a \pref_i b$.
+A partial preference  is encoded by a partial order $\ppref_i$  of voter $i$; in this work we assume that preference information is truthful, i.e. $a \ppref_i b \implies a \pref_i b$.
+An incomplete profile is a set of partial votes  $\textbf{p}=(\ppref_1,\ldots,\ppref_n)$.
 
@@
 Let $C(\ppref_i)$ be the set of completions of $\ppref_i$, that is the set of all complete rankings that extend $\ppref_i$.
-An incomplete profile is a set of partial votes %$\textbf{p}=(p_1,\ldots,p_n)$.
-$\textbf{p}=(\ppref_1,\ldots,\ppref_n)$.
-
 We let $C(\textbf{p})=C(\ppref_1)\times \ldots \times C(\ppref_n)$ be the set of complete profiles extending $p$.
@@
 We also assume that the weights of the scoring rule are only partially specified.
-We consider a monotonic non-increasing sequence of weights: $w_{1} \geq w_{2} \geq \ldots \geq w_{m}$. Without loss of generality, we assume $w_1=1$ and $w_m=0$
-%Without loss of generality, we assume $w_1=1$ and $w_m=0$.
-The preferences of the chair are encoded with linear constraints, for instance one may state
-that $w_2>0.5$.
-We assume the weight sequence to be convex, that means that the difference between the weight of the first position and the weight of the second position is at least as much as the difference between the weights of the second and third positions, etc.
-\[ \forall i \in \{1,\ldots,n\} \;\; w_i - w_{i+1} \geq w_{i+1}-w_{i+2} \iff  w_i - 2 w_{i+1} + w_{i+2} \geq 0 \]
-This is a constraint often used when aggregating rankings in sport competitions.
+We consider a monotonic non-increasing sequence of weights: $w_{1} \geq w_{2} \geq \ldots \geq w_{m}$; this is a natural assumption, as it is better to be ranked first than second, second than third, etc.
+Without loss of generality, we assume $w_1=1$ and $w_m=0$.
+
+The weights of a scoring rule can model different preferences of the committee. 
+For instance, the weights can control the inclination to favour ``extreme'' alternatives (often at either the top or the bottom of the rankings) at the expenses of ``moderate'' alternatives (that are more consistently in the middle part of the rankings).
+However, we argue that in general it can be difficult to set the weights in an appropriate way.
+
+An important class of scoring rule is the one composed of weights that are a convex sequence, meaning that the difference between the weight of the first position and the weight of the second position is at least as much as the difference between the weights of the second and third positions, etc.
+\begin{align} \forall i \in \{1,\ldots,n-2\} \;\; & w_i - w_{i+1} \geq w_{i+1}-w_{i+2} \iff  \\
+& w_i - 2 w_{i+1} + w_{i+2} \geq 0 \label{eq:convexity}
+\end{align}
+The constraint above is often used when aggregating rankings in sport competitions.
 We use $\mathcal{W}$ to denote the set of convex weight vectors.
 
+Additionally the chair (the person or the organization that is supervising the voting process) may be able to specify additional preferences about how the social choice function should behave.
+In this work we assume that preferences of the chair are encoded with linear constraints on the vector $\w$, relating the value of the weights of different positions.
+Of course it may be difficult for real decision makers to state preferences about the voting rule in such an abstract way, unless perhaps in some limited cases (a specific instance of these preferences may consist in giving upper or lower bound on the value of $w_{i}$ for position $i$).
+These additional preferences can be elicited by asking questions about concrete profiles, for instance, by showing a complete profile of a small synthetic election and asking who should be elected in this case.
+We discuss queries asked to the chairs and strategies to select queries later in Section \ref{sec:elicit}.
+
 % Theoretical complexity of partial completition
-
 % We are given  $\ppref_i $,  a partial preference.
@@
 
-\section[Minimax regret under partial profile and weight information]{Minimax regret under partial profile and weight information}
+\section[Minimax regret under partial profile and weight information]{
+Robust winner determination}
 \label{sec:mmr}
@@
 %The regret-minimizing alternative may not be a possible winner for some voting rules.
-The weights of a scoring rule can model different preferences of the committee. 
-For instance, the weights can control the inclination to favour ``extreme'' alternatives (often at either the top or the bottom of the rankings) at the expenses of ``moderate'' alternatives (that are more consistently in the middle part of the rankings).
-However in general it can be difficult to set the weights in an appropriate way.
-
 In this paper, we consider a setting where both the voters' preferences and the preferences of the chair about the voting rule are incomplete.
-
 %\medskip
@@
 
-We propose to use the minimax regret as a decision criterion to determine a winner.
+As a decision criterion to determine a winner, we propose to use the minimax regret. 
 Minimax regret \cite{Savage1954} is a decision criterion that has been used for robust optimization under data uncertainty \cite{Kouvelis1997} and as well in decision-making with uncertain utility values  \cite{Salo2001,Boutilier2006}.
-Minimax regret \cite{Boutilier2006} has been used for making decisions under utility uncertainty and for preference elicitation.
+%Minimax regret \cite{Boutilier2006} has been used for making decisions under utility uncertainty and for preference elicitation.
 Lu and Boutilier \cite{Lu2011} have adopted minimax regret for winner determination in social choice with
-the preferences of the voters that are only partially known (while the social choice function is known and fixed in advance; it is assumed to be decomposable).
+the preferences of the voters that are only partially known, while the social choice function is known and fixed in advance.
 
-This paper extends the work of  to the simultaneous presence of uncertainty in the agents' preferences and uncertainty in the weights.
+This paper tackles the more challenging setting of the simultaneous presence of uncertainty in the agents' preferences and uncertainty in the weights.
 Intuitively, the quality of a proposed alternative $a$ is how far from optimal $a$  could be in the worst case, given the current knowledge about the voting rule and about the voters' preferences.
@@
 %A scoring rule associates each alternative to a score that is given by the sum of points obtained for each voter.
-Let $s(x; v_j,\w)=w_{v_j(x)}$ be the number of points that $x$ obtains in the ranking $v_j$ (see Equation \ref{eq:srule}), that is the weight of position $v_j(x)$.
+Let $s(x; v_j,\w)=w_{v_j(x)}$ be the number of points that $x$ obtains in the ranking $v_j$ (see Equation \ref{eq:srule}), that is given by weight of position $v_j(x)$.
 Obviously we have 
@@
 \begin{align*}
-\PMR(x,y; \pprofile, W) &= \max_{\w \in W} \max_{\profile \in C(\pprofile)} [ s(y; \profile,\w) - s(x; \profile,\w) ] = \\
-&=  \max_{\w \in W} \sum_{j=1}^{n} \max_{v_j \in C(\succ_j^p)} [s(y; v_j,\w) - s(x; v_j,\w)]=\\
-&=  \max_{\w \in W} \sum_{j=1}^{n} \max_{v_j \in C(\succ_j^p)} [w_{v_j(y)} - w_{v_j(x)}] \\
+& \PMR(x,y; \pprofile, W) = \max_{\w \in W} \max_{\profile \in C(\pprofile)} [ s(y; \profile,\w) - s(x; \profile,\w) ] = \\
+& =  \max_{\w \in W} \sum_{j=1}^{n} \max_{v_j \in C(\succ_j^p)} [s(y; v_j,\w) - s(x; v_j,\w)]=\\
+& =  \max_{\w \in W} \sum_{j=1}^{n} \max_{v_j \in C(\succ_j^p)} [w_{v_j(y)} - w_{v_j(x)}] \\
 \end{align*}
@@
  \item $j \in A^-$: If we know that agent $j$ prefers $x$ to $y$ then the adversary will place as few alternatives as possible between $x$ and $y$.
- We define $U$ as the set of alternatives that are incomparable with $x$ and $y$ according to $\ppref_i$.
+Define $U$ as the set of alternatives that are incomparable with $x$ and $y$ according to $\ppref_i$.
 Since weights are assumed to be convex, the adversary will place all alternatives in $U$ as better than $x$.
@@
 In summary, some best completion $\pref$ satisfies two properties: (1) for all $c \pinc x$, $c \pref x$; and (2) for all $c \pinc y$, if not $c \pref x \pref y$ then $y \pref c$.
-These two properties are intuitively understandable by observing that maximizing the PMR requires placing $x$ as low as possible, hence the first property; and $y$ as high as possible, hence the second property, with the exception that sometimes it is not possible to satisfy both desires and noting that the first desire is more important by convexity of the weights.
+These two properties are intuitively understandable by observing that maximizing the PMR requires placing $x$ as low as possible, hence the first property; and $y$ as high as possible, hence the second property, with the exception that sometimes it is not possible to satisfy both goals and noting that the first goal is more important by convexity of the weights.
 A proof that this reasoning is correct is in \cref{sec:prfCompl}.
@@
 The PMR can be written as:
-\[ \PMR(x,y) = \sum_{j=1}^n w_{\hat{v}_i(y)} - w_{\hat{v}_i(x)} 
-= \sum_{i=1}^m \alpha_i w_i \]
-where the coefficient $\alpha_i$ is the number of times $y$ is in the $i-th$ position minus the number of times $x$ is the in the $i$-th position in the rankings of the completed profile $\hat{v}$:
-\[ \alpha_{i} = \sum_{j=1}^{n}  I[\hat{v}_{j}(y)=i] - I[\hat{v}_{j}(x)=i]\]
+\[ \PMR(x,y; \pprofile, W) = \sum_{j=1}^n w_{\hat{v}_i(y)} - w_{\hat{v}_i(x)} 
+= \sum_{i=1}^m (\alpha_{i}^{y} - \alpha_{i}^{x}) w_i \]
+where the coefficient $ (\alpha_{i}^{y} - \alpha_{i}^{x})$ is the number of times $y$ is in position $i$ minus the number of times $x$ is the in position $i$ in the rankings of the completed profile $\hat{v}$:
+$\alpha_{i}^{x} = \sum_{j=1}^{n}  I[\hat{v}_{j}(x)=i]$.
+%\[ \alpha_{i} = \sum_{j=1}^{n}  I[\hat{v}_{j}(y)=i] - I[\hat{v}_{j}(x)=i]\]
 where $I$ is the indicator function.
-The linear program is then the following:
-\begin{align}
-\max & \sum_{i=1}^m \alpha_i w_{i}\\
-\text{ s.t. } & w \in W
-\end{align}
+Then, what we have to to compute pairwise max regret is to compute the solution of the following linear program :
+\begin{align*}
+\PMR(x,y; \pprofile,W) = \max_{\w} & \sum_{i=1}^m \alpha_i w_{i}\\
+\text{ s.t. } & \w \in W \\
+& \text{Equation } (\ref{eq:convexity})
+\end{align*}
+The result of the optimization is the value of the pairwise max regret $\PMR$.
 
 \subsection{Minimax regret without the convex assumption}
+{\em (will probably go to a later section, or to the appendix) }
 
-\begin{itemize}	
-	\item (will probably go to a later section, or to the appendix)
-\end{itemize}
-
+\medskip
 Let $\hat{v}_i$ be the linear order extending $p_i$ according to the above procedure (described in \cite{Lu2011}).
 Then PMR can be written as follows:
-\[ \PMR(x,y; \pprofile, W) = \max_{\w \in W} \Big \{ \max_{v_j \in C(\succ_j^p)} [w_{v_j(y)} - w_{v_j(x)}]  + \sum_{j \in A^+, j \in A^?} [w_{\hat{v}_j(y)} - w_{\hat{v}_j(x)}] \Big \} \]
+\begin{align*}
+ &\PMR(x,y; \pprofile, W) =\\ 
+ &\max_{\w \in W} \Big \{ \max_{v_j \in C(\succ_j^p)} [w_{v_j(y)} \!-\! w_{v_j(x)}]  \!+\!	 \sum_{j \in A^+ \cup  A^?} [w_{\hat{v}_j(y)} \!-\! w_{\hat{v}_j(x)}] \Big \} 
+ \end{align*}
 
-We compute pairwise maximum regret by considering binary variables to represent optimization choices related to where to position the alternatives.
+%We compute pairwise maximum regret by considering binary variables $\{ B_{i} \}_{i=1,\ldots,m}$ to represent optimization choices related to where to position the alternatives.
+We introduce two set of binary variables $B^{+}_{i,j}$ and $B^{-}_{i,j}$  for each voter $i$ and each position $j$.
+The variable $B_{i,j}^{+}$ encodes the fact that the alternative $y$ is placed in position $j$ in the ranking of agent $i$; while  $B_{i,j}^{-}$ encodes the position of the alternative $x$.
+
 We also have numerical variables to represent the weights of the scoring rule.
+Since each alternative needs to be placed exactly in one place for each agent, we adopt the constraints
+$\sum_{i=1}^{m} B_{i,j}^{+} = 1$ and $\sum_{i=1}^{m} B_{i,j}^{-} = 1$.
 %Since the objective is to maximize pairwise regret...
 
- The objective function can be written as:
- \[ \max \sum_{l=1}^n B^j_l w_l -  B^j_l w_l \]
+The score of alternative $y$ can be written as $\sum_{i=1}^{n} \sum_{j=1}^{m} w_{j} B_{i,j}^{+}$.
+Our objective function is now:
+ \[ \max \sum_{i=1}^{n} \sum_{j=1}^{m} B_{i,j}^{+} w_j- B_{i,j}^{-}  w_j \]
 
-We use enconding trick in order to solve the problem.
-We replace the multiplicative terms by new variables.
-\[ V_{l}^{j} \sim B^j_l w_l  \]
+We use integer programming enconding tricks in order to linearize the problem formulation.
+We introduce yet another set of variables  $V_{i,j}^{+} $  and $V_{i,j}^{-}$ % the multiplicative terms by new variables.
+and we introduce constraints so that $V_{i,j}^{+} = B^{+}_{i,j} w_j$.
+To impose the desired behavior, we set $V_{l}^{j} \leq B^j $ and $V_{l}^{j} \leq w_l$.
+%\begin{align*} 
+%V_{l}^{j} \leq B^j \\
+%V_{l}^{j} \leq w_l
+%\end{align*}
+%The expression $B^j_l w_l$ evaluates to $w_l$ if $I^j_l = 1$, and to $0$ otherwise.
 
-To impose the desired behavior:
-\begin{align*} 
-V_{l}^{j} \leq B^j \\
-V_{l}^{j} \leq w_l
-\end{align*}
-The expression $I^j_l w_l$ evaluates to $w_l$ if $I^j_l = 1$, and to $0$ otherwise.
-
-We write $w \in W$ as a shourtcut to represent the constraints that the weights are chosen to be in the feasible set.
 %Variable $I^j$ associated with the constraint $0 \leq I \leq |U^j|$.
  Finally, the following is the optimization problem that compute the value $\PMR$.
- The variables are $w$, $V$, $B$,...
+ %The decision variables are $w$, $V$, $B$,...
+
+We therefore obtain the following mixed integer linear program:
 \begin{align}
-Z := \max & \sum_{l=1}^m  V_{l}^{j,+} - V_{l}^{j,-}\\
+\max & \sum_{i=1}^n  \sum_{j=1}^m  V_{i,j}^{+} - V_{i,j}^{-}\\
 \text{ s.t. } & w \in W  \\
-& \sum_{B=i_{1}}^{i_{2}} I^{j}_{l} = 1 & \forall j \\
-& V_{l}^{j,+} \leq B^j_{l}  & \forall l,j \\
-& V_{l}^{j,+} \leq w_l & \forall l,j \\
-& V_{l}^{j,-} \geq w + B_{l}^j - 1 & \forall l,j \\
-& V_{l}^{j,-} \geq 0 & \forall l,j\\
+& \sum_{i=t_{1}}^{t_{2}} B_{i,j}^{+} = 1 & \forall j \\
+& V_{i,j}^{+} \leq B_{i,j}^{+}  & \forall i,j \\
+& V_{i,j}^{+} \leq w_j & \forall i,j \\
+& V_{i,j}^{-} \geq w + B_{i,j}^{-} - 1 & \forall i,j \\
+& V_{i,j}^{-} \geq 0 & \forall i,j
 \end{align} 
+%We write $w \in W$ as a shourtcut to represent the constraints that the weights are chosen to be in the feasible set.
+
 The optimization program can be solved by any suitable MILP solver.
@@
 
-If the available information is too limited, the potential error associated with the robust winner (i.e., its max regret) may be unacceptable.
+We propose an incremental elicitation method based on minimax regret.
+At each step, the system may either ask a question to one of the agents, or ask a question to the chair about the voting rule. 
+The goal is to acquire relevant information to reduce minimax regret as quick as possible.
+%Minimax regret can be used to guide the elicitation process.
+As termination condition of elicitation, we can check whether minimax regret is lower than a threshold; if we wish optimality, we can perform elicitation until minimax regret drops to zero.
 
-Minimax regret can be used to guide the elicitation process.
-As termination condition of elicitation, we can check whether minimax regret is lower than a threshold. If we wish optimality, we can perform elicitation until minimax regret drops to zero.
-
-At each step, the system needs to decide whether to ask a question to one of the agents or ask a question to the chair about the voting rule
-
-In this Section, we describe different strategies to determine informative queries to ask next, with the goal of reducing $\MMR(\pprofile,W)$ quickly.
-
-We propose an regret-based incremental elicitation method...
+The remainder of this Section is structured as follows.
+First of all, we discuss the different types of queries that can be asked to the voters and to the chair, and the way responses are handled.
+Then, we describe different strategies to determine informative queries to ask next, with the goal of reducing $\MMR(\pprofile,W)$ quickly.
 
@@
 We distinguish between queries asked to the voters and questions asked to the chair.
+As {\em questions asked to the voters}, it is natural to consider comparison queries asking to compare two alternatives.
+Another common type or queries are {\em top-k}, asking to each voter his $k$ most alternatives.
+The effect of a response to a query asked to the voters, is to augment our knowledge about the voters rankings, thus augmenting the partial profile $\pprofile$. 
+If voter $i$ answers a comparison query stating that alternative $a$ is preferred to $b$, then the partial order $\succ^{p}_{i}$ is augmented with $a \succ^{p}_{i} b$ and by transitive closure.
 
-Questions to the voters: it is natural to consider comparison queries asking to compare two alternatives.
-Another common type or queries are {\em top-k}, asking to each voter his $k$ most alternatives.
-
-Questions to the committee: we consider questions that refine our knowledge about the weighting vectors $w$.
+A bit more discussion is need about {\em questions asked to the chair}.
+A query asked to the chair has the goal of refining our knowledge about the scoring rule;
+a response to a query gives us a constraint on the weighting vectors $w$.
 
 In particular, we want to acquire constraints of the type:
-\[ w_{i} - w_{+1i} \geq \lambda (w_{i+1} - w_{i+2}) \]
+\[ w_{j} - w_{j+1} \geq \lambda (w_{j+1} - w_{j+2}) \] 
+for $j \in \{1,\ldots,m-2\}$.
+This constraint relates the difference between the importance of positions $i$ and $i+1$ with the difference between positions $i+1$ and $i+2$.
+While perhaps in some cases the decision maker may be able to state pferences of this kind, we argue that a more concrete way is better.
+Notice that the constraint above is equivalent to $w_{i} - (\lambda+1) w_{i+1} + \alpha w_{i+2} \geq 0$.
+%We conjecture that preferences of this kind are relatively easy to state
+%(``do you think that the difference between the importance of position $i$ and $i+1$ is at least the difference between positions $i+1$ and $i+2$ ?'').
+We present them a profile representing the situation described by the query and then deduce its answer from the selected winner. 
+%We argue that it may be cognitively easier to ask to pick a winner from a profile, rather than answering an abstract question.
+Therefore we generate profiles specifically in such a way that user answers gives us the kind of constraint that we want to acquire.
+We provide a systematic way to construct such profiles.  %that reflects the situation outlined by the query for two alternatives and the others are not better than them.
+
+We consider a profile where a fictious alternative $a$ is $1$ time in position $i$, and $\lambda$ times 
+in position $i+2$ and another fictitious alternative, $b$, is ranked $\lambda+1$ times in position $i+1$.
+To have a valid profile, we need to include other alternatives.
+We add other alternatives in such a way that they are dominated by $a$ or $b$. 
+(if the chair answers an alternative that is either $a$ or $b$ this is a signale that the model is incorrect).
+
+\begin{example}
+Suppose our query strategy suggests us to ask the committee the following query:
+\[ w_{2} - w_{3} \geq 2(w_{3} - w_{4}) \]
+In order to impose this constraints,
+It is straightforward to see that we want the  chair of the committee to choose between $a$ or $b$ with the following rank distribution:
+\[
+\begin{array}{ccccc}
+& 1^\circ
+& 2^\circ
+& 3^\circ
+& 4^\circ \\
+\cmidrule{2-5}
+a & 0& 1& 0& 2 \\
+b& 0& 0& 3& 0 \\
+\end{array}
+\]
+In order to obtain a valid profile, we need to include a number of other alternatives in such a way that the are dominated by $a$ and $b$.
+The following profile is exactly what we want.
+%We add voters in order to increase the number of times $a$ and $b$ are ranked at first position.
+Please note we must maintain these scheme, so every add of a position to the ranking of $a$ must correspond to the same in the ranking of $b$.
+
+\[
+\begin{array}{cccccc}
+v_1& v_2& v_3 & v_4& v_5& v_6 \\
+\midrule 
+a& b& c & d& a& b \\
+c& a& d& c& b& a \\
+b& d& b& b& d& c \\
+d& c& a& a& c& d \\
+\end{array}
+\]
+giving the rank distribution (number of times each alternatives is ranked first, second, etc): 
+\[
+\begin{array}{ccccc}
+& 1^\circ& 2^\circ& 3^\circ& 4^\circ \\
+\cmidrule{2-5}
+a & 2& 2& 0& 2 \\
+b& 2& 1& 3& 0 \\
+c& 1& 2& 1& 2 \\
+d& 1& 1& 2& 2 \\
+\end{array}
+\]
+Indeed alternative $c$ and $d$ are dominated and they cannot win for any instantiation of the weights; this can be seen by comparing the cumulative ranks (see  \cite{Stein1994}).
+\[
+\begin{array}{ccccc}
+& \geq 1^\circ
+& \geq 2^\circ
+& \geq 3^\circ
+& \geq 4^\circ \\
+\cmidrule{2-5}
+a & 2 & 4& 4& 6 \\
+b & 2 & 3& 6& 6 \\
+c& 1& 3& 4& 6 \\
+d& 1& 2& 4& 6 \\
+\end{array}
+\]
+\end{example}
+
+\vspace{1cm}
+{\bf Complete section}
+\vspace{1cm}
+***
 
@@
 
+% unless $\MMR=0$ we ask a question that reduce uncertainty
+
 \section{Empirical Evaluation} \label{sec:experiments}
+
+\begin{figure}[t]
+\begin{center}PLACEHOLDER\end{center}
+\vspace{3.5cm}
+\caption{Minimax regret reduction in our experiments (synthetic dataset).}
+\end{figure}
+
+\begin{figure}[t]
+\begin{center}PLACEHOLDER\end{center}
+\vspace{3.5cm}
+\caption{Minimax regret reduction in our experiments (real dataset).}
+\end{figure}
 
@@
 For each of the elicitation strategy, we simulate an elicitation session.
-We compare the performance  of the different strategies of Section \ref{sec:elicit} with respect to decrement in max regret and with respect to the real loss.
+%Queries are posed to simulated users, that answer accor
+%We compare the performance  of the different strategies of Section \ref{sec:elicit} with respect to decrement in max regret and with respect to the real loss.
+We measure the effectiveness of our strategies of Section \ref{sec:elicit} by examining regret reduction as a function of the number of queries.
 
 %For each of the elicitation strategy, we simulate the elicitation by asking the queries selected by the strategy.
- %\item 
-%\%end{itemize}
 We performed tests with different values of $m$ (number of alternatives) and $n$ (number of agents); test with different population sizes, different number of alternatives, etc.
@@
 \section{Conclusions}  \label{sec:conclusions}
-%  We have proposed the use of minimax regret as a means of robust winner determination to support the informational approximation of voting rules, as well as to guide the process of incremental elicitation of voter preferences.
-%In this paper we have proposed the use of minimax regret as a way to determine a winner in a robust way when considering uncertainty on both the voting rule and the voters' preferences.
 
+% integrated preference elicitation methodology
 In this paper we have considered a  social choice setting with partial  information about the voter's  
 preferences and as well a partially specified voting rule.
-We have proposed the use of minimax regret as a means of robust winner determination in this setting, and as well as to guide the process of incremental elicitation of voter preferences.
+We have proposed the use of minimax regret as a means of robust winner determination in this setting, and as well as to guide the process of simultaneous elicitation of preferences and voting rule.
 Our experimental results on randomly generated and real world data sets show that regret-based elicitation is effective and allow to find a near-optimal consensus choice in a limited number of steps.
+%The detection of optimal or near-optimal product recommendation is generally possible with little concept and utility information
 %Regret-based elicitation allows to determine near-optimal winners using only few information about the voters' preferences.
@@
 \bibliography{biblio}
-\bibliographystyle{plain} 
+\bibliographystyle{named}
+%\bibliographystyle{plain} 
 %}
@@
 \pagebreak
+\ifappendix
 \appendix
@@
 \end{itemize}
-
+\fi
 \end{document}

### 2019-02-15 draft.tex
improving MIP optimization

@@
 where the coefficient $ (\alpha_{i}^{y} - \alpha_{i}^{x})$ is the number of times $y$ is in position $i$ minus the number of times $x$ is the in position $i$ in the rankings of the completed profile $\hat{v}$:
-$\alpha_{i}^{x} = \sum_{j=1}^{n}  I[\hat{v}_{j}(x)=i]$.
+$\alpha_{i}^{x} = \sum_{j=1}^{n}  I[\hat{v}_{j}(x)=i]$ where $I$ is the indicator function.
 %\[ \alpha_{i} = \sum_{j=1}^{n}  I[\hat{v}_{j}(y)=i] - I[\hat{v}_{j}(x)=i]\]
-where $I$ is the indicator function.
 Then, what we have to to compute pairwise max regret is to compute the solution of the following linear program :
 \begin{align*}
-\PMR(x,y; \pprofile,W) = \max_{\w} & \sum_{i=1}^m \alpha_i w_{i}\\
+\PMR(x,y; \pprofile,W) = \max_{\w} & \sum_{i=1}^m (\alpha_{i}^{y} - \alpha_{i}^{x}) w_{i}\\
 \text{ s.t. } & \w \in W \\
@@
  \end{align*}
-
+%Note that the second addendum inside the max do not depend on the choice of $\w$.
+Consider the two addendum inside the outer ``max''. 
+The first addendum is concern with positioning of alternatives $x$ and $y$ for voters in $A^{-}$for which we know that $x$ is preferred to $y$.
+The second addendum is concerned with voters in $A^{+}$ and $A^{?}$.
+We rewrite the second addendum as:
+\begin{align*}
+\sum_{j \in A^+ \cup  A^?} [w_{\hat{v}_j(y)} \!-\! w_{\hat{v}_j(x)}] 
+= \sum_{i = 1}^{m} (\hat{\alpha}_{i}^{y} - \hat{\alpha}_{i}^{x}) w_{i}
+\end{align*}
+where $\hat{\alpha}_{i}^{x}$ is the number of times that $x$ is ranked  in position $i$  considering the profile $\hat{v}$ of voters in $A^+ \cup  A^?$.
 %We compute pairwise maximum regret by considering binary variables $\{ B_{i} \}_{i=1,\ldots,m}$ to represent optimization choices related to where to position the alternatives.
-We introduce two set of binary variables $B^{+}_{i,j}$ and $B^{-}_{i,j}$  for each voter $i$ and each position $j$.
-The variable $B_{i,j}^{+}$ encodes the fact that the alternative $y$ is placed in position $j$ in the ranking of agent $i$; while  $B_{i,j}^{-}$ encodes the position of the alternative $x$.
+
+We now show how to optimize $\PMR$.
+In addition to variables $\{ w_{j} \}_{j=1,\ldots,m}$ (one for each position) we need to employ several additional decision variables.
+We introduce two set of binary variables $B^{+}_{i,j}$ and $B^{-}_{i,j}$  for each position $i$ and for each voter $j$.
+Variable $B_{i,j}^{+}$ encodes the fact that the alternative $y$ is placed in position $i$ in the ranking of agent $j$; while  $B_{i,j}^{-}$ encodes the same thing for alternative $x$.
 
@@
 
-The score of alternative $y$ can be written as $\sum_{i=1}^{n} \sum_{j=1}^{m} w_{j} B_{i,j}^{+}$.
-Our objective function is now:
- \[ \max \sum_{i=1}^{n} \sum_{j=1}^{m} B_{i,j}^{+} w_j- B_{i,j}^{-}  w_j \]
+The score of alternative $y$ can be written as $\sum_{i = 1}^{m} \hat{\alpha}_{i}^{y} + \sum_{i=1}^{n} \sum_{j=1}^{m} w_{j} B_{i,j}^{+}$.
+The objective function is now:
+ \[ \max \sum_{i = 1}^{m} (\hat{\alpha}_{i}^{y} - \hat{\alpha}_{i}^{x}) w_{i}  \sum_{i=1}^{n} \sum_{j=1}^{m} B_{i,j}^{+} w_j- B_{i,j}^{-}  w_j \]
 
@@
 We introduce yet another set of variables  $V_{i,j}^{+} $  and $V_{i,j}^{-}$ % the multiplicative terms by new variables.
-and we introduce constraints so that $V_{i,j}^{+} = B^{+}_{i,j} w_j$.
-To impose the desired behavior, we set $V_{l}^{j} \leq B^j $ and $V_{l}^{j} \leq w_l$.
+and we enforce that $V_{i,j}^{+} = B^{+}_{i,j} w_j$ by setting constraints $V_{l}^{j} \leq B^j $ and $V_{l}^{j} \leq w_l$.
 %\begin{align*} 
@@
 \begin{align}
-\max & \sum_{i=1}^n  \sum_{j=1}^m  V_{i,j}^{+} - V_{i,j}^{-}\\
-\text{ s.t. } & w \in W  \\
+\max & \sum_{i=1}^m  [(\hat{\alpha}_{i}^{y} - \hat{\alpha}_{i}^{x}) w_{i}] +
+ \sum_{i=1}^m \sum_{j=1}^n  [V_{i,j}^{+} - V_{i,j}^{-}]\\
+\text{ s.t. } & \w \in W  \\
 & \sum_{i=t_{1}}^{t_{2}} B_{i,j}^{+} = 1 & \forall j \\
+& \sum_{i=t_{1}}^{t_{2}} B_{i,j}^{-} = 1 & \forall j \\
 & V_{i,j}^{+} \leq B_{i,j}^{+}  & \forall i,j \\
@@
 \[ w_{j} - w_{j+1} \geq \lambda (w_{j+1} - w_{j+2}) \] 
-for $j \in \{1,\ldots,m-2\}$.
-This constraint relates the difference between the importance of positions $i$ and $i+1$ with the difference between positions $i+1$ and $i+2$.
-While perhaps in some cases the decision maker may be able to state pferences of this kind, we argue that a more concrete way is better.
-Notice that the constraint above is equivalent to $w_{i} - (\lambda+1) w_{i+1} + \alpha w_{i+2} \geq 0$.
+for $j \in \{1,\ldots,m-2\}$, relating the difference between the importance of positions $i$ and $i+1$ with the difference between positions $i+1$ and $i+2$.
+While perhaps in some cases the decision maker may be able to state preferences of this kind, we argue that a more concrete way is better.
+Notice that the constraint above is equivalent to 
+$w_{i} - (\lambda+1) w_{i+1} + \lambda w_{i+2} \geq 0$
+and to $w_{i} + \lambda w_{i+2} \geq  (\lambda+1) w_{i+1}$.
 %We conjecture that preferences of this kind are relatively easy to state
@@
 (if the chair answers an alternative that is either $a$ or $b$ this is a signale that the model is incorrect).
+
+\vspace{1cm}
+{\bf Complete section:} give a precise algorithm for completing the profile
+\vspace{1cm}
 
@@
 
-\vspace{1cm}
-{\bf Complete section}
-\vspace{1cm}
-***
-
 \paragraph{Elicitation strategies}
@@
 We test the elicitation protocols in randomly generated datasets and real datasets. % (sushi and iris).
-
 We evaluate the proposed method using the following simulated protocol.

### 2019-02-18 draft.tex
minor edits

@@
 \newif\ifappendix
-%\appendixtrue %COMMENT to remove appendix
+\appendixtrue %COMMENT to remove appendix
 \ifijcai
@@
 	\author{Olivier Cailloux$^1$	\and Beatrice Napolitano$^1$\and Paolo Viappiani$^{2}$
-	\affiliations $^1$ LAMSADE, CNRS and Dauphine University, PSL, Paris, France\\ $^2$ LIP6, UMR 7606, CNRS and Sorbonne Universit\'e, Paris, France
+	\affiliations $^1$ LAMSADE, UMR 7243, CNRS and Universit\'e Paris Dauphine, PSL Research University, Paris, France\\ $^2$ LIP6, UMR 7606, CNRS and Sorbonne Universit\'e, Paris, France
 	\emails \{first, second\}@lamsade.fr, paolo.viappiani@lip6.fr
@@
 \newcommand{\ppref}{\succ^\text{p}}%partial pref
+\newcommand{\nppref}{\nsucc^\text{p}}%negated partial pref
+
 %Thanks to https://tex.stackexchange.com/q/154549
@@
 \newrelation{\myRgood}{R^X}
-\newrelation{\pinc}{Q^\text{p}}%partial pref, complement (incomparable)
+\newrelation{\pinc}{\!\parallel\!}%partial pref, complement (incomparable)
+%\newrelation{\pinc}{Q^\text{p}}%partial pref, complement (incomparable)
 
@@
 \newtheorem{claim}{Claim}
+\newtheorem{prop}{Proposition}
 \newtheorem{corollary}{Corollary}
@@
 In the classical setting, the voting rule is fixed beforehand and full preference information is provided by the voters. 
-Recently, the assumption of full preference information has been questioned by a number of researchers and 
-number of frameworks for vote elicitation have been proposed.
+Recently, the assumption of full preference information has been questioned by a number of researchers and several methods for eliciting voters information have been proposed.
 
 In this paper we go one step further and we assume that both the voting rule and the voters preferences are partially specified.
-Focusing on positional scoring rules, we assume that the chair %is not able to give the definition of the rule but 
-is able to answer simple questions  requiring to pick a winner from a specific  example profile.
+Focusing on positional scoring rules, we assume that the chair, while  not able to give a precise definition of the rule, is capable of answering simple questions  requiring to pick a winner from a specific  example profile.
 Moreover, the preferences of the voters are incrementally acquired by asking comparison queries.
@@
 We then provide an interactive elicitation protocol based on minimax regret
-%We then show how minimax regret can be used to drive the elicitation in order to ask informative queries in order to a
-and develop several query strategies that interleave questions to the chair and questions to the voters in order to acquire the most relevant information about the preferences and voting rule.
+and develop several query strategies that interleave questions to the chair and questions to the voters in order to acquire the most relevant information in order to quickly converge to optimal or a near-optimal alternative.
 \end{abstract}
@@
 The traditional approach to social choice assumes that both the social function and the full preference orderings of the voters are expressed beforehand. 
-As noted by several authors requiring voters to express full preference orderings can be prohibitively costly (in term of cognitive and communication cost), especially for  large sets of alternatives.
-This observation has motivated a number of recent works \cite{Xia2008,Kalech2011,Lu2011,Naamani-Dery2015} have considered social choice with partially specified preferences and incremental elicitation of voters preferences.
-% including several works on social choice with partial profiles.
-
-%Recently, the assumption of full a has been questioned by a number of researchers
-%In many real situations, however, it may be necessary to reason with partial preferences, as some preferences are not available and too expensive to obtain (with respect to a cognitive or economic cost).
+As noted by several authors requiring voters to express full preference orderings can be prohibitively costly (in term of cognitive and communication cost), especially for decisions with large sets of alternatives.
+This observation has motivated a number of recent works considering social choice with partial preference orders  \cite{Xia2008,Pini2009,Konczak05} and incremental elicitation \cite{Kalech2011,Lu2011,Naamani-Dery2015} of voters preferences.
+
 On the other hand, in several situations it may not be easy to precisely define the voting rule.
-In particular, when considering positional scoring rules, it is possible to derive dominance relations (akin to stochastic dominance) that allow to eliminate some alternatives since they will be less preferred than another one for any instantiation of the weights \cite{Stein1994}.
-Among others, Llamazares and Pe{\~{n}}a \cite{Llamazares2013} have considered  the problem of dealing with underspecified weights in positional scoring rules.
-Cailloux and Endriss \cite{Cailloux2014} have proposed elicitation methods for based on partial orders.
 Indeed, it is possible that the chair may have some preferences over the desired aggregation method, but may still be not able to formalize the voting rule upfront.
-%argued that it might not always be realistic to assume that a voting rule is known precisely.
-
-%We argue that it is possible that the committee wants to precise some preferences about the aggregations.
+The work of Cailloux and Endriss \cite{Cailloux2014} is particularly notable: it provides elicitation methods  for a quite general class of rules based on well orders.
+In particular, when considering positional scoring rules, several authors \cite{Stein1994,Llamazares2013,Viappiani2018} have worked on  positional scoring rules with uncertain weights (assuming that the preferences of the voters are fully known).
+%it is possible to derive dominance relations (akin to stochastic dominance) that allow to eliminate some alternatives since they will be less preferred than another one for any instantiation of the weights \cite{Stein1994}.
+%Among others, Llamazares and Pe{\~{n}}a have considered  the problem of dealing with underspecified weights in positional scoring rules.
+
 In this paper we consider that both preferences and the social choice rule can be only partially specified.
-We develop methods for computing the minimax-optimal alternative for scoring rules with partial preference information and partial information about the weights.
-While previous works have considered either partial preferences or a partially specified aggregation, we do not know of any work considering both sources of uncertainty at the same time.
-
+We develop methods for computing the minimax-optimal alternative for scoring rules with partial preference information and partial information about the weights of the scoring rule.
+While previous works have considered either partial information about the voters preferences or a partially specified aggregation method, we do not know of any work considering both sources of uncertainty at the same time.
+
+%We consider that the committee wants to express preferences for some voting rules
 % Incremental elicitation of preferences is critical to easing the cognitive and communication cost for users 
@@
 
-We focus on positional scoring rules, that  are a particularly common methods used to aggregate rankings and determine  a winner.
-We also address the problem of elicitation, providing incremental elicitation methods to acquire relevant preference information. 
-%The score can be seen as a utility for the society.
-%and often captures more information than is needed to determine the winner
-We discuss  heuristics that allow us to determine queries that quickly allow to reduce minimax regret.
-We develop several query strategies that  focus simultaneously on reduction of relevant preference and voting rule uncertainty.
+In this work, we focus on positional scoring rules, that  are a particularly common method used to aggregate rankings and determine  a winner.
+We also address the problem of elicitation, providing incremental elicitation methods to acquire relevant preference information; we discuss  several heuristics that allow us to determine queries that quickly allow to reduce minimax regret.
+In particular, our query strategies  focus simultaneously on reduction of relevant preference and voting rule uncertainty.
 % the value of certain preference information is often not worth the cost of obtaining it.
-
-%We consider that the committee wants to express preferences for some voting rules
-
 % We must engage in simultaneous elictation of the rule and of the preferences.
@@
 %At each step we need to decide whether we want to ask a question to the committee or to one of the agents (and to which agent in particular).
-
-%We want to design a questioning strategy to minimize the worst regret in the long run
-% A questioning strategy indicates, given a partial profile and a set of feasible weights, which question to ask next.
-A question is either a query to the voter $i$ about her preference relation $\succ_i$ or a query to the committee about the feasible weights.
-
-%The voting scheme selects the winner (a consensus option).
-%Incremental elicitation 
 The paper is organized as follows.
@@
 We introduce the minimax criterion and in Section \ref{sec:mmr}.
-In Section \ref{sec:elicit} we provide an interactive elicitation protocol based on minima regret; finally in Section 
-\ref{sec:conclusions} we provide some final thoughts.
-
-\begin{itemize}
-\item References: \cite{Cailloux2014}, \cite{Llamazares2013}, \cite{Konczak05}, \cite{Kalech2011}, \cite{Pini2009}, relation to necessary and possible winners \cite{Xia2008}.
-Also this reference: \cite{Naamani-Dery2015}.
-\end{itemize}
-
-% we define a model that allows simultaneous elicitation of the voting rule and user preferences, making appropriate tradeoffs be- tween the two types of information
-
-%\subsection{Related works}
-\paragraph{Text to be placed somewhere:}
-%A number of works have dealt with the problem of reasoning with incompletely specified aggregation functions.
-%In particular, when considering positional scoring rules, it is possible to derive dominance relations (akin to stochastic dominance) that allow to eliminate some alternatives since they will be less preferred than another one for any instantiation of the weights \cite{Stein1994}.
-More recently the characterization of methods for aggregating the uncertainty over the scoring vectors has been studied in \cite{Viappiani2018}.
-
-\medskip
-Using {\em maximum regret} to quantify the worst-case error, the alternative that minimize this error is selected as winner, providing us with a form of robust optimization.
-
-\medskip
-Possible and necessary winner determination \cite{Xia2008}: in typical settings, there will be no necessary winner and too many possible winners.
-
-%We also note that the elicitation methods based on minimax regret described in \cite{Boutilier2006} (and in many other recent papers), while not specifically targeted to scoring rules, can be easily adapted (from a technical point of view) to elicit the scoring vector from a committee.
-
-%\paragraph{Incomplete profiles}
-%In this setting, the system knows a partial preference profile $\ppref$ 
-%The partial preference relation $\ppref_i$ represents our knowledge about the preferences of agent $i$.
-
-%Lu and Boutilier \cite{Lu2011} assume that the preferences of the voters are only partially known (while the social choice function is known and fixed in advance; it is assumed to be decomposable) and
-% propose to use minimax regret to produce a robust approximation.
-%Each alternative is associated with a max regret value that measures how far from optimal it could be in the worst case given any completion of the partial profile.
-%The computation of max regret is facilitated by the fact the score is decomposable.
+In Section \ref{sec:elicit} we provide an interactive elicitation protocol based on minima regret;  in Section \ref{sec:experiments} we present the empirical validation of our approach with simulations, and finally in Section \ref{sec:conclusions} we provide some final thoughts.
 
@@
 
-In this Section we introduce some basic concepts.
+We now introduce some basic concepts.
 We assume that there is a set $A$ of $m$ alternatives (for instance products, restaurants, movies, public projects, job candidates, etc.) and $n$ agents (voters); each agent is associated to a preference order.
@@
 A social choice function $f : V \rightarrow 2^A$ associates a profile with a set of winners.
-Among the many possible social choice functions, we consider {\em positional scoring rules}, which attach weights to positions; 
+Among the many possible social choice functions, we consider {\em positional scoring rules}, which attach weights to positions according to  the vector $(w_1,\ldots,w_m)$ (also called the scoring vector).
 %A scoring rule associates each alternative to a score that is given by the sum of points obtained for each voter.
-an alternative obtains a score that depends on the rank obtained in each of the preference orders:
+An alternative obtains a score that depends on the rank obtained in each of the preference orders:
 \begin{align}
@@
 The winner is the alternative with highest score.
-The vector $(w_1,\ldots,w_m)$ is called the scoring vector.
 %We assume that the weights constitute a monotonic sequence: $w_{1} \geq w_{2} \geq \ldots \geq w_{m}$.
+
 In this work we want to reason about partial preference information.
-A partial preference  is encoded by a partial order $\ppref_i$  of voter $i$; in this work we assume that preference information is truthful, i.e. $a \ppref_i b \implies a \pref_i b$.
+A partial preference  is encoded by a partial order $\ppref_j$  of voter $j$; in this work we assume that preference information is truthful, i.e. $a \ppref_j b \implies a \pref_j b$.
+We use $\pinc$ to denote incomparability, that is $a \pinc_{j} b$ iff $a \nppref_j b \wedge b \nppref_j a$.
 An incomplete profile is a set of partial votes  $\textbf{p}=(\ppref_1,\ldots,\ppref_n)$.
@@
 We also assume that the weights of the scoring rule are only partially specified.
-We consider a monotonic non-increasing sequence of weights: $w_{1} \geq w_{2} \geq \ldots \geq w_{m}$; this is a natural assumption, as it is better to be ranked first than second, second than third, etc.
+Therefore the vector $(w_1,\ldots,w_m)$  is not known but we are given a set of constraints restraining the possible values that weight can take.
+We consider a non-increasing sequence of weights:
+\begin{align}
+1=w_{1} \geq w_{2} \geq \ldots \geq w_{m}=0 \label{eq:monotone}
+\end{align}
+this is a natural assumption, as it is better to be ranked first than second, second than third, etc. 
 Without loss of generality, we assume $w_1=1$ and $w_m=0$.
@@
 For instance, the weights can control the inclination to favour ``extreme'' alternatives (often at either the top or the bottom of the rankings) at the expenses of ``moderate'' alternatives (that are more consistently in the middle part of the rankings).
-However, we argue that in general it can be difficult to set the weights in an appropriate way.
 
 An important class of scoring rule is the one composed of weights that are a convex sequence, meaning that the difference between the weight of the first position and the weight of the second position is at least as much as the difference between the weights of the second and third positions, etc.
-\begin{align} \forall i \in \{1,\ldots,n-2\} \;\; & w_i - w_{i+1} \geq w_{i+1}-w_{i+2} \iff  \\
-& w_i - 2 w_{i+1} + w_{i+2} \geq 0 \label{eq:convexity}
+\begin{align} \forall i \in \{1,\ldots,n-2\} \;\; & w_i - w_{i+1} \geq w_{i+1}-w_{i+2}  \\
+\iff & w_i - 2 w_{i+1} + w_{i+2} \geq 0 \label{eq:convexity}
 \end{align}
@@
 
-Additionally the chair (the person or the organization that is supervising the voting process) may be able to specify additional preferences about how the social choice function should behave.
+We argue that in general it can be difficult to set the weights in an appropriate way.
+We assume that in addition of basic requirments (monotonicity and convexity)  the chair (the person or the organization that is supervising the voting process) may be able to specify additional preferences about how the social choice function should behave.
 In this work we assume that preferences of the chair are encoded with linear constraints on the vector $\w$, relating the value of the weights of different positions.
@@
 
-% Theoretical complexity of partial completition
-% We are given  $\ppref_i $,  a partial preference.
-% The maximum regret is considered by assuming an adversary can choose the profile
-% \begin{align*}
-% \PMR(a,b; p) & = \max_{v \in C(p)} s(b; v) - s(a; v) \\
-% \MR(a; p) & = \max_{b} \PMR(a,b) 
-% \end{align*}
-% 
-% We then choose the minimax regret optimal alternative:
-% \begin{align*}
-% \MMR(p) & = \min \PMR(a,b) \\
-% a^{*}(p) & \in \arg\min \PMR(a,b) 
-% \end{align*}
-%Max regret and minimax regret can be computed using independent completion of partial votes for non-decomposable scoring rules.
-
 \section[Minimax regret under partial profile and weight information]{
@@
 
-% This leads to interesting tradeoffs in elicitation
-%The regret-minimizing alternative may not be a possible winner for some voting rules.
+%The quality of an alternative can be quantified by considering the maximum regret with respect to an adversary that can choose the instantiation of both a complete profile (extending the known preferences of the agents) and of the scoring vectors (associated to the preferences of the committee).
 In this paper, we consider a setting where both the voters' preferences and the preferences of the chair about the voting rule are incomplete.
-%\medskip
-%The quality of an alternative can be quantified by considering the maximum regret with respect to an adversary that can choose the instantiation of both a complete profile (extending the known preferences of the agents) and of the scoring vectors (associated to the preferences of the committee).
-
-As a decision criterion to determine a winner, we propose to use the minimax regret. 
+Notice that some authors have considered possible and necessary winners assuming a partial profile  \cite{Xia2008} or assuming an incompletely specified scoring rule \cite{Viappiani2018};
+however, we note that, in typical settings, there will be no necessary winner and too many possible winners.
+In practice, however, it is often imperative to declare a winner given partial information.
+
+As a decision criterion to determine a winner, we propose to use minimax regret. 
 Minimax regret \cite{Savage1954} is a decision criterion that has been used for robust optimization under data uncertainty \cite{Kouvelis1997} and as well in decision-making with uncertain utility values  \cite{Salo2001,Boutilier2006}.
@@
 
-This paper tackles the more challenging setting of the simultaneous presence of uncertainty in the agents' preferences and uncertainty in the weights.
+In this work we consider the simultaneous presence of uncertainty in the agents' preferences and uncertainty in the weights.
+Using {\em maximum regret} to quantify the worst-case error, the alternative that minimize this error is selected as winner, providing us with a form of robust optimization.
 Intuitively, the quality of a proposed alternative $a$ is how far from optimal $a$  could be in the worst case, given the current knowledge about the voting rule and about the voters' preferences.
@@
 
-Finally,  $\MMR(\pprofile,W)$ is the value of minimax regret under $\pprofile$ and $W$, obtained when recommending the minimax optimal alternative $x^*$:
+Finally,  $\MMR(\pprofile,W)$ is the value of minimax regret under $\pprofile$ and $W$, obtained when recommending a minimax optimal alternative $x^*$:
 \begin{align*}
 \MMR(\pprofile,W) & = \min_{x \in A} \MR(x;\pprofile,W) \\
-x^{*}(\pprofile,W) & \in \arg\min_{x \in A} \MR(x;\pprofile,W) 
+x^{*}_{\pprofile,W} & \in \arg\min_{x \in A} \MR(x;\pprofile,W) 
 \end{align*}
@@
 
-Notice that if $MMR(\pprofile, W)=0$, then $x^{*}(\pprofile,W)$  is a necessary co-winner.
+Notice that if $MMR(\pprofile, W)=0$, then $x^{*}_{\pprofile,W}$  is a necessary co-winner.
 
@@
 
-Let $A^+=\{ i \ | \ y \ppref_i x\}$ be the set of agents for which we know that $y$ is preferred to $x$ (positive contribution to pairwise regret), $A^-=\{ i \mid x \ppref_i y\}$ 
-be the set of agents for wich we  know that $x$ is preferred to $y$ (negative contribution) and $A^?=\{ i \mid x \pinc_i y\}$ the remaining case, where the preference between $x$ and $y$ is not known.
+Let $A^+=\{ i \mid \ y \ppref_i x\}$ be the set of agents for which we know that $y$ is preferred to $x$ (positive contribution to pairwise regret), $A^-=\{ i \mid x \ppref_i y\}$ 
+be the set of agents for wich we  know that $x$ is preferred to $y$ (negative contribution) and 
+$A^?=\{ i \mid x \pinc_i y\}$ 
+%$A^?=\{ i \mid x \nsucc_{i} y \wedge y \nsucc_{i} x \}$ 
+the remaining case, where the preference between $x$ and $y$ is not known.
 Consider how the adversary will complete the partial orders:
@@
 
- \item $j \in A^?$: If we do not know whether $x$ or $y$ is preferred by agent $j$ then the adversary will place $y$ before $x$ in the linear order and this case reduce to the first one; therefore also in this case the completion of the partial order can be done independently of the choice of $w$.
+ \item $j \in A^?$: If we do not know whether $x$ or $y$ is preferred by agent $j$ then the adversary will place $y$ before $x$ (since the goal is to maximize the difference in score between $y$ and $x$, and weights are monotone) in the linear order and this case reduce to the first one; therefore also in this case the completion of the partial order can be done independently of the choice of $w$.
 
@@
 
-Let $\hat{v}$ be the compute profile computed according to the above procedure, and  $\hat{v}_j$ the $j$-th element (the linear order extending the partial order $p_j$ of the $j$-th voter).
+Let $\hat{\profile}$ be the profile computed according to the above procedure, and  $\hat{v}_j$ the $j$-th element (the linear order extending the partial order $p_j$ of the $j$-th voter).
+\begin{prop}
+Assume convex weights.
 The PMR can be written as:
-\[ \PMR(x,y; \pprofile, W) = \sum_{j=1}^n w_{\hat{v}_i(y)} - w_{\hat{v}_i(x)} 
-= \sum_{i=1}^m (\alpha_{i}^{y} - \alpha_{i}^{x}) w_i \]
-where the coefficient $ (\alpha_{i}^{y} - \alpha_{i}^{x})$ is the number of times $y$ is in position $i$ minus the number of times $x$ is the in position $i$ in the rankings of the completed profile $\hat{v}$:
-$\alpha_{i}^{x} = \sum_{j=1}^{n}  I[\hat{v}_{j}(x)=i]$ where $I$ is the indicator function.
+\begin{align} 
+\PMR(x,y; \pprofile, W) =  
+\max_{w \in W} s(y; \hat{\profile}, \w) - s(y; \hat{\profile}, \w) =\\
+=\max_{w \in W} \sum_{j=1}^n w_{\hat{v}_i(y)} - w_{\hat{v}_i(x)} =
+\max_{w \in W} \sum_{i=1}^m (\hat{\alpha}_{i}^{y} - \hat{\alpha}_{i}^{x}) w_i 
+\end{align}
+where the coefficient $ (\hat{\alpha}_{i}^{y} - \hat{\alpha}_{i}^{x})$ is the number of times $y$ is in position $i$ minus the number of times $x$ is the in position $i$ in the rankings of the completed profile $\hat{v}$:
+$\hat{\alpha}_{i}^{x} = \sum_{j=1}^{n}  I[\hat{v}_{j}(x)=i]$ where $I$ is the indicator function.
+\end{prop}
 %\[ \alpha_{i} = \sum_{j=1}^{n}  I[\hat{v}_{j}(y)=i] - I[\hat{v}_{j}(x)=i]\]
-Then, what we have to to compute pairwise max regret is to compute the solution of the following linear program :
+Then, what we have to to compute pairwise max regret $\PMR(x,y; \pprofile,W)$ is to compute the solution of the following linear program defined on variables\footnote{In fact, given our assumpations, $w_{1}=1$ and $w_{m}=0$, therefore there are only $m-2$ variables.} $w_{1},\ldots,w_{m}$:
 \begin{align*}
-\PMR(x,y; \pprofile,W) = \max_{\w} & \sum_{i=1}^m (\alpha_{i}^{y} - \alpha_{i}^{x}) w_{i}\\
+\max_{\w} & \sum_{i=1}^m (\hat{\alpha}_{i}^{y} - \hat{\alpha}_{i}^{x}) w_{i}\\
 \text{ s.t. } & \w \in W \\
+& \text{Equation } (\ref{eq:monotone})\\
 & \text{Equation } (\ref{eq:convexity})
@@
 \medskip
-Let $\hat{v}_i$ be the linear order extending $p_i$ according to the above procedure (described in \cite{Lu2011}).
+Let $\hat{v}_i$ be the linear order extending $\succ^{p}_i$ according to the above procedure (described in \cite{Lu2011}).
 Then PMR can be written as follows:
@@
 Consider the two addendum inside the outer ``max''. 
-The first addendum is concern with positioning of alternatives $x$ and $y$ for voters in $A^{-}$for which we know that $x$ is preferred to $y$.
+The first addendum is concerned with positioning of alternatives $x$ and $y$ for voters in $A^{-}$ for which we know that $x$ is preferred to $y$.
 The second addendum is concerned with voters in $A^{+}$ and $A^{?}$.
@@
 In addition to variables $\{ w_{j} \}_{j=1,\ldots,m}$ (one for each position) we need to employ several additional decision variables.
-We introduce two set of binary variables $B^{+}_{i,j}$ and $B^{-}_{i,j}$  for each position $i$ and for each voter $j$.
+We introduce two sets of binary variables $B^{+}_{i,j}$ and $B^{-}_{i,j}$  for each position $i$ and for each voter $j$.
 Variable $B_{i,j}^{+}$ encodes the fact that the alternative $y$ is placed in position $i$ in the ranking of agent $j$; while  $B_{i,j}^{-}$ encodes the same thing for alternative $x$.
@@
 The objective function is now:
- \[ \max \sum_{i = 1}^{m} (\hat{\alpha}_{i}^{y} - \hat{\alpha}_{i}^{x}) w_{i}  \sum_{i=1}^{n} \sum_{j=1}^{m} B_{i,j}^{+} w_j- B_{i,j}^{-}  w_j \]
+ \[ \max \sum_{i = 1}^{m} (\hat{\alpha}_{i}^{y} - \hat{\alpha}_{i}^{x}) w_{i} +  \sum_{i=1}^{n} \sum_{j=1}^{m} B_{i,j}^{+} w_i- B_{i,j}^{-}  w_i \]
 
@@
 We introduce yet another set of variables  $V_{i,j}^{+} $  and $V_{i,j}^{-}$ % the multiplicative terms by new variables.
-and we enforce that $V_{i,j}^{+} = B^{+}_{i,j} w_j$ by setting constraints $V_{l}^{j} \leq B^j $ and $V_{l}^{j} \leq w_l$.
+and we enforce that $V_{i,j}^{+} = B^{+}_{i,j} w_i$ by setting constraints $V_{l}^{j} \leq B^j $ and $V_{l}^{j} \leq w_l$.
 %\begin{align*} 
@@
 %The expression $B^j_l w_l$ evaluates to $w_l$ if $I^j_l = 1$, and to $0$ otherwise.
-
   %Variable $I^j$ associated with the constraint $0 \leq I \leq |U^j|$.
- Finally, the following is the optimization problem that compute the value $\PMR$.
+% Finally, the following is the optimization problem that compute the value $\PMR$.
  %The decision variables are $w$, $V$, $B$,...
-
 We therefore obtain the following mixed integer linear program:
@@
 & V_{i,j}^{+} \leq B_{i,j}^{+}  & \forall i,j \\
-& V_{i,j}^{+} \leq w_j & \forall i,j \\
-& V_{i,j}^{-} \geq w + B_{i,j}^{-} - 1 & \forall i,j \\
+& V_{i,j}^{+} \leq w_i & \forall i,j \\
+& V_{i,j}^{-} \geq w_{i} + B_{i,j}^{-} - 1 & \forall i,j \\
 & V_{i,j}^{-} \geq 0 & \forall i,j
@@
 We add other alternatives in such a way that they are dominated by $a$ or $b$. 
-(if the chair answers an alternative that is either $a$ or $b$ this is a signale that the model is incorrect).
+(if the chair picks an alternative that is either $a$ or $b$ this is a signale that the model is incorrect).
 
 \vspace{1cm}
-{\bf Complete section:} give a precise algorithm for completing the profile
+{\em {\bf TODO:} complete section and give a precise algorithm for completing the profile}
 \vspace{1cm}
@@
 In order to obtain a valid profile, we need to include a number of other alternatives in such a way that the are dominated by $a$ and $b$.
-The following profile is exactly what we want.
+The following profile is exactly what we want,
 %We add voters in order to increase the number of times $a$ and $b$ are ranked at first position.
@@
 \]
-giving the rank distribution (number of times each alternatives is ranked first, second, etc): 
+giving the following rank distribution (number of times each alternatives is ranked first, second, etc): 
 \[
@@
 Answers given by the committee about the scoring rule refine our knowledge of the weights $w_1,\ldots,w_n$, while
-answers given by one of the agents refine our knowledge about the agent's preferences.
+answers given by one of the voters refine our knowledge about the voters preferences.
 
@@
 		\item Random strategy: randomly chooses an agent $i$ and a comparison query such that $x \pinc_i y$.
-		\item Volumetric strategy: chooses an agent $i$ and a query that maximizes the number of new pairwise preferences revealed given the worst response.
+		\item {\em Volumetric} strategy: chooses an agent $i$ and a query that maximizes the number of new pairwise preferences revealed given the worst response.
 	\end{itemize}
@@
 \section{Empirical Evaluation} \label{sec:experiments}
+
+{\em {\bf TODO:} update with actual experiments}
 
@@
 We evaluate the proposed method using the following simulated protocol.
+Our goal is to 
+ to verify our intuition that an interleaved elicitation approach (mixing questions to the chair and questions asked to the voters) is more efficient than performing the elicitation of the rule first and than eliciting the voters preferences.
 First of all, we randomly generate the true preferences of the users (i.e. the linear orders) and the weights associated with the committee's scoring rule.
@@
 We experimented with both settings that assume a convex sequences of weights, and others without this assumption.
+
+{\em {\bf TODO:} say something about computation times}
 

### 2019-02-18 draft.tex
many changes (mostly in minimax regret computation)

@@
 \newif\ifappendix
-\appendixtrue %COMMENT to remove appendix
+%\appendixtrue %COMMENT to remove appendix % UNCOMMENT to add apendix
 \ifijcai
  	\input{ijcai_preamble} 
-	\author{Olivier Cailloux$^1$	\and Beatrice Napolitano$^1$\and Paolo Viappiani$^{2}$
+	\author{Beatrice Napolitano$^1$\and Olivier Cailloux$^1$	\and  Paolo Viappiani$^{2}$
 	\affiliations $^1$ LAMSADE, UMR 7243, CNRS and Universit\'e Paris Dauphine, PSL Research University, Paris, France\\ $^2$ LIP6, UMR 7606, CNRS and Sorbonne Universit\'e, Paris, France
@@
 \newcommand{\w}{\textbf{w}}%partial profile
+\newcommand{\C}{\mathcal{C}}%partial profile
 
@@
 Indeed, it is possible that the chair may have some preferences over the desired aggregation method, but may still be not able to formalize the voting rule upfront.
-The work of Cailloux and Endriss \cite{Cailloux2014} is particularly notable: it provides elicitation methods  for a quite general class of rules based on well orders.
-In particular, when considering positional scoring rules, several authors \cite{Stein1994,Llamazares2013,Viappiani2018} have worked on  positional scoring rules with uncertain weights (assuming that the preferences of the voters are fully known).
+The work of Cailloux and Endriss \cite{Cailloux2014} provides elicitation methods  for a quite general class of rules based on well orders.
+When considering positional scoring rules, several authors \cite{Stein1994,Llamazares2013,Viappiani2018} have worked on  positional scoring rules with uncertain weights (assuming that the preferences of the voters are fully known).
 %it is possible to derive dominance relations (akin to stochastic dominance) that allow to eliminate some alternatives since they will be less preferred than another one for any instantiation of the weights \cite{Stein1994}.
@@
 The weights of a scoring rule can model different preferences of the committee. 
-For instance, the weights can control the inclination to favour ``extreme'' alternatives (often at either the top or the bottom of the rankings) at the expenses of ``moderate'' alternatives (that are more consistently in the middle part of the rankings).
+For instance, the weights can control the inclination to favour ``extreme'' alternatives (often at either the top or the bottom of the input rankings) at the expenses of ``moderate'' alternatives (that are more consistently in the middle part of the input rankings).
 
@@
 In this work we assume that preferences of the chair are encoded with linear constraints on the vector $\w$, relating the value of the weights of different positions.
+We use $\C(\w)$ to denote, in an abstract way, the preferences of the chair about the scoring vector.
+
 Of course it may be difficult for real decision makers to state preferences about the voting rule in such an abstract way, unless perhaps in some limited cases (a specific instance of these preferences may consist in giving upper or lower bound on the value of $w_{i}$ for position $i$).
@@
 however, we note that, in typical settings, there will be no necessary winner and too many possible winners.
-In practice, however, it is often imperative to declare a winner given partial information.
+In practice, however, it is often imperative to declare a winner (consensus choice) given partial information.
 
@@
 First of all, $\Regret(x, \profile, \w)$ is the loss or ``actual'' regret  of selecting $x$ as a winner instead of choosing the optimal alternative under $\profile$ and $\w$:
-\[\Regret(x, \profile, \w) = \max_{y} s(y; \profile,\w) - s(x; \profile, \w).\]
+\[\Regret(x, \profile, \w) = \max_{y \in A} s(y; \profile,\w) - s(x; \profile, \w).\]
 
@@
 \end{align*}
-By recommending the alternative associated with minimax regret, we can provide a recommendation that gives worst-case guarantees, giving some robustness in face of uncertainty (due to both not knowing the agents' preferences and the weights used in the aggregation).
-
-Notice that if $MMR(\pprofile, W)=0$, then $x^{*}_{\pprofile,W}$  is a necessary co-winner.
+By picking as consensus choice\footnote{In cases of ties in minimax regret, we can either decide to return all minimax alternatives as ``winner'' or to pick just one of them using some tie-breaking strategy.} an alternative associated with minimax regret, we can provide a recommendation that gives worst-case guarantees, giving some robustness in face of uncertainty (due to both not knowing the agents' preferences and the weights used in the aggregation).
+
+Notice that if $MMR(\pprofile, W)=0$, then $x^{*}_{\pprofile,W}$  is a necessary co-winner; this means that for any valid completition of the profile and any feasible weight $w \in W$, $x^{*}_{\pprofile,W}$ obtains the highest score (possibly with ties).
 
@@
 \end{align*}
-Given our hypothesis, for all pairs of alternatives, there exist completions of the partial preferences $\ppref$ that maximize the PMR and that do not depend on the weights. 
-That is, we can exhibit, for each voter $j$, a completion $v_j$ such that $\forall \w, \forall v'_j \in C(\ppref_j): [w_{v_j(y)} - w_{v_j(x)}] \geq [w_{v'_j(y)} - w_{v'_j(x)}]$.
-
-Let $A^+=\{ i \mid \ y \ppref_i x\}$ be the set of agents for which we know that $y$ is preferred to $x$ (positive contribution to pairwise regret), $A^-=\{ i \mid x \ppref_i y\}$ 
+Note that in general the inner max will depend on the weights chosen by the outer min.
+
+We consider now a procedure for completing a partial profile that was first proposed by Lu and Boutilier \cite{Lu2011} when considering minimax regret with a fixed rule.
+We will show how this procedure can be used the in the case of uncertain weight vector:
+in the case of convex scoring rules we will be able to greatly simplify the problem by decoupling the two maximizations, while in the general case we will propose to solve it using a mixed integer program.
+
+Let $U^+=\{ i \mid \ y \ppref_i x\}$ be the set of agents for which we know that $y$ is preferred to $x$ (positive contribution to pairwise regret), $U^-=\{ i \mid x \ppref_i y\}$ 
 be the set of agents for wich we  know that $x$ is preferred to $y$ (negative contribution) and 
-$A^?=\{ i \mid x \pinc_i y\}$ 
-%$A^?=\{ i \mid x \nsucc_{i} y \wedge y \nsucc_{i} x \}$ 
+$U^?=\{ i \mid x \pinc_i y\}$ 
+%$U^?=\{ i \mid x \nsucc_{i} y \wedge y \nsucc_{i} x \}$ 
 the remaining case, where the preference between $x$ and $y$ is not known.
-Consider how the adversary will complete the partial orders:
+Consider how the adversary, whose goal is to maximize $\PMR$ between $x$ and $y$, will complete the partial orders:
 \begin{itemize}
- \item $j \in A^+$: If we know that agent $j$ prefers $y$ to $x$ then the adversary will complete the partial order of agent $j$ by placing as many alternatives as possible between $y$ and $x$.
- The way the partial order is completed does not depend on the weights.
-
- \item $j \in A^?$: If we do not know whether $x$ or $y$ is preferred by agent $j$ then the adversary will place $y$ before $x$ (since the goal is to maximize the difference in score between $y$ and $x$, and weights are monotone) in the linear order and this case reduce to the first one; therefore also in this case the completion of the partial order can be done independently of the choice of $w$.
-
- \item $j \in A^-$: If we know that agent $j$ prefers $x$ to $y$ then the adversary will place as few alternatives as possible between $x$ and $y$.
-Define $U$ as the set of alternatives that are incomparable with $x$ and $y$ according to $\ppref_i$.
-Since weights are assumed to be convex, the adversary will place all alternatives in $U$ as better than $x$.
+ \item $j \in U^+$: If we know that agent $j$ prefers $y$ to $x$ then the contribution to $\PMR$ is positive and adversary will complete the partial order of agent $j$ by placing as many alternatives as possible between $y$ and $x$ (because of monotonicity of the weights).
+ The way the partial order is completed does not depend on the actual values of the weights.
+
+ \item $j \in U^?$: If we do not know whether $x$ or $y$ is preferred by agent $j$ then the adversary will place $y$ before $x$ (since the goal is to maximize the difference in score between $y$ and $x$, and weights are monotone) in the linear order and this case reduce to the first one; therefore also in this case the completion of the partial order can be done independently of the choice of $w$.
+
+ \item $j \in U^-$: If we know that agent $j$ prefers $x$ to $y$ then (as the contribution of this agent to $\PMR$ is negative) the adversary will place as few alternatives as possible between $x$ and $y$.
+
+The only issue is with respect to the  alternatives that are incomparable with $x$ and $y$ according to $\ppref_i$: should they be placed better than $x$ or worse than $y$ ?
+If the scoring vector is known to be convex,  than these alternatives will be placed better than $x$ in the completion; otherwise the placements of these depend on the weights $\w$.
 \end{itemize}
-In summary, some best completion $\pref$ satisfies two properties: (1) for all $c \pinc x$, $c \pref x$; and (2) for all $c \pinc y$, if not $c \pref x \pref y$ then $y \pref c$.
-These two properties are intuitively understandable by observing that maximizing the PMR requires placing $x$ as low as possible, hence the first property; and $y$ as high as possible, hence the second property, with the exception that sometimes it is not possible to satisfy both goals and noting that the first goal is more important by convexity of the weights.
-A proof that this reasoning is correct is in \cref{sec:prfCompl}.
+
+\subsubsection{Minimax regret computation under the convex assumption}
+
+Since weights are assumed to be convex, the adversary will place all alternatives $c$ that are such that $c \pinc_{j} y \wedge c \pinc_{j} x$ as better than $x$.
+We now formalize the reasoning about the best (with respect to maximizing $\PMR$) completion with the following definition.
+\begin{definition}
+Given the partial profile $\pprofile$, define $\hat{\profile}$ as the completition of $\pprofile$ such that:
+\begin{itemize}
+\item For each $j \in U^{+}$, set   $\hat{\profile}$ as follows, for all $c \in A$:\\
+if $c \pinc_{j} x$ we set $c \succ_{j}^{\hat{\profile}} x$;\\
+if  $c \pinc_{j} y$ we set $y \succ_{j}^{\hat{\profile}} c$.
+\item For each $j \in U^{?}$, set  $\hat{\profile}$ as follows:\\
+$y \succ_{j}^{\hat{\profile}} x$;\\
+for all $c \in A$, if   $c \pinc_{j} x$ we set $c \succ_{j}^{\hat{\profile}} x$;\\
+for all $c \in A$, if   $c \pinc_{j} y$ we set $y \succ_{j}^{\hat{\profile}} c$.
+\item For each $j \in U^{-}$,  set  $\hat{\profile}$ as follows, for all $c \in A$:\\
+if $c \pinc_{j} x \wedge c \succ^{p}_{j} y$ we set $c \succ_{j}^{\hat{\profile}} x$;\\
+if $c \pinc_{j} y \wedge  x \succ^{p}_{j} c$ we set $y \succ_{j}^{\hat{\profile}} c$;\\
+if $c \pinc_{j} y \wedge c \pinc_{j} x$ we set $c \succ_{j}^{\hat{\profile}} x$.
+\end{itemize}
+\end{definition}
+
+%Given our hypothesis, for all pairs of alternatives, there exist completions of the partial preferences $\ppref$ that maximize the PMR and that do not depend on the weights. 
+%That is, we can exhibit, for each voter $j$, a completion $v_j$ such that $\forall \w, \forall v'_j \in C(\ppref_j): [w_{v_j(y)} - w_{v_j(x)}] \geq [w_{v'_j(y)} - w_{v'_j(x)}]$.
+
+%In summary, some best completion $\pref$ satisfies two properties: (1) for all $c \pinc x$, $c \pref x$; and (2) for all $c \pinc y$, if not $c \pref x \pref y$ then $y \pref c$. 
+%These two properties are intuitively understandable by observing that maximizing the PMR requires placing $x$ as low as possible, hence the first property; and $y$ as high as possible, hence the second property, with the exception that sometimes it is not possible to satisfy both goals and noting that the first goal is more important by convexity of the weights.
+%A proof that this reasoning is correct is in \cref{sec:prfCompl}.
 
@@
 Therefore the pairwise maximum regret can be computed with a linear program.
-
-\subsection{Linear program under the convex assumption}
 
@@
 %\[ \alpha_{i} = \sum_{j=1}^{n}  I[\hat{v}_{j}(y)=i] - I[\hat{v}_{j}(x)=i]\]
-Then, what we have to to compute pairwise max regret $\PMR(x,y; \pprofile,W)$ is to compute the solution of the following linear program defined on variables\footnote{In fact, given our assumpations, $w_{1}=1$ and $w_{m}=0$, therefore there are only $m-2$ variables.} $w_{1},\ldots,w_{m}$:
+Then, what we have to to compute pairwise max regret $\PMR(x,y; \pprofile,W)$ is just to compute the solution of the following linear program defined on variables\footnote{In fact, given our assumptions, $w_{1}=1$ and $w_{m}=0$, therefore there are only $m-2$ variables.
+We leave $w_{1}$ and $w_{m}$ in the linear program just for ease of presentation.} $w_{1},\ldots,w_{m}$:
 \begin{align*}
 \max_{\w} & \sum_{i=1}^m (\hat{\alpha}_{i}^{y} - \hat{\alpha}_{i}^{x}) w_{i}\\
-\text{ s.t. } & \w \in W \\
-& \text{Equation } (\ref{eq:monotone})\\
-& \text{Equation } (\ref{eq:convexity})
+\text{ s.t. } & \text{Equation } (\ref{eq:monotone})\\
+& \text{Equation } (\ref{eq:convexity})\\
+& \C(\w)
 \end{align*}
+where $\C(w)$ are the linear constraints on $\w$ encoding the chair's preferences.
 The result of the optimization is the value of the pairwise max regret $\PMR$.
 
-\subsection{Minimax regret without the convex assumption}
-{\em (will probably go to a later section, or to the appendix) }
-
-\medskip
-Let $\hat{v}_i$ be the linear order extending $\succ^{p}_i$ according to the above procedure (described in \cite{Lu2011}).
+\subsubsection{Minimax regret without the convex assumption}
+{\em (Still here? Or move it somewhere else?) }
+
+Without the convex assumption, we cannot use $\hat{v}$ for the agents in $U^{-}$, but only for agents in $U^{+}$ and $U^{?}$.
+%Let $\hat{v}_i$ be the linear order extending $\succ^{p}_i$ according to the above procedure.
 Then PMR can be written as follows:
@@
  &\PMR(x,y; \pprofile, W) =\\ 
- &\max_{\w \in W} \Big \{ \max_{v_j \in C(\succ_j^p)} [w_{v_j(y)} \!-\! w_{v_j(x)}]  \!+\!	 \sum_{j \in A^+ \cup  A^?} [w_{\hat{v}_j(y)} \!-\! w_{\hat{v}_j(x)}] \Big \} 
+ &\max_{\w \in W} \Big \{ \sum_{j \in U^-} [\max_{v_j \in C(\succ_j^p)} [w_{v_j(y)} \!-\! w_{v_j(x)}]] 
+  \!+\!	 \sum_{j \in A^+ \cup  U^?} [w_{\hat{v}_j(y)} \!-\! w_{\hat{v}_j(x)}] \Big \} 
  \end{align*}
 %Note that the second addendum inside the max do not depend on the choice of $\w$.
-Consider the two addendum inside the outer ``max''. 
-The first addendum is concerned with positioning of alternatives $x$ and $y$ for voters in $A^{-}$ for which we know that $x$ is preferred to $y$.
-The second addendum is concerned with voters in $A^{+}$ and $A^{?}$.
+Consider the two addenda inside the ``max''. 
+The first addendum is concerned with positioning of alternatives $x$ and $y$ for voters in $U^{-}$ for which we know that $x$ is preferred to $y$.
+The second addendum is concerned with voters in $U^{+}$ and $U^{?}$.
 We rewrite the second addendum as:
 \begin{align*}
-\sum_{j \in A^+ \cup  A^?} [w_{\hat{v}_j(y)} \!-\! w_{\hat{v}_j(x)}] 
+\sum_{j \in U^+ \cup  U^?} [w_{\hat{v}_j(y)} \!-\! w_{\hat{v}_j(x)}] 
 = \sum_{i = 1}^{m} (\hat{\alpha}_{i}^{y} - \hat{\alpha}_{i}^{x}) w_{i}
 \end{align*}
-where $\hat{\alpha}_{i}^{x}$ is the number of times that $x$ is ranked  in position $i$  considering the profile $\hat{v}$ of voters in $A^+ \cup  A^?$.
+where $\hat{\alpha}_{i}^{x}$ is the number of times that $x$ is ranked  in position $i$  considering the profile $\hat{v}$ of voters in $U^+ \cup  U^?$.
 %We compute pairwise maximum regret by considering binary variables $\{ B_{i} \}_{i=1,\ldots,m}$ to represent optimization choices related to where to position the alternatives.
+
+We now address the agents in $A^{-}$
+For a given $j$, let $\beta$ be the number of alternatives that are incomparable with $x$ and $y$:
+\[ \beta_{j} = \mid \{ c : c \pinc_{j} y \wedge c \pinc_{j} x \} \mid \]
+$x$ can be ranked between $t_{1}(j)=\mid \{ c \in A : c \ppref_{j} y \wedge x \nppref_{j} c \} \mid $ and position $t_{2}(j)=t_{1}(j)+\beta_{j}$.
+The completion for agent $j$ is such that the positions of $x$ and $y$ differ of exactly $\gamma_{j} =
+\mid \{ c \in A : x \ppref c \ppref y \} \mid$ positions.
 
@@
 Variable $B_{i,j}^{+}$ encodes the fact that the alternative $y$ is placed in position $i$ in the ranking of agent $j$; while  $B_{i,j}^{-}$ encodes the same thing for alternative $x$.
-
-We also have numerical variables to represent the weights of the scoring rule.
+%We also have numerical variables to represent the weights of the scoring rule.
 Since each alternative needs to be placed exactly in one place for each agent, we adopt the constraints
-$\sum_{i=1}^{m} B_{i,j}^{+} = 1$ and $\sum_{i=1}^{m} B_{i,j}^{-} = 1$.
+$\sum_{i=t_{1}(j)}^{t_{2}(j)} B_{i,j}^{+} = 1$.
+Since we know that $x$ and $y$ are ranked $\gamma{j}$ positions apart, we set the constraint:
+$B_{i+\gamma{j},j}^{-} \geq B_{i,j}^{+}$,  for $i = \{ t_{1}(j), \ldots, t_{2}(j)\}$.
+
+% and $\sum_{i=1}^{m} B_{i,j}^{-} = 1$.
 %Since the objective is to maximize pairwise regret...
 
-The score of alternative $y$ can be written as $\sum_{i = 1}^{m} \hat{\alpha}_{i}^{y} + \sum_{i=1}^{n} \sum_{j=1}^{m} w_{j} B_{i,j}^{+}$.
+The score of alternative $y$ can be written as $\sum_{i = 1}^{m} \hat{\alpha}_{i}^{y}  w_{i} + \sum_{i=1}^{n} \sum_{j=1}^{m} w_{j} B_{i,j}^{+}$.
 The objective function is now:
- \[ \max \sum_{i = 1}^{m} (\hat{\alpha}_{i}^{y} - \hat{\alpha}_{i}^{x}) w_{i} +  \sum_{i=1}^{n} \sum_{j=1}^{m} B_{i,j}^{+} w_i- B_{i,j}^{-}  w_i \]
-
-We use integer programming enconding tricks in order to linearize the problem formulation.
+ \[ \max \sum_{i = 1}^{m} (\hat{\alpha}_{i}^{y} - \hat{\alpha}_{i}^{x}) w_{i} +  \sum_{i=1}^{n} \sum_{j=1}^{m} (B_{i,j}^{+} - B_{i,j}^{-})  w_i \]
+
+We use integer programming enconding tricks in order to linearize the problem.
 We introduce yet another set of variables  $V_{i,j}^{+} $  and $V_{i,j}^{-}$ % the multiplicative terms by new variables.
-and we enforce that $V_{i,j}^{+} = B^{+}_{i,j} w_i$ by setting constraints $V_{l}^{j} \leq B^j $ and $V_{l}^{j} \leq w_l$.
-%\begin{align*} 
-%V_{l}^{j} \leq B^j \\
-%V_{l}^{j} \leq w_l
-%\end{align*}
-%The expression $B^j_l w_l$ evaluates to $w_l$ if $I^j_l = 1$, and to $0$ otherwise.
-  %Variable $I^j$ associated with the constraint $0 \leq I \leq |U^j|$.
-% Finally, the following is the optimization problem that compute the value $\PMR$.
- %The decision variables are $w$, $V$, $B$,...
+and we enforce that $V_{i,j}^{+} = B^{+}_{i,j} w_i$ by setting constraints $V_{i,j}^{+} \leq B^{+}_{i,j}$ and $V_{i,j}^{+}  \leq w_i$.
+We have similar constraints for enforcing $V_{i,j}^{-} = B^{-}_{i,j} w_i$.
+
 We therefore obtain the following mixed integer linear program:
@@
 \max & \sum_{i=1}^m  [(\hat{\alpha}_{i}^{y} - \hat{\alpha}_{i}^{x}) w_{i}] +
- \sum_{i=1}^m \sum_{j=1}^n  [V_{i,j}^{+} - V_{i,j}^{-}]\\
-\text{ s.t. } & \w \in W  \\
-& \sum_{i=t_{1}}^{t_{2}} B_{i,j}^{+} = 1 & \forall j \\
-& \sum_{i=t_{1}}^{t_{2}} B_{i,j}^{-} = 1 & \forall j \\
-& V_{i,j}^{+} \leq B_{i,j}^{+}  & \forall i,j \\
-& V_{i,j}^{+} \leq w_i & \forall i,j \\
-& V_{i,j}^{-} \geq w_{i} + B_{i,j}^{-} - 1 & \forall i,j \\
-& V_{i,j}^{-} \geq 0 & \forall i,j
+  \sum_{j \in A^{-}} \sum_{i=t_{1}}^{t_{2}}  [V_{i,j}^{+} - V_{i,j}^{-}]
+\end{align}
+\begin{align}
+\text{ s.t. } &  \text{Equation } (\ref{eq:monotone}) & \\
+&  \C(\w) &  \\
+& \sum_{i=t_{1}}^{t_{2}} B_{i,j}^{+} = 1 & \forall j \in A^{-} \\
+& B_{i+\gamma_{j},j}^{-} \geq B_{i,j}^{+} & \forall i \in \{ t_{1}, \ldots t_{2}\}, \forall j \in A^{-} \\
+& V_{i,j}^{+} \leq B_{i,j}^{+}  & \forall i \in \{ t_{1}, \ldots t_{2}\}, j \in A^{-} \\
+& V_{i,j}^{+} \leq w_i & \forall i \in \{ t_{1}, \ldots t_{2}\}, j \in A^{-} \\
+& V_{i,j}^{-} \geq w_{i} + B_{i,j}^{-} - 1 & \forall i \in \{ t_{1}, \ldots t_{2}\}, j \in A^{-}\\
+& V_{i,j}^{-} \geq 0 & \forall i \in \{ t_{1}, \ldots t_{2}\}, j \in A^{-}
 \end{align} 
 %We write $w \in W$ as a shourtcut to represent the constraints that the weights are chosen to be in the feasible set.
-
-The optimization program can be solved by any suitable MILP solver.
-
-\begin{claim}
-The $\PMR$ is computed using the above optimization problem.
-\end{claim}
+There are (at most) $nm$ binary variables and $m(n+1)$ numerical variables.
+The optimization program can be solved by any suitable MILP solver, although it is not suitable to large problem instances.
+
+% DONT KNOW IF WE HAVE TO FORMALIZE THIS AS A CLAIM
+%\begin{claim}
+%The $\PMR$ is computed using the above optimization problem.
+%\end{claim}
 
@@
 At each step we need to decide whether we want to ask a question to the committee or to one of the agents (and to which agent in particular).
-We can ask comparison queries to the agents and questions comparing the differences of weights to the committee.
+We assume that we can ask comparison queries to the agents and questions comparing the differences of weights to the committee.
 
@@
 \item {\em Current solution strategy}: consider the solution of the minimax regret game, 
- $(x,y,\w^{a},\profile^{a})$, where $x$ is the minimax regret optimal alternative, $y$ the adversarial choice, $\w^{a}$ the weights, and $\profile^{a}$ the profile completed by the adversary.
+ $(x,y,\profile^{a},\w^{a})$, where $x$ is the minimax regret optimal alternative, $y$ the adversarial choice, $\w^{a}$ the weights, and $\profile^{a}$ the profile completed by the adversary.
 
@@
 % We introduce a set integer variables $I^i$, one for each position $i$.
-% Let $U^j$ be, for the agents in $A^-$, the alternatives that, in the partial order $\succ^p_j$ of some agent $j \in A^-$, are incomparable with $x$ and $y$.
+% Let $U^j$ be, for the agents in $U^-$, the alternatives that, in the partial order $\succ^p_j$ of some agent $j \in U^-$, are incomparable with $x$ and $y$.
 % \[ \sum_{l=1}^n I^j_l w_l \]

### 2019-02-18 draft.tex
typo

@@
 $\sum_{i=t_{1}(j)}^{t_{2}(j)} B_{i,j}^{+} = 1$.
-Since we know that $x$ and $y$ are ranked $\gamma{j}$ positions apart, we set the constraint:
-$B_{i+\gamma{j},j}^{-} \geq B_{i,j}^{+}$,  for $i = \{ t_{1}(j), \ldots, t_{2}(j)\}$.
+Since we know that $x$ and $y$ are ranked $\gamma_{j}$ positions apart, we set the constraint:
+$B_{i+\gamma_{j},j}^{-} \geq B_{i,j}^{+}$,  for $i = \{ t_{1}(j), \ldots, t_{2}(j)\}$.
 

### 2019-02-19 draft.tex
Some rewording (unfinished)

@@
-\newif\ifijcai
- \ijcaitrue  %UNCOMMENT this to have the ijcai formatting / COMMENT for draft format
-
 \newif\ifappendix
 %\appendixtrue %COMMENT to remove appendix % UNCOMMENT to add apendix
-\ifijcai
 \input{ijcai_preamble} 
@@
 	\affiliations $^1$ LAMSADE, UMR 7243, CNRS and Universit\'e Paris Dauphine, PSL Research University, Paris, France\\ $^2$ LIP6, UMR 7606, CNRS and Sorbonne Universit\'e, Paris, France
-	\emails \{first, second\}@lamsade.fr, paolo.viappiani@lip6.fr
+	\emails \{firstname.lastname\}@dauphine.fr, paolo.viappiani@lip6.fr
 }
-\else
-	\documentclass[12pt]{article}
-	\usepackage[top=2cm, bottom=2cm, left=2cm, right=2cm]{geometry}
-	\geometry{a4paper}
-	\usepackage{graphicx}
-	%\usepackage{authblk}
-	\usepackage{booktabs}
-	\usepackage{algorithm, algpseudocode}
-	\algrenewcommand\algorithmicrequire{\textbf{Input:}}
-	\algrenewcommand\algorithmicensure{\textbf{Output:}}
-	\author{Various Authors}
-\fi
-
+%Restoring page numbers as missing them out violates basic human rights of the reviewers. -- Olivier
+\thispagestyle{plain}
+\pagestyle{plain}
+
+\usepackage[T1]{fontenc}
+\usepackage[utf8]{inputenc}
+\usepackage{newunicodechar}
+\newunicodechar{⇒}{\implies}
+\newunicodechar{≠}{\ensuremath{\neq}}
+\newunicodechar{≤}{\leq}
+\newunicodechar{≥}{\geq}
+%… Horizontal Ellipsis
+\DeclareUnicodeCharacter{2026}{\ifmmode\dots\else\textellipsis\fi}
 \usepackage{algorithm, algpseudocode}
 \usepackage{amsmath,amssymb,enumerate,amsthm}
+\usepackage{natbib}
 \usepackage{hyperref}
@@
 \usepackage{bm}
+\usepackage{empheq}
 \usepackage{cleveref}
@@
 
-%\newcommand{\rank}{\text{rank}}
-\newcommand{\rank}{v}
-\newcommand{\preflarge}{\boldsymbol{\succeq}^\textbf{r}}%real, complete pref
-%\newcommand{\pref}{\boldsymbol{\succ}^\textbf{r}}%real, connected pref, strict
 \newcommand{\pref}{\succ}%real, connected pref, strict
@@
 \newcommand{\nppref}{\nsucc^\text{p}}%negated partial pref
+\newcommand{\linors}{\mathcal{L}(A)}
+%https://tex.stackexchange.com/a/45732, works within both \set and \set*, same spacing than \mid (https://tex.stackexchange.com/a/52905).
+\newcommand{\suchthat}{\;\ifnum\currentgrouptype=16 \middle\fi|\;}
 
@@
 
-\newrelation{\myRgood}{R^X}
 \newrelation{\pinc}{\!\parallel\!}%partial pref, complement (incomparable)
@@
 
-\newcommand{\profile}{\textbf{v}}%(complete) profile
-\newcommand{\pprofile}{\textbf{p}}%partial profile
-\newcommand{\w}{\textbf{w}}%partial profile
+\newcommand{\profile}{\bm{v}}%(complete) profile
+\newcommand{\pprofile}{\bm{p}}%partial profile
+\newcommand{\w}{\bm{w}}%partial weights
 \newcommand{\C}{\mathcal{C}}%partial profile
+\newcommand{\powersetz}[1]{\mathscr{P}^*(#1)}
 
@@
 
+\DeclarePairedDelimiter\set{\{}{\}}
+
 \title{Robust Winner Determination and Simultaneous Elicitation of Scoring Rules and Preferences}
-%\author{Olivier Cailloux  \and Beatrice Napolitano \and Paolo Viappiani}
-
-%\affil{LIP6\\\email{paolo.viappiani@lip6.fr}
-%\author{Olivier Cailloux} 
-%\author{Stefano Moretti}%\affil{LAMSADE}
-%\author{Beatrice Napolitano}\affil{LAMSADE}
 
@@
 \maketitle
-% aggregate different opinions
-
-%Given a full profile: use linear programming to maximize regret
-%Given a partial profile: use techniques of Lu and Boutilier (2011).
 \begin{abstract}
@@
 \section{Introduction}
-% indeed many works analyze the properties of different rules (including axiomatic treatments) in order to justify the choice of specific social choice functions. 
-%Moreover, it is usually assumed that the preferences of the voters are known completely.
-
-%General motivation: need to deal with partially specified preferences and as well partially specified voting rules
+\commentOC{Do we agree that we should talk systematically about agents (or systematically about voters)? Currently we talk about voters in first section, then agents.}
 Aggregation of preference information is a central task in many computer systems (recommender systems, search engines, etc).
@@
 
-The traditional approach to social choice assumes that both the social function and the full preference orderings of the voters are expressed beforehand. 
-As noted by several authors requiring voters to express full preference orderings can be prohibitively costly (in term of cognitive and communication cost), especially for decisions with large sets of alternatives.
-This observation has motivated a number of recent works considering social choice with partial preference orders  \cite{Xia2008,Pini2009,Konczak05} and incremental elicitation \cite{Kalech2011,Lu2011,Naamani-Dery2015} of voters preferences.
-
-On the other hand, in several situations it may not be easy to precisely define the voting rule.
+The traditional approach to social choice assumes that both the social function and the full preference orderings of the voters are expressed beforehand. This represents two strong hypothesis.
+About the second one, requiring voters to express full preference orderings can be prohibitively costly (in term of cognitive and communication cost), especially for decisions with large sets of alternatives.
+This observation has motivated a number of recent works considering social choice with partial preference orders  \citep{Xia2008,Pini2009,Konczak05} and incremental elicitation \citep{Kalech2011, Lu2011, Naamani-Dery2015} of voters’ preferences.
+
+The first hypothesis also should be relaxed, for in several situations it may not be easy to precisely define the voting rule.
 Indeed, it is possible that the chair may have some preferences over the desired aggregation method, but may still be not able to formalize the voting rule upfront.
-The work of Cailloux and Endriss \cite{Cailloux2014} provides elicitation methods  for a quite general class of rules based on well orders.
-When considering positional scoring rules, several authors \cite{Stein1994,Llamazares2013,Viappiani2018} have worked on  positional scoring rules with uncertain weights (assuming that the preferences of the voters are fully known).
-%it is possible to derive dominance relations (akin to stochastic dominance) that allow to eliminate some alternatives since they will be less preferred than another one for any instantiation of the weights \cite{Stein1994}.
+The work of \citet{Cailloux2014} provides elicitation methods for a quite general class of rules based on weak orders.
+When considering positional scoring rules, several authors \citep{Stein1994, Llamazares2013, Viappiani2018} have worked on positional scoring rules with uncertain weights, assuming that the preferences of the voters are fully known.
+%it is possible to derive dominance relations (akin to stochastic dominance) that allow to eliminate some alternatives since they will be less preferred than another one for any instantiation of the weights \citep{Stein1994}.
 %Among others, Llamazares and Pe{\~{n}}a have considered  the problem of dealing with underspecified weights in positional scoring rules.
 
-In this paper we consider that both preferences and the social choice rule can be only partially specified.
-We develop methods for computing the minimax-optimal alternative for scoring rules with partial preference information and partial information about the weights of the scoring rule.
+In this paper we consider that both the voters’ preferences and the social choice rule are partially specified.
+We develop methods for computing the minimax-optimal alternative for scoring rules with partial voter preference information and partial information about the weights of the scoring rule.
 While previous works have considered either partial information about the voters preferences or a partially specified aggregation method, we do not know of any work considering both sources of uncertainty at the same time.
 
-%We consider that the committee wants to express preferences for some voting rules
-% Incremental elicitation of preferences is critical to easing the cognitive and communication cost for users 
-%In this paper we provide a method for approximate winner determination and an incremental elicitation protocol based on minimax regret. 
-%In this paper we relax the traditional assumptions.
-%Incremental elicitation of preferences can help mitigating the cognitive and communication costs
-
 In this work, we focus on positional scoring rules, that  are a particularly common method used to aggregate rankings and determine a winner.
-We also address the problem of elicitation, providing incremental elicitation methods to acquire relevant preference information; we discuss  several heuristics that allow us to determine queries that quickly allow to reduce minimax regret.
+We also address the problem of elicitation, providing incremental elicitation methods to acquire relevant preference information; we discuss  several heuristics that determine queries that quickly reduce minimax regret.
 In particular, our query strategies focus simultaneously on reduction of relevant preference and voting rule uncertainty.
 % the value of certain preference information is often not worth the cost of obtaining it.
-% We must engage in simultaneous elictation of the rule and of the preferences.
 
@@
 In Section \ref{sec:background} we provide the necessary background.
-We introduce the minimax criterion and in Section \ref{sec:mmr}.
-In Section \ref{sec:elicit} we provide an interactive elicitation protocol based on minima regret;  in Section \ref{sec:experiments} we present the empirical validation of our approach with simulations, and finally in Section \ref{sec:conclusions} we provide some final thoughts.
+We introduce the minimax criterion, that selects a winner that minimizes the worst possible regret, in Section \ref{sec:mmr}.
+In Section \ref{sec:elicit} we provide an interactive elicitation protocol based on minimal regret;  in Section \ref{sec:experiments} we present the empirical validation of our approach with simulations; and Section \ref{sec:conclusions} provides some final thoughts.
 
 \section{Social choice with partial information}\label{sec:background}
-
 We now introduce some basic concepts.
-We assume that there is a set $A$ of $m$ alternatives (for instance products, restaurants, movies, public projects, job candidates, etc.) and $n$ agents (voters); each agent is associated to a preference order.
-The goal of the voters is to make a consensus choice, in order to select a ``winner'' given voter rankings.
-
-%The set of preference orders is called profile and it is denoted by $v$.
-The preferences of the agents are supposed to be linear orders (connected, transitive, asymmetric relations) involving the alternatives;
-$\pref_i$ denotes the ``real'' preference relation of agent $i$. 
-The set $(\pref_1,\ldots,\pref_n)$ is known in the social choice literature as the {\em preference  profile}.
-The profile is equivalently represented by $\profile=(v_1,\ldots,v_n)$ where $v_i(j)$ denotes the rank (position) of alternative $j$ in the preference order $\pref_i$. 
-With a little abuse of notation, we will use the term profile to refer to either $\profile$ or to the preference relations, depending on the context.
-
-Let $V$ be the set of possible preference profiles (the cartesian product of $n$ linear orders).
-A social choice function $f : V \rightarrow 2^A$ associates a profile with a set of winners.
-Among the many possible social choice functions, we consider {\em positional scoring rules}, which attach weights to positions according to  the vector $(w_1,\ldots,w_m)$ (also called the scoring vector).
+We assume defined a set $A$ of $m$ alternatives (products, restaurants, movies, public projects, job candidates, etc.) and a set $\set{1, …, n}$ of agents (voters); each agent $j$ is associated to her “real” preference order $\pref_j$.
+The real preferences of the agents are elements of $\linors$, the linear orders (connected, transitive, asymmetric relations) over the alternatives.
+Following the social choice nomenclature, we call {\em profile} the association of a preference to each voter, denoted by $(\pref_1,\ldots,\pref_n)$, which we assume is fixed but unknown.
+The profile is equivalently represented by $\profile=(v_1,\ldots,v_n)$ where $v_j(i) \in \set{1, \ldots, m}$ denotes the rank (position) of alternative $i$ in the preference order $\pref_j$. 
+%With a little abuse of terminology, we will use the term profile to refer to either $\profile$ or to the preference relations, depending on the context.
+
+Let $V$ be the set of possible preference profiles (the $n$-fold cartesian product of the linear orders over the alternatives).
+A social choice function $f : V \rightarrow \powersetz{A}$ associates a profile with a set of winners, where $\powersetz{A}$ represents the set of subsets of $A$ except for the emptyset.
+(Sets are used for tied winners.)
+Among the many possible social choice functions, we consider {\em positional scoring rules}, which attach weights to positions according to  the vector $(w_1, \ldots, w_m)$ (also called the scoring vector).
 %A scoring rule associates each alternative to a score that is given by the sum of points obtained for each voter.
-An alternative obtains a score that depends on the rank obtained in each of the preference orders:
+An alternative obtains a score that depends on the rank obtained in each of the preference orders \commentOC{Consider removing $v$ and $w$}:
 \begin{align}
+\label{eq:srule}
 s(x; \profile, \w) = \sum_{j=1}^{n} w_{v_j(x)}
-= \sum_{i=1}^{m} \alpha^{x}_i w_i . \label{eq:srule}
+= \sum_{r=1}^{m} \alpha^{x}_r w_r 
 \end{align}
-where $\alpha^{x}_i$ is the number of times that alternative $x$ was ranked in the $i$-th position.
-The winner is the alternative with highest score.
+where $\alpha^{x}_r$ is the number of times that alternative $x$ was ranked in the $r$-th position.
+The winners are the alternatives with highest scores.
 %We assume that the weights constitute a monotonic sequence: $w_{1} \geq w_{2} \geq \ldots \geq w_{m}$.
@@
 In this work we want to reason about partial preference information.
-A partial preference  is encoded by a partial order $\ppref_j$  of voter $j$; in this work we assume that preference information is truthful, i.e. $a \ppref_j b \implies a \pref_j b$.
+Our knowledge at a given time of the preference of voter $j$ is encoded by a partial order over the alternatives, thus a transitive and asymmetric binary relation, denoted by $\ppref_j$. 
+In this work we assume that preference information is truthful, i.e. $a \ppref_j b ⇒ a \pref_j b$.
 We use $\pinc$ to denote incomparability, that is $a \pinc_{j} b$ iff $a \nppref_j b \wedge b \nppref_j a$.
-An incomplete profile is a set of partial votes  $\textbf{p}=(\ppref_1,\ldots,\ppref_n)$.
-
-A completion of $\ppref_i$ is any linear order $\pref_i$ that extends $\ppref_i$.
-Let $C(\ppref_i)$ be the set of completions of $\ppref_i$, that is the set of all complete rankings that extend $\ppref_i$.
-We let $C(\textbf{p})=C(\ppref_1)\times \ldots \times C(\ppref_n)$ be the set of complete profiles extending $p$.
+An incomplete profile $\pprofile = (\ppref_1, \ldots, \ppref_n)$ maps each voter to a partial preference.
+
+A completion of $\ppref_j$ is any linear order $\pref$ that extends $\ppref_j$.
+Let $C(\ppref_i) = \set{{\succ} \in \linors \suchthat {\ppref_j} \subseteq {\succ}}$ be the set of possible completions of $\ppref_i$.
+We let $C(\pprofile)=C(\ppref_1)\times \ldots \times C(\ppref_n)$ be the set of complete profiles extending $p$.
 
@@
 We also assume that the weights of the scoring rule are only partially specified.
-Therefore the vector $(w_1,\ldots,w_m)$  is not known but we are given a set of constraints restraining the possible values that weight can take.
+Therefore the vector $(w_1,\ldots,w_m)$  is not known but we are given a set of constraints restraining the possible values that weights can take.
 We consider a non-increasing sequence of weights:
 \begin{align}
-1=w_{1} \geq w_{2} \geq \ldots \geq w_{m}=0 \label{eq:monotone}
+1=w_{1} \geq w_{2} \geq \ldots \geq w_{m}=0. \label{eq:monotone}
 \end{align}
-this is a natural assumption, as it is better to be ranked first than second, second than third, etc. 
-Without loss of generality, we assume $w_1=1$ and $w_m=0$.
+This is a natural assumption, as it is better to be ranked first than second, second than third, etc. 
+Without loss of generality, we consider that $w_1=1$ and $w_m=0$.
 
 The weights of a scoring rule can model different preferences of the committee. 
-For instance, the weights can control the inclination to favour ``extreme'' alternatives (often at either the top or the bottom of the input rankings) at the expenses of ``moderate'' alternatives (that are more consistently in the middle part of the input rankings).
+For instance, the weights can control the inclination to favor ``extreme'' alternatives (often at either the top or the bottom of the input rankings) at the expenses of ``moderate'' alternatives (that are more consistently in the middle part of the input rankings).
 
 An important class of scoring rule is the one composed of weights that are a convex sequence, meaning that the difference between the weight of the first position and the weight of the second position is at least as much as the difference between the weights of the second and third positions, etc.
-\begin{align} \forall i \in \{1,\ldots,n-2\} \;\; & w_i - w_{i+1} \geq w_{i+1}-w_{i+2}  \\
-\iff & w_i - 2 w_{i+1} + w_{i+2} \geq 0 \label{eq:convexity}
-\end{align}
+%\begin{align} \forall r \in \{1,\ldots,m-2\} \;\; & w_r - w_{r+1} \geq w_{r+1}-w_{r+2}  \\
+%\iff & w_r - 2 w_{r+1} + w_{r+2} \geq 0 \label{eq:convexity}
+%\end{align}
+\begin{equation} 
+\label{eq:convexity}
+\forall r \in \{1,\ldots,m-2\}: w_r - w_{r+1} \geq w_{r+1}-w_{r+2}.
+\end{equation}
 The constraint above is often used when aggregating rankings in sport competitions.
@@
 
-We argue that in general it can be difficult to set the weights in an appropriate way.
-We assume that in addition of basic requirments (monotonicity and convexity)  the chair (the person or the organization that is supervising the voting process) may be able to specify additional preferences about how the social choice function should behave.
-In this work we assume that preferences of the chair are encoded with linear constraints on the vector $\w$, relating the value of the weights of different positions.
-We use $\C(\w)$ to denote, in an abstract way, the preferences of the chair about the scoring vector.
-
-Of course it may be difficult for real decision makers to state preferences about the voting rule in such an abstract way, unless perhaps in some limited cases (a specific instance of these preferences may consist in giving upper or lower bound on the value of $w_{i}$ for position $i$).
-These additional preferences can be elicited by asking questions about concrete profiles, for instance, by showing a complete profile of a small synthetic election and asking who should be elected in this case.
-We discuss queries asked to the chairs and strategies to select queries later in Section \ref{sec:elicit}.
+In general it can be difficult to set the weights in an appropriate way.
+We assume that in addition of basic requirements (monotonicity and convexity), the chair (the person or the organization that is supervising the voting process) is able to specify additional preferences about how the social choice function should behave.
+In this work we assume that preferences of the chair are encoded with linear constraints about the vector $\w$, relating the value of the weights of different positions.
+We use $\C(\w^\text{p})$ to denote the set of weight vectors compatible with the preferences expressed by the chair about the scoring vector. \commentOC{Think about this.}
+
+Of course it may be difficult for real decision makers to state preferences about the voting rule in such an abstract way.
+These additional preferences can be elicited by asking questions about concrete profiles, for instance, by showing a complete profile of a small synthetic election and asking who should be elected in this case, as shown in Section \ref{sec:elicit}.
 
@@
 In this paper, we consider a setting where both the voters' preferences and the preferences of the chair about the voting rule are incomplete.
-Notice that some authors have considered possible and necessary winners assuming a partial profile  \cite{Xia2008} or assuming an incompletely specified scoring rule \cite{Viappiani2018};
+Notice that some authors have considered possible and necessary winners assuming a partial profile  \citep{Xia2008} or assuming an incompletely specified scoring rule \citep{Viappiani2018};
 however, we note that, in typical settings, there will be no necessary winner and too many possible winners.
-In practice, however, it is often imperative to declare a winner (consensus choice) given partial information.
+In practice, however, it is often useful to declare a winner given partial information.
 
 As a decision criterion to determine a winner, we propose to use minimax regret. 
-Minimax regret \cite{Savage1954} is a decision criterion that has been used for robust optimization under data uncertainty \cite{Kouvelis1997} and as well in decision-making with uncertain utility values  \cite{Salo2001,Boutilier2006}.
-%Minimax regret \cite{Boutilier2006} has been used for making decisions under utility uncertainty and for preference elicitation.
-Lu and Boutilier \cite{Lu2011} have adopted minimax regret for winner determination in social choice with
-the preferences of the voters that are only partially known, while the social choice function is known and fixed in advance.
+Minimax regret \citep{Savage1954} is a decision criterion that has been used for robust optimization under data uncertainty \citep{Kouvelis1997} as well as in decision-making with uncertain utility values \citep{Salo2001,Boutilier2006}.
+\citet{Lu2011} have adopted minimax regret for winner determination in social choice with
+the preferences of the voters that are only partially known, while the social choice function is predetermined and known.
 
@@
 
-The maximum regret is considered by assuming an adversary can choose both 1) to extend the partial profile into a complete profile 2) can instantiate the weights choosing among any feasible weight vector in $W \subseteq \mathcal{W}$.
+The maximum regret is considered by assuming that an adversary both 1) can extend the partial profile $\pprofile$ into a complete profile, and 2) can instantiate the weights choosing among any weight vector in $C(\w^\text{p})$, where $\pprofile$ and $\w^\text{p}$ represent our knowledge so far.
 
@@
 \subsection{Computation of minimax regret}
-In order to compute pairwise maximum regret and therefore minimax regret, we adapt the reasoning from \cite{Lu2011} so that we decompose the $\PMR$ into the contributions that is associated to each agent.
+In order to compute pairwise maximum regret and therefore minimax regret, we adapt the reasoning from \citep{Lu2011} so that we decompose the $\PMR$ into the contributions that is associated to each agent.
 The settings is however more challenging due to the presence of uncertainty in the weights.
@@
 
-We consider now a procedure for completing a partial profile that was first proposed by Lu and Boutilier \cite{Lu2011} when considering minimax regret with a fixed rule.
+We consider now a procedure for completing a partial profile that was first proposed by Lu and Boutilier \citep{Lu2011} when considering minimax regret with a fixed rule.
 We will show how this procedure can be used the in the case of uncertain weight vector:
@@
 \]
-Indeed alternative $c$ and $d$ are dominated and they cannot win for any instantiation of the weights; this can be seen by comparing the cumulative ranks (see  \cite{Stein1994}).
+Indeed alternative $c$ and $d$ are dominated and they cannot win for any instantiation of the weights; this can be seen by comparing the cumulative ranks (see  \citep{Stein1994}).
 \[
@@
 
-Refer to \cite{Lu2011}
+Refer to \citep{Lu2011}
 The goal is to choose as a winner the alternative $x^*$ whose worst case loss is minimal under all possible realizations of the full profile and all possible choices of weights. 

### 2019-02-20 draft.tex
Moved around and started alt def PMR

@@
 \newcommand{\profile}{\bm{v}}%(complete) profile
-\newcommand{\pprofile}{\bm{p}}%partial profile
-\newcommand{\w}{\bm{w}}%partial weights
+\newcommand{\pprofile}{{\bm{p}}}%partial profile
+\newcommand{\w}{\bm{w}}
+\newcommand{\pw}{W}%our knowledge about the weights
 \newcommand{\C}{\mathcal{C}}%partial profile
@@
 
-\section{Social choice with partial information}\label{sec:background}
+\section{Social choice with partial information}
+\label{sec:background}
 We now introduce some basic concepts.
@@
 The real preferences of the agents are elements of $\linors$, the linear orders (connected, transitive, asymmetric relations) over the alternatives.
-Following the social choice nomenclature, we call {\em profile} the association of a preference to each voter, denoted by $(\pref_1,\ldots,\pref_n)$, which we assume is fixed but unknown.
+Following the social choice nomenclature, we call {\em profile} the association of a preference to each voter, denoted by $(\pref_1,\ldots,\pref_n)$.
 The profile is equivalently represented by $\profile=(v_1,\ldots,v_n)$ where $v_j(i) \in \set{1, \ldots, m}$ denotes the rank (position) of alternative $i$ in the preference order $\pref_j$.
-%With a little abuse of terminology, we will use the term profile to refer to either $\profile$ or to the preference relations, depending on the context.
 
@@
 %A scoring rule associates each alternative to a score that is given by the sum of points obtained for each voter.
-An alternative obtains a score that depends on the rank obtained in each of the preference orders \commentOC{Consider removing $v$ and $w$}:
+An alternative obtains a score that depends on the rank obtained in each of the preference orders:
 \begin{align}
@@
 
-In this work we want to reason about partial preference information.
+In this work we assume fixed, but unknown, a profile $\profile^*$ (and corresponding voters preferences $\pref_j^*$) and a weight vector $\w^*$, and we want to reason about partial preference information concerning those objects.
 Our knowledge at a given time of the preference of voter $j$ is encoded by a partial order over the alternatives, thus a transitive and asymmetric binary relation, denoted by $\ppref_j$. 
-In this work we assume that preference information is truthful, i.e. $a \ppref_j b ⇒ a \pref_j b$.
+In this work we assume that preference information is truthful, i.e. $a \ppref_j b ⇒ a \pref_j^* b$.
 We use $\pinc$ to denote incomparability, that is $a \pinc_{j} b$ iff $a \nppref_j b \wedge b \nppref_j a$.
@@
 A completion of $\ppref_j$ is any linear order $\pref$ that extends $\ppref_j$.
-Let $C(\ppref_i) = \set{{\succ} \in \linors \suchthat {\ppref_j} \subseteq {\succ}}$ be the set of possible completions of $\ppref_i$.
-We let $C(\pprofile)=C(\ppref_1)\times \ldots \times C(\ppref_n)$ be the set of complete profiles extending $p$.
+Let $C(\ppref_j) = \set{{\succ} \in \linors \suchthat {\ppref_j} \subseteq {\succ}}$ be the set of possible completions of $\ppref_i$.
+We let $C(\pprofile)=C(\ppref_1)\times … \times C(\ppref_n)$ be the set of complete profiles extending $p$. Note that $\profile^* \in C(\pprofile)$.
 
@@
 Therefore the vector $(w_1,\ldots,w_m)$  is not known but we are given a set of constraints restraining the possible values that weights can take.
-We consider a non-increasing sequence of weights:
+We consider a decreasing sequence of weights:
 \begin{align}
-1=w_{1} \geq w_{2} \geq \ldots \geq w_{m}=0. \label{eq:monotone}
+1=w_{1} > w_{2} > \ldots > w_{m}=0. \label{eq:monotone}
 \end{align}
@@
 Without loss of generality, we consider that $w_1=1$ and $w_m=0$.
+\commentOC{I suggest we say no more than this to justify this assumption.
+Otherwise, we might say something like the following.
+If the committee considers that, for example, “only the first ten positions matter” (so that $w_r = 0$ for $r > 10$), then we simply assume the committee is able to express this constraint at the start of the querying process, thus, that this information is known.}
 
@@
 In this work we assume that preferences of the chair are encoded with linear constraints about the vector $\w$, relating the value of the weights of different positions.
-We use $\C(\w^\text{p})$ to denote the set of weight vectors compatible with the preferences expressed by the chair about the scoring vector. \commentOC{Think about this.}
+We use $\pw \subseteq \mathcal{W}$ to denote the set of weight vectors compatible with the preferences expressed by the chair about the scoring vector.
 
@@
 
-The maximum regret is considered by assuming that an adversary both 1) can extend the partial profile $\pprofile$ into a complete profile, and 2) can instantiate the weights choosing among any weight vector in $C(\w^\text{p})$, where $\pprofile$ and $\w^\text{p}$ represent our knowledge so far.
+The maximum regret is considered by assuming that an adversary both 1) can extend the partial profile $\pprofile$ into a complete profile, and 2) can instantiate the weights choosing among any weight vector in $\pw$, where $\pprofile$ and $\pw$ represent our knowledge so far.
 
 We formalize the notion of minimax regret in multiple steps.
-First of all, $\Regret(x, \profile, \w)$ is the loss or ``actual'' regret  of selecting $x$ as a winner instead of choosing the optimal alternative under $\profile$ and $\w$:
-\[\Regret(x, \profile, \w) = \max_{y \in A} s(y; \profile,\w) - s(x; \profile, \w).\]
-
-The pairwise max regret of $x$ relative to $y$ given partial profile $\pprofile$ and the space of weights $W$
-$\PMR(x,y;\pprofile,W)$ is the worst-case loss under all possible realizations of the full profile {\em and} all possible instantiations of the weights:
-\begin{align}
-\PMR(x,y; \pprofile, W) & = \max_{\w \in W} \max_{\profile \in C(p)} s(y; \profile,\w) - s(x; \profile,\w).
-\end{align}
+First of all, denote by $s^*_{\profile, \w} = \max_{y \in A} s(y; \profile, \w)$ the score achieved by winning alternatives under $\profile$ and using weights $\w$.
+Now define $\Regret(x, \profile, \w)$ as the “regret” of selecting $x$ as a winner instead of choosing the optimal alternative under $\profile$ and $\w$:
+\[\Regret(x, \profile, \w) = s^*_{\profile, \w} - s(x; \profile, \w).\]
+
+%The pairwise max regret $\PMR(x,y;\pprofile,W)$ of $x$ relative to $y$ given partial profile $\pprofile$ and the set of weights $W$
+%is the worst-case loss under all possible realizations of the full profile {\em and} all possible instantiations of the weights:
+%\begin{align}
+%\PMR(x,y; \pprofile, W) & = \max_{\w \in W} \max_{\profile \in C(\pprofile)} s(y; \profile,\w) - s(x; \profile,\w).
+%\end{align}
 
 Max regret $\MR(x;\pprofile,W)$ is the worst-case loss of $x$.
-It is the loss occurred by an adversarial selection of a complete profile $\profile$ extending $\pprofile$ and a selection of $\w \in W$ to maximize the loss between $x$ and the true winner under $\profile$ and $w$.
+It is the loss occurred by an adversarial selection of a complete profile $\profile$ extending $\pprofile$ and a selection of $\w \in W$ to maximize the loss between $x$ and the true winner under $\profile$ and $\w$.
 \begin{align}
@@
 
-\subsubsection{Minimax regret without the convex assumption}
-{\em (Still here? Or move it somewhere else?) }
-
-Without the convex assumption, we cannot use $\hat{v}$ for the agents in $U^{-}$, but only for agents in $U^{+}$ and $U^{?}$.
-%Let $\hat{v}_i$ be the linear order extending $\succ^{p}_i$ according to the above procedure.
-Then PMR can be written as follows:
-\begin{align*}
- &\PMR(x,y; \pprofile, W) =\\ 
- &\max_{\w \in W} \Big \{ \sum_{j \in U^-} [\max_{v_j \in C(\succ_j^p)} [w_{v_j(y)} \!-\! w_{v_j(x)}]] 
-  \!+\!	 \sum_{j \in A^+ \cup  U^?} [w_{\hat{v}_j(y)} \!-\! w_{\hat{v}_j(x)}] \Big \} 
- \end{align*}
-%Note that the second addendum inside the max do not depend on the choice of $\w$.
-Consider the two addenda inside the ``max''. 
-The first addendum is concerned with positioning of alternatives $x$ and $y$ for voters in $U^{-}$ for which we know that $x$ is preferred to $y$.
-The second addendum is concerned with voters in $U^{+}$ and $U^{?}$.
-We rewrite the second addendum as:
-\begin{align*}
-\sum_{j \in U^+ \cup  U^?} [w_{\hat{v}_j(y)} \!-\! w_{\hat{v}_j(x)}] 
-= \sum_{i = 1}^{m} (\hat{\alpha}_{i}^{y} - \hat{\alpha}_{i}^{x}) w_{i}
-\end{align*}
-where $\hat{\alpha}_{i}^{x}$ is the number of times that $x$ is ranked  in position $i$  considering the profile $\hat{v}$ of voters in $U^+ \cup  U^?$.
-%We compute pairwise maximum regret by considering binary variables $\{ B_{i} \}_{i=1,\ldots,m}$ to represent optimization choices related to where to position the alternatives.
-
-We now address the agents in $A^{-}$
-For a given $j$, let $\beta$ be the number of alternatives that are incomparable with $x$ and $y$:
-\[ \beta_{j} = \mid \{ c : c \pinc_{j} y \wedge c \pinc_{j} x \} \mid \]
-$x$ can be ranked between $t_{1}(j)=\mid \{ c \in A : c \ppref_{j} y \wedge x \nppref_{j} c \} \mid $ and position $t_{2}(j)=t_{1}(j)+\beta_{j}$.
-The completion for agent $j$ is such that the positions of $x$ and $y$ differ of exactly $\gamma_{j} =
-\mid \{ c \in A : x \ppref c \ppref y \} \mid$ positions.
-
-We now show how to optimize $\PMR$.
-In addition to variables $\{ w_{j} \}_{j=1,\ldots,m}$ (one for each position) we need to employ several additional decision variables.
-We introduce two sets of binary variables $B^{+}_{i,j}$ and $B^{-}_{i,j}$  for each position $i$ and for each voter $j$.
-Variable $B_{i,j}^{+}$ encodes the fact that the alternative $y$ is placed in position $i$ in the ranking of agent $j$; while  $B_{i,j}^{-}$ encodes the same thing for alternative $x$.
-%We also have numerical variables to represent the weights of the scoring rule.
-Since each alternative needs to be placed exactly in one place for each agent, we adopt the constraints
-$\sum_{i=t_{1}(j)}^{t_{2}(j)} B_{i,j}^{+} = 1$.
-Since we know that $x$ and $y$ are ranked $\gamma_{j}$ positions apart, we set the constraint:
-$B_{i+\gamma_{j},j}^{-} \geq B_{i,j}^{+}$,  for $i = \{ t_{1}(j), \ldots, t_{2}(j)\}$.
-
-% and $\sum_{i=1}^{m} B_{i,j}^{-} = 1$.
-%Since the objective is to maximize pairwise regret...
-
-The score of alternative $y$ can be written as $\sum_{i = 1}^{m} \hat{\alpha}_{i}^{y}  w_{i} + \sum_{i=1}^{n} \sum_{j=1}^{m} w_{j} B_{i,j}^{+}$.
-The objective function is now:
- \[ \max \sum_{i = 1}^{m} (\hat{\alpha}_{i}^{y} - \hat{\alpha}_{i}^{x}) w_{i} +  \sum_{i=1}^{n} \sum_{j=1}^{m} (B_{i,j}^{+} - B_{i,j}^{-})  w_i \]
-
-We use integer programming enconding tricks in order to linearize the problem.
-We introduce yet another set of variables  $V_{i,j}^{+} $  and $V_{i,j}^{-}$ % the multiplicative terms by new variables.
-and we enforce that $V_{i,j}^{+} = B^{+}_{i,j} w_i$ by setting constraints $V_{i,j}^{+} \leq B^{+}_{i,j}$ and $V_{i,j}^{+}  \leq w_i$.
-We have similar constraints for enforcing $V_{i,j}^{-} = B^{-}_{i,j} w_i$.
-
-We therefore obtain the following mixed integer linear program:
-\begin{align}
-\max & \sum_{i=1}^m  [(\hat{\alpha}_{i}^{y} - \hat{\alpha}_{i}^{x}) w_{i}] +
-  \sum_{j \in A^{-}} \sum_{i=t_{1}}^{t_{2}}  [V_{i,j}^{+} - V_{i,j}^{-}]
-\end{align}
-\begin{align}
-\text{ s.t. } &  \text{Equation } (\ref{eq:monotone}) & \\
-&  \C(\w) &  \\
-& \sum_{i=t_{1}}^{t_{2}} B_{i,j}^{+} = 1 & \forall j \in A^{-} \\
-& B_{i+\gamma_{j},j}^{-} \geq B_{i,j}^{+} & \forall i \in \{ t_{1}, \ldots t_{2}\}, \forall j \in A^{-} \\
-& V_{i,j}^{+} \leq B_{i,j}^{+}  & \forall i \in \{ t_{1}, \ldots t_{2}\}, j \in A^{-} \\
-& V_{i,j}^{+} \leq w_i & \forall i \in \{ t_{1}, \ldots t_{2}\}, j \in A^{-} \\
-& V_{i,j}^{-} \geq w_{i} + B_{i,j}^{-} - 1 & \forall i \in \{ t_{1}, \ldots t_{2}\}, j \in A^{-}\\
-& V_{i,j}^{-} \geq 0 & \forall i \in \{ t_{1}, \ldots t_{2}\}, j \in A^{-}
-\end{align} 
-%We write $w \in W$ as a shourtcut to represent the constraints that the weights are chosen to be in the feasible set.
-There are (at most) $nm$ binary variables and $m(n+1)$ numerical variables.
-The optimization program can be solved by any suitable MILP solver, although it is not suitable to large problem instances.
-
-% DONT KNOW IF WE HAVE TO FORMALIZE THIS AS A CLAIM
-%\begin{claim}
-%The $\PMR$ is computed using the above optimization problem.
-%\end{claim}
-
-\section{Interactive Elicitation} \label{sec:elicit}
-
+\section{Interactive Elicitation} 
+\label{sec:elicit}
 We propose an incremental elicitation method based on minimax regret.
@@
 %
+
+\section{Minimax regret without the convex assumption}
+Without the convex assumption, we cannot use $\hat{v}$ for the agents in $U^{-}$, but only for agents in $U^{+}$ and $U^{?}$.
+%Let $\hat{v}_i$ be the linear order extending $\succ^{p}_i$ according to the above procedure.
+Then PMR can be written as follows:
+\begin{align*}
+ &\PMR(x,y; \pprofile, W) =\\ 
+ &\max_{\w \in W} \Big \{ \sum_{j \in U^-} [\max_{v_j \in C(\succ_j^p)} [w_{v_j(y)} \!-\! w_{v_j(x)}]] 
+  \!+\!	 \sum_{j \in A^+ \cup  U^?} [w_{\hat{v}_j(y)} \!-\! w_{\hat{v}_j(x)}] \Big \} 
+ \end{align*}
+%Note that the second addendum inside the max do not depend on the choice of $\w$.
+Consider the two addenda inside the ``max''. 
+The first addendum is concerned with positioning of alternatives $x$ and $y$ for voters in $U^{-}$ for which we know that $x$ is preferred to $y$.
+The second addendum is concerned with voters in $U^{+}$ and $U^{?}$.
+We rewrite the second addendum as:
+\begin{align*}
+\sum_{j \in U^+ \cup  U^?} [w_{\hat{v}_j(y)} \!-\! w_{\hat{v}_j(x)}] 
+= \sum_{i = 1}^{m} (\hat{\alpha}_{i}^{y} - \hat{\alpha}_{i}^{x}) w_{i}
+\end{align*}
+where $\hat{\alpha}_{i}^{x}$ is the number of times that $x$ is ranked  in position $i$  considering the profile $\hat{v}$ of voters in $U^+ \cup  U^?$.
+%We compute pairwise maximum regret by considering binary variables $\{ B_{i} \}_{i=1,\ldots,m}$ to represent optimization choices related to where to position the alternatives.
+
+We now address the agents in $A^{-}$
+For a given $j$, let $\beta$ be the number of alternatives that are incomparable with $x$ and $y$:
+\[ \beta_{j} = \mid \{ c : c \pinc_{j} y \wedge c \pinc_{j} x \} \mid \]
+$x$ can be ranked between $t_{1}(j)=\mid \{ c \in A : c \ppref_{j} y \wedge x \nppref_{j} c \} \mid $ and position $t_{2}(j)=t_{1}(j)+\beta_{j}$.
+The completion for agent $j$ is such that the positions of $x$ and $y$ differ of exactly $\gamma_{j} =
+\mid \{ c \in A : x \ppref c \ppref y \} \mid$ positions.
+
+We now show how to optimize $\PMR$.
+In addition to variables $\{ w_{j} \}_{j=1,\ldots,m}$ (one for each position) we need to employ several additional decision variables.
+We introduce two sets of binary variables $B^{+}_{i,j}$ and $B^{-}_{i,j}$  for each position $i$ and for each voter $j$.
+Variable $B_{i,j}^{+}$ encodes the fact that the alternative $y$ is placed in position $i$ in the ranking of agent $j$; while  $B_{i,j}^{-}$ encodes the same thing for alternative $x$.
+%We also have numerical variables to represent the weights of the scoring rule.
+Since each alternative needs to be placed exactly in one place for each agent, we adopt the constraints
+$\sum_{i=t_{1}(j)}^{t_{2}(j)} B_{i,j}^{+} = 1$.
+Since we know that $x$ and $y$ are ranked $\gamma_{j}$ positions apart, we set the constraint:
+$B_{i+\gamma_{j},j}^{-} \geq B_{i,j}^{+}$,  for $i = \{ t_{1}(j), \ldots, t_{2}(j)\}$.
+
+% and $\sum_{i=1}^{m} B_{i,j}^{-} = 1$.
+%Since the objective is to maximize pairwise regret...
+
+The score of alternative $y$ can be written as $\sum_{i = 1}^{m} \hat{\alpha}_{i}^{y}  w_{i} + \sum_{i=1}^{n} \sum_{j=1}^{m} w_{j} B_{i,j}^{+}$.
+The objective function is now:
+ \[ \max \sum_{i = 1}^{m} (\hat{\alpha}_{i}^{y} - \hat{\alpha}_{i}^{x}) w_{i} +  \sum_{i=1}^{n} \sum_{j=1}^{m} (B_{i,j}^{+} - B_{i,j}^{-})  w_i \]
+
+We use integer programming enconding tricks in order to linearize the problem.
+We introduce yet another set of variables  $V_{i,j}^{+} $  and $V_{i,j}^{-}$ % the multiplicative terms by new variables.
+and we enforce that $V_{i,j}^{+} = B^{+}_{i,j} w_i$ by setting constraints $V_{i,j}^{+} \leq B^{+}_{i,j}$ and $V_{i,j}^{+}  \leq w_i$.
+We have similar constraints for enforcing $V_{i,j}^{-} = B^{-}_{i,j} w_i$.
+
+We therefore obtain the following mixed integer linear program:
+\begin{align}
+\max & \sum_{i=1}^m  [(\hat{\alpha}_{i}^{y} - \hat{\alpha}_{i}^{x}) w_{i}] +
+  \sum_{j \in A^{-}} \sum_{i=t_{1}}^{t_{2}}  [V_{i,j}^{+} - V_{i,j}^{-}]
+\end{align}
+\begin{align}
+\text{ s.t. } &  \text{Equation } (\ref{eq:monotone}) & \\
+&  \C(\w) &  \\
+& \sum_{i=t_{1}}^{t_{2}} B_{i,j}^{+} = 1 & \forall j \in A^{-} \\
+& B_{i+\gamma_{j},j}^{-} \geq B_{i,j}^{+} & \forall i \in \{ t_{1}, \ldots t_{2}\}, \forall j \in A^{-} \\
+& V_{i,j}^{+} \leq B_{i,j}^{+}  & \forall i \in \{ t_{1}, \ldots t_{2}\}, j \in A^{-} \\
+& V_{i,j}^{+} \leq w_i & \forall i \in \{ t_{1}, \ldots t_{2}\}, j \in A^{-} \\
+& V_{i,j}^{-} \geq w_{i} + B_{i,j}^{-} - 1 & \forall i \in \{ t_{1}, \ldots t_{2}\}, j \in A^{-}\\
+& V_{i,j}^{-} \geq 0 & \forall i \in \{ t_{1}, \ldots t_{2}\}, j \in A^{-}
+\end{align} 
+%We write $w \in W$ as a shourtcut to represent the constraints that the weights are chosen to be in the feasible set.
+There are (at most) $nm$ binary variables and $m(n+1)$ numerical variables.
+The optimization program can be solved by any suitable MILP solver, although it is not suitable to large problem instances.
+
+% DONT KNOW IF WE HAVE TO FORMALIZE THIS AS A CLAIM
+%\begin{claim}
+%The $\PMR$ is computed using the above optimization problem.
+%\end{claim}
 

### 2019-02-20 draft.tex
Given up alt def PMR

@@
 We formalize the notion of minimax regret in multiple steps.
-First of all, denote by $s^*_{\profile, \w} = \max_{y \in A} s(y; \profile, \w)$ the score achieved by winning alternatives under $\profile$ and using weights $\w$.
-Now define $\Regret(x, \profile, \w)$ as the “regret” of selecting $x$ as a winner instead of choosing the optimal alternative under $\profile$ and $\w$:
-\[\Regret(x, \profile, \w) = s^*_{\profile, \w} - s(x; \profile, \w).\]
-
-%The pairwise max regret $\PMR(x,y;\pprofile,W)$ of $x$ relative to $y$ given partial profile $\pprofile$ and the set of weights $W$
-%is the worst-case loss under all possible realizations of the full profile {\em and} all possible instantiations of the weights:
-%\begin{align}
-%\PMR(x,y; \pprofile, W) & = \max_{\w \in W} \max_{\profile \in C(\pprofile)} s(y; \profile,\w) - s(x; \profile,\w).
-%\end{align}
+First of all, $\Regret(x, \profile, \w)$ is the “regret” of selecting $x$ as a winner instead of choosing the optimal alternative under $\profile$ and $\w$:
+\[\Regret(x, \profile, \w) = \max_{y \in A} s(y; \profile,\w) - s(x; \profile, \w).\]
+
+The pairwise max regret $\PMR(x,y;\pprofile,W)$ of $x$ relative to $y$ given partial profile $\pprofile$ and the set of weights $W$
+is the worst-case loss under all possible realizations of the full profile {\em and} all possible instantiations of the weights:
+\begin{align}
+\PMR(x,y; \pprofile, W) & = \max_{\w \in W} \max_{\profile \in C(\pprofile)} s(y; \profile,\w) - s(x; \profile,\w).
+\end{align}
 

### 2019-02-23 draft.tex
Reworked Secs 1 to 3.

@@
 \newif\ifappendix
-%\appendixtrue %COMMENT to remove appendix % UNCOMMENT to add apendix
+\appendixtrue %COMMENT to remove appendix % UNCOMMENT to add apendix
 \input{ijcai_preamble} 
@@
 \DeclareUnicodeCharacter{2026}{\ifmmode\dots\else\textellipsis\fi}
+\newunicodechar{∧}{\land}
+\newunicodechar{∨}{\lor}
+\newunicodechar{∩}{\cap}
+\newunicodechar{∪}{\cup}
+%¬ Not Sign
+\DeclareUnicodeCharacter{00AC}{\ifmmode\lnot\else\textlnot\fi}
+\newunicodechar{⇔}{\Leftrightarrow}
 \usepackage{algorithm, algpseudocode}
@@
 \newcommand{\ppref}{\succ^\text{p}}%partial pref
+\newcommand{\pprefinv}{\prec^\text{p}}%partial pref
 \newcommand{\nppref}{\nsucc^\text{p}}%negated partial pref
@@
 \newcommand{\pw}{W}%our knowledge about the weights
-\newcommand{\C}{\mathcal{C}}%partial profile
 \newcommand{\powersetz}[1]{\mathscr{P}^*(#1)}
@@
 \DeclareMathOperator{\MMR}{MMR}
+\DeclareMathOperator*{\argmax}{argmax}
+\DeclareMathOperator*{\argmin}{argmin}
 
@@
 \DeclarePairedDelimiter\set{\{}{\}}
+\DeclarePairedDelimiter\card{\lvert}{\rvert}
+
+%TODO remove this before submission
+	\tolerance=2000
+	%Accept overfull hbox up to...
+	\hfuzz=1cm
+	%Reduces verbosity about the bad line breaks.
+	\hbadness 10000
+	%Reduces verbosity about the underful vboxes.
+	\vbadness=10000
 
@@
 Otherwise, we might say something like the following.
-If the committee considers that, for example, “only the first ten positions matter” (so that $w_r = 0$ for $r > 10$), then we simply assume the committee is able to express this constraint at the start of the querying process, thus, that this information is known.}
-
-The weights of a scoring rule can model different preferences of the committee. 
+If the chair considers that, for example, “only the first ten positions matter” (so that $w_r = 0$ for $r > 10$), then we simply assume the chair is able to express this constraint at the start of the querying process, thus, that this information is known, and approximate the problem by considering that it is only about the first ten alternatives, thus, set $m=10$.}
+
+The weights of a scoring rule can model different preferences of the chair. 
 For instance, the weights can control the inclination to favor ``extreme'' alternatives (often at either the top or the bottom of the input rankings) at the expenses of ``moderate'' alternatives (that are more consistently in the middle part of the input rankings).
 
-An important class of scoring rule is the one composed of weights that are a convex sequence, meaning that the difference between the weight of the first position and the weight of the second position is at least as much as the difference between the weights of the second and third positions, etc.
+An important class of scoring rule is the one composed of weights that are a convex sequence, meaning that the difference between the weight of the first position and the weight of the second position is at least as great as the difference between the weights of the second and third positions, etc.
 %\begin{align} \forall r \in \{1,\ldots,m-2\} \;\; & w_r - w_{r+1} \geq w_{r+1}-w_{r+2}  \\
@@
 In this work we assume that preferences of the chair are encoded with linear constraints about the vector $\w$, relating the value of the weights of different positions.
-We use $\pw \subseteq \mathcal{W}$ to denote the set of weight vectors compatible with the preferences expressed by the chair about the scoring vector.
+We use $\pw \subseteq \mathcal{W}$ to denote the set of weight vectors compatible with the preferences expressed by the chair about the scoring vector, and $C_W$ to denote the set of linear constraints expressed by the chair.
 
@@
 
-%The quality of an alternative can be quantified by considering the maximum regret with respect to an adversary that can choose the instantiation of both a complete profile (extending the known preferences of the agents) and of the scoring vectors (associated to the preferences of the committee).
+%The quality of an alternative can be quantified by considering the maximum regret with respect to an adversary that can choose the instantiation of both a complete profile (extending the known preferences of the agents) and of the scoring vectors (associated to the preferences of the chair).
 In this paper, we consider a setting where both the voters' preferences and the preferences of the chair about the voting rule are incomplete.
@@
 
-Finally,  $\MMR(\pprofile,W)$ is the value of minimax regret under $\pprofile$ and $W$, obtained when recommending a minimax optimal alternative $x^*$:
+Finally,  $\MMR(\pprofile,W)$ is the value of minimax regret under $\pprofile$ and $W$, obtained when recommending a minimax optimal alternative $x^*_{\pprofile, W}$:
 \begin{align*}
 \MMR(\pprofile,W) & = \min_{x \in A} \MR(x;\pprofile,W) \\
-x^{*}_{\pprofile,W} & \in \arg\min_{x \in A} \MR(x;\pprofile,W) 
+x^{*}_{\pprofile,W} \in A^*_{\pprofile, W} & = \argmin_{x \in A} \MR(x;\pprofile,W) 
 \end{align*}
-By picking as consensus choice\footnote{In cases of ties in minimax regret, we can either decide to return all minimax alternatives as ``winner'' or to pick just one of them using some tie-breaking strategy.} an alternative associated with minimax regret, we can provide a recommendation that gives worst-case guarantees, giving some robustness in face of uncertainty (due to both not knowing the agents' preferences and the weights used in the aggregation).
-
-Notice that if $MMR(\pprofile, W)=0$, then $x^{*}_{\pprofile,W}$  is a necessary co-winner; this means that for any valid completition of the profile and any feasible weight $w \in W$, $x^{*}_{\pprofile,W}$ obtains the highest score (possibly with ties).
+By picking as consensus choice
+ an alternative associated with minimax regret, we can provide a recommendation that gives worst-case guarantees, giving some robustness in face of uncertainty (due to both not knowing the agents' preferences and the weights used in the aggregation).
+In cases of ties in minimax regret, we can either decide to return all minimax alternatives $A^*_{\pprofile, W}$ as winners or to pick just one of them using some tie-breaking strategy.
+
+Notice that if $MMR(\pprofile, W)=0$, then $x^{*}_{\pprofile,W}$  is a necessary co-winner; this means that for any valid completition of the profile and any feasible weight $w \in W$, $x^{*}_{\pprofile,W}$ obtains a highest score.
+
+We note that our notion of regret gives some cardinal meaning to the scores: instead of just being used to select winners under the corresponding PSR, their differences are considered as representing the regret of the chair.
 
 % Add some general remarks about using minimax regret
+
 \subsection{Computation of minimax regret}
-In order to compute pairwise maximum regret and therefore minimax regret, we adapt the reasoning from \citep{Lu2011} so that we decompose the $\PMR$ into the contributions that is associated to each agent.
-The settings is however more challenging due to the presence of uncertainty in the weights.
+In order to compute pairwise maximum regret and therefore minimax regret, we adapt the reasoning from \citet{Lu2011} so that we decompose the $\PMR$ into the contributions associated to each agent.
+The setting is however more challenging due to the presence of uncertainty in the weights.
 
@@
 %A scoring rule associates each alternative to a score that is given by the sum of points obtained for each voter.
-Let $s(x; v_j,\w)=w_{v_j(x)}$ be the number of points that $x$ obtains in the ranking $v_j$ (see Equation \ref{eq:srule}), that is given by weight of position $v_j(x)$.
-Obviously we have 
-\[ s(x; \profile, \w) = \sum_{j=1}^n s(x; v_j,\w). \]
-
-By exploiting the decomposition of the score in terms of votes, we write the actual regret of choosing $x$ instead of $y$ as:
+Recall that when computing $s(x; \profile, \w)$, $w_{v_j(x)}$ is the number of points that $x$ obtains in the ranking $v_j$ (see Equation \ref{eq:srule}).
+By exploiting the decomposition of the score in terms of votes, we write the actual regret of choosing $x$ instead of $y$ as
 \[
-s(y; \profile,\w) - s(x; \profile, \w) = [\sum_{j=1}^n s(y; v_j,\w) - s(x; v_j,\w)]
+s(y; \profile,\w) - s(x; \profile, \w) = \sum_{j=1}^n w_{v_j(y)} - w_{v_j(x)},
 \]
@@
 \begin{align*}
-& \PMR(x,y; \pprofile, W) = \max_{\w \in W} \max_{\profile \in C(\pprofile)} [ s(y; \profile,\w) - s(x; \profile,\w) ] = \\
-& =  \max_{\w \in W} \sum_{j=1}^{n} \max_{v_j \in C(\succ_j^p)} [s(y; v_j,\w) - s(x; v_j,\w)]=\\
-& =  \max_{\w \in W} \sum_{j=1}^{n} \max_{v_j \in C(\succ_j^p)} [w_{v_j(y)} - w_{v_j(x)}] \\
+& \PMR(x,y; \pprofile, W) = \max_{\w \in W} \max_{\profile \in C(\pprofile)} [ s(y; \profile,\w) - s(x; \profile,\w) ] \\
+& =  \max_{\w \in W} \sum_{j=1}^{n} \max_{v_j \in C(\succ_j^p)} [w_{v_j(y)} - w_{v_j(x)}]. \\
 \end{align*}
@@
 
-We consider now a procedure for completing a partial profile that was first proposed by Lu and Boutilier \citep{Lu2011} when considering minimax regret with a fixed rule.
-We will show how this procedure can be used the in the case of uncertain weight vector:
-in the case of convex scoring rules we will be able to greatly simplify the problem by decoupling the two maximizations, while in the general case we will propose to solve it using a mixed integer program.
-
-Let $U^+=\{ i \mid \ y \ppref_i x\}$ be the set of agents for which we know that $y$ is preferred to $x$ (positive contribution to pairwise regret), $U^-=\{ i \mid x \ppref_i y\}$ 
-be the set of agents for wich we  know that $x$ is preferred to $y$ (negative contribution) and 
-$U^?=\{ i \mid x \pinc_i y\}$ 
-%$U^?=\{ i \mid x \nsucc_{i} y \wedge y \nsucc_{i} x \}$ 
-the remaining case, where the preference between $x$ and $y$ is not known.
-Consider how the adversary, whose goal is to maximize $\PMR$ between $x$ and $y$, will complete the partial orders:
-\begin{itemize}
- \item $j \in U^+$: If we know that agent $j$ prefers $y$ to $x$ then the contribution to $\PMR$ is positive and adversary will complete the partial order of agent $j$ by placing as many alternatives as possible between $y$ and $x$ (because of monotonicity of the weights).
- The way the partial order is completed does not depend on the actual values of the weights.
-
- \item $j \in U^?$: If we do not know whether $x$ or $y$ is preferred by agent $j$ then the adversary will place $y$ before $x$ (since the goal is to maximize the difference in score between $y$ and $x$, and weights are monotone) in the linear order and this case reduce to the first one; therefore also in this case the completion of the partial order can be done independently of the choice of $w$.
-
- \item $j \in U^-$: If we know that agent $j$ prefers $x$ to $y$ then (as the contribution of this agent to $\PMR$ is negative) the adversary will place as few alternatives as possible between $x$ and $y$.
-
-The only issue is with respect to the  alternatives that are incomparable with $x$ and $y$ according to $\ppref_i$: should they be placed better than $x$ or worse than $y$ ?
-If the scoring vector is known to be convex,  than these alternatives will be placed better than $x$ in the completion; otherwise the placements of these depend on the weights $\w$.
-\end{itemize}
-
-\subsubsection{Minimax regret computation under the convex assumption}
-
-Since weights are assumed to be convex, the adversary will place all alternatives $c$ that are such that $c \pinc_{j} y \wedge c \pinc_{j} x$ as better than $x$.
-We now formalize the reasoning about the best (with respect to maximizing $\PMR$) completion with the following definition.
-\begin{definition}
-Given the partial profile $\pprofile$, define $\hat{\profile}$ as the completition of $\pprofile$ such that:
-\begin{itemize}
-\item For each $j \in U^{+}$, set   $\hat{\profile}$ as follows, for all $c \in A$:\\
-if $c \pinc_{j} x$ we set $c \succ_{j}^{\hat{\profile}} x$;\\
-if  $c \pinc_{j} y$ we set $y \succ_{j}^{\hat{\profile}} c$.
-\item For each $j \in U^{?}$, set  $\hat{\profile}$ as follows:\\
-$y \succ_{j}^{\hat{\profile}} x$;\\
-for all $c \in A$, if   $c \pinc_{j} x$ we set $c \succ_{j}^{\hat{\profile}} x$;\\
-for all $c \in A$, if   $c \pinc_{j} y$ we set $y \succ_{j}^{\hat{\profile}} c$.
-\item For each $j \in U^{-}$,  set  $\hat{\profile}$ as follows, for all $c \in A$:\\
-if $c \pinc_{j} x \wedge c \succ^{p}_{j} y$ we set $c \succ_{j}^{\hat{\profile}} x$;\\
-if $c \pinc_{j} y \wedge  x \succ^{p}_{j} c$ we set $y \succ_{j}^{\hat{\profile}} c$;\\
-if $c \pinc_{j} y \wedge c \pinc_{j} x$ we set $c \succ_{j}^{\hat{\profile}} x$.
-\end{itemize}
-\end{definition}
+We consider now a procedure for completing a partial profile that was first proposed by \citet{Lu2011} when considering minimax regret with a fixed weight vector.
+As we will show, this procedure can also be used in our case of uncertain weight vector.
+%in the case of convex scoring rules we will be able to greatly simplify the problem by decoupling the two maximizations.
+
+We are interested in computing $PMR(x, y; \pprofile, W)$.
+This represents the “worst” difference of score, thus the difference of score between $y$ and $x$ under the worst case preferences compatible with $\pprofile$ and $W$, where the worst case is the one that maximizes this difference of score.
+Consider our knowledge $\ppref_j$ of the preference of an agent $j$.
+The adversary has to make the score of $y$ as high as possible, and the score of $x$ as low as possible.
+To do this, he should complete $\ppref_j$ to $\pref_j$ by putting above $x$ as many alternatives as he can, that is, all the alternatives except those that are known to be worst than $x$ (those $a$ such that $x \ppref_j a$); and similarly, put below $y$ all the alternatives he can, thus, put above $y$ only those $a$ such that $a \ppref_j y$.
+Sometimes these two objectives conflict: when an alternative should go above $x$ according to the first objective and below $y$ according to the second one (because $¬(x \ppref_j a) ∧ ¬(a \ppref_j y)$), and $x$ is known to be better than $y$ (thus $x \ppref_j y$).
+In this case, the first objective should take priority, and $a$ should be put above $x$, which will move both $x$ and $y$ one rank lower than if $a$ had been put below $y$.
+This maximizes the adversary’s interests: because the weight vector is convex, the difference in scores will be lower when both alternatives are one rank lower (Equation \ref{eq:convexity}), and that difference of score is in favor of $x$ when $x \ppref_j y$, thus to be minimized from the point of view of the adversary.
+To summarize:\commentOC{TODO only one number here} 
+\begin{align} 
+\label{eq:compl}
+a \pref_j x &⇔ ¬(x \ppref_j a)\\
+y \pref_j a &⇔ ¬(a \ppref_j y) ∧ (¬(x \ppref_j y) ∨ (x \ppref_j a)).
+\end{align}
+
+We just sketched a proof of the following claim, and leave the rest of the proof to the reader.
+\begin{claim}
+	There exists one completion ${\pref_j} \in C(\ppref_j)$ such that $\PMR(x,y; \pprofile, W) = \max_{\w \in W} \max_{\profile \in C(\pprofile), {\pref_j} \in \profile} [ s(y; \profile,\w) - s(x; \profile,\w) ]$ and that satisfies \ref{eq:compl}.
+\end{claim}
+In this claim, we abuse notation by writing ${\pref_j} \in \profile$ to mean that the preference ordering corresponding to agent $j$ in $\profile$ is $\pref_j$.
+
+It follows that the rank of $x$ for voter $j$ in $\PMR(x,y; \pprofile, W)$ is $1+\card{A}-\card{{\ppref_j}(x)}$, where ${\ppref_j}(x)$ designates the set of alternatives that are less good than $x$ according to $\ppref_j$, and the rank of $y$ is $1+\card{{\pprefinv_j}(y)}+\alpha$, where $\alpha = \card{A} - \card{{\ppref_j}(x)}$ if $(x \ppref_j y)$ and $\alpha = 0$ otherwise.
+
+%Proof: Define $\pref$ as just $\ppref_j$ with the arcs added to minimally satisfy the above.
+Thus, add the following arcs: when $x ?
+a$, add $a > x$.
+When $a ?
+y ∧ x \ppref_j y ∧ ¬(x \ppref_j a)$, add $a \pref y$.
+When $a ?
+y ∧ [¬(x \ppref_j y) ∨ (x \ppref_j a)]$, add $y \pref a$.
+Observe that $\ppref_j \subseteq \pref$.
+We have to show that it is acyclic.
+(Then we take its transitive closure to make it a partial order, and it’s done.) Note that if there is a cycle in $\pref$, it’s because of some new arcs, as $\ppref_j$ is acyclic.
+Thus, the cycle must go through one of these new arcs.
+…
+
+%Let $U^+=\{ i \mid \ y \ppref_i x\}$ be the set of agents for which we know that $y$ is preferred to $x$ (positive contribution to pairwise regret), $U^-=\{ i \mid x \ppref_i y\}$ 
+%be the set of agents for wich we  know that $x$ is preferred to $y$ (negative contribution) and 
+%$U^?=\{ i \mid x \pinc_i y\}$ 
+%%$U^?=\{ i \mid x \nsucc_{i} y \wedge y \nsucc_{i} x \}$ 
+%the remaining case, where the preference between $x$ and $y$ is not known.
+%Consider how the adversary, whose goal is to maximize $\PMR$ between $x$ and $y$, will complete the partial orders:
+%\begin{itemize}
+% \item $j \in U^+$: If we know that agent $j$ prefers $y$ to $x$ then the contribution to $\PMR$ is positive and adversary will complete the partial order of agent $j$ by placing as many alternatives as possible between $y$ and $x$ (because of monotonicity of the weights).
+% The way the partial order is completed does not depend on the actual values of the weights.
+%
+% \item $j \in U^?$: If we do not know whether $x$ or $y$ is preferred by agent $j$ then the adversary will place $y$ before $x$ (since the goal is to maximize the difference in score between $y$ and $x$, and weights are monotone) in the linear order and this case reduce to the first one; therefore also in this case the completion of the partial order can be done independently of the choice of $w$.
+%
+% \item $j \in U^-$: If we know that agent $j$ prefers $x$ to $y$ then (as the contribution of this agent to $\PMR$ is negative) the adversary will place as few alternatives as possible between $x$ and $y$.
+%
+%The only issue is with respect to the  alternatives that are incomparable with $x$ and $y$ according to $\ppref_i$: should they be placed better than $x$ or worse than $y$ ?
+%If the scoring vector is known to be convex,  than these alternatives will be placed better than $x$ in the completion; otherwise the placements of these depend on the weights $\w$.
+%\end{itemize}
+
+\subsubsection{Minimax regret computation}
+
+%Since weights are assumed to be convex, the adversary will place all alternatives $c$ that are such that $c \pinc_{j} y \wedge c \pinc_{j} x$ as better than $x$.
+%We now formalize the reasoning about the best (with respect to maximizing $\PMR$) completion with the following definition.
+%\begin{definition}
+%Given the partial profile $\pprofile$, define $\hat{\profile}$ as the completition of $\pprofile$ such that:
+%\begin{itemize}
+%\item For each $j \in U^{+}$, set   $\hat{\profile}$ as follows, for all $c \in A$:\\
+%if $c \pinc_{j} x$ we set $c \succ_{j}^{\hat{\profile}} x$;\\
+%if  $c \pinc_{j} y$ we set $y \succ_{j}^{\hat{\profile}} c$.
+%\item For each $j \in U^{?}$, set  $\hat{\profile}$ as follows:\\
+%$y \succ_{j}^{\hat{\profile}} x$;\\
+%for all $c \in A$, if   $c \pinc_{j} x$ we set $c \succ_{j}^{\hat{\profile}} x$;\\
+%for all $c \in A$, if   $c \pinc_{j} y$ we set $y \succ_{j}^{\hat{\profile}} c$.
+%\item For each $j \in U^{-}$,  set  $\hat{\profile}$ as follows, for all $c \in A$:\\
+%if $c \pinc_{j} x \wedge c \succ^{p}_{j} y$ we set $c \succ_{j}^{\hat{\profile}} x$;\\
+%if $c \pinc_{j} y \wedge  x \succ^{p}_{j} c$ we set $y \succ_{j}^{\hat{\profile}} c$;\\
+%if $c \pinc_{j} y \wedge c \pinc_{j} x$ we set $c \succ_{j}^{\hat{\profile}} x$.
+%\end{itemize}
+%\end{definition}
 
@@
 
-The space of feasible weights $W$ is encoded with linear constraints that model the preferences of the committee.
+The space of feasible weights $W$ is encoded with linear constraints that model the preferences of the chair.
 Therefore the pairwise maximum regret can be computed with a linear program.
 
-By solving a sequence of pairwise max regret computations is possible to determine the minimax regret solution.
+The minimax regret solution $\MMR(\pprofile, W)$ is determined by solving a sequence of pairwise max regret computations.
 Each PMR is computed using a linear program.
 The decision variables correspond to the weights attached to the different positions.
-Constraints are on the feasible parameters (the ``weights'' of the scoring rules); contraints represent the preferences of the chair about the scoring rule.
+Constraints are on the feasible parameters (the weights of the scoring rules); contraints represent the preferences of the chair about the scoring rule.
 
@@
 \begin{prop}
-Assume convex weights.
+%Assume convex weights.
 The PMR can be written as:
@@
 \PMR(x,y; \pprofile, W) =  
-\max_{w \in W} s(y; \hat{\profile}, \w) - s(y; \hat{\profile}, \w) =\\
-=\max_{w \in W} \sum_{j=1}^n w_{\hat{v}_i(y)} - w_{\hat{v}_i(x)} =
-\max_{w \in W} \sum_{i=1}^m (\hat{\alpha}_{i}^{y} - \hat{\alpha}_{i}^{x}) w_i 
+\max_{w \in W} s(y; \hat{\profile}, \w) - s(y; \hat{\profile}, \w)\\
+=\max_{w \in W} \sum_{j=1}^n w_{\hat{v}_j(y)} - w_{\hat{v}_j(x)} =
+\max_{w \in W} \sum_{r=1}^m (\hat{\alpha}_{r}^{y} - \hat{\alpha}_{r}^{x}) w_i 
 \end{align}
-where the coefficient $ (\hat{\alpha}_{i}^{y} - \hat{\alpha}_{i}^{x})$ is the number of times $y$ is in position $i$ minus the number of times $x$ is the in position $i$ in the rankings of the completed profile $\hat{v}$:
-$\hat{\alpha}_{i}^{x} = \sum_{j=1}^{n}  I[\hat{v}_{j}(x)=i]$ where $I$ is the indicator function.
+where the coefficient $ (\hat{\alpha}_{r}^{y} - \hat{\alpha}_{r}^{x})$ is the number of times $y$ is at rank $r$ minus the number of times $x$ is at rank $r$ in the rankings of the completed profile $\hat{\profile}$.
+%$\hat{\alpha}_{i}^{x} = \sum_{j=1}^{n}  I[\hat{v}_{j}(x)=i]$ where $I$ is the indicator function.
 \end{prop}
 %\[ \alpha_{i} = \sum_{j=1}^{n}  I[\hat{v}_{j}(y)=i] - I[\hat{v}_{j}(x)=i]\]
-Then, what we have to to compute pairwise max regret $\PMR(x,y; \pprofile,W)$ is just to compute the solution of the following linear program defined on variables\footnote{In fact, given our assumptions, $w_{1}=1$ and $w_{m}=0$, therefore there are only $m-2$ variables.
-We leave $w_{1}$ and $w_{m}$ in the linear program just for ease of presentation.} $w_{1},\ldots,w_{m}$:
+The pairwise max regret $\PMR(x,y; \pprofile,W)$ is now obtained as the solution of the following linear program defined on the variables $w_1, …, w_m$. 
 \begin{align*}
-\max_{\w} & \sum_{i=1}^m (\hat{\alpha}_{i}^{y} - \hat{\alpha}_{i}^{x}) w_{i}\\
+\max_{\w} & \sum_{r=1}^m (\hat{\alpha}_{r}^{y} - \hat{\alpha}_{r}^{x}) w_{r}\\
 \text{ s.t. } & \text{Equation } (\ref{eq:monotone})\\
 & \text{Equation } (\ref{eq:convexity})\\
-& \C(\w)
+& C_W.
 \end{align*}
-where $\C(w)$ are the linear constraints on $\w$ encoding the chair's preferences.
-The result of the optimization is the value of the pairwise max regret $\PMR$.
+Note that given our choice $w_{1}=1$ and $w_{m}=0$, there are only $m-2$ variables. We leave $w_{1}$ and $w_{m}$ in the linear program just for clarity of presentation.
 
@@
 At each step, the system may either ask a question to one of the agents, or ask a question to the chair about the voting rule. 
-The goal is to acquire relevant information to reduce minimax regret as quick as possible.
+The goal is to acquire relevant information to reduce minimax regret as quickly as possible.
 %Minimax regret can be used to guide the elicitation process.
@@
 The remainder of this Section is structured as follows.
-First of all, we discuss the different types of queries that can be asked to the voters and to the chair, and the way responses are handled.
+First of all, we discuss the different types of questions that can be asked to the voters and to the chair, and the way responses are handled.
 Then, we describe different strategies to determine informative queries to ask next, with the goal of reducing $\MMR(\pprofile,W)$ quickly.
 
-\paragraph{Query types}
-We distinguish between queries asked to the voters and questions asked to the chair.
+\paragraph{Question types}
+We distinguish between questions asked to the voters and questions asked to the chair.
 As {\em questions asked to the voters}, it is natural to consider comparison queries asking to compare two alternatives.
-Another common type or queries are {\em top-k}, asking to each voter his $k$ most alternatives.
-The effect of a response to a query asked to the voters, is to augment our knowledge about the voters rankings, thus augmenting the partial profile $\pprofile$. 
-If voter $i$ answers a comparison query stating that alternative $a$ is preferred to $b$, then the partial order $\succ^{p}_{i}$ is augmented with $a \succ^{p}_{i} b$ and by transitive closure.
-
-A bit more discussion is need about {\em questions asked to the chair}.
-A query asked to the chair has the goal of refining our knowledge about the scoring rule;
-a response to a query gives us a constraint on the weighting vectors $w$.
+%Another common type of queries are {\em top-k}, asking to each voter her $k$ most preferred alternatives.
+The effect of a response to a question asked to a voter is to augment our knowledge about the voters rankings, thus augmenting the partial profile $\pprofile$. 
+If voter $j$ answers a comparison query stating that alternative $a$ is preferred to $b$, then the partial order $\ppref_j$ is augmented with $a \ppref_j b$ and by transitive closure.
+
+A bit more discussion is needed about {\em questions asked to the chair}.
+Such a question aims at refining our knowledge about the scoring rule;
+a response gives us a constraint on the weight vector $\w$.
 
 In particular, we want to acquire constraints of the type:
-\[ w_{j} - w_{j+1} \geq \lambda (w_{j+1} - w_{j+2}) \] 
-for $j \in \{1,\ldots,m-2\}$, relating the difference between the importance of positions $i$ and $i+1$ with the difference between positions $i+1$ and $i+2$.
-While perhaps in some cases the decision maker may be able to state preferences of this kind, we argue that a more concrete way is better.
+\[ w_{r} - w_{r+1} \geq \lambda (w_{r+1} - w_{r+2}) \] 
+for $r \in \{1,\ldots,m-2\}$, relating the difference between the importance of ranks $r$ and $r+1$ with the difference between ranks $r+1$ and $r+2$.
+As we assume the scores constitute the utility components of the chair, it might be reasonable to assume that the chair is able to answer such abstract questions in our setting.
+However, it is important to make sure that the question can also, in principle, be asked in a more concrete way, in terms of winners of example profiles.
+This permits to test whether the chair understands the question as we do; this permits to relate the preference of the chair as we understand it to her choice behavior in the economic sense; and this will be necessary for an ordinal extension of our work where the scores would not be considered as cardinal utilities.
+
 Notice that the constraint above is equivalent to 
@@
 \begin{example}
-Suppose our query strategy suggests us to ask the committee the following query:
+Suppose our query strategy suggests us to ask the chair the following query:
 \[ w_{2} - w_{3} \geq 2(w_{3} - w_{4}) \]
@@
 In our interactive  protocol for simultaneously eliciting the preferences of the chair about the voting rule and the voters' preferences about the alternatives.
-Indeed, it can be beneficial to interleave questions asked to the committee and questions asked to voters, depending on which is estimated to be more informative.
-
-Answers given by the committee about the scoring rule refine our knowledge of the weights $w_1,\ldots,w_n$, while
+Indeed, it can be beneficial to interleave questions asked to the chair and questions asked to voters, depending on which is estimated to be more informative.
+
+Answers given by the chair about the scoring rule refine our knowledge of the weights $w_1,\ldots,w_n$, while
 answers given by one of the voters refine our knowledge about the voters preferences.
 
-At each step we need to decide whether we want to ask a question to the committee or to one of the agents (and to which agent in particular).
-We assume that we can ask comparison queries to the agents and questions comparing the differences of weights to the committee.
+At each step we need to decide whether we want to ask a question to the chair or to one of the agents (and to which agent in particular).
+We assume that we can ask comparison queries to the agents and questions comparing the differences of weights to the chair.
 
@@
 %We consider strategies of the following form
-%{\em if} condition {\em then} ask comparison query {\em else} ask a committee query
+%{\em if} condition {\em then} ask comparison query {\em else} ask a chair query
 %Define a score associated to each potential query that we may ask.
@@
 What is the complexity of this strategy?
-Let's define $Q$ as the set of all possible queries we can address to the agents and to the committee.
+Let's define $Q$ as the set of all possible queries we can address to the agents and to the chair.
 The worst case is represented by the situation in which we do not have any information about both the agents' preferences and the weights constraints.
 In this case we can address $\binom{m}{2}=\frac{m(m-1)}{2}$ questions to each agent.
-Moreover, we need to ask at least $m$ questions to the committee.
+Moreover, we need to ask at least $m$ questions to the chair.
 Then, each question induces two possible pairs of $(\pprofile,W)$ for each of which we compute the $\MMR$, whose worst case complexity is $O(nm^3)$.
@@
  to verify our intuition that an interleaved elicitation approach (mixing questions to the chair and questions asked to the voters) is more efficient than performing the elicitation of the rule first and than eliciting the voters preferences.
-First of all, we randomly generate the true preferences of the users (i.e. the linear orders) and the weights associated with the committee's scoring rule.
+First of all, we randomly generate the true preferences of the users (i.e. the linear orders) and the weights associated with the chair's scoring rule.
 For each of the elicitation strategy, we simulate an elicitation session.
@@
 We therefore obtain the following mixed integer linear program:
+\newcommand{\C}{\mathcal{C}}
 \begin{align}
@@
 
-\section{Querying the committee}
-Suppose our query strategy suggests us to ask the committee the following query:
+\section{Querying the chair}
+Suppose our query strategy suggests us to ask the chair the following query:
 \[ w_{2} - w_{3} \geq 2(w_{3} - w_{4}) \]

### 2019-02-24 draft.tex
Preuve constr profil question concrète et mineurs

@@
 \newunicodechar{⇔}{\Leftrightarrow}
+\newcommand{\N}{ℕ}
+\newunicodechar{ℕ}{\mathbb{N}}
 \usepackage{algorithm, algpseudocode}
@@
 \newcommand{\w}{\bm{w}}
+\newcommand{\W}{\mathcal{W}}
 \newcommand{\pw}{W}%our knowledge about the weights
@@
 We assume defined a set $A$ of $m$ alternatives (products, restaurants, movies, public projects, job candidates, etc.) and a set $\set{1, …, n}$ of agents (voters); each agent $j$ is associated to her “real” preference order $\pref_j$.
+The agents come from an infinite set $\N$ of potential voters.
 The real preferences of the agents are elements of $\linors$, the linear orders (connected, transitive, asymmetric relations) over the alternatives.
-Following the social choice nomenclature, we call {\em profile} the association of a preference to each voter, denoted by $(\pref_1,\ldots,\pref_n)$.
-The profile is equivalently represented by $\profile=(v_1,\ldots,v_n)$ where $v_j(i) \in \set{1, \ldots, m}$ denotes the rank (position) of alternative $i$ in the preference order $\pref_j$.
-
-Let $V$ be the set of possible preference profiles (the $n$-fold cartesian product of the linear orders over the alternatives).
+Following the social choice nomenclature, we call {\em profile} the association of a preference to each voter, considering a subset of voters from the set $\N$, and denote a profile by $(\pref_1,\ldots,\pref_n)$.
+A profile is equivalently represented by $\profile=(v_1,\ldots,v_n)$ where $v_j(i) \in \set{1, \ldots, m}$ denotes the rank (position) of alternative $i$ in the preference order $\pref_j$.
+
+Let $V$ be the set of possible preference profiles (the union for any integer $n$ of the $n$-fold cartesian product of the linear orders over the alternatives).
 A social choice function $f : V \rightarrow \powersetz{A}$ associates a profile with a set of winners, where $\powersetz{A}$ represents the set of subsets of $A$ except for the emptyset.
@@
 The constraint above is often used when aggregating rankings in sport competitions.
-We use $\mathcal{W}$ to denote the set of convex weight vectors.
+We use $\W$ to denote the set of convex weight vectors.
 
@@
 In this work we assume that preferences of the chair are encoded with linear constraints about the vector $\w$, relating the value of the weights of different positions.
-We use $\pw \subseteq \mathcal{W}$ to denote the set of weight vectors compatible with the preferences expressed by the chair about the scoring vector, and $C_W$ to denote the set of linear constraints expressed by the chair.
+We use $\pw \subseteq \W$ to denote the set of weight vectors compatible with the preferences expressed by the chair about the scoring vector, and $C_W$ to denote the set of linear constraints expressed by the chair.
 
@@
 \begin{claim}
-	There exists one completion ${\pref_j} \in C(\ppref_j)$ such that $\PMR(x,y; \pprofile, W) = \max_{\w \in W} \max_{\profile \in C(\pprofile), {\pref_j} \in \profile} [ s(y; \profile,\w) - s(x; \profile,\w) ]$ and that satisfies \ref{eq:compl}.
+	There exists a completion ${\pref_j} \in C(\ppref_j)$ such that $\PMR(x,y; \pprofile, W) = \max_{\w \in W} \max_{\profile \in C(\pprofile), {\pref_j} \in \profile} [ s(y; \profile,\w) - s(x; \profile,\w) ]$ and that satisfies \ref{eq:compl}.
 \end{claim}
@@
 a response gives us a constraint on the weight vector $\w$.
-
 In particular, we want to acquire constraints of the type:
@@
 for $r \in \{1,\ldots,m-2\}$, relating the difference between the importance of ranks $r$ and $r+1$ with the difference between ranks $r+1$ and $r+2$.
-As we assume the scores constitute the utility components of the chair, it might be reasonable to assume that the chair is able to answer such abstract questions in our setting.
+
+\paragraph{Building concrete questions for the chair}
+As we assume the weights constitute the utility components of the chair, it might be reasonable to assume, as we do here, that the chair is able to answer such abstract questions in our setting.
 However, it is important to make sure that the question can also, in principle, be asked in a more concrete way, in terms of winners of example profiles.
 This permits to test whether the chair understands the question as we do; this permits to relate the preference of the chair as we understand it to her choice behavior in the economic sense; and this will be necessary for an ordinal extension of our work where the scores would not be considered as cardinal utilities.
-
-Notice that the constraint above is equivalent to 
-$w_{i} - (\lambda+1) w_{i+1} + \lambda w_{i+2} \geq 0$
-and to $w_{i} + \lambda w_{i+2} \geq  (\lambda+1) w_{i+1}$.
-%We conjecture that preferences of this kind are relatively easy to state
-%(``do you think that the difference between the importance of position $i$ and $i+1$ is at least the difference between positions $i+1$ and $i+2$ ?'').
-We present them a profile representing the situation described by the query and then deduce its answer from the selected winner. 
-%We argue that it may be cognitively easier to ask to pick a winner from a profile, rather than answering an abstract question.
-Therefore we generate profiles specifically in such a way that user answers gives us the kind of constraint that we want to acquire.
-We provide a systematic way to construct such profiles.  %that reflects the situation outlined by the query for two alternatives and the others are not better than them.
-
-We consider a profile where a fictious alternative $a$ is $1$ time in position $i$, and $\lambda$ times 
-in position $i+2$ and another fictitious alternative, $b$, is ranked $\lambda+1$ times in position $i+1$.
-To have a valid profile, we need to include other alternatives.
-We add other alternatives in such a way that they are dominated by $a$ or $b$. 
-(if the chair picks an alternative that is either $a$ or $b$ this is a signale that the model is incorrect).
-
-\vspace{1cm}
-{\em {\bf TODO:} complete section and give a precise algorithm for completing the profile}
-\vspace{1cm}
-
+Thus, our task is to build a profile, given $\lambda$ and $r ≤ m-2$, in such a way that the set of (tied) winners picked by the chair reveals whether $w_{r} - w_{r+1} \geq \lambda (w_{r+1} - w_{r+2})$.
+We assume that $\lambda$ is rational, and define $\lambda = p/q$.
+
+Observe that the question may be defined equivalently as whether $q w_{r} + p w_{r+2} ≥ (p + q) w_{r+1}$, where $p, q$ are natural numbers.
+As a first attempt to make this question concrete, let us define a profile $P$ containing $p+q$ voters.
+Define an alternative $a$ that receives $q$ times the rank $r$ and $p$ times the rank $r+2$ and an alternative $b$ that receives $p+q$ times the rank $r+1$.
+Observing that the score of $a$ in that profile is exactly the left hand side of the question, and that the score of $b$ is the right hand side, intuition suggests that observing whether the chair picks $a$ or $b$ as winner will let us determine which side is greater; equality occurring when the chair declares $a$ and $b$ as tied for the victory.
+However, we still need to complete the profile, thus, come up with other $m-2$ alternatives defined so that each voter in the resulting profile has given each rank once.
+And we must ensure, doing this, that these other alternatives are not better than $a$ or $b$.
+For if the chair picks a different alternative $c$, it only tells us that the chair prefers $c$ to both $a$ and $b$, but it generally does not answer the question we are interested in.
+Taking $p = q = 1$, $m=4$, $r=2$, we see that such a completion may be impossible.
+Luckily, this problem can be worked around, at the price of increasing the number of voters.
+
+First build a temporary profile $P$ of $p+q$ voters with $a$ and $b$ ranked as just described.
+Complete it with $m-2$ alternatives ranked in arbitrary orders so that the resulting profile has complete strict rankings for each of the $p+q$ voter.
+Now we will make the other alternatives as bad as desired by adding voters to $P$ that appreciate $a$ and $b$ more than the other alternatives, thus building a profile $P'$ in which, whatever the weights, $c$ may not have a better score than $a$.
+Observe that if we add $\delta$ voters (with $\delta$ a natural number) that put $a$ at first rank and $b$ at second rank, and $\delta$ voters that put $b$ at first rank and $a$ at second rank, we do not change the difference of the scores of $a$ and $b$, and thus, observing the chair choosing $a$ or $b$ still answers the question.
+Choose arbitrarily a matching of the remaining $m-2$ alternatives to the ranks $3$ to $m$, say, $c \mapsto 3$, $d \mapsto 4$, and so on.
+The first $\delta$ supplementary voters, who rank $a$ first and $b$ second, rank the other alternatives as the just defined mapping suggests.
+The other $\delta$ supplementary voters, who rank $b$ first and $a$ second, use the opposite ranking for the remaining alternatives, say, $c \mapsto m$, $d \mapsto m-1$, and so on.
+We can now prove that, for $\delta = p+q$, and whatever the weight vector $w \in \W$, no alternative, except possibly $b$, has a better score than $a$.
+(In fact, as the construction will exhibit, they are all worst than both $a$ and $b$, but the weaker fact is enough for our claim.)
+
+Pick any alternative $c$ that is not $a$ or $b$. 
+%Let $c_t$ denote the number of times $c$ reaches rank $t$ or better in $P$.
+Note that $c_m = p+q$ and $c_t ≤ p + q, 1 ≤ t ≤ m$.
+Define $a_t$ similarly, for the alternative $a$.
+By construction, $a_r = q$, $a_{r+2} = q+p = a_m$.
+Define $c'_t$ as the number of times $c$ gets rank $t$ or better in $P'$, and define $a'_t$ similarly.
+Now $a'_1 ≥ \delta, a'_t ≥ 2\delta \text{ for } 2 ≤ t < m, a'_{r+2} = q+p+2\delta = a'_m$.
+To obtain upper bounds for $c'_t$, assume $c$ is ranked first by the $p+q$ voters voting in profile $P$.
+By our construction, the two times $\delta$ new voters of $P'$ give to $c$ the ranks $(3, m)$, or $(4, m-1)$, … Observe that the score of $c$ is maximal for attribution $(3, m)$, by convexity of the weights.
+Therefore, in the best case for $c$, $c'_1 ≤ p + q, c'_2 ≤ p+q, c'_t ≤ p+q+\delta \text{ for } 3 ≤ t < m, c'_m ≤ p+q+2\delta$.
+Observe that $a'_t ≥ c'_t, 1 ≤ t ≤ m$ (with strict inequality for $t=2$).
+Because weights are non increasing, this guarantees, with $\delta = p + q$, that the score of $a$ is not lower than the one of $c$ (it is even strictly higher, thanks to the strict inequality).
+This concludes the proof of the following claim.
+
+\begin{claim}
+	Given a rational $\lambda$ and a rank $r$ between $1$ and $m - 2$, the profile named $P'$ in the foregoing description is such that, for any weight vector $\w \in \W$, $a \in f(P')$ iff $w_{r} - w_{r+1} ≥ \lambda (w_{r+1} - w_{r+2})$ and $b \in f(P')$ iff $w_{r} - w_{r+1} ≤ \lambda (w_{r+1} - w_{r+2})$, where $f$ is the PSR parameterized with $\w$.
+\end{claim}
+
+\commentOC{I suppose we have, unfortunately, to get rid of this useful example, for reason of space.
+(If we manage to keep it, I’ll need to rework it a bit so that it follows the strategy in the proof.)}
 \begin{example}

### 2019-02-25 draft.tex
references about convexity + heuristic strategy

@@
 
-An important class of scoring rule is the one composed of weights that are a convex sequence, meaning that the difference between the weight of the first position and the weight of the second position is at least as great as the difference between the weights of the second and third positions, etc.
+An important class of scoring rule is the one composed of weights that are a convex sequence \cite{Stein1994,Llamazares2016}, meaning that the difference between the weight of the first position and the weight of the second position is at least as great as the difference between the weights of the second and third positions, etc.
 %\begin{align} \forall r \in \{1,\ldots,m-2\} \;\; & w_r - w_{r+1} \geq w_{r+1}-w_{r+2}  \\
@@
 \MR(x; \pprofile, W) & = \max_{y \in A} \PMR(x,y; \pprofile, W)\\
-& = \max_{\w \in W} \max_{\profile \in C(p)} \Regret(x, \profile, \w).
+& = \max_{\w \in W} \max_{\profile \in C(\profile)} \Regret(x, \profile, \w).
 \end{align}
@@
 
-We are interested in computing $PMR(x, y; \pprofile, W)$.
+We are interested in computing $\PMR(x, y; \pprofile, W)$.
 This represents the “worst” difference of score, thus the difference of score between $y$ and $x$ under the worst case preferences compatible with $\pprofile$ and $W$, where the worst case is the one that maximizes this difference of score.
@@
 %Assume convex weights.
-The PMR can be written as:
+The $\PMR$ can be written as:
 \begin{align} 
@@
 \item {\em Current solution strategy}: consider the solution of the minimax regret game, 
- $(x,y,\profile^{a},\w^{a})$, where $x$ is the minimax regret optimal alternative, $y$ the adversarial choice, $\w^{a}$ the weights, and $\profile^{a}$ the profile completed by the adversary.
-
-Ask a question to compare $x$ with $y$ to an agent.
-
+ $(x^{*},\bar{y},\bar{\profile},\bar{\w})$, where $x^{*}$ is the minimax regret optimal alternative,  $\bar{y} = \arg \max_{y \in A} \PMR(x,y; \pprofile, W)$; is the adversarial choice, and $\bar{\profile}$ and $\w$ are the instantiations\footnote{ $\bar{\profile} \!=\!
+\arg \max_{\profile \in C(\pprofile)} s(y; \profile, \bar{\w}) \!-\!
+s(x; \profile, \bar{\w})$; and $\bar{\w} \!=\!
+\arg \max_{w \in W} s(y; \pprofile, w) \!-\!
+s(x; \pprofile, w)$ .} of the weights associated with maximum regret.
  % Determine the part of ``regret'' due to uncertainty in $w$
 % Determine the part of ``regret' due to uncertainty in $p$
+Define: 
+\begin{align}
+\tau_{1} & = \min_{\w \in W} s(\bar{x}; \bar{\profile}, \w) - s(x^{*}; \bar{\profile}, \w)  \label{eq:tau1} \\
+\tau_{2} & = \min_{\profile \in C(\pprofile)} s(\bar{x},\profile, \bar{\w}) -  s(x^{*}; \profile, \bar{\w}).
+\end{align}
+Intuitively the quantity $\MMR - \tau_{1} $ measures the contribution to regret of our uncertainty about the weights $\w$, while $\MMR - \tau_{2} $ measures the uncertainty about the profile.
+Therefore, whenever $\tau_{1} < \tau_{2}$ we ask a question to the chair, and compare $\bar{\w}$ and $\w_{\tau}$.
+the argmax of Eq.
+(\ref{eq:tau1}), componentwise to find the position $r$ that is most valuable to ask about.
+Instead, if $\tau_{1} > \tau_{2}$ we ask a question to one of the agent, with the following heuristics.
 

### 2019-02-25 draft.tex
several fixes

@@
 \newcommand{\W}{\mathcal{W}}
+\newcommand{\Co}{\mathcal{C}}
 \newcommand{\pw}{W}%our knowledge about the weights
@@
 Social choice deals with the problem of determining a consensus choice from the preferences of different agents (voters).
-In the classical setting, the voting rule is fixed beforehand and full preference information is provided by the voters. 
-Recently, the assumption of full preference information has been questioned by a number of researchers and several methods for eliciting voters information have been proposed.
-
-In this paper we go one step further and we assume that both the voting rule and the voters preferences are partially specified.
+In the classical setting, the voting rule is fixed beforehand and full preference information is provided.% by the voters. 
+Recently, the assumption of full preference information has been questioned by a number of researchers and several methods for eliciting preferences have been proposed.
+
+In this paper we go one step further and we assume that both the voting rule and the agents preferences are partially specified.
 Focusing on positional scoring rules, we assume that the chair, while  not able to give a precise definition of the rule, is capable of answering simple questions  requiring to pick a winner from a specific  example profile.
-Moreover, the preferences of the voters are incrementally acquired by asking comparison queries.
+Moreover, the preferences of the agents are incrementally acquired by asking comparison queries.
 
@@
 We then provide an interactive elicitation protocol based on minimax regret
-and develop several query strategies that interleave questions to the chair and questions to the voters in order to acquire the most relevant information in order to quickly converge to optimal or a near-optimal alternative.
+and develop several query strategies that interleave questions to the chair and questions to the agents in order to acquire the most relevant information in order to quickly converge to optimal or a near-optimal alternative.
 \end{abstract}
@@
 
-In this paper we consider that both the voters’ preferences and the social choice rule are partially specified.
-We develop methods for computing the minimax-optimal alternative for scoring rules with partial voter preference information and partial information about the weights of the scoring rule.
-While previous works have considered either partial information about the voters preferences or a partially specified aggregation method, we do not know of any work considering both sources of uncertainty at the same time.
+In this paper we consider that both the agents’ preferences and the social choice rule are partially specified.
+We develop methods for computing the minimax-optimal alternative for scoring rules with partial agent preference information and partial information about the weights of the scoring rule.
+While previous works have considered either partial information about the agents preferences or a partially specified aggregation method, we do not know of any work considering both sources of uncertainty at the same time.
 
@@
 
-%In this paper we propose an interactive adaptive protocol for eliciting both the voters preferences and the voting rule.
+%In this paper we propose an interactive adaptive protocol for eliciting both the agents preferences and the voting rule.
 %At each step we need to decide whether we want to ask a question to the committee or to one of the agents (and to which agent in particular).
@@
 We assume defined a set $A$ of $m$ alternatives (products, restaurants, movies, public projects, job candidates, etc.) and a set $\set{1, …, n}$ of agents (voters); each agent $j$ is associated to her “real” preference order $\pref_j$.
-The agents come from an infinite set $\N$ of potential voters.
+The agents come from an infinite set $\N$ of potential agents.
 The real preferences of the agents are elements of $\linors$, the linear orders (connected, transitive, asymmetric relations) over the alternatives.
-Following the social choice nomenclature, we call {\em profile} the association of a preference to each voter, considering a subset of voters from the set $\N$, and denote a profile by $(\pref_1,\ldots,\pref_n)$.
+Following the social choice nomenclature, we call {\em profile} the association of a preference to each agent, considering a subset of agents from the set $\N$, and denote a profile by $(\pref_1,\ldots,\pref_n)$.
 A profile is equivalently represented by $\profile=(v_1,\ldots,v_n)$ where $v_j(i) \in \set{1, \ldots, m}$ denotes the rank (position) of alternative $i$ in the preference order $\pref_j$.
@@
 
-In this work we assume fixed, but unknown, a profile $\profile^*$ (and corresponding voters preferences $\pref_j^*$) and a weight vector $\w^*$, and we want to reason about partial preference information concerning those objects.
+In this work we assume fixed, but unknown, a profile $\profile^*$ (and corresponding agents preferences $\pref_j^*$) and a weight vector $\w^*$, and we want to reason about partial preference information concerning those objects.
 Our knowledge at a given time of the preference of voter $j$ is encoded by a partial order over the alternatives, thus a transitive and asymmetric binary relation, denoted by $\ppref_j$. 
@@
 
-An important class of scoring rule is the one composed of weights that are a convex sequence \cite{Stein1994,Llamazares2016}, meaning that the difference between the weight of the first position and the weight of the second position is at least as great as the difference between the weights of the second and third positions, etc.
+An important class of scoring rule is the one composed of weights that are a convex sequence \citep{Stein1994,Llamazares2016}, meaning that the difference between the weight of the first position and the weight of the second position is at least as great as the difference between the weights of the second and third positions, etc.
 %\begin{align} \forall r \in \{1,\ldots,m-2\} \;\; & w_r - w_{r+1} \geq w_{r+1}-w_{r+2}  \\
@@
 In this work we assume that preferences of the chair are encoded with linear constraints about the vector $\w$, relating the value of the weights of different positions.
-We use $\pw \subseteq \W$ to denote the set of weight vectors compatible with the preferences expressed by the chair about the scoring vector, and $C_W$ to denote the set of linear constraints expressed by the chair.
+We use $\pw \subseteq \W$ to denote the set of weight vectors compatible with the preferences expressed by the chair about the scoring vector, and $\Co_W$ to denote the set of linear constraints expressed by the chair.
 
@@
 %The quality of an alternative can be quantified by considering the maximum regret with respect to an adversary that can choose the instantiation of both a complete profile (extending the known preferences of the agents) and of the scoring vectors (associated to the preferences of the chair).
-In this paper, we consider a setting where both the voters' preferences and the preferences of the chair about the voting rule are incomplete.
+In this paper, we consider a setting where both the agents' preferences and the preferences of the chair about the voting rule are incomplete.
 Notice that some authors have considered possible and necessary winners assuming a partial profile  \citep{Xia2008} or assuming an incompletely specified scoring rule \citep{Viappiani2018};
@@
 \citet{Lu2011} have adopted minimax regret for winner determination in social choice with
-the preferences of the voters that are only partially known, while the social choice function is predetermined and known.
+the preferences of the agents that are only partially known, while the social choice function is predetermined and known.
 
@@
 Using {\em maximum regret} to quantify the worst-case error, the alternative that minimize this error is selected as winner, providing us with a form of robust optimization.
-Intuitively, the quality of a proposed alternative $a$ is how far from optimal $a$  could be in the worst case, given the current knowledge about the voting rule and about the voters' preferences.
+Intuitively, the quality of a proposed alternative $a$ is how far from optimal $a$  could be in the worst case, given the current knowledge about the voting rule and about the agents' preferences.
 
@@
 In this claim, we abuse notation by writing ${\pref_j} \in \profile$ to mean that the preference ordering corresponding to agent $j$ in $\profile$ is $\pref_j$.
-
 It follows that the rank of $x$ for voter $j$ in $\PMR(x,y; \pprofile, W)$ is $1+\card{A}-\card{{\ppref_j}(x)}$, where ${\ppref_j}(x)$ designates the set of alternatives that are less good than $x$ according to $\ppref_j$, and the rank of $y$ is $1+\card{{\pprefinv_j}(y)}+\alpha$, where $\alpha = \card{A} - \card{{\ppref_j}(x)}$ if $(x \ppref_j y)$ and $\alpha = 0$ otherwise.
@@
 %\end{itemize}
-
-\subsubsection{Minimax regret computation}
-
+%\subsubsection{Minimax regret computation}
 %Since weights are assumed to be convex, the adversary will place all alternatives $c$ that are such that $c \pinc_{j} y \wedge c \pinc_{j} x$ as better than $x$.
@@
 Let $\hat{\profile}$ be the profile computed according to the above procedure, and  $\hat{v}_j$ the $j$-th element (the linear order extending the partial order $p_j$ of the $j$-th voter).
-\begin{prop}
+\begin{claim}
 %Assume convex weights.
@@
 %$\hat{\alpha}_{i}^{x} = \sum_{j=1}^{n}  I[\hat{v}_{j}(x)=i]$ where $I$ is the indicator function.
-\end{prop}
+\end{claim}
 %\[ \alpha_{i} = \sum_{j=1}^{n}  I[\hat{v}_{j}(y)=i] - I[\hat{v}_{j}(x)=i]\]
@@
 & \text{Equation } (\ref{eq:convexity})\\
-& C_W.
+& \Co_W.
 \end{align*}
@@
 The remainder of this Section is structured as follows.
-First of all, we discuss the different types of questions that can be asked to the voters and to the chair, and the way responses are handled.
+First of all, we discuss the different types of questions that can be asked to the agents and to the chair, and the way responses are handled.
 Then, we describe different strategies to determine informative queries to ask next, with the goal of reducing $\MMR(\pprofile,W)$ quickly.
@@
 \paragraph{Question types}
-We distinguish between questions asked to the voters and questions asked to the chair.
-As {\em questions asked to the voters}, it is natural to consider comparison queries asking to compare two alternatives.
+We distinguish between questions asked to the agents and questions asked to the chair.
+As {\em questions asked to the agents}, it is natural to consider comparison queries asking to compare two alternatives.
 %Another common type of queries are {\em top-k}, asking to each voter her $k$ most preferred alternatives.
-The effect of a response to a question asked to a voter is to augment our knowledge about the voters rankings, thus augmenting the partial profile $\pprofile$. 
+The effect of a response to a question asked to a voter is to augment our knowledge about the agents rankings, thus augmenting the partial profile $\pprofile$. 
 If voter $j$ answers a comparison query stating that alternative $a$ is preferred to $b$, then the partial order $\ppref_j$ is augmented with $a \ppref_j b$ and by transitive closure.
@@
 Observe that the question may be defined equivalently as whether $q w_{r} + p w_{r+2} ≥ (p + q) w_{r+1}$, where $p, q$ are natural numbers.
-As a first attempt to make this question concrete, let us define a profile $P$ containing $p+q$ voters.
+As a first attempt to make this question concrete, let us define a profile $P$ containing $p+q$ agents.
 Define an alternative $a$ that receives $q$ times the rank $r$ and $p$ times the rank $r+2$ and an alternative $b$ that receives $p+q$ times the rank $r+1$.
@@
 Taking $p = q = 1$, $m=4$, $r=2$, we see that such a completion may be impossible.
-Luckily, this problem can be worked around, at the price of increasing the number of voters.
-
-First build a temporary profile $P$ of $p+q$ voters with $a$ and $b$ ranked as just described.
+Luckily, this problem can be worked around, at the price of increasing the number of agents.
+
+First build a temporary profile $P$ of $p+q$ agents with $a$ and $b$ ranked as just described.
 Complete it with $m-2$ alternatives ranked in arbitrary orders so that the resulting profile has complete strict rankings for each of the $p+q$ voter.
-Now we will make the other alternatives as bad as desired by adding voters to $P$ that appreciate $a$ and $b$ more than the other alternatives, thus building a profile $P'$ in which, whatever the weights, $c$ may not have a better score than $a$.
-Observe that if we add $\delta$ voters (with $\delta$ a natural number) that put $a$ at first rank and $b$ at second rank, and $\delta$ voters that put $b$ at first rank and $a$ at second rank, we do not change the difference of the scores of $a$ and $b$, and thus, observing the chair choosing $a$ or $b$ still answers the question.
+Now we will make the other alternatives as bad as desired by adding agents to $P$ that appreciate $a$ and $b$ more than the other alternatives, thus building a profile $P'$ in which, whatever the weights, $c$ may not have a better score than $a$.
+Observe that if we add $\delta$ agents (with $\delta$ a natural number) that put $a$ at first rank and $b$ at second rank, and $\delta$ agents that put $b$ at first rank and $a$ at second rank, we do not change the difference of the scores of $a$ and $b$, and thus, observing the chair choosing $a$ or $b$ still answers the question.
 Choose arbitrarily a matching of the remaining $m-2$ alternatives to the ranks $3$ to $m$, say, $c \mapsto 3$, $d \mapsto 4$, and so on.
-The first $\delta$ supplementary voters, who rank $a$ first and $b$ second, rank the other alternatives as the just defined mapping suggests.
-The other $\delta$ supplementary voters, who rank $b$ first and $a$ second, use the opposite ranking for the remaining alternatives, say, $c \mapsto m$, $d \mapsto m-1$, and so on.
+The first $\delta$ supplementary agents, who rank $a$ first and $b$ second, rank the other alternatives as the just defined mapping suggests.
+The other $\delta$ supplementary agents, who rank $b$ first and $a$ second, use the opposite ranking for the remaining alternatives, say, $c \mapsto m$, $d \mapsto m-1$, and so on.
 We can now prove that, for $\delta = p+q$, and whatever the weight vector $w \in \W$, no alternative, except possibly $b$, has a better score than $a$.
@@
 Now $a'_1 ≥ \delta, a'_t ≥ 2\delta \text{ for } 2 ≤ t < m, a'_{r+2} = q+p+2\delta = a'_m$.
-To obtain upper bounds for $c'_t$, assume $c$ is ranked first by the $p+q$ voters voting in profile $P$.
-By our construction, the two times $\delta$ new voters of $P'$ give to $c$ the ranks $(3, m)$, or $(4, m-1)$, … Observe that the score of $c$ is maximal for attribution $(3, m)$, by convexity of the weights.
+To obtain upper bounds for $c'_t$, assume $c$ is ranked first by the $p+q$ agents voting in profile $P$.
+By our construction, the two times $\delta$ new agents of $P'$ give to $c$ the ranks $(3, m)$, or $(4, m-1)$, … Observe that the score of $c$ is maximal for attribution $(3, m)$, by convexity of the weights.
 Therefore, in the best case for $c$, $c'_1 ≤ p + q, c'_2 ≤ p+q, c'_t ≤ p+q+\delta \text{ for } 3 ≤ t < m, c'_m ≤ p+q+2\delta$.
@@
 \begin{example}
-Suppose our query strategy suggests us to ask the chair the following query:
-\[ w_{2} - w_{3} \geq 2(w_{3} - w_{4}) \]
+Suppose our query strategy suggests us to ask the chair the following query: $w_{2} - w_{3} \geq 2(w_{3} - w_{4})$.
 In order to impose this constraints,
@@
 The following profile is exactly what we want,
-%We add voters in order to increase the number of times $a$ and $b$ are ranked at first position.
+%We add agents in order to increase the number of times $a$ and $b$ are ranked at first position.
 Please note we must maintain these scheme, so every add of a position to the ranking of $a$ must correspond to the same in the ranking of $b$.
@@
 
-We develop some elicitation strategies for simultaneous elicitation of voters' preferences and of the scoring rule.
+We develop some elicitation strategies for simultaneous elicitation of agents' preferences and of the scoring rule.
 Starting from some initial partial knowledge, our goal is to learn both the scoring rule function and the agents' preferences.
 While it is of course possible doing full elicitation of the weights and afterwards elicit the agents' preferences (or the other way around) we propose an interleaved approach.
-In our interactive  protocol for simultaneously eliciting the preferences of the chair about the voting rule and the voters' preferences about the alternatives.
-Indeed, it can be beneficial to interleave questions asked to the chair and questions asked to voters, depending on which is estimated to be more informative.
+In our interactive  protocol for simultaneously eliciting the preferences of the chair about the voting rule and the agents' preferences about the alternatives.
+Indeed, it can be beneficial to interleave questions asked to the chair and questions asked to agents, depending on which is estimated to be more informative.
 
 Answers given by the chair about the scoring rule refine our knowledge of the weights $w_1,\ldots,w_n$, while
-answers given by one of the voters refine our knowledge about the voters preferences.
+answers given by one of the agents refine our knowledge about the agents preferences.
 
@@
 
-In the experiments we want to compare the interleaved approach with a baseline challenger, a method  that elicits the preferences of the voters first and then the voting rule (or the other way around)
+In the experiments we want to compare the interleaved approach with a baseline challenger, a method  that elicits the preferences of the agents first and then the voting rule (or the other way around)
 
@@
 We consider different strategies to determine the next question to ask given the current information.
-%{\em Some ideas: decompose the regret into two components, one due to $\w$ and one due to $\pprofile$, and ask a question to the chair / or to one of the agents depending on which is highest}
-
-%We consider strategies of the following form
-%{\em if} condition {\em then} ask comparison query {\em else} ask a chair query
-%Define a score associated to each potential query that we may ask.
-
-\begin{itemize}
-\item {\em Current solution strategy}: consider the solution of the minimax regret game, 
- $(x^{*},\bar{y},\bar{\profile},\bar{\w})$, where $x^{*}$ is the minimax regret optimal alternative,  $\bar{y} = \arg \max_{y \in A} \PMR(x,y; \pprofile, W)$; is the adversarial choice, and $\bar{\profile}$ and $\w$ are the instantiations\footnote{ $\bar{\profile} \!=\!
+
+%\begin{itemize}
+%\item
+\medskip \noindent
+{\em Current solution strategy}: consider the solution of the minimax regret game, 
+ $(x^{*},\bar{y},\bar{\profile},\bar{\w})$, where $x^{*}$ is the minimax regret optimal alternative,  $\bar{y} = \arg \max_{y \in A} \PMR(x^{*},y; \pprofile, W)$; is the adversarial choice, and $\bar{\profile}$ and $\w$ are the instantiations\footnote{ $\bar{\profile} \!=\!
 \arg \max_{\profile \in C(\pprofile)} s(y; \profile, \bar{\w}) \!-\!
@@
 \arg \max_{w \in W} s(y; \pprofile, w) \!-\!
-s(x; \pprofile, w)$ .} of the weights associated with maximum regret.
+s(x; \pprofile, w)$ .} of the profile and weights associated with maximum regret.
  % Determine the part of ``regret'' due to uncertainty in $w$
@@
 \begin{align}
-\tau_{1} & = \min_{\w \in W} s(\bar{x}; \bar{\profile}, \w) - s(x^{*}; \bar{\profile}, \w)  \label{eq:tau1} \\
-\tau_{2} & = \min_{\profile \in C(\pprofile)} s(\bar{x},\profile, \bar{\w}) -  s(x^{*}; \profile, \bar{\w}).
+\tau_{1} & = \min_{\w \in W} s(\bar{y}; \bar{\profile}, \w) - s(x^{*}; \bar{\profile}, \w)  \label{eq:tau1} \\
+\tau_{2} & = \min_{\profile \in C(\pprofile)} s(\bar{y},\profile, \bar{\w}) -  s(x^{*}; \profile, \bar{\w}).
 \end{align}
@@
 
- \item One possibility is to consider the MMR {\em a posteriori}.
+ %\item 
+ One possibility is to consider the MMR {\em a posteriori}.
 Assume that the different answers to a query induce the possible sets to be $(\pprofile_1,W_1)$ and $(\pprofile_2,W_2)$, then the score according to worst-case maximum regret is:
@@
 
-\item Two phase method.
+\medskip \noindent
+{\em Two phase method.}
 Ask a predefined (non adaptive) sequence of questions in order to learn the weights $w$ of the scoring rule).
@@
 %\item Non-interleaved regret method: comparison with a method based on minimax regret, but not interleaved. 
-
-\item Non-interleaved non-regret strategies (useful as benchmarks).	
+\medskip \noindent
+{\em Non-interleaved non-regret strategies (useful as benchmarks)}	
 	\begin{itemize}
@@
 	\end{itemize}
-\end{itemize}
+%\end{itemize}
 
@@
 Our goal is to 
- to verify our intuition that an interleaved elicitation approach (mixing questions to the chair and questions asked to the voters) is more efficient than performing the elicitation of the rule first and than eliciting the voters preferences.
+ to verify our intuition that an interleaved elicitation approach (mixing questions to the chair and questions asked to the agents) is more efficient than performing the elicitation of the rule first and than eliciting the agents preferences.
 First of all, we randomly generate the true preferences of the users (i.e. the linear orders) and the weights associated with the chair's scoring rule.
@@
 %The detection of optimal or near-optimal product recommendation is generally possible with little concept and utility information
-%Regret-based elicitation allows to determine near-optimal winners using only few information about the voters' preferences.
+%Regret-based elicitation allows to determine near-optimal winners using only few information about the agents' preferences.
 We mention some  important directions for future works.
@@
 Consider the two addenda inside the ``max''. 
-The first addendum is concerned with positioning of alternatives $x$ and $y$ for voters in $U^{-}$ for which we know that $x$ is preferred to $y$.
-The second addendum is concerned with voters in $U^{+}$ and $U^{?}$.
+The first addendum is concerned with positioning of alternatives $x$ and $y$ for agents in $U^{-}$ for which we know that $x$ is preferred to $y$.
+The second addendum is concerned with agents in $U^{+}$ and $U^{?}$.
 We rewrite the second addendum as:
@@
 \end{align*}
-where $\hat{\alpha}_{i}^{x}$ is the number of times that $x$ is ranked  in position $i$  considering the profile $\hat{v}$ of voters in $U^+ \cup  U^?$.
+where $\hat{\alpha}_{i}^{x}$ is the number of times that $x$ is ranked  in position $i$  considering the profile $\hat{v}$ of agents in $U^+ \cup  U^?$.
 %We compute pairwise maximum regret by considering binary variables $\{ B_{i} \}_{i=1,\ldots,m}$ to represent optimization choices related to where to position the alternatives.
@@
 
-Assume we have a profile of $3$ voters ranking $4$ alternatives. We can represent it by columns where each of them represents the preference ordering of one voter.
+Assume we have a profile of $3$ agents ranking $4$ alternatives. We can represent it by columns where each of them represents the preference ordering of one voter.
 \[
@@
 
-Assuming anonymity, we can also write the profile expressing for each alternative $i \in A$ the number of voters placing it at a given rank.
+Assuming anonymity, we can also write the profile expressing for each alternative $i \in A$ the number of agents placing it at a given rank.
 
@@
 Nevertheless, in this example it is clear that $c$ will always be preferred to other alternatives (see Claim \ref{clm:wsequence} in Section \ref{sec:weights}).
-To see it we can express for each alternative the number of voters placing it at a given rank or at a higher one.
+To see it we can express for each alternative the number of agents placing it at a given rank or at a higher one.
 
@@
 It is worth noting that we cannot say anything when $r_1(i) = r_1(j)$.
-Indeed, as said in Corollary \ref{cor:weq}, all the weights for other position but the first one can be equal, thus the number of voters ranking the alternatives at a certain position does not matter anymore.
+Indeed, as said in Corollary \ref{cor:weq}, all the weights for other position but the first one can be equal, thus the number of agents ranking the alternatives at a certain position does not matter anymore.
 \end{proof}
@@
 So the strategy for querying the committee is to use two alternatives $i$ and $j$ to represent the query and complete the profile such that the other alternatives are all dominated by them.
-An algorithmic approach is to start from the initial profile and then add as many voters as needed that rank $i$ and $j$ as their top choices and the other alternatives afterwards.
+An algorithmic approach is to start from the initial profile and then add as many agents as needed that rank $i$ and $j$ as their top choices and the other alternatives afterwards.
 As an example let consider again the query \ref*{eqn:juryquery}.
@@
 
-We add voters in order to increase the number of times $a$ and $b$ are ranked at first position.
+We add agents in order to increase the number of times $a$ and $b$ are ranked at first position.
 Please note we must maintain these scheme, so every add of a position to the ranking of $a$ must correspond to the same in the ranking of $b$.

### 2019-02-25 draft.tex
some other fixes

@@
 The maximum regret is considered by assuming that an adversary both 1) can extend the partial profile $\pprofile$ into a complete profile, and 2) can instantiate the weights choosing among any weight vector in $\pw$, where $\pprofile$ and $\pw$ represent our knowledge so far.
-
 We formalize the notion of minimax regret in multiple steps.
@@
 \[\Regret(x, \profile, \w) = \max_{y \in A} s(y; \profile,\w) - s(x; \profile, \w).\]
-
 The pairwise max regret $\PMR(x,y;\pprofile,W)$ of $x$ relative to $y$ given partial profile $\pprofile$ and the set of weights $W$
@@
 
-Notice that if $MMR(\pprofile, W)=0$, then $x^{*}_{\pprofile,W}$  is a necessary co-winner; this means that for any valid completition of the profile and any feasible weight $w \in W$, $x^{*}_{\pprofile,W}$ obtains a highest score.
+Notice that if $\MMR(\pprofile, W)=0$, then $x^{*}_{\pprofile,W}$  is a necessary co-winner; this means that for any valid completition of the profile and any feasible weight $w \in W$, $x^{*}_{\pprofile,W}$ obtains a highest score.
 

### 2019-02-25 draft.tex
profile completion

@@
 In this case, the first objective should take priority, and $a$ should be put above $x$, which will move both $x$ and $y$ one rank lower than if $a$ had been put below $y$. 
-This maximizes the adversary’s interests: because the weight vector is convex, the difference in scores will be lower when both alternatives are one rank lower (Equation \ref{eq:convexity}), and that difference of score is in favor of $x$ when $x \ppref_j y$, thus to be minimized from the point of view of the adversary.
+This maximizes the adversary’s interests: because the weight vector is convex, the difference in scores will be lower when both alternatives are ranked lower (Equation \ref{eq:convexity}), and that difference of score is in favor of $x$ when $x \ppref_j y$, thus to be minimized from the point of view of the adversary.
 To summarize:\commentOC{TODO only one number here} 
@@
 \end{align} 
-
 We just sketched a proof of the following claim, and leave the rest of the proof to the reader.
 \begin{claim}
-	There exists a completion ${\pref_j} \in C(\ppref_j)$ such that $\PMR(x,y; \pprofile, W) = \max_{\w \in W} \max_{\profile \in C(\pprofile), {\pref_j} \in \profile} [ s(y; \profile,\w) - s(x; \profile,\w) ]$ and that satisfies \ref{eq:compl}.
+There exists a completion $\hat{\profile} \in C(\pprofile)$ such that $\PMR(x,y; \pprofile, W) = \max_{\w \in W} [ s(y; \profile,\w) - s(x; \profile,\w) ]$ and that the linear order $\hat{v}_{j}$ of each agent $j$ satisfies (\ref{eq:compl}).
+%There exists a completion ${\pref_j} \in C(\ppref_j)$ such that $\PMR(x,y; \pprofile, W) = \max_{\w \in W} \max_{\profile \in C(\pprofile), {\pref_j} \in \profile} [ s(y; \profile,\w) - s(x; \profile,\w) ]$ and that satisfies
 \end{claim}
-In this claim, we abuse notation by writing ${\pref_j} \in \profile$ to mean that the preference ordering corresponding to agent $j$ in $\profile$ is $\pref_j$.
+%In this claim, we abuse notation by writing ${\pref_j} \in \profile$ to mean that the preference ordering corresponding to agent $j$ in $\profile$ is $\pref_j$.
 It follows that the rank of $x$ for voter $j$ in $\PMR(x,y; \pprofile, W)$ is $1+\card{A}-\card{{\ppref_j}(x)}$, where ${\ppref_j}(x)$ designates the set of alternatives that are less good than $x$ according to $\ppref_j$, and the rank of $y$ is $1+\card{{\pprefinv_j}(y)}+\alpha$, where $\alpha = \card{A} - \card{{\ppref_j}(x)}$ if $(x \ppref_j y)$ and $\alpha = 0$ otherwise.
 
+Let $\hat{\profile}$ be the profile computed according to the above procedure, and  $\hat{v}_j$ the $j$-th element (the linear order extending the partial order $p_j$ of the $j$-th voter).
 %Proof: Define $\pref$ as just $\ppref_j$ with the arcs added to minimally satisfy the above.
@@
 
-The space of feasible weights $W$ is encoded with linear constraints that model the preferences of the chair.
-Therefore the pairwise maximum regret can be computed with a linear program.
-
-The minimax regret solution $\MMR(\pprofile, W)$ is determined by solving a sequence of pairwise max regret computations.
-Each PMR is computed using a linear program.
-The decision variables correspond to the weights attached to the different positions.
-Constraints are on the feasible parameters (the weights of the scoring rules); contraints represent the preferences of the chair about the scoring rule.
-
-Let $\hat{\profile}$ be the profile computed according to the above procedure, and  $\hat{v}_j$ the $j$-th element (the linear order extending the partial order $p_j$ of the $j$-th voter).
 \begin{claim}
@@
 %\[ \alpha_{i} = \sum_{j=1}^{n}  I[\hat{v}_{j}(y)=i] - I[\hat{v}_{j}(x)=i]\]
+We remind that the space of feasible weights $W$ is encoded with linear constraints $\Co_{W}$ that model the preferences of the chair.
+We now show that the pairwise maximum regret can be computed with a linear program.
+
+The PMR is computed using a linear program where the decision variables correspond to the weights attached to the different positions.
+Constraints are on the feasible parameters (the weights of the scoring rules); contraints represent the preferences of the chair about the scoring rule.
 The pairwise max regret $\PMR(x,y; \pprofile,W)$ is now obtained as the solution of the following linear program defined on the variables $w_1, …, w_m$. 
@@
 \end{align*}
-Note that given our choice $w_{1}=1$ and $w_{m}=0$, there are only $m-2$ variables. We leave $w_{1}$ and $w_{m}$ in the linear program just for clarity of presentation.
+Note that given our choice $w_{1}=1$ and $w_{m}=0$, there are only $m-2$ variables (we leave $w_{1}$ and $w_{m}$ in the linear program just for clarity of presentation).
+
+Finally the minimax regret solution $\MMR(\pprofile, W)$ is determined by solving a sequence of pairwise max regret computations, solving the above linear program for every different pair $(x,y) \in A^{2}$.
 
@@
 
+%Type of questions that we can ask to the chair:	bound queries (Is this alternative among your top-k most preferred items?), comparison queries (do you prefer alternative x or alternative y?).
+% we discuss the different forms of queries and develop several query strategies 
 \paragraph{Question types}
@@
 answers given by one of the agents refine our knowledge about the agents preferences.
-
 At each step we need to decide whether we want to ask a question to the chair or to one of the agents (and to which agent in particular).
@@
 In the experiments we want to compare the interleaved approach with a baseline challenger, a method  that elicits the preferences of the agents first and then the voting rule (or the other way around)
-
-%Type of questions that we can ask to the chair:	bound queries (Is this alternative among your top-k most preferred items?), comparison queries (do you prefer alternative x or alternative y?).
-
-% we discuss the different forms of queries and develop several query strategies 
-%\paragraph{Query methods}
 We consider different strategies to determine the next question to ask given the current information.
@@
 In this case, the query with least value is chosen.
-
 What is the complexity of this strategy?

### 2019-02-25 draft.tex
handling of blue comments by OC

@@
 \newif\ifappendix
-\appendixtrue %COMMENT to remove appendix % UNCOMMENT to add apendix
+%\appendixtrue %COMMENT to remove appendix % UNCOMMENT to add apendix
 \input{ijcai_preamble} 
@@
 \section{Introduction}
-\commentOC{Do we agree that we should talk systematically about agents (or systematically about voters)? Currently we talk about voters in first section, then agents.}
+%\commentOC{Do we agree that we should talk systematically about agents (or systematically about voters)? Currently we talk about voters in first section, then agents.}
 Aggregation of preference information is a central task in many computer systems (recommender systems, search engines, etc).
@@
 Therefore the vector $(w_1,\ldots,w_m)$  is not known but we are given a set of constraints restraining the possible values that weights can take.
-We consider a decreasing sequence of weights:
+We consider a decreasing sequence of weights\footnote{We assume all positions from $1$ to $m-1$ may contribute positively to the score of an alternative.
+The case where it is known that only the first $k<m-1$ positions matter can be easily dealt with by specifying $w_r = 0$ for $r > k$ as constraints.
+}:
+% If the chair considers that, for example, “only the first ten positions matter” (so that $w_r = 0$ for $r > 10$), then we simply assume the chair is able to express this constraint at the start of the querying process, thus, that this information is known, and approximate the problem by considering that it is only about the first ten alternatives, thus, set $m=10$.}
 \begin{align}
@@
 Without loss of generality, we consider that $w_1=1$ and $w_m=0$. 
-\commentOC{I suggest we say no more than this to justify this assumption.
-Otherwise, we might say something like the following.
-If the chair considers that, for example, “only the first ten positions matter” (so that $w_r = 0$ for $r > 10$), then we simply assume the chair is able to express this constraint at the start of the querying process, thus, that this information is known, and approximate the problem by considering that it is only about the first ten alternatives, thus, set $m=10$.}
+%\commentOC{I suggest we say no more than this to justify this assumption. Otherwise, we might say something like the following.
 
@@
 This maximizes the adversary’s interests: because the weight vector is convex, the difference in scores will be lower when both alternatives are ranked lower (Equation \ref{eq:convexity}), and that difference of score is in favor of $x$ when $x \ppref_j y$, thus to be minimized from the point of view of the adversary.
-To summarize:\commentOC{TODO only one number here} 
+To summarize:
 \begin{align} 
 \label{eq:compl}
+\begin{split}
 a \pref_j x &⇔ ¬(x \ppref_j a)\\
 y \pref_j a &⇔ ¬(a \ppref_j y) ∧ (¬(x \ppref_j y) ∨ (x \ppref_j a)).
+\end{split}
 \end{align} 
@@
 \begin{claim}
-%Assume convex weights.
 The $\PMR$ can be written as:
 \begin{align} 
-\PMR(x,y; \pprofile, W) =  
-\max_{w \in W} s(y; \hat{\profile}, \w) - s(y; \hat{\profile}, \w)\\
-=\max_{w \in W} \sum_{j=1}^n w_{\hat{v}_j(y)} - w_{\hat{v}_j(x)} =
-\max_{w \in W} \sum_{r=1}^m (\hat{\alpha}_{r}^{y} - \hat{\alpha}_{r}^{x}) w_i 
+\PMR(x,y; \pprofile, W)  
+%\max_{w \in W} s(y; \hat{\profile}, \w) - s(y; \hat{\profile}, \w)\\
+& = \max_{w \in W} \sum_{j=1}^n w_{\hat{v}_j(y)} - w_{\hat{v}_j(x)} = \\ 
+& = \max_{w \in W} \sum_{r=1}^m (\hat{\alpha}_{r}^{y} - \hat{\alpha}_{r}^{x}) w_i. 
 \end{align}
@@
 
-\commentOC{I suppose we have, unfortunately, to get rid of this useful example, for reason of space.
+%\commentOC{I suppose we have, unfortunately, to get rid of this useful example, for reason of space.
 (If we manage to keep it, I’ll need to rework it a bit so that it follows the strategy in the proof.)}

### 2019-02-25 draft.tex
\w, not w

--- 2019-02-25 draft.tex
@@
 \newcommand{\W}{\mathcal{W}}
-\newcommand{\Co}{\mathcal{C}}
 \newcommand{\pw}{W}%our knowledge about the weights
@@
 Social choice deals with the problem of determining a consensus choice from the preferences of different agents (voters).
-In the classical setting, the voting rule is fixed beforehand and full preference information is provided.% by the voters. 
-Recently, the assumption of full preference information has been questioned by a number of researchers and several methods for eliciting preferences have been proposed.
-
-In this paper we go one step further and we assume that both the voting rule and the agents preferences are partially specified.
+In the classical setting, the voting rule is fixed beforehand and full preference information is provided by the voters. 
+Recently, the assumption of full preference information has been questioned by a number of researchers and several methods for eliciting voters information have been proposed.
+
+In this paper we go one step further and we assume that both the voting rule and the voters preferences are partially specified.
 Focusing on positional scoring rules, we assume that the chair, while  not able to give a precise definition of the rule, is capable of answering simple questions  requiring to pick a winner from a specific  example profile.
-Moreover, the preferences of the agents are incrementally acquired by asking comparison queries.
+Moreover, the preferences of the voters are incrementally acquired by asking comparison queries.
 
@@
 We then provide an interactive elicitation protocol based on minimax regret
-and develop several query strategies that interleave questions to the chair and questions to the agents in order to acquire the most relevant information in order to quickly converge to optimal or a near-optimal alternative.
+and develop several query strategies that interleave questions to the chair and questions to the voters in order to acquire the most relevant information in order to quickly converge to optimal or a near-optimal alternative.
 \end{abstract}
@@
 
-In this paper we consider that both the agents’ preferences and the social choice rule are partially specified.
-We develop methods for computing the minimax-optimal alternative for scoring rules with partial agent preference information and partial information about the weights of the scoring rule.
-While previous works have considered either partial information about the agents preferences or a partially specified aggregation method, we do not know of any work considering both sources of uncertainty at the same time.
+In this paper we consider that both the voters’ preferences and the social choice rule are partially specified.
+We develop methods for computing the minimax-optimal alternative for scoring rules with partial voter preference information and partial information about the weights of the scoring rule.
+While previous works have considered either partial information about the voters preferences or a partially specified aggregation method, we do not know of any work considering both sources of uncertainty at the same time.
 
@@
 
-%In this paper we propose an interactive adaptive protocol for eliciting both the agents preferences and the voting rule.
+%In this paper we propose an interactive adaptive protocol for eliciting both the voters preferences and the voting rule.
 %At each step we need to decide whether we want to ask a question to the committee or to one of the agents (and to which agent in particular).
@@
 We assume defined a set $A$ of $m$ alternatives (products, restaurants, movies, public projects, job candidates, etc.) and a set $\set{1, …, n}$ of agents (voters); each agent $j$ is associated to her “real” preference order $\pref_j$.
-The agents come from an infinite set $\N$ of potential agents.
+The agents come from an infinite set $\N$ of potential voters.
 The real preferences of the agents are elements of $\linors$, the linear orders (connected, transitive, asymmetric relations) over the alternatives.
-Following the social choice nomenclature, we call {\em profile} the association of a preference to each agent, considering a subset of agents from the set $\N$, and denote a profile by $(\pref_1,\ldots,\pref_n)$.
+Following the social choice nomenclature, we call {\em profile} the association of a preference to each voter, considering a subset of voters from the set $\N$, and denote a profile by $(\pref_1,\ldots,\pref_n)$.
 A profile is equivalently represented by $\profile=(v_1,\ldots,v_n)$ where $v_j(i) \in \set{1, \ldots, m}$ denotes the rank (position) of alternative $i$ in the preference order $\pref_j$.
@@
 
-In this work we assume fixed, but unknown, a profile $\profile^*$ (and corresponding agents preferences $\pref_j^*$) and a weight vector $\w^*$, and we want to reason about partial preference information concerning those objects.
+In this work we assume fixed, but unknown, a profile $\profile^*$ (and corresponding voters preferences $\pref_j^*$) and a weight vector $\w^*$, and we want to reason about partial preference information concerning those objects.
 Our knowledge at a given time of the preference of voter $j$ is encoded by a partial order over the alternatives, thus a transitive and asymmetric binary relation, denoted by $\ppref_j$. 
@@
 
-An important class of scoring rule is the one composed of weights that are a convex sequence \citep{Stein1994,Llamazares2016}, meaning that the difference between the weight of the first position and the weight of the second position is at least as great as the difference between the weights of the second and third positions, etc.
+An important class of scoring rule is the one composed of weights that are a convex sequence \cite{Stein1994,Llamazares2016}, meaning that the difference between the weight of the first position and the weight of the second position is at least as great as the difference between the weights of the second and third positions, etc.
 %\begin{align} \forall r \in \{1,\ldots,m-2\} \;\; & w_r - w_{r+1} \geq w_{r+1}-w_{r+2}  \\
@@
 In this work we assume that preferences of the chair are encoded with linear constraints about the vector $\w$, relating the value of the weights of different positions.
-We use $\pw \subseteq \W$ to denote the set of weight vectors compatible with the preferences expressed by the chair about the scoring vector, and $\Co_W$ to denote the set of linear constraints expressed by the chair.
+We use $\pw \subseteq \W$ to denote the set of weight vectors compatible with the preferences expressed by the chair about the scoring vector, and $C_W$ to denote the set of linear constraints expressed by the chair.
 
@@
 %The quality of an alternative can be quantified by considering the maximum regret with respect to an adversary that can choose the instantiation of both a complete profile (extending the known preferences of the agents) and of the scoring vectors (associated to the preferences of the chair).
-In this paper, we consider a setting where both the agents' preferences and the preferences of the chair about the voting rule are incomplete.
+In this paper, we consider a setting where both the voters' preferences and the preferences of the chair about the voting rule are incomplete.
 Notice that some authors have considered possible and necessary winners assuming a partial profile  \citep{Xia2008} or assuming an incompletely specified scoring rule \citep{Viappiani2018};
@@
 \citet{Lu2011} have adopted minimax regret for winner determination in social choice with
-the preferences of the agents that are only partially known, while the social choice function is predetermined and known.
+the preferences of the voters that are only partially known, while the social choice function is predetermined and known.
 
@@
 Using {\em maximum regret} to quantify the worst-case error, the alternative that minimize this error is selected as winner, providing us with a form of robust optimization.
-Intuitively, the quality of a proposed alternative $a$ is how far from optimal $a$  could be in the worst case, given the current knowledge about the voting rule and about the agents' preferences.
+Intuitively, the quality of a proposed alternative $a$ is how far from optimal $a$  could be in the worst case, given the current knowledge about the voting rule and about the voters' preferences.
 
 The maximum regret is considered by assuming that an adversary both 1) can extend the partial profile $\pprofile$ into a complete profile, and 2) can instantiate the weights choosing among any weight vector in $\pw$, where $\pprofile$ and $\pw$ represent our knowledge so far.
+
 We formalize the notion of minimax regret in multiple steps.
@@
 \[\Regret(x, \profile, \w) = \max_{y \in A} s(y; \profile,\w) - s(x; \profile, \w).\]
+
 The pairwise max regret $\PMR(x,y;\pprofile,W)$ of $x$ relative to $y$ given partial profile $\pprofile$ and the set of weights $W$
@@
 
-Notice that if $\MMR(\pprofile, W)=0$, then $x^{*}_{\pprofile,W}$  is a necessary co-winner; this means that for any valid completition of the profile and any feasible weight $w \in W$, $x^{*}_{\pprofile,W}$ obtains a highest score.
+Notice that if $MMR(\pprofile, W)=0$, then $x^{*}_{\pprofile,W}$  is a necessary co-winner; this means that for any valid completition of the profile and any feasible weight $w \in W$, $x^{*}_{\pprofile,W}$ obtains a highest score.
 
@@
 In this claim, we abuse notation by writing ${\pref_j} \in \profile$ to mean that the preference ordering corresponding to agent $j$ in $\profile$ is $\pref_j$.
+
 It follows that the rank of $x$ for voter $j$ in $\PMR(x,y; \pprofile, W)$ is $1+\card{A}-\card{{\ppref_j}(x)}$, where ${\ppref_j}(x)$ designates the set of alternatives that are less good than $x$ according to $\ppref_j$, and the rank of $y$ is $1+\card{{\pprefinv_j}(y)}+\alpha$, where $\alpha = \card{A} - \card{{\ppref_j}(x)}$ if $(x \ppref_j y)$ and $\alpha = 0$ otherwise.
@@
 %\end{itemize}
-%\subsubsection{Minimax regret computation}
+
+\subsubsection{Minimax regret computation}
+
 %Since weights are assumed to be convex, the adversary will place all alternatives $c$ that are such that $c \pinc_{j} y \wedge c \pinc_{j} x$ as better than $x$.
@@
 Let $\hat{\profile}$ be the profile computed according to the above procedure, and  $\hat{v}_j$ the $j$-th element (the linear order extending the partial order $p_j$ of the $j$-th voter).
-\begin{claim}
+\begin{prop}
 %Assume convex weights.
@@
 %$\hat{\alpha}_{i}^{x} = \sum_{j=1}^{n}  I[\hat{v}_{j}(x)=i]$ where $I$ is the indicator function.
-\end{claim}
+\end{prop}
 %\[ \alpha_{i} = \sum_{j=1}^{n}  I[\hat{v}_{j}(y)=i] - I[\hat{v}_{j}(x)=i]\]
@@
 & \text{Equation } (\ref{eq:convexity})\\
-& \Co_W.
+& C_W.
 \end{align*}
@@
 The remainder of this Section is structured as follows.
-First of all, we discuss the different types of questions that can be asked to the agents and to the chair, and the way responses are handled.
+First of all, we discuss the different types of questions that can be asked to the voters and to the chair, and the way responses are handled.
 Then, we describe different strategies to determine informative queries to ask next, with the goal of reducing $\MMR(\pprofile,W)$ quickly.
@@
 \paragraph{Question types}
-We distinguish between questions asked to the agents and questions asked to the chair.
-As {\em questions asked to the agents}, it is natural to consider comparison queries asking to compare two alternatives.
+We distinguish between questions asked to the voters and questions asked to the chair.
+As {\em questions asked to the voters}, it is natural to consider comparison queries asking to compare two alternatives.
 %Another common type of queries are {\em top-k}, asking to each voter her $k$ most preferred alternatives.
-The effect of a response to a question asked to a voter is to augment our knowledge about the agents rankings, thus augmenting the partial profile $\pprofile$. 
+The effect of a response to a question asked to a voter is to augment our knowledge about the voters rankings, thus augmenting the partial profile $\pprofile$. 
 If voter $j$ answers a comparison query stating that alternative $a$ is preferred to $b$, then the partial order $\ppref_j$ is augmented with $a \ppref_j b$ and by transitive closure.
@@
 Observe that the question may be defined equivalently as whether $q w_{r} + p w_{r+2} ≥ (p + q) w_{r+1}$, where $p, q$ are natural numbers.
-As a first attempt to make this question concrete, let us define a profile $P$ containing $p+q$ agents.
+As a first attempt to make this question concrete, let us define a profile $P$ containing $p+q$ voters.
 Define an alternative $a$ that receives $q$ times the rank $r$ and $p$ times the rank $r+2$ and an alternative $b$ that receives $p+q$ times the rank $r+1$.
@@
 Taking $p = q = 1$, $m=4$, $r=2$, we see that such a completion may be impossible.
-Luckily, this problem can be worked around, at the price of increasing the number of agents.
-
-First build a temporary profile $P$ of $p+q$ agents with $a$ and $b$ ranked as just described.
+Luckily, this problem can be worked around, at the price of increasing the number of voters.
+
+First build a temporary profile $P$ of $p+q$ voters with $a$ and $b$ ranked as just described.
 Complete it with $m-2$ alternatives ranked in arbitrary orders so that the resulting profile has complete strict rankings for each of the $p+q$ voter.
-Now we will make the other alternatives as bad as desired by adding agents to $P$ that appreciate $a$ and $b$ more than the other alternatives, thus building a profile $P'$ in which, whatever the weights, $c$ may not have a better score than $a$.
-Observe that if we add $\delta$ agents (with $\delta$ a natural number) that put $a$ at first rank and $b$ at second rank, and $\delta$ agents that put $b$ at first rank and $a$ at second rank, we do not change the difference of the scores of $a$ and $b$, and thus, observing the chair choosing $a$ or $b$ still answers the question.
+Now we will make the other alternatives as bad as desired by adding voters to $P$ that appreciate $a$ and $b$ more than the other alternatives, thus building a profile $P'$ in which, whatever the weights, $c$ may not have a better score than $a$.
+Observe that if we add $\delta$ voters (with $\delta$ a natural number) that put $a$ at first rank and $b$ at second rank, and $\delta$ voters that put $b$ at first rank and $a$ at second rank, we do not change the difference of the scores of $a$ and $b$, and thus, observing the chair choosing $a$ or $b$ still answers the question.
 Choose arbitrarily a matching of the remaining $m-2$ alternatives to the ranks $3$ to $m$, say, $c \mapsto 3$, $d \mapsto 4$, and so on.
-The first $\delta$ supplementary agents, who rank $a$ first and $b$ second, rank the other alternatives as the just defined mapping suggests.
-The other $\delta$ supplementary agents, who rank $b$ first and $a$ second, use the opposite ranking for the remaining alternatives, say, $c \mapsto m$, $d \mapsto m-1$, and so on.
-We can now prove that, for $\delta = p+q$, and whatever the weight vector $w \in \W$, no alternative, except possibly $b$, has a better score than $a$.
+The first $\delta$ supplementary voters, who rank $a$ first and $b$ second, rank the other alternatives as the just defined mapping suggests.
+The other $\delta$ supplementary voters, who rank $b$ first and $a$ second, use the opposite ranking for the remaining alternatives, say, $c \mapsto m$, $d \mapsto m-1$, and so on.
+We can now prove that, for $\delta = p+q$, and whatever the weight vector $\w \in \W$, no alternative, except possibly $b$, has a better score than $a$.
 (In fact, as the construction will exhibit, they are all worst than both $a$ and $b$, but the weaker fact is enough for our claim.)
@@
 Now $a'_1 ≥ \delta, a'_t ≥ 2\delta \text{ for } 2 ≤ t < m, a'_{r+2} = q+p+2\delta = a'_m$.
-To obtain upper bounds for $c'_t$, assume $c$ is ranked first by the $p+q$ agents voting in profile $P$.
-By our construction, the two times $\delta$ new agents of $P'$ give to $c$ the ranks $(3, m)$, or $(4, m-1)$, … Observe that the score of $c$ is maximal for attribution $(3, m)$, by convexity of the weights.
+To obtain upper bounds for $c'_t$, assume $c$ is ranked first by the $p+q$ voters voting in profile $P$.
+By our construction, the two times $\delta$ new voters of $P'$ give to $c$ the ranks $(3, m)$, or $(4, m-1)$, … Observe that the score of $c$ is maximal for attribution $(3, m)$, by convexity of the weights.
 Therefore, in the best case for $c$, $c'_1 ≤ p + q, c'_2 ≤ p+q, c'_t ≤ p+q+\delta \text{ for } 3 ≤ t < m, c'_m ≤ p+q+2\delta$.
@@
 \begin{example}
-Suppose our query strategy suggests us to ask the chair the following query: $w_{2} - w_{3} \geq 2(w_{3} - w_{4})$.
+Suppose our query strategy suggests us to ask the chair the following query:
+\[ w_{2} - w_{3} \geq 2(w_{3} - w_{4}) \]
 In order to impose this constraints,
@@
 The following profile is exactly what we want,
-%We add agents in order to increase the number of times $a$ and $b$ are ranked at first position.
+%We add voters in order to increase the number of times $a$ and $b$ are ranked at first position.
 Please note we must maintain these scheme, so every add of a position to the ranking of $a$ must correspond to the same in the ranking of $b$.
@@
 
-We develop some elicitation strategies for simultaneous elicitation of agents' preferences and of the scoring rule.
+We develop some elicitation strategies for simultaneous elicitation of voters' preferences and of the scoring rule.
 Starting from some initial partial knowledge, our goal is to learn both the scoring rule function and the agents' preferences.
 While it is of course possible doing full elicitation of the weights and afterwards elicit the agents' preferences (or the other way around) we propose an interleaved approach.
-In our interactive  protocol for simultaneously eliciting the preferences of the chair about the voting rule and the agents' preferences about the alternatives.
-Indeed, it can be beneficial to interleave questions asked to the chair and questions asked to agents, depending on which is estimated to be more informative.
+In our interactive  protocol for simultaneously eliciting the preferences of the chair about the voting rule and the voters' preferences about the alternatives.
+Indeed, it can be beneficial to interleave questions asked to the chair and questions asked to voters, depending on which is estimated to be more informative.
 
 Answers given by the chair about the scoring rule refine our knowledge of the weights $w_1,\ldots,w_n$, while
-answers given by one of the agents refine our knowledge about the agents preferences.
+answers given by one of the voters refine our knowledge about the voters preferences.
 
@@
 
-In the experiments we want to compare the interleaved approach with a baseline challenger, a method  that elicits the preferences of the agents first and then the voting rule (or the other way around)
+In the experiments we want to compare the interleaved approach with a baseline challenger, a method  that elicits the preferences of the voters first and then the voting rule (or the other way around)
 
@@
 We consider different strategies to determine the next question to ask given the current information.
-
-%\begin{itemize}
-%\item
-\medskip \noindent
-{\em Current solution strategy}: consider the solution of the minimax regret game, 
- $(x^{*},\bar{y},\bar{\profile},\bar{\w})$, where $x^{*}$ is the minimax regret optimal alternative,  $\bar{y} = \arg \max_{y \in A} \PMR(x^{*},y; \pprofile, W)$; is the adversarial choice, and $\bar{\profile}$ and $\w$ are the instantiations\footnote{ $\bar{\profile} \!=\!
+%{\em Some ideas: decompose the regret into two components, one due to $\w$ and one due to $\pprofile$, and ask a question to the chair / or to one of the agents depending on which is highest}
+
+%We consider strategies of the following form
+%{\em if} condition {\em then} ask comparison query {\em else} ask a chair query
+%Define a score associated to each potential query that we may ask.
+
+\begin{itemize}
+\item {\em Current solution strategy}: consider the solution of the minimax regret game, 
+ $(x^{*},\bar{y},\bar{\profile},\bar{\w})$, where $x^{*}$ is the minimax regret optimal alternative,  $\bar{y} = \arg \max_{y \in A} \PMR(x,y; \pprofile, W)$; is the adversarial choice, and $\bar{\profile}$ and $\w$ are the instantiations\footnote{ $\bar{\profile} \!=\!
 \arg \max_{\profile \in C(\pprofile)} s(y; \profile, \bar{\w}) \!-\!
@@
 \arg \max_{w \in W} s(y; \pprofile, w) \!-\!
-s(x; \pprofile, w)$ .} of the profile and weights associated with maximum regret.
+s(x; \pprofile, w)$ .} of the weights associated with maximum regret.
  % Determine the part of ``regret'' due to uncertainty in $w$
@@
 \begin{align}
-\tau_{1} & = \min_{\w \in W} s(\bar{y}; \bar{\profile}, \w) - s(x^{*}; \bar{\profile}, \w)  \label{eq:tau1} \\
-\tau_{2} & = \min_{\profile \in C(\pprofile)} s(\bar{y},\profile, \bar{\w}) -  s(x^{*}; \profile, \bar{\w}).
+\tau_{1} & = \min_{\w \in W} s(\bar{x}; \bar{\profile}, \w) - s(x^{*}; \bar{\profile}, \w)  \label{eq:tau1} \\
+\tau_{2} & = \min_{\profile \in C(\pprofile)} s(\bar{x},\profile, \bar{\w}) -  s(x^{*}; \profile, \bar{\w}).
 \end{align}
@@
 
- %\item 
- One possibility is to consider the MMR {\em a posteriori}.
+ \item One possibility is to consider the MMR {\em a posteriori}.
 Assume that the different answers to a query induce the possible sets to be $(\pprofile_1,W_1)$ and $(\pprofile_2,W_2)$, then the score according to worst-case maximum regret is:
@@
 
-\medskip \noindent
-{\em Two phase method.}
+\item Two phase method.
 Ask a predefined (non adaptive) sequence of questions in order to learn the weights $w$ of the scoring rule).
@@
 %\item Non-interleaved regret method: comparison with a method based on minimax regret, but not interleaved.
-\medskip \noindent
-{\em Non-interleaved non-regret strategies (useful as benchmarks)}	
+
+\item Non-interleaved non-regret strategies (useful as benchmarks).	
 	\begin{itemize}
@@
 	\end{itemize}
-%\end{itemize}
+\end{itemize}
 
@@
 Our goal is to 
- to verify our intuition that an interleaved elicitation approach (mixing questions to the chair and questions asked to the agents) is more efficient than performing the elicitation of the rule first and than eliciting the agents preferences.
+ to verify our intuition that an interleaved elicitation approach (mixing questions to the chair and questions asked to the voters) is more efficient than performing the elicitation of the rule first and than eliciting the voters preferences.
 First of all, we randomly generate the true preferences of the users (i.e. the linear orders) and the weights associated with the chair's scoring rule.
@@
 %The detection of optimal or near-optimal product recommendation is generally possible with little concept and utility information
-%Regret-based elicitation allows to determine near-optimal winners using only few information about the agents' preferences.
+%Regret-based elicitation allows to determine near-optimal winners using only few information about the voters' preferences.
 We mention some  important directions for future works.
@@
 Consider the two addenda inside the ``max''. 
-The first addendum is concerned with positioning of alternatives $x$ and $y$ for agents in $U^{-}$ for which we know that $x$ is preferred to $y$.
-The second addendum is concerned with agents in $U^{+}$ and $U^{?}$.
+The first addendum is concerned with positioning of alternatives $x$ and $y$ for voters in $U^{-}$ for which we know that $x$ is preferred to $y$.
+The second addendum is concerned with voters in $U^{+}$ and $U^{?}$.
 We rewrite the second addendum as:
@@
 \end{align*}
-where $\hat{\alpha}_{i}^{x}$ is the number of times that $x$ is ranked  in position $i$  considering the profile $\hat{v}$ of agents in $U^+ \cup  U^?$.
+where $\hat{\alpha}_{i}^{x}$ is the number of times that $x$ is ranked  in position $i$  considering the profile $\hat{v}$ of voters in $U^+ \cup  U^?$.
 %We compute pairwise maximum regret by considering binary variables $\{ B_{i} \}_{i=1,\ldots,m}$ to represent optimization choices related to where to position the alternatives.
@@
 
-Assume we have a profile of $3$ agents ranking $4$ alternatives. We can represent it by columns where each of them represents the preference ordering of one voter.
+Assume we have a profile of $3$ voters ranking $4$ alternatives. We can represent it by columns where each of them represents the preference ordering of one voter.
 \[
@@
 
-Assuming anonymity, we can also write the profile expressing for each alternative $i \in A$ the number of agents placing it at a given rank.
+Assuming anonymity, we can also write the profile expressing for each alternative $i \in A$ the number of voters placing it at a given rank.
 
@@
 Nevertheless, in this example it is clear that $c$ will always be preferred to other alternatives (see Claim \ref{clm:wsequence} in Section \ref{sec:weights}).
-To see it we can express for each alternative the number of agents placing it at a given rank or at a higher one.
+To see it we can express for each alternative the number of voters placing it at a given rank or at a higher one.
 
@@
 It is worth noting that we cannot say anything when $r_1(i) = r_1(j)$.
-Indeed, as said in Corollary \ref{cor:weq}, all the weights for other position but the first one can be equal, thus the number of agents ranking the alternatives at a certain position does not matter anymore.
+Indeed, as said in Corollary \ref{cor:weq}, all the weights for other position but the first one can be equal, thus the number of voters ranking the alternatives at a certain position does not matter anymore.
 \end{proof}
@@
 So the strategy for querying the committee is to use two alternatives $i$ and $j$ to represent the query and complete the profile such that the other alternatives are all dominated by them.
-An algorithmic approach is to start from the initial profile and then add as many agents as needed that rank $i$ and $j$ as their top choices and the other alternatives afterwards.
+An algorithmic approach is to start from the initial profile and then add as many voters as needed that rank $i$ and $j$ as their top choices and the other alternatives afterwards.
 As an example let consider again the query \ref*{eqn:juryquery}.
@@
 
-We add agents in order to increase the number of times $a$ and $b$ are ranked at first position.
+We add voters in order to increase the number of times $a$ and $b$ are ranked at first position.
 Please note we must maintain these scheme, so every add of a position to the ranking of $a$ must correspond to the same in the ranking of $b$.

### 2019-02-25 draft.tex
anonymization

--- 2019-02-25 draft.tex
@@
 \input{ijcai_preamble} 
-\author{Beatrice Napolitano$^1$\and Olivier Cailloux$^1$	\and  Paolo Viappiani$^{2}$
-	\affiliations $^1$ LAMSADE, UMR 7243, CNRS and Universit\'e Paris Dauphine, PSL Research University, Paris, France\\ $^2$ LIP6, UMR 7606, CNRS and Sorbonne Universit\'e, Paris, France
-	\emails \{firstname.lastname\}@dauphine.fr, paolo.viappiani@lip6.fr
-}
+\author{ID: 2696}
+%\author{Beatrice Napolitano$^1$\and Olivier Cailloux$^1$	\and  Paolo Viappiani$^{2}$
+%	\affiliations $^1$ LAMSADE, UMR 7243, CNRS and Universit\'e Paris Dauphine, PSL Research University, Paris, France\\ $^2$ LIP6, UMR 7606, CNRS and Sorbonne Universit\'e, Paris, France
+%	\emails \{firstname.lastname\}@dauphine.fr, paolo.viappiani@lip6.fr
+%}
 %Restoring page numbers as missing them out violates basic human rights of the reviewers. -- Olivier

### 2019-02-25 draft.tex
several small fixes

@@
 Social choice deals with the problem of determining a consensus choice from the preferences of different agents (voters).
-In the classical setting, the voting rule is fixed beforehand and full preference information is provided.% by the voters. 
+In the classical setting, the voting rule is fixed beforehand and full preference information is provided.
 Recently, the assumption of full preference information has been questioned by a number of researchers and several methods for eliciting preferences have been proposed.
@@
 (Sets are used for tied winners.)
-Among the many possible social choice functions, we consider {\em positional scoring rules}, which attach weights to positions according to  the vector $(w_1, \ldots, w_m)$ (also called the scoring vector).
+Among the many possible social choice functions, we consider {\em positional scoring rules (PSR)}, which attach weights to positions according to  the vector $(w_1, \ldots, w_m)$ (also called the scoring vector).
 %A scoring rule associates each alternative to a score that is given by the sum of points obtained for each voter.
@@
 
-Notice that if $\MMR(\pprofile, W)=0$, then $x^{*}_{\pprofile,W}$  is a necessary co-winner; this means that for any valid completition of the profile and any feasible weight $w \in W$, $x^{*}_{\pprofile,W}$ obtains a highest score.
+Notice that if $\MMR(\pprofile, W)\!=\!0$, then $x^{*}_{\pprofile,W}$  is a necessary co-winner; this means that for any valid completion of the profile and any feasible $w \!\in\!
+W$, $x^{*}_{\pprofile,W}$ obtains a highest score.
 
@@
 The adversary has to make the score of $y$ as high as possible, and the score of $x$ as low as possible. 
-To do this, he should complete $\ppref_j$ to $\pref_j$ by putting above $x$ as many alternatives as he can, that is, all the alternatives except those that are known to be worst than $x$ (those $a$ such that $x \ppref_j a$); and similarly, put below $y$ all the alternatives he can, thus, put above $y$ only those $a$ such that $a \ppref_j y$.
+To do this, he should complete $\ppref_j$ to $\pref_j$ by putting above $x$ as many alternatives as he can, that is, all the alternatives except those that are known to be worse than $x$ (those $a$ such that $x \ppref_j a$); and similarly, put below $y$ all the alternatives he can, thus, put above $y$ only those $a$ such that $a \ppref_j y$.
 Sometimes these two objectives conflict: when an alternative should go above $x$ according to the first objective and below $y$ according to the second one (because $¬(x \ppref_j a) ∧ ¬(a \ppref_j y)$), and $x$ is known to be better than $y$ (thus $x \ppref_j y$).
@@
 \end{align} 
+In what follows let $\hat{\profile}$ be the profile computed according to the above procedure, and  $\hat{v}_j$ the $j$-th element (the linear order extending the partial order $p_j$ of the $j$-th voter).
 We just sketched a proof of the following claim, and leave the rest of the proof to the reader.
@@
 %In this claim, we abuse notation by writing ${\pref_j} \in \profile$ to mean that the preference ordering corresponding to agent $j$ in $\profile$ is $\pref_j$.
-It follows that the rank of $x$ for voter $j$ in $\PMR(x,y; \pprofile, W)$ is $1+\card{A}-\card{{\ppref_j}(x)}$, where ${\ppref_j}(x)$ designates the set of alternatives that are less good than $x$ according to $\ppref_j$, and the rank of $y$ is $1+\card{{\pprefinv_j}(y)}+\alpha$, where $\alpha = \card{A} - \card{{\ppref_j}(x)}$ if $(x \ppref_j y)$ and $\alpha = 0$ otherwise.
-
-Let $\hat{\profile}$ be the profile computed according to the above procedure, and  $\hat{v}_j$ the $j$-th element (the linear order extending the partial order $p_j$ of the $j$-th voter).
+\noindent It follows that $\hat{v}_{j}(x)$, the rank of $x$ for voter $j$ in the PMR-maximizing linear order $\bar{v}_{j}$ %$\PMR(x,y; \pprofile, W)$ 
+is $\hat{v}_{j}(x) = 1+\card{A}-\card{{\ppref_j}(x)}$, where ${\ppref_j}(x)$ designates the set of alternatives that are less good than $x$ according to $\ppref_j$, and the rank of $y$ is $\hat{v}_{j}(x)=1+\card{{\pprefinv_j}(y)}+\beta$, where $\beta = \card{A} - \card{{\ppref_j}(x)}$ if $(x \ppref_j y)$ and $\alpha = 0$ otherwise.
+
 %Proof: Define $\pref$ as just $\ppref_j$ with the arcs added to minimally satisfy the above.
@@
 \end{align}
-where the coefficient $ (\hat{\alpha}_{r}^{y} - \hat{\alpha}_{r}^{x})$ is the number of times $y$ is at rank $r$ minus the number of times $x$ is at rank $r$ in the rankings of the completed profile $\hat{\profile}$.
+where the $\hat{\alpha}_{r}^{y}$ (resp. $\hat{\alpha}_{r}^{x}$)  is the number of times $y$ (resp. $x$) is at rank $r$ in the rankings of the completed profile $\hat{\profile}$.
 %$\hat{\alpha}_{i}^{x} = \sum_{j=1}^{n}  I[\hat{v}_{j}(x)=i]$ where $I$ is the indicator function.
@@
 %\[ \alpha_{i} = \sum_{j=1}^{n}  I[\hat{v}_{j}(y)=i] - I[\hat{v}_{j}(x)=i]\]
-We remind that the space of feasible weights $W$ is encoded with linear constraints $\Co_{W}$ that model the preferences of the chair.
-We now show that the pairwise maximum regret can be computed with a linear program.
-
-The PMR is computed using a linear program where the decision variables correspond to the weights attached to the different positions.
-Constraints are on the feasible parameters (the weights of the scoring rules); contraints represent the preferences of the chair about the scoring rule.
+%We now show that the pairwise maximum regret can be computed with a linear program.
+The PMR can be now computed by optimizing a linear program (LP) where the decision variables correspond to the weights attached to the different positions.
+Constraints are on the feasible parameters (the weights of the scoring rules).
+We remind that the preferences of the char are encoded with linear constraints $\Co_{W}$.
+% contraints represent the preferences $\Co_{W}$ of the chair about the scoring rule.
 The pairwise max regret $\PMR(x,y; \pprofile,W)$ is now obtained as the solution of the following linear program defined on the variables $w_1, …, w_m$. 
@@
 \end{align*}
-Note that given our choice $w_{1}=1$ and $w_{m}=0$, there are only $m-2$ variables (we leave $w_{1}$ and $w_{m}$ in the linear program just for clarity of presentation).
-
-Finally the minimax regret solution $\MMR(\pprofile, W)$ is determined by solving a sequence of pairwise max regret computations, solving the above linear program for every different pair $(x,y) \in A^{2}$.
+Note that given our choice $w_{1}=1$ and $w_{m}=0$, there are only $m-2$ variables 
+(we leave $w_{1}$ and $w_{m}$ in the LP just for clarity of presentation).
+
+%Finally the minimax regret solution $\MMR(\pprofile, W)$ is determined by solving a sequence of pairwise max regret computations, solving the above linear program for every different pair $(x,y) \in A^{2}$.
+The max regret $\MR(x; \pprofile, W)$ is determined by considering the pairwise regret of $x$ with each other alternative in $A$.
+The optimal alternative w.r.t. minimax regret is the one with least max regret. 
+Notice that, whenever the PMR of an alternative $x$ (against some other alternative) exceeds the best MR value found so far, we don't need to further evaluate $x$. 
+This idea can be exploited further by adopting a minimax-search tree (see \cite{Braziunas2011}).
+%The computation can be made faster by adopting an efficient scheme of evaluation of PMR where .
 
@@
 We distinguish between questions asked to the agents and questions asked to the chair.
-As {\em questions asked to the agents}, it is natural to consider comparison queries asking to compare two alternatives.
+As {\em questions asked to the agents} it is natural to consider comparison queries asking to compare two alternatives.
 %Another common type of queries are {\em top-k}, asking to each voter her $k$ most preferred alternatives.
-The effect of a response to a question asked to a voter is to augment our knowledge about the agents rankings, thus augmenting the partial profile $\pprofile$. 
+The effect of a response to a question asked to an agent is to increase our knowledge about the agents rankings, thus augmenting the partial profile $\pprofile$. 
 If voter $j$ answers a comparison query stating that alternative $a$ is preferred to $b$, then the partial order $\ppref_j$ is augmented with $a \ppref_j b$ and by transitive closure.
@@
 A bit more discussion is needed about {\em questions asked to the chair}.
-Such a question aims at refining our knowledge about the scoring rule;
-a response gives us a constraint on the weight vector $\w$.
+Such questions aim at refining our knowledge about the scoring rule; a response gives us a constraint on the weight vector $\w$.
 In particular, we want to acquire constraints of the type:
@@
 \paragraph{Building concrete questions for the chair}
-As we assume the weights constitute the utility components of the chair, it might be reasonable to assume, as we do here, that the chair is able to answer such abstract questions in our setting.
+As we assume the weights constitute the utility components of the chair, it might be reasonable to assume, 
+%as we do here, 
+that the chair is able to answer such abstract questions in our setting.
 However, it is important to make sure that the question can also, in principle, be asked in a more concrete way, in terms of winners of example profiles.
-This permits to test whether the chair understands the question as we do; this permits to relate the preference of the chair as we understand it to her choice behavior in the economic sense; and this will be necessary for an ordinal extension of our work where the scores would not be considered as cardinal utilities.
+This permits to test whether the chair understands the question as we do; this permits to relate the preference of the chair  to her choice behavior in the economic sense; and this will be necessary for an ordinal extension of our work where the scores would not be considered as cardinal utilities.
 Thus, our task is to build a profile, given $\lambda$ and $r ≤ m-2$, in such a way that the set of (tied) winners picked by the chair reveals whether $w_{r} - w_{r+1} \geq \lambda (w_{r+1} - w_{r+2})$.
@@
 Observing that the score of $a$ in that profile is exactly the left hand side of the question, and that the score of $b$ is the right hand side, intuition suggests that observing whether the chair picks $a$ or $b$ as winner will let us determine which side is greater; equality occurring when the chair declares $a$ and $b$ as tied for the victory.
-However, we still need to complete the profile, thus, come up with other $m-2$ alternatives defined so that each voter in the resulting profile has given each rank once.
-And we must ensure, doing this, that these other alternatives are not better than $a$ or $b$.
-For if the chair picks a different alternative $c$, it only tells us that the chair prefers $c$ to both $a$ and $b$, but it generally does not answer the question we are interested in.
-Taking $p = q = 1$, $m=4$, $r=2$, we see that such a completion may be impossible.
-Luckily, this problem can be worked around, at the price of increasing the number of agents.
+However, we still need to complete the profile, thus, come up with other $m-2$ alternatives defined so that each agent in the resulting profile has placed exactly one alternative in each rank. 
+And we must ensure, doing this, that these other alternatives are not better than $a$ or $b$.\footnote{Because, if the chair picks a different alternative $c$, it only tells us that the chair prefers $c$ to both $a$ and $b$, but it generally does not answer the question we are interested in.}
+Taking $p = q = 1$, $m=4$, $r=2$, we see that such a completion may be impossible. Luckily, this problem can be worked around, at the price of increasing the number of agents.
 
@@
 We develop some elicitation strategies for simultaneous elicitation of agents' preferences and of the scoring rule.
-Starting from some initial partial knowledge, our goal is to learn both the scoring rule function and the agents' preferences.
+Starting from some initial partial knowledge, our goal is to acquire the relevant preference information 
+%(about both the scoring rule function and the agents' preferences) 
+in order to determine an approximate winner.
 While it is of course possible doing full elicitation of the weights and afterwards elicit the agents' preferences (or the other way around) we propose an interleaved approach.
@@
 At each step we need to decide whether we want to ask a question to the chair or to one of the agents (and to which agent in particular). 
-We assume that we can ask comparison queries to the agents and questions comparing the differences of weights to the chair.
+%We ask comparison queries to the agents and questions comparing the differences of weights to the chair.
 
@@
 (\ref{eq:tau1}), componentwise to find the position $r$ that is most valuable to ask about.
-Instead, if $\tau_{1} > \tau_{2}$ we ask a question to one of the agent, with the following heuristics.
+Instead, if $\tau_{1} > \tau_{2}$ we ask a question to one of the agent, with the following heuristics: COMPLETE
 
@@
 Let's define $Q$ as the set of all possible queries we can address to the agents and to the chair.
-The worst case is represented by the situation in which we do not have any information about both the agents' preferences and the weights constraints.
+The worst case is represented by the situation of complete ignorance.
+%in which we do not have any information about both the agents' preferences and the weights constraints. 
 In this case we can address $\binom{m}{2}=\frac{m(m-1)}{2}$ questions to each agent.
@@
 \section{Conclusions}  \label{sec:conclusions}
-
-% integrated preference elicitation methodology
 In this paper we have considered a  social choice setting with partial  information about the voter's  
@@
 We have proposed the use of minimax regret as a means of robust winner determination in this setting, and as well as to guide the process of simultaneous elicitation of preferences and voting rule.
-Our experimental results on randomly generated and real world data sets show that regret-based elicitation is effective and allow to find a near-optimal consensus choice in a limited number of steps.
-%The detection of optimal or near-optimal product recommendation is generally possible with little concept and utility information
+Our experimental results %on randomly generated and real world data sets 
+show that regret-based elicitation is effective and allow to quickly find a near-optimal consensus choice.
 %Regret-based elicitation allows to determine near-optimal winners using only few information about the agents' preferences.
+
 We mention some  important directions for future works.
@@
 A third direction is that of considering probabilistic methods for elicitation.
-Finally, we are interested in studying the effect of strategic agents, that may not report their true preferences.
+Finally, we are interested in studying the effect of strategic agents. %that may not report their true preferences.
 % distribution-free heuristics

### 2019-02-25 draft.tex
small fixes

@@
 \noindent It follows that $\hat{v}_{j}(x)$, the rank of $x$ for voter $j$ in the PMR-maximizing linear order $\bar{v}_{j}$ %$\PMR(x,y; \pprofile, W)$ 
-is $\hat{v}_{j}(x) = 1+\card{A}-\card{{\ppref_j}(x)}$, where ${\ppref_j}(x)$ designates the set of alternatives that are less good than $x$ according to $\ppref_j$, and the rank of $y$ is $\hat{v}_{j}(x)=1+\card{{\pprefinv_j}(y)}+\beta$, where $\beta = \card{A} - \card{{\ppref_j}(x)}$ if $(x \ppref_j y)$ and $\alpha = 0$ otherwise.
+is $\hat{v}_{j}(y) = 1+\card{A}-\card{{\ppref_j}(x)}$, where ${\ppref_j}(x)$ designates the set of alternatives that are less good than $x$ according to $\ppref_j$, and the rank of $y$ is $\hat{v}_{j}(x)=1+\card{{\pprefinv_j}(y)}+\beta$, where $\beta = \card{A} - \card{{\ppref_j}(x)}$ if $(x \ppref_j y)$ and $\beta = 0$ otherwise.
 
@@
 However, we still need to complete the profile, thus, come up with other $m-2$ alternatives defined so that each agent in the resulting profile has placed exactly one alternative in each rank. 
-And we must ensure, doing this, that these other alternatives are not better than $a$ or $b$.\footnote{Because, if the chair picks a different alternative $c$, it only tells us that the chair prefers $c$ to both $a$ and $b$, but it generally does not answer the question we are interested in.}
+And we must ensure, doing this, that these other alternatives are not better than $a$ or $b$.\footnote{Because, if the chair picks a different alternative $c$, it tells us that the chair prefers $c$ to both $a$ and $b$,
+%but it generally does not  answer the question we are interested in
+but in general we do not acquire the type of constraint we are interested in.} 
 Taking $p = q = 1$, $m=4$, $r=2$, we see that such a completion may be impossible. Luckily, this problem can be worked around, at the price of increasing the number of agents.

### 2019-02-25 draft.tex
proof environment for claim 3

@@
 %but it generally does not  answer the question we are interested in
-but in general we do not acquire the type of constraint we are interested in.} 
+but in general we do not acquire the type of constraints we are interested in.} 
 Taking $p = q = 1$, $m=4$, $r=2$, we see that such a completion may be impossible. Luckily, this problem can be worked around, at the price of increasing the number of agents.
@@
 Now we will make the other alternatives as bad as desired by adding agents to $P$ that appreciate $a$ and $b$ more than the other alternatives, thus building a profile $P'$ in which, whatever the weights, $c$ may not have a better score than $a$.
-Observe that if we add $\delta$ agents (with $\delta$ a natural number) that put $a$ at first rank and $b$ at second rank, and $\delta$ agents that put $b$ at first rank and $a$ at second rank, we do not change the difference of the scores of $a$ and $b$, and thus, observing the chair choosing $a$ or $b$ still answers the question.
+Observe that if we add $\delta$ agents (with $\delta$ a natural number) that put $a$ at first rank and $b$ at second rank, and $\delta$ agents that put $b$ at first rank and $a$ at second rank, we do not change the difference of the scores of $a$ and $b$ (and thus, observing the chair choosing $a$ or $b$ still answers the question).
 Choose arbitrarily a matching of the remaining $m-2$ alternatives to the ranks $3$ to $m$, say, $c \mapsto 3$, $d \mapsto 4$, and so on.
@@
 
+ %This concludes the proof of the following claim.
+\begin{claim}
+	Given a rational $\lambda$ and a rank $r$ between $1$ and $m - 2$, the profile named $P'$ in the foregoing description is such that, for any weight vector $\w \in \W$, $a \in f(P')$ iff $w_{r} - w_{r+1} ≥ \lambda (w_{r+1} - w_{r+2})$ and $b \in f(P')$ iff $w_{r} - w_{r+1} ≤ \lambda (w_{r+1} - w_{r+2})$, where $f$ is the PSR parameterized with $\w$.
+\end{claim}
+\begin{proof}
 Pick any alternative $c$ that is not $a$ or $b$. 
@@
 Because weights are non increasing, this guarantees, with $\delta = p + q$, that the score of $a$ is not lower than the one of $c$ (it is even strictly higher, thanks to the strict inequality).
-This concludes the proof of the following claim.
-
-\begin{claim}
-	Given a rational $\lambda$ and a rank $r$ between $1$ and $m - 2$, the profile named $P'$ in the foregoing description is such that, for any weight vector $\w \in \W$, $a \in f(P')$ iff $w_{r} - w_{r+1} ≥ \lambda (w_{r+1} - w_{r+2})$ and $b \in f(P')$ iff $w_{r} - w_{r+1} ≤ \lambda (w_{r+1} - w_{r+2})$, where $f$ is the PSR parameterized with $\w$.
-\end{claim}
+\end{proof}
 

### 2019-02-25 draft.tex
typos and small fixes

@@
 %A proof that this reasoning is correct is in \cref{sec:prfCompl}.
-
 \begin{claim}
@@
 %We now show that the pairwise maximum regret can be computed with a linear program.
-The PMR can be now computed by optimizing a linear program (LP) where the decision variables correspond to the weights attached to the different positions.
-Constraints are on the feasible parameters (the weights of the scoring rules).
-We remind that the preferences of the char are encoded with linear constraints $\Co_{W}$.
+%The PMR can be now computed by optimizing a linear program (LP). 
+%Constraints are on the feasible parameters (the weights of the scoring rules).
+The last proposition shows us that PMR is linear in the weights.
+We remind that the preferences of the chair are encoded with linear constraints $\Co_{W}$.
 % contraints represent the preferences $\Co_{W}$ of the chair about the scoring rule.
-The pairwise max regret $\PMR(x,y; \pprofile,W)$ is now obtained as the solution of the following linear program defined on the variables $w_1, …, w_m$. 
+The pairwise max regret $\PMR(x,y; \pprofile,W)$ can be obtained as the solution of the following linear program defined on the variables $w_1, …, w_m$ (weights attached to the different positions). 
 \begin{align*}
@@
 & \text{Equation } (\ref{eq:convexity})\\
-& \Co_W.
+& \Co_W
 \end{align*}

### 2019-02-25 draft.tex
Strategies

--- 2019-02-25 draft.tex
@@
 \newif\ifappendix
-%\appendixtrue %COMMENT to remove appendix % UNCOMMENT to add apendix
+\appendixtrue %COMMENT to remove appendix % UNCOMMENT to add apendix
 \input{ijcai_preamble} 
-\author{ID: 2696}
-%\author{Beatrice Napolitano$^1$\and Olivier Cailloux$^1$	\and  Paolo Viappiani$^{2}$
-%	\affiliations $^1$ LAMSADE, UMR 7243, CNRS and Universit\'e Paris Dauphine, PSL Research University, Paris, France\\ $^2$ LIP6, UMR 7606, CNRS and Sorbonne Universit\'e, Paris, France
-%	\emails \{firstname.lastname\}@dauphine.fr, paolo.viappiani@lip6.fr
-%}
+\author{Beatrice Napolitano$^1$\and Olivier Cailloux$^1$	\and  Paolo Viappiani$^{2}$
+	\affiliations $^1$ LAMSADE, UMR 7243, CNRS and Universit\'e Paris Dauphine, PSL Research University, Paris, France\\ $^2$ LIP6, UMR 7606, CNRS and Sorbonne Universit\'e, Paris, France
+	\emails \{firstname.lastname\}@dauphine.fr, paolo.viappiani@lip6.fr
+}
 %Restoring page numbers as missing them out violates basic human rights of the reviewers. -- Olivier
@@
 \newcommand{\W}{\mathcal{W}}
-\newcommand{\Co}{\mathcal{C}}
 \newcommand{\pw}{W}%our knowledge about the weights
 \newcommand{\powersetz}[1]{\mathscr{P}^*(#1)}
+\newcommand{\strat}[1]{\emph{#1}}
 
@@
 \DeclarePairedDelimiter\card{\lvert}{\rvert}
+\DeclarePairedDelimiter\abs{\lvert}{\rvert}
 
@@
 Social choice deals with the problem of determining a consensus choice from the preferences of different agents (voters).
-In the classical setting, the voting rule is fixed beforehand and full preference information is provided.
-Recently, the assumption of full preference information has been questioned by a number of researchers and several methods for eliciting preferences have been proposed.
-
-In this paper we go one step further and we assume that both the voting rule and the agents preferences are partially specified.
+In the classical setting, the voting rule is fixed beforehand and full preference information is provided by the voters. 
+Recently, the assumption of full preference information has been questioned by a number of researchers and several methods for eliciting voters information have been proposed.
+
+In this paper we go one step further and we assume that both the voting rule and the voters preferences are partially specified.
 Focusing on positional scoring rules, we assume that the chair, while  not able to give a precise definition of the rule, is capable of answering simple questions  requiring to pick a winner from a specific  example profile.
-Moreover, the preferences of the agents are incrementally acquired by asking comparison queries.
+Moreover, the preferences of the voters are incrementally acquired by asking comparison queries.
 
@@
 \section{Introduction}
-%\commentOC{Do we agree that we should talk systematically about agents (or systematically about voters)? Currently we talk about voters in first section, then agents.}
+\commentOC{Do we agree that we should talk systematically about agents (or systematically about voters)? Currently we talk about voters in first section, then agents.}
 Aggregation of preference information is a central task in many computer systems (recommender systems, search engines, etc).
@@
 (Sets are used for tied winners.)
-Among the many possible social choice functions, we consider {\em positional scoring rules (PSR)}, which attach weights to positions according to  the vector $(w_1, \ldots, w_m)$ (also called the scoring vector).
+Among the many possible social choice functions, we consider {\em positional scoring rules}, which attach weights to positions according to  the vector $(w_1, \ldots, w_m)$ (also called the scoring vector).
 %A scoring rule associates each alternative to a score that is given by the sum of points obtained for each voter.
@@
 Therefore the vector $(w_1,\ldots,w_m)$  is not known but we are given a set of constraints restraining the possible values that weights can take.
-We consider a decreasing sequence of weights\footnote{We assume all positions from $1$ to $m-1$ may contribute positively to the score of an alternative.
-The case where it is known that only the first $k<m-1$ positions matter can be easily dealt with by specifying $w_r = 0$ for $r > k$ as constraints.
-}:
-% If the chair considers that, for example, “only the first ten positions matter” (so that $w_r = 0$ for $r > 10$), then we simply assume the chair is able to express this constraint at the start of the querying process, thus, that this information is known, and approximate the problem by considering that it is only about the first ten alternatives, thus, set $m=10$.}
+We consider a decreasing sequence of weights:
 \begin{align}
@@
 Without loss of generality, we consider that $w_1=1$ and $w_m=0$.
-%\commentOC{I suggest we say no more than this to justify this assumption. Otherwise, we might say something like the following.
+\commentOC{I suggest we say no more than this to justify this assumption.
+Otherwise, we might say something like the following.
+If the chair considers that, for example, “only the first ten positions matter” (so that $w_r = 0$ for $r > 10$), then we simply assume the chair is able to express this constraint at the start of the querying process, thus, that this information is known, and approximate the problem by considering that it is only about the first ten alternatives, thus, set $m=10$.}
 
@@
 
-Notice that if $\MMR(\pprofile, W)\!=\!0$, then $x^{*}_{\pprofile,W}$  is a necessary co-winner; this means that for any valid completion of the profile and any feasible $w \!\in\!
-W$, $x^{*}_{\pprofile,W}$ obtains a highest score.
+Notice that if $MMR(\pprofile, W)=0$, then $x^{*}_{\pprofile,W}$  is a necessary co-winner; this means that for any valid completition of the profile and any feasible weight $w \in W$, $x^{*}_{\pprofile,W}$ obtains a highest score.
 
@@
 The adversary has to make the score of $y$ as high as possible, and the score of $x$ as low as possible.
-To do this, he should complete $\ppref_j$ to $\pref_j$ by putting above $x$ as many alternatives as he can, that is, all the alternatives except those that are known to be worse than $x$ (those $a$ such that $x \ppref_j a$); and similarly, put below $y$ all the alternatives he can, thus, put above $y$ only those $a$ such that $a \ppref_j y$.
+To do this, he should complete $\ppref_j$ to $\pref_j$ by putting above $x$ as many alternatives as he can, that is, all the alternatives except those that are known to be worst than $x$ (those $a$ such that $x \ppref_j a$); and similarly, put below $y$ all the alternatives he can, thus, put above $y$ only those $a$ such that $a \ppref_j y$.
 Sometimes these two objectives conflict: when an alternative should go above $x$ according to the first objective and below $y$ according to the second one (because $¬(x \ppref_j a) ∧ ¬(a \ppref_j y)$), and $x$ is known to be better than $y$ (thus $x \ppref_j y$).
 In this case, the first objective should take priority, and $a$ should be put above $x$, which will move both $x$ and $y$ one rank lower than if $a$ had been put below $y$.
-This maximizes the adversary’s interests: because the weight vector is convex, the difference in scores will be lower when both alternatives are ranked lower (Equation \ref{eq:convexity}), and that difference of score is in favor of $x$ when $x \ppref_j y$, thus to be minimized from the point of view of the adversary.
-To summarize:
+This maximizes the adversary’s interests: because the weight vector is convex, the difference in scores will be lower when both alternatives are one rank lower (Equation \ref{eq:convexity}), and that difference of score is in favor of $x$ when $x \ppref_j y$, thus to be minimized from the point of view of the adversary.
+To summarize:\commentOC{TODO only one number here} 
 \begin{align} 
 \label{eq:compl}
-\begin{split}
 a \pref_j x &⇔ ¬(x \ppref_j a)\\
 y \pref_j a &⇔ ¬(a \ppref_j y) ∧ (¬(x \ppref_j y) ∨ (x \ppref_j a)).
-\end{split}
 \end{align}
-In what follows let $\hat{\profile}$ be the profile computed according to the above procedure, and  $\hat{v}_j$ the $j$-th element (the linear order extending the partial order $p_j$ of the $j$-th voter).
+
 We just sketched a proof of the following claim, and leave the rest of the proof to the reader.
 \begin{claim}
-There exists a completion $\hat{\profile} \in C(\pprofile)$ such that $\PMR(x,y; \pprofile, W) = \max_{\w \in W} [ s(y; \profile,\w) - s(x; \profile,\w) ]$ and that the linear order $\hat{v}_{j}$ of each agent $j$ satisfies (\ref{eq:compl}).
-%There exists a completion ${\pref_j} \in C(\ppref_j)$ such that $\PMR(x,y; \pprofile, W) = \max_{\w \in W} \max_{\profile \in C(\pprofile), {\pref_j} \in \profile} [ s(y; \profile,\w) - s(x; \profile,\w) ]$ and that satisfies
+	There exists a completion ${\pref_j} \in C(\ppref_j)$ such that $\PMR(x,y; \pprofile, W) = \max_{\w \in W} \max_{\profile \in C(\pprofile), {\pref_j} \in \profile} [ s(y; \profile,\w) - s(x; \profile,\w) ]$ and that satisfies \ref{eq:compl}.
 \end{claim}
-%In this claim, we abuse notation by writing ${\pref_j} \in \profile$ to mean that the preference ordering corresponding to agent $j$ in $\profile$ is $\pref_j$.
-\noindent It follows that $\hat{v}_{j}(x)$, the rank of $x$ for voter $j$ in the PMR-maximizing linear order $\bar{v}_{j}$ %$\PMR(x,y; \pprofile, W)$ 
-is $\hat{v}_{j}(y) = 1+\card{A}-\card{{\ppref_j}(x)}$, where ${\ppref_j}(x)$ designates the set of alternatives that are less good than $x$ according to $\ppref_j$, and the rank of $y$ is $\hat{v}_{j}(x)=1+\card{{\pprefinv_j}(y)}+\beta$, where $\beta = \card{A} - \card{{\ppref_j}(x)}$ if $(x \ppref_j y)$ and $\beta = 0$ otherwise.
+In this claim, we abuse notation by writing ${\pref_j} \in \profile$ to mean that the preference ordering corresponding to agent $j$ in $\profile$ is $\pref_j$.
+
+It follows that the rank of $x$ for voter $j$ in $\PMR(x,y; \pprofile, W)$ is $1+\card{A}-\card{{\ppref_j}(x)}$, where ${\ppref_j}(x)$ designates the set of alternatives that are less good than $x$ according to $\ppref_j$, and the rank of $y$ is $1+\card{{\pprefinv_j}(y)}+\alpha$, where $\alpha = \card{A} - \card{{\ppref_j}(x)}$ if $(x \ppref_j y)$ and $\alpha = 0$ otherwise.
 
@@
 
-\begin{claim}
+The space of feasible weights $W$ is encoded with linear constraints that model the preferences of the chair.
+Therefore the pairwise maximum regret can be computed with a linear program.
+
+The minimax regret solution $\MMR(\pprofile, W)$ is determined by solving a sequence of pairwise max regret computations.
+Each PMR is computed using a linear program.
+The decision variables correspond to the weights attached to the different positions.
+Constraints are on the feasible parameters (the weights of the scoring rules); contraints represent the preferences of the chair about the scoring rule.
+
+Let $\hat{\profile}$ be the profile computed according to the above procedure, and  $\hat{v}_j$ the $j$-th element (the linear order extending the partial order $p_j$ of the $j$-th voter).
+\begin{prop}
+%Assume convex weights.
 The $\PMR$ can be written as:
 \begin{align} 
-\PMR(x,y; \pprofile, W)  
-%\max_{w \in W} s(y; \hat{\profile}, \w) - s(y; \hat{\profile}, \w)\\
-& = \max_{w \in W} \sum_{j=1}^n w_{\hat{v}_j(y)} - w_{\hat{v}_j(x)} = \\ 
-& = \max_{w \in W} \sum_{r=1}^m (\hat{\alpha}_{r}^{y} - \hat{\alpha}_{r}^{x}) w_i. 
+\PMR(x,y; \pprofile, W) =  
+\max_{w \in W} s(y; \hat{\profile}, \w) - s(y; \hat{\profile}, \w)\\
+=\max_{w \in W} \sum_{j=1}^n w_{\hat{v}_j(y)} - w_{\hat{v}_j(x)} =
+\max_{w \in W} \sum_{r=1}^m (\hat{\alpha}_{r}^{y} - \hat{\alpha}_{r}^{x}) w_i 
 \end{align}
-where the $\hat{\alpha}_{r}^{y}$ (resp. $\hat{\alpha}_{r}^{x}$)  is the number of times $y$ (resp. $x$) is at rank $r$ in the rankings of the completed profile $\hat{\profile}$.
+where the coefficient $ (\hat{\alpha}_{r}^{y} - \hat{\alpha}_{r}^{x})$ is the number of times $y$ is at rank $r$ minus the number of times $x$ is at rank $r$ in the rankings of the completed profile $\hat{\profile}$.
 %$\hat{\alpha}_{i}^{x} = \sum_{j=1}^{n}  I[\hat{v}_{j}(x)=i]$ where $I$ is the indicator function.
-\end{claim}
+\end{prop}
 %\[ \alpha_{i} = \sum_{j=1}^{n}  I[\hat{v}_{j}(y)=i] - I[\hat{v}_{j}(x)=i]\]
-%We now show that the pairwise maximum regret can be computed with a linear program.
-The PMR can be now computed by optimizing a linear program (LP) where the decision variables correspond to the weights attached to the different positions.
-Constraints are on the feasible parameters (the weights of the scoring rules).
-We remind that the preferences of the char are encoded with linear constraints $\Co_{W}$.
-% contraints represent the preferences $\Co_{W}$ of the chair about the scoring rule.
 The pairwise max regret $\PMR(x,y; \pprofile,W)$ is now obtained as the solution of the following linear program defined on the variables $w_1, …, w_m$. 
@@
 & \text{Equation } (\ref{eq:convexity})\\
-& \Co_W.
+& C_W.
 \end{align*}
-Note that given our choice $w_{1}=1$ and $w_{m}=0$, there are only $m-2$ variables 
-(we leave $w_{1}$ and $w_{m}$ in the LP just for clarity of presentation).
-
-%Finally the minimax regret solution $\MMR(\pprofile, W)$ is determined by solving a sequence of pairwise max regret computations, solving the above linear program for every different pair $(x,y) \in A^{2}$.
-The max regret $\MR(x; \pprofile, W)$ is determined by considering the pairwise regret of $x$ with each other alternative in $A$.
-The optimal alternative w.r.t. minimax regret is the one with least max regret. 
-Notice that, whenever the PMR of an alternative $x$ (against some other alternative) exceeds the best MR value found so far, we don't need to further evaluate $x$. 
-This idea can be exploited further by adopting a minimax-search tree (see \cite{Braziunas2011}).
-%The computation can be made faster by adopting an efficient scheme of evaluation of PMR where .
+Note that given our choice $w_{1}=1$ and $w_{m}=0$, there are only $m-2$ variables. We leave $w_{1}$ and $w_{m}$ in the linear program just for clarity of presentation.
 
@@
 The remainder of this Section is structured as follows.
-First of all, we discuss the different types of questions that can be asked to the agents and to the chair, and the way responses are handled.
+First of all, we discuss the different types of questions that can be asked to the voters and to the chair, and the way responses are handled.
 Then, we describe different strategies to determine informative queries to ask next, with the goal of reducing $\MMR(\pprofile,W)$ quickly.
 
-%Type of questions that we can ask to the chair:	bound queries (Is this alternative among your top-k most preferred items?), comparison queries (do you prefer alternative x or alternative y?).
-% we discuss the different forms of queries and develop several query strategies 
 \paragraph{Question types}
-We distinguish between questions asked to the agents and questions asked to the chair.
-As {\em questions asked to the agents} it is natural to consider comparison queries asking to compare two alternatives.
+We distinguish between questions asked to the voters and questions asked to the chair.
+As {\em questions asked to the voters}, it is natural to consider comparison queries asking to compare two alternatives.
 %Another common type of queries are {\em top-k}, asking to each voter her $k$ most preferred alternatives.
-The effect of a response to a question asked to an agent is to increase our knowledge about the agents rankings, thus augmenting the partial profile $\pprofile$. 
+The effect of a response to a question asked to a voter is to augment our knowledge about the voters rankings, thus augmenting the partial profile $\pprofile$. 
 If voter $j$ answers a comparison query stating that alternative $a$ is preferred to $b$, then the partial order $\ppref_j$ is augmented with $a \ppref_j b$ and by transitive closure.
@@
 A bit more discussion is needed about {\em questions asked to the chair}.
-Such questions aim at refining our knowledge about the scoring rule; a response gives us a constraint on the weight vector $\w$.
+Such a question aims at refining our knowledge about the scoring rule;
+a response gives us a constraint on the weight vector $\w$.
 In particular, we want to acquire constraints of the type:
@@
 \paragraph{Building concrete questions for the chair}
-As we assume the weights constitute the utility components of the chair, it might be reasonable to assume, 
-%as we do here, 
-that the chair is able to answer such abstract questions in our setting.
+As we assume the weights constitute the utility components of the chair, it might be reasonable to assume, as we do here, that the chair is able to answer such abstract questions in our setting.
 However, it is important to make sure that the question can also, in principle, be asked in a more concrete way, in terms of winners of example profiles.
-This permits to test whether the chair understands the question as we do; this permits to relate the preference of the chair  to her choice behavior in the economic sense; and this will be necessary for an ordinal extension of our work where the scores would not be considered as cardinal utilities.
+This permits to test whether the chair understands the question as we do; this permits to relate the preference of the chair as we understand it to her choice behavior in the economic sense; and this will be necessary for an ordinal extension of our work where the scores would not be considered as cardinal utilities.
 Thus, our task is to build a profile, given $\lambda$ and $r ≤ m-2$, in such a way that the set of (tied) winners picked by the chair reveals whether $w_{r} - w_{r+1} \geq \lambda (w_{r+1} - w_{r+2})$.
@@
 Observe that the question may be defined equivalently as whether $q w_{r} + p w_{r+2} ≥ (p + q) w_{r+1}$, where $p, q$ are natural numbers.
-As a first attempt to make this question concrete, let us define a profile $P$ containing $p+q$ agents. 
+As a first attempt to make this question concrete, let us define a profile $P$ containing $p+q$ voters.
 Define an alternative $a$ that receives $q$ times the rank $r$ and $p$ times the rank $r+2$ and an alternative $b$ that receives $p+q$ times the rank $r+1$.
 Observing that the score of $a$ in that profile is exactly the left hand side of the question, and that the score of $b$ is the right hand side, intuition suggests that observing whether the chair picks $a$ or $b$ as winner will let us determine which side is greater; equality occurring when the chair declares $a$ and $b$ as tied for the victory.
-However, we still need to complete the profile, thus, come up with other $m-2$ alternatives defined so that each agent in the resulting profile has placed exactly one alternative in each rank. 
-And we must ensure, doing this, that these other alternatives are not better than $a$ or $b$.\footnote{Because, if the chair picks a different alternative $c$, it tells us that the chair prefers $c$ to both $a$ and $b$,
-%but it generally does not  answer the question we are interested in
-but in general we do not acquire the type of constraint we are interested in.} 
-Taking $p = q = 1$, $m=4$, $r=2$, we see that such a completion may be impossible. Luckily, this problem can be worked around, at the price of increasing the number of agents.
-
-First build a temporary profile $P$ of $p+q$ agents with $a$ and $b$ ranked as just described.
+However, we still need to complete the profile, thus, come up with other $m-2$ alternatives defined so that each voter in the resulting profile has given each rank once.
+And we must ensure, doing this, that these other alternatives are not better than $a$ or $b$.
+For if the chair picks a different alternative $c$, it only tells us that the chair prefers $c$ to both $a$ and $b$, but it generally does not answer the question we are interested in.
+Taking $p = q = 1$, $m=4$, $r=2$, we see that such a completion may be impossible.
+Luckily, this problem can be worked around, at the price of increasing the number of voters.
+
+First build a temporary profile $P$ of $p+q$ voters with $a$ and $b$ ranked as just described.
 Complete it with $m-2$ alternatives ranked in arbitrary orders so that the resulting profile has complete strict rankings for each of the $p+q$ voter.
-Now we will make the other alternatives as bad as desired by adding agents to $P$ that appreciate $a$ and $b$ more than the other alternatives, thus building a profile $P'$ in which, whatever the weights, $c$ may not have a better score than $a$.
-Observe that if we add $\delta$ agents (with $\delta$ a natural number) that put $a$ at first rank and $b$ at second rank, and $\delta$ agents that put $b$ at first rank and $a$ at second rank, we do not change the difference of the scores of $a$ and $b$, and thus, observing the chair choosing $a$ or $b$ still answers the question.
+Now we will make the other alternatives as bad as desired by adding voters to $P$ that appreciate $a$ and $b$ more than the other alternatives, thus building a profile $P'$ in which, whatever the weights, $c$ may not have a better score than $a$.
+Observe that if we add $\delta$ voters (with $\delta$ a natural number) that put $a$ at first rank and $b$ at second rank, and $\delta$ voters that put $b$ at first rank and $a$ at second rank, we do not change the difference of the scores of $a$ and $b$, and thus, observing the chair choosing $a$ or $b$ still answers the question.
 Choose arbitrarily a matching of the remaining $m-2$ alternatives to the ranks $3$ to $m$, say, $c \mapsto 3$, $d \mapsto 4$, and so on.
-The first $\delta$ supplementary agents, who rank $a$ first and $b$ second, rank the other alternatives as the just defined mapping suggests.
-The other $\delta$ supplementary agents, who rank $b$ first and $a$ second, use the opposite ranking for the remaining alternatives, say, $c \mapsto m$, $d \mapsto m-1$, and so on.
-We can now prove that, for $\delta = p+q$, and whatever the weight vector $w \in \W$, no alternative, except possibly $b$, has a better score than $a$.
+The first $\delta$ supplementary voters, who rank $a$ first and $b$ second, rank the other alternatives as the just defined mapping suggests.
+The other $\delta$ supplementary voters, who rank $b$ first and $a$ second, use the opposite ranking for the remaining alternatives, say, $c \mapsto m$, $d \mapsto m-1$, and so on.
+We can now prove that, for $\delta = p+q$, and whatever the weight vector $\w \in \W$, no alternative, except possibly $b$, has a better score than $a$.
 (In fact, as the construction will exhibit, they are all worst than both $a$ and $b$, but the weaker fact is enough for our claim.)
@@
 
-%\commentOC{I suppose we have, unfortunately, to get rid of this useful example, for reason of space.
+\commentOC{I suppose we have, unfortunately, to get rid of this useful example, for reason of space.
 (If we manage to keep it, I’ll need to rework it a bit so that it follows the strategy in the proof.)}
 \begin{example}
-Suppose our query strategy suggests us to ask the chair the following query: $w_{2} - w_{3} \geq 2(w_{3} - w_{4})$.
+Suppose our query strategy suggests us to ask the chair the following query:
+\[ w_{2} - w_{3} \geq 2(w_{3} - w_{4}) \]
 In order to impose this constraints,
@@
 \paragraph{Elicitation strategies}
-
-We develop some elicitation strategies for simultaneous elicitation of agents' preferences and of the scoring rule.
-Starting from some initial partial knowledge, our goal is to acquire the relevant preference information 
-%(about both the scoring rule function and the agents' preferences) 
-in order to determine an approximate winner.
-While it is of course possible doing full elicitation of the weights and afterwards elicit the agents' preferences (or the other way around) we propose an interleaved approach.
-In our interactive  protocol for simultaneously eliciting the preferences of the chair about the voting rule and the agents' preferences about the alternatives.
+\commentOC{TODO move this.} At this stage, we are content that a procedure exists to transform our questions to questions about winners of a PSR.
+Further studies would investigate, for example, what is lost in terms of elicitation efficiency when we are forced to restrain to realistic concrete questions, meaning, questions involving small profiles; or investigate the relationship between our understanding of scores as (cardinal) utility and (ordinal) scores as definition of a PSR.
+
+We develop several elicitation strategies for simultaneous elicitation of agents' preferences and of the scoring rule.
+While it is of course possible to first fully elicit the agents’ preferences and afterwards elicit weights, we also want to propose interleaved approaches and compare them experimentally.
 Indeed, it can be beneficial to interleave questions asked to the chair and questions asked to agents, depending on which is estimated to be more informative.
 
-Answers given by the chair about the scoring rule refine our knowledge of the weights $w_1,\ldots,w_n$, while
-answers given by one of the agents refine our knowledge about the agents preferences.
-At each step we need to decide whether we want to ask a question to the chair or to one of the agents (and to which agent in particular). 
-%We ask comparison queries to the agents and questions comparing the differences of weights to the chair.
-
-In the experiments we want to compare the interleaved approach with a baseline challenger, a method  that elicits the preferences of the agents first and then the voting rule (or the other way around)
-We consider different strategies to determine the next question to ask given the current information.
-
-%\begin{itemize}
-%\item
-\medskip \noindent
-{\em Current solution strategy}: consider the solution of the minimax regret game, 
- $(x^{*},\bar{y},\bar{\profile},\bar{\w})$, where $x^{*}$ is the minimax regret optimal alternative,  $\bar{y} = \arg \max_{y \in A} \PMR(x^{*},y; \pprofile, W)$; is the adversarial choice, and $\bar{\profile}$ and $\w$ are the instantiations\footnote{ $\bar{\profile} \!=\!
+We define here the various strategies we tested experimentally.
+A strategy is a function (or a random process) that gives us, given our partial knowledge so far $(\pprofile, W)$, a question that should be asked, according to that strategy.
+
+Among them, the \strat{Random} strategy is used to capture how hard an elicitation problem is, by giving us a baseline: using it we can estimate how fast the regret diminishes when we ask questions randomly.
+%It also estimates how much information of that kind we would need if we assume the information would not be elicited experimentally using an active learning approach, but would be collected empirically as they randomly appear to us.
+(This estimate is however very rough as it is most relevant only when the observations follow the same random distribution as the one we chose.)
+Choosing the questions purely randomly however, that is, independently of what we know already, would be pointless, as we would most of the time ask questions we already know the answer of.
+Thus, that strategy choses questions in a minimally “clever” way, just by picking questions in a set of a priori relevant questions.
+The \strat{Random} strategy first decides with a probability of $1/2$ each whether it will ask a question about weights or a question about a preference ordering (unless the profile is already known entirely).
+If it opted for a question about weights, it draws one rank in $2 ≤ r ≤ m-2$ equiprobably, takes the middle of the interval of values for $\lambda$ that are still possible considering our knowledge so far, and asks whether $w_r - w_{r+1} ≥ \lambda (w_{r+1} - w_{r+2})$.
+The intervals are initialized to $[1, n]$.
+If it opted for a question to agents, it draws equiprobably among the voters whose preference is not known entirely; picks an alternative $a$ randomly with equal probability among those involved in some incomparabilities in $\ppref_j$; and picks an alternative $b$ with equal probability among those incomparable with $a$ in $\ppref_j$.
+
+We also define the \strat{Extreme completions} strategy \commentOC{Previously called Current solution}, which we consider as a more realistic baseline. 
+Consider the solution of the minimax regret game, 
+ $(x^{*},\bar{y},\bar{\profile},\bar{\w})$, where $x^{*}$ is the minimax regret optimal alternative, and $\bar{y} = \arg \max_{y \in A} \PMR(x,y; \pprofile, W)$, $\bar{\profile}$ and $\bar{\w}$ are the adversarial choices, thus, the instantiations that, given the choice of $x^*$, maximize the regret.
+%\footnote{ $\bar{\profile} \!=\!
 \arg \max_{\profile \in C(\pprofile)} s(y; \profile, \bar{\w}) \!-\!
@@
 \arg \max_{w \in W} s(y; \pprofile, w) \!-\!
-s(x; \pprofile, w)$ .} of the profile and weights associated with maximum regret.
- % Determine the part of ``regret'' due to uncertainty in $w$
-% Determine the part of ``regret' due to uncertainty in $p$
+s(x; \pprofile, w)$ .}
 Define: 
 \begin{align}
-\tau_{1} & = \min_{\w \in W} s(\bar{y}; \bar{\profile}, \w) - s(x^{*}; \bar{\profile}, \w)  \label{eq:tau1} \\
+\tau_{1} & = \min_{\w \in W} s(\bar{y}; \bar{\profile}, \w) - s(x^{*}; \bar{\profile}, \w),  \label{eq:tau1} \\
 \tau_{2} & = \min_{\profile \in C(\pprofile)} s(\bar{y},\profile, \bar{\w}) -  s(x^{*}; \profile, \bar{\w}).
 \end{align}
-Intuitively the quantity $\MMR - \tau_{1} $ measures the contribution to regret of our uncertainty about the weights $\w$, while $\MMR - \tau_{2} $ measures the uncertainty about the profile.
-Therefore, whenever $\tau_{1} < \tau_{2}$ we ask a question to the chair, and compare $\bar{\w}$ and $\w_{\tau}$.
-the argmax of Eq.
-(\ref{eq:tau1}), componentwise to find the position $r$ that is most valuable to ask about.
-Instead, if $\tau_{1} > \tau_{2}$ we ask a question to one of the agent, with the following heuristics: COMPLETE
-
- %\item 
- One possibility is to consider the MMR {\em a posteriori}.
-Assume that the different answers to a query induce the possible sets to be $(\pprofile_1,W_1)$ and $(\pprofile_2,W_2)$, then the score according to worst-case maximum regret is:
-\[\SCORE(x)= \max_{i=1,2} \MMR(\pprofile_i,W_i) \]
-In this case, the query with least value is chosen.
-What is the complexity of this strategy?
-Let's define $Q$ as the set of all possible queries we can address to the agents and to the chair.
-The worst case is represented by the situation of complete ignorance.
-%in which we do not have any information about both the agents' preferences and the weights constraints. 
-In this case we can address $\binom{m}{2}=\frac{m(m-1)}{2}$ questions to each agent.
-Moreover, we need to ask at least $m$ questions to the chair.
-Then, each question induces two possible pairs of $(\pprofile,W)$ for each of which we compute the $\MMR$, whose worst case complexity is $O(nm^3)$.
-Thus, the cardinality of $Q$ in the worst case is $\approx n \cdot \frac{m(m-1)}{2} + \lambda m$, and the worst case time complexity of the strategy is $O(n^2m^5)$.
-
-\medskip \noindent
-{\em Two phase method.}
+Intuitively the quantity $\MMR - \tau_{1} = \max_{\w \in W} s(\bar{y}; \bar{\profile}, \w) - s(x^{*}; \bar{\profile}, \w) - \min_{\w \in W} s(\bar{y}; \bar{\profile}, \w) - s(x^{*}; \bar{\profile}, \w)$ estimates the contribution to regret of our uncertainty about the weights $\w$, while $\MMR - \tau_{2} $ estimates the uncertainty about the profile.
+Therefore, whenever $\tau_{1} < \tau_{2}$ we ask a question to the chair, and compare componentwise $\bar{\w}$ and $\w^{\tau}$, the argmax of Eq.
+(\ref{eq:tau1}), to find the position $r$ that is most valuable to ask about (the one that maximizes $\abs{\bar{\w}_r - \w^{\tau}_r}$).
+Instead, if $\tau_{1} > \tau_{2}$ we ask a question to one of the agent, picking the alternative randomly as described above.
+\commentOC{We’d better check for each $j$ the difference between the difference of the ranks of $x$ and $y$ in the worst $v$ and in the best $v$ and pick a voter related to highest difference, pick $x$ or $y$ with $1/2$ chances, and pick an incomparable alternative equiprobably.}
+
+The \strat{Pessimistic} strategy selects the question that leads to minimal regret in the worst case, considering both possible answers to the question.
+Assume that a question leads to the possible new knowledge states $(\pprofile_1, W_1)$ and $(\pprofile_2, W_2)$, depending on the answer.
+Then the badness of the question in the worst case is:
+\[\max_{i=1,2} \MMR(\pprofile_i,W_i) \]
+This badness measure gives a way of picking questions among a set of possible questions, by picking one that minimizes the measure.
+Note that other aggregators than $\max$ can be used as well.
+The \strat{Pessimistic} strategy considers as possible questions the ones defined by the \strat{Random} strategy \commentOC{To check}.
+It uses a variant of the $\max$ as an aggregator: if the maximal $\MMR$ of two questions are equal, it prefers the question that has the lowest $\MMR$.
+We expect this strategy to perform very well, but only for very small problem instances: its complexity is in $O(n^2 m^5)$, because we consider $O(m^2)$ questions for each agent and need for each question to compute $\MMR$ twice, whose complexity is $O(nm^3)$.
+For small dimensions, it gives us an estimate of an upper bound to the possible quality of a strategy.
+
+\commentOC{TODO Continue here.}
+Two phase method.
 Ask a predefined (non adaptive) sequence of questions in order to learn the weights $w$ of the scoring rule).
@@
 %\item Non-interleaved regret method: comparison with a method based on minimax regret, but not interleaved.
-\medskip \noindent
-{\em Non-interleaved non-regret strategies (useful as benchmarks)}	
+
+Non-interleaved non-regret strategies (useful as benchmarks).	
 	\begin{itemize}
@@
 	\end{itemize}
-%\end{itemize}
 
@@
 \section{Conclusions}  \label{sec:conclusions}
+
+% integrated preference elicitation methodology
 In this paper we have considered a  social choice setting with partial  information about the voter's  
@@
 We have proposed the use of minimax regret as a means of robust winner determination in this setting, and as well as to guide the process of simultaneous elicitation of preferences and voting rule.
-Our experimental results %on randomly generated and real world data sets 
-show that regret-based elicitation is effective and allow to quickly find a near-optimal consensus choice.
-%Regret-based elicitation allows to determine near-optimal winners using only few information about the agents' preferences.
-
+Our experimental results on randomly generated and real world data sets show that regret-based elicitation is effective and allow to find a near-optimal consensus choice in a limited number of steps.
+%The detection of optimal or near-optimal product recommendation is generally possible with little concept and utility information
+%Regret-based elicitation allows to determine near-optimal winners using only few information about the voters' preferences.
 We mention some  important directions for future works.
@@
 A third direction is that of considering probabilistic methods for elicitation.
-Finally, we are interested in studying the effect of strategic agents. %that may not report their true preferences.
+Finally, we are interested in studying the effect of strategic agents, that may not report their true preferences.
 % distribution-free heuristics

### 2019-02-25 draft.tex

--- 2019-02-25 draft.tex
@@
 \newcommand{\powersetz}[1]{\mathscr{P}^*(#1)}
+\newcommand{\strat}[1]{\emph{#1}}
 
@@
 
-First build a temporary profile $P$ of $p+q$ agents with $a$ and $b$ ranked as just described.
+First build a temporary profile $P$ of $p+q$ voters with $a$ and $b$ ranked as just described.
 Complete it with $m-2$ alternatives ranked in arbitrary orders so that the resulting profile has complete strict rankings for each of the $p+q$ voter.
-Now we will make the other alternatives as bad as desired by adding agents to $P$ that appreciate $a$ and $b$ more than the other alternatives, thus building a profile $P'$ in which, whatever the weights, $c$ may not have a better score than $a$.
-Observe that if we add $\delta$ agents (with $\delta$ a natural number) that put $a$ at first rank and $b$ at second rank, and $\delta$ agents that put $b$ at first rank and $a$ at second rank, we do not change the difference of the scores of $a$ and $b$ (and thus, observing the chair choosing $a$ or $b$ still answers the question).
+Now we will make the other alternatives as bad as desired by adding voters to $P$ that appreciate $a$ and $b$ more than the other alternatives, thus building a profile $P'$ in which, whatever the weights, $c$ may not have a better score than $a$.
+Observe that if we add $\delta$ voters (with $\delta$ a natural number) that put $a$ at first rank and $b$ at second rank, and $\delta$ voters that put $b$ at first rank and $a$ at second rank, we do not change the difference of the scores of $a$ and $b$, and thus, observing the chair choosing $a$ or $b$ still answers the question.
 Choose arbitrarily a matching of the remaining $m-2$ alternatives to the ranks $3$ to $m$, say, $c \mapsto 3$, $d \mapsto 4$, and so on.
-The first $\delta$ supplementary agents, who rank $a$ first and $b$ second, rank the other alternatives as the just defined mapping suggests.
-The other $\delta$ supplementary agents, who rank $b$ first and $a$ second, use the opposite ranking for the remaining alternatives, say, $c \mapsto m$, $d \mapsto m-1$, and so on.
-We can now prove that, for $\delta = p+q$, and whatever the weight vector $w \in \W$, no alternative, except possibly $b$, has a better score than $a$.
+The first $\delta$ supplementary voters, who rank $a$ first and $b$ second, rank the other alternatives as the just defined mapping suggests.
+The other $\delta$ supplementary voters, who rank $b$ first and $a$ second, use the opposite ranking for the remaining alternatives, say, $c \mapsto m$, $d \mapsto m-1$, and so on.
+We can now prove that, for $\delta = p+q$, and whatever the weight vector $\w \in \W$, no alternative, except possibly $b$, has a better score than $a$.
 (In fact, as the construction will exhibit, they are all worst than both $a$ and $b$, but the weaker fact is enough for our claim.)
 
- %This concludes the proof of the following claim.
-\begin{claim}
-	Given a rational $\lambda$ and a rank $r$ between $1$ and $m - 2$, the profile named $P'$ in the foregoing description is such that, for any weight vector $\w \in \W$, $a \in f(P')$ iff $w_{r} - w_{r+1} ≥ \lambda (w_{r+1} - w_{r+2})$ and $b \in f(P')$ iff $w_{r} - w_{r+1} ≤ \lambda (w_{r+1} - w_{r+2})$, where $f$ is the PSR parameterized with $\w$.
-\end{claim}
-\begin{proof}
 Pick any alternative $c$ that is not $a$ or $b$. 
@@
 Because weights are non increasing, this guarantees, with $\delta = p + q$, that the score of $a$ is not lower than the one of $c$ (it is even strictly higher, thanks to the strict inequality).
-\end{proof}
+
+This concludes the proof of the following claim.
+\commentOC{I don’t think the reorganization with moving the claim slightly upwards works.
+The proof really starts much higher and would be cut in half if moving the claim slightly.
+Moving it more would require more reorganisation of the text.}
+\begin{claim}
+	Given a rational $\lambda$ and a rank $r$ between $1$ and $m - 2$, the profile named $P'$ in the foregoing description is such that, for any weight vector $\w \in \W$, $a \in f(P')$ iff $w_{r} - w_{r+1} ≥ \lambda (w_{r+1} - w_{r+2})$ and $b \in f(P')$ iff $w_{r} - w_{r+1} ≤ \lambda (w_{r+1} - w_{r+2})$, where $f$ is the PSR parameterized with $\w$.
+\end{claim}
 

### 2019-02-25 draft.tex
Minor modifs

@@
 Social choice deals with the problem of determining a consensus choice from the preferences of different agents (voters).
-In the classical setting, the voting rule is fixed beforehand and full preference information is provided.
+In the classical setting, the voting rule is fixed beforehand and full information concerning the preferences of the agents is provided.
 Recently, the assumption of full preference information has been questioned by a number of researchers and several methods for eliciting preferences have been proposed.
@@
 \section{Introduction}
-%\commentOC{Do we agree that we should talk systematically about agents (or systematically about voters)? Currently we talk about voters in first section, then agents.}
 Aggregation of preference information is a central task in many computer systems (recommender systems, search engines, etc).
@@
 The case where it is known that only the first $k<m-1$ positions matter can be easily dealt with by specifying $w_r = 0$ for $r > k$ as constraints.
-}:
+} \commentOC{It’s not clear to me that this is true…}:
 % If the chair considers that, for example, “only the first ten positions matter” (so that $w_r = 0$ for $r > 10$), then we simply assume the chair is able to express this constraint at the start of the querying process, thus, that this information is known, and approximate the problem by considering that it is only about the first ten alternatives, thus, set $m=10$.}
@@
 In this case, the first objective should take priority, and $a$ should be put above $x$, which will move both $x$ and $y$ one rank lower than if $a$ had been put below $y$. 
-This maximizes the adversary’s interests: because the weight vector is convex, the difference in scores will be lower when both alternatives are ranked lower (Equation \ref{eq:convexity}), and that difference of score is in favor of $x$ when $x \ppref_j y$, thus to be minimized from the point of view of the adversary.
+This maximizes the adversary’s interests: because the weight vector is convex, the difference of scores will be lower when both alternatives are ranked lower (Equation \ref{eq:convexity}), and that difference of scores is in favor of $x$ when $x \ppref_j y$, thus to be minimized from the point of view of the adversary.
 To summarize:
@@
 \end{align} 
-In what follows let $\hat{\profile}$ be the profile computed according to the above procedure, and  $\hat{v}_j$ the $j$-th element (the linear order extending the partial order $p_j$ of the $j$-th voter).
 We just sketched a proof of the following claim, and leave the rest of the proof to the reader.
 \begin{claim}
-There exists a completion $\hat{\profile} \in C(\pprofile)$ such that $\PMR(x,y; \pprofile, W) = \max_{\w \in W} [ s(y; \profile,\w) - s(x; \profile,\w) ]$ and that the linear order $\hat{v}_{j}$ of each agent $j$ satisfies (\ref{eq:compl}).
+There exists a completion $\hat{\profile} \in C(\pprofile)$ such that $\PMR(x,y; \pprofile, W) = \max_{\w \in W} [ s(y; \hat{\profile}, \w) - s(x; \hat{\profile}, \w) ]$ and such that the linear order $\hat{v}_{j}$ of each agent $j$ satisfies (\ref{eq:compl}).
 %There exists a completion ${\pref_j} \in C(\ppref_j)$ such that $\PMR(x,y; \pprofile, W) = \max_{\w \in W} \max_{\profile \in C(\pprofile), {\pref_j} \in \profile} [ s(y; \profile,\w) - s(x; \profile,\w) ]$ and that satisfies
@@
 %In this claim, we abuse notation by writing ${\pref_j} \in \profile$ to mean that the preference ordering corresponding to agent $j$ in $\profile$ is $\pref_j$.
-\noindent It follows that $\hat{v}_{j}(x)$, the rank of $x$ for voter $j$ in the PMR-maximizing linear order $\bar{v}_{j}$ %$\PMR(x,y; \pprofile, W)$ 
-is $\hat{v}_{j}(y) = 1+\card{A}-\card{{\ppref_j}(x)}$, where ${\ppref_j}(x)$ designates the set of alternatives that are less good than $x$ according to $\ppref_j$, and the rank of $y$ is $\hat{v}_{j}(x)=1+\card{{\pprefinv_j}(y)}+\beta$, where $\beta = \card{A} - \card{{\ppref_j}(x)}$ if $(x \ppref_j y)$ and $\beta = 0$ otherwise.
+It follows that $\hat{v}_{j}(x)$, the rank of $x$ in the PMR-maximizing linear order of voter $j$, %$\PMR(x,y; \pprofile, W)$ 
+is $\hat{v}_{j}(x) = 1+\card{A}-\card{{\ppref_j}(x)}$, where ${\ppref_j}(x)$ designates the set of alternatives that are less good than $x$ according to $\ppref_j$, and the rank of $y$ is $\hat{v}_{j}(y)=1+\card{{\pprefinv_j}(y)}+\beta$, where $\beta = \card{A} - \card{{\ppref_j}(x)}$ if $(x \ppref_j y)$ and $\beta = 0$ otherwise.
 
@@
 %A proof that this reasoning is correct is in \cref{sec:prfCompl}.
+
 \begin{claim}
@@
 This concludes the proof of the following claim. 
-\commentOC{I don’t think the reorganization with moving the claim slightly upwards works.
-The proof really starts much higher and would be cut in half if moving the claim slightly.
-Moving it more would require more reorganisation of the text.}
 \begin{claim}
@@
 \end{claim}
+\commentOC{Plz others check this.} At this stage, we are content that a procedure exists to transform our abstract questions to questions about winners of a PSR.
+Further studies would investigate, for example, what is lost in terms of elicitation efficiency when we are forced to restrain to realistic concrete questions, meaning, questions involving small profiles; or investigate the relationship between our understanding of scores as (cardinal) utility and (ordinal) scores as definition of a PSR.
 
@@
 \paragraph{Elicitation strategies}
-\commentOC{TODO move this.} At this stage, we are content that a procedure exists to transform our questions to questions about winners of a PSR.
-Further studies would investigate, for example, what is lost in terms of elicitation efficiency when we are forced to restrain to realistic concrete questions, meaning, questions involving small profiles; or investigate the relationship between our understanding of scores as (cardinal) utility and (ordinal) scores as definition of a PSR.
-
 We develop several elicitation strategies for simultaneous elicitation of agents' preferences and of the scoring rule.
@@
 
-\commentOC{TODO Continue here.}
-Two phase method.
-Ask a predefined (non adaptive) sequence of questions in order to learn the weights $w$ of the scoring rule).
+\commentOC{TODO continue from here.}
+The \strat{Two phase} strategy asks a predefined, non adaptive sequence of questions in order to gather informations about the weights $w$ of the scoring rule. \commentOC{To check.}
 Then use minimax regret as in Lu and Boutilier.
 
-%\item Non-interleaved regret method: comparison with a method based on minimax regret, but not interleaved. 
-\medskip \noindent
-{\em Non-interleaved non-regret strategies (useful as benchmarks)}	
-	\begin{itemize}
-		\item Random strategy: randomly chooses an agent $i$ and a comparison query such that $x \pinc_i y$.
-		\item {\em Volumetric} strategy: chooses an agent $i$ and a query that maximizes the number of new pairwise preferences revealed given the worst response.
-	\end{itemize}
-
-% unless $\MMR=0$ we ask a question that reduce uncertainty
-
-\section{Empirical Evaluation} \label{sec:experiments}
+%\item {\em Volumetric} strategy: chooses an agent $i$ and a query that maximizes the number of new pairwise preferences revealed given the worst response.
+
+\section{Empirical Evaluation} 
+\label{sec:experiments}
 

### 2019-02-25 draft.tex
tiny changes

@@
 The pairwise max regret $\PMR(x,y;\pprofile,W)$ of $x$ relative to $y$ given partial profile $\pprofile$ and the set of weights $W$
-is the worst-case loss under all possible realizations of the full profile {\em and} all possible instantiations of the weights:
+is the worst-case loss of choosing $x$ instead of $y$ under all possible realizations of the full profile {\em and} all possible instantiations of the weights:
 \begin{align}
@@
 The optimal alternative w.r.t. minimax regret is the one with least max regret. 
-Notice that, whenever the PMR of an alternative $x$ (against some other alternative) exceeds the best MR value found so far, we don't need to further evaluate $x$. 
+Notice that, whenever the PMR of an alternative $x$ (against some other alternative) exceeds the best MR value found so far, we don't need to further evaluate $x$, as it can't be optimal. 
 This idea can be exploited further by adopting a minimax-search tree (see \cite{Braziunas2011}).

### 2019-02-25 draft.tex
tiny changes

@@
 To obtain upper bounds for $c'_t$, assume $c$ is ranked first by the $p+q$ agents voting in profile $P$.
-By our construction, the two times $\delta$ new agents of $P'$ give to $c$ the ranks $(3, m)$, or $(4, m-1)$, … Observe that the score of $c$ is maximal for attribution $(3, m)$, by convexity of the weights.
+By our construction, the  $2 \delta$ new agents of $P'$ give to $c$ the ranks $(3, m)$, or $(4, m-1)$, … Observe that the score of $c$ is maximal for attribution $(3, m)$, by convexity of the weights.
 Therefore, in the best case for $c$, $c'_1 ≤ p + q, c'_2 ≤ p+q, c'_t ≤ p+q+\delta \text{ for } 3 ≤ t < m, c'_m ≤ p+q+2\delta$.

### 2019-02-26 draft.tex
Experiments: reported some results

--- 2019-02-25 draft.tex
@@
-\newif\ifappendix
-%\appendixtrue %COMMENT to remove appendix % UNCOMMENT to add apendix
 \input{ijcai_preamble} 
@@
 \usepackage{newunicodechar}
+\newunicodechar{±}{\ensuremath{\pm}}
 \newunicodechar{⇒}{\implies}
@@
 
-The traditional approach to social choice assumes that both the social function and the full preference orderings of the voters are expressed beforehand. This represents two strong hypothesis.
-About the second one, requiring voters to express full preference orderings can be prohibitively costly (in term of cognitive and communication cost), especially for decisions with large sets of alternatives.
-This observation has motivated a number of recent works considering social choice with partial preference orders  \citep{Xia2008,Pini2009,Konczak05} and incremental elicitation \citep{Kalech2011, Lu2011, Naamani-Dery2015} of voters’ preferences.
+The traditional approach to social choice assumes that both the social function and the full preference orderings of the agents are expressed beforehand. This represents two strong hypothesis.
+About the second one, requiring agents to express full preference orderings can be prohibitively costly (in term of cognitive and communication cost), especially for decisions with large sets of alternatives.
+This observation has motivated a number of recent works considering social choice with partial preference orders \citep{Xia2008, Pini2009, Konczak05} and incremental elicitation \citep{Kalech2011, Lu2011, Naamani-Dery2015} of agents’ preferences.
 
@@
 The work of \citet{Cailloux2014} provides elicitation methods for a quite general class of rules based on weak orders.
-When considering positional scoring rules, several authors \citep{Stein1994, Llamazares2013, Viappiani2018} have worked on positional scoring rules with uncertain weights, assuming that the preferences of the voters are fully known.
+When considering positional scoring rules, several authors \citep{Stein1994, Llamazares2013, Viappiani2018} have worked on positional scoring rules with uncertain weights, assuming that the preferences of the agents are fully known.
 %it is possible to derive dominance relations (akin to stochastic dominance) that allow to eliminate some alternatives since they will be less preferred than another one for any instantiation of the weights \citep{Stein1994}.
@@
 In particular, our query strategies focus simultaneously on reduction of relevant preference and voting rule uncertainty.
-% the value of certain preference information is often not worth the cost of obtaining it.
-
-%In this paper we propose an interactive adaptive protocol for eliciting both the agents preferences and the voting rule.
-%At each step we need to decide whether we want to ask a question to the committee or to one of the agents (and to which agent in particular).
+
 The paper is organized as follows.
@@
 Among the many possible social choice functions, we consider {\em positional scoring rules (PSR)}, which attach weights to positions according to the vector $(w_1, \ldots, w_m)$ (also called the scoring vector).
-%A scoring rule associates each alternative to a score that is given by the sum of points obtained for each voter.
 An alternative obtains a score that depends on the rank obtained in each of the preference orders:
@@
 The winners are the alternatives with highest scores.
-%We assume that the weights constitute a monotonic sequence: $w_{1} \geq w_{2} \geq \ldots \geq w_{m}$.
 
 In this work we assume fixed, but unknown, a profile $\profile^*$ (and corresponding agents preferences $\pref_j^*$) and a weight vector $\w^*$, and we want to reason about partial preference information concerning those objects.
-Our knowledge at a given time of the preference of voter $j$ is encoded by a partial order over the alternatives, thus a transitive and asymmetric binary relation, denoted by $\ppref_j$. 
+Our knowledge at a given time of the preference of agent $j$ is encoded by a partial order over the alternatives, thus a transitive and asymmetric binary relation, denoted by $\ppref_j$. 
 In this work we assume that preference information is truthful, i.e. $a \ppref_j b ⇒ a \pref_j^* b$.
 We use $\pinc$ to denote incomparability, that is $a \pinc_{j} b$ iff $a \nppref_j b \wedge b \nppref_j a$.
-An incomplete profile $\pprofile = (\ppref_1, \ldots, \ppref_n)$ maps each voter to a partial preference.
+An incomplete profile $\pprofile = (\ppref_1, \ldots, \ppref_n)$ maps each agent to a partial preference.
 
@@
 Therefore the vector $(w_1,\ldots,w_m)$  is not known but we are given a set of constraints restraining the possible values that weights can take.
-We consider a decreasing sequence of weights\footnote{We assume all positions from $1$ to $m-1$ may contribute positively to the score of an alternative.
-The case where it is known that only the first $k<m-1$ positions matter can be easily dealt with by specifying $w_r = 0$ for $r > k$ as constraints.
-} \commentOC{It’s not clear to me that this is true…}:
-% If the chair considers that, for example, “only the first ten positions matter” (so that $w_r = 0$ for $r > 10$), then we simply assume the chair is able to express this constraint at the start of the querying process, thus, that this information is known, and approximate the problem by considering that it is only about the first ten alternatives, thus, set $m=10$.}
+We consider a decreasing sequence of weights:
 \begin{align}
@@
 Without loss of generality, we consider that $w_1=1$ and $w_m=0$.
-%\commentOC{I suggest we say no more than this to justify this assumption. Otherwise, we might say something like the following.
 
@@
 An important class of scoring rule is the one composed of weights that are a convex sequence \citep{Stein1994,Llamazares2016}, meaning that the difference between the weight of the first position and the weight of the second position is at least as great as the difference between the weights of the second and third positions, etc.
-%\begin{align} \forall r \in \{1,\ldots,m-2\} \;\; & w_r - w_{r+1} \geq w_{r+1}-w_{r+2}  \\
-%\iff & w_r - 2 w_{r+1} + w_{r+2} \geq 0 \label{eq:convexity}
-%\end{align}
 \begin{equation} 
@@
 \label{sec:mmr}
-
-%The quality of an alternative can be quantified by considering the maximum regret with respect to an adversary that can choose the instantiation of both a complete profile (extending the known preferences of the agents) and of the scoring vectors (associated to the preferences of the chair).
 In this paper, we consider a setting where both the agents' preferences and the preferences of the chair about the voting rule are incomplete.
@@
 
-\subsection{Computation of minimax regret}
+\paragraph{Computation of minimax regret}
 In order to compute pairwise maximum regret and therefore minimax regret, we adapt the reasoning from \citet{Lu2011} so that we decompose the $\PMR$ into the contributions associated to each agent.
@@
 Scoring rules are additively decomposable.
-%A scoring rule associates each alternative to a score that is given by the sum of points obtained for each voter.
+%A scoring rule associates each alternative to a score that is given by the sum of points obtained for each agent.
 Recall that when computing $s(x; \profile, \w)$, $w_{v_j(x)}$ is the number of points that $x$ obtains in the ranking $v_j$ (see Equation \ref{eq:srule}).
@@
 As we will show, this procedure can also be used in our case of uncertain weight vector.
-%in the case of convex scoring rules we will be able to greatly simplify the problem by decoupling the two maximizations.
 
@@
 There exists a completion $\hat{\profile} \in C(\pprofile)$ such that $\PMR(x,y; \pprofile, W) = \max_{\w \in W} [ s(y; \hat{\profile}, \w) - s(x; \hat{\profile}, \w) ]$ and such that the linear order $\hat{v}_{j}$ of each agent $j$ satisfies (\ref{eq:compl}).
-%There exists a completion ${\pref_j} \in C(\ppref_j)$ such that $\PMR(x,y; \pprofile, W) = \max_{\w \in W} \max_{\profile \in C(\pprofile), {\pref_j} \in \profile} [ s(y; \profile,\w) - s(x; \profile,\w) ]$ and that satisfies
 \end{claim}
-%In this claim, we abuse notation by writing ${\pref_j} \in \profile$ to mean that the preference ordering corresponding to agent $j$ in $\profile$ is $\pref_j$.
-It follows that $\hat{v}_{j}(x)$, the rank of $x$ in the PMR-maximizing linear order of voter $j$, %$\PMR(x,y; \pprofile, W)$ 
+It follows that $\hat{v}_{j}(x)$, the rank of $x$ in the PMR-maximizing linear order of agent $j$, 
 is $\hat{v}_{j}(x) = 1+\card{A}-\card{{\ppref_j}(x)}$, where ${\ppref_j}(x)$ designates the set of alternatives that are less good than $x$ according to $\ppref_j$, and the rank of $y$ is $\hat{v}_{j}(y)=1+\card{{\pprefinv_j}(y)}+\beta$, where $\beta = \card{A} - \card{{\ppref_j}(x)}$ if $(x \ppref_j y)$ and $\beta = 0$ otherwise.
@@
 
-%Let $U^+=\{ i \mid \ y \ppref_i x\}$ be the set of agents for which we know that $y$ is preferred to $x$ (positive contribution to pairwise regret), $U^-=\{ i \mid x \ppref_i y\}$ 
-%be the set of agents for wich we  know that $x$ is preferred to $y$ (negative contribution) and 
-%$U^?=\{ i \mid x \pinc_i y\}$ 
-%%$U^?=\{ i \mid x \nsucc_{i} y \wedge y \nsucc_{i} x \}$ 
-%the remaining case, where the preference between $x$ and $y$ is not known.
-%Consider how the adversary, whose goal is to maximize $\PMR$ between $x$ and $y$, will complete the partial orders:
-%\begin{itemize}
-% \item $j \in U^+$: If we know that agent $j$ prefers $y$ to $x$ then the contribution to $\PMR$ is positive and adversary will complete the partial order of agent $j$ by placing as many alternatives as possible between $y$ and $x$ (because of monotonicity of the weights).
-% The way the partial order is completed does not depend on the actual values of the weights.
-%
-% \item $j \in U^?$: If we do not know whether $x$ or $y$ is preferred by agent $j$ then the adversary will place $y$ before $x$ (since the goal is to maximize the difference in score between $y$ and $x$, and weights are monotone) in the linear order and this case reduce to the first one; therefore also in this case the completion of the partial order can be done independently of the choice of $w$.
-%
-% \item $j \in U^-$: If we know that agent $j$ prefers $x$ to $y$ then (as the contribution of this agent to $\PMR$ is negative) the adversary will place as few alternatives as possible between $x$ and $y$.
-%
-%The only issue is with respect to the  alternatives that are incomparable with $x$ and $y$ according to $\ppref_i$: should they be placed better than $x$ or worse than $y$ ?
-%If the scoring vector is known to be convex,  than these alternatives will be placed better than $x$ in the completion; otherwise the placements of these depend on the weights $\w$.
-%\end{itemize}
-%\subsubsection{Minimax regret computation}
-%Since weights are assumed to be convex, the adversary will place all alternatives $c$ that are such that $c \pinc_{j} y \wedge c \pinc_{j} x$ as better than $x$.
-%We now formalize the reasoning about the best (with respect to maximizing $\PMR$) completion with the following definition.
-%\begin{definition}
-%Given the partial profile $\pprofile$, define $\hat{\profile}$ as the completition of $\pprofile$ such that:
-%\begin{itemize}
-%\item For each $j \in U^{+}$, set   $\hat{\profile}$ as follows, for all $c \in A$:\\
-%if $c \pinc_{j} x$ we set $c \succ_{j}^{\hat{\profile}} x$;\\
-%if  $c \pinc_{j} y$ we set $y \succ_{j}^{\hat{\profile}} c$.
-%\item For each $j \in U^{?}$, set  $\hat{\profile}$ as follows:\\
-%$y \succ_{j}^{\hat{\profile}} x$;\\
-%for all $c \in A$, if   $c \pinc_{j} x$ we set $c \succ_{j}^{\hat{\profile}} x$;\\
-%for all $c \in A$, if   $c \pinc_{j} y$ we set $y \succ_{j}^{\hat{\profile}} c$.
-%\item For each $j \in U^{-}$,  set  $\hat{\profile}$ as follows, for all $c \in A$:\\
-%if $c \pinc_{j} x \wedge c \succ^{p}_{j} y$ we set $c \succ_{j}^{\hat{\profile}} x$;\\
-%if $c \pinc_{j} y \wedge  x \succ^{p}_{j} c$ we set $y \succ_{j}^{\hat{\profile}} c$;\\
-%if $c \pinc_{j} y \wedge c \pinc_{j} x$ we set $c \succ_{j}^{\hat{\profile}} x$.
-%\end{itemize}
-%\end{definition}
-
-%Given our hypothesis, for all pairs of alternatives, there exist completions of the partial preferences $\ppref$ that maximize the PMR and that do not depend on the weights. 
-%That is, we can exhibit, for each voter $j$, a completion $v_j$ such that $\forall \w, \forall v'_j \in C(\ppref_j): [w_{v_j(y)} - w_{v_j(x)}] \geq [w_{v'_j(y)} - w_{v'_j(x)}]$.
-
-%In summary, some best completion $\pref$ satisfies two properties: (1) for all $c \pinc x$, $c \pref x$; and (2) for all $c \pinc y$, if not $c \pref x \pref y$ then $y \pref c$. 
-%These two properties are intuitively understandable by observing that maximizing the PMR requires placing $x$ as low as possible, hence the first property; and $y$ as high as possible, hence the second property, with the exception that sometimes it is not possible to satisfy both goals and noting that the first goal is more important by convexity of the weights.
-%A proof that this reasoning is correct is in \cref{sec:prfCompl}.
-
 \begin{claim}
@@
 \PMR(x,y; \pprofile, W)  
-%\max_{w \in W} s(y; \hat{\profile}, \w) - s(y; \hat{\profile}, \w)\\
 & = \max_{w \in W} \sum_{j=1}^n w_{\hat{v}_j(y)} - w_{\hat{v}_j(x)} = \\ 
@@
 where the $\hat{\alpha}_{r}^{y}$ (resp. $\hat{\alpha}_{r}^{x}$)  is the number of times $y$ (resp. $x$) is at rank $r$ in the rankings of the completed profile $\hat{\profile}$.
-%$\hat{\alpha}_{i}^{x} = \sum_{j=1}^{n}  I[\hat{v}_{j}(x)=i]$ where $I$ is the indicator function.
 \end{claim}
-%\[ \alpha_{i} = \sum_{j=1}^{n}  I[\hat{v}_{j}(y)=i] - I[\hat{v}_{j}(x)=i]\]
-%We now show that the pairwise maximum regret can be computed with a linear program.
-%The PMR can be now computed by optimizing a linear program (LP). 
-%Constraints are on the feasible parameters (the weights of the scoring rules).
-The last proposition shows us that PMR is linear in the weights.
-We remind that the preferences of the chair are encoded with linear constraints $\Co_{W}$.
-% contraints represent the preferences $\Co_{W}$ of the chair about the scoring rule.
-The pairwise max regret $\PMR(x,y; \pprofile,W)$ can be obtained as the solution of the following linear program defined on the variables $w_1, …, w_m$ (weights attached to the different positions). 
+The last claim shows that PMR is linear in the weights.
+Recall that the preferences of the chair are encoded with linear constraints $\Co_{W}$.
+The pairwise max regret $\PMR(x,y; \pprofile,W)$ can be obtained as the solution of the following linear program defined on the variables $w_1, …, w_m$, the weights attached to the different positions.
 \begin{align*}
@@
 
-%Finally the minimax regret solution $\MMR(\pprofile, W)$ is determined by solving a sequence of pairwise max regret computations, solving the above linear program for every different pair $(x,y) \in A^{2}$.
 The max regret $\MR(x; \pprofile, W)$ is determined by considering the pairwise regret of $x$ with each other alternative in $A$.
-The optimal alternative w.r.t. minimax regret is the one with least max regret. 
+Optimal alternatives w.r.t. minimax regret are the ones with least max regret. 
 Notice that, whenever the PMR of an alternative $x$ (against some other alternative) exceeds the best MR value found so far, we don't need to further evaluate $x$. 
-This idea can be exploited further by adopting a minimax-search tree (see \cite{Braziunas2011}).
-%The computation can be made faster by adopting an efficient scheme of evaluation of PMR where .
+This idea can be exploited further by adopting a minimax-search tree \citep{Braziunas2011}.
 
@@
 The goal is to acquire relevant information to reduce minimax regret as quickly as possible.
-%Minimax regret can be used to guide the elicitation process.
 As termination condition of elicitation, we can check whether minimax regret is lower than a threshold; if we wish optimality, we can perform elicitation until minimax regret drops to zero.
@@
 
-%Type of questions that we can ask to the chair:	bound queries (Is this alternative among your top-k most preferred items?), comparison queries (do you prefer alternative x or alternative y?).
-% we discuss the different forms of queries and develop several query strategies 
 \paragraph{Question types}
@@
 As {\em questions asked to the agents} it is natural to consider comparison queries asking to compare two alternatives.
-%Another common type of queries are {\em top-k}, asking to each voter her $k$ most preferred alternatives.
+%Another common type of queries are {\em top-k}, asking to each agent her $k$ most preferred alternatives.
 The effect of a response to a question asked to an agent is to increase our knowledge about the agents rankings, thus augmenting the partial profile $\pprofile$. 
-If voter $j$ answers a comparison query stating that alternative $a$ is preferred to $b$, then the partial order $\ppref_j$ is augmented with $a \ppref_j b$ and by transitive closure.
+If agent $j$ answers a comparison query stating that alternative $a$ is preferred to $b$, then the partial order $\ppref_j$ is augmented with $a \ppref_j b$ and by transitive closure.
 
@@
 However, we still need to complete the profile, thus, come up with other $m-2$ alternatives defined so that each agent in the resulting profile has placed exactly one alternative in each rank. 
-And we must ensure, doing this, that these other alternatives are not better than $a$ or $b$.\footnote{Because, if the chair picks a different alternative $c$, it tells us that the chair prefers $c$ to both $a$ and $b$,
-%but it generally does not  answer the question we are interested in
-but in general we do not acquire the type of constraints we are interested in.} 
+And we must ensure, doing this, that these other alternatives are not better than $a$ or $b$: if the chair picks a different alternative $c$, it tells us that the chair prefers $c$ to both $a$ and $b$,
+but it generally does not  answer the question we are interested in. 
 Taking $p = q = 1$, $m=4$, $r=2$, we see that such a completion may be impossible. Luckily, this problem can be worked around, at the price of increasing the number of agents.
 
-First build a temporary profile $P$ of $p+q$ voters with $a$ and $b$ ranked as just described.
-Complete it with $m-2$ alternatives ranked in arbitrary orders so that the resulting profile has complete strict rankings for each of the $p+q$ voter.
-Now we will make the other alternatives as bad as desired by adding voters to $P$ that appreciate $a$ and $b$ more than the other alternatives, thus building a profile $P'$ in which, whatever the weights, $c$ may not have a better score than $a$.
-Observe that if we add $\delta$ voters (with $\delta$ a natural number) that put $a$ at first rank and $b$ at second rank, and $\delta$ voters that put $b$ at first rank and $a$ at second rank, we do not change the difference of the scores of $a$ and $b$, and thus, observing the chair choosing $a$ or $b$ still answers the question.
+First build a temporary profile $P$ of $p+q$ agents with $a$ and $b$ ranked as just described.
+Complete it with $m-2$ alternatives ranked in arbitrary orders so that the resulting profile has complete strict rankings for each of the $p+q$ agent.
+Now we will make the other alternatives as bad as desired by adding agents to $P$ that appreciate $a$ and $b$ more than the other alternatives, thus building a profile $P'$ in which, whatever the weights, $c$ may not have a better score than $a$.
+Observe that if we add $\delta$ agents (with $\delta$ a natural number) that put $a$ at first rank and $b$ at second rank, and $\delta$ agents that put $b$ at first rank and $a$ at second rank, we do not change the difference of the scores of $a$ and $b$, and thus, observing the chair choosing $a$ or $b$ still answers the question.
 Choose arbitrarily a matching of the remaining $m-2$ alternatives to the ranks $3$ to $m$, say, $c \mapsto 3$, $d \mapsto 4$, and so on.
-The first $\delta$ supplementary voters, who rank $a$ first and $b$ second, rank the other alternatives as the just defined mapping suggests.
-The other $\delta$ supplementary voters, who rank $b$ first and $a$ second, use the opposite ranking for the remaining alternatives, say, $c \mapsto m$, $d \mapsto m-1$, and so on.
+The first $\delta$ supplementary agents, who rank $a$ first and $b$ second, rank the other alternatives as the just defined mapping suggests.
+The other $\delta$ supplementary agents, who rank $b$ first and $a$ second, use the opposite ranking for the remaining alternatives, say, $c \mapsto m$, $d \mapsto m-1$, and so on.
 We can now prove that, for $\delta = p+q$, and whatever the weight vector $\w \in \W$, no alternative, except possibly $b$, has a better score than $a$.
@@
 \end{claim}
-\commentOC{Plz others check this.} At this stage, we are content that a procedure exists to transform our abstract questions to questions about winners of a PSR.
+At this stage, we are content that a procedure exists to transform our abstract questions to questions about winners of a PSR.
 Further studies would investigate, for example, what is lost in terms of elicitation efficiency when we are forced to restrain to realistic concrete questions, meaning, questions involving small profiles; or investigate the relationship between our understanding of scores as (cardinal) utility and (ordinal) scores as definition of a PSR.
-
-%\commentOC{I suppose we have, unfortunately, to get rid of this useful example, for reason of space.
-(If we manage to keep it, I’ll need to rework it a bit so that it follows the strategy in the proof.)}
-\begin{example}
-Suppose our query strategy suggests us to ask the chair the following query: $w_{2} - w_{3} \geq 2(w_{3} - w_{4})$.
-In order to impose this constraints,
-It is straightforward to see that we want the  chair of the committee to choose between $a$ or $b$ with the following rank distribution:
-\[
-\begin{array}{ccccc}
-& 1^\circ
-& 2^\circ
-& 3^\circ
-& 4^\circ \\
-\cmidrule{2-5}
-a & 0& 1& 0& 2 \\
-b& 0& 0& 3& 0 \\
-\end{array}
-\]
-In order to obtain a valid profile, we need to include a number of other alternatives in such a way that the are dominated by $a$ and $b$.
-The following profile is exactly what we want,
-%We add agents in order to increase the number of times $a$ and $b$ are ranked at first position.
-Please note we must maintain these scheme, so every add of a position to the ranking of $a$ must correspond to the same in the ranking of $b$.
-
-\[
-\begin{array}{cccccc}
-v_1& v_2& v_3 & v_4& v_5& v_6 \\
-\midrule 
-a& b& c & d& a& b \\
-c& a& d& c& b& a \\
-b& d& b& b& d& c \\
-d& c& a& a& c& d \\
-\end{array}
-\]
-giving the following rank distribution (number of times each alternatives is ranked first, second, etc): 
-\[
-\begin{array}{ccccc}
-& 1^\circ& 2^\circ& 3^\circ& 4^\circ \\
-\cmidrule{2-5}
-a & 2& 2& 0& 2 \\
-b& 2& 1& 3& 0 \\
-c& 1& 2& 1& 2 \\
-d& 1& 1& 2& 2 \\
-\end{array}
-\]
-Indeed alternative $c$ and $d$ are dominated and they cannot win for any instantiation of the weights; this can be seen by comparing the cumulative ranks (see  \citep{Stein1994}).
-\[
-\begin{array}{ccccc}
-& \geq 1^\circ
-& \geq 2^\circ
-& \geq 3^\circ
-& \geq 4^\circ \\
-\cmidrule{2-5}
-a & 2 & 4& 4& 6 \\
-b & 2 & 3& 6& 6 \\
-c& 1& 3& 4& 6 \\
-d& 1& 2& 4& 6 \\
-\end{array}
-\]
-\end{example}
 
@@
 Among them, the \strat{Random} strategy is used to capture how hard an elicitation problem is, by giving us a baseline: using it we can estimate how fast the regret diminishes when we ask questions randomly.
-%It also estimates how much information of that kind we would need if we assume the information would not be elicited experimentally using an active learning approach, but would be collected empirically as they randomly appear to us.
-(This estimate is however very rough as it is most relevant only when the observations follow the same random distribution as the one we chose.)
 Choosing the questions purely randomly however, that is, independently of what we know already, would be pointless, as we would most of the time ask questions we already know the answer of.
@@
 The intervals are initialized to $[1, n]$.
-If it opted for a question to agents, it draws equiprobably among the voters whose preference is not known entirely; picks an alternative $a$ randomly with equal probability among those involved in some incomparabilities in $\ppref_j$; and picks an alternative $b$ with equal probability among those incomparable with $a$ in $\ppref_j$.
-
-We also define the \strat{Extreme completions} strategy \commentOC{Previously called Current solution}, which we consider as a more realistic baseline. 
+If it opted for a question to agents, it draws equiprobably among the agents whose preference is not known entirely; picks an alternative $a$ randomly with equal probability among those involved in some incomparabilities in $\ppref_j$; and picks an alternative $b$ with equal probability among those incomparable with $a$ in $\ppref_j$.
+
+% In the code, called Current solution
+We also define the \strat{Extreme completions} strategy, which we consider as a more realistic baseline. 
 Consider the solution of the minimax regret game, 
  $(x^{*},\bar{y},\bar{\profile},\bar{\w})$, where $x^{*}$ is the minimax regret optimal alternative, and $\bar{y} = \arg \max_{y \in A} \PMR(x,y; \pprofile, W)$, $\bar{\profile}$ and $\bar{\w}$ are the adversarial choices, thus, the instantiations that, given the choice of $x^*$, maximize the regret.
-%\footnote{ $\bar{\profile} \!=\!
-\arg \max_{\profile \in C(\pprofile)} s(y; \profile, \bar{\w}) \!-\!
-s(x; \profile, \bar{\w})$; and $\bar{\w} \!=\!
-\arg \max_{w \in W} s(y; \pprofile, w) \!-\!
-s(x; \pprofile, w)$ .}
 Define: 
@@
 Therefore, whenever $\tau_{1} < \tau_{2}$ we ask a question to the chair, and compare componentwise $\bar{\w}$ and $\w^{\tau}$, the argmax of Eq.
-(\ref{eq:tau1}), to find the position $r$ that is most valuable to ask about (the one that maximizes $\abs{\bar{\w}_r - \w^{\tau}_r}$).
-Instead, if $\tau_{1} > \tau_{2}$ we ask a question to one of the agent, picking the alternative randomly as described above.
-\commentOC{We’d better check for each $j$ the difference between the difference of the ranks of $x$ and $y$ in the worst $v$ and in the best $v$ and pick a voter related to highest difference, pick $x$ or $y$ with $1/2$ chances, and pick an incomparable alternative equiprobably.}
+(\ref{eq:tau1}), to find the position $r$ that is most valuable to ask about (the one that maximizes $\abs{\bar{\w}_r - \w^{\tau}_r}$), and choose $\lambda$ as the middle of the interval of possible values for that rank.
+Instead, if $\tau_{1} > \tau_{2}$ we ask a question to one of the agent.
+We select the question by checking for each agent $j$ the difference between the difference of the ranks of $x$ and $y$ in the profile that minimizes compared to the one that maximizes the difference of scores, and pick an agent related to the highest difference, then pick $x$ or $y$ with $1/2$ chances as the first alternative of the question, and pick an incomparable alternative equiprobably as the second one.
 
@@
 Note that other aggregators than $\max$ can be used as well.
-The \strat{Pessimistic} strategy considers as possible questions the ones defined by the \strat{Random} strategy \commentOC{To check}.
+The \strat{Pessimistic} strategy considers as possible questions the ones defined by the \strat{Random} strategy (with the difference that a threshold is used: if for some rank $r$ the interval of possible values for $\lambda$ is not larger than $0.1$, the question is not considered).
 It uses a variant of the $\max$ as an aggregator: if the maximal $\MMR$ of two questions are equal, it prefers the question that has the lowest $\MMR$.
@@
 
-\commentOC{TODO continue from here.}
-The \strat{Two phase} strategy asks a predefined, non adaptive sequence of questions in order to gather informations about the weights $w$ of the scoring rule. \commentOC{To check.}
-Then use minimax regret as in Lu and Boutilier.
+The \strat{Two phase} strategy asks a predefined, non adaptive sequence of $m-2$ questions in order to gather informations about the weights $\w$ of the scoring rule, using one question per rank (except the extreme ones) as defined in the other strategies, thus, each cutting the initial interval of possibilities into two equal parts.
+Then it only asks questions about the voters, using questions as defined in the \strat{Pessimistic} strategy.
+%TODO Then use minimax regret as in Lu and Boutilier. check what’s this.
 
@@
 
-{\em {\bf TODO:} update with actual experiments}
-
-\begin{figure}[t]
-\begin{center}PLACEHOLDER\end{center}
-\vspace{3.5cm}
-\caption{Minimax regret reduction in our experiments (synthetic dataset).}
-\end{figure}
-
-\begin{figure}[t]
-\begin{center}PLACEHOLDER\end{center}
-\vspace{3.5cm}
-\caption{Minimax regret reduction in our experiments (real dataset).}
-\end{figure}
-
-% We can stop elicitation when minimax regret is sufficiently small.
-We test the elicitation protocols in randomly generated datasets and real datasets. % (sushi and iris).
-We evaluate the proposed method using the following simulated protocol.
-Our goal is to 
- to verify our intuition that an interleaved elicitation approach (mixing questions to the chair and questions asked to the agents) is more efficient than performing the elicitation of the rule first and than eliciting the agents preferences.
-First of all, we randomly generate the true preferences of the users (i.e. the linear orders) and the weights associated with the chair's scoring rule.
-For each of the elicitation strategy, we simulate an elicitation session.
-%Queries are posed to simulated users, that answer accor
-%We compare the performance  of the different strategies of Section \ref{sec:elicit} with respect to decrement in max regret and with respect to the real loss.
-We measure the effectiveness of our strategies of Section \ref{sec:elicit} by examining regret reduction as a function of the number of queries.
-
-%For each of the elicitation strategy, we simulate the elicitation by asking the queries selected by the strategy.
-We performed tests with different values of $m$ (number of alternatives) and $n$ (number of agents); test with different population sizes, different number of alternatives, etc.
-
-We experimented with both settings that assume a convex sequences of weights, and others without this assumption.
-
-{\em {\bf TODO:} say something about computation times}
-
-%Comparison between our interleaved strategy and a strategy, still based on minimax regret  but that is not interleaved; also compare to some heuristic baselines.
-
-\section{Conclusions}  \label{sec:conclusions}
-In this paper we have considered a  social choice setting with partial  information about the voter's  
+\begin{table}
+	\begin{center}
+		\begin{tabular}{rr@{ ± }lr@{ ± }lr@{ ± }l}
+			\toprule
+			k & Random & sd & Two phases & sd & Pess & sd \\
+			\midrule
+			0 & 4.0 & 0 & 4.0 & 0 & 4.0 & 0\\
+			5 & 3.40 & 0.40 & 3.86 & 0.13 & 2.63 & 0.28\\
+			10 & 2.59 & 0.75 & 2.63 & 0.39 & 1.29 & 0.50\\
+			15 & 2.37 & 0.33 & 0.92 & 0.76 & 0.43 & 0.50\\
+			20 & 1.23 & 1.04 & 0.15 & 0.23 & 0.09 & 0.27\\
+			25 & 0.90 & 0.80 & 0 & 0 & 0.25 & 0.75 \\
+			30 & 0.34 & 0.57 & 0.02 & 0 & 0 & 0\\
+			\bottomrule
+		\end{tabular}
+	\end{center}
+	\caption{Minimax regret in problems of size $(4, 4)$ after $k$ questions.}
+	\label{fig:xp1}
+\end{table}
+
+\begin{table}
+	\begin{center}
+		\begin{tabular}{rr@{ ± }lr@{ ± }lr@{ ± }l}
+			\toprule
+			k & Random & sd & Two phases & sd & Pess & sd \\
+			\midrule
+			0 & 5.0 & 0 & 5.0 & 0 & 5.0 & 0\\
+			5 & 4.93 & 0.16 & 4.98 & 0.01 & 4.15 & 0.32\\
+			10 & 4.84 & 0.22 & 4.35 & 0.28 & 3.44 & 0.46\\
+			15 & 4.28 & 0.58 & 3.70 & 0.25 & 2.66 &0.54 \\
+			20 & 3.85 & 0.33 & 2.67 & 0.51 & 1.62 & 0.82\\
+			25 & 3.50 & 0.78 & 2.17 & 0.66 & 0.84 &  0.57\\
+			30 & 2.96 & 0.80 & 1.47 & 1.10 & 0.53 & 0.70\\
+			\bottomrule
+		\end{tabular}
+	\end{center}
+	\caption{Minimax regret in problems of size $(5, 5)$ after $k$ questions.}
+	\label{fig:xp2}
+\end{table}
+
+\begin{table}
+	\begin{center}
+		\begin{tabular}{rr@{ ± }lr@{ ± }lr@{ ± }l}
+			\toprule
+			k & Random & sd & Two phases & sd & Pess & sd \\
+			\midrule
+			0 & 6.0 &  &  &  &  & \\
+			5 &  &  &  &  &  & \\
+			10 &  &  &  &  &  & \\
+			15 &  &  &  &  &  & \\
+			20 &  &  &  &  &  & \\
+			25 &  &  &  &  &  &  \\
+			30 &  &  &  &  &  & \\
+			\bottomrule
+		\end{tabular}
+	\end{center}
+	\caption{Minimax regret in problems of size $(6, 6)$ after $k$ questions.}
+	\label{fig:xp3}
+\end{table}
+
+We test the elicitation protocols in randomly generated datasets. %TODO and real datasets. (sushi and iris).
+Our goal is to see how much we gain with an interleaved elicitation approach mixing questions to the chair and questions asked to the agents compared to performing a partial elicitation of the rule first and then eliciting the agents preferences.
+We also want to see how realistic our approach is for various problem sizes, by estimating the number of questions we would have to ask before being able to reduce the worst regret significantly.
+
+We use the following protocol.
+Having picked a problem size $(m, n)$, a number of questions $k$ and a strategy, we randomly generate an “oracle”, containing the true preferences of the agents (i.e.
+the linear orders) and the weights associated with the chair's scoring rule.
+We start with empty knowledge ($\pprofile = (\emptyset_j), W = \W$) about the preference orderings of the agents or the weight differences favored by the chair.
+We obtain the first question to be asked using the selected strategy, as described above.
+We use the oracle to answer the question and update our knowledge, which is thus used to obtain the next question.
+This is repeated until $k$ answers have been obtained.
+Then we compute the resulting $\MMR$.
+We repeat this whole experiment 10 times, for a given $(m, n, k)$, and report the average resulting $\MMR$ and the standard deviation.
+
+The results are displayed in \cref{fig:xp1,fig:xp2,fig:xp3}. In these tables, the strategies are designated by Rnd for Random, Two ph. for Two phases, and Pess. for Pessimistic.
+
+\section{Conclusions}  
+\label{sec:conclusions}
+In this paper we have considered a  social choice setting with partial  information about the agent's  
 preferences and as well a partially specified voting rule.
@@
 Our experimental results %on randomly generated and real world data sets 
-show that regret-based elicitation is effective and allow to quickly find a near-optimal consensus choice.
+suggest that regret-based elicitation is effective and allow to quickly reduce worst regret significantly.
 %Regret-based elicitation allows to determine near-optimal winners using only few information about the agents' preferences.
 
-We mention some  important directions for future works.
-First of all, further development of elicitation strategies, considering alternative heuristics, is an important direction. 
-Second, we are interested in extending elicitation of voting rules going beyond scoring rules.
-A third direction is that of considering probabilistic methods for elicitation.
-Finally, we are interested in studying the effect of strategic agents. %that may not report their true preferences.
-% distribution-free heuristics
-
+%As part of the contribution of this work, we publish an open-source library that allows to reproduce our experiments and more, at https://github.com/…
+
+We mention some directions for future works.
+Further development of elicitation strategies, considering alternative heuristics, is an important direction. 
+Second, elicitation could be extended to voting rules beyond scoring rules.
+Finally, an important direction of extension aims at studying how to elicit preferences while restraining to concrete and easy questions.
 % Acknowledgements: We thank the reviewers for comments helping to improve the paper. 
@@
 %}
-
-\pagebreak
-\ifappendix
+\end{document}
+
 \appendix
@@
 Indeed, the construction of $\PMR(x,y,\pprofile,\w)$ can be viewed as an adversary's attempt to maximize the regret of choosing $x$ instead of $y$.
-For doing this, he can choose a completion $\profile_i \in C(\pprofile_i)$ of the partial profile and a (feasible) scoring vector $\w$ that maximize the contribution of the voter $i$ to $\PMR(x,y,\pprofile,\w)$.
+For doing this, he can choose a completion $\profile_i \in C(\pprofile_i)$ of the partial profile and a (feasible) scoring vector $\w$ that maximize the contribution of the agent $i$ to $\PMR(x,y,\pprofile,\w)$.
 Let us now analyze how it could be done depending on the relation between alternatives $x$ and $y$ in $\pprofile_i$.
@@
 
-%\subsection{Profile completion, again}
-% %{\bf \em TODO: still have to find out exactly how to do it}
-% 
-% We introduce a set integer variables $I^i$, one for each position $i$.
-% Let $U^j$ be, for the agents in $U^-$, the alternatives that, in the partial order $\succ^p_j$ of some agent $j \in U^-$, are incomparable with $x$ and $y$.
-% \[ \sum_{l=1}^n I^j_l w_l \]
-% Variable $I^j$ associated with the constraint $0 \leq I \leq |U^j|$.
-% 
-% We provide the following MIP (mixed integer linear program).
-% 
-%% Use linearization techniques to handle the multiplications...
-%
-%
-%%\section{Even more fun}
-%%We can consider different types of questions: asking to compare a pair of alternatives, asking about top-k alternatives.
-%
-
 \section{Minimax regret without the convex assumption}
@@
 In addition to variables $\{ w_{j} \}_{j=1,\ldots,m}$ (one for each position) we need to employ several additional decision variables.
-We introduce two sets of binary variables $B^{+}_{i,j}$ and $B^{-}_{i,j}$  for each position $i$ and for each voter $j$.
+We introduce two sets of binary variables $B^{+}_{i,j}$ and $B^{-}_{i,j}$  for each position $i$ and for each agent $j$.
 Variable $B_{i,j}^{+}$ encodes the fact that the alternative $y$ is placed in position $i$ in the ranking of agent $j$; while  $B_{i,j}^{-}$ encodes the same thing for alternative $x$.
@@
 %\end{claim}
-
-\section{Proof of completion}
-\label{sec:prfCompl}
-Given $w$ and ${\pref} \in C(\ppref)$, let $w[\pref]$ denote $w_{|\pref(y)|} - w_{|\pref(x)|}$. \commentOC{Changing the notation to slightly reduce the number of symbols, to be discussed.}
-
-Given ${\pref} \in C(\ppref)$, define $\pref^1$ as $\pref$ except that the elements in $C = \{c \pinc x \land x \pref c\}$ come just above $x$ in $\pref^1$, respecting in $\pref^1$ their internal ordering in $\pref$.
-We show first that $\pref^1$ is an element of $C(\ppref)$; and second that $\forall w: w[\pref^1] \geq w[\pref]$.
-
-First, it is an element of $C(\ppref)$ as it does not contradict $\ppref$.
-To show this, recall first that $\pref$ does not contradict $\ppref$.
-Left to show is that $\forall c \in C, d \notin C: x \pref d \pref c \Rightarrow d \pinc c$ (thus any element $d$ whose relation with $c$ has changed from $\pref$ to $\pref^1$ were incomparable with $c$ in $\ppref$).
-Consider any such pair $c, d$.
-As $d \notin C$, $\lnot(d \pinc x)$ or $d \pref x$.
-From the hypothesis, $d \pref x$ is excluded.
-As $\pref$ extends $\ppref$, $\lnot(d \ppref x)$ and $\lnot (c \ppref d)$.
-Because $\lnot (d \pinc x)$, $x \ppref d$.
-Thus, $\lnot (d \ppref c)$, otherwise by transitivity $x \ppref c$.
-The conclusion now follows from $\lnot (c \ppref d)$ and $\lnot (d \ppref c)$.
-
-Second, in $\pref^1$, compared to $\pref$, $x$ is $|C|$ positions lower, and $y$ is at most $|C|$ positions lower, depending on where $y$ was in $\pref$.
-Hence, by convexity of the weights, $w[\pref^1] \geq w[\pref]$.
-
-Now define $\pref^2$ as $\pref^1$ except that the elements from $C' = \{c \pinc y \land \lnot (c \pref^1 x \pref^1 y) \land c \pref^1 y\}$ move just below $y$, respecting in $\pref^2$ their internal ordering in $\pref^1$.
-Observe that this move keeps property (1), that was satisfied by construction in $\pref^1$, intact, and satisfies property (2).
-The rest of the reasoning is similar to the previous move, as the situations are symmetric.
-(To be checked?) Hence, ${\pref^2} \in C(\pref)$ and it satisfies both properties.
-
-Given any $x, y, w$, as $C(\pref)$ has an element maximizing $w[.]$ (by finiteness of the set), the above reasoning shows that some element in $C(\pref)$ satisfies both properties and maximizes $w[.]$.
-And any element in $C(\pref)$ satisfying both properties attribute the same positions to $x$ and $y$, thus, maximizes $w[.]$.
 

### 2019-02-26 draft.tex

@@
 
-%TODO remove this before submission
-	\tolerance=2000
-	%Accept overfull hbox up to...
-	\hfuzz=1cm
-	%Reduces verbosity about the bad line breaks.
-	\hbadness 10000
-	%Reduces verbosity about the underful vboxes.
-	\vbadness=10000
+%	\tolerance=2000
+%	%Accept overfull hbox up to...
+%	\hfuzz=1cm
+%	%Reduces verbosity about the bad line breaks.
+%	\hbadness 10000
+%	%Reduces verbosity about the underful vboxes.
+%	\vbadness=10000
 
@@
 Optimal alternatives w.r.t. minimax regret are the ones with least max regret. 
-Notice that, whenever the PMR of an alternative $x$ (against some other alternative) exceeds the best MR value found so far, we don't need to further evaluate $x$. 
+Notice that, whenever the PMR of an alternative $x$ (against some other alternative) exceeds the best MR value found so far, we don't need to further evaluate $x$, as it can't be optimal. 
 This idea can be exploited further by adopting a minimax-search tree \citep{Braziunas2011}.
@@
 			\toprule
-			k & Random & sd & Two phases & sd & Pess & sd \\
+			k & Rnd & sd & Two ph. & sd & Pess. & sd \\
 			\midrule
@@
 
-We test the elicitation protocols in randomly generated datasets. %TODO and real datasets. (sushi and iris).
+We test our strategies using randomly generated datasets. %TODO and real datasets. (sushi and iris).
 Our goal is to see how much we gain with an interleaved elicitation approach mixing questions to the chair and questions asked to the agents compared to performing a partial elicitation of the rule first and then eliciting the agents preferences.

### 2019-02-26 draft.tex
Better tables

@@
 \usepackage{newunicodechar}
-\newunicodechar{±}{\ensuremath{\pm}}
+\usepackage{textcomp}
 \newunicodechar{⇒}{\implies}
@@
 \usepackage{natbib}
+\usepackage[strict]{siunitx}
 \usepackage{hyperref}
@@
 
+\sisetup{round-mode=places, round-precision=1, table-figures-integer=1, table-figures-decimal=1}
 \begin{table}
 	\begin{center}
-		\begin{tabular}{rr@{ ± }lr@{ ± }lr@{ ± }l}
+		\begin{tabular}{S[table-figures-integer=2, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
 			\toprule
-			k & Rnd & sd & Two ph. & sd & Pess. & sd \\
+			{k} & {Rnd} & {sd} & {T. ph.} & {sd} & {Pes.} & {sd} & {Pes.} & {sd} \\
 			\midrule
-			0 & 4.0 & 0 & 4.0 & 0 & 4.0 & 0\\
-			5 & 3.40 & 0.40 & 3.86 & 0.13 & 2.63 & 0.28\\
+			0 & 4.0 & 0 & 4.0 & 0 & 4.0 & 0 & 4.0 & 0\\
+			5 & 3.40 & 0.40 & 3.86 & 0.13 & 2.63 & 0.28 & 2.63 & 0.28\\
 			10 & 2.59 & 0.75 & 2.63 & 0.39 & 1.29 & 0.50\\
@@
 	\begin{center}
-		\begin{tabular}{rr@{ ± }lr@{ ± }lr@{ ± }l}
+		\begin{tabular}{S[table-figures-integer=2, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
 			\toprule
-			k & Rnd & sd & Two ph. & sd & Pess. & sd \\
+			{k} & {Rnd} & {sd} & {T. ph.} & {sd} & {Pes.} & {sd} & {Pes.} & {sd} \\
 			\midrule
@@
 
-The results are displayed in \cref{fig:xp1,fig:xp2,fig:xp3}. In these tables, the strategies are designated by Rnd for Random, Two ph. for Two phases, and Pess. for Pessimistic.
+The results are displayed in \cref{fig:xp1,fig:xp2,fig:xp3}.
+In these tables, the strategies are designated by Rnd for Random, T.
+ph.
+for Two phases, EC for Extreme completions, and Pes.
+for Pessimistic.
 

### 2019-03-29 RJCIA2019/Style_articles_PFIA2019/latex/latex2018.tex
RJCIA2019

%%%% patron de format latex pour rfia 2000.
%%%% sans garanties. Plaintes \`a envoyer \`a \dev\null.
%%%% deux colonnes pas de num\'erotation et 10 points
%%%% necessite les fichiers a4.sty french.sty et rfia2000.sty

%%%% Pour \LaTeXe
\documentclass[a4paper,twoside,french]{article}
\usepackage{rfia2000}
\usepackage[T1]{fontenc}
\usepackage{babel}
\usepackage{times}

%%%% Pour \LaTeXe sans babel
%%%% \documentclass[a4paper,twoside]{article}
%%%% \usepackage{rfia2000}
%%%% \usepackage{french}
%%%% \usepackage{times}

%%%% Pour \LaTeX remplacer les trois ligne pr\'ec\'edente par les deux
%%%% suivantes
%%%%\documentstyle[a4,french]{article}
%%%%\input{rfia2000}

\begin{document}
%%%%%Pas de date
\date{}
%%%%% Titre gras 14 points
\title{\Large\bf Mon  article pour IC'2018
       }
%%%%% Si auteur unique
%\author{L. Auteur \\
%%  Son institut \\
%%  Son addresse \\
%%  Son email}
%%%% pour deux auteurs
\author{\begin{tabular}[t]{c@{\extracolsep{8em}}c}
%%%% pour trois auteurs
%%%%\author{\begin{tabular}[t]{c@{\extracolsep{6em}}c@{\extracolsep{6em}}c}
%%%% pour quatre auteurs
%%%%\author{\begin{tabular}[t]{c@{\extracolsep{4em}}c@{\extracolsep{4em}}c@{\extracolsep{4em}}c}
%%%%pour plus d\'ebrouillez-vous !
M. Oim\^eme${}^1$  & M. Oncopain${}^2$ \\
\end{tabular}
{} \\
 \\
${}^1$        Mon Institut   \\
${}^2$        Son Institut
{} \\
 \\
%Mon adresse compl\`ete \\
Mon adresse \'electronique\\
%{\bf Domaine principal de recherche}: RFP ou IA\\
%{\bf Papier soumis dans le cadre de la journée commune}: OUI ou NON
}
\maketitle
%%%%  Pas de num\'erotation sur la page de titre
\thispagestyle{empty}
\subsection*{R\'esum\'e}
{\em
C'est mon r\'esum\'e. Il doit occuper quelques centim\`etres (moins de 10)
y compris son titre qui est en 12 points gras.
}
\subsection*{Mots Clef}
Exemple type, format, modele.

\subsection*{Abstract}
{\em
It's the English version of the abstract. Exactly as in French it must
be short. It must speak of the same topics...
}
\subsection*{Keywords}
Example, model, template.

\section{Introduction}
Le contenu de l'article peut \^etre r\'edig\'e avec n'importe quel formateur
ou traitement de texte, pourvu qu'il r\'eponde aux crit\`eres de
pr\'esentation donn\'es ici. L'objectif vis\'e est de proposer une unit\'e
de pr\'esentation des actes, et nous vous invitons \`a tenter de respecter
ce mod\`ele autant que le permet votre logiciel favori.

Pour les auteurs utilisant \LaTeX\, le fichier source de ce
texte (\verb|latex.tex|) est lui-m\^eme une base pour obtenir une
sortie conforme avec \LaTeXe\footnote{ou \LaTeX}.

Les autres trouveront des renseignements (peut-\^etre) plus lisibles
pour eux dans le fichier \verb|word.doc| (Word).

Un fichier PDF contient \'egalement la d\'efinition compl\`ete de la
pagination. Il a pour nom \verb|pages.pdf| et est cliquable sur la page
Web.

La base du texte est du Times-Roman 10 points pr\'esent\'e en deux colonnes.
La s\'eparation inter-colonne est de 1 cm.

Le titre principal est en 14 points gras (28 points = 1cm).

Dans les sections, le titre est en 12 points gras.
Les paragraphes ne sont pas decal\'es.

Les sous-sections num\'erot\'ees comme suit~:
\subsection{Travaux ant\'erieurs}
Les en-t\^etes sont \'egalement en 12 points gras.

Il n'y a pas n\'ecessairement d'espacement entre les paragraphes.

Les r\'ef\'erences \`a la Bibliographie peuvent \^etre de la forme
 \cite{key:foo} o\`u \cite{foo:baz}.  Les num\'eros correspondent \`a
 l'ordre d'apparition dans la bibliographie, pas dans le texte.
 L'ordre alphab\'etique est conseill\'e.

\section{Le coin \LaTeX}
Pour les utilisateurs de \LaTeX,
ce patron est minimaliste et vous aurez besoin de votre manuel \LaTeX
pour ins\'erer \'equations et images.

Pour les images le << paquet >> \verb|graphicx| est tr\`es bien.

Les fichiers de style n\'ecessaires pour la compilation \LaTeX\ sont :
\begin{itemize}
  \item \verb|a4.sty|  (pour \LaTeX, mais pas \LaTeXe)
  \item \verb|french.sty| (ou Babel fran\c{c}ais)
  \item \verb|rfia2000.sty|
\end{itemize}
Vous devriez avoir les deux premiers dans votre instalation de
\LaTeX. Le dernier contient la d\'efinition des marges et vous devrez le
r\'ecup\'erer.

\subsection*{Annexe}
Merci de votre participation.

\begin{thebibliography}{9}
\bibitem{foo:baz}
U. Nexpert,
{\em Le livre,}
Son Editeur, 1929.
\bibitem{key:foo}
I. Troiseu-Pami,
 Un article int\'eressant,
{\em Journal de Spirou}, Vol. 17, pp. 1-100, 1987.
\end{thebibliography}
\end{document}

### 2019-03-29 RJCIA2019/short_draft.tex
RJCIA2019

--- 2019-02-26 draft.tex
@@
-\input{ijcai_preamble} 
-\author{ID: 2696}
-%\author{Beatrice Napolitano$^1$\and Olivier Cailloux$^1$	\and  Paolo Viappiani$^{2}$
-%	\affiliations $^1$ LAMSADE, UMR 7243, CNRS and Universit\'e Paris Dauphine, PSL Research University, Paris, France\\ $^2$ LIP6, UMR 7606, CNRS and Sorbonne Universit\'e, Paris, France
-%	\emails \{firstname.lastname\}@dauphine.fr, paolo.viappiani@lip6.fr
-%}
-%Restoring page numbers as missing them out violates basic human rights of the reviewers. -- Olivier
+%\input{rfia} 
+\documentclass[a4paper,twoside]{article}
+\usepackage{rfia2000}
+\usepackage[T1]{fontenc}
+\usepackage{babel}
+\usepackage{times}
+
+%\author{ID: 2696}
+\author{\begin{tabular}[t]{c@{\extracolsep{6em}}c@{\extracolsep{6em}}c}
+	B. Napolitano${}^1$ & O. Cailloux${}^1$ & P. Viappiani${}^2$ \\
+	\end{tabular}
+{} \\
+\\
+${}^1$        LAMSADE, UMR 7243, CNRS and Universit\'e Paris Dauphine, PSL Research University, Paris, France   \\
+${}^2$        LIP6, UMR 7606, CNRS and Sorbonne Universit\'e, Paris, France
+{} \\
+\\
+%Mon adresse compl\`ete \\
+\{firstname.lastname\}@dauphine.fr, paolo.viappiani@lip6.fr\\
+%{\bf Domaine principal de recherche}: RFP ou IA\\
+%{\bf Papier soumis dans le cadre de la journée commune}: OUI ou NON
+}
+
 \thispagestyle{plain}
@@
 \usepackage{natbib}
+\usepackage[strict]{siunitx}
 \usepackage{hyperref}
 \usepackage{mathrsfs}
+
+\usepackage[small]{caption}
+\usepackage{graphicx}
+\usepackage{amsmath}
+\usepackage{booktabs}
 
@@
 
-\title{Robust Winner Determination and Simultaneous Elicitation of Scoring Rules and Preferences}
+\title{\Large\bf Simultaneous Elicitation of Committee and Voters Preferences}
 
 \begin{document}
+\date{}
 \maketitle
-\begin{abstract}
+\thispagestyle{empty}
+%\subsection*{R\'esum\'e}
+%{\em
+%	Le choix social traite du probl\`eme de la d\'etermination d'un choix consensuel \`a partir des pr\'ef\'erences de diff\'erents agents.
+Dans le cadre classique, la r\`egle de vote est fix\'ee \`a l’avance et les informations compl\`etes concernant les pr\'ef\'erences des agents sont fournies.
+Dans cet article, nous supposons que la r\`egle de vote et les pr\'ef\'erences des agents sont partiellement connues.
+Ainsi, nous fournissons un protocole interactif d’\'elicitation bas\'e sur le regret minimax et d\'eveloppons plusieurs strat\'egies d’interrogation, associant questions au comit\'e et questions aux agents, afin d’obtenir les informations les plus pertinentes et de converger rapidement vers un r\'esultat optimal ou s'approchant de l'optimal.
+%}
+%\subsection*{Mots Clef}
+%Choix social computationnel, IA dans l'incertain, \'elicitation des pr\'ef\'erences, regret minimax.
+
+\subsection*{Abstract}
+{\em
 	Social choice deals with the problem of determining a consensus choice from the preferences of different agents (voters).
 In the classical setting, the voting rule is fixed beforehand and full information concerning the preferences of the agents is provided.
-Recently, the assumption of full preference information has been questioned by a number of researchers and several methods for eliciting preferences have been proposed.
-
 In this paper we go one step further and we assume that both the voting rule and the agents preferences are partially specified.
-Focusing on positional scoring rules, we assume that the chair, while  not able to give a precise definition of the rule, is capable of answering simple questions  requiring to pick a winner from a specific  example profile.
-Moreover, the preferences of the agents are incrementally acquired by asking comparison queries.
-
-We propose a method  for robust approximate winner determination in this setting with minimax regret. 
-We then provide an interactive elicitation protocol based on minimax regret
-and develop several query strategies that interleave questions to the chair and questions to the agents in order to acquire the most relevant information in order to quickly converge to optimal or a near-optimal alternative.
-\end{abstract}
+In this setting, we provide an interactive elicitation protocol based on minimax regret and develop several query strategies that interleave questions to the chair and questions to the agents in order to acquire the most relevant information in order to quickly converge to optimal or a near-optimal alternative.
+}
+\subsection*{Keywords}
+Computational Social Choice, uncertainty in AI, preference elicitation, minimax regret.
 
 \section{Introduction}
-Aggregation of preference information is a central task in many computer systems (recommender systems, search engines, etc).
-In many situations, such as in group recommender systems, the goal is to find a consensus choice.
-It is therefore natural to look at methods from social choice and see how they can be adapted for group decision-making in a computerized setting.
-
-The traditional approach to social choice assumes that both the social function and the full preference orderings of the agents are expressed beforehand. This represents two strong hypothesis.
-About the second one, requiring agents to express full preference orderings can be prohibitively costly (in term of cognitive and communication cost), especially for decisions with large sets of alternatives.
+%Aggregation of preference information is a central task in many computer systems (recommender systems, search engines, etc) whose final goal is to find a consensus choice.
+%In this contexts, a natural approach consists in looking at methods from social choice and see how they can be adapted for group decision-making in a computerized setting.
+In a traditional social choice setting both the social function and the full preference orderings of the agents are expressed beforehand.
+Nevertheless, sometimes requiring agents to express full preference orderings can be prohibitively costly (in term of cognitive and communication cost), especially for decisions with large sets of alternatives.
 This observation has motivated a number of recent works considering social choice with partial preference orders \citep{Xia2008, Pini2009, Konczak05} and incremental elicitation \citep{Kalech2011, Lu2011, Naamani-Dery2015} of agents’ preferences.
-
-The first hypothesis also should be relaxed, for in several situations it may not be easy to precisely define the voting rule.
-Indeed, it is possible that the chair may have some preferences over the desired aggregation method, but may still be not able to formalize the voting rule upfront.
-The work of \citet{Cailloux2014} provides elicitation methods for a quite general class of rules based on weak orders.
+Furthermore, several situations for which it may not be easy to precisely define the voting rule exist.
+Indeed, it is possible that the chair has some preferences over the desired aggregation method, but it is still not able to formalize the voting rule upfront.
+The work of Cailloux and Endriss \citep{Cailloux2014} provides elicitation methods for a quite general class of rules based on weak orders.
 When considering positional scoring rules, several authors \citep{Stein1994, Llamazares2013, Viappiani2018} have worked on positional scoring rules with uncertain weights, assuming that the preferences of the agents are fully known.
-%it is possible to derive dominance relations (akin to stochastic dominance) that allow to eliminate some alternatives since they will be less preferred than another one for any instantiation of the weights \citep{Stein1994}.
-%Among others, Llamazares and Pe{\~{n}}a have considered  the problem of dealing with underspecified weights in positional scoring rules.
-
 In this paper we consider that both the agents’ preferences and the social choice rule are partially specified.
-We develop methods for computing the minimax-optimal alternative for scoring rules with partial agent preference information and partial information about the weights of the scoring rule.
+We develop methods for computing the minimax-optimal alternative using positional scoring rules and we provide incremental elicitation methods to acquire relevant preference information.
+We then discuss several heuristics that determine queries, either to a voter or to the committee, that quickly reduce minimax regret.
 While previous works have considered either partial information about the agents preferences or a partially specified aggregation method, we do not know of any work considering both sources of uncertainty at the same time.
 
-In this work, we focus on positional scoring rules, that  are a particularly common method used to aggregate rankings and determine a winner.
-We also address the problem of elicitation, providing incremental elicitation methods to acquire relevant preference information; we discuss  several heuristics that determine queries that quickly reduce minimax regret.
-In particular, our query strategies focus simultaneously on reduction of relevant preference and voting rule uncertainty.
+\section{Partial information}
+\label{sec:background}
+We assume defined a set $A$ of $m$ alternatives (products, restaurants, public projects, etc.) and a set $\set{1, …, n}$ of agents (voters).
+Each agent $j$ comes from an infinite set $\N$ of potential agents and is associated to her “real” preference order $\pref_j \in \linors$ which is a linear order (connected, transitive, asymmetric relation) over the alternatives.
+A {\em profile} is the association of a preference to each agent and it is equivalently represented by $(\pref_1,\ldots,\pref_n)$ or by $\profile=(v_1,\ldots,v_n) \in V$ where $v_j(i) \in \set{1, \ldots, m}$ denotes the rank (position) of alternative $i$ in the preference order $\pref_j$.
+%Given $V$ the set of possible preference profiles, a social choice function $f : V \rightarrow \powersetz{A}$ associates a profile with a set of winners; where $\powersetz{A}$ represents the set of subsets of $A$ except for the emptyset.
+A social choice function associates a profile with a set of winners; we consider {\em positional scoring rules (PSR)}, which attach weights to positions according to the scoring vector $(w_1, \ldots, w_m)$.
+An alternative obtains a score that depends on the rank obtained in each of the preference orders and the winners are the alternatives with highest scores.
 
-The paper is organized as follows.
-In Section \ref{sec:background} we provide the necessary background.
-We introduce the minimax criterion, that selects a winner that minimizes the worst possible regret, in Section \ref{sec:mmr}.
-In Section \ref{sec:elicit} we provide an interactive elicitation protocol based on minimal regret;  in Section \ref{sec:experiments} we present the empirical validation of our approach with simulations; and Section \ref{sec:conclusions} provides some final thoughts.
+In this work we assume fixed, but unknown, a profile $\profile^*$ and a weight vector $\w^*$.
+Our knowledge at a given time of the preference of agent $j$ is encoded by a partial order over the alternatives, thus a transitive and asymmetric binary relation, denoted by $\ppref_j$; we assume that preference information is truthful, i.e.
+$a \ppref_j b ⇒ a \pref_j^* b$.
+%We use $\pinc$ to denote incomparability, that is $a \pinc_{j} b$ iff $a \nppref_j b \wedge b \nppref_j a$.
+An incomplete profile $\pprofile = (\ppref_1, \ldots, \ppref_n)$ maps each agent to a partial preference.
+A completion of $\ppref_j$ is any linear order $\pref$ that extends $\ppref_j$ and we indicate with $C(\ppref_j) = \set{{\succ} \in \linors \suchthat {\ppref_j} \subseteq {\succ}}$ the set of possible completions of $\ppref_i$.
+%We let $C(\pprofile)=C(\ppref_1)\times … \times C(\ppref_n)$ be the set of complete profiles extending $p$. Note that $\profile^* \in C(\pprofile)$.
 
-\section{Social choice with partial information}
-\label{sec:background}
-We now introduce some basic concepts.
-We assume defined a set $A$ of $m$ alternatives (products, restaurants, movies, public projects, job candidates, etc.) and a set $\set{1, …, n}$ of agents (voters); each agent $j$ is associated to her “real” preference order $\pref_j$.
-The agents come from an infinite set $\N$ of potential agents.
-The real preferences of the agents are elements of $\linors$, the linear orders (connected, transitive, asymmetric relations) over the alternatives.
-Following the social choice nomenclature, we call {\em profile} the association of a preference to each agent, considering a subset of agents from the set $\N$, and denote a profile by $(\pref_1,\ldots,\pref_n)$.
-A profile is equivalently represented by $\profile=(v_1,\ldots,v_n)$ where $v_j(i) \in \set{1, \ldots, m}$ denotes the rank (position) of alternative $i$ in the preference order $\pref_j$.
-
-Let $V$ be the set of possible preference profiles (the union for any integer $n$ of the $n$-fold cartesian product of the linear orders over the alternatives).
-A social choice function $f : V \rightarrow \powersetz{A}$ associates a profile with a set of winners, where $\powersetz{A}$ represents the set of subsets of $A$ except for the emptyset.
-(Sets are used for tied winners.)
-Among the many possible social choice functions, we consider {\em positional scoring rules (PSR)}, which attach weights to positions according to the vector $(w_1, \ldots, w_m)$ (also called the scoring vector).
-An alternative obtains a score that depends on the rank obtained in each of the preference orders:
-\begin{align}
-\label{eq:srule}
-s(x; \profile, \w) = \sum_{j=1}^{n} w_{v_j(x)}
-= \sum_{r=1}^{m} \alpha^{x}_r w_r 
-\end{align}
-where $\alpha^{x}_r$ is the number of times that alternative $x$ was ranked in the $r$-th position.
-The winners are the alternatives with highest scores.
-
-In this work we assume fixed, but unknown, a profile $\profile^*$ (and corresponding agents preferences $\pref_j^*$) and a weight vector $\w^*$, and we want to reason about partial preference information concerning those objects.
-Our knowledge at a given time of the preference of agent $j$ is encoded by a partial order over the alternatives, thus a transitive and asymmetric binary relation, denoted by $\ppref_j$. 
-In this work we assume that preference information is truthful, i.e. $a \ppref_j b ⇒ a \pref_j^* b$.
-We use $\pinc$ to denote incomparability, that is $a \pinc_{j} b$ iff $a \nppref_j b \wedge b \nppref_j a$.
-An incomplete profile $\pprofile = (\ppref_1, \ldots, \ppref_n)$ maps each agent to a partial preference.
-
-A completion of $\ppref_j$ is any linear order $\pref$ that extends $\ppref_j$.
-Let $C(\ppref_j) = \set{{\succ} \in \linors \suchthat {\ppref_j} \subseteq {\succ}}$ be the set of possible completions of $\ppref_i$.
-We let $C(\pprofile)=C(\ppref_1)\times … \times C(\ppref_n)$ be the set of complete profiles extending $p$. Note that $\profile^* \in C(\pprofile)$.
-
-\medskip
-We also assume that the weights of the scoring rule are only partially specified.
-Therefore the vector $(w_1,\ldots,w_m)$  is not known but we are given a set of constraints restraining the possible values that weights can take.
-We consider a decreasing sequence of weights:
-\begin{align}
-1=w_{1} > w_{2} > \ldots > w_{m}=0. \label{eq:monotone}
-\end{align}
-This is a natural assumption, as it is better to be ranked first than second, second than third, etc. 
-Without loss of generality, we consider that $w_1=1$ and $w_m=0$.
-
-The weights of a scoring rule can model different preferences of the chair. 
-For instance, the weights can control the inclination to favor ``extreme'' alternatives (often at either the top or the bottom of the input rankings) at the expenses of ``moderate'' alternatives (that are more consistently in the middle part of the input rankings).
-
-An important class of scoring rule is the one composed of weights that are a convex sequence \citep{Stein1994,Llamazares2016}, meaning that the difference between the weight of the first position and the weight of the second position is at least as great as the difference between the weights of the second and third positions, etc.
-\begin{equation} 
-\label{eq:convexity}
-\forall r \in \{1,\ldots,m-2\}: w_r - w_{r+1} \geq w_{r+1}-w_{r+2}.
-\end{equation}
-The constraint above is often used when aggregating rankings in sport competitions.
-We use $\W$ to denote the set of convex weight vectors.
-
-In general it can be difficult to set the weights in an appropriate way.
-We assume that in addition of basic requirements (monotonicity and convexity), the chair (the person or the organization that is supervising the voting process) is able to specify additional preferences about how the social choice function should behave.
-In this work we assume that preferences of the chair are encoded with linear constraints about the vector $\w$, relating the value of the weights of different positions.
-We use $\pw \subseteq \W$ to denote the set of weight vectors compatible with the preferences expressed by the chair about the scoring vector, and $\Co_W$ to denote the set of linear constraints expressed by the chair.
-
-Of course it may be difficult for real decision makers to state preferences about the voting rule in such an abstract way.
-These additional preferences can be elicited by asking questions about concrete profiles, for instance, by showing a complete profile of a small synthetic election and asking who should be elected in this case, as shown in Section \ref{sec:elicit}.
+Our knowledge regarding the weights of the scoring rule is, instead, represented by
+%We also assume that the weights of the scoring rule are only partially specified.
+%Therefore the vector $(w_1,\ldots,w_m)$  is not known but we are given 
+a set of constraints restraining the possible values that they can take. We consider a convex sequence of weights and we assume that 
+%, i.e.
+a decreasing sequence $1=w_{1} > w_{2} > \ldots > w_{m}=0$ such that the difference between the weights of the first and second positions is at least as great as the difference between the weights of the second and third positions, etc.
+%\begin{equation} 
+%\label{eq:convexity}
+%\forall r \in \{1,\ldots,m-2\}: w_r - w_{r+1} \geq w_{r+1}-w_{r+2}.
+%\end{equation}
+%We assume that in addition of basic requirements (monotonicity and convexity), 
+the chair is able to specify additional preferences about how the social choice function should behave.
+Of course it may be difficult for real decision makers to state these preferences, thus we can elicit them, for instance, by showing a complete profile of a small synthetic election and asking who should be elected in this case.
+Such requirements are encoded with linear constraints about the vector $\w$ and the set of these constraints is denoted by $\Co_W$.
+We use $\pw \subseteq \W$ to denote the set of weight vectors compatible with the preferences expressed by the chair.
 
@@
 \label{sec:mmr}
-In this paper, we consider a setting where both the agents' preferences and the preferences of the chair about the voting rule are incomplete.
-Notice that some authors have considered possible and necessary winners assuming a partial profile  \citep{Xia2008} or assuming an incompletely specified scoring rule \citep{Viappiani2018};
-however, we note that, in typical settings, there will be no necessary winner and too many possible winners.
-In practice, however, it is often useful to declare a winner given partial information.
-
-As a decision criterion to determine a winner, we propose to use minimax regret. 
-Minimax regret \citep{Savage1954} is a decision criterion that has been used for robust optimization under data uncertainty \citep{Kouvelis1997} as well as in decision-making with uncertain utility values \citep{Salo2001,Boutilier2006}.
-\citet{Lu2011} have adopted minimax regret for winner determination in social choice with
-the preferences of the agents that are only partially known, while the social choice function is predetermined and known.
-
-In this work we consider the simultaneous presence of uncertainty in the agents' preferences and uncertainty in the weights.
-Using {\em maximum regret} to quantify the worst-case error, the alternative that minimize this error is selected as winner, providing us with a form of robust optimization.
-Intuitively, the quality of a proposed alternative $a$ is how far from optimal $a$  could be in the worst case, given the current knowledge about the voting rule and about the agents' preferences.
-
-The maximum regret is considered by assuming that an adversary both 1) can extend the partial profile $\pprofile$ into a complete profile, and 2) can instantiate the weights choosing among any weight vector in $\pw$, where $\pprofile$ and $\pw$ represent our knowledge so far.
+As a decision criterion to determine a winner, we propose to use minimax regret \citep{Savage1954} . 
+%Minimax regret \citep{Savage1954} is a decision criterion that has been used for robust optimization under data uncertainty \citep{Kouvelis1997} as well as in decision-making with uncertain utility values \citep{Salo2001,Boutilier2006}.
+%\citet{Lu2011} have adopted minimax regret for winner determination in social choice with
+%the preferences of the agents that are only partially known, while the social choice function is predetermined and known.
+%In this work we consider the simultaneous presence of uncertainty in the agents' preferences and uncertainty in the weights.
+We use {\em maximum regret} to quantify the worst-case error, which measures, intuitively, how far an alternative is from the optimal one given current knowledge.
+% about the voting rule and the agents' preferences.
+The alternative that minimize this error is selected as winner, providing us with a form of robust optimization.
+The maximum regret is considered by assuming that an adversary can both 1) extend the partial profile $\pprofile$ into a complete one, and 2) instantiate the weights choosing among any weight vector in $\pw$.
 We formalize the notion of minimax regret in multiple steps.
@@
 \[\Regret(x, \profile, \w) = \max_{y \in A} s(y; \profile,\w) - s(x; \profile, \w).\]
-The pairwise max regret $\PMR(x,y;\pprofile,W)$ of $x$ relative to $y$ given partial profile $\pprofile$ and the set of weights $W$
-is the worst-case loss of choosing $x$ instead of $y$ under all possible realizations of the full profile {\em and} all possible instantiations of the weights:
+The pairwise max regret $\PMR(x,y;\pprofile,W)$ of $x$ relative to $y$ given partial profile $\pprofile$ and the set of weights $W$ is the worst-case loss of choosing $x$ instead of $y$ under all possible realizations of the full profile {\em and} all possible instantiations of the weights.
+Max regret $\MR(x;\pprofile,W)$ is the worst-case loss of $x$ and $\MMR(\pprofile,W)$ is the value of minimax regret obtained when recommending a minimax optimal alternative $x^*_{\pprofile, W}$.
+%\begin{align}
+%\PMR(x,y; \pprofile, W) & = \max_{\w \in W} \max_{\profile \in C(\pprofile)} s(y; \profile,\w) - s(x; \profile,\w).
+%\end{align}
+%It is the loss occurred by an adversarial selection of a complete profile $\profile$ extending $\pprofile$ and a selection of $\w \in W$ to maximize the loss between $x$ and the true winner under $\profile$ and $\w$.
 \begin{align}
-\PMR(x,y; \pprofile, W) & = \max_{\w \in W} \max_{\profile \in C(\pprofile)} s(y; \profile,\w) - s(x; \profile,\w).
+\PMR(x,y; \pprofile, W) & = \max_{\w \in W} \max_{\profile \in C(\pprofile)} s(y; \profile,\w) - s(x; \profile,\w) \\
+\MR(x; \pprofile, W) & = \max_{y \in A} \PMR(x,y; \pprofile, W)\\
+%& = \max_{\w \in W} \max_{\profile \in C(\profile)} \Regret(x, \profile, \w) \\
+\MMR(\pprofile,W) & = \min_{x \in A} \MR(x;\pprofile,W) \\
+x^{*}_{\pprofile,W} \in A^*_{\pprofile, W} & = \argmin_{x \in A} \MR(x;\pprofile,W) 
 \end{align}
 
-Max regret $\MR(x;\pprofile,W)$ is the worst-case loss of $x$.
-It is the loss occurred by an adversarial selection of a complete profile $\profile$ extending $\pprofile$ and a selection of $\w \in W$ to maximize the loss between $x$ and the true winner under $\profile$ and $\w$.
-\begin{align}
-\MR(x; \pprofile, W) & = \max_{y \in A} \PMR(x,y; \pprofile, W)\\
-& = \max_{\w \in W} \max_{\profile \in C(\profile)} \Regret(x, \profile, \w).
-\end{align}
-
-Finally,  $\MMR(\pprofile,W)$ is the value of minimax regret under $\pprofile$ and $W$, obtained when recommending a minimax optimal alternative $x^*_{\pprofile, W}$:
-\begin{align*}
-\MMR(\pprofile,W) & = \min_{x \in A} \MR(x;\pprofile,W) \\
-x^{*}_{\pprofile,W} \in A^*_{\pprofile, W} & = \argmin_{x \in A} \MR(x;\pprofile,W) 
-\end{align*}
-By picking as consensus choice
- an alternative associated with minimax regret, we can provide a recommendation that gives worst-case guarantees, giving some robustness in face of uncertainty (due to both not knowing the agents' preferences and the weights used in the aggregation).
-In cases of ties in minimax regret, we can either decide to return all minimax alternatives $A^*_{\pprofile, W}$ as winners or to pick just one of them using some tie-breaking strategy.
-
-Notice that if $\MMR(\pprofile, W)\!=\!0$, then $x^{*}_{\pprofile,W}$ is a necessary co-winner; this means that for any valid completion of the profile and any feasible $w \!\in\!
+%Finally,  $\MMR(\pprofile,W)$ is the value of minimax regret under $\pprofile$ and $W$, obtained when recommending a minimax optimal alternative $x^*_{\pprofile, W}$:
+%\begin{align*}
+%\MMR(\pprofile,W) & = \min_{x \in A} \MR(x;\pprofile,W) \\
+%x^{*}_{\pprofile,W} \in A^*_{\pprofile, W} & = \argmin_{x \in A} \MR(x;\pprofile,W) 
+%\end{align*}
+By picking as consensus choice an alternative associated with minimax regret, we can provide a recommendation that gives worst-case guarantees, giving some robustness in face of uncertainty. 
+%In cases of ties in minimax regret, we can either decide to return all minimax alternatives $A^*_{\pprofile, W}$ as winners or to pick just one of them using some tie-breaking strategy.
+%
+%Notice that if $\MMR(\pprofile, W)\!=\!0$, then $x^{*}_{\pprofile,W}$ is a necessary co-winner; this means that for any valid completion of the profile and any feasible $w \!\in\!
 W$, $x^{*}_{\pprofile,W}$ obtains a highest score.
-
-We note that our notion of regret gives some cardinal meaning to the scores: instead of just being used to select winners under the corresponding PSR, their differences are considered as representing the regret of the chair.
-
-% Add some general remarks about using minimax regret
-
-\paragraph{Computation of minimax regret}
-In order to compute pairwise maximum regret and therefore minimax regret, we adapt the reasoning from \citet{Lu2011} so that we decompose the $\PMR$ into the contributions associated to each agent.
-The setting is however more challenging due to the presence of uncertainty in the weights.
-
-Scoring rules are additively decomposable.
-%A scoring rule associates each alternative to a score that is given by the sum of points obtained for each agent.
-Recall that when computing $s(x; \profile, \w)$, $w_{v_j(x)}$ is the number of points that $x$ obtains in the ranking $v_j$ (see Equation \ref{eq:srule}).
-By exploiting the decomposition of the score in terms of votes, we write the actual regret of choosing $x$ instead of $y$ as
-\[
-s(y; \profile,\w) - s(x; \profile, \w) = \sum_{j=1}^n w_{v_j(y)} - w_{v_j(x)},
-\]
-and  can rewrite $\PMR$ as follows:
-\begin{align*}
-& \PMR(x,y; \pprofile, W) = \max_{\w \in W} \max_{\profile \in C(\pprofile)} [ s(y; \profile,\w) - s(x; \profile,\w) ] \\
-& =  \max_{\w \in W} \sum_{j=1}^{n} \max_{v_j \in C(\succ_j^p)} [w_{v_j(y)} - w_{v_j(x)}]. \\
-\end{align*}
-Note that in general the inner max will depend on the weights chosen by the outer min.
-
-We consider now a procedure for completing a partial profile that was first proposed by \citet{Lu2011} when considering minimax regret with a fixed weight vector.
-As we will show, this procedure can also be used in our case of uncertain weight vector.
-
-We are interested in computing $\PMR(x, y; \pprofile, W)$.
-This represents the “worst” difference of score, thus the difference of score between $y$ and $x$ under the worst case preferences compatible with $\pprofile$ and $W$, where the worst case is the one that maximizes this difference of score.
-Consider our knowledge $\ppref_j$ of the preference of an agent $j$. 
-The adversary has to make the score of $y$ as high as possible, and the score of $x$ as low as possible. 
-To do this, he should complete $\ppref_j$ to $\pref_j$ by putting above $x$ as many alternatives as he can, that is, all the alternatives except those that are known to be worse than $x$ (those $a$ such that $x \ppref_j a$); and similarly, put below $y$ all the alternatives he can, thus, put above $y$ only those $a$ such that $a \ppref_j y$.
-Sometimes these two objectives conflict: when an alternative should go above $x$ according to the first objective and below $y$ according to the second one (because $¬(x \ppref_j a) ∧ ¬(a \ppref_j y)$), and $x$ is known to be better than $y$ (thus $x \ppref_j y$).
-In this case, the first objective should take priority, and $a$ should be put above $x$, which will move both $x$ and $y$ one rank lower than if $a$ had been put below $y$. 
-This maximizes the adversary’s interests: because the weight vector is convex, the difference of scores will be lower when both alternatives are ranked lower (Equation \ref{eq:convexity}), and that difference of scores is in favor of $x$ when $x \ppref_j y$, thus to be minimized from the point of view of the adversary.
-To summarize:
-\begin{align} 
-\label{eq:compl}
-\begin{split}
-a \pref_j x &⇔ ¬(x \ppref_j a)\\
-y \pref_j a &⇔ ¬(a \ppref_j y) ∧ (¬(x \ppref_j y) ∨ (x \ppref_j a)).
-\end{split}
-\end{align} 
-We just sketched a proof of the following claim, and leave the rest of the proof to the reader.
-\begin{claim}
-There exists a completion $\hat{\profile} \in C(\pprofile)$ such that $\PMR(x,y; \pprofile, W) = \max_{\w \in W} [ s(y; \hat{\profile}, \w) - s(x; \hat{\profile}, \w) ]$ and such that the linear order $\hat{v}_{j}$ of each agent $j$ satisfies (\ref{eq:compl}).
-\end{claim}
-It follows that $\hat{v}_{j}(x)$, the rank of $x$ in the PMR-maximizing linear order of agent $j$, 
-is $\hat{v}_{j}(x) = 1+\card{A}-\card{{\ppref_j}(x)}$, where ${\ppref_j}(x)$ designates the set of alternatives that are less good than $x$ according to $\ppref_j$, and the rank of $y$ is $\hat{v}_{j}(y)=1+\card{{\pprefinv_j}(y)}+\beta$, where $\beta = \card{A} - \card{{\ppref_j}(x)}$ if $(x \ppref_j y)$ and $\beta = 0$ otherwise.
-
-%Proof: Define $\pref$ as just $\ppref_j$ with the arcs added to minimally satisfy the above.
-Thus, add the following arcs: when $x ?
-a$, add $a > x$.
-When $a ?
-y ∧ x \ppref_j y ∧ ¬(x \ppref_j a)$, add $a \pref y$.
-When $a ?
-y ∧ [¬(x \ppref_j y) ∨ (x \ppref_j a)]$, add $y \pref a$.
-Observe that $\ppref_j \subseteq \pref$.
-We have to show that it is acyclic.
-(Then we take its transitive closure to make it a partial order, and it’s done.) Note that if there is a cycle in $\pref$, it’s because of some new arcs, as $\ppref_j$ is acyclic.
-Thus, the cycle must go through one of these new arcs.
-…
-
-\begin{claim}
-The $\PMR$ can be written as:
-\begin{align} 
-\PMR(x,y; \pprofile, W)  
-& = \max_{w \in W} \sum_{j=1}^n w_{\hat{v}_j(y)} - w_{\hat{v}_j(x)} = \\ 
-& = \max_{w \in W} \sum_{r=1}^m (\hat{\alpha}_{r}^{y} - \hat{\alpha}_{r}^{x}) w_i. 
-\end{align}
-where the $\hat{\alpha}_{r}^{y}$ (resp. $\hat{\alpha}_{r}^{x}$)  is the number of times $y$ (resp. $x$) is at rank $r$ in the rankings of the completed profile $\hat{\profile}$.
-\end{claim}
-The last claim shows that PMR is linear in the weights.
-Recall that the preferences of the chair are encoded with linear constraints $\Co_{W}$.
-The pairwise max regret $\PMR(x,y; \pprofile,W)$ can be obtained as the solution of the following linear program defined on the variables $w_1, …, w_m$, the weights attached to the different positions.
-\begin{align*}
-\max_{\w} & \sum_{r=1}^m (\hat{\alpha}_{r}^{y} - \hat{\alpha}_{r}^{x}) w_{r}\\
-\text{ s.t. } & \text{Equation } (\ref{eq:monotone})\\
-& \text{Equation } (\ref{eq:convexity})\\
-& \Co_W
-\end{align*}
-Note that given our choice $w_{1}=1$ and $w_{m}=0$, there are only $m-2$ variables 
-(we leave $w_{1}$ and $w_{m}$ in the LP just for clarity of presentation).
-
-The max regret $\MR(x; \pprofile, W)$ is determined by considering the pairwise regret of $x$ with each other alternative in $A$.
-Optimal alternatives w.r.t. minimax regret are the ones with least max regret. 
-Notice that, whenever the PMR of an alternative $x$ (against some other alternative) exceeds the best MR value found so far, we don't need to further evaluate $x$, as it can't be optimal. 
-This idea can be exploited further by adopting a minimax-search tree \citep{Braziunas2011}.
+%
+%We note that our notion of regret gives some cardinal meaning to the scores: instead of just being used to select winners under the corresponding PSR, their differences are considered as representing the regret of the chair.
 
@@
 We propose an incremental elicitation method based on minimax regret.
-At each step, the system may either ask a question to one of the agents, or ask a question to the chair about the voting rule. 
+At each step, the system may ask a question either to one of the agents or to the chair.
 The goal is to acquire relevant information to reduce minimax regret as quickly as possible.
-As termination condition of elicitation, we can check whether minimax regret is lower than a threshold; if we wish optimality, we can perform elicitation until minimax regret drops to zero.
-
-The remainder of this Section is structured as follows.
-First of all, we discuss the different types of questions that can be asked to the agents and to the chair, and the way responses are handled.
-Then, we describe different strategies to determine informative queries to ask next, with the goal of reducing $\MMR(\pprofile,W)$ quickly.
+As termination condition of elicitation, we can check whether minimax regret is lower than a threshold or, if we wish optimality, we can perform elicitation until minimax regret drops to zero.
 
@@
 We distinguish between questions asked to the agents and questions asked to the chair.
-As {\em questions asked to the agents} it is natural to consider comparison queries asking to compare two alternatives.
-%Another common type of queries are {\em top-k}, asking to each agent her $k$ most preferred alternatives.
-The effect of a response to a question asked to an agent is to increase our knowledge about the agents rankings, thus augmenting the partial profile $\pprofile$. 
-If agent $j$ answers a comparison query stating that alternative $a$ is preferred to $b$, then the partial order $\ppref_j$ is augmented with $a \ppref_j b$ and by transitive closure.
-
-A bit more discussion is needed about {\em questions asked to the chair}.
-Such questions aim at refining our knowledge about the scoring rule; a response gives us a constraint on the weight vector $\w$.
-In particular, we want to acquire constraints of the type:
+For the first we consider comparison queries that ask a particular agent to compare two alternatives. Then, the partial profile $\pprofile$ is augmented on the bases of the agent's answer.
+The latter, instead, aim at refining our knowledge about the scoring rule; in particular, we want to acquire constraints of the type:
 \[ w_{r} - w_{r+1} \geq \lambda (w_{r+1} - w_{r+2}) \] 
-for $r \in \{1,\ldots,m-2\}$, relating the difference between the importance of ranks $r$ and $r+1$ with the difference between ranks $r+1$ and $r+2$.
-
-\paragraph{Building concrete questions for the chair}
-As we assume the weights constitute the utility components of the chair, it might be reasonable to assume, 
-%as we do here, 
-that the chair is able to answer such abstract questions in our setting.
-However, it is important to make sure that the question can also, in principle, be asked in a more concrete way, in terms of winners of example profiles.
-This permits to test whether the chair understands the question as we do; this permits to relate the preference of the chair  to her choice behavior in the economic sense; and this will be necessary for an ordinal extension of our work where the scores would not be considered as cardinal utilities.
-Thus, our task is to build a profile, given $\lambda$ and $r ≤ m-2$, in such a way that the set of (tied) winners picked by the chair reveals whether $w_{r} - w_{r+1} \geq \lambda (w_{r+1} - w_{r+2})$.
-We assume that $\lambda$ is rational, and define $\lambda = p/q$.
-
-Observe that the question may be defined equivalently as whether $q w_{r} + p w_{r+2} ≥ (p + q) w_{r+1}$, where $p, q$ are natural numbers. 
-As a first attempt to make this question concrete, let us define a profile $P$ containing $p+q$ agents. 
-Define an alternative $a$ that receives $q$ times the rank $r$ and $p$ times the rank $r+2$ and an alternative $b$ that receives $p+q$ times the rank $r+1$. 
-Observing that the score of $a$ in that profile is exactly the left hand side of the question, and that the score of $b$ is the right hand side, intuition suggests that observing whether the chair picks $a$ or $b$ as winner will let us determine which side is greater; equality occurring when the chair declares $a$ and $b$ as tied for the victory.
-However, we still need to complete the profile, thus, come up with other $m-2$ alternatives defined so that each agent in the resulting profile has placed exactly one alternative in each rank. 
-And we must ensure, doing this, that these other alternatives are not better than $a$ or $b$: if the chair picks a different alternative $c$, it tells us that the chair prefers $c$ to both $a$ and $b$,
-but it generally does not  answer the question we are interested in. 
-Taking $p = q = 1$, $m=4$, $r=2$, we see that such a completion may be impossible. Luckily, this problem can be worked around, at the price of increasing the number of agents.
-
-First build a temporary profile $P$ of $p+q$ agents with $a$ and $b$ ranked as just described.
-Complete it with $m-2$ alternatives ranked in arbitrary orders so that the resulting profile has complete strict rankings for each of the $p+q$ agent.
-Now we will make the other alternatives as bad as desired by adding agents to $P$ that appreciate $a$ and $b$ more than the other alternatives, thus building a profile $P'$ in which, whatever the weights, $c$ may not have a better score than $a$.
-Observe that if we add $\delta$ agents (with $\delta$ a natural number) that put $a$ at first rank and $b$ at second rank, and $\delta$ agents that put $b$ at first rank and $a$ at second rank, we do not change the difference of the scores of $a$ and $b$, and thus, observing the chair choosing $a$ or $b$ still answers the question.
-Choose arbitrarily a matching of the remaining $m-2$ alternatives to the ranks $3$ to $m$, say, $c \mapsto 3$, $d \mapsto 4$, and so on.
-The first $\delta$ supplementary agents, who rank $a$ first and $b$ second, rank the other alternatives as the just defined mapping suggests.
-The other $\delta$ supplementary agents, who rank $b$ first and $a$ second, use the opposite ranking for the remaining alternatives, say, $c \mapsto m$, $d \mapsto m-1$, and so on.
-We can now prove that, for $\delta = p+q$, and whatever the weight vector $\w \in \W$, no alternative, except possibly $b$, has a better score than $a$.
-(In fact, as the construction will exhibit, they are all worst than both $a$ and $b$, but the weaker fact is enough for our claim.)
-
-Pick any alternative $c$ that is not $a$ or $b$. 
-%Let $c_t$ denote the number of times $c$ reaches rank $t$ or better in $P$.
-Note that $c_m = p+q$ and $c_t ≤ p + q, 1 ≤ t ≤ m$.
-Define $a_t$ similarly, for the alternative $a$.
-By construction, $a_r = q$, $a_{r+2} = q+p = a_m$.
-Define $c'_t$ as the number of times $c$ gets rank $t$ or better in $P'$, and define $a'_t$ similarly.
-Now $a'_1 ≥ \delta, a'_t ≥ 2\delta \text{ for } 2 ≤ t < m, a'_{r+2} = q+p+2\delta = a'_m$.
-To obtain upper bounds for $c'_t$, assume $c$ is ranked first by the $p+q$ agents voting in profile $P$.
-By our construction, the  $2 \delta$ new agents of $P'$ give to $c$ the ranks $(3, m)$, or $(4, m-1)$, … Observe that the score of $c$ is maximal for attribution $(3, m)$, by convexity of the weights.
-Therefore, in the best case for $c$, $c'_1 ≤ p + q, c'_2 ≤ p+q, c'_t ≤ p+q+\delta \text{ for } 3 ≤ t < m, c'_m ≤ p+q+2\delta$.
-Observe that $a'_t ≥ c'_t, 1 ≤ t ≤ m$ (with strict inequality for $t=2$).
-Because weights are non increasing, this guarantees, with $\delta = p + q$, that the score of $a$ is not lower than the one of $c$ (it is even strictly higher, thanks to the strict inequality).
-
-This concludes the proof of the following claim. 
-\begin{claim}
-	Given a rational $\lambda$ and a rank $r$ between $1$ and $m - 2$, the profile named $P'$ in the foregoing description is such that, for any weight vector $\w \in \W$, $a \in f(P')$ iff $w_{r} - w_{r+1} ≥ \lambda (w_{r+1} - w_{r+2})$ and $b \in f(P')$ iff $w_{r} - w_{r+1} ≤ \lambda (w_{r+1} - w_{r+2})$, where $f$ is the PSR parameterized with $\w$.
-\end{claim}
-At this stage, we are content that a procedure exists to transform our abstract questions to questions about winners of a PSR.
-Further studies would investigate, for example, what is lost in terms of elicitation efficiency when we are forced to restrain to realistic concrete questions, meaning, questions involving small profiles; or investigate the relationship between our understanding of scores as (cardinal) utility and (ordinal) scores as definition of a PSR.
+for $r \in \{1,\ldots,m-2\}$, relating the difference between the importance of consecutive ranks.
+% $r$ and $r+1$ with the difference between ranks $r+1$ and $r+2$.
 
 \paragraph{Elicitation strategies}
-We develop several elicitation strategies for simultaneous elicitation of agents' preferences and of the scoring rule.
-While it is of course possible to first fully elicit the agents’ preferences and afterwards elicit weights, we also want to propose interleaved approaches and compare them experimentally.
-Indeed, it can be beneficial to interleave questions asked to the chair and questions asked to agents, depending on which is estimated to be more informative.
+A strategy is a function (or a random process) that, given our partial knowledge so far, gives us a question that should be asked.
 
-We define here the various strategies we tested experimentally.
-A strategy is a function (or a random process) that gives us, given our partial knowledge so far $(\pprofile, W)$, a question that should be asked, according to that strategy.
+The \strat{Random} strategy first decides with a probability of $1/2$ each whether it will ask a question about weights or about a preference ordering.
+Then it equiprobably draws a question among the set of the possible ones.
+This strategy is clearly non efficient but it gives us a baseline for comparisons.
 
-Among them, the \strat{Random} strategy is used to capture how hard an elicitation problem is, by giving us a baseline: using it we can estimate how fast the regret diminishes when we ask questions randomly.
-Choosing the questions purely randomly however, that is, independently of what we know already, would be pointless, as we would most of the time ask questions we already know the answer of.
-Thus, that strategy choses questions in a minimally “clever” way, just by picking questions in a set of a priori relevant questions.
-The \strat{Random} strategy first decides with a probability of $1/2$ each whether it will ask a question about weights or a question about a preference ordering (unless the profile is already known entirely).
-If it opted for a question about weights, it draws one rank in $2 ≤ r ≤ m-2$ equiprobably, takes the middle of the interval of values for $\lambda$ that are still possible considering our knowledge so far, and asks whether $w_r - w_{r+1} ≥ \lambda (w_{r+1} - w_{r+2})$.
-The intervals are initialized to $[1, n]$.
-If it opted for a question to agents, it draws equiprobably among the agents whose preference is not known entirely; picks an alternative $a$ randomly with equal probability among those involved in some incomparabilities in $\ppref_j$; and picks an alternative $b$ with equal probability among those incomparable with $a$ in $\ppref_j$.
+The \strat{Extreme completions} strategy considers the solution of the minimax regret game and estimates the contribution to the regret of our uncertainty about the weights and the profile.
+Then it asks a question to the chair or to the agents depending on which of these two values is the highest.
 
-% In the code, called Current solution
-We also define the \strat{Extreme completions} strategy, which we consider as a more realistic baseline. 
-Consider the solution of the minimax regret game, 
- $(x^{*},\bar{y},\bar{\profile},\bar{\w})$, where $x^{*}$ is the minimax regret optimal alternative, and $\bar{y} = \arg \max_{y \in A} \PMR(x,y; \pprofile, W)$, $\bar{\profile}$ and $\bar{\w}$ are the adversarial choices, thus, the instantiations that, given the choice of $x^*$, maximize the regret.
-Define: 
-\begin{align}
-\tau_{1} & = \min_{\w \in W} s(\bar{y}; \bar{\profile}, \w) - s(x^{*}; \bar{\profile}, \w),  \label{eq:tau1} \\
-\tau_{2} & = \min_{\profile \in C(\pprofile)} s(\bar{y},\profile, \bar{\w}) -  s(x^{*}; \profile, \bar{\w}).
-\end{align}
-Intuitively the quantity $\MMR - \tau_{1} = \max_{\w \in W} s(\bar{y}; \bar{\profile}, \w) - s(x^{*}; \bar{\profile}, \w) - \min_{\w \in W} s(\bar{y}; \bar{\profile}, \w) - s(x^{*}; \bar{\profile}, \w)$ estimates the contribution to regret of our uncertainty about the weights $\w$, while $\MMR - \tau_{2} $ estimates the uncertainty about the profile.
-Therefore, whenever $\tau_{1} < \tau_{2}$ we ask a question to the chair, and compare componentwise $\bar{\w}$ and $\w^{\tau}$, the argmax of Eq.
-(\ref{eq:tau1}), to find the position $r$ that is most valuable to ask about (the one that maximizes $\abs{\bar{\w}_r - \w^{\tau}_r}$), and choose $\lambda$ as the middle of the interval of possible values for that rank.
-Instead, if $\tau_{1} > \tau_{2}$ we ask a question to one of the agent.
-We select the question by checking for each agent $j$ the difference between the difference of the ranks of $x$ and $y$ in the profile that minimizes compared to the one that maximizes the difference of scores, and pick an agent related to the highest difference, then pick $x$ or $y$ with $1/2$ chances as the first alternative of the question, and pick an incomparable alternative equiprobably as the second one.
+The \strat{Pessimistic} strategy selects among all the possible questions the one that leads to minimal regret in the worst case.
+For each question, it considers both possible answers to the question and uses some aggregation of their MMRs as a score of the question.
 
-The \strat{Pessimistic} strategy selects the question that leads to minimal regret in the worst case, considering both possible answers to the question.
-Assume that a question leads to the possible new knowledge states $(\pprofile_1, W_1)$ and $(\pprofile_2, W_2)$, depending on the answer.
-Then the badness of the question in the worst case is:
-\[\max_{i=1,2} \MMR(\pprofile_i,W_i) \]
-This badness measure gives a way of picking questions among a set of possible questions, by picking one that minimizes the measure.
-Note that other aggregators than $\max$ can be used as well.
-The \strat{Pessimistic} strategy considers as possible questions the ones defined by the \strat{Random} strategy (with the difference that a threshold is used: if for some rank $r$ the interval of possible values for $\lambda$ is not larger than $0.1$, the question is not considered).
-It uses a variant of the $\max$ as an aggregator: if the maximal $\MMR$ of two questions are equal, it prefers the question that has the lowest $\MMR$.
-We expect this strategy to perform very well, but only for very small problem instances: its complexity is in $O(n^2 m^5)$, because we consider $O(m^2)$ questions for each agent and need for each question to compute $\MMR$ twice, whose complexity is $O(nm^3)$.
-For small dimensions, it gives us an estimate of an upper bound to the possible quality of a strategy.
-
-The \strat{Two phase} strategy asks a predefined, non adaptive sequence of $m-2$ questions in order to gather informations about the weights $\w$ of the scoring rule, using one question per rank (except the extreme ones) as defined in the other strategies, thus, each cutting the initial interval of possibilities into two equal parts.
-Then it only asks questions about the voters, using questions as defined in the \strat{Pessimistic} strategy.
-%TODO Then use minimax regret as in Lu and Boutilier. check what’s this.
-
-%\item {\em Volumetric} strategy: chooses an agent $i$ and a query that maximizes the number of new pairwise preferences revealed given the worst response.
-
-\section{Empirical Evaluation} 
-\label{sec:experiments}
-
-\begin{table}
-	\begin{center}
-		\begin{tabular}{rr@{ ± }lr@{ ± }lr@{ ± }l}
-			\toprule
-			k & Rnd & sd & Two ph. & sd & Pess. & sd \\
-			\midrule
-			0 & 4.0 & 0 & 4.0 & 0 & 4.0 & 0\\
-			5 & 3.40 & 0.40 & 3.86 & 0.13 & 2.63 & 0.28\\
-			10 & 2.59 & 0.75 & 2.63 & 0.39 & 1.29 & 0.50\\
-			15 & 2.37 & 0.33 & 0.92 & 0.76 & 0.43 & 0.50\\
-			20 & 1.23 & 1.04 & 0.15 & 0.23 & 0.09 & 0.27\\
-			25 & 0.90 & 0.80 & 0 & 0 & 0.25 & 0.75 \\
-			30 & 0.34 & 0.57 & 0.02 & 0 & 0 & 0\\
-			\bottomrule
-		\end{tabular}
-	\end{center}
-	\caption{Minimax regret in problems of size $(4, 4)$ after $k$ questions.}
-	\label{fig:xp1}
-\end{table}
-
-\begin{table}
-	\begin{center}
-		\begin{tabular}{rr@{ ± }lr@{ ± }lr@{ ± }l}
-			\toprule
-			k & Rnd & sd & Two ph. & sd & Pess. & sd \\
-			\midrule
-			0 & 5.0 & 0 & 5.0 & 0 & 5.0 & 0\\
-			5 & 4.93 & 0.16 & 4.98 & 0.01 & 4.15 & 0.32\\
-			10 & 4.84 & 0.22 & 4.35 & 0.28 & 3.44 & 0.46\\
-			15 & 4.28 & 0.58 & 3.70 & 0.25 & 2.66 &0.54 \\
-			20 & 3.85 & 0.33 & 2.67 & 0.51 & 1.62 & 0.82\\
-			25 & 3.50 & 0.78 & 2.17 & 0.66 & 0.84 &  0.57\\
-			30 & 2.96 & 0.80 & 1.47 & 1.10 & 0.53 & 0.70\\
-			\bottomrule
-		\end{tabular}
-	\end{center}
-	\caption{Minimax regret in problems of size $(5, 5)$ after $k$ questions.}
-	\label{fig:xp2}
-\end{table}
-
-\begin{table}
-	\begin{center}
-		\begin{tabular}{rr@{ ± }lr@{ ± }lr@{ ± }l}
-			\toprule
-			k & Rnd & sd & Two ph. & sd & Pess. & sd \\
-			\midrule
-			0 & 6.0 &  &  &  &  & \\
-			5 &  &  &  &  &  & \\
-			10 &  &  &  &  &  & \\
-			15 &  &  &  &  &  & \\
-			20 &  &  &  &  &  & \\
-			25 &  &  &  &  &  &  \\
-			30 &  &  &  &  &  & \\
-			\bottomrule
-		\end{tabular}
-	\end{center}
-	\caption{Minimax regret in problems of size $(6, 6)$ after $k$ questions.}
-	\label{fig:xp3}
-\end{table}
-
-We test our strategies using randomly generated datasets. %TODO and real datasets. (sushi and iris).
-Our goal is to see how much we gain with an interleaved elicitation approach mixing questions to the chair and questions asked to the agents compared to performing a partial elicitation of the rule first and then eliciting the agents preferences.
-We also want to see how realistic our approach is for various problem sizes, by estimating the number of questions we would have to ask before being able to reduce the worst regret significantly.
-
-We use the following protocol.
-Having picked a problem size $(m, n)$, a number of questions $k$ and a strategy, we randomly generate an “oracle”, containing the true preferences of the agents (i.e.
-the linear orders) and the weights associated with the chair's scoring rule.
-We start with empty knowledge ($\pprofile = (\emptyset_j), W = \W$) about the preference orderings of the agents or the weight differences favored by the chair.
-We obtain the first question to be asked using the selected strategy, as described above.
-We use the oracle to answer the question and update our knowledge, which is thus used to obtain the next question.
-This is repeated until $k$ answers have been obtained.
-Then we compute the resulting $\MMR$.
-We repeat this whole experiment 10 times, for a given $(m, n, k)$, and report the average resulting $\MMR$ and the standard deviation.
-
-The results are displayed in \cref{fig:xp1,fig:xp2,fig:xp3}. In these tables, the strategies are designated by Rnd for Random, Two ph. for Two phases, and Pess. for Pessimistic.
+The \strat{Two phase} strategy asks a predefined, non adaptive sequence of $m-2$ questions to the chair and then it only asks questions about the voters, using questions as defined in the \strat{Pessimistic} strategy.
 
@@
 \label{sec:conclusions}
-In this paper we have considered a  social choice setting with partial  information about the agent's  
-preferences and as well a partially specified voting rule.
-We have proposed the use of minimax regret as a means of robust winner determination in this setting, and as well as to guide the process of simultaneous elicitation of preferences and voting rule.
-Our experimental results %on randomly generated and real world data sets 
-suggest that regret-based elicitation is effective and allow to quickly reduce worst regret significantly.
-%Regret-based elicitation allows to determine near-optimal winners using only few information about the agents' preferences.
+In this paper we have considered a social choice setting with partial information and we have proposed the use of minimax regret both as a means of robust winner determination as well as a guide to the process of simultaneous elicitation of preferences and voting rule.
 
-%As part of the contribution of this work, we publish an open-source library that allows to reproduce our experiments and more, at https://github.com/…
+The next step is to test our strategies in order to compare the performance of our interleaved elicitation approach that mix questions to the chair and to the agents, to a more classical approach that elicit the rule first and then the agents preferences (or vice-versa).
 
-We mention some directions for future works.
-Further development of elicitation strategies, considering alternative heuristics, is an important direction. 
-Second, elicitation could be extended to voting rules beyond scoring rules.
-Finally, an important direction of extension aims at studying how to elicit preferences while restraining to concrete and easy questions.
+Further development of elicitation strategies, considering alternative heuristics, is also an important direction for future works together with the extension of the approach to voting rules beyond scoring rules.
+
 % Acknowledgements: We thank the reviewers for comments helping to improve the paper. 
@@
 \bibliography{biblio}
-\bibliographystyle{named}
+\bibliographystyle{plain}
 %\bibliographystyle{plain} 

### 2019-03-30 RJCIA2019/short_draft.tex
Comments

@@
 \usepackage[T1]{fontenc}
-\usepackage{babel}
+\usepackage[english]{babel}
 \usepackage{times}
@@
 In the classical setting, the voting rule is fixed beforehand and full information concerning the preferences of the agents is provided.
-In this paper we go one step further and we assume that both the voting rule and the agents preferences are partially specified.
-In this setting, we provide an interactive elicitation protocol based on minimax regret and develop several query strategies that interleave questions to the chair and questions to the agents in order to acquire the most relevant information in order to quickly converge to optimal or a near-optimal alternative.
+\commentOC{This “we go one step further” sounds odd here.
+I suggest one more sentence about the normal elicitation setting with only the agents preferences partially specified.} In this paper we go one step further and we assume that both the voting rule and the agents preferences are partially specified.
+In this setting, we provide an interactive elicitation protocol based on minimax regret and develop \commentOC{I’d say “present”, because they are not precisely specified in the text.} several query strategies that interleave questions to the chair and questions to the agents in order to \commentOC{attempt to} acquire the most relevant information in order to quickly converge to optimal or a near-optimal alternative.
 }
@@
 %In this contexts, a natural approach consists in looking at methods from social choice and see how they can be adapted for group decision-making in a computerized setting.
-In a traditional social choice setting both the social function and the full preference orderings of the agents are expressed beforehand.
-Nevertheless, sometimes requiring agents to express full preference orderings can be prohibitively costly (in term of cognitive and communication cost), especially for decisions with large sets of alternatives.
+In a traditional social choice setting, both the social function and the full preference orderings of the agents are expressed beforehand.
+Nevertheless, requiring agents to express full preference orderings can be prohibitively costly (in term of cognitive and communication cost), especially for decisions with large sets of alternatives.
 This observation has motivated a number of recent works considering social choice with partial preference orders \citep{Xia2008, Pini2009, Konczak05} and incremental elicitation \citep{Kalech2011, Lu2011, Naamani-Dery2015} of agents’ preferences.
 Furthermore, several situations for which it may not be easy to precisely define the voting rule exist.
-Indeed, it is possible that the chair has some preferences over the desired aggregation method, but it is still not able to formalize the voting rule upfront.
+Indeed, it is possible that the chair has some preferences over the desired aggregation method, but is not able to formalize the voting rule upfront.
 The work of Cailloux and Endriss \citep{Cailloux2014} provides elicitation methods for a quite general class of rules based on weak orders.
@@
 
-In this work we assume fixed, but unknown, a profile $\profile^*$ and a weight vector $\w^*$.
+In this work \commentOC{Any idea why the paragraph beginnings are not distinguished by either a separation from the left margin or a wider vertical space?
+(As it should be for typographical correctness.) If because of rjcia style, either we leave it like this (“their mistake”), or we correct it for them.} we assume fixed, but unknown, a profile $\profile^* = (\pref^*_j, j \in \{1, \ldots, n\})$ and a weight vector $\w^*$.
 Our knowledge at a given time of the preference of agent $j$ is encoded by a partial order over the alternatives, thus a transitive and asymmetric binary relation, denoted by $\ppref_j$; we assume that preference information is truthful, i.e.
-$a \ppref_j b ⇒ a \pref_j^* b$.
+$a \ppref_j b ⇒ a \pref_j^* b$ \commentOC{Or simply ${\ppref_j} \subseteq {\pref_j^*}$, if you need to save space}.
 %We use $\pinc$ to denote incomparability, that is $a \pinc_{j} b$ iff $a \nppref_j b \wedge b \nppref_j a$.
@@
 
-Our knowledge regarding the weights of the scoring rule is, instead, represented by
+Our knowledge regarding the weights of the scoring rule is represented by
 %We also assume that the weights of the scoring rule are only partially specified.
@@
 Of course it may be difficult for real decision makers to state these preferences, thus we can elicit them, for instance, by showing a complete profile of a small synthetic election and asking who should be elected in this case.
+\commentOC{Not entirely true as stated here.
+This works only in a subset of the case.
+So this remark should be dropped or amended, to say that we worked on this problem and it is still a work in progress to come up with an elicitation procedure that uses only questions that can effectively be asked using such a small synthetic election, and that it is not discussed further in this short article for lack of space.
+Also I’d remove “Of course”, it’s not obviously true.}
 Such requirements are encoded with linear constraints about the vector $\w$ and the set of these constraints is denoted by $\Co_W$.
-We use $\pw \subseteq \W$ to denote the set of weight vectors compatible with the preferences expressed by the chair.
+We use $\pw \subseteq \W$ \commentOC{Not defined, I believe (maybe it’s not absolutely necessary to define it, but then the symbol must not be used).} to denote the set of weight vectors compatible with the preferences expressed by the chair.
 
@@
 \label{sec:mmr}
-As a decision criterion to determine a winner, we propose to use minimax regret \citep{Savage1954} . 
+As a decision criterion to determine a winner, we propose to use minimax regret \citep{Savage1954}. 
 %Minimax regret \citep{Savage1954} is a decision criterion that has been used for robust optimization under data uncertainty \citep{Kouvelis1997} as well as in decision-making with uncertain utility values \citep{Salo2001,Boutilier2006}.
@@
 % about the voting rule and the agents' preferences.
-The alternative that minimize this error is selected as winner, providing us with a form of robust optimization.
-The maximum regret is considered by assuming that an adversary can both 1) extend the partial profile $\pprofile$ into a complete one, and 2) instantiate the weights choosing among any weight vector in $\pw$.
+The alternatives that minimize this error are selected as tied winners, providing us with a form of robust optimization.
+The maximum regret, given our current knowledge and an alternative $x$, is the highest possible difference between the score of $x$ and the score achievable by any alternative in any state compatible with our current knowledge.
+\commentOC{Added a sentence because we need to explain what this adversary represents, otherwise the reader might not understand that it is a fictitious way of choosing the worst possible scenario, not a real adversary.} It is considered by assuming that an adversary can both 1) extend the partial profile $\pprofile$ into a complete one, and 2) instantiate the weights choosing among any weight vector in $\pw$.
 We formalize the notion of minimax regret in multiple steps.
@@
 We distinguish between questions asked to the agents and questions asked to the chair.
-For the first we consider comparison queries that ask a particular agent to compare two alternatives. Then, the partial profile $\pprofile$ is augmented on the bases of the agent's answer.
-The latter, instead, aim at refining our knowledge about the scoring rule; in particular, we want to acquire constraints of the type:
+For the first we consider comparison queries that ask a particular agent to compare two alternatives. Then, the partial profile $\pprofile$ is augmented on the basis of the agent's answer.
+The latter, instead, aims at refining our knowledge about the scoring rule; in particular, we assume we can acquire constraints of the type:
 \[ w_{r} - w_{r+1} \geq \lambda (w_{r+1} - w_{r+2}) \] 
@@
 
-The next step is to test our strategies in order to compare the performance of our interleaved elicitation approach that mix questions to the chair and to the agents, to a more classical approach that elicit the rule first and then the agents preferences (or vice-versa).
+The next step is to test our strategies in order to compare the performance of our interleaved elicitation approach that mixes questions to the chair and to the agents, to a more classical approach that elicits the rule first and then the agents preferences (or vice-versa).
 

### 2019-03-30 draft.tex
Comments

@@
 \newcommand{\pref}{\succ}%real, connected pref, strict
+\newcommand{\prefeq}{\succeq}%real, connected pref, strict
 \newcommand{\prefr}{{\succ}^\text{r}}%real, connected pref, strict
-\newcommand{\ppreflarge}{\succeq^\text{p}}%partial pref
+\newcommand{\pprefeq}{\succeq^\text{p}}%partial pref
 \newcommand{\ppref}{\succ^\text{p}}%partial pref
@@
 
-\newrelation{\pinc}{\!\parallel\!}%partial pref, complement (incomparable)
-%\newrelation{\pinc}{Q^\text{p}}%partial pref, complement (incomparable)
+\newrelation{\prefinc}{\!\parallel\!}%partial pref, complement (incomparable)
+\newrelation{\pinc}{\bowtie^\text{p}}
+%\newrelation{\prefinc}{Q^\text{p}}%partial pref, complement (incomparable)
 
@@
 In this work we assume that preference information is truthful, i.e. $a \ppref_j b ⇒ a \pref_j^* b$.
-We use $\pinc$ to denote incomparability, that is $a \pinc_{j} b$ iff $a \nppref_j b \wedge b \nppref_j a$.
+%We use $\prefinc$ to denote incomparability, that is $a \prefinc_{j} b$ iff $a \nppref_j b \wedge b \nppref_j a$.
 An incomplete profile $\pprofile = (\ppref_1, \ldots, \ppref_n)$ maps each agent to a partial preference.
@@
 The adversary has to make the score of $y$ as high as possible, and the score of $x$ as low as possible. 
-To do this, he should complete $\ppref_j$ to $\pref_j$ by putting above $x$ as many alternatives as he can, that is, all the alternatives except those that are known to be worse than $x$ (those $a$ such that $x \ppref_j a$); and similarly, put below $y$ all the alternatives he can, thus, put above $y$ only those $a$ such that $a \ppref_j y$.
-Sometimes these two objectives conflict: when an alternative should go above $x$ according to the first objective and below $y$ according to the second one (because $¬(x \ppref_j a) ∧ ¬(a \ppref_j y)$), and $x$ is known to be better than $y$ (thus $x \ppref_j y$).
+To do this, he should complete $\ppref_j$ to $\pref_j$ by putting above $x$ as many alternatives as he can, that is, all the alternatives except those that are known to be worse than $x$ (those $a$ such that $x \pprefeq_j a$); and similarly, put below $y$ all the alternatives he can, thus, put above $y$ only those $a$ such that $a \ppref_j y$.
+Sometimes these two objectives conflict: when an alternative should go above $x$ according to the first objective and below $y$ according to the second one (because $¬(x \pprefeq_j a) ∧ ¬(a \ppref_j y)$), and $x$ is known to be better than $y$ (thus $x \pprefeq_j y$).
 In this case, the first objective should take priority, and $a$ should be put above $x$, which will move both $x$ and $y$ one rank lower than if $a$ had been put below $y$. 
@@
 \begin{split}
-a \pref_j x &⇔ ¬(x \ppref_j a)\\
-y \pref_j a &⇔ ¬(a \ppref_j y) ∧ (¬(x \ppref_j y) ∨ (x \ppref_j a)).
+a \pref_j x &⇔ ¬(x \pprefeq_j a)\\
+y \prefeq_j a &⇔ ¬(a \ppref_j y) ∧ (¬(x \pprefeq_j y) ∨ (x \pprefeq_j a)).
 \end{split}
@@
 It follows that $\hat{v}_{j}(x)$, the rank of $x$ in the PMR-maximizing linear order of agent $j$, 
-is $\hat{v}_{j}(x) = 1+\card{A}-\card{{\ppref_j}(x)}$, where ${\ppref_j}(x)$ designates the set of alternatives that are less good than $x$ according to $\ppref_j$, and the rank of $y$ is $\hat{v}_{j}(y)=1+\card{{\pprefinv_j}(y)}+\beta$, where $\beta = \card{A} - \card{{\ppref_j}(x)}$ if $(x \ppref_j y)$ and $\beta = 0$ otherwise.
+is $\hat{v}_{j}(x) = 1+\card{A}-\card{{\pprefeq_j}(x)}$, where ${\pprefeq_j}(x)$ designates the set of alternatives that are less good than $x$ according to $\pprefeq_j$ (thus including $x$ itself), and the rank of $y$ is $\hat{v}_{j}(y)=1+\card{{\pprefinv_j}(y)}+\beta$, where $\beta = \card{{\pinc_j}(x)}$ if $(x \pprefeq_j y)$ and $\beta = 0$ otherwise and with ${\pinc_j}(x)$ designating the alternatives incomparable with $x$ in $\pprefeq_j$.
 
@@
 
-The results are displayed in \cref{fig:xp1,fig:xp2,fig:xp3}.
-In these tables, the strategies are designated by Rnd for Random, T.
-ph.
-for Two phases, EC for Extreme completions, and Pes.
-for Pessimistic.
+The results are displayed in \cref{fig:xp1,fig:xp2,fig:xp3}, where strategies are designated by Rnd for Random, T. ph. for Two phases, EC for Extreme completions, and Pes. for Pessimistic.
 
@@
 For a given $j$, let $\beta$ be the number of alternatives that are incomparable with $x$ and $y$:
-\[ \beta_{j} = \mid \{ c : c \pinc_{j} y \wedge c \pinc_{j} x \} \mid \]
+\[ \beta_{j} = \mid \{ c : c \prefinc_{j} y \wedge c \prefinc_{j} x \} \mid \]
 $x$ can be ranked between $t_{1}(j)=\mid \{ c \in A : c \ppref_{j} y \wedge x \nppref_{j} c \} \mid $ and position $t_{2}(j)=t_{1}(j)+\beta_{j}$.

### 2019-03-31 RJCIA2019/short_draft.tex
corrected according to the comments

--- 2019-03-29 RJCIA2019/short_draft.tex
@@
 \usepackage[T1]{fontenc}
-\usepackage{babel}
+%\usepackage[english]{babel}
 \usepackage{times}
@@
 {\em
-	Social choice deals with the problem of determining a consensus choice from the preferences of different agents (voters).
+	Social choice deals with the problem of determining a consensus choice from the preferences of different agents.
 In the classical setting, the voting rule is fixed beforehand and full information concerning the preferences of the agents is provided.
+	Recently, the assumption of full preference information has been questioned by a number of researchers and several methods for eliciting preferences have been proposed.
+%	\commentOC{This “we go one step further” sounds odd here. I suggest one more sentence about the normal elicitation setting with only the agents preferences partially specified.}
 	In this paper we go one step further and we assume that both the voting rule and the agents preferences are partially specified.
-In this setting, we provide an interactive elicitation protocol based on minimax regret and develop several query strategies that interleave questions to the chair and questions to the agents in order to acquire the most relevant information in order to quickly converge to optimal or a near-optimal alternative.
+In this setting, we present an interactive elicitation protocol based on minimax regret and develop several query strategies that interleave questions to the chair and questions to the agents in order to attempt to acquire the most relevant information in order to quickly converge to optimal or a near-optimal alternative.
 }
@@
 %In this contexts, a natural approach consists in looking at methods from social choice and see how they can be adapted for group decision-making in a computerized setting.
-In a traditional social choice setting both the social function and the full preference orderings of the agents are expressed beforehand.
-Nevertheless, sometimes requiring agents to express full preference orderings can be prohibitively costly (in term of cognitive and communication cost), especially for decisions with large sets of alternatives.
+In a traditional social choice setting, both the social function and the full preference orderings of the agents are expressed beforehand.
+Nevertheless, requiring agents to express full preference orderings can be prohibitively costly (in terms of cognitive and communication cost), especially for decisions with large sets of alternatives.
 This observation has motivated a number of recent works considering social choice with partial preference orders \citep{Xia2008, Pini2009, Konczak05} and incremental elicitation \citep{Kalech2011, Lu2011, Naamani-Dery2015} of agents’ preferences.
 Furthermore, several situations for which it may not be easy to precisely define the voting rule exist.
-Indeed, it is possible that the chair has some preferences over the desired aggregation method, but it is still not able to formalize the voting rule upfront.
+Indeed, it is possible that the chair has some preferences over the desired aggregation method, but is not able to formalize the voting rule upfront.
 The work of Cailloux and Endriss \citep{Cailloux2014} provides elicitation methods for a quite general class of rules based on weak orders.
@@
 We develop methods for computing the minimax-optimal alternative using positional scoring rules and we provide incremental elicitation methods to acquire relevant preference information.
-We then discuss several heuristics that determine queries, either to a voter or to the committee, that quickly reduce minimax regret.
+We then discuss several heuristics that determine queries, either to an agent or to the committee, that quickly reduce minimax regret.
 While previous works have considered either partial information about the agents preferences or a partially specified aggregation method, we do not know of any work considering both sources of uncertainty at the same time.
@@
 \label{sec:background}
-We assume defined a set $A$ of $m$ alternatives (products, restaurants, public projects, etc.) and a set $\set{1, …, n}$ of agents (voters).
+We assume defined a set $A$ of $m$ alternatives (products, restaurants, public projects, etc.) and a set $\set{1, …, n}$ of agents.
 Each agent $j$ comes from an infinite set $\N$ of potential agents and is associated to her “real” preference order $\pref_j \in \linors$ which is a linear order (connected, transitive, asymmetric relation) over the alternatives.
@@
 An alternative obtains a score that depends on the rank obtained in each of the preference orders and the winners are the alternatives with highest scores.
-
-In this work we assume fixed, but unknown, a profile $\profile^*$ and a weight vector $\w^*$.
+In this work we assume fixed, but unknown, a profile $\profile^* = (\pref^*_j, j \in \{1, \ldots, n\})$ and a weight vector $\w^*$.
 Our knowledge at a given time of the preference of agent $j$ is encoded by a partial order over the alternatives, thus a transitive and asymmetric binary relation, denoted by $\ppref_j$; we assume that preference information is truthful, i.e.
+%${\ppref_j} \subseteq {\pref_j^*}$.
 $a \ppref_j b ⇒ a \pref_j^* b$.
+%\commentOC{Or simply ${\ppref_j} \subseteq {\pref_j^*}$, if you need to save space}
 %We use $\pinc$ to denote incomparability, that is $a \pinc_{j} b$ iff $a \nppref_j b \wedge b \nppref_j a$.
@@
 the chair is able to specify additional preferences about how the social choice function should behave. 
-Of course it may be difficult for real decision makers to state these preferences, thus we can elicit them, for instance, by showing a complete profile of a small synthetic election and asking who should be elected in this case.
+%Of course it may be difficult for real decision makers to state these preferences, thus we can elicit them, for instance, by showing a complete profile of a small synthetic election and asking who should be elected in this case.
+\commentOC{Not entirely true as stated here.
+This works only in a subset of the case.
+So this remark should be dropped or amended, to say that we worked on this problem and it is still a work in progress to come up with an elicitation procedure that uses only questions that can effectively be asked using such a small synthetic election, and that it is not discussed further in this short article for lack of space.
+Also I’d remove “Of course”, it’s not obviously true.}
 Such requirements are encoded with linear constraints about the vector $\w$ and the set of these constraints is denoted by $\Co_W$.
-We use $\pw \subseteq \W$ to denote the set of weight vectors compatible with the preferences expressed by the chair.
+Given the set of convex weight vectors $\W$, we use $\pw \subseteq \W$ to denote the set of weight vectors compatible with the preferences expressed by the chair.
 
@@
 % about the voting rule and the agents' preferences.
-The alternative that minimize this error is selected as winner, providing us with a form of robust optimization.
-The maximum regret is considered by assuming that an adversary can both 1) extend the partial profile $\pprofile$ into a complete one, and 2) instantiate the weights choosing among any weight vector in $\pw$.
+The alternatives that minimize this error are selected as tied winners, providing us with a form of robust optimization.
+The maximum regret of an alternative is the highest possible difference between its score and the one achievable by any alternative in any state compatible with our current knowledge.
+%The maximum regret, given our current knowledge and an alternative $x$, is the highest possible difference between the score of $x$ and the score achievable by any alternative in any state compatible with our current knowledge.
+It is considered by assuming that an adversary can both 1) extend the partial profile $\pprofile$ into a complete one, and 2) instantiate the weights choosing among any weight vector in $\pw$.
 We formalize the notion of minimax regret in multiple steps.
@@
 \[\Regret(x, \profile, \w) = \max_{y \in A} s(y; \profile,\w) - s(x; \profile, \w).\]
-The pairwise max regret $\PMR(x,y;\pprofile,W)$ of $x$ relative to $y$ given partial profile $\pprofile$ and the set of weights $W$ is the worst-case loss of choosing $x$ instead of $y$ under all possible realizations of the full profile {\em and} all possible instantiations of the weights.
+The pairwise max regret $\PMR(x,y;\pprofile,W)$ of $x$ relative to $y$ given partial profile $\pprofile$ and the set of weights $W$ is the worst-case loss of choosing $x$ instead of $y$ under all possible realizations of the full profile {\em and} weights.
 Max regret $\MR(x;\pprofile,W)$ is the worst-case loss of $x$ and $\MMR(\pprofile,W)$ is the value of minimax regret obtained when recommending a minimax optimal alternative $x^*_{\pprofile, W}$.
@@
 
-The \strat{Two phase} strategy asks a predefined, non adaptive sequence of $m-2$ questions to the chair and then it only asks questions about the voters, using questions as defined in the \strat{Pessimistic} strategy.
+The \strat{Two phase} strategy asks a predefined, non adaptive sequence of $m-2$ questions to the chair and then it only asks questions about the agents, using questions as defined in the \strat{Pessimistic} strategy.
 
@@
 
-Assume we have a profile of $3$ agents ranking $4$ alternatives. We can represent it by columns where each of them represents the preference ordering of one voter.
+Assume we have a profile of $3$ agents ranking $4$ alternatives. We can represent it by columns where each of them represents the preference ordering of one agent.
 \[

### 2019-04-01 RJCIA2019/short_draft.tex
more corrections

@@
 %In this contexts, a natural approach consists in looking at methods from social choice and see how they can be adapted for group decision-making in a computerized setting.
-In a traditional social choice setting, both the social function and the full preference orderings of the agents are expressed beforehand.
+In a traditional social choice setting, both the social choice function and the full preference orderings of the agents are expressed beforehand.
 Nevertheless, requiring agents to express full preference orderings can be prohibitively costly (in terms of cognitive and communication cost), especially for decisions with large sets of alternatives.
@@
 \label{sec:background}
-We assume defined a set $A$ of $m$ alternatives (products, restaurants, public projects, etc.) and a set $\set{1, …, n}$ of agents.
+We consider a set $A$ of $m$ alternatives (products, restaurants, public projects, etc.) and a set $\set{1, …, n}$ of agents.
 Each agent $j$ comes from an infinite set $\N$ of potential agents and is associated to her “real” preference order $\pref_j \in \linors$ which is a linear order (connected, transitive, asymmetric relation) over the alternatives.

### 2019-04-03 RJCIA2019/short_draft.tex
added sentence about PMR computation

@@
 Such requirements are encoded with linear constraints about the vector $\w$ and the set of these constraints is denoted by $\Co_W$.
-Given the set of convex weight vectors $\W$, we use $\pw \subseteq \W$ to denote the set of weight vectors compatible with the preferences expressed by the chair.
+Given the set of convex weight vectors $\W$, we use $\pw \subseteq \W$ to denote the set of weight vectors compatible with the chair's preferences.
 
@@
 %In this work we consider the simultaneous presence of uncertainty in the agents' preferences and uncertainty in the weights.
-We use {\em maximum regret} to quantify the worst-case error, which measures, intuitively, how far an alternative is from the optimal one given current knowledge.
+We use {\em maximum regret} to quantify the worst-case error, which measures, intuitively, how far an alternative is from the optimal one given current knowledge; 
 % about the voting rule and the agents' preferences.
-The alternatives that minimize this error are selected as tied winners, providing us with a form of robust optimization.
+the alternatives that minimize this error are selected as tied winners.
+%, providing us with a form of robust optimization.
 The maximum regret of an alternative is the highest possible difference between its score and the one achievable by any alternative in any state compatible with our current knowledge.
@@
 By picking as consensus choice an alternative associated with minimax regret, we can provide a recommendation that gives worst-case guarantees, giving some robustness in face of uncertainty. 
+$\PMR$ can be computed by adapting the reasoning of Lu and Boutilier \cite{Lu2011} to the case of uncertain weights using linear programming.
 %In cases of ties in minimax regret, we can either decide to return all minimax alternatives $A^*_{\pprofile, W}$ as winners or to pick just one of them using some tie-breaking strategy.

### 2019-04-03 draft.tex
revision: minors and rephrasings

@@
 In the classical setting, the voting rule is fixed beforehand and full information concerning the preferences of the agents is provided.
+
 Recently, the assumption of full preference information has been questioned by a number of researchers and several methods for eliciting preferences have been proposed.
-
 In this paper we go one step further and we assume that both the voting rule and the agents preferences are partially specified.
+
 Focusing on positional scoring rules, we assume that the chair, while  not able to give a precise definition of the rule, is capable of answering simple questions  requiring to pick a winner from a specific  example profile.
@@
 
-We propose a method  for robust approximate winner determination in this setting with minimax regret. 
-We then provide an interactive elicitation protocol based on minimax regret
-and develop several query strategies that interleave questions to the chair and questions to the agents in order to acquire the most relevant information in order to quickly converge to optimal or a near-optimal alternative.
+In this setting, we propose a method  for robust approximate winner determination with minimax regret. 
+Moreover, we provide an interactive elicitation protocol based on minimax regret
+and develop several query strategies that interleave questions to the chair and questions to the agents in order to attempt to acquire the most relevant information in order to quickly converge to optimal or a near-optimal alternative.
 \end{abstract}
@@
 
-The traditional approach to social choice assumes that both the social function and the full preference orderings of the agents are expressed beforehand. This represents two strong hypothesis.
-About the second one, requiring agents to express full preference orderings can be prohibitively costly (in term of cognitive and communication cost), especially for decisions with large sets of alternatives.
+The traditional approach to social choice assumes that both the social choice function and the full preference orderings of the agents are expressed beforehand. These represent two strong hypothesis.
+Requiring agents to express full preference orderings can be prohibitively costly (in terms of cognitive and communication cost), especially for decisions with large sets of alternatives.
 This observation has motivated a number of recent works considering social choice with partial preference orders \citep{Xia2008, Pini2009, Konczak05} and incremental elicitation \citep{Kalech2011, Lu2011, Naamani-Dery2015} of agents’ preferences.
 
-The first hypothesis also should be relaxed, for in several situations it may not be easy to precisely define the voting rule.
-Indeed, it is possible that the chair may have some preferences over the desired aggregation method, but may still be not able to formalize the voting rule upfront.
+Also the first hypothesis should be relaxed considering that in several situations it may not be easy to precisely define the voting rule.
+Indeed, it is possible that the chair has some preferences over the desired aggregation method, but is not able to formalize the voting rule upfront.
 The work of \citet{Cailloux2014} provides elicitation methods for a quite general class of rules based on weak orders.
@@
 
-In this paper we consider that both the agents’ preferences and the social choice rule are partially specified.
-We develop methods for computing the minimax-optimal alternative for scoring rules with partial agent preference information and partial information about the weights of the scoring rule.
+In this paper we consider that both the agents’ preferences and the social choice rule are partially specified and we develop methods for computing the minimax-optimal alternative under these assumptions.
+%changed from: We develop methods for computing the minimax-optimal alternative for scoring rules with partial agent preference information and partial information about the weights of the scoring rule.
 While previous works have considered either partial information about the agents preferences or a partially specified aggregation method, we do not know of any work considering both sources of uncertainty at the same time.
@@
 In this work, we focus on positional scoring rules, that are a particularly common method used to aggregate rankings and determine a winner.
-We also address the problem of elicitation, providing incremental elicitation methods to acquire relevant preference information; we discuss  several heuristics that determine queries that quickly reduce minimax regret.
-In particular, our query strategies focus simultaneously on reduction of relevant preference and voting rule uncertainty.
+We also address the problem of elicitation, providing incremental elicitation methods to acquire relevant preference information.
+We then discuss several heuristics that attempt to simultaneously reduce the preference and voting rule uncertainty by determining queries, either to an agent or to the chair, that quickly reduce minimax regret.
+%In particular, our query strategies focus simultaneously on reduction of relevant preference and voting rule uncertainty.
 
 The paper is organized as follows.
-In Section \ref{sec:background} we provide the necessary background.
-We introduce the minimax criterion, that selects a winner that minimizes the worst possible regret, in Section \ref{sec:mmr}.
-In Section \ref{sec:elicit} we provide an interactive elicitation protocol based on minimal regret;  in Section \ref{sec:experiments} we present the empirical validation of our approach with simulations; and Section \ref{sec:conclusions} provides some final thoughts.
+In Section \ref{sec:background} we provide the necessary background and in Section \ref{sec:mmr} we introduce the minimax criterion, that selects a winner that minimizes the worst possible regret.
+Then, in Section \ref{sec:elicit} we provide an interactive elicitation protocol based on minimal regret;  in Section \ref{sec:experiments} we present the empirical validation of our approach with simulations; and Section \ref{sec:conclusions} provides some final thoughts.
 
@@
 We now introduce some basic concepts.
-We assume defined a set $A$ of $m$ alternatives (products, restaurants, movies, public projects, job candidates, etc.) and a set $\set{1, …, n}$ of agents (voters); each agent $j$ is associated to her “real” preference order $\pref_j$.
-The agents come from an infinite set $\N$ of potential agents.
-The real preferences of the agents are elements of $\linors$, the linear orders (connected, transitive, asymmetric relations) over the alternatives.
+We consider a set $A$ of $m$ alternatives (products, restaurants, movies, public projects, job candidates, etc.) and a set $\set{1, …, n}$ of agents (voters).
+Each agent $j$ comes from an infinite set $\N$ of potential agents and is associated to her “real” preference order $\pref_j \in \linors$ which is a linear order (connected, transitive, asymmetric relations) over the alternatives.
 Following the social choice nomenclature, we call {\em profile} the association of a preference to each agent, considering a subset of agents from the set $\N$, and denote a profile by $(\pref_1,\ldots,\pref_n)$.
@@
 
-Let $V$ be the set of possible preference profiles (the union for any integer $n$ of the $n$-fold cartesian product of the linear orders over the alternatives).
+Let $V$ be the set of possible preference profiles (the union, for any integer, $n$ of the $n$-fold cartesian product of the linear orders over the alternatives).
 A social choice function $f : V \rightarrow \powersetz{A}$ associates a profile with a set of winners, where $\powersetz{A}$ represents the set of subsets of $A$ except for the emptyset.
@@
 
-A completion of $\ppref_j$ is any linear order $\pref$ that extends $\ppref_j$.
-Let $C(\ppref_j) = \set{{\succ} \in \linors \suchthat {\ppref_j} \subseteq {\succ}}$ be the set of possible completions of $\ppref_i$.
-We let $C(\pprofile)=C(\ppref_1)\times … \times C(\ppref_n)$ be the set of complete profiles extending $p$. Note that $\profile^* \in C(\pprofile)$.
+A completion of $\ppref_j$ is any linear order $\pref$ that extends $\ppref_j$ and we indicate with $C(\ppref_j) = \set{{\succ} \in \linors \suchthat {\ppref_j} \subseteq {\succ}}$ the set of possible completions of $\ppref_i$.
+Then $C(\pprofile)=C(\ppref_1)\times … \times C(\ppref_n)$ is the set of complete profiles extending $p$. Note that $\profile^* \in C(\pprofile)$.
 
@@
 We also assume that the weights of the scoring rule are only partially specified.
-Therefore the vector $(w_1,\ldots,w_m)$  is not known but we are given a set of constraints restraining the possible values that weights can take.
+Therefore, the vector $(w_1,\ldots,w_m)$  is not known but we are given a set of constraints restraining the possible values that weights can take.
 We consider a decreasing sequence of weights:
@@
 
-An important class of scoring rule is the one composed of weights that are a convex sequence \citep{Stein1994,Llamazares2016}, meaning that the difference between the weight of the first position and the weight of the second position is at least as great as the difference between the weights of the second and third positions, etc.
+An important class of scoring rule is the one composed of weights that represent a convex sequence \citep{Stein1994,Llamazares2016}, meaning that the difference between the weight of the first position and the weight of the second position is at least as great as the difference between the weights of the second and third positions, etc.
 \begin{equation} 
@@
 We assume that in addition of basic requirements (monotonicity and convexity), the chair (the person or the organization that is supervising the voting process) is able to specify additional preferences about how the social choice function should behave.
-In this work we assume that preferences of the chair are encoded with linear constraints about the vector $\w$, relating the value of the weights of different positions.
-We use $\pw \subseteq \W$ to denote the set of weight vectors compatible with the preferences expressed by the chair about the scoring vector, and $\Co_W$ to denote the set of linear constraints expressed by the chair.
+In this work we assume that the preferences of the chair are encoded with linear constraints about the vector $\w$, relating the value of the weights of different positions, and the set of these constraints is denoted by $\Co_W$.
+Moreover, we use $\pw \subseteq \W$ to denote the set of weight vectors compatible with the preferences expressed by the chair about the scoring vector.
 
@@
 In this paper, we consider a setting where both the agents' preferences and the preferences of the chair about the voting rule are incomplete.
-Notice that some authors have considered possible and necessary winners assuming a partial profile  \citep{Xia2008} or assuming an incompletely specified scoring rule \citep{Viappiani2018};
-however, we note that, in typical settings, there will be no necessary winner and too many possible winners.
-In practice, however, it is often useful to declare a winner given partial information.
+Some authors have considered possible and necessary winners assuming a partial profile  \citep{Xia2008} or assuming an incompletely specified scoring rule \citep{Viappiani2018};
+however, we note that, in typical settings, there are no necessary winner and too many possible winners.
+In practice it is often useful to declare a winner given partial information.
 
@@
 
-In this work we consider the simultaneous presence of uncertainty in the agents' preferences and uncertainty in the weights.
-Using {\em maximum regret} to quantify the worst-case error, the alternative that minimize this error is selected as winner, providing us with a form of robust optimization.
-Intuitively, the quality of a proposed alternative $a$ is how far from optimal $a$  could be in the worst case, given the current knowledge about the voting rule and about the agents' preferences.
-
-The maximum regret is considered by assuming that an adversary both 1) can extend the partial profile $\pprofile$ into a complete profile, and 2) can instantiate the weights choosing among any weight vector in $\pw$, where $\pprofile$ and $\pw$ represent our knowledge so far.
+In this work, we consider the simultaneous presence of uncertainty in agents' preferences and in weights.
+Using {\em maximum regret} to quantify the worst-case error, the alternatives that minimize this error are selected as tied winners, providing us with a form of robust optimization.
+Intuitively, the quality of a proposed alternative $a$ is how far $a$ is from the optimal one in the worst case, given current knowledge.
+
+The maximum regret is considered by assuming that an adversary can both 1) extend the partial profile $\pprofile$ into a complete profile, and 2) instantiate the weights choosing among any weight vector in $\pw$, where $\pprofile$ and $\pw$ represent our knowledge so far.
 We formalize the notion of minimax regret in multiple steps.
@@
 Max regret $\MR(x;\pprofile,W)$ is the worst-case loss of $x$.
-It is the loss occurred by an adversarial selection of a complete profile $\profile$ extending $\pprofile$ and a selection of $\w \in W$ to maximize the loss between $x$ and the true winner under $\profile$ and $\w$.
+That is the loss occurred as the result of an adversarial selection of the complete profile $\profile \in C(\pprofile)$ and of the scoring vector $\w \in W$ that together maximize the loss between $x$ and the true winner under $\profile$ and $\w$.
 \begin{align}
@@
 
-Notice that if $\MMR(\pprofile, W)\!=\!0$, then $x^{*}_{\pprofile,W}$ is a necessary co-winner; this means that for any valid completion of the profile and any feasible $w \!\in\!
+Notice \commentOC{?} that if $\MMR(\pprofile, W)\!=\!0$, then $x^{*}_{\pprofile,W}$ is a necessary co-winner; this means that for any valid completion of the profile and any feasible $w \!\in\!
 W$, $x^{*}_{\pprofile,W}$ obtains a highest score.
@@
 \paragraph{Computation of minimax regret}
-In order to compute pairwise maximum regret and therefore minimax regret, we adapt the reasoning from \citet{Lu2011} so that we decompose the $\PMR$ into the contributions associated to each agent.
+In order to compute pairwise maximum regret, and therefore minimax regret, we decompose the $\PMR$ into the contributions associated to each agent by adapting the reasoning from \citet{Lu2011}.
 The setting is however more challenging due to the presence of uncertainty in the weights.
@@
 By exploiting the decomposition of the score in terms of votes, we write the actual regret of choosing $x$ instead of $y$ as
+\commentOC{Recall that, in the computation of $s(x; \profile, \w)$, $w_{v_j(x)}$ represents the score that $x$ obtains in the ranking $v_j$ (see Equation \ref{eq:srule}).
+Since scoring rules are additively decomposable, we can decompose the score in terms of votes. Thus, we can write the actual regret of choosing $x$ instead of $y$ as}
 \[
@@
 \]
-and  can rewrite $\PMR$ as follows:
+and we can rewrite $\PMR$ as follows:
 \begin{align*}
@@
 \end{align*}
-Note that in general the inner max will depend on the weights chosen by the outer min.
+Note that in general the inner max depends on the weights chosen by the outer min.
 
 We consider now a procedure for completing a partial profile that was first proposed by \citet{Lu2011} when considering minimax regret with a fixed weight vector.
-As we will show, this procedure can also be used in our case of uncertain weight vector.
+As we will show, this procedure can also be used when the weight vector is not completely known.
 
@@
 This represents the “worst” difference of score, thus the difference of score between $y$ and $x$ under the worst case preferences compatible with $\pprofile$ and $W$, where the worst case is the one that maximizes this difference of score.
-Consider our knowledge $\ppref_j$ of the preference of an agent $j$. 
-The adversary has to make the score of $y$ as high as possible, and the score of $x$ as low as possible. 
+Consider our knowledge $\ppref_j$ about the preference of the agent $j$. 
+The adversary's goal is to make the score of $y$ as high as possible and the score of $x$ as low as possible. 
 To do this, he should complete $\ppref_j$ to $\pref_j$ by putting above $x$ as many alternatives as he can, that is, all the alternatives except those that are known to be worse than $x$ (those $a$ such that $x \pprefeq_j a$); and similarly, put below $y$ all the alternatives he can, thus, put above $y$ only those $a$ such that $a \ppref_j y$.
@@
 It follows that $\hat{v}_{j}(x)$, the rank of $x$ in the PMR-maximizing linear order of agent $j$, 
-is $\hat{v}_{j}(x) = 1+\card{A}-\card{{\pprefeq_j}(x)}$, where ${\pprefeq_j}(x)$ designates the set of alternatives that are less good than $x$ according to $\pprefeq_j$ (thus including $x$ itself), and the rank of $y$ is $\hat{v}_{j}(y)=1+\card{{\pprefinv_j}(y)}+\beta$, where $\beta = \card{{\pinc_j}(x)}$ if $(x \pprefeq_j y)$ and $\beta = 0$ otherwise and with ${\pinc_j}(x)$ designating the alternatives incomparable with $x$ in $\pprefeq_j$.
+is $\hat{v}_{j}(x) = 1+\card{A}-\card{{\pprefeq_j}(x)}$, where ${\pprefeq_j}(x)$ designates the set of alternatives that are less good than $x$ according to $\pprefeq_j$ (thus including $x$ itself) \commentOC{Is it not better write $\hat{v}_{j}(x) = 1+\card{A}-\card{{\ppref_j}(x)}$?
+I guess it's for coherence for the $\beta$ expression but it doesn't make much sense pointing out we're removing and adding x.}, and the rank of $y$ is $\hat{v}_{j}(y)=1+\card{{\pprefinv_j}(y)}+\beta$, where $\beta = \card{{\pinc_j}(x)}$ if $(x \pprefeq_j y)$ and $\beta = 0$ otherwise and with ${\pinc_j}(x)$ designating the alternatives incomparable with $x$ in $\pprefeq_j$ \commentOC{Still not good.
+In the set of alternatives incomparable with $x$ there could be alternatives strictly better than $y$.
+It is exactly the problem we had before.
+Instead, $\beta$ represents the number of alternatives incomparable with $x$ that are no better than $y$: $\beta = \card{A \setminus ({\pprefeq_j}(x) \cup {\pprefinv_j}(y))}$ }.
 
@@
 \end{align}
-where the $\hat{\alpha}_{r}^{y}$ (resp. $\hat{\alpha}_{r}^{x}$)  is the number of times $y$ (resp. $x$) is at rank $r$ in the rankings of the completed profile $\hat{\profile}$.
+where the $\hat{\alpha}_{r}^{y}$ (resp. $\hat{\alpha}_{r}^{x}$)  is the number of times $y$ (resp. $x$) is at rank $r$ in the rankings of the completed \commentOC{?} profile $\hat{\profile}$.
 \end{claim}
@@
 Recall that the preferences of the chair are encoded with linear constraints $\Co_{W}$.
-The pairwise max regret $\PMR(x,y; \pprofile,W)$ can be obtained as the solution of the following linear program defined on the variables $w_1, …, w_m$, the weights attached to the different positions.
+The pairwise max regret $\PMR(x,y; \pprofile,W)$ can be obtained as the solution of the following linear program defined on the variables $w_1, …, w_m$, which represent the weights attached to different positions.
 \begin{align*}
@@
 
-The max regret $\MR(x; \pprofile, W)$ is determined by considering the pairwise regret of $x$ with each other alternative in $A$.
+The max regret $\MR(x; \pprofile, W)$ is determined by considering the pairwise regret of $x$ with all other alternatives in $A$.
 Optimal alternatives w.r.t. minimax regret are the ones with least max regret. 
-Notice that, whenever the PMR of an alternative $x$ (against some other alternative) exceeds the best MR value found so far, we don't need to further evaluate $x$, as it can't be optimal. 
+Notice \commentOC{?} that, whenever the PMR of an alternative $x$ (against some other alternative) exceeds the best MR value found so far, we don't need to further evaluate $x$, as it can't be optimal.
+\commentOC{?}
 This idea can be exploited further by adopting a minimax-search tree \citep{Braziunas2011}.
@@
 We propose an incremental elicitation method based on minimax regret.
-At each step, the system may either ask a question to one of the agents, or ask a question to the chair about the voting rule. 
+At each step, the system may ask a question either to one of the agents about her preferences or to the chair about the voting rule. 
 The goal is to acquire relevant information to reduce minimax regret as quickly as possible.
@@
 %Another common type of queries are {\em top-k}, asking to each agent her $k$ most preferred alternatives.
-The effect of a response to a question asked to an agent is to increase our knowledge about the agents rankings, thus augmenting the partial profile $\pprofile$. 
+The effect of a response to a question asked to an agent is the increase in our knowledge about the agents rankings, thus augmenting the partial profile $\pprofile$. 
 If agent $j$ answers a comparison query stating that alternative $a$ is preferred to $b$, then the partial order $\ppref_j$ is augmented with $a \ppref_j b$ and by transitive closure.
@@
 \paragraph{Building concrete questions for the chair}
-As we assume the weights constitute the utility components of the chair, it might be reasonable to assume, 
+As we assume the weights constitute the utility components of the chair, it might be reasonable to assume
 %as we do here, 
 that the chair is able to answer such abstract questions in our setting.
-However, it is important to make sure that the question can also, in principle, be asked in a more concrete way, in terms of winners of example profiles.
-This permits to test whether the chair understands the question as we do; this permits to relate the preference of the chair  to her choice behavior in the economic sense; and this will be necessary for an ordinal extension of our work where the scores would not be considered as cardinal utilities.
+However, it is important to make sure that a question can also, in principle, be asked in a more concrete way, in terms of winners of example profiles.
+This permits to test whether the chair understands the question as we do and to relate the preference of the chair to her choice behavior in the economic sense.
+Furthermore this will be necessary for an ordinal extension of our work where the scores would not be considered as cardinal utilities.
 Thus, our task is to build a profile, given $\lambda$ and $r ≤ m-2$, in such a way that the set of (tied) winners picked by the chair reveals whether $w_{r} - w_{r+1} \geq \lambda (w_{r+1} - w_{r+2})$.
@@
 
-Observe that the question may be defined equivalently as whether $q w_{r} + p w_{r+2} ≥ (p + q) w_{r+1}$, where $p, q$ are natural numbers. 
+Observe that the question may be defined equivalently as $q \cdot w_{r} + p \cdot w_{r+2} ≥ (p + q) \cdot w_{r+1}$, where $p, q$ are natural numbers. 
 As a first attempt to make this question concrete, let us define a profile $P$ containing $p+q$ agents. 
@@
 Because weights are non increasing, this guarantees, with $\delta = p + q$, that the score of $a$ is not lower than the one of $c$ (it is even strictly higher, thanks to the strict inequality).
+\commentOC{Here using the strict inequality assumption.}
 
@@
 We define here the various strategies we tested experimentally.
-A strategy is a function (or a random process) that gives us, given our partial knowledge so far $(\pprofile, W)$, a question that should be asked, according to that strategy.
+A strategy is a function (or a random process) that gives us, given our partial knowledge so far $(\pprofile, W)$, a question that should be asked according to that strategy.
 
@@
 Choosing the questions purely randomly however, that is, independently of what we know already, would be pointless, as we would most of the time ask questions we already know the answer of.
-Thus, that strategy choses questions in a minimally “clever” way, just by picking questions in a set of a priori relevant questions.
+Thus, this strategy choses questions in a minimally “clever” way, just by picking questions in a set of a priori relevant questions.
 The \strat{Random} strategy first decides with a probability of $1/2$ each whether it will ask a question about weights or a question about a preference ordering (unless the profile is already known entirely).
@@
 (\ref{eq:tau1}), to find the position $r$ that is most valuable to ask about (the one that maximizes $\abs{\bar{\w}_r - \w^{\tau}_r}$), and choose $\lambda$ as the middle of the interval of possible values for that rank.
-Instead, if $\tau_{1} > \tau_{2}$ we ask a question to one of the agent.
+Instead, if $\tau_{1} > \tau_{2}$ we ask a question to one of the agents.
 We select the question by checking for each agent $j$ the difference between the difference of the ranks of $x$ and $y$ in the profile that minimizes compared to the one that maximizes the difference of scores, and pick an agent related to the highest difference, then pick $x$ or $y$ with $1/2$ chances as the first alternative of the question, and pick an incomparable alternative equiprobably as the second one.
@@
 The \strat{Pessimistic} strategy considers as possible questions the ones defined by the \strat{Random} strategy (with the difference that a threshold is used: if for some rank $r$ the interval of possible values for $\lambda$ is not larger than $0.1$, the question is not considered).
-It uses a variant of the $\max$ as an aggregator: if the maximal $\MMR$ of two questions are equal, it prefers the question that has the lowest $\MMR$.
+It uses a variant of the $\max$ as an aggregator: if the maximal $\MMR$ of two questions are equal, it prefers the question that has the lowest $\MMR$ \commentOC{if the maximal $\MMR$ of two questions are equal, then it considers the other $\MMR$ values, that are the one associated to the opposite answer, preferring the question with the lowest of this value.}.
 We expect this strategy to perform very well, but only for very small problem instances: its complexity is in $O(n^2 m^5)$, because we consider $O(m^2)$ questions for each agent and need for each question to compute $\MMR$ twice, whose complexity is $O(nm^3)$.
@@
 The \strat{Two phase} strategy asks a predefined, non adaptive sequence of $m-2$ questions in order to gather informations about the weights $\w$ of the scoring rule, using one question per rank (except the extreme ones) as defined in the other strategies, thus, each cutting the initial interval of possibilities into two equal parts.
-Then it only asks questions about the voters, using questions as defined in the \strat{Pessimistic} strategy.
+Then it only asks questions about the agents, using questions as defined in the \strat{Pessimistic} strategy.
 %TODO Then use minimax regret as in Lu and Boutilier. check what’s this.
@@
 \label{sec:conclusions}
-In this paper we have considered a  social choice setting with partial  information about the agent's  
-preferences and as well a partially specified voting rule.
-We have proposed the use of minimax regret as a means of robust winner determination in this setting, and as well as to guide the process of simultaneous elicitation of preferences and voting rule.
+In this paper we have considered a social choice setting with partial information about the agent's preferences and a partially specified voting rule.
+In this setting, we have proposed the use of minimax regret both as a means of robust winner determination as well as a guide to the process of simultaneous elicitation of preferences and voting rule.
 Our experimental results %on randomly generated and real world data sets 
@@
 \bibliography{biblio}
-\bibliographystyle{named}
-%\bibliographystyle{plain} 
+%\bibliographystyle{named}
+\bibliographystyle{plain} 
 %}

### 2019-04-03 draft.tex
Minor, bib

@@
 \newcommand{\commentOC}[1]{\textcolor{blue}{\small$\big[$OC: #1$\big]$}}
+\newcommand{\commentBN}[1]{\textcolor{red}{\small$\big[$BN: #1$\big]$}}
 
@@
 
-Notice \commentOC{?} that if $\MMR(\pprofile, W)\!=\!0$, then $x^{*}_{\pprofile,W}$ is a necessary co-winner; this means that for any valid completion of the profile and any feasible $w \!\in\!
+Observe that if $\MMR(\pprofile, W)\!=\!0$, then $x^{*}_{\pprofile,W}$ is a necessary co-winner; this means that for any valid completion of the profile and any feasible $w \!\in\!
 W$, $x^{*}_{\pprofile,W}$ obtains a highest score.
@@
 By exploiting the decomposition of the score in terms of votes, we write the actual regret of choosing $x$ instead of $y$ as
-\commentOC{Recall that, in the computation of $s(x; \profile, \w)$, $w_{v_j(x)}$ represents the score that $x$ obtains in the ranking $v_j$ (see Equation \ref{eq:srule}).
+\commentBN{Recall that, in the computation of $s(x; \profile, \w)$, $w_{v_j(x)}$ represents the score that $x$ obtains in the ranking $v_j$ (see Equation \ref{eq:srule}).
 Since scoring rules are additively decomposable, we can decompose the score in terms of votes. Thus, we can write the actual regret of choosing $x$ instead of $y$ as}
@@
 It follows that $\hat{v}_{j}(x)$, the rank of $x$ in the PMR-maximizing linear order of agent $j$, 
-is $\hat{v}_{j}(x) = 1+\card{A}-\card{{\pprefeq_j}(x)}$, where ${\pprefeq_j}(x)$ designates the set of alternatives that are less good than $x$ according to $\pprefeq_j$ (thus including $x$ itself) \commentOC{Is it not better write $\hat{v}_{j}(x) = 1+\card{A}-\card{{\ppref_j}(x)}$?
-I guess it's for coherence for the $\beta$ expression but it doesn't make much sense pointing out we're removing and adding x.}, and the rank of $y$ is $\hat{v}_{j}(y)=1+\card{{\pprefinv_j}(y)}+\beta$, where $\beta = \card{{\pinc_j}(x)}$ if $(x \pprefeq_j y)$ and $\beta = 0$ otherwise and with ${\pinc_j}(x)$ designating the alternatives incomparable with $x$ in $\pprefeq_j$ \commentOC{Still not good.
+is $\hat{v}_{j}(x) = 1+\card{A}-\card{{\pprefeq_j}(x)}$, where ${\pprefeq_j}(x)$ designates the set of alternatives that are less good than $x$ according to $\pprefeq_j$ (thus including $x$ itself) \commentBN{Is it not better write $\hat{v}_{j}(x) = 1+\card{A}-\card{{\ppref_j}(x)}$?
+I guess it's for coherence for the $\beta$ expression but it doesn't make much sense pointing out we're removing and adding x.}, and the rank of $y$ is $\hat{v}_{j}(y)=1+\card{{\pprefinv_j}(y)}+\beta$, where $\beta = \card{{\pinc_j}(x)}$ if $(x \pprefeq_j y)$ and $\beta = 0$ otherwise and with ${\pinc_j}(x)$ designating the alternatives incomparable with $x$ in $\pprefeq_j$ \commentBN{Still not good.
 In the set of alternatives incomparable with $x$ there could be alternatives strictly better than $y$.
@@
 \end{align}
-where the $\hat{\alpha}_{r}^{y}$ (resp. $\hat{\alpha}_{r}^{x}$)  is the number of times $y$ (resp. $x$) is at rank $r$ in the rankings of the completed \commentOC{?} profile $\hat{\profile}$.
+where the $\hat{\alpha}_{r}^{y}$ (resp. $\hat{\alpha}_{r}^{x}$)  is the number of times $y$ (resp. $x$) is at rank $r$ in the rankings of the completed \commentBN{?} profile $\hat{\profile}$.
 \end{claim}
@@
 Optimal alternatives w.r.t. minimax regret are the ones with least max regret. 
-Notice \commentOC{?} that, whenever the PMR of an alternative $x$ (against some other alternative) exceeds the best MR value found so far, we don't need to further evaluate $x$, as it can't be optimal.
-\commentOC{?}
+Observe that, whenever the PMR of an alternative $x$ (against some other alternative) exceeds the best MR value found so far, we don't need to further evaluate $x$, as it can't be optimal.
+\commentBN{?}
 This idea can be exploited further by adopting a minimax-search tree \citep{Braziunas2011}.
@@
 Because weights are non increasing, this guarantees, with $\delta = p + q$, that the score of $a$ is not lower than the one of $c$ (it is even strictly higher, thanks to the strict inequality).
-\commentOC{Here using the strict inequality assumption.}
+\commentBN{Here using the strict inequality assumption.}
 
@@
 The \strat{Pessimistic} strategy considers as possible questions the ones defined by the \strat{Random} strategy (with the difference that a threshold is used: if for some rank $r$ the interval of possible values for $\lambda$ is not larger than $0.1$, the question is not considered).
-It uses a variant of the $\max$ as an aggregator: if the maximal $\MMR$ of two questions are equal, it prefers the question that has the lowest $\MMR$ \commentOC{if the maximal $\MMR$ of two questions are equal, then it considers the other $\MMR$ values, that are the one associated to the opposite answer, preferring the question with the lowest of this value.}.
+It uses a variant of the $\max$ as an aggregator: if the maximal $\MMR$ of two questions are equal, it prefers the question that has the lowest $\MMR$ \commentBN{if the maximal $\MMR$ of two questions are equal, then it considers the other $\MMR$ values, that are the one associated to the opposite answer, preferring the question with the lowest of this value.}.
 We expect this strategy to perform very well, but only for very small problem instances: its complexity is in $O(n^2 m^5)$, because we consider $O(m^2)$ questions for each agent and need for each question to compute $\MMR$ twice, whose complexity is $O(nm^3)$.
@@
 %\bibliographystyle{named}
-\bibliographystyle{plain} 
+\bibliographystyle{abbrvnat} 
 %}

### 2019-04-03 draft.tex
Minor

@@
 
-%	\tolerance=2000
-%	%Accept overfull hbox up to...
-%	\hfuzz=1cm
-%	%Reduces verbosity about the bad line breaks.
-%	\hbadness 10000
-%	%Reduces verbosity about the underful vboxes.
-%	\vbadness=10000
+\tolerance=2000
+%Accept overfull hbox up to...
+\hfuzz=1cm
+%Reduces verbosity about the bad line breaks.
+\hbadness 10000
+%Reduces verbosity about the underful vboxes.
+\vbadness=10000
 
@@
 
-Scoring rules are additively decomposable.
-%A scoring rule associates each alternative to a score that is given by the sum of points obtained for each agent.
-Recall that when computing $s(x; \profile, \w)$, $w_{v_j(x)}$ is the number of points that $x$ obtains in the ranking $v_j$ (see Equation \ref{eq:srule}).
-By exploiting the decomposition of the score in terms of votes, we write the actual regret of choosing $x$ instead of $y$ as
-\commentBN{Recall that, in the computation of $s(x; \profile, \w)$, $w_{v_j(x)}$ represents the score that $x$ obtains in the ranking $v_j$ (see Equation \ref{eq:srule}).
-Since scoring rules are additively decomposable, we can decompose the score in terms of votes. Thus, we can write the actual regret of choosing $x$ instead of $y$ as}
+Recall that, in the computation of $s(x; \profile, \w)$, $w_{v_j(x)}$ represents the score that $x$ obtains in the ranking $v_j$ (see Equation \ref{eq:srule}).
+Since scoring rules are additively decomposable, we can consider separately the contribution of each voter to the total score. Thus, we can write the actual regret of choosing $x$ instead of $y$ as
 \[
@@
 \end{align}
-where the $\hat{\alpha}_{r}^{y}$ (resp. $\hat{\alpha}_{r}^{x}$)  is the number of times $y$ (resp. $x$) is at rank $r$ in the rankings of the completed \commentBN{?} profile $\hat{\profile}$.
+where $\hat{\alpha}_{r}^{y}$ (resp. $\hat{\alpha}_{r}^{x}$)  is the number of times $y$ (resp. $x$) is at rank $r$ in the complete profile $\hat{\profile}$.
 \end{claim}

### 2019-04-03 draft.tex
Make the complex equation fit the paper
Weak inequality weights

@@
 \begin{align}
-1=w_{1} > w_{2} > \ldots > w_{m}=0. \label{eq:monotone}
+1=w_{1} ≥ w_{2} ≥ \ldots ≥ w_{m}=0. \label{eq:monotone}
 \end{align}
@@
 a \pref_j x &⇔ ¬(x \pprefeq_j a)\\
-y \prefeq_j a &⇔ ¬(a \ppref_j y) ∧ (¬(x \pprefeq_j y) ∨ (x \pprefeq_j a)).
+y \pref_j a &⇔ ¬(a \ppref_j y) ∧ (¬(x \pprefeq_j y) ∨ (x \ppref_j a)).
 \end{split}
@@
 Observe that $a'_t ≥ c'_t, 1 ≤ t ≤ m$ (with strict inequality for $t=2$).
-Because weights are non increasing, this guarantees, with $\delta = p + q$, that the score of $a$ is not lower than the one of $c$ (it is even strictly higher, thanks to the strict inequality).
-\commentBN{Here using the strict inequality assumption.}
+Because weights are non increasing, this guarantees, with $\delta = p + q$, that the score of $a$ is not lower than the one of $c$.
 

### 2019-04-03 draft.tex
Minor

@@
 The \strat{Pessimistic} strategy considers as possible questions the ones defined by the \strat{Random} strategy (with the difference that a threshold is used: if for some rank $r$ the interval of possible values for $\lambda$ is not larger than $0.1$, the question is not considered).
-It uses a variant of the $\max$ as an aggregator: if the maximal $\MMR$ of two questions are equal, it prefers the question that has the lowest $\MMR$ \commentBN{if the maximal $\MMR$ of two questions are equal, then it considers the other $\MMR$ values, that are the one associated to the opposite answer, preferring the question with the lowest of this value.}.
+It uses a variant of the $\max$ as an aggregator: if the maximal $\MMR$ of two questions are equal, then it considers the other $\MMR$ values, that are the one associated to the opposite answer, preferring the question with the lowest of this value.
 We expect this strategy to perform very well, but only for very small problem instances: its complexity is in $O(n^2 m^5)$, because we consider $O(m^2)$ questions for each agent and need for each question to compute $\MMR$ twice, whose complexity is $O(nm^3)$.

### 2019-04-07 draft.tex
Expl small diff weights

@@
 %}
+%\end{document}
+
+\appendix
+\section{Bounding differences of weights}
+We want to check whether we can round PMR values to (for example) $10^{-4}$. Thus, we want to bound the difference of scores (unless it is zero).
+
+Consider $s(a) = w_2 + w_4$, $s(b) = w_3 + w_3$, $w_1 = 1, w_2 = w_3 + \epsilon, w_4 = 0$, with $w_3$ and $\epsilon$ two small positive numbers.
+Then convexity is satisfied and $s(a) - s(b) = \epsilon$.
+
+Note that in this example, $w_3 ≤ \epsilon$, thus the difference of scores is indeed at least the smallest weight!
+
+Consider $w_1 = 1, w_2 = 0.45, w_3 = 0.1, w_4 = 0$, $s(a) - s(b) = (w_2 - w_3) -3 (w_3 - w_4) = 0.35 - 0.30 = 0.05 < w_3$.
+
+Problem: we can make the difference of scores very small, even with $n=2$ voters and $m=3$ alternatives and while satisfying convexity.
+Consider $w_1 = 1, w_2 = \frac{1-\epsilon}{n}, w_3 = 0$, $s(a) - s(b) = (w_1 - w_2) - (n-1) (w_2 - w_3) = w_1 - n w_2 = \epsilon$.
+Choose $\epsilon < \frac{1}{n+1}$ so that $w_2 > \epsilon$ and $n ≥ 2$ to satisfy convexity.
+For example, $\epsilon = 1/1000, n = 2, w_2 = 999/2000$.
 \end{document}
 
-\appendix
 \section{Minimax Computation under Convex Assumption} 
-
 Refer to \citep{Lu2011}

### 2019-04-08 draft.tex
merge

@@
 It follows that $\hat{v}_{j}(x)$, the rank of $x$ in the PMR-maximizing linear order of agent $j$, 
-is $\hat{v}_{j}(x) = 1+\card{A}-\card{{\pprefeq_j}(x)}$, where ${\pprefeq_j}(x)$ designates the set of alternatives that are less good than $x$ according to $\pprefeq_j$ (thus including $x$ itself) \commentBN{Is it not better write $\hat{v}_{j}(x) = 1+\card{A}-\card{{\ppref_j}(x)}$?
-I guess it's for coherence for the $\beta$ expression but it doesn't make much sense pointing out we're removing and adding x.}, and the rank of $y$ is $\hat{v}_{j}(y)=1+\card{{\pprefinv_j}(y)}+\beta$, where $\beta = \card{{\pinc_j}(x)}$ if $(x \pprefeq_j y)$ and $\beta = 0$ otherwise and with ${\pinc_j}(x)$ designating the alternatives incomparable with $x$ in $\pprefeq_j$ \commentBN{Still not good.
+is $\hat{v}_{j}(x) = 1+\card{A}-\card{{\pprefeq_j}(x)}$, where ${\pprefeq_j}(x)$ designates the set of alternatives that are less good than $x$ according to $\pprefeq_j$ (thus including $x$ itself), and the rank of $y$ is $\hat{v}_{j}(y)=1+\card{{\pprefinv_j}(y)}+\beta$, where $\beta = \card{{\pinc_j}(x)}$ if $(x \pprefeq_j y)$ and $\beta = 0$ otherwise and with ${\pinc_j}(x)$ designating the alternatives incomparable with $x$ in $\pprefeq_j$ \commentBN{Still not good.
 In the set of alternatives incomparable with $x$ there could be alternatives strictly better than $y$.

### 2019-04-08 draft.tex
rephrasing the heuristic for search space pruning

@@
 Optimal alternatives w.r.t. minimax regret are the ones with least max regret. 
-Observe that, whenever the PMR of an alternative $x$ (against some other alternative) exceeds the best MR value found so far, we don't need to further evaluate $x$, as it can't be optimal.
-\commentBN{?}
+Observe that, whenever the $\PMR$ of an alternative $x$ (against some other alternative $y$) exceeds the best MR value found so far, we don't need to further evaluate $x$. 
+%, as it can't be optimal. 
+\commentBN{Indeed, the maximum regret of an alternative is the maximum value among all the PMRs, so we already know that $\MR(x) \geq \PMR(x,y)$, which is greater than the current MR.
+Thus, x will never be selected as a winner in the minimizing step.}
 This idea can be exploited further by adopting a minimax-search tree \citep{Braziunas2011}.

### 2019-04-09 draft.tex
beta construction

@@
 a \pref_j x &⇔ ¬(x \pprefeq_j a)\\
-y \pref_j a &⇔ ¬(a \ppref_j y) ∧ (¬(x \pprefeq_j y) ∨ (x \ppref_j a)).
+y \pref_j a &⇔ ¬(a \ppref_j y) ∧ (¬(x \pprefeq_j y) ∨ (x \pprefeq_j a)).
 \end{split}
 \end{align} 
+\commentBN{I think it would be more intuitive writing: \\ $ y \pref_j a ⇔ ¬(a \ppref_j y) ∧ ¬((x \pprefeq_j y) ∧ ¬(x \pprefeq_j a))$}
 We just sketched a proof of the following claim, and leave the rest of the proof to the reader.
@@
 It follows that $\hat{v}_{j}(x)$, the rank of $x$ in the PMR-maximizing linear order of agent $j$, 
-is $\hat{v}_{j}(x) = 1+\card{A}-\card{{\pprefeq_j}(x)}$, where ${\pprefeq_j}(x)$ designates the set of alternatives that are less good than $x$ according to $\pprefeq_j$ (thus including $x$ itself), and the rank of $y$ is $\hat{v}_{j}(y)=1+\card{{\pprefinv_j}(y)}+\beta$, where $\beta = \card{{\pinc_j}(x)}$ if $(x \pprefeq_j y)$ and $\beta = 0$ otherwise and with ${\pinc_j}(x)$ designating the alternatives incomparable with $x$ in $\pprefeq_j$ \commentBN{Still not good.
-In the set of alternatives incomparable with $x$ there could be alternatives strictly better than $y$.
-It is exactly the problem we had before.
-Instead, $\beta$ represents the number of alternatives incomparable with $x$ that are no better than $y$: $\beta = \card{A \setminus ({\pprefeq_j}(x) \cup {\pprefinv_j}(y))}$ }.
+is $\hat{v}_{j}(x) = 1+\card{A}-\card{{\pprefeq_j}(x)}$, where ${\pprefeq_j}(x)$ designates the set of alternatives that are less good than $x$ according to $\pprefeq_j$ (thus including $x$ itself), and the rank of $y$ is $\hat{v}_{j}(y)=1+\card{{\pprefinv_j}(y)}+\card{\beta}$, where $\card{\beta} = \card{A \setminus ({\pprefeq_j}(x) \cup {\pprefinv_j}(y))}$ if $(x \pprefeq_j y)$ and $\card{\beta} = 0$ otherwise.
+In the case $(x \pprefeq_j y)$, intuitively $\beta$ represents the number of alternatives incomparable with $x$ that are no better than $y$.
+Let's reason about what alternatives must be placed above $y$ by negating the second equation of \ref{eq:compl}:
+\begin{align}
+\label{eq:betaproof} 
+\begin{split}
+a \prefeq_j y &⇔ (a \ppref_j y) ∨ ((x \pprefeq_j y) ∧ ¬(x \pprefeq_j a))\\
+a \pref_j y &⇔ (a \neq_j y) ∧ [(a \ppref_j y) ∨ ((x \pprefeq_j y) ∧ ¬(x \pprefeq_j a))]
+\end{split}
+\end{align} 
+But the term in the square brackets implies $(a \neq_j y)$, indeed:
+\[(a \ppref_j y) ∨ ((x \pprefeq_j y) ∧ ¬(x \pprefeq_j a)) \Rightarrow (a \neq_j y)\]
+$(a \ppref_j y) \Rightarrow (a \neq_j y)$ is always true, and we can rewrite $¬(x \pprefeq_j a)$ as $(a \ppref_j x) ∨ (a \pinc_j x)$, where $\pinc_j$ designates incomparability. Thus:
+\begin{gather*} 
+(x \pprefeq_j y) ∧ ¬(x \pprefeq_j a) \Rightarrow (a \neq_j y) \\
+(x \pprefeq_j y) ∧ ((a \ppref_j x) ∨ (a \pinc_j x)) \Rightarrow (a \neq_j y) \\
+((x \pprefeq_j y) ∧ (a \ppref_j x)) ∨ ((x \pprefeq_j y) ∧ (a \pinc_j x)) \Rightarrow (a \neq_j y).
+\end{gather*}
+So we can go back to \ref{eq:betaproof} dropping the $(a \neq_j y)$ term:
+\[a \pref_j y ⇔ (a \ppref_j y) ∨ ((x \pprefeq_j y) ∧ ¬(x \pprefeq_j a) ∧ ¬(a \ppref_j y))\]
+In case $(x \pprefeq_j y)$, we say an alternative $a \in \beta$ iff $¬((x \pprefeq_j a) ∨ (a \ppref_j y))$. Thus defining $\beta=A \setminus ({\pprefeq_j}(x) \cup {\pprefinv_j}(y))$.
 

### 2019-04-14 draft.tex
Proufs

--- 2019-04-08 draft.tex
@@
 \usepackage{textcomp}
-\newunicodechar{⇒}{\implies}
+%\newunicodechar{⇒}{\implies}
+\newunicodechar{⇒}{\Rightarrow}
 \newunicodechar{≠}{\ensuremath{\neq}}
@@
 
+We are interested in computing $\PMR(x, y; \pprofile, W)$.
+This represents the “worst” difference of score, thus the difference of score between $y$ and $x$ under the worst case preferences compatible with $\pprofile$ and $W$, where the worst case is the one that maximizes this difference of score.
 We consider now a procedure for completing a partial profile that was first proposed by \citet{Lu2011} when considering minimax regret with a fixed weight vector.
@@
 
-We are interested in computing $\PMR(x, y; \pprofile, W)$.
-This represents the “worst” difference of score, thus the difference of score between $y$ and $x$ under the worst case preferences compatible with $\pprofile$ and $W$, where the worst case is the one that maximizes this difference of score.
-Consider our knowledge $\ppref_j$ about the preference of the agent $j$. 
+\begin{claim}
+There exists a completion $\hat{\profile} \in C(\pprofile)$ such that $\PMR(x,y; \pprofile, W) = \max_{\w \in W} [ s(y; \hat{\profile}, \w) - s(x; \hat{\profile}, \w) ]$ and such that the linear order $\hat{v}_{j}$ of each agent $j$ satisfies:
+\begin{align} 
+\label{eq:complx}
+a \pref_j x &⇔ ¬(x \pprefeq_j a)\\
+\label{eq:comply}
+y \pref_j a &⇔ ¬(a \pprefeq_j y) ∧ ¬((x \pprefeq_j y) ∧ ¬(x \pprefeq_j a)).
+\end{align} 
+\end{claim}
+\begin{proof}[Sketch of proof]
+Consider our knowledge $\pprefeq_j$ about the preference of the agent $j$. 
 The adversary's goal is to make the score of $y$ as high as possible and the score of $x$ as low as possible. 
-To do this, he should complete $\ppref_j$ to $\pref_j$ by putting above $x$ as many alternatives as he can, that is, all the alternatives except those that are known to be worse than $x$ (those $a$ such that $x \pprefeq_j a$); and similarly, put below $y$ all the alternatives he can, thus, put above $y$ only those $a$ such that $a \ppref_j y$.
-Sometimes these two objectives conflict: when an alternative should go above $x$ according to the first objective and below $y$ according to the second one (because $¬(x \pprefeq_j a) ∧ ¬(a \ppref_j y)$), and $x$ is known to be better than $y$ (thus $x \pprefeq_j y$).
-In this case, the first objective should take priority, and $a$ should be put above $x$, which will move both $x$ and $y$ one rank lower than if $a$ had been put below $y$. 
+To do this, he should complete $\ppref_j$ to $\pref_j$ by putting above $x$ as many alternatives as he can, that is, all the alternatives except those that are known to be worse than $x$ (those $a$ such that $x \pprefeq_j a$); and similarly, he should put below $y$ all the alternatives he can.
+Two conditions must be excluded for $a$ to go below $y$.
+The alternatives such that $a \pprefeq_j y$ can’t be put below $y$.
+Furthermore, the first objective must take priority over the second one: when an alternative should go above $x$ according to the first objective (because $¬(x \pprefeq_j a)$), and $x$ is known to be better than $y$ (thus $x \pprefeq_j y$), then $a$ should be put above $x$ (irrespective of whether $a \pprefeq_j y$), which will move both $x$ and $y$ one rank lower than if $a$ had been put below $y$.
 This maximizes the adversary’s interests: because the weight vector is convex, the difference of scores will be lower when both alternatives are ranked lower (Equation \ref{eq:convexity}), and that difference of scores is in favor of $x$ when $x \ppref_j y$, thus to be minimized from the point of view of the adversary.
-To summarize:
-\begin{align} 
-\label{eq:compl}
-\begin{split}
-a \pref_j x &⇔ ¬(x \pprefeq_j a)\\
-y \pref_j a &⇔ ¬(a \ppref_j y) ∧ (¬(x \pprefeq_j y) ∨ (x \ppref_j a)).
-\end{split}
-\end{align} 
-We just sketched a proof of the following claim, and leave the rest of the proof to the reader.
+\end{proof}
+
+Let ${\pprefeq_j}(x)$ designate the set of alternatives that are known to be considered by $j$ as less good than or equal to $x$, and ${\pprefinv_j}(y)$ be the set of alternatives known to be considered by $j$ as strictly better than $y$.
 \begin{claim}
-There exists a completion $\hat{\profile} \in C(\pprofile)$ such that $\PMR(x,y; \pprofile, W) = \max_{\w \in W} [ s(y; \hat{\profile}, \w) - s(x; \hat{\profile}, \w) ]$ and such that the linear order $\hat{v}_{j}$ of each agent $j$ satisfies (\ref{eq:compl}).
+	The rank of $x$ in the PMR-maximizing linear orders of agent $j$ is $\hat{v}_{j}(x) = 1+\card{A}-\card{{\pprefeq_j}(x)}$, and the rank of $y$ is $\hat{v}_{j}(y)=1+\card{{\pprefinv_j}(y)}+\card{\beta}$, where $\card{\beta} = \card{A \setminus ({\pprefeq_j}(x) \cup {\pprefinv_j}(y))}$ if $(x \pprefeq_j y)$ and $\card{\beta} = 0$ otherwise.
 \end{claim}
-It follows that $\hat{v}_{j}(x)$, the rank of $x$ in the PMR-maximizing linear order of agent $j$, 
-is $\hat{v}_{j}(x) = 1+\card{A}-\card{{\pprefeq_j}(x)}$, where ${\pprefeq_j}(x)$ designates the set of alternatives that are less good than $x$ according to $\pprefeq_j$ (thus including $x$ itself), and the rank of $y$ is $\hat{v}_{j}(y)=1+\card{{\pprefinv_j}(y)}+\beta$, where $\beta = \card{{\pinc_j}(x)}$ if $(x \pprefeq_j y)$ and $\beta = 0$ otherwise and with ${\pinc_j}(x)$ designating the alternatives incomparable with $x$ in $\pprefeq_j$ \commentBN{Still not good.
-In the set of alternatives incomparable with $x$ there could be alternatives strictly better than $y$.
-It is exactly the problem we had before.
-Instead, $\beta$ represents the number of alternatives incomparable with $x$ that are no better than $y$: $\beta = \card{A \setminus ({\pprefeq_j}(x) \cup {\pprefinv_j}(y))}$ }.
-
-%Proof: Define $\pref$ as just $\ppref_j$ with the arcs added to minimally satisfy the above.
-Thus, add the following arcs: when $x ?
-a$, add $a > x$.
-When $a ?
-y ∧ x \ppref_j y ∧ ¬(x \ppref_j a)$, add $a \pref y$.
-When $a ?
-y ∧ [¬(x \ppref_j y) ∨ (x \ppref_j a)]$, add $y \pref a$.
-Observe that $\ppref_j \subseteq \pref$.
-We have to show that it is acyclic.
-(Then we take its transitive closure to make it a partial order, and it’s done.) Note that if there is a cycle in $\pref$, it’s because of some new arcs, as $\ppref_j$ is acyclic.
-Thus, the cycle must go through one of these new arcs.
-…
+\begin{proof}
+The rank of $x$ is directly obtained from \cref{eq:complx}.
+The rank of $y$ is obtained by complementing \cref{eq:comply}, obtaining $a \prefeq_j y ⇔ (a \pprefeq_j y) ∨ ((x \pprefeq_j y) ∧ ¬(x \pprefeq_j a))$, and, observing that $a \pref_j y ⇔ a ≠ y ∧ a \prefeq_j y$, obtaining that $a \pref_j y$ if and only if
+\begin{equation}
+\label{eq:betteryinter}
+(a \neq y) ∧ [(a \pprefeq_j y) ∨ ((x \pprefeq_j y) ∧ ¬(x \pprefeq_j a))],
+\end{equation} 
+or equivalently, if and only if
+\begin{equation}
+\label{eq:bettery}
+%a \pref_j y ⇔ 
+(a \ppref_j y) ∨ ((x \pprefeq_j y) ∧ ¬(x \pprefeq_j a)).
+\end{equation} 
+Indeed, \eqref{eq:betteryinter} $⇒$ \eqref{eq:bettery}, and \eqref{eq:bettery} $⇒$ \eqref{eq:betteryinter} because $(x \pprefeq_j y) ∧ ¬(x \pprefeq_j a) ⇒ a ≠ y$ (as when $a = y$, $(x \pprefeq_j y)$ and $¬(x \pprefeq_j a)$ are opposite claims).
+Suffices now to rewrite \cref{eq:bettery} to let the two disjuncts designate disjoint sets:
+\begin{equation}
+\label{eq:betteryfinal}
+a \pref_j y ⇔ 
+(a \ppref_j y) ∨ ((x \pprefeq_j y) ∧ ¬(x \pprefeq_j a) ∧ ¬(a \ppref_j y)).
+\end{equation} 
+\end{proof}
+
+The claim can also be understood by observing that in the case $(x \pprefeq_j y)$, $\beta$ is the number of alternatives incomparable with both $x$ and $y$.
 
@@
 \max_{\w} & \sum_{r=1}^m (\hat{\alpha}_{r}^{y} - \hat{\alpha}_{r}^{x}) w_{r}\\
-\text{ s.t. } & \text{Equation } (\ref{eq:monotone})\\
-& \text{Equation } (\ref{eq:convexity})\\
+\text{ s.t. } & \text{\cref{eq:monotone}}\\
+& \text{\cref{eq:convexity}}\\
 & \Co_W
@@
 However, it is important to make sure that a question can also, in principle, be asked in a more concrete way, in terms of winners of example profiles.
-This permits to test whether the chair understands the question as we do and to relate the preference of the chair to her choice behavior in the economic sense.
+This permits to test how the chair understands the question and to relate the preference of the chair to her choice behavior in the economic sense.
 Furthermore this will be necessary for an ordinal extension of our work where the scores would not be considered as cardinal utilities.
 Thus, our task is to build a profile, given $\lambda$ and $r ≤ m-2$, in such a way that the set of (tied) winners picked by the chair reveals whether $w_{r} - w_{r+1} \geq \lambda (w_{r+1} - w_{r+2})$.
-We assume that $\lambda$ is rational, and define $\lambda = p/q$.
-
+\begin{claim}
+	Given a rational $\lambda = p/q$ and a rank $r$ between $1$ and $m - 2$, the profile named $P'$ in the ensuing description is such that, for any weight vector $\w \in \W$, $a \in f(P')$ iff $w_{r} - w_{r+1} ≥ \lambda (w_{r+1} - w_{r+2})$ and $b \in f(P')$ iff $w_{r} - w_{r+1} ≤ \lambda (w_{r+1} - w_{r+2})$, where $f$ is the PSR parameterized with $\w$.
+\end{claim}
+\begin{proof}
 Observe that the question may be defined equivalently as $q \cdot w_{r} + p \cdot w_{r+2} ≥ (p + q) \cdot w_{r+1}$, where $p, q$ are natural numbers. 
@@
 Because weights are non increasing, this guarantees, with $\delta = p + q$, that the score of $a$ is not lower than the one of $c$.
-
-This concludes the proof of the following claim. 
-\begin{claim}
-	Given a rational $\lambda$ and a rank $r$ between $1$ and $m - 2$, the profile named $P'$ in the foregoing description is such that, for any weight vector $\w \in \W$, $a \in f(P')$ iff $w_{r} - w_{r+1} ≥ \lambda (w_{r+1} - w_{r+2})$ and $b \in f(P')$ iff $w_{r} - w_{r+1} ≤ \lambda (w_{r+1} - w_{r+2})$, where $f$ is the PSR parameterized with $\w$.
-\end{claim}
+\end{proof}
+
 At this stage, we are content that a procedure exists to transform our abstract questions to questions about winners of a PSR.

### 2019-05-31 Amsterdam (abstract500words)/abstract500w.tex
abstract amsterdam

--- 2019-03-31 RJCIA2019/short_draft.tex
@@
-%\input{rfia} 
-\documentclass[a4paper,twoside]{article}
-\usepackage{rfia2000}
+\documentclass[a4paper]{article}
+%\usepackage[a4paper, total={5.5in, 7.7in}]{geometry}
+%\usepackage{rfia2000}
 \usepackage[T1]{fontenc}
@@
 \usepackage{times}
+\usepackage{authblk}
 
-%\author{ID: 2696}
-\author{\begin{tabular}[t]{c@{\extracolsep{6em}}c@{\extracolsep{6em}}c}
-	B. Napolitano${}^1$ & O. Cailloux${}^1$ & P. Viappiani${}^2$ \\
-	\end{tabular}
-{} \\
-\\
-${}^1$        LAMSADE, UMR 7243, CNRS and Universit\'e Paris Dauphine, PSL Research University, Paris, France   \\
-${}^2$        LIP6, UMR 7606, CNRS and Sorbonne Universit\'e, Paris, France
-{} \\
-\\
-%Mon adresse compl\`ete \\
-\{firstname.lastname\}@dauphine.fr, paolo.viappiani@lip6.fr\\
-%{\bf Domaine principal de recherche}: RFP ou IA\\
-%{\bf Papier soumis dans le cadre de la journée commune}: OUI ou NON
-}
+%%\author{ID: 2696}
+%\author{\begin{tabular}[t]{c@{\extracolsep{3em}}c@{\extracolsep{3em}}c}
+%	B. Napolitano${}^1$ & O. Cailloux${}^1$ & P. Viappiani${}^2$ \\
+%	\end{tabular}
+%{} \\
+%\\
+%${}^1$        LAMSADE, UMR 7243, CNRS and Universit\'e Paris Dauphine, PSL Research University, Paris, France   \\
+%${}^2$        LIP6, UMR 7606, CNRS and Sorbonne Universit\'e, Paris, France
+%{} \\
+%\\
+%%Mon adresse compl\`ete \\
+%\{firstname.lastname\}@dauphine.fr, paolo.viappiani@lip6.fr\\
+%%{\bf Domaine principal de recherche}: RFP ou IA\\
+%%{\bf Papier soumis dans le cadre de la journée commune}: OUI ou NON
+%}
+\author[1]{Beatrice Napolitano}
+\author[1]{Olivier Cailloux}
+\author[2]{Paolo Viappiani}
+\affil[1]{LAMSADE, UMR 7243, CNRS and Universit\'e Paris Dauphine, PSL Research University, Paris, France}
+\affil[2]{LIP6, UMR 7606, CNRS and Sorbonne Universit\'e, Paris, France}
+\affil[ ]{ }
+\affil[ ]{\{firstname.lastname\}@dauphine.fr, paolo.viappiani@lip6.fr}
+\renewcommand\Authands{ and }
+
+%\author{%
+%	Beatrice Napolitano \affmark[1], Olivier Cailloux\affmark[1] and Paolo Viappiani\affmark[2]\\
+%	\affaddr{\affmark[1]LAMSADE, UMR 7243, CNRS and Universit\'e Paris Dauphine, PSL Research University, Paris, France}\\
+%	\affaddr{\affmark[2]LIP6, UMR 7606, CNRS and Sorbonne Universit\'e, Paris, France}\\
+%	\email{\{firstname.lastname\}@dauphine.fr, paolo.viappiani@lip6.fr}\\
+%}
 
@@
 \newcommand{\email}[1]{\href{mailto:#1}{#1}}
+\newcommand*{\affaddr}[1]{#1} % No op here. Customize it for different styles.
+\newcommand*{\affmark}[1][*]{\textsuperscript{#1}}
 \newcommand{\denselist}{\itemsep -2pt\topsep-6pt\partopsep-6pt}
@@
 
+\begin{document}
+\date{}
 \title{\Large\bf Simultaneous Elicitation of Committee and Voters Preferences}
 
-\begin{document}
-\date{}
 \maketitle
-\thispagestyle{empty}
-%\subsection*{R\'esum\'e}
-%{\em
-%	Le choix social traite du probl\`eme de la d\'etermination d'un choix consensuel \`a partir des pr\'ef\'erences de diff\'erents agents.
-Dans le cadre classique, la r\`egle de vote est fix\'ee \`a l’avance et les informations compl\`etes concernant les pr\'ef\'erences des agents sont fournies.
-Dans cet article, nous supposons que la r\`egle de vote et les pr\'ef\'erences des agents sont partiellement connues.
-Ainsi, nous fournissons un protocole interactif d’\'elicitation bas\'e sur le regret minimax et d\'eveloppons plusieurs strat\'egies d’interrogation, associant questions au comit\'e et questions aux agents, afin d’obtenir les informations les plus pertinentes et de converger rapidement vers un r\'esultat optimal ou s'approchant de l'optimal.
-%}
-%\subsection*{Mots Clef}
-%Choix social computationnel, IA dans l'incertain, \'elicitation des pr\'ef\'erences, regret minimax.
 
-\subsection*{Abstract}
-{\em
-	Social choice deals with the problem of determining a consensus choice from the preferences of different agents.
-In the classical setting, the voting rule is fixed beforehand and full information concerning the preferences of the agents is provided.
-	Recently, the assumption of full preference information has been questioned by a number of researchers and several methods for eliciting preferences have been proposed.
-%	\commentOC{This “we go one step further” sounds odd here. I suggest one more sentence about the normal elicitation setting with only the agents preferences partially specified.}
-	In this paper we go one step further and we assume that both the voting rule and the agents preferences are partially specified.
-In this setting, we present an interactive elicitation protocol based on minimax regret and develop several query strategies that interleave questions to the chair and questions to the agents in order to attempt to acquire the most relevant information in order to quickly converge to optimal or a near-optimal alternative.
-}
+\section*{Abstract}
+Social choice deals with the problem of aggregating the preferences of different agents over several alternatives determining the ones that represent a consensus choice.
+In a traditional social choice setting both the social choice function and the full preference orderings of the agents are expressed beforehand.
+Nevertheless, in real situations this is not always the case.
+When considering decisions with large sets of alternatives, requiring agents to express full preference orderings can be prohibitively costly and, perhaps, not necessary in order to determine a consensus choice.
+
+Consider as an example a situation in which the council of a city wants to build a community allotment and the decision of what to grow has to be taken.
+The agents, or voters, are the residents of the neighborhood and the alternatives consist of all the fruits and vegetables that can grow in that particular area.
+Imagine now to be an external observer (someone helping with the voting procedure for example) who does not know anything about both residents preferences and the aggregation method chosen by the council.
+If, after collecting some preferences, we notice that a vegetable is ranked very low by a large number of residents then we are not interested in knowing how a particular agent, we do not know anything about, ranks this vegetable.
+This is because it is really unlikely that it would be selected as a winner by any reasonable voting rule.
+A clever approach would be, instead, to ask that agent her preferences regarding alternatives for which, considering the information collected so far, even a single vote can be decisive for them to be selected as consensus choices.
+Furthermore, following the same reasoning, if we notice that a particular vegetable is the most preferred of almost the totality of the residents we do not need to know the specific voting rule.
+Any reasonable aggregation procedure, in fact, would select this alternative as a winner.
+The reason behind this consideration is that is not unrealistic to assume that the committee that has to decide how to aggregate these preferences is not able to define a specific procedure.
+Indeed, it is often difficult for non-expert users to formalize a voting rule on the basis of some generic preferences over a desired aggregation method.
+
+These observations have motivated a number of recent works considering social choice with partial preference orders \citep{Xia2008, Pini2009, Konczak05} and incremental elicitation \citep{Kalech2011, Lu2011, Naamani-Dery2015} of agents preferences.
+Furthermore, several authors \citep{Stein1994, Llamazares2013, Viappiani2018} have worked on positional scoring rules with uncertain weights, assuming that the preferences of the agents are fully known.
+Some elicitation methods for a quite general class of rules based on weak orders have also been proposed by Cailloux and Endriss \citep{Cailloux2014}.
+
+In this work we go one step further and we assume that both the voting rule and the agents preferences are partially specified.
+We consider positional scoring rules and develop methods for computing the minimax-optimal alternative using the notion of regret.
+The main idea is to use this procedure both as a means of robust winner determination as well as a guide to the process of simultaneous elicitation of preferences and voting rule.
+The latter leads to the development of query strategies that interleave questions to the chair and questions to the agents in order to attempt to acquire the most relevant information as quickly as possible.
+While previous works have considered either partial information about the agents preferences or a partially specified aggregation method, we do not know of any work considering both sources of uncertainty at the same time.
+
+%, providing incremental elicitation methods that aim to acquire relevant preference information.
+We then discuss several heuristics that determine queries, either to an agent or to the committee, that quickly reduce minimax regret.
 \subsection*{Keywords}
@@
 
-\section{Introduction}
-%Aggregation of preference information is a central task in many computer systems (recommender systems, search engines, etc) whose final goal is to find a consensus choice.
-%In this contexts, a natural approach consists in looking at methods from social choice and see how they can be adapted for group decision-making in a computerized setting.
-In a traditional social choice setting, both the social function and the full preference orderings of the agents are expressed beforehand.
-Nevertheless, requiring agents to express full preference orderings can be prohibitively costly (in terms of cognitive and communication cost), especially for decisions with large sets of alternatives.
-This observation has motivated a number of recent works considering social choice with partial preference orders \citep{Xia2008, Pini2009, Konczak05} and incremental elicitation \citep{Kalech2011, Lu2011, Naamani-Dery2015} of agents’ preferences.
-Furthermore, several situations for which it may not be easy to precisely define the voting rule exist.
-Indeed, it is possible that the chair has some preferences over the desired aggregation method, but is not able to formalize the voting rule upfront.
-The work of Cailloux and Endriss \citep{Cailloux2014} provides elicitation methods for a quite general class of rules based on weak orders.
-When considering positional scoring rules, several authors \citep{Stein1994, Llamazares2013, Viappiani2018} have worked on positional scoring rules with uncertain weights, assuming that the preferences of the agents are fully known.
-In this paper we consider that both the agents’ preferences and the social choice rule are partially specified.
-We develop methods for computing the minimax-optimal alternative using positional scoring rules and we provide incremental elicitation methods to acquire relevant preference information.
-We then discuss several heuristics that determine queries, either to an agent or to the committee, that quickly reduce minimax regret.
-While previous works have considered either partial information about the agents preferences or a partially specified aggregation method, we do not know of any work considering both sources of uncertainty at the same time.
-
-\section{Partial information}
-\label{sec:background}
-We assume defined a set $A$ of $m$ alternatives (products, restaurants, public projects, etc.) and a set $\set{1, …, n}$ of agents.
-Each agent $j$ comes from an infinite set $\N$ of potential agents and is associated to her “real” preference order $\pref_j \in \linors$ which is a linear order (connected, transitive, asymmetric relation) over the alternatives.
-A {\em profile} is the association of a preference to each agent and it is equivalently represented by $(\pref_1,\ldots,\pref_n)$ or by $\profile=(v_1,\ldots,v_n) \in V$ where $v_j(i) \in \set{1, \ldots, m}$ denotes the rank (position) of alternative $i$ in the preference order $\pref_j$.
-%Given $V$ the set of possible preference profiles, a social choice function $f : V \rightarrow \powersetz{A}$ associates a profile with a set of winners; where $\powersetz{A}$ represents the set of subsets of $A$ except for the emptyset.
-A social choice function associates a profile with a set of winners; we consider {\em positional scoring rules (PSR)}, which attach weights to positions according to the scoring vector $(w_1, \ldots, w_m)$.
-An alternative obtains a score that depends on the rank obtained in each of the preference orders and the winners are the alternatives with highest scores.
-In this work we assume fixed, but unknown, a profile $\profile^* = (\pref^*_j, j \in \{1, \ldots, n\})$ and a weight vector $\w^*$.
-Our knowledge at a given time of the preference of agent $j$ is encoded by a partial order over the alternatives, thus a transitive and asymmetric binary relation, denoted by $\ppref_j$; we assume that preference information is truthful, i.e.
-%${\ppref_j} \subseteq {\pref_j^*}$.
-$a \ppref_j b ⇒ a \pref_j^* b$.
-%\commentOC{Or simply ${\ppref_j} \subseteq {\pref_j^*}$, if you need to save space}
-%We use $\pinc$ to denote incomparability, that is $a \pinc_{j} b$ iff $a \nppref_j b \wedge b \nppref_j a$.
-An incomplete profile $\pprofile = (\ppref_1, \ldots, \ppref_n)$ maps each agent to a partial preference.
-A completion of $\ppref_j$ is any linear order $\pref$ that extends $\ppref_j$ and we indicate with $C(\ppref_j) = \set{{\succ} \in \linors \suchthat {\ppref_j} \subseteq {\succ}}$ the set of possible completions of $\ppref_i$.
-%We let $C(\pprofile)=C(\ppref_1)\times … \times C(\ppref_n)$ be the set of complete profiles extending $p$. Note that $\profile^* \in C(\pprofile)$.
-
-Our knowledge regarding the weights of the scoring rule is represented by
-%We also assume that the weights of the scoring rule are only partially specified.
-%Therefore the vector $(w_1,\ldots,w_m)$  is not known but we are given 
-a set of constraints restraining the possible values that they can take. We consider a convex sequence of weights and we assume that 
-%, i.e.
-a decreasing sequence $1=w_{1} > w_{2} > \ldots > w_{m}=0$ such that the difference between the weights of the first and second positions is at least as great as the difference between the weights of the second and third positions, etc.
-%\begin{equation} 
-%\label{eq:convexity}
-%\forall r \in \{1,\ldots,m-2\}: w_r - w_{r+1} \geq w_{r+1}-w_{r+2}.
-%\end{equation}
-%We assume that in addition of basic requirements (monotonicity and convexity), 
-the chair is able to specify additional preferences about how the social choice function should behave. 
-%Of course it may be difficult for real decision makers to state these preferences, thus we can elicit them, for instance, by showing a complete profile of a small synthetic election and asking who should be elected in this case.
-\commentOC{Not entirely true as stated here.
-This works only in a subset of the case.
-So this remark should be dropped or amended, to say that we worked on this problem and it is still a work in progress to come up with an elicitation procedure that uses only questions that can effectively be asked using such a small synthetic election, and that it is not discussed further in this short article for lack of space.
-Also I’d remove “Of course”, it’s not obviously true.}
-Such requirements are encoded with linear constraints about the vector $\w$ and the set of these constraints is denoted by $\Co_W$.
-Given the set of convex weight vectors $\W$, we use $\pw \subseteq \W$ to denote the set of weight vectors compatible with the preferences expressed by the chair.
-
-\section[Minimax regret under partial profile and weight information]{
-Robust winner determination}
-\label{sec:mmr}
-As a decision criterion to determine a winner, we propose to use minimax regret \citep{Savage1954}. 
-%Minimax regret \citep{Savage1954} is a decision criterion that has been used for robust optimization under data uncertainty \citep{Kouvelis1997} as well as in decision-making with uncertain utility values \citep{Salo2001,Boutilier2006}.
-%\citet{Lu2011} have adopted minimax regret for winner determination in social choice with
-%the preferences of the agents that are only partially known, while the social choice function is predetermined and known.
-%In this work we consider the simultaneous presence of uncertainty in the agents' preferences and uncertainty in the weights.
-We use {\em maximum regret} to quantify the worst-case error, which measures, intuitively, how far an alternative is from the optimal one given current knowledge.
-% about the voting rule and the agents' preferences.
-The alternatives that minimize this error are selected as tied winners, providing us with a form of robust optimization.
-The maximum regret of an alternative is the highest possible difference between its score and the one achievable by any alternative in any state compatible with our current knowledge.
-%The maximum regret, given our current knowledge and an alternative $x$, is the highest possible difference between the score of $x$ and the score achievable by any alternative in any state compatible with our current knowledge.
-It is considered by assuming that an adversary can both 1) extend the partial profile $\pprofile$ into a complete one, and 2) instantiate the weights choosing among any weight vector in $\pw$.
-We formalize the notion of minimax regret in multiple steps.
-First of all, $\Regret(x, \profile, \w)$ is the “regret” of selecting $x$ as a winner instead of choosing the optimal alternative under $\profile$ and $\w$:
-\[\Regret(x, \profile, \w) = \max_{y \in A} s(y; \profile,\w) - s(x; \profile, \w).\]
-The pairwise max regret $\PMR(x,y;\pprofile,W)$ of $x$ relative to $y$ given partial profile $\pprofile$ and the set of weights $W$ is the worst-case loss of choosing $x$ instead of $y$ under all possible realizations of the full profile {\em and} weights.
-Max regret $\MR(x;\pprofile,W)$ is the worst-case loss of $x$ and $\MMR(\pprofile,W)$ is the value of minimax regret obtained when recommending a minimax optimal alternative $x^*_{\pprofile, W}$.
-%\begin{align}
-%\PMR(x,y; \pprofile, W) & = \max_{\w \in W} \max_{\profile \in C(\pprofile)} s(y; \profile,\w) - s(x; \profile,\w).
-%\end{align}
-%It is the loss occurred by an adversarial selection of a complete profile $\profile$ extending $\pprofile$ and a selection of $\w \in W$ to maximize the loss between $x$ and the true winner under $\profile$ and $\w$.
-\begin{align}
-\PMR(x,y; \pprofile, W) & = \max_{\w \in W} \max_{\profile \in C(\pprofile)} s(y; \profile,\w) - s(x; \profile,\w) \\
-\MR(x; \pprofile, W) & = \max_{y \in A} \PMR(x,y; \pprofile, W)\\
-%& = \max_{\w \in W} \max_{\profile \in C(\profile)} \Regret(x, \profile, \w) \\
-\MMR(\pprofile,W) & = \min_{x \in A} \MR(x;\pprofile,W) \\
-x^{*}_{\pprofile,W} \in A^*_{\pprofile, W} & = \argmin_{x \in A} \MR(x;\pprofile,W) 
-\end{align}
-
-%Finally,  $\MMR(\pprofile,W)$ is the value of minimax regret under $\pprofile$ and $W$, obtained when recommending a minimax optimal alternative $x^*_{\pprofile, W}$:
-%\begin{align*}
-%\MMR(\pprofile,W) & = \min_{x \in A} \MR(x;\pprofile,W) \\
-%x^{*}_{\pprofile,W} \in A^*_{\pprofile, W} & = \argmin_{x \in A} \MR(x;\pprofile,W) 
-%\end{align*}
-By picking as consensus choice an alternative associated with minimax regret, we can provide a recommendation that gives worst-case guarantees, giving some robustness in face of uncertainty. 
-%In cases of ties in minimax regret, we can either decide to return all minimax alternatives $A^*_{\pprofile, W}$ as winners or to pick just one of them using some tie-breaking strategy.
-%
-%Notice that if $\MMR(\pprofile, W)\!=\!0$, then $x^{*}_{\pprofile,W}$ is a necessary co-winner; this means that for any valid completion of the profile and any feasible $w \!\in\!
-W$, $x^{*}_{\pprofile,W}$ obtains a highest score.
-%
-%We note that our notion of regret gives some cardinal meaning to the scores: instead of just being used to select winners under the corresponding PSR, their differences are considered as representing the regret of the chair.
-
-\section{Interactive Elicitation} 
-\label{sec:elicit}
-We propose an incremental elicitation method based on minimax regret.
-At each step, the system may ask a question either to one of the agents or to the chair.
-The goal is to acquire relevant information to reduce minimax regret as quickly as possible.
-As termination condition of elicitation, we can check whether minimax regret is lower than a threshold or, if we wish optimality, we can perform elicitation until minimax regret drops to zero.
-
-\paragraph{Question types}
-We distinguish between questions asked to the agents and questions asked to the chair.
-For the first we consider comparison queries that ask a particular agent to compare two alternatives. Then, the partial profile $\pprofile$ is augmented on the basis of the agent's answer.
-The latter, instead, aims at refining our knowledge about the scoring rule; in particular, we assume we can acquire constraints of the type:
-\[ w_{r} - w_{r+1} \geq \lambda (w_{r+1} - w_{r+2}) \] 
-for $r \in \{1,\ldots,m-2\}$, relating the difference between the importance of consecutive ranks.
-% $r$ and $r+1$ with the difference between ranks $r+1$ and $r+2$.
-
-\paragraph{Elicitation strategies}
-A strategy is a function (or a random process) that, given our partial knowledge so far, gives us a question that should be asked.
-
-The \strat{Random} strategy first decides with a probability of $1/2$ each whether it will ask a question about weights or about a preference ordering.
-Then it equiprobably draws a question among the set of the possible ones.
-This strategy is clearly non efficient but it gives us a baseline for comparisons.
-
-The \strat{Extreme completions} strategy considers the solution of the minimax regret game and estimates the contribution to the regret of our uncertainty about the weights and the profile.
-Then it asks a question to the chair or to the agents depending on which of these two values is the highest.
-
-The \strat{Pessimistic} strategy selects among all the possible questions the one that leads to minimal regret in the worst case.
-For each question, it considers both possible answers to the question and uses some aggregation of their MMRs as a score of the question.
-
-The \strat{Two phase} strategy asks a predefined, non adaptive sequence of $m-2$ questions to the chair and then it only asks questions about the agents, using questions as defined in the \strat{Pessimistic} strategy.
-
-\section{Conclusions}  
-\label{sec:conclusions}
-In this paper we have considered a social choice setting with partial information and we have proposed the use of minimax regret both as a means of robust winner determination as well as a guide to the process of simultaneous elicitation of preferences and voting rule.
-
-The next step is to test our strategies in order to compare the performance of our interleaved elicitation approach that mixes questions to the chair and to the agents, to a more classical approach that elicits the rule first and then the agents preferences (or vice-versa).
-
-Further development of elicitation strategies, considering alternative heuristics, is also an important direction for future works together with the extension of the approach to voting rules beyond scoring rules.
-
-% Acknowledgements: We thank the reviewers for comments helping to improve the paper. 
-%{\small
 \bibliography{biblio}
-\bibliographystyle{plain}
-%\bibliographystyle{plain} 
-%}
+\bibliographystyle{apalike}
 \end{document}
-
-\appendix
-\section{Minimax Computation under Convex Assumption}
-
-Refer to \citep{Lu2011}
-The goal is to choose as a winner the alternative $x^*$ whose worst case loss is minimal under all possible realizations of the full profile and all possible choices of weights. 
-Assume hereinafter the selected weights sequence $\w \in W$ to be convex. 
-In order to compute the minimal max regret $\MMR(\pprofile)$ under partial profile $\pprofile$ we need to compute the pairwise max regret between all pairs of alternatives $(x,y)$, where $x$ is a proposed winner and $y$ is the ``adversary'' alternative.
-Indeed, the construction of $\PMR(x,y,\pprofile,\w)$ can be viewed as an adversary's attempt to maximize the regret of choosing $x$ instead of $y$.
-For doing this, he can choose a completion $\profile_i \in C(\pprofile_i)$ of the partial profile and a (feasible) scoring vector $\w$ that maximize the contribution of the agent $i$ to $\PMR(x,y,\pprofile,\w)$.
-Let us now analyze how it could be done depending on the relation between alternatives $x$ and $y$ in $\pprofile_i$.
-\begin{itemize}
-	\item $x \succ_i^\pprofile y$
-	\newline If we know $x$ is preferred to $y$ and we choose $x$ as a winner, $\pprofile_i$ contribution to $\PMR(x,y,\pprofile,\w)$ must be negative.
-In this situation, our adversary can only try to minimize this advantage by minimizing the positional gap between the two alternatives.
-To achieve that, he can arbitrary place all the alternatives preferred to $x$ above $x$, together with all the ones with unknown relation to $x$.
-Moreover, he can place all the alternatives less preferred to $x$ and with unknown relation to $y$ below $y$.
-We can summarize it for each $q \in A$ as follows:
-	\begin{align*}
-	q \succ_i^\pprofile x \vee q \ ?_i^\pprofile \ x \ & \Rightarrow \ \uparrow_x \\
-	x \succ_i^\pprofile q \wedge ( q \ ?_i^\pprofile \ y \vee y \succ_i^\pprofile q) \ & \Rightarrow \ \downarrow_y \\
-	x \succ_i^\pprofile q \succ_i^\pprofile y \ & \Rightarrow \ \text{in between} \\
-	\end{align*}
-	It is worth noting that when the relation between $q$ and $x$ is not known in the partial profile, the adversary takes advantage by placing $q$ above $x$ only under the assumption of convex weight sequences.
-	\item $y \succ_i^\pprofile x$
-	\newline If $y$ is preferred to $x$ the construction proceeds similarly to the previous case, but now the adversary takes advantage by maximizing the gap between $x$ and $y$ placing as much alternatives as he can between the two.
-We can summarize the procedure for each $q \in A$ as follows:
-	\begin{align*}
-	q \succ_i^\pprofile y \ & \Rightarrow \ \uparrow_y \\
-	x \succ_i^\pprofile q \ & \Rightarrow \ \downarrow_x \\
-	(y \succ_i^\pprofile q \vee y \ ?_i^\pprofile \ q) \wedge (q \succ_i^\pprofile x \vee q \ ?_i^\pprofile \ x) \ & \Rightarrow \ \text{in between} \\
-	\end{align*}
-	\item $x \ ?_i^\pprofile \ y$
-	\newline If the partial profile $\pprofile_i$ does not specify the relation between $x$ and $y$, the advantage is maximized by ordering $y$ over $x$ and maximizing the gap between them following the procedure for the case $y \succ_i^\pprofile x$.
-\end{itemize}
-
-\section{Dropping the Convex Assumption}
-\subsection{Profile completion}
-What if the sequence of weights is not convex?
-When $y \succ_i^\pprofile x$ or $x \ ?_i^\pprofile \ y$ weights do not influence the arbitrary placement of alternatives.
-Please remind we are working under the assumption that weights constitute a monotonic non-increasing sequence.
-Thus, there is no way for the adversary to take advantage from the weights distribution in order to increase the gap between $y$ and $x$ besides placing as much alternatives as he can between the two.
-The only case in which weights can influence the positional gap between $x$ and $y$ is when $x \succ_i^\pprofile y$ and $q \ ?_i^\pprofile \ x$.
-For convex sequences we place such alternatives $q$ above $x$, but it is not obvious that this is the best option for other sequences.
-For example, suppose $x$ and $y$ are ranked respectively in first and second position in the partial profile and we wonder where to place an alternative $q$ with unknown relation to $x$ (and thus to $y$).
-Suppose also that in the weight sequence the distance between the first and second positions is much lower than the one between the second and the third ones.
-In this case, placing $q$ above $x$ does not minimize the gap between $x$ and $y$ but we want, instead, to place $q$ below $y$.
-\newline The constraints expressed by the chair may result in a set of feasible vectors such that none of them forms a convex sequence.
-In this case we need to analyze the particular sequence of weights in order to decide how to maximize the adversary advantage.
-Before going into details, let us define $A$ as the set of alternatives (if any) preferred to $x$, $B$ as the set of alternatives preferred to $y$ but not to $x$, and $U$ the set of those with unknown relation to both $x$ and $y$.
-The idea is to determine the positions that minimize $x$'s advantage over $y$ and then place some of the alternatives in $U$ above $x$ and some below $y$ in order to get that desired ranking.
-Since we cannot change the order of the alternatives in the set $B$ we know that $x$ and $y$ are separated exactly by $|B|$ positions (the adversary would not take any advantage by adding alternatives between them).
-So, starting from the position of $x$ in the partial completion of $\pprofile_i$ computed so far ($\hat{\profile}_i$), we find the two positions separated by $|B|$ alternatives whose weights difference is the lowest.
-Note that we can only add $|U|$ alternatives so we can check only until the position $\hat{\profile}_i(x)+|U|$.
-Algorithm \ref{alg:splittingU} shows the procedure described.
-
-It is easy to see that we check at most $|U|$ positions.
-In the worst case the size of $U$ is equal to $m-2$, thus the procedure can be computed in $O(m)$ time.
-This cost does not affect the minimax regret computation time complexity that remains $O(nm^3)$.
-
-\begin{algorithm}[h] 
-	\caption{Placing alternatives in $U$ without Convex Assumption}
-	\label{alg:splittingU} 
-	\begin{algorithmic}
-		\Require $x$, $y$, $\hat{\profile}_i$, $\w$, $U$, $B$
-		\Ensure $\profile_i \in C(\pprofile)$
-		\Statex
-		\State $ j \gets 0$;
-		\State $ i \gets \hat{\profile}_i(x)$;
-		\State $ \mathit{posmin} \gets i$;
-		\State $ \mathit{min} \gets \w(i) - \w(i+1+|B|)$;
-		\While {$( j \leq |U| )$}
-		\If{ $(\w(i+j)-\w(i+1+|B|+j) < \mathit{min})$ }
-		\State $ \mathit{min} \gets \w(i+j) - \w(i+1+|B|+j)$;
-		\State $ \mathit{posmin} \gets i+j$;
-		\EndIf
-		\EndWhile
-
-		\State $U_{\mathit{abovex}} \gets (i-\mathit{posmin}) \text{ alternatives} \in U $;
-		\State $U_{\mathit{belowy}} \gets U \setminus U_{\mathit{above}}$;
-		\Statex
-		\State $\profile_i \gets place(\pprofile_i,U_{\mathit{abovex}},U_{\mathit{belowy}})$;
-		\Statex \Return $\profile_i$
-
-	\end{algorithmic}
-\end{algorithm}
-
-\section{Minimax regret without the convex assumption}
-Without the convex assumption, we cannot use $\hat{v}$ for the agents in $U^{-}$, but only for agents in $U^{+}$ and $U^{?}$.
-%Let $\hat{v}_i$ be the linear order extending $\succ^{p}_i$ according to the above procedure.
-Then PMR can be written as follows:
-\begin{align*}
- &\PMR(x,y; \pprofile, W) =\\ 
- &\max_{\w \in W} \Big \{ \sum_{j \in U^-} [\max_{v_j \in C(\succ_j^p)} [w_{v_j(y)} \!-\! w_{v_j(x)}]] 
-  \!+\!	 \sum_{j \in A^+ \cup  U^?} [w_{\hat{v}_j(y)} \!-\! w_{\hat{v}_j(x)}] \Big \} 
- \end{align*}
-%Note that the second addendum inside the max do not depend on the choice of $\w$.
-Consider the two addenda inside the ``max''. 
-The first addendum is concerned with positioning of alternatives $x$ and $y$ for agents in $U^{-}$ for which we know that $x$ is preferred to $y$.
-The second addendum is concerned with agents in $U^{+}$ and $U^{?}$.
-We rewrite the second addendum as:
-\begin{align*}
-\sum_{j \in U^+ \cup  U^?} [w_{\hat{v}_j(y)} \!-\! w_{\hat{v}_j(x)}] 
-= \sum_{i = 1}^{m} (\hat{\alpha}_{i}^{y} - \hat{\alpha}_{i}^{x}) w_{i}
-\end{align*}
-where $\hat{\alpha}_{i}^{x}$ is the number of times that $x$ is ranked  in position $i$  considering the profile $\hat{v}$ of agents in $U^+ \cup  U^?$.
-%We compute pairwise maximum regret by considering binary variables $\{ B_{i} \}_{i=1,\ldots,m}$ to represent optimization choices related to where to position the alternatives.
-
-We now address the agents in $A^{-}$
-For a given $j$, let $\beta$ be the number of alternatives that are incomparable with $x$ and $y$:
-\[ \beta_{j} = \mid \{ c : c \pinc_{j} y \wedge c \pinc_{j} x \} \mid \]
-$x$ can be ranked between $t_{1}(j)=\mid \{ c \in A : c \ppref_{j} y \wedge x \nppref_{j} c \} \mid $ and position $t_{2}(j)=t_{1}(j)+\beta_{j}$.
-The completion for agent $j$ is such that the positions of $x$ and $y$ differ of exactly $\gamma_{j} =
-\mid \{ c \in A : x \ppref c \ppref y \} \mid$ positions.
-
-We now show how to optimize $\PMR$.
-In addition to variables $\{ w_{j} \}_{j=1,\ldots,m}$ (one for each position) we need to employ several additional decision variables.
-We introduce two sets of binary variables $B^{+}_{i,j}$ and $B^{-}_{i,j}$  for each position $i$ and for each agent $j$.
-Variable $B_{i,j}^{+}$ encodes the fact that the alternative $y$ is placed in position $i$ in the ranking of agent $j$; while  $B_{i,j}^{-}$ encodes the same thing for alternative $x$.
-%We also have numerical variables to represent the weights of the scoring rule.
-Since each alternative needs to be placed exactly in one place for each agent, we adopt the constraints
-$\sum_{i=t_{1}(j)}^{t_{2}(j)} B_{i,j}^{+} = 1$.
-Since we know that $x$ and $y$ are ranked $\gamma_{j}$ positions apart, we set the constraint:
-$B_{i+\gamma_{j},j}^{-} \geq B_{i,j}^{+}$,  for $i = \{ t_{1}(j), \ldots, t_{2}(j)\}$.
-
-% and $\sum_{i=1}^{m} B_{i,j}^{-} = 1$.
-%Since the objective is to maximize pairwise regret...
-
-The score of alternative $y$ can be written as $\sum_{i = 1}^{m} \hat{\alpha}_{i}^{y}  w_{i} + \sum_{i=1}^{n} \sum_{j=1}^{m} w_{j} B_{i,j}^{+}$.
-The objective function is now:
- \[ \max \sum_{i = 1}^{m} (\hat{\alpha}_{i}^{y} - \hat{\alpha}_{i}^{x}) w_{i} +  \sum_{i=1}^{n} \sum_{j=1}^{m} (B_{i,j}^{+} - B_{i,j}^{-})  w_i \]
-
-We use integer programming enconding tricks in order to linearize the problem.
-We introduce yet another set of variables  $V_{i,j}^{+} $  and $V_{i,j}^{-}$ % the multiplicative terms by new variables.
-and we enforce that $V_{i,j}^{+} = B^{+}_{i,j} w_i$ by setting constraints $V_{i,j}^{+} \leq B^{+}_{i,j}$ and $V_{i,j}^{+}  \leq w_i$.
-We have similar constraints for enforcing $V_{i,j}^{-} = B^{-}_{i,j} w_i$.
-
-We therefore obtain the following mixed integer linear program:
-\newcommand{\C}{\mathcal{C}}
-\begin{align}
-\max & \sum_{i=1}^m  [(\hat{\alpha}_{i}^{y} - \hat{\alpha}_{i}^{x}) w_{i}] +
-  \sum_{j \in A^{-}} \sum_{i=t_{1}}^{t_{2}}  [V_{i,j}^{+} - V_{i,j}^{-}]
-\end{align}
-\begin{align}
-\text{ s.t. } &  \text{Equation } (\ref{eq:monotone}) & \\
-&  \C(\w) &  \\
-& \sum_{i=t_{1}}^{t_{2}} B_{i,j}^{+} = 1 & \forall j \in A^{-} \\
-& B_{i+\gamma_{j},j}^{-} \geq B_{i,j}^{+} & \forall i \in \{ t_{1}, \ldots t_{2}\}, \forall j \in A^{-} \\
-& V_{i,j}^{+} \leq B_{i,j}^{+}  & \forall i \in \{ t_{1}, \ldots t_{2}\}, j \in A^{-} \\
-& V_{i,j}^{+} \leq w_i & \forall i \in \{ t_{1}, \ldots t_{2}\}, j \in A^{-} \\
-& V_{i,j}^{-} \geq w_{i} + B_{i,j}^{-} - 1 & \forall i \in \{ t_{1}, \ldots t_{2}\}, j \in A^{-}\\
-& V_{i,j}^{-} \geq 0 & \forall i \in \{ t_{1}, \ldots t_{2}\}, j \in A^{-}
-\end{align} 
-%We write $w \in W$ as a shourtcut to represent the constraints that the weights are chosen to be in the feasible set.
-There are (at most) $nm$ binary variables and $m(n+1)$ numerical variables.
-The optimization program can be solved by any suitable MILP solver, although it is not suitable to large problem instances.
-
-% DONT KNOW IF WE HAVE TO FORMALIZE THIS AS A CLAIM
-%\begin{claim}
-%The $\PMR$ is computed using the above optimization problem.
-%\end{claim}
-
-\section{Considerations on weights}
-\label{sec:weights}
-Let us consider a monotonic non-increasing sequence of weights: $w_{1} \geq w_{2} \geq \ldots \geq w_{m}$. Without loss of generality, we can assume $w_1=1$ and $w_m=0$.
-
-\begin{claim}
-	\label{clm:wsequence}
-	If the weight sequence is convex then $w_{1} > w_{2}$.
-	\[\forall i \in \{1,\ldots,m\} \;\; w_i - w_{i+1} \geq w_{i+1}-w_{i+2} \Rightarrow w_{1} > w_{2} \geq \ldots \geq w_{m}\] 
-\end{claim}
-\begin{proof}
-	By contradiction let assume $w_{1} = w_{2}$ then 
-	\begin{align*}
-	w_{1} - w_{2} \geq w_{2} - w_{3} &\geq \dots \geq w_{m-1} - w_{m} \\
-	1 - 1 \geq 1 - w_{3} &\geq \dots \geq w_{m-1} - 0 \\
-	0 \geq 1 - w_{3} &\geq \dots \geq w_{m-1}
-	\end{align*}
-	At this point either $0\leq w_{3}<1$ or $w_{3}=1$. In the first case 
-	\[0 \ngeq 1 - w_{3}\]
-	This breaks the convexity assumption so it is impossible.
-	In the second case, by definition there is a $w_{i} \neq 1$ where $2 < i \leq m$. So it would be 
-	\[0 \ngeq 1 - w_{i}\]
-	for some $i$. Again, the convexity is not satisfied.
-\end{proof}
-
-\begin{corollary}
-	\label{cor:weq}
-	If the weight sequence is convex and $w_{i} = w_{i+1}$ for some $i$, then $w_{j}=0 \ \forall \
-	j=i, \dots m$.
-\end{corollary}
-
-\section{Querying the chair}
-Suppose our query strategy suggests us to ask the chair the following query:
-\[ w_{2} - w_{3} \geq 2(w_{3} - w_{4}) \]
-Then we can transform it in:
-\begin{align}
-\label{eqn:juryquery}
-w_{2} - w_{3} &\geq 2 \cdot w_{3} - 2 \cdot w_{4} \notag \\
-w_{2} + 2 \cdot w_{4} &\geq 3 \cdot w_{3} 
-\end{align}
-and ask the committee if they would prefer as a winner an alternative ranked first one time and third three times rather than an alternative ranked second four times.
-
-Another way to query the committee, a more concrete one, is to present them a profile representing the situation described by the query and then deduce its answer from the selected winner.
-Obviously we have to be sure to choose a profile where only the alternatives we are interested in could be pick as winners.
-Therefore, we need a systematic way to construct a profile that reflects the situation outlined by the query for two alternatives and the others are not better than them.
-
-Assume we have a profile of $3$ agents ranking $4$ alternatives. We can represent it by columns where each of them represents the preference ordering of one agent.
-\[
-\begin{array}{ccc}
-v_1
-& v_2
-& v_3 \\
-\midrule 
-c
-& d
-& c \\
-a
-& c
-& d \\
-b
-& b
-& b \\
-d
-& a
-& a \\
-\end{array}
-\]
-
-Assuming anonymity, we can also write the profile expressing for each alternative $i \in A$ the number of agents placing it at a given rank.
-
-\[
-\begin{array}{ccccc}
-& 1^\circ
-& 2^\circ
-& 3^\circ
-& 4^\circ \\
-\cmidrule{2-5}
-a 
-& 0
-& 1
-& 0
-& 2 \\
-b
-& 0
-& 0
-& 3
-& 0 \\
-c
-& 2
-& 1
-& 0
-& 0 \\
-d
-& 0
-& 1
-& 1
-& 1 \\
-\end{array}
-\]
-
-Recalling the query (\ref{eqn:juryquery}) we are considering as an example, it is easy to see that in the current profile alternatives $a$ and $b$ represent the situation as described by the query.
-Therefore, if after proposing this profile to the committee the winning alternative turns out to be $a$ then we know that $w_{2} - w_{3} > 2(w_{3} - w_{4})$; if, instead, the winner is $b$ we know that $w_{2} - w_{3} < 2(w_{3} - w_{4})$ and if both alternatives are picked as winners then $w_{2} - w_{3} = 2(w_{3} - w_{4})$.
-
-Nevertheless, in this example it is clear that $c$ will always be preferred to other alternatives (see Claim \ref{clm:wsequence} in Section \ref{sec:weights}).
-To see it we can express for each alternative the number of agents placing it at a given rank or at a higher one.
-
-\[
-\begin{array}{ccccc}
-& \geq 1^\circ
-& \geq 2^\circ
-& \geq 3^\circ
-& \geq 4^\circ \\
-\cmidrule{2-5}
-a 
-& 0
-& 1
-& 1
-& 3 \\
-b
-& 0
-& 0
-& 3
-& 3 \\
-c
-& 2
-& 3
-& 3
-& 3 \\
-d
-& 0
-& 1
-& 2
-& 3 \\
-\end{array}
-\]
-
-\begin{claim}
-	Consider a set $A$ of $m$ alternatives and let $r_k(i)$ be the number of times the alternative $i$ obtains a rank $k$ or a higher one.
-Consider two alternatives $ i,j \in A$, if $\forall \ k=2, \dots,m \ r_k(i)\geq r_k(j)$ and $r_1(i) > r_1(j)$ then $i$ is always preferred to $j$ for any choice of weights.
-\end{claim}
-
-\begin{proof}
-	For our assumptions we know the sequence of weights is monotonic non-increasing and convex.
-Moreover, for the Claim \ref{clm:wsequence} in Section \ref{sec:weights}, we know that $w_1 > w_2$.
-Therefore, even in the worst case where $r_k(i) = r_k(j) \ forall \ k=2, \dots,m$ the sum of weights for alternative $i$ cannot be lower than the one for $j$.
-It is worth noting that we cannot say anything when $r_1(i) = r_1(j)$.
-Indeed, as said in Corollary \ref{cor:weq}, all the weights for other position but the first one can be equal, thus the number of agents ranking the alternatives at a certain position does not matter anymore.
-\end{proof}
-
-So the strategy for querying the committee is to use two alternatives $i$ and $j$ to represent the query and complete the profile such that the other alternatives are all dominated by them.
-An algorithmic approach is to start from the initial profile and then add as many agents as needed that rank $i$ and $j$ as their top choices and the other alternatives afterwards.
-As an example let consider again the query \ref*{eqn:juryquery}.
-We want the committee to choose between $a$ or $b$:
-
-\[
-\begin{array}{ccccc}
-& 1^\circ
-& 2^\circ
-& 3^\circ
-& 4^\circ \\
-\cmidrule{2-5}
-a 
-& 0
-& 1
-& 0
-& 2 \\
-b
-& 0
-& 0
-& 3
-& 0 \\
-\end{array}
-\]
-
-We add agents in order to increase the number of times $a$ and $b$ are ranked at first position.
-Please note we must maintain these scheme, so every add of a position to the ranking of $a$ must correspond to the same in the ranking of $b$.
-
-\[
-\begin{array}{cccccc}
-v_1
-& v_2
-& v_3 
-& v_4
-& v_5
-& v_6 \\
-\midrule 
-a
-& b
-& c 
-& d
-& a
-& b \\
-c
-& a
-& d
-& c
-& b
-& a \\
-b
-& d
-& b
-& b
-& d
-& c \\
-d
-& c
-& a
-& a
-& c
-& d \\
-\end{array}
-\]
-
-\[
-\begin{array}{ccccc}
-& 1^\circ
-& 2^\circ
-& 3^\circ
-& 4^\circ \\
-\cmidrule{2-5}
-a 
-& 2
-& 2
-& 0
-& 2 \\
-b
-& 2
-& 1
-& 3
-& 0 \\
-c
-& 1
-& 2
-& 1
-& 2 \\
-d
-& 1
-& 1
-& 2
-& 2 \\
-\end{array}
-\]
-
-\[
-\begin{array}{ccccc}
-& \geq 1^\circ
-& \geq 2^\circ
-& \geq 3^\circ
-& \geq 4^\circ \\
-\cmidrule{2-5}
-a 
-& 2
-& 4
-& 4
-& 6 \\
-b
-& 2
-& 3
-& 6
-& 6 \\
-c
-& 1
-& 3
-& 4
-& 6 \\
-d
-& 1
-& 2
-& 4
-& 6 \\
-\end{array}
-\]
-\textbf{Remarks:}
-\begin{itemize}
-	\item We are considering $\lambda \in \mathbb{N} \setminus \{0\}$ but we could be interested in a real number. \textit{Solution}: we can multiply both sides.
-\end{itemize}
-\fi
-\end{document}

### 2019-05-31 RJCIA2019/short_draft.tex
final version RJCIA

@@
 %Mon adresse compl\`ete \\
-\{firstname.lastname\}@dauphine.fr, paolo.viappiani@lip6.fr\\
+beatrice.napolitano@dauphine.fr, olivier.cailloux@dauphine.fr, paolo.viappiani@lip6.fr\\
 %{\bf Domaine principal de recherche}: RFP ou IA\\
@@
 
-\title{\Large\bf Simultaneous Elicitation of Committee and Voters Preferences}
+\title{\Large\bf Simultaneous Elicitation of Committee and Voters' Preferences}
 
@@
 {\em
-	Social choice deals with the problem of determining a consensus choice from the preferences of different agents.
-In the classical setting, the voting rule is fixed beforehand and full information concerning the preferences of the agents is provided.
+	Social choice deals with the problem of determining a consensus choice from the preferences of different voters.
+In the classical setting, the voting rule is fixed beforehand and full information concerning the preferences of the voters is provided.
 	Recently, the assumption of full preference information has been questioned by a number of researchers and several methods for eliciting preferences have been proposed.
 %	\commentOC{This “we go one step further” sounds odd here. I suggest one more sentence about the normal elicitation setting with only the agents preferences partially specified.}
-	In this paper we go one step further and we assume that both the voting rule and the agents preferences are partially specified.
-In this setting, we present an interactive elicitation protocol based on minimax regret and develop several query strategies that interleave questions to the chair and questions to the agents in order to attempt to acquire the most relevant information in order to quickly converge to optimal or a near-optimal alternative.
+	In this paper we go one step further and we assume that both the voting rule and the voters' preferences are partially specified.
+In this setting, we present an interactive elicitation protocol based on minimax regret and develop several query strategies that interleave questions to the chair and questions to the voters in order to attempt to acquire the most relevant information in order to quickly converge to optimal or a near-optimal alternative.
 }
@@
 %In this contexts, a natural approach consists in looking at methods from social choice and see how they can be adapted for group decision-making in a computerized setting. 
-In a traditional social choice setting, both the social choice function and the full preference orderings of the agents are expressed beforehand.
-Nevertheless, requiring agents to express full preference orderings can be prohibitively costly (in terms of cognitive and communication cost), especially for decisions with large sets of alternatives.
-This observation has motivated a number of recent works considering social choice with partial preference orders \citep{Xia2008, Pini2009, Konczak05} and incremental elicitation \citep{Kalech2011, Lu2011, Naamani-Dery2015} of agents’ preferences.
-Furthermore, several situations for which it may not be easy to precisely define the voting rule exist.
-Indeed, it is possible that the chair has some preferences over the desired aggregation method, but is not able to formalize the voting rule upfront.
-The work of Cailloux and Endriss \citep{Cailloux2014} provides elicitation methods for a quite general class of rules based on weak orders.
-When considering positional scoring rules, several authors \citep{Stein1994, Llamazares2013, Viappiani2018} have worked on positional scoring rules with uncertain weights, assuming that the preferences of the agents are fully known.
-In this paper we consider that both the agents’ preferences and the social choice rule are partially specified.
+In a traditional social choice setting, both the social choice function and the full preference orderings of the voters are expressed beforehand.
+Nevertheless, in real situations this is not always the case.
+When considering decisions with large sets of alternatives, requiring voters to express full preference orderings can be prohibitively costly and, perhaps, not necessary in order to determine a consensus choice.
+Furthermore, it is often difficult for non-expert users to formalize a voting rule on the basis of some generic preferences over a desired aggregation method.
+Consider as an example a situation in which the council of a city wants to build a community allotment and the decision of what to grow has to be taken.
+The voters are the residents of the neighborhood and the alternatives consist of all the vegetables that can grow in that particular area.
+An external observer, who is helping with the voting procedure, is responsible for collecting the preferences of both the residents (regarding the vegetable to grow) and the members of the council (regarding the method for aggregating the residents' preferences).
+Imagine that, after collecting some preferences, she notices that some alternatives are always the least preferred.
+In this case, it is really unlikely that these alternatives would be selected as winners by any reasonable voting rule.
+Thus, she may consider to ask the voters only their preferences over few strategical alternatives instead of asking them the full preference orderings.
+Furthermore, if she notices that a particular vegetable is the most preferred of almost the totality of the residents there is no need to know the specific voting rule.
+Any reasonable aggregation procedure, in fact, would select this alternative as a winner.
+The reason behind this consideration is that is not unrealistic to assume that the committee, that has to decide how to aggregate these preferences, is not able to define a specific procedure.
+\\
+These observations have motivated a number of recent works considering social choice with partial preference orders \citep{Xia2008, Pini2009, Konczak05} and incremental elicitation \citep{Kalech2011, Naamani-Dery2015} of voters' preferences.
+Lu and Boutilier \cite{Lu2011} have proposed the use of minimax regret to drive incremental vote and preferences elicitation when the social choice function is fixed and known.
+Furthermore, several authors \citep{Stein1994, Llamazares2013, Viappiani2018} have worked on positional scoring rules with uncertain weights, assuming that the preferences of the voters are fully known.
+Some elicitation methods for a quite general class of rules based on weak orders have also been proposed by Cailloux and Endriss \citep{Cailloux2014}.
+\\
+In this paper we focus on positional scoring rules, that are
+a particularly common method used to aggregate rankings, and we assume that both the voters’ preferences and the social choice rule are partially specified.
 We develop methods for computing the minimax-optimal alternative using positional scoring rules and we provide incremental elicitation methods to acquire relevant preference information.
-We then discuss several heuristics that determine queries, either to an agent or to the committee, that quickly reduce minimax regret.
-While previous works have considered either partial information about the agents preferences or a partially specified aggregation method, we do not know of any work considering both sources of uncertainty at the same time.
+We then discuss several heuristics that determine queries, either to a voter or to the committee, that quickly reduce minimax regret.
+While previous works have considered either partial information about the voters' preferences or a partially specified aggregation method, we do not know of any work considering both sources of uncertainty at the same time.
 
@@
 \label{sec:background}
-We consider a set $A$ of $m$ alternatives (products, restaurants, public projects, etc.) and a set $\set{1, …, n}$ of agents.
-Each agent $j$ comes from an infinite set $\N$ of potential agents and is associated to her “real” preference order $\pref_j \in \linors$ which is a linear order (connected, transitive, asymmetric relation) over the alternatives.
-A {\em profile} is the association of a preference to each agent and it is equivalently represented by $(\pref_1,\ldots,\pref_n)$ or by $\profile=(v_1,\ldots,v_n) \in V$ where $v_j(i) \in \set{1, \ldots, m}$ denotes the rank (position) of alternative $i$ in the preference order $\pref_j$.
-%Given $V$ the set of possible preference profiles, a social choice function $f : V \rightarrow \powersetz{A}$ associates a profile with a set of winners; where $\powersetz{A}$ represents the set of subsets of $A$ except for the emptyset.
-A social choice function associates a profile with a set of winners; we consider {\em positional scoring rules (PSR)}, which attach weights to positions according to the scoring vector $(w_1, \ldots, w_m)$.
-An alternative obtains a score that depends on the rank obtained in each of the preference orders and the winners are the alternatives with highest scores.
-In this work we assume fixed, but unknown, a profile $\profile^* = (\pref^*_j, j \in \{1, \ldots, n\})$ and a weight vector $\w^*$.
-Our knowledge at a given time of the preference of agent $j$ is encoded by a partial order over the alternatives, thus a transitive and asymmetric binary relation, denoted by $\ppref_j$; we assume that preference information is truthful, i.e.
-%${\ppref_j} \subseteq {\pref_j^*}$.
-$a \ppref_j b ⇒ a \pref_j^* b$.
+We consider a set $A$ of $m$ alternatives (products, restaurants, public projects, etc.) and a set $\set{1, …, n}$ of voters.
+Each voter $j$ comes from an infinite set $\N$ of potential voters and is associated to her “real” preference order $\pref_j$ which is a linear order (connex, transitive, asymmetric relation) over the alternatives.
+A {\em profile} is the association of a preference to each voter and it is equivalently represented by $(\pref_1,\ldots,\pref_n)$ or by ${\profile=(v_1,\ldots,v_n) \in V}$ where $v_j(i) \in \set{1, \ldots, m}$ denotes the rank (position) of alternative $i$ in the preference order $\pref_j$ and $V$ is the set of all possible preference profiles.
+A social choice function associates a profile with a set of winners; we consider {\em positional scoring rules (PSR)} which attach weights to positions according to the scoring vector $(w_1, \ldots, w_m)$.
+Without loss of generality, we assume $w_1=1$ and $w_m=0$.
+An alternative $x$ obtains a score that depends on the rank obtained in each of the preference orders:
+\begin{align*}
+\label{eq:srule}
+s^{\profile, \w}(x) = \sum_{j=1}^{n} w_{v_j(x)}
+= \sum_{r=1}^{m} \alpha^{x}_r w_r 
+\end{align*}
+where $\alpha^{x}_r$ is the number of times that alternative $x$ was ranked in the $r$-th position. The winners are the alternatives with highest scores.
+
+In this work we assume fixed, but unknown, a profile $\profile^* = (\pref^*_1, \ldots, \pref^*_n)$ and a weight vector $\w^*$.
+Our knowledge at a given time of the preference of voter $j$ is encoded by a partial order over the alternatives, thus a transitive and asymmetric binary relation, denoted by $\ppref_j$; we assume that preference information is truthful, i.e.
+${a \ppref_j b ⇒ a \pref_j^* b}$.
 %\commentOC{Or simply ${\ppref_j} \subseteq {\pref_j^*}$, if you need to save space}
 %We use $\pinc$ to denote incomparability, that is $a \pinc_{j} b$ iff $a \nppref_j b \wedge b \nppref_j a$.
-An incomplete profile $\pprofile = (\ppref_1, \ldots, \ppref_n)$ maps each agent to a partial preference.
-A completion of $\ppref_j$ is any linear order $\pref$ that extends $\ppref_j$ and we indicate with $C(\ppref_j) = \set{{\succ} \in \linors \suchthat {\ppref_j} \subseteq {\succ}}$ the set of possible completions of $\ppref_i$.
+An incomplete profile ${\pprofile = (\ppref_1, \ldots, \ppref_n)}$ maps each voter to a partial preference.
+A completion of $\ppref_j$ is any linear order $\pref$ that extends $\ppref_j$ and we indicate with $C(\ppref_j) = \set{{\succ} \in \linors \suchthat {\ppref_j} \subseteq {\succ}}$ the set of possible completions of $\ppref_j$, where $\linors$ is the set of linear orders on $A$.
 %We let $C(\pprofile)=C(\ppref_1)\times … \times C(\ppref_n)$ be the set of complete profiles extending $p$. Note that $\profile^* \in C(\pprofile)$.
 
-Our knowledge regarding the weights of the scoring rule is represented by
+Our knowledge regarding the weights of the positional scoring rule is represented by
 %We also assume that the weights of the scoring rule are only partially specified.
@@
 Given the set of convex weight vectors $\W$, we use $\pw \subseteq \W$ to denote the set of weight vectors compatible with the chair's preferences.
+We will provide an example of such constraints, used to specify information about weights, in Section \ref{sec:elicit}.
 
@@
 \label{sec:mmr}
-As a decision criterion to determine a winner, we propose to use minimax regret \citep{Savage1954}. 
-%Minimax regret \citep{Savage1954} is a decision criterion that has been used for robust optimization under data uncertainty \citep{Kouvelis1997} as well as in decision-making with uncertain utility values \citep{Salo2001,Boutilier2006}.
-%\citet{Lu2011} have adopted minimax regret for winner determination in social choice with
-%the preferences of the agents that are only partially known, while the social choice function is predetermined and known.
-%In this work we consider the simultaneous presence of uncertainty in the agents' preferences and uncertainty in the weights.
+As a decision criterion to determine a winner, we propose to use minimax regret \cite{Savage1954}.
+This concept has been used for robust optimization under data uncertainty \cite{Kouvelis1997} as well as in decision-making with uncertain utility values \cite{Salo2001,Boutilier2006}.
+Lu and Boutilier \cite{Lu2011} have adopted this criterion for winner determination in social choice with the preferences of the voters that are only partially known, while the social choice function is predetermined and known.
+%In this work we consider the simultaneous presence of uncertainty in the voters' preferences and uncertainty in the weights.
 We use {\em maximum regret} to quantify the worst-case error, which measures, intuitively, how far an alternative is from the optimal one given current knowledge; 
-% about the voting rule and the agents' preferences.
+% about the voting rule and the voters' preferences.
 the alternatives that minimize this error are selected as tied winners.
@@
 We formalize the notion of minimax regret in multiple steps.
-First of all, $\Regret(x, \profile, \w)$ is the “regret” of selecting $x$ as a winner instead of choosing the optimal alternative under $\profile$ and $\w$:
-\[\Regret(x, \profile, \w) = \max_{y \in A} s(y; \profile,\w) - s(x; \profile, \w).\]
-The pairwise max regret $\PMR(x,y;\pprofile,W)$ of $x$ relative to $y$ given partial profile $\pprofile$ and the set of weights $W$ is the worst-case loss of choosing $x$ instead of $y$ under all possible realizations of the full profile {\em and} weights.
-Max regret $\MR(x;\pprofile,W)$ is the worst-case loss of $x$ and $\MMR(\pprofile,W)$ is the value of minimax regret obtained when recommending a minimax optimal alternative $x^*_{\pprofile, W}$.
+First of all, $\Regret^{\profile,\w}(x)$ is the “regret” of selecting $x$ as a winner instead of choosing the optimal alternative under $\profile$ and $\w$:
+\[\Regret^{\profile,\w}(x) = \max_{y \in A} s^{\profile,\w}(y) - s^{\profile, \w}(x).\]
+The pairwise max regret $\PMR^{\pprofile,W}(x,y)$ of $x$ relative to $y$ given partial profile $\pprofile$ and the set of weights $W$ is the worst-case loss of choosing $x$ instead of $y$ under all possible realizations of the full profile {\em and} weights.
+Max regret $\MR^{\pprofile,W}(x)$ is the worst-case loss of $x$ and $\MMR^{\pprofile,W}$ is the value of minimax regret obtained when recommending a minimax optimal alternative.
 %\begin{align}
@@
 \begin{align}
-\PMR(x,y; \pprofile, W) & = \max_{\w \in W} \max_{\profile \in C(\pprofile)} s(y; \profile,\w) - s(x; \profile,\w) \\
-\MR(x; \pprofile, W) & = \max_{y \in A} \PMR(x,y; \pprofile, W)\\
+\PMR^{\pprofile,W}(x,y) & = \max_{\w \in W} \max_{\profile \in C(\pprofile)}s^{\profile,\w}(y) - s^{\profile, \w}(x) \\
+\MR^{\pprofile,W}(x) & = \max_{y \in A} \PMR^{\pprofile,W}(x,y)\\
 %& = \max_{\w \in W} \max_{\profile \in C(\profile)} \Regret(x, \profile, \w) \\
-\MMR(\pprofile,W) & = \min_{x \in A} \MR(x;\pprofile,W) \\
-x^{*}_{\pprofile,W} \in A^*_{\pprofile, W} & = \argmin_{x \in A} \MR(x;\pprofile,W) 
+\MMR^{\pprofile,W} & = \min_{x \in A} \MR^{\pprofile,W}(x) \\
+x^{*}_{\pprofile,W} & = \argmin_{x \in A}\MR^{\pprofile,W}(x) \in A^*_{\pprofile, W}
 \end{align}
@@
 %\end{align*}
-By picking as consensus choice an alternative associated with minimax regret, we can provide a recommendation that gives worst-case guarantees, giving some robustness in face of uncertainty. 
-$\PMR$ can be computed by adapting the reasoning of Lu and Boutilier \cite{Lu2011} to the case of uncertain weights using linear programming.
+By picking as consensus choice an alternative associated with minimax regret $x^*_{\pprofile, W} \in A^*_{\pprofile, W} $, we can provide a recommendation that gives worst-case guarantees, giving some robustness in face of uncertainty.
+%\[x^{*}_{\pprofile,W} = \argmin_{x \in A}\MR^{\pprofile,W}(x)\]
+In cases of ties in minimax regret, we can either decide to return all minimax alternatives $A^*_{\pprofile, W}$ as winners or to pick just one of them using a tie-breaking strategy.
+Because the constraints in $\Co_W$ are not necessarily linear $\PMR$ is not straightforwardly optimized, but it can be computed by adapting the reasoning of Lu and Boutilier \cite{Lu2011} to the case of uncertain weights using linear programming.
+This optimization strategy uses the assumption of convexity.
 %In cases of ties in minimax regret, we can either decide to return all minimax alternatives $A^*_{\pprofile, W}$ as winners or to pick just one of them using some tie-breaking strategy.
@@
 We propose an incremental elicitation method based on minimax regret.
-At each step, the system may ask a question either to one of the agents or to the chair.
+At each step, the system may ask a question either to one of the voters or to the chair.
 The goal is to acquire relevant information to reduce minimax regret as quickly as possible.
@@
 \paragraph{Question types}
-We distinguish between questions asked to the agents and questions asked to the chair.
-For the first we consider comparison queries that ask a particular agent to compare two alternatives. Then, the partial profile $\pprofile$ is augmented on the basis of the agent's answer.
-The latter, instead, aims at refining our knowledge about the scoring rule; in particular, we assume we can acquire constraints of the type:
+We distinguish between questions asked to the voters and questions asked to the chair.
+For the first we consider comparison queries that ask a particular voter to compare two alternatives.
+Then, the partial profile $\pprofile$ is augmented on the basis of the voter's answer.
+Thus, if voter $j$ answers a comparison query stating that alternative $a$ is preferred to $b$, then the partial order $\ppref_j$ is augmented with $a \ppref_j b$ and by transitive closure.
+The query for the chair, instead, aims at refining our knowledge about the scoring rule; in particular, we assume we can acquire constraints of the type:
 \[ w_{r} - w_{r+1} \geq \lambda (w_{r+1} - w_{r+2}) \] 
@@
 
-The \strat{Extreme completions} strategy considers the solution of the minimax regret game and estimates the contribution to the regret of our uncertainty about the weights and the profile.
-Then it asks a question to the chair or to the agents depending on which of these two values is the highest.
+The \strat{Extreme completions} strategy considers the solution of the minimax regret game, given the current knowledge, and estimates the contribution to the regret of our uncertainty about the weights and the profile.
+Then, it selects a question for the chair or for the voters depending on which of these two values is the highest.
 
 The \strat{Pessimistic} strategy selects among all the possible questions the one that leads to minimal regret in the worst case.
-For each question, it considers both possible answers to the question and uses some aggregation of their MMRs as a score of the question.
+Because all our questions are binary questions, for each of them the pessimistic strategy first assumes the answer is \emph{"No"}, it updates the knowledge according to this negative answer and computes the minimax regret.
+Then, it does the same assuming the answer is positive.
+Finally, it uses some aggregation of these two MMR values (for example \emph{max} or \emph{avg}) as a score of the question.
+The question with the highest score is selected.
 
-The \strat{Two phase} strategy asks a predefined, non adaptive sequence of $m-2$ questions to the chair and then it only asks questions about the agents, using questions as defined in the \strat{Pessimistic} strategy.
+The \strat{Two phase} strategy asks a predefined, non adaptive sequence of $m-2$ questions to the chair in order to gather informations about the weights $\w$ of the scoring rule, using one question per rank except the extreme ones that we are assuming known ($w_1=1$, $w_m=0$).
+Then it only asks questions about the voters, using questions as defined in the \strat{Pessimistic} strategy.
 
@@
 
-The next step is to test our strategies in order to compare the performance of our interleaved elicitation approach that mixes questions to the chair and to the agents, to a more classical approach that elicits the rule first and then the agents preferences (or vice-versa).
+The next step is to test our strategies in order to compare the performance of our interleaved elicitation approach that mixes questions to the chair and to the voters, to a more classical approach that elicits the rule first and then the voters' preferences (or vice-versa).
 
-Further development of elicitation strategies, considering alternative heuristics, is also an important direction for future works together with the extension of the approach to voting rules beyond scoring rules.
+Further development of elicitation strategies, considering alternative heuristics, is also an important direction for future work together with the extension of the approach to voting rules beyond scoring rules.
+\bigskip
 
-% Acknowledgements: We thank the reviewers for comments helping to improve the paper. 
+Acknowledgements: We thank the reviewers for comments helping to improve the paper. 
 %{\small
 \bibliography{biblio}
-\bibliographystyle{plain}
+\bibliographystyle{abbrv}
 %\bibliographystyle{plain} 
@@
 \end{document}
-
-\appendix
-\section{Minimax Computation under Convex Assumption}
-
-Refer to \citep{Lu2011}
-The goal is to choose as a winner the alternative $x^*$ whose worst case loss is minimal under all possible realizations of the full profile and all possible choices of weights. 
-Assume hereinafter the selected weights sequence $\w \in W$ to be convex. 
-In order to compute the minimal max regret $\MMR(\pprofile)$ under partial profile $\pprofile$ we need to compute the pairwise max regret between all pairs of alternatives $(x,y)$, where $x$ is a proposed winner and $y$ is the ``adversary'' alternative.
-Indeed, the construction of $\PMR(x,y,\pprofile,\w)$ can be viewed as an adversary's attempt to maximize the regret of choosing $x$ instead of $y$.
-For doing this, he can choose a completion $\profile_i \in C(\pprofile_i)$ of the partial profile and a (feasible) scoring vector $\w$ that maximize the contribution of the agent $i$ to $\PMR(x,y,\pprofile,\w)$.
-Let us now analyze how it could be done depending on the relation between alternatives $x$ and $y$ in $\pprofile_i$.
-\begin{itemize}
-	\item $x \succ_i^\pprofile y$
-	\newline If we know $x$ is preferred to $y$ and we choose $x$ as a winner, $\pprofile_i$ contribution to $\PMR(x,y,\pprofile,\w)$ must be negative.
-In this situation, our adversary can only try to minimize this advantage by minimizing the positional gap between the two alternatives.
-To achieve that, he can arbitrary place all the alternatives preferred to $x$ above $x$, together with all the ones with unknown relation to $x$.
-Moreover, he can place all the alternatives less preferred to $x$ and with unknown relation to $y$ below $y$.
-We can summarize it for each $q \in A$ as follows:
-	\begin{align*}
-	q \succ_i^\pprofile x \vee q \ ?_i^\pprofile \ x \ & \Rightarrow \ \uparrow_x \\
-	x \succ_i^\pprofile q \wedge ( q \ ?_i^\pprofile \ y \vee y \succ_i^\pprofile q) \ & \Rightarrow \ \downarrow_y \\
-	x \succ_i^\pprofile q \succ_i^\pprofile y \ & \Rightarrow \ \text{in between} \\
-	\end{align*}
-	It is worth noting that when the relation between $q$ and $x$ is not known in the partial profile, the adversary takes advantage by placing $q$ above $x$ only under the assumption of convex weight sequences.
-	\item $y \succ_i^\pprofile x$
-	\newline If $y$ is preferred to $x$ the construction proceeds similarly to the previous case, but now the adversary takes advantage by maximizing the gap between $x$ and $y$ placing as much alternatives as he can between the two.
-We can summarize the procedure for each $q \in A$ as follows:
-	\begin{align*}
-	q \succ_i^\pprofile y \ & \Rightarrow \ \uparrow_y \\
-	x \succ_i^\pprofile q \ & \Rightarrow \ \downarrow_x \\
-	(y \succ_i^\pprofile q \vee y \ ?_i^\pprofile \ q) \wedge (q \succ_i^\pprofile x \vee q \ ?_i^\pprofile \ x) \ & \Rightarrow \ \text{in between} \\
-	\end{align*}
-	\item $x \ ?_i^\pprofile \ y$
-	\newline If the partial profile $\pprofile_i$ does not specify the relation between $x$ and $y$, the advantage is maximized by ordering $y$ over $x$ and maximizing the gap between them following the procedure for the case $y \succ_i^\pprofile x$.
-\end{itemize}
-
-\section{Dropping the Convex Assumption}
-\subsection{Profile completion}
-What if the sequence of weights is not convex?
-When $y \succ_i^\pprofile x$ or $x \ ?_i^\pprofile \ y$ weights do not influence the arbitrary placement of alternatives.
-Please remind we are working under the assumption that weights constitute a monotonic non-increasing sequence.
-Thus, there is no way for the adversary to take advantage from the weights distribution in order to increase the gap between $y$ and $x$ besides placing as much alternatives as he can between the two.
-The only case in which weights can influence the positional gap between $x$ and $y$ is when $x \succ_i^\pprofile y$ and $q \ ?_i^\pprofile \ x$.
-For convex sequences we place such alternatives $q$ above $x$, but it is not obvious that this is the best option for other sequences.
-For example, suppose $x$ and $y$ are ranked respectively in first and second position in the partial profile and we wonder where to place an alternative $q$ with unknown relation to $x$ (and thus to $y$).
-Suppose also that in the weight sequence the distance between the first and second positions is much lower than the one between the second and the third ones.
-In this case, placing $q$ above $x$ does not minimize the gap between $x$ and $y$ but we want, instead, to place $q$ below $y$.
-\newline The constraints expressed by the chair may result in a set of feasible vectors such that none of them forms a convex sequence.
-In this case we need to analyze the particular sequence of weights in order to decide how to maximize the adversary advantage.
-Before going into details, let us define $A$ as the set of alternatives (if any) preferred to $x$, $B$ as the set of alternatives preferred to $y$ but not to $x$, and $U$ the set of those with unknown relation to both $x$ and $y$.
-The idea is to determine the positions that minimize $x$'s advantage over $y$ and then place some of the alternatives in $U$ above $x$ and some below $y$ in order to get that desired ranking.
-Since we cannot change the order of the alternatives in the set $B$ we know that $x$ and $y$ are separated exactly by $|B|$ positions (the adversary would not take any advantage by adding alternatives between them).
-So, starting from the position of $x$ in the partial completion of $\pprofile_i$ computed so far ($\hat{\profile}_i$), we find the two positions separated by $|B|$ alternatives whose weights difference is the lowest.
-Note that we can only add $|U|$ alternatives so we can check only until the position $\hat{\profile}_i(x)+|U|$.
-Algorithm \ref{alg:splittingU} shows the procedure described.
-
-It is easy to see that we check at most $|U|$ positions.
-In the worst case the size of $U$ is equal to $m-2$, thus the procedure can be computed in $O(m)$ time.
-This cost does not affect the minimax regret computation time complexity that remains $O(nm^3)$.
-
-\begin{algorithm}[h] 
-	\caption{Placing alternatives in $U$ without Convex Assumption}
-	\label{alg:splittingU} 
-	\begin{algorithmic}
-		\Require $x$, $y$, $\hat{\profile}_i$, $\w$, $U$, $B$
-		\Ensure $\profile_i \in C(\pprofile)$
-		\Statex
-		\State $ j \gets 0$;
-		\State $ i \gets \hat{\profile}_i(x)$;
-		\State $ \mathit{posmin} \gets i$;
-		\State $ \mathit{min} \gets \w(i) - \w(i+1+|B|)$;
-		\While {$( j \leq |U| )$}
-		\If{ $(\w(i+j)-\w(i+1+|B|+j) < \mathit{min})$ }
-		\State $ \mathit{min} \gets \w(i+j) - \w(i+1+|B|+j)$;
-		\State $ \mathit{posmin} \gets i+j$;
-		\EndIf
-		\EndWhile
-
-		\State $U_{\mathit{abovex}} \gets (i-\mathit{posmin}) \text{ alternatives} \in U $;
-		\State $U_{\mathit{belowy}} \gets U \setminus U_{\mathit{above}}$;
-		\Statex
-		\State $\profile_i \gets place(\pprofile_i,U_{\mathit{abovex}},U_{\mathit{belowy}})$;
-		\Statex \Return $\profile_i$
-
-	\end{algorithmic}
-\end{algorithm}
-
-\section{Minimax regret without the convex assumption}
-Without the convex assumption, we cannot use $\hat{v}$ for the agents in $U^{-}$, but only for agents in $U^{+}$ and $U^{?}$.
-%Let $\hat{v}_i$ be the linear order extending $\succ^{p}_i$ according to the above procedure.
-Then PMR can be written as follows:
-\begin{align*}
- &\PMR(x,y; \pprofile, W) =\\ 
- &\max_{\w \in W} \Big \{ \sum_{j \in U^-} [\max_{v_j \in C(\succ_j^p)} [w_{v_j(y)} \!-\! w_{v_j(x)}]] 
-  \!+\!	 \sum_{j \in A^+ \cup  U^?} [w_{\hat{v}_j(y)} \!-\! w_{\hat{v}_j(x)}] \Big \} 
- \end{align*}
-%Note that the second addendum inside the max do not depend on the choice of $\w$.
-Consider the two addenda inside the ``max''. 
-The first addendum is concerned with positioning of alternatives $x$ and $y$ for agents in $U^{-}$ for which we know that $x$ is preferred to $y$.
-The second addendum is concerned with agents in $U^{+}$ and $U^{?}$.
-We rewrite the second addendum as:
-\begin{align*}
-\sum_{j \in U^+ \cup  U^?} [w_{\hat{v}_j(y)} \!-\! w_{\hat{v}_j(x)}] 
-= \sum_{i = 1}^{m} (\hat{\alpha}_{i}^{y} - \hat{\alpha}_{i}^{x}) w_{i}
-\end{align*}
-where $\hat{\alpha}_{i}^{x}$ is the number of times that $x$ is ranked  in position $i$  considering the profile $\hat{v}$ of agents in $U^+ \cup  U^?$.
-%We compute pairwise maximum regret by considering binary variables $\{ B_{i} \}_{i=1,\ldots,m}$ to represent optimization choices related to where to position the alternatives.
-
-We now address the agents in $A^{-}$
-For a given $j$, let $\beta$ be the number of alternatives that are incomparable with $x$ and $y$:
-\[ \beta_{j} = \mid \{ c : c \pinc_{j} y \wedge c \pinc_{j} x \} \mid \]
-$x$ can be ranked between $t_{1}(j)=\mid \{ c \in A : c \ppref_{j} y \wedge x \nppref_{j} c \} \mid $ and position $t_{2}(j)=t_{1}(j)+\beta_{j}$.
-The completion for agent $j$ is such that the positions of $x$ and $y$ differ of exactly $\gamma_{j} =
-\mid \{ c \in A : x \ppref c \ppref y \} \mid$ positions.
-
-We now show how to optimize $\PMR$.
-In addition to variables $\{ w_{j} \}_{j=1,\ldots,m}$ (one for each position) we need to employ several additional decision variables.
-We introduce two sets of binary variables $B^{+}_{i,j}$ and $B^{-}_{i,j}$  for each position $i$ and for each agent $j$.
-Variable $B_{i,j}^{+}$ encodes the fact that the alternative $y$ is placed in position $i$ in the ranking of agent $j$; while  $B_{i,j}^{-}$ encodes the same thing for alternative $x$.
-%We also have numerical variables to represent the weights of the scoring rule.
-Since each alternative needs to be placed exactly in one place for each agent, we adopt the constraints
-$\sum_{i=t_{1}(j)}^{t_{2}(j)} B_{i,j}^{+} = 1$.
-Since we know that $x$ and $y$ are ranked $\gamma_{j}$ positions apart, we set the constraint:
-$B_{i+\gamma_{j},j}^{-} \geq B_{i,j}^{+}$,  for $i = \{ t_{1}(j), \ldots, t_{2}(j)\}$.
-
-% and $\sum_{i=1}^{m} B_{i,j}^{-} = 1$.
-%Since the objective is to maximize pairwise regret...
-
-The score of alternative $y$ can be written as $\sum_{i = 1}^{m} \hat{\alpha}_{i}^{y}  w_{i} + \sum_{i=1}^{n} \sum_{j=1}^{m} w_{j} B_{i,j}^{+}$.
-The objective function is now:
- \[ \max \sum_{i = 1}^{m} (\hat{\alpha}_{i}^{y} - \hat{\alpha}_{i}^{x}) w_{i} +  \sum_{i=1}^{n} \sum_{j=1}^{m} (B_{i,j}^{+} - B_{i,j}^{-})  w_i \]
-
-We use integer programming enconding tricks in order to linearize the problem.
-We introduce yet another set of variables  $V_{i,j}^{+} $  and $V_{i,j}^{-}$ % the multiplicative terms by new variables.
-and we enforce that $V_{i,j}^{+} = B^{+}_{i,j} w_i$ by setting constraints $V_{i,j}^{+} \leq B^{+}_{i,j}$ and $V_{i,j}^{+}  \leq w_i$.
-We have similar constraints for enforcing $V_{i,j}^{-} = B^{-}_{i,j} w_i$.
-
-We therefore obtain the following mixed integer linear program:
-\newcommand{\C}{\mathcal{C}}
-\begin{align}
-\max & \sum_{i=1}^m  [(\hat{\alpha}_{i}^{y} - \hat{\alpha}_{i}^{x}) w_{i}] +
-  \sum_{j \in A^{-}} \sum_{i=t_{1}}^{t_{2}}  [V_{i,j}^{+} - V_{i,j}^{-}]
-\end{align}
-\begin{align}
-\text{ s.t. } &  \text{Equation } (\ref{eq:monotone}) & \\
-&  \C(\w) &  \\
-& \sum_{i=t_{1}}^{t_{2}} B_{i,j}^{+} = 1 & \forall j \in A^{-} \\
-& B_{i+\gamma_{j},j}^{-} \geq B_{i,j}^{+} & \forall i \in \{ t_{1}, \ldots t_{2}\}, \forall j \in A^{-} \\
-& V_{i,j}^{+} \leq B_{i,j}^{+}  & \forall i \in \{ t_{1}, \ldots t_{2}\}, j \in A^{-} \\
-& V_{i,j}^{+} \leq w_i & \forall i \in \{ t_{1}, \ldots t_{2}\}, j \in A^{-} \\
-& V_{i,j}^{-} \geq w_{i} + B_{i,j}^{-} - 1 & \forall i \in \{ t_{1}, \ldots t_{2}\}, j \in A^{-}\\
-& V_{i,j}^{-} \geq 0 & \forall i \in \{ t_{1}, \ldots t_{2}\}, j \in A^{-}
-\end{align} 
-%We write $w \in W$ as a shourtcut to represent the constraints that the weights are chosen to be in the feasible set.
-There are (at most) $nm$ binary variables and $m(n+1)$ numerical variables.
-The optimization program can be solved by any suitable MILP solver, although it is not suitable to large problem instances.
-
-% DONT KNOW IF WE HAVE TO FORMALIZE THIS AS A CLAIM
-%\begin{claim}
-%The $\PMR$ is computed using the above optimization problem.
-%\end{claim}
-
-\section{Considerations on weights}
-\label{sec:weights}
-Let us consider a monotonic non-increasing sequence of weights: $w_{1} \geq w_{2} \geq \ldots \geq w_{m}$. Without loss of generality, we can assume $w_1=1$ and $w_m=0$.
-
-\begin{claim}
-	\label{clm:wsequence}
-	If the weight sequence is convex then $w_{1} > w_{2}$.
-	\[\forall i \in \{1,\ldots,m\} \;\; w_i - w_{i+1} \geq w_{i+1}-w_{i+2} \Rightarrow w_{1} > w_{2} \geq \ldots \geq w_{m}\] 
-\end{claim}
-\begin{proof}
-	By contradiction let assume $w_{1} = w_{2}$ then 
-	\begin{align*}
-	w_{1} - w_{2} \geq w_{2} - w_{3} &\geq \dots \geq w_{m-1} - w_{m} \\
-	1 - 1 \geq 1 - w_{3} &\geq \dots \geq w_{m-1} - 0 \\
-	0 \geq 1 - w_{3} &\geq \dots \geq w_{m-1}
-	\end{align*}
-	At this point either $0\leq w_{3}<1$ or $w_{3}=1$. In the first case 
-	\[0 \ngeq 1 - w_{3}\]
-	This breaks the convexity assumption so it is impossible.
-	In the second case, by definition there is a $w_{i} \neq 1$ where $2 < i \leq m$. So it would be 
-	\[0 \ngeq 1 - w_{i}\]
-	for some $i$. Again, the convexity is not satisfied.
-\end{proof}
-
-\begin{corollary}
-	\label{cor:weq}
-	If the weight sequence is convex and $w_{i} = w_{i+1}$ for some $i$, then $w_{j}=0 \ \forall \
-	j=i, \dots m$.
-\end{corollary}
-
-\section{Querying the chair}
-Suppose our query strategy suggests us to ask the chair the following query:
-\[ w_{2} - w_{3} \geq 2(w_{3} - w_{4}) \]
-Then we can transform it in:
-\begin{align}
-\label{eqn:juryquery}
-w_{2} - w_{3} &\geq 2 \cdot w_{3} - 2 \cdot w_{4} \notag \\
-w_{2} + 2 \cdot w_{4} &\geq 3 \cdot w_{3} 
-\end{align}
-and ask the committee if they would prefer as a winner an alternative ranked first one time and third three times rather than an alternative ranked second four times.
-
-Another way to query the committee, a more concrete one, is to present them a profile representing the situation described by the query and then deduce its answer from the selected winner.
-Obviously we have to be sure to choose a profile where only the alternatives we are interested in could be pick as winners.
-Therefore, we need a systematic way to construct a profile that reflects the situation outlined by the query for two alternatives and the others are not better than them.
-
-Assume we have a profile of $3$ agents ranking $4$ alternatives. We can represent it by columns where each of them represents the preference ordering of one agent.
-\[
-\begin{array}{ccc}
-v_1
-& v_2
-& v_3 \\
-\midrule 
-c
-& d
-& c \\
-a
-& c
-& d \\
-b
-& b
-& b \\
-d
-& a
-& a \\
-\end{array}
-\]
-
-Assuming anonymity, we can also write the profile expressing for each alternative $i \in A$ the number of agents placing it at a given rank.
-
-\[
-\begin{array}{ccccc}
-& 1^\circ
-& 2^\circ
-& 3^\circ
-& 4^\circ \\
-\cmidrule{2-5}
-a 
-& 0
-& 1
-& 0
-& 2 \\
-b
-& 0
-& 0
-& 3
-& 0 \\
-c
-& 2
-& 1
-& 0
-& 0 \\
-d
-& 0
-& 1
-& 1
-& 1 \\
-\end{array}
-\]
-
-Recalling the query (\ref{eqn:juryquery}) we are considering as an example, it is easy to see that in the current profile alternatives $a$ and $b$ represent the situation as described by the query.
-Therefore, if after proposing this profile to the committee the winning alternative turns out to be $a$ then we know that $w_{2} - w_{3} > 2(w_{3} - w_{4})$; if, instead, the winner is $b$ we know that $w_{2} - w_{3} < 2(w_{3} - w_{4})$ and if both alternatives are picked as winners then $w_{2} - w_{3} = 2(w_{3} - w_{4})$.
-
-Nevertheless, in this example it is clear that $c$ will always be preferred to other alternatives (see Claim \ref{clm:wsequence} in Section \ref{sec:weights}).
-To see it we can express for each alternative the number of agents placing it at a given rank or at a higher one.
-
-\[
-\begin{array}{ccccc}
-& \geq 1^\circ
-& \geq 2^\circ
-& \geq 3^\circ
-& \geq 4^\circ \\
-\cmidrule{2-5}
-a 
-& 0
-& 1
-& 1
-& 3 \\
-b
-& 0
-& 0
-& 3
-& 3 \\
-c
-& 2
-& 3
-& 3
-& 3 \\
-d
-& 0
-& 1
-& 2
-& 3 \\
-\end{array}
-\]
-
-\begin{claim}
-	Consider a set $A$ of $m$ alternatives and let $r_k(i)$ be the number of times the alternative $i$ obtains a rank $k$ or a higher one.
-Consider two alternatives $ i,j \in A$, if $\forall \ k=2, \dots,m \ r_k(i)\geq r_k(j)$ and $r_1(i) > r_1(j)$ then $i$ is always preferred to $j$ for any choice of weights.
-\end{claim}
-
-\begin{proof}
-	For our assumptions we know the sequence of weights is monotonic non-increasing and convex.
-Moreover, for the Claim \ref{clm:wsequence} in Section \ref{sec:weights}, we know that $w_1 > w_2$.
-Therefore, even in the worst case where $r_k(i) = r_k(j) \ forall \ k=2, \dots,m$ the sum of weights for alternative $i$ cannot be lower than the one for $j$.
-It is worth noting that we cannot say anything when $r_1(i) = r_1(j)$.
-Indeed, as said in Corollary \ref{cor:weq}, all the weights for other position but the first one can be equal, thus the number of agents ranking the alternatives at a certain position does not matter anymore.
-\end{proof}
-
-So the strategy for querying the committee is to use two alternatives $i$ and $j$ to represent the query and complete the profile such that the other alternatives are all dominated by them.
-An algorithmic approach is to start from the initial profile and then add as many agents as needed that rank $i$ and $j$ as their top choices and the other alternatives afterwards.
-As an example let consider again the query \ref*{eqn:juryquery}.
-We want the committee to choose between $a$ or $b$:
-
-\[
-\begin{array}{ccccc}
-& 1^\circ
-& 2^\circ
-& 3^\circ
-& 4^\circ \\
-\cmidrule{2-5}
-a 
-& 0
-& 1
-& 0
-& 2 \\
-b
-& 0
-& 0
-& 3
-& 0 \\
-\end{array}
-\]
-
-We add agents in order to increase the number of times $a$ and $b$ are ranked at first position.
-Please note we must maintain these scheme, so every add of a position to the ranking of $a$ must correspond to the same in the ranking of $b$.
-
-\[
-\begin{array}{cccccc}
-v_1
-& v_2
-& v_3 
-& v_4
-& v_5
-& v_6 \\
-\midrule 
-a
-& b
-& c 
-& d
-& a
-& b \\
-c
-& a
-& d
-& c
-& b
-& a \\
-b
-& d
-& b
-& b
-& d
-& c \\
-d
-& c
-& a
-& a
-& c
-& d \\
-\end{array}
-\]
-
-\[
-\begin{array}{ccccc}
-& 1^\circ
-& 2^\circ
-& 3^\circ
-& 4^\circ \\
-\cmidrule{2-5}
-a 
-& 2
-& 2
-& 0
-& 2 \\
-b
-& 2
-& 1
-& 3
-& 0 \\
-c
-& 1
-& 2
-& 1
-& 2 \\
-d
-& 1
-& 1
-& 2
-& 2 \\
-\end{array}
-\]
-
-\[
-\begin{array}{ccccc}
-& \geq 1^\circ
-& \geq 2^\circ
-& \geq 3^\circ
-& \geq 4^\circ \\
-\cmidrule{2-5}
-a 
-& 2
-& 4
-& 4
-& 6 \\
-b
-& 2
-& 3
-& 6
-& 6 \\
-c
-& 1
-& 3
-& 4
-& 6 \\
-d
-& 1
-& 2
-& 4
-& 6 \\
-\end{array}
-\]
-\textbf{Remarks:}
-\begin{itemize}
-	\item We are considering $\lambda \in \mathbb{N} \setminus \{0\}$ but we could be interested in a real number. \textit{Solution}: we can multiply both sides.
-\end{itemize}
-\fi
-\end{document}

### 2019-06-02 RJCIA2019/simultaneousElicitation.tex
final version RJCIA

--- 2019-05-31 RJCIA2019/short_draft.tex
@@
-%\input{rfia} 
 \documentclass[a4paper,twoside]{article}
@@
 \usepackage[T1]{fontenc}
-%\usepackage[english]{babel}
 \usepackage{times}
 
-%\author{ID: 2696}
 \author{\begin{tabular}[t]{c@{\extracolsep{6em}}c@{\extracolsep{6em}}c}
@@
 	Recently, the assumption of full preference information has been questioned by a number of researchers and several methods for eliciting preferences have been proposed.
-%	\commentOC{This “we go one step further” sounds odd here. I suggest one more sentence about the normal elicitation setting with only the agents preferences partially specified.}
 	In this paper we go one step further and we assume that both the voting rule and the voters' preferences are partially specified.
@@
 \section{Introduction}
-%Aggregation of preference information is a central task in many computer systems (recommender systems, search engines, etc) whose final goal is to find a consensus choice.
-%In this contexts, a natural approach consists in looking at methods from social choice and see how they can be adapted for group decision-making in a computerized setting. 
 In a traditional social choice setting, both the social choice function and the full preference orderings of the voters are expressed beforehand.
@@
 Any reasonable aggregation procedure, in fact, would select this alternative as a winner.
-The reason behind this consideration is that is not unrealistic to assume that the committee, that has to decide how to aggregate these preferences, is not able to define a specific procedure.
+The reasoning behind this is that it is not unrealistic to assume that the committee, that has to decide how to aggregate these preferences, is not able to define a specific procedure.
 \\
 These observations have motivated a number of recent works considering social choice with partial preference orders \citep{Xia2008, Pini2009, Konczak05} and incremental elicitation \citep{Kalech2011, Naamani-Dery2015} of voters' preferences.
-Lu and Boutilier \cite{Lu2011} have proposed the use of minimax regret to drive incremental vote and preferences elicitation when the social choice function is fixed and known.
-Furthermore, several authors \citep{Stein1994, Llamazares2013, Viappiani2018} have worked on positional scoring rules with uncertain weights, assuming that the preferences of the voters are fully known.
+Lu and Boutilier \cite{Lu2011} proposed the use of minimax regret to drive incremental vote and preferences elicitation when the social choice function is fixed and known.
+Furthermore, several authors \citep{Stein1994, Llamazares2013, Viappiani2018} worked on positional scoring rules with uncertain weights, assuming that the preferences of the voters are fully known.
 Some elicitation methods for a quite general class of rules based on weak orders have also been proposed by Cailloux and Endriss \citep{Cailloux2014}.
@@
 ${a \ppref_j b ⇒ a \pref_j^* b}$.
-%\commentOC{Or simply ${\ppref_j} \subseteq {\pref_j^*}$, if you need to save space}
-%We use $\pinc$ to denote incomparability, that is $a \pinc_{j} b$ iff $a \nppref_j b \wedge b \nppref_j a$.
 An incomplete profile ${\pprofile = (\ppref_1, \ldots, \ppref_n)}$ maps each voter to a partial preference.
 A completion of $\ppref_j$ is any linear order $\pref$ that extends $\ppref_j$ and we indicate with $C(\ppref_j) = \set{{\succ} \in \linors \suchthat {\ppref_j} \subseteq {\succ}}$ the set of possible completions of $\ppref_j$, where $\linors$ is the set of linear orders on $A$.
-%We let $C(\pprofile)=C(\ppref_1)\times … \times C(\ppref_n)$ be the set of complete profiles extending $p$. Note that $\profile^* \in C(\pprofile)$.
 
-Our knowledge regarding the weights of the positional scoring rule is represented by
-%We also assume that the weights of the scoring rule are only partially specified.
-%Therefore the vector $(w_1,\ldots,w_m)$  is not known but we are given 
-a set of constraints restraining the possible values that they can take. We consider a convex sequence of weights and we assume that 
-%, i.e.
-a decreasing sequence $1=w_{1} > w_{2} > \ldots > w_{m}=0$ such that the difference between the weights of the first and second positions is at least as great as the difference between the weights of the second and third positions, etc.
-%\begin{equation} 
-%\label{eq:convexity}
-%\forall r \in \{1,\ldots,m-2\}: w_r - w_{r+1} \geq w_{r+1}-w_{r+2}.
-%\end{equation}
-%We assume that in addition of basic requirements (monotonicity and convexity), 
-the chair is able to specify additional preferences about how the social choice function should behave. 
-%Of course it may be difficult for real decision makers to state these preferences, thus we can elicit them, for instance, by showing a complete profile of a small synthetic election and asking who should be elected in this case.
-\commentOC{Not entirely true as stated here.
-This works only in a subset of the case.
-So this remark should be dropped or amended, to say that we worked on this problem and it is still a work in progress to come up with an elicitation procedure that uses only questions that can effectively be asked using such a small synthetic election, and that it is not discussed further in this short article for lack of space.
-Also I’d remove “Of course”, it’s not obviously true.}
+Our knowledge regarding the weights of the positional scoring rule is represented by a set of constraints restraining the possible values that they can take.
+We consider a convex sequence of weights and we assume that the chair is able to specify additional preferences about how the social choice function should behave.
 Such requirements are encoded with linear constraints about the vector $\w$ and the set of these constraints is denoted by $\Co_W$.
@@
 Lu and Boutilier \cite{Lu2011} have adopted this criterion for winner determination in social choice with the preferences of the voters that are only partially known, while the social choice function is predetermined and known.
-%In this work we consider the simultaneous presence of uncertainty in the voters' preferences and uncertainty in the weights.
-We use {\em maximum regret} to quantify the worst-case error, which measures, intuitively, how far an alternative is from the optimal one given current knowledge; 
-% about the voting rule and the voters' preferences.
-the alternatives that minimize this error are selected as tied winners.
+We use {\em maximum regret} to quantify the worst-case error, which measures, intuitively, how far an alternative is from the optimal one given current knowledge; the alternatives that minimize this error are selected as tied winners.
 %, providing us with a form of robust optimization.
 The maximum regret of an alternative is the highest possible difference between its score and the one achievable by any alternative in any state compatible with our current knowledge.
-%The maximum regret, given our current knowledge and an alternative $x$, is the highest possible difference between the score of $x$ and the score achievable by any alternative in any state compatible with our current knowledge.
 It is considered by assuming that an adversary can both 1) extend the partial profile $\pprofile$ into a complete one, and 2) instantiate the weights choosing among any weight vector in $\pw$.
@@
 Max regret $\MR^{\pprofile,W}(x)$ is the worst-case loss of $x$ and $\MMR^{\pprofile,W}$ is the value of minimax regret obtained when recommending a minimax optimal alternative.
-%\begin{align}
-%\PMR(x,y; \pprofile, W) & = \max_{\w \in W} \max_{\profile \in C(\pprofile)} s(y; \profile,\w) - s(x; \profile,\w).
-%\end{align}
-%It is the loss occurred by an adversarial selection of a complete profile $\profile$ extending $\pprofile$ and a selection of $\w \in W$ to maximize the loss between $x$ and the true winner under $\profile$ and $\w$.
 \begin{align}
@@
 
-%Finally,  $\MMR(\pprofile,W)$ is the value of minimax regret under $\pprofile$ and $W$, obtained when recommending a minimax optimal alternative $x^*_{\pprofile, W}$:
-%\begin{align*}
-%\MMR(\pprofile,W) & = \min_{x \in A} \MR(x;\pprofile,W) \\
-%x^{*}_{\pprofile,W} \in A^*_{\pprofile, W} & = \argmin_{x \in A} \MR(x;\pprofile,W) 
-%\end{align*}
 By picking as consensus choice an alternative associated with minimax regret $x^*_{\pprofile, W} \in A^*_{\pprofile, W} $, we can provide a recommendation that gives worst-case guarantees, giving some robustness in face of uncertainty.
@@
 This optimization strategy uses the assumption of convexity.
-%In cases of ties in minimax regret, we can either decide to return all minimax alternatives $A^*_{\pprofile, W}$ as winners or to pick just one of them using some tie-breaking strategy.
-%
-%Notice that if $\MMR(\pprofile, W)\!=\!0$, then $x^{*}_{\pprofile,W}$ is a necessary co-winner; this means that for any valid completion of the profile and any feasible $w \!\in\!
-W$, $x^{*}_{\pprofile,W}$ obtains a highest score.
-%
-%We note that our notion of regret gives some cardinal meaning to the scores: instead of just being used to select winners under the corresponding PSR, their differences are considered as representing the regret of the chair.
 
-\section{Interactive Elicitation} 
+\section{Interactive elicitation} 
 \label{sec:elicit}

### 2020-01-06 draft.tex
new tau

@@
 \end{align}
+{\color{red}
+\begin{align}
+	\tau_{\w} & = \min_{\w \in W} s^{\bar{\profile},\w}(\bar{y}) - s^{\bar{\profile},\w}(x^{*}) \\
+	\tau_{\profile_i} & = \min_{\hat{\profile_i} \in C(\pprofile)} s^{\hat{\profile_i},\bar{\w}}(\bar{y}) -  s^{\hat{\profile_i},\bar{\w}}(x^{*}) 
+\end{align}
+where $\hat{\profile_i}$ is defined as $\bar{\profile}$ except for $i$, $\forall i \in \{1, \dots, n\}$. }
+
 Intuitively the quantity $\MMR - \tau_{1} = \max_{\w \in W} s(\bar{y}; \bar{\profile}, \w) - s(x^{*}; \bar{\profile}, \w) - \min_{\w \in W} s(\bar{y}; \bar{\profile}, \w) - s(x^{*}; \bar{\profile}, \w)$ estimates the contribution to regret of our uncertainty about the weights $\w$, while $\MMR - \tau_{2} $ estimates the uncertainty about the profile.
-Therefore, whenever $\tau_{1} < \tau_{2}$ we ask a question to the chair, and compare componentwise $\bar{\w}$ and $\w^{\tau}$, the argmax of Eq.
+Therefore, whenever $\tau_{1} < \tau_{2}$ we ask a question to the chair, and compare component-wise $\bar{\w}$ and $\w^{\tau}$, the argmax of Eq.
 (\ref{eq:tau1}), to find the position $r$ that is most valuable to ask about (the one that maximizes $\abs{\bar{\w}_r - \w^{\tau}_r}$), and choose $\lambda$ as the middle of the interval of possible values for that rank.

### 2020-01-08 draft.tex
minors

@@
 \end{align}
+\commentBN{$s^{\profile,\w}(x)$}
+
 where $\alpha^{x}_r$ is the number of times that alternative $x$ was ranked in the $r$-th position.
@@
 \begin{align}
-	\tau_{\w} & = \min_{\w \in W} s^{\bar{\profile},\w}(\bar{y}) - s^{\bar{\profile},\w}(x^{*}) \\
-	\tau_{\profile_i} & = \min_{\hat{\profile_i} \in C(\pprofile)} s^{\hat{\profile_i},\bar{\w}}(\bar{y}) -  s^{\hat{\profile_i},\bar{\w}}(x^{*}) 
+	\tau_{wg} & = \min_{\w \in W} s^{\bar{\profile},\w}(\bar{y}) - s^{\bar{\profile},\w}(x^{*}) \\
+	\tau_{i} & = \min_{\profile_i \in C(\pprofile)} s^{(\bar{\profile}_{-i},\profile_i),\bar{\w}}(\bar{y}) -  s^{(\bar{\profile}_{-i},\profile_i),\bar{\w}}(x^{*}) 
 \end{align}
-where $\hat{\profile_i}$ is defined as $\bar{\profile}$ except for $i$, $\forall i \in \{1, \dots, n\}$. }
+or we can use $\hat{\profile_i}=(\bar{\profile}_{-i},\profile_i)$ which is defined as $\bar{\profile}$ except for $i$, $\forall i \in \{1, \dots, n\}$. }
 
 Intuitively the quantity $\MMR - \tau_{1} = \max_{\w \in W} s(\bar{y}; \bar{\profile}, \w) - s(x^{*}; \bar{\profile}, \w) - \min_{\w \in W} s(\bar{y}; \bar{\profile}, \w) - s(x^{*}; \bar{\profile}, \w)$ estimates the contribution to regret of our uncertainty about the weights $\w$, while $\MMR - \tau_{2} $ estimates the uncertainty about the profile.
-Therefore, whenever $\tau_{1} < \tau_{2}$ we ask a question to the chair, and compare component-wise $\bar{\w}$ and $\w^{\tau}$, the argmax of Eq.
+Therefore, whenever ${\color{red} \lambda *} \tau_{1} < \tau_{2}$ we ask a question to the chair, and compare component-wise $\bar{\w}$ and $\w^{\tau}$, the argmax of Eq.
 (\ref{eq:tau1}), to find the position $r$ that is most valuable to ask about (the one that maximizes $\abs{\bar{\w}_r - \w^{\tau}_r}$), and choose $\lambda$ as the middle of the interval of possible values for that rank.

### 2020-01-10 draft.tex
New draft section

@@
 \usepackage{textcomp}
+
 %\newunicodechar{⇒}{\implies}
@@
 \newunicodechar{ℕ}{\mathbb{N}}
+\newcommand{\R}{ℝ}
+\newunicodechar{ℝ}{\mathbb{R}}
 \usepackage{algorithm, algpseudocode}
@@
 \DeclareMathOperator*{\argmin}{argmin}
+\DeclareMathOperator{\badn}{badness}
 
@@
 Observe that if $\MMR(\pprofile, W)\!=\!0$, then $x^{*}_{\pprofile,W}$ is a necessary co-winner; this means that for any valid completion of the profile and any feasible $w \!\in\!
-W$, $x^{*}_{\pprofile,W}$ obtains a highest score.
+W$, $x^{*}_{\pprofile,W}$ obtains the highest score.
 
@@
 \section{Bounding differences of weights}
+\newcommand{\Wq}{W_\text{q}}
+
 We want to check whether we can round PMR values to (for example) $10^{-4}$. Thus, we want to bound the difference of scores (unless it is zero).
@@
 For example, $\epsilon = 1/1000, n = 2, w_2 = 999/2000$.
+
+\section{Best question}
+\subsection{Much fixed}
+Throughout, $\Wq$ designates a closed set.
+
+Fix $x, y, \profile^*, W \subseteq \W$, fix $m = 3$.
+$\Wq \subseteq W$, define $\PMR(\Wq) = \PMR(x, y, \profile^*, \Wq)$.
+Define $\PMR(w) = PMR(\set{w})$, denoting the pairwise regret when the weight vector is $w$.
+Let $P$ be a probability defined on the whole set $\W$ of possible weights.
+%Define $\overline{w} = \argmax_{w \in W} s(y, \profile^*, w) - s(x, \profile^*, w) = \argmax PMR(w)$.
+
+For $\emptyset ≠ \Wq \subset W$, define $\badn(\Wq) = P[w^* \in \Wq] \PMR(\Wq) + P[w^* \notin \Wq] \PMR(W \setminus \Wq).$
+Equivalently, we could define the quality of a question as $P[w^* \in \Wq] (PMR(W) - PMR(\Wq)) + P[w^* \notin \Wq] (PMR(W) - PMR(W \setminus \Wq))$.
+This yields the same ordering.
+Still equivalently, we could define the badness using $P[\Wq \mid W]$ and $P[W \setminus \Wq \mid W]$, so that these probabilities sum to one.
+
+NB in general, this badness measure could perhaps be too short sighted, but that doesn’t seem to be a problem with the restrictions adopted here.
+
+With $m=3$, we can consider that $W \subseteq [0, 1]$, with $w \in W$ denoting the weight associated with the second rank.
+Let $P$ be the Lebesgue measure (or the uniform probability distribution) on $[0, 1]$.
+
+Recalling that $\alpha^y_1$ denotes the number of times $y$ is ranked first in $\profile^*$, define $t_1 = \alpha^y_1 - \alpha^x_1$ and $t_2 = \alpha^y_2 - \alpha^x_2$ to represent the difference in number of voters placing at a given position.
+Then $\PMR(w) = t_1 + t_2 w$.
+Thus, the worst (maximal) regret $\PMR(\Wq)$ is reached, for any set of weights $\Wq$, at an extremum of $\Wq$.
+If $t_2 ≥ 0$, the supremum of $\Wq$ is an optimal adversarial choice, and if $t_2 ≤ 0$, the infimum of $\Wq$ is an optimal adversarial choice.
+Thus $\PMR(\Wq) = t_1 + t_2 \sup(\Wq)$ if $t_2 ≥ 0$ and $\PMR(\Wq) = t_1 + t_2 \inf(\Wq)$ if $t_2 ≤ 0$.
+
+Assume that $W$ has the form $W = [\inf W, \sup W]$.
+
+Let $W_q$, with $q \in W$, denote asking whether $w^* ≥ q$, thus $W_q = \set{w ≥ q} ∩ W$. 
+We can say the following about the question $W_q$.
+\begin{itemize}
+	\item $P[W_q] = \sup W - q$
+	\item $P[W \setminus W_q] = q - \inf W$
+	\item $\PMR(W_q) = t_1 + t_2 \sup W$ if $t_2 ≥ 0$
+	\item $\PMR(W_q) = t_1 + t_2 q$ if $t_2 ≤ 0$
+	\item $\PMR(W \setminus W_q) = t_1 + t_2 q$ if $t_2 ≥ 0$. 
+	\item $\PMR(W \setminus W_q) = t_1 + t_2 \inf W$ if $t_2 ≤ 0$
+	\item $\badn(W_q) = (\sup W - q) (t_1 + t_2 \sup W) + (q - \inf W) (t_1 + t_2 q)$ if $t_2 ≥ 0$, whose derivative is $-(t_1 + t_2 \sup W) + (t_1 + t_2 q) + (q - \inf W) t_2 = 2 t_2 q - t_2 \sup W - t_2 \inf W$, thus the least badness is reached at $q = \frac{\sup W + \inf W}{2}$
+	\item $\badn(W_q) = (\sup W - q) (t_1 + t_2 q) + (q - \inf W) (t_1 + t_2 \inf W)$ if $t_2 ≤ 0$, whose derivative is $-(t_1 + t_2 q) + (\sup W - q) t_2 + (t_1 + t_2 \inf W) = -2 t_2 q + t_2 \sup W + t_2 \inf W$, thus the least badness is reached at $q = \frac{\sup W + \inf W}{2}$
+\end{itemize}
+In both cases, asking a question about the middle of the interval is optimal.
+
+\subsection{y variable}
+Fix $x, \profile^*, W \subseteq \W$, fix $m = 3$. 
+Assume that $W$ has the form $W = [\inf W, \sup W]$.
+For $\Wq \subseteq W$, define $\MR(\Wq) = \max_{y \in A} \PMR(x, y, \profile^*, \Wq) = \max_{y \in A, w \in \Wq} s(y, \profile^*, w) - s(x, \profile^*, w)$.
+For $w \in W$, define $\MR(w) = \MR(\set{w})$.
+
+For $\Wq \subseteq W$, define $\badn(\Wq) = P[\Wq] \MR(\Wq) + P[W \setminus \Wq] \MR(W \setminus \Wq)$.
+
+Let $t_1^a = \alpha_1^a - \alpha_1^x$ and $t_2^a = \alpha_2^a - \alpha_2^x$, for $a \in A$, representing the difference of number of times an alternative reaches a given position compared to the alternative $x$.
+Thus, $t_1^x = t_2^x = 0$.
+For $q \in W$, $\PMR(x, a, \profile^*, q) = t_1^a + t_2^a q$.
+Thus, $\MR(q) = \max \set{t_1^x + t_2^x q, t_1^y + t_2^y q, t_1^z + t_2^z q}$, with $A = \set{x, y, z}$.
+Therefore, $\MR$ has a maximal value at an extremum point of $W$.
+
+We obtain that $\MR(\Wq) = \max \set{\MR(\inf \Wq), \MR(\sup \Wq)}$.
+
+Define $W_q = \set{w ≥ q} ∩ W$, with $q \in W$.
+
+Assume that $t_2^y ≤ 0$ and $t_2^z ≤ 0$. 
+Sort alternatives by slope, thus, let $a, b, c$ denote different alternatives such that $t_2^a ≤ t_2^b ≤ t_2^c$ and $t_2^a = t_2^b ⇒ t_1^a ≥ t_1^b$ and $t_2^b = t_2^c ⇒ t_1^b ≥ t_2^b$ (picking one naming arbitrarily if several namings are compatible with these constraints).
+TODO it should follow that $\inf W$ is a maximum of $\MR$ over $W$. 
+Let $q_{a \sim b} \in ℝ$ denote the point such that $t_1^a + t_2^a q_{a \sim b} = t_1^b + t_2^b q_{a \sim b}$.
+If several or no points match this requirement, define $q_{a \sim b} = -1$.
+Define similarly $q_{b \sim c}$; setting it at 1 if several or no points match the requirement.
+TODO it follows that $q_{a \sim b} ≤ q_{b \sim c}$.
+
+TODO it follows that $\MR(q) = t_1^a + t_2^a q$ for $q ≤ q_{a \sim b}$, 
+$\MR(q) = t_1^b + t_2^b q$ for $q_{a \sim b} ≤ q ≤ q_{b \sim c}$, 
+$\MR(q) = t_1^c + t_2^c q$ for $q_{b \sim c} ≤ q$.
+
+Also, $\MR(W_q) = \MR(q)$, and 
+$\MR(W \setminus W_q) = \MR(\inf W)$.
+
+Thus for $q ≤ q_{a \sim b}$, $\badn(W_q) = (\sup W - q) (t_1^a + t_2^a q) + (q - \inf W) (t_1^a + t_2^a \inf W)$.
+
+\begin{example}
+	When $q_{a \sim b} ≤ \inf W$ and $q_{b \sim c} ≤ \frac{1}{2}$, $q_{b \sim c}$ is an optimum. (TODO prove it)
+	\begin{itemize}
+		\item Def $\inf W = 0, \sup W = 1$.
+		\item Def $t_1^a = 0, t_2^a = -20, t_1^b = 1, t_2^b = -10$.
+		\item $q_{a \sim b} = -1/10, q_{b \sim c} = 1/10$.
+		\item $\MR(\frac{1}{20}) = \frac{1}{2}$, $\MR(\frac{1}{10}) = 0$.
+		\item $\MR(\frac{3}{20}) = 0 = \MR(\frac{4}{20})$.
+		\item $\MR(W \setminus W_q) = 1, \forall q \in W$.
+		\item $\badn(W_\frac{1}{20}) = \frac{19}{20} \frac{1}{2} + \frac{1}{20} 1 = \frac{21}{40}$.
+		\item $\badn(W_\frac{1}{10}) = \frac{9}{10} 0 + \frac{1}{10} 1 = \frac{4}{40}$.
+		\item $\badn(W_q) = (1 - q) 0 + q 1 = q$, with $\frac{1}{10} ≤ q$.
+	\end{itemize}
+	The optimum is at $\frac{1}{10}$ as expected.
+\end{example}
+
+\begin{example}
+	Here, the optimum should be for some $q_{a \sim b} ≤ q ≤ \frac{1}{2}$.
+	\begin{itemize}
+		\item Def $\inf W = 0, \sup W = 1$.
+		\item Def $t_1^a = 1, t_2^a = -10, t_1^b = 8/15, t_2^b = -2/3$.
+		\item $q_{a \sim b} = 1/20, q_{b \sim c} = 8/10$.
+		\item $\MR(\frac{1}{40}) = \frac{3}{4}$, $\MR(\frac{1}{20}) = \frac{1}{2}$.
+		\item $\MR(\frac{2}{20}) = \frac{14}{30}$, $\MR(\frac{3}{20}) = \frac{13}{30}$, $\MR(\frac{4}{20}) = \frac{12}{30}$, $\MR(\frac{6}{20}) = \frac{10}{30}$, $\MR(\frac{1}{2}) = \frac{3}{15}$.
+		\item $\MR(W \setminus W_q) = 1, \forall q \in W$.
+		\item $\badn(W_\frac{1}{40}) = \frac{39}{40} \frac{3}{4} + \frac{1}{40} 1 = \frac{3}{4} + \frac{1}{160}$.
+		\item $\badn(W_\frac{1}{20}) = \frac{19}{20} \frac{1}{2} + \frac{1}{20} 1 = \frac{1}{2} + \frac{1}{40}$.
+		\item $\badn(W_\frac{2}{20}) = \frac{9}{10} \frac{7}{15} + \frac{1}{10} 1 = \frac{1}{2} + \frac{1}{50}$.
+		\item $\badn(W_\frac{3}{20}) = \frac{17}{20} \frac{13}{30} + \frac{3}{20} 1 = \frac{1}{2} + \frac{11}{600}$.
+		\item $\badn(W_\frac{4}{20}) = \frac{8}{10} \frac{12}{30} + \frac{2}{10} 1 = \frac{1}{2} + \frac{1}{50}$.
+		\item For $\frac{1}{20} ≤ q ≤ \frac{8}{10}$, $\badn(W_q) = (1 - q) (\frac{8}{15} - \frac{2}{3} q) + q$; derivative is $-\frac{1}{5} + \frac{4}{3} q$, zero when $q = \frac{3}{20}$.
+	\end{itemize}
+\end{example}
+
+\subsection{x variable}
+Define $\MR_x(\Wq) = \max_{y \in A, w \in W_q} \PMR(x, y, \profile^*, w)$. Define $\MMR(\Wq) = \min_{x \in A} \MR_x(\Wq)$. Define $\badn(W_q) = (1 - q) \MMR(W_q) + q \MMR(W \setminus \W_q$.
+
+Define $\MR_x(w) = \MR_x(\set{w})$.
+
+We want to 1. Plot $\MR_x(w) = \max \set{t_1^{a, x} + t_2^{a, x} w, …}$. 2. Plot $\MR_x(W_q)$. 3. Plot $\MMR(W_q) = \min_x \MR_x(W_q)$.
 \end{document}

### 2020-01-15 draft.tex
title and abstract

--- 2020-01-08 draft.tex
@@
 
-\title{Robust Winner Determination and Simultaneous Elicitation of Scoring Rules and Preferences}
+\title{Robust Winner Determination and Simultaneous Elicitation of Scoring Rule and Agents Preferences}
 
@@
 In this setting, we propose a method  for robust approximate winner determination with minimax regret. 
-Moreover, we provide an interactive elicitation protocol based on minimax regret
+We also provide an interactive elicitation protocol based on minimax regret
 and develop several query strategies that interleave questions to the chair and questions to the agents in order to attempt to acquire the most relevant information in order to quickly converge to optimal or a near-optimal alternative.
@@
 \begin{align}
-	\tau_{wg} & = \min_{\w \in W} s^{\bar{\profile},\w}(\bar{y}) - s^{\bar{\profile},\w}(x^{*}) \\
+	\tau_{\text{wgt}} & = \min_{\w \in W} s^{\bar{\profile},\w}(\bar{y}) - s^{\bar{\profile},\w}(x^{*}) \\
 	\tau_{i} & = \min_{\profile_i \in C(\pprofile)} s^{(\bar{\profile}_{-i},\profile_i),\bar{\w}}(\bar{y}) -  s^{(\bar{\profile}_{-i},\profile_i),\bar{\w}}(x^{*}) 

### 2020-01-17 draft.tex
title
paper ID
small changes

@@
 \input{ijcai_preamble} 
-\author{ID: 2696}
+\author{ID: 7094}
 %\author{Beatrice Napolitano$^1$\and Olivier Cailloux$^1$	\and  Paolo Viappiani$^{2}$
@@
 
-\title{Robust Winner Determination and Simultaneous Elicitation of Scoring Rule and Agents Preferences}
+\title{Simultaneous Elicitation of Scoring Rule and Agents Preferences for Robust Winner Determination}
 
@@
 \end{align*}
-Note that in general the inner max depends on the weights chosen by the outer min.
+Note that in general the inner max depends on the weights chosen by the outer max.
 
@@
 Observe that, whenever the $\PMR$ of an alternative $x$ (against some other alternative $y$) exceeds the best MR value found so far, we don't need to further evaluate $x$. 
-%, as it can't be optimal. 
-\commentBN{Indeed, the maximum regret of an alternative is the maximum value among all the PMRs, so we already know that $\MR(x) \geq \PMR(x,y)$, which is greater than the current MR.
+%\commentBN{Indeed, the maximum regret of an alternative is the maximum value among all the PMRs, so we already know that $\MR(x) \geq \PMR(x,y)$, which is greater than the current MR.
 Thus, x will never be selected as a winner in the minimizing step.}

### 2020-01-20 draft.tex
some cleaning and minor fixed

@@
 While previous works have considered either partial information about the agents preferences or a partially specified aggregation method, we do not know of any work considering both sources of uncertainty at the same time.
-
 In this work, we focus on positional scoring rules, that are a particularly common method used to aggregate rankings and determine a winner.
@@
 \end{align}
-\commentBN{$s^{\profile,\w}(x)$}
-
+%\commentBN{$s^{\profile,\w}(x)$}
 where $\alpha^{x}_r$ is the number of times that alternative $x$ was ranked in the $r$-th position.
@@
 
-\medskip
 We also assume that the weights of the scoring rule are only partially specified.
@@
 This represents the “worst” difference of score, thus the difference of score between $y$ and $x$ under the worst case preferences compatible with $\pprofile$ and $W$, where the worst case is the one that maximizes this difference of score.
-We consider now a procedure for completing a partial profile that was first proposed by \citet{Lu2011} when considering minimax regret with a fixed weight vector.
+We consider now a procedure for completing a partial profile that was first proposed by \citet{Lu2011} when considering %minimax regret with 
+a fixed weight vector.
 As we will show, this procedure can also be used when the weight vector is not completely known.
@@
 \end{proof}
-
-At this stage, we are content that a procedure exists to transform our abstract questions to questions about winners of a PSR.
+At this stage, we are satisfied that a procedure exists to transform our abstract questions to questions about winners of a PSR.
 Further studies would investigate, for example, what is lost in terms of elicitation efficiency when we are forced to restrain to realistic concrete questions, meaning, questions involving small profiles; or investigate the relationship between our understanding of scores as (cardinal) utility and (ordinal) scores as definition of a PSR.
@@
 
-We define here the various strategies we tested experimentally.
-A strategy is a function (or a random process) that gives us, given our partial knowledge so far $(\pprofile, W)$, a question that should be asked according to that strategy.
-
-Among them, the \strat{Random} strategy is used to capture how hard an elicitation problem is, by giving us a baseline: using it we can estimate how fast the regret diminishes when we ask questions randomly.
+We define here the various strategies we tested experimentally; a strategy %is a function (or a random process) that 
+gives us, given the current partial knowledge $(\pprofile, W)$, a question that should be asked. % according to that strategy. 
+Among them, the \strat{Random} strategy is used to capture how hard an elicitation problem is, by giving us a baseline.
+%: using it we can estimate how fast the regret diminishes when we ask questions randomly.
 Choosing the questions purely randomly however, that is, independently of what we know already, would be pointless, as we would most of the time ask questions we already know the answer of.
@@
 \end{align}
-{\color{red}
-\begin{align}
-	\tau_{\text{wgt}} & = \min_{\w \in W} s^{\bar{\profile},\w}(\bar{y}) - s^{\bar{\profile},\w}(x^{*}) \\
-	\tau_{i} & = \min_{\profile_i \in C(\pprofile)} s^{(\bar{\profile}_{-i},\profile_i),\bar{\w}}(\bar{y}) -  s^{(\bar{\profile}_{-i},\profile_i),\bar{\w}}(x^{*}) 
-\end{align}
-or we can use $\hat{\profile_i}=(\bar{\profile}_{-i},\profile_i)$ which is defined as $\bar{\profile}$ except for $i$, $\forall i \in \{1, \dots, n\}$. }
+%{\color{red}
+%\begin{align}
+%	\tau_{\text{wgt}} & = \min_{\w \in W} s^{\bar{\profile},\w}(\bar{y}) - s^{\bar{\profile},\w}(x^{*}) \\
+%	\tau_{i} & = \min_{\profile_i \in C(\pprofile)} s^{(\bar{\profile}_{-i},\profile_i),\bar{\w}}(\bar{y}) -  s^{(\bar{\profile}_{-i},\profile_i),\bar{\w}}(x^{*}) 
+%\end{align}
+%or we can use $\hat{\profile_i}=(\bar{\profile}_{-i},\profile_i)$ which is defined as $\bar{\profile}$ except for $i$, $\forall i \in \{1, \dots, n\}$. }
 

### 2020-01-20 draft.tex
minor changes in strategy description

@@
 \DeclareMathOperator{\MMR}{MMR}
+\DeclareMathOperator{\leximax}{leximax}
 \DeclareMathOperator*{\argmax}{argmax}
@@
 
-% In the code, called Current solution
 We also define the \strat{Extreme completions} strategy, which we consider as a more realistic baseline. 
@@
 \end{align}
-%{\color{red}
-%\begin{align}
-%	\tau_{\text{wgt}} & = \min_{\w \in W} s^{\bar{\profile},\w}(\bar{y}) - s^{\bar{\profile},\w}(x^{*}) \\
-%	\tau_{i} & = \min_{\profile_i \in C(\pprofile)} s^{(\bar{\profile}_{-i},\profile_i),\bar{\w}}(\bar{y}) -  s^{(\bar{\profile}_{-i},\profile_i),\bar{\w}}(x^{*}) 
-%\end{align}
-%or we can use $\hat{\profile_i}=(\bar{\profile}_{-i},\profile_i)$ which is defined as $\bar{\profile}$ except for $i$, $\forall i \in \{1, \dots, n\}$. }
 
@@
 \[\max_{i=1,2} \MMR(\pprofile_i,W_i) \]
-This badness measure gives a way of picking questions among a set of possible questions, by picking one that minimizes the measure.
-Note that other aggregators than $\max$ can be used as well.
-The \strat{Pessimistic} strategy considers as possible questions the ones defined by the \strat{Random} strategy (with the difference that a threshold is used: if for some rank $r$ the interval of possible values for $\lambda$ is not larger than $0.1$, the question is not considered).
-It uses a variant of the $\max$ as an aggregator: if the maximal $\MMR$ of two questions are equal, then it considers the other $\MMR$ values, that are the one associated to the opposite answer, preferring the question with the lowest of this value.
+This badness measure gives a way of picking questions among a set of possible questions, by picking one that minimizes the measure. Note that other aggregators than $\max$ can be used as well. 
+%The \strat{Pessimistic} strategy considers as possible questions the ones defined by the \strat{Random} strategy (with the difference that a threshold is used: if for some rank $r$ the interval of possible values for $\lambda$ is not larger than $0.1$, the question is not considered).
+It uses the $\leximax$ criterion %a variant of the $\max$ 
+as an aggregator: if the maximal $\MMR$ of two questions are equal, then it considers the other $\MMR$ values, that are the one associated to the opposite answer, preferring the question with the lowest of this value.
  We expect this strategy to perform very well, but only for very small problem instances: its complexity is in $O(n^2 m^5)$, because we consider $O(m^2)$ questions for each agent and need for each question to compute $\MMR$ twice, whose complexity is $O(nm^3)$.

### 2020-01-21 draft.tex
changes in strategy description

@@
 
-We also define the \strat{Extreme completions} strategy, which we consider as a more realistic baseline. 
-Consider the solution of the minimax regret game, 
- $(x^{*},\bar{y},\bar{\profile},\bar{\w})$, where $x^{*}$ is the minimax regret optimal alternative, and $\bar{y} = \arg \max_{y \in A} \PMR(x,y; \pprofile, W)$, $\bar{\profile}$ and $\bar{\w}$ are the adversarial choices, thus, the instantiations that, given the choice of $x^*$, maximize the regret.
-Define: 
-\begin{align}
-\tau_{1} & = \min_{\w \in W} s(\bar{y}; \bar{\profile}, \w) - s(x^{*}; \bar{\profile}, \w),  \label{eq:tau1} \\
-\tau_{2} & = \min_{\profile \in C(\pprofile)} s(\bar{y},\profile, \bar{\w}) -  s(x^{*}; \profile, \bar{\w}).
-\end{align}
-
-Intuitively the quantity $\MMR - \tau_{1} = \max_{\w \in W} s(\bar{y}; \bar{\profile}, \w) - s(x^{*}; \bar{\profile}, \w) - \min_{\w \in W} s(\bar{y}; \bar{\profile}, \w) - s(x^{*}; \bar{\profile}, \w)$ estimates the contribution to regret of our uncertainty about the weights $\w$, while $\MMR - \tau_{2} $ estimates the uncertainty about the profile.
-Therefore, whenever ${\color{red} \lambda *} \tau_{1} < \tau_{2}$ we ask a question to the chair, and compare component-wise $\bar{\w}$ and $\w^{\tau}$, the argmax of Eq.
+%We also define the \strat{Extreme completions} strategy, which we consider as a more realistic baseline. 
+%Consider the solution of the minimax regret game, 
+% $(x^{*},\bar{y},\bar{\profile},\bar{\w})$, where $x^{*}$ is the minimax regret optimal alternative, and $\bar{y} = \arg \max_{y \in A} \PMR(x,y; \pprofile, W)$, $\bar{\profile}$ and $\bar{\w}$ are the adversarial choices, thus, the instantiations that, given the choice of $x^*$, maximize the regret.
+%Define: 
+%\begin{align}
+%\tau_{1} & = \min_{\w \in W} s(\bar{y}; \bar{\profile}, \w) - s(x^{*}; \bar{\profile}, \w),  \label{eq:tau1} \\
+%\tau_{2} & = \min_{\profile \in C(\pprofile)} s(\bar{y},\profile, \bar{\w}) -  s(x^{*}; \profile, \bar{\w}).
+%\end{align}
+
+%Intuitively the quantity $\MMR - \tau_{1} = \max_{\w \in W} s(\bar{y}; \bar{\profile}, \w) - s(x^{*}; \bar{\profile}, \w) - \min_{\w \in W} s(\bar{y}; \bar{\profile}, \w) - s(x^{*}; \bar{\profile}, \w)$ estimates the contribution to regret of our uncertainty about the weights $\w$, while $\MMR - \tau_{2} $ estimates the uncertainty about the profile.
+%Therefore, whenever ${\color{red} \lambda *} \tau_{1} < \tau_{2}$ we ask a question to the chair, and compare component-wise $\bar{\w}$ and $\w^{\tau}$, the argmax of Eq.
 (\ref{eq:tau1}), to find the position $r$ that is most valuable to ask about (the one that maximizes $\abs{\bar{\w}_r - \w^{\tau}_r}$), and choose $\lambda$ as the middle of the interval of possible values for that rank.
-Instead, if $\tau_{1} > \tau_{2}$ we ask a question to one of the agents.
+%Instead, if $\tau_{1} > \tau_{2}$ we ask a question to one of the agents.
 We select the question by checking for each agent $j$ the difference between the difference of the ranks of $x$ and $y$ in the profile that minimizes compared to the one that maximizes the difference of scores, and pick an agent related to the highest difference, then pick $x$ or $y$ with $1/2$ chances as the first alternative of the question, and pick an incomparable alternative equiprobably as the second one.
@@
 Assume that a question leads to the possible new knowledge states $(\pprofile_1, W_1)$ and $(\pprofile_2, W_2)$, depending on the answer.
-Then the badness of the question in the worst case is:
-\[\max_{i=1,2} \MMR(\pprofile_i,W_i) \]
-This badness measure gives a way of picking questions among a set of possible questions, by picking one that minimizes the measure. Note that other aggregators than $\max$ can be used as well. 
+Then the badness of the question in the worst case is: $\max_{i=1,2} \MMR(\pprofile_i,W_i)$.
+This badness measure gives a way of picking questions among a set of possible questions, by picking one that minimizes the measure. %Note that other aggregators than $\max$ can be used as well. 
 %The \strat{Pessimistic} strategy considers as possible questions the ones defined by the \strat{Random} strategy (with the difference that a threshold is used: if for some rank $r$ the interval of possible values for $\lambda$ is not larger than $0.1$, the question is not considered).
-It uses the $\leximax$ criterion %a variant of the $\max$ 
-as an aggregator: if the maximal $\MMR$ of two questions are equal, then it considers the other $\MMR$ values, that are the one associated to the opposite answer, preferring the question with the lowest of this value.
+However, to avoid the absorption property of max, we adopt the $\leximax$ criterion %a variant of the $\max$ 
+as an aggregator: if the maximal $\MMR$ of two questions are equal, then it considers the other $\MMR$ values, (the ones associated to the opposite answer), preferring the question with the lowest of this value.
  We expect this strategy to perform very well, but only for very small problem instances: its complexity is in $O(n^2 m^5)$, because we consider $O(m^2)$ questions for each agent and need for each question to compute $\MMR$ twice, whose complexity is $O(nm^3)$.
 For small dimensions, it gives us an estimate of an upper bound to the possible quality of a strategy.
+
+ The \strat{LimitedPessimistic} strategy uses the same criterion as the pessimistic strategy, but only considering a small set of candidate questions.
+For each voter, a candidate question is chosen by considering the heuristic proposed by Lu and Boutilier \cite{Lu2011}. 
+For the chair, we define
+\begin{align}
+\tau & = \min_{\w \in W} s(\bar{y}; \bar{\profile}, \w) - s(x^{*}; \bar{\profile}, \w),  \label{eq:tau1} 
+\end{align}
+and compare component-wise $\bar{\w}$ and $\w^{\tau}$, the argmax of Eq.
+(\ref{eq:tau1}), to find the position $r$ that is most valuable to ask about (the one that maximizes $\abs{\bar{\w}_r - \w^{\tau}_r}$), and choose $\lambda$ as the middle of the interval of possible values for that rank.
+
+We then evaluate, for each candidate question, the minimax regret for each possible answer; finally we choose the best according to $\leximax$.
 

### 2020-01-21 draft.tex
XPs: expl and (mostly empty) tables

--- 2020-01-20 draft.tex
@@
 While it is of course possible to first fully elicit the agents’ preferences and afterwards elicit weights, we also want to propose interleaved approaches and compare them experimentally.
-Indeed, it can be beneficial to interleave questions asked to the chair and questions asked to agents, depending on which is estimated to be more informative.
-
-We define here the various strategies we tested experimentally; a strategy %is a function (or a random process) that 
-gives us, given the current partial knowledge $(\pprofile, W)$, a question that should be asked. % according to that strategy. 
-Among them, the \strat{Random} strategy is used to capture how hard an elicitation problem is, by giving us a baseline.
-%: using it we can estimate how fast the regret diminishes when we ask questions randomly.
-Choosing the questions purely randomly however, that is, independently of what we know already, would be pointless, as we would most of the time ask questions we already know the answer of.
-Thus, this strategy choses questions in a minimally “clever” way, just by picking questions in a set of a priori relevant questions.
-The \strat{Random} strategy first decides with a probability of $1/2$ each whether it will ask a question about weights or a question about a preference ordering (unless the profile is already known entirely).
+Indeed, it can be beneficial to split efforts asking questions to the chair and to agents, depending on which is estimated to be more informative.
+We define here the various strategies we tested experimentally. A strategy tells us, given the current partial knowledge $(\pprofile, W)$, which question should be asked next.
+
+The \strat{Random} strategy gives a baseline for comparison and informs about the difficulty of an elicitation problem. 
+This strategy first decides with a probability of $1/2$ each whether it will ask a question about weights or a question about a preference ordering (unless the profile is already known entirely).
 If it opted for a question about weights, it draws one rank in $2 ≤ r ≤ m-2$ equiprobably, takes the middle of the interval of values for $\lambda$ that are still possible considering our knowledge so far, and asks whether $w_r - w_{r+1} ≥ \lambda (w_{r+1} - w_{r+2})$.
@@
 If it opted for a question to agents, it draws equiprobably among the agents whose preference is not known entirely; picks an alternative $a$ randomly with equal probability among those involved in some incomparabilities in $\ppref_j$; and picks an alternative $b$ with equal probability among those incomparable with $a$ in $\ppref_j$.
-
-We also define the \strat{Extreme completions} strategy, which we consider as a more realistic baseline. 
-Consider the solution of the minimax regret game, 
- $(x^{*},\bar{y},\bar{\profile},\bar{\w})$, where $x^{*}$ is the minimax regret optimal alternative, and $\bar{y} = \arg \max_{y \in A} \PMR(x,y; \pprofile, W)$, $\bar{\profile}$ and $\bar{\w}$ are the adversarial choices, thus, the instantiations that, given the choice of $x^*$, maximize the regret.
-Define: 
-\begin{align}
-\tau_{1} & = \min_{\w \in W} s(\bar{y}; \bar{\profile}, \w) - s(x^{*}; \bar{\profile}, \w),  \label{eq:tau1} \\
-\tau_{2} & = \min_{\profile \in C(\pprofile)} s(\bar{y},\profile, \bar{\w}) -  s(x^{*}; \profile, \bar{\w}).
-\end{align}
-
-Intuitively the quantity $\MMR - \tau_{1} = \max_{\w \in W} s(\bar{y}; \bar{\profile}, \w) - s(x^{*}; \bar{\profile}, \w) - \min_{\w \in W} s(\bar{y}; \bar{\profile}, \w) - s(x^{*}; \bar{\profile}, \w)$ estimates the contribution to regret of our uncertainty about the weights $\w$, while $\MMR - \tau_{2} $ estimates the uncertainty about the profile.
-Therefore, whenever ${\color{red} \lambda *} \tau_{1} < \tau_{2}$ we ask a question to the chair, and compare component-wise $\bar{\w}$ and $\w^{\tau}$, the argmax of Eq.
-(\ref{eq:tau1}), to find the position $r$ that is most valuable to ask about (the one that maximizes $\abs{\bar{\w}_r - \w^{\tau}_r}$), and choose $\lambda$ as the middle of the interval of possible values for that rank.
-Instead, if $\tau_{1} > \tau_{2}$ we ask a question to one of the agents.
-We select the question by checking for each agent $j$ the difference between the difference of the ranks of $x$ and $y$ in the profile that minimizes compared to the one that maximizes the difference of scores, and pick an agent related to the highest difference, then pick $x$ or $y$ with $1/2$ chances as the first alternative of the question, and pick an incomparable alternative equiprobably as the second one.
 
@@
 \[\max_{i=1,2} \MMR(\pprofile_i,W_i) \]
-This badness measure gives a way of picking questions among a set of possible questions, by picking one that minimizes the measure. Note that other aggregators than $\max$ can be used as well. 
-%The \strat{Pessimistic} strategy considers as possible questions the ones defined by the \strat{Random} strategy (with the difference that a threshold is used: if for some rank $r$ the interval of possible values for $\lambda$ is not larger than $0.1$, the question is not considered).
-It uses the $\leximax$ criterion %a variant of the $\max$ 
-as an aggregator: if the maximal $\MMR$ of two questions are equal, then it considers the other $\MMR$ values, that are the one associated to the opposite answer, preferring the question with the lowest of this value.
+This badness measure gives a way of picking questions among a set of possible questions, by picking one that minimizes the measure.
+Note that other aggregators than $\max$ can be used as well.
+%We use the $\max$ operator because \citet{Cailloux2014} reported that pessimistic aggregation works much better than optimistic aggregation, although our experiments in this context suggested a weak impact of that choice on the performance of the strategy.
+It uses the $\leximax$ criterion as an aggregator: if the maximal $\MMR$ of two questions are equal, then it considers the other $\MMR$ values, that are the one associated to the opposite answer, preferring the question with the lowest of this value.
  We expect this strategy to perform very well, but only for very small problem instances: its complexity is in $O(n^2 m^5)$, because we consider $O(m^2)$ questions for each agent and need for each question to compute $\MMR$ twice, whose complexity is $O(nm^3)$.
@@
 
-The \strat{Two phase} strategy asks a predefined, non adaptive sequence of $m-2$ questions in order to gather informations about the weights $\w$ of the scoring rule, using one question per rank (except the extreme ones) as defined in the other strategies, thus, each cutting the initial interval of possibilities into two equal parts.
-Then it only asks questions about the agents, using questions as defined in the \strat{Pessimistic} strategy.
-%TODO Then use minimax regret as in Lu and Boutilier. check what’s this.
+The \strat{Pessimistic with heuristic} strategy is a much faster version of the previous strategy.
+It chooses among the set of possible questions in the same way, but considers only one possible question per voter and one possible question about the weights, thereby reducing the complexity to $O(n^2 m^3)$.
+\commentOC{Is this right?
+If we can solve easily a size $(m, n) = (15, 15)$ with the Pwh strategy, which requires about $15^5 \approx 8 .
+10^5$ operations, we should be able to solve easily a size $(m, n) = (6, 6)$ with the Pessimistic strategy, which requires about $6^7 \approx 3 .
+10^5$ operations.}
+The possible question associated to each voter is determined using a heuristic proposed by \citet{Boutilier2006}.
+\commentOC{Please check that the reference is correct and explain briefly their heuristic.} The possible question to the committee is determined as follows.
+\commentOC{I am not so happy about this.
+If we have time, we should consider one question per rank and drop the tau business.}
+Recall that $x^{*}$ is the minimax regret optimal alternative, and $\bar{y} = \arg \max_{y \in A} \PMR(x,y; \pprofile, W)$, $\bar{\profile}$ and $\bar{\w}$ are the adversarial choices, thus, the instantiations that, given the choice of $x^*$, maximize the regret.
+Define $w^\tau = \argmin_{\w \in W} s(\bar{y}; \bar{\profile}, \w) - s(x^{*}; \bar{\profile}, \w)$.
+The vector $\bar{w} - w^\tau = \argmax_{\w \in W} (s(\bar{y}; \bar{\profile}, \w) - s(x^{*}; \bar{\profile}, \w)) - \argmin_{\w \in W} (s(\bar{y}; \bar{\profile}, \w) - s(x^{*}; \bar{\profile}, \w))$ estimates our uncertainty about the weights $\w$ when fixing our choice of alternative $x^*$ and the adversarial choices $\bar{y}$ and $\bar{\profile}$.
+Therefore, we compare component-wise $\bar{\w}$ and $\w^{\tau}$, to find the position $r$ that is most valuable to ask about (the one that maximizes $\abs{\bar{\w}_r - \w^{\tau}_r}$), and choose $\lambda$ as the middle of the interval of possible values for that rank.
+
+Finally, the \strat{Two phase} strategy is developed in order to investigate the effect of varying the proportion of questions asked to voters and to the committee.
+The \strat{Two phase - vc} first asks $p$ questions to the voters, then $k-p$ questions to the committee, using in both cases Pessimistic with heuristic to select the specific question.
+The \strat{Two phase - cv} strategy starts with $p$ questions to the committee, then asks to the voters.
+\commentOC{If our XPs exhibit no significant change between vc and cv (or if we don’t have time to run them), I will drop this distinction.}
 
@@
 \sisetup{round-mode=places, round-precision=1, table-figures-integer=1, table-figures-decimal=1}
+\begin{table}
+	\begin{center}
+		\begin{tabular}{S[table-figures-integer=2, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
+			\toprule
+			{k} & {Rnd} & {sd} & {Pes.} & {sd} & {Pes.\ w.\ h.} & {sd} \\
+			\midrule
+			0 & 5.0 & 0 & 5.0 & 0\\
+			5 & 4.93 & 0.16 & 4.15 & 0.32\\
+			10 & 4.84 & 0.22 & 3.44 & 0.46\\
+			15 & 4.28 & 0.58 & 2.66 &0.54 \\
+			20 & 3.85 & 0.33 & 1.62 & 0.82\\
+			25 & 3.50 & 0.78 & 0.84 &  0.57\\
+			30 & 2.96 & 0.80 & 0.53 & 0.70\\
+			\bottomrule
+		\end{tabular}
+	\end{center}
+	\caption{Minimax regret in problems of size $(5, 5)$ after $k$ questions.}
+	\label{fig:55}
+\end{table}
+
+\begin{table}
+	\begin{center}
+		\begin{tabular}{S[table-figures-integer=2, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
+			\toprule
+			{k} & {Rnd} & {sd} & {Pes.\ w.\ h.} & {sd} \\
+			\midrule
+			0 & 6.0 & 0 &  &  \\
+			5 &  &  &  &  \\
+			10 &  &  &  &  \\
+			15 &  &  &  &  \\
+			20 &  &  &  &  \\
+			25 &  &  &  &  \\
+			30 &  &  &  &  \\
+			\bottomrule
+		\end{tabular}
+	\end{center}
+	\caption{Regret in problems of size $(10, 20)$ after $k$ questions.}
+	\label{fig:1020}
+\end{table}
+
+We test our strategies using randomly generated datasets. %TODO and real datasets. (sushi and iris).
+Our first goal is to see, with a small problem size ($m = 5, n = 5$) and the (time consuming) Pessimistic strategy, if an important lowering of the maximal regret can be achieved with a reasonable number of questions.
+We also want to estimate how “hard” such a problem is, by using the Random strategy as a baseline.
+Third, we want to estimate the loss (in terms of worst regret) when switching to the faster Pessimistic with heuristic strategy.
+Fourth, we want to see, on a bigger problem size ($m = 10, n = 20$), how many questions must be asked for that strategy to achieve a significant reduction of the worst regret.
+Finally, we want to evaluate, thanks to the Two phases strategy, the impact of varying the proportion of questions asked to the voters (with respect to questions asked to the committee) on the reduction of the worst regret.
+%We also want to see how realistic our approach is for various problem sizes, by estimating the number of questions we would have to ask before being able to reduce the worst regret significantly.
+
+We use the following protocol.
+Having picked a problem size $(m, n)$, a number of questions $k$ and a strategy, we randomly generate an “oracle”, containing the true preferences of the agents (i.e.
+the linear orders) and the weights associated with the chair's scoring rule.
+We start with empty knowledge ($\pprofile = (\emptyset_j), W = \W$) about the preference orderings of the agents or the weight differences favored by the chair.
+We obtain the first question to be asked using the selected strategy, as described above.
+We use the oracle to answer the question and update our knowledge, which is thus used to obtain the next question.
+This is repeated until $k$ answers have been obtained.
+Then we compute the resulting $\MMR$.
+We repeat this whole experiment 10 times, for a given $(m, n, k)$, and report the average resulting $\MMR$ and the standard deviation.
+
+The results are displayed in \cref{fig:55,fig:1020,fig:p}, where strategies are designated by Rnd for Random, 2 ph.
+for Two phases, Pes.
+for Pessimistic and Pes.\ w.\ h.
+for Pessimistic with heuristic.
+
+\begin{table}
+	\begin{center}
+		\begin{tabular}{S[table-figures-integer=2, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
+			\toprule
+			{p} & {Rnd} & {sd} & {2 ph.} & {sd} \\
+			\midrule
+			0 &  &  &  &  \\
+			20 &  &  &  &  \\
+			40 &  &  &  &  \\
+			60 &  &  &  &  \\
+			80 &  &  &  &  \\
+			100 &  &  &  &  \\
+			\bottomrule
+		\end{tabular}
+	\end{center}
+	\caption{Regret in problems of size $(10, 20)$ after $100$ questions.}
+	\label{fig:p}
+\end{table}
+
+\section{Conclusions}  
+\label{sec:conclusions}
+In this paper we have considered a social choice setting with partial information about the agent's preferences and a partially specified voting rule.
+In this setting, we have proposed the use of minimax regret both as a means of robust winner determination as well as a guide to the process of simultaneous elicitation of preferences and voting rule.
+Our experimental results %on randomly generated and real world data sets 
+suggest that regret-based elicitation is effective and allow to quickly reduce worst regret significantly.
+%Regret-based elicitation allows to determine near-optimal winners using only few information about the agents' preferences.
+
+%As part of the contribution of this work, we publish an open-source library that allows to reproduce our experiments and more, at https://github.com/…
+
+We mention some directions for future works.
+Further development of elicitation strategies, considering alternative heuristics, is an important direction. 
+Second, elicitation could be extended to voting rules beyond scoring rules.
+Finally, an important direction of extension aims at studying how to elicit preferences while restraining to concrete and easy questions.
+% Acknowledgements: We thank the reviewers for comments helping to improve the paper. 
+\bibliography{biblio}
+%\bibliographystyle{named}
+\bibliographystyle{abbrvnat} 
+%\end{document}
+
+\appendix
+\section{Old table}
 \begin{table}
@@
 	\caption{Minimax regret in problems of size $(4, 4)$ after $k$ questions.}
-	\label{fig:xp1}
+	\label{fig:44}
 \end{table}
-
-\begin{table}
-	\begin{center}
-		\begin{tabular}{S[table-figures-integer=2, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
-			\toprule
-			{k} & {Rnd} & {sd} & {T. ph.} & {sd} & {Pes.} & {sd} & {Pes.} & {sd} \\
-			\midrule
-			0 & 5.0 & 0 & 5.0 & 0 & 5.0 & 0\\
-			5 & 4.93 & 0.16 & 4.98 & 0.01 & 4.15 & 0.32\\
-			10 & 4.84 & 0.22 & 4.35 & 0.28 & 3.44 & 0.46\\
-			15 & 4.28 & 0.58 & 3.70 & 0.25 & 2.66 &0.54 \\
-			20 & 3.85 & 0.33 & 2.67 & 0.51 & 1.62 & 0.82\\
-			25 & 3.50 & 0.78 & 2.17 & 0.66 & 0.84 &  0.57\\
-			30 & 2.96 & 0.80 & 1.47 & 1.10 & 0.53 & 0.70\\
-			\bottomrule
-		\end{tabular}
-	\end{center}
-	\caption{Minimax regret in problems of size $(5, 5)$ after $k$ questions.}
-	\label{fig:xp2}
-\end{table}
-
-\begin{table}
-	\begin{center}
-		\begin{tabular}{S[table-figures-integer=2, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
-			\toprule
-			{k} & {Rnd} & {sd} & {T. ph.} & {sd} & {Pes.} & {sd} & {Pes.} & {sd} \\
-			\midrule
-			0 & 6.0 &  &  &  &  & \\
-			5 &  &  &  &  &  & \\
-			10 &  &  &  &  &  & \\
-			15 &  &  &  &  &  & \\
-			20 &  &  &  &  &  & \\
-			25 &  &  &  &  &  &  \\
-			30 &  &  &  &  &  & \\
-			\bottomrule
-		\end{tabular}
-	\end{center}
-	\caption{Minimax regret in problems of size $(6, 6)$ after $k$ questions.}
-	\label{fig:xp3}
-\end{table}
-
-We test our strategies using randomly generated datasets. %TODO and real datasets. (sushi and iris).
-Our goal is to see how much we gain with an interleaved elicitation approach mixing questions to the chair and questions asked to the agents compared to performing a partial elicitation of the rule first and then eliciting the agents preferences.
-We also want to see how realistic our approach is for various problem sizes, by estimating the number of questions we would have to ask before being able to reduce the worst regret significantly.
-
-We use the following protocol.
-Having picked a problem size $(m, n)$, a number of questions $k$ and a strategy, we randomly generate an “oracle”, containing the true preferences of the agents (i.e.
-the linear orders) and the weights associated with the chair's scoring rule.
-We start with empty knowledge ($\pprofile = (\emptyset_j), W = \W$) about the preference orderings of the agents or the weight differences favored by the chair.
-We obtain the first question to be asked using the selected strategy, as described above.
-We use the oracle to answer the question and update our knowledge, which is thus used to obtain the next question.
-This is repeated until $k$ answers have been obtained.
-Then we compute the resulting $\MMR$.
-We repeat this whole experiment 10 times, for a given $(m, n, k)$, and report the average resulting $\MMR$ and the standard deviation.
-
-The results are displayed in \cref{fig:xp1,fig:xp2,fig:xp3}, where strategies are designated by Rnd for Random, T. ph. for Two phases, EC for Extreme completions, and Pes. for Pessimistic.
-
-\section{Conclusions}  
-\label{sec:conclusions}
-In this paper we have considered a social choice setting with partial information about the agent's preferences and a partially specified voting rule.
-In this setting, we have proposed the use of minimax regret both as a means of robust winner determination as well as a guide to the process of simultaneous elicitation of preferences and voting rule.
-Our experimental results %on randomly generated and real world data sets 
-suggest that regret-based elicitation is effective and allow to quickly reduce worst regret significantly.
-%Regret-based elicitation allows to determine near-optimal winners using only few information about the agents' preferences.
-
-%As part of the contribution of this work, we publish an open-source library that allows to reproduce our experiments and more, at https://github.com/…
-
-We mention some directions for future works.
-Further development of elicitation strategies, considering alternative heuristics, is an important direction. 
-Second, elicitation could be extended to voting rules beyond scoring rules.
-Finally, an important direction of extension aims at studying how to elicit preferences while restraining to concrete and easy questions.
-% Acknowledgements: We thank the reviewers for comments helping to improve the paper. 
-%{\small
-\bibliography{biblio}
-%\bibliographystyle{named}
-\bibliographystyle{abbrvnat} 
-%}
-%\end{document}
-
-\appendix
+See \cref{fig:44}.
+
 \section{Bounding differences of weights}

### 2020-01-21 draft.tex

@@
 %We use the $\max$ operator because \citet{Cailloux2014} reported that pessimistic aggregation works much better than optimistic aggregation, although our experiments in this context suggested a weak impact of that choice on the performance of the strategy.
-It uses the $\leximax$ criterion as an aggregator: if the maximal $\MMR$ of two questions are equal, then it considers the other $\MMR$ values, that are the one associated to the opposite answer, preferring the question with the lowest of this value.
+However, to avoid the absorption property of max, we adopt the $\leximax$ criterion as an aggregator: if the maximal $\MMR$ of two questions are equal, then it considers the other $\MMR$ values, that are the one associated to the opposite answer, preferring the question with the lowest of this value.
  We expect this strategy to perform very well, but only for very small problem instances: its complexity is in $O(n^2 m^5)$, because we consider $O(m^2)$ questions for each agent and need for each question to compute $\MMR$ twice, whose complexity is $O(nm^3)$.
@@
 
-The \strat{Pessimistic with heuristic} strategy is a much faster version of the previous strategy.
-It chooses among the set of possible questions in the same way, but considers only one possible question per voter and one possible question about the weights, thereby reducing the complexity to $O(n^2 m^3)$.
-\commentOC{Is this right?
+%TODO Limited; chair
+The \strat{LimitedPessimistic} strategy uses the same criterion as the pessimistic strategy, but only considering a small set of candidate questions.
+For each voter, a candidate question is chosen by considering the heuristic proposed by \citet{Lu2011}. 
+For the chair, we define
+\begin{align}
+w^\tau & = \argmin_{\w \in W} s(\bar{y}; \bar{\profile}, \w) - s(x^{*}; \bar{\profile}, \w), \label{eq:tau} 
+\end{align}
+and compare component-wise $\bar{\w}$ and $\w^{\tau}$, to find the position $r$ that is most valuable to ask about (the one that maximizes $\abs{\bar{\w}_r - \w^{\tau}_r}$), and choose $\lambda$ as the middle of the interval of possible values for that rank.
+\commentOC{I am not so happy about this. If we have time, we should consider one question per rank and drop the tau business.}
+We then evaluate, for each candidate question, the minimax regret for each possible answer; finally we choose the best according to $\leximax$.
+%\commentOC{Reducing the complexity to $O(n^2 m^3).
+Is this right?
 If we can solve easily a size $(m, n) = (15, 15)$ with the Pwh strategy, which requires about $15^5 \approx 8 .
@@
 10^5$ operations.}
-The possible question associated to each voter is determined using a heuristic proposed by \citet{Boutilier2006}.
-\commentOC{Please check that the reference is correct and explain briefly their heuristic.} The possible question to the committee is determined as follows.
-\commentOC{I am not so happy about this.
-If we have time, we should consider one question per rank and drop the tau business.}
-Recall that $x^{*}$ is the minimax regret optimal alternative, and $\bar{y} = \arg \max_{y \in A} \PMR(x,y; \pprofile, W)$, $\bar{\profile}$ and $\bar{\w}$ are the adversarial choices, thus, the instantiations that, given the choice of $x^*$, maximize the regret.
-Define $w^\tau = \argmin_{\w \in W} s(\bar{y}; \bar{\profile}, \w) - s(x^{*}; \bar{\profile}, \w)$.
-The vector $\bar{w} - w^\tau = \argmax_{\w \in W} (s(\bar{y}; \bar{\profile}, \w) - s(x^{*}; \bar{\profile}, \w)) - \argmin_{\w \in W} (s(\bar{y}; \bar{\profile}, \w) - s(x^{*}; \bar{\profile}, \w))$ estimates our uncertainty about the weights $\w$ when fixing our choice of alternative $x^*$ and the adversarial choices $\bar{y}$ and $\bar{\profile}$.
-Therefore, we compare component-wise $\bar{\w}$ and $\w^{\tau}$, to find the position $r$ that is most valuable to ask about (the one that maximizes $\abs{\bar{\w}_r - \w^{\tau}_r}$), and choose $\lambda$ as the middle of the interval of possible values for that rank.
 

### 2020-01-21 draft.tex
rephrasing, minors and comments

@@
 In the classical setting, the voting rule is fixed beforehand and full information concerning the preferences of the agents is provided.
-
 Recently, the assumption of full preference information has been questioned by a number of researchers and several methods for eliciting preferences have been proposed.
 In this paper we go one step further and we assume that both the voting rule and the agents preferences are partially specified.
-
 Focusing on positional scoring rules, we assume that the chair, while  not able to give a precise definition of the rule, is capable of answering simple questions  requiring to pick a winner from a specific  example profile.
 Moreover, the preferences of the agents are incrementally acquired by asking comparison queries.
-
 In this setting, we propose a method  for robust approximate winner determination with minimax regret.
-We also provide an interactive elicitation protocol based on minimax regret
-and develop several query strategies that interleave questions to the chair and questions to the agents in order to attempt to acquire the most relevant information in order to quickly converge to optimal or a near-optimal alternative.
+We also provide an interactive elicitation protocol based on minimax regret and develop several query strategies that interleave questions to the chair and questions to the agents in order to attempt to acquire the most relevant information in order to quickly converge to optimal or a near-optimal alternative.
 \end{abstract}
@@
 This observation has motivated a number of recent works considering social choice with partial preference orders \citep{Xia2008, Pini2009, Konczak05} and incremental elicitation \citep{Kalech2011, Lu2011, Naamani-Dery2015} of agents’ preferences.
-
-Also the first hypothesis should be relaxed considering that in several situations it may not be easy to precisely define the voting rule.
-Indeed, it is possible that the chair has some preferences over the desired aggregation method, but is not able to formalize the voting rule upfront.
+\\ Furthermore, it is often difficult for non-expert users to formalize a voting rule on the basis of some generic preferences over a desired aggregation method.
+Thus, the first hypothesis should also be relaxed.
+%Also the first hypothesis should be relaxed considering that, in several situations, it may not be easy to precisely define the voting rule.Indeed, it is possible that the chair has some preferences over the desired aggregation method, but is not able to formalize the voting rule upfront.
 The work of \citet{Cailloux2014} provides elicitation methods for a quite general class of rules based on weak orders.
@@
 
-In this paper we consider that both the agents’ preferences and the social choice rule are partially specified and we develop methods for computing the minimax-optimal alternative under these assumptions.
+In this paper we focus on positional scoring rules, that are a particularly common method used to aggregate rankings, and we assume that both the agents’ preferences and the social choice rule are partially specified.
+We develop methods for computing the minimax-optimal
+alternative using positional scoring rules and we provide incremental elicitation methods to acquire relevant preference information.
+We then discuss several heuristics that determine queries, either to a voter or to the committee, that quickly reduce minimax regret.
+While previous works have considered either partial information about the agents’
+preferences or a partially specified aggregation method, we do not know of any work considering both sources of uncertainty at the same time.
+
+%In this paper we consider that both the agents’ preferences and the social choice rule are partially specified and we develop methods for computing the minimax-optimal alternative under these assumptions.
 %changed from: We develop methods for computing the minimax-optimal alternative for scoring rules with partial agent preference information and partial information about the weights of the scoring rule.
-While previous works have considered either partial information about the agents preferences or a partially specified aggregation method, we do not know of any work considering both sources of uncertainty at the same time.
-In this work, we focus on positional scoring rules, that are a particularly common method used to aggregate rankings and determine a winner.
-We also address the problem of elicitation, providing incremental elicitation methods to acquire relevant preference information.
+
+%We also address the problem of elicitation, providing incremental elicitation methods to acquire relevant preference information.
 We then discuss several heuristics that attempt to simultaneously reduce the preference and voting rule uncertainty by determining queries, either to an agent or to the chair, that quickly reduce minimax regret.
@@
 We now introduce some basic concepts.
-We consider a set $A$ of $m$ alternatives (products, restaurants, movies, public projects, job candidates, etc.) and a set $\set{1, …, n}$ of agents (voters).
-Each agent $j$ comes from an infinite set $\N$ of potential agents and is associated to her “real” preference order $\pref_j \in \linors$ which is a linear order (connected, transitive, asymmetric relations) over the alternatives.
+We consider a set $A$ of $m$ alternatives (products, restaurants, movies, public projects, job candidates, etc.) \commentBN{I think we should stick with only few example useful for our purpose} and a set $\set{1, …, n}$ of agents (voters) \commentBN{I think we should use either agent or voter}.
+Each agent $j$ comes from an infinite set $\N$ of potential agents and is associated to her “real” preference order $\pref_j \in \linors$ which is a linear order (a connected, transitive, asymmetric relation) over the alternatives.
 Following the social choice nomenclature, we call {\em profile} the association of a preference to each agent, considering a subset of agents from the set $\N$, and denote a profile by $(\pref_1,\ldots,\pref_n)$.
@@
 
-In this work we assume fixed, but unknown, a profile $\profile^*$ (and corresponding agents preferences $\pref_j^*$) and a weight vector $\w^*$, and we want to reason about partial preference information concerning those objects.
-Our knowledge at a given time of the preference of agent $j$ is encoded by a partial order over the alternatives, thus a transitive and asymmetric binary relation, denoted by $\ppref_j$. 
+In this work we assume fixed, but unknown \commentBN{I think we should phrase it better to be sure that the reader understands that this represents what's on people mind and it's unknown only to us}, a profile $\profile^*$ (and corresponding agents preferences $\pref_j^*$) and a weight vector $\w^*$, and we want to reason about partial preference information concerning those objects.
+At a given time, our knowledge of agent $j$'s preference is encoded by a partial order over the alternatives, thus a transitive and asymmetric binary relation, denoted by $\ppref_j$. 
 In this work we assume that preference information is truthful, i.e. $a \ppref_j b ⇒ a \pref_j^* b$.
@@
 Using {\em maximum regret} to quantify the worst-case error, the alternatives that minimize this error are selected as tied winners, providing us with a form of robust optimization.
-Intuitively, the quality of a proposed alternative $a$ is how far $a$ is from the optimal one in the worst case, given current knowledge.
+Intuitively, the quality of a proposed alternative $a$ is how far $a$ is from the optimal one in the worst case, given the current knowledge.
 
@@
 \end{claim}
+%TODO If space is needed, check if we can cut something here; 1.5 columns seems too much for that
 \begin{proof}
@@
 The intervals are initialized to $[1, n]$.
-If it opted for a question to agents, it draws equiprobably among the agents whose preference is not known entirely; picks an alternative $a$ randomly with equal probability among those involved in some incomparabilities in $\ppref_j$; and picks an alternative $b$ with equal probability among those incomparable with $a$ in $\ppref_j$.
+If it opted for a question to agents, it draws equiprobably among the agents whose preference is not known entirely \commentBN{and picks with equal probability two alternatives that are incomparable in her partial preference profile.}; picks an alternative $a$ randomly with equal probability among those involved in some incomparabilities in $\ppref_j$; and picks an alternative $b$ with equal probability among those incomparable with $a$ in $\ppref_j$.
 
@@
  We expect this strategy to perform very well, but only for very small problem instances: its complexity is in $O(n^2 m^5)$, because we consider $O(m^2)$ questions for each agent and need for each question to compute $\MMR$ twice, whose complexity is $O(nm^3)$.
-For small dimensions, it gives us an estimate of an upper bound to the possible quality of a strategy.
+For small dimensions, it gives us an estimate \commentBN{estimation?} of an upper bound to the possible quality of a strategy.
 
@@
 Finally, the \strat{Two phase} strategy is developed in order to investigate the effect of varying the proportion of questions asked to voters and to the committee.
-The \strat{Two phase - vc} first asks $p$ questions to the voters, then $k-p$ questions to the committee, using in both cases Pessimistic with heuristic to select the specific question.
+The \strat{Two phase - vc} first asks $p$ questions to the voters, then $k-p$ questions to the committee, using in both cases Pessimistic with heuristic \commentBN{limitedPessimistic?} to select the specific question.
 The \strat{Two phase - cv} strategy starts with $p$ questions to the committee, then asks to the voters.

### 2020-01-21 draft.tex
Renamed strats

@@
 where $\alpha^{x}_r$ is the number of times that alternative $x$ was ranked in the $r$-th position.
-The winners are the alternatives with highest scores.
+The winners are the alternatives gighest scores.
 
@@
 %TODO Limited; chair
-The \strat{LimitedPessimistic} strategy uses the same criterion as the pessimistic strategy, but only considering a small set of candidate questions.
+The \strat{Limited pessimistic} strategy uses the same criterion as the pessimistic strategy, but only considering a small set of candidate questions.
 For each voter, a candidate question is chosen by considering the heuristic proposed by \citet{Lu2011}. 
@@
 
-Finally, the \strat{Two phase} strategy is developed in order to investigate the effect of varying the proportion of questions asked to voters and to the committee.
-The \strat{Two phase - vc} first asks $p$ questions to the voters, then $k-p$ questions to the committee, using in both cases Pessimistic with heuristic \commentBN{limitedPessimistic?} to select the specific question.
-The \strat{Two phase - cv} strategy starts with $p$ questions to the committee, then asks to the voters.
+Finally, the \strat{Two phases} strategy is developed in order to investigate the effect of varying the proportion of questions asked to voters and to the committee.
+The \strat{Two phases - vc} first asks $p$ questions to the voters, then $k-p$ questions to the committee, using in both cases Limited pessimistic to select the specific question.
+The \strat{Two phases - cv} strategy starts with $p$ questions to the committee, then asks to the voters.
 \commentOC{If our XPs exhibit no significant change between vc and cv (or if we don’t have time to run them), I will drop this distinction.}
@@
 			\toprule
-			{k} & {Rnd} & {sd} & {Pes.} & {sd} & {Pes.\ w.\ h.} & {sd} \\
+			{k} & {Rnd} & {sd} & {Pes.} & {sd} & {L.\ pes.} & {sd} \\
 			\midrule
@@
 			\toprule
-			{k} & {Rnd} & {sd} & {Pes.\ w.\ h.} & {sd} \\
+			{k} & {Rnd} & {sd} & {L.\ pes.} & {sd} \\
 			\midrule
@@
 We also want to estimate how “hard” such a problem is, by using the Random strategy as a baseline.
-Third, we want to estimate the loss (in terms of worst regret) when switching to the faster Pessimistic with heuristic strategy.
+Third, we want to estimate the loss (in terms of worst regret) when switching to the faster Limited pessimistic strategy.
 Fourth, we want to see, on a bigger problem size ($m = 10, n = 20$), how many questions must be asked for that strategy to achieve a significant reduction of the worst regret.
@@
 
-The results are displayed in \cref{fig:55,fig:1020,fig:p}, where strategies are designated by Rnd for Random, 2 ph.
-for Two phases, Pes.
-for Pessimistic and Pes.\ w.\ h.
-for Pessimistic with heuristic.
+The results are displayed in \cref{fig:55,fig:1020,fig:p}, where strategies are designated by Rnd for Random, 2 ph. for Two phases, Pes. for Pessimistic and L.\ pes. for Limited pessimistic.
 

### 2020-01-21 draft.tex
Voter ⇒ agent

@@
 alternative using positional scoring rules and we provide incremental elicitation methods to acquire relevant preference information.
-We then discuss several heuristics that determine queries, either to a voter or to the committee, that quickly reduce minimax regret.
+We then discuss several heuristics that determine queries, either to an agent or to the chair, that quickly reduce minimax regret.
 While previous works have considered either partial information about the agents’
@@
 We now introduce some basic concepts.
-We consider a set $A$ of $m$ alternatives (products, restaurants, movies, public projects, job candidates, etc.) \commentBN{I think we should stick with only few example useful for our purpose} and a set $\set{1, …, n}$ of agents (voters) \commentBN{I think we should use either agent or voter}.
+We consider a set $A$ of $m$ alternatives (products, restaurants, movies, public projects, job candidates, etc.) \commentBN{I think we should stick with only few example useful for our purpose} and a set $\set{1, …, n}$ of agents (voters).
 Each agent $j$ comes from an infinite set $\N$ of potential agents and is associated to her “real” preference order $\pref_j \in \linors$ which is a linear order (a connected, transitive, asymmetric relation) over the alternatives.
@@
 Recall that, in the computation of $s(x; \profile, \w)$, $w_{v_j(x)}$ represents the score that $x$ obtains in the ranking $v_j$ (see Equation \ref{eq:srule}).
-Since scoring rules are additively decomposable, we can consider separately the contribution of each voter to the total score. Thus, we can write the actual regret of choosing $x$ instead of $y$ as
+Since scoring rules are additively decomposable, we can consider separately the contribution of each agent to the total score. Thus, we can write the actual regret of choosing $x$ instead of $y$ as
 \[
@@
 The \strat{Limited pessimistic} strategy uses the same criterion as the pessimistic strategy, but only considering a small set of candidate questions.
-For each voter, a candidate question is chosen by considering the heuristic proposed by \citet{Lu2011}. 
+For each agent, a candidate question is chosen by considering the heuristic proposed by \citet{Lu2011}. 
 For the chair, we define
@@
 
-Finally, the \strat{Two phases} strategy is developed in order to investigate the effect of varying the proportion of questions asked to voters and to the committee.
-The \strat{Two phases - vc} first asks $p$ questions to the voters, then $k-p$ questions to the committee, using in both cases Limited pessimistic to select the specific question.
-The \strat{Two phases - cv} strategy starts with $p$ questions to the committee, then asks to the voters.
+Finally, the \strat{Two phases} strategy is developed in order to investigate the effect of varying the proportion of questions asked to agents and to the chair.
+The \strat{Two phases - vc} first asks $p$ questions to the agents, then $k-p$ questions to the chair, using in both cases Limited pessimistic to select the specific question.
+The \strat{Two phases - cv} strategy starts with $p$ questions to the chair, then asks to the agents.
 \commentOC{If our XPs exhibit no significant change between vc and cv (or if we don’t have time to run them), I will drop this distinction.}
@@
 Fourth, we want to see, on a bigger problem size ($m = 10, n = 20$), how many questions must be asked for that strategy to achieve a significant reduction of the worst regret.
-Finally, we want to evaluate, thanks to the Two phases strategy, the impact of varying the proportion of questions asked to the voters (with respect to questions asked to the committee) on the reduction of the worst regret.
+Finally, we want to evaluate, thanks to the Two phases strategy, the impact of varying the proportion of questions asked to the agents (with respect to questions asked to the chair) on the reduction of the worst regret.
 %We also want to see how realistic our approach is for various problem sizes, by estimating the number of questions we would have to ask before being able to reduce the worst regret significantly.
@@
 
-Problem: we can make the difference of scores very small, even with $n=2$ voters and $m=3$ alternatives and while satisfying convexity.
+Problem: we can make the difference of scores very small, even with $n=2$ agents and $m=3$ alternatives and while satisfying convexity.
 Consider $w_1 = 1, w_2 = \frac{1-\epsilon}{n}, w_3 = 0$, $s(a) - s(b) = (w_1 - w_2) - (n-1) (w_2 - w_3) = w_1 - n w_2 = \epsilon$.
@@
 \end{align}
-and ask the committee if they would prefer as a winner an alternative ranked first one time and third three times rather than an alternative ranked second four times.
-
-Another way to query the committee, a more concrete one, is to present them a profile representing the situation described by the query and then deduce its answer from the selected winner.
+and ask the chair if they would prefer as a winner an alternative ranked first one time and third three times rather than an alternative ranked second four times.
+
+Another way to query the chair, a more concrete one, is to present them a profile representing the situation described by the query and then deduce its answer from the selected winner.
 Obviously we have to be sure to choose a profile where only the alternatives we are interested in could be pick as winners.
@@
 Recalling the query (\ref{eqn:juryquery}) we are considering as an example, it is easy to see that in the current profile alternatives $a$ and $b$ represent the situation as described by the query.
-Therefore, if after proposing this profile to the committee the winning alternative turns out to be $a$ then we know that $w_{2} - w_{3} > 2(w_{3} - w_{4})$; if, instead, the winner is $b$ we know that $w_{2} - w_{3} < 2(w_{3} - w_{4})$ and if both alternatives are picked as winners then $w_{2} - w_{3} = 2(w_{3} - w_{4})$.
+Therefore, if after proposing this profile to the chair the winning alternative turns out to be $a$ then we know that $w_{2} - w_{3} > 2(w_{3} - w_{4})$; if, instead, the winner is $b$ we know that $w_{2} - w_{3} < 2(w_{3} - w_{4})$ and if both alternatives are picked as winners then $w_{2} - w_{3} = 2(w_{3} - w_{4})$.
 
@@
 
-So the strategy for querying the committee is to use two alternatives $i$ and $j$ to represent the query and complete the profile such that the other alternatives are all dominated by them.
+So the strategy for querying the chair is to use two alternatives $i$ and $j$ to represent the query and complete the profile such that the other alternatives are all dominated by them.
 An algorithmic approach is to start from the initial profile and then add as many agents as needed that rank $i$ and $j$ as their top choices and the other alternatives afterwards.

### 2020-01-21 draft.tex
Some last comments; started fill tables

@@
 The traditional approach to social choice assumes that both the social choice function and the full preference orderings of the agents are expressed beforehand. These represent two strong hypothesis.
-Requiring agents to express full preference orderings can be prohibitively costly (in terms of cognitive and communication cost), especially for decisions with large sets of alternatives.
+Requiring agents to express full preference orderings can be prohibitively costly (in terms of cognitive and communication cost).
 This observation has motivated a number of recent works considering social choice with partial preference orders \citep{Xia2008, Pini2009, Konczak05} and incremental elicitation \citep{Kalech2011, Lu2011, Naamani-Dery2015} of agents’ preferences.
@@
 We now introduce some basic concepts.
-We consider a set $A$ of $m$ alternatives (products, restaurants, movies, public projects, job candidates, etc.) \commentBN{I think we should stick with only few example useful for our purpose} and a set $\set{1, …, n}$ of agents (voters).
+We consider a set $A$ of $m$ alternatives (products, restaurants, movies, public projects, job candidates, etc.) and a set $\set{1, …, n}$ of agents (voters).
 Each agent $j$ comes from an infinite set $\N$ of potential agents and is associated to her “real” preference order $\pref_j \in \linors$ which is a linear order (a connected, transitive, asymmetric relation) over the alternatives.
@@
 \end{align}
-%\commentBN{$s^{\profile,\w}(x)$}
 where $\alpha^{x}_r$ is the number of times that alternative $x$ was ranked in the $r$-th position.
@@
 
-In this work we assume fixed, but unknown \commentBN{I think we should phrase it better to be sure that the reader understands that this represents what's on people mind and it's unknown only to us}, a profile $\profile^*$ (and corresponding agents preferences $\pref_j^*$) and a weight vector $\w^*$, and we want to reason about partial preference information concerning those objects.
+In this work we assume fixed, but unknown to us, a profile $\profile^*$, representing the preferences $\pref_j^*$ of the agents, and a weight vector $\w^*$, representing the preferences of the chair, and we want to reason about partial preference information concerning those objects.
 At a given time, our knowledge of agent $j$'s preference is encoded by a partial order over the alternatives, thus a transitive and asymmetric binary relation, denoted by $\ppref_j$. 
@@
 Observe that, whenever the $\PMR$ of an alternative $x$ (against some other alternative $y$) exceeds the best MR value found so far, we don't need to further evaluate $x$. 
-%\commentBN{Indeed, the maximum regret of an alternative is the maximum value among all the PMRs, so we already know that $\MR(x) \geq \PMR(x,y)$, which is greater than the current MR.
-Thus, x will never be selected as a winner in the minimizing step.}
 This idea can be exploited further by adopting a minimax-search tree \citep{Braziunas2011}.
@@
 The intervals are initialized to $[1, n]$.
-If it opted for a question to agents, it draws equiprobably among the agents whose preference is not known entirely \commentBN{and picks with equal probability two alternatives that are incomparable in her partial preference profile.}; picks an alternative $a$ randomly with equal probability among those involved in some incomparabilities in $\ppref_j$; and picks an alternative $b$ with equal probability among those incomparable with $a$ in $\ppref_j$.
+If it opted for a question to agents, it draws equiprobably among the agents whose preference is not known entirely; picks an alternative $a$ randomly with equal probability among those involved in some incomparabilities in $\ppref_j$; and picks an alternative $b$ with equal probability among those incomparable with $a$ in $\ppref_j$.
 
@@
  We expect this strategy to perform very well, but only for very small problem instances: its complexity is in $O(n^2 m^5)$, because we consider $O(m^2)$ questions for each agent and need for each question to compute $\MMR$ twice, whose complexity is $O(nm^3)$.
-For small dimensions, it gives us an estimate \commentBN{estimation?} of an upper bound to the possible quality of a strategy.
-
-%TODO Limited; chair
+For small dimensions, it gives us an estimate of an upper bound to the possible quality of a strategy.
+
 The \strat{Limited pessimistic} strategy uses the same criterion as the pessimistic strategy, but only considering a small set of candidate questions.
@@
 and compare component-wise $\bar{\w}$ and $\w^{\tau}$, to find the position $r$ that is most valuable to ask about (the one that maximizes $\abs{\bar{\w}_r - \w^{\tau}_r}$), and choose $\lambda$ as the middle of the interval of possible values for that rank.
-\commentOC{I am not so happy about this. If we have time, we should consider one question per rank and drop the tau business.}
+%\commentOC{I am not so happy about this. If we have time, we should consider one question per rank and drop the tau business.}
 We then evaluate, for each candidate question, the minimax regret for each possible answer; finally we choose the best according to $\leximax$.
-%\commentOC{Reducing the complexity to $O(n^2 m^3).
-Is this right?
-If we can solve easily a size $(m, n) = (15, 15)$ with the Pwh strategy, which requires about $15^5 \approx 8 .
-10^5$ operations, we should be able to solve easily a size $(m, n) = (6, 6)$ with the Pessimistic strategy, which requires about $6^7 \approx 3 .
-10^5$ operations.}
 
@@
 			0 & 5.0 & 0 & 5.0 & 0\\
-			5 & 4.93 & 0.16 & 4.15 & 0.32\\
-			10 & 4.84 & 0.22 & 3.44 & 0.46\\
-			15 & 4.28 & 0.58 & 2.66 &0.54 \\
-			20 & 3.85 & 0.33 & 1.62 & 0.82\\
-			25 & 3.50 & 0.78 & 0.84 &  0.57\\
-			30 & 2.96 & 0.80 & 0.53 & 0.70\\
+			5 & 4.958 & 0.100 & 3.741 & 0.024\\
+			10 & 4.709 & 0.436 & 3.283 & 0.423\\
+			15 & 4.432 & 0.467 & 2.716 &0.410 \\
+			20 & 3.666 & 0.522 & 1.549 & 0.430\\
+			25 & 3.068 & 0.679 & 1.424 &  0.512\\
+			30 & 2.631 & 0.466 & 0.394 & 0.359\\
 			\bottomrule

### 2020-01-22 draft.tex
More numbers in tables
strategies

@@
 
-\begin{claim}
+\begin{claim} \label{claim:completion}
 There exists a completion $\hat{\profile} \in C(\pprofile)$ such that $\PMR(x,y; \pprofile, W) = \max_{\w \in W} [ s(y; \hat{\profile}, \w) - s(x; \hat{\profile}, \w) ]$ and such that the linear order $\hat{v}_{j}$ of each agent $j$ satisfies:
@@
 
-The \strat{Limited pessimistic} strategy uses the same criterion as the pessimistic strategy, but only considering a small set of candidate questions.
-For each agent, a candidate question is chosen by considering the heuristic proposed by \citet{Lu2011}. 
-For the chair, we define
+The \strat{Limited pessimistic} strategy uses the same criterion as the pessimistic strategy, but limiting it only to a small set of candidate questions.
+It considers the current solution of the $\MMR$, i.e.
+the minimax optimal alternative $x^{*}$ and the adversarial choices $\bar{y}, \bar{w}, \bar{v}$.
+Then, it selects n questions (one per agent) by adopting the heuristic proposed by \citet{Lu2011}.
+If we consider an agent $j$, there are only three possible relations between the alternatives $x^{*}$ and $\bar{y}$ in her partial preference: either $x^{*} \ppref_j \bar{y}$, or $\bar{y} \ppref_j x^{*}$, or they are incomparable.
+As shown in the proof of Claim \ref{claim:completion}, in order to increase $\PMR(x^{*},\bar{y})$, an adversary should place as many alternatives as he can above $x^{*}$ in the first case, and between $\bar{y}$ and $x^{*}$ in the second.
+An intuitive way to reduce the pairwise max regret is, therefore, to directly ask questions involving such alternatives, hoping for an answer that would prevent the adversary to play his best game.
+If $x^{*}$ and $\bar{y}$ are incomparable, then we just ask the voter $j$ to compare them.
+To conclude the set of candidate questions, the \strat{Limited pessimistic} strategy also selects a question to the committee. We define
 \begin{align}
@@
 \end{align}
-and compare component-wise $\bar{\w}$ and $\w^{\tau}$, to find the position $r$ that is most valuable to ask about (the one that maximizes $\abs{\bar{\w}_r - \w^{\tau}_r}$), and choose $\lambda$ as the middle of the interval of possible values for that rank.
+as the weight vector that minimize the $\PMR$ in the worst case.
+We compare component-wise $\bar{\w}$ and $\w^{\tau}$ to find the position $r$ that is most valuable to ask about (the one that maximizes $\abs{\bar{\w}_r - \w^{\tau}_r}$), and choose $\lambda$ as the middle of the interval of possible values for that rank.
 %\commentOC{I am not so happy about this. If we have time, we should consider one question per rank and drop the tau business.}
-We then evaluate, for each candidate question, the minimax regret for each possible answer; finally we choose the best according to $\leximax$.
-
-Finally, the \strat{Two phases} strategy is developed in order to investigate the effect of varying the proportion of questions asked to agents and to the chair.
-The \strat{Two phases - vc} first asks $p$ questions to the agents, then $k-p$ questions to the chair, using in both cases Limited pessimistic to select the specific question.
+We then evaluate, for each candidate question, the minimax regret for the two possible answers; finally we choose the best according to $\leximax$.
+
+Lastly, the \strat{Two phases} strategy is developed in order to investigate the effect of varying the proportion of questions asked to agents and to the chair.
+%The \strat{Two phases - vc} first asks $p$ questions to the agents, then $k-p$ questions to the chair, using in both cases Limited pessimistic to select the specific question.
 The \strat{Two phases - cv} strategy starts with $p$ questions to the chair, then asks to the agents.
 \commentOC{If our XPs exhibit no significant change between vc and cv (or if we don’t have time to run them), I will drop this distinction.}
+It first asks $p$ questions to the chair, then $k-p$ questions to the agents, using in both cases \strat{Limited pessimistic} strategy to select the specific question.
+The aim of this strategy is to simulate the current state of the art when considering incomplete preferences.
+In fact, by asking enough questions to the chair we can reduce our problem into a well studied one of incompleteness of preferences knowing the voting rule.
+Moreover, if we invert to whom ask questions first, we fall instead, in an already studied case of uncertainty of the voting rule with a known complete profile.
 
@@
 			\midrule
-			0 & 5.0 & 0 & 5.0 & 0\\
-			5 & 4.958 & 0.100 & 3.741 & 0.024\\
-			10 & 4.709 & 0.436 & 3.283 & 0.423\\
-			15 & 4.432 & 0.467 & 2.716 &0.410 \\
-			20 & 3.666 & 0.522 & 1.549 & 0.430\\
-			25 & 3.068 & 0.679 & 1.424 &  0.512\\
-			30 & 2.631 & 0.466 & 0.394 & 0.359\\
+			0 & 5.0 & 0 & 5.0 & 0 & 5.0 & 0\\
+			5 & 4.958 & 0.100 & 3.741 & 0.024 & 4.350 & 0.604\\
+			10 & 4.709 & 0.436 & 3.283 & 0.423 & 3.323 & 0.374\\
+			15 & 4.432 & 0.467 & 2.716 &0.410 & 2.722 & 0.672\\
+			20 & 3.666 & 0.522 & 1.549 & 0.430 & 2.145 & 0.716\\
+			25 & 3.068 & 0.679 & 1.424 &  0.512 & 0.921 & 0.569\\
+			30 & 2.631 & 0.466 & 0.394 & 0.359 & 0.470 & 0.355\\
 			\bottomrule
@@
 			\midrule
-			0 & 6.0 & 0 &  &  \\
-			5 &  &  &  &  \\
-			10 &  &  &  &  \\
-			15 &  &  &  &  \\
-			20 &  &  &  &  \\
-			25 &  &  &  &  \\
-			30 &  &  &  &  \\
+			0 & 20.0 & 0 & 20.0 & 0 \\
+			20 & 19.985 & 0.042 & 18.770 & 0.111 \\
+			40 & 19.903 & 0.080 & 17.659 & 0.290 \\
+			60 & 19.764 & 0.159 & 16.951 & 0.541 \\
+			80 & 19.403 & 0.221 & 15.736 & 0.367 \\
+			100 & 18.947 & 0.383 & 14.621 & 0.703 \\
 			\bottomrule
@@
 
-The results are displayed in \cref{fig:55,fig:1020,fig:p}, where strategies are designated by Rnd for Random, 2 ph. for Two phases, Pes. for Pessimistic and L.\ pes. for Limited pessimistic.
+The results are displayed in \cref{fig:55,fig:1020,fig:p}, where strategies are designated by Rnd for Random, Pes. for Pessimistic, L.\ pes. for Limited pessimistic and 2 ph. for Two phases.
 
@@
 			\toprule
-			{p} & {Rnd} & {sd} & {2 ph.} & {sd} \\
+			{p} & {Two ph.} & {sd} \\%& {2 ph. vc} & {sd} \\
 			\midrule
-			0 &  &  &  &  \\
-			20 &  &  &  &  \\
-			40 &  &  &  &  \\
-			60 &  &  &  &  \\
-			80 &  &  &  &  \\
-			100 &  &  &  &  \\
+			0 & 100.0 & 0 \\%&  &  \\
+			20 & 18.778 & 0.125 \\%&  &  \\
+			40 & 17.648 & 0.473 \\%&  &  \\
+			60 & 16.460 & 0.609 \\%&  &  \\
+			80 & 15.470 & 0.597 \\%&  &  \\
+			100 & 14.876 & 0.460 \\%&  &  \\
 			\bottomrule

### 2020-01-22 draft.tex
cutting on Claim4 and some analysis

@@
 \max_{\w} & \sum_{r=1}^m (\hat{\alpha}_{r}^{y} - \hat{\alpha}_{r}^{x}) w_{r}\\
-\text{ s.t. } & \text{\cref{eq:monotone}}\\
-& \text{\cref{eq:convexity}}\\
-& \Co_W
+\text{ s.t. } & \text{\cref{eq:monotone}} \text{ and } \text{\cref{eq:convexity}} \text{ and } \Co_W
 \end{align*}
@@
 This permits to test how the chair understands the question and to relate the preference of the chair to her choice behavior in the economic sense.
-Furthermore this will be necessary for an ordinal extension of our work where the scores would not be considered as cardinal utilities.
+%Furthermore this will be necessary for an ordinal extension of our work where the scores would not be considered as cardinal utilities.
 Thus, our task is to build a profile, given $\lambda$ and $r ≤ m-2$, in such a way that the set of (tied) winners picked by the chair reveals whether $w_{r} - w_{r+1} \geq \lambda (w_{r+1} - w_{r+2})$.
@@
 Observe that the question may be defined equivalently as $q \cdot w_{r} + p \cdot w_{r+2} ≥ (p + q) \cdot w_{r+1}$, where $p, q$ are natural numbers. 
-As a first attempt to make this question concrete, let us define a profile $P$ containing $p+q$ agents. 
-Define an alternative $a$ that receives $q$ times the rank $r$ and $p$ times the rank $r+2$ and an alternative $b$ that receives $p+q$ times the rank $r+1$. 
+As a first attempt to make this question concrete, we could define a profile $P$ such that there is an alternative $a$ that receives $q$ times the rank $r$ and $p$ times the rank $r+2$, and an alternative $b$ that receives $p+q$ times the rank $r+1$.
 Observing that the score of $a$ in that profile is exactly the left hand side of the question, and that the score of $b$ is the right hand side, intuition suggests that observing whether the chair picks $a$ or $b$ as winner will let us determine which side is greater; equality occurring when the chair declares $a$ and $b$ as tied for the victory.
-However, we still need to complete the profile, thus, come up with other $m-2$ alternatives defined so that each agent in the resulting profile has placed exactly one alternative in each rank. 
-And we must ensure, doing this, that these other alternatives are not better than $a$ or $b$: if the chair picks a different alternative $c$, it tells us that the chair prefers $c$ to both $a$ and $b$,
+However, we still need to complete the profile, in a way that none of these other alternatives is better than $a$ or $b$: if the chair picks a different alternative $c$, it tells us that the chair prefers $c$ to both $a$ and $b$,
 but it generally does not  answer the question we are interested in. 
@@
 Observe that if we add $\delta$ agents (with $\delta$ a natural number) that put $a$ at first rank and $b$ at second rank, and $\delta$ agents that put $b$ at first rank and $a$ at second rank, we do not change the difference of the scores of $a$ and $b$, and thus, observing the chair choosing $a$ or $b$ still answers the question.
-Choose arbitrarily a matching of the remaining $m-2$ alternatives to the ranks $3$ to $m$, say, $c \mapsto 3$, $d \mapsto 4$, and so on.
+% Choose arbitrarily a matching of the remaining $m-2$ alternatives to the ranks $3$ to $m$, say, $c \mapsto 3$, $d \mapsto 4$, and so on.
 The first $\delta$ supplementary agents, who rank $a$ first and $b$ second, rank the other alternatives as the just defined mapping suggests.
 The other $\delta$ supplementary agents, who rank $b$ first and $a$ second, use the opposite ranking for the remaining alternatives, say, $c \mapsto m$, $d \mapsto m-1$, and so on.
-We can now prove that, for $\delta = p+q$, and whatever the weight vector $\w \in \W$, no alternative, except possibly $b$, has a better score than $a$.
+
+We can prove that, for $\delta = p+q$, and whatever the weight vector $\w \in \W$, no alternative, except possibly $b$, has a better score than $a$.
 (In fact, as the construction will exhibit, they are all worst than both $a$ and $b$, but the weaker fact is enough for our claim.)
-
 Pick any alternative $c$ that is not $a$ or $b$. 
@@
 
+We can see in Table \ref{fig:55} that while the \strat{Pessimistic} strategy is able to reduce the regret almost completely after $30$ questions, it takes $1000$ times more time than the \strat{Random} strategy ($16s$ of the Pessimistic compared to $0.014s$ of the Random).
+Moreover, the results of the \strat{Limited pessimistic}, that takes almost $80\%$ less of the time of the \strat{Pessimistic} ($2.6s$), are essentially the same.
+In Table \ref{fig:1020}, we can see the drop of regret using a bigger instance.
+%Finally in Table \ref{fig:p}
+
 \begin{table}
@@
 %\end{document}
+\end{document}
 
@@
 For example, $\epsilon = 1/1000, n = 2, w_2 = 999/2000$.
-\end{document}
 

### 2020-01-22 draft.tex
Restored some text, minor changes, fit in 6 pages

--- 2020-01-22 draft.tex
@@
 \end{claim}
-%TODO If space is needed, check if we can cut something here; 1.5 columns seems too much for that
 \begin{proof}
 Observe that the question may be defined equivalently as $q \cdot w_{r} + p \cdot w_{r+2} ≥ (p + q) \cdot w_{r+1}$, where $p, q$ are natural numbers. 
-As a first attempt to make this question concrete, let us define a profile $P$ containing $p+q$ agents. 
-Define an alternative $a$ that receives $q$ times the rank $r$ and $p$ times the rank $r+2$ and an alternative $b$ that receives $p+q$ times the rank $r+1$. 
+As a first attempt to make this question concrete, we could define a profile $P$
+%TODO
+containing $p+q$ agents
+in such a way that an alternative $a$ receives $q$ times the rank $r$ and $p$ times the rank $r+2$, and an alternative $b$ receives $p+q$ times the rank $r+1$. 
 Observing that the score of $a$ in that profile is exactly the left hand side of the question, and that the score of $b$ is the right hand side, intuition suggests that observing whether the chair picks $a$ or $b$ as winner will let us determine which side is greater; equality occurring when the chair declares $a$ and $b$ as tied for the victory.
@@
 Observe that if we add $\delta$ agents (with $\delta$ a natural number) that put $a$ at first rank and $b$ at second rank, and $\delta$ agents that put $b$ at first rank and $a$ at second rank, we do not change the difference of the scores of $a$ and $b$, and thus, observing the chair choosing $a$ or $b$ still answers the question.
-Choose arbitrarily a matching of the remaining $m-2$ alternatives to the ranks $3$ to $m$, say, $c \mapsto 3$, $d \mapsto 4$, and so on.
+% Choose arbitrarily a matching of the remaining $m-2$ alternatives to the ranks $3$ to $m$, say, $c \mapsto 3$, $d \mapsto 4$, and so on.
 The first $\delta$ supplementary agents, who rank $a$ first and $b$ second, rank the other alternatives as the just defined mapping suggests.
 The other $\delta$ supplementary agents, who rank $b$ first and $a$ second, use the opposite ranking for the remaining alternatives, say, $c \mapsto m$, $d \mapsto m-1$, and so on.
-We can now prove that, for $\delta = p+q$, and whatever the weight vector $\w \in \W$, no alternative, except possibly $b$, has a better score than $a$.
-(In fact, as the construction will exhibit, they are all worst than both $a$ and $b$, but the weaker fact is enough for our claim.)
-
+
+We can prove that, for $\delta = p+q$, and whatever the weight vector $\w \in \W$, no alternative, except possibly $b$, has a better score than $a$. 
+%(In fact, as the construction will exhibit, they are all worst than both $a$ and $b$, but the weaker fact is enough for our claim.)
 Pick any alternative $c$ that is not $a$ or $b$. 
@@
  We expect this strategy to perform very well, but only for very small problem instances: its complexity is in $O(n^2 m^5)$, because we consider $O(m^2)$ questions for each agent and need for each question to compute $\MMR$ twice, whose complexity is $O(nm^3)$.
-For small dimensions, it gives us an estimate of an upper bound to the possible quality of a strategy.
-
-The \strat{Limited pessimistic} strategy uses the same criterion as the pessimistic strategy, but limiting it only to a small set of candidate questions.
-It considers the current solution of the $\MMR$, i.e.
-the minimax optimal alternative $x^{*}$ and the adversarial choices $\bar{y}, \bar{w}, \bar{v}$.
-Then, it selects n questions (one per agent) by adopting the heuristic proposed by \citet{Lu2011}.
-If we consider an agent $j$, there are only three possible relations between the alternatives $x^{*}$ and $\bar{y}$ in her partial preference: either $x^{*} \ppref_j \bar{y}$, or $\bar{y} \ppref_j x^{*}$, or they are incomparable.
+For small dimensions, it estimates an upper bound to the possible quality of a strategy.
+
+The \strat{Limited pessimistic} strategy uses the same criterion as the pessimistic strategy, but limiting it to a small set of $n+1$ candidate questions: one per agent, and one to the chair.
+It uses the heuristic proposed by \citet{Lu2011} to define the candidate questions to the agents.
+Considering agent $j$, either $x^{*} \ppref_j \bar{y}$, or $\bar{y} \ppref_j x^{*}$, or $x^{*}$ and $\bar{y}$ are incomparable in $\ppref_j$.
 As shown in the proof of Claim \ref{claim:completion}, in order to increase $\PMR(x^{*},\bar{y})$, an adversary should place as many alternatives as he can above $x^{*}$ in the first case, and between $\bar{y}$ and $x^{*}$ in the second.
@@
 If $x^{*}$ and $\bar{y}$ are incomparable, then we just ask the voter $j$ to compare them.
-To conclude the set of candidate questions, the \strat{Limited pessimistic} strategy also selects a question to the committee. We define
-\begin{align}
-w^\tau & = \argmin_{\w \in W} s(\bar{y}; \bar{\profile}, \w) - s(x^{*}; \bar{\profile}, \w), \label{eq:tau} 
-\end{align}
-as the weight vector that minimize the $\PMR$ in the worst case.
+To define the candidate question to the chair, consider
+%\begin{align}
+$w^\tau = \argmin_{\w \in W} s(\bar{y}; \bar{\profile}, \w) - s(x^{*}; \bar{\profile}, \w)$,
+%\end{align}
+the weight vector that minimize the $\PMR$ in the worst case.
 We compare component-wise $\bar{\w}$ and $\w^{\tau}$ to find the position $r$ that is most valuable to ask about (the one that maximizes $\abs{\bar{\w}_r - \w^{\tau}_r}$), and choose $\lambda$ as the middle of the interval of possible values for that rank.
-%\commentOC{I am not so happy about this. If we have time, we should consider one question per rank and drop the tau business.}
+%TODO
 We then evaluate, for each candidate question, the minimax regret for the two possible answers; finally we choose the best according to $\leximax$.
@@
 \commentOC{If our XPs exhibit no significant change between vc and cv (or if we don’t have time to run them), I will drop this distinction.}
-It first asks $p$ questions to the chair, then $k-p$ questions to the agents, using in both cases \strat{Limited pessimistic} strategy to select the specific question.
+It first asks $p$ questions to the chair, then $k-p$ questions to the agents, using in both cases the \strat{Limited pessimistic} strategy to select the specific question.
 The aim of this strategy is to simulate the current state of the art when considering incomplete preferences.
 In fact, by asking enough questions to the chair we can reduce our problem into a well studied one of incompleteness of preferences knowing the voting rule.
-Moreover, if we invert to whom ask questions first, we fall instead, in an already studied case of uncertainty of the voting rule with a known complete profile.
+Moreover, if we invert to whom ask questions first, we fall instead in an already studied case of uncertainty of the voting rule with a known complete profile.
 
@@
 
+We observe that the Pessimistic strategy is able to reduce the regret almost completely after $30$ questions.
+We also see that Limited pessimistic performs essentially as well as Pessimistic.
+This is good news, since for that size, Pessimistic takes $16s$ compared to $2.6s$ for finding a question.
+%However, it takes $1000$ times more time than the \strat{Random} strategy ($16s$ of the Pessimistic compared to $0.014s$ of the Random).
+Moreover, the results of the \strat{Limited pessimistic}, that takes almost $80\%$ less of the time of the \strat{Pessimistic} ($2.6s$), are essentially the same.
+%In Table \ref{fig:1020}, we can see the drop of regret using a bigger instance.
+%Finally in Table \ref{fig:p}
+
 \begin{table}
@@
 
-%As part of the contribution of this work, we publish an open-source library that allows to reproduce our experiments and more, at https://github.com/…
+As part of the contribution of this work, we publish an open-source library that allows to reproduce our experiments, and more (url not displayed for anonymity reasons).
 
@@
 \bibliographystyle{abbrvnat} 
-%\end{document}
+\end{document}
 

### 2020-01-22 draft.tex
Restored remark

@@
 We can prove that, for $\delta = p+q$, and whatever the weight vector $\w \in \W$, no alternative, except possibly $b$, has a better score than $a$. 
-%(In fact, as the construction will exhibit, they are all worst than both $a$ and $b$, but the weaker fact is enough for our claim.)
+(In fact, as the construction will exhibit, they are all worst than both $a$ and $b$, but the weaker fact is enough for our claim.)
 Pick any alternative $c$ that is not $a$ or $b$. 
@@
 Now $a'_1 ≥ \delta, a'_t ≥ 2\delta \text{ for } 2 ≤ t < m, a'_{r+2} = q+p+2\delta = a'_m$.
-To obtain upper bounds for $c'_t$, assume $c$ is ranked first by the $p+q$ agents voting in profile $P$.
+To obtain upper bounds for $c'_t$, assume $c$ is ranked first by the $p+q$ agents in $P$.
 By our construction, the  $2 \delta$ new agents of $P'$ give to $c$ the ranks $(3, m)$, or $(4, m-1)$, … Observe that the score of $c$ is maximal for attribution $(3, m)$, by convexity of the weights.
@@
 %\begin{align}
-$w^\tau = \argmin_{\w \in W} s(\bar{y}; \bar{\profile}, \w) - s(x^{*}; \bar{\profile}, \w)$,
+$\w^\tau = \argmin_{\w \in W} s(\bar{y}; \bar{\profile}, \w) - s(x^{*}; \bar{\profile}, \w)$,
 %\end{align}
 the weight vector that minimize the $\PMR$ in the worst case.
-We compare component-wise $\bar{\w}$ and $\w^{\tau}$ to find the position $r$ that is most valuable to ask about (the one that maximizes $\abs{\bar{\w}_r - \w^{\tau}_r}$), and choose $\lambda$ as the middle of the interval of possible values for that rank.
+We compare $\bar{\w}$ and $\w^{\tau}$ component-wise to find the position $r$ that is most valuable to ask about (the one that maximizes $\abs{\bar{\w}_r - \w^{\tau}_r}$), and choose $\lambda$ as the middle of the interval of possible values for that rank.
 %TODO

### 2020-01-22 draft.tex
Better phrasing time comparison

@@
 We observe that the Pessimistic strategy is able to reduce the regret almost completely after $30$ questions.
-We also see that Limited pessimistic performs essentially as well as Pessimistic.
-This is good news, since for that size, Pessimistic takes $16s$ compared to $2.6s$ for finding a question.
+We also see that Limited pessimistic performs almost as well as Pessimistic.
+This is good news, since for that size, it takes only $2.6s$ for finding a question, compared to $16s$ for Pessimistic.
 %However, it takes $1000$ times more time than the \strat{Random} strategy ($16s$ of the Pessimistic compared to $0.014s$ of the Random).

### 2020-01-22 draft.tex
two-phase section

@@
 \[\max_{i=1,2} \MMR(\pprofile_i,W_i) \]
-This badness measure gives a way of picking questions among a set of possible questions, by picking one that minimizes the measure.
-Note that other aggregators than $\max$ can be used as well.
+This badness measure gives a way of picking questions among a set of possible questions, by picking one that minimizes ths measure of minimax regret {\em a posteriori}. 
+%Note that other aggregators than $\max$ can be used as well.
 %We use the $\max$ operator because \citet{Cailloux2014} reported that pessimistic aggregation works much better than optimistic aggregation, although our experiments in this context suggested a weak impact of that choice on the performance of the strategy.
-However, to avoid the absorption property of max, we adopt the $\leximax$ criterion as an aggregator: if the maximal $\MMR$ of two questions are equal, then it considers the other $\MMR$ values, that are the one associated to the opposite answer, preferring the question with the lowest of this value.
+However, to avoid the absorption property of max, we adopt the $\leximax$ criterion as an aggregator: if the maximal $\MMR$ of two questions are equal, then it considers the other $\MMR$ values, that are the one associated to the opposite answer, preferring the question with the lowest value.
  We expect this strategy to perform very well, but only for very small problem instances: its complexity is in $O(n^2 m^5)$, because we consider $O(m^2)$ questions for each agent and need for each question to compute $\MMR$ twice, whose complexity is $O(nm^3)$.
@@
 An intuitive way to reduce the pairwise max regret is, therefore, to directly ask questions involving such alternatives, hoping for an answer that would prevent the adversary to play his best game.
-If $x^{*}$ and $\bar{y}$ are incomparable, then we just ask the voter $j$ to compare them.
+If $x^{*}$ and $\bar{y}$ are incomparable, then we just ask the agent $j$ to compare them.
 To define the candidate question to the chair, consider
@@
 \commentOC{If our XPs exhibit no significant change between vc and cv (or if we don’t have time to run them), I will drop this distinction.}
-It first asks $p$ questions to the chair, then $k-p$ questions to the agents, using in both cases the \strat{Limited pessimistic} strategy to select the specific question.
-The aim of this strategy is to simulate the current state of the art when considering incomplete preferences.
+It first asks $p$ questions to the chair, then $k-p$ questions to the agents, using in both cases the same method as \strat{Limited pessimistic} to select the specific question. 
+Note that when asking first only questions to the chair, if the obtained knowledge approximates well the scoring vector, then in the second part of the elicitation we fall into the more classical setting of incompleteness of preferences assuming a known the voting rule.
+%And vice-versa when asking first questions to the agents, the second part of the elicitation is similar to the setting of incompletely specified scoring rule. 
+%The aim of this strategy is to simulate the current state of the art when considering incomplete preferences.
 In fact, by asking enough questions to the chair we can reduce our problem into a well studied one of incompleteness of preferences knowing the voting rule.

### 2020-01-22 draft.tex
computation times

@@
 We observe that the Pessimistic strategy is able to reduce the regret almost completely after $30$ questions.
-We also see that Limited pessimistic performs almost as well as Pessimistic.
-This is good news, since for that size, it takes only $2.6s$ for finding a question, compared to $16s$ for Pessimistic.
+We also see that Limited pessimistic performs almost as well as Pessimistic; this is good news since (for $m=5$ and $n=5$), the former strategy is much faster and takes only $2.6s$ for a complete elicitation session, while the latter takes $16s$.
 %However, it takes $1000$ times more time than the \strat{Random} strategy ($16s$ of the Pessimistic compared to $0.014s$ of the Random).

### 2020-01-22 draft.tex
Typo

@@
 Observe that the question may be defined equivalently as $q \cdot w_{r} + p \cdot w_{r+2} ≥ (p + q) \cdot w_{r+1}$, where $p, q$ are natural numbers. 
-As a first attempt to make this question concrete, we could define a profile $P$
-%TODO
-containing $p+q$ agents
-in such a way that an alternative $a$ receives $q$ times the rank $r$ and $p$ times the rank $r+2$, and an alternative $b$ receives $p+q$ times the rank $r+1$. 
+As a first attempt to make this question concrete, we could define a profile $P$ containing $p+q$ agents in such a way that an alternative $a$ receives $q$ times the rank $r$ and $p$ times the rank $r+2$, and an alternative $b$ receives $p+q$ times the rank $r+1$.
 Observing that the score of $a$ in that profile is exactly the left hand side of the question, and that the score of $b$ is the right hand side, intuition suggests that observing whether the chair picks $a$ or $b$ as winner will let us determine which side is greater; equality occurring when the chair declares $a$ and $b$ as tied for the victory.
@@
 We compare $\bar{\w}$ and $\w^{\tau}$ component-wise to find the position $r$ that is most valuable to ask about (the one that maximizes $\abs{\bar{\w}_r - \w^{\tau}_r}$), and choose $\lambda$ as the middle of the interval of possible values for that rank.
-%TODO
 We then evaluate, for each candidate question, the minimax regret for the two possible answers; finally we choose the best according to $\leximax$.
@@
 It first asks $p$ questions to the chair, then $k-p$ questions to the agents, using in both cases the same method as \strat{Limited pessimistic} to select the specific question. 
-Note that when asking first only questions to the chair, if the obtained knowledge approximates well the scoring vector, then in the second part of the elicitation we fall into the more classical setting of incompleteness of preferences assuming a known the voting rule.
+Note that when asking first only questions to the chair, if the obtained knowledge approximates well the scoring vector, then in the second part of the elicitation we fall into the more classical setting of incompleteness of preferences assuming a known voting rule.
 %And vice-versa when asking first questions to the agents, the second part of the elicitation is similar to the setting of incompletely specified scoring rule. 
@@
 
-We test our strategies using randomly generated datasets. %TODO and real datasets. (sushi and iris).
+We test our strategies using randomly generated datasets. 
 Our first goal is to see, with a small problem size ($m = 5, n = 5$) and the (time consuming) Pessimistic strategy, if an important lowering of the maximal regret can be achieved with a reasonable number of questions.

### 2020-01-23 draft.tex
T3 should start at 20, I suppose.
T3 200 q
Legend
submission

--- 2020-01-22 draft.tex
@@
 is the worst-case loss of choosing $x$ instead of $y$ under all possible realizations of the full profile {\em and} all possible instantiations of the weights:
-\begin{align}
+\begin{align*}
 \PMR(x,y; \pprofile, W) & = \max_{\w \in W} \max_{\profile \in C(\pprofile)} s(y; \profile,\w) - s(x; \profile,\w).
-\end{align}
+\end{align*}
 
@@
 Recall that, in the computation of $s(x; \profile, \w)$, $w_{v_j(x)}$ represents the score that $x$ obtains in the ranking $v_j$ (see Equation \ref{eq:srule}).
-Since scoring rules are additively decomposable, we can consider separately the contribution of each agent to the total score. Thus, we can write the actual regret of choosing $x$ instead of $y$ as
-\[
-s(y; \profile,\w) - s(x; \profile, \w) = \sum_{j=1}^n w_{v_j(y)} - w_{v_j(x)},
-\]
+Since scoring rules are additively decomposable, we can consider separately the contribution of each agent to the total score.
+Thus, we can write the actual regret of choosing $x$ instead of $y$ as $s(y; \profile,\w) - s(x; \profile, \w) = \sum_{j=1}^n w_{v_j(y)} - w_{v_j(x)}$,
 and we can rewrite $\PMR$ as follows:
@@
 & \PMR(x,y; \pprofile, W) = \max_{\w \in W} \max_{\profile \in C(\pprofile)} [ s(y; \profile,\w) - s(x; \profile,\w) ] \\
-& =  \max_{\w \in W} \sum_{j=1}^{n} \max_{v_j \in C(\succ_j^p)} [w_{v_j(y)} - w_{v_j(x)}]. \\
+& =  \max_{\w \in W} \sum_{j=1}^{n} \max_{v_j \in C(\succ_j^p)} [w_{v_j(y)} - w_{v_j(x)}].
 \end{align*}
@@
 Suffices now to rewrite \cref{eq:bettery} to let the two disjuncts designate disjoint sets:
-\begin{equation}
+\begin{equation*}
 \label{eq:betteryfinal}
@@
 (a \ppref_j y) ∨ ((x \pprefeq_j y) ∧ ¬(x \pprefeq_j a) ∧ ¬(a \ppref_j y)).
-\end{equation} 
+\end{equation*} 
 \end{proof}
@@
 \begin{align*}
-\max_{\w} & \sum_{r=1}^m (\hat{\alpha}_{r}^{y} - \hat{\alpha}_{r}^{x}) w_{r}\\
-\text{ s.t. } & \text{\cref{eq:monotone}} \text{ and } \text{\cref{eq:convexity}} \text{ and } \Co_W
+\max_{\w} & \sum_{r=1}^m (\hat{\alpha}_{r}^{y} - \hat{\alpha}_{r}^{x}) w_{r}
 \end{align*}
-Note that given our choice $w_{1}=1$ and $w_{m}=0$, there are only $m-2$ variables 
+$\text{ s.t. } \text{\cref{eq:monotone}} \text{ and } \text{\cref{eq:convexity}} \text{ and } \Co_W$. Note that given our choice $w_{1}=1$ and $w_{m}=0$, there are only $m-2$ variables 
 (we leave $w_{1}$ and $w_{m}$ in the LP just for clarity of presentation).
@@
 Assume that a question leads to the possible new knowledge states $(\pprofile_1, W_1)$ and $(\pprofile_2, W_2)$, depending on the answer.
-Then the badness of the question in the worst case is:
-\[\max_{i=1,2} \MMR(\pprofile_i,W_i) \]
+Then the badness of the question in the worst case is: $\max_{i=1,2} \MMR(\pprofile_i,W_i) $.
 This badness measure gives a way of picking questions among a set of possible questions, by picking one that minimizes ths measure of minimax regret {\em a posteriori}. 
@@
 			\midrule
-			0 & 100.0 & 0 \\%&  &  \\
-			20 & 18.778 & 0.125 \\%&  &  \\
-			40 & 17.648 & 0.473 \\%&  &  \\
-			60 & 16.460 & 0.609 \\%&  &  \\
-			80 & 15.470 & 0.597 \\%&  &  \\
-			100 & 14.876 & 0.460 \\%&  &  \\
+			0 & 20.0 & 0 \\%&  &  \\
+			25 & 18.851 & 0.125 \\%&  &  \\
+			50 & 17.296 & 0.473 \\%&  &  \\
+			75 & 15.774 & 0.609 \\%&  &  \\
+			100 & 14.707 & 0.597 \\%&  &  \\
+			125 & 12.999 & 0.460 \\%&  &  \\
+			150 & 11.975 & 0.473 \\%&  &  \\
+			175 & 9.999 & 0.609 \\%&  &  \\
+			200 & 11.499 & 0.597 \\%&  &  \\
 			\bottomrule
@@
 	\end{center}
-	\caption{Regret in problems of size $(10, 20)$ after $100$ questions.}
+	\caption{Regret in problems of size $(10, 20)$ after $200$ questions.}
 	\label{fig:p}
@@
 Our experimental results %on randomly generated and real world data sets 
-suggest that regret-based elicitation is effective and allow to quickly reduce worst regret significantly.
+suggest that regret-based elicitation is effective and allow to quickly reduce worst regret, but they also show that starting with zero knowledge became a pretentious approach really quickly when increasing the size of the problem.
+Future works will therefore include the test of these strategies on partial specified profiles, ideally on real datasets.
+An other important direction is the extension to voting rules beyond scoring rules.
+%Finally, an important direction of extension aims at studying how to elicit preferences while restraining to concrete and easy questions.
 %Regret-based elicitation allows to determine near-optimal winners using only few information about the agents' preferences.
-
 As part of the contribution of this work, we publish an open-source library that allows to reproduce our experiments, and more (url not displayed for anonymity reasons).
 
-We mention some directions for future works.
-Further development of elicitation strategies, considering alternative heuristics, is an important direction. 
-Second, elicitation could be extended to voting rules beyond scoring rules.
-Finally, an important direction of extension aims at studying how to elicit preferences while restraining to concrete and easy questions.
 % Acknowledgements: We thank the reviewers for comments helping to improve the paper. 

### 2020-01-23 draft.tex

@@
 	\begin{center}
-		\begin{tabular}{S[table-figures-integer=2, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
+		\begin{tabular}{S[table-figures-integer=2, table-number-alignment = right, table-figures-decimal=0]r}
 			\toprule
-			{p} & {Two ph.} & {sd} \\%& {2 ph. vc} & {sd} \\
+			{p} & {Two ph.} \\
 			\midrule
-			0 & 20.0 & 0 \\%&  &  \\
-			25 & 18.851 & 0.125 \\%&  &  \\
-			50 & 17.296 & 0.473 \\%&  &  \\
-			75 & 15.774 & 0.609 \\%&  &  \\
-			100 & 14.707 & 0.597 \\%&  &  \\
-			125 & 12.999 & 0.460 \\%&  &  \\
-			150 & 11.975 & 0.473 \\%&  &  \\
-			175 & 9.999 & 0.609 \\%&  &  \\
-			200 & 11.499 & 0.597 \\%&  &  \\
+			0 & 20.000 \\
+			25 & 18.851 \\
+			50 & 17.296 \\
+			75 & 15.774 \\
+			100 & 14.707 \\
+			125 & 12.999 \\
+			150 & 11.975 \\
+			175 & 9.999 \\
+			200 & 11.499 \\
 			\bottomrule
@@
 	\end{center}
-	\caption{Regret in problems of size $(10, 20)$ after $200$ questions.}
+	\caption{Regret in problems of size $(10, 20)$ after $200$ questions (one repetition only).}
 	\label{fig:p}

### 2020-02-25 draft.tex
New concl from Beatrice
Restored the right number from Beatrice
ijcai 2020 format and minors

--- 2020-01-22 draft.tex
@@
-\input{ijcai_preamble} 
+\input{ijcai20} 
 \author{ID: 7094}
@@
 where $\alpha^{x}_r$ is the number of times that alternative $x$ was ranked in the $r$-th position.
-The winners are the alternatives gighest scores.
+The winners are the alternatives with the highest scores.
 
@@
 	\begin{center}
-		\begin{tabular}{S[table-figures-integer=2, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
+		\begin{tabular}{S[table-figures-integer=2, table-number-alignment = right, table-figures-decimal=0]r}
 			\toprule
-			{p} & {Two ph.} & {sd} \\%& {2 ph. vc} & {sd} \\
+			{p} & {Two ph.} \\
 			\midrule
-			0 & 100.0 & 0 \\%&  &  \\
-			20 & 18.778 & 0.125 \\%&  &  \\
-			40 & 17.648 & 0.473 \\%&  &  \\
-			60 & 16.460 & 0.609 \\%&  &  \\
-			80 & 15.470 & 0.597 \\%&  &  \\
-			100 & 14.876 & 0.460 \\%&  &  \\
+			0 & 20.00 \\
+			25 & 18.85 \\
+			50 & 17.29 \\
+			75 & 15.77 \\
+			100 & 14.70 \\
+			125 & 12.99 \\
+			150 & 11.97 \\
+			175 & 9.99 \\
+			200 & 11.49 \\
 			\bottomrule
@@
 	\end{center}
-	\caption{Regret in problems of size $(10, 20)$ after $100$ questions.}
+	\caption{Regret in problems of size $(10, 20)$ after $200$ questions (one repetition only).}
 	\label{fig:p}
@@
 suggest that regret-based elicitation is effective and allow to quickly reduce worst regret significantly.
+%regret, but they also show that starting with zero knowledge became a pretentious approach really quickly when increasing the size of the problem.
+Future works will therefore include the test of these strategies on partial specified profiles, ideally on real datasets.
+An other important direction is the extension to voting rules beyond scoring rules.
  %Regret-based elicitation allows to determine near-optimal winners using only few information about the agents' preferences.

### 2020-06-03 draft.tex
corrected table 3
Some comments

@@
 This strategy first decides with a probability of $1/2$ each whether it will ask a question about weights or a question about a preference ordering (unless the profile is already known entirely).
-If it opted for a question about weights, it draws one rank in $2 ≤ r ≤ m-2$ equiprobably, takes the middle of the interval of values for $\lambda$ that are still possible considering our knowledge so far, and asks whether $w_r - w_{r+1} ≥ \lambda (w_{r+1} - w_{r+2})$.
+If it opted for a question about weights, it draws one rank in $2 ≤ r ≤ m-2$ equiprobably \commentOC{Isn’t this $1 ≤ r$?}, takes the middle of the interval of values for $\lambda$ that are still possible considering our knowledge so far, and asks whether $w_r - w_{r+1} ≥ \lambda (w_{r+1} - w_{r+2})$.
 The intervals are initialized to $[1, n]$.
-If it opted for a question to agents, it draws equiprobably among the agents whose preference is not known entirely; picks an alternative $a$ randomly with equal probability among those involved in some incomparabilities in $\ppref_j$; and picks an alternative $b$ with equal probability among those incomparable with $a$ in $\ppref_j$.
+If it opted for a question to agents, it draws equiprobably among the agents whose preference is not known entirely; draws an alternative $a$ equiprobably among those involved in some incomparabilities in $\ppref_j$; and draws an alternative $b$ equiprobably among those incomparable with $a$ in $\ppref_j$.
 
@@
 Considering agent $j$, either $x^{*} \ppref_j \bar{y}$, or $\bar{y} \ppref_j x^{*}$, or $x^{*}$ and $\bar{y}$ are incomparable in $\ppref_j$.
-As shown in the proof of Claim \ref{claim:completion}, in order to increase $\PMR(x^{*},\bar{y})$, an adversary should place as many alternatives as he can above $x^{*}$ in the first case, and between $\bar{y}$ and $x^{*}$ in the second.
-An intuitive way to reduce the pairwise max regret is, therefore, to directly ask questions involving such alternatives, hoping for an answer that would prevent the adversary to play his best game.
+\commentOC{I think $\bar{y}$ is not defined.} As shown in the proof of Claim \ref{claim:completion}, in order to increase $\PMR(x^{*},\bar{y})$, an adversary should place as many alternatives as he can above $x^{*}$ in the first case, and between $\bar{y}$ and $x^{*}$ in the second.
+An intuitive way to reduce the pairwise max regret is, therefore, to directly ask questions involving such alternatives \commentOC{(with equal likelyhood?)}, hoping for an answer that would prevent the adversary to play his best game.
 If $x^{*}$ and $\bar{y}$ are incomparable, then we just ask the agent $j$ to compare them.
@@
 			\midrule
-			0 & 20.00 \\
-			25 & 18.85 \\
-			50 & 17.29 \\
-			75 & 15.77 \\
+			0 & 11.49 \\
+			25 & 9.99 \\
+			50 & 11.97 \\
+			75 & 12.99 \\
 			100 & 14.70 \\
-			125 & 12.99 \\
-			150 & 11.97 \\
-			175 & 9.99 \\
-			200 & 11.49 \\
+			125 & 15.77 \\
+			150 & 17.29 \\
+			175 & 18.85 \\
+			200 & 20.00 \\
 			\bottomrule

### 2020-09-08 AAMAS2021/minimax.tex
paper conform to aamas formatting

--- 2020-06-03 draft.tex
@@
-\input{ijcai20} 
-\author{ID: 7094}
-%\author{Beatrice Napolitano$^1$\and Olivier Cailloux$^1$	\and  Paolo Viappiani$^{2}$
-%	\affiliations $^1$ LAMSADE, UMR 7243, CNRS and Universit\'e Paris Dauphine, PSL Research University, Paris, France\\ $^2$ LIP6, UMR 7606, CNRS and Sorbonne Universit\'e, Paris, France
-%	\emails \{firstname.lastname\}@dauphine.fr, paolo.viappiani@lip6.fr
-%}
-%Restoring page numbers as missing them out violates basic human rights of the reviewers. -- Olivier
-\thispagestyle{plain}
-\pagestyle{plain}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\usepackage[T1]{fontenc}
-\usepackage[utf8]{inputenc}
-\usepackage{newunicodechar}
-\usepackage{textcomp}
-%\newunicodechar{⇒}{\implies}
-\newunicodechar{⇒}{\Rightarrow}
-\newunicodechar{≠}{\ensuremath{\neq}}
-\newunicodechar{≤}{\leq}
-\newunicodechar{≥}{\geq}
-%… Horizontal Ellipsis
-\DeclareUnicodeCharacter{2026}{\ifmmode\dots\else\textellipsis\fi}
-\newunicodechar{∧}{\land}
-\newunicodechar{∨}{\lor}
-\newunicodechar{∩}{\cap}
-\newunicodechar{∪}{\cup}
-%¬ Not Sign
-\DeclareUnicodeCharacter{00AC}{\ifmmode\lnot\else\textlnot\fi}
-\newunicodechar{⇔}{\Leftrightarrow}
-\newcommand{\N}{ℕ}
-\newunicodechar{ℕ}{\mathbb{N}}
+%%% LaTeX Template for AAMAS-2021 (based on sample-sigconf.tex)
+%%% Prepared by Natasha Alechina and Ulle Endriss (version 2020-08-06)
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%% Start your document with the \documentclass command.
+%%% Use the first variant below for the final paper.
+%%% Use the second variant below for submission.
+
+\documentclass[sigconf]{aamas} 
+%\documentclass[sigconf,anonymous]{aamas}
+
+%%% Load required packages here (note that many are included already).
+\input{preamble/packages}
+%\input{preamble/redac}
+%\input{preamble/math_basics}
+\input{preamble/math}
+%for appendix
+\usepackage{import}
 \usepackage{algorithm, algpseudocode}
-\usepackage{amsmath,amssymb,enumerate,amsthm}
-\usepackage{natbib}
-\usepackage[strict]{siunitx}
-\usepackage{hyperref}
-\usepackage{mathrsfs}
 
-\usepackage{bm}
-\usepackage{empheq}
-\usepackage{cleveref}
-\usepackage{xcolor}
+\usepackage{balance} % for balancing columns on the final page
 
-\newcommand{\email}[1]{\href{mailto:#1}{#1}}
-\newcommand{\denselist}{\itemsep -2pt\topsep-6pt\partopsep-6pt}
 \newcommand{\commentOC}[1]{\textcolor{blue}{\small$\big[$OC: #1$\big]$}}
@@
 
-\newcommand{\pref}{\succ}%real, connected pref, strict
-\newcommand{\prefeq}{\succeq}%real, connected pref, strict
-\newcommand{\prefr}{{\succ}^\text{r}}%real, connected pref, strict
-\newcommand{\pprefeq}{\succeq^\text{p}}%partial pref
-\newcommand{\ppref}{\succ^\text{p}}%partial pref
-\newcommand{\pprefinv}{\prec^\text{p}}%partial pref
-\newcommand{\nppref}{\nsucc^\text{p}}%negated partial pref
-\newcommand{\linors}{\mathcal{L}(A)}
-%https://tex.stackexchange.com/a/45732, works within both \set and \set*, same spacing than \mid (https://tex.stackexchange.com/a/52905).
-\newcommand{\suchthat}{\;\ifnum\currentgrouptype=16 \middle\fi|\;}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-%Thanks to https://tex.stackexchange.com/q/154549
-\makeatletter
-\newcommand{\newrelation}[2]{% #1 = control sequence, #2 = replacement text
-  \@ifdefinable{#1}{%
-    \def#1{%
-    \@ifnextchar_{\csname\string#1\endcsname}{\mathrel{#2}}%
-    }%
-    \@namedef{\string#1}##1##2{\mathrel{#2_{##2}}}%
-  }%
-}
-\makeatother
+%%% AAMAS-2021 copyright block (do not change!)
 
-\newrelation{\prefinc}{\!\parallel\!}%partial pref, complement (incomparable)
-\newrelation{\pinc}{\bowtie^\text{p}}
-%\newrelation{\prefinc}{Q^\text{p}}%partial pref, complement (incomparable)
+\setcopyright{ifaamas}
+\acmConference[AAMAS '21]{Proc.\@ of the 20th International Conference on Autonomous Agents and Multiagent Systems (AAMAS 2021)}{May 3--7, 2021}{London, UK}{U.~Endriss, A.~Now\'{e}, F.~Dignum, A.~Lomuscio (eds.)}
+\copyrightyear{2021}
+\acmYear{2021}
+\acmDOI{}
+\acmPrice{}
+\acmISBN{}
 
-\newcommand{\profile}{\bm{v}}%(complete) profile
-\newcommand{\pprofile}{{\bm{p}}}%partial profile
-\newcommand{\w}{\bm{w}}
-\newcommand{\W}{\mathcal{W}}
-\newcommand{\Co}{\mathcal{C}}
-\newcommand{\pw}{W}%our knowledge about the weights
-\newcommand{\powersetz}[1]{\mathscr{P}^*(#1)}
-\newcommand{\strat}[1]{\emph{#1}}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\DeclareMathOperator{\Regret}{Regret}
-\DeclareMathOperator{\SCORE}{Score}
-\DeclareMathOperator{\PMR}{PMR}
-\DeclareMathOperator{\MR}{MR}
-\DeclareMathOperator{\MMR}{MMR}
-\DeclareMathOperator{\leximax}{leximax}
-\DeclareMathOperator*{\argmax}{argmax}
-\DeclareMathOperator*{\argmin}{argmin}
+%%% Use this command to specify your EasyChair submission number.
+%%% In anonymous mode, it will be printed on the first page.
 
-\newtheorem{claim}{Claim}
-\newtheorem{prop}{Proposition}
-\newtheorem{corollary}{Corollary}
-\newtheorem{definition}{Definition}
-\newtheorem{example}{Example}
+\acmSubmissionID{???}
 
-\DeclarePairedDelimiter\set{\{}{\}}
-\DeclarePairedDelimiter\card{\lvert}{\rvert}
-\DeclarePairedDelimiter\abs{\lvert}{\rvert}
-
-\tolerance=2000
-%Accept overfull hbox up to...
-\hfuzz=1cm
-%Reduces verbosity about the bad line breaks.
-\hbadness 10000
-%Reduces verbosity about the underful vboxes.
-\vbadness=10000
+%%% Use this command to specify the title of your paper.
 
@@
 
-\begin{document}
-\maketitle
+%%% Provide names, affiliations, and email addresses for all authors.
+
+\author{Beatrice Napolitano}
+\affiliation{
+	\institution{LAMSADE, UMR 7243, CNRS and Universit\'e Paris Dauphine, PSL Research University}
+	\city{Paris}
+	\state{France}}
+\email{beatrice.napolitano@dauphine.fr}
+
+\author{Olivier Cailloux}
+\affiliation{
+	\institution{LAMSADE, UMR 7243, CNRS and Universit\'e Paris Dauphine, PSL Research University}
+	\city{Paris}
+	\state{France}}
+\email{olivier.cailloux@dauphine.fr}
+
+\author{Paolo Viappiani}
+\affiliation{
+	\institution{LIP6, UMR 7606, CNRS and Sorbonne Universit\'e}
+	\city{Paris}
+	\state{France}}
+\email{paolo.viappiani@lip6.fr}
+
+%%% Use this environment to specify a short abstract for your paper.
+
 \begin{abstract}
@@
 
+%%% The code below was generated by the tool at http://dl.acm.org/ccs.cfm.
+%%% Please replace this example with code appropriate for your own paper.
+
+%%% Use this command to specify a few keywords describing your work.
+%%% Keywords should be separated by commas.
+
+\keywords{Uncertainty in AI, Computational Social Choice, Knowledge Representation and Reasoning}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%% Include any author-defined commands here.
+
+\newcommand{\BibTeX}{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em\TeX}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{document}
+
+%%% The following commands remove the headers in your paper. For final 
+%%% papers, these will be inserted during the pagination process.
+
+\pagestyle{fancy}
+\fancyhead{}
+
+%%% The next command prints the information defined in the preamble.
+
+\maketitle
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Introduction}
+
 Aggregation of preference information is a central task in many computer systems (recommender systems, search engines, etc).
@@
 
-Max regret $\MR(x;\pprofile,W)$ is the worst-case loss of $x$.
+Max regret $\MaxR(x;\pprofile,W)$ is the worst-case loss of $x$.
 That is the loss occurred as the result of an adversarial selection of the complete profile $\profile \in C(\pprofile)$ and of the scoring vector $\w \in W$ that together maximize the loss between $x$ and the true winner under $\profile$ and $\w$.
 \begin{align}
-\MR(x; \pprofile, W) & = \max_{y \in A} \PMR(x,y; \pprofile, W)\\
+	\MaxR(x; \pprofile, W) & = \max_{y \in A} \PMR(x,y; \pprofile, W)\\
 	& = \max_{\w \in W} \max_{\profile \in C(\profile)} \Regret(x, \profile, \w).
@@
 Finally,  $\MMR(\pprofile,W)$ is the value of minimax regret under $\pprofile$ and $W$, obtained when recommending a minimax optimal alternative $x^*_{\pprofile, W}$:
-\begin{align*}
-\MMR(\pprofile,W) & = \min_{x \in A} \MR(x;\pprofile,W) \\
-x^{*}_{\pprofile,W} \in A^*_{\pprofile, W} & = \argmin_{x \in A} \MR(x;\pprofile,W) 
-\end{align*}
+
+\begin{align}
+	\MMR(\pprofile,W) & = \min_{x \in A} \MaxR(x;\pprofile,W) \\
+	x^{*}_{\pprofile,W} \in A^*_{\pprofile, W} & = \argmin_{x \in A} \MaxR(x;\pprofile,W)
+\end{align}
 By picking as consensus choice
@@
 and we can rewrite $\PMR$ as follows:
-\begin{align*}
+
+\begin{align}
 	& \PMR(x,y; \pprofile, W) = \max_{\w \in W} \max_{\profile \in C(\pprofile)} [ s(y; \profile,\w) - s(x; \profile,\w) ] \\
 	& =  \max_{\w \in W} \sum_{j=1}^{n} \max_{v_j \in C(\succ_j^p)} [w_{v_j(y)} - w_{v_j(x)}]. \\
-\end{align*}
+\end{align}
 Note that in general the inner max depends on the weights chosen by the outer max.
@@
 The pairwise max regret $\PMR(x,y; \pprofile,W)$ can be obtained as the solution of the following linear program defined on the variables $w_1, …, w_m$, which represent the weights attached to different positions.
-\begin{align*}
+
+\begin{align}
 	\max_{\w} & \sum_{r=1}^m (\hat{\alpha}_{r}^{y} - \hat{\alpha}_{r}^{x}) w_{r}\\
 	\text{ s.t. } & \text{\cref{eq:monotone}} \text{ and } \text{\cref{eq:convexity}} \text{ and } \Co_W
-\end{align*}
+\end{align}
 Note that given our choice $w_{1}=1$ and $w_{m}=0$, there are only $m-2$ variables 
@@
 
-The max regret $\MR(x; \pprofile, W)$ is determined by considering the pairwise regret of $x$ with all other alternatives in $A$.
+The max regret $\MaxR(x; \pprofile, W)$ is determined by considering the pairwise regret of $x$ with all other alternatives in $A$.
 Optimal alternatives w.r.t. minimax regret are the ones with least max regret. 
@@
 
+\balance
+
 \section{Conclusions}  
@@
 % Acknowledgements: We thank the reviewers for comments helping to improve the paper.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%% The acknowledgments section is defined using the "acks" environment
+%%% (rather than an unnumbered section). The use of this environment 
+%%% ensures the proper identification of the section in the article 
+%%% metadata as well as the consistent spelling of the heading.
+
+%\begin{acks}
+%If you wish to include any acknowledgments in your paper (e.g., to 
+%people or funding agencies), please do so using the `\texttt{acks}' 
+%environment. Note that the text of your acknowledgments will be omitted
+%if you compile your document with the `\texttt{anonymous}' option.
+%\end{acks}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%% The next two lines define, first, the bibliography style to be 
+%%% applied, and, second, the bibliography file to be used.
+%\bibliographystyle{abbrvnat} 
+%\bibliography{biblio}
+
+\bibliographystyle{ACM-Reference-Format} 
 \bibliography{biblio}
-%\bibliographystyle{named}
-\bibliographystyle{abbrvnat} 
 \end{document}
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \appendix
-\section{Old table}
-\begin{table}
-	\begin{center}
-		\begin{tabular}{S[table-figures-integer=2, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
-			\toprule
-			{k} & {Rnd} & {sd} & {T. ph.} & {sd} & {Pes.} & {sd} & {Pes.} & {sd} \\
-			\midrule
-			0 & 4.0 & 0 & 4.0 & 0 & 4.0 & 0 & 4.0 & 0\\
-			5 & 3.40 & 0.40 & 3.86 & 0.13 & 2.63 & 0.28 & 2.63 & 0.28\\
-			10 & 2.59 & 0.75 & 2.63 & 0.39 & 1.29 & 0.50\\
-			15 & 2.37 & 0.33 & 0.92 & 0.76 & 0.43 & 0.50\\
-			20 & 1.23 & 1.04 & 0.15 & 0.23 & 0.09 & 0.27\\
-			25 & 0.90 & 0.80 & 0 & 0 & 0.25 & 0.75 \\
-			30 & 0.34 & 0.57 & 0.02 & 0 & 0 & 0\\
-			\bottomrule
-		\end{tabular}
-	\end{center}
-	\caption{Minimax regret in problems of size $(4, 4)$ after $k$ questions.}
-	\label{fig:44}
-\end{table}
-See \cref{fig:44}.
+\import{preamble/}{appendix.tex}
 
-\section{Bounding differences of weights}
-We want to check whether we can round PMR values to (for example) $10^{-4}$. Thus, we want to bound the difference of scores (unless it is zero).
-
-Consider $s(a) = w_2 + w_4$, $s(b) = w_3 + w_3$, $w_1 = 1, w_2 = w_3 + \epsilon, w_4 = 0$, with $w_3$ and $\epsilon$ two small positive numbers.
-Then convexity is satisfied and $s(a) - s(b) = \epsilon$.
-
-Note that in this example, $w_3 ≤ \epsilon$, thus the difference of scores is indeed at least the smallest weight!
-
-Consider $w_1 = 1, w_2 = 0.45, w_3 = 0.1, w_4 = 0$, $s(a) - s(b) = (w_2 - w_3) -3 (w_3 - w_4) = 0.35 - 0.30 = 0.05 < w_3$.
-
-Problem: we can make the difference of scores very small, even with $n=2$ agents and $m=3$ alternatives and while satisfying convexity.
-Consider $w_1 = 1, w_2 = \frac{1-\epsilon}{n}, w_3 = 0$, $s(a) - s(b) = (w_1 - w_2) - (n-1) (w_2 - w_3) = w_1 - n w_2 = \epsilon$.
-Choose $\epsilon < \frac{1}{n+1}$ so that $w_2 > \epsilon$ and $n ≥ 2$ to satisfy convexity.
-For example, $\epsilon = 1/1000, n = 2, w_2 = 999/2000$.
-
-\section{Minimax Computation under Convex Assumption} 
-Refer to \citep{Lu2011}
-The goal is to choose as a winner the alternative $x^*$ whose worst case loss is minimal under all possible realizations of the full profile and all possible choices of weights. 
-Assume hereinafter the selected weights sequence $\w \in W$ to be convex. 
-In order to compute the minimal max regret $\MMR(\pprofile)$ under partial profile $\pprofile$ we need to compute the pairwise max regret between all pairs of alternatives $(x,y)$, where $x$ is a proposed winner and $y$ is the ``adversary'' alternative.
-Indeed, the construction of $\PMR(x,y,\pprofile,\w)$ can be viewed as an adversary's attempt to maximize the regret of choosing $x$ instead of $y$.
-For doing this, he can choose a completion $\profile_i \in C(\pprofile_i)$ of the partial profile and a (feasible) scoring vector $\w$ that maximize the contribution of the agent $i$ to $\PMR(x,y,\pprofile,\w)$.
-Let us now analyze how it could be done depending on the relation between alternatives $x$ and $y$ in $\pprofile_i$.
-\begin{itemize}
-	\item $x \succ_i^\pprofile y$
-	\newline If we know $x$ is preferred to $y$ and we choose $x$ as a winner, $\pprofile_i$ contribution to $\PMR(x,y,\pprofile,\w)$ must be negative.
-In this situation, our adversary can only try to minimize this advantage by minimizing the positional gap between the two alternatives.
-To achieve that, he can arbitrary place all the alternatives preferred to $x$ above $x$, together with all the ones with unknown relation to $x$.
-Moreover, he can place all the alternatives less preferred to $x$ and with unknown relation to $y$ below $y$.
-We can summarize it for each $q \in A$ as follows:
-	\begin{align*}
-	q \succ_i^\pprofile x \vee q \ ?_i^\pprofile \ x \ & \Rightarrow \ \uparrow_x \\
-	x \succ_i^\pprofile q \wedge ( q \ ?_i^\pprofile \ y \vee y \succ_i^\pprofile q) \ & \Rightarrow \ \downarrow_y \\
-	x \succ_i^\pprofile q \succ_i^\pprofile y \ & \Rightarrow \ \text{in between} \\
-	\end{align*}
-	It is worth noting that when the relation between $q$ and $x$ is not known in the partial profile, the adversary takes advantage by placing $q$ above $x$ only under the assumption of convex weight sequences.
-	\item $y \succ_i^\pprofile x$
-	\newline If $y$ is preferred to $x$ the construction proceeds similarly to the previous case, but now the adversary takes advantage by maximizing the gap between $x$ and $y$ placing as much alternatives as he can between the two.
-We can summarize the procedure for each $q \in A$ as follows:
-	\begin{align*}
-	q \succ_i^\pprofile y \ & \Rightarrow \ \uparrow_y \\
-	x \succ_i^\pprofile q \ & \Rightarrow \ \downarrow_x \\
-	(y \succ_i^\pprofile q \vee y \ ?_i^\pprofile \ q) \wedge (q \succ_i^\pprofile x \vee q \ ?_i^\pprofile \ x) \ & \Rightarrow \ \text{in between} \\
-	\end{align*}
-	\item $x \ ?_i^\pprofile \ y$
-	\newline If the partial profile $\pprofile_i$ does not specify the relation between $x$ and $y$, the advantage is maximized by ordering $y$ over $x$ and maximizing the gap between them following the procedure for the case $y \succ_i^\pprofile x$.
-\end{itemize}
-
-\section{Dropping the Convex Assumption}
-\subsection{Profile completion}
-What if the sequence of weights is not convex?
-When $y \succ_i^\pprofile x$ or $x \ ?_i^\pprofile \ y$ weights do not influence the arbitrary placement of alternatives.
-Please remind we are working under the assumption that weights constitute a monotonic non-increasing sequence.
-Thus, there is no way for the adversary to take advantage from the weights distribution in order to increase the gap between $y$ and $x$ besides placing as much alternatives as he can between the two.
-The only case in which weights can influence the positional gap between $x$ and $y$ is when $x \succ_i^\pprofile y$ and $q \ ?_i^\pprofile \ x$.
-For convex sequences we place such alternatives $q$ above $x$, but it is not obvious that this is the best option for other sequences.
-For example, suppose $x$ and $y$ are ranked respectively in first and second position in the partial profile and we wonder where to place an alternative $q$ with unknown relation to $x$ (and thus to $y$).
-Suppose also that in the weight sequence the distance between the first and second positions is much lower than the one between the second and the third ones.
-In this case, placing $q$ above $x$ does not minimize the gap between $x$ and $y$ but we want, instead, to place $q$ below $y$.
-\newline The constraints expressed by the chair may result in a set of feasible vectors such that none of them forms a convex sequence.
-In this case we need to analyze the particular sequence of weights in order to decide how to maximize the adversary advantage.
-Before going into details, let us define $A$ as the set of alternatives (if any) preferred to $x$, $B$ as the set of alternatives preferred to $y$ but not to $x$, and $U$ the set of those with unknown relation to both $x$ and $y$.
-The idea is to determine the positions that minimize $x$'s advantage over $y$ and then place some of the alternatives in $U$ above $x$ and some below $y$ in order to get that desired ranking.
-Since we cannot change the order of the alternatives in the set $B$ we know that $x$ and $y$ are separated exactly by $|B|$ positions (the adversary would not take any advantage by adding alternatives between them).
-So, starting from the position of $x$ in the partial completion of $\pprofile_i$ computed so far ($\hat{\profile}_i$), we find the two positions separated by $|B|$ alternatives whose weights difference is the lowest.
-Note that we can only add $|U|$ alternatives so we can check only until the position $\hat{\profile}_i(x)+|U|$.
-Algorithm \ref{alg:splittingU} shows the procedure described.
-
-It is easy to see that we check at most $|U|$ positions.
-In the worst case the size of $U$ is equal to $m-2$, thus the procedure can be computed in $O(m)$ time.
-This cost does not affect the minimax regret computation time complexity that remains $O(nm^3)$.
-
-\begin{algorithm}[h] 
-	\caption{Placing alternatives in $U$ without Convex Assumption}
-	\label{alg:splittingU} 
-	\begin{algorithmic}
-		\Require $x$, $y$, $\hat{\profile}_i$, $\w$, $U$, $B$
-		\Ensure $\profile_i \in C(\pprofile)$
-		\Statex
-		\State $ j \gets 0$;
-		\State $ i \gets \hat{\profile}_i(x)$;
-		\State $ \mathit{posmin} \gets i$;
-		\State $ \mathit{min} \gets \w(i) - \w(i+1+|B|)$;
-		\While {$( j \leq |U| )$}
-		\If{ $(\w(i+j)-\w(i+1+|B|+j) < \mathit{min})$ }
-		\State $ \mathit{min} \gets \w(i+j) - \w(i+1+|B|+j)$;
-		\State $ \mathit{posmin} \gets i+j$;
-		\EndIf
-		\EndWhile
-
-		\State $U_{\mathit{abovex}} \gets (i-\mathit{posmin}) \text{ alternatives} \in U $;
-		\State $U_{\mathit{belowy}} \gets U \setminus U_{\mathit{above}}$;
-		\Statex
-		\State $\profile_i \gets place(\pprofile_i,U_{\mathit{abovex}},U_{\mathit{belowy}})$;
-		\Statex \Return $\profile_i$
-
-	\end{algorithmic}
-\end{algorithm}
-
-\section{Minimax regret without the convex assumption}
-Without the convex assumption, we cannot use $\hat{v}$ for the agents in $U^{-}$, but only for agents in $U^{+}$ and $U^{?}$.
-%Let $\hat{v}_i$ be the linear order extending $\succ^{p}_i$ according to the above procedure.
-Then PMR can be written as follows:
-\begin{align*}
- &\PMR(x,y; \pprofile, W) =\\ 
- &\max_{\w \in W} \Big \{ \sum_{j \in U^-} [\max_{v_j \in C(\succ_j^p)} [w_{v_j(y)} \!-\! w_{v_j(x)}]] 
-  \!+\!	 \sum_{j \in A^+ \cup  U^?} [w_{\hat{v}_j(y)} \!-\! w_{\hat{v}_j(x)}] \Big \} 
- \end{align*}
-%Note that the second addendum inside the max do not depend on the choice of $\w$.
-Consider the two addenda inside the ``max''. 
-The first addendum is concerned with positioning of alternatives $x$ and $y$ for agents in $U^{-}$ for which we know that $x$ is preferred to $y$.
-The second addendum is concerned with agents in $U^{+}$ and $U^{?}$.
-We rewrite the second addendum as:
-\begin{align*}
-\sum_{j \in U^+ \cup  U^?} [w_{\hat{v}_j(y)} \!-\! w_{\hat{v}_j(x)}] 
-= \sum_{i = 1}^{m} (\hat{\alpha}_{i}^{y} - \hat{\alpha}_{i}^{x}) w_{i}
-\end{align*}
-where $\hat{\alpha}_{i}^{x}$ is the number of times that $x$ is ranked  in position $i$  considering the profile $\hat{v}$ of agents in $U^+ \cup  U^?$.
-%We compute pairwise maximum regret by considering binary variables $\{ B_{i} \}_{i=1,\ldots,m}$ to represent optimization choices related to where to position the alternatives.
-
-We now address the agents in $A^{-}$
-For a given $j$, let $\beta$ be the number of alternatives that are incomparable with $x$ and $y$:
-\[ \beta_{j} = \mid \{ c : c \prefinc_{j} y \wedge c \prefinc_{j} x \} \mid \]
-$x$ can be ranked between $t_{1}(j)=\mid \{ c \in A : c \ppref_{j} y \wedge x \nppref_{j} c \} \mid $ and position $t_{2}(j)=t_{1}(j)+\beta_{j}$.
-The completion for agent $j$ is such that the positions of $x$ and $y$ differ of exactly $\gamma_{j} =
-\mid \{ c \in A : x \ppref c \ppref y \} \mid$ positions.
-
-We now show how to optimize $\PMR$.
-In addition to variables $\{ w_{j} \}_{j=1,\ldots,m}$ (one for each position) we need to employ several additional decision variables.
-We introduce two sets of binary variables $B^{+}_{i,j}$ and $B^{-}_{i,j}$  for each position $i$ and for each agent $j$.
-Variable $B_{i,j}^{+}$ encodes the fact that the alternative $y$ is placed in position $i$ in the ranking of agent $j$; while  $B_{i,j}^{-}$ encodes the same thing for alternative $x$.
-%We also have numerical variables to represent the weights of the scoring rule.
-Since each alternative needs to be placed exactly in one place for each agent, we adopt the constraints
-$\sum_{i=t_{1}(j)}^{t_{2}(j)} B_{i,j}^{+} = 1$.
-Since we know that $x$ and $y$ are ranked $\gamma_{j}$ positions apart, we set the constraint:
-$B_{i+\gamma_{j},j}^{-} \geq B_{i,j}^{+}$,  for $i = \{ t_{1}(j), \ldots, t_{2}(j)\}$.
-
-% and $\sum_{i=1}^{m} B_{i,j}^{-} = 1$.
-%Since the objective is to maximize pairwise regret...
-
-The score of alternative $y$ can be written as $\sum_{i = 1}^{m} \hat{\alpha}_{i}^{y}  w_{i} + \sum_{i=1}^{n} \sum_{j=1}^{m} w_{j} B_{i,j}^{+}$.
-The objective function is now:
- \[ \max \sum_{i = 1}^{m} (\hat{\alpha}_{i}^{y} - \hat{\alpha}_{i}^{x}) w_{i} +  \sum_{i=1}^{n} \sum_{j=1}^{m} (B_{i,j}^{+} - B_{i,j}^{-})  w_i \]
-
-We use integer programming enconding tricks in order to linearize the problem.
-We introduce yet another set of variables  $V_{i,j}^{+} $  and $V_{i,j}^{-}$ % the multiplicative terms by new variables.
-and we enforce that $V_{i,j}^{+} = B^{+}_{i,j} w_i$ by setting constraints $V_{i,j}^{+} \leq B^{+}_{i,j}$ and $V_{i,j}^{+}  \leq w_i$.
-We have similar constraints for enforcing $V_{i,j}^{-} = B^{-}_{i,j} w_i$.
-
-We therefore obtain the following mixed integer linear program:
-\newcommand{\C}{\mathcal{C}}
-\begin{align}
-\max & \sum_{i=1}^m  [(\hat{\alpha}_{i}^{y} - \hat{\alpha}_{i}^{x}) w_{i}] +
-  \sum_{j \in A^{-}} \sum_{i=t_{1}}^{t_{2}}  [V_{i,j}^{+} - V_{i,j}^{-}]
-\end{align}
-\begin{align}
-\text{ s.t. } &  \text{Equation } (\ref{eq:monotone}) & \\
-&  \C(\w) &  \\
-& \sum_{i=t_{1}}^{t_{2}} B_{i,j}^{+} = 1 & \forall j \in A^{-} \\
-& B_{i+\gamma_{j},j}^{-} \geq B_{i,j}^{+} & \forall i \in \{ t_{1}, \ldots t_{2}\}, \forall j \in A^{-} \\
-& V_{i,j}^{+} \leq B_{i,j}^{+}  & \forall i \in \{ t_{1}, \ldots t_{2}\}, j \in A^{-} \\
-& V_{i,j}^{+} \leq w_i & \forall i \in \{ t_{1}, \ldots t_{2}\}, j \in A^{-} \\
-& V_{i,j}^{-} \geq w_{i} + B_{i,j}^{-} - 1 & \forall i \in \{ t_{1}, \ldots t_{2}\}, j \in A^{-}\\
-& V_{i,j}^{-} \geq 0 & \forall i \in \{ t_{1}, \ldots t_{2}\}, j \in A^{-}
-\end{align} 
-%We write $w \in W$ as a shourtcut to represent the constraints that the weights are chosen to be in the feasible set.
-There are (at most) $nm$ binary variables and $m(n+1)$ numerical variables.
-The optimization program can be solved by any suitable MILP solver, although it is not suitable to large problem instances.
-
-% DONT KNOW IF WE HAVE TO FORMALIZE THIS AS A CLAIM
-%\begin{claim}
-%The $\PMR$ is computed using the above optimization problem.
-%\end{claim}
-
-\section{Considerations on weights}
-\label{sec:weights}
-Let us consider a monotonic non-increasing sequence of weights: $w_{1} \geq w_{2} \geq \ldots \geq w_{m}$. Without loss of generality, we can assume $w_1=1$ and $w_m=0$.
-
-\begin{claim}
-	\label{clm:wsequence}
-	If the weight sequence is convex then $w_{1} > w_{2}$.
-	\[\forall i \in \{1,\ldots,m\} \;\; w_i - w_{i+1} \geq w_{i+1}-w_{i+2} \Rightarrow w_{1} > w_{2} \geq \ldots \geq w_{m}\] 
-\end{claim}
-\begin{proof}
-	By contradiction let assume $w_{1} = w_{2}$ then 
-	\begin{align*}
-	w_{1} - w_{2} \geq w_{2} - w_{3} &\geq \dots \geq w_{m-1} - w_{m} \\
-	1 - 1 \geq 1 - w_{3} &\geq \dots \geq w_{m-1} - 0 \\
-	0 \geq 1 - w_{3} &\geq \dots \geq w_{m-1}
-	\end{align*}
-	At this point either $0\leq w_{3}<1$ or $w_{3}=1$. In the first case 
-	\[0 \ngeq 1 - w_{3}\]
-	This breaks the convexity assumption so it is impossible.
-	In the second case, by definition there is a $w_{i} \neq 1$ where $2 < i \leq m$. So it would be 
-	\[0 \ngeq 1 - w_{i}\]
-	for some $i$. Again, the convexity is not satisfied.
-\end{proof}
-
-\begin{corollary}
-	\label{cor:weq}
-	If the weight sequence is convex and $w_{i} = w_{i+1}$ for some $i$, then $w_{j}=0 \ \forall \
-	j=i, \dots m$.
-\end{corollary}
-
-\section{Querying the chair}
-Suppose our query strategy suggests us to ask the chair the following query:
-\[ w_{2} - w_{3} \geq 2(w_{3} - w_{4}) \]
-Then we can transform it in:
-\begin{align}
-\label{eqn:juryquery}
-w_{2} - w_{3} &\geq 2 \cdot w_{3} - 2 \cdot w_{4} \notag \\
-w_{2} + 2 \cdot w_{4} &\geq 3 \cdot w_{3} 
-\end{align}
-and ask the chair if they would prefer as a winner an alternative ranked first one time and third three times rather than an alternative ranked second four times.
-
-Another way to query the chair, a more concrete one, is to present them a profile representing the situation described by the query and then deduce its answer from the selected winner.
-Obviously we have to be sure to choose a profile where only the alternatives we are interested in could be pick as winners.
-Therefore, we need a systematic way to construct a profile that reflects the situation outlined by the query for two alternatives and the others are not better than them.
-
-Assume we have a profile of $3$ agents ranking $4$ alternatives. We can represent it by columns where each of them represents the preference ordering of one agent.
-\[
-\begin{array}{ccc}
-v_1
-& v_2
-& v_3 \\
-\midrule 
-c
-& d
-& c \\
-a
-& c
-& d \\
-b
-& b
-& b \\
-d
-& a
-& a \\
-\end{array}
-\]
-
-Assuming anonymity, we can also write the profile expressing for each alternative $i \in A$ the number of agents placing it at a given rank.
-
-\[
-\begin{array}{ccccc}
-& 1^\circ
-& 2^\circ
-& 3^\circ
-& 4^\circ \\
-\cmidrule{2-5}
-a 
-& 0
-& 1
-& 0
-& 2 \\
-b
-& 0
-& 0
-& 3
-& 0 \\
-c
-& 2
-& 1
-& 0
-& 0 \\
-d
-& 0
-& 1
-& 1
-& 1 \\
-\end{array}
-\]
-
-Recalling the query (\ref{eqn:juryquery}) we are considering as an example, it is easy to see that in the current profile alternatives $a$ and $b$ represent the situation as described by the query.
-Therefore, if after proposing this profile to the chair the winning alternative turns out to be $a$ then we know that $w_{2} - w_{3} > 2(w_{3} - w_{4})$; if, instead, the winner is $b$ we know that $w_{2} - w_{3} < 2(w_{3} - w_{4})$ and if both alternatives are picked as winners then $w_{2} - w_{3} = 2(w_{3} - w_{4})$.
-
-Nevertheless, in this example it is clear that $c$ will always be preferred to other alternatives (see Claim \ref{clm:wsequence} in Section \ref{sec:weights}).
-To see it we can express for each alternative the number of agents placing it at a given rank or at a higher one.
-
-\[
-\begin{array}{ccccc}
-& \geq 1^\circ
-& \geq 2^\circ
-& \geq 3^\circ
-& \geq 4^\circ \\
-\cmidrule{2-5}
-a 
-& 0
-& 1
-& 1
-& 3 \\
-b
-& 0
-& 0
-& 3
-& 3 \\
-c
-& 2
-& 3
-& 3
-& 3 \\
-d
-& 0
-& 1
-& 2
-& 3 \\
-\end{array}
-\]
-
-\begin{claim}
-	Consider a set $A$ of $m$ alternatives and let $r_k(i)$ be the number of times the alternative $i$ obtains a rank $k$ or a higher one.
-Consider two alternatives $ i,j \in A$, if $\forall \ k=2, \dots,m \ r_k(i)\geq r_k(j)$ and $r_1(i) > r_1(j)$ then $i$ is always preferred to $j$ for any choice of weights.
-\end{claim}
-
-\begin{proof}
-	For our assumptions we know the sequence of weights is monotonic non-increasing and convex.
-Moreover, for the Claim \ref{clm:wsequence} in Section \ref{sec:weights}, we know that $w_1 > w_2$.
-Therefore, even in the worst case where $r_k(i) = r_k(j) \ forall \ k=2, \dots,m$ the sum of weights for alternative $i$ cannot be lower than the one for $j$.
-It is worth noting that we cannot say anything when $r_1(i) = r_1(j)$.
-Indeed, as said in Corollary \ref{cor:weq}, all the weights for other position but the first one can be equal, thus the number of agents ranking the alternatives at a certain position does not matter anymore.
-\end{proof}
-
-So the strategy for querying the chair is to use two alternatives $i$ and $j$ to represent the query and complete the profile such that the other alternatives are all dominated by them.
-An algorithmic approach is to start from the initial profile and then add as many agents as needed that rank $i$ and $j$ as their top choices and the other alternatives afterwards.
-As an example let consider again the query \ref*{eqn:juryquery}.
-We want the committee to choose between $a$ or $b$:
-
-\[
-\begin{array}{ccccc}
-& 1^\circ
-& 2^\circ
-& 3^\circ
-& 4^\circ \\
-\cmidrule{2-5}
-a 
-& 0
-& 1
-& 0
-& 2 \\
-b
-& 0
-& 0
-& 3
-& 0 \\
-\end{array}
-\]
-
-We add agents in order to increase the number of times $a$ and $b$ are ranked at first position.
-Please note we must maintain these scheme, so every add of a position to the ranking of $a$ must correspond to the same in the ranking of $b$.
-
-\[
-\begin{array}{cccccc}
-v_1
-& v_2
-& v_3 
-& v_4
-& v_5
-& v_6 \\
-\midrule 
-a
-& b
-& c 
-& d
-& a
-& b \\
-c
-& a
-& d
-& c
-& b
-& a \\
-b
-& d
-& b
-& b
-& d
-& c \\
-d
-& c
-& a
-& a
-& c
-& d \\
-\end{array}
-\]
-
-\[
-\begin{array}{ccccc}
-& 1^\circ
-& 2^\circ
-& 3^\circ
-& 4^\circ \\
-\cmidrule{2-5}
-a 
-& 2
-& 2
-& 0
-& 2 \\
-b
-& 2
-& 1
-& 3
-& 0 \\
-c
-& 1
-& 2
-& 1
-& 2 \\
-d
-& 1
-& 1
-& 2
-& 2 \\
-\end{array}
-\]
-
-\[
-\begin{array}{ccccc}
-& \geq 1^\circ
-& \geq 2^\circ
-& \geq 3^\circ
-& \geq 4^\circ \\
-\cmidrule{2-5}
-a 
-& 2
-& 4
-& 4
-& 6 \\
-b
-& 2
-& 3
-& 6
-& 6 \\
-c
-& 1
-& 3
-& 4
-& 6 \\
-d
-& 1
-& 2
-& 4
-& 6 \\
-\end{array}
-\]
-\textbf{Remarks:}
-\begin{itemize}
-	\item We are considering $\lambda \in \mathbb{N} \setminus \{0\}$ but we could be interested in a real number. \textit{Solution}: we can multiply both sides.
-\end{itemize}
-\fi
-\end{document}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2020-09-08 AAMAS2021/preamble/appendix.tex
paper conform to aamas formatting

--- 2020-01-23 draft.tex
@@
-\input{ijcai_preamble} 
-\author{ID: 7094}
-%\author{Beatrice Napolitano$^1$\and Olivier Cailloux$^1$	\and  Paolo Viappiani$^{2}$
-%	\affiliations $^1$ LAMSADE, UMR 7243, CNRS and Universit\'e Paris Dauphine, PSL Research University, Paris, France\\ $^2$ LIP6, UMR 7606, CNRS and Sorbonne Universit\'e, Paris, France
-%	\emails \{firstname.lastname\}@dauphine.fr, paolo.viappiani@lip6.fr
-%}
-%Restoring page numbers as missing them out violates basic human rights of the reviewers. -- Olivier
-\thispagestyle{plain}
-\pagestyle{plain}
-
-\usepackage[T1]{fontenc}
-\usepackage[utf8]{inputenc}
-\usepackage{newunicodechar}
-\usepackage{textcomp}
-%\newunicodechar{⇒}{\implies}
-\newunicodechar{⇒}{\Rightarrow}
-\newunicodechar{≠}{\ensuremath{\neq}}
-\newunicodechar{≤}{\leq}
-\newunicodechar{≥}{\geq}
-%… Horizontal Ellipsis
-\DeclareUnicodeCharacter{2026}{\ifmmode\dots\else\textellipsis\fi}
-\newunicodechar{∧}{\land}
-\newunicodechar{∨}{\lor}
-\newunicodechar{∩}{\cap}
-\newunicodechar{∪}{\cup}
-%¬ Not Sign
-\DeclareUnicodeCharacter{00AC}{\ifmmode\lnot\else\textlnot\fi}
-\newunicodechar{⇔}{\Leftrightarrow}
-\newcommand{\N}{ℕ}
-\newunicodechar{ℕ}{\mathbb{N}}
-\usepackage{algorithm, algpseudocode}
-\usepackage{amsmath,amssymb,enumerate,amsthm}
-\usepackage{natbib}
-\usepackage[strict]{siunitx}
-\usepackage{hyperref}
-\usepackage{mathrsfs}
-
-\usepackage{bm}
-\usepackage{empheq}
-\usepackage{cleveref}
-\usepackage{xcolor}
-
-\newcommand{\email}[1]{\href{mailto:#1}{#1}}
-\newcommand{\denselist}{\itemsep -2pt\topsep-6pt\partopsep-6pt}
-\newcommand{\commentOC}[1]{\textcolor{blue}{\small$\big[$OC: #1$\big]$}}
-\newcommand{\commentBN}[1]{\textcolor{red}{\small$\big[$BN: #1$\big]$}}
-
-\newcommand{\pref}{\succ}%real, connected pref, strict
-\newcommand{\prefeq}{\succeq}%real, connected pref, strict
-\newcommand{\prefr}{{\succ}^\text{r}}%real, connected pref, strict
-\newcommand{\pprefeq}{\succeq^\text{p}}%partial pref
-\newcommand{\ppref}{\succ^\text{p}}%partial pref
-\newcommand{\pprefinv}{\prec^\text{p}}%partial pref
-\newcommand{\nppref}{\nsucc^\text{p}}%negated partial pref
-\newcommand{\linors}{\mathcal{L}(A)}
-%https://tex.stackexchange.com/a/45732, works within both \set and \set*, same spacing than \mid (https://tex.stackexchange.com/a/52905).
-\newcommand{\suchthat}{\;\ifnum\currentgrouptype=16 \middle\fi|\;}
-
-%Thanks to https://tex.stackexchange.com/q/154549
-\makeatletter
-\newcommand{\newrelation}[2]{% #1 = control sequence, #2 = replacement text
-  \@ifdefinable{#1}{%
-    \def#1{%
-    \@ifnextchar_{\csname\string#1\endcsname}{\mathrel{#2}}%
-    }%
-    \@namedef{\string#1}##1##2{\mathrel{#2_{##2}}}%
-  }%
-}
-\makeatother
-
-\newrelation{\prefinc}{\!\parallel\!}%partial pref, complement (incomparable)
-\newrelation{\pinc}{\bowtie^\text{p}}
-%\newrelation{\prefinc}{Q^\text{p}}%partial pref, complement (incomparable)
-
-\newcommand{\profile}{\bm{v}}%(complete) profile
-\newcommand{\pprofile}{{\bm{p}}}%partial profile
-\newcommand{\w}{\bm{w}}
-\newcommand{\W}{\mathcal{W}}
-\newcommand{\Co}{\mathcal{C}}
-\newcommand{\pw}{W}%our knowledge about the weights
-\newcommand{\powersetz}[1]{\mathscr{P}^*(#1)}
-\newcommand{\strat}[1]{\emph{#1}}
-
-\DeclareMathOperator{\Regret}{Regret}
-\DeclareMathOperator{\SCORE}{Score}
-\DeclareMathOperator{\PMR}{PMR}
-\DeclareMathOperator{\MR}{MR}
-\DeclareMathOperator{\MMR}{MMR}
-\DeclareMathOperator{\leximax}{leximax}
-\DeclareMathOperator*{\argmax}{argmax}
-\DeclareMathOperator*{\argmin}{argmin}
-
-\newtheorem{claim}{Claim}
-\newtheorem{prop}{Proposition}
-\newtheorem{corollary}{Corollary}
-\newtheorem{definition}{Definition}
-\newtheorem{example}{Example}
-
-\DeclarePairedDelimiter\set{\{}{\}}
-\DeclarePairedDelimiter\card{\lvert}{\rvert}
-\DeclarePairedDelimiter\abs{\lvert}{\rvert}
-
-\tolerance=2000
-%Accept overfull hbox up to...
-\hfuzz=1cm
-%Reduces verbosity about the bad line breaks.
-\hbadness 10000
-%Reduces verbosity about the underful vboxes.
-\vbadness=10000
-
-\title{Simultaneous Elicitation of Scoring Rule and Agents Preferences for Robust Winner Determination}
-
-\begin{document}
-\maketitle
-\begin{abstract}
-Social choice deals with the problem of determining a consensus choice from the preferences of different agents (voters).
-In the classical setting, the voting rule is fixed beforehand and full information concerning the preferences of the agents is provided.
-Recently, the assumption of full preference information has been questioned by a number of researchers and several methods for eliciting preferences have been proposed.
-In this paper we go one step further and we assume that both the voting rule and the agents preferences are partially specified.
-Focusing on positional scoring rules, we assume that the chair, while  not able to give a precise definition of the rule, is capable of answering simple questions  requiring to pick a winner from a specific  example profile.
-Moreover, the preferences of the agents are incrementally acquired by asking comparison queries.
-In this setting, we propose a method  for robust approximate winner determination with minimax regret.
-We also provide an interactive elicitation protocol based on minimax regret and develop several query strategies that interleave questions to the chair and questions to the agents in order to attempt to acquire the most relevant information in order to quickly converge to optimal or a near-optimal alternative.
-\end{abstract}
-
-\section{Introduction}
-Aggregation of preference information is a central task in many computer systems (recommender systems, search engines, etc).
-In many situations, such as in group recommender systems, the goal is to find a consensus choice.
-It is therefore natural to look at methods from social choice and see how they can be adapted for group decision-making in a computerized setting.
-
-The traditional approach to social choice assumes that both the social choice function and the full preference orderings of the agents are expressed beforehand. These represent two strong hypothesis.
-Requiring agents to express full preference orderings can be prohibitively costly (in terms of cognitive and communication cost).
-This observation has motivated a number of recent works considering social choice with partial preference orders \citep{Xia2008, Pini2009, Konczak05} and incremental elicitation \citep{Kalech2011, Lu2011, Naamani-Dery2015} of agents’ preferences.
-\\ Furthermore, it is often difficult for non-expert users to formalize a voting rule on the basis of some generic preferences over a desired aggregation method.
-Thus, the first hypothesis should also be relaxed.
-%Also the first hypothesis should be relaxed considering that, in several situations, it may not be easy to precisely define the voting rule.Indeed, it is possible that the chair has some preferences over the desired aggregation method, but is not able to formalize the voting rule upfront.
-The work of \citet{Cailloux2014} provides elicitation methods for a quite general class of rules based on weak orders.
-When considering positional scoring rules, several authors \citep{Stein1994, Llamazares2013, Viappiani2018} have worked on positional scoring rules with uncertain weights, assuming that the preferences of the agents are fully known.
-%it is possible to derive dominance relations (akin to stochastic dominance) that allow to eliminate some alternatives since they will be less preferred than another one for any instantiation of the weights \citep{Stein1994}.
-%Among others, Llamazares and Pe{\~{n}}a have considered  the problem of dealing with underspecified weights in positional scoring rules.
-
-In this paper we focus on positional scoring rules, that are a particularly common method used to aggregate rankings, and we assume that both the agents’ preferences and the social choice rule are partially specified.
-We develop methods for computing the minimax-optimal
-alternative using positional scoring rules and we provide incremental elicitation methods to acquire relevant preference information.
-We then discuss several heuristics that determine queries, either to an agent or to the chair, that quickly reduce minimax regret.
-While previous works have considered either partial information about the agents’
-preferences or a partially specified aggregation method, we do not know of any work considering both sources of uncertainty at the same time.
-
-%In this paper we consider that both the agents’ preferences and the social choice rule are partially specified and we develop methods for computing the minimax-optimal alternative under these assumptions.
-%changed from: We develop methods for computing the minimax-optimal alternative for scoring rules with partial agent preference information and partial information about the weights of the scoring rule.
-
-%We also address the problem of elicitation, providing incremental elicitation methods to acquire relevant preference information.
-We then discuss several heuristics that attempt to simultaneously reduce the preference and voting rule uncertainty by determining queries, either to an agent or to the chair, that quickly reduce minimax regret.
-%In particular, our query strategies focus simultaneously on reduction of relevant preference and voting rule uncertainty.
-
-The paper is organized as follows.
-In Section \ref{sec:background} we provide the necessary background and in Section \ref{sec:mmr} we introduce the minimax criterion, that selects a winner that minimizes the worst possible regret.
-Then, in Section \ref{sec:elicit} we provide an interactive elicitation protocol based on minimal regret;  in Section \ref{sec:experiments} we present the empirical validation of our approach with simulations; and Section \ref{sec:conclusions} provides some final thoughts.
-
-\section{Social choice with partial information}
-\label{sec:background}
-We now introduce some basic concepts.
-We consider a set $A$ of $m$ alternatives (products, restaurants, movies, public projects, job candidates, etc.) and a set $\set{1, …, n}$ of agents (voters).
-Each agent $j$ comes from an infinite set $\N$ of potential agents and is associated to her “real” preference order $\pref_j \in \linors$ which is a linear order (a connected, transitive, asymmetric relation) over the alternatives.
-Following the social choice nomenclature, we call {\em profile} the association of a preference to each agent, considering a subset of agents from the set $\N$, and denote a profile by $(\pref_1,\ldots,\pref_n)$.
-A profile is equivalently represented by $\profile=(v_1,\ldots,v_n)$ where $v_j(i) \in \set{1, \ldots, m}$ denotes the rank (position) of alternative $i$ in the preference order $\pref_j$.
-
-Let $V$ be the set of possible preference profiles (the union, for any integer, $n$ of the $n$-fold cartesian product of the linear orders over the alternatives).
-A social choice function $f : V \rightarrow \powersetz{A}$ associates a profile with a set of winners, where $\powersetz{A}$ represents the set of subsets of $A$ except for the emptyset.
-(Sets are used for tied winners.)
-Among the many possible social choice functions, we consider {\em positional scoring rules (PSR)}, which attach weights to positions according to the vector $(w_1, \ldots, w_m)$ (also called the scoring vector).
-An alternative obtains a score that depends on the rank obtained in each of the preference orders:
-\begin{align}
-\label{eq:srule}
-s(x; \profile, \w) = \sum_{j=1}^{n} w_{v_j(x)}
-= \sum_{r=1}^{m} \alpha^{x}_r w_r 
-\end{align}
-where $\alpha^{x}_r$ is the number of times that alternative $x$ was ranked in the $r$-th position.
-The winners are the alternatives gighest scores.
-
-In this work we assume fixed, but unknown to us, a profile $\profile^*$, representing the preferences $\pref_j^*$ of the agents, and a weight vector $\w^*$, representing the preferences of the chair, and we want to reason about partial preference information concerning those objects.
-At a given time, our knowledge of agent $j$'s preference is encoded by a partial order over the alternatives, thus a transitive and asymmetric binary relation, denoted by $\ppref_j$. 
-In this work we assume that preference information is truthful, i.e. $a \ppref_j b ⇒ a \pref_j^* b$.
-%We use $\prefinc$ to denote incomparability, that is $a \prefinc_{j} b$ iff $a \nppref_j b \wedge b \nppref_j a$.
-An incomplete profile $\pprofile = (\ppref_1, \ldots, \ppref_n)$ maps each agent to a partial preference.
-
-A completion of $\ppref_j$ is any linear order $\pref$ that extends $\ppref_j$ and we indicate with $C(\ppref_j) = \set{{\succ} \in \linors \suchthat {\ppref_j} \subseteq {\succ}}$ the set of possible completions of $\ppref_i$.
-Then $C(\pprofile)=C(\ppref_1)\times … \times C(\ppref_n)$ is the set of complete profiles extending $p$. Note that $\profile^* \in C(\pprofile)$.
-
-We also assume that the weights of the scoring rule are only partially specified.
-Therefore, the vector $(w_1,\ldots,w_m)$  is not known but we are given a set of constraints restraining the possible values that weights can take.
-We consider a decreasing sequence of weights:
-\begin{align}
-1=w_{1} ≥ w_{2} ≥ \ldots ≥ w_{m}=0. \label{eq:monotone}
-\end{align}
-This is a natural assumption, as it is better to be ranked first than second, second than third, etc. 
-Without loss of generality, we consider that $w_1=1$ and $w_m=0$.
-
-The weights of a scoring rule can model different preferences of the chair. 
-For instance, the weights can control the inclination to favor ``extreme'' alternatives (often at either the top or the bottom of the input rankings) at the expenses of ``moderate'' alternatives (that are more consistently in the middle part of the input rankings).
-
-An important class of scoring rule is the one composed of weights that represent a convex sequence \citep{Stein1994,Llamazares2016}, meaning that the difference between the weight of the first position and the weight of the second position is at least as great as the difference between the weights of the second and third positions, etc.
-\begin{equation} 
-\label{eq:convexity}
-\forall r \in \{1,\ldots,m-2\}: w_r - w_{r+1} \geq w_{r+1}-w_{r+2}.
-\end{equation}
-The constraint above is often used when aggregating rankings in sport competitions.
-We use $\W$ to denote the set of convex weight vectors.
-
-In general it can be difficult to set the weights in an appropriate way.
-We assume that in addition of basic requirements (monotonicity and convexity), the chair (the person or the organization that is supervising the voting process) is able to specify additional preferences about how the social choice function should behave.
-In this work we assume that the preferences of the chair are encoded with linear constraints about the vector $\w$, relating the value of the weights of different positions, and the set of these constraints is denoted by $\Co_W$.
-Moreover, we use $\pw \subseteq \W$ to denote the set of weight vectors compatible with the preferences expressed by the chair about the scoring vector.
-
-Of course it may be difficult for real decision makers to state preferences about the voting rule in such an abstract way.
-These additional preferences can be elicited by asking questions about concrete profiles, for instance, by showing a complete profile of a small synthetic election and asking who should be elected in this case, as shown in Section \ref{sec:elicit}.
-
-\section[Minimax regret under partial profile and weight information]{
-Robust winner determination}
-\label{sec:mmr}
-In this paper, we consider a setting where both the agents' preferences and the preferences of the chair about the voting rule are incomplete.
-Some authors have considered possible and necessary winners assuming a partial profile  \citep{Xia2008} or assuming an incompletely specified scoring rule \citep{Viappiani2018};
-however, we note that, in typical settings, there are no necessary winner and too many possible winners.
-In practice it is often useful to declare a winner given partial information.
-
-As a decision criterion to determine a winner, we propose to use minimax regret. 
-Minimax regret \citep{Savage1954} is a decision criterion that has been used for robust optimization under data uncertainty \citep{Kouvelis1997} as well as in decision-making with uncertain utility values \citep{Salo2001,Boutilier2006}.
-\citet{Lu2011} have adopted minimax regret for winner determination in social choice with
-the preferences of the agents that are only partially known, while the social choice function is predetermined and known.
-
-In this work, we consider the simultaneous presence of uncertainty in agents' preferences and in weights.
-Using {\em maximum regret} to quantify the worst-case error, the alternatives that minimize this error are selected as tied winners, providing us with a form of robust optimization.
-Intuitively, the quality of a proposed alternative $a$ is how far $a$ is from the optimal one in the worst case, given the current knowledge.
-
-The maximum regret is considered by assuming that an adversary can both 1) extend the partial profile $\pprofile$ into a complete profile, and 2) instantiate the weights choosing among any weight vector in $\pw$, where $\pprofile$ and $\pw$ represent our knowledge so far.
-We formalize the notion of minimax regret in multiple steps.
-First of all, $\Regret(x, \profile, \w)$ is the “regret” of selecting $x$ as a winner instead of choosing the optimal alternative under $\profile$ and $\w$:
-\[\Regret(x, \profile, \w) = \max_{y \in A} s(y; \profile,\w) - s(x; \profile, \w).\]
-The pairwise max regret $\PMR(x,y;\pprofile,W)$ of $x$ relative to $y$ given partial profile $\pprofile$ and the set of weights $W$
-is the worst-case loss of choosing $x$ instead of $y$ under all possible realizations of the full profile {\em and} all possible instantiations of the weights:
-\begin{align*}
-\PMR(x,y; \pprofile, W) & = \max_{\w \in W} \max_{\profile \in C(\pprofile)} s(y; \profile,\w) - s(x; \profile,\w).
-\end{align*}
-
-Max regret $\MR(x;\pprofile,W)$ is the worst-case loss of $x$.
-That is the loss occurred as the result of an adversarial selection of the complete profile $\profile \in C(\pprofile)$ and of the scoring vector $\w \in W$ that together maximize the loss between $x$ and the true winner under $\profile$ and $\w$.
-\begin{align}
-\MR(x; \pprofile, W) & = \max_{y \in A} \PMR(x,y; \pprofile, W)\\
-& = \max_{\w \in W} \max_{\profile \in C(\profile)} \Regret(x, \profile, \w).
-\end{align}
-
-Finally,  $\MMR(\pprofile,W)$ is the value of minimax regret under $\pprofile$ and $W$, obtained when recommending a minimax optimal alternative $x^*_{\pprofile, W}$:
-\begin{align*}
-\MMR(\pprofile,W) & = \min_{x \in A} \MR(x;\pprofile,W) \\
-x^{*}_{\pprofile,W} \in A^*_{\pprofile, W} & = \argmin_{x \in A} \MR(x;\pprofile,W) 
-\end{align*}
-By picking as consensus choice
- an alternative associated with minimax regret, we can provide a recommendation that gives worst-case guarantees, giving some robustness in face of uncertainty (due to both not knowing the agents' preferences and the weights used in the aggregation).
-In cases of ties in minimax regret, we can either decide to return all minimax alternatives $A^*_{\pprofile, W}$ as winners or to pick just one of them using some tie-breaking strategy.
-
-Observe that if $\MMR(\pprofile, W)\!=\!0$, then $x^{*}_{\pprofile,W}$ is a necessary co-winner; this means that for any valid completion of the profile and any feasible $w \!\in\!
-W$, $x^{*}_{\pprofile,W}$ obtains a highest score.
-
-We note that our notion of regret gives some cardinal meaning to the scores: instead of just being used to select winners under the corresponding PSR, their differences are considered as representing the regret of the chair.
-
-% Add some general remarks about using minimax regret
-
-\paragraph{Computation of minimax regret}
-In order to compute pairwise maximum regret, and therefore minimax regret, we decompose the $\PMR$ into the contributions associated to each agent by adapting the reasoning from \citet{Lu2011}.
-The setting is however more challenging due to the presence of uncertainty in the weights.
-
-Recall that, in the computation of $s(x; \profile, \w)$, $w_{v_j(x)}$ represents the score that $x$ obtains in the ranking $v_j$ (see Equation \ref{eq:srule}).
-Since scoring rules are additively decomposable, we can consider separately the contribution of each agent to the total score.
-Thus, we can write the actual regret of choosing $x$ instead of $y$ as $s(y; \profile,\w) - s(x; \profile, \w) = \sum_{j=1}^n w_{v_j(y)} - w_{v_j(x)}$,
-and we can rewrite $\PMR$ as follows:
-\begin{align*}
-& \PMR(x,y; \pprofile, W) = \max_{\w \in W} \max_{\profile \in C(\pprofile)} [ s(y; \profile,\w) - s(x; \profile,\w) ] \\
-& =  \max_{\w \in W} \sum_{j=1}^{n} \max_{v_j \in C(\succ_j^p)} [w_{v_j(y)} - w_{v_j(x)}].
-\end{align*}
-Note that in general the inner max depends on the weights chosen by the outer max.
-
-We are interested in computing $\PMR(x, y; \pprofile, W)$.
-This represents the “worst” difference of score, thus the difference of score between $y$ and $x$ under the worst case preferences compatible with $\pprofile$ and $W$, where the worst case is the one that maximizes this difference of score.
-We consider now a procedure for completing a partial profile that was first proposed by \citet{Lu2011} when considering %minimax regret with 
-a fixed weight vector.
-As we will show, this procedure can also be used when the weight vector is not completely known.
-
-\begin{claim} \label{claim:completion}
-There exists a completion $\hat{\profile} \in C(\pprofile)$ such that $\PMR(x,y; \pprofile, W) = \max_{\w \in W} [ s(y; \hat{\profile}, \w) - s(x; \hat{\profile}, \w) ]$ and such that the linear order $\hat{v}_{j}$ of each agent $j$ satisfies:
-\begin{align} 
-\label{eq:complx}
-a \pref_j x &⇔ ¬(x \pprefeq_j a)\\
-\label{eq:comply}
-y \pref_j a &⇔ ¬(a \pprefeq_j y) ∧ ¬((x \pprefeq_j y) ∧ ¬(x \pprefeq_j a)).
-\end{align} 
-\end{claim}
-\begin{proof}[Sketch of proof]
-Consider our knowledge $\pprefeq_j$ about the preference of the agent $j$. 
-The adversary's goal is to make the score of $y$ as high as possible and the score of $x$ as low as possible. 
-To do this, he should complete $\ppref_j$ to $\pref_j$ by putting above $x$ as many alternatives as he can, that is, all the alternatives except those that are known to be worse than $x$ (those $a$ such that $x \pprefeq_j a$); and similarly, he should put below $y$ all the alternatives he can.
-Two conditions must be excluded for $a$ to go below $y$.
-The alternatives such that $a \pprefeq_j y$ can’t be put below $y$.
-Furthermore, the first objective must take priority over the second one: when an alternative should go above $x$ according to the first objective (because $¬(x \pprefeq_j a)$), and $x$ is known to be better than $y$ (thus $x \pprefeq_j y$), then $a$ should be put above $x$ (irrespective of whether $a \pprefeq_j y$), which will move both $x$ and $y$ one rank lower than if $a$ had been put below $y$.
-This maximizes the adversary’s interests: because the weight vector is convex, the difference of scores will be lower when both alternatives are ranked lower (Equation \ref{eq:convexity}), and that difference of scores is in favor of $x$ when $x \ppref_j y$, thus to be minimized from the point of view of the adversary.
-\end{proof}
-
-Let ${\pprefeq_j}(x)$ designate the set of alternatives that are known to be considered by $j$ as less good than or equal to $x$, and ${\pprefinv_j}(y)$ be the set of alternatives known to be considered by $j$ as strictly better than $y$.
-\begin{claim}
-	The rank of $x$ in the PMR-maximizing linear orders of agent $j$ is $\hat{v}_{j}(x) = 1+\card{A}-\card{{\pprefeq_j}(x)}$, and the rank of $y$ is $\hat{v}_{j}(y)=1+\card{{\pprefinv_j}(y)}+\card{\beta}$, where $\card{\beta} = \card{A \setminus ({\pprefeq_j}(x) \cup {\pprefinv_j}(y))}$ if $(x \pprefeq_j y)$ and $\card{\beta} = 0$ otherwise.
-\end{claim}
-\begin{proof}
-The rank of $x$ is directly obtained from \cref{eq:complx}.
-The rank of $y$ is obtained by complementing \cref{eq:comply}, obtaining $a \prefeq_j y ⇔ (a \pprefeq_j y) ∨ ((x \pprefeq_j y) ∧ ¬(x \pprefeq_j a))$, and, observing that $a \pref_j y ⇔ a ≠ y ∧ a \prefeq_j y$, obtaining that $a \pref_j y$ if and only if
-\begin{equation}
-\label{eq:betteryinter}
-(a \neq y) ∧ [(a \pprefeq_j y) ∨ ((x \pprefeq_j y) ∧ ¬(x \pprefeq_j a))],
-\end{equation} 
-or equivalently, if and only if
-\begin{equation}
-\label{eq:bettery}
-%a \pref_j y ⇔ 
-(a \ppref_j y) ∨ ((x \pprefeq_j y) ∧ ¬(x \pprefeq_j a)).
-\end{equation} 
-Indeed, \eqref{eq:betteryinter} $⇒$ \eqref{eq:bettery}, and \eqref{eq:bettery} $⇒$ \eqref{eq:betteryinter} because $(x \pprefeq_j y) ∧ ¬(x \pprefeq_j a) ⇒ a ≠ y$ (as when $a = y$, $(x \pprefeq_j y)$ and $¬(x \pprefeq_j a)$ are opposite claims).
-Suffices now to rewrite \cref{eq:bettery} to let the two disjuncts designate disjoint sets:
-\begin{equation*}
-\label{eq:betteryfinal}
-a \pref_j y ⇔ 
-(a \ppref_j y) ∨ ((x \pprefeq_j y) ∧ ¬(x \pprefeq_j a) ∧ ¬(a \ppref_j y)).
-\end{equation*} 
-\end{proof}
-
-The claim can also be understood by observing that in the case $(x \pprefeq_j y)$, $\beta$ is the number of alternatives incomparable with both $x$ and $y$.
-
-\begin{claim}
-The $\PMR$ can be written as:
-\begin{align} 
-\PMR(x,y; \pprofile, W)  
-& = \max_{w \in W} \sum_{j=1}^n w_{\hat{v}_j(y)} - w_{\hat{v}_j(x)} = \\ 
-& = \max_{w \in W} \sum_{r=1}^m (\hat{\alpha}_{r}^{y} - \hat{\alpha}_{r}^{x}) w_i. 
-\end{align}
-where $\hat{\alpha}_{r}^{y}$ (resp. $\hat{\alpha}_{r}^{x}$)  is the number of times $y$ (resp. $x$) is at rank $r$ in the complete profile $\hat{\profile}$.
-\end{claim}
-The last claim shows that PMR is linear in the weights.
-Recall that the preferences of the chair are encoded with linear constraints $\Co_{W}$.
-The pairwise max regret $\PMR(x,y; \pprofile,W)$ can be obtained as the solution of the following linear program defined on the variables $w_1, …, w_m$, which represent the weights attached to different positions.
-\begin{align*}
-\max_{\w} & \sum_{r=1}^m (\hat{\alpha}_{r}^{y} - \hat{\alpha}_{r}^{x}) w_{r}
-\end{align*}
-$\text{ s.t. } \text{\cref{eq:monotone}} \text{ and } \text{\cref{eq:convexity}} \text{ and } \Co_W$. Note that given our choice $w_{1}=1$ and $w_{m}=0$, there are only $m-2$ variables 
-(we leave $w_{1}$ and $w_{m}$ in the LP just for clarity of presentation).
-
-The max regret $\MR(x; \pprofile, W)$ is determined by considering the pairwise regret of $x$ with all other alternatives in $A$.
-Optimal alternatives w.r.t. minimax regret are the ones with least max regret. 
-Observe that, whenever the $\PMR$ of an alternative $x$ (against some other alternative $y$) exceeds the best MR value found so far, we don't need to further evaluate $x$. 
-This idea can be exploited further by adopting a minimax-search tree \citep{Braziunas2011}.
-
-\section{Interactive Elicitation} 
-\label{sec:elicit}
-We propose an incremental elicitation method based on minimax regret.
-At each step, the system may ask a question either to one of the agents about her preferences or to the chair about the voting rule. 
-The goal is to acquire relevant information to reduce minimax regret as quickly as possible.
-As termination condition of elicitation, we can check whether minimax regret is lower than a threshold; if we wish optimality, we can perform elicitation until minimax regret drops to zero.
-
-The remainder of this Section is structured as follows.
-First of all, we discuss the different types of questions that can be asked to the agents and to the chair, and the way responses are handled.
-Then, we describe different strategies to determine informative queries to ask next, with the goal of reducing $\MMR(\pprofile,W)$ quickly.
-
-\paragraph{Question types}
-We distinguish between questions asked to the agents and questions asked to the chair.
-As {\em questions asked to the agents} it is natural to consider comparison queries asking to compare two alternatives.
-%Another common type of queries are {\em top-k}, asking to each agent her $k$ most preferred alternatives.
-The effect of a response to a question asked to an agent is the increase in our knowledge about the agents rankings, thus augmenting the partial profile $\pprofile$. 
-If agent $j$ answers a comparison query stating that alternative $a$ is preferred to $b$, then the partial order $\ppref_j$ is augmented with $a \ppref_j b$ and by transitive closure.
-
-A bit more discussion is needed about {\em questions asked to the chair}.
-Such questions aim at refining our knowledge about the scoring rule; a response gives us a constraint on the weight vector $\w$.
-In particular, we want to acquire constraints of the type:
-\[ w_{r} - w_{r+1} \geq \lambda (w_{r+1} - w_{r+2}) \] 
-for $r \in \{1,\ldots,m-2\}$, relating the difference between the importance of ranks $r$ and $r+1$ with the difference between ranks $r+1$ and $r+2$.
-
-\paragraph{Building concrete questions for the chair}
-As we assume the weights constitute the utility components of the chair, it might be reasonable to assume
-%as we do here, 
-that the chair is able to answer such abstract questions in our setting.
-However, it is important to make sure that a question can also, in principle, be asked in a more concrete way, in terms of winners of example profiles.
-This permits to test how the chair understands the question and to relate the preference of the chair to her choice behavior in the economic sense.
-Furthermore this will be necessary for an ordinal extension of our work where the scores would not be considered as cardinal utilities.
-Thus, our task is to build a profile, given $\lambda$ and $r ≤ m-2$, in such a way that the set of (tied) winners picked by the chair reveals whether $w_{r} - w_{r+1} \geq \lambda (w_{r+1} - w_{r+2})$.
-\begin{claim}
-	Given a rational $\lambda = p/q$ and a rank $r$ between $1$ and $m - 2$, the profile named $P'$ in the ensuing description is such that, for any weight vector $\w \in \W$, $a \in f(P')$ iff $w_{r} - w_{r+1} ≥ \lambda (w_{r+1} - w_{r+2})$ and $b \in f(P')$ iff $w_{r} - w_{r+1} ≤ \lambda (w_{r+1} - w_{r+2})$, where $f$ is the PSR parameterized with $\w$.
-\end{claim}
-\begin{proof}
-Observe that the question may be defined equivalently as $q \cdot w_{r} + p \cdot w_{r+2} ≥ (p + q) \cdot w_{r+1}$, where $p, q$ are natural numbers. 
-As a first attempt to make this question concrete, we could define a profile $P$ containing $p+q$ agents in such a way that an alternative $a$ receives $q$ times the rank $r$ and $p$ times the rank $r+2$, and an alternative $b$ receives $p+q$ times the rank $r+1$.
-Observing that the score of $a$ in that profile is exactly the left hand side of the question, and that the score of $b$ is the right hand side, intuition suggests that observing whether the chair picks $a$ or $b$ as winner will let us determine which side is greater; equality occurring when the chair declares $a$ and $b$ as tied for the victory.
-However, we still need to complete the profile, thus, come up with other $m-2$ alternatives defined so that each agent in the resulting profile has placed exactly one alternative in each rank.
-And we must ensure, doing this, that these other alternatives are not better than $a$ or $b$: if the chair picks a different alternative $c$, it tells us that the chair prefers $c$ to both $a$ and $b$,
-but it generally does not  answer the question we are interested in. 
-Taking $p = q = 1$, $m=4$, $r=2$, we see that such a completion may be impossible. Luckily, this problem can be worked around, at the price of increasing the number of agents.
-
-First build a temporary profile $P$ of $p+q$ agents with $a$ and $b$ ranked as just described.
-Complete it with $m-2$ alternatives ranked in arbitrary orders so that the resulting profile has complete strict rankings for each of the $p+q$ agent.
-Now we will make the other alternatives as bad as desired by adding agents to $P$ that appreciate $a$ and $b$ more than the other alternatives, thus building a profile $P'$ in which, whatever the weights, $c$ may not have a better score than $a$.
-Observe that if we add $\delta$ agents (with $\delta$ a natural number) that put $a$ at first rank and $b$ at second rank, and $\delta$ agents that put $b$ at first rank and $a$ at second rank, we do not change the difference of the scores of $a$ and $b$, and thus, observing the chair choosing $a$ or $b$ still answers the question.
-% Choose arbitrarily a matching of the remaining $m-2$ alternatives to the ranks $3$ to $m$, say, $c \mapsto 3$, $d \mapsto 4$, and so on.
-The first $\delta$ supplementary agents, who rank $a$ first and $b$ second, rank the other alternatives as the just defined mapping suggests.
-The other $\delta$ supplementary agents, who rank $b$ first and $a$ second, use the opposite ranking for the remaining alternatives, say, $c \mapsto m$, $d \mapsto m-1$, and so on.
-
-We can prove that, for $\delta = p+q$, and whatever the weight vector $\w \in \W$, no alternative, except possibly $b$, has a better score than $a$. 
-(In fact, as the construction will exhibit, they are all worst than both $a$ and $b$, but the weaker fact is enough for our claim.)
-Pick any alternative $c$ that is not $a$ or $b$. 
-%Let $c_t$ denote the number of times $c$ reaches rank $t$ or better in $P$.
-Note that $c_m = p+q$ and $c_t ≤ p + q, 1 ≤ t ≤ m$.
-Define $a_t$ similarly, for the alternative $a$.
-By construction, $a_r = q$, $a_{r+2} = q+p = a_m$.
-Define $c'_t$ as the number of times $c$ gets rank $t$ or better in $P'$, and define $a'_t$ similarly.
-Now $a'_1 ≥ \delta, a'_t ≥ 2\delta \text{ for } 2 ≤ t < m, a'_{r+2} = q+p+2\delta = a'_m$.
-To obtain upper bounds for $c'_t$, assume $c$ is ranked first by the $p+q$ agents in $P$.
-By our construction, the  $2 \delta$ new agents of $P'$ give to $c$ the ranks $(3, m)$, or $(4, m-1)$, … Observe that the score of $c$ is maximal for attribution $(3, m)$, by convexity of the weights.
-Therefore, in the best case for $c$, $c'_1 ≤ p + q, c'_2 ≤ p+q, c'_t ≤ p+q+\delta \text{ for } 3 ≤ t < m, c'_m ≤ p+q+2\delta$.
-Observe that $a'_t ≥ c'_t, 1 ≤ t ≤ m$ (with strict inequality for $t=2$).
-Because weights are non increasing, this guarantees, with $\delta = p + q$, that the score of $a$ is not lower than the one of $c$.
-\end{proof}
-At this stage, we are satisfied that a procedure exists to transform our abstract questions to questions about winners of a PSR.
-Further studies would investigate, for example, what is lost in terms of elicitation efficiency when we are forced to restrain to realistic concrete questions, meaning, questions involving small profiles; or investigate the relationship between our understanding of scores as (cardinal) utility and (ordinal) scores as definition of a PSR.
-
-\paragraph{Elicitation strategies}
-We develop several elicitation strategies for simultaneous elicitation of agents' preferences and of the scoring rule.
-While it is of course possible to first fully elicit the agents’ preferences and afterwards elicit weights, we also want to propose interleaved approaches and compare them experimentally.
-Indeed, it can be beneficial to split efforts asking questions to the chair and to agents, depending on which is estimated to be more informative.
-We define here the various strategies we tested experimentally. A strategy tells us, given the current partial knowledge $(\pprofile, W)$, which question should be asked next.
-
-The \strat{Random} strategy gives a baseline for comparison and informs about the difficulty of an elicitation problem. 
-This strategy first decides with a probability of $1/2$ each whether it will ask a question about weights or a question about a preference ordering (unless the profile is already known entirely).
-If it opted for a question about weights, it draws one rank in $2 ≤ r ≤ m-2$ equiprobably, takes the middle of the interval of values for $\lambda$ that are still possible considering our knowledge so far, and asks whether $w_r - w_{r+1} ≥ \lambda (w_{r+1} - w_{r+2})$.
-The intervals are initialized to $[1, n]$.
-If it opted for a question to agents, it draws equiprobably among the agents whose preference is not known entirely; picks an alternative $a$ randomly with equal probability among those involved in some incomparabilities in $\ppref_j$; and picks an alternative $b$ with equal probability among those incomparable with $a$ in $\ppref_j$.
-
-The \strat{Pessimistic} strategy selects the question that leads to minimal regret in the worst case, considering both possible answers to the question.
-Assume that a question leads to the possible new knowledge states $(\pprofile_1, W_1)$ and $(\pprofile_2, W_2)$, depending on the answer.
-Then the badness of the question in the worst case is: $\max_{i=1,2} \MMR(\pprofile_i,W_i) $.
-This badness measure gives a way of picking questions among a set of possible questions, by picking one that minimizes ths measure of minimax regret {\em a posteriori}. 
-%Note that other aggregators than $\max$ can be used as well.
-%We use the $\max$ operator because \citet{Cailloux2014} reported that pessimistic aggregation works much better than optimistic aggregation, although our experiments in this context suggested a weak impact of that choice on the performance of the strategy.
-However, to avoid the absorption property of max, we adopt the $\leximax$ criterion as an aggregator: if the maximal $\MMR$ of two questions are equal, then it considers the other $\MMR$ values, that are the one associated to the opposite answer, preferring the question with the lowest value.
- We expect this strategy to perform very well, but only for very small problem instances: its complexity is in $O(n^2 m^5)$, because we consider $O(m^2)$ questions for each agent and need for each question to compute $\MMR$ twice, whose complexity is $O(nm^3)$.
-For small dimensions, it estimates an upper bound to the possible quality of a strategy.
-
-The \strat{Limited pessimistic} strategy uses the same criterion as the pessimistic strategy, but limiting it to a small set of $n+1$ candidate questions: one per agent, and one to the chair.
-It uses the heuristic proposed by \citet{Lu2011} to define the candidate questions to the agents.
-Considering agent $j$, either $x^{*} \ppref_j \bar{y}$, or $\bar{y} \ppref_j x^{*}$, or $x^{*}$ and $\bar{y}$ are incomparable in $\ppref_j$.
-As shown in the proof of Claim \ref{claim:completion}, in order to increase $\PMR(x^{*},\bar{y})$, an adversary should place as many alternatives as he can above $x^{*}$ in the first case, and between $\bar{y}$ and $x^{*}$ in the second.
-An intuitive way to reduce the pairwise max regret is, therefore, to directly ask questions involving such alternatives, hoping for an answer that would prevent the adversary to play his best game.
-If $x^{*}$ and $\bar{y}$ are incomparable, then we just ask the agent $j$ to compare them.
-To define the candidate question to the chair, consider
-%\begin{align}
-$\w^\tau = \argmin_{\w \in W} s(\bar{y}; \bar{\profile}, \w) - s(x^{*}; \bar{\profile}, \w)$,
-%\end{align}
-the weight vector that minimize the $\PMR$ in the worst case.
-We compare $\bar{\w}$ and $\w^{\tau}$ component-wise to find the position $r$ that is most valuable to ask about (the one that maximizes $\abs{\bar{\w}_r - \w^{\tau}_r}$), and choose $\lambda$ as the middle of the interval of possible values for that rank.
-We then evaluate, for each candidate question, the minimax regret for the two possible answers; finally we choose the best according to $\leximax$.
-
-Lastly, the \strat{Two phases} strategy is developed in order to investigate the effect of varying the proportion of questions asked to agents and to the chair.
-%The \strat{Two phases - vc} first asks $p$ questions to the agents, then $k-p$ questions to the chair, using in both cases Limited pessimistic to select the specific question.
-The \strat{Two phases - cv} strategy starts with $p$ questions to the chair, then asks to the agents.
-\commentOC{If our XPs exhibit no significant change between vc and cv (or if we don’t have time to run them), I will drop this distinction.}
-It first asks $p$ questions to the chair, then $k-p$ questions to the agents, using in both cases the same method as \strat{Limited pessimistic} to select the specific question. 
-Note that when asking first only questions to the chair, if the obtained knowledge approximates well the scoring vector, then in the second part of the elicitation we fall into the more classical setting of incompleteness of preferences assuming a known voting rule.
-%And vice-versa when asking first questions to the agents, the second part of the elicitation is similar to the setting of incompletely specified scoring rule. 
-%The aim of this strategy is to simulate the current state of the art when considering incomplete preferences.
-In fact, by asking enough questions to the chair we can reduce our problem into a well studied one of incompleteness of preferences knowing the voting rule.
-Moreover, if we invert to whom ask questions first, we fall instead in an already studied case of uncertainty of the voting rule with a known complete profile.
-
-%\item {\em Volumetric} strategy: chooses an agent $i$ and a query that maximizes the number of new pairwise preferences revealed given the worst response.
-
-\section{Empirical Evaluation} 
-\label{sec:experiments}
-
-\sisetup{round-mode=places, round-precision=1, table-figures-integer=1, table-figures-decimal=1}
-\begin{table}
-	\begin{center}
-		\begin{tabular}{S[table-figures-integer=2, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
-			\toprule
-			{k} & {Rnd} & {sd} & {Pes.} & {sd} & {L.\ pes.} & {sd} \\
-			\midrule
-			0 & 5.0 & 0 & 5.0 & 0 & 5.0 & 0\\
-			5 & 4.958 & 0.100 & 3.741 & 0.024 & 4.350 & 0.604\\
-			10 & 4.709 & 0.436 & 3.283 & 0.423 & 3.323 & 0.374\\
-			15 & 4.432 & 0.467 & 2.716 &0.410 & 2.722 & 0.672\\
-			20 & 3.666 & 0.522 & 1.549 & 0.430 & 2.145 & 0.716\\
-			25 & 3.068 & 0.679 & 1.424 &  0.512 & 0.921 & 0.569\\
-			30 & 2.631 & 0.466 & 0.394 & 0.359 & 0.470 & 0.355\\
-			\bottomrule
-		\end{tabular}
-	\end{center}
-	\caption{Minimax regret in problems of size $(5, 5)$ after $k$ questions.}
-	\label{fig:55}
-\end{table}
-
-\begin{table}
-	\begin{center}
-		\begin{tabular}{S[table-figures-integer=2, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
-			\toprule
-			{k} & {Rnd} & {sd} & {L.\ pes.} & {sd} \\
-			\midrule
-			0 & 20.0 & 0 & 20.0 & 0 \\
-			20 & 19.985 & 0.042 & 18.770 & 0.111 \\
-			40 & 19.903 & 0.080 & 17.659 & 0.290 \\
-			60 & 19.764 & 0.159 & 16.951 & 0.541 \\
-			80 & 19.403 & 0.221 & 15.736 & 0.367 \\
-			100 & 18.947 & 0.383 & 14.621 & 0.703 \\
-			\bottomrule
-		\end{tabular}
-	\end{center}
-	\caption{Regret in problems of size $(10, 20)$ after $k$ questions.}
-	\label{fig:1020}
-\end{table}
-
-We test our strategies using randomly generated datasets. 
-Our first goal is to see, with a small problem size ($m = 5, n = 5$) and the (time consuming) Pessimistic strategy, if an important lowering of the maximal regret can be achieved with a reasonable number of questions.
-We also want to estimate how “hard” such a problem is, by using the Random strategy as a baseline.
-Third, we want to estimate the loss (in terms of worst regret) when switching to the faster Limited pessimistic strategy.
-Fourth, we want to see, on a bigger problem size ($m = 10, n = 20$), how many questions must be asked for that strategy to achieve a significant reduction of the worst regret.
-Finally, we want to evaluate, thanks to the Two phases strategy, the impact of varying the proportion of questions asked to the agents (with respect to questions asked to the chair) on the reduction of the worst regret.
-%We also want to see how realistic our approach is for various problem sizes, by estimating the number of questions we would have to ask before being able to reduce the worst regret significantly.
-
-We use the following protocol.
-Having picked a problem size $(m, n)$, a number of questions $k$ and a strategy, we randomly generate an “oracle”, containing the true preferences of the agents (i.e.
-the linear orders) and the weights associated with the chair's scoring rule.
-We start with empty knowledge ($\pprofile = (\emptyset_j), W = \W$) about the preference orderings of the agents or the weight differences favored by the chair.
-We obtain the first question to be asked using the selected strategy, as described above.
-We use the oracle to answer the question and update our knowledge, which is thus used to obtain the next question.
-This is repeated until $k$ answers have been obtained.
-Then we compute the resulting $\MMR$.
-We repeat this whole experiment 10 times, for a given $(m, n, k)$, and report the average resulting $\MMR$ and the standard deviation.
-
-The results are displayed in \cref{fig:55,fig:1020,fig:p}, where strategies are designated by Rnd for Random, Pes. for Pessimistic, L.\ pes. for Limited pessimistic and 2 ph. for Two phases.
-
-We observe that the Pessimistic strategy is able to reduce the regret almost completely after $30$ questions.
-We also see that Limited pessimistic performs almost as well as Pessimistic; this is good news since (for $m=5$ and $n=5$), the former strategy is much faster and takes only $2.6s$ for a complete elicitation session, while the latter takes $16s$.
-%However, it takes $1000$ times more time than the \strat{Random} strategy ($16s$ of the Pessimistic compared to $0.014s$ of the Random).
-Moreover, the results of the \strat{Limited pessimistic}, that takes almost $80\%$ less of the time of the \strat{Pessimistic} ($2.6s$), are essentially the same.
-%In Table \ref{fig:1020}, we can see the drop of regret using a bigger instance.
-%Finally in Table \ref{fig:p}
-
-\begin{table}
-	\begin{center}
-		\begin{tabular}{S[table-figures-integer=2, table-number-alignment = right, table-figures-decimal=0]r}
-			\toprule
-			{p} & {Two ph.} \\
-			\midrule
-			0 & 20.000 \\
-			25 & 18.851 \\
-			50 & 17.296 \\
-			75 & 15.774 \\
-			100 & 14.707 \\
-			125 & 12.999 \\
-			150 & 11.975 \\
-			175 & 9.999 \\
-			200 & 11.499 \\
-			\bottomrule
-		\end{tabular}
-	\end{center}
-	\caption{Regret in problems of size $(10, 20)$ after $200$ questions (one repetition only).}
-	\label{fig:p}
-\end{table}
-
-\section{Conclusions}  
-\label{sec:conclusions}
-In this paper we have considered a social choice setting with partial information about the agent's preferences and a partially specified voting rule.
-In this setting, we have proposed the use of minimax regret both as a means of robust winner determination as well as a guide to the process of simultaneous elicitation of preferences and voting rule.
-Our experimental results %on randomly generated and real world data sets 
-suggest that regret-based elicitation is effective and allow to quickly reduce worst regret, but they also show that starting with zero knowledge became a pretentious approach really quickly when increasing the size of the problem.
-Future works will therefore include the test of these strategies on partial specified profiles, ideally on real datasets.
-An other important direction is the extension to voting rules beyond scoring rules.
-%Finally, an important direction of extension aims at studying how to elicit preferences while restraining to concrete and easy questions.
-%Regret-based elicitation allows to determine near-optimal winners using only few information about the agents' preferences.
-As part of the contribution of this work, we publish an open-source library that allows to reproduce our experiments, and more (url not displayed for anonymity reasons).
-
-% Acknowledgements: We thank the reviewers for comments helping to improve the paper. 
-\bibliography{biblio}
-%\bibliographystyle{named}
-\bibliographystyle{abbrvnat} 
-\end{document}
-
-\appendix
 \section{Old table}
@@
 We can summarize it for each $q \in A$ as follows:
-	\begin{align*}
+	\begin{align}
 	q \succ_i^\pprofile x \vee q \ ?_i^\pprofile \ x \ & \Rightarrow \ \uparrow_x \\
@@
 	x \succ_i^\pprofile q \succ_i^\pprofile y \ & \Rightarrow \ \text{in between} \\
-	\end{align*}
+	\end{align}
 	It is worth noting that when the relation between $q$ and $x$ is not known in the partial profile, the adversary takes advantage by placing $q$ above $x$ only under the assumption of convex weight sequences.
@@
 We can summarize the procedure for each $q \in A$ as follows:
-	\begin{align*}
+	\begin{align}
 	q \succ_i^\pprofile y \ & \Rightarrow \ \uparrow_y \\
@@
 	(y \succ_i^\pprofile q \vee y \ ?_i^\pprofile \ q) \wedge (q \succ_i^\pprofile x \vee q \ ?_i^\pprofile \ x) \ & \Rightarrow \ \text{in between} \\
-	\end{align*}
+	\end{align}
 	\item $x \ ?_i^\pprofile \ y$
@@
 Then PMR can be written as follows:
-\begin{align*}
+\begin{align}
  &\PMR(x,y; \pprofile, W) =\\ 
@@
   \!+\!	 \sum_{j \in A^+ \cup  U^?} [w_{\hat{v}_j(y)} \!-\! w_{\hat{v}_j(x)}] \Big \} 
- \end{align*}
+ \end{align}
 %Note that the second addendum inside the max do not depend on the choice of $\w$.
@@
 We rewrite the second addendum as:
-\begin{align*}
+\begin{align}
 \sum_{j \in U^+ \cup  U^?} [w_{\hat{v}_j(y)} \!-\! w_{\hat{v}_j(x)}] 
 = \sum_{i = 1}^{m} (\hat{\alpha}_{i}^{y} - \hat{\alpha}_{i}^{x}) w_{i}
-\end{align*}
+\end{align}
 where $\hat{\alpha}_{i}^{x}$ is the number of times that $x$ is ranked  in position $i$  considering the profile $\hat{v}$ of agents in $U^+ \cup  U^?$.
@@
 We therefore obtain the following mixed integer linear program:
-\newcommand{\C}{\mathcal{C}}
+
 \begin{align}
@@
 \text{ s.t. } &  \text{Equation } (\ref{eq:monotone}) & \\
-&  \C(\w) &  \\
+&  \mathcal{C}(\w) &  \\
 & \sum_{i=t_{1}}^{t_{2}} B_{i,j}^{+} = 1 & \forall j \in A^{-} \\
@@
 	By contradiction let assume $w_{1} = w_{2}$ then 
-	\begin{align*}
+	\begin{align}
 	w_{1} - w_{2} \geq w_{2} - w_{3} &\geq \dots \geq w_{m-1} - w_{m} \\
@@
 	0 \geq 1 - w_{3} &\geq \dots \geq w_{m-1}
-	\end{align*}
+	\end{align}
 	At this point either $0\leq w_{3}<1$ or $w_{3}=1$. In the first case 
@@
 \end{itemize}
-\fi
-\end{document}

### 2020-09-09 AAMAS2021/minimax.tex
Comments, Table1 and part of Table3

@@
 Recently, the assumption of full preference information has been questioned by a number of researchers and several methods for eliciting preferences have been proposed.
-In this paper we go one step further and we assume that both the voting rule and the agents preferences are partially specified.
+In this paper we go one step further and we assume that both the voting rule and the agents' preferences are partially specified.
 Focusing on positional scoring rules, we assume that the chair, while  not able to give a precise definition of the rule, is capable of answering simple questions  requiring to pick a winner from a specific  example profile.
@@
 %Another common type of queries are {\em top-k}, asking to each agent her $k$ most preferred alternatives.
-The effect of a response to a question asked to an agent is the increase in our knowledge about the agents rankings, thus augmenting the partial profile $\pprofile$. 
+The effect of a response to a question asked to an agent is the increase in our knowledge about the agents' rankings, thus augmenting the partial profile $\pprofile$. 
 If agent $j$ answers a comparison query stating that alternative $a$ is preferred to $b$, then the partial order $\ppref_j$ is augmented with $a \ppref_j b$ and by transitive closure.
@@
 This strategy first decides with a probability of $1/2$ each whether it will ask a question about weights or a question about a preference ordering (unless the profile is already known entirely).
-If it opted for a question about weights, it draws one rank in $2 ≤ r ≤ m-2$ equiprobably \commentOC{Isn’t this $1 ≤ r$?}, takes the middle of the interval of values for $\lambda$ that are still possible considering our knowledge so far, and asks whether $w_r - w_{r+1} ≥ \lambda (w_{r+1} - w_{r+2})$.
+If it opted for a question about weights, it draws one rank in $1 ≤ r ≤ m-2$ equiprobably \commentOC{Isn’t this $1 ≤ r$?} \commentBN{Yep.}, takes the middle of the interval of values for $\lambda$ that are still possible considering our knowledge so far, and asks whether $w_r - w_{r+1} ≥ \lambda (w_{r+1} - w_{r+2})$.
 The intervals are initialized to $[1, n]$.
@@
 The \strat{Limited pessimistic} strategy uses the same criterion as the pessimistic strategy, but limiting it to a small set of $n+1$ candidate questions: one per agent, and one to the chair.
-It uses the heuristic proposed by \citet{Lu2011} to define the candidate questions to the agents.
+Let $(x^{*},\bar{y}, \bar{\profile}, \bar{\w})$ be the current solution of the minimax regret, where $\bar{y}, \bar{\profile}, \bar{\w}$ are, respectively, the choice of $y$, the completion of the profile and the selection of weights for which $x^{*}$ is the minimax optimal alternative.
+The \strat{Limited pessimistic} strategy first selects $n$ candidates questions to the agents using the heuristic proposed by \citet{Lu2011}.
 Considering agent $j$, either $x^{*} \ppref_j \bar{y}$, or $\bar{y} \ppref_j x^{*}$, or $x^{*}$ and $\bar{y}$ are incomparable in $\ppref_j$.
-\commentOC{I think $\bar{y}$ is not defined.} As shown in the proof of Claim \ref{claim:completion}, in order to increase $\PMR(x^{*},\bar{y})$, an adversary should place as many alternatives as he can above $x^{*}$ in the first case, and between $\bar{y}$ and $x^{*}$ in the second.
-An intuitive way to reduce the pairwise max regret is, therefore, to directly ask questions involving such alternatives \commentOC{(with equal likelyhood?)}, hoping for an answer that would prevent the adversary to play his best game.
-If $x^{*}$ and $\bar{y}$ are incomparable, then we just ask the agent $j$ to compare them.
+As shown in the proof of Claim \ref{claim:completion}, in order to increase $\PMR(x^{*},\bar{y})$, an adversary should place as many alternatives as he can above $x^{*}$ in the first case, and between $\bar{y}$ and $x^{*}$ in the second.
+An intuitive way to reduce the pairwise max regret would be, therefore, to ask questions involving such alternatives \commentOC{(with equal likelyhood?)}\commentBN{We are not asking questions yet.
+We select as a candidate question the one corresponding to the situation.
+If you mean "what if there are several alternatives that can be placed between the two?" then yes, we pick one equiprobably.}, hoping for an answer that would prevent the adversary to play his best game.
+If $x^{*}$ and $\bar{y}$ are incomparable, then the candidate question to agent $j$ simply consists in comparing the two alternatives.
 To define the candidate question to the chair, consider
@@
 We compare $\bar{\w}$ and $\w^{\tau}$ component-wise to find the position $r$ that is most valuable to ask about (the one that maximizes $\abs{\bar{\w}_r - \w^{\tau}_r}$), and choose $\lambda$ as the middle of the interval of possible values for that rank.
-We then evaluate, for each candidate question, the minimax regret for the two possible answers; finally we choose the best according to $\leximax$.
+After having selected the candidate questions, we apply the Pessimistic strategy.
+We evaluate, for each of the questions, the minimax regret for the two possible answers and we choose the best according to $\leximax$.
 
@@
 \label{sec:experiments}
+\commentBN{Change the text according to the new tables.}
 
-\sisetup{round-mode=places, round-precision=1, table-figures-integer=1, table-figures-decimal=1}
+\sisetup{round-mode=places, round-precision=2, table-figures-integer=1, table-figures-decimal=2}
 \begin{table}
@@
 			\midrule
-			0 & 5.0 & 0 & 5.0 & 0 & 5.0 & 0\\
-			5 & 4.958 & 0.100 & 3.741 & 0.024 & 4.350 & 0.604\\
-			10 & 4.709 & 0.436 & 3.283 & 0.423 & 3.323 & 0.374\\
-			15 & 4.432 & 0.467 & 2.716 &0.410 & 2.722 & 0.672\\
-			20 & 3.666 & 0.522 & 1.549 & 0.430 & 2.145 & 0.716\\
-			25 & 3.068 & 0.679 & 1.424 &  0.512 & 0.921 & 0.569\\
-			30 & 2.631 & 0.466 & 0.394 & 0.359 & 0.470 & 0.355\\
+			0 & 10.0 & 0.0 & 10.0 & 0.0 & 10.0 & 0.0\\
+			20 & 9.05 & 0.51 & 7.38 & 0.65 & 6.08 & 0.76\\
+			40 & 7.3 & 0.62 & 4.21 & 1.18 & 2.77 & 1.27\\
+			60 & 6.01 & 0.81 & 1.56 &0.98 & 1.23 & 1.22\\
+			80 & 4.72 & 1.07 & 0.2 & 0.33 & 0.55 & 0.71\\
+			100 & 3.0 & 0.97 & 0.0 &  0.0 & 0.2 & 0.28\\
+			120 & 1.31 & 1.15 & 0.0 & 0.0 & 0.1 & 0.21\\
+			140 & 0.44 & 0.85 & 0.0 & 0.0 & 0.1 & 0.21\\
+			150 & 0.21 & 0.58 & 0.0 & 0.0 & 0.1 & 0.21\\
 			\bottomrule
@@
 	\end{center}
-	\caption{Minimax regret in problems of size $(5, 5)$ after $k$ questions.}
+	\caption{Minimax regret in problems of size $(5, 10)$ after $k$ questions over $25$ runs.}
 	\label{fig:55}
@@
 Then we compute the resulting $\MMR$.
-We repeat this whole experiment 10 times, for a given $(m, n, k)$, and report the average resulting $\MMR$ and the standard deviation.
+We repeat this whole experiment 10 times, for a given $(m, n, k)$, and report the average resulting $\MMR$ and the standard deviation \textit{sd}.
 
@@
 	\begin{center}
-		\begin{tabular}{S[table-figures-integer=2, table-number-alignment = right, table-figures-decimal=0]r}
+		\begin{tabular}{S[table-figures-integer=2, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
 			\toprule
-			{p} & {Two ph.} \\
+			{p} & {Comm. Fst.} & {sd} & {Vot. Fst.} & {sd} \\
 			\midrule
-			0 & 11.49 \\
-			25 & 9.99 \\
-			50 & 11.97 \\
-			75 & 12.99 \\
-			100 & 14.70 \\
-			125 & 15.77 \\
-			150 & 17.29 \\
-			175 & 18.85 \\
-			200 & 20.00 \\
+			0 & 5.02 & 0.82 & & \\
+			50 & 6.47 & 1.14 & & \\
+			100 & 9.4 & 1.58 & & \\
+			150 &  & & & \\
+			100 &  & & & \\
+			125 &  & & & \\
+			150 &  & & 12.31 & 0.96 \\
+			200 &  & & 16.12 & 1.06 \\
+			250 &  & & 20.0 & 0.0 \\
 			\bottomrule
@@
 	\end{center}
-	\caption{Regret in problems of size $(10, 20)$ after $200$ questions (one repetition only).}
+	\caption{Regret in problems of size $(10, 20)$ after $250$ questions over $5$ runs. Where $p$ represents the number of questions asked to the committee.}
 	\label{fig:p}

### 2020-09-10 AAMAS2021/minimax.tex
Table 2 and 3

@@
 	\end{center}
-	\caption{Minimax regret in problems of size $(5, 10)$ after $k$ questions over $25$ runs.}
+	\caption{Average minimax regret in problems of size $(5, 10)$ after $k$ questions over $25$ runs.}
 	\label{fig:55}
@@
 			\toprule
-			{k} & {Rnd} & {sd} & {L.\ pes.} & {sd} \\
+			{k} & {Rnd} & {sd} & {L.\ pes.} & {sd??} \\
 			\midrule
-			0 & 20.0 & 0 & 20.0 & 0 \\
-			20 & 19.985 & 0.042 & 18.770 & 0.111 \\
-			40 & 19.903 & 0.080 & 17.659 & 0.290 \\
-			60 & 19.764 & 0.159 & 16.951 & 0.541 \\
-			80 & 19.403 & 0.221 & 15.736 & 0.367 \\
-			100 & 18.947 & 0.383 & 14.621 & 0.703 \\
+			0 & 20.0 & 0.0 & 20.0 & 0.0 \\
+			50 & 19.81 & 0.12 & 17.19 & 1.2 \\
+			100 & 19.22 & 0.25 & 14.72 & 2.4 \\
+			150 & 18.18 & 0.54 & 12.52 & 3.89 \\
+			200 & 17.05  & 0.29 & 10.57 & 5.14 \\
+			250 & 15.95 & 0.26 & 9.28 & 6.17 \\
 			\bottomrule
@@
 	\end{center}
-	\caption{Regret in problems of size $(10, 20)$ after $k$ questions.}
+	\caption{Average regret in problems of size $(10, 20)$ after $k$ questions over $5$ runs.}
 	\label{fig:1020}
@@
 			\midrule
-			0 & 5.02 & 0.82 & & \\
-			50 & 6.47 & 1.14 & & \\
-			100 & 9.4 & 1.58 & & \\
-			150 &  & & & \\
-			100 &  & & & \\
-			125 &  & & & \\
-			150 &  & & 12.31 & 0.96 \\
-			200 &  & & 16.12 & 1.06 \\
-			250 &  & & 20.0 & 0.0 \\
+			0 & 5.02 & 0.82 & 3.21 & 1.6 \\
+			25 & 5.83 & 1.25 & 6.79 & 1.2 \\
+			50 & 6.47 & 1.14 & 5.2 & 1.58 \\
+			100 & 9.4 & 1.58 & 8.66 & 0.51 \\
+			150 & 11.89 & 1.1 & 12.31 & 0.96 \\
+			200 & 15.64  & 0.52 & 16.12 & 1.06 \\
+			250 & 20.0 & 0.0 & 20.0 & 0.0 \\
 			\bottomrule
@@
 	\end{center}
-	\caption{Regret in problems of size $(10, 20)$ after $250$ questions over $5$ runs. Where $p$ represents the number of questions asked to the committee.}
+	\caption{Average regret in problems of size $(10, 20)$ after $250$ questions over $5$ runs. Where $p$ represents the number of questions asked to the committee.}
 	\label{fig:p}

### 2020-09-10 draft.tex
Comment

@@
 %\end{align}
-the weight vector that minimize the $\PMR$ in the worst case.
-We compare $\bar{\w}$ and $\w^{\tau}$ component-wise to find the position $r$ that is most valuable to ask about (the one that maximizes $\abs{\bar{\w}_r - \w^{\tau}_r}$), and choose $\lambda$ as the middle of the interval of possible values for that rank.
+the weight vector that minimize the $\PMR$ in the worst case. \commentOC{Changed this.} Define the spread at rank $r$ as $\sum_{k \in \set{0, 1, 2}}\abs{\bar{\w}_{r + k} - \w^{\tau}_{r + k}}$.
+We compare $\bar{\w}$ and $\w^{\tau}$ component-wise to find the position $r$ that is most valuable to ask about (the one that maximizes the spread at $r$), and choose $\lambda$ as the middle of the interval of possible values for that rank.
 We then evaluate, for each candidate question, the minimax regret for the two possible answers; finally we choose the best according to $\leximax$.

### 2020-09-10 AAMAS2021/minimax.tex
Merge and Agent Preferences

@@
 
-\title{Simultaneous Elicitation of Scoring Rule and Agents Preferences for Robust Winner Determination}
+\title{Simultaneous Elicitation of Scoring Rule and Agent Preferences for Robust Winner Determination}
 
@@
 Recently, the assumption of full preference information has been questioned by a number of researchers and several methods for eliciting preferences have been proposed.
-In this paper we go one step further and we assume that both the voting rule and the agents' preferences are partially specified.
+In this paper we go one step further and we assume that both the voting rule and the agent preferences are partially specified.
 Focusing on positional scoring rules, we assume that the chair, while  not able to give a precise definition of the rule, is capable of answering simple questions  requiring to pick a winner from a specific  example profile.
@@
 Requiring agents to express full preference orderings can be prohibitively costly (in terms of cognitive and communication cost).
-This observation has motivated a number of recent works considering social choice with partial preference orders \citep{Xia2008, Pini2009, Konczak05} and incremental elicitation \citep{Kalech2011, Lu2011, Naamani-Dery2015} of agents’ preferences.
+This observation has motivated a number of recent works considering social choice with partial preference orders \citep{Xia2008, Pini2009, Konczak05} and incremental elicitation \citep{Kalech2011, Lu2011, Naamani-Dery2015} of agent preferences.
 \\ Furthermore, it is often difficult for non-expert users to formalize a voting rule on the basis of some generic preferences over a desired aggregation method.
@@
 
-In this paper we focus on positional scoring rules, that are a particularly common method used to aggregate rankings, and we assume that both the agents’ preferences and the social choice rule are partially specified.
+In this paper we focus on positional scoring rules, that are a particularly common method used to aggregate rankings, and we assume that both the agent preferences and the social choice rule are partially specified.
 We develop methods for computing the minimax-optimal
@@
 We then discuss several heuristics that determine queries, either to an agent or to the chair, that quickly reduce minimax regret.
-While previous works have considered either partial information about the agents’
-preferences or a partially specified aggregation method, we do not know of any work considering both sources of uncertainty at the same time.
+While previous works have considered either partial information about the agent preferences or a partially specified aggregation method, we do not know of any work considering both sources of uncertainty at the same time.
 
-%In this paper we consider that both the agents’ preferences and the social choice rule are partially specified and we develop methods for computing the minimax-optimal alternative under these assumptions.
+%In this paper we consider that both the agent preferences and the social choice rule are partially specified and we develop methods for computing the minimax-optimal alternative under these assumptions.
 %changed from: We develop methods for computing the minimax-optimal alternative for scoring rules with partial agent preference information and partial information about the weights of the scoring rule.
@@
 \label{sec:mmr}
-In this paper, we consider a setting where both the agents' preferences and the preferences of the chair about the voting rule are incomplete.
+In this paper, we consider a setting where both the agent preferences and the preferences of the chair about the voting rule are incomplete.
 Some authors have considered possible and necessary winners assuming a partial profile  \citep{Xia2008} or assuming an incompletely specified scoring rule \citep{Viappiani2018};
@@
 
-In this work, we consider the simultaneous presence of uncertainty in agents' preferences and in weights.
+In this work, we consider the simultaneous presence of uncertainty in agent preferences and in weights.
 Using {\em maximum regret} to quantify the worst-case error, the alternatives that minimize this error are selected as tied winners, providing us with a form of robust optimization.
@@
 By picking as consensus choice
-an alternative associated with minimax regret, we can provide a recommendation that gives worst-case guarantees, giving some robustness in face of uncertainty (due to both not knowing the agents' preferences and the weights used in the aggregation).
+an alternative associated with minimax regret, we can provide a recommendation that gives worst-case guarantees, giving some robustness in face of uncertainty (due to both not knowing the agent preferences and the weights used in the aggregation).
 In cases of ties in minimax regret, we can either decide to return all minimax alternatives $A^*_{\pprofile, W}$ as winners or to pick just one of them using some tie-breaking strategy.
@@
 
-The remainder of this Section is structured as follows.
+The remainder of this section is structured as follows.
 First of all, we discuss the different types of questions that can be asked to the agents and to the chair, and the way responses are handled.
@@
 %Another common type of queries are {\em top-k}, asking to each agent her $k$ most preferred alternatives.
-The effect of a response to a question asked to an agent is the increase in our knowledge about the agents' rankings, thus augmenting the partial profile $\pprofile$. 
+The effect of a response to a question asked to an agent is the increase in our knowledge about the agent rankings, thus augmenting the partial profile $\pprofile$. 
 If agent $j$ answers a comparison query stating that alternative $a$ is preferred to $b$, then the partial order $\ppref_j$ is augmented with $a \ppref_j b$ and by transitive closure.
@@
 \paragraph{Elicitation strategies}
-We develop several elicitation strategies for simultaneous elicitation of agents' preferences and of the scoring rule.
-While it is of course possible to first fully elicit the agents’ preferences and afterwards elicit weights, we also want to propose interleaved approaches and compare them experimentally.
+We develop several elicitation strategies for simultaneous elicitation of agent preferences and of the scoring rule.
+While it is of course possible to first fully elicit the agent preferences and afterwards elicit weights, we also want to propose interleaved approaches and compare them experimentally.
 Indeed, it can be beneficial to split efforts asking questions to the chair and to agents, depending on which is estimated to be more informative.
@@
 This strategy first decides with a probability of $1/2$ each whether it will ask a question about weights or a question about a preference ordering (unless the profile is already known entirely).
-If it opted for a question about weights, it draws one rank in $1 ≤ r ≤ m-2$ equiprobably \commentOC{Isn’t this $1 ≤ r$?} \commentBN{Yep.}, takes the middle of the interval of values for $\lambda$ that are still possible considering our knowledge so far, and asks whether $w_r - w_{r+1} ≥ \lambda (w_{r+1} - w_{r+2})$.
+If it opted for a question about weights, it draws one rank in $1 ≤ r ≤ m-2$ equiprobably, takes the middle of the interval of values for $\lambda$ that are still possible considering our knowledge so far, and asks whether $w_r - w_{r+1} ≥ \lambda (w_{r+1} - w_{r+2})$.
 The intervals are initialized to $[1, n]$.
@@
 the weight vector that minimize the $\PMR$ in the worst case.
-We compare $\bar{\w}$ and $\w^{\tau}$ component-wise to find the position $r$ that is most valuable to ask about (the one that maximizes $\abs{\bar{\w}_r - \w^{\tau}_r}$), and choose $\lambda$ as the middle of the interval of possible values for that rank.
+\commentOC{Changed this.} Define the spread at rank $r$ as $\sum_{k \in \set{0, 1, 2}}\abs{\bar{\w}_{r + k} - \w^{\tau}_{r + k}}$.
+We compare $\bar{\w}$ and $\w^{\tau}$ component-wise to find the position $r$ that is most valuable to ask about (the one that maximizes the spread at $r$), and choose $\lambda$ as the middle of the interval of possible values for that rank.
 After having selected the candidate questions, we apply the Pessimistic strategy.
@@
 An other important direction is the extension to voting rules beyond scoring rules.
-%Regret-based elicitation allows to determine near-optimal winners using only few information about the agents' preferences.
+%Regret-based elicitation allows to determine near-optimal winners using only few information about the agent preferences.
 

### 2020-10-01 AAMAS2021/minimax.tex
temporary abstract

@@
 In the classical setting, the voting rule is fixed beforehand and full information concerning the preferences of the agents is provided.
-Recently, the assumption of full preference information has been questioned by a number of researchers and several methods for eliciting preferences have been proposed.
-In this paper we go one step further and we assume that both the voting rule and the agent preferences are partially specified.
+However, requiring the agents to express full preference orderings can be costly, and formalizing a voting rule it is not an easy task.
+Methods for eliciting the voting rule when the preferences of the agents are completely known have been proposed, as well as techniques that consider the opposite scenario.
+However, both of them may be unknown.
+This paper addresses this case, and proposes a method which permits to obtain recommendations without requiring full knowledge of either.
 Focusing on positional scoring rules, we assume that the chair, while  not able to give a precise definition of the rule, is capable of answering simple questions  requiring to pick a winner from a specific  example profile.

### 2020-10-01 AAMAS2021/minimax.tex
my abstract proposition

@@
 Social choice deals with the problem of determining a consensus choice from the preferences of different agents (voters).
-In the classical setting, the voting rule is fixed beforehand and full information concerning the preferences of the agents is provided.
-However, requiring the agents to express full preference orderings can be costly, and formalizing a voting rule it is not an easy task.
+In the classical setting, the voting rule is fixed beforehand and full information regarding the preferences of the agents is provided.
+In practice, this is not always the case.
+Requiring the agents to express full preference orderings can be costly, and formalizing a voting rule is not an easy task for non-expert users.
 Methods for eliciting the voting rule when the preferences of the agents are completely known have been proposed, as well as techniques that consider the opposite scenario.
-However, both of them may be unknown.
-This paper addresses this case, and proposes a method which permits to obtain recommendations without requiring full knowledge of either.
+However, there may be cases where both of them are only partially known.
+This paper considers both sources of uncertainty at the same time, and proposes a method able to recommend a consensus choice without requiring full knowledge of either.
 Focusing on positional scoring rules, we assume that the chair, while not able to give a precise definition of the rule, is capable of answering simple questions requiring to pick a winner from a specific example profile.
-Moreover, the preferences of the agents are incrementally acquired by asking comparison queries.
+In addition, the preferences of the agents are incrementally acquired by asking comparison queries.
 In this setting, we propose a method for robust approximate winner determination with minimax regret.
-We also provide an interactive elicitation protocol based on minimax regret and develop several query strategies that interleave questions to the chair and questions to the agents in order to attempt to acquire the most relevant information in order to quickly converge to optimal or a near-optimal alternative.
+We also provide an interactive elicitation protocol based on minimax regret and develop several query strategies which attempt to acquire the most relevant information in order to quickly converge to optimal or a near-optimal alternative.
 \end{abstract}

### 2020-10-01 AAMAS2021/minimax.tex
anonymous
chair
Merged prop abstract

--- 2020-10-01 AAMAS2021/minimax.tex
@@
 
-\documentclass[sigconf]{aamas} 
-%\documentclass[sigconf,anonymous]{aamas}
+%\documentclass[sigconf]{aamas} 
+\documentclass[sigconf, anonymous]{aamas}
 
@@
 \begin{abstract}
-Social choice deals with the problem of determining a consensus choice from the preferences of different agents (voters).
+Social choice deals with the problem of determining a consensus choice from the preferences of different agents.
 In the classical setting, the voting rule is fixed beforehand and full information concerning the preferences of the agents is provided.
-However, requiring the agents to express full preference orderings can be costly, and formalizing a voting rule it is not an easy task.
+This assumption of full preference information has recently been questioned by a number of researchers.
 Methods for eliciting the voting rule when the preferences of the agents are completely known have been proposed, as well as techniques that consider the opposite scenario.
-However, both of them may be unknown.
-This paper addresses this case, and proposes a method which permits to obtain recommendations without requiring full knowledge of either.
+%, viewing the voting rule as representing the preference of the chair.
+This article goes one step further by tackling one important new case, namely, when both the voting rule and the agents preferences are partially known.
+It also permits to obtain a progressively refined recommendation without requiring to achieve full knowledge of either sort of information.
+%However, there may be cases where both of them are only partially known.
+%This paper considers both sources of uncertainty at the same time, and proposes a method able to recommend a consensus choice without requiring full knowledge of either.
+This is useful because providing such information is often costly: the chair may find it hard to specify a rule completely; voters may need time to form reflective preferences.
 Focusing on positional scoring rules, we assume that the chair, while not able to give a precise definition of the rule, is capable of answering simple questions requiring to pick a winner from a specific example profile.
-Moreover, the preferences of the agents are incrementally acquired by asking comparison queries.
+In addition, the preferences of the agents are incrementally acquired by asking comparison queries.
 In this setting, we propose a method for robust approximate winner determination with minimax regret.
-We also provide an interactive elicitation protocol based on minimax regret and develop several query strategies that interleave questions to the chair and questions to the agents in order to attempt to acquire the most relevant information in order to quickly converge to optimal or a near-optimal alternative.
+We also provide an interactive elicitation protocol based on minimax regret and develop several query strategies that question the chair and the agents in order to acquire the most relevant information for quickly converging to a near-optimal alternative.
 \end{abstract}
@@
 
-The traditional approach to social choice assumes that both the social choice function and the full preference orderings of the agents are expressed beforehand. These represent two strong hypothesis.
+The traditional approach to social choice assumes that both the social choice function and the full preference orderings of the agents (voters) are expressed beforehand.
+These represent two strong hypothesis.
 Requiring agents to express full preference orderings can be prohibitively costly (in terms of cognitive and communication cost).
@@
 	\end{center}
-	\caption{Average regret in problems of size $(10, 20)$ after $250$ questions over $5$ runs. Where $p$ represents the number of questions asked to the committee.}
+	\caption{Average regret in problems of size $(10, 20)$ after $250$ questions over $5$ runs. Where $p$ represents the number of questions asked to the chair.}
 	\label{fig:p}

### 2020-10-02 minimax.tex
solved warnings

--- 2020-10-01 AAMAS2021/minimax.tex
@@
 
-Aggregation of preference information is a central task in many computer systems (recommender systems, search engines, etc).
+èàù Aggregation of preference information is a central task in many computer systems (recommender systems, search engines, etc).
 In many situations, such as in group recommender systems, the goal is to find a consensus choice.
@@
 Then the badness of the question in the worst case is:
-\[\max_{i=1,2} \MMR(\pprofile_i,W_i) \]
+\begin{align}
+	\max_{i=1,2} \MMR(\pprofile_i,W_i)
+\end{align}
 This badness measure gives a way of picking questions among a set of possible questions, by picking one that minimizes ths measure of minimax regret {\em a posteriori}. 

### 2020-10-02 minimax.tex
cleaning

@@
 
-\acmSubmissionID{???}
+\acmSubmissionID{554}
 
@@
 \affiliation{
-	\institution{LAMSADE, UMR 7243, CNRS and Universit\'e Paris Dauphine, PSL Research University}
-	\city{Paris}
+	\institution{Université Paris-Dauphine, Université PSL, CNRS, LAMSADE}
+	\city{75016 Paris}
 	\state{France}}
@@
 
-\keywords{Uncertainty in AI, Computational Social Choice, Knowledge Representation and Reasoning}
+\keywords{Uncertainty in AI, Computational Social Choice, Preference Elicitation}
 
@@
 
-èàù Aggregation of preference information is a central task in many computer systems (recommender systems, search engines, etc).
+Aggregation of preference information is a central task in many computer systems (recommender systems, search engines, etc).
 In many situations, such as in group recommender systems, the goal is to find a consensus choice.
@@
 First of all, $\Regret(x, \profile, \w)$ is the “regret” of selecting $x$ as a winner instead of choosing the optimal alternative under $\profile$ and $\w$:
-\[\Regret(x, \profile, \w) = \max_{y \in A} s(y; \profile,\w) - s(x; \profile, \w).\]
+\begin{align} 
+	\Regret(x, \profile, \w) = \max_{y \in A} s(y; \profile,\w) - s(x; \profile, \w).
+\end{align}
 The pairwise max regret $\PMR(x,y;\pprofile,W)$ of $x$ relative to $y$ given partial profile $\pprofile$ and the set of weights $W$
@@
 In particular, we want to acquire constraints of the type:
-\[ w_{r} - w_{r+1} \geq \lambda (w_{r+1} - w_{r+2}) \] 
+\begin{align}
+	w_{r} - w_{r+1} \geq \lambda (w_{r+1} - w_{r+2})
+\end{align}
 for $r \in \{1,\ldots,m-2\}$, relating the difference between the importance of ranks $r$ and $r+1$ with the difference between ranks $r+1$ and $r+2$.
@@
 %\item {\em Volumetric} strategy: chooses an agent $i$ and a query that maximizes the number of new pairwise preferences revealed given the worst response.
-
+\balance
 \section{Empirical Evaluation} 
@@
 
-\balance
-
 \section{Conclusions}  

### 2020-10-04 minimax.tex
Solved a few warnings

@@
 \input{preamble/packages}
+%TODO consider removing anyfontsize and mathrsfs when submitting.
+They are needed for the \mathscr command at Olivier’s box (probably due to some outdated package) and for removing a warning about rsfs font size.
+\usepackage{anyfontsize}
+\usepackage{mathrsfs}
 %\input{preamble/redac}
@@
 
+\begin{CCSXML}
+<ccs2012>
+   <concept>
+       <concept_id>10010147.10010178.10010187</concept_id>
+       <concept_desc>Computing methodologies~Knowledge representation and reasoning</concept_desc>
+       <concept_significance>500</concept_significance>
+       </concept>
+ </ccs2012>
+\end{CCSXML}
+
+\ccsdesc[500]{Computing methodologies~Knowledge representation and reasoning}
+
 %%% Use this command to specify a few keywords describing your work.
@@
 \section{Introduction}
-
 Aggregation of preference information is a central task in many computer systems (recommender systems, search engines, etc).
@@
 \begin{claim} \label{claim:completion}
-	There exists a completion $\hat{\profile} \in C(\pprofile)$ such that $\PMR(x,y; \pprofile, W) = \max_{\w \in W} [ s(y; \hat{\profile}, \w) - s(x; \hat{\profile}, \w) ]$ and such that the linear order $\hat{v}_{j}$ of each agent $j$ satisfies:
+	There exists a completion $\hat{\profile} \in C(\pprofile)$ of the profile $\profile$ such that $\PMR(x,y; \pprofile, W) = \max_{\w \in W} [ s(y; \hat{\profile}, \w) - s(x; \hat{\profile}, \w) ]$ and such that the linear order $\hat{v}_{j}$ of each agent $j$ satisfies:
 	\begin{align} 
@@
 \paragraph{Building concrete questions for the chair}
-As we assume the weights constitute the utility components of the chair, it might be reasonable to assume
-%as we do here, 
-that the chair is able to answer such abstract questions in our setting.
+As we assume that the weights constitute the utility components of the chair, it might be reasonable to assume that the chair is able to answer such abstract questions in our setting.
 However, it is important to make sure that a question can also, in principle, be asked in a more concrete way, in terms of winners of example profiles.

### 2020-10-04 minimax.tex
Solved pbl with autonum & hyperref
Hiding CCS

@@
 
+\PassOptionsToPackage{hypertexnames=false, pdfusetitle, linkbordercolor={1 1 1}, citebordercolor={1 1 1}, urlbordercolor={1 1 1}}{hyperref}
 %\documentclass[sigconf]{aamas} 
@@
 %%% Please replace this example with code appropriate for your own paper.
-
-\begin{CCSXML}
-<ccs2012>
-   <concept>
-       <concept_id>10010147.10010178.10010187</concept_id>
-       <concept_desc>Computing methodologies~Knowledge representation and reasoning</concept_desc>
-       <concept_significance>500</concept_significance>
-       </concept>
- </ccs2012>
-\end{CCSXML}
-
+%TODO remove this before submission. This only serves to suppress the warning, but nobody seems to want this.
+\settopmatter{printccs=false}
 \ccsdesc[500]{Computing methodologies~Knowledge representation and reasoning}

### 2020-10-04 minimax.tex
Finished solving warnings

@@
 \newcommand{\commentBN}[1]{\textcolor{red}{\small$\big[$BN: #1$\big]$}}
+
+%TODO remove this before submission, check vboxes
+\vbadness=9000
 
@@
 
-\sisetup{round-mode=places, round-precision=2, table-figures-integer=1, table-figures-decimal=2}
+\sisetup{round-mode=places, round-precision=2, table-figures-integer=2, table-figures-decimal=2}
 \begin{table}
 	\begin{center}
-		\begin{tabular}{S[table-figures-integer=2, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
+		\begin{tabular}{S[table-figures-integer=3, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
 			\toprule
@@
 	\begin{center}
-		\begin{tabular}{S[table-figures-integer=2, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
+		\begin{tabular}{S[table-figures-integer=3, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
 			\toprule
@@
 \bibliographystyle{ACM-Reference-Format} 
+%TODO remove this when submitting, and consider solving the vertical overflows
+\vfuzz=5pt
 \bibliography{biblio}

### 2020-10-05 minimax.tex
Plan about conclusions

@@
 %In particular, our query strategies focus simultaneously on reduction of relevant preference and voting rule uncertainty.
+
+\paragraph{Experimental conclusions}
+Our approach permits to compare experimentally strategies that question the chair, the voters, or both.
+We describe informally here a few of the conclusions stemming from these experiments, given a problem involving $m$ alternatives and $n$ voters.
+First, low levels of regret can be reached by asking approximately $m n$ questions to the voters and $m$ questions to the chair.
+Second, the decrease in MMR is approximately linear with the number of questions asked, except when the regret approaches zero.
+Third, the value of information of one question to the chair is similar to the value of information of one question to a voter (in the ranges we considered).
+Knowing this permits to choose the questioning strategy wisely depending on the estimated cost of each kind of question, which depends on the application.
 
@@
 We develop several elicitation strategies for simultaneous elicitation of agent preferences and of the scoring rule.
-While it is of course possible to first fully elicit the agent preferences and afterwards elicit weights, we also want to propose interleaved approaches and compare them experimentally.
-Indeed, it can be beneficial to split efforts asking questions to the chair and to agents, depending on which is estimated to be more informative.
+While it is of course possible to first fully elicit the agent preferences and afterwards elicit weights, we want to investigate experimentally approaches that are able to recommend winning alternatives before obtaining complete knowledge of the profile or the rule.
+%Indeed, it can be beneficial to split efforts asking questions to the chair and to agents, depending on which is estimated to be more informative.
 We define here the various strategies we tested experimentally. A strategy tells us, given the current partial knowledge $(\pprofile, W)$, which question should be asked next.
@@
 \commentBN{Change the text according to the new tables.}
+
+1. Pessimistic is feasible and much better than Random
+	Graph featuring (5, 10, 150, 200 runs), Random, Pess, L. pess, Elitist.
+	And table like table 1.
+2. Limited pessimistic performs well.
+	Reach regret: $n/10$. For this, we need $m^x n$ questions. TODO Olivier: find $x$. TODO Beatrice: check and compile results in a table specifically for this (see: function regret by k).
+	Almost as good as Pess and better than the Elitist one (see previous graphs or table)
+	Much faster [do this later]
+3. Decrease in MMR is linear with nb of questions
+	include nice graph of Beatrice.
+4. Value of information qC VS qV with 2 phases and 2phases VS interleaving
+	A question to the chair has a similar value (in regret) as a qV.
+	Interleaving $k$ questions is similar to asking $p$ questions to the chair first and then $k - p$ to the voters when $p$ is chosen optimally. 
+5. Limited pessimistic approx Limited optimistic
 

### 2020-10-05 minimax.tex
More of the plan decided during meeting

@@
 	Almost as good as Pess and better than the Elitist one (see previous graphs or table)
-	Much faster [do this later]
+	Much faster [do this much later]
 3. Decrease in MMR is linear with nb of questions
-	include nice graph of Beatrice.
+	Redo nice graph of Beatrice with same sizes.
 4. Value of information qC VS qV with 2 phases and 2phases VS interleaving
-	A question to the chair has a similar value (in regret) as a qV.
-	Interleaving $k$ questions is similar to asking $p$ questions to the chair first and then $k - p$ to the voters when $p$ is chosen optimally. 
-5. Limited pessimistic approx Limited optimistic
+	Interleaving $k$ questions is similar to asking $p$ questions to the chair first and then $k - p$ to the voters when $p$ is chosen optimally. [do this a bit later]
+	A question to the chair has a similar value (in regret) as a qV: use the graph summarized by Olivier. Check prop. qC. Check on other sizes.
+5. Limited pessimistic approx Limited optimistic [do this much later]
 

### 2020-10-05 minimax.tex
Started chng descr strats

@@
 %TODO remove this before submission, check vboxes
-\vbadness=9000
+\vbadness=10000
 
@@
 The \strat{Random} strategy gives a baseline for comparison and informs about the difficulty of an elicitation problem. 
-This strategy first decides with a probability of $1/2$ each whether it will ask a question about weights or a question about a preference ordering (unless the profile is already known entirely).
+It admits a parameter $\pi \in [0, 1]$.
+This strategy first decides whether it will ask a question about weights (probability $\pi$) or a question about a preference ordering (probability $1-\pi$).
 If it opted for a question about weights, it draws one rank in $1 ≤ r ≤ m-2$ equiprobably, takes the middle of the interval of values for $\lambda$ that are still possible considering our knowledge so far, and asks whether $w_r - w_{r+1} ≥ \lambda (w_{r+1} - w_{r+2})$.
@@
 We expect this strategy to perform very well, but only for very small problem instances: its complexity is in $O(n^2 m^5)$, because we consider $O(m^2)$ questions for each agent and need for each question to compute $\MMR$ twice, whose complexity is $O(nm^3)$.
-For small dimensions, it estimates an upper bound to the possible quality of a strategy.
+For small dimensions, it estimates an upper bound to the possible quality of a myopic strategy.
 

### 2020-10-05 minimax.tex
Started chng Limited

@@
 
-The \strat{Limited pessimistic} strategy uses the same criterion as the pessimistic strategy, but limiting it to a small set of $n+1$ candidate questions: one per agent, and one to the chair.
+The \strat{Limited pessimistic} strategy uses the same criterion as the pessimistic strategy, but limiting it to a small set of $n + m$ candidate questions: one per agent, and one per rank.
 Let $(x^{*},\bar{y}, \bar{\profile}, \bar{\w})$ be the current solution of the minimax regret, where $\bar{y}, \bar{\profile}, \bar{\w}$ are, respectively, the choice of $y$, the completion of the profile and the selection of weights for which $x^{*}$ is the minimax optimal alternative.

### 2020-10-05 minimax.tex
small changes

--- 2020-10-05 minimax.tex
@@
 %, viewing the voting rule as representing the preference of the chair.
+
 This article goes one step further by tackling one important new case, namely, when both the voting rule and the agents preferences are partially known.
@@
 This is useful because providing such information is often costly: the chair may find it hard to specify a rule completely; voters may need time to form reflective preferences.
+
 Focusing on positional scoring rules, we assume that the chair, while not able to give a precise definition of the rule, is capable of answering simple questions requiring to pick a winner from a specific example profile.
@@
 Requiring agents to express full preference orderings can be prohibitively costly (in terms of cognitive and communication cost).
-This observation has motivated a number of recent works considering social choice with partial preference orders \citep{Xia2008, Pini2009, Konczak05} and incremental elicitation \citep{Kalech2011, Lu2011, Naamani-Dery2015} of agent preferences.
+This observation has motivated a number of recent works considering social choice with partial preference orders \citep{Xia2008, Pini2009, Konczak05} and incremental elicitation \citep{Kalech2011, Lu2011, Naamani-Dery2015,Benabbou2016} of agent preferences.
 \\ Furthermore, it is often difficult for non-expert users to formalize a voting rule on the basis of some generic preferences over a desired aggregation method.
@@
 We consider a set $A$ of $m$ alternatives (products, restaurants, movies, public projects, job candidates, etc.) and a set $\set{1, …, n}$ of agents (voters).
-Each agent $j$ comes from an infinite set $\N$ of potential agents and is associated to her “real” preference order $\pref_j \in \linors$ which is a linear order (a connected, transitive, asymmetric relation) over the alternatives.
+Each agent $j$ comes from an infinite set $\N$ of potential agents and is associated to her “real” preference order $\pref_j \, \in \!\linors$ which is a linear order (a connected, transitive, asymmetric relation) over the alternatives.
 Following the social choice nomenclature, we call {\em profile} the association of a preference to each agent, considering a subset of agents from the set $\N$, and denote a profile by $(\pref_1,\ldots,\pref_n)$.
@@
 Let $V$ be the set of possible preference profiles (the union, for any integer, $n$ of the $n$-fold cartesian product of the linear orders over the alternatives).
-A social choice function $f : V \rightarrow \powersetz{A}$ associates a profile with a set of winners, where $\powersetz{A}$ represents the set of subsets of $A$ except for the emptyset.
-(Sets are used for tied winners.)
+A social choice function $f : V \rightarrow \powersetz{A}$ associates a profile with a set of winners, where $\powersetz{A}$ represents the set of subsets of $A$ except for the emptyset (sets are used for tied winners).
 Among the many possible social choice functions, we consider {\em positional scoring rules (PSR)}, which attach weights to positions according to the vector $(w_1, \ldots, w_m)$ (also called the scoring vector).
@@
 
-In this work we assume fixed, but unknown to us, a profile $\profile^*$, representing the preferences $\pref_j^*$ of the agents, and a weight vector $\w^*$, representing the preferences of the chair, and we want to reason about partial preference information concerning those objects.
+In this work we assume a fixed, but unknown to us, profile $\profile^*$, representing the preferences $\pref_j^*$ of the agents, and a weight vector $\w^*$, representing the preferences of the chair, and we want to reason about partial preference information concerning those objects.
 At a given time, our knowledge of agent $j$'s preference is encoded by a partial order over the alternatives, thus a transitive and asymmetric binary relation, denoted by $\ppref_j$. 
@@
 In this paper, we consider a setting where both the agent preferences and the preferences of the chair about the voting rule are incomplete.
-Some authors have considered possible and necessary winners assuming a partial profile  \citep{Xia2008} or assuming an incompletely specified scoring rule \citep{Viappiani2018};
+Some authors have considered possible and necessary winners assuming a partial profile  \citep{Kalech2011,Xia2008} or assuming an incompletely specified scoring rule \citep{Stein1994};
 however, we note that, in typical settings, there are no necessary winner and too many possible winners.
@@
 	Almost as good as Pess and better than the Elitist one (see previous graphs or table)
-	Much faster [do this much later]
+	Much faster [do this later]
 3. Decrease in MMR is linear with nb of questions
-	Redo nice graph of Beatrice with same sizes.
+	include nice graph of Beatrice.
 4. Value of information qC VS qV with 2 phases and 2phases VS interleaving
-	Interleaving $k$ questions is similar to asking $p$ questions to the chair first and then $k - p$ to the voters when $p$ is chosen optimally. [do this a bit later]
-	A question to the chair has a similar value (in regret) as a qV: use the graph summarized by Olivier. Check prop. qC. Check on other sizes.
-5. Limited pessimistic approx Limited optimistic [do this much later]
+	A question to the chair has a similar value (in regret) as a qV.
+	Interleaving $k$ questions is similar to asking $p$ questions to the chair first and then $k - p$ to the voters when $p$ is chosen optimally. 
+5. Limited pessimistic approx Limited optimistic
 

### 2020-10-05 minimax.tex
Sects 4 (mostly) done and 5 prepared

--- 2020-10-05 minimax.tex
@@
 
-The \strat{Pessimistic} strategy selects the question that leads to minimal regret in the worst case, considering both possible answers to the question.
+The \strat{Pessimistic} strategy considers the same candidate questions as the Random strategy, but instead of picking one among those randomly, selects the question that leads to minimal regret in the worst case, considering both possible answers to the question.
 Assume that a question leads to the possible new knowledge states $(\pprofile_1, W_1)$ and $(\pprofile_2, W_2)$, depending on the answer.
@@
 This badness measure gives a way of picking questions among a set of possible questions, by picking one that minimizes ths measure of minimax regret {\em a posteriori}. 
-%Note that other aggregators than $\max$ can be used as well.
-%We use the $\max$ operator because \citet{Cailloux2014} reported that pessimistic aggregation works much better than optimistic aggregation, although our experiments in this context suggested a weak impact of that choice on the performance of the strategy.
+Note that other aggregators than $\max$ can be used as well. 
+We use the $\max$ operator because \citet{Cailloux2014} reported that pessimistic aggregation works much better than optimistic aggregation, although our experiments in this context suggested a weak impact of that choice on the performance of the strategy.
 However, to avoid the absorption property of max, we adopt the $\leximax$ criterion as an aggregator: if the maximal $\MMR$ of two questions are equal, then it considers the other $\MMR$ values, that are the one associated to the opposite answer, preferring the question with the lowest value.
+(Technically, instead of applying a pure lexicographic aggregation, which is very sensitive to small errors due to floating-point computations, we apply a weighted sum between the maximal and the minimal $\MMR$ values, with a predominant weight to the maximal one.)
 We expect this strategy to perform very well, but only for very small problem instances: its complexity is in $O(n^2 m^5)$, because we consider $O(m^2)$ questions for each agent and need for each question to compute $\MMR$ twice, whose complexity is $O(nm^3)$.
@@
 Let $(x^{*},\bar{y}, \bar{\profile}, \bar{\w})$ be the current solution of the minimax regret, where $\bar{y}, \bar{\profile}, \bar{\w}$ are, respectively, the choice of $y$, the completion of the profile and the selection of weights for which $x^{*}$ is the minimax optimal alternative.
-The \strat{Limited pessimistic} strategy first selects $n$ candidates questions to the agents using the heuristic proposed by \citet{Lu2011}.
-Considering agent $j$, either $x^{*} \ppref_j \bar{y}$, or $\bar{y} \ppref_j x^{*}$, or $x^{*}$ and $\bar{y}$ are incomparable in $\ppref_j$.
-As shown in the proof of Claim \ref{claim:completion}, in order to increase $\PMR(x^{*},\bar{y})$, an adversary should place as many alternatives as he can above $x^{*}$ in the first case, and between $\bar{y}$ and $x^{*}$ in the second.
-An intuitive way to reduce the pairwise max regret would be, therefore, to ask questions involving such alternatives \commentOC{(with equal likelyhood?)}\commentBN{We are not asking questions yet.
-We select as a candidate question the one corresponding to the situation.
-If you mean "what if there are several alternatives that can be placed between the two?" then yes, we pick one equiprobably.}, hoping for an answer that would prevent the adversary to play his best game.
-If $x^{*}$ and $\bar{y}$ are incomparable, then the candidate question to agent $j$ simply consists in comparing the two alternatives.
-To define the candidate question to the chair, consider
-%\begin{align}
-$\w^\tau = \argmin_{\w \in W} s(\bar{y}; \bar{\profile}, \w) - s(x^{*}; \bar{\profile}, \w)$,
-%\end{align}
-the weight vector that minimize the $\PMR$ in the worst case.
-\commentOC{Changed this.} Define the spread at rank $r$ as $\sum_{k \in \set{0, 1, 2}}\abs{\bar{\w}_{r + k} - \w^{\tau}_{r + k}}$.
-We compare $\bar{\w}$ and $\w^{\tau}$ component-wise to find the position $r$ that is most valuable to ask about (the one that maximizes the spread at $r$), and choose $\lambda$ as the middle of the interval of possible values for that rank.
-After having selected the candidate questions, we apply the Pessimistic strategy.
-We evaluate, for each of the questions, the minimax regret for the two possible answers and we choose the best according to $\leximax$.
+The \strat{Limited pessimistic} strategy first selects $n$ candidates questions to the agents using the heuristic proposed by \citet{Lu2011}: for each agent $j$, if $x^*$ and $\bar{y}$ are incomparable in $\ppref_j$, the candidate question concerns the pair $(x^*, \bar{y})$, otherwise, the candidate question concerns the pair $(x^*, z)$ for some $z$ incomparable to $x^*$ (randomly chosen), or if none such $z$ exist, the pair $(\bar{y}, z)$ for some $z$ incomparable to $\bar{y}$, or, if both $x^*$ and $\bar{y}$ are comparable to every alternatives in $\ppref_j$, any incomparable pair is picked at random.
+To understand the intuition behind favoring these two alternatives for our questions, recall that, as shown in the proof of \cref{claim:completion}, in order to increase $\PMR(x^{*},\bar{y})$, an adversary should place as many alternatives as she can above $x^{*}$ if $x^* \ppref_j \bar{y}$, and between $\bar{y}$ and $x^{*}$ if $\bar{y} \ppref_j x^*$.
+\commentOC{I do not understand the reasoning in the next sentence.}
+An intuitive way to reduce the pairwise max regret would be, therefore, to ask questions involving such alternatives, hoping for an answer that would prevent the adversary to play his best game. 
+The candidate questions to the chair are determined as in the Random and Pessimistic strategies.
+After having selected the candidate questions, we apply the Pessimistic strategy: we evaluate, for each of the questions, the minimax regret for the two possible answers and we choose the best according to $\leximax$.
 
-Lastly, the \strat{Two phases} strategy is developed in order to investigate the effect of varying the proportion of questions asked to agents and to the chair.
-%The \strat{Two phases - vc} first asks $p$ questions to the agents, then $k-p$ questions to the chair, using in both cases Limited pessimistic to select the specific question.
-The \strat{Two phases - cv} strategy starts with $p$ questions to the chair, then asks to the agents.
-\commentOC{If our XPs exhibit no significant change between vc and cv (or if we don’t have time to run them), I will drop this distinction.}
-It first asks $p$ questions to the chair, then $k-p$ questions to the agents, using in both cases the same method as \strat{Limited pessimistic} to select the specific question. 
-Note that when asking first only questions to the chair, if the obtained knowledge approximates well the scoring vector, then in the second part of the elicitation we fall into the more classical setting of incompleteness of preferences assuming a known voting rule.
+The \strat{Two phases} strategy is developed in order to investigate the effect of varying the proportion of questions asked to agents and to the chair, and compare the performance of asking questions to the chair first or to the voters first.
+The \strat{Two phases - ac} variant first asks $p$ questions to the agents, then $k-p$ questions to the chair, using in both cases Limited pessimistic to select the specific questions; whereas the \strat{Two phases - ca} variant starts with $p$ questions to the chair, then questions the agents.
+%Note that when asking first only questions to the chair, if the obtained knowledge approximates well the scoring vector, then in the second part of the elicitation we fall into the more classical setting of incompleteness of preferences assuming a known voting rule.
 %And vice-versa when asking first questions to the agents, the second part of the elicitation is similar to the setting of incompletely specified scoring rule. 
-%The aim of this strategy is to simulate the current state of the art when considering incomplete preferences.
-In fact, by asking enough questions to the chair we can reduce our problem into a well studied one of incompleteness of preferences knowing the voting rule.
-Moreover, if we invert to whom ask questions first, we fall instead in an already studied case of uncertainty of the voting rule with a known complete profile.
+This strategy also permits to simulate the current state of the art when considering incomplete preferences.
+By asking enough questions to the chair we can reduce our problem into a well studied one of incompleteness of preferences knowing the voting rule.
+Similarly, if we invert to whom ask questions first, we fall instead in an already studied case of uncertainty of the voting rule with a known complete profile.
+
+Finally, the \strat{Elitist} strategy aims at uncovering as quickly as possible the top alternative of each agent. It asks $m-1$ questions to each agent in turn. 
+Given an agent to query $j$, it asks about an alternative currently undominated in $\ppref_j$ and any alternative that it has not yet asked about for that agent, or equivalently, any alternative that is currently incomparable to this alternative.
+This approach guarantees that the top alternative in the ranking of $j$ will be known after having asked $j$ exactly $m-1$ questions.
+After having asked $n (m-1)$ questions to the agents, it questions the chair only, using the same approach as the Limited strategy.
+This strategy can be expected to perform well when the chair assigns an important weight to the first rank, as compared to the other ranks.
+It will be useful to further challenge the Limited strategy, which is not specifically tailored to such a situation.
 
 %\item {\em Volumetric} strategy: chooses an agent $i$ and a query that maximizes the number of new pairwise preferences revealed given the worst response.
-\balance
+
 \section{Empirical Evaluation} 
 \label{sec:experiments}
-\commentBN{Change the text according to the new tables.}
+\commentOC{
+	\begin{enumerate}
+		\item Pessimistic is feasible and much better than Random
+		\begin{itemize}
+			\item Graph featuring (5, 10, 150, 200 runs), Random, Pess, L. pess, Elitist.
+			\item And table like table 1.
+		\end{itemize}
+		\item Limited pessimistic performs well.
+		\begin{itemize}
+			\item Reach regret: $n/10$. For this, we need $m^x n$ questions. TODO Olivier: find $x$. TODO Beatrice: check and compile results in a table specifically for this (see: function regret by k).
+			\item Almost as good as Pess and better than the Elitist one (see previous graphs or table)
+			\item Much faster [do this much later]
+		\end{itemize}
+		\item Decrease in MMR is linear with nb of questions
+		\begin{itemize}
+			\item Redo nice graph of Beatrice with same sizes.
+		\end{itemize}
+		\item Value of information qC VS qV with 2 phases and 2phases VS interleaving
+		\begin{itemize}
+			\item Interleaving $k$ questions is similar to asking $p$ questions to the chair first and then $k - p$ to the voters when $p$ is chosen optimally. [do this a bit later]
+			\item A question to the chair has a similar value (in regret) as a qV: use the graph summarized by Olivier. Check prop. qC. Check on other sizes.
+		\end{itemize}
+		\item Limited pessimistic approx Limited optimistic [do this much later]
+	\end{enumerate}
+}
+Our experiments are described by topic here below. We generally use the following protocol, deviations are indicated below for each experiment.
 
-1. Pessimistic is feasible and much better than Random
-	Graph featuring (5, 10, 150, 200 runs), Random, Pess, L. pess, Elitist.
-	And table like table 1.
-2. Limited pessimistic performs well.
-	Reach regret: $n/10$. For this, we need $m^x n$ questions. TODO Olivier: find $x$. TODO Beatrice: check and compile results in a table specifically for this (see: function regret by k).
-	Almost as good as Pess and better than the Elitist one (see previous graphs or table)
-	Much faster [do this much later]
-3. Decrease in MMR is linear with nb of questions
-	Redo nice graph of Beatrice with same sizes.
-4. Value of information qC VS qV with 2 phases and 2phases VS interleaving
-	Interleaving $k$ questions is similar to asking $p$ questions to the chair first and then $k - p$ to the voters when $p$ is chosen optimally. [do this a bit later]
-	A question to the chair has a similar value (in regret) as a qV: use the graph summarized by Olivier. Check prop. qC. Check on other sizes.
-5. Limited pessimistic approx Limited optimistic [do this much later]
+Having picked a problem size $(m, n)$, a number of questions $k$ and a strategy to test, we randomly generate an “oracle”, containing the true preferences of the agents (i.e.
+the linear orders) and the weights associated with the chair's scoring rule.
+The preferences are generated following an impartial culture assumption: the linear order of each voter is generated independently from the other ones and all have the same probability of appearing.
+The weights are generated by drawing $m-1$ differences randomly with uniform distribution, normalizing them, then ordering them, in order to ensure convexity.
 
+We start with empty knowledge ($\pprofile = (\emptyset_j), W = \W$) about the preference orderings of the agents or the weight differences favored by the chair.
+We obtain the first question to be asked using the strategy under test, as described above.
+We use the oracle to answer the question and update our knowledge, which is thus used to obtain the next question.
+This is repeated until $k$ answers have been obtained, compute the resulting $\MMR$ values along the way for various values of $k$.
+We repeat this whole experiment a variable number of times indicated below, for a given $(m, n, k)$, and report the average resulting $\MMR$ and the standard deviation \textit{sd}.
+
+\subsection{Small size elections}
+Our first experimental result concerns small size situations.
+We picked $m = 5, n = 10$ to illustrate our results (variations around these sizes yield similar conclusions).
+In such situations, we can run the resource-consuming Pessimistic strategy.
+Table x / graph x compares it to other strategies.
+We see that these strategies perform much better than random, even when its parameter $\pi$ is chosen in an optimal way, that is, when the proportion of questions asked to the chair is ideal.
+We also see a first important positive result for applicability of our approach, namely, that it is possible to reach a small regret with a reasonable number of questions in such problems.
+
+\subsection{Limited pessimistic}
+We next investigate the better performing Limited pessimistic strategy, because Pessimistic is too slow to be ran repeatedly on much bigger problem sizes.
+
+\subsection{Our previous presentation}
 \sisetup{round-mode=places, round-precision=2, table-figures-integer=2, table-figures-decimal=2}
@@
 
-We use the following protocol.
-Having picked a problem size $(m, n)$, a number of questions $k$ and a strategy, we randomly generate an “oracle”, containing the true preferences of the agents (i.e.
-the linear orders) and the weights associated with the chair's scoring rule.
-We start with empty knowledge ($\pprofile = (\emptyset_j), W = \W$) about the preference orderings of the agents or the weight differences favored by the chair.
-We obtain the first question to be asked using the selected strategy, as described above.
-We use the oracle to answer the question and update our knowledge, which is thus used to obtain the next question.
-This is repeated until $k$ answers have been obtained.
-Then we compute the resulting $\MMR$.
-We repeat this whole experiment 10 times, for a given $(m, n, k)$, and report the average resulting $\MMR$ and the standard deviation \textit{sd}.
-
 The results are displayed in \cref{fig:55,fig:1020,fig:p}, where strategies are designated by Rnd for Random, Pes. for Pessimistic, L.\ pes. for Limited pessimistic and 2 ph. for Two phases.
@@
 \label{sec:conclusions}
+%TODO balance columns appropriately before submitting
+%\balance
 In this paper we have considered a social choice setting with partial information about the agent's preferences and a partially specified voting rule.

### 2020-10-05 minimax.tex
Minor fmt

@@
 We consider a set $A$ of $m$ alternatives (products, restaurants, movies, public projects, job candidates, etc.) and a set $\set{1, …, n}$ of agents (voters).
-Each agent $j$ comes from an infinite set $\N$ of potential agents and is associated to her “real” preference order $\pref_j \, \in \!\linors$ which is a linear order (a connected, transitive, asymmetric relation) over the alternatives.
+Each agent $j$ comes from an infinite set $\N$ of potential agents and is associated to her “real” preference order ${\pref_j}  \in \linors$ which is a linear order (a connected, transitive, asymmetric relation) over the alternatives.
 Following the social choice nomenclature, we call {\em profile} the association of a preference to each agent, considering a subset of agents from the set $\N$, and denote a profile by $(\pref_1,\ldots,\pref_n)$.

### 2020-10-06 minimax.tex
Table/Plot Comparison and partial Plot Linearity

@@
 	\begin{center}
-		\begin{tabular}{S[table-figures-integer=3, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
+		\resizebox{\columnwidth}{!}{
+		\begin{tabular}{S[table-figures-integer=3, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
 			\toprule
-			{k} & {Rnd} & {sd} & {Pes.} & {sd} & {L.\ pes.} & {sd} \\
+			{k} & {Rd.\tiny{$\pi=0.1$}} & {sd} & {Pes.} & {sd} & {L.\ pes.} & {sd} & {Eli.} & {sd} \\
 			\midrule
-			0 & 10.0 & 0.0 & 10.0 & 0.0 & 10.0 & 0.0\\
-			20 & 9.05 & 0.51 & 7.38 & 0.65 & 6.08 & 0.76\\
-			40 & 7.3 & 0.62 & 4.21 & 1.18 & 2.77 & 1.27\\
-			60 & 6.01 & 0.81 & 1.56 &0.98 & 1.23 & 1.22\\
-			80 & 4.72 & 1.07 & 0.2 & 0.33 & 0.55 & 0.71\\
-			100 & 3.0 & 0.97 & 0.0 &  0.0 & 0.2 & 0.28\\
-			120 & 1.31 & 1.15 & 0.0 & 0.0 & 0.1 & 0.21\\
-			140 & 0.44 & 0.85 & 0.0 & 0.0 & 0.1 & 0.21\\
-			150 & 0.21 & 0.58 & 0.0 & 0.0 & 0.1 & 0.21\\
+			0 & 10.0 & 0.0 & 10.0 & 0.0 & 10.0 & 0.0 & 10.0 & 0.0\\
+			20 & 8.07 & 0.52 & 6.17 & 0.78 & 5.85 & 0.87& 6.32 & 0.61\\
+			40 & 5.26 & 0.88 & 2.98 & 0.99 & 2.57 & 1.05 & 3.37 & 0.83\\
+			60 & 2.37 & 0.93 & 0.77 &0.78 & 0.67 & 0.67 & 2.33 & 1.05\\
+			80 & 0.33 & 0.49 & 0.05 & 0.18 & 0.03 & 0.12 & 2.28 & 1.05\\
+			100 & 0.0 & 0.02 & 0.0 &  0.0 & 0.0 & 0.0& 2.28 & 1.05\\
 			\bottomrule
 		\end{tabular}
+		}
 	\end{center}
-	\caption{Average minimax regret in problems of size $(5, 10)$ after $k$ questions over $25$ runs.}
-	\label{fig:55}
+	\caption{Average minimax regret in problems of size $(5, 10)$ after $k$ questions and $200$ runs.}
+	\label{tab:comparison}
 \end{table}
 
-\begin{table}
-	\begin{center}
-		\begin{tabular}{S[table-figures-integer=3, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
-			\toprule
-			{k} & {Rnd} & {sd} & {L.\ pes.} & {sd??} \\
-			\midrule
-			0 & 20.0 & 0.0 & 20.0 & 0.0 \\
-			50 & 19.81 & 0.12 & 17.19 & 1.2 \\
-			100 & 19.22 & 0.25 & 14.72 & 2.4 \\
-			150 & 18.18 & 0.54 & 12.52 & 3.89 \\
-			200 & 17.05  & 0.29 & 10.57 & 5.14 \\
-			250 & 15.95 & 0.26 & 9.28 & 6.17 \\
-			\bottomrule
-		\end{tabular}
-	\end{center}
-	\caption{Average regret in problems of size $(10, 20)$ after $k$ questions over $5$ runs.}
-	\label{fig:1020}
-\end{table}
+\begin{figure}
+	\centering
+	\includegraphics[width=.45\textwidth]{comparison.png}
+	\caption{Plot in support of \cref{tab:comparison}}
+	\label{fig:comparison}
+\end{figure}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=.45\textwidth]{linearity.png}
+	\caption{Average regret after $k$ questions with Limited Pessimistic strategy after 10 runs for different problem sizes.}
+	\label{fig:linearity}
+\end{figure}
 
@@
 
-The results are displayed in \cref{fig:55,fig:1020,fig:p}, where strategies are designated by Rnd for Random, Pes. for Pessimistic, L.\ pes. for Limited pessimistic and 2 ph. for Two phases.
+The results are displayed in \cref{tab:comparison,fig:1020,fig:p}, where strategies are designated by Rnd for Random, Pes. for Pessimistic, L.\ pes. for Limited pessimistic and 2 ph. for Two phases.
 
@@
 			\midrule
-			0 & 5.02 & 0.82 & 3.21 & 1.6 \\
-			25 & 5.83 & 1.25 & 6.79 & 1.2 \\
-			50 & 6.47 & 1.14 & 5.2 & 1.58 \\
-			100 & 9.4 & 1.58 & 8.66 & 0.51 \\
-			150 & 11.89 & 1.1 & 12.31 & 0.96 \\
-			200 & 15.64  & 0.52 & 16.12 & 1.06 \\
-			250 & 20.0 & 0.0 & 20.0 & 0.0 \\
+			0 &  &  &  &  \\
+			50 &  &  &  &  \\
+			100 &  &  &  &  \\
+			150 &  &  & &  \\
+			200 &   &  &  &  \\
+			250 &  & &  &  \\
+			300 &&&& \\
+			350 &&&& \\
+			400 &&&& \\
+			450 &&&& \\
+			500 &&&& \\
 			\bottomrule
@@
 	\end{center}
-	\caption{Average regret in problems of size $(10, 20)$ after $250$ questions over $5$ runs. Where $p$ represents the number of questions asked to the chair.}
+	\caption{Average regret in problems of size $(10, 20)$ after $500$ questions and $10$ runs. Where $p$ represents the number of questions asked to the chair.}
 	\label{fig:p}

### 2020-10-06 minimax.tex
Random not parameterized
Table/Plot Comparison with Random pi=0.5

@@
 			\toprule
-			{k} & {Rd.\tiny{$\pi=0.1$}} & {sd} & {Pes.} & {sd} & {L.\ pes.} & {sd} & {Eli.} & {sd} \\
+			{k} & {Rnd.} & {sd} & {Pes.} & {sd} & {L.\ pes.} & {sd} & {Eli.} & {sd} \\
 			\midrule
 			0 & 10.0 & 0.0 & 10.0 & 0.0 & 10.0 & 0.0 & 10.0 & 0.0\\
-			20 & 8.07 & 0.52 & 6.17 & 0.78 & 5.85 & 0.87& 6.32 & 0.61\\
-			40 & 5.26 & 0.88 & 2.98 & 0.99 & 2.57 & 1.05 & 3.37 & 0.83\\
-			60 & 2.37 & 0.93 & 0.77 &0.78 & 0.67 & 0.67 & 2.33 & 1.05\\
-			80 & 0.33 & 0.49 & 0.05 & 0.18 & 0.03 & 0.12 & 2.28 & 1.05\\
-			100 & 0.0 & 0.02 & 0.0 &  0.0 & 0.0 & 0.0& 2.28 & 1.05\\
+			20 & 9.06 & 0.49 & 6.17 & 0.78 & 5.85 & 0.87& 6.32 & 0.61\\
+			40 & 7.35 & 0.82 & 2.98 & 0.99 & 2.57 & 1.05 & 3.37 & 0.83\\
+			60 & 5.74 & 1.03 & 0.77 &0.78 & 0.67 & 0.67 & 2.33 & 1.05\\
+			80 & 4.10 & 1.15 & 0.05 & 0.18 & 0.03 & 0.12 & 2.28 & 1.05\\
+			100 & 2.63 & 1.19 & 0.0 &  0.0 & 0.0 & 0.0& 2.28 & 1.05\\
 			\bottomrule
@@
 	\end{center}
-	\caption{Average minimax regret in problems of size $(5, 10)$ after $k$ questions and $200$ runs.}
+	\caption{Average MMR in problems of size $(5, 10)$ after $k$ questions and $200$ runs.}
 	\label{tab:comparison}
@@
 	\includegraphics[width=.45\textwidth]{linearity.png}
-	\caption{Average regret after $k$ questions with Limited Pessimistic strategy after 10 runs for different problem sizes.}
+	\caption{Average MMR after $k$ questions with Limited Pessimistic strategy after 10 runs for different problem sizes.}
 	\label{fig:linearity}
 \end{figure}
+
+\begin{table}
+	\begin{center}
+		\begin{tabular}{S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-number-alignment = center]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]}
+			\toprule
+			{m} & {n} & {$\frac{n}{10}$} & {$k_{MMR}$} & {$m\cdot n +m^?$} \\
+			\midrule
+			5 & 10 & 1.0 & 60 &  \\
+			5 & 15 & 1.5 & 80 &  \\
+			5 & 20 & 2.0 & 110 &  \\
+			10 & 20 & 2.0 & 340 &  \\
+			10 & 30 & 3.0 & 527 &  \\
+			15 & 30 & 3.0 &  &  \\
+			\bottomrule
+		\end{tabular}
+	\end{center}
+	\caption{}
+	\label{tab:linearity}
+\end{table}
 
@@
 
-The results are displayed in \cref{tab:comparison,fig:1020,fig:p}, where strategies are designated by Rnd for Random, Pes. for Pessimistic, L.\ pes. for Limited pessimistic and 2 ph. for Two phases.
+The results are displayed in \cref{tab:comparison,fig:linearity,tab:twoP}, where strategies are designated by Rnd for Random, Pes.
+for Pessimistic, L.\ pes.
+for Limited pessimistic and 2 ph.
+for Two phases.
 
@@
 	\caption{Average regret in problems of size $(10, 20)$ after $500$ questions and $10$ runs. Where $p$ represents the number of questions asked to the chair.}
-	\label{fig:p}
+	\label{tab:twoP}
 \end{table}

### 2020-10-07 minimax.tex
adjusted tables and figures

@@
 The \strat{Random} strategy gives a baseline for comparison and informs about the difficulty of an elicitation problem. 
-It admits a parameter $\pi \in [0, 1]$.
-This strategy first decides whether it will ask a question about weights (probability $\pi$) or a question about a preference ordering (probability $1-\pi$).
+This strategy first chooses equiprobably whether it will ask a question about weights or a question about a preference ordering.
 If it opted for a question about weights, it draws one rank in $1 ≤ r ≤ m-2$ equiprobably, takes the middle of the interval of values for $\lambda$ that are still possible considering our knowledge so far, and asks whether $w_r - w_{r+1} ≥ \lambda (w_{r+1} - w_{r+2})$.
@@
 			\toprule
-			{k} & {Rnd.} & {sd} & {Pes.} & {sd} & {L.\ pes.} & {sd} & {Eli.} & {sd} \\
+			{k} & {Rnd.} & {sd} & {Pes.} & {sd} & {Ex.\ pes.} & {sd} & {Eli.} & {sd} \\
 			\midrule
 			0 & 10.0 & 0.0 & 10.0 & 0.0 & 10.0 & 0.0 & 10.0 & 0.0\\
-			20 & 9.06 & 0.49 & 6.17 & 0.78 & 5.85 & 0.87& 6.32 & 0.61\\
-			40 & 7.35 & 0.82 & 2.98 & 0.99 & 2.57 & 1.05 & 3.37 & 0.83\\
-			60 & 5.74 & 1.03 & 0.77 &0.78 & 0.67 & 0.67 & 2.33 & 1.05\\
-			80 & 4.10 & 1.15 & 0.05 & 0.18 & 0.03 & 0.12 & 2.28 & 1.05\\
+			20 & 9.06 & 0.49 & 5.85 & 0.87 & 6.17 & 0.78 & 6.32 & 0.61\\
+			40 & 7.35 & 0.82 & 2.57 & 1.05 & 2.98 & 0.99 & 3.37 & 0.83\\
+			60 & 5.74 & 1.03 & 0.67 & 0.67 & 0.77 &0.78 & 2.33 & 1.05\\
+			80 & 4.10 & 1.15 & 0.03 & 0.12 & 0.05 & 0.18 & 2.28 & 1.05\\
 			100 & 2.63 & 1.19 & 0.0 &  0.0 & 0.0 & 0.0& 2.28 & 1.05\\
@@
 	\end{center}
-	\caption{Average MMR in problems of size $(5, 10)$ after $k$ questions and $200$ runs.}
+	\caption{Average $\MMR$ in problems of size $(5, 10)$ after $k$ questions and $200$ runs.\commentBN{Attention, I already corrected the table with the new names.
+The column Pes.
+here is the Limited Pessimistic, I inverted them to follow the presentation order.}}
 	\label{tab:comparison}
@@
 	\includegraphics[width=.45\textwidth]{linearity.png}
-	\caption{Average MMR after $k$ questions with Limited Pessimistic strategy after 10 runs for different problem sizes.}
+	\caption{Average $\MMR$ after $k$ questions with Pessimistic strategy after 10 runs for different problem sizes.}
 	\label{fig:linearity}
@@
 			\toprule
-			{m} & {n} & {$\frac{n}{10}$} & {$k_{MMR}$} & {$m\cdot n +m^?$} \\
+			{m} & {n} & {$\frac{n}{10}$} & {$k_{\MMR}$} & {$m\cdot n +m^?$} \\
 			\midrule
@@
 	\end{center}
-	\caption{}
+	\caption{Number of questions needed by Pessimistic strategy to reach $\MMR=\frac{n}{10}$ (represented by $k_{\MMR}$), for different problem sizes.}
 	\label{tab:linearity}
@@
 %Finally in Table \ref{fig:p}
+%
+%\begin{table}
+%	\begin{center}
+%		\begin{tabular}{S[table-figures-integer=3, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
+%			\toprule
+%			{p} & {Comm. Fst.} & {sd} & {Vot. Fst.} & {sd} \\
+%			\midrule
+%			0 & 0.48 &0.59 & 0.48 &0.59  \\
+%			50 & 0.01 & 0.04& 0.0 & 0.0 \\
+%			100 & 0.04 & 0.09 & 0.13 & 0.35 \\
+%			150 & 0.68 & 0.65 & 0.66 & 0.77 \\
+%			200 &   &  &  &  \\
+%			250 & 3.2 & 1.67 & 4.07	& 1.51 \\
+%			300 &&&& \\
+%			350 &&&& \\
+%			400 &&&& \\
+%			450 &&&& \\
+%			500 &&&& \\
+%			\bottomrule
+%		\end{tabular}
+%	\end{center}
+%	\caption{Average regret in problems of size $(10, 20)$ after $500$ questions and $10$ runs. Where $p$ represents the number of questions asked to the chair.}
+%	\label{tab:twoP500}
+%\end{table}
 
@@
 			\toprule
-			{p} & {Comm. Fst.} & {sd} & {Vot. Fst.} & {sd} \\
+			{p} & {Com. Fst.} & {sd} & {Vot. Fst.} & {sd} \\
 			\midrule
-			0 &  &  &  &  \\
-			50 &  &  &  &  \\
-			100 &  &  &  &  \\
-			150 &  &  & &  \\
+			0 & 0.66 & 0.67 & 0.65 & 0.65  \\
+			50 & 1.23 & 1.46 & 0.8 & 0.79 \\
+			100 & 2.03 & 1.56 &  &  \\
+			150 & 3.41 & 1.79 & 4.07 & 1.51 \\
 			200 &   &  &  &  \\
-			250 &  & &  &  \\
+			250 & 8.4 & 1.86 & 	& \\
 			300 &&&& \\
@@
 			400 &&&& \\
-			450 &&&& \\
-			500 &&&& \\
 			\bottomrule
@@
 	\end{center}
-	\caption{Average regret in problems of size $(10, 20)$ after $500$ questions and $10$ runs. Where $p$ represents the number of questions asked to the chair.}
-	\label{tab:twoP}
+	\caption{Average $\MMR$ in problems of size $(10, 20)$ after $400$ questions and $10$ runs.
+Where $p$ represents the number of questions asked to the chair.
+(The $\MMR$ after 400 questions with Pessimistic is $0.62$ ± $0.56$)}
+	\label{tab:twoP400}
 \end{table}

### 2020-10-07 minimax.tex
comment on linearity

@@
 %Also the first hypothesis should be relaxed considering that, in several situations, it may not be easy to precisely define the voting rule.Indeed, it is possible that the chair has some preferences over the desired aggregation method, but is not able to formalize the voting rule upfront.
-The work of \citet{Cailloux2014} provides elicitation methods for a quite general class of rules based on weak orders.
 When considering positional scoring rules, several authors \citep{Stein1994, Llamazares2013, Viappiani2018} have worked on positional scoring rules with uncertain weights, assuming that the preferences of the agents are fully known.
@@
 First, low levels of regret can be reached by asking approximately $m n$ questions to the voters and $m$ questions to the chair.
-Second, the decrease in MMR is approximately linear with the number of questions asked, except when the regret approaches zero.
+Second, the decrease in $\MMR$ is approximately linear with the number of questions asked, except when the regret approaches zero.
+\commentBN{Not true anymore, some example with Pess (former Lim.Pes.)
+$\begin{array}{ccc}
+	k \quad & \textbf{(5,10)}&\textbf{(10,20)}\\
+	0 \quad &10&20\\
+	10 \quad &7.93&19.5\\
+	20 \quad &5.85&18.2\\
+	30 \quad &4.31&17.43\\
+	40 \quad &3.01&16.56\\
+	50 \quad &1.95&15.59\\
+	100 \quad &0.0&11.91\\
+	150 \quad &0.0&8.92\\
+	200 \quad &0.0&6.24\\
+\end{array}
+$
+}\\
 Third, the value of information of one question to the chair is similar to the value of information of one question to a voter (in the ranges we considered).
@@
 Then, in Section \ref{sec:elicit} we provide an interactive elicitation protocol based on minimal regret;  in Section \ref{sec:experiments} we present the empirical validation of our approach with simulations; and Section \ref{sec:conclusions} provides some final thoughts.
+
+\section{Related Work}
+%The work of \citet{Cailloux2014} provides elicitation methods for a quite general class of rules based on weak orders.
+%it is possible to derive dominance relations (akin to stochastic dominance) that allow to eliminate some alternatives since they will be less preferred than another one for any instantiation of the weights \citep{Stein1994}.
+%Among others, Llamazares and Pe{\~{n}}a have considered  the problem of dealing with underspecified weights in positional scoring rules.
 

### 2020-10-07 minimax.tex
Phrased XPs

--- 2020-10-06 minimax.tex
@@
 	\begin{enumerate}
-		\item Pessimistic is feasible and much better than Random
+		\item Limited pessimistic performs best.
 		\begin{itemize}
+			\item Much better than Random
+			\item Better than Pess and Elitist!
 			\item Graph featuring (5, 10, 150, 200 runs), Random, Pess, L. pess, Elitist.
@@
 		\end{itemize}
-		\item Limited pessimistic performs well.
+		\item L pess performs well.
 		\begin{itemize}
 			\item Reach regret: $n/10$. For this, we need $m^x n$ questions. TODO Olivier: find $x$. TODO Beatrice: check and compile results in a table specifically for this (see: function regret by k).
-			\item Almost as good as Pess and better than the Elitist one (see previous graphs or table)
-			\item Much faster [do this much later]
+			\item Much faster than Pess [do this much later]
 		\end{itemize}
@@
 	\end{enumerate}
+	TODO: find a way of displaying the graph so that it is understandable in B/W.
 }
@@
 \subsection{Small size elections}
-Our first experimental result concerns small size situations.
-We picked $m = 5, n = 10$ to illustrate our results (variations around these sizes yield similar conclusions).
 In such situations, we can run the resource-consuming Pessimistic strategy.
@@
 
-\subsection{Limited pessimistic}
-We next investigate the better performing Limited pessimistic strategy, because Pessimistic is too slow to be ran repeatedly on much bigger problem sizes.
-
-\subsection{Our previous presentation}
-\sisetup{round-mode=places, round-precision=2, table-figures-integer=2, table-figures-decimal=2}
 \begin{table}
@@
 	\caption{Average MMR in problems of size $(5, 10)$ after $k$ questions and $200$ runs.}
-	\label{tab:comparison}
+	\label{tab:smallSize}
 \end{table}
@@
 	\includegraphics[width=.45\textwidth]{comparison.png}
-	\caption{Plot in support of \cref{tab:comparison}}
-	\label{fig:comparison}
+	\caption{Plot in support of \cref{tab:smallSize}}
+	\label{fig:smallSize}
 \end{figure}
 
+\subsection{Comparing limited pessimistic}
+Our first experimental result concerns small size situations. We picked $m = 5, n = 10$ to illustrate our results (variations around these sizes yield similar conclusions). 
+\Cref{tab:smallSize} and \cref{fig:smallSize} compares some of our strategies in this case.
+We see that that Limited pessimistic performs better than Random and Pessimistic on a small size problem.
+(These figures also display the performance of the Elitist strategy, to which we will come back.)
+
+Asking Random questions does not permit to reach a low regret level even after having asked 100 questions, whereas a low regret level (MMR = 1) is reached by Limited pessimistic before having asked 60 questions.
+
+We also see that Pessimistic performs slightly less well than Limited pessimistic.
+Although they come close, Pessimistic performs significatively less well, in the sense that the numbers are consistently in favor of Limited pessimistic if running the experiment again.
+
+We next focus on the Limited pessimistic strategy, because Pessimistic is too slow to be ran repeatedly on much bigger problem sizes.
+
+\subsection{Judging limited pessimistic absolutely}
+\label{sec:lowRegret}
+\begin{table}
+	\begin{center}
+		\begin{tabular}{S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-number-alignment = center]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]}
+			\toprule
+			{m} & {n} & {$\frac{n}{10}$} & {$k_{MMR}$} & {$0.4 m^{1.6} n$} \\
+			\midrule
+			5 & 10 & 1.0 & 60 &  55 \\
+			5 & 15 & 1.5 & 80 &  83 \\
+			5 & 20 & 2.0 & 110 &  110 \\
+			10 & 20 & 2.0 & 340 &  341 \\
+			10 & 30 & 3.0 & 527 &  512 \\
+			15 & 30 & 3.0 &  &  991 \\
+			\bottomrule
+		\end{tabular}
+	\end{center}
+	\caption{}
+	\label{tab:lowRegret}
+\end{table}
+
+The previous section compares Limited pessimistic to other strategies.
+In this set of experiments, we wonder about the absolute quality of Limited pessimistic.
+For practical usability, it is important to know how many questions should be asked in order to reach a low regret level.
+Here, we consider a low level to be a tenth of the number of voters ($n/10$): such a regret is equivalent to the difference of score of an alternative $x$ that results from switching from a profile $P$ to a profile $P'$ where ten percent of the voters rank $x$ last instead of first.
+The results for various sizes are displayed in \cref{tab:lowRegret}.
+From these numbers, we obtain the function $0.4m^{1.6}n$ as a general approximation formula for the number of questions required to reach a low regret level.
+We see that the number of questions required grows approximately linearly with the number of voters and grows less fast than the square of the number of alternatives, for the sizes we considered.
+In other words, on average, assuming no questions get asked to the committee, each voter will have to answer $0.4m^{1.6}$ questions in order to to reach a low regret level.
+For $m = 5$, that is about $6$ questions per voter; for $m = 10$, that is about $17$ questions per voter; and for $m = 15$, that is about $33$ questions per voter.
+
+\subsection{Comparing with full elicitation}
+In this work, we advocate obtaining an approximate winner without obtaining the full profile or determine completely the voting rule.
+The previous section evaluate the number of questions per voter to reach a low regret value.
+In order to contrast our approach to one that would apply existing works to, on the one hand, obtain the full profile, and on the other hand, to determine the voting rule, it is interesting to compute the number of questions that would be required to elicit the complete profile.
+We focus on the profile because eliciting the scores to full precision would require infinitely many questions, with the questions we use, and existing works do not propose to use such questions, thus they are not readily comparable on that aspect.
+Note that this may underestimate the number of questions required to determine completely the profile and the rule, as these questions yield no information about the scoring vector.
+
+To estimate this number, we assume the following querying process: given a partial ordering representing our knowledge so far of an agent preferences, we pick a question equiprobably among the remaining edges, and add the edge in the appropriate direction to our partial ordering.
+We count the average number of questions required to reach a complete ordering, assuming that every linear order is equally probable as a representation of the real agent preferences.
+
+\subsection{Decrease in MMR values}
 \begin{figure}
@@
 
-\begin{table}
-	\begin{center}
-		\begin{tabular}{S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-number-alignment = center]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]}
-			\toprule
-			{m} & {n} & {$\frac{n}{10}$} & {$k_{MMR}$} & {$m\cdot n +m^?$} \\
-			\midrule
-			5 & 10 & 1.0 & 60 &  \\
-			5 & 15 & 1.5 & 80 &  \\
-			5 & 20 & 2.0 & 110 &  \\
-			10 & 20 & 2.0 & 340 &  \\
-			10 & 30 & 3.0 & 527 &  \\
-			15 & 30 & 3.0 &  &  \\
-			\bottomrule
-		\end{tabular}
-	\end{center}
-	\caption{}
-	\label{tab:linearity}
-\end{table}
+We next wonder how fact the regret decreases, measured as a function of the number of questions asked.
+This is important practically because one may not be able to ask enough questions to reach low level of regrets, as computed in \cref{sec:lowRegret}.
+Knowing the speed of decrease thus permits to know which trade-offs can be achieved between the quality of the resulting recommendation and the number of questions that participants have to answer.
 
+\subsection{Our previous presentation}
+\sisetup{round-mode=places, round-precision=2, table-figures-integer=2, table-figures-decimal=2}
 We test our strategies using randomly generated datasets. 
@@
 
-The results are displayed in \cref{tab:comparison,fig:linearity,tab:twoP}, where strategies are designated by Rnd for Random, Pes.
+%The results are displayed in \cref{tab:comparison,fig:linearity,tab:twoP}, where strategies are designated by Rnd for Random, Pes.
 for Pessimistic, L.\ pes.

### 2020-10-07 minimax.tex

@@
 	\end{center}
-	\caption{Average MMR in problems of size $(5, 10)$ after $k$ questions and $200$ runs.}
+	\caption{Average MMR in problems of size $(5, 10)$ after $k$ questions and $200$ runs.\commentBN{Attention, I already corrected the table with the new names.
+The column Pes.
+here is the Limited Pessimistic, I inverted them to follow the presentation order.}}
 	\label{tab:smallSize}
@@
 
-\subsection{Comparing limited pessimistic}
+\subsection{Judging limited pessimistic relatively}
 Our first experimental result concerns small size situations. We picked $m = 5, n = 10$ to illustrate our results (variations around these sizes yield similar conclusions). 
@@
 			\toprule
-			{m} & {n} & {$\frac{n}{10}$} & {$k_{MMR}$} & {$0.4 m^{1.6} n$} \\
+			{m} & {n} & {$\frac{n}{10}$} & {$k_{\MMR}$} & {$0.4 m^{1.6} n$} \\
 			\midrule
@@
 	\end{center}
-	\caption{}
+	\caption{Number of questions needed by Pessimistic strategy to reach $\MMR=\frac{n}{10}$ (represented by $k_{\MMR}$), for various problem sizes.}
 	\label{tab:lowRegret}

### 2020-10-07 minimax.tex
More sections XPs

@@
 
-We next wonder how fact the regret decreases, measured as a function of the number of questions asked.
-This is important practically because one may not be able to ask enough questions to reach low level of regrets, as computed in \cref{sec:lowRegret}.
+We next wonder how fast the regret decreases, measured as a function of the number of questions asked.
+This is important practically because it may be impossible or unwanted to ask enough questions to reach low level of regrets, as computed in \cref{sec:lowRegret}.
 Knowing the speed of decrease thus permits to know which trade-offs can be achieved between the quality of the resulting recommendation and the number of questions that participants have to answer.
+\Cref{fig:linearity} shows graphically the decrease in $\MMR$ according to the number of questions asked for various problem sizes.
+We see that this function is convex, apart from the very few questions, indicating to users of our approach that asking, for example, half the number of questions required to reach a low regret value will still yield a significant gain in regret, namely, more than half the distance to the low regret value.
+
+\subsection{Value of information comparison}
+\begin{table}
+	\begin{center}
+		\begin{tabular}{S[table-figures-integer=3, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
+			\toprule
+			{p} & {Com. Fst.} & {sd} & {Vot. Fst.} & {sd} \\
+			\midrule
+			0 & 0.66 & 0.67 & 0.65 & 0.65  \\
+			50 & 1.23 & 1.46 & 0.8 & 0.79 \\
+			100 & 2.03 & 1.56 &  &  \\
+			150 & 3.41 & 1.79 & 4.07 & 1.51 \\
+			200 &   &  &  &  \\
+			250 & 8.4 & 1.86 & 	& \\
+			300 &&&& \\
+			350 &&&& \\
+			400 &&&& \\
+			\bottomrule
+		\end{tabular}
+	\end{center}
+	\caption{Average $\MMR$ in problems of size $(10, 20)$ after $400$ questions and $10$ runs.
+Where $p$ represents the number of questions asked to the chair.
+(The $\MMR$ after 400 questions with Pessimistic is $0.62$ ± $0.56$)}
+	\label{tab:twoP400}
+\end{table}
+
+The experiments so far let the strategy decide the target of its questions, leaving the possibility to question the chair or the agents at each step.
+It may be desired in practical implementations to restrict the strategy to ask questions to agents only, or mostly, or to wonder what is lost in terms of regret by asking more questions to the chair.
+That may be because of unavailability of the chair, or because the estimated cognitive costs may differ sensibly, as these types of questions differ in nature.
 
@@
 %\end{table}
-
-\begin{table}
-	\begin{center}
-		\begin{tabular}{S[table-figures-integer=3, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
-			\toprule
-			{p} & {Com. Fst.} & {sd} & {Vot. Fst.} & {sd} \\
-			\midrule
-			0 & 0.66 & 0.67 & 0.65 & 0.65  \\
-			50 & 1.23 & 1.46 & 0.8 & 0.79 \\
-			100 & 2.03 & 1.56 &  &  \\
-			150 & 3.41 & 1.79 & 4.07 & 1.51 \\
-			200 &   &  &  &  \\
-			250 & 8.4 & 1.86 & 	& \\
-			300 &&&& \\
-			350 &&&& \\
-			400 &&&& \\
-			\bottomrule
-		\end{tabular}
-	\end{center}
-	\caption{Average $\MMR$ in problems of size $(10, 20)$ after $400$ questions and $10$ runs.
-Where $p$ represents the number of questions asked to the chair.
-(The $\MMR$ after 400 questions with Pessimistic is $0.62$ ± $0.56$)}
-	\label{tab:twoP400}
-\end{table}
 

### 2020-10-07 minimax.tex
Better pres sec 5

@@
 	TODO: find a way of displaying the graph so that it is understandable in B/W.
+	Variations around the small size. Time comparison Pess VS LPess?
 }
@@
 
-\subsection{Small size elections}
-In such situations, we can run the resource-consuming Pessimistic strategy.
-Table x / graph x compares it to other strategies.
-We see that these strategies perform much better than random, even when its parameter $\pi$ is chosen in an optimal way, that is, when the proportion of questions asked to the chair is ideal.
-We also see a first important positive result for applicability of our approach, namely, that it is possible to reach a small regret with a reasonable number of questions in such problems.
-
+\subsection{Judging limited pessimistic relatively}
 \begin{table}
@@
 
-\subsection{Judging limited pessimistic relatively}
-Our first experimental result concerns small size situations. We picked $m = 5, n = 10$ to illustrate our results (variations around these sizes yield similar conclusions). 
+Our first experimental result concerns small size situations. We picked $m = 5, n = 10$ to illustrate our results (variations around this size yield similar conclusions). 
 \Cref{tab:smallSize} and \cref{fig:smallSize} compares some of our strategies in this case.
@@
 (These figures also display the performance of the Elitist strategy, to which we will come back.)
+
+We observe that the Pessimistic strategy is able to reduce the regret almost completely after $30$ questions.
+We also see that Limited pessimistic performs better than Pessimistic, showing that Limited pessimistic chooses candidate questions wisely; this is good news since (for $m=5$ and $n=5$), the latter strategy is much faster and takes only $2.6s$ for a complete elicitation session, while the former takes $16s$.
 
@@
 We focus on the profile because eliciting the scores to full precision would require infinitely many questions, with the questions we use, and existing works do not propose to use such questions, thus they are not readily comparable on that aspect.
-Note that this may underestimate the number of questions required to determine completely the profile and the rule, as these questions yield no information about the scoring vector.
+Note that this may underestimate the number of questions required to determine completely the profile and the rule, as questions to the agents yield no information about the scoring vector.
 
@@
 	\end{center}
-	\caption{Average $\MMR$ in problems of size $(10, 20)$ after $400$ questions and $10$ runs.
-Where $p$ represents the number of questions asked to the chair.
-(The $\MMR$ after 400 questions with Pessimistic is $0.62$ ± $0.56$)}
+	\caption{Average $\MMR$ in problems of size $(10, 20)$ after $400$ questions and $10$ runs. Where $p$ represents the number of questions asked to the chair.}
 	\label{tab:twoP400}
@@
 
-The experiments so far let the strategy decide the target of its questions, leaving the possibility to question the chair or the agents at each step.
-It may be desired in practical implementations to restrict the strategy to ask questions to agents only, or mostly, or to wonder what is lost in terms of regret by asking more questions to the chair.
-That may be because of unavailability of the chair, or because the estimated cognitive costs may differ sensibly, as these types of questions differ in nature.
-
-\subsection{Our previous presentation}
-\sisetup{round-mode=places, round-precision=2, table-figures-integer=2, table-figures-decimal=2}
-We test our strategies using randomly generated datasets. 
-Our first goal is to see, with a small problem size ($m = 5, n = 5$) and the (time consuming) Pessimistic strategy, if an important lowering of the maximal regret can be achieved with a reasonable number of questions.
-We also want to estimate how “hard” such a problem is, by using the Random strategy as a baseline.
-Third, we want to estimate the loss (in terms of worst regret) when switching to the faster Limited pessimistic strategy.
-Fourth, we want to see, on a bigger problem size ($m = 10, n = 20$), how many questions must be asked for that strategy to achieve a significant reduction of the worst regret.
-Finally, we want to evaluate, thanks to the Two phases strategy, the impact of varying the proportion of questions asked to the agents (with respect to questions asked to the chair) on the reduction of the worst regret.
-%We also want to see how realistic our approach is for various problem sizes, by estimating the number of questions we would have to ask before being able to reduce the worst regret significantly.
-
-%The results are displayed in \cref{tab:comparison,fig:linearity,tab:twoP}, where strategies are designated by Rnd for Random, Pes.
-for Pessimistic, L.\ pes.
-for Limited pessimistic and 2 ph.
-for Two phases.
-
-We observe that the Pessimistic strategy is able to reduce the regret almost completely after $30$ questions.
-We also see that Limited pessimistic performs almost as well as Pessimistic; this is good news since (for $m=5$ and $n=5$), the former strategy is much faster and takes only $2.6s$ for a complete elicitation session, while the latter takes $16s$.
-%However, it takes $1000$ times more time than the \strat{Random} strategy ($16s$ of the Pessimistic compared to $0.014s$ of the Random).
-Moreover, the results of the \strat{Limited pessimistic}, that takes almost $80\%$ less of the time of the \strat{Pessimistic} ($2.6s$), are essentially the same.
-%In Table \ref{fig:1020}, we can see the drop of regret using a bigger instance.
-%Finally in Table \ref{fig:p}
-%
-%\begin{table}
-%	\begin{center}
-%		\begin{tabular}{S[table-figures-integer=3, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
-%			\toprule
-%			{p} & {Comm. Fst.} & {sd} & {Vot. Fst.} & {sd} \\
-%			\midrule
-%			0 & 0.48 &0.59 & 0.48 &0.59  \\
-%			50 & 0.01 & 0.04& 0.0 & 0.0 \\
-%			100 & 0.04 & 0.09 & 0.13 & 0.35 \\
-%			150 & 0.68 & 0.65 & 0.66 & 0.77 \\
-%			200 &   &  &  &  \\
-%			250 & 3.2 & 1.67 & 4.07	& 1.51 \\
-%			300 &&&& \\
-%			350 &&&& \\
-%			400 &&&& \\
-%			450 &&&& \\
-%			500 &&&& \\
-%			\bottomrule
-%		\end{tabular}
-%	\end{center}
-%	\caption{Average regret in problems of size $(10, 20)$ after $500$ questions and $10$ runs. Where $p$ represents the number of questions asked to the chair.}
-%	\label{tab:twoP500}
-%\end{table}
+The experiments so far let the strategy decide the target of its questions, leaving open the possibility of questioning either the chair or an agent at each step.
+It may be desired in practical implementations to restrict the strategy to ask questions to agents only, or mostly, or to wonder what is lost in terms of regret by asking more questions to the chair, or what is lost if the circumstances require to ask all questions to the chair first, then only question the voters, or the other way around.
+Such restrictions may be useful because of (partial) unavailability of the chair, or because the estimated cognitive costs may differ sensibly, as these types of questions differ in nature.
+\Cref{tab:twoP400} show the MMR value that is reached in a problem of size $m = 10, n = 20$ after $400$ questions, using various constraints added to the Limited pessimistic strategy.
+The constraints have this form: the strategy must ask $p$ questions to the chair first, then $400 - p$ questions to the agents; or conversely, must ask $400 - p$ questions to the agents before turning to the chair.
+These numbers are to be compared with the MMR value reached after 400 questions with the unconstrained Limited pessimistic strategy (displayed in \cref{fig:linearity}), which is $0.62$.% ± $0.56$.
 

### 2020-10-07 minimax.tex
Renamed Limited pess ⇒ Pess and Pess ⇒ Extended pess

@@
 First, low levels of regret can be reached by asking approximately $m n$ questions to the voters and $m$ questions to the chair.
-Second, the decrease in $\MMR$ is approximately linear with the number of questions asked, except when the regret approaches zero.
-\commentBN{Not true anymore, some example with Pess (former Lim.Pes.)
+Second, the decrease in $\MMR$ is approximately linear with the number of questions asked, except when the regret approaches zero. \commentBN{Not true anymore, some example with Pess 
 $\begin{array}{ccc}
@@
 
-The \strat{Pessimistic} strategy considers the same candidate questions as the Random strategy, but instead of picking one among those randomly, selects the question that leads to minimal regret in the worst case, considering both possible answers to the question.
-Assume that a question leads to the possible new knowledge states $(\pprofile_1, W_1)$ and $(\pprofile_2, W_2)$, depending on the answer.
-Then the badness of the question in the worst case is:
-\begin{align}
-	\max_{i=1,2} \MMR(\pprofile_i,W_i)
-\end{align}
-This badness measure gives a way of picking questions among a set of possible questions, by picking one that minimizes ths measure of minimax regret {\em a posteriori}. 
-Note that other aggregators than $\max$ can be used as well. 
-We use the $\max$ operator because \citet{Cailloux2014} reported that pessimistic aggregation works much better than optimistic aggregation, although our experiments in this context suggested a weak impact of that choice on the performance of the strategy.
-However, to avoid the absorption property of max, we adopt the $\leximax$ criterion as an aggregator: if the maximal $\MMR$ of two questions are equal, then it considers the other $\MMR$ values, that are the one associated to the opposite answer, preferring the question with the lowest value.
-(Technically, instead of applying a pure lexicographic aggregation, which is very sensitive to small errors due to floating-point computations, we apply a weighted sum between the maximal and the minimal $\MMR$ values, with a predominant weight to the maximal one.)
-We expect this strategy to perform very well, but only for very small problem instances: its complexity is in $O(n^2 m^5)$, because we consider $O(m^2)$ questions for each agent and need for each question to compute $\MMR$ twice, whose complexity is $O(nm^3)$.
-For small dimensions, it estimates an upper bound to the possible quality of a myopic strategy.
-
-The \strat{Limited pessimistic} strategy uses the same criterion as the pessimistic strategy, but limiting it to a small set of $n + m$ candidate questions: one per agent, and one per rank.
 Let $(x^{*},\bar{y}, \bar{\profile}, \bar{\w})$ be the current solution of the minimax regret, where $\bar{y}, \bar{\profile}, \bar{\w}$ are, respectively, the choice of $y$, the completion of the profile and the selection of weights for which $x^{*}$ is the minimax optimal alternative.
-The \strat{Limited pessimistic} strategy first selects $n$ candidates questions to the agents using the heuristic proposed by \citet{Lu2011}: for each agent $j$, if $x^*$ and $\bar{y}$ are incomparable in $\ppref_j$, the candidate question concerns the pair $(x^*, \bar{y})$, otherwise, the candidate question concerns the pair $(x^*, z)$ for some $z$ incomparable to $x^*$ (randomly chosen), or if none such $z$ exist, the pair $(\bar{y}, z)$ for some $z$ incomparable to $\bar{y}$, or, if both $x^*$ and $\bar{y}$ are comparable to every alternatives in $\ppref_j$, any incomparable pair is picked at random.
+The \strat{Pessimistic} strategy considers a set of $n + m$ candidate questions: one per agent, and one per rank.
+The candidate questions to the agents use the heuristic proposed by \citet{Lu2011}: for each agent $j$, if $x^*$ and $\bar{y}$ are incomparable in $\ppref_j$, the candidate question concerns the pair $(x^*, \bar{y})$, otherwise, the candidate question concerns the pair $(x^*, z)$ for some $z$ incomparable to $x^*$ (randomly chosen), or if none such $z$ exist, the pair $(\bar{y}, z)$ for some $z$ incomparable to $\bar{y}$, or, if both $x^*$ and $\bar{y}$ are comparable to every alternatives in $\ppref_j$, any incomparable pair is picked at random.
 To understand the intuition behind favoring these two alternatives for our questions, recall that, as shown in the proof of \cref{claim:completion}, in order to increase $\PMR(x^{*},\bar{y})$, an adversary should place as many alternatives as she can above $x^{*}$ if $x^* \ppref_j \bar{y}$, and between $\bar{y}$ and $x^{*}$ if $\bar{y} \ppref_j x^*$.
@@
 An intuitive way to reduce the pairwise max regret would be, therefore, to ask questions involving such alternatives, hoping for an answer that would prevent the adversary to play his best game. 
-The candidate questions to the chair are determined as in the Random and Pessimistic strategies.
-After having selected the candidate questions, we apply the Pessimistic strategy: we evaluate, for each of the questions, the minimax regret for the two possible answers and we choose the best according to $\leximax$.
+The candidate questions to the chair are determined as in the Random strategy.
+The strategy then selects among these $n + m$ candidate questions one that leads to minimal regret in the worst case, considering both possible answers to the question.
+Assume that a question leads to the possible new knowledge states $(\pprofile_1, W_1)$ and $(\pprofile_2, W_2)$, depending on the answer, numbering them so that $\MMR(\pprofile_1, W_1) ≥ \MMR(\pprofile_2, W_2)$.
+Then the badness of the question in the worst case is:
+\begin{align}
+	\MMR(\pprofile_1,W_1) + \frac{1}{10000}\MMR(\pprofile_2, W_2).
+\end{align}
+This badness measure gives a way of picking questions among a set of possible questions, by picking one that minimizes this approximate measure of minimax regret {\em a posteriori}. 
+We use this operator that is similar to a $\max$ operator because \citet{Cailloux2014} reported that pessimistic aggregation works much better than optimistic aggregation, although our experiments in this context suggested a weak impact of that choice on the performance of the strategy.
+However, to avoid the absorption property of max, we adopt criterion closer to $\leximax$ as an aggregator: if the maximal $\MMR$ of two questions are (nearly) equal, then it considers the other $\MMR$ values, that are the one associated to the opposite answer, preferring the question with the lowest value.
+(Technically, instead of applying a pure lexicographic aggregation, which is very sensitive to small errors due to floating-point computations, we apply a weighted sum between the maximal and the minimal $\MMR$ values, with a predominant weight to the maximal one.)
+
+The \strat{Extended pessimistic} strategy uses the same criterion as the pessimistic strategy, but extending it to a bigger set of $m² n + m$ candidate questions, the same as those considered by the Random strategy.
+After having selected the candidate questions, we apply the same operator as for the Pessimistic strategy: we evaluate, for each of the possible questions, the minimax regret for the two possible answers and we choose the best according to (quasi-)$\leximax$.
+We use this strategy to test whether Pessimistic performs well: depending on the quality of the heuristic of the Pessimistic strategy, it might perform nearly equally well, or perhaps even better, than Extended pessimistic, while being (much) more efficient.
+We expect that Extended pessimistic will be applicable only to very small problem instances: its complexity is in $O(n^2 m^5)$, because we consider $O(m^2)$ questions for each agent and need for each question to compute $\MMR$ twice, whose complexity is $O(nm^3)$.
 
 The \strat{Two phases} strategy is developed in order to investigate the effect of varying the proportion of questions asked to agents and to the chair, and compare the performance of asking questions to the chair first or to the voters first.
-The \strat{Two phases - ac} variant first asks $p$ questions to the agents, then $k-p$ questions to the chair, using in both cases Limited pessimistic to select the specific questions; whereas the \strat{Two phases - ca} variant starts with $p$ questions to the chair, then questions the agents.
+The \strat{Two phases - ac} variant first asks $p$ questions to the agents, then $k-p$ questions to the chair, using in both cases Pessimistic to select the specific questions; whereas the \strat{Two phases - ca} variant starts with $p$ questions to the chair, then questions the agents.
 %Note that when asking first only questions to the chair, if the obtained knowledge approximates well the scoring vector, then in the second part of the elicitation we fall into the more classical setting of incompleteness of preferences assuming a known voting rule.
 %And vice-versa when asking first questions to the agents, the second part of the elicitation is similar to the setting of incompletely specified scoring rule. 
-This strategy also permits to simulate the current state of the art when considering incomplete preferences.
+%This strategy also permits to simulate the current state of the art when considering incomplete preferences.
 By asking enough questions to the chair we can reduce our problem into a well studied one of incompleteness of preferences knowing the voting rule.
@@
 	\begin{enumerate}
-		\item Limited pessimistic performs best.
+		\item Pessimistic performs best.
 		\begin{itemize}
 			\item Much better than Random
-			\item Better than Pess and Elitist!
-			\item Graph featuring (5, 10, 150, 200 runs), Random, Pess, L. pess, Elitist.
+			\item Better than XPess and Elitist!
+			\item Graph featuring (5, 10, 150, 200 runs), Random, XPess, Pess, Elitist.
 			\item And table like table 1.
 		\end{itemize}
-		\item L pess performs well.
+		\item Pess performs well.
 		\begin{itemize}
 			\item Reach regret: $n/10$. For this, we need $m^x n$ questions. TODO Olivier: find $x$. TODO Beatrice: check and compile results in a table specifically for this (see: function regret by k).
-			\item Much faster than Pess [do this much later]
+			\item Much faster than XPess [do this much later]
 		\end{itemize}
@@
 		\end{itemize}
-		\item Limited pessimistic approx Limited optimistic [do this much later]
+		\item Pessimistic approx Optimistic [do this much later]
 	\end{enumerate}
 	TODO: find a way of displaying the graph so that it is understandable in B/W.
-	Variations around the small size. Time comparison Pess VS LPess?
+	Variations around the small size. Time comparison XPess VS Pess?
+	Check Pess VS XPess on other sizes.
 }
@@
 
-\subsection{Judging limited pessimistic relatively}
+\subsection{Judging pessimistic relatively}
 \begin{table}
@@
 	\end{center}
-	\caption{Average MMR in problems of size $(5, 10)$ after $k$ questions and $200$ runs.\commentBN{Attention, I already corrected the table with the new names.
-The column Pes.
-here is the Limited Pessimistic, I inverted them to follow the presentation order.}}
+	\caption{Average MMR in problems of size $(5, 10)$ after $k$ questions and $200$ runs.}
 	\label{tab:smallSize}
@@
 \Cref{tab:smallSize} and \cref{fig:smallSize} compares some of our strategies in this case.
-We see that that Limited pessimistic performs better than Random and Pessimistic on a small size problem.
+We see that that Pessimistic performs better than Random and Extended pessimistic on a small size problem.
 (These figures also display the performance of the Elitist strategy, to which we will come back.)
 
-We observe that the Pessimistic strategy is able to reduce the regret almost completely after $30$ questions.
-We also see that Limited pessimistic performs better than Pessimistic, showing that Limited pessimistic chooses candidate questions wisely; this is good news since (for $m=5$ and $n=5$), the latter strategy is much faster and takes only $2.6s$ for a complete elicitation session, while the former takes $16s$.
+%We observe that the Pessimistic strategy is able to reduce the regret almost completely after $30$ questions.
+We also see that Pessimistic performs better than Extended pessimistic, showing that Pessimistic chooses candidate questions wisely; this is good news since (for $m=5$ and $n=5$), the latter strategy is much faster and takes only $2.6s$ for a complete elicitation session, while the former takes $16s$.
 
-Asking Random questions does not permit to reach a low regret level even after having asked 100 questions, whereas a low regret level (MMR = 1) is reached by Limited pessimistic before having asked 60 questions.
+Asking Random questions does not permit to reach a low regret level even after having asked 100 questions, whereas a low regret level (MMR = 1) is reached by Pessimistic before having asked 60 questions.
 
-We also see that Pessimistic performs slightly less well than Limited pessimistic.
-Although they come close, Pessimistic performs significatively less well, in the sense that the numbers are consistently in favor of Limited pessimistic if running the experiment again.
+We also see that Extended pessimistic performs slightly less well than Pessimistic.
+Although they come close, Extended pessimistic performs significatively less well, in the sense that the numbers are consistently in favor of Pessimistic if running the experiment again.
 
-We next focus on the Limited pessimistic strategy, because Pessimistic is too slow to be ran repeatedly on much bigger problem sizes.
+We next focus on the Pessimistic strategy, because Extended pessimistic is too slow to be ran repeatedly on much bigger problem sizes.
 
-\subsection{Judging limited pessimistic absolutely}
+\subsection{Judging Pessimistic absolutely}
 \label{sec:lowRegret}
@@
 
-The previous section compares Limited pessimistic to other strategies.
-In this set of experiments, we wonder about the absolute quality of Limited pessimistic.
+The previous section compares Pessimistic to other strategies.
+In this set of experiments, we wonder about the absolute quality of Pessimistic.
 For practical usability, it is important to know how many questions should be asked in order to reach a low regret level.
@@
 Such restrictions may be useful because of (partial) unavailability of the chair, or because the estimated cognitive costs may differ sensibly, as these types of questions differ in nature.
-\Cref{tab:twoP400} show the MMR value that is reached in a problem of size $m = 10, n = 20$ after $400$ questions, using various constraints added to the Limited pessimistic strategy.
+\Cref{tab:twoP400} show the MMR value that is reached in a problem of size $m = 10, n = 20$ after $400$ questions, using various constraints added to the Pessimistic strategy.
 The constraints have this form: the strategy must ask $p$ questions to the chair first, then $400 - p$ questions to the agents; or conversely, must ask $400 - p$ questions to the agents before turning to the chair.
-These numbers are to be compared with the MMR value reached after 400 questions with the unconstrained Limited pessimistic strategy (displayed in \cref{fig:linearity}), which is $0.62$.% ± $0.56$.
+These numbers are to be compared with the MMR value reached after 400 questions with the unconstrained Pessimistic strategy (displayed in \cref{fig:linearity}), which is $0.62$.% ± $0.56$.
 

### 2020-10-08 minimax.tex
Wording and openness about qC

@@
 We also provide an interactive elicitation protocol based on minimax regret and develop several query strategies that question the chair and the agents in order to acquire the most relevant information for quickly converging to a near-optimal alternative.
+Finally, we find out experimentally that questioning voters is more useful than questioning the chair in our setting.
 \end{abstract}
@@
 Our approach permits to compare experimentally strategies that question the chair, the voters, or both.
-We describe informally here a few of the conclusions stemming from these experiments, given a problem involving $m$ alternatives and $n$ voters.
-First, low levels of regret can be reached by asking approximately $m n$ questions to the voters and $m$ questions to the chair.
-Second, the decrease in $\MMR$ is approximately linear with the number of questions asked, except when the regret approaches zero. \commentBN{Not true anymore, some example with Pess 
-$\begin{array}{ccc}
-	k \quad & \textbf{(5,10)}&\textbf{(10,20)}\\
-	0 \quad &10&20\\
-	10 \quad &7.93&19.5\\
-	20 \quad &5.85&18.2\\
-	30 \quad &4.31&17.43\\
-	40 \quad &3.01&16.56\\
-	50 \quad &1.95&15.59\\
-	100 \quad &0.0&11.91\\
-	150 \quad &0.0&8.92\\
-	200 \quad &0.0&6.24\\
-\end{array}
-$
-}\\
-Third, the value of information of one question to the chair is similar to the value of information of one question to a voter (in the ranges we considered).
+We describe informally here a few of the conclusions stemming from these experiments, given a problem involving $m$ alternatives and $n$ agents.
+First, a good quality recommendation can be reached by asking what can be considered a reasonable number of questions to the chair and agents.
+For example, in a problem of size $m = 5$, $n = 10$, $55$ questions in total are required to reach a good quality recommendation, whcih can be considered reasonable as these questions are to be dispatched over $10$ agents and the chair.
+Second, the quality of the recommendation increases faster than linearly with the number of questions, after only a few questions (the first few questions yield no increase in quality).
+Third, we experimentally find out that asking questions to the voters only performs similarly than asking questions both to the voters and the chair, although questions to the chair do have a positive value in terms of quality of the recommendation.
+%the value of information of one question to the chair is similar to the value of information of one question to a voter (in the ranges we considered), up to a certain proportion of questions asked to the chair.
 Knowing this permits to choose the questioning strategy wisely depending on the estimated cost of each kind of question, which depends on the application.
 
-The paper is organized as follows.
+The paper is organized as follows. \Cref{sec:related} reviews the works related to our objective.
 In Section \ref{sec:background} we provide the necessary background and in Section \ref{sec:mmr} we introduce the minimax criterion, that selects a winner that minimizes the worst possible regret.
@@
 \section{Related Work}
+\label{sec:related}
 %The work of \citet{Cailloux2014} provides elicitation methods for a quite general class of rules based on weak orders.
@@
 Optimal alternatives w.r.t. minimax regret are the ones with least max regret. 
-Observe that, whenever the $\PMR$ of an alternative $x$ (against some other alternative $y$) exceeds the best MR value found so far, we don't need to further evaluate $x$. 
+Observe that, whenever the $\PMR$ of an alternative $x$ (against some other alternative $y$) exceeds the best MR value found so far, we do not need to further evaluate $x$. 
 This idea can be exploited further by adopting a minimax-search tree \citep{Braziunas2011}.
@@
 To understand the intuition behind favoring these two alternatives for our questions, recall that, as shown in the proof of \cref{claim:completion}, in order to increase $\PMR(x^{*},\bar{y})$, an adversary should place as many alternatives as she can above $x^{*}$ if $x^* \ppref_j \bar{y}$, and between $\bar{y}$ and $x^{*}$ if $\bar{y} \ppref_j x^*$.
-\commentOC{I do not understand the reasoning in the next sentence.}
-An intuitive way to reduce the pairwise max regret would be, therefore, to ask questions involving such alternatives, hoping for an answer that would prevent the adversary to play his best game. 
+Asking questions involving $x^*$ or $\bar{y}$ thus has a particular chance of reducing usefully the possibilities of the adversary.
 The candidate questions to the chair are determined as in the Random strategy.
@@
 
-The \strat{Extended pessimistic} strategy uses the same criterion as the pessimistic strategy, but extending it to a bigger set of $m² n + m$ candidate questions, the same as those considered by the Random strategy.
+The \strat{Extended pessimistic} strategy uses the same criterion as the pessimistic strategy, but extending it to a bigger set of $m^2 n + m$ candidate questions, the same as those considered by the Random strategy.
 After having selected the candidate questions, we apply the same operator as for the Pessimistic strategy: we evaluate, for each of the possible questions, the minimax regret for the two possible answers and we choose the best according to (quasi-)$\leximax$.
@@
 
-\subsection{Judging pessimistic relatively}
+\subsection{Judging Pessimistic relatively}
 \begin{table}
@@
 
-%We observe that the Pessimistic strategy is able to reduce the regret almost completely after $30$ questions.
-We also see that Pessimistic performs better than Extended pessimistic, showing that Pessimistic chooses candidate questions wisely; this is good news since (for $m=5$ and $n=5$), the latter strategy is much faster and takes only $2.6s$ for a complete elicitation session, while the former takes $16s$.
+We observe that the Pessimistic strategy is able to reduce the regret almost completely after $30$ questions.
+We also see that Pessimistic performs slightly better than Extended pessimistic, showing that Pessimistic chooses candidate questions wisely; this is good news since (for $m = 5$ and $n = 10$), the latter strategy is much faster and takes only $15s$ for a complete elicitation session, while the former takes $80s$.
 
@@
 The previous section evaluate the number of questions per voter to reach a low regret value.
-In order to contrast our approach to one that would apply existing works to, on the one hand, obtain the full profile, and on the other hand, to determine the voting rule, it is interesting to compute the number of questions that would be required to elicit the complete profile.
-We focus on the profile because eliciting the scores to full precision would require infinitely many questions, with the questions we use, and existing works do not propose to use such questions, thus they are not readily comparable on that aspect.
+In this section we want to contrast our approach to one that would obtain the full profile on the one hand, and determine the voting rule on the other hand.
+More precisely, we want to estimate the number of questions that would be required to elicit the complete profile.
+We focus on the profile because eliciting the scores to full precision would require infinitely many questions, with the questions we use.
 Note that this may underestimate the number of questions required to determine completely the profile and the rule, as questions to the agents yield no information about the scoring vector.
 
-To estimate this number, we assume the following querying process: given a partial ordering representing our knowledge so far of an agent preferences, we pick a question equiprobably among the remaining edges, and add the edge in the appropriate direction to our partial ordering.
-We count the average number of questions required to reach a complete ordering, assuming that every linear order is equally probable as a representation of the real agent preferences.
+To estimate this number, we draw one linear order randomly (with equiprobability over all possible linear orders) and assume the following querying process: given a partial ordering representing our knowledge so far of an agent preferences, we pick a question equiprobably among the remaining edges, and add the edge in the appropriate direction to our partial ordering.
+We count the average number of questions required to reach a complete ordering.
 

### 2020-10-08 minimax.tex
Some TODOs and minor wording

@@
 Second, the quality of the recommendation increases faster than linearly with the number of questions, after only a few questions (the first few questions yield no increase in quality).
-Third, we experimentally find out that asking questions to the voters only performs similarly than asking questions both to the voters and the chair, although questions to the chair do have a positive value in terms of quality of the recommendation.
+Third, we experimentally find out that asking questions to the agents only performs similarly than asking questions both to the agents and the chair, although questions to the chair do have a positive value in terms of quality of the recommendation.
 %the value of information of one question to the chair is similar to the value of information of one question to a voter (in the ranges we considered), up to a certain proportion of questions asked to the chair.
@@
 	\begin{enumerate}
-		\item Pessimistic performs best.
-		\begin{itemize}
-			\item Much better than Random
-			\item Better than XPess and Elitist!
-			\item Graph featuring (5, 10, 150, 200 runs), Random, XPess, Pess, Elitist.
-			\item And table like table 1.
-		\end{itemize}
-		\item Pess performs well.
-		\begin{itemize}
-			\item Reach regret: $n/10$. For this, we need $m^x n$ questions. TODO Olivier: find $x$. TODO Beatrice: check and compile results in a table specifically for this (see: function regret by k).
-			\item Much faster than XPess [do this much later]
-		\end{itemize}
-		\item Decrease in MMR is linear with nb of questions
-		\begin{itemize}
-			\item Redo nice graph of Beatrice with same sizes.
-		\end{itemize}
+		\item Pessimistic VS Elitist
+		\item Reach regret: $n/10$. For this, we need $m^x n$ questions. 
 		\item Value of information qC VS qV with 2 phases and 2phases VS interleaving
@@
 		\end{itemize}
-		\item Pessimistic approx Optimistic [do this much later]
+		\item find a way of displaying the graph so that it is understandable in B/W.
+		\item Time comparison XPess VS Pess?
+		\item Check Pess VS XPess on other sizes.
+		\item ?
 	\end{enumerate}
-	TODO: find a way of displaying the graph so that it is understandable in B/W.
-	Variations around the small size. Time comparison XPess VS Pess?
-	Check Pess VS XPess on other sizes.
 }

### 2020-10-08 minimax.tex
Better value of info

@@
 The \strat{Two phases} strategy is developed in order to investigate the effect of varying the proportion of questions asked to agents and to the chair, and compare the performance of asking questions to the chair first or to the voters first.
-The \strat{Two phases - ac} variant first asks $p$ questions to the agents, then $k-p$ questions to the chair, using in both cases Pessimistic to select the specific questions; whereas the \strat{Two phases - ca} variant starts with $p$ questions to the chair, then questions the agents.
+It is parameterized by $p$, a value indicating the number of questions that must be asked to the chair.
+The \strat{Two phases - ca} variant first asks $p$ questions to the chair, then $k-p$ questions to the agents, using in both cases Pessimistic to select the specific questions; whereas the \strat{Two phases - ac} variant starts with $k - p$ questions to the agents, then questions the chair.
 %Note that when asking first only questions to the chair, if the obtained knowledge approximates well the scoring vector, then in the second part of the elicitation we fall into the more classical setting of incompleteness of preferences assuming a known voting rule.
@@
 		\item Reach regret: $n/10$. For this, we need $m^x n$ questions. 
-		\item Value of information qC VS qV with 2 phases and 2phases VS interleaving
-		\begin{itemize}
-			\item Interleaving $k$ questions is similar to asking $p$ questions to the chair first and then $k - p$ to the voters when $p$ is chosen optimally. [do this a bit later]
-			\item A question to the chair has a similar value (in regret) as a qV: use the graph summarized by Olivier. Check prop. qC. Check on other sizes.
-		\end{itemize}
 		\item find a way of displaying the graph so that it is understandable in B/W.
@@
 		\item Check Pess VS XPess on other sizes.
-		\item ?
+		\item Prop qC in value of information
 	\end{enumerate}
@@
 
-\subsection{Judging Pessimistic relatively}
+\subsection{Relative evaluation of Pessimistic strategy}
 \begin{table}
@@
 
-\subsection{Judging Pessimistic absolutely}
+\subsection{Absolute evaluation of Pessimistic strategy}
 \label{sec:lowRegret}
@@
 
-\subsection{Comparing with full elicitation}
-In this work, we advocate obtaining an approximate winner without obtaining the full profile or determine completely the voting rule.
-The previous section evaluate the number of questions per voter to reach a low regret value.
-In this section we want to contrast our approach to one that would obtain the full profile on the one hand, and determine the voting rule on the other hand.
-More precisely, we want to estimate the number of questions that would be required to elicit the complete profile.
-We focus on the profile because eliciting the scores to full precision would require infinitely many questions, with the questions we use.
-Note that this may underestimate the number of questions required to determine completely the profile and the rule, as questions to the agents yield no information about the scoring vector.
-
-To estimate this number, we draw one linear order randomly (with equiprobability over all possible linear orders) and assume the following querying process: given a partial ordering representing our knowledge so far of an agent preferences, we pick a question equiprobably among the remaining edges, and add the edge in the appropriate direction to our partial ordering.
-We count the average number of questions required to reach a complete ordering.
-
 \subsection{Decrease in MMR values}
@@
 This is important practically because it may be impossible or unwanted to ask enough questions to reach low level of regrets, as computed in \cref{sec:lowRegret}.
-Knowing the speed of decrease thus permits to know which trade-offs can be achieved between the quality of the resulting recommendation and the number of questions that participants have to answer.
+Knowing the speed of decrease permits to know which trade-offs can be achieved between the quality of the resulting recommendation and the number of questions that participants have to answer.
 \Cref{fig:linearity} shows graphically the decrease in $\MMR$ according to the number of questions asked for various problem sizes.
-We see that this function is convex, apart from the very few questions, indicating to users of our approach that asking, for example, half the number of questions required to reach a low regret value will still yield a significant gain in regret, namely, more than half the distance to the low regret value.
+We see that this function is convex, apart from the very first few questions, indicating to users of our approach that asking, for example, half the number of questions required to reach a low regret value will still yield a significant gain in regret, namely, more than half the distance to the low regret value.
 
@@
 
-The experiments so far let the strategy decide the target of its questions, leaving open the possibility of questioning either the chair or an agent at each step.
-It may be desired in practical implementations to restrict the strategy to ask questions to agents only, or mostly, or to wonder what is lost in terms of regret by asking more questions to the chair, or what is lost if the circumstances require to ask all questions to the chair first, then only question the voters, or the other way around.
+%In this work, we advocate obtaining an approximate winner without determining completely the voting rule, or the profile.
+\Cref{sec:lowRegret} evaluates the number of questions per voter required to reach a low regret value.
+%In this section we want to explore to which extent it is possible to recommend without knowing the voting rule.
+One extreme, in our setting, consists in knowing only that the weights are convex, our basis hypothesis.
+The
+
+%contrast our approach to one that would obtain the full profile on the one hand, and determine the voting rule on the other hand.
+More precisely, we want to estimate the number of questions that would be required to elicit the complete profile.
+We focus on the profile because eliciting the weights to full precision would require infinitely many questions, with the questions we use.
+%Note that this may underestimate the number of questions required to determine completely the profile and the rule, as questions to the agents yield no information about the scoring vector.
+
+%To estimate this number, we draw one linear order randomly (with equiprobability over all possible linear orders) and assume the following querying process: given a partial ordering representing our knowledge so far of an agent preferences, we pick a question equiprobably among the remaining edges, and add the edge in the appropriate direction to our partial ordering.
+We count the average number of questions required to reach a complete ordering.
+
+The experiments so far let the strategy target its questions unrestrictively, leaving open the possibility of questioning either the chair or an agent at each step.
+It may be desired in practical implementations to restrict the strategy to question the agents only, or mostly, or to wonder what is lost in terms of regret by asking different proportions of questions to the chair and the agents.
 Such restrictions may be useful because of (partial) unavailability of the chair, or because the estimated cognitive costs may differ sensibly, as these types of questions differ in nature.
-\Cref{tab:twoP400} show the MMR value that is reached in a problem of size $m = 10, n = 20$ after $400$ questions, using various constraints added to the Pessimistic strategy.
+\Cref{tab:twoP400} show the MMR value that is reached in a problem of size $m = 10, n = 20$ after $400$ questions, using the Two phases strategy.
 The constraints have this form: the strategy must ask $p$ questions to the chair first, then $400 - p$ questions to the agents; or conversely, must ask $400 - p$ questions to the agents before turning to the chair.
 These numbers are to be compared with the MMR value reached after 400 questions with the unconstrained Pessimistic strategy (displayed in \cref{fig:linearity}), which is $0.62$.% ± $0.56$.
+
+These numbers highlight that it is possible to obtain a good-quality recommendation while knowing only that the voting rule is a scoring rule and that the weights are convex, which is our basic hypothesis: when $p = 0$, no question is asked to the chair, and a good-quality recommendation is still reached after a relatively small number of questions.
+By contrast, the Pessimistic strategy, when unconstrained, asks X questions to the chair.
 
@@
 suggest that regret-based elicitation is effective and allow to quickly reduce worst regret significantly.
+They also highlight the importance of not insisting to obtain a completely specified voting rule, as good quality (low regret) recommendations can be achieved short of knowing the weights precisely, in our setting.
 %regret, but they also show that starting with zero knowledge became a pretentious approach really quickly when increasing the size of the problem.

### 2020-10-08 minimax.tex
Better descr Pess

@@
 The candidate questions to the agents use the heuristic proposed by \citet{Lu2011}: for each agent $j$, if $x^*$ and $\bar{y}$ are incomparable in $\ppref_j$, the candidate question concerns the pair $(x^*, \bar{y})$, otherwise, the candidate question concerns the pair $(x^*, z)$ for some $z$ incomparable to $x^*$ (randomly chosen), or if none such $z$ exist, the pair $(\bar{y}, z)$ for some $z$ incomparable to $\bar{y}$, or, if both $x^*$ and $\bar{y}$ are comparable to every alternatives in $\ppref_j$, any incomparable pair is picked at random.
-To understand the intuition behind favoring these two alternatives for our questions, recall that, as shown in the proof of \cref{claim:completion}, in order to increase $\PMR(x^{*},\bar{y})$, an adversary should place as many alternatives as she can above $x^{*}$ if $x^* \ppref_j \bar{y}$, and between $\bar{y}$ and $x^{*}$ if $\bar{y} \ppref_j x^*$.
+To understand the intuition behind favoring these two alternatives, recall that, as shown in the proof of \cref{claim:completion}, in order to increase $\PMR(x^{*},\bar{y})$, an adversary should place as many alternatives as she can above $x^{*}$ if $x^* \ppref_j \bar{y}$, and between $\bar{y}$ and $x^{*}$ if $\bar{y} \ppref_j x^*$.
 Asking questions involving $x^*$ or $\bar{y}$ thus has a particular chance of reducing usefully the possibilities of the adversary.
 The candidate questions to the chair are determined as in the Random strategy.
-The strategy then selects among these $n + m$ candidate questions one that leads to minimal regret in the worst case, considering both possible answers to the question.
-Assume that a question leads to the possible new knowledge states $(\pprofile_1, W_1)$ and $(\pprofile_2, W_2)$, depending on the answer, numbering them so that $\MMR(\pprofile_1, W_1) ≥ \MMR(\pprofile_2, W_2)$.
-Then the badness of the question in the worst case is:
+The strategy then selects among these $n + m$ candidate questions one that leads to minimal regret in the worst case, considering both possible answers to the question, and with penalty terms depending on the kind of question.
+To define this comparison precisely, assume that a question $q_1$ has type $t_1$ (being “chair” or “agent”), and leads to the possible new knowledge states $(\pprofile_1, W_1)$ and $(\pprofile'_1, W'_1)$, depending on the answer.
+Define $R^{\max}_1 = \max\set{\MMR(\pprofile_1, W_1), \MMR(\pprofile'_1, W'_1)}$
+and $R^{\min}_1 = \min\set{\MMR(\pprofile_1, W_1), \MMR(\pprofile'_1, W'_1)} p(t) + p'(t)$.
+%If $(\pprofile_1, W_1) ≥ (\pprofile'_1, W'_1)$, define $\MMR^{\max} = \MMR(\pprofile_1, W_1)$ and $\MMR^{\min} = \MMR(\pprofile'_1, W'_1)$; otherwise, define $\MMR^{\max} = \MMR(\pprofile'_1, W'_1)$ and $\MMR^{\min} = \MMR(\pprofile_1, W_1)$.
+% and and $(\pprofile^\min_2, W^\min_2)$. numbering them so that $\MMR(\pprofile_1, W_1) ≥ \MMR(\pprofile_2, W_2)$. Then the badness of the question in the worst case is:
+The terms $p(t)$ and $p'(t)$ are real numbers depending on the kind of question. These parameters are to be determined experimentally.
+Define similarly $t_2$, $R^{\max}_2$ and $R^{\min}_2$ for a question $q_2$.
+Then, the Pessimistic strategy considers question $q_1$ more suitable than $q_2$ iff
 \begin{align}
-	\MMR(\pprofile_1,W_1) + \frac{1}{10000}\MMR(\pprofile_2, W_2).
+	R^{\max}_1 ≤ R^{\max}_2 \text{ or } [R^{\max}_1 = R^{\max}_2 \text{ and } R^{\min}_1 ≤ R^{\min}_2].
 \end{align}
-This badness measure gives a way of picking questions among a set of possible questions, by picking one that minimizes this approximate measure of minimax regret {\em a posteriori}. 
+This comparison gives a way of picking questions among a set of possible questions, by picking one that minimizes this approximate measure of minimax regret {\em a posteriori}. 
 We use this operator that is similar to a $\max$ operator because \citet{Cailloux2014} reported that pessimistic aggregation works much better than optimistic aggregation, although our experiments in this context suggested a weak impact of that choice on the performance of the strategy.
-However, to avoid the absorption property of max, we adopt criterion closer to $\leximax$ as an aggregator: if the maximal $\MMR$ of two questions are (nearly) equal, then it considers the other $\MMR$ values, that are the one associated to the opposite answer, preferring the question with the lowest value.
-(Technically, instead of applying a pure lexicographic aggregation, which is very sensitive to small errors due to floating-point computations, we apply a weighted sum between the maximal and the minimal $\MMR$ values, with a predominant weight to the maximal one.)
+However, to avoid the absorption property of max, we adopt a criterion closer to $\leximax$ as an aggregator: if the maximal MMR of two questions are (nearly) equal, then it considers the other MMR values, that are the one associated to the opposite answer, preferring the question with the lowest value.
+(Technically, instead of applying a pure lexicographic aggregation, which is very sensitive to small errors due to floating-point computations, we apply a weighted sum between the maximal and the (penalized) minimal MMR values, with a predominant weight to the maximal one.)
 
@@
 The weights are generated by drawing $m-1$ differences randomly with uniform distribution, normalizing them, then ordering them, in order to ensure convexity.
+The penalty parameters for the Pessimistic and Extended pessimistic strategies are set to $p(t) = 1.1$ and $p'(t) = 10^{-6}$ when $t = $“chair” and $p(t) = 1.0$ and $p'(t) = 0$ when $t = $“agent”.
 
@@
 We see that the number of questions required grows approximately linearly with the number of voters and grows less fast than the square of the number of alternatives, for the sizes we considered.
-In other words, on average, assuming no questions get asked to the committee, each voter will have to answer $0.4m^{1.6}$ questions in order to to reach a low regret level.
+In other words, on average, assuming no questions get asked to the committee, each voter will have to answer $0.4m^{1.6}$ questions in order to to reach a low regret level, if this experimental formula reveals correct.
 For $m = 5$, that is about $6$ questions per voter; for $m = 10$, that is about $17$ questions per voter; and for $m = 15$, that is about $33$ questions per voter.

### 2020-10-08 minimax.tex
related work

--- 2020-10-08 minimax.tex
@@
 We also provide an interactive elicitation protocol based on minimax regret and develop several query strategies that question the chair and the agents in order to acquire the most relevant information for quickly converging to a near-optimal alternative.
-Finally, we find out experimentally that questioning voters is more useful than questioning the chair in our setting.
 \end{abstract}
@@
 %Also the first hypothesis should be relaxed considering that, in several situations, it may not be easy to precisely define the voting rule.Indeed, it is possible that the chair has some preferences over the desired aggregation method, but is not able to formalize the voting rule upfront.
-When considering positional scoring rules, several authors \citep{Stein1994, Llamazares2013, Viappiani2018} have worked on positional scoring rules with uncertain weights, assuming that the preferences of the agents are fully known.
+
 %it is possible to derive dominance relations (akin to stochastic dominance) that allow to eliminate some alternatives since they will be less preferred than another one for any instantiation of the weights \citep{Stein1994}.
@@
 Our approach permits to compare experimentally strategies that question the chair, the voters, or both.
-We describe informally here a few of the conclusions stemming from these experiments, given a problem involving $m$ alternatives and $n$ agents.
-First, a good quality recommendation can be reached by asking what can be considered a reasonable number of questions to the chair and agents.
-For example, in a problem of size $m = 5$, $n = 10$, $55$ questions in total are required to reach a good quality recommendation, whcih can be considered reasonable as these questions are to be dispatched over $10$ agents and the chair.
-Second, the quality of the recommendation increases faster than linearly with the number of questions, after only a few questions (the first few questions yield no increase in quality).
-Third, we experimentally find out that asking questions to the agents only performs similarly than asking questions both to the agents and the chair, although questions to the chair do have a positive value in terms of quality of the recommendation.
-%the value of information of one question to the chair is similar to the value of information of one question to a voter (in the ranges we considered), up to a certain proportion of questions asked to the chair.
+We describe informally here a few of the conclusions stemming from these experiments, given a problem involving $m$ alternatives and $n$ voters.
+First, low levels of regret can be reached by asking approximately $m n$ questions to the voters and $m$ questions to the chair.
+Second, the decrease in $\MMR$ is approximately linear with the number of questions asked, except when the regret approaches zero.
+\commentBN{Not true anymore, some example with Pess (former Lim.Pes.)
+$\begin{array}{ccc}
+	k \quad & \textbf{(5,10)}&\textbf{(10,20)}\\
+	0 \quad &10&20\\
+	10 \quad &7.93&19.5\\
+	20 \quad &5.85&18.2\\
+	30 \quad &4.31&17.43\\
+	40 \quad &3.01&16.56\\
+	50 \quad &1.95&15.59\\
+	100 \quad &0.0&11.91\\
+	150 \quad &0.0&8.92\\
+	200 \quad &0.0&6.24\\
+\end{array}
+$
+}\\
+Third, the value of information of one question to the chair is similar to the value of information of one question to a voter (in the ranges we considered).
 Knowing this permits to choose the questioning strategy wisely depending on the estimated cost of each kind of question, which depends on the application.
 
-The paper is organized as follows. \Cref{sec:related} reviews the works related to our objective.
+The paper is organized as follows.
 In Section \ref{sec:background} we provide the necessary background and in Section \ref{sec:mmr} we introduce the minimax criterion, that selects a winner that minimizes the worst possible regret.
@@
 \section{Related Work}
-\label{sec:related}
-%The work of \citet{Cailloux2014} provides elicitation methods for a quite general class of rules based on weak orders.
-%it is possible to derive dominance relations (akin to stochastic dominance) that allow to eliminate some alternatives since they will be less preferred than another one for any instantiation of the weights \citep{Stein1994}.
-%Among others, Llamazares and Pe{\~{n}}a have considered  the problem of dealing with underspecified weights in positional scoring rules.
+The recent growing interest in voting theory has also led to an increase in attention to its problems.
+One of these, the full information assumption; which has driven an increasing number of authors to question its validity.
+\citet{Conitzer2005} have studied the complexity of communication, using different voting rules, determining lower and upper bounds for it.
+They showed that, in the worst case, the agents should send their complete set of preference for most of the rule investigated.
+Considering then, cases where the information of agent preferences is only partial, \citet{Konczak05} have proposed a way to compute possible and necessary winners.
+They also showed that, even though this computation is hard in the general case, their method is polynomial in case of positional scoring rule.
+Later on, for the necessary winner problem, other authors have proposed polynomial-time algorithms when using maximin and Bucklin \citep{Xia2008}; sufficient conditions that assure tractability have been proved \citep{Pini2007}; and the uncertainty in weights has been considered \citep{Walsh2007,Viappiani2018}.
+From this starting point several studies on elicitation of agent preferences have been proposed \citep{Naamani-Dery2015,Kalech2011,Lu2011,Pini2009,Benabbou2016,Cailloux2014,Dey2016,Dey2016_2}, and analysis on when to stop the elicitation process have been conducted \citep{Walsh2009,Conitzer2009}.
+Although more interest
+
+Although more interest has been shown in the incompleteness of agent preferences, several authors have considered scenarios where the voting rule is partially defined.
+\citep{Stein1994, Viappiani2018}.
+Among others, \citet{Llamazares2013} have considered  the problem of dealing with variable weights in positional scoring rules.
+
+In this context, questions on the manipulability of voting rules have begun to arise.
+In fact, studies on the reactions of agents after others actions have been proposed \citep{Endriss2016,Dey2018,Dey2018_2}.
+It is worth precising that, in our work, we consider the agents to give their preferences in a secret way.
 
@@
 Optimal alternatives w.r.t. minimax regret are the ones with least max regret. 
-Observe that, whenever the $\PMR$ of an alternative $x$ (against some other alternative $y$) exceeds the best MR value found so far, we do not need to further evaluate $x$. 
+Observe that, whenever the $\PMR$ of an alternative $x$ (against some other alternative $y$) exceeds the best MR value found so far, we don't need to further evaluate $x$. 
 This idea can be exploited further by adopting a minimax-search tree \citep{Braziunas2011}.
@@
 
-Let $(x^{*},\bar{y}, \bar{\profile}, \bar{\w})$ be the current solution of the minimax regret, where $\bar{y}, \bar{\profile}, \bar{\w}$ are, respectively, the choice of $y$, the completion of the profile and the selection of weights for which $x^{*}$ is the minimax optimal alternative.
-The \strat{Pessimistic} strategy considers a set of $n + m$ candidate questions: one per agent, and one per rank.
-The candidate questions to the agents use the heuristic proposed by \citet{Lu2011}: for each agent $j$, if $x^*$ and $\bar{y}$ are incomparable in $\ppref_j$, the candidate question concerns the pair $(x^*, \bar{y})$, otherwise, the candidate question concerns the pair $(x^*, z)$ for some $z$ incomparable to $x^*$ (randomly chosen), or if none such $z$ exist, the pair $(\bar{y}, z)$ for some $z$ incomparable to $\bar{y}$, or, if both $x^*$ and $\bar{y}$ are comparable to every alternatives in $\ppref_j$, any incomparable pair is picked at random.
-To understand the intuition behind favoring these two alternatives for our questions, recall that, as shown in the proof of \cref{claim:completion}, in order to increase $\PMR(x^{*},\bar{y})$, an adversary should place as many alternatives as she can above $x^{*}$ if $x^* \ppref_j \bar{y}$, and between $\bar{y}$ and $x^{*}$ if $\bar{y} \ppref_j x^*$.
-Asking questions involving $x^*$ or $\bar{y}$ thus has a particular chance of reducing usefully the possibilities of the adversary.
-The candidate questions to the chair are determined as in the Random strategy.
-The strategy then selects among these $n + m$ candidate questions one that leads to minimal regret in the worst case, considering both possible answers to the question.
-Assume that a question leads to the possible new knowledge states $(\pprofile_1, W_1)$ and $(\pprofile_2, W_2)$, depending on the answer, numbering them so that $\MMR(\pprofile_1, W_1) ≥ \MMR(\pprofile_2, W_2)$.
+The \strat{Pessimistic} strategy considers the same candidate questions as the Random strategy, but instead of picking one among those randomly, selects the question that leads to minimal regret in the worst case, considering both possible answers to the question.
+Assume that a question leads to the possible new knowledge states $(\pprofile_1, W_1)$ and $(\pprofile_2, W_2)$, depending on the answer.
 Then the badness of the question in the worst case is:
 \begin{align}
-	\MMR(\pprofile_1,W_1) + \frac{1}{10000}\MMR(\pprofile_2, W_2).
+	\max_{i=1,2} \MMR(\pprofile_i,W_i)
 \end{align}
-This badness measure gives a way of picking questions among a set of possible questions, by picking one that minimizes this approximate measure of minimax regret {\em a posteriori}. 
-We use this operator that is similar to a $\max$ operator because \citet{Cailloux2014} reported that pessimistic aggregation works much better than optimistic aggregation, although our experiments in this context suggested a weak impact of that choice on the performance of the strategy.
-However, to avoid the absorption property of max, we adopt criterion closer to $\leximax$ as an aggregator: if the maximal $\MMR$ of two questions are (nearly) equal, then it considers the other $\MMR$ values, that are the one associated to the opposite answer, preferring the question with the lowest value.
+This badness measure gives a way of picking questions among a set of possible questions, by picking one that minimizes ths measure of minimax regret {\em a posteriori}. 
+Note that other aggregators than $\max$ can be used as well. 
+We use the $\max$ operator because \citet{Cailloux2014} reported that pessimistic aggregation works much better than optimistic aggregation, although our experiments in this context suggested a weak impact of that choice on the performance of the strategy.
+However, to avoid the absorption property of max, we adopt the $\leximax$ criterion as an aggregator: if the maximal $\MMR$ of two questions are equal, then it considers the other $\MMR$ values, that are the one associated to the opposite answer, preferring the question with the lowest value.
 (Technically, instead of applying a pure lexicographic aggregation, which is very sensitive to small errors due to floating-point computations, we apply a weighted sum between the maximal and the minimal $\MMR$ values, with a predominant weight to the maximal one.)
+We expect this strategy to perform very well, but only for very small problem instances: its complexity is in $O(n^2 m^5)$, because we consider $O(m^2)$ questions for each agent and need for each question to compute $\MMR$ twice, whose complexity is $O(nm^3)$.
+For small dimensions, it estimates an upper bound to the possible quality of a myopic strategy.
 
-The \strat{Extended pessimistic} strategy uses the same criterion as the pessimistic strategy, but extending it to a bigger set of $m^2 n + m$ candidate questions, the same as those considered by the Random strategy.
-After having selected the candidate questions, we apply the same operator as for the Pessimistic strategy: we evaluate, for each of the possible questions, the minimax regret for the two possible answers and we choose the best according to (quasi-)$\leximax$.
-We use this strategy to test whether Pessimistic performs well: depending on the quality of the heuristic of the Pessimistic strategy, it might perform nearly equally well, or perhaps even better, than Extended pessimistic, while being (much) more efficient.
-We expect that Extended pessimistic will be applicable only to very small problem instances: its complexity is in $O(n^2 m^5)$, because we consider $O(m^2)$ questions for each agent and need for each question to compute $\MMR$ twice, whose complexity is $O(nm^3)$.
+The \strat{Limited pessimistic} strategy uses the same criterion as the pessimistic strategy, but limiting it to a small set of $n + m$ candidate questions: one per agent, and one per rank.
+Let $(x^{*},\bar{y}, \bar{\profile}, \bar{\w})$ be the current solution of the minimax regret, where $\bar{y}, \bar{\profile}, \bar{\w}$ are, respectively, the choice of $y$, the completion of the profile and the selection of weights for which $x^{*}$ is the minimax optimal alternative.
+The \strat{Limited pessimistic} strategy first selects $n$ candidates questions to the agents using the heuristic proposed by \citet{Lu2011}: for each agent $j$, if $x^*$ and $\bar{y}$ are incomparable in $\ppref_j$, the candidate question concerns the pair $(x^*, \bar{y})$, otherwise, the candidate question concerns the pair $(x^*, z)$ for some $z$ incomparable to $x^*$ (randomly chosen), or if none such $z$ exist, the pair $(\bar{y}, z)$ for some $z$ incomparable to $\bar{y}$, or, if both $x^*$ and $\bar{y}$ are comparable to every alternatives in $\ppref_j$, any incomparable pair is picked at random.
+To understand the intuition behind favoring these two alternatives for our questions, recall that, as shown in the proof of \cref{claim:completion}, in order to increase $\PMR(x^{*},\bar{y})$, an adversary should place as many alternatives as she can above $x^{*}$ if $x^* \ppref_j \bar{y}$, and between $\bar{y}$ and $x^{*}$ if $\bar{y} \ppref_j x^*$.
+\commentOC{I do not understand the reasoning in the next sentence.}
+An intuitive way to reduce the pairwise max regret would be, therefore, to ask questions involving such alternatives, hoping for an answer that would prevent the adversary to play his best game. 
+The candidate questions to the chair are determined as in the Random and Pessimistic strategies.
+After having selected the candidate questions, we apply the Pessimistic strategy: we evaluate, for each of the questions, the minimax regret for the two possible answers and we choose the best according to $\leximax$.
 
 The \strat{Two phases} strategy is developed in order to investigate the effect of varying the proportion of questions asked to agents and to the chair, and compare the performance of asking questions to the chair first or to the voters first.
-The \strat{Two phases - ac} variant first asks $p$ questions to the agents, then $k-p$ questions to the chair, using in both cases Pessimistic to select the specific questions; whereas the \strat{Two phases - ca} variant starts with $p$ questions to the chair, then questions the agents.
+The \strat{Two phases - ac} variant first asks $p$ questions to the agents, then $k-p$ questions to the chair, using in both cases Limited pessimistic to select the specific questions; whereas the \strat{Two phases - ca} variant starts with $p$ questions to the chair, then questions the agents.
 %Note that when asking first only questions to the chair, if the obtained knowledge approximates well the scoring vector, then in the second part of the elicitation we fall into the more classical setting of incompleteness of preferences assuming a known voting rule.
 %And vice-versa when asking first questions to the agents, the second part of the elicitation is similar to the setting of incompletely specified scoring rule. 
-%This strategy also permits to simulate the current state of the art when considering incomplete preferences.
+This strategy also permits to simulate the current state of the art when considering incomplete preferences.
 By asking enough questions to the chair we can reduce our problem into a well studied one of incompleteness of preferences knowing the voting rule.
@@
 	\begin{enumerate}
-		\item Pessimistic VS Elitist
-		\item Reach regret: $n/10$. For this, we need $m^x n$ questions. 
+		\item Pessimistic is feasible and much better than Random
+		\begin{itemize}
+			\item Graph featuring (5, 10, 150, 200 runs), Random, Pess, L. pess, Elitist.
+			\item And table like table 1.
+		\end{itemize}
+		\item Limited pessimistic performs well.
+		\begin{itemize}
+			\item Reach regret: $n/10$. For this, we need $m^x n$ questions. TODO Olivier: find $x$. TODO Beatrice: check and compile results in a table specifically for this (see: function regret by k).
+			\item Almost as good as Pess and better than the Elitist one (see previous graphs or table)
+			\item Much faster [do this much later]
+		\end{itemize}
+		\item Decrease in MMR is linear with nb of questions
+		\begin{itemize}
+			\item Redo nice graph of Beatrice with same sizes.
+		\end{itemize}
 		\item Value of information qC VS qV with 2 phases and 2phases VS interleaving
@@
 		\end{itemize}
-		\item find a way of displaying the graph so that it is understandable in B/W.
-		\item Time comparison XPess VS Pess?
-		\item Check Pess VS XPess on other sizes.
-		\item ?
+		\item Limited pessimistic approx Limited optimistic [do this much later]
 	\end{enumerate}
@@
 
-\subsection{Judging Pessimistic relatively}
+\subsection{Small size elections}
+Our first experimental result concerns small size situations.
+We picked $m = 5, n = 10$ to illustrate our results (variations around these sizes yield similar conclusions).
+In such situations, we can run the resource-consuming Pessimistic strategy.
+Table x / graph x compares it to other strategies.
+We see that these strategies perform much better than random, even when its parameter $\pi$ is chosen in an optimal way, that is, when the proportion of questions asked to the chair is ideal.
+We also see a first important positive result for applicability of our approach, namely, that it is possible to reach a small regret with a reasonable number of questions in such problems.
+
+\subsection{Limited pessimistic}
+We next investigate the better performing Limited pessimistic strategy, because Pessimistic is too slow to be ran repeatedly on much bigger problem sizes.
+
+\subsection{Our previous presentation}
+\sisetup{round-mode=places, round-precision=2, table-figures-integer=2, table-figures-decimal=2}
 \begin{table}
@@
 	\end{center}
-	\caption{Average MMR in problems of size $(5, 10)$ after $k$ questions and $200$ runs.}
-	\label{tab:smallSize}
+	\caption{Average $\MMR$ in problems of size $(5, 10)$ after $k$ questions and $200$ runs.\commentBN{Attention, I already corrected the table with the new names.
+The column Pes.
+here is the Limited Pessimistic, I inverted them to follow the presentation order.}}
+	\label{tab:comparison}
 \end{table}
@@
 	\includegraphics[width=.45\textwidth]{comparison.png}
-	\caption{Plot in support of \cref{tab:smallSize}}
-	\label{fig:smallSize}
+	\caption{Plot in support of \cref{tab:comparison}}
+	\label{fig:comparison}
 \end{figure}
 
-Our first experimental result concerns small size situations. We picked $m = 5, n = 10$ to illustrate our results (variations around this size yield similar conclusions). 
-\Cref{tab:smallSize} and \cref{fig:smallSize} compares some of our strategies in this case.
-We see that that Pessimistic performs better than Random and Extended pessimistic on a small size problem.
-(These figures also display the performance of the Elitist strategy, to which we will come back.)
-
-We observe that the Pessimistic strategy is able to reduce the regret almost completely after $30$ questions.
-We also see that Pessimistic performs slightly better than Extended pessimistic, showing that Pessimistic chooses candidate questions wisely; this is good news since (for $m = 5$ and $n = 10$), the latter strategy is much faster and takes only $15s$ for a complete elicitation session, while the former takes $80s$.
-
-Asking Random questions does not permit to reach a low regret level even after having asked 100 questions, whereas a low regret level (MMR = 1) is reached by Pessimistic before having asked 60 questions.
-
-We also see that Extended pessimistic performs slightly less well than Pessimistic.
-Although they come close, Extended pessimistic performs significatively less well, in the sense that the numbers are consistently in favor of Pessimistic if running the experiment again.
-
-We next focus on the Pessimistic strategy, because Extended pessimistic is too slow to be ran repeatedly on much bigger problem sizes.
-
-\subsection{Judging Pessimistic absolutely}
-\label{sec:lowRegret}
-\begin{table}
-	\begin{center}
-		\begin{tabular}{S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-number-alignment = center]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]}
-			\toprule
-			{m} & {n} & {$\frac{n}{10}$} & {$k_{\MMR}$} & {$0.4 m^{1.6} n$} \\
-			\midrule
-			5 & 10 & 1.0 & 60 &  55 \\
-			5 & 15 & 1.5 & 80 &  83 \\
-			5 & 20 & 2.0 & 110 &  110 \\
-			10 & 20 & 2.0 & 340 &  341 \\
-			10 & 30 & 3.0 & 527 &  512 \\
-			15 & 30 & 3.0 &  &  991 \\
-			\bottomrule
-		\end{tabular}
-	\end{center}
-	\caption{Number of questions needed by Pessimistic strategy to reach $\MMR=\frac{n}{10}$ (represented by $k_{\MMR}$), for various problem sizes.}
-	\label{tab:lowRegret}
-\end{table}
-
-The previous section compares Pessimistic to other strategies.
-In this set of experiments, we wonder about the absolute quality of Pessimistic.
-For practical usability, it is important to know how many questions should be asked in order to reach a low regret level.
-Here, we consider a low level to be a tenth of the number of voters ($n/10$): such a regret is equivalent to the difference of score of an alternative $x$ that results from switching from a profile $P$ to a profile $P'$ where ten percent of the voters rank $x$ last instead of first.
-The results for various sizes are displayed in \cref{tab:lowRegret}.
-From these numbers, we obtain the function $0.4m^{1.6}n$ as a general approximation formula for the number of questions required to reach a low regret level.
-We see that the number of questions required grows approximately linearly with the number of voters and grows less fast than the square of the number of alternatives, for the sizes we considered.
-In other words, on average, assuming no questions get asked to the committee, each voter will have to answer $0.4m^{1.6}$ questions in order to to reach a low regret level.
-For $m = 5$, that is about $6$ questions per voter; for $m = 10$, that is about $17$ questions per voter; and for $m = 15$, that is about $33$ questions per voter.
-
-\subsection{Comparing with full elicitation}
-In this work, we advocate obtaining an approximate winner without obtaining the full profile or determine completely the voting rule.
-The previous section evaluate the number of questions per voter to reach a low regret value.
-In this section we want to contrast our approach to one that would obtain the full profile on the one hand, and determine the voting rule on the other hand.
-More precisely, we want to estimate the number of questions that would be required to elicit the complete profile.
-We focus on the profile because eliciting the scores to full precision would require infinitely many questions, with the questions we use.
-Note that this may underestimate the number of questions required to determine completely the profile and the rule, as questions to the agents yield no information about the scoring vector.
-
-To estimate this number, we draw one linear order randomly (with equiprobability over all possible linear orders) and assume the following querying process: given a partial ordering representing our knowledge so far of an agent preferences, we pick a question equiprobably among the remaining edges, and add the edge in the appropriate direction to our partial ordering.
-We count the average number of questions required to reach a complete ordering.
-
-\subsection{Decrease in MMR values}
 \begin{figure}
@@
 
-We next wonder how fast the regret decreases, measured as a function of the number of questions asked.
-This is important practically because it may be impossible or unwanted to ask enough questions to reach low level of regrets, as computed in \cref{sec:lowRegret}.
-Knowing the speed of decrease thus permits to know which trade-offs can be achieved between the quality of the resulting recommendation and the number of questions that participants have to answer.
-\Cref{fig:linearity} shows graphically the decrease in $\MMR$ according to the number of questions asked for various problem sizes.
-We see that this function is convex, apart from the very few questions, indicating to users of our approach that asking, for example, half the number of questions required to reach a low regret value will still yield a significant gain in regret, namely, more than half the distance to the low regret value.
+\begin{table}
+	\begin{center}
+		\begin{tabular}{S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-number-alignment = center]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]}
+			\toprule
+			{m} & {n} & {$\frac{n}{10}$} & {$k_{\MMR}$} & {$m\cdot n +m^?$} \\
+			\midrule
+			5 & 10 & 1.0 & 60 &  \\
+			5 & 15 & 1.5 & 80 &  \\
+			5 & 20 & 2.0 & 110 &  \\
+			10 & 20 & 2.0 & 340 &  \\
+			10 & 30 & 3.0 & 527 &  \\
+			15 & 30 & 3.0 & 919 &  \\
+			\bottomrule
+		\end{tabular}
+	\end{center}
+	\caption{Number of questions needed by Pessimistic strategy to reach $\MMR=\frac{n}{10}$ (represented by $k_{\MMR}$), for different problem sizes.}
+	\label{tab:linearity}
+\end{table}
 
-\subsection{Value of information comparison}
+We test our strategies using randomly generated datasets. 
+Our first goal is to see, with a small problem size ($m = 5, n = 5$) and the (time consuming) Pessimistic strategy, if an important lowering of the maximal regret can be achieved with a reasonable number of questions.
+We also want to estimate how “hard” such a problem is, by using the Random strategy as a baseline.
+Third, we want to estimate the loss (in terms of worst regret) when switching to the faster Limited pessimistic strategy.
+Fourth, we want to see, on a bigger problem size ($m = 10, n = 20$), how many questions must be asked for that strategy to achieve a significant reduction of the worst regret.
+Finally, we want to evaluate, thanks to the Two phases strategy, the impact of varying the proportion of questions asked to the agents (with respect to questions asked to the chair) on the reduction of the worst regret.
+%We also want to see how realistic our approach is for various problem sizes, by estimating the number of questions we would have to ask before being able to reduce the worst regret significantly.
+
+The results are displayed in \cref{tab:comparison,fig:linearity,tab:twoP}, where strategies are designated by Rnd for Random, Pes.
+for Pessimistic, L.\ pes.
+for Limited pessimistic and 2 ph.
+for Two phases.
+
+We observe that the Pessimistic strategy is able to reduce the regret almost completely after $30$ questions.
+We also see that Limited pessimistic performs almost as well as Pessimistic; this is good news since (for $m=5$ and $n=5$), the former strategy is much faster and takes only $2.6s$ for a complete elicitation session, while the latter takes $16s$.
+%However, it takes $1000$ times more time than the \strat{Random} strategy ($16s$ of the Pessimistic compared to $0.014s$ of the Random).
+Moreover, the results of the \strat{Limited pessimistic}, that takes almost $80\%$ less of the time of the \strat{Pessimistic} ($2.6s$), are essentially the same.
+%In Table \ref{fig:1020}, we can see the drop of regret using a bigger instance.
+%Finally in Table \ref{fig:p}
+%
+%\begin{table}
+%	\begin{center}
+%		\begin{tabular}{S[table-figures-integer=3, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
+%			\toprule
+%			{p} & {Comm. Fst.} & {sd} & {Vot. Fst.} & {sd} \\
+%			\midrule
+%			0 & 0.48 &0.59 & 0.48 &0.59  \\
+%			50 & 0.01 & 0.04& 0.0 & 0.0 \\
+%			100 & 0.04 & 0.09 & 0.13 & 0.35 \\
+%			150 & 0.68 & 0.65 & 0.66 & 0.77 \\
+%			200 &   &  &  &  \\
+%			250 & 3.2 & 1.67 & 4.07	& 1.51 \\
+%			300 &&&& \\
+%			350 &&&& \\
+%			400 &&&& \\
+%			450 &&&& \\
+%			500 &&&& \\
+%			\bottomrule
+%		\end{tabular}
+%	\end{center}
+%	\caption{Average regret in problems of size $(10, 20)$ after $500$ questions and $10$ runs. Where $p$ represents the number of questions asked to the chair.}
+%	\label{tab:twoP500}
+%\end{table}
+
 \begin{table}
@@
 			50 & 1.23 & 1.46 & 0.8 & 0.79 \\
-			100 & 2.03 & 1.56 &  &  \\
+			100 & 2.03 & 1.56 & 1.88 & 1.02  \\
 			150 & 3.41 & 1.79 & 4.07 & 1.51 \\
-			200 &   &  &  &  \\
-			250 & 8.4 & 1.86 & 	& \\
-			300 &&&& \\
-			350 &&&& \\
-			400 &&&& \\
+			200 & 4.61	& 1.35  & 6.53 & 2.0  \\
+			250 & 8.4 & 1.86 & 	7.69 & 1.24 \\
+			300 &11.07 & 0.86& 11.87 & 1.25 \\
+			350 &&&15.59 & 0.6 \\
+			400 &20.0 & 0.0 & 20.0 & 20.0 \\
 			\bottomrule
@@
 	\end{center}
-	\caption{Average $\MMR$ in problems of size $(10, 20)$ after $400$ questions and $10$ runs. Where $p$ represents the number of questions asked to the chair.}
+	\caption{Average $\MMR$ in problems of size $(10, 20)$ after $400$ questions and $10$ runs.
+Where $p$ represents the number of questions asked to the chair.
+(The $\MMR$ after 400 questions with Pessimistic is $0.62$ ± $0.56$)}
 	\label{tab:twoP400}
 \end{table}
-
-The experiments so far let the strategy decide the target of its questions, leaving open the possibility of questioning either the chair or an agent at each step.
-It may be desired in practical implementations to restrict the strategy to ask questions to agents only, or mostly, or to wonder what is lost in terms of regret by asking more questions to the chair, or what is lost if the circumstances require to ask all questions to the chair first, then only question the voters, or the other way around.
-Such restrictions may be useful because of (partial) unavailability of the chair, or because the estimated cognitive costs may differ sensibly, as these types of questions differ in nature.
-\Cref{tab:twoP400} show the MMR value that is reached in a problem of size $m = 10, n = 20$ after $400$ questions, using various constraints added to the Pessimistic strategy.
-The constraints have this form: the strategy must ask $p$ questions to the chair first, then $400 - p$ questions to the agents; or conversely, must ask $400 - p$ questions to the agents before turning to the chair.
-These numbers are to be compared with the MMR value reached after 400 questions with the unconstrained Pessimistic strategy (displayed in \cref{fig:linearity}), which is $0.62$.% ± $0.56$.
 

### 2020-10-08 minimax.tex

--- 2020-10-08 minimax.tex
@@
 \label{sec:related}
-%The work of \citet{Cailloux2014} provides elicitation methods for a quite general class of rules based on weak orders.
-%it is possible to derive dominance relations (akin to stochastic dominance) that allow to eliminate some alternatives since they will be less preferred than another one for any instantiation of the weights \citep{Stein1994}.
-%Among others, Llamazares and Pe{\~{n}}a have considered  the problem of dealing with underspecified weights in positional scoring rules.
+The recent growing interest in voting theory has also led to an increase in attention to its problems.
+One of these, the full information assumption; which has driven an increasing number of authors to question its validity.
+\citet{Conitzer2005} have studied the complexity of communication, using different voting rules, determining lower and upper bounds for it.
+They showed that, in the worst case, the agents should send their complete set of preference for most of the rule investigated.
+Considering then, cases where the information of agent preferences is only partial, \citet{Konczak05} have proposed a way to compute possible and necessary winners.
+They also showed that, even though this computation is hard in the general case, their method is polynomial in case of positional scoring rule.
+Later on, for the necessary winner problem, other authors have proposed polynomial-time algorithms when using maximin and Bucklin \citep{Xia2008}; sufficient conditions that assure tractability have been proved \citep{Pini2007}; and the uncertainty in weights has been considered \citep{Walsh2007,Viappiani2018}.
+From this starting point several studies on elicitation of agent preferences have been proposed \citep{Naamani-Dery2015,Kalech2011,Lu2011,Pini2009,Benabbou2016,Cailloux2014,Dey2016,Dey2016_2}, and analysis on when to stop the elicitation process have been conducted \citep{Walsh2009,Conitzer2009}.
+Although more interest
+
+Although more interest has been shown in the incompleteness of agent preferences, several authors have considered scenarios where the voting rule is partially defined.
+\citep{Stein1994, Viappiani2018}.
+Among others, \citet{Llamazares2013} have considered  the problem of dealing with variable weights in positional scoring rules.
+
+In this context, questions on the manipulability of voting rules have begun to arise.
+In fact, studies on the reactions of agents after others actions have been proposed \citep{Endriss2016,Dey2018,Dey2018_2}.
+It is worth precising that, in our work, we consider the agents to give their preferences in a secret way.
 
@@
 			10 & 30 & 3.0 & 527 &  512 \\
-			15 & 30 & 3.0 &  &  991 \\
+			15 & 30 & 3.0 & 919 &  991 \\
 			\bottomrule

### 2020-10-08 minimax.tex
Wording
Minor again

@@
 This approach guarantees that the top alternative in the ranking of $j$ will be known after having asked $j$ exactly $m-1$ questions.
-After having asked $n (m-1)$ questions to the agents, it questions the chair only, using the same approach as the Limited strategy.
+After having asked $n (m-1)$ questions to the agents, it questions the chair only, using the same approach as the Pessimistic strategy.
 This strategy can be expected to perform well when the chair assigns an important weight to the first rank, as compared to the other ranks.
-It will be useful to further challenge the Limited strategy, which is not specifically tailored to such a situation.
+It will be useful to further challenge the Pessimistic strategy, which is not specifically tailored to such a situation.
 

### 2020-10-08 minimax.tex
One more table (whoohoo) and agen instead of voter

@@
 %This paper considers both sources of uncertainty at the same time, and proposes a method able to recommend a consensus choice without requiring full knowledge of either.
-This is useful because providing such information is often costly: the chair may find it hard to specify a rule completely; voters may need time to form reflective preferences.
+This is useful because providing such information is often costly: the chair may find it hard to specify a rule completely; agents may need time to form reflective preferences.
 
@@
 We also provide an interactive elicitation protocol based on minimax regret and develop several query strategies that question the chair and the agents in order to acquire the most relevant information for quickly converging to a near-optimal alternative.
-Finally, we find out experimentally that questioning voters is more useful than questioning the chair in our setting.
+Finally, we find out experimentally that questioning agents is more useful than questioning the chair in our setting.
 \end{abstract}
@@
 \paragraph{Experimental conclusions}
-Our approach permits to compare experimentally strategies that question the chair, the voters, or both.
+Our approach permits to compare experimentally strategies that question the chair, the agents, or both.
 We describe informally here a few of the conclusions stemming from these experiments, given a problem involving $m$ alternatives and $n$ agents.
@@
 Third, we experimentally find out that asking questions to the agents only performs similarly than asking questions both to the agents and the chair, although questions to the chair do have a positive value in terms of quality of the recommendation.
-%the value of information of one question to the chair is similar to the value of information of one question to a voter (in the ranges we considered), up to a certain proportion of questions asked to the chair.
+%the value of information of one question to the chair is similar to the value of information of one question to a agent (in the ranges we considered), up to a certain proportion of questions asked to the chair.
 Knowing this permits to choose the questioning strategy wisely depending on the estimated cost of each kind of question, which depends on the application.
@@
 We now introduce some basic concepts.
-We consider a set $A$ of $m$ alternatives (products, restaurants, movies, public projects, job candidates, etc.) and a set $\set{1, …, n}$ of agents (voters).
+We consider a set $A$ of $m$ alternatives (products, restaurants, movies, public projects, job candidates, etc.) and a set $\set{1, …, n}$ of agents.
 Each agent $j$ comes from an infinite set $\N$ of potential agents and is associated to her “real” preference order ${\pref_j}  \in \linors$ which is a linear order (a connected, transitive, asymmetric relation) over the alternatives.
@@
 
-The \strat{Two phases} strategy is developed in order to investigate the effect of varying the proportion of questions asked to agents and to the chair, and compare the performance of asking questions to the chair first or to the voters first.
+The \strat{Two phases} strategy is developed in order to investigate the effect of varying the proportion of questions asked to agents and to the chair, and compare the performance of asking questions to the chair first or to the agents first.
 It is parameterized by $p$, a value indicating the number of questions that must be asked to the chair.
@@
 		\item Prop qC in value of information
+		\item Fix approximation formula
 	\end{enumerate}
@@
 the linear orders) and the weights associated with the chair's scoring rule.
-The preferences are generated following an impartial culture assumption: the linear order of each voter is generated independently from the other ones and all have the same probability of appearing.
+The preferences are generated following an impartial culture assumption: the linear order of each agent is generated independently from the other ones and all have the same probability of appearing.
 The weights are generated by drawing $m-1$ differences randomly with uniform distribution, normalizing them, then ordering them, in order to ensure convexity.
@@
 \end{table}
+\begin{table}
+	\begin{center}
+		\begin{tabular}{S[table-figures-integer=2, table-number-alignment = center, table-figures-decimal=0]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=2]}
+			\toprule
+			m & k \\
+			\midrule
+			5 & 6.6\\
+			10 & 24.8\\
+			15 & \\
+			\bottomrule
+		\end{tabular}
+	\end{center}
+	\caption{Number of questions needed by the Pessimistic strategy to elicit the complete preference of one agent.}
+	\label{tab:fullProfile}
+\end{table}
 
@@
 For practical usability, it is important to know how many questions should be asked in order to reach a low regret level.
-Here, we consider a low level to be a tenth of the number of voters ($n/10$): such a regret is equivalent to the difference of score of an alternative $x$ that results from switching from a profile $P$ to a profile $P'$ where ten percent of the voters rank $x$ last instead of first.
+Here, we consider a low level to be a tenth of the number of agents ($n/10$): such a regret is equivalent to the difference of score of an alternative $x$ that results from switching from a profile $P$ to a profile $P'$ where ten percent of the agents rank $x$ last instead of first.
 The results for various sizes are displayed in \cref{tab:lowRegret}. 
-From these numbers, we obtain the function $0.4m^{1.6}n$ as a general approximation formula for the number of questions required to reach a low regret level.
-We see that the number of questions required grows approximately linearly with the number of voters and grows less fast than the square of the number of alternatives, for the sizes we considered.
-In other words, on average, assuming no questions get asked to the committee, each voter will have to answer $0.4m^{1.6}$ questions in order to to reach a low regret level, if this experimental formula reveals correct.
-For $m = 5$, that is about $6$ questions per voter; for $m = 10$, that is about $17$ questions per voter; and for $m = 15$, that is about $33$ questions per voter.
+By relating the sizes to the column $k_{\MMR}$, we obtain the function $0.4m^{1.6}n$ as an approximation formula for the number of questions required to reach a low regret level.
+We see that the number of questions required grows approximately linearly with the number of agents and grows less fast than the square of the number of alternatives, for the sizes we considered.
+In other words, on average, assuming no questions get asked to the committee, each agent will have to answer $0.4m^{1.6}$ questions in order to to reach a low regret level, if this experimental formula reveals correct.
+For $m = 5$, that is about $6$ questions per agent; for $m = 10$, that is about $17$ questions per agent; and for $m = 15$, that is about $33$ questions per agent.
+These numbers have to be contrasted with those displayed in \cref{tab:fullProfile}.
+We constrained the Pessimistic strategy to ask questions to the agent only, and ran it on a single agent problem, with various values for $m$, to evaluate the number of questions required to elicit the full preference of an agent.
 
@@
 %In this work, we advocate obtaining an approximate winner without determining completely the voting rule, or the profile.
-\Cref{sec:lowRegret} evaluates the number of questions per voter required to reach a low regret value.
+\Cref{sec:lowRegret} evaluates the number of questions per agent required to reach a low regret value.
 %In this section we want to explore to which extent it is possible to recommend without knowing the voting rule.

### 2020-10-08 minimax.tex
Merge together (mostly Refs)

@@
 \label{sec:related}
-The recent growing interest in voting theory has also led to an increase in attention to its problems.
-One of these, the full information assumption; which has driven an increasing number of authors to question its validity.
-\citet{Conitzer2005} have studied the complexity of communication, using different voting rules, determining lower and upper bounds for it.
-They showed that, in the worst case, the agents should send their complete set of preference for most of the rule investigated.
-Considering then, cases where the information of agent preferences is only partial, \citet{Konczak05} have proposed a way to compute possible and necessary winners.
+In a social choice context, an increasing number of authors has been interested in obtaining information about winners with reduced assumptions about the knowledge of the agent preferences, assuming that the voting rule is known.
+\Citet{Conitzer2005} have studied the complexity of communication, using different voting rules, determining lower and upper bounds for it.
+They showed that, in the worst case, the agents should send their complete set of preference for most of the rules they investigated.
+\Citet{Konczak05} have proposed a way to compute possible and necessary winners when the knowledge of agent preferences is only partial, for various voting rules.
 They also showed that, even though this computation is hard in the general case, their method is polynomial in case of positional scoring rule.
-Later on, for the necessary winner problem, other authors have proposed polynomial-time algorithms when using maximin and Bucklin \citep{Xia2008}; sufficient conditions that assure tractability have been proved \citep{Pini2007}; and the uncertainty in weights has been considered \citep{Walsh2007,Viappiani2018}.
-From this starting point several studies on elicitation of agent preferences have been proposed \citep{Naamani-Dery2015,Kalech2011,Lu2011,Pini2009,Benabbou2016,Cailloux2014,Dey2016,Dey2016_2}, and analysis on when to stop the elicitation process have been conducted \citep{Walsh2009,Conitzer2009}.
-Although more interest
+Later on, for the necessary winner problem, other authors have proposed polynomial-time algorithms when using maximin and Bucklin \citep{Xia2008}; sufficient conditions that ensure tractability have been proved \citep{Pini2007}.
 
-Although more interest has been shown in the incompleteness of agent preferences, several authors have considered scenarios where the voting rule is partially defined.
-\citep{Stein1994, Viappiani2018}.
-Among others, \citet{Llamazares2013} have considered  the problem of dealing with variable weights in positional scoring rules.
+From this starting point, several studies on elicitation of agent preferences have been proposed \citep{Naamani-Dery2015,Kalech2011,Lu2011,Pini2009,Benabbou2016,Cailloux2014,Dey2016,Dey2016_2}, and analysis on when to stop the elicitation process have been conducted \citep{Walsh2009,Conitzer2009}.
 
-In this context, questions on the manipulability of voting rules have begun to arise.
-In fact, studies on the reactions of agents after others actions have been proposed \citep{Endriss2016,Dey2018,Dey2018_2}.
-It is worth precising that, in our work, we consider the agents to give their preferences in a secret way.
+Although more interest has been shown in the incompleteness of agent preferences, several authors have considered scenarios where the voting rule is partially defined \citep{Stein1994}.
+Among others, \citet{Llamazares2013} have considered the problem of dealing with variable weights in positional scoring rules, and \citet{Walsh2007, Viappiani2018} consider the uncertainty in weights assuming a positional scoring rule has been considered under the assumption that the agents preferences are known.
+\commentOC{Check Walsh.}
+
+Studies related to the manipulability of voting rules have been proposed in this context \citep{Endriss2016,Dey2018,Dey2018_2}, studying the reactions of agents when they learn incrementally about other agents preferences.
 
@@
 		\item Pessimistic VS Elitist
-		\item Reach regret: $n/10$. For this, we need $m^x n$ questions. 
+		\item Reach regret: $n/10$. For this, we need $m^x n$ questions. (Correct formula)
 		\item find a way of displaying the graph so that it is understandable in B/W.
-		\item Time comparison XPess VS Pess?
 		\item Check Pess VS XPess on other sizes.
 		\item Prop qC in value of information
-		\item Fix approximation formula
+		\item Time comparison XPess VS Pess? (If time, check our estimate)
 	\end{enumerate}
@@
 We see that the number of questions required grows approximately linearly with the number of agents and grows less fast than the square of the number of alternatives, for the sizes we considered.
-In other words, on average, assuming no questions get asked to the committee, each agent will have to answer $0.4m^{1.6}$ questions in order to to reach a low regret level, if this experimental formula reveals correct.
+In other words, on average, assuming no questions get asked to the chair, each agent will have to answer $0.4m^{1.6}$ questions in order to to reach a low regret level, if this experimental formula reveals correct.
 For $m = 5$, that is about $6$ questions per agent; for $m = 10$, that is about $17$ questions per agent; and for $m = 15$, that is about $33$ questions per agent.
@@
 			\toprule
-			{p} & {Com. Fst.} & {sd} & {Vot. Fst.} & {sd} \\
+			{p} & {2 ph.\ ca} & {sd} & {2 ph.\ ag} & {sd} \\
 			\midrule
@@
 Such restrictions may be useful because of (partial) unavailability of the chair, or because the estimated cognitive costs may differ sensibly, as these types of questions differ in nature.
-\Cref{tab:twoP400} show the MMR value that is reached in a problem of size $m = 10, n = 20$ after $400$ questions, using the Two phases strategy.
-The constraints have this form: the strategy must ask $p$ questions to the chair first, then $400 - p$ questions to the agents; or conversely, must ask $400 - p$ questions to the agents before turning to the chair.
+\Cref{tab:twoP400} show the MMR value that is reached in a problem of size $m = 10, n = 20$ after $400$ questions, using the Two phases strategy, in the “ca” (chair then agents) and in the “ac” (agents then chair) variants.
 These numbers are to be compared with the MMR value reached after 400 questions with the unconstrained Pessimistic strategy (displayed in \cref{fig:linearity}), which is $0.62$.% ± $0.56$.

### 2020-10-09 minimax.tex
More TODOs (yeah)
new figures and tables, more on rel work

@@
 They also showed that, even though this computation is hard in the general case, their method is polynomial in case of positional scoring rule.
-Later on, for the necessary winner problem, other authors have proposed polynomial-time algorithms when using maximin and Bucklin \citep{Xia2008}; sufficient conditions that ensure tractability have been proved \citep{Pini2007}.
+Later on, for the necessary winner problem, other authors have proposed polynomial-time algorithms when using maximin and Bucklin \citep{Xia2008}; showed that the general case remains computationally hard even when restricting to single-peaked preferences \citep{Walsh2007}; proved sufficient conditions that ensure tractability \citep{Pini2007}.
 
@@
 
-Although more interest has been shown in the incompleteness of agent preferences, several authors have considered scenarios where the voting rule is partially defined \citep{Stein1994}.
-Among others, \citet{Llamazares2013} have considered the problem of dealing with variable weights in positional scoring rules, and \citet{Walsh2007, Viappiani2018} consider the uncertainty in weights assuming a positional scoring rule has been considered under the assumption that the agents preferences are known.
-\commentOC{Check Walsh.}
+Although more interest has been shown in the incompleteness of agent preferences, several authors have considered scenarios where the voting rule is partially defined.
+Among others, \citet{Llamazares2013} have considered the problem of dealing with variable weights in positional scoring rules, and \citet{Stein1994,Viappiani2018} consider the uncertainty in weights of a positional scoring rule assuming that the agents preferences are known.
 
-Studies related to the manipulability of voting rules have been proposed in this context \citep{Endriss2016,Dey2018,Dey2018_2}, studying the reactions of agents when they learn incrementally about other agents preferences.
+Studies related to the manipulability of voting rules have been proposed in this context \citep{Elkind2012,Dey2018,Dey2018_2,Conitzer2011}, and strategic behaviors, when agents learn incrementally about other agents preferences, have been investigated \citep{Endriss2016,Lev2019,Annemieke2012}.
 
@@
 	\begin{enumerate}
-		\item Pessimistic VS Elitist
+		\item Pessimistic VS Elitist Geometric
+		\item Pessimistic VS Elitist VS Random
+		\item 2 more lines in table
 		\item Reach regret: $n/10$. For this, we need $m^x n$ questions. (Correct formula)
@@
 We also see that Extended pessimistic performs slightly less well than Pessimistic.
-Although they come close, Extended pessimistic performs significatively less well, in the sense that the numbers are consistently in favor of Pessimistic if running the experiment again.
+Although they come close, Extended pessimistic performs significantly less well, in the sense that the numbers are consistently in favor of Pessimistic if running the experiment again.
 
 We next focus on the Pessimistic strategy, because Extended pessimistic is too slow to be ran repeatedly on much bigger problem sizes.
+\begin{table}
+	\begin{center}
+			\begin{tabular}{S[table-figures-integer=3, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
+				\toprule
+				{k} & {Rnd.} & {sd} & {Pes.} & {sd} & {Eli.} & {sd} \\
+				\midrule
+				0 &20.0 & 0.0 & 20.0 & 0.0&  20.0 & 0.0 \\
+				50 & 19.82 & 0.04 &	15.59 &0.56	&17.38& 0.7\\
+				100 & 19.12	& 0.26&	11.91&	1.26 &15.23& 0.73\\
+				150 & 18.06	& 0.47&	8.92&	1.53 &13.38& 1.11\\
+				200 & 16.89	& 0.62&6.24&2.02&11.76& 1.03\\
+				250 & 15.63 & 0.84&	4.64&1.72&10.56& 0.89\\
+				300 & 14.72	& 0.94&	3.01& 1.35 &10.48& 0.87\\
+				350 & 13.41	& 1.15& 1.76& 0.95&10.48& 0.86\\
+				400 & 11.98	& 0.68&	0.62&0.56 &10.48& 0.86\\
+				\bottomrule
+			\end{tabular}
+	\end{center}
+	\caption{Average MMR in problems of size $(10, 20)$ after $k$ questions and $10$ runs.}
+	\label{tab:biggerSize}
+\end{table}
+
+\begin{table}
+	\begin{center}
+
+			\begin{tabular}{S[table-figures-integer=3, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
+				\toprule
+				{sd} & {Pes.} & {sd} & {Eli.} & {sd} \\
+				\midrule
+				0	&20.0	&0.0	&20.0	&0.0\\
+				50	&15.96	&0.54	&17.26	&0.42\\
+				100	&12.48	&0.93	&15.6	&0.43\\
+				150	&9.58	&1.37	&13.94	&0.76\\
+				200	&7.43	&1.25	&10.95	&1.12\\
+				250	&5.26	&1.52	&6.6	&0.79\\
+				300	&3.47	&1.32	&6.57	&0.79\\
+				350	&1.75	&1.36	&6.57	&0.79\\
+				400	&0.49	&0.68	&6.57	&0.79\\
+				\bottomrule
+			\end{tabular}
+	\end{center}
+	\caption{Average MMR in problems of size $(10, 20)$ and geometric weights after $k$ questions and $10$ runs.}
+	\label{tab:geometricWeights}
+\end{table}
 
@@
 			\toprule
-			{p} & {2 ph.\ ca} & {sd} & {2 ph.\ ag} & {sd} \\
+			{p} & {2 ph.\ ca} & {sd} & {2 ph.\ ac} & {sd} \\
 			\midrule
@@
 			300 &11.07 & 0.86& 11.87 & 1.25 \\
-			350 &&&15.59 & 0.6 \\
+			350 &15.06 & 0.68&15.59 & 0.6 \\
 			400 &20.0 & 0.0 & 20.0 & 20.0 \\

### 2020-10-09 minimax.tex
updated TODOs
typo in one table and more lines in twoPhases
related works section

@@
 \label{sec:related}
-In a social choice context, an increasing number of authors has been interested in obtaining information about winners with reduced assumptions about the knowledge of the agent preferences, assuming that the voting rule is known.
-\Citet{Conitzer2005} have studied the complexity of communication, using different voting rules, determining lower and upper bounds for it.
-They showed that, in the worst case, the agents should send their complete set of preference for most of the rules they investigated.
-\Citet{Konczak05} have proposed a way to compute possible and necessary winners when the knowledge of agent preferences is only partial, for various voting rules.
-They also showed that, even though this computation is hard in the general case, their method is polynomial in case of positional scoring rule.
-Later on, for the necessary winner problem, other authors have proposed polynomial-time algorithms when using maximin and Bucklin \citep{Xia2008}; showed that the general case remains computationally hard even when restricting to single-peaked preferences \citep{Walsh2007}; proved sufficient conditions that ensure tractability \citep{Pini2007}.
+In the context of social choice, several authors have been interested in obtaining information about winners with reduced assumptions about the knowledge of the agent preferences (assuming that the voting rule is known).
+One early work is  by \Citet{Conitzer2005} who studied the complexity of communication, using different voting rules, determining lower and upper bounds; they showed that, in the worst case, the agents should send their complete set of preference for most of the rules they investigated.
 
-From this starting point, several studies on elicitation of agent preferences have been proposed \citep{Naamani-Dery2015,Kalech2011,Lu2011,Pini2009,Benabbou2016,Cailloux2014,Dey2016,Dey2016_2}, and analysis on when to stop the elicitation process have been conducted \citep{Walsh2009,Conitzer2009}.
+\Citet{Konczak05} were the first to consider the problem of computing, for various voting rules, possible and necessary winners in the case of partial knowledge of agent preferences and showed that the problem is hard in the general case.
+This work was then extended by \citet{Xia2008} that showed that, while the identification of a necessary co-winner in scoring rules is polynomial,  the determination of possible co-winners is NP-hard (the authors found a mistake in a proof in the Konczak and Lang's paper that claimed it to be polynomial); they also  proposed polynomial-time algorithms when using maximin and Bucklin \citep{Xia2008}.
+In other papers it was showed that the general case remains computationally hard even when restricting to single-peaked preferences \citep{Walsh2007};  sufficient conditions that ensure tractability were then found \citep{Pini2007}.
 
-Although more interest has been shown in the incompleteness of agent preferences, several authors have considered scenarios where the voting rule is partially defined.
-Among others, \citet{Llamazares2013} have considered the problem of dealing with variable weights in positional scoring rules, and \citet{Stein1994,Viappiani2018} consider the uncertainty in weights of a positional scoring rule assuming that the agents preferences are known.
+%They also showed that, even though this computation is hard in the general case, their method is polynomial in case of positional scoring rule. 
+%Later on, for the necessary winner problem, other authors have proposed polynomial-time algorithms when using maximin and Bucklin \citep{Xia2008}; showed that the general case remains computationally hard even when restricting to single-peaked preferences \citep{Walsh2007}; proved sufficient conditions that ensure tractability \citep{Pini2007}.
 
-Studies related to the manipulability of voting rules have been proposed in this context \citep{Elkind2012,Dey2018,Dey2018_2,Conitzer2011}, and strategic behaviors, when agents learn incrementally about other agents preferences, have been investigated \citep{Endriss2016,Lev2019,Annemieke2012}.
+Thereafter, noticing that in many practical situations there would be too many possible winners but no necessary winners, the importance of proposing efficient elicitation strategies has been identified.
+Indeeed, several works addressed the problem of  elicitation of agent preferences \citep{Naamani-Dery2015,Kalech2011,Lu2011,Pini2009,Benabbou2016,Dey2016,Dey2016_2} using a variety of approaches (minimax regret, Bayesian methods, etc.), and analysis on when to stop the elicitation process \citep{Walsh2009,Conitzer2009}.
+
+While most of the focus in the research community has been in dealing with incomplete agent preferences, 
+%Although more interest has been shown in the incompleteness of agent preferences, 
+another line of research has dealt with scenarios where it is instead the voting rule that is partially defined, but the preferences are given. 
+A classic paper is the one by \citet{Stein1994} that, considering scoring rules, identified dominance relations between alternatives; these relations allow to determine pairs of alternatives where the first is at least as good as the second no matter which weights are chosen among a generic class of weights (decreasing weighs or convex decreasing weights).
+
+More recently \citet{Llamazares2013} and \cite{Viappiani2018} (among others) considered the problem of dealing with unspecified weights in positional scoring rules; the first  \citep{Llamazares2013} proposed a method based on Data Envelope Analysis, while the second \citep{Viappiani2018} proposed to aggregate the uncertainty in weights using criteria used in decision-making under uncertainty (such as minimax regret).
+We also mention the work of \citet{Cailloux2014} that deals with the problem of eliciting a generic voting rule.
+
+Finally we also mention works related to the manipulability of voting rules %have been proposed in this context 
+\citep{Elkind2012,Dey2018,Dey2018_2,Conitzer2011}, and work concerning strategic behaviors, when agents learn incrementally about other agents preferences \citep{Endriss2016,Lev2019,Annemieke2012}.
 
@@
 	\begin{enumerate}
-		\item Pessimistic VS Elitist Geometric
-		\item Pessimistic VS Elitist VS Random
-		\item 2 more lines in table
+		\item Comment on Table Pessimistic VS Elitist Geometric
+		\item Comment on Table Pessimistic VS Elitist VS Random
+		\item Waiting for the result of 2 more lines (p=15,30) in table two phases
 		\item Reach regret: $n/10$. For this, we need $m^x n$ questions. (Correct formula)
-		\item find a way of displaying the graph so that it is understandable in B/W.
 		\item Check Pess VS XPess on other sizes.
@@
 				\toprule
-				{sd} & {Pes.} & {sd} & {Eli.} & {sd} \\
+				{k} & {Pes.} & {sd} & {Eli.} & {sd} \\
 				\midrule
@@
 			0 & 0.66 & 0.67 & 0.65 & 0.65  \\
+			15 & 0.71 & 0.73 & 0.67	& 0.64 \\
+			30 & 0.62 & 0.5 & 0.8 & 0.62 \\
 			50 & 1.23 & 1.46 & 0.8 & 0.79 \\

### 2020-10-09 minimax.tex
related works section

@@
 Thereafter, noticing that in many practical situations there would be too many possible winners but no necessary winners, the importance of proposing efficient elicitation strategies has been identified.
-Indeeed, several works addressed the problem of  elicitation of agent preferences \citep{Naamani-Dery2015,Kalech2011,Lu2011,Pini2009,Benabbou2016,Dey2016,Dey2016_2} using a variety of approaches (minimax regret, Bayesian methods, etc.), and analysis on when to stop the elicitation process \citep{Walsh2009,Conitzer2009}.
+Indeeed, several works addressed the problem of  elicitation of agent preferences \citep{Naamani-Dery2015,Kalech2011,Lu2011,Pini2009,Benabbou2016,Dey2016,Dey2016_2} using a variety of approaches (minimax regret, Bayesian methods, etc.), and others \citep{Walsh2009,Conitzer2009}  analyzed when to stop the elicitation process.
 

### 2020-10-09 minimax.tex
Related works (minor)

--- 2020-10-09 minimax.tex
@@
 \Citet{Konczak05} were the first to consider the problem of computing, for various voting rules, possible and necessary winners in the case of partial knowledge of agent preferences and showed that the problem is hard in the general case.
-This work was then extended by \citet{Xia2008} that showed that, while the identification of a necessary co-winner in scoring rules is polynomial,  the determination of possible co-winners is NP-hard (the authors found a mistake in a proof in the Konczak and Lang's paper that claimed it to be polynomial); they also  proposed polynomial-time algorithms when using maximin and Bucklin \citep{Xia2008}.
+This work was then extended by \citet{Xia2008} that showed that, while the identification of a necessary co-winner in scoring rules is polynomial,  the determination of possible co-winners is NP-hard; they also  proposed polynomial-time algorithms when using maximin and Bucklin \citep{Xia2008}.
 In other papers it was showed that the general case remains computationally hard even when restricting to single-peaked preferences \citep{Walsh2007};  sufficient conditions that ensure tractability were then found \citep{Pini2007}.
@@
 Thereafter, noticing that in many practical situations there would be too many possible winners but no necessary winners, the importance of proposing efficient elicitation strategies has been identified.
-Indeeed, several works addressed the problem of  elicitation of agent preferences \citep{Naamani-Dery2015,Kalech2011,Lu2011,Pini2009,Benabbou2016,Dey2016,Dey2016_2} using a variety of approaches (minimax regret, Bayesian methods, etc.), and analysis on when to stop the elicitation process \citep{Walsh2009,Conitzer2009}.
+Several works addressed the problem of  elicitation of agent preferences \citep{Naamani-Dery2015,Kalech2011,Lu2011,Pini2009,Benabbou2016,Dey2016,Dey2016_2} using a variety of approaches (minimax regret, Bayesian methods, etc.), and others \citep{Walsh2009,Conitzer2009}  analyzed when to stop the elicitation process.
 
@@
 
-More recently \citet{Llamazares2013} and \cite{Viappiani2018} (among others) considered the problem of dealing with unspecified weights in positional scoring rules; the first  \citep{Llamazares2013} proposed a method based on Data Envelope Analysis, while the second \citep{Viappiani2018} proposed to aggregate the uncertainty in weights using criteria used in decision-making under uncertainty (such as minimax regret).
-We also mention the work of \citet{Cailloux2014} that deals with the problem of eliciting a generic voting rule.
+More recently \citet{Llamazares2013} and \citet{Viappiani2018} (among others \commentOC{Which others?}) considered the problem of dealing with unspecified weights in positional scoring rules; the first \citep{Llamazares2013} proposed a method based on Data Envelope Analysis, while the second \citep{Viappiani2018} proposed to aggregate the uncertainty in weights using criteria used in decision-making under uncertainty (such as minimax regret).
+The work of \citet{Cailloux2014} deals with the problem of eliciting a generic voting rule.
 

### 2020-10-09 minimax.tex
Impr Sec 4

@@
 
-Let $V$ be the set of possible preference profiles (the union, for any integer, $n$ of the $n$-fold cartesian product of the linear orders over the alternatives).
+Let $V$ be the set of possible preference profiles (the union, for any integer $n$, of the $n$-fold cartesian product of the linear orders over the alternatives).
 A social choice function $f : V \rightarrow \powersetz{A}$ associates a profile with a set of winners, where $\powersetz{A}$ represents the set of subsets of $A$ except for the emptyset (sets are used for tied winners).
@@
 where $\alpha^{x}_r$ is the number of times that alternative $x$ was ranked in the $r$-th position.
-The winners are the alternatives with the highest scores.
+The winners are the alternatives with the highest score.
 
-In this work we assume a fixed, but unknown to us, profile $\profile^*$, representing the preferences $\pref_j^*$ of the agents, and a weight vector $\w^*$, representing the preferences of the chair, and we want to reason about partial preference information concerning those objects.
+In this work we assume fixed, but unknown to us, a profile $\profile^*$ representing the preferences $\pref_j^*$ of the agents, and a weight vector $\w^*$, representing the preferences of the chair, and we want to reason about partial preference information concerning those objects.
 At a given time, our knowledge of agent $j$'s preference is encoded by a partial order over the alternatives, thus a transitive and asymmetric binary relation, denoted by $\ppref_j$. 
@@
 Of course it may be difficult for real decision makers to state preferences about the voting rule in such an abstract way.
-These additional preferences can be elicited by asking questions about concrete profiles, for instance, by showing a complete profile of a small synthetic election and asking who should be elected in this case, as shown in Section \ref{sec:elicit}.
+We will show in \cref{sec:elicit} that the additional preferences we use can be elicited by 
+%asking questions about concrete profiles, for instance, by 
+showing a complete profile of a small synthetic election and asking who should be elected in this case.
 
-\section[Minimax regret under partial profile and weight information]{
-	Robust winner determination}
+\section{Robust winner determination}
 \label{sec:mmr}
 In this paper, we consider a setting where both the agent preferences and the preferences of the chair about the voting rule are incomplete.
-Some authors have considered possible and necessary winners assuming a partial profile  \citep{Kalech2011,Xia2008} or assuming an incompletely specified scoring rule \citep{Stein1994};
-however, we note that, in typical settings, there are no necessary winner and too many possible winners.
+As reviewed in \cref{sec:related}, some authors have considered possible and necessary winners assuming a partial profile or assuming an incompletely specified scoring rule, but in typical settings, there are no necessary winner and too many possible winners.
 In practice it is often useful to declare a winner given partial information.
@@
 Minimax regret \citep{Savage1954} is a decision criterion that has been used for robust optimization under data uncertainty \citep{Kouvelis1997} as well as in decision-making with uncertain utility values \citep{Salo2001,Boutilier2006}.
-\citet{Lu2011} have adopted minimax regret for winner determination in social choice with
-the preferences of the agents that are only partially known, while the social choice function is predetermined and known.
+\citet{Lu2011} have adopted minimax regret for winner determination in social choice where
+the preferences of agents that are only partially known, while the social choice function is predetermined and known.
 
@@
 \end{align}
-The pairwise max regret $\PMR(x,y;\pprofile,W)$ of $x$ relative to $y$ given partial profile $\pprofile$ and the set of weights $W$
+The pairwise maximum regret $\PMR(x,y;\pprofile,W)$ of $x$ relative to $y$ given the partial profile $\pprofile$ and the set of weights $W$
 is the worst-case loss of choosing $x$ instead of $y$ under all possible realizations of the full profile {\em and} all possible instantiations of the weights:
@@
 
-Max regret $\MaxR(x;\pprofile,W)$ is the worst-case loss of $x$.
-That is the loss occurred as the result of an adversarial selection of the complete profile $\profile \in C(\pprofile)$ and of the scoring vector $\w \in W$ that together maximize the loss between $x$ and the true winner under $\profile$ and $\w$.
+The maximum regret $\MaxR(x;\pprofile,W)$ is the worst-case loss of $x$.
+That is the loss occurred as the result of an adversarial selection of the complete profile $\profile \in C(\pprofile)$ and of the scoring vector $\w \in W$ that together maximize the loss between $x$ and the true winner under $\profile$ and $\w$:
 \begin{align}
@@
 
-Finally,  $\MMR(\pprofile,W)$ is the value of minimax regret under $\pprofile$ and $W$, obtained when recommending a minimax optimal alternative $x^*_{\pprofile, W}$:
+Finally,  $\MMR(\pprofile,W)$ is the value of minimax regret under $\pprofile$ and $W$, obtained when recommending a minimax optimal alternative $x^*_{\pprofile, W} \in A^*_{\pprofile, W}$:
 
 \begin{align}
-	\MMR(\pprofile,W) & = \min_{x \in A} \MaxR(x;\pprofile,W) \\
-	x^{*}_{\pprofile,W} \in A^*_{\pprofile, W} & = \argmin_{x \in A} \MaxR(x;\pprofile,W)
+	\MMR(\pprofile,W) & = \min_{x \in A} \MaxR(x;\pprofile,W); \\
+	A^*_{\pprofile, W} & = \argmin_{x \in A} \MaxR(x;\pprofile,W).
 \end{align}
@@
 
-Observe that if $\MMR(\pprofile, W)\!=\!0$, then $x^{*}_{\pprofile,W}$ is a necessary co-winner; this means that for any valid completion of the profile and any feasible $w \!\in\!
-W$, $x^{*}_{\pprofile,W}$ obtains a highest score.
+Observe that if $\MMR(\pprofile, W)\!=\!0$, then any $x^{*}_{\pprofile,W} \in A^*_{\pprofile, W}$ is a necessary co-winner; this means that for any valid completion of the profile and any feasible $w \in W$, $x^{*}_{\pprofile,W}$ obtains the highest score.
 
@@
 
-Recall that, in the computation of $s(x; \profile, \w)$, $w_{v_j(x)}$ represents the score that $x$ obtains in the ranking $v_j$ (see Equation \ref{eq:srule}).
+Recall that, in the computation of $s(x; \profile, \w)$, $w_{v_j(x)}$ represents the score that $x$ obtains in the ranking $v_j$ (see \cref{eq:srule}).
 Since scoring rules are additively decomposable, we can consider separately the contribution of each agent to the total score. Thus, we can write the actual regret of choosing $x$ instead of $y$ as
@@
 
-Let ${\pprefeq_j}(x)$ designate the set of alternatives that are known to be considered by $j$ as less good than or equal to $x$, and ${\pprefinv_j}(y)$ be the set of alternatives known to be considered by $j$ as strictly better than $y$.
+Let ${\pprefeq_j}(x)$ designate the set of alternatives known to be considered by $j$ as less good than or equal to $x$, and ${\pprefinv_j}(y)$ be the set of alternatives known to be considered by $j$ as strictly better than $y$.
 \begin{claim}
@@
 Recall that the preferences of the chair are encoded with linear constraints $\Co_{W}$.
-The pairwise max regret $\PMR(x,y; \pprofile,W)$ can be obtained as the solution of the following linear program defined on the variables $w_1, …, w_m$, which represent the weights attached to different positions.
+The pairwise max regret $\PMR(x,y; \pprofile,W)$ can be obtained as the solution of the following linear program defined on the variables $w_1, …, w_m$, which represent the weights attached to different positions:
 
@@
 	\max_{\w} & \sum_{r=1}^m (\hat{\alpha}_{r}^{y} - \hat{\alpha}_{r}^{x}) w_{r}\\
-	\text{ s.t. } & \text{\cref{eq:monotone}} \text{ and } \text{\cref{eq:convexity}} \text{ and } \Co_W
+	\text{ s.t. } & \text{\cref{eq:monotone}} \text{ and } \text{\cref{eq:convexity}} \text{ and } \Co_W.
 \end{align}

### 2020-10-09 minimax.tex
changes

@@
 This observation has motivated a number of recent works considering social choice with partial preference orders \citep{Xia2008, Pini2009, Konczak05} and incremental elicitation \citep{Kalech2011, Lu2011, Naamani-Dery2015,Benabbou2016} of agent preferences.
-\\ Furthermore, it is often difficult for non-expert users to formalize a voting rule on the basis of some generic preferences over a desired aggregation method.
+\\
+Furthermore, it is often difficult for non-expert users to formalize a voting rule on the basis of some generic preferences over a desired aggregation method.
 Thus, the first hypothesis should also be relaxed.
@@
 alternative using positional scoring rules and we provide incremental elicitation methods to acquire relevant preference information.
-We then discuss several heuristics that determine queries, either to an agent or to the chair, that quickly reduce minimax regret.
+We then discuss several heuristics that determine queries, to an agent or to the chair (the person or organization supervising the voting process), that quickly reduce minimax regret.
 While previous works have considered either partial information about the agent preferences or a partially specified aggregation method, we do not know of any work considering both sources of uncertainty at the same time.
@@
 First, a good quality recommendation can be reached by asking what can be considered a reasonable number of questions to the chair and agents.
-For example, in a problem of size $m = 5$, $n = 10$, $55$ questions in total are required to reach a good quality recommendation, whcih can be considered reasonable as these questions are to be dispatched over $10$ agents and the chair.
+For example, in a problem of size $m = 5$, $n = 10$, $55$ questions in total are required to reach a good quality recommendation, which can be considered reasonable as these questions are to be dispatched over $10$ agents and the chair.
 Second, the quality of the recommendation increases faster than linearly with the number of questions, after only a few questions (the first few questions yield no increase in quality).
-Third, we experimentally find out that asking questions to the agents only performs similarly than asking questions both to the agents and the chair, although questions to the chair do have a positive value in terms of quality of the recommendation.
+Third, we experimentally find out that asking questions only to the agents performs similarly than asking questions both to the agents and the chair, although questions to the chair do have a positive value in terms of quality of the recommendation.
 %the value of information of one question to the chair is similar to the value of information of one question to a agent (in the ranges we considered), up to a certain proportion of questions asked to the chair.
@@
 The paper is organized as follows. \Cref{sec:related} reviews the works related to our objective.
-In Section \ref{sec:background} we provide the necessary background and in Section \ref{sec:mmr} we introduce the minimax criterion, that selects a winner that minimizes the worst possible regret.
+In Section \ref{sec:background} we provide the necessary background and in Section \ref{sec:mmr} we introduce the minimax criterion, a method that selects a winner that minimizes the worst possible regret.
 Then, in Section \ref{sec:elicit} we provide an interactive elicitation protocol based on minimal regret;  in Section \ref{sec:experiments} we present the empirical validation of our approach with simulations; and Section \ref{sec:conclusions} provides some final thoughts.
@@
 \Citet{Konczak05} were the first to consider the problem of computing, for various voting rules, possible and necessary winners in the case of partial knowledge of agent preferences and showed that the problem is hard in the general case.
-This work was then extended by \citet{Xia2008} that showed that, while the identification of a necessary co-winner in scoring rules is polynomial,  the determination of possible co-winners is NP-hard; they also  proposed polynomial-time algorithms when using maximin and Bucklin \citep{Xia2008}.
+This work was then extended by \citet{Xia2008} that showed that, while the identification of a necessary co-winner in scoring rules is polynomial,  the determination of possible co-winners is NP-hard; they also  proposed polynomial-time algorithms when using maximin and Bucklin.
 In other papers it was showed that the general case remains computationally hard even when restricting to single-peaked preferences \citep{Walsh2007};  sufficient conditions that ensure tractability were then found \citep{Pini2007}.
@@
 
-More recently \citet{Llamazares2013} and \citet{Viappiani2018} (among others \commentOC{Which others?}) considered the problem of dealing with unspecified weights in positional scoring rules; the first \citep{Llamazares2013} proposed a method based on Data Envelope Analysis, while the second \citep{Viappiani2018} proposed to aggregate the uncertainty in weights using criteria used in decision-making under uncertainty (such as minimax regret).
+More recently \citet{Llamazares2013} and \citet{Viappiani2018} %(among others \commentOC{Which others?}) 
+considered the problem of dealing with unspecified weights in positional scoring rules; the first proposed a method based on Data Envelope Analysis, while the second proposed to aggregate the uncertainty in weights using criteria used in decision-making under uncertainty (such as minimax regret).
 The work of \citet{Cailloux2014} deals with the problem of eliciting a generic voting rule.
@@
 Finally we also mention works related to the manipulability of voting rules %have been proposed in this context 
-\citep{Elkind2012,Dey2018,Dey2018_2,Conitzer2011}, and work concerning strategic behaviors, when agents learn incrementally about other agents preferences \citep{Endriss2016,Lev2019,Annemieke2012}.
+\citep{Elkind2012,Dey2018,Dey2018_2,Conitzer2011}, and work concerning strategic behaviors, when agents learn incrementally about other agent preferences \citep{Endriss2016,Lev2019,Annemieke2012}.
 
@@
 
-In this work we assume fixed, but unknown to us, a profile $\profile^*$ representing the preferences $\pref_j^*$ of the agents, and a weight vector $\w^*$, representing the preferences of the chair, and we want to reason about partial preference information concerning those objects.
+In this work we assume fixed, but unknown to us, a profile $\profile^*$ representing the preferences $\pref_j^*$ of the agents, and a weight vector $\w^*$, representing the preferences of the chair.
+We want to reason about partial preference information concerning those objects.
 At a given time, our knowledge of agent $j$'s preference is encoded by a partial order over the alternatives, thus a transitive and asymmetric binary relation, denoted by $\ppref_j$. 
@@
 
-An important class of scoring rule is the one composed of weights that represent a convex sequence \citep{Stein1994,Llamazares2016}, meaning that the difference between the weight of the first position and the weight of the second position is at least as great as the difference between the weights of the second and third positions, etc.
+An important class of scoring rule is the one composed of weights that represent a convex sequence \citep{Stein1994,Llamazares2016}, meaning that the difference between the weight of the first position and the weight of the second position is at least as large as the difference between the weights of the second and third positions, etc.
 \begin{equation} 
@@
 In general it can be difficult to set the weights in an appropriate way.
-We assume that in addition of basic requirements (monotonicity and convexity), the chair (the person or the organization that is supervising the voting process) is able to specify additional preferences about how the social choice function should behave.
+We assume that, in addition of basic requirements (monotonicity and convexity), the chair is able to specify additional preferences about how the social choice function should behave.
 In this work we assume that the preferences of the chair are encoded with linear constraints about the vector $\w$, relating the value of the weights of different positions, and the set of these constraints is denoted by $\Co_W$.
 Moreover, we use $\pw \subseteq \W$ to denote the set of weight vectors compatible with the preferences expressed by the chair about the scoring vector.
-
 Of course it may be difficult for real decision makers to state preferences about the voting rule in such an abstract way.
@@
 \begin{align} 
-	\Regret(x, \profile, \w) = \max_{y \in A} s(y; \profile,\w) - s(x; \profile, \w).
+	\Regret(x; \profile, \w) = \max_{y \in A} s(y; \profile,\w) - s(x; \profile, \w).
 \end{align}
@@
 	\MaxR(x; \pprofile, W) & = \max_{y \in A} \PMR(x,y; \pprofile, W)\\
-	& = \max_{\w \in W} \max_{\profile \in C(\profile)} \Regret(x, \profile, \w).
+	& = \max_{\w \in W} \max_{\profile \in C(\profile)} \Regret(x; \profile, \w).
 \end{align}
@@
 a fixed weight vector.
-As we will show, this procedure can also be used when the weight vector is not completely known.
+As we will show, this procedure can also be used when the weight vector is not completely known. Let us write $a \pprefeq_j b$ iff $a \ppref_j b \lor a = b$.
 
@@
 The goal is to acquire relevant information to reduce minimax regret as quickly as possible.
-As termination condition of elicitation, we can check whether minimax regret is lower than a threshold; if we wish optimality, we can perform elicitation until minimax regret drops to zero.
+As termination condition of elicitation, we can check whether minimax regret is lower than a threshold; or after having asked a given number of questions.
+
+%if we wish optimality, we can perform elicitation until minimax regret drops to zero.
 
 The remainder of this section is structured as follows.
-First of all, we discuss the different types of questions that can be asked to the agents and to the chair, and the way responses are handled.
+First, we discuss the different types of questions that can be asked to the agents and to the chair, and the way responses are handled.
 Then, we describe different strategies to determine informative queries to ask next, with the goal of reducing $\MMR(\pprofile,W)$ quickly.
@@
 We use this operator that is similar to a $\max$ operator because \citet{Cailloux2014} reported that pessimistic aggregation works much better than optimistic aggregation, although our experiments in this context suggested a weak impact of that choice on the performance of the strategy.
-However, to avoid the absorption property of max, we adopt a criterion closer to $\leximax$ as an aggregator: if the maximal MMR of two questions are (nearly) equal, then it considers the other MMR values, that are the one associated to the opposite answer, preferring the question with the lowest value.
-(Technically, instead of applying a pure lexicographic aggregation, which is very sensitive to small errors due to floating-point computations, we apply a weighted sum between the maximal and the (penalized) minimal MMR values, with a predominant weight to the maximal one.)
+However, to avoid the absorption property of max, we adopt a criterion closer to $\leximax$ as an aggregator: if the maximal $\MMR$ of two questions are (nearly) equal, then it considers the other $\MMR$ values, that are the one associated to the opposite answer, preferring the question with the lowest value.
+(Technically, instead of applying a pure lexicographic aggregation, which is very sensitive to small errors due to floating-point computations, we apply a weighted sum between the maximal and the (penalized) minimal $\MMR$ values, with a predominant weight to the maximal one.)
 
@@
 Given an agent to query $j$, it asks about an alternative currently undominated in $\ppref_j$ and any alternative that it has not yet asked about for that agent, or equivalently, any alternative that is currently incomparable to this alternative.
-This approach guarantees that the top alternative in the ranking of $j$ will be known after having asked $j$ exactly $m-1$ questions.
+This approach guarantees that the top alternative in the ranking of $j$ will be known after having asked exactly $m-1$ questions to $j$.
 After having asked $n (m-1)$ questions to the agents, it questions the chair only, using the same approach as the Pessimistic strategy.
@@
 		\item Comment on Table Pessimistic VS Elitist VS Random
-		\item Waiting for the result of 2 more lines (p=15,30) in table two phases
-		\item Reach regret: $n/10$. For this, we need $m^x n$ questions. (Correct formula)
-		\item Check Pess VS XPess on other sizes.
+		\item Reach regret: $n/10$. For this, we need $m^x n$ questions. Wait for more runs (Correct formula)
 		\item Prop qC in value of information
@@
 	\end{center}
-	\caption{Average MMR in problems of size $(5, 10)$ after $k$ questions and $200$ runs.}
+	\caption{Average $\MMR$ in problems of size $(5, 10)$ after $k$ questions.}
 	\label{tab:smallSize}
@@
 
-Our first experimental result concerns small size situations. We picked $m = 5, n = 10$ to illustrate our results (variations around this size yield similar conclusions). 
+Our first experimental result concerns small size situations.
+We picked $m = 5, n = 10$ to illustrate our results (variations around this size yield similar conclusions), ran it $200$ times and averaged the results.
 \Cref{tab:smallSize} and \cref{fig:smallSize} compares some of our strategies in this case.
@@
 
-Asking Random questions does not permit to reach a low regret level even after having asked 100 questions, whereas a low regret level (MMR = 1) is reached by Pessimistic before having asked 60 questions.
+Asking Random questions does not permit to reach a low regret level even after having asked 100 questions, whereas a low regret level ($\MMR$ = 1) is reached by Pessimistic before having asked 60 questions.
 
 We also see that Extended pessimistic performs slightly less well than Pessimistic.
-Although they come close, Extended pessimistic performs significantly less well, in the sense that the numbers are consistently in favor of Pessimistic if running the experiment again.
+Although they come close, Pessimistic performs significantly better, in the sense that the numbers are consistently in favor of Pessimistic if running the experiment again.
 
@@
 	\end{center}
-	\caption{Average MMR in problems of size $(10, 20)$ after $k$ questions and $10$ runs.}
+	\caption{Average $\MMR$ in problems of size $(10, 20)$ after $k$ questions.}
 	\label{tab:biggerSize}
@@
 				0	&20.0	&0.0	&20.0	&0.0\\
-				50	&15.96	&0.54	&17.26	&0.42\\
 				100	&12.48	&0.93	&15.6	&0.43\\
-				150	&9.58	&1.37	&13.94	&0.76\\
 				200	&7.43	&1.25	&10.95	&1.12\\
-				250	&5.26	&1.52	&6.6	&0.79\\
 				300	&3.47	&1.32	&6.57	&0.79\\
-				350	&1.75	&1.36	&6.57	&0.79\\
-				400	&0.49	&0.68	&6.57	&0.79\\
 				\bottomrule
@@
 	\end{center}
-	\caption{Average MMR in problems of size $(10, 20)$ and geometric weights after $k$ questions and $10$ runs.}
+	\caption{Average $\MMR$ in problems of size $(10, 20)$ and geometric weights after $k$ questions.}
 	\label{tab:geometricWeights}
@@
 			10 & 30 & 3.0 & 527 &  512 \\
-			15 & 30 & 3.0 & 919 &  991 \\
+			15 & 30 & 3.0 & 812 &  991 \\
 			\bottomrule
@@
 By relating the sizes to the column $k_{\MMR}$, we obtain the function $0.4m^{1.6}n$ as an approximation formula for the number of questions required to reach a low regret level.
-We see that the number of questions required grows approximately linearly with the number of agents and grows less fast than the square of the number of alternatives, for the sizes we considered.
+We see that this number grows approximately linearly with the number of agents and grows less fast than the square of the number of alternatives, for the sizes we considered.
 In other words, on average, assuming no questions get asked to the chair, each agent will have to answer $0.4m^{1.6}$ questions in order to to reach a low regret level, if this experimental formula reveals correct.
@@
 	\end{center}
-	\caption{Average $\MMR$ in problems of size $(10, 20)$ after $400$ questions and $10$ runs. Where $p$ represents the number of questions asked to the chair.}
+	\caption{Average $\MMR$ in problems of size $(10, 20)$ after $400$ questions. Where $p$ represents the number of questions asked to the chair.}
 	\label{tab:twoP400}
@@
 Such restrictions may be useful because of (partial) unavailability of the chair, or because the estimated cognitive costs may differ sensibly, as these types of questions differ in nature.
-\Cref{tab:twoP400} show the MMR value that is reached in a problem of size $m = 10, n = 20$ after $400$ questions, using the Two phases strategy, in the “ca” (chair then agents) and in the “ac” (agents then chair) variants.
-These numbers are to be compared with the MMR value reached after 400 questions with the unconstrained Pessimistic strategy (displayed in \cref{fig:linearity}), which is $0.62$.% ± $0.56$.
+\Cref{tab:twoP400} shows the $\MMR$ value that is reached in a problem of size $m = 10, n = 20$ after $400$ questions, using the Two phases strategy, in the “ca” (chair then agents) and in the “ac” (agents then chair) variants.
+These numbers are to be compared with the $\MMR$ value reached after 400 questions with the unconstrained Pessimistic strategy (displayed in \cref{fig:linearity}), which is $0.62$.% ± $0.56$.
 

### 2020-10-09 minimax.tex
Further minor wording issues

--- 2020-10-09 minimax.tex
@@
 At each step, the system may ask a question either to one of the agents about her preferences or to the chair about the voting rule. 
-The goal is to acquire relevant information to reduce minimax regret as quickly as possible.
+The goal is to obtain relevant information to reduce minimax regret as quickly as possible.
 As termination condition of elicitation, we can check whether minimax regret is lower than a threshold; if we wish optimality, we can perform elicitation until minimax regret drops to zero.
@@
 Such questions aim at refining our knowledge about the scoring rule; a response gives us a constraint on the weight vector $\w$.
-In particular, we want to acquire constraints of the type:
+In particular, we want to obtain constraints of the type
 \begin{align}
@@
 We use this operator that is similar to a $\max$ operator because \citet{Cailloux2014} reported that pessimistic aggregation works much better than optimistic aggregation, although our experiments in this context suggested a weak impact of that choice on the performance of the strategy.
-However, to avoid the absorption property of max, we adopt a criterion closer to $\leximax$ as an aggregator: if the maximal MMR of two questions are (nearly) equal, then it considers the other MMR values, that are the one associated to the opposite answer, preferring the question with the lowest value.
-(Technically, instead of applying a pure lexicographic aggregation, which is very sensitive to small errors due to floating-point computations, we apply a weighted sum between the maximal and the (penalized) minimal MMR values, with a predominant weight to the maximal one.)
+However, to avoid the absorption property of max, we adopt a criterion closer to $\leximax$ as an aggregator: if the maximal MMR of two questions are (nearly) equal, then it considers the penalized minimal MMR values, preferring the question with the lowest value.
+(Technically, instead of applying a pure lexicographic aggregation, which is very sensitive to small errors due to floating-point computations, we apply a weighted sum between the maximal and the penalized minimal MMR values, with a predominant weight to the maximal one.)
 
@@
 After having selected the candidate questions, we apply the same operator as for the Pessimistic strategy: we evaluate, for each of the possible questions, the minimax regret for the two possible answers and we choose the best according to (quasi-)$\leximax$.
-We use this strategy to test whether Pessimistic performs well: depending on the quality of the heuristic of the Pessimistic strategy, it might perform nearly equally well, or perhaps even better, than Extended pessimistic, while being (much) more efficient.
-We expect that Extended pessimistic will be applicable only to very small problem instances: its complexity is in $O(n^2 m^5)$, because we consider $O(m^2)$ questions for each agent and need for each question to compute $\MMR$ twice, whose complexity is $O(nm^3)$.
+We use this strategy to test whether Pessimistic performs well: depending on the quality of the heuristic of the Pessimistic strategy, it might perform nearly equally well, or perhaps even better, than Extended pessimistic, while being (much) faster.
+Extended pessimistic is applicable only to small problem instances: its complexity is in $O(n^2 m^5)$, because we consider $O(m^2)$ questions for each agent and need for each question to compute $\MMR$ twice, whose complexity is $O(nm^3)$.
 
 The \strat{Two phases} strategy is developed in order to investigate the effect of varying the proportion of questions asked to agents and to the chair, and compare the performance of asking questions to the chair first or to the agents first.
-It is parameterized by $p$, a value indicating the number of questions that must be asked to the chair.
-The \strat{Two phases - ca} variant first asks $p$ questions to the chair, then $k-p$ questions to the agents, using in both cases Pessimistic to select the specific questions; whereas the \strat{Two phases - ac} variant starts with $k - p$ questions to the agents, then questions the chair.
+It is parameterized by $q_c$, a value indicating the number of questions that must be asked to the chair.
+The \strat{Two phases - ca} variant first asks $q_c$ questions to the chair, then $k - q_c$ questions to the agents, using in both cases Pessimistic to select the specific questions; whereas the \strat{Two phases - ac} variant starts with $k - q_c$ questions to the agents, then questions the chair.
 %Note that when asking first only questions to the chair, if the obtained knowledge approximates well the scoring vector, then in the second part of the elicitation we fall into the more classical setting of incompleteness of preferences assuming a known voting rule.
@@
 
-Finally, the \strat{Elitist} strategy aims at uncovering as quickly as possible the top alternative of each agent. It asks $m-1$ questions to each agent in turn. 
+Finally, the \strat{Elitist} strategy aims at uncovering as quickly as possible the top alternative of each agent. It asks $m - 1$ questions to each agent in turn. 
 Given an agent to query $j$, it asks about an alternative currently undominated in $\ppref_j$ and any alternative that it has not yet asked about for that agent, or equivalently, any alternative that is currently incomparable to this alternative.
@@
 
-We start with empty knowledge ($\pprofile = (\emptyset_j), W = \W$) about the preference orderings of the agents or the weight differences favored by the chair.
+We start with empty knowledge ($\pprofile = (\emptyset, \emptyset, …), W = \W$) about the preference orderings of the agents or the weight differences favored by the chair.
 We obtain the first question to be asked using the strategy under test, as described above.

### 2020-10-09 minimax.tex

--- 2020-10-09 minimax.tex
@@
 At each step, the system may ask a question either to one of the agents about her preferences or to the chair about the voting rule. 
-The goal is to acquire relevant information to reduce minimax regret as quickly as possible.
+The goal is to obtain relevant information to reduce minimax regret as quickly as possible.
 As termination condition of elicitation, we can check whether minimax regret is lower than a threshold; or after having asked a given number of questions.
-
 %if we wish optimality, we can perform elicitation until minimax regret drops to zero.
@@
 We use this operator that is similar to a $\max$ operator because \citet{Cailloux2014} reported that pessimistic aggregation works much better than optimistic aggregation, although our experiments in this context suggested a weak impact of that choice on the performance of the strategy.
-However, to avoid the absorption property of max, we adopt a criterion closer to $\leximax$ as an aggregator: if the maximal $\MMR$ of two questions are (nearly) equal, then it considers the other $\MMR$ values, that are the one associated to the opposite answer, preferring the question with the lowest value.
-(Technically, instead of applying a pure lexicographic aggregation, which is very sensitive to small errors due to floating-point computations, we apply a weighted sum between the maximal and the (penalized) minimal $\MMR$ values, with a predominant weight to the maximal one.)
+However, to avoid the absorption property of max, we adopt a criterion closer to $\leximax$ as an aggregator: if the maximal MMR of two questions are (nearly) equal, then it considers the penalized minimal MMR values, preferring the question with the lowest value.
+(Technically, instead of applying a pure lexicographic aggregation, which is very sensitive to small errors due to floating-point computations, we apply a weighted sum between the maximal and the penalized minimal MMR values, with a predominant weight to the maximal one.)
 
@@
 After having selected the candidate questions, we apply the same operator as for the Pessimistic strategy: we evaluate, for each of the possible questions, the minimax regret for the two possible answers and we choose the best according to (quasi-)$\leximax$.
-We use this strategy to test whether Pessimistic performs well: depending on the quality of the heuristic of the Pessimistic strategy, it might perform nearly equally well, or perhaps even better, than Extended pessimistic, while being (much) more efficient.
-We expect that Extended pessimistic will be applicable only to very small problem instances: its complexity is in $O(n^2 m^5)$, because we consider $O(m^2)$ questions for each agent and need for each question to compute $\MMR$ twice, whose complexity is $O(nm^3)$.
+We use this strategy to test whether Pessimistic performs well: depending on the quality of the heuristic of the Pessimistic strategy, it might perform nearly equally well, or perhaps even better, than Extended pessimistic, while being (much) faster.
+Extended pessimistic is applicable only to small problem instances: its complexity is in $O(n^2 m^5)$, because we consider $O(m^2)$ questions for each agent and need for each question to compute MMR twice, whose complexity is $O(nm^3)$.
 
 The \strat{Two phases} strategy is developed in order to investigate the effect of varying the proportion of questions asked to agents and to the chair, and compare the performance of asking questions to the chair first or to the agents first.
-It is parameterized by $p$, a value indicating the number of questions that must be asked to the chair.
-The \strat{Two phases - ca} variant first asks $p$ questions to the chair, then $k-p$ questions to the agents, using in both cases Pessimistic to select the specific questions; whereas the \strat{Two phases - ac} variant starts with $k - p$ questions to the agents, then questions the chair.
+It is parameterized by $q_c$, a value indicating the number of questions that must be asked to the chair.
+The \strat{Two phases - ca} variant first asks $q_c$ questions to the chair, then $k - q_c$ questions to the agents, using in both cases Pessimistic to select the specific questions; whereas the \strat{Two phases - ac} variant starts with $k - q_c$ questions to the agents, then questions the chair.
 %Note that when asking first only questions to the chair, if the obtained knowledge approximates well the scoring vector, then in the second part of the elicitation we fall into the more classical setting of incompleteness of preferences assuming a known voting rule.

### 2020-10-09 minimax.tex
MMR text

@@
 We use the oracle to answer the question and update our knowledge, which is thus used to obtain the next question.
-This is repeated until $k$ answers have been obtained, compute the resulting $\MMR$ values along the way for various values of $k$.
-We repeat this whole experiment a variable number of times indicated below, for a given $(m, n, k)$, and report the average resulting $\MMR$ and the standard deviation \textit{sd}.
+This is repeated until $k$ answers have been obtained, compute the resulting MMR values along the way for various values of $k$.
+We repeat this whole experiment a variable number of times indicated below, for a given $(m, n, k)$, and report the average resulting MMR and the standard deviation \textit{sd}.
 
@@
 	\end{center}
-	\caption{Average $\MMR$ in problems of size $(5, 10)$ after $k$ questions.}
+	\caption{Average MMR in problems of size $(5, 10)$ after $k$ questions.}
 	\label{tab:smallSize}
@@
 	\end{center}
-	\caption{Average $\MMR$ in problems of size $(10, 20)$ after $k$ questions.}
+	\caption{Average MMR in problems of size $(10, 20)$ after $k$ questions.}
 	\label{tab:biggerSize}
@@
 	\end{center}
-	\caption{Average $\MMR$ in problems of size $(10, 20)$ and geometric weights after $k$ questions.}
+	\caption{Average MMR in problems of size $(10, 20)$ and geometric weights after $k$ questions.}
 	\label{tab:geometricWeights}
@@
 	\includegraphics[width=.45\textwidth]{linearity.png}
-	\caption{Average $\MMR$ after $k$ questions with Pessimistic strategy after 10 runs for different problem sizes.}
+	\caption{Average MMR after $k$ questions with Pessimistic strategy after 10 runs for different problem sizes.}
 	\label{fig:linearity}
@@
 Knowing the speed of decrease permits to know which trade-offs can be achieved between the quality of the resulting recommendation and the number of questions that participants have to answer.
-\Cref{fig:linearity} shows graphically the decrease in $\MMR$ according to the number of questions asked for various problem sizes.
+\Cref{fig:linearity} shows graphically the decrease in MMR according to the number of questions asked for various problem sizes.
 We see that this function is convex, apart from the very first few questions, indicating to users of our approach that asking, for example, half the number of questions required to reach a low regret value will still yield a significant gain in regret, namely, more than half the distance to the low regret value.
@@
 	\end{center}
-	\caption{Average $\MMR$ in problems of size $(10, 20)$ after $400$ questions. Where $p$ represents the number of questions asked to the chair.}
+	\caption{Average MMR in problems of size $(10, 20)$ after $400$ questions. Where $p$ represents the number of questions asked to the chair.}
 	\label{tab:twoP400}
@@
 Such restrictions may be useful because of (partial) unavailability of the chair, or because the estimated cognitive costs may differ sensibly, as these types of questions differ in nature.
-\Cref{tab:twoP400} shows the $\MMR$ value that is reached in a problem of size $m = 10, n = 20$ after $400$ questions, using the Two phases strategy, in the “ca” (chair then agents) and in the “ac” (agents then chair) variants.
-These numbers are to be compared with the $\MMR$ value reached after 400 questions with the unconstrained Pessimistic strategy (displayed in \cref{fig:linearity}), which is $0.62$.% ± $0.56$.
+\Cref{tab:twoP400} shows the MMR value that is reached in a problem of size $m = 10, n = 20$ after $400$ questions, using the Two phases strategy, in the “ca” (chair then agents) and in the “ac” (agents then chair) variants.
+These numbers are to be compared with the MMR value reached after 400 questions with the unconstrained Pessimistic strategy (displayed in \cref{fig:linearity}), which is $0.62$.% ± $0.56$.
 

### 2020-10-09 minimax.tex
Wording

@@
 We observe that the Pessimistic strategy is able to reduce the regret almost completely after $30$ questions.
-We also see that Pessimistic performs slightly better than Extended pessimistic, showing that Pessimistic chooses candidate questions wisely; this is good news since (for $m = 5$ and $n = 10$), the latter strategy is much faster and takes only $15s$ for a complete elicitation session, while the former takes $80s$.
+We also see that Pessimistic performs slightly better than Extended pessimistic, showing that Pessimistic chooses candidate questions wisely; this is good news since (for $m = 5$ and $n = 10$), Pessimistic is much faster: it takes only $15$ seconds for a complete elicitation session, while Extended pessimistic takes $80$ seconds.
 
@@
 	\end{center}
-	\caption{Number of questions needed by Pessimistic strategy to reach $\MMR=\frac{n}{10}$ (represented by $k_{\MMR}$), for various problem sizes.}
+	\caption{Number of questions needed by Pessimistic strategy to reach an MMR of $\frac{n}{10}$ (represented by $k_{\MMR}$), by size.}
 	\label{tab:lowRegret}

### 2020-10-09 minimax.tex
qC, not p

@@
 			\toprule
-			{p} & {2 ph.\ ca} & {sd} & {2 ph.\ ac} & {sd} \\
+			{$q_c$} & {2 ph.\ ca} & {sd} & {2 ph.\ ac} & {sd} \\
 			\midrule
@@
 	\end{center}
-	\caption{Average MMR in problems of size $(10, 20)$ after $400$ questions. Where $p$ represents the number of questions asked to the chair.}
+	\caption{Average MMR in problems of size $(10, 20)$ after $400$ questions, among which $q_c$ to the chair.}
 	\label{tab:twoP400}

### 2020-10-09 minimax.tex
Commented Relative evaluation, removed first table

@@
 \subsection{Relative evaluation of Pessimistic strategy}
-\begin{table}
-	\begin{center}
-		\resizebox{\columnwidth}{!}{
-		\begin{tabular}{S[table-figures-integer=3, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
-			\toprule
-			{k} & {Rnd.} & {sd} & {Pes.} & {sd} & {Ex.\ pes.} & {sd} & {Eli.} & {sd} \\
-			\midrule
-			0 & 10.0 & 0.0 & 10.0 & 0.0 & 10.0 & 0.0 & 10.0 & 0.0\\
-			20 & 9.06 & 0.49 & 5.85 & 0.87 & 6.17 & 0.78 & 6.32 & 0.61\\
-			40 & 7.35 & 0.82 & 2.57 & 1.05 & 2.98 & 0.99 & 3.37 & 0.83\\
-			60 & 5.74 & 1.03 & 0.67 & 0.67 & 0.77 &0.78 & 2.33 & 1.05\\
-			80 & 4.10 & 1.15 & 0.03 & 0.12 & 0.05 & 0.18 & 2.28 & 1.05\\
-			100 & 2.63 & 1.19 & 0.0 &  0.0 & 0.0 & 0.0& 2.28 & 1.05\\
-			\bottomrule
-		\end{tabular}
-		}
-	\end{center}
-	\caption{Average MMR in problems of size $(5, 10)$ after $k$ questions.}
-	\label{tab:smallSize}
-\end{table}
-
 \begin{figure}
@@
 \end{figure}
-
-Our first experimental result concerns small size situations.
-We picked $m = 5, n = 10$ to illustrate our results (variations around this size yield similar conclusions), ran it $200$ times and averaged the results.
-\Cref{tab:smallSize} and \cref{fig:smallSize} compares some of our strategies in this case.
-We see that that Pessimistic performs better than Random and Extended pessimistic on a small size problem.
-(These figures also display the performance of the Elitist strategy, to which we will come back.)
-
-We observe that the Pessimistic strategy is able to reduce the regret almost completely after $30$ questions.
-We also see that Pessimistic performs slightly better than Extended pessimistic, showing that Pessimistic chooses candidate questions wisely; this is good news since (for $m = 5$ and $n = 10$), Pessimistic is much faster: it takes only $15$ seconds for a complete elicitation session, while Extended pessimistic takes $80$ seconds.
-
-Asking Random questions does not permit to reach a low regret level even after having asked 100 questions, whereas a low regret level ($\MMR$ = 1) is reached by Pessimistic before having asked 60 questions.
-
-We also see that Extended pessimistic performs slightly less well than Pessimistic.
-Although they come close, Pessimistic performs significantly better, in the sense that the numbers are consistently in favor of Pessimistic if running the experiment again.
-
-We next focus on the Pessimistic strategy, because Extended pessimistic is too slow to be ran repeatedly on much bigger problem sizes.
 \begin{table}
@@
 \end{table}
-
 \begin{table}
 	\begin{center}
-
 			\begin{tabular}{S[table-figures-integer=3, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
@@
 \end{table}
+
+Our first experimental result concerns small size situations.
+We picked $m = 5, n = 10$ to illustrate our results (variations around this size yield similar conclusions), ran it $200$ times and averaged the results.
+\Cref{fig:smallSize} compares some of our strategies in this case.
+We see that that Pessimistic performs better than Random and Extended pessimistic on a small size problem.
+(The figure also displays the performance of the Elitist strategy, to which we will come back.)
+Asking Random questions does not permit to reach a low regret level even after having asked 100 questions, whereas a low regret level ($\MMR$ = 1) is reached by Pessimistic before having asked 60 questions.
+We also see that Pessimistic performs slightly better than Extended pessimistic, showing that Pessimistic chooses candidate questions wisely; this is good news since (for $m = 5$ and $n = 10$), Pessimistic is much faster: it takes only $15$ seconds for a complete elicitation session, while Extended pessimistic takes $80$ seconds.
+(Although they come close, Pessimistic performs significantly better, in the sense that the numbers are consistently in favor of Pessimistic if running the experiment again.)
+\Cref{tab:biggerSize} shows that these conclusions also hold for a bigger size ($m = 10, n = 20$), except that this table does not feature Extended pessimistic, which is too slow to be ran repeatedly on much bigger problem sizes.
+
+We also compared the Pessimistic strategy against Elitist in a situation specifically tailored to advantage Elitsit.
+For that experiment specifically, instead of drawing the weights of the oracle randomly, we fix it to a “geometric” weight vector, such that $w_r - w_{r + 1} = 2(w_{r + 1} - w_{r + 2})$, for all $r ≤ m - 2$, so as to increase the importance of the weights associated to the top ranks.
+Even in that case, we see in \cref{tab:geometricWeights} that Pessimistic performs better than Elitist.
 

### 2020-10-09 minimax.tex
Comment fig 1
Minor stuff, mostly to save space.

@@
 \end{align}
-This comparison gives a way of picking questions among a set of possible questions, by picking one that minimizes this approximate measure of minimax regret {\em a posteriori}. 
-We use this operator that is similar to a $\max$ operator because \citet{Cailloux2014} reported that pessimistic aggregation works much better than optimistic aggregation, although our experiments in this context suggested a weak impact of that choice on the performance of the strategy.
+%This comparison gives a way of picking questions among a set of possible questions, by picking one that minimizes this approximate measure of minimax regret {\em a posteriori}. 
+We use this operator, similar to a $\max$ operator, because \citet{Cailloux2014} reported that pessimistic aggregation works much better than optimistic aggregation, although our experiments in this context suggested a weak impact of that choice on the performance of the strategy.
 However, to avoid the absorption property of max, we adopt a criterion closer to $\leximax$ as an aggregator: if the maximal MMR of two questions are (nearly) equal, then it considers the penalized minimal MMR values, preferring the question with the lowest value.
@@
 
-The \strat{Extended pessimistic} strategy uses the same criterion as the pessimistic strategy, but extending it to a bigger set of $m^2 n + m$ candidate questions, the same as those considered by the Random strategy.
-After having selected the candidate questions, we apply the same operator as for the Pessimistic strategy: we evaluate, for each of the possible questions, the minimax regret for the two possible answers and we choose the best according to (quasi-)$\leximax$.
+The \strat{Extended pessimistic} strategy uses the same criterion as the pessimistic strategy, but extending it to a bigger set of candidate questions, the same as those considered by the Random strategy.
+These candidate questions are then evaluated using the same operator as for the Pessimistic strategy, that is, we compute the minimax regret for the two possible answers, for each candidate question, and choose the best according to (quasi-)$\leximax$.
 We use this strategy to test whether Pessimistic performs well: depending on the quality of the heuristic of the Pessimistic strategy, it might perform nearly equally well, or perhaps even better, than Extended pessimistic, while being (much) faster.
@@
 \label{sec:experiments}
-\commentOC{
-	\begin{enumerate}
-		\item Comment on Table Pessimistic VS Elitist Geometric
-		\item Comment on Table Pessimistic VS Elitist VS Random
-		\item Reach regret: $n/10$. For this, we need $m^x n$ questions. Wait for more runs (Correct formula)
-		\item Prop qC in value of information
-		\item Time comparison XPess VS Pess? (If time, check our estimate)
-	\end{enumerate}
-}
+%TODO
+%\begin{enumerate}
+%	\item Reach regret: $n/10$. For this, we need $m^x n$ questions. Wait for more runs (Correct formula)
+%	\item Prop qC in value of information
+%	\item Time comparison XPess VS Pess? (If time, check our estimate)
+%\end{enumerate}
+
 Our experiments are described by topic here below. We generally use the following protocol, deviations are indicated below for each experiment.
@@
 	\includegraphics[width=.45\textwidth]{comparison.png}
-	\caption{Plot in support of \cref{tab:smallSize}}
+	\caption{Average MMR in problems of size $(5, 10)$ after $k$ questions.}
 	\label{fig:smallSize}
@@
 			10 & 24.8\\
-			15 & \\
+			15 & 48.4\\
 			\bottomrule
@@
 \Cref{fig:linearity} shows graphically the decrease in MMR according to the number of questions asked for various problem sizes.
-We see that this function is convex, apart from the very first few questions, indicating to users of our approach that asking, for example, half the number of questions required to reach a low regret value will still yield a significant gain in regret, namely, more than half the distance to the low regret value.
+We see that this function is convex, apart from the very first few questions, indicating to users of our approach that havling the number of questions will do less harm than halving the gain in regret, on average.
 
@@
 The experiments so far let the strategy target its questions unrestrictively, leaving open the possibility of questioning either the chair or an agent at each step.
-It may be desired in practical implementations to restrict the strategy to question the agents only, or mostly, or to wonder what is lost in terms of regret by asking different proportions of questions to the chair and the agents.
+One may wonder what is lost in terms of regret by asking different proportions of questions to the chair and the agents.
 Such restrictions may be useful because of (partial) unavailability of the chair, or because the estimated cognitive costs may differ sensibly, as these types of questions differ in nature.
-\Cref{tab:twoP400} shows the MMR value that is reached in a problem of size $m = 10, n = 20$ after $400$ questions, using the Two phases strategy, in the “ca” (chair then agents) and in the “ac” (agents then chair) variants.
+\Cref{tab:twoP400} shows the MMR value reached in a problem of size $m = 10, n = 20$ after $400$ questions, using the Two phases strategy, in the “ca” (chair then agents) and in the “ac” (agents then chair) variants.
 These numbers are to be compared with the MMR value reached after 400 questions with the unconstrained Pessimistic strategy (displayed in \cref{fig:linearity}), which is $0.62$.% ± $0.56$.

### 2020-10-09 minimax.tex
Fixing floats
Saving a bit more space, reduced to 8 pages

@@
 \begin{figure}
-	\centering
-	\includegraphics[width=.45\textwidth]{comparison.png}
 	\caption{Average MMR in problems of size $(5, 10)$ after $k$ questions.}
 	\label{fig:smallSize}
+	\includegraphics[width=.45\textwidth]{comparison.png}
 \end{figure}
 \begin{table}
-	\begin{center}
+	\caption{Average MMR in problems of size $(10, 20)$ after $k$ questions.}
+	\label{tab:biggerSize}
 	\begin{tabular}{S[table-figures-integer=3, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
@@
 	\end{tabular}
-	\end{center}
-	\caption{Average MMR in problems of size $(10, 20)$ after $k$ questions.}
-	\label{tab:biggerSize}
 \end{table}
 \begin{table}
-	\begin{center}
+	\caption{Average MMR in problems of size $(10, 20)$ and geometric weights after $k$ questions.}
+	\label{tab:geometricWeights}
 	\begin{tabular}{S[table-figures-integer=3, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
@@
 	\end{tabular}
-	\end{center}
-	\caption{Average MMR in problems of size $(10, 20)$ and geometric weights after $k$ questions.}
-	\label{tab:geometricWeights}
 \end{table}
@@
 \begin{table}
-	\begin{center}
+	\caption{Number of questions needed by Pessimistic strategy to reach an MMR of $\frac{n}{10}$ (represented by $k_{\MMR}$), by size.}
+	\label{tab:lowRegret}
 	\begin{tabular}{S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-number-alignment = center]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]}
@@
 	\end{tabular}
-	\end{center}
-	\caption{Number of questions needed by Pessimistic strategy to reach an MMR of $\frac{n}{10}$ (represented by $k_{\MMR}$), by size.}
-	\label{tab:lowRegret}
 \end{table}
 \begin{table}
-	\begin{center}
+	\caption{Number of questions needed by the Pessimistic strategy to elicit the complete preference of one agent.}
+	\label{tab:fullProfile}
 	\begin{tabular}{S[table-figures-integer=2, table-number-alignment = center, table-figures-decimal=0]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=2]}
@@
 	\end{tabular}
-	\end{center}
-	\caption{Number of questions needed by the Pessimistic strategy to elicit the complete preference of one agent.}
-	\label{tab:fullProfile}
 \end{table}
@@
 \subsection{Decrease in MMR values}
+%TODO balance columns appropriately before submitting
+\balance
 \begin{figure}
-	\centering
-	\includegraphics[width=.45\textwidth]{linearity.png}
 	\caption{Average MMR after $k$ questions with Pessimistic strategy after 10 runs for different problem sizes.}
 	\label{fig:linearity}
+	\includegraphics[width=.45\textwidth]{linearity.png}
 \end{figure}
@@
 \begin{table}
-	\begin{center}
+	\caption{Average MMR in problems of size $(10, 20)$ after $400$ questions, among which $q_c$ to the chair.}
+	\label{tab:twoP400}
 	\begin{tabular}{S[table-figures-integer=3, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
@@
 	\end{tabular}
-	\end{center}
-	\caption{Average MMR in problems of size $(10, 20)$ after $400$ questions, among which $q_c$ to the chair.}
-	\label{tab:twoP400}
 \end{table}
@@
 
-These numbers highlight that it is possible to obtain a good-quality recommendation while knowing only that the voting rule is a scoring rule and that the weights are convex, which is our basic hypothesis: when $p = 0$, no question is asked to the chair, and a good-quality recommendation is still reached after a relatively small number of questions.
+These numbers highlight that it is possible to obtain a good-quality recommendation while knowing only that the voting rule is a scoring rule and that the weights are convex, which is our basic hypothesis (corresponding to the line $q_c = 0$, where no question is asked to the chair).
 By contrast, the Pessimistic strategy, when unconstrained, asks X questions to the chair.
@@
 \label{sec:conclusions}
-%TODO balance columns appropriately before submitting
-%\balance
 In this paper we have considered a social choice setting with partial information about the agent's preferences and a partially specified voting rule.
@@
 suggest that regret-based elicitation is effective and allow to quickly reduce worst regret significantly.
-They also highlight the importance of not insisting to obtain a completely specified voting rule, as good quality (low regret) recommendations can be achieved short of knowing the weights precisely, in our setting.
+They also show that good quality (low regret) recommendations can be achieved short of knowing the weights precisely or the profile completely, in our setting.
 %regret, but they also show that starting with zero knowledge became a pretentious approach really quickly when increasing the size of the problem.

### 2020-10-09 minimax.tex
CCS and 10 runs
Drop estimation xm^yn

@@
 \end{abstract}
-
-%%% The code below was generated by the tool at http://dl.acm.org/ccs.cfm.
-%%% Please replace this example with code appropriate for your own paper.
-%TODO remove this before submission. This only serves to suppress the warning, but nobody seems to want this.
-\settopmatter{printccs=false}
-\ccsdesc[500]{Computing methodologies~Knowledge representation and reasoning}
-
-%%% Use this command to specify a few keywords describing your work.
-%%% Keywords should be separated by commas.
 
@@
 %	\item Time comparison XPess VS Pess? (If time, check our estimate)
+%Graphs: order symbols in the legend. Reduce number of marks on the X axis.
+%MMR and sd with systematically one decimal exactly
 %\end{enumerate}
@@
 
-We also compared the Pessimistic strategy against Elitist in a situation specifically tailored to advantage Elitsit.
+We also compared the Pessimistic strategy against Elitist in a situation specifically tailored to advantage Elitist.
 For that experiment specifically, instead of drawing the weights of the oracle randomly, we fix it to a “geometric” weight vector, such that $w_r - w_{r + 1} = 2(w_{r + 1} - w_{r + 2})$, for all $r ≤ m - 2$, so as to increase the importance of the weights associated to the top ranks.
@@
 	\label{tab:lowRegret}
-	\begin{tabular}{S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-number-alignment = center]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]}
+	\begin{tabular}{S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-number-alignment = center]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]}
 		\toprule
-		{m} & {n} & {$\frac{n}{10}$} & {$k_{\MMR}$} & {$0.4 m^{1.6} n$} \\
+		{m} & {n} & {$\frac{n}{10}$} & {$k_{\MMR}$} \\
 		\midrule
-		5 & 10 & 1.0 & 60 &  55 \\
-		5 & 15 & 1.5 & 80 &  83 \\
-		5 & 20 & 2.0 & 110 &  110 \\
-		10 & 20 & 2.0 & 340 &  341 \\
-		10 & 30 & 3.0 & 527 &  512 \\
-		15 & 30 & 3.0 & 812 &  991 \\
+		5 & 10 & 1.0 & 60 \\
+		5 & 15 & 1.5 & 80 \\
+		5 & 20 & 2.0 & 110 \\
+		10 & 20 & 2.0 & 340 \\
+		10 & 30 & 3.0 & 527 \\
+		15 & 30 & 3.0 & 812 \\
 		\bottomrule
@@
 The results for various sizes are displayed in \cref{tab:lowRegret}. 
-By relating the sizes to the column $k_{\MMR}$, we obtain the function $0.4m^{1.6}n$ as an approximation formula for the number of questions required to reach a low regret level.
-We see that this number grows approximately linearly with the number of agents and grows less fast than the square of the number of alternatives, for the sizes we considered.
-In other words, on average, assuming no questions get asked to the chair, each agent will have to answer $0.4m^{1.6}$ questions in order to to reach a low regret level, if this experimental formula reveals correct.
-For $m = 5$, that is about $6$ questions per agent; for $m = 10$, that is about $17$ questions per agent; and for $m = 15$, that is about $33$ questions per agent.
-These numbers have to be contrasted with those displayed in \cref{tab:fullProfile}.
-We constrained the Pessimistic strategy to ask questions to the agent only, and ran it on a single agent problem, with various values for $m$, to evaluate the number of questions required to elicit the full preference of an agent.
+We see that the number of questions required to reach a low regret level grows approximately linearly with the number of agents and grows less fast than the square of the number of alternatives, for the sizes we considered.
+Averaging these data by category of value for $m$, and assuming no questions get asked to the chair, in order to to reach a low regret level, each agent will have to answer $5.6$ questions for $m = 5$, $17.2$ questions for $m = 10$ and $27.1$ questions for $m = 15$.
+These numbers have to be contrasted with those displayed in \cref{tab:fullProfile}, that estimate the number of questions required to elicit the full preference of an agent.
+To obtain the data for this table, we constrained the Pessimistic strategy to ask questions to the agents only, and ran it on a single agent problem, with various values for $m$.
 
@@
 \begin{figure}
-	\caption{Average MMR after $k$ questions with Pessimistic strategy after 10 runs for different problem sizes.}
+	\caption{Average MMR after $k$ questions with Pessimistic strategy for different problem sizes.}
 	\label{fig:linearity}

### 2020-10-09 minimax.tex
nb qC and times

--- 2020-10-09 minimax.tex
@@
 %	\item Reach regret: $n/10$. For this, we need $m^x n$ questions. Wait for more runs (Correct formula)
-%	\item Prop qC in value of information
-%	\item Time comparison XPess VS Pess? (If time, check our estimate)
+%Graphs: order symbols in the legend. Reduce number of marks on the X axis.
 %\end{enumerate}
@@
 Asking Random questions does not permit to reach a low regret level even after having asked 100 questions, whereas a low regret level ($\MMR$ = 1) is reached by Pessimistic before having asked 60 questions.
-We also see that Pessimistic performs slightly better than Extended pessimistic, showing that Pessimistic chooses candidate questions wisely; this is good news since (for $m = 5$ and $n = 10$), Pessimistic is much faster: it takes only $15$ seconds for a complete elicitation session, while Extended pessimistic takes $80$ seconds.
+We also see that Pessimistic performs slightly better than Extended pessimistic, showing that Pessimistic chooses candidate questions wisely; this is good news since (for $m = 5$ and $n = 10$), Pessimistic is much faster: it takes on average only $24$s for a complete elicitation session ($150$ questions), while Extended pessimistic takes $76$s.
 (Although they come close, Pessimistic performs significantly better, in the sense that the numbers are consistently in favor of Pessimistic if running the experiment again.)
@@
 Knowing the speed of decrease permits to know which trade-offs can be achieved between the quality of the resulting recommendation and the number of questions that participants have to answer.
-\Cref{fig:linearity} shows graphically the decrease in MMR according to the number of questions asked for various problem sizes.
-We see that this function is convex, apart from the very first few questions, indicating to users of our approach that havling the number of questions will do less harm than halving the gain in regret, on average.
+\Cref{fig:linearity} shows graphically the decrease in $\MMR$ according to the number of questions asked for various problem sizes.
+We see that this function is convex, apart from the very first few questions, indicating to users of our approach that halving the number of questions will do less harm than halving the gain in regret, on average.
 
@@
 Such restrictions may be useful because of (partial) unavailability of the chair, or because the estimated cognitive costs may differ sensibly, as these types of questions differ in nature.
-\Cref{tab:twoP400} shows the MMR value reached in a problem of size $m = 10, n = 20$ after $400$ questions, using the Two phases strategy, in the “ca” (chair then agents) and in the “ac” (agents then chair) variants.
-These numbers are to be compared with the MMR value reached after 400 questions with the unconstrained Pessimistic strategy (displayed in \cref{fig:linearity}), which is $0.62$.% ± $0.56$.
+\Cref{tab:twoP400} shows the $\MMR$ value reached in a problem of size $m = 10, n = 20$ after $400$ questions, using the Two phases strategy, in the “ca” (chair then agents) and in the “ac” (agents then chair) variants.
+These numbers are to be compared with the $\MMR$ value reached after 400 questions with the unconstrained Pessimistic strategy (displayed in \cref{fig:linearity}), which is $0.62$.% ± $0.56$.
 
 These numbers highlight that it is possible to obtain a good-quality recommendation while knowing only that the voting rule is a scoring rule and that the weights are convex, which is our basic hypothesis (corresponding to the line $q_c = 0$, where no question is asked to the chair).
-By contrast, the Pessimistic strategy, when unconstrained, asks X questions to the chair.
+By contrast, the Pessimistic strategy, when unconstrained, asks on average $48$ questions to the chair.
 

### 2020-10-09 minimax.tex
minors spellCheck

@@
 
-Let $V$ be the set of possible preference profiles (the union, for any integer $n$, of the $n$-fold cartesian product of the linear orders over the alternatives).
-A social choice function $f : V \rightarrow \powersetz{A}$ associates a profile with a set of winners, where $\powersetz{A}$ represents the set of subsets of $A$ except for the emptyset (sets are used for tied winners).
+Let $V$ be the set of possible preference profiles (the union, for any integer $n$, of the $n$-fold Cartesian product of the linear orders over the alternatives).
+A social choice function $f : V \rightarrow \powersetz{A}$ associates a profile with a set of winners, where $\powersetz{A}$ represents the set of subsets of $A$ except for the empty set (sets are used for tied winners).
 Among the many possible social choice functions, we consider {\em positional scoring rules (PSR)}, which attach weights to positions according to the vector $(w_1, \ldots, w_m)$ (also called the scoring vector).
@@
 We use this operator, similar to a $\max$ operator, because \citet{Cailloux2014} reported that pessimistic aggregation works much better than optimistic aggregation, although our experiments in this context suggested a weak impact of that choice on the performance of the strategy.
-However, to avoid the absorption property of max, we adopt a criterion closer to $\leximax$ as an aggregator: if the maximal MMR of two questions are (nearly) equal, then it considers the penalized minimal MMR values, preferring the question with the lowest value.
-(Technically, instead of applying a pure lexicographic aggregation, which is very sensitive to small errors due to floating-point computations, we apply a weighted sum between the maximal and the penalized minimal MMR values, with a predominant weight to the maximal one.)
+However, to avoid the absorption property of max, we adopt a criterion closer to $\leximax$ as an aggregator: if the maximal $\MMR$ of two questions are (nearly) equal, then it considers the penalized minimal $\MMR$ values, preferring the question with the lowest value.
+(Technically, instead of applying a pure lexicographic aggregation, which is very sensitive to small errors due to floating-point computations, we apply a weighted sum between the maximal and the penalized minimal $\MMR$ values, with a predominant weight to the maximal one.)
 
@@
 We use this strategy to test whether Pessimistic performs well: depending on the quality of the heuristic of the Pessimistic strategy, it might perform nearly equally well, or perhaps even better, than Extended pessimistic, while being (much) faster.
-Extended pessimistic is applicable only to small problem instances: its complexity is in $O(n^2 m^5)$, because we consider $O(m^2)$ questions for each agent and need for each question to compute MMR twice, whose complexity is $O(nm^3)$.
+Extended pessimistic is applicable only to small problem instances: its complexity is in $O(n^2 m^5)$, because we consider $O(m^2)$ questions for each agent and need for each question to compute $\MMR$ twice, whose complexity is $O(nm^3)$.
 
@@
 We use the oracle to answer the question and update our knowledge, which is thus used to obtain the next question.
-This is repeated until $k$ answers have been obtained, compute the resulting MMR values along the way for various values of $k$.
-We repeat this whole experiment a variable number of times indicated below, for a given $(m, n, k)$, and report the average resulting MMR and the standard deviation \textit{sd}.
+This is repeated until $k$ answers have been obtained, compute the resulting $\MMR$ values along the way for various values of $k$.
+We repeat this whole experiment a variable number of times indicated below, for a given $(m, n, k)$, and report the average resulting $\MMR$ and the standard deviation \textit{sd}.
 
@@
 Finally, an important direction of extension aims at studying how to elicit preferences while restraining to concrete and easy questions.
-% Acknowledgements: We thank the reviewers for comments helping to improve the paper.
+% Acknowledgments: We thank the reviewers for comments helping to improve the paper.
 

### 2020-10-09 minimax.tex

@@
 %Graphs: order symbols in the legend. Reduce number of marks on the X axis.
+%MMR and sd with systematically one decimal exactly
 %\end{enumerate}

### 2020-10-09 minimax.tex
small changes

@@
 More recently \citet{Llamazares2013} and \citet{Viappiani2018} %(among others \commentOC{Which others?}) 
-considered the problem of dealing with unspecified weights in positional scoring rules; the first proposed a method based on Data Envelope Analysis, while the second proposed to aggregate the uncertainty in weights using criteria used in decision-making under uncertainty (such as minimax regret).
+considered the problem of dealing with unspecified weights in positional scoring rules; the first proposed a method based on Data Envelopment Analysis (DEA), while the second proposed to aggregate the uncertainty in weights using criteria used in decision-making under uncertainty (such as minimax regret).
 The work of \citet{Cailloux2014} deals with the problem of eliciting a generic voting rule.
@@
 	The rank of $x$ in the PMR-maximizing linear orders of agent $j$ is $\hat{v}_{j}(x) = 1+\card{A}-\card{{\pprefeq_j}(x)}$, and the rank of $y$ is $\hat{v}_{j}(y)=1+\card{{\pprefinv_j}(y)}+\card{\beta}$, where $\card{\beta} = \card{A \setminus ({\pprefeq_j}(x) \cup {\pprefinv_j}(y))}$ if $(x \pprefeq_j y)$ and $\card{\beta} = 0$ otherwise.
+	\label{claim:rankPMR}
 \end{claim}
@@
 \end{proof}
-
 The claim can also be understood by observing that in the case $(x \pprefeq_j y)$, $\beta$ is the number of alternatives incomparable with both $x$ and $y$.
-
 \begin{claim}
@@
 	\end{align}
-	where $\hat{\alpha}_{r}^{y}$ (resp. $\hat{\alpha}_{r}^{x}$)  is the number of times $y$ (resp. $x$) is at rank $r$ in the complete profile $\hat{\profile}$.
+	where $\hat{\alpha}_{r}^{y}$ (resp.
+$\hat{\alpha}_{r}^{x}$)  is the number of times $y$ (resp.
+$x$) is at rank $r$ in the complete profile $\hat{\profile}$ as determined in Claim \ref{claim:rankPMR}.
+%\ref{claim:completion}.
 \end{claim}
@@
 The pairwise max regret $\PMR(x,y; \pprofile,W)$ can be obtained as the solution of the following linear program defined on the variables $w_1, …, w_m$, which represent the weights attached to different positions:
-
 \begin{align}

### 2020-10-09 minimax.tex
description Pessimistic

@@
 A social choice function $f : V \rightarrow \powersetz{A}$ associates a profile with a set of winners, where $\powersetz{A}$ represents the set of subsets of $A$ except for the empty set (sets are used for tied winners).
-Among the many possible social choice functions, we consider {\em positional scoring rules (PSR)}, which attach weights to positions according to the vector $(w_1, \ldots, w_m)$ (also called the scoring vector).
+Among the many possible social choice functions, we consider {\em positional scoring rules (PSR)}, which attach weights to positions according to the vector $(w_1, \ldots, w_m)$, also known as the {\em scoring vector}.
 An alternative obtains a score that depends on the rank obtained in each of the preference orders:
@@
 In this paper, we consider a setting where both the agent preferences and the preferences of the chair about the voting rule are incomplete.
-As reviewed in \cref{sec:related}, some authors have considered possible and necessary winners assuming a partial profile or assuming an incompletely specified scoring rule, but in typical settings, there are no necessary winner and too many possible winners.
-In practice it is often useful to declare a winner given partial information.
+As reviewed in \cref{sec:related}, some authors have considered possible and necessary winners assuming 
+either a partial profile or assuming an incompletely specified scoring rule.
 
+Notice that often there are no necessary winner and too many possible winners; it is therefore useful to declare a winner given partial information.
 As a decision criterion to determine a winner, we propose to use minimax regret. 
 Minimax regret \citep{Savage1954} is a decision criterion that has been used for robust optimization under data uncertainty \citep{Kouvelis1997} as well as in decision-making with uncertain utility values \citep{Salo2001,Boutilier2006}.
-\citet{Lu2011} have adopted minimax regret for winner determination in social choice where
+In particular, \citet{Lu2011} have adopted minimax regret for winner determination in social choice where
 the preferences of agents that are only partially known, while the social choice function is predetermined and known.
 
-In this work, we consider the simultaneous presence of uncertainty in agent preferences and in weights.
+In this work, we consider the simultaneous presence of uncertainty in agent preferences and in the weights of the scoring rule used as a social choice function.
 Using {\em maximum regret} to quantify the worst-case error, the alternatives that minimize this error are selected as tied winners, providing us with a form of robust optimization.
@@
 The candidate questions to the agents use the heuristic proposed by \citet{Lu2011}: for each agent $j$, if $x^*$ and $\bar{y}$ are incomparable in $\ppref_j$, the candidate question concerns the pair $(x^*, \bar{y})$, otherwise, the candidate question concerns the pair $(x^*, z)$ for some $z$ incomparable to $x^*$ (randomly chosen), or if none such $z$ exist, the pair $(\bar{y}, z)$ for some $z$ incomparable to $\bar{y}$, or, if both $x^*$ and $\bar{y}$ are comparable to every alternatives in $\ppref_j$, any incomparable pair is picked at random.
-To understand the intuition behind favoring these two alternatives, recall that, as shown in the proof of \cref{claim:completion}, in order to increase $\PMR(x^{*},\bar{y})$, an adversary should place as many alternatives as she can above $x^{*}$ if $x^* \ppref_j \bar{y}$, and between $\bar{y}$ and $x^{*}$ if $\bar{y} \ppref_j x^*$.
-Asking questions involving $x^*$ or $\bar{y}$ thus has a particular chance of reducing usefully the possibilities of the adversary.
-The candidate questions to the chair are determined as in the Random strategy.
-The strategy then selects among these $n + m$ candidate questions one that leads to minimal regret in the worst case, considering both possible answers to the question, and with penalty terms depending on the kind of question.
+To understand the rationale behind the heuristic %relies oo understand the intuition behind %favoring these two alternatives, 
+recall that, as shown in the proof of \cref{claim:completion}, in order to increase $\PMR(x^{*},\bar{y})$, the adversary should place as many alternatives as possible above $x^{*}$ if $x^* \ppref_j \bar{y}$, and between $\bar{y}$ and $x^{*}$ if $\bar{y} \ppref_j x^*$.
+Responses to questions involving $x^*$ or $\bar{y}$ constrain the ability of the adversary to complete the profile in such manner, possibly reducing minimax regret.
+
+\noindent The candidate questions to the chair are determined as in the Random strategy.
+The Pessimistic strategy then selects among these $n + m$ candidate questions one that leads to minimal regret in the worst case, considering both possible answers to the question, and with penalty terms depending on the kind of question.
 To define this comparison precisely, assume that a question $q_1$ has type $t_1$ (being “chair” or “agent”), and leads to the possible new knowledge states $(\pprofile_1, W_1)$ and $(\pprofile'_1, W'_1)$, depending on the answer.
@@
 Define similarly $t_2$, $R^{\max}_2$ and $R^{\min}_2$ for a question $q_2$.
-Then, the Pessimistic strategy considers question $q_1$ more suitable than $q_2$ iff
+We are now faced with the problem of aggregating these values to determine the informative value of the question.
+Motivated by  \citet{Cailloux2014} we adopt a pessimistic approach, reported to perform much better than optimistic aggregation.
+% use this operator, similar to a $\max$ operator, because \citet{Cailloux2014} reported that pessimistic aggregation works much better than optimistic aggregation, although our experiments in this context suggested a weak impact of that choice on the performance of the strategy.
+However, to avoid the absorption property of the max, we adopt $\leximax$ as an aggregator.
+Pessimistic considers question $q_1$ to be better  than $q_2$ iff
 \begin{align}
-	R^{\max}_1 ≤ R^{\max}_2 \text{ or } [R^{\max}_1 = R^{\max}_2 \text{ and } R^{\min}_1 ≤ R^{\min}_2].
+	R^{\max}_1 < R^{\max}_2 \text{ or } [R^{\max}_1 = R^{\max}_2 \text{ and } R^{\min}_1 < R^{\min}_2].
 \end{align}
 %This comparison gives a way of picking questions among a set of possible questions, by picking one that minimizes this approximate measure of minimax regret {\em a posteriori}. 
-We use this operator, similar to a $\max$ operator, because \citet{Cailloux2014} reported that pessimistic aggregation works much better than optimistic aggregation, although our experiments in this context suggested a weak impact of that choice on the performance of the strategy.
-However, to avoid the absorption property of max, we adopt a criterion closer to $\leximax$ as an aggregator: if the maximal $\MMR$ of two questions are (nearly) equal, then it considers the penalized minimal $\MMR$ values, preferring the question with the lowest value.
+%The motivation for using this operator lies in 
+In other words if the maximal {\em a posteriori} $\MMR$ of two questions are (nearly) equal, then it considers the (penalized) minimal $\MMR$ values, preferring the question with the lowest value.
 (Technically, instead of applying a pure lexicographic aggregation, which is very sensitive to small errors due to floating-point computations, we apply a weighted sum between the maximal and the penalized minimal $\MMR$ values, with a predominant weight to the maximal one.)

### 2020-10-09 minimax.tex
epsilon for penalty

@@
 Define $R^{\max}_1 = \max\set{\MMR(\pprofile_1, W_1), \MMR(\pprofile'_1, W'_1)}$
-and $R^{\min}_1 = \min\set{\MMR(\pprofile_1, W_1), \MMR(\pprofile'_1, W'_1)} p(t) + p'(t)$.
+and $R^{\min}_1 = \min\set{\MMR(\pprofile_1, W_1), \MMR(\pprofile'_1, W'_1)} \epsilon_{t} + \epsilon'_{t}$.
 %If $(\pprofile_1, W_1) ≥ (\pprofile'_1, W'_1)$, define $\MMR^{\max} = \MMR(\pprofile_1, W_1)$ and $\MMR^{\min} = \MMR(\pprofile'_1, W'_1)$; otherwise, define $\MMR^{\max} = \MMR(\pprofile'_1, W'_1)$ and $\MMR^{\min} = \MMR(\pprofile_1, W_1)$.
 % and and $(\pprofile^\min_2, W^\min_2)$. numbering them so that $\MMR(\pprofile_1, W_1) ≥ \MMR(\pprofile_2, W_2)$. Then the badness of the question in the worst case is:
-The terms $p(t)$ and $p'(t)$ are real numbers depending on the kind of question. These parameters are to be determined experimentally.
+The terms $\epsilon_t$ and $\epsilon'_{t}$ are real numbers depending on the kind of question; these parameters are to be determined experimentally and are use to fine control the choice of the question type.
 Define similarly $t_2$, $R^{\max}_2$ and $R^{\min}_2$ for a question $q_2$.
@@
 In other words if the maximal {\em a posteriori} $\MMR$ of two questions are (nearly) equal, then it considers the (penalized) minimal $\MMR$ values, preferring the question with the lowest value.
-(Technically, instead of applying a pure lexicographic aggregation, which is very sensitive to small errors due to floating-point computations, we apply a weighted sum between the maximal and the penalized minimal $\MMR$ values, with a predominant weight to the maximal one.)
+(Technically, instead of applying a pure lexicographic aggregation, which is very sensitive to small errors due to floating-point computations, we apply a weighted sum between the maximal and the penalized minimal $\MMR$ values, with a predominant weight given to the maximal one, several order of magnitudes higher than the weight given to the penalized minimal $\MMR$.)
 
@@
 The weights are generated by drawing $m-1$ differences randomly with uniform distribution, normalizing them, then ordering them, in order to ensure convexity.
-The penalty parameters for the Pessimistic and Extended pessimistic strategies are set to $p(t) = 1.1$ and $p'(t) = 10^{-6}$ when $t = $“chair” and $p(t) = 1.0$ and $p'(t) = 0$ when $t = $“agent”.
+The penalty parameters for the Pessimistic and Extended pessimistic strategies are set to $\epsilon_{\text{chair}} = 1.1$ and $\epsilon'_{\text{chair}} = 10^{-6}$ and $\epsilon_{\text{agent}} = 1.0$ and $\epsilon'_{\text{agent}} = 0$.
 

### 2020-10-09 minimax.tex

@@
 % and and $(\pprofile^\min_2, W^\min_2)$. numbering them so that $\MMR(\pprofile_1, W_1) ≥ \MMR(\pprofile_2, W_2)$. Then the badness of the question in the worst case is:
-The terms $\epsilon_t$ and $\epsilon'_{t}$ are real numbers depending on the kind of question; these parameters are to be determined experimentally and are use to fine control the choice of the question type.
+The terms $\epsilon_t$ and $\epsilon'_{t}$ are real numbers associated to the type $t$ of question; these parameters are to be determined experimentally and are used to fine control the choice of the question type.
 Define similarly $t_2$, $R^{\max}_2$ and $R^{\min}_2$ for a question $q_2$.
@@
 %\end{enumerate}
-
-Our experiments are described by topic here below. We generally use the following protocol, deviations are indicated below for each experiment.
-
+We  performed a number of numerical experiments in order to validate our approach and to test the performance of the different elicitation strategies.
+%Our experiments are described by topic here below.
+We start by describing the general protocol of experimentation. %use the following protocol, deviations are indicated below for each experiment.
 Having picked a problem size $(m, n)$, a number of questions $k$ and a strategy to test, we randomly generate an “oracle”, containing the true preferences of the agents (i.e.
@@
 The preferences are generated following an impartial culture assumption: the linear order of each agent is generated independently from the other ones and all have the same probability of appearing. 
-The weights are generated by drawing $m-1$ differences randomly with uniform distribution, normalizing them, then ordering them, in order to ensure convexity.
+For gerenerating the weights we first draw $m-1$ numbers uniformly at random (representing weight ``differences''), normalize and sort them; 
+a sequence of convex decreasing weight is then obtained by a decumulative sum.% to the former numbers.
+% ordering them, in order to ensure convexity.
 The penalty parameters for the Pessimistic and Extended pessimistic strategies are set to $\epsilon_{\text{chair}} = 1.1$ and $\epsilon'_{\text{chair}} = 10^{-6}$ and $\epsilon_{\text{agent}} = 1.0$ and $\epsilon'_{\text{agent}} = 0$.
@@
 We obtain the first question to be asked using the strategy under test, as described above.
-We use the oracle to answer the question and update our knowledge, which is thus used to obtain the next question.
-This is repeated until $k$ answers have been obtained, compute the resulting $\MMR$ values along the way for various values of $k$.
+We then use the oracle to answer the question and update the system's knowledge, which is thus used to obtain the next question.
+This is repeated until $k$ answers have been obtained, computinh the resulting $\MMR$ values along the way for various values of $k$.
 We repeat this whole experiment a variable number of times indicated below, for a given $(m, n, k)$, and report the average resulting $\MMR$ and the standard deviation \textit{sd}.

### 2020-10-09 minimax.tex
experiment section

@@
 
-\subsection{Relative evaluation of Pessimistic strategy}
+%\subsection{Relative evaluation of Pessimistic strategy}
+\paragraph{Comparison of all strategies in problem instances of small size}
+
 \begin{figure}
@@
 \end{table}
-
-Our first experimental result concerns small size situations.
-We picked $m = 5, n = 10$ to illustrate our results (variations around this size yield similar conclusions), ran it $200$ times and averaged the results.
+%Our first experimental result concerns small size situations. 
+In the first experiment we picked $m = 5, n = 10$ to illustrate our results (variations around this size yield similar conclusions), ran it $200$ times and averaged the results.
 \Cref{fig:smallSize} compares some of our strategies in this case.
-We see that that Pessimistic performs better than Random and Extended pessimistic on a small size problem.
-(The figure also displays the performance of the Elitist strategy, to which we will come back.)
-Asking Random questions does not permit to reach a low regret level even after having asked 100 questions, whereas a low regret level ($\MMR$ = 1) is reached by Pessimistic before having asked 60 questions.
+We see that that Pessimistic performs better than Random,  Extended pessimistic, %. % on a small size problem.
+and as well Elitist.
+%(The figure also displays the performance of the Elitist strategy).
+Asking random questions does not allow to reach a low regret level even after having asked 100 questions, whereas a low regret level ($\MMR$ = 1) is reached by Pessimistic before having asked 60 questions.
 We also see that Pessimistic performs slightly better than Extended pessimistic, showing that Pessimistic chooses candidate questions wisely; this is good news since (for $m = 5$ and $n = 10$), Pessimistic is much faster: it takes on average only $24$s for a complete elicitation session ($150$ questions), while Extended pessimistic takes $76$s.
-(Although they come close, Pessimistic performs significantly better, in the sense that the numbers are consistently in favor of Pessimistic if running the experiment again.)
-\Cref{tab:biggerSize} shows that these conclusions also hold for a bigger size ($m = 10, n = 20$), except that this table does not feature Extended pessimistic, which is too slow to be ran repeatedly on much bigger problem sizes.
+Notice that although they exhibit a close performance, Pessimistic performs %significantly %better, in the sense that the numbers are
+consistently better Pessimistic in the different runs of the experiment).
+\Cref{tab:biggerSize} shows that these conclusions also hold for a problem of larger size ($m = 10, n = 20$), except that this table does not feature Extended pessimistic, which is too slow to be ran repeatedly on such instance.
 
 We also compared the Pessimistic strategy against Elitist in a situation specifically tailored to advantage Elitist.
-For that experiment specifically, instead of drawing the weights of the oracle randomly, we fix it to a “geometric” weight vector, such that $w_r - w_{r + 1} = 2(w_{r + 1} - w_{r + 2})$, for all $r ≤ m - 2$, so as to increase the importance of the weights associated to the top ranks.
+For that experiment specifically, instead of drawing the weights of the oracle randomly, we fix it to a “geometric” weight vector, such that $w_r - w_{r + 1} = 2(w_{r + 1} - w_{r + 2})$, for all $r ≤ m - 2$, so as to dramatically increase the importance of the weights associated to the top ranks.
 Even in that case, we see in \cref{tab:geometricWeights} that Pessimistic performs better than Elitist.
 
-\subsection{Absolute evaluation of Pessimistic strategy}
+%\subsection{Absolute evaluation of Pessimistic strategy}
+\paragraph{In-dept evaluation of Pessimistic}
 \label{sec:lowRegret}
@@
 \end{table}
-
-The previous section compares Pessimistic to other strategies.
-In this set of experiments, we wonder about the absolute quality of Pessimistic.
-For practical usability, it is important to know how many questions should be asked in order to reach a low regret level.
+While in previous experiments we compared Pessimistic to the other strategies, in this set of experiments, we focus %about the absolute quality of 
+on Pessimistic. 
+We %For practical usability,
+think that it is important to know how many questions should be asked in order to reach a low regret level.
 Here, we consider a low level to be a tenth of the number of agents ($n/10$): such a regret is equivalent to the difference of score of an alternative $x$ that results from switching from a profile $P$ to a profile $P'$ where ten percent of the agents rank $x$ last instead of first.
@@
 
-\subsection{Decrease in MMR values}
+%\subsection{Decrease in MMR values}
+\paragraph{Decrease in MMR values}
 %TODO balance columns appropriately before submitting
@@
 We next wonder how fast the regret decreases, measured as a function of the number of questions asked.
-This is important practically because it may be impossible or unwanted to ask enough questions to reach low level of regrets, as computed in \cref{sec:lowRegret}.
+This is important practically because it may be impossible or undesiderable to ask enough questions to reach low level of regrets, as computed in \cref{sec:lowRegret}.
 Knowing the speed of decrease permits to know which trade-offs can be achieved between the quality of the resulting recommendation and the number of questions that participants have to answer.
 \Cref{fig:linearity} shows graphically the decrease in $\MMR$ according to the number of questions asked for various problem sizes.
-We see that this function is convex, apart from the very first few questions, indicating to users of our approach that halving the number of questions will do less harm than halving the gain in regret, on average.
+We see that this function is convex, apart from the very first few questions, indicating %to users of our approach
+that, on average, halving the number of questions will reduce the reduction in regret by less than half.% do less harm than halving the gain in regret, on average.
 
-\subsection{Value of information comparison}
+%\subsection{Value of information comparison}
+\paragraph{Value of information comparison}
+
 \begin{table}
@@
 Such restrictions may be useful because of (partial) unavailability of the chair, or because the estimated cognitive costs may differ sensibly, as these types of questions differ in nature.
-\Cref{tab:twoP400} shows the $\MMR$ value reached in a problem of size $m = 10, n = 20$ after $400$ questions, using the Two phases strategy, in the “ca” (chair then agents) and in the “ac” (agents then chair) variants.
+\Cref{tab:twoP400} shows the $\MMR$ value reached in a problem of size $m = 10, n = 20$ after $400$ questions, using the Two phases strategy, in the “ca” ({\em chair then agents}) and in the “ac” ({\em agents then chair}) variants.
+The former variant first asks $q_{c}$ questions to the chair and then $400-q_{c}$ to the agents; the latter first $400-q_{c}$ to the agents and then $q_{c}$ questions to the chair.
  These numbers are to be compared with the $\MMR$ value reached after 400 questions with the unconstrained Pessimistic strategy (displayed in \cref{fig:linearity}), which is $0.62$.% ± $0.56$.

### 2020-10-09 minimax.tex
experiment section 2
Introduction and Experiments

@@
 We develop methods for computing the minimax-optimal
-alternative using positional scoring rules and we provide incremental elicitation methods to acquire relevant preference information.
-We then discuss several heuristics that determine queries, to an agent or to the chair (the person or organization supervising the voting process), that quickly reduce minimax regret.
+alternative using positional scoring rules and we provide incremental elicitation methods that 
+%to acquire relevant preference information; 
+at each step of the elicitation ask a question either to one of the agents or to the chair (the person or organization supervising the voting process).
+We discuss several heuristics that determine queries that quickly reduce minimax regret. 
 While previous works have considered either partial information about the agent preferences or a partially specified aggregation method, we do not know of any work considering both sources of uncertainty at the same time.
@@
 %In particular, our query strategies focus simultaneously on reduction of relevant preference and voting rule uncertainty.
-
-\paragraph{Experimental conclusions}
+%\paragraph{Experimental conclusions}
 Our approach permits to compare experimentally strategies that question the chair, the agents, or both.
@@
 First, a good quality recommendation can be reached by asking what can be considered a reasonable number of questions to the chair and agents.
-For example, in a problem of size $m = 5$, $n = 10$, $55$ questions in total are required to reach a good quality recommendation, which can be considered reasonable as these questions are to be dispatched over $10$ agents and the chair.
-Second, the quality of the recommendation increases faster than linearly with the number of questions, after only a few questions (the first few questions yield no increase in quality).
-Third, we experimentally find out that asking questions only to the agents performs similarly than asking questions both to the agents and the chair, although questions to the chair do have a positive value in terms of quality of the recommendation.
+For example, in a problem of size $m = 5$, $n = 10$, only $55$ questions in total are required to reach a good quality recommendation, which can be considered reasonable as these questions are to be dispatched over $10$ agents and the chair.
+Second, the quality of the recommendation increases faster than linearly with the number of questions, 
+after an initial phase with almost no increase in quality, before slowing down and converging to an optimal recommendation.
+%; so it is possible to stop the elicitation early and to pick a near-optimal recommendation.
+%after only a few questions (the first few questions yield no increase in quality), so it .
+Third, we experimentally find out that asking questions only to the agents performs almost as good than interleaving questions both to the agents and the chair, although questions to the chair do have a positive value in terms of quality of the recommendation.
 %the value of information of one question to the chair is similar to the value of information of one question to a agent (in the ranges we considered), up to a certain proportion of questions asked to the chair.
@@
 %\subsection{Relative evaluation of Pessimistic strategy}
-\paragraph{Comparison of all strategies in problem instances of small size}
+\paragraph{Comparison of strategies in problem instances of small size}
 
@@
 We next wonder how fast the regret decreases, measured as a function of the number of questions asked.
-This is important practically because it may be impossible or undesiderable to ask enough questions to reach low level of regrets, as computed in \cref{sec:lowRegret}.
+This is important practically because it may be impossible or undesiderable to ask all questions necessary to reach low level of regrets, as computed in \cref{sec:lowRegret}.
 Knowing the speed of decrease permits to know which trade-offs can be achieved between the quality of the resulting recommendation and the number of questions that participants have to answer.
@@
 %\subsection{Value of information comparison}
-\paragraph{Value of information comparison}
+\paragraph{Comparison with Two Phase}
 
@@
 We count the average number of questions required to reach a complete ordering.
-
-The experiments so far let the strategy target its questions unrestrictively, leaving open the possibility of questioning either the chair or an agent at each step.
-One may wonder what is lost in terms of regret by asking different proportions of questions to the chair and the agents.
+The experiments so far considered strategies that, at each step, mix questions to the chair and to the agents.
+One may wonder what is lost in terms of regret by focusing on the Two Phase strategy that asks a bulk of question of one type first and then switches to the other type.
+%different proportions of questions to the chair and the agents.
 Such restrictions may be useful because of (partial) unavailability of the chair, or because the estimated cognitive costs may differ sensibly, as these types of questions differ in nature.
-\Cref{tab:twoP400} shows the $\MMR$ value reached in a problem of size $m = 10, n = 20$ after $400$ questions, using the Two phases strategy, in the “ca” ({\em chair then agents}) and in the “ac” ({\em agents then chair}) variants.
-The former variant first asks $q_{c}$ questions to the chair and then $400-q_{c}$ to the agents; the latter first $400-q_{c}$ to the agents and then $q_{c}$ questions to the chair.
- These numbers are to be compared with the $\MMR$ value reached after 400 questions with the unconstrained Pessimistic strategy (displayed in \cref{fig:linearity}), which is $0.62$.% ± $0.56$.
+Notice that there might be practical reasons (for example, the chair may be unavailable during part of the process) for restricting a question type to a specific part of the elicitation process.
+We are also interested in analyzing the performance of different proportions of question types, since  (notice that the estimated cognitive costs may differ sensibly, as these types of questions differ in nature).
+\Cref{tab:twoP400} shows the $\MMR$ value reached in a problem of size $m = 10, n = 20$ after $400$ questions, using the Two phases strategy, in the “ca” ({\em chair then agents}) and in the “ac” ({\em agents then chair}) variants, for different values of $q_{c}$, the number of questions to the chair;
+e.g. the former variant first asks $q_{c}$ questions to the chair and then $400-q_{c}$ to the agents. %, while the latter asks $400-q_{c}$ to the agents and then $q_{c}$ questions to the chair.
+These numbers are to be compared with the $\MMR$ value reached after 400 questions with the Pessimistic strategy (displayed in \cref{fig:linearity}), which is $0.62$.% ± $0.56$.
 
 These numbers highlight that it is possible to obtain a good-quality recommendation while knowing only that the voting rule is a scoring rule and that the weights are convex, which is our basic hypothesis (corresponding to the line $q_c = 0$, where no question is asked to the chair).
-By contrast, the Pessimistic strategy, when unconstrained, asks on average $48$ questions to the chair.
+By contrast, the Pessimistic strategy (that interleaves the two types of questions) asks on average $48$ questions to the chair.
 

### 2020-10-10 minimax.tex
Restored similar perfs

@@
 %after only a few questions (the first few questions yield no increase in quality), so it .
-Third, we experimentally find out that asking questions only to the agents performs almost as good than interleaving questions both to the agents and the chair, although questions to the chair do have a positive value in terms of quality of the recommendation.
+Third, we experimentally find out that asking questions only to the agents performs similarly to asking questions both to the agents and the chair, although questions to the chair do have a positive value in terms of quality of the recommendation.
 %the value of information of one question to the chair is similar to the value of information of one question to a agent (in the ranges we considered), up to a certain proportion of questions asked to the chair.

### 2020-10-10 minimax.tex
Par
Restored opt sim to pess

@@
 The candidate questions to the agents use the heuristic proposed by \citet{Lu2011}: for each agent $j$, if $x^*$ and $\bar{y}$ are incomparable in $\ppref_j$, the candidate question concerns the pair $(x^*, \bar{y})$, otherwise, the candidate question concerns the pair $(x^*, z)$ for some $z$ incomparable to $x^*$ (randomly chosen), or if none such $z$ exist, the pair $(\bar{y}, z)$ for some $z$ incomparable to $\bar{y}$, or, if both $x^*$ and $\bar{y}$ are comparable to every alternatives in $\ppref_j$, any incomparable pair is picked at random.
-To understand the rationale behind the heuristic %relies oo understand the intuition behind %favoring these two alternatives, 
+To understand the rationale behind the heuristic, 
 recall that, as shown in the proof of \cref{claim:completion}, in order to increase $\PMR(x^{*},\bar{y})$, the adversary should place as many alternatives as possible above $x^{*}$ if $x^* \ppref_j \bar{y}$, and between $\bar{y}$ and $x^{*}$ if $\bar{y} \ppref_j x^*$.
 Responses to questions involving $x^*$ or $\bar{y}$ constrain the ability of the adversary to complete the profile in such manner, possibly reducing minimax regret.
+The candidate questions to the chair are determined as in the Random strategy.
 
-\noindent The candidate questions to the chair are determined as in the Random strategy.
 The Pessimistic strategy then selects among these $n + m$ candidate questions one that leads to minimal regret in the worst case, considering both possible answers to the question, and with penalty terms depending on the kind of question.
@@
 We are now faced with the problem of aggregating these values to determine the informative value of the question.
-Motivated by  \citet{Cailloux2014} we adopt a pessimistic approach, reported to perform much better than optimistic aggregation.
-% use this operator, similar to a $\max$ operator, because \citet{Cailloux2014} reported that pessimistic aggregation works much better than optimistic aggregation, although our experiments in this context suggested a weak impact of that choice on the performance of the strategy.
+Motivated by  \citet{Cailloux2014} we adopt a pessimistic approach, reported to perform better than optimistic aggregation, although our experiments in this context suggested a weak impact of that choice on the performance of the strategy.
 However, to avoid the absorption property of the max, we adopt $\leximax$ as an aggregator.

### 2020-10-10 minimax.tex
Rephrase to avoid overful

@@
 The Pessimistic strategy then selects among these $n + m$ candidate questions one that leads to minimal regret in the worst case, considering both possible answers to the question, and with penalty terms depending on the kind of question.
-To define this comparison precisely, assume that a question $q_1$ has type $t_1$ (being “chair” or “agent”), and leads to the possible new knowledge states $(\pprofile_1, W_1)$ and $(\pprofile'_1, W'_1)$, depending on the answer.
+To define this comparison precisely, assume that a question $q_1$ has type $t_1$ (being “chair” or “agent”), and leads to the new knowledge states $(\pprofile_1, W_1)$ if answered positively and $(\pprofile'_1, W'_1)$ if the answer is negative.
 Define $R^{\max}_1 = \max\set{\MMR(\pprofile_1, W_1), \MMR(\pprofile'_1, W'_1)}$
@@
 Define similarly $t_2$, $R^{\max}_2$ and $R^{\min}_2$ for a question $q_2$.
-We are now faced with the problem of aggregating these values to determine the informative value of the question.
-Motivated by  \citet{Cailloux2014} we adopt a pessimistic approach, reported to perform better than optimistic aggregation, although our experiments in this context suggested a weak impact of that choice on the performance of the strategy.
-However, to avoid the absorption property of the max, we adopt $\leximax$ as an aggregator.
-Pessimistic considers question $q_1$ to be better  than $q_2$ iff
+We now must aggregate these values to determine the informative value of the question.
+We adopt a pessimistic approach, reported to perform better than optimistic aggregation \citep{Cailloux2014}, although our experiments in this context suggested a weak impact of that choice on the performance of the strategy.
+To avoid the absorption property of the max, we adopt $\leximax$ as an aggregator.
+Pessimistic thus considers question $q_1$ to be better  than $q_2$ iff
 \begin{align}

### 2020-10-10 minimax.tex
Restored text MMR

@@
 %The motivation for using this operator lies in 
-In other words if the maximal {\em a posteriori} $\MMR$ of two questions are (nearly) equal, then it considers the (penalized) minimal $\MMR$ values, preferring the question with the lowest value.
-(Technically, instead of applying a pure lexicographic aggregation, which is very sensitive to small errors due to floating-point computations, we apply a weighted sum between the maximal and the penalized minimal $\MMR$ values, with a predominant weight given to the maximal one, several order of magnitudes higher than the weight given to the penalized minimal $\MMR$.)
+In other words if the maximal {\em a posteriori} MMR of two questions are (nearly) equal, then it considers the (penalized) minimal MMR values, preferring the question with the lowest value.
+(Technically, instead of applying a pure lexicographic aggregation, which is very sensitive to small errors due to floating-point computations, we apply a weighted sum between the maximal and the penalized minimal MMR values, with a predominant weight given to the maximal one, several order of magnitudes higher than the weight given to the penalized minimal MMR.)
 
@@
 We use this strategy to test whether Pessimistic performs well: depending on the quality of the heuristic of the Pessimistic strategy, it might perform nearly equally well, or perhaps even better, than Extended pessimistic, while being (much) faster.
-Extended pessimistic is applicable only to small problem instances: its complexity is in $O(n^2 m^5)$, because we consider $O(m^2)$ questions for each agent and need for each question to compute $\MMR$ twice, whose complexity is $O(nm^3)$.
+Extended pessimistic is applicable only to small problem instances: its complexity is in $O(n^2 m^5)$, because we consider $O(m^2)$ questions for each agent and need for each question to compute MMR twice, whose complexity is $O(nm^3)$.
 
@@
 We then use the oracle to answer the question and update the system's knowledge, which is thus used to obtain the next question.
-This is repeated until $k$ answers have been obtained, computinh the resulting $\MMR$ values along the way for various values of $k$.
-We repeat this whole experiment a variable number of times indicated below, for a given $(m, n, k)$, and report the average resulting $\MMR$ and the standard deviation \textit{sd}.
+This is repeated until $k$ answers have been obtained, computinh the resulting MMR values along the way for various values of $k$.
+We repeat this whole experiment a variable number of times indicated below, for a given $(m, n, k)$, and report the average resulting MMR and the standard deviation \textit{sd}.
 
@@
 Knowing the speed of decrease permits to know which trade-offs can be achieved between the quality of the resulting recommendation and the number of questions that participants have to answer.
-\Cref{fig:linearity} shows graphically the decrease in $\MMR$ according to the number of questions asked for various problem sizes.
+\Cref{fig:linearity} shows graphically the decrease in MMR according to the number of questions asked for various problem sizes.
 We see that this function is convex, apart from the very first few questions, indicating %to users of our approach
@@
 We are also interested in analyzing the performance of different proportions of question types, since  (notice that the estimated cognitive costs may differ sensibly, as these types of questions differ in nature).
-\Cref{tab:twoP400} shows the $\MMR$ value reached in a problem of size $m = 10, n = 20$ after $400$ questions, using the Two phases strategy, in the “ca” ({\em chair then agents}) and in the “ac” ({\em agents then chair}) variants, for different values of $q_{c}$, the number of questions to the chair;
+\Cref{tab:twoP400} shows the MMR value reached in a problem of size $m = 10, n = 20$ after $400$ questions, using the Two phases strategy, in the “ca” ({\em chair then agents}) and in the “ac” ({\em agents then chair}) variants, for different values of $q_{c}$, the number of questions to the chair;
 e.g. the former variant first asks $q_{c}$ questions to the chair and then $400-q_{c}$ to the agents. %, while the latter asks $400-q_{c}$ to the agents and then $q_{c}$ questions to the chair.
-These numbers are to be compared with the $\MMR$ value reached after 400 questions with the Pessimistic strategy (displayed in \cref{fig:linearity}), which is $0.62$.% ± $0.56$.
+These numbers are to be compared with the MMR value reached after 400 questions with the Pessimistic strategy (displayed in \cref{fig:linearity}), which is $0.62$.% ± $0.56$.
 

### 2020-10-10 minimax.tex
Various minor; restored previous 2 phase.

@@
 %MMR and sd with systematically one decimal exactly
+%$150$ questions?
+%Pessimistic systematically better than XPess?
 %\end{enumerate}
@@
 The preferences are generated following an impartial culture assumption: the linear order of each agent is generated independently from the other ones and all have the same probability of appearing. 
-For gerenerating the weights we first draw $m-1$ numbers uniformly at random (representing weight ``differences''), normalize and sort them; 
-a sequence of convex decreasing weight is then obtained by a decumulative sum.% to the former numbers.
-% ordering them, in order to ensure convexity.
-The penalty parameters for the Pessimistic and Extended pessimistic strategies are set to $\epsilon_{\text{chair}} = 1.1$ and $\epsilon'_{\text{chair}} = 10^{-6}$ and $\epsilon_{\text{agent}} = 1.0$ and $\epsilon'_{\text{agent}} = 0$.
+For generating the weights we first draw $m - 1$ numbers uniformly at random (representing weight ``differences''), normalize and sort them; 
+a sequence of convex decreasing weight is then obtained by a decumulative sum.
+The penalty parameters for the Pessimistic and Extended pessimistic strategies are set to $\epsilon_{\text{chair}} = 1.1$, $\epsilon'_{\text{chair}} = 10^{-6}$, $\epsilon_{\text{agent}} = 1.0$ and $\epsilon'_{\text{agent}} = 0$.
 
@@
 We then use the oracle to answer the question and update the system's knowledge, which is thus used to obtain the next question.
-This is repeated until $k$ answers have been obtained, computinh the resulting MMR values along the way for various values of $k$.
+This is repeated until $k$ answers have been obtained, computing the resulting MMR values along the way for various values of $k$.
 We repeat this whole experiment a variable number of times indicated below, for a given $(m, n, k)$, and report the average resulting MMR and the standard deviation \textit{sd}.
 
-%\subsection{Relative evaluation of Pessimistic strategy}
-\paragraph{Comparison of strategies in problem instances of small size}
-
+\paragraph{Comparison of strategies}
 \begin{figure}
@@
 \end{table}
-%Our first experimental result concerns small size situations. 
-In the first experiment we picked $m = 5, n = 10$ to illustrate our results (variations around this size yield similar conclusions), ran it $200$ times and averaged the results.
-\Cref{fig:smallSize} compares some of our strategies in this case.
-We see that that Pessimistic performs better than Random,  Extended pessimistic, %. % on a small size problem.
-and as well Elitist.
-%(The figure also displays the performance of the Elitist strategy).
-Asking random questions does not allow to reach a low regret level even after having asked 100 questions, whereas a low regret level ($\MMR$ = 1) is reached by Pessimistic before having asked 60 questions.
-We also see that Pessimistic performs slightly better than Extended pessimistic, showing that Pessimistic chooses candidate questions wisely; this is good news since (for $m = 5$ and $n = 10$), Pessimistic is much faster: it takes on average only $24$s for a complete elicitation session ($150$ questions), while Extended pessimistic takes $76$s.
+Our first experiment concerns small size situations.
+\Cref{fig:smallSize} compares some of our strategies in the case $m = 5, n = 10$ (variations around this size yield similar conclusions), where the results are averaged over $200$ runs.
+%(The figure also displays the performance of the Elitist strategy, to which we will come back.)
+We see that asking random questions does not allow to reach a low regret level even after having asked 100 questions, whereas a low regret level ($\MMR$ = 1) is reached by Pessimistic before having asked 60 questions.
+We also see that Pessimistic performs slightly better than Extended pessimistic, showing that Pessimistic chooses candidate questions wisely; this is good news since Pessimistic is much faster: it takes on average only $24$s for a complete elicitation session (for $m = 5$, $n = 10$ and $150$ questions), while Extended pessimistic takes $76$s.
 Notice that although they exhibit a close performance, Pessimistic performs %significantly %better, in the sense that the numbers are
-consistently better Pessimistic in the different runs of the experiment).
+consistently better than Extended pessimistic in the different runs of the experiment).
 \Cref{tab:biggerSize} shows that these conclusions also hold for a problem of larger size ($m = 10, n = 20$), except that this table does not feature Extended pessimistic, which is too slow to be ran repeatedly on such instance.
@@
 \end{table}
-While in previous experiments we compared Pessimistic to the other strategies, in this set of experiments, we focus %about the absolute quality of 
-on Pessimistic. 
-We %For practical usability,
-think that it is important to know how many questions should be asked in order to reach a low regret level.
+While in previous experiments we compared Pessimistic to the other strategies, in this set of experiments, we evaluate the Pessimistic strategy in absolute terms. 
+We first wonder how many questions should be asked in order to reach a low regret level.
 Here, we consider a low level to be a tenth of the number of agents ($n/10$): such a regret is equivalent to the difference of score of an alternative $x$ that results from switching from a profile $P$ to a profile $P'$ where ten percent of the agents rank $x$ last instead of first.
@@
 We next wonder how fast the regret decreases, measured as a function of the number of questions asked.
-This is important practically because it may be impossible or undesiderable to ask all questions necessary to reach low level of regrets, as computed in \cref{sec:lowRegret}.
+This is important practically because it may be impossible or undesirable to ask sufficient questions to reach a low regret level.
 Knowing the speed of decrease permits to know which trade-offs can be achieved between the quality of the resulting recommendation and the number of questions that participants have to answer.
@@
 
-%In this work, we advocate obtaining an approximate winner without determining completely the voting rule, or the profile.
-\Cref{sec:lowRegret} evaluates the number of questions per agent required to reach a low regret value.
-%In this section we want to explore to which extent it is possible to recommend without knowing the voting rule.
-One extreme, in our setting, consists in knowing only that the weights are convex, our basis hypothesis.
-The
-
-%contrast our approach to one that would obtain the full profile on the one hand, and determine the voting rule on the other hand.
-More precisely, we want to estimate the number of questions that would be required to elicit the complete profile.
-We focus on the profile because eliciting the weights to full precision would require infinitely many questions, with the questions we use.
-%Note that this may underestimate the number of questions required to determine completely the profile and the rule, as questions to the agents yield no information about the scoring vector.
-
-%To estimate this number, we draw one linear order randomly (with equiprobability over all possible linear orders) and assume the following querying process: given a partial ordering representing our knowledge so far of an agent preferences, we pick a question equiprobably among the remaining edges, and add the edge in the appropriate direction to our partial ordering.
-We count the average number of questions required to reach a complete ordering.
-The experiments so far considered strategies that, at each step, mix questions to the chair and to the agents.
-One may wonder what is lost in terms of regret by focusing on the Two Phase strategy that asks a bulk of question of one type first and then switches to the other type.
-%different proportions of questions to the chair and the agents.
+The experiments so far let the strategy target its questions unrestrictively, leaving open the possibility of questioning either the chair or an agent at each step.
+One may wonder what is lost in terms of regret by asking different proportions of questions to the chair and the agents.
 Such restrictions may be useful because of (partial) unavailability of the chair, or because the estimated cognitive costs may differ sensibly, as these types of questions differ in nature.
-Notice that there might be practical reasons (for example, the chair may be unavailable during part of the process) for restricting a question type to a specific part of the elicitation process.
-We are also interested in analyzing the performance of different proportions of question types, since  (notice that the estimated cognitive costs may differ sensibly, as these types of questions differ in nature).
-\Cref{tab:twoP400} shows the MMR value reached in a problem of size $m = 10, n = 20$ after $400$ questions, using the Two phases strategy, in the “ca” ({\em chair then agents}) and in the “ac” ({\em agents then chair}) variants, for different values of $q_{c}$, the number of questions to the chair;
-e.g. the former variant first asks $q_{c}$ questions to the chair and then $400-q_{c}$ to the agents. %, while the latter asks $400-q_{c}$ to the agents and then $q_{c}$ questions to the chair.
+\Cref{tab:twoP400} shows the MMR value reached in a problem of size $m = 10, n = 20$ after $400$ questions, using the Two phases strategy, in the “ca” (chair then agents) and in the “ac” (agents then chair) variants.
 These numbers are to be compared with the MMR value reached after 400 questions with the Pessimistic strategy (displayed in \cref{fig:linearity}), which is $0.62$.% ± $0.56$.
+The Pessimistic strategy asks on average $48$ questions to the chair in this setting.
 
 These numbers highlight that it is possible to obtain a good-quality recommendation while knowing only that the voting rule is a scoring rule and that the weights are convex, which is our basic hypothesis (corresponding to the line $q_c = 0$, where no question is asked to the chair).
-By contrast, the Pessimistic strategy (that interleaves the two types of questions) asks on average $48$ questions to the chair.
 

### 2020-10-10 minimax.tex
Let’s being slightly more verbose, as space remains

@@
 Define similarly $t_2$, $R^{\max}_2$ and $R^{\min}_2$ for a question $q_2$.
-We now must aggregate these values to determine the informative value of the question.
+We are now faced with the problem of aggregating these values on order to compare the informative values of the candidate questions.
 We adopt a pessimistic approach, reported to perform better than optimistic aggregation \citep{Cailloux2014}, although our experiments in this context suggested a weak impact of that choice on the performance of the strategy.
@@
 Such restrictions may be useful because of (partial) unavailability of the chair, or because the estimated cognitive costs may differ sensibly, as these types of questions differ in nature.
-\Cref{tab:twoP400} shows the MMR value reached in a problem of size $m = 10, n = 20$ after $400$ questions, using the Two phases strategy, in the “ca” (chair then agents) and in the “ac” (agents then chair) variants.
-These numbers are to be compared with the MMR value reached after 400 questions with the Pessimistic strategy (displayed in \cref{fig:linearity}), which is $0.62$.% ± $0.56$.
+\Cref{tab:twoP400} shows the MMR value reached in problems of size $m = 10, n = 20$ after $400$ questions, using the Two phases strategy, in the “ca” (chair then agents) and in the “ac” (agents then chair) variants.
+These numbers are to be compared with the MMR value reached after 400 questions with the Pessimistic strategy (displayed in \cref{fig:linearity}), which is $0.62$.
+% ± $0.56$.
 The Pessimistic strategy asks on average $48$ questions to the chair in this setting.

### 2020-10-10 minimax.tex
corrected estimation formula for n/10

@@
 	\label{tab:lowRegret}
-	\begin{tabular}{S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-number-alignment = center]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]}
+	\begin{tabular}{S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-number-alignment = center]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]}
 		\toprule
-		{m} & {n} & {$\frac{n}{10}$} & {$k_{\MMR}$} \\
+		{m} & {n} & {$\frac{n}{10}$} & {$k_{\MMR}$} & {$0.4 m^{1.6} n$}\\
 		\midrule
-		5 & 10 & 1.0 & 60 \\
-		5 & 15 & 1.5 & 80 \\
-		5 & 20 & 2.0 & 110 \\
-		10 & 20 & 2.0 & 340 \\
-		10 & 30 & 3.0 & 527 \\
-		15 & 30 & 3.0 & 812 \\
+		5 & 10 & 1.0 & 60 & 53\\
+		5 & 15 & 1.5 & 80 & 79\\
+		5 & 20 & 2.0 & 110 & 105\\
+		10 & 20 & 2.0 & 340 & 318\\
+		10 & 30 & 3.0 & 527 & 479 \\
+		15 & 30 & 3.0 & 951 & 914\\
 		\bottomrule		

### 2020-10-10 minimax.tex
Solved warnings; aligned and rounded numbers

--- 2020-10-10 minimax.tex
@@
 	\label{fig:smallSize}
+	\Description{Graph showing that Pessimistic performs slightly better than Extended pessimistic, itself performing better than Elitist, itself performing much better than Random.}
 	\includegraphics[width=.45\textwidth]{comparison.png}
 \end{figure}
+\sisetup{table-number-alignment = center, table-figures-integer=2, table-figures-decimal=1, table-auto-round}
 \begin{table}
@@
 	\label{tab:biggerSize}
-	\begin{tabular}{S[table-figures-integer=3, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
+	\begin{tabular}{S[table-figures-integer=3, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=1]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=1]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=1]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
 		\toprule
@@
 	\label{tab:geometricWeights}
-	\begin{tabular}{S[table-figures-integer=3, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
+	\begin{tabular}{S[table-figures-integer=3, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=1]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=1]}
 		\toprule
@@
 	\label{tab:lowRegret}
-	\begin{tabular}{S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-number-alignment = center]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]}
+	\begin{tabular}{S[table-figures-decimal=0]S[table-figures-decimal=0]SS[table-figures-integer=3, table-figures-decimal=0]}
 		\toprule
@@
 		\midrule
-		5 & 10 & 1.0 & 60 \\
+		5 & 10 & 1 & 60 \\
 		5 & 15 & 1.5 & 80 \\
-		5 & 20 & 2.0 & 110 \\
-		10 & 20 & 2.0 & 340 \\
-		10 & 30 & 3.0 & 527 \\
-		15 & 30 & 3.0 & 812 \\
+		5 & 20 & 2 & 110 \\
+		10 & 20 & 2 & 340 \\
+		10 & 30 & 3 & 527 \\
+		15 & 30 & 3 & 812 \\
 		\bottomrule
@@
 	\label{tab:fullProfile}
-	\begin{tabular}{S[table-figures-integer=2, table-number-alignment = center, table-figures-decimal=0]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=2]}
+	\begin{tabular}{S[table-figures-decimal=0]S}
 		\toprule
-		m & k \\
+		{m} & {k} \\
 		\midrule
@@
 	\label{fig:linearity}
+	\Description{Graph showing that the MMR decreases very approximately linearly, and is convex, as a function of the number of questions.}
 	\includegraphics[width=.45\textwidth]{linearity.png}
@@
 	\label{tab:twoP400}
-	\begin{tabular}{S[table-figures-integer=3, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
+	\begin{tabular}{S[table-figures-integer=3, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=1]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=1]}
 		\toprule
@@
 		350 &15.06 & 0.68&15.59 & 0.6 \\
-		400 &20.0 & 0.0 & 20.0 & 20.0 \\
+		400 &20.0 & 0.0 & 20.0 & 0.0 \\
 		\bottomrule
@@
 \Cref{tab:twoP400} shows the MMR value reached in problems of size $m = 10, n = 20$ after $400$ questions, using the Two phases strategy, in the “ca” (chair then agents) and in the “ac” (agents then chair) variants.
-These numbers are to be compared with the MMR value reached after 400 questions with the Pessimistic strategy (displayed in \cref{fig:linearity}), which is $0.62$.
-% ± $0.56$.
+These numbers are to be compared with the MMR value reached after 400 questions with the Pessimistic strategy (displayed in \cref{fig:linearity}), which is $0.6$.
 The Pessimistic strategy asks on average $48$ questions to the chair in this setting.

### 2020-10-10 minimax.tex
Changed my mind about CCS (and no more warnings)
Moved stuff around for better float display; rm balance

@@
 \usepackage{algorithm, algpseudocode}
-
-\usepackage{balance} % for balancing columns on the final page
 
@@
 \end{abstract}
+
+%%% The code below was generated by the tool at http://dl.acm.org/ccs.cfm.
+%%% Please replace this example with code appropriate for your own paper.
+%NB Olivier: suppresses the warning.
+\settopmatter{printccs=false}
+\ccsdesc[500]{Computing methodologies~Knowledge representation and reasoning}
 
@@
 \end{table}
+
+While in previous experiments we compared Pessimistic to the other strategies, in this set of experiments, we evaluate the Pessimistic strategy in absolute terms. 
+We first wonder how many questions should be asked in order to reach a low regret level.
+Here, we consider a low level to be a tenth of the number of agents ($n/10$): such a regret is equivalent to the difference of score of an alternative $x$ that results from switching from a profile $P$ to a profile $P'$ where ten percent of the agents rank $x$ last instead of first.
+The results for various sizes are displayed in \cref{tab:lowRegret}. 
+We see that the number of questions required to reach a low regret level grows approximately linearly with the number of agents and grows less fast than the square of the number of alternatives, for the sizes we considered.
+Averaging these data by category of value for $m$, and assuming no questions get asked to the chair, in order to to reach a low regret level, each agent will have to answer $5.6$ questions for $m = 5$, $17.2$ questions for $m = 10$ and $27.1$ questions for $m = 15$.
+These numbers have to be contrasted with those displayed in \cref{tab:fullProfile}, that estimate the number of questions required to elicit the full preference of an agent.
+To obtain the data for this table, we constrained the Pessimistic strategy to ask questions to the agents only, and ran it on a single agent problem, with various values for $m$.
+
 \begin{table}
@@
 \end{table}
-While in previous experiments we compared Pessimistic to the other strategies, in this set of experiments, we evaluate the Pessimistic strategy in absolute terms. 
-We first wonder how many questions should be asked in order to reach a low regret level.
-Here, we consider a low level to be a tenth of the number of agents ($n/10$): such a regret is equivalent to the difference of score of an alternative $x$ that results from switching from a profile $P$ to a profile $P'$ where ten percent of the agents rank $x$ last instead of first.
-The results for various sizes are displayed in \cref{tab:lowRegret}. 
-We see that the number of questions required to reach a low regret level grows approximately linearly with the number of agents and grows less fast than the square of the number of alternatives, for the sizes we considered.
-Averaging these data by category of value for $m$, and assuming no questions get asked to the chair, in order to to reach a low regret level, each agent will have to answer $5.6$ questions for $m = 5$, $17.2$ questions for $m = 10$ and $27.1$ questions for $m = 15$.
-These numbers have to be contrasted with those displayed in \cref{tab:fullProfile}, that estimate the number of questions required to elicit the full preference of an agent.
-To obtain the data for this table, we constrained the Pessimistic strategy to ask questions to the agents only, and ran it on a single agent problem, with various values for $m$.
 
@@
 \paragraph{Decrease in MMR values}
-%TODO balance columns appropriately before submitting
-\balance
 \begin{figure}
@@
 \paragraph{Comparison with Two Phase}
-
 \begin{table}

### 2020-10-10 minimax.tex
restored table n/10 and changed the time for 100 questions

--- 2020-10-10 minimax.tex
@@
 %\begin{enumerate}
-%	\item Reach regret: $n/10$. For this, we need $m^x n$ questions. Wait for more runs (Correct formula)
-%Graphs: order symbols in the legend. Reduce number of marks on the X axis.
+%	\item Reach regret: $n/10$. Add considerations.
+%Graphs: Reduce number of marks on the X axis.
 %MMR and sd with systematically one decimal exactly
-%$150$ questions?
 %Pessimistic systematically better than XPess?
@@
 We see that asking random questions does not allow to reach a low regret level even after having asked 100 questions, whereas a low regret level ($\MMR$ = 1) is reached by Pessimistic before having asked 60 questions.
-We also see that Pessimistic performs slightly better than Extended pessimistic, showing that Pessimistic chooses candidate questions wisely; this is good news since Pessimistic is much faster: it takes on average only $24$s for a complete elicitation session (for $m = 5$, $n = 10$ and $150$ questions), while Extended pessimistic takes $76$s.
+We also see that Pessimistic performs slightly better than Extended pessimistic, showing that Pessimistic chooses candidate questions wisely; this is good news since Pessimistic is much faster: it takes on average only $16$s for a complete elicitation session (for $m = 5$, $n = 10$ and $100$ questions), while Extended pessimistic takes $50$s.
 Notice that although they exhibit a close performance, Pessimistic performs %significantly %better, in the sense that the numbers are
@@
 	\label{tab:lowRegret}
-	\begin{tabular}{S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-number-alignment = center]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]}
+	\begin{tabular}{S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-number-alignment = center]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]}
 		\toprule
-		{m} & {n} & {$\frac{n}{10}$} & {$k_{\MMR}$} & {$0.4 m^{1.6} n$}\\
+		{m} & {n} & {$\frac{n}{10}$} & {$k_{\MMR}$} \\
 		\midrule
-		5 & 10 & 1.0 & 60 & 53\\
-		5 & 15 & 1.5 & 80 & 79\\
-		5 & 20 & 2.0 & 110 & 105\\
-		10 & 20 & 2.0 & 340 & 318\\
-		10 & 30 & 3.0 & 527 & 479 \\
-		15 & 30 & 3.0 & 951 & 914\\
+		5 & 10 & 1.0 & 60 \\
+		5 & 15 & 1.5 & 80 \\
+		5 & 20 & 2.0 & 110 \\
+		10 & 20 & 2.0 & 340 \\
+		10 & 30 & 3.0 & 527 \\
+		15 & 30 & 3.0 & 951 \\
 		\bottomrule		

### 2020-10-10 minimax.tex

--- 2020-10-10 minimax.tex
@@
 		10 & 30 & 3 & 527 \\
-		15 & 30 & 3 & 812 \\
+		15 & 30 & 3 & 951 \\
 		\bottomrule

### 2020-10-10 minimax.tex
Less redundancies

--- 2020-10-10 minimax.tex
@@
 We also provide an interactive elicitation protocol based on minimax regret and develop several query strategies that question the chair and the agents in order to acquire the most relevant information for quickly converging to a near-optimal alternative.
-Finally, we find out experimentally that questioning agents is more useful than questioning the chair in our setting.
+Finally, we study these strategies experimentally in order to validate our approach and obtain practical guidelines.
 \end{abstract}
@@
 Requiring agents to express full preference orderings can be prohibitively costly (in terms of cognitive and communication cost).
-This observation has motivated a number of recent works considering social choice with partial preference orders \citep{Xia2008, Pini2009, Konczak05} and incremental elicitation \citep{Kalech2011, Lu2011, Naamani-Dery2015,Benabbou2016} of agent preferences.
-\\
+This observation has motivated a number of recent works considering social choice with partial preference orders and incremental elicitation of agent preferences. 
 Furthermore, it is often difficult for non-expert users to formalize a voting rule on the basis of some generic preferences over a desired aggregation method.
@@
 The paper is organized as follows. \Cref{sec:related} reviews the works related to our objective.
-In Section \ref{sec:background} we provide the necessary background and in Section \ref{sec:mmr} we introduce the minimax criterion, a method that selects a winner that minimizes the worst possible regret.
-Then, in Section \ref{sec:elicit} we provide an interactive elicitation protocol based on minimal regret;  in Section \ref{sec:experiments} we present the empirical validation of our approach with simulations; and Section \ref{sec:conclusions} provides some final thoughts.
+\Cref{sec:background} provides the necessary background and \cref{sec:mmr} introduces the minimax criterion, a method that selects a winner that minimizes the worst possible regret.
+In Section \ref{sec:elicit} we provide an interactive elicitation protocol based on minimal regret;  Section \ref{sec:experiments} presents the experiments validation of our approach and the guidelines stemming from these simulations; and Section \ref{sec:conclusions} provides some final thoughts.
 
@@
 
-\Citet{Konczak05} were the first to consider the problem of computing, for various voting rules, possible and necessary winners in the case of partial knowledge of agent preferences and showed that the problem is hard in the general case.
+\Citet{Konczak05} studied the computation of possible and necessary winners in the case of partial knowledge of agent preferences, for various voting rules, and showed that the problem is hard in the general case.
 This work was then extended by \citet{Xia2008} that showed that, while the identification of a necessary co-winner in scoring rules is polynomial,  the determination of possible co-winners is NP-hard; they also  proposed polynomial-time algorithms when using maximin and Bucklin.
@@
 
-More recently \citet{Llamazares2013} and \citet{Viappiani2018} %(among others \commentOC{Which others?}) 
-considered the problem of dealing with unspecified weights in positional scoring rules; the first proposed a method based on Data Envelopment Analysis (DEA), while the second proposed to aggregate the uncertainty in weights using criteria used in decision-making under uncertainty (such as minimax regret).
-The work of \citet{Cailloux2014} deals with the problem of eliciting a generic voting rule.
+More recent articles considered the problem of dealing with unspecified weights in positional scoring rules: \citet{Llamazares2013} proposed a method based on Data Envelopment Analysis (DEA), while \citet{Viappiani2018} proposed to aggregate the uncertainty in weights using criteria used in decision-making under uncertainty (such as minimax regret).
+\Citet{Cailloux2014} are interested in elicitation of a different class of rules.
 
-Finally we also mention works related to the manipulability of voting rules %have been proposed in this context 
-\citep{Elkind2012,Dey2018,Dey2018_2,Conitzer2011}, and work concerning strategic behaviors, when agents learn incrementally about other agent preferences \citep{Endriss2016,Lev2019,Annemieke2012}.
+Finally, we mention works related to the manipulability of voting rules \citep{Elkind2012,Dey2018,Dey2018_2,Conitzer2011}, and studies of strategic behaviors, when agents learn incrementally about other agent preferences \citep{Endriss2016,Lev2019,Annemieke2012}.
 
@@
 %Pessimistic systematically better than XPess?
+%Page numbers
+%reflexive?
 %\end{enumerate}

### 2020-10-10 minimax.tex
Rm some TODOs done.
Page numbers
Wording intro

@@
 \fancyhead{}
+\setlength{\footskip}{1.6cm}
+\cfoot{\thepage}
 
@@
 \Cref{sec:background} provides the necessary background and \cref{sec:mmr} introduces the minimax criterion, a method that selects a winner that minimizes the worst possible regret.
-In Section \ref{sec:elicit} we provide an interactive elicitation protocol based on minimal regret;  Section \ref{sec:experiments} presents the experiments validation of our approach and the guidelines stemming from these simulations; and Section \ref{sec:conclusions} provides some final thoughts.
+In Section \ref{sec:elicit} we provide an interactive elicitation protocol based on minimal regret;  Section \ref{sec:experiments} presents an experimental validation of our approach and some guidelines stemming from these simulations; and Section \ref{sec:conclusions} provides some final thoughts.
 
@@
 %	\item Reach regret: $n/10$. Add considerations.
-%Graphs: Reduce number of marks on the X axis.
 %MMR and sd with systematically one decimal exactly
-%Pessimistic systematically better than XPess?
 %Page numbers
-%reflexive?
 %\end{enumerate}

### 2020-10-10 minimax.tex
Further wording bugs

@@
 We start by describing the general protocol of experimentation. %use the following protocol, deviations are indicated below for each experiment.
-Having picked a problem size $(m, n)$, a number of questions $k$ and a strategy to test, we randomly generate an “oracle”, containing the true preferences of the agents (i.e.
+Having picked a problem size $(m, n)$, a number of questions $k$ and a strategy to test, we randomly generate an “oracle”, representing the true preferences of the agents (i.e.
 the linear orders) and the weights associated with the chair's scoring rule.
@@
 We see that the number of questions required to reach a low regret level grows approximately linearly with the number of agents and grows less fast than the square of the number of alternatives, for the sizes we considered.
-Averaging these data by category of value for $m$, and assuming no questions get asked to the chair, in order to to reach a low regret level, each agent will have to answer $5.6$ questions for $m = 5$, $17.2$ questions for $m = 10$ and $27.1$ questions for $m = 15$.
+Averaging these data by category of value for $m$, and assuming no questions get asked to the chair, we see that in order to reach a low regret level, each agent will have to answer $5.6$ questions for $m = 5$, $17.2$ questions for $m = 10$ and $27.1$ questions for $m = 15$.
 These numbers have to be contrasted with those displayed in \cref{tab:fullProfile}, that estimate the number of questions required to elicit the full preference of an agent.
@@
 We see that this function is convex, apart from the very first few questions, indicating %to users of our approach
-that, on average, halving the number of questions will reduce the reduction in regret by less than half.% do less harm than halving the gain in regret, on average.
+that, on average, halving the number of questions will only reduce the gain in regret by less than half.% do less harm than halving the gain in regret, on average.
 

### 2020-10-10 minimax.tex
Consistently

@@
 We also see that Pessimistic performs slightly better than Extended pessimistic, showing that Pessimistic chooses candidate questions wisely; this is good news since Pessimistic is much faster: it takes on average only $16$s for a complete elicitation session (for $m = 5$, $n = 10$ and $100$ questions), while Extended pessimistic takes $50$s.
-Notice that although they exhibit a close performance, Pessimistic performs %significantly %better, in the sense that the numbers are
-consistently better than Extended pessimistic in the different runs of the experiment).
+Notice that although they exhibit a close performance, Pessimistic performs consistently better, in the sense that the numbers are systematically in favor of Extended pessimistic when performing the experiment again.
 \Cref{tab:biggerSize} shows that these conclusions also hold for a problem of larger size ($m = 10, n = 20$), except that this table does not feature Extended pessimistic, which is too slow to be ran repeatedly on such instance.

### 2020-12-04 minimax.tex
add lines table 2
changes completed before changing to IJCAI format

@@
 \usepackage{anyfontsize}
-\usepackage{mathrsfs}
+\usepackage{mathrsfs,stmaryrd}
 %\input{preamble/redac}
@@
 Our approach permits to compare experimentally strategies that question the chair, the agents, or both.
+
+A concrete application of our work might be a committee that is about to hire a new employee, whose performances are evaluated by several experts.
+The members of the committee may not have a voting rule in mind at the start of the process, and might not wish to agree on a specific voting rule, but they might be willing to answer enough questions about selecting winners out of specific profiles to determine their employee of choice.
+
 We describe informally here a few of the conclusions stemming from these experiments, given a problem involving $m$ alternatives and $n$ agents.
@@
 \Citet{Konczak05} studied the computation of possible and necessary winners in the case of partial knowledge of agent preferences, for various voting rules, and showed that the problem is hard in the general case.
-This work was then extended by \citet{Xia2008} that showed that, while the identification of a necessary co-winner in scoring rules is polynomial,  the determination of possible co-winners is NP-hard; they also  proposed polynomial-time algorithms when using maximin and Bucklin.
+This work was then extended by \citet{Xia2008} who showed that, while the identification of a necessary co-winner in scoring rules is polynomial,  the determination of possible co-winners is NP-hard; they also  proposed polynomial-time algorithms when using maximin and Bucklin.
 In other papers it was showed that the general case remains computationally hard even when restricting to single-peaked preferences \citep{Walsh2007};  sufficient conditions that ensure tractability were then found \citep{Pini2007}.
@@
 
-Finally, we mention works related to the manipulability of voting rules \citep{Elkind2012,Dey2018,Dey2018_2,Conitzer2011}, and studies of strategic behaviors, when agents learn incrementally about other agent preferences \citep{Endriss2016,Lev2019,Annemieke2012}.
+Finally, we mention works related to the manipulability of voting rules \citep{Elkind2012,Dey2018,Dey2018_2,Conitzer2011,Baumeister2019}, and studies of strategic behaviors, when agents learn incrementally about other agent preferences \citep{Endriss2016,Lev2019,Annemieke2012}.
 
@@
 The constraint above is often used when aggregating rankings in sport competitions.
-We use $\W$ to denote the set of convex weight vectors.
+We use $\W$ to denote the set of convex weight vectors. It is also a natural and common assumption: losing ranks at the top of the ranking is more damaging than losing ranks at the bottom.
 
@@
 
-Notice that often there are no necessary winner and too many possible winners; it is therefore useful to declare a winner given partial information.
+Notice that often there are no necessary winners and too many possible winners; it is therefore useful to declare a winner given partial information.
 As a decision criterion to determine a winner, we propose to use minimax regret. 
@@
 Observe that, whenever the $\PMR$ of an alternative $x$ (against some other alternative $y$) exceeds the best MR value found so far, we do not need to further evaluate $x$. 
-This idea can be exploited further by adopting a minimax-search tree \citep{Braziunas2011}.
+This idea can be exploited further by adopting a minimax-search tree \citep{Braziunas2012}.
 
@@
 This permits to test how the chair understands the question and to relate the preference of the chair to her choice behavior in the economic sense.
+
+Such questions have precise semantics whose understanding is shared by the chair.
+This way of asking questions is sufficiently natural that it has been used in experimental settings investigating the feeling of justice of individuals \citep{Giritligil2005}.
+To the best of our knowledge, the use of such questions to systematically guide an elicitation process is novel.
+
+Our approach is analogous to that of decision theorists with preference elicitation: a large stream of research considers more meaningful to ask direct choice questions ("please choose either a or b") than to question the decision maker about the shape of its utility function.
+The former are considered "observable": acts of choice are translated to preference statements.
+
 Furthermore this will be necessary for an ordinal extension of our work where the scores would not be considered as cardinal utilities.
@@
 	First build a temporary profile $P$ of $p+q$ agents with $a$ and $b$ ranked as just described.
-Complete it with $m-2$ alternatives ranked in arbitrary orders so that the resulting profile has complete strict rankings for each of the $p+q$ agent.
+Complete it with $m-2$ alternatives ranked in arbitrary orders so that the resulting profile has complete strict rankings for each of the $p+q$ agents.
 Now we will make the other alternatives as bad as desired by adding agents to $P$ that appreciate $a$ and $b$ more than the other alternatives, thus building a profile $P'$ in which, whatever the weights, $c$ may not have a better score than $a$.
@@
 	We can prove that, for $\delta = p+q$, and whatever the weight vector $\w \in \W$, no alternative, except possibly $b$, has a better score than $a$. 
-	(In fact, as the construction will exhibit, they are all worst than both $a$ and $b$, but the weaker fact is enough for our claim.)
+	(In fact, as the construction will exhibit, they are all worse than both $a$ and $b$, but the weaker fact is enough for our claim.)
 	Pick any alternative $c$ that is not $a$ or $b$. 
@@
 To obtain upper bounds for $c'_t$, assume $c$ is ranked first by the $p+q$ agents in $P$.
-By our construction, the  $2 \delta$ new agents of $P'$ give to $c$ the ranks $(3, m)$, or $(4, m-1)$, … Observe that the score of $c$ is maximal for attribution $(3, m)$, by convexity of the weights.
+By our construction, the  $2 \delta$ new agents of $P'$ give to $c$ the ranks $3$ and $m$, or $4$ and $m-1$, … Observe that the score of $c$ is maximal for attribution $(3, m)$, by convexity of the weights.
 Therefore, in the best case for $c$, $c'_1 ≤ p + q, c'_2 ≤ p+q, c'_t ≤ p+q+\delta \text{ for } 3 ≤ t < m, c'_m ≤ p+q+2\delta$.
@@
 If it opted for a question about weights, it draws one rank in $1 ≤ r ≤ m-2$ equiprobably, takes the middle of the interval of values for $\lambda$ that are still possible considering our knowledge so far, and asks whether $w_r - w_{r+1} ≥ \lambda (w_{r+1} - w_{r+2})$.
-The intervals are initialized to $[1, n]$.
+The intervals are initialized to $[1, n]$: $\lambda≥1$ by convexity and we assume $\lambda≤n$ wlog, in fact for $\lambda≥n$, the rule coincides with Plurality.
 If it opted for a question to agents, it draws equiprobably among the agents whose preference is not known entirely; draws an alternative $a$ equiprobably among those involved in some incomparabilities in $\ppref_j$; and draws an alternative $b$ equiprobably among those incomparable with $a$ in $\ppref_j$.
@@
 Define similarly $t_2$, $R^{\max}_2$ and $R^{\min}_2$ for a question $q_2$.
-We are now faced with the problem of aggregating these values on order to compare the informative values of the candidate questions.
+We are now faced with the problem of aggregating these values in order to compare the informative values of the candidate questions.
 We adopt a pessimistic approach, reported to perform better than optimistic aggregation \citep{Cailloux2014}, although our experiments in this context suggested a weak impact of that choice on the performance of the strategy.
@@
 After having asked $n (m-1)$ questions to the agents, it questions the chair only, using the same approach as the Pessimistic strategy.
-This strategy can be expected to perform well when the chair assigns an important weight to the first rank, as compared to the other ranks.
+This strategy can be expected to perform well when the chair assigns a large weight to the first rank, as compared to the other ranks.
 It will be useful to further challenge the Pessimistic strategy, which is not specifically tailored to such a situation.
@@
 The preferences are generated following an impartial culture assumption: the linear order of each agent is generated independently from the other ones and all have the same probability of appearing.
-For generating the weights we first draw $m - 1$ numbers uniformly at random (representing weight ``differences''), normalize and sort them; 
+IC is a quite challenging situation: as can be expected intuitively (and shown experimentally by \citet{Lu2011} in their setting), the number of questions to be asked decrease with less varied profiles.
+We want to focus on the most critical setting, as there is a wide variety of possible situations to test in such experiments.
+For generating the weights we first draw $m - 1$ numbers uniformly at random (in the interval $\intvl{0,1}$ representing weight ``differences''), normalize and sort them; 
 a sequence of convex decreasing weight is then obtained by a decumulative sum.
@@
 We repeat this whole experiment a variable number of times indicated below, for a given $(m, n, k)$, and report the average resulting MMR and the standard deviation \textit{sd}.
+The sizes of the considered scenarios are comparable to the ones used by \citet{Cailloux2014}.
 
@@
 		0	&20.0	&0.0	&20.0	&0.0\\
+		50	&15.96	&0.54	&17.26	&0.42\\
 		100	&12.48	&0.93	&15.6	&0.43\\
+		150	&9.58	&1.37	&13.94	&0.76\\
 		200	&7.43	&1.25	&10.95	&1.12\\
+		250	&5.26	&1.52	&6.6	&0.79\\
 		300	&3.47	&1.32	&6.57	&0.79\\
@@
 Notice that although they exhibit a close performance, Pessimistic performs consistently better, in the sense that the numbers are systematically in favor of Extended pessimistic when performing the experiment again.
-\Cref{tab:biggerSize} shows that these conclusions also hold for a problem of larger size ($m = 10, n = 20$), except that this table does not feature Extended pessimistic, which is too slow to be ran repeatedly on such instance.
+\Cref{tab:biggerSize} shows that these conclusions also hold for a problem of larger size ($m = 10, n = 20$), except that this table does not feature Extended pessimistic, which is too slow to be run repeatedly on such instance.
 
@@
 %\subsection{Absolute evaluation of Pessimistic strategy}
-\paragraph{In-dept evaluation of Pessimistic}
+\paragraph{In-depth evaluation of Pessimistic}
 \label{sec:lowRegret}
@@
 We see that this function is convex, apart from the very first few questions, indicating %to users of our approach
-that, on average, halving the number of questions will only reduce the gain in regret by less than half.% do less harm than halving the gain in regret, on average.
+that, on average, halving the number of questions will only reduce the gain in regret by less than half.
+
+At the start of the elicitation, the space of uncertainty is so large that the adversary can attain the maximum possible value of regret; multiple answers are needed to constrain her enough for the MMR to start decreasing.
+When approaching optimality, the pace of MMR reduction decreases.
+
+% do less harm than halving the gain in regret, on average.
 
@@
 Our experimental results %on randomly generated and real world data sets 
-suggest that regret-based elicitation is effective and allow to quickly reduce worst regret significantly.
+suggest that regret-based elicitation is effective and allows to quickly reduce worst-case regret significantly.
 They also show that good quality (low regret) recommendations can be achieved short of knowing the weights precisely or the profile completely, in our setting.

### 2020-12-04 minimax.tex
IJCAI format (some warnings)

@@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\documentclass{article}
+\pdfpagewidth=8.5in
+\pdfpageheight=11in
+% The file ijcai21.sty is NOT the same than previous years'
+\usepackage{ijcai21}
+\usepackage{times}
+\usepackage{soul}
 
-%%% LaTeX Template for AAMAS-2021 (based on sample-sigconf.tex)
-%%% Prepared by Natasha Alechina and Ulle Endriss (version 2020-08-06)
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%% Start your document with the \documentclass command.
-%%% Use the first variant below for the final paper.
-%%% Use the second variant below for submission.
-
-\PassOptionsToPackage{hypertexnames=false, pdfusetitle, linkbordercolor={1 1 1}, citebordercolor={1 1 1}, urlbordercolor={1 1 1}}{hyperref}
-%\documentclass[sigconf]{aamas} 
-\documentclass[sigconf, anonymous]{aamas}
+\usepackage[hidelinks]{hyperref}
 
@@
 \usepackage{algorithm, algpseudocode}
+\usepackage{booktabs}
 
@@
 
-%TODO remove this before submission, check vboxes
-\vbadness=10000
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%% AAMAS-2021 copyright block (do not change!)
-
-\setcopyright{ifaamas} 
-\acmConference[AAMAS '21]{Proc.\@ of the 20th International Conference on Autonomous Agents and Multiagent Systems (AAMAS 2021)}{May 3--7, 2021}{London, UK}{U.~Endriss, A.~Now\'{e}, F.~Dignum, A.~Lomuscio (eds.)}
-\copyrightyear{2021}
-\acmYear{2021}
-\acmDOI{}
-\acmPrice{}
-\acmISBN{}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%% Use this command to specify your EasyChair submission number.
-%%% In anonymous mode, it will be printed on the first page.
-
-\acmSubmissionID{554}
+\pdfinfo{
+	/TemplateVersion (IJCAI.2021.0)
+}
 
@@
 
-\author{Beatrice Napolitano}
-\affiliation{
-	\institution{Université Paris-Dauphine, Université PSL, CNRS, LAMSADE}
-	\city{75016 Paris}
-	\state{France}}
-\email{beatrice.napolitano@dauphine.fr}
+\author{
+	Beatrice Napolitano$^1$\footnote{Contact Author}\and
+	Olivier Cailloux$^1$\and
+	Paolo Viappiani$^2$\\
+	\affiliations
+	$^1$Université Paris-Dauphine, Université PSL, CNRS, LAMSADE\\
+	$^2$LIP6, UMR 7606, CNRS and Sorbonne Universit\'e\\
+	\emails
+	\{beatrice.napolitano, olivier.cailloux\}@dauphine.fr,
+	paolo.viappiani@lip6.fr
+}
 
-\author{Olivier Cailloux}
-\affiliation{
-	\institution{Université Paris-Dauphine, Université PSL, CNRS, LAMSADE}
-	\city{75016 Paris}
-	\state{France}}
-\email{olivier.cailloux@dauphine.fr}
+\newcommand{\BibTeX}{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em\TeX}
 
-\author{Paolo Viappiani}
-\affiliation{
-	\institution{LIP6, UMR 7606, CNRS and Sorbonne Universit\'e}
-	\city{Paris}
-	\state{France}}
-\email{paolo.viappiani@lip6.fr}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-%%% Use this environment to specify a short abstract for your paper.
+\begin{document}
+
+\maketitle
 
@@
 \end{abstract}
-
-%%% The code below was generated by the tool at http://dl.acm.org/ccs.cfm.
-%%% Please replace this example with code appropriate for your own paper.
-%NB Olivier: suppresses the warning.
-\settopmatter{printccs=false}
-\ccsdesc[500]{Computing methodologies~Knowledge representation and reasoning}
-
-\keywords{Uncertainty in AI, Computational Social Choice, Preference Elicitation}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%% Include any author-defined commands here.
-
-\newcommand{\BibTeX}{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em\TeX}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{document}
-
-%%% The following commands remove the headers in your paper. For final 
-%%% papers, these will be inserted during the pagination process.
-
-\pagestyle{fancy}
-\fancyhead{}
-\setlength{\footskip}{1.6cm}
-\cfoot{\thepage}
-
-%%% The next command prints the information defined in the preamble.
-
-\maketitle
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 	\label{fig:smallSize}
-	\Description{Graph showing that Pessimistic performs slightly better than Extended pessimistic, itself performing better than Elitist, itself performing much better than Random.}
+%	\Description{Graph showing that Pessimistic performs slightly better than Extended pessimistic, itself performing better than Elitist, itself performing much better than Random.}
 	\includegraphics[width=.45\textwidth]{comparison.png}
@@
 	\label{fig:linearity}
-	\Description{Graph showing that the MMR decreases very approximately linearly, and is convex, as a function of the number of questions.}
+	%\Description{Graph showing that the MMR decreases very approximately linearly, and is convex, as a function of the number of questions.}
 	\includegraphics[width=.45\textwidth]{linearity.png}
@@
 
-\bibliographystyle{ACM-Reference-Format} 
-%TODO remove this when submitting, and consider solving the vertical overflows
-\vfuzz=5pt
+\bibliographystyle{named}
 \bibliography{biblio}

### 2020-12-09 minimax.tex
Some LaTeX corr
Corr overfull boxes
Proof using profile to question the chair (and a typo)

@@
 \input{preamble/packages}
-%TODO consider removing anyfontsize and mathrsfs when submitting.
-They are needed for the \mathscr command at Olivier’s box (probably due to some outdated package) and for removing a warning about rsfs font size.
-\usepackage{anyfontsize}
-\usepackage{mathrsfs,stmaryrd}
-%\input{preamble/redac}
-%\input{preamble/math_basics}
 \input{preamble/math}
@@
 }
+
+%I find these settings useful in draft mode. Should be removed for final versions.
+	%Which line breaks are chosen: accept worse lines, therefore reducing risk of overfull lines. Default = 200.
+		\tolerance=2000
+	%Accept overfull hbox up to...
+		\hfuzz=2cm
+	%Reduces verbosity about the bad line breaks.
+		\hbadness 5000
+	%Reduces verbosity about the underful vboxes.
+		\vbadness=6000
 
@@
 \end{claim}
-\begin{proof}[Sketch of proof]
+\begin{proof}[Sketch]
 	Consider our knowledge $\pprefeq_j$ about the preference of the agent $j$. 
@@
 		\PMR(x,y; \pprofile, W)  
-		& = \max_{w \in W} \sum_{j=1}^n w_{\hat{v}_j(y)} - w_{\hat{v}_j(x)} = \\ 
+		& = \max_{w \in W} \sum_{j=1}^n w_{\hat{v}_j(y)} - w_{\hat{v}_j(x)} \\ 
 		& = \max_{w \in W} \sum_{r=1}^m (\hat{\alpha}_{r}^{y} - \hat{\alpha}_{r}^{x}) w_i. 
@@
 \begin{claim}
-	Given a rational $\lambda = p/q$ and a rank $r$ between $1$ and $m - 2$, the profile named $P'$ in the ensuing description is such that, for any weight vector $\w \in \W$, $a \in f(P')$ iff $w_{r} - w_{r+1} ≥ \lambda (w_{r+1} - w_{r+2})$ and $b \in f(P')$ iff $w_{r} - w_{r+1} ≤ \lambda (w_{r+1} - w_{r+2})$, where $f$ is the PSR parameterized with $\w$.
+	Given a rational $\lambda = p/q > 1$ and a rank $r$ between $1$ and $m - 2$, there exists a profile $P$ such that, for any weight vector $\w \in \W$, $a \in f(P)$ iff $w_{r} - w_{r+1} ≥ \lambda (w_{r+1} - w_{r+2})$ and $b \in f(P)$ iff $w_{r} - w_{r+1} ≤ \lambda (w_{r+1} - w_{r+2})$, where $f$ is the PSR parameterized with $\w$.
 \end{claim}
 \begin{proof}
-	Observe that the question may be defined equivalently as $q \cdot w_{r} + p \cdot w_{r+2} ≥ (p + q) \cdot w_{r+1}$, where $p, q$ are natural numbers. 
-	As a first attempt to make this question concrete, we could define a profile $P$ containing $p+q$ agents in such a way that an alternative $a$ receives $q$ times the rank $r$ and $p$ times the rank $r+2$, and an alternative $b$ receives $p+q$ times the rank $r+1$.
-	Observing that the score of $a$ in that profile is exactly the left hand side of the question, and that the score of $b$ is the right hand side, intuition suggests that observing whether the chair picks $a$ or $b$ as winner will let us determine which side is greater; equality occurring when the chair declares $a$ and $b$ as tied for the victory.
-	However, we still need to complete the profile, thus, come up with other $m-2$ alternatives defined so that each agent in the resulting profile has placed exactly one alternative in each rank.
-	And we must ensure, doing this, that these other alternatives are not better than $a$ or $b$: if the chair picks a different alternative $c$, it tells us that the chair prefers $c$ to both $a$ and $b$,
-	but it generally does not  answer the question we are interested in. 
-	Taking $p = q = 1$, $m=4$, $r=2$, we see that such a completion may be impossible. Luckily, this problem can be worked around, at the price of increasing the number of agents.
+	Define a linear order $>_1$ over $A$ as placing $a$ at rank $r$, $b$ at rank $r + 1$, and the remaining alternatives arbitrarily. 
+	Define a linear order $>_2$ over $A$ as placing $a$ at rank $r + 2$, $b$ at rank $r + 1$, and the remaining alternatives arbitrarily.
+	Define an arbitrary linear ordering $>$ over $A \setminus \set{a, b}$. 
+	Define a linear order $>_3$ as placing $a$ first, $b$ second, and following the order of $>$ for the remaining positions.
+	Finally, define a linear order $>_4$ as placing $b$ first, $a$ second, and following the \emph{inverse} order of $>$ for the remaining positions.
 
-	First build a temporary profile $P$ of $p+q$ agents with $a$ and $b$ ranked as just described.
-Complete it with $m-2$ alternatives ranked in arbitrary orders so that the resulting profile has complete strict rankings for each of the $p+q$ agents.
-Now we will make the other alternatives as bad as desired by adding agents to $P$ that appreciate $a$ and $b$ more than the other alternatives, thus building a profile $P'$ in which, whatever the weights, $c$ may not have a better score than $a$.
-Observe that if we add $\delta$ agents (with $\delta$ a natural number) that put $a$ at first rank and $b$ at second rank, and $\delta$ agents that put $b$ at first rank and $a$ at second rank, we do not change the difference of the scores of $a$ and $b$, and thus, observing the chair choosing $a$ or $b$ still answers the question.
-	% Choose arbitrarily a matching of the remaining $m-2$ alternatives to the ranks $3$ to $m$, say, $c \mapsto 3$, $d \mapsto 4$, and so on.
-The first $\delta$ supplementary agents, who rank $a$ first and $b$ second, rank the other alternatives as the just defined mapping suggests.
-The other $\delta$ supplementary agents, who rank $b$ first and $a$ second, use the opposite ranking for the remaining alternatives, say, $c \mapsto m$, $d \mapsto m-1$, and so on.
+	Define $P$ as the profile of $3 (p + q)$ voters containing $q$ times $>_1$, $p$ times $>_2$, and $>_3$ and $>_4$ each $p + q$ times.
+	As a result, $a$ obtains the following ranks: $q$ times $r$, $p$ times $r + 2$, $p + q$ times first, and $p + q$ times second.
+The alternative $b$ obtains the ranks $r + 1$, $2$ and $1$, each $p + q$ times.
+Consider any alternative $c \in A \setminus \set{a, b}$.
+Its score is maximal when it comes first in $>_1$, first in $>_2$ and first in $>$, by convexity of the weights.
+In that case, $c$ is positioned at the ranks $1$, $3$ and $m$, each $p + q$ times.
 
-	We can prove that, for $\delta = p+q$, and whatever the weight vector $\w \in \W$, no alternative, except possibly $b$, has a better score than $a$. 
-	(In fact, as the construction will exhibit, they are all worse than both $a$ and $b$, but the weaker fact is enough for our claim.)
-	Pick any alternative $c$ that is not $a$ or $b$. 
-	%Let $c_t$ denote the number of times $c$ reaches rank $t$ or better in $P$.
-Note that $c_m = p+q$ and $c_t ≤ p + q, 1 ≤ t ≤ m$.
-Define $a_t$ similarly, for the alternative $a$.
-By construction, $a_r = q$, $a_{r+2} = q+p = a_m$.
-	Define $c'_t$ as the number of times $c$ gets rank $t$ or better in $P'$, and define $a'_t$ similarly.
-Now $a'_1 ≥ \delta, a'_t ≥ 2\delta \text{ for } 2 ≤ t < m, a'_{r+2} = q+p+2\delta = a'_m$.
-To obtain upper bounds for $c'_t$, assume $c$ is ranked first by the $p+q$ agents in $P$.
-By our construction, the  $2 \delta$ new agents of $P'$ give to $c$ the ranks $3$ and $m$, or $4$ and $m-1$, … Observe that the score of $c$ is maximal for attribution $(3, m)$, by convexity of the weights.
-Therefore, in the best case for $c$, $c'_1 ≤ p + q, c'_2 ≤ p+q, c'_t ≤ p+q+\delta \text{ for } 3 ≤ t < m, c'_m ≤ p+q+2\delta$.
-Observe that $a'_t ≥ c'_t, 1 ≤ t ≤ m$ (with strict inequality for $t=2$).
-Because weights are non increasing, this guarantees, with $\delta = p + q$, that the score of $a$ is not lower than the one of $c$.
+	Letting $s(x)$ denote the score of $x$ at $P$, we obtain $s(a) = q w_r + p w_{r + 2} + (p + q) w_1 + (p + q) w_2$, thus, $s(a) ≥ (p + q) w_m + (p + q) w_1 + (p + q) w_2$; $s(b) = (p + q) w_{r + 1} + (p + q) w_2 + (p + q) w_1$; and, $\forall c \in A \setminus \set{a, b}$,
+	$s(c) ≤ (p + q) w_1 + (p + q) w_3 + (p + q) w_m$.
+It follows that $a$ or $b$ maximize $s$ (as $s(a) ≥ s(c)$).
+We conclude by observing that $a \in f(P) ⇔ s(a) ≥ s(b) ⇔ q w_r + p w_{r + 2} ≥ (p + q) w_{r + 1} ⇔ w_r - w_{r + 1} ≥ (p / q) (w_{r + 1} - w_{r + 2})$, and similarly for $b \in f(P)$.
 \end{proof}

### 2020-12-14 minimax.tex
changes after meeting

@@
 \usepackage{soul}
-
+\usepackage{amsthm}
 \usepackage[hidelinks]{hyperref}
@@
 
-\begin{claim} \label{claim:completion}
+\begin{proposition} \label{claim:completion}
 	There exists a completion $\hat{\profile} \in C(\pprofile)$ of the profile $\profile$ such that $\PMR(x,y; \pprofile, W) = \max_{\w \in W} [ s(y; \hat{\profile}, \w) - s(x; \hat{\profile}, \w) ]$ and such that the linear order $\hat{v}_{j}$ of each agent $j$ satisfies:
@@
 	\end{align} 
-\end{claim}
-\begin{proof}[Sketch]
+\end{proposition}
+\begin{proof*}[Sketch]
 	Consider our knowledge $\pprefeq_j$ about the preference of the agent $j$. 
@@
 	This maximizes the adversary’s interests: because the weight vector is convex, the difference of scores will be lower when both alternatives are ranked lower (Equation \ref{eq:convexity}), and that difference of scores is in favor of $x$ when $x \ppref_j y$, thus to be minimized from the point of view of the adversary.
-\end{proof}
+\end{proof*}
 
 Let ${\pprefeq_j}(x)$ designate the set of alternatives known to be considered by $j$ as less good than or equal to $x$, and ${\pprefinv_j}(y)$ be the set of alternatives known to be considered by $j$ as strictly better than $y$.
-\begin{claim}
+\begin{proposition}
 	The rank of $x$ in the PMR-maximizing linear orders of agent $j$ is $\hat{v}_{j}(x) = 1+\card{A}-\card{{\pprefeq_j}(x)}$, and the rank of $y$ is $\hat{v}_{j}(y)=1+\card{{\pprefinv_j}(y)}+\card{\beta}$, where $\card{\beta} = \card{A \setminus ({\pprefeq_j}(x) \cup {\pprefinv_j}(y))}$ if $(x \pprefeq_j y)$ and $\card{\beta} = 0$ otherwise.
 	\label{claim:rankPMR}
-\end{claim}
-\begin{proof}
+\end{proposition}
+\begin{proof*}
 	The rank of $x$ is directly obtained from \cref{eq:complx}.
@@
 	\end{equation}
-\end{proof}
-The claim can also be understood by observing that in the case $(x \pprefeq_j y)$, $\beta$ is the number of alternatives incomparable with both $x$ and $y$.
-\begin{claim}
+\end{proof*}
+The proposition can also be understood by observing that in the case $(x \pprefeq_j y)$, $\beta$ is the number of alternatives incomparable with both $x$ and $y$.
+\begin{proposition}
 	The $\PMR$ can be written as:
@@
 $\hat{\alpha}_{r}^{x}$)  is the number of times $y$ (resp.
-$x$) is at rank $r$ in the complete profile $\hat{\profile}$ as determined in Claim \ref{claim:rankPMR}.
+$x$) is at rank $r$ in the complete profile $\hat{\profile}$ as determined in \cref{claim:rankPMR}.
 %\ref{claim:completion}.
-\end{claim}
-The last claim shows that PMR is linear in the weights.
+\end{proposition}
+The last proposition shows that PMR is linear in the weights.
 Recall that the preferences of the chair are encoded with linear constraints $\Co_{W}$.
@@
 Thus, our task is to build a profile, given $\lambda$ and $r ≤ m-2$, in such a way that the set of (tied) winners picked by the chair reveals whether $w_{r} - w_{r+1} \geq \lambda (w_{r+1} - w_{r+2})$.
-\begin{claim}
+\begin{proposition}
 	Given a rational $\lambda = p/q > 1$ and a rank $r$ between $1$ and $m - 2$, there exists a profile $P$ such that, for any weight vector $\w \in \W$, $a \in f(P)$ iff $w_{r} - w_{r+1} ≥ \lambda (w_{r+1} - w_{r+2})$ and $b \in f(P)$ iff $w_{r} - w_{r+1} ≤ \lambda (w_{r+1} - w_{r+2})$, where $f$ is the PSR parameterized with $\w$.
-\end{claim}
-\begin{proof}
+\end{proposition}
+\begin{proof*}
 	Define a linear order $>_1$ over $A$ as placing $a$ at rank $r$, $b$ at rank $r + 1$, and the remaining alternatives arbitrarily. 
@@
 We conclude by observing that $a \in f(P) ⇔ s(a) ≥ s(b) ⇔ q w_r + p w_{r + 2} ≥ (p + q) w_{r + 1} ⇔ w_r - w_{r + 1} ≥ (p / q) (w_{r + 1} - w_{r + 2})$, and similarly for $b \in f(P)$.
-\end{proof}
+\end{proof*}
 At this stage, we are satisfied that a procedure exists to transform our abstract questions to questions about winners of a PSR.
@@
 The results for various sizes are displayed in \cref{tab:lowRegret}. 
-We see that the number of questions required to reach a low regret level grows approximately linearly with the number of agents and grows less fast than the square of the number of alternatives, for the sizes we considered.
+For the experiments we performed, we see that the number of questions required to reach a low regret level grows approximately linearly with the number of agents and grows less fast than the square of the number of alternatives.
 Averaging these data by category of value for $m$, and assuming no questions get asked to the chair, we see that in order to reach a low regret level, each agent will have to answer $5.6$ questions for $m = 5$, $17.2$ questions for $m = 10$ and $27.1$ questions for $m = 15$.
@@
 We see that this function is convex, apart from the very first few questions, indicating %to users of our approach
-that, on average, halving the number of questions will only reduce the gain in regret by less than half.
+that, on average, halving the number of questions will only reduce the gain in regret by less than half. \commentBN{Reviewer: Halving the number of questions reduces the regret by more than 50\%.}
 
@@
 
-As part of the contribution of this work, we publish an open-source library that allows to reproduce our experiments, and more (url not displayed for anonymity reasons).
+As part of the contribution of this work, we publish an open-source library that allows to reproduce our experiments, and serve as a basis for further research (url not displayed for anonymity reasons).
 

### 2020-12-15 minimax.tex
new figures

@@
 \usepackage{booktabs}
+\usepackage{pgfplots}
 
@@
 	\label{fig:smallSize}
-%	\Description{Graph showing that Pessimistic performs slightly better than Extended pessimistic, itself performing better than Elitist, itself performing much better than Random.}
-	\includegraphics[width=.45\textwidth]{comparison.png}
+	\begin{tikzpicture}
+		\begin{axis}[
+			y=10,
+			xlabel=Number of Questions,
+			ylabel=Avg. Regret,
+			ytick={0,2,4,6,8,10,12},
+			xtick distance=10,
+			ytick distance=2,
+			xtick pos=left,
+			ymajorgrids=true,
+			ytick style={draw=none},
+			ymin=0,
+			ymax=12,
+			xmin=0,
+			xmax=100,
+			yticklabels={0,2,4,6,8,10,12}]
+			\addlegendimage{mark=*,teal,mark size=2}
+			\addlegendimage{mark=triangle*,orange,mark size=2}
+			\addlegendimage{mark=square*,blue,mark size=2}
+			\addlegendimage{mark=diamond*,red,mark size=2}
+
+			\addplot[thick, mark=*, mark size = {2}, mark indices = {35}, teal] table [x=k, y=Pes.]{data/comparison.dat};
+			\addlegendentry{Pes.}
+			\addplot[thick, mark=triangle*, mark size = {2}, mark indices = {45}, orange] table [x=k, y=Ex.Pes.]{data/comparison.dat};
+			\addlegendentry{Ex.Pes.}
+			\addplot[thick, mark=square*, mark size = {2}, mark indices = {50}, blue] table [x=k, y=Eli.]{data/comparison.dat};
+			\addlegendentry{Eli.}
+			\addplot[thick, mark=diamond*, mark size = {2}, mark indices = {50}, red] table [x=k, y=Rnd.]{data/comparison.dat};
+			\addlegendentry{Rnd.}
+
+		\end{axis}
+	\end{tikzpicture}
 \end{figure}
+
+%\begin{figure}
+%	\caption{Average MMR in problems of size $(5, 10)$ after $k$ questions.}
+%	\label{fig:smallSize}
+%%	\Description{Graph showing that Pessimistic performs slightly better than Extended pessimistic, itself performing better than Elitist, itself performing much better than Random.}
+%	\includegraphics[width=.45\textwidth]{comparison.png}
+%\end{figure}
 \sisetup{table-number-alignment = center, table-figures-integer=2, table-figures-decimal=1, table-auto-round}
@@
 \paragraph{Decrease in MMR values}
+
 \begin{figure}
@@
 	\label{fig:linearity}
-	%\Description{Graph showing that the MMR decreases very approximately linearly, and is convex, as a function of the number of questions.}
-	\includegraphics[width=.45\textwidth]{linearity.png}
+	\begin{tikzpicture}
+		\pgfplotsset{
+			every axis legend/.append style={
+				at={(0.5,1.03)},
+				anchor=south
+			},
+		}
+		\begin{axis}[
+			y=3.5,
+			legend columns=3,
+			xlabel=Number of Questions,
+			ylabel=Avg. Regret,
+			ytick={0,5,10,15,20,25,30,35},
+			xtick distance=100,
+			ytick distance=5,
+			xtick pos=left,
+			ymajorgrids=true,
+			ytick style={draw=none},
+			ymin=0,
+			ymax=35,
+			xmin=0,
+			xmax=800,
+			yticklabels={0,5,10,15,20,25,30,35}]
+
+			\addlegendimage{mark=triangle*,teal,mark size=2}
+			\addlegendimage{mark=*,violet,mark size=2}
+			\addlegendimage{mark=square*,green,mark size=2}
+			\addlegendimage{mark=diamond*,red,mark size=2}
+			\addlegendimage{mark=pentagon*,cyan,mark size=2}
+			\addlegendimage{mark=halfsquare*,magenta,mark size=2}
+
+			\addplot[thick, mark=triangle*, mark size = {2}, mark indices = {35}, teal] table [x=k, y=5.10]{data/linearity.dat};
+			\addlegendentry{m=5, n=10}
+			\addplot[thick, mark=*, mark size = {2}, mark indices = {45}, violet] table [x=k, y=5.15]{data/linearity.dat};
+			\addlegendentry{m=5, n=15}
+			\addplot[thick, mark=square*, mark size = {2}, mark indices = {90}, green] table [x=k, y=5.20]{data/linearity.dat};
+			\addlegendentry{m=5, n=20}
+			\addplot[thick, mark=diamond*, mark size = {2}, mark indices = {150}, red] table [x=k, y=10.20]{data/linearity.dat};
+			\addlegendentry{m=10, n=20}
+			\addplot[thick, mark=pentagon*, mark size = {2}, mark indices = {300}, cyan] table [x=k, y=10.30]{data/linearity.dat};
+			\addlegendentry{m=10, n=30}
+			\addplot[thick, mark=halfsquare*, mark size = {2}, mark indices = {400}, magenta] table [x=k, y=15.30]{data/linearity.dat};
+			\addlegendentry{m=15, n=30}
+		\end{axis}
+	\end{tikzpicture}
 \end{figure}
+%\begin{figure}
+%	\caption{Average MMR after $k$ questions with Pessimistic strategy for different problem sizes.}
+%
+%	%\Description{Graph showing that the MMR decreases very approximately linearly, and is convex, as a function of the number of questions.}
+%	\includegraphics[width=.45\textwidth]{linearity.png}
+%\end{figure}
 

### 2021-01-04 minimax.tex
new logarithmic plot for linearityFig with courses xps

@@
 
+%\begin{figure}
+%	\caption{Average MMR after $k$ questions with Pessimistic strategy for different problem sizes.}
+%	\label{fig:linearity}
+%	\begin{tikzpicture}
+%		\pgfplotsset{
+%			every axis legend/.append style={
+%				at={(0.5,1.03)},
+%				anchor=south
+%			},
+%		}
+%		\begin{axis}[
+%			y=3.5,
+%			legend columns=3,
+%			xlabel=Number of Questions,
+%			ylabel=Avg. Regret,
+%			ytick={0,5,10,15,20,25,30,35,146},
+%			xtick distance=100,
+%			ytick distance=5,
+%			xtick pos=left,
+%			ymajorgrids=true,
+%			ytick style={draw=none},
+%			ymin=0,
+%			ymax=146,
+%			xmin=0,
+%			xmax=1000,
+%			yticklabels={0,5,10,15,20,25,30,35,146}]
+%			
+%			\addlegendimage{mark=triangle*,teal,mark size=2}
+%			\addlegendimage{mark=*,violet,mark size=2}
+%			\addlegendimage{mark=square*,green,mark size=2}
+%			\addlegendimage{mark=diamond*,red,mark size=2}
+%			\addlegendimage{mark=pentagon*,cyan,mark size=2}
+%			\addlegendimage{mark=halfsquare*,magenta,mark size=2}
+%			\addlegendimage{mark=halfsquare right*,brown,mark size=2}
+%			
+%			\addplot[thick, mark=triangle*, mark size = {2}, mark indices = {35}, teal] table [x=k, y=5.10]{data/linearity.dat};
+%			\addlegendentry{m=5, n=10}
+%			\addplot[thick, mark=*, mark size = {2}, mark indices = {45}, violet] table [x=k, y=5.15]{data/linearity.dat};
+%			\addlegendentry{m=5, n=15}
+%			\addplot[thick, mark=square*, mark size = {2}, mark indices = {90}, green] table [x=k, y=5.20]{data/linearity.dat};
+%			\addlegendentry{m=5, n=20}
+%			\addplot[thick, mark=diamond*, mark size = {2}, mark indices = {150}, red] table [x=k, y=10.20]{data/linearity.dat};
+%			\addlegendentry{m=10, n=20}
+%			\addplot[thick, mark=pentagon*, mark size = {2}, mark indices = {300}, cyan] table [x=k, y=10.30]{data/linearity.dat};
+%			\addlegendentry{m=10, n=30}
+%			\addplot[thick, mark=halfsquare*, mark size = {2}, mark indices = {400}, magenta] table [x=k, y=15.30]{data/linearity.dat};
+%			\addlegendentry{m=15, n=30}
+%			\addplot[thick, mark=halfsquare right*, mark size = {2}, mark indices = {400}, brown] table [x=k, y=courses]{data/linearity.dat};
+%			\addlegendentry{courses}
+%		\end{axis}
+%	\end{tikzpicture}
+%\end{figure}
+
 \begin{figure}
-	\caption{Average MMR after $k$ questions with Pessimistic strategy for different problem sizes.}
+	\caption{Logarithmic plot representing the MMR reduction after $k$ questions with Pessimistic strategy for different problem sizes.}
 	\label{fig:linearity}
@@
 		}
-		\begin{axis}[
-			y=3.5,
+		\begin{semilogyaxis}[
 			legend columns=3,
@@
 			ylabel=Avg. Regret,
-			ytick={0,5,10,15,20,25,30,35},
-			xtick distance=100,
-			ytick distance=5,
-			xtick pos=left,
+			log basis y= 10,
+			ymin=10e-2,
+			ymax=10e2,
+			ytick={10e-2,1,2,10,15,20,30,146},
+			yticklabels={0.01,1,2,10,15,20,30,146},
 			ymajorgrids=true,
 			ytick style={draw=none},
-			ymin=0,
-			ymax=35,
 			xmin=0,
-			xmax=800,
-			yticklabels={0,5,10,15,20,25,30,35}]
+			xmax=1000,
+			xtick={0,100,200,300,400,500,600,700,800,900,1000},
+			xticklabels={0,100,200,300,400,500,600,700,800,900,1000},
+			ticklabel style = {font=\tiny}
+			]
 
@@
 			\addlegendimage{mark=halfsquare*,magenta,mark size=2}
+			\addlegendimage{mark=halfsquare right*,brown,mark size=2}
 
-			\addplot[thick, mark=triangle*, mark size = {2}, mark indices = {35}, teal] table [x=k, y=5.10]{data/linearity.dat};
+			\addplot[thick, mark=triangle*, mark size = {2}, mark indices = {35}, teal, domain=-5:5] table [x=k, y=5.10]{data/linearity.dat};
 			\addlegendentry{m=5, n=10}
-			\addplot[thick, mark=*, mark size = {2}, mark indices = {45}, violet] table [x=k, y=5.15]{data/linearity.dat};
+			\addplot[thick, mark=*, mark size = {2}, mark indices = {45}, violet,domain=-5:5] table [x=k, y=5.15]{data/linearity.dat};
 			\addlegendentry{m=5, n=15}
@@
 			\addlegendentry{m=15, n=30}
-		\end{axis}
+			\addplot[thick, mark=halfsquare right*, mark size = {2}, mark indices = {400}, brown] table [x=k, y=courses]{data/linearity.dat};
+			\addlegendentry{courses}
+		\end{semilogyaxis}
 	\end{tikzpicture}
 \end{figure}
+
 %\begin{figure}

### 2021-01-05 cover letter/cover_letter.tex
resubmission material

(Rebuttal)\\
Our proposal is methodologically innovative: it addresses in a new way the difficult problem of eliciting preferences about voting rules. It opens up a novel path to gather and exploit preferential information about voting rules, in parallel with more classical preferential information about the alternatives under scrutiny. As a result, multiple challenging research questions open up, several of which are raised by the reviewers. We warmly thank them for these observations.

As reviewer 1 points out, one could simply ask for direct information about the parameters of the rules, such as the weight vector. But it is unclear whether the answers to such questions would be meaningful. For example, in many cases, the chair (supposed to be human) may not know whether the largest weight should be twice, or three times, the weight associated with the second rank.

We ask the chair which alternative should win given a concrete profile. Such questions have precise semantics whose understanding is shared by the chair. This way of asking questions is sufficiently natural that it has been used in experimental settings investigating the feeling of justice of individuals (Does majoritarian approval matter in selecting a social choice rule? An exploratory panel study, Ebru Giritligil and Sertel, Social Choice and Welfare 25(1):43-73, 2005). To the best of our knowledge, the use of such questions to systematically guide an elicitation process is novel. We will highlight this aspect in the paper.

Our approach is analogous to that of decision theorists with preference elicitation: a large stream of research considers more meaningful to ask direct choice questions ("please choose either a or b") than to question the decision maker about the shape of its utility function. The former are considered "observable": acts of choice are translated to preference statements.

Concerning the hypothesis of convexity raised by reviewer 1, we need to assume that we look for a function inside a specific class of functions (here, the scoring rules with convex weights) because the class of all possible functions is too large. This allows for mixing an axiomatic basis with more precise "observable" questions; again, as it is usually done in decision theory (which often assumes the Subjective Expected Utility axioms). The use of convex weights is a natural and common assumption: losing ranks at the top of the ranking is more damaging than losing ranks at the bottom.

A concrete application of our work might be a committee that is about to hire a new employee, whose performances are evaluated by several experts. The members of the committee may not have a voting rule in mind at the start of the process, and might not wish to agree on a specific voting rule, but they might be willing to answer enough questions about selecting winners out of specific profiles to determine their employee of choice.

Regarding the experimental concerns addressed by reviewer 1, our strategies and setting are meant to tackle small scale social choice situations such as just exemplified. Our questioning method, in particular, does not scale to hundreds of candidates because the chair must be assumed to have limited cognitive capacity.

IC is a quite challenging situation: as can be expected intuitively (and shown experimentally by Lu and Boutilier in their setting), the number of questions to be asked decrease with less varied profiles. We want to focus on the most critical setting, as there is a wide variety of possible situations to test in such experiments.

The reviewers are right to point out that our comments about Table 3 were overconfident, this will be corrected.

Reviewer 1 Question6 : We should have written “given to c the ranks 3 and m” instead of (3, m) in the proof of Claim 4.

Reviewer 2 Question2: The $\lambda$-range is initialized to [1,n] because $\lambda \geq1$ by convexity and we assume $\lambda \leq n$ wlog: for $\lambda \geq n$, the rule coincides with Plurality.

Regarding the guarantees concerns raised by reviewer 2: The general lack of theoretical guarantees with respect to the number of questions in the literature adopting minimax regret approaches suggest that obtaining such results is very difficult, if possible. However, our approach guarantees to return the true winners when the elicitation is completed. Note that the process can be terminated early, and offers a guaranteed bound on the regret at any time.

Reviewer 2 Question1: At the start of the elicitation, the space of uncertainty is so large that the adversary can attain the maximum possible value of regret; multiple answers are needed to constrain her enough for the MMR to start decreasing. When approaching optimality, the pace of MMR reduction decreases.

Reviewer 3 Question1: We did not investigate a systematic way of mixing strategies but we manually mixed different ideas in order to obtain the strategies we presented. For example Two phase and Extended Pessimistic reuse ideas present in the Pessimistic strategy.

### 2021-01-05 cover letter/resubmission.tex
resubmission material

\documentclass[a4paper]{article}
\input{../preamble/packages}
\usepackage{pdfpages}

\date{}

\title{Resubmission \\ \vspace{1cm} \textbf{\Large Simultaneous Elicitation of Scoring Rule and Agent Preferences for Robust Winner Determination} \\ {\large Submission ID: 554, AAMAS-2021}}

\begin{document}
\maketitle

\section{Cover Letter}
\input{cover_letter.tex}

\section{Reviews AAMAS-2021}
\input{reviews_aamas.tex}

\section{Reviews IJCAI-20}
\input{reviews_ijcai.tex}

\section{Rejected paper AAMAS-2021}
\includepdf[pages=-]{aamas21_paper_554.pdf}

\end{document}

### 2021-01-05 cover letter/reviews_aamas.tex
resubmission material

\subsection*{Review 1}
\subsubsection*{Summary:}	The authors use the notion of minimax regret to guide the process of preference elicitation in an election (they elicit both the voters' preferences and the preferences of the chair regarding the scoring rule used). The authors show that the methodology of Lu and Boutilier for computing minimax regret still applies in their setting and present some experimental results.
\subsubsection*{Strengths:}	1) Minimax regret is a rather natural notion, which has not received much attention so far.
\subsubsection*{Weaknesses:}
1) The theoretical results are relatively simple extensions of the results of Lu and Boutilier
\newline 2) The experimental results seem quite preliminary.

\subsubsection*{Detailed comments:}	The paper is quite well written, clear, relevant for the conference. The biggest issues I have regard significance. The idea of using minimax regret to guide elicitation is very good, but is explored quite well by Lu and Boutilier. Here the authors extend this framework by eliciting the scoring rule used, but there is very little discussion as to why this really is such a good idea. I cannot easily think of a half-realistic setting where one would know that the scores need to be convex, but at the same time one would not know which ones exactly to use.

More specific comments come below:
\begin{enumerate}
\item Related work \\
As the paper is partially related to designing/choosing a scoring rule for a given setting---and as the problem of manipulation is mentioned---it might be worth to consider the following paper:

Dorothea Baumeister, Tobias Hogrebe:
Manipulative Design of Scoring Systems. AAMAS 2019: 1814-1816

Regarding partial preferences and manipulation, one may also look at the following one (although it is less related, for sure):

Dorothea Baumeister, Piotr Faliszewski, Jérôme Lang, Jörg Rothe:
Campaigns for lazy voters: truncated ballots. AAMAS 2012: 577-584

\item Concurrent elicitation of the scoring rule \\
I am not really convinced that the assumption that a scoring rule is not known makes sense. On the one hand, there is the problem of choosing the scoring rule manipulatively (but since the authors mention that the elections at hand are built into recommendation systems etc., this is not really an issue). The other problem is that I can hardly think of a scenario where the chair can answer the questions about the scoring rule, but somehow it is difficult for him to produce the full rule in a single step. So what do we gain?

\item Claims vs Propositions \\
I do not understand why the authors use "Claims" and not "Propositions".

\item I think that Claim 4 should say something along the lines: "There is a profile P', such that ... and P' can be computed effectively".

\item I can hardly imagine a person who faced with the profile P' from Claim 4 could meaningfully answer if a is better than b or the other way round. A piece of software could do it, though---but probably by precomputing the scoring rule to use (which removed the need for eliciation).

\item Proof of Claim 4: I do not understand notation (3,m) or (4,m-1) etc.

\item Empirical evaluation is very preliminary
I have a number of complaints regarding the evaluation process:
	\begin{enumerate}
		\item Why do the authors use IC only? Why not other statistical cultures? Why not some real-life data? After all, the experimental part is the main contribution of the paper and it is done in a fairly minimalistic way.

		\item Why do the authors look at very small elections only? 15 candidates and 30 voters seems completely inadequate for the motivations from the introduction.

		\item The conclusion that the number of questions required to reach low regret cannot be made based on Table 3. There is simply far too little data to have any sort of confidence in claims like this.	
	\end{enumerate}

\end{enumerate}

All in all, I think it is certainly a nice enough paper to be accepted as short, but is below the bar for the full acceptance.

\subsubsection*{Questions for rebuttal:}
Q1: Why did you only look at IC elections?
\newline Q2: How to use your approach in large elections? Hundreds of candidates, thousands of voters? After all, showing a strategy that can deal with large elections would meaningfully extend the work of Lu and Boutilier?
\newline Q3: Can you provide a realistic example where elicitation of the scoring rule is useful?
\subsubsection*{Score:}	
4: (poor (good attempt but too many concerns, so probably should be rejected))

\subsubsection*{Comments added after rebuttal:}
I found the example provided in the response to be convincing.

I still think that testing the heuristics on IC only is insufficient. Even if it is the hardest case, I would also like to see how the algorithm peforms in the easier ones. Can it exploit the structure when the structure is present? One cannot evaluate such issues by looking at IC alone.

\subsection*{Review 2}
\subsubsection*{Summary:}
The paper studies a voting problem wherein neither the voting rule nor the voters' preferences are specified in advance. Rather, an elicitation procedure is used to determine the election winner by asking the voters questions about their preferences and asking the chair questions about the voting rule.

Specifically, the preferences of the voters are assumed to be given by a fixed set of linear orders that are unknown to the elicitation platform. In addition, the voting rule is assumed to belong to the class of positional scoring rules with monotone weights with diminishing differences. The elicitation procedure comprises of the chair specifying the winning candidates on example profiles, and the voters responding to a series of pairwise comparisons.

At each step, the minimax regret criterion (Lu and Boutilier, IJCAI'11) is used to determine the next query, and this procedure is continued until convergence (e.g., either the regret drops below a certain threshold or a certain number of questions have been asked). The regret of an alternative, informally speaking, is the "loss" incurred for picking that alternative instead of an "optimal" one under adversarial choice of completion of the partial preferences elicited so far as well as the worst-case choice of positional weights.

The main contributions of the submission are:
1. Proposing a framework for simultaneously eliciting voters' preferences and information about the voting rule based on the minimax regret criterion.
2. Experimental comparison of a number of elicitation heuristics in terms of the number of questions asked or the regret value.

The empirical observations suggest that a modest number of questions (to the voters as well as the chair) are sufficient in arriving at a reasonable choice, and that the regret drops super-linearly as a function of the number of questions asked over the course of elicitation.
\subsubsection*{Strengths:}	The idea of modeling simultaneous uncertainty in the voting rule as well as the voters' preferences is quite interesting. It is also useful to know that the minimax regret framework of Lu and Boutilier (IJCAI'11), previously studied in the setting of a known voting rule, can be extended to the aforementioned more general problem.
\subsubsection*{Weaknesses:}	The lack of theoretical guarantees for the proposed elicitation strategy, as well as missing reasoning behind several of the experimental observations, makes this a weak paper in my opinion.

\subsubsection*{Detailed comments:}
I like the high-level question asked by the paper, namely whether it is possible to simultaneously elicit the information about the voting rule and the voters' preferences. However, the significance of the contribution is less clear. The results, which largely comprise of experiments, are at the level of proposing a heuristic that seems to work well in simulations but lacks formal theoretical guarantees.

I believe the paper will be much stronger if the authors could provide theoretical convergence guarantees for the proposed heuristics. Additionally, in the "Empirical Evaluation" section, instead of simply describing the observations, it would be useful to also formally state the hypotheses used in each experiment, and explain how the experiments support or refute those hypotheses. For example, you could describe whether (and why) one might expect "Pessimistic" strategy to work better than the "Elitist" strategy, and then discuss to what extent did the simulations confirm that hypothesis.

Some minor comments are below.
\begin{enumerate}
\item Page 1
\begin{itemize}
	\item In several places you use the phrase "permits to" when it might be clearer to say "allows for".
\end{itemize}

\item Page 2
\begin{itemize}
	\item "that showed that"-->who showed that.
\end{itemize}

\item Page 3 
\begin{itemize}
	\item "there are no necessary winner"-->there is no necessary winner.
\end{itemize}

\item Page 4 
\begin{itemize}
	\item "less good than or equal to"-->You could rather say "weakly worse".
	\item Using $\succeq^p_j(x)$ to denote the set of alternatives weakly worse than x can be confusing. Please consider using a different notation such as $A^(\succeq^p_j,x)$.
\end{itemize}

\item Page 5
\begin{itemize}
	\item Claim 4 is written in the form of a definition, and it is not clear what is actually being claimed here. Maybe you could say that "there exists a profile P' satisfying such and such properties".
	\item "each of the p+q agent"-->each of the p+q agents
	\item "worst than"-->worse than
\end{itemize}

\item Page 6 
\begin{itemize}
	\item "on order to"-->in order to
	\item "an important weight"-->a large weight
	\item "For generating the weights we first draw $m - 1$ numbers uniformly at random"-->What is the range from which you make the draws?
\end{itemize}

\item Page 7 
\begin{itemize}
	\item "In-dept evaluation"-->In-depth evaluation
	\item Figure 1, X axis label should say "Number of questions"
	\item "to be ran"-->to be run
	\item "We see that the number of questions required to reach a low regret level grows approximately linearly with the number of agents"-->Can you provide a formal regression analysis to support this claim?
\end{itemize}

\item Page 8 
\begin{itemize}
	\item "allow to quickly"-->allows to quickly
	\item "worst regret"-->worst-case regret
	\item "that allows to reproduce our experiments, and more"-->It would be useful to mention the other benefits explicitly.
	\item "halving the number of questions will only reduce the gain in regret by less than half"-->Might be clearer to say "halving the number of questions reduces the regret by more than 50$\%$".
\end{itemize}

\end{enumerate}
\subsubsection*{Questions for rebuttal:}	1. On Page 1, you write that "The quality of the recommendation increases faster than linearly with the number of questions, after an initial phase with almost no increase in quality, before slowing down and converging to an optimal recommendation." What is the reasoning behind this trend?
\newline 2. How did you decide the range of the parameter $\lambda$ to be [1,n]?
\subsubsection*{Score:}	
4: (poor (good attempt but too many concerns, so probably should be rejected))

\subsubsection*{Comments added after rebuttal:}
Thanks to the authors for responding to the questions raised in my review. My concern about the significance of the paper remains. In the absence of any formal theoretical guarantees about the performance of the elicitation heuristic, the paper will likely be of limited interest. The authors note that obtaining such guarantees could be difficult. Nevertheless, the paper could certainly benefit from a revised experimental analysis that clearly formulates the hypotheses to be tested and how the experiments support or refute those hypotheses.

\subsection*{Review 3}
\subsubsection*{Summary:}
This paper considers elicitation in the context of scoring rules when both the preferences of the voters and the weights defining the rule might be missing. The authors model the problem via regret minimization and propose several types of queries and querying strategies. The paper also presents an interesting experimental study which supports the presented approach.
\subsubsection*{Strengths:}	The problem addressed is interesting and has potential for practical applicability.
Addressing missing information in both voters and the chair’s preferences is novel. The experimental section is a good starting point.
\subsubsection*{Weaknesses:}	The discussion on the motivation behind considering uncertainty on the scoring rule’s weights is not very convincing. They claim the chair might not be able to formalize the rule…
Another point that is not clear is when, in practice a system like this would be deployed.
The application of regret minimization is somewhat incremental w.r.t. the literature.

\subsubsection*{Detailed comments:}	reference elicitation in the context of voting is certainly a relevant topic for AAMAS.
The setting considered here is not per se novel, as elicitation of voters’ and the chair’s preferences have been considered before. The originality lies in considering them both at the same time.
While this is original, the motivation of when such a setting may occur in practice is not clear. In particular, I wonder about the timing. It is assumed that voters and candidates are known, information about the voters preferences is available and yet the voting rule has not yet been decided and the elicitation process is going on at the same time. It seams unlikely to me.
As I mentioned, I am also not very convinced about a chair not knowing which rule he wants/or is using while voters are expressing preferences. A much stronger argument would be that of a third party discovering information about a voter’s preferences and the rule by being able to observe results or to tap in and acquire some information. Obviously that would mean having much less control over what information is acquired than assumed here…it might be similar to random strategy studied in the experimental section.

The content is technically not overly sophisticated, so I have no doubt about its soundness.
The presentation flows well and all parts are clearly written. The description of the experimental results is also sufficiently detailed to enable reproducibility.

A minor complaint is that Figures 1 and 2 are blurred.
\subsubsection*{Questions for rebuttal:}
1) Could testing mixed strategies yield better results than the pure ones?
\subsubsection*{Score:}	
7: (good (probably should be accepted))

\subsection*{Metareview}
The main reason for the reject recommendation is the missing novelty in this paper. It basically is a reimplementation of the ideas from Lu and Boutilier. Furthermore, in the experimental section, clear hypotheses are missing and the reasons for limiting the analysis to IC are not convincing.

### 2021-01-05 cover letter/reviews_ijcai.tex
resubmission material

\subsection*{Review 1}
\subsubsection*{Overall score}
Accept (good paper. I can argue for accepting it)
\subsubsection*{Comments to authors}
The paper makes a substantial contribution to social choice, which has clear implications for AI applications whenever a consensus result is needed.

In the first part, a method of robust winner determination is derived, relying on the minimax (regret) principle. This part is written concisely, but still quite comprehensively. Each step follows logically from the previous one.

The second part (Section 4) reflects on concrete elicitation procedures, which, of course, are highly relevant for practical use. At least for me, this part was much harder to read. Admittedly, one has to look at many details, but maybe some additional meta sentences summarizing the basic ideas would be highly appreciated.

Some details:

* Please be more precise with using the word 'robust'. Robustness is always robustness against something.

* typos etc : please check the genitive: agents''''''''' preferences,
p1 recent work? 2005,
sd standard deviation?
check the reference for double doi/link, superfluous ISSN

\subsubsection*{Why should this paper be presented at IJCAI-PRICAI 2020?}
As just said, the paper makes a substantial contribution to the general issue of how to arrive at a consensus choice, a question that is not only theoretically interesting but also of broader practical relevance. The novelty of the paper lies in the low structure of the setting: both the voting rule as well as the agents' preferences are only partially specified. This expands considerably the range of potential applications.

\subsection*{Review 2}
\subsubsection*{Overall score}
Weak Accept (marginally above the acceptance threshold. Rejecting it would not be that bad)
\subsubsection*{Comments to authors}
This paper examines a social choice problem where agent preferences and the criteria for aggregating preferences across agents are partially specified. The paper provides theory for representing partial preferences, enumerating consistent total preference orders, aggregating such preferences across agents, and determining a winner per a model that minimizes worst case regret. The paper examines strategies for querying agents and the chair (arbiter of social choice) to elicit their preferences/aggregation criteria. It reports minimum worst case regret as a function of the number of elicitation questions across several strategies.

The paper provides a thorough mathematical development, and clearly identifies contrasting elicitation strategies. The text provides clear descriptions of the required set manipulations, which would otherwise be hard to parse.

The abstract would be stronger if it motivated the simultaneous elicitation task. The introductory material would appeal to more readers if it clarified the task by defining the roles of agents, the chair, the concept of regret in social choice scenarios, and the meaning of minimax-optimal alternatives. The paper does not have a separate related work section, and while it cites appropriate work, the alternatives to this approach could use more discussion. The paper presents, but does not discuss the experimental results, and it would be much stronger if the authors provided that analysis/interpretation. As it stands, it is unclear what the work is teaching us.
\subsubsection*{Why should this paper be presented at IJCAI-PRICAI 2020?}
Research on voting strategies and preference elicitation relates to real-world problems of interest. The extension to simultaneous elicitation of partially specified agent and chair preferences is sound, and relevant to the broader inquiry.

\subsection*{Review 3}
\subsubsection*{Overall score}
Weak Reject (marginally below the acceptance threshold. Accepting it would not be that bad)
\subsubsection*{Comments to authors}
This paper develops a minimax regret decision approach when preferences and voting rules are partly specified. The paper seems technically correct, however, the presentation would be improved with a larger example. Also, the evaluation discussion in section 5 could be expanded as there is room in the paper within a 7 page limit.

\subsection*{Review 4}
\subsubsection*{Overall score}
Reject (Not good enough. I can argue for rejecting it)
\subsubsection*{Comments to authors}
The authors study the problem of winner determination when both the voting rule and voters' preferences are not fully determined. They propose an interactive elicitation protocol and query strategies for the minimax regret rule. In particular, they focus on minimax regret version of the positional scoring rule to aggregate incomplete preferences. The main contribution of the paper is to simultaneously consider both partial information about the agents’ preferences and partial
specification of aggregation method. Both partial information about the agents’ preferences and partial specification of aggregation method have been studied separately in the literature.

My main concern is that the authors ignores (or unaware of) almost entire literature on both preference elicitation and voting with incomplete preferences. Few examples (not at all exhaustive) of vast related work with whom the authors must compare and position their work are as follows.
\begin{itemize}
	\item Palash Dey, Neeldhara Misra, and Y. Narahari. Complexity of manipulation with partial information in voting. Theor. Comput. Sci., 726:78–99, 2018.
	\item Ulle Endriss, Svetlana Obraztsova, Maria Polukarov, and Jeffrey S. Rosenschein. Strategic voting with incomplete information. In Proc. the Twenty-Fifth International Joint Conference on Artificial Intelligence, IJCAI 2016, New York, NY, USA, 9-15 July 2016, pages 236–242, 2016.
	\item Omer Lev, Reshef Meir, Svetlana Obraztsova, and Maria Polukarov. Heuristic voting as ordinal dominance strategies. In Proc. The Thirty-Third AAAI Conference on Artificial Intelligence, AAAI 2019,
	\item The Thirty-First Innovative Applications of Artificial Intelligence Conference, IAAI 2019, The Ninth AAAI Symposium on Educational Advances in Artificial Intelligence, EAAI 2019, Honolulu, Hawaii, USA, January 27 - February 1, 2019, pages 2077–2084, 2019.
	\item Reshef Meir. Plurality voting under uncertainty. In Proc. Twenty-Ninth AAAI Conference on Artificial Intelligence, January 25-30, 2015, Austin, Texas, USA, pages 2103–2109, 2015.
	\item Annemieke Reijngoud and Ulle Endriss. Voter response to iterated poll information. In International Conference on Autonomous Agents and Multiagent Systems, AAMAS 2012, Valencia, Spain, June 4-8, 2012 (3 Volumes), pages 635–644, 2012.
	\item Palash Dey: Manipulative elicitation - A new attack on elections with incomplete preferences. Theor. Comput. Sci. 731: 36-49 (2018)
	\item Vincent Conitzer: Eliciting Single-Peaked Preferences Using Comparison Queries. J. Artif. Intell. Res. 35: 161-191 (2009)
	\item Palash Dey, Neeldhara Misra: Elicitation for Preferences Single Peaked on Trees. IJCAI 2016: 215-221
	\item Palash Dey, Neeldhara Misra: Preference Elicitation for Single Crossing Domain. IJCAI 2016: 222-228
\end{itemize}

Also the results in the paper, in my opinion, in incremental in nature. I also found the writing style of the paper quite odd. For example, it is almost impossible to find the main contribution or take away message from the paper. Overall I think that the paper may contain some interesting results worth publishing but it has to be positioned correctly with respect to existing literature. The authors could also consider explicitly writing a bulleted list of contribution with pointers to parts of the paper that prove/discuss it.

\subsection*{Metareview}
The paper combines ideas from [Lu and Boutilier, 2011] and [Viappiani, 2018], and builds on other work on minimax regret-based preference elicitation, to generate an interactive elicitation approach for a situation in which there is incomplete knowledge about both (a) the voters' preference orders and (b) the weights of a positional scoring rule that generates the overall winner. Given those two earlier papers, this is a natural further step to make, and the paper successfully develops the previous approaches. One might view the work as somewhat incremental, but there is some substantial solid work here.

There are some other issues, pointed out by the reviewers. The discussion of the empirical evaluation is very brief. There is a substantial body of literature that was not cited, related to preference elicitation and incomplete preferences in a voting situation. Although they do not seem to be on exactly the same topic, it is important that the paper is positioned correctly with respect to the existing literature.

Because of these issues, I'm recommending rejection of the paper. However, I think after some further work on the paper there's a reasonable chance that it could be accepted for another high quality conference.

### 2021-01-06 minimax.tex
abstract and introduction

@@
 In the classical setting, the voting rule is fixed beforehand and full information concerning the preferences of the agents is provided.
-	This assumption of full preference information has recently been questioned by a number of researchers.
-	Methods for eliciting the voting rule when the preferences of the agents are completely known have been proposed, as well as techniques that consider the opposite scenario.
-%, viewing the voting rule as representing the preference of the chair.
+This assumption of full preference information has recently been questioned by a number of researchers and
+	several methods for eliciting the preferences of the agents have been proposed.
+	%  are completely known have been proposed, as well as techniques that consider the opposite scenario.
 
-	This article goes one step further by tackling one important new case, namely, when both the voting rule and the agents preferences are partially known.
+In this paper we argue that in many situations one should consider as well the voting rule to be 	partially specified.
+%	This article goes one step further by tackling one important new case, namely, when both the voting rule and the agents preferences are partially known.
 It also permits to obtain a progressively refined recommendation without requiring to achieve full knowledge of either sort of information.
-	%However, there may be cases where both of them are only partially known.
-	%This paper considers both sources of uncertainty at the same time, and proposes a method able to recommend a consensus choice without requiring full knowledge of either.
-	This is useful because providing such information is often costly: the chair may find it hard to specify a rule completely; agents may need time to form reflective preferences.
-
+%This is useful because providing such information is often costly: the chair may find it hard to specify a rule completely; agents may need time to form reflective preferences.	
 	Focusing on positional scoring rules, we assume that the chair, while not able to give a precise definition of the rule, is capable of answering simple questions requiring to pick a winner from a specific example profile.
-In addition, the preferences of the agents are incrementally acquired by asking comparison queries.
-	In this setting, we propose a method for robust approximate winner determination with minimax regret.
-We also provide an interactive elicitation protocol based on minimax regret and develop several query strategies that question the chair and the agents in order to acquire the most relevant information for quickly converging to a near-optimal alternative.
-Finally, we study these strategies experimentally in order to validate our approach and obtain practical guidelines.
+In addition, we assume that the agent preferences have to be elicited as well and are acquired by asking comparison queries.
+	We propose a method for robust approximate winner determination and interactive elicitation based on minimax regret; we develop several strategies for choosing the questions to ask to  the chair and the agents in order to %acquire the most relevant information for
+converge quickly to a near-optimal alternative. Finally, we analyze these strategies in experiments %in order to validate our approach
+ %focusing on settings 
+ where the voting rule and the preferences are simultaneously elicited.
+ %and obtain practical guidelines.
 \end{abstract}
@@
 This observation has motivated a number of recent works considering social choice with partial preference orders and incremental elicitation of agent preferences.
+
 Furthermore, it is often difficult for non-expert users to formalize a voting rule on the basis of some generic preferences over a desired aggregation method.
 Thus, the first hypothesis should also be relaxed.
-%Also the first hypothesis should be relaxed considering that, in several situations, it may not be easy to precisely define the voting rule.Indeed, it is possible that the chair has some preferences over the desired aggregation method, but is not able to formalize the voting rule upfront.
+Consider, as an example, a committee that is about to hire a new employee, whose performances are evaluated by several experts.
+The members of the committee may not have a voting rule in mind at the start of the process, and might not wish to agree on a specific voting rule, but they might be willing to answer a few questions requiring to select who should be the winner out of specific profiles.
+%The information provided can be used to   % to determine their employee of choice.
 
-%it is possible to derive dominance relations (akin to stochastic dominance) that allow to eliminate some alternatives since they will be less preferred than another one for any instantiation of the weights \citep{Stein1994}.
-%Among others, Llamazares and Pe{\~{n}}a have considered  the problem of dealing with underspecified weights in positional scoring rules.
+%This paper considers both sources of uncertainty at the same time, and proposes a method able to recommend a consensus choice without requiring full knowledge of either.
+In this paper we focus on positional scoring rules, that are a particularly common method used to aggregate rankings, and we assume that both the agent preferences and the social choice rule are partially specified.
+We develop methods, based on the notion of minimax regret, for determining a robust ``winner'' under uncertainty of both the voting rule and the agent preferences.
+%alternative using positional scoring rules and 
+We provide incremental elicitation methods that 
+at each step of the elicitation ask a question either to one of the agents or to the chair (the person or organization supervising the voting process) and discuss several heuristics that determine queries that quickly reduce regret.
+Answers to questions are encoded in terms of constraints; questions to the agents are comparions between pairs of alternatives while
+questions to the chair ask  to select who should be the winner in a synthetic profile.
+While previous works have considered either partial information about the agent preferences or a partially specified aggregation method, we do not know of any work considering both sources of uncertainty at the same time.
+Actually, very few works altogether have considered the problem of eliciting a voting rule by asking questions to the chair.
 
-In this paper we focus on positional scoring rules, that are a particularly common method used to aggregate rankings, and we assume that both the agent preferences and the social choice rule are partially specified.
-We develop methods for computing the minimax-optimal
-alternative using positional scoring rules and we provide incremental elicitation methods that 
-%to acquire relevant preference information; 
-at each step of the elicitation ask a question either to one of the agents or to the chair (the person or organization supervising the voting process).
-We discuss several heuristics that determine queries that quickly reduce minimax regret. 
-While previous works have considered either partial information about the agent preferences or a partially specified aggregation method, we do not know of any work considering both sources of uncertainty at the same time.
+Our approach is evaluated experimentally in simulations where the both the voting rule and the agent's preferences are initially unknown to the system and incrementally revealed by answering questions.
+We compare the effectiveness of several different strategies  including strategies that proceed in phases, learning first as much as possible about the voting rule and then focus on eliciting agent's preferences, and as well strategies that interwind questions to chair and to the agents based on which is estimated to provide more information.
+%Our approach permits to compare experimentally strategies that question the chair, the agents, or both.
 
-%In this paper we consider that both the agent preferences and the social choice rule are partially specified and we develop methods for computing the minimax-optimal alternative under these assumptions.
-%changed from: We develop methods for computing the minimax-optimal alternative for scoring rules with partial agent preference information and partial information about the weights of the scoring rule.
-
-%We also address the problem of elicitation, providing incremental elicitation methods to acquire relevant preference information.
-We then discuss several heuristics that attempt to simultaneously reduce the preference and voting rule uncertainty by determining queries, either to an agent or to the chair, that quickly reduce minimax regret.
-%In particular, our query strategies focus simultaneously on reduction of relevant preference and voting rule uncertainty.
-%\paragraph{Experimental conclusions}
-Our approach permits to compare experimentally strategies that question the chair, the agents, or both.
-
-A concrete application of our work might be a committee that is about to hire a new employee, whose performances are evaluated by several experts.
+%A concrete application of our work might be a committee that is about to hire a new employee, whose performances are evaluated by several experts.
 The members of the committee may not have a voting rule in mind at the start of the process, and might not wish to agree on a specific voting rule, but they might be willing to answer enough questions about selecting winners out of specific profiles to determine their employee of choice.
 
-We describe informally here a few of the conclusions stemming from these experiments, given a problem involving $m$ alternatives and $n$ agents.
+%We describe informally here a few of the conclusions stemming from these experiments, given a problem involving $m$ alternatives and $n$ agents.
 First, a good quality recommendation can be reached by asking what can be considered a reasonable number of questions to the chair and agents.
 For example, in a problem of size $m = 5$, $n = 10$, only $55$ questions in total are required to reach a good quality recommendation, which can be considered reasonable as these questions are to be dispatched over $10$ agents and the chair.
-Second, the quality of the recommendation increases faster than linearly with the number of questions, 
-after an initial phase with almost no increase in quality, before slowing down and converging to an optimal recommendation.
-%; so it is possible to stop the elicitation early and to pick a near-optimal recommendation.
-%after only a few questions (the first few questions yield no increase in quality), so it .
-Third, we experimentally find out that asking questions only to the agents performs similarly to asking questions both to the agents and the chair, although questions to the chair do have a positive value in terms of quality of the recommendation.
-%the value of information of one question to the chair is similar to the value of information of one question to a agent (in the ranges we considered), up to a certain proportion of questions asked to the chair.
-Knowing this permits to choose the questioning strategy wisely depending on the estimated cost of each kind of question, which depends on the application.
+%Second, the quality of the recommendation increases faster than linearly with the number of questions,  after an initial phase with almost no increase in quality, before slowing down and converging to an optimal recommendation.
+%Third, we experimentally find out that asking questions only to the agents performs similarly to asking questions both to the agents and the chair, although questions to the chair do have a positive value in terms of quality of the recommendation.
+%Knowing this permits to choose the questioning strategy wisely depending on the estimated cost of each kind of question, which depends on the application.
 
-The paper is organized as follows. \Cref{sec:related} reviews the works related to our objective.
-\Cref{sec:background} provides the necessary background and \cref{sec:mmr} introduces the minimax criterion, a method that selects a winner that minimizes the worst possible regret.
+The paper is organized as follows. \Cref{sec:related} reviews the works related to our objective and
+\Cref{sec:background} provides the necessary background.
+In \cref{sec:mmr} we provide a method for robust winner determination using the minimax criterion.
+%, a method that selects a winner that minimizes the worst possible regret.
 In Section \ref{sec:elicit} we provide an interactive elicitation protocol based on minimal regret;  Section \ref{sec:experiments} presents an experimental validation of our approach and some guidelines stemming from these simulations; and Section \ref{sec:conclusions} provides some final thoughts.
@@
 
-%They also showed that, even though this computation is hard in the general case, their method is polynomial in case of positional scoring rule. 
-%Later on, for the necessary winner problem, other authors have proposed polynomial-time algorithms when using maximin and Bucklin \citep{Xia2008}; showed that the general case remains computationally hard even when restricting to single-peaked preferences \citep{Walsh2007}; proved sufficient conditions that ensure tractability \citep{Pini2007}.
-
 Thereafter, noticing that in many practical situations there would be too many possible winners but no necessary winners, the importance of proposing efficient elicitation strategies has been identified.
@@
 While most of the focus in the research community has been in dealing with incomplete agent preferences, 
-%Although more interest has been shown in the incompleteness of agent preferences, 
 another line of research has dealt with scenarios where it is instead the voting rule that is partially defined, but the preferences are given. 
@@
 suggest that regret-based elicitation is effective and allows to quickly reduce worst-case regret significantly.
-They also show that good quality (low regret) recommendations can be achieved short of knowing the weights precisely or the profile completely, in our setting.
+They also show that, in our setting, good quality (low regret) recommendations can be achieved short of knowing the weights precisely or the profile completely.
 %regret, but they also show that starting with zero knowledge became a pretentious approach really quickly when increasing the size of the problem.

### 2021-01-07 minimax.tex
pgfplots version
removing the paragraph about structure of the paper in the introduction

@@
 \usepackage{pgfplots}
+\pgfplotsset{compat=1.17}
 
@@
 
-The paper is organized as follows. \Cref{sec:related} reviews the works related to our objective and
-\Cref{sec:background} provides the necessary background.
+%NOTE: the structure of the article is perhaps self evident...
+%The paper is organized as follows. \Cref{sec:related} reviews the works related to our objective and
+%\Cref{sec:background} provides the necessary background.
 In \cref{sec:mmr} we provide a method for robust winner determination using the minimax criterion.
 %, a method that selects a winner that minimizes the worst possible regret.
-In Section \ref{sec:elicit} we provide an interactive elicitation protocol based on minimal regret;  Section \ref{sec:experiments} presents an experimental validation of our approach and some guidelines stemming from these simulations; and Section \ref{sec:conclusions} provides some final thoughts.
+%In Section \ref{sec:elicit} we provide an interactive elicitation protocol based on minimal regret;  Section \ref{sec:experiments} presents an experimental validation of our approach and some guidelines stemming from these simulations; and Section \ref{sec:conclusions} provides some final thoughts.
 
@@
 				at={(0.5,1.03)},
-				anchor=south
+				anchor=south,
 			},

### 2021-01-08 minimax.tex
new plot linearity

@@
 
+\begin{figure}
+	\caption{Average MMR after $k$ questions with Pessimistic strategy for different problem sizes.}
+	\label{fig:linearity}
+	\begin{tikzpicture}
+		\pgfplotsset{
+			every axis legend/.append style={
+				at={(0.5,1.03)},
+				anchor=south
+			},
+		}
+		\begin{axis}[
+			y=3.5,
+			legend columns=3,
+			xlabel=Number of Questions,
+			ylabel=Avg. Regret,
+			ytick={0,5,10,15,20,25,30},
+			xtick distance=100,
+			ytick distance=5,
+			xtick pos=left,
+			ymajorgrids=true,
+			ytick style={draw=none},
+			ymin=0,
+			ymax=31,
+			xmin=0,
+			xmax=1000,
+			yticklabels={0,5,10,15,20,25,30}]
+
+			\addlegendimage{mark=triangle*,teal,mark size=2}
+			\addlegendimage{mark=*,violet,mark size=2}
+			\addlegendimage{mark=square*,green,mark size=2}
+			\addlegendimage{mark=diamond*,red,mark size=2}
+			\addlegendimage{mark=halfsquare right*,brown,mark size=2}
+			\addlegendimage{mark=oplus*,blue,mark size=2}
+			\addlegendimage{mark=pentagon*,cyan,mark size=2}
+			\addlegendimage{mark=halfsquare left*,pink,mark size=2}
+			\addlegendimage{mark=halfsquare*,magenta,mark size=2}
+
+			\addplot[thick, mark=triangle*, mark size = {2}, mark indices = {35}, teal] table [x=k, y=5.10]{data/linearity.dat};
+			\addlegendentry{m=5, n=10}
+			\addplot[thick, mark=*, mark size = {2}, mark indices = {45}, violet] table [x=k, y=5.15]{data/linearity.dat};
+			\addlegendentry{m=5, n=15}
+			\addplot[thick, mark=square*, mark size = {2}, mark indices = {90}, green] table [x=k, y=5.20]{data/linearity.dat};
+			\addlegendentry{m=5, n=20}
+			\addplot[thick, mark=diamond*, mark size = {2}, mark indices = {150}, red] table [x=k, y=10.20]{data/linearity.dat};
+			\addlegendentry{m=10, n=20}
+			\addplot[thick, mark=oplus*, mark size = {2}, mark indices = {60}, blue] table [x=k, y=14.9]{data/linearity.dat};
+			\addlegendentry{m=14, n=9}
+			\addplot[thick, mark=halfsquare right*, mark size = {2}, mark indices = {60}, brown] table [x=k, y=skate]{data/linearity.dat};
+			\addlegendentry{skate m14n9}
+			\addplot[thick, mark=pentagon*, mark size = {2}, mark indices = {300}, cyan] table [x=k, y=10.30]{data/linearity.dat};
+			\addlegendentry{m=10, n=30}
+			\addplot[thick, mark=halfsquare left*, mark size = {2}, mark indices = {200}, pink] table [x=k, y=sushi]{data/linearity.dat};
+			\addlegendentry{sushi m10n30}
+			\addplot[thick, mark=halfsquare*, mark size = {2}, mark indices = {400}, magenta] table [x=k, y=15.30]{data/linearity.dat};
+			\addlegendentry{m=15, n=30}
+
+		\end{axis}
+	\end{tikzpicture}
+\end{figure}
+
 %\begin{figure}
-%	\caption{Average MMR after $k$ questions with Pessimistic strategy for different problem sizes.}
+%	\caption{Logarithmic plot representing the MMR reduction after $k$ questions with Pessimistic strategy for different problem sizes.}
 %	\label{fig:linearity}
@@
 %				at={(0.5,1.03)},
-%				anchor=south
+%				anchor=south,
 %			},
 %		}
-%		\begin{axis}[
-%			y=3.5,
+%		\begin{semilogyaxis}[
 %			legend columns=3,
@@
 %			ylabel=Avg. Regret,
-%			ytick={0,5,10,15,20,25,30,35,146},
-%			xtick distance=100,
-%			ytick distance=5,
-%			xtick pos=left,
+%			log basis y= 10,
+%			ymin=10e-2,
+%			ymax=10e2,
+%			ytick={10e-2,1,2,10,15,20,30,146},
+%			yticklabels={0.01,1,2,10,15,20,30,146},
 %			ymajorgrids=true,
 %			ytick style={draw=none},
-%			ymin=0,
-%			ymax=146,
 %			xmin=0,
 %			xmax=1000,
-%			yticklabels={0,5,10,15,20,25,30,35,146}]
+%			xtick={0,100,200,300,400,500,600,700,800,900,1000},
+%			xticklabels={0,100,200,300,400,500,600,700,800,900,1000},
+%			ticklabel style = {font=\tiny}
+%			]
 %			
@@
 %			
-%			\addplot[thick, mark=triangle*, mark size = {2}, mark indices = {35}, teal] table [x=k, y=5.10]{data/linearity.dat};
+%			\addplot[thick, mark=triangle*, mark size = {2}, mark indices = {35}, teal, domain=-5:5] table [x=k, y=5.10]{data/linearity.dat};
 %			\addlegendentry{m=5, n=10}
-%			\addplot[thick, mark=*, mark size = {2}, mark indices = {45}, violet] table [x=k, y=5.15]{data/linearity.dat};
+%			\addplot[thick, mark=*, mark size = {2}, mark indices = {45}, violet,domain=-5:5] table [x=k, y=5.15]{data/linearity.dat};
 %			\addlegendentry{m=5, n=15}
@@
 %			\addlegendentry{courses}
-%		\end{axis}
+%		\end{semilogyaxis}
 %	\end{tikzpicture}
 %\end{figure}
-
-\begin{figure}
-	\caption{Logarithmic plot representing the MMR reduction after $k$ questions with Pessimistic strategy for different problem sizes.}
-	\label{fig:linearity}
-	\begin{tikzpicture}
-		\pgfplotsset{
-			every axis legend/.append style={
-				at={(0.5,1.03)},
-				anchor=south,
-			},
-		}
-		\begin{semilogyaxis}[
-			legend columns=3,
-			xlabel=Number of Questions,
-			ylabel=Avg. Regret,
-			log basis y= 10,
-			ymin=10e-2,
-			ymax=10e2,
-			ytick={10e-2,1,2,10,15,20,30,146},
-			yticklabels={0.01,1,2,10,15,20,30,146},
-			ymajorgrids=true,
-			ytick style={draw=none},
-			xmin=0,
-			xmax=1000,
-			xtick={0,100,200,300,400,500,600,700,800,900,1000},
-			xticklabels={0,100,200,300,400,500,600,700,800,900,1000},
-			ticklabel style = {font=\tiny}
-			]
-
-			\addlegendimage{mark=triangle*,teal,mark size=2}
-			\addlegendimage{mark=*,violet,mark size=2}
-			\addlegendimage{mark=square*,green,mark size=2}
-			\addlegendimage{mark=diamond*,red,mark size=2}
-			\addlegendimage{mark=pentagon*,cyan,mark size=2}
-			\addlegendimage{mark=halfsquare*,magenta,mark size=2}
-			\addlegendimage{mark=halfsquare right*,brown,mark size=2}
-
-			\addplot[thick, mark=triangle*, mark size = {2}, mark indices = {35}, teal, domain=-5:5] table [x=k, y=5.10]{data/linearity.dat};
-			\addlegendentry{m=5, n=10}
-			\addplot[thick, mark=*, mark size = {2}, mark indices = {45}, violet,domain=-5:5] table [x=k, y=5.15]{data/linearity.dat};
-			\addlegendentry{m=5, n=15}
-			\addplot[thick, mark=square*, mark size = {2}, mark indices = {90}, green] table [x=k, y=5.20]{data/linearity.dat};
-			\addlegendentry{m=5, n=20}
-			\addplot[thick, mark=diamond*, mark size = {2}, mark indices = {150}, red] table [x=k, y=10.20]{data/linearity.dat};
-			\addlegendentry{m=10, n=20}
-			\addplot[thick, mark=pentagon*, mark size = {2}, mark indices = {300}, cyan] table [x=k, y=10.30]{data/linearity.dat};
-			\addlegendentry{m=10, n=30}
-			\addplot[thick, mark=halfsquare*, mark size = {2}, mark indices = {400}, magenta] table [x=k, y=15.30]{data/linearity.dat};
-			\addlegendentry{m=15, n=30}
-			\addplot[thick, mark=halfsquare right*, mark size = {2}, mark indices = {400}, brown] table [x=k, y=courses]{data/linearity.dat};
-			\addlegendentry{courses}
-		\end{semilogyaxis}
-	\end{tikzpicture}
-\end{figure}
 

### 2021-01-08 minimax.tex
fix leg figure2

@@
 \usepackage{pgfplots}
-\pgfplotsset{compat=1.17}
+%\pgfplotsset{compat=1.17}
 
@@
 			\addlegendimage{mark=diamond*,red,mark size=2}
+			\addlegendimage{mark=halfsquare left*,blue,mark size=2}
 			\addlegendimage{mark=halfsquare right*,brown,mark size=2}
-			\addlegendimage{mark=oplus*,blue,mark size=2}
 			\addlegendimage{mark=pentagon*,cyan,mark size=2}
-			\addlegendimage{mark=halfsquare left*,pink,mark size=2}
 			\addlegendimage{mark=halfsquare*,magenta,mark size=2}
@@
 			\addlegendentry{m=10, n=20}
-			\addplot[thick, mark=oplus*, mark size = {2}, mark indices = {60}, blue] table [x=k, y=14.9]{data/linearity.dat};
+			\addplot[thick, mark=halfquare left*, mark size = {2}, mark indices = {60}, blue] table [x=k, y=14.9]{data/linearity.dat};
 			\addlegendentry{m=14, n=9}
@@
 			\addlegendentry{m=10, n=30}
-			\addplot[thick, mark=halfsquare left*, mark size = {2}, mark indices = {200}, pink] table [x=k, y=sushi]{data/linearity.dat};
-			\addlegendentry{sushi m10n30}
 			\addplot[thick, mark=halfsquare*, mark size = {2}, mark indices = {400}, magenta] table [x=k, y=15.30]{data/linearity.dat};

### 2021-01-09 cover letter/resubmission.tex
Canvas

@@
-\documentclass[a4paper]{article}
-\input{../preamble/packages}
+\RequirePackage[l2tabu, orthodox]{nag}
+\documentclass[version=3.21, pagesize, twoside=off, bibliography=totoc, DIV=calc, fontsize=12pt, a4paper]{scrartcl}
+\input{preamble/packages}
+\input{preamble/redac}
+\input{preamble/math_basics}
+\input{preamble/math_mine}
 \usepackage{pdfpages}
 
+%I find these settings useful in draft mode. Should be removed for final versions.
+	%Which line breaks are chosen: accept worse lines, therefore reducing risk of overfull lines. Default = 200.
+		\tolerance=2000
+	%Accept overfull hbox up to...
+		\hfuzz=2cm
+	%Reduces verbosity about the bad line breaks.
+		\hbadness 5000
+	%Reduces verbosity about the underful vboxes.
+		\vbadness=1300
+
+\title{Resubmission: Simultaneous Elicitation of Scoring Rule and Agent Preferences for Robust Winner Determination}
+\author{Submission ID: 554, AAMAS-2021}
 \date{}
-
-\title{Resubmission \\ \vspace{1cm} \textbf{\Large Simultaneous Elicitation of Scoring Rule and Agent Preferences for Robust Winner Determination} \\ {\large Submission ID: 554, AAMAS-2021}}
+\hypersetup{
+	pdfsubject={Cover letter},
+	pdfkeywords={elicitation},
+}
 
@@
 \section{Rejected paper AAMAS-2021}
-\includepdf[pages=-]{aamas21_paper_554.pdf}
+%\includepdf[pages=-]{aamas21_paper_554.pdf}
+
+%\bibliography{bibl}
 

### 2021-01-09 cover letter/cover_letter.tex
main file directive
Wrote cover; moved rebuttal

@@
-(Rebuttal)\\
-Our proposal is methodologically innovative: it addresses in a new way the difficult problem of eliciting preferences about voting rules.
-It opens up a novel path to gather and exploit preferential information about voting rules, in parallel with more classical preferential information about the alternatives under scrutiny.
-As a result, multiple challenging research questions open up, several of which are raised by the reviewers.
-We warmly thank them for these observations.
+% !TEX root = resubmission.tex
 
-As reviewer 1 points out, one could simply ask for direct information about the parameters of the rules, such as the weight vector.
-But it is unclear whether the answers to such questions would be meaningful.
-For example, in many cases, the chair (supposed to be human) may not know whether the largest weight should be twice, or three times, the weight associated with the second rank.
+Dear editors and reviewers,
 
-We ask the chair which alternative should win given a concrete profile.
-Such questions have precise semantics whose understanding is shared by the chair.
-This way of asking questions is sufficiently natural that it has been used in experimental settings investigating the feeling of justice of individuals (Does majoritarian approval matter in selecting a social choice rule?
-An exploratory panel study, Ebru Giritligil and Sertel, Social Choice and Welfare 25(1):43-73, 2005).
-To the best of our knowledge, the use of such questions to systematically guide an elicitation process is novel.
-We will highlight this aspect in the paper.
+We have submitted this article for the first time for IJCAI 2020.
+The reviewer’s evaluations of it were: from R1, Accept (good paper, I can argue for accepting it); from R2, Weak accept (marginally above the acceptance theshold, rejecting it would not be that bad); from R3, Weak reject (marginally below the acceptance threshold, accepting it would not be that bad); and from R4, Reject (Not good enough, I can argue for rejecting it).
+The strongest criticisms from the last two reviewers were, from R3, to improve presentation with a larger example and to expand the discussion (R3 incorrectly thought that we had room to spare within the constraints imposed by IJCAI); and from R4, that our literature review omitted important related works; that the results in the paper were incremental in nature; and that it was almost impossible to find the main contribution or take away message from the paper.
+The metareview pointed out that “One might view the work as somewhat incremental, but there is some substantial solid work here”; but recommended rejection because of 1) the very brief discussion of the empirical evaluation and 2) the incomplete literature review.
+The metareviewer also commented that “after some further work on the paper there's a reasonable chance that it could be accepted for another high quality conference.”
 
-Our approach is analogous to that of decision theorists with preference elicitation: a large stream of research considers more meaningful to ask direct choice questions ("please choose either a or b") than to question the decision maker about the shape of its utility function.
-The former are considered "observable": acts of choice are translated to preference statements.
-
-Concerning the hypothesis of convexity raised by reviewer 1, we need to assume that we look for a function inside a specific class of functions (here, the scoring rules with convex weights) because the class of all possible functions is too large.
-This allows for mixing an axiomatic basis with more precise "observable" questions; again, as it is usually done in decision theory (which often assumes the Subjective Expected Utility axioms).
-The use of convex weights is a natural and common assumption: losing ranks at the top of the ranking is more damaging than losing ranks at the bottom.
-
-A concrete application of our work might be a committee that is about to hire a new employee, whose performances are evaluated by several experts.
-The members of the committee may not have a voting rule in mind at the start of the process, and might not wish to agree on a specific voting rule, but they might be willing to answer enough questions about selecting winners out of specific profiles to determine their employee of choice.
-
-Regarding the experimental concerns addressed by reviewer 1, our strategies and setting are meant to tackle small scale social choice situations such as just exemplified.
-Our questioning method, in particular, does not scale to hundreds of candidates because the chair must be assumed to have limited cognitive capacity.
-
-IC is a quite challenging situation: as can be expected intuitively (and shown experimentally by Lu and Boutilier in their setting), the number of questions to be asked decrease with less varied profiles.
-We want to focus on the most critical setting, as there is a wide variety of possible situations to test in such experiments.
-
-The reviewers are right to point out that our comments about Table 3 were overconfident, this will be corrected.
-
-Reviewer 1 Question6 : We should have written “given to c the ranks 3 and m” instead of (3, m) in the proof of Claim 4.
-
-Reviewer 2 Question2: The $\lambda$-range is initialized to [1,n] because $\lambda \geq1$ by convexity and we assume $\lambda \leq n$ wlog: for $\lambda \geq n$, the rule coincides with Plurality.
-
-Regarding the guarantees concerns raised by reviewer 2: The general lack of theoretical guarantees with respect to the number of questions in the literature adopting minimax regret approaches suggest that obtaining such results is very difficult, if possible.
-However, our approach guarantees to return the true winners when the elicitation is completed.
-Note that the process can be terminated early, and offers a guaranteed bound on the regret at any time.
-
-Reviewer 2 Question1: At the start of the elicitation, the space of uncertainty is so large that the adversary can attain the maximum possible value of regret; multiple answers are needed to constrain her enough for the MMR to start decreasing.
-When approaching optimality, the pace of MMR reduction decreases.
-
-Reviewer 3 Question1: We did not investigate a systematic way of mixing strategies but we manually mixed different ideas in order to obtain the strategies we presented.
-For example Two phase and Extended Pessimistic reuse ideas present in the Pessimistic strategy.
+We extended very significantly the literature review and the experimental section, also taking advantage of two supplementary pages, and re-submitted the work for AAMAS 2021.
+The evaluations were: from R1 and R2, poor (4, good attempt but too many concerns, so probably should be rejected); and from R3, good (7, probably should be accepted).
+R1 considered our theoretical results as relatively simple extensions of the results of Lu and Boutilier and found the experimental results quite preliminary.
+About the first point, R1 stated to be unable to think about an example of a setting where our proposition would apply.
+After rebuttal, R1 stated that the example we provided in our response was convincing, but insisted that we need to test our heuristics beyond the impartial culture hypothesis.
+About experiments, R1 regretted that we use only impartial culture assumption; that we look at very small elections only; and that the way some of our conclusions are phrased make them appear more general than allowed by the experimental observations.
+R2 criticized the lack of theoretical guarantees for the proposed elicitation strategies, as well as the missing reasoning behind several of the experimental observations.
+After rebuttal, R2 took note of our observation that obtaining theoretical guarantees is generally considered beyond reach in a regret minimization setting; but insisted that experimental analysis should be presented by first formulating hypotheses to be tested, then showing how the experiments support or refute those hypotheses.
+Finally, R3, similarly to R1, found unclear which sorts of situations would permit an application of our proposed approach.

### 2021-01-09 cover letter/resubmission.tex
Wrote cover; moved rebuttal

@@
 
+\begin{abstract}
+Social choice deals with the problem of determining a consensus choice from the preferences of different agents.
+In the classical setting, the voting rule is fixed beforehand and full information concerning the preferences of the agents is provided.
+This assumption of full preference information has recently been questioned by a number of researchers and
+	several methods for eliciting the preferences of the agents have been proposed.
+	%  are completely known have been proposed, as well as techniques that consider the opposite scenario.
+
+In this paper we argue that in many situations one should consider as well the voting rule to be 	partially specified.
+%	This article goes one step further by tackling one important new case, namely, when both the voting rule and the agents preferences are partially known.
+It also permits to obtain a progressively refined recommendation without requiring to achieve full knowledge of either sort of information.
+%This is useful because providing such information is often costly: the chair may find it hard to specify a rule completely; agents may need time to form reflective preferences.	
+	Focusing on positional scoring rules, we assume that the chair, while not able to give a precise definition of the rule, is capable of answering simple questions requiring to pick a winner from a specific example profile.
+In addition, we assume that the agent preferences have to be elicited as well and are acquired by asking comparison queries.
+	We propose a method for robust approximate winner determination and interactive elicitation based on minimax regret; we develop several strategies for choosing the questions to ask to  the chair and the agents in order to %acquire the most relevant information for
+converge quickly to a near-optimal alternative. Finally, we analyze these strategies in experiments %in order to validate our approach
+ %focusing on settings 
+ where the voting rule and the preferences are simultaneously elicited.
+ %and obtain practical guidelines.
+\end{abstract}
+
 \section{Cover Letter}
@@
 \input{reviews_aamas.tex}
+
+\subsection{Our rebuttal}
+Our proposal is methodologically innovative: it addresses in a new way the difficult problem of eliciting preferences about voting rules.
+It opens up a novel path to gather and exploit preferential information about voting rules, in parallel with more classical preferential information about the alternatives under scrutiny.
+As a result, multiple challenging research questions open up, several of which are raised by the reviewers.
+We warmly thank them for these observations.
+
+As reviewer 1 points out, one could simply ask for direct information about the parameters of the rules, such as the weight vector.
+But it is unclear whether the answers to such questions would be meaningful.
+For example, in many cases, the chair (supposed to be human) may not know whether the largest weight should be twice, or three times, the weight associated with the second rank.
+
+We ask the chair which alternative should win given a concrete profile.
+Such questions have precise semantics whose understanding is shared by the chair.
+This way of asking questions is sufficiently natural that it has been used in experimental settings investigating the feeling of justice of individuals (Does majoritarian approval matter in selecting a social choice rule?
+An exploratory panel study, Ebru Giritligil and Sertel, Social Choice and Welfare 25(1):43-73, 2005).
+To the best of our knowledge, the use of such questions to systematically guide an elicitation process is novel.
+We will highlight this aspect in the paper.
+
+Our approach is analogous to that of decision theorists with preference elicitation: a large stream of research considers more meaningful to ask direct choice questions ("please choose either a or b") than to question the decision maker about the shape of its utility function.
+The former are considered "observable": acts of choice are translated to preference statements.
+
+Concerning the hypothesis of convexity raised by reviewer 1, we need to assume that we look for a function inside a specific class of functions (here, the scoring rules with convex weights) because the class of all possible functions is too large.
+This allows for mixing an axiomatic basis with more precise "observable" questions; again, as it is usually done in decision theory (which often assumes the Subjective Expected Utility axioms).
+The use of convex weights is a natural and common assumption: losing ranks at the top of the ranking is more damaging than losing ranks at the bottom.
+
+A concrete application of our work might be a committee that is about to hire a new employee, whose performances are evaluated by several experts.
+The members of the committee may not have a voting rule in mind at the start of the process, and might not wish to agree on a specific voting rule, but they might be willing to answer enough questions about selecting winners out of specific profiles to determine their employee of choice.
+
+Regarding the experimental concerns addressed by reviewer 1, our strategies and setting are meant to tackle small scale social choice situations such as just exemplified.
+Our questioning method, in particular, does not scale to hundreds of candidates because the chair must be assumed to have limited cognitive capacity.
+
+IC is a quite challenging situation: as can be expected intuitively (and shown experimentally by Lu and Boutilier in their setting), the number of questions to be asked decrease with less varied profiles.
+We want to focus on the most critical setting, as there is a wide variety of possible situations to test in such experiments.
+
+The reviewers are right to point out that our comments about Table 3 were overconfident, this will be corrected.
+
+Reviewer 1 Question6 : We should have written “given to c the ranks 3 and m” instead of (3, m) in the proof of Claim 4.
+
+Reviewer 2 Question2: The $\lambda$-range is initialized to [1,n] because $\lambda \geq1$ by convexity and we assume $\lambda \leq n$ wlog: for $\lambda \geq n$, the rule coincides with Plurality.
+
+Regarding the guarantees concerns raised by reviewer 2: The general lack of theoretical guarantees with respect to the number of questions in the literature adopting minimax regret approaches suggest that obtaining such results is very difficult, if possible.
+However, our approach guarantees to return the true winners when the elicitation is completed.
+Note that the process can be terminated early, and offers a guaranteed bound on the regret at any time.
+
+Reviewer 2 Question1: At the start of the elicitation, the space of uncertainty is so large that the adversary can attain the maximum possible value of regret; multiple answers are needed to constrain her enough for the MMR to start decreasing.
+When approaching optimality, the pace of MMR reduction decreases.
+
+Reviewer 3 Question1: We did not investigate a systematic way of mixing strategies but we manually mixed different ideas in order to obtain the strategies we presented.
+For example Two phase and Extended Pessimistic reuse ideas present in the Pessimistic strategy.
 

### 2021-01-09 cover letter/resubmission.tex
Structure cover and improvements

@@
 
-\title{Resubmission: Simultaneous Elicitation of Scoring Rule and Agent Preferences for Robust Winner Determination}
-\author{Submission ID: 554, AAMAS-2021}
+\title{Cover letter}
+\subtitle{Simultaneous Elicitation of Scoring Rule and Agent Preferences for Robust Winner Determination}
+\author{}
 \date{}
@@
 
-\section{Cover Letter}
-\input{cover_letter.tex}
+\section{Summary of previous criticisms and our corrections}
+\commentOC{See \href{https://ijcai-21.org/cfp/}{CFP, Resubmissions}.}
 
-\section{Reviews AAMAS-2021}
-\input{reviews_aamas.tex}
+Dear editors and reviewers,
+
+We have submitted this article for the first time to IJCAI 2020 (TODO ID?).
+The reviewer’s evaluations of it were: from R1, Accept (good paper, I can argue for accepting it); from R2, Weak accept (marginally above the acceptance theshold, rejecting it would not be that bad); from R3, Weak reject (marginally below the acceptance threshold, accepting it would not be that bad); and from R4, Reject (Not good enough, I can argue for rejecting it).
+The strongest criticisms from the last two reviewers were, from R3, that we should improve presentation with a larger example and expand the discussion (R3 incorrectly thought that we had room to spare within the constraints imposed by IJCAI); and from R4, that our literature review omitted important related works; that the results in the paper were incremental in nature; and that it was almost impossible to find the main contribution or take away message from the paper.
+The metareview pointed out that “One might view the work as somewhat incremental, but there is some substantial solid work here”; but recommended rejection because of 1) the very brief discussion of the empirical evaluation and 2) the incomplete literature review.
+The metareviewer also commented that “after some further work on the paper there's a reasonable chance that it could be accepted for another high quality conference.”
+
+We extended very significantly the literature review and the experimental section, also taking advantage of two supplementary pages, and submitted the resulting work to AAMAS 2021 (with submission ID 554).
+The evaluations were: from R1 and R2, poor (4, good attempt but too many concerns, so probably should be rejected); and from R3, good (7, probably should be accepted).
+R1 considered our theoretical results as relatively simple extensions of the results of Lu and Boutilier and found the experimental results quite preliminary.
+About the first point, R1 stated to be unable to think about an example of a setting where our proposition would apply.
+(After rebuttal, R1 stated that the example we provided in our response was convincing.) 
+About experiments, R1 regretted that we use only impartial culture assumption; that we look at very small elections only; and that the way some of our conclusions are phrased make them appear more general than allowed by the experimental observations.
+R2 criticized the lack of theoretical guarantees for the proposed elicitation strategies, as well as the missing reasoning behind several of the experimental observations.
+After rebuttal, R2 took note of our observation that obtaining theoretical guarantees is generally considered beyond reach in a regret minimization setting; but insisted that experimental analysis should be presented by first formulating hypotheses to be tested, then showing how the experiments support or refute those hypotheses.
+Finally, R3, similarly to R1, found unclear which sorts of situations would permit an application of our proposed approach.
+The metareview stated that the paper misses novelty and that hypotheses are missing from the experimental section and experiments should not be limited to the impartial culture assumption.
+
+\section{Improvements}
+Compared to the submission to AAMAS 2021, and thanks to the reviews, we have brought the following changes to the article.
+
+\begin{itemize}
+	\item The introduction provides an example of a situation where our approach is applicable.
+	\item We better explain our motivation for asking questions that can be phrased as choices of winners out of a profile (which makes the answer “observable” in an econometric sense), and highlight the methodological novelty of this approach.
+	\item We integrated the Related Works section into the Introduction to save space, but kept all the references we added following the earlier criticisms about the missing references to the literature.
+	\item We went beyond impartial culture by testing our heuristics on real data.
+The results show that the number of questions to be asked is much smaller with real data than with impartial culture, as expected.
+	\item TODO We better explain what results can be anticipated before presenting the experimental results.
+	\item We changed the phrasing of some of our conclusions that were too general.
+\end{itemize}
+
+\section{Submission to AAMAS-2021}
+\subsection{Review 1}
+\subsubsection*{Summary:}	The authors use the notion of minimax regret to guide the process of preference elicitation in an election (they elicit both the voters' preferences and the preferences of the chair regarding the scoring rule used).
+The authors show that the methodology of Lu and Boutilier for computing minimax regret still applies in their setting and present some experimental results.
+\subsubsection*{Strengths:}	1) Minimax regret is a rather natural notion, which has not received much attention so far.
+\subsubsection*{Weaknesses:}
+1) The theoretical results are relatively simple extensions of the results of Lu and Boutilier
+\newline 2) The experimental results seem quite preliminary.
+
+\subsubsection*{Detailed comments:}	The paper is quite well written, clear, relevant for the conference.
+The biggest issues I have regard significance.
+The idea of using minimax regret to guide elicitation is very good, but is explored quite well by Lu and Boutilier.
+Here the authors extend this framework by eliciting the scoring rule used, but there is very little discussion as to why this really is such a good idea.
+I cannot easily think of a half-realistic setting where one would know that the scores need to be convex, but at the same time one would not know which ones exactly to use.
+
+More specific comments come below:
+\begin{enumerate}
+\item Related work \\
+As the paper is partially related to designing/choosing a scoring rule for a given setting---and as the problem of manipulation is mentioned---it might be worth to consider the following paper:
+
+Dorothea Baumeister, Tobias Hogrebe:
+Manipulative Design of Scoring Systems. AAMAS 2019: 1814-1816
+
+Regarding partial preferences and manipulation, one may also look at the following one (although it is less related, for sure):
+
+Dorothea Baumeister, Piotr Faliszewski, Jérôme Lang, Jörg Rothe:
+Campaigns for lazy voters: truncated ballots. AAMAS 2012: 577-584
+
+\item Concurrent elicitation of the scoring rule \\
+I am not really convinced that the assumption that a scoring rule is not known makes sense.
+On the one hand, there is the problem of choosing the scoring rule manipulatively (but since the authors mention that the elections at hand are built into recommendation systems etc., this is not really an issue).
+The other problem is that I can hardly think of a scenario where the chair can answer the questions about the scoring rule, but somehow it is difficult for him to produce the full rule in a single step.
+So what do we gain?
+
+\item Claims vs Propositions \\
+I do not understand why the authors use "Claims" and not "Propositions".
+
+\item I think that Claim 4 should say something along the lines: "There is a profile P', such that ... and P' can be computed effectively".
+
+\item I can hardly imagine a person who faced with the profile P' from Claim 4 could meaningfully answer if a is better than b or the other way round.
+A piece of software could do it, though---but probably by precomputing the scoring rule to use (which removed the need for eliciation).
+
+\item Proof of Claim 4: I do not understand notation (3,m) or (4,m-1) etc.
+
+\item Empirical evaluation is very preliminary
+I have a number of complaints regarding the evaluation process:
+	\begin{enumerate}
+		\item Why do the authors use IC only?
+Why not other statistical cultures?
+Why not some real-life data?
+After all, the experimental part is the main contribution of the paper and it is done in a fairly minimalistic way.
+
+		\item Why do the authors look at very small elections only? 15 candidates and 30 voters seems completely inadequate for the motivations from the introduction.
+
+		\item The conclusion that the number of questions required to reach low regret cannot be made based on Table 3.
+There is simply far too little data to have any sort of confidence in claims like this.
+	\end{enumerate}
+
+\end{enumerate}
+
+All in all, I think it is certainly a nice enough paper to be accepted as short, but is below the bar for the full acceptance.
+
+\subsubsection*{Questions for rebuttal:}
+Q1: Why did you only look at IC elections?
+\newline Q2: How to use your approach in large elections?
+Hundreds of candidates, thousands of voters?
+After all, showing a strategy that can deal with large elections would meaningfully extend the work of Lu and Boutilier?
+\newline Q3: Can you provide a realistic example where elicitation of the scoring rule is useful?
+\subsubsection*{Score:}	
+4: (poor (good attempt but too many concerns, so probably should be rejected))
+
+\subsubsection*{Comments added after rebuttal:}
+I found the example provided in the response to be convincing.
+
+I still think that testing the heuristics on IC only is insufficient.
+Even if it is the hardest case, I would also like to see how the algorithm peforms in the easier ones.
+Can it exploit the structure when the structure is present?
+One cannot evaluate such issues by looking at IC alone.
+
+\subsection{Review 2}
+\subsubsection*{Summary:}
+The paper studies a voting problem wherein neither the voting rule nor the voters' preferences are specified in advance.
+Rather, an elicitation procedure is used to determine the election winner by asking the voters questions about their preferences and asking the chair questions about the voting rule.
+
+Specifically, the preferences of the voters are assumed to be given by a fixed set of linear orders that are unknown to the elicitation platform.
+In addition, the voting rule is assumed to belong to the class of positional scoring rules with monotone weights with diminishing differences.
+The elicitation procedure comprises of the chair specifying the winning candidates on example profiles, and the voters responding to a series of pairwise comparisons.
+
+At each step, the minimax regret criterion (Lu and Boutilier, IJCAI'11) is used to determine the next query, and this procedure is continued until convergence (e.g., either the regret drops below a certain threshold or a certain number of questions have been asked).
+The regret of an alternative, informally speaking, is the "loss" incurred for picking that alternative instead of an "optimal" one under adversarial choice of completion of the partial preferences elicited so far as well as the worst-case choice of positional weights.
+
+The main contributions of the submission are:
+1. Proposing a framework for simultaneously eliciting voters' preferences and information about the voting rule based on the minimax regret criterion.
+2. Experimental comparison of a number of elicitation heuristics in terms of the number of questions asked or the regret value.
+
+The empirical observations suggest that a modest number of questions (to the voters as well as the chair) are sufficient in arriving at a reasonable choice, and that the regret drops super-linearly as a function of the number of questions asked over the course of elicitation.
+\subsubsection*{Strengths:}	The idea of modeling simultaneous uncertainty in the voting rule as well as the voters' preferences is quite interesting.
+It is also useful to know that the minimax regret framework of Lu and Boutilier (IJCAI'11), previously studied in the setting of a known voting rule, can be extended to the aforementioned more general problem.
+\subsubsection*{Weaknesses:}	The lack of theoretical guarantees for the proposed elicitation strategy, as well as missing reasoning behind several of the experimental observations, makes this a weak paper in my opinion.
+
+\subsubsection*{Detailed comments:}
+I like the high-level question asked by the paper, namely whether it is possible to simultaneously elicit the information about the voting rule and the voters' preferences.
+However, the significance of the contribution is less clear.
+The results, which largely comprise of experiments, are at the level of proposing a heuristic that seems to work well in simulations but lacks formal theoretical guarantees.
+
+I believe the paper will be much stronger if the authors could provide theoretical convergence guarantees for the proposed heuristics.
+Additionally, in the "Empirical Evaluation" section, instead of simply describing the observations, it would be useful to also formally state the hypotheses used in each experiment, and explain how the experiments support or refute those hypotheses.
+For example, you could describe whether (and why) one might expect "Pessimistic" strategy to work better than the "Elitist" strategy, and then discuss to what extent did the simulations confirm that hypothesis.
+
+Some minor comments are below.
+\begin{enumerate}
+\item Page 1
+\begin{itemize}
+	\item In several places you use the phrase "permits to" when it might be clearer to say "allows for".
+\end{itemize}
+
+\item Page 2
+\begin{itemize}
+	\item "that showed that"-->who showed that.
+\end{itemize}
+
+\item Page 3 
+\begin{itemize}
+	\item "there are no necessary winner"-->there is no necessary winner.
+\end{itemize}
+
+\item Page 4 
+\begin{itemize}
+	\item "less good than or equal to"-->You could rather say "weakly worse".
+	\item Using $\succeq^p_j(x)$ to denote the set of alternatives weakly worse than x can be confusing. Please consider using a different notation such as $A^(\succeq^p_j,x)$.
+\end{itemize}
+
+\item Page 5
+\begin{itemize}
+	\item Claim 4 is written in the form of a definition, and it is not clear what is actually being claimed here.
+Maybe you could say that "there exists a profile P' satisfying such and such properties".
+	\item "each of the p+q agent"-->each of the p+q agents
+	\item "worst than"-->worse than
+\end{itemize}
+
+\item Page 6 
+\begin{itemize}
+	\item "on order to"-->in order to
+	\item "an important weight"-->a large weight
+	\item "For generating the weights we first draw $m - 1$ numbers uniformly at random"-->What is the range from which you make the draws?
+\end{itemize}
+
+\item Page 7 
+\begin{itemize}
+	\item "In-dept evaluation"-->In-depth evaluation
+	\item Figure 1, X axis label should say "Number of questions"
+	\item "to be ran"-->to be run
+	\item "We see that the number of questions required to reach a low regret level grows approximately linearly with the number of agents"-->Can you provide a formal regression analysis to support this claim?
+\end{itemize}
+
+\item Page 8 
+\begin{itemize}
+	\item "allow to quickly"-->allows to quickly
+	\item "worst regret"-->worst-case regret
+	\item "that allows to reproduce our experiments, and more"-->It would be useful to mention the other benefits explicitly.
+	\item "halving the number of questions will only reduce the gain in regret by less than half"-->Might be clearer to say "halving the number of questions reduces the regret by more than 50$\%$".
+\end{itemize}
+
+\end{enumerate}
+\subsubsection*{Questions for rebuttal:}	1.
+On Page 1, you write that "The quality of the recommendation increases faster than linearly with the number of questions, after an initial phase with almost no increase in quality, before slowing down and converging to an optimal recommendation." What is the reasoning behind this trend?
+\newline 2. How did you decide the range of the parameter $\lambda$ to be [1,n]?
+\subsubsection*{Score:}	
+4: (poor (good attempt but too many concerns, so probably should be rejected))
+
+\subsubsection*{Comments added after rebuttal:}
+Thanks to the authors for responding to the questions raised in my review.
+My concern about the significance of the paper remains.
+In the absence of any formal theoretical guarantees about the performance of the elicitation heuristic, the paper will likely be of limited interest.
+The authors note that obtaining such guarantees could be difficult.
+Nevertheless, the paper could certainly benefit from a revised experimental analysis that clearly formulates the hypotheses to be tested and how the experiments support or refute those hypotheses.
+
+\subsection{Review 3}
+\subsubsection*{Summary:}
+This paper considers elicitation in the context of scoring rules when both the preferences of the voters and the weights defining the rule might be missing.
+The authors model the problem via regret minimization and propose several types of queries and querying strategies.
+The paper also presents an interesting experimental study which supports the presented approach.
+\subsubsection*{Strengths:}	The problem addressed is interesting and has potential for practical applicability.
+Addressing missing information in both voters and the chair’s preferences is novel. The experimental section is a good starting point.
+\subsubsection*{Weaknesses:}	The discussion on the motivation behind considering uncertainty on the scoring rule’s weights is not very convincing.
+They claim the chair might not be able to formalize the rule…
+Another point that is not clear is when, in practice a system like this would be deployed.
+The application of regret minimization is somewhat incremental w.r.t. the literature.
+
+\subsubsection*{Detailed comments:}	reference elicitation in the context of voting is certainly a relevant topic for AAMAS.
+The setting considered here is not per se novel, as elicitation of voters’ and the chair’s preferences have been considered before. The originality lies in considering them both at the same time.
+While this is original, the motivation of when such a setting may occur in practice is not clear.
+In particular, I wonder about the timing.
+It is assumed that voters and candidates are known, information about the voters preferences is available and yet the voting rule has not yet been decided and the elicitation process is going on at the same time.
+It seams unlikely to me.
+As I mentioned, I am also not very convinced about a chair not knowing which rule he wants/or is using while voters are expressing preferences.
+A much stronger argument would be that of a third party discovering information about a voter’s preferences and the rule by being able to observe results or to tap in and acquire some information.
+Obviously that would mean having much less control over what information is acquired than assumed here…it might be similar to random strategy studied in the experimental section.
+
+The content is technically not overly sophisticated, so I have no doubt about its soundness.
+The presentation flows well and all parts are clearly written. The description of the experimental results is also sufficiently detailed to enable reproducibility.
+
+A minor complaint is that Figures 1 and 2 are blurred.
+\subsubsection*{Questions for rebuttal:}
+1) Could testing mixed strategies yield better results than the pure ones?
+\subsubsection*{Score:}	
+7: (good (probably should be accepted))
+
+\subsection{Metareview}
+The main reason for the reject recommendation is the missing novelty in this paper.
+It basically is a reimplementation of the ideas from Lu and Boutilier.
+Furthermore, in the experimental section, clear hypotheses are missing and the reasons for limiting the analysis to IC are not convincing.
 
@@
 
-\section{Reviews IJCAI-20}
+\section{Submission to IJCAI 2020}
 \input{reviews_ijcai.tex}

### 2021-01-09 cover letter/resubmission.tex
More merge

@@
 
-\title{Cover letter}
-\subtitle{Simultaneous Elicitation of Scoring Rule and Agent Preferences for Robust Winner Determination}
-\author{}
+\title{Resubmission: Simultaneous Elicitation of Scoring Rule and Agent Preferences for Robust Winner Determination}
+\author{Submission ID: 554, AAMAS-2021}
 \date{}
@@
 
-\section{Summary of previous criticisms and our corrections}
-\commentOC{See \href{https://ijcai-21.org/cfp/}{CFP, Resubmissions}.}
-
+\section{Cover Letter}
 Dear editors and reviewers,
 
-We have submitted this article for the first time to IJCAI 2020 (TODO ID?).
+We have submitted this article for the first time for IJCAI 2020.
 The reviewer’s evaluations of it were: from R1, Accept (good paper, I can argue for accepting it); from R2, Weak accept (marginally above the acceptance theshold, rejecting it would not be that bad); from R3, Weak reject (marginally below the acceptance threshold, accepting it would not be that bad); and from R4, Reject (Not good enough, I can argue for rejecting it).
-The strongest criticisms from the last two reviewers were, from R3, that we should improve presentation with a larger example and expand the discussion (R3 incorrectly thought that we had room to spare within the constraints imposed by IJCAI); and from R4, that our literature review omitted important related works; that the results in the paper were incremental in nature; and that it was almost impossible to find the main contribution or take away message from the paper.
+The strongest criticisms from the last two reviewers were, from R3, to improve presentation with a larger example and to expand the discussion (R3 incorrectly thought that we had room to spare within the constraints imposed by IJCAI); and from R4, that our literature review omitted important related works; that the results in the paper were incremental in nature; and that it was almost impossible to find the main contribution or take away message from the paper.
 The metareview pointed out that “One might view the work as somewhat incremental, but there is some substantial solid work here”; but recommended rejection because of 1) the very brief discussion of the empirical evaluation and 2) the incomplete literature review.
@@
 
-We extended very significantly the literature review and the experimental section, also taking advantage of two supplementary pages, and submitted the resulting work to AAMAS 2021 (with submission ID 554).
+We extended very significantly the literature review and the experimental section, also taking advantage of two supplementary pages, and re-submitted the work for AAMAS 2021.
 The evaluations were: from R1 and R2, poor (4, good attempt but too many concerns, so probably should be rejected); and from R3, good (7, probably should be accepted).
@@
 About the first point, R1 stated to be unable to think about an example of a setting where our proposition would apply.
-(After rebuttal, R1 stated that the example we provided in our response was convincing.) 
+After rebuttal, R1 stated that the example we provided in our response was convincing, but insisted that we need to test our heuristics beyond the impartial culture hypothesis.
 About experiments, R1 regretted that we use only impartial culture assumption; that we look at very small elections only; and that the way some of our conclusions are phrased make them appear more general than allowed by the experimental observations.
@@
 Finally, R3, similarly to R1, found unclear which sorts of situations would permit an application of our proposed approach.
-The metareview stated that the paper misses novelty and that hypotheses are missing from the experimental section and experiments should not be limited to the impartial culture assumption.
 
-\section{Improvements}
-Compared to the submission to AAMAS 2021, and thanks to the reviews, we have brought the following changes to the article.
-
-\begin{itemize}
-	\item The introduction provides an example of a situation where our approach is applicable.
-	\item We better explain our motivation for asking questions that can be phrased as choices of winners out of a profile (which makes the answer “observable” in an econometric sense), and highlight the methodological novelty of this approach.
-	\item We integrated the Related Works section into the Introduction to save space, but kept all the references we added following the earlier criticisms about the missing references to the literature.
-	\item We went beyond impartial culture by testing our heuristics on real data.
-The results show that the number of questions to be asked is much smaller with real data than with impartial culture, as expected.
-	\item TODO We better explain what results can be anticipated before presenting the experimental results.
-	\item We changed the phrasing of some of our conclusions that were too general.
-\end{itemize}
-
-\section{Submission to AAMAS-2021}
-\subsection{Review 1}
+\section{Reviews AAMAS-2021}
+\subsection*{Review 1}
 \subsubsection*{Summary:}	The authors use the notion of minimax regret to guide the process of preference elicitation in an election (they elicit both the voters' preferences and the preferences of the chair regarding the scoring rule used).
@@
 
-\subsection{Review 2}
+\subsection*{Review 2}
 \subsubsection*{Summary:}
@@
 
-\subsection{Review 3}
+\subsection*{Review 3}
 \subsubsection*{Summary:}
@@
 
-\subsection{Metareview}
+\subsection*{Metareview}
 The main reason for the reject recommendation is the missing novelty in this paper.
@@
 
-\section{Submission to IJCAI 2020}
+\section{Reviews IJCAI-20}
 \input{reviews_ijcai.tex}

### 2021-01-09 cover letter/resubmission.tex
More integration into cover letter

--- 2021-01-09 cover letter/resubmission.tex
@@
 \end{itemize}
+
+\section{Submission to IJCAI 2020}
+\subsection{Review 1}
+\subsubsection*{Overall score}
+Accept (good paper. I can argue for accepting it)
+\subsubsection*{Comments to authors}
+The paper makes a substantial contribution to social choice, which has clear implications for AI applications whenever a consensus result is needed.
+
+In the first part, a method of robust winner determination is derived, relying on the minimax (regret) principle.
+This part is written concisely, but still quite comprehensively.
+Each step follows logically from the previous one.
+
+The second part (Section 4) reflects on concrete elicitation procedures, which, of course, are highly relevant for practical use.
+At least for me, this part was much harder to read.
+Admittedly, one has to look at many details, but maybe some additional meta sentences summarizing the basic ideas would be highly appreciated.
+
+Some details:
+
+* Please be more precise with using the word 'robust'. Robustness is always robustness against something.
+
+* typos etc : please check the genitive: agents''''''''' preferences,
+p1 recent work? 2005,
+sd standard deviation?
+check the reference for double doi/link, superfluous ISSN
+
+\subsubsection*{Why should this paper be presented at IJCAI-PRICAI 2020?}
+As just said, the paper makes a substantial contribution to the general issue of how to arrive at a consensus choice, a question that is not only theoretically interesting but also of broader practical relevance.
+The novelty of the paper lies in the low structure of the setting: both the voting rule as well as the agents' preferences are only partially specified.
+This expands considerably the range of potential applications.
+
+\subsection{Review 2}
+\subsubsection*{Overall score}
+Weak Accept (marginally above the acceptance threshold. Rejecting it would not be that bad)
+\subsubsection*{Comments to authors}
+This paper examines a social choice problem where agent preferences and the criteria for aggregating preferences across agents are partially specified.
+The paper provides theory for representing partial preferences, enumerating consistent total preference orders, aggregating such preferences across agents, and determining a winner per a model that minimizes worst case regret.
+The paper examines strategies for querying agents and the chair (arbiter of social choice) to elicit their preferences/aggregation criteria.
+It reports minimum worst case regret as a function of the number of elicitation questions across several strategies.
+
+The paper provides a thorough mathematical development, and clearly identifies contrasting elicitation strategies.
+The text provides clear descriptions of the required set manipulations, which would otherwise be hard to parse.
+
+The abstract would be stronger if it motivated the simultaneous elicitation task.
+The introductory material would appeal to more readers if it clarified the task by defining the roles of agents, the chair, the concept of regret in social choice scenarios, and the meaning of minimax-optimal alternatives.
+The paper does not have a separate related work section, and while it cites appropriate work, the alternatives to this approach could use more discussion.
+The paper presents, but does not discuss the experimental results, and it would be much stronger if the authors provided that analysis/interpretation.
+As it stands, it is unclear what the work is teaching us.
+\subsubsection*{Why should this paper be presented at IJCAI-PRICAI 2020?}
+Research on voting strategies and preference elicitation relates to real-world problems of interest.
+The extension to simultaneous elicitation of partially specified agent and chair preferences is sound, and relevant to the broader inquiry.
+
+\subsection{Review 3}
+\subsubsection*{Overall score}
+Weak Reject (marginally below the acceptance threshold. Accepting it would not be that bad)
+\subsubsection*{Comments to authors}
+This paper develops a minimax regret decision approach when preferences and voting rules are partly specified.
+The paper seems technically correct, however, the presentation would be improved with a larger example.
+Also, the evaluation discussion in section 5 could be expanded as there is room in the paper within a 7 page limit.
+
+\subsection{Review 4}
+\subsubsection*{Overall score}
+Reject (Not good enough. I can argue for rejecting it)
+\subsubsection*{Comments to authors}
+The authors study the problem of winner determination when both the voting rule and voters' preferences are not fully determined.
+They propose an interactive elicitation protocol and query strategies for the minimax regret rule.
+In particular, they focus on minimax regret version of the positional scoring rule to aggregate incomplete preferences.
+The main contribution of the paper is to simultaneously consider both partial information about the agents’ preferences and partial
+specification of aggregation method. Both partial information about the agents’ preferences and partial specification of aggregation method have been studied separately in the literature.
+
+My main concern is that the authors ignores (or unaware of) almost entire literature on both preference elicitation and voting with incomplete preferences.
+Few examples (not at all exhaustive) of vast related work with whom the authors must compare and position their work are as follows.
+\begin{itemize}
+	\item Palash Dey, Neeldhara Misra, and Y. Narahari. Complexity of manipulation with partial information in voting. Theor. Comput. Sci., 726:78–99, 2018.
+	\item Ulle Endriss, Svetlana Obraztsova, Maria Polukarov, and Jeffrey S.
+Rosenschein.
+Strategic voting with incomplete information.
+In Proc.
+the Twenty-Fifth International Joint Conference on Artificial Intelligence, IJCAI 2016, New York, NY, USA, 9-15 July 2016, pages 236–242, 2016.
+	\item Omer Lev, Reshef Meir, Svetlana Obraztsova, and Maria Polukarov.
+Heuristic voting as ordinal dominance strategies.
+In Proc.
+The Thirty-Third AAAI Conference on Artificial Intelligence, AAAI 2019,
+	\item The Thirty-First Innovative Applications of Artificial Intelligence Conference, IAAI 2019, The Ninth AAAI Symposium on Educational Advances in Artificial Intelligence, EAAI 2019, Honolulu, Hawaii, USA, January 27 - February 1, 2019, pages 2077–2084, 2019.
+	\item Reshef Meir. Plurality voting under uncertainty. In Proc. Twenty-Ninth AAAI Conference on Artificial Intelligence, January 25-30, 2015, Austin, Texas, USA, pages 2103–2109, 2015.
+	\item Annemieke Reijngoud and Ulle Endriss.
+Voter response to iterated poll information.
+In International Conference on Autonomous Agents and Multiagent Systems, AAMAS 2012, Valencia, Spain, June 4-8, 2012 (3 Volumes), pages 635–644, 2012.
+	\item Palash Dey: Manipulative elicitation - A new attack on elections with incomplete preferences. Theor. Comput. Sci. 731: 36-49 (2018)
+	\item Vincent Conitzer: Eliciting Single-Peaked Preferences Using Comparison Queries. J. Artif. Intell. Res. 35: 161-191 (2009)
+	\item Palash Dey, Neeldhara Misra: Elicitation for Preferences Single Peaked on Trees. IJCAI 2016: 215-221
+	\item Palash Dey, Neeldhara Misra: Preference Elicitation for Single Crossing Domain. IJCAI 2016: 222-228
+\end{itemize}
+
+Also the results in the paper, in my opinion, in incremental in nature.
+I also found the writing style of the paper quite odd.
+For example, it is almost impossible to find the main contribution or take away message from the paper.
+Overall I think that the paper may contain some interesting results worth publishing but it has to be positioned correctly with respect to existing literature.
+The authors could also consider explicitly writing a bulleted list of contribution with pointers to parts of the paper that prove/discuss it.
+
+\subsection{Metareview}
+The paper combines ideas from [Lu and Boutilier, 2011] and [Viappiani, 2018], and builds on other work on minimax regret-based preference elicitation, to generate an interactive elicitation approach for a situation in which there is incomplete knowledge about both (a) the voters' preference orders and (b) the weights of a positional scoring rule that generates the overall winner.
+Given those two earlier papers, this is a natural further step to make, and the paper successfully develops the previous approaches.
+One might view the work as somewhat incremental, but there is some substantial solid work here.
+
+There are some other issues, pointed out by the reviewers.
+The discussion of the empirical evaluation is very brief.
+There is a substantial body of literature that was not cited, related to preference elicitation and incomplete preferences in a voting situation.
+Although they do not seem to be on exactly the same topic, it is important that the paper is positioned correctly with respect to the existing literature.
+
+Because of these issues, I'm recommending rejection of the paper.
+However, I think after some further work on the paper there's a reasonable chance that it could be accepted for another high quality conference.
 
@@
 
-\section{Submission to IJCAI 2020}
-\input{reviews_ijcai.tex}
-
-\section{Rejected paper AAMAS-2021}
+\section{Rejected paper AAMAS 2021}
+You will find here below the version of this article that was submitted to AAMAS 2021.
 %\includepdf[pages=-]{aamas21_paper_554.pdf}
-
-%\bibliography{bibl}
-
 \end{document}

### 2021-01-10 minimax.tex
minimal changes introduction

@@
 
-\section{Related Work}
+\paragraph{Related Work}
 \label{sec:related}
 In the context of social choice, several authors have been interested in obtaining information about winners with reduced assumptions about the knowledge of the agent preferences (assuming that the voting rule is known).
-One early work is  by \Citet{Conitzer2005} who studied the complexity of communication, using different voting rules, determining lower and upper bounds; they showed that, in the worst case, the agents should send their complete set of preference for most of the rules they investigated.
+One early work is  by \Citet{Conitzer2005} who studied the complexity of communication, using different voting rules, determining lower and upper bounds; they showed that, in the worst case, the agents should send their complete set of preference for several rules.
 

### 2021-01-11 minimax.tex
proofs in appendix, rmv Table 4, new Figure 2

@@
 \usepackage{pgfplots}
-%\pgfplotsset{compat=1.17}
+\pgfplotsset{compat=1.16}
 
@@
 \end{proposition}
-\begin{proof*}[Sketch]
-	Consider our knowledge $\pprefeq_j$ about the preference of the agent $j$. 
-	The adversary's goal is to make the score of $y$ as high as possible and the score of $x$ as low as possible. 
-	To do this, he should complete $\ppref_j$ to $\pref_j$ by putting above $x$ as many alternatives as he can, that is, all the alternatives except those that are known to be worse than $x$ (those $a$ such that $x \pprefeq_j a$); and similarly, he should put below $y$ all the alternatives he can.
-Two conditions must be excluded for $a$ to go below $y$.
-The alternatives such that $a \pprefeq_j y$ can’t be put below $y$.
-	Furthermore, the first objective must take priority over the second one: when an alternative should go above $x$ according to the first objective (because $¬(x \pprefeq_j a)$), and $x$ is known to be better than $y$ (thus $x \pprefeq_j y$), then $a$ should be put above $x$ (irrespective of whether $a \pprefeq_j y$), which will move both $x$ and $y$ one rank lower than if $a$ had been put below $y$.
-	This maximizes the adversary’s interests: because the weight vector is convex, the difference of scores will be lower when both alternatives are ranked lower (Equation \ref{eq:convexity}), and that difference of scores is in favor of $x$ when $x \ppref_j y$, thus to be minimized from the point of view of the adversary.
-\end{proof*}
 
 Let ${\pprefeq_j}(x)$ designate the set of alternatives known to be considered by $j$ as less good than or equal to $x$, and ${\pprefinv_j}(y)$ be the set of alternatives known to be considered by $j$ as strictly better than $y$.
-\begin{proposition}
+\begin{proposition} \label{claim:rankPMR}
 	The rank of $x$ in the PMR-maximizing linear orders of agent $j$ is $\hat{v}_{j}(x) = 1+\card{A}-\card{{\pprefeq_j}(x)}$, and the rank of $y$ is $\hat{v}_{j}(y)=1+\card{{\pprefinv_j}(y)}+\card{\beta}$, where $\card{\beta} = \card{A \setminus ({\pprefeq_j}(x) \cup {\pprefinv_j}(y))}$ if $(x \pprefeq_j y)$ and $\card{\beta} = 0$ otherwise.
-	\label{claim:rankPMR}
 \end{proposition}
-\begin{proof*}
-	The rank of $x$ is directly obtained from \cref{eq:complx}.
-The rank of $y$ is obtained by complementing \cref{eq:comply}, obtaining $a \prefeq_j y ⇔ (a \pprefeq_j y) ∨ ((x \pprefeq_j y) ∧ ¬(x \pprefeq_j a))$, and, observing that $a \pref_j y ⇔ a ≠ y ∧ a \prefeq_j y$, obtaining that $a \pref_j y$ if and only if
-	\begin{equation}
-		\label{eq:betteryinter}
-		(a \neq y) ∧ [(a \pprefeq_j y) ∨ ((x \pprefeq_j y) ∧ ¬(x \pprefeq_j a))],
-	\end{equation} 
-	or equivalently, if and only if
-	\begin{equation}
-		\label{eq:bettery}
-		%a \pref_j y ⇔ 
-		(a \ppref_j y) ∨ ((x \pprefeq_j y) ∧ ¬(x \pprefeq_j a)).
-	\end{equation} 
-	Indeed, \eqref{eq:betteryinter} $⇒$ \eqref{eq:bettery}, and \eqref{eq:bettery} $⇒$ \eqref{eq:betteryinter} because $(x \pprefeq_j y) ∧ ¬(x \pprefeq_j a) ⇒ a ≠ y$ (as when $a = y$, $(x \pprefeq_j y)$ and $¬(x \pprefeq_j a)$ are opposite claims).
-Suffices now to rewrite \cref{eq:bettery} to let the two disjuncts designate disjoint sets:
-	\begin{equation}
-		\label{eq:betteryfinal}
-		a \pref_j y ⇔ 
-		(a \ppref_j y) ∨ ((x \pprefeq_j y) ∧ ¬(x \pprefeq_j a) ∧ ¬(a \ppref_j y)).
-	\end{equation}
-\end{proof*}
+
 The proposition can also be understood by observing that in the case $(x \pprefeq_j y)$, $\beta$ is the number of alternatives incomparable with both $x$ and $y$.
@@
 Thus, our task is to build a profile, given $\lambda$ and $r ≤ m-2$, in such a way that the set of (tied) winners picked by the chair reveals whether $w_{r} - w_{r+1} \geq \lambda (w_{r+1} - w_{r+2})$.
-\begin{proposition}
+\begin{proposition}\label{prop:chairQuestions}
 	Given a rational $\lambda = p/q > 1$ and a rank $r$ between $1$ and $m - 2$, there exists a profile $P$ such that, for any weight vector $\w \in \W$, $a \in f(P)$ iff $w_{r} - w_{r+1} ≥ \lambda (w_{r+1} - w_{r+2})$ and $b \in f(P)$ iff $w_{r} - w_{r+1} ≤ \lambda (w_{r+1} - w_{r+2})$, where $f$ is the PSR parameterized with $\w$.
 \end{proposition}
-\begin{proof*}
-	Define a linear order $>_1$ over $A$ as placing $a$ at rank $r$, $b$ at rank $r + 1$, and the remaining alternatives arbitrarily. 
-	Define a linear order $>_2$ over $A$ as placing $a$ at rank $r + 2$, $b$ at rank $r + 1$, and the remaining alternatives arbitrarily.
-	Define an arbitrary linear ordering $>$ over $A \setminus \set{a, b}$. 
-	Define a linear order $>_3$ as placing $a$ first, $b$ second, and following the order of $>$ for the remaining positions.
-	Finally, define a linear order $>_4$ as placing $b$ first, $a$ second, and following the \emph{inverse} order of $>$ for the remaining positions.
 
-	Define $P$ as the profile of $3 (p + q)$ voters containing $q$ times $>_1$, $p$ times $>_2$, and $>_3$ and $>_4$ each $p + q$ times.
-	As a result, $a$ obtains the following ranks: $q$ times $r$, $p$ times $r + 2$, $p + q$ times first, and $p + q$ times second.
-The alternative $b$ obtains the ranks $r + 1$, $2$ and $1$, each $p + q$ times.
-Consider any alternative $c \in A \setminus \set{a, b}$.
-Its score is maximal when it comes first in $>_1$, first in $>_2$ and first in $>$, by convexity of the weights.
-In that case, $c$ is positioned at the ranks $1$, $3$ and $m$, each $p + q$ times.
-
-	Letting $s(x)$ denote the score of $x$ at $P$, we obtain $s(a) = q w_r + p w_{r + 2} + (p + q) w_1 + (p + q) w_2$, thus, $s(a) ≥ (p + q) w_m + (p + q) w_1 + (p + q) w_2$; $s(b) = (p + q) w_{r + 1} + (p + q) w_2 + (p + q) w_1$; and, $\forall c \in A \setminus \set{a, b}$,
-	$s(c) ≤ (p + q) w_1 + (p + q) w_3 + (p + q) w_m$.
-It follows that $a$ or $b$ maximize $s$ (as $s(a) ≥ s(c)$).
-We conclude by observing that $a \in f(P) ⇔ s(a) ≥ s(b) ⇔ q w_r + p w_{r + 2} ≥ (p + q) w_{r + 1} ⇔ w_r - w_{r + 1} ≥ (p / q) (w_{r + 1} - w_{r + 2})$, and similarly for $b \in f(P)$.
-\end{proof*}
 At this stage, we are satisfied that a procedure exists to transform our abstract questions to questions about winners of a PSR.
@@
 \paragraph{Comparison of strategies}
-\begin{figure}
+\begin{figure}[ht]
 	\caption{Average MMR in problems of size $(5, 10)$ after $k$ questions.}
@@
 Averaging these data by category of value for $m$, and assuming no questions get asked to the chair, we see that in order to reach a low regret level, each agent will have to answer $5.6$ questions for $m = 5$, $17.2$ questions for $m = 10$ and $27.1$ questions for $m = 15$.
-These numbers have to be contrasted with those displayed in \cref{tab:fullProfile}, that estimate the number of questions required to elicit the full preference of an agent.
-To obtain the data for this table, we constrained the Pessimistic strategy to ask questions to the agents only, and ran it on a single agent problem, with various values for $m$.
+These numbers have to be contrasted with the estimated number of questions required to elicit the full preference of an agent which are $6.6$ for $m=5$, $24.8$ for $m=10$ and $48.4$ for $m=15$.
+To obtain these data, we constrained the Pessimistic strategy to ask questions to the agents only, and ran it on a single agent problem, with various values for $m$.
 
-\begin{table}
-	\caption{Number of questions needed by the Pessimistic strategy to elicit the complete preference of one agent.}
-	\label{tab:fullProfile}
-	\begin{tabular}{S[table-figures-decimal=0]S}
-		\toprule
-		{m} & {k} \\
-		\midrule
-		5 & 6.6\\
-		10 & 24.8\\
-		15 & 48.4\\
-		\bottomrule
-	\end{tabular}
-\end{table}
+%\begin{table}
+%	\caption{Number of questions needed by the Pessimistic strategy to elicit the complete preference of one agent.}
+%	\label{tab:fullProfile}
+%	\begin{tabular}{S[table-figures-decimal=0]S}
+%		\toprule
+%		{m} & {k} \\
+%		\midrule
+%		5 & 6.6\\
+%		10 & 24.8\\
+%		15 & 48.4\\
+%		\bottomrule
+%	\end{tabular}
+%\end{table}
 
@@
 
-\begin{figure}
-	\caption{Average MMR after $k$ questions with Pessimistic strategy for different problem sizes.}
+\begin{figure}[ht]
+	\caption{Average MMR (normalized on the number of voters $n$) after $k$ questions with Pessimistic strategy for different problem sizes.}
 	\label{fig:linearity}
@@
 			every axis legend/.append style={
-				at={(0.5,1.03)},
+				at={(0.5,1.1)},
 				anchor=south
@@
 		\begin{axis}[
-			y=3.5,
+			y=100,
 			legend columns=3,
 			xlabel=Number of Questions,
-			ylabel=Avg. Regret,
-			ytick={0,5,10,15,20,25,30},
+			ylabel=MMR/n,
+			ytick={0,0.5,1},
 			xtick distance=100,
-			ytick distance=5,
 			xtick pos=left,
@@
 			ymin=0,
-			ymax=31,
+			ymax=1,
 			xmin=0,
 			xmax=1000,
-			yticklabels={0,5,10,15,20,25,30}]
+			yticklabels={0,0.5,1}]
 
 			\addlegendimage{mark=triangle*,teal,mark size=2}
-			\addlegendimage{mark=*,violet,mark size=2}
+%			\addlegendimage{mark=*,violet,mark size=2}
 			\addlegendimage{mark=square*,green,mark size=2}
 			\addlegendimage{mark=diamond*,red,mark size=2}
+			\addlegendimage{mark=pentagon*,cyan,mark size=2}
+			\addlegendimage{mark=*,pink,mark size=2}
 			\addlegendimage{mark=halfsquare left*,blue,mark size=2}
 			\addlegendimage{mark=halfsquare right*,brown,mark size=2}
-			\addlegendimage{mark=pentagon*,cyan,mark size=2}
 			\addlegendimage{mark=halfsquare*,magenta,mark size=2}
 
-			\addplot[thick, mark=triangle*, mark size = {2}, mark indices = {35}, teal] table [x=k, y=5.10]{data/linearity.dat};
+			\addplot[thick, mark=triangle*, mark size = {2}, mark indices = {35}, teal] table [x=k, y=5.10]{data/normalizedLin.dat};
 			\addlegendentry{m=5, n=10}
-			\addplot[thick, mark=*, mark size = {2}, mark indices = {45}, violet] table [x=k, y=5.15]{data/linearity.dat};
-			\addlegendentry{m=5, n=15}
-			\addplot[thick, mark=square*, mark size = {2}, mark indices = {90}, green] table [x=k, y=5.20]{data/linearity.dat};
+%			\addplot[thick, mark=*, mark size = {2}, mark indices = {45}, violet] table [x=k, y=5.15]{data/normalizedLin.dat};
+%			\addlegendentry{m=5, n=15}
+			\addplot[thick, mark=square*, mark size = {2}, mark indices = {90}, green] table [x=k, y=5.20]{data/normalizedLin.dat};
 			\addlegendentry{m=5, n=20}
-			\addplot[thick, mark=diamond*, mark size = {2}, mark indices = {150}, red] table [x=k, y=10.20]{data/linearity.dat};
+			\addplot[thick, mark=diamond*, mark size = {2}, mark indices = {150}, red] table [x=k, y=10.20]{data/normalizedLin.dat};
 			\addlegendentry{m=10, n=20}
-			\addplot[thick, mark=halfquare left*, mark size = {2}, mark indices = {60}, blue] table [x=k, y=14.9]{data/linearity.dat};
+			\addplot[thick, mark=pentagon*, mark size = {2}, mark indices = {300}, cyan] table [x=k, y=10.30]{data/normalizedLin.dat};
+			\addlegendentry{m=10, n=30}
+			\addplot[thick, mark=*, mark size = {2}, mark indices = {400}, pink] table [x=k, y=courses]{data/normalizedLin.dat};
+			\addlegendentry{courses m9n146}
+			\addplot[thick, mark=halfsquare left*, mark size = {2}, mark indices = {200}, blue] table [x=k, y=14.9]{data/normalizedLin.dat};
 			\addlegendentry{m=14, n=9}
-			\addplot[thick, mark=halfsquare right*, mark size = {2}, mark indices = {60}, brown] table [x=k, y=skate]{data/linearity.dat};
+			\addplot[thick, mark=halfsquare right*, mark size = {2}, mark indices = {60}, brown] table [x=k, y=skate]{data/normalizedLin.dat};
 			\addlegendentry{skate m14n9}
-			\addplot[thick, mark=pentagon*, mark size = {2}, mark indices = {300}, cyan] table [x=k, y=10.30]{data/linearity.dat};
-			\addlegendentry{m=10, n=30}
-			\addplot[thick, mark=halfsquare*, mark size = {2}, mark indices = {400}, magenta] table [x=k, y=15.30]{data/linearity.dat};
+			\addplot[thick, mark=halfsquare*, mark size = {2}, mark indices = {400}, magenta] table [x=k, y=15.30]{data/normalizedLin.dat};
 			\addlegendentry{m=15, n=30}
-
 		\end{axis}
@@
 %\begin{figure}
-%	\caption{Logarithmic plot representing the MMR reduction after $k$ questions with Pessimistic strategy for different problem sizes.}
+%	\caption{Average MMR after $k$ questions with Pessimistic strategy for different problem sizes.}
 %	\label{fig:linearity}
@@
 %				at={(0.5,1.03)},
-%				anchor=south,
+%				anchor=south
 %			},
 %		}
-%		\begin{semilogyaxis}[
+%		\begin{axis}[
+%			y=3.5,
 %			legend columns=3,
@@
 %			ylabel=Avg. Regret,
-%			log basis y= 10,
-%			ymin=10e-2,
-%			ymax=10e2,
-%			ytick={10e-2,1,2,10,15,20,30,146},
-%			yticklabels={0.01,1,2,10,15,20,30,146},
+%			ytick={0,5,10,15,20,25,30},
+%			xtick distance=100,
+%			ytick distance=5,
+%			xtick pos=left,
 %			ymajorgrids=true,
 %			ytick style={draw=none},
+%			ymin=0,
+%			ymax=31,
 %			xmin=0,
 %			xmax=1000,
-%			xtick={0,100,200,300,400,500,600,700,800,900,1000},
-%			xticklabels={0,100,200,300,400,500,600,700,800,900,1000},
-%			ticklabel style = {font=\tiny}
-%			]
+%			yticklabels={0,5,10,15,20,25,30}]
 %			
@@
 %			\addlegendimage{mark=diamond*,red,mark size=2}
+%			\addlegendimage{mark=halfsquare left*,blue,mark size=2}
+%			\addlegendimage{mark=halfsquare right*,brown,mark size=2}
 %			\addlegendimage{mark=pentagon*,cyan,mark size=2}
 %			\addlegendimage{mark=halfsquare*,magenta,mark size=2}
-%			\addlegendimage{mark=halfsquare right*,brown,mark size=2}
 %			
-%			\addplot[thick, mark=triangle*, mark size = {2}, mark indices = {35}, teal, domain=-5:5] table [x=k, y=5.10]{data/linearity.dat};
+%			
+%			\addplot[thick, mark=triangle*, mark size = {2}, mark indices = {35}, teal] table [x=k, y=5.10]{data/linearity.dat};
 %			\addlegendentry{m=5, n=10}
-%			\addplot[thick, mark=*, mark size = {2}, mark indices = {45}, violet,domain=-5:5] table [x=k, y=5.15]{data/linearity.dat};
+%			\addplot[thick, mark=*, mark size = {2}, mark indices = {45}, violet] table [x=k, y=5.15]{data/linearity.dat};
 %			\addlegendentry{m=5, n=15}
@@
 %			\addlegendentry{m=10, n=20}
+%			\addplot[thick, mark=halfquare left*, mark size = {2}, mark indices = {60}, blue] table [x=k, y=14.9]{data/linearity.dat};
+%			\addlegendentry{m=14, n=9}
+%			\addplot[thick, mark=halfsquare right*, mark size = {2}, mark indices = {60}, brown] table [x=k, y=skate]{data/linearity.dat};
+%			\addlegendentry{skate m14n9}
 %			\addplot[thick, mark=pentagon*, mark size = {2}, mark indices = {300}, cyan] table [x=k, y=10.30]{data/linearity.dat};
@@
 %			\addlegendentry{m=15, n=30}
-%			\addplot[thick, mark=halfsquare right*, mark size = {2}, mark indices = {400}, brown] table [x=k, y=courses]{data/linearity.dat};
-%			\addlegendentry{courses}
-%		\end{semilogyaxis}
+%			
+%		\end{axis}
 %	\end{tikzpicture}
@@
 
+\newpage
+
 \bibliographystyle{named}
 \bibliography{biblio}
+
+\newpage
+\appendix
+\section{Appendix}
+\begin{sketch*}[\cref{claim:completion}]
+	Consider our knowledge $\pprefeq_j$ about the preference of the agent $j$. 
+	The adversary's goal is to make the score of $y$ as high as possible and the score of $x$ as low as possible. 
+	To do this, he should complete $\ppref_j$ to $\pref_j$ by putting above $x$ as many alternatives as he can, that is, all the alternatives except those that are known to be worse than $x$ (those $a$ such that $x \pprefeq_j a$); and similarly, he should put below $y$ all the alternatives he can.
+Two conditions must be excluded for $a$ to go below $y$.
+The alternatives such that $a \pprefeq_j y$ can’t be put below $y$.
+	Furthermore, the first objective must take priority over the second one: when an alternative should go above $x$ according to the first objective (because $¬(x \pprefeq_j a)$), and $x$ is known to be better than $y$ (thus $x \pprefeq_j y$), then $a$ should be put above $x$ (irrespective of whether $a \pprefeq_j y$), which will move both $x$ and $y$ one rank lower than if $a$ had been put below $y$.
+	This maximizes the adversary’s interests: because the weight vector is convex, the difference of scores will be lower when both alternatives are ranked lower (Equation \ref{eq:convexity}), and that difference of scores is in favor of $x$ when $x \ppref_j y$, thus to be minimized from the point of view of the adversary.
+\end{sketch*}
+
+\begin{proof*}[\cref{claim:rankPMR}]
+	The rank of $x$ is directly obtained from \cref{eq:complx}.
+The rank of $y$ is obtained by complementing \cref{eq:comply}, obtaining $a \prefeq_j y ⇔ (a \pprefeq_j y) ∨ ((x \pprefeq_j y) ∧ ¬(x \pprefeq_j a))$, and, observing that $a \pref_j y ⇔ a ≠ y ∧ a \prefeq_j y$, obtaining that $a \pref_j y$ if and only if
+	\begin{equation}
+		\label{eq:betteryinter}
+		(a \neq y) ∧ [(a \pprefeq_j y) ∨ ((x \pprefeq_j y) ∧ ¬(x \pprefeq_j a))],
+	\end{equation} 
+	or equivalently, if and only if
+	\begin{equation}
+		\label{eq:bettery}
+		%a \pref_j y ⇔ 
+		(a \ppref_j y) ∨ ((x \pprefeq_j y) ∧ ¬(x \pprefeq_j a)).
+	\end{equation} 
+	Indeed, \eqref{eq:betteryinter} $⇒$ \eqref{eq:bettery}, and \eqref{eq:bettery} $⇒$ \eqref{eq:betteryinter} because $(x \pprefeq_j y) ∧ ¬(x \pprefeq_j a) ⇒ a ≠ y$ (as when $a = y$, $(x \pprefeq_j y)$ and $¬(x \pprefeq_j a)$ are opposite claims).
+Suffices now to rewrite \cref{eq:bettery} to let the two disjuncts designate disjoint sets:
+	\begin{equation}
+		\label{eq:betteryfinal}
+		a \pref_j y ⇔ 
+		(a \ppref_j y) ∨ ((x \pprefeq_j y) ∧ ¬(x \pprefeq_j a) ∧ ¬(a \ppref_j y)).
+	\end{equation}
+\end{proof*}
+
+\begin{proof*}[\cref{prop:chairQuestions}]
+	Define a linear order $>_1$ over $A$ as placing $a$ at rank $r$, $b$ at rank $r + 1$, and the remaining alternatives arbitrarily. 
+	Define a linear order $>_2$ over $A$ as placing $a$ at rank $r + 2$, $b$ at rank $r + 1$, and the remaining alternatives arbitrarily.
+	Define an arbitrary linear ordering $>$ over $A \setminus \set{a, b}$. 
+	Define a linear order $>_3$ as placing $a$ first, $b$ second, and following the order of $>$ for the remaining positions.
+	Finally, define a linear order $>_4$ as placing $b$ first, $a$ second, and following the \emph{inverse} order of $>$ for the remaining positions.
+
+	Define $P$ as the profile of $3 (p + q)$ voters containing $q$ times $>_1$, $p$ times $>_2$, and $>_3$ and $>_4$ each $p + q$ times.
+	As a result, $a$ obtains the following ranks: $q$ times $r$, $p$ times $r + 2$, $p + q$ times first, and $p + q$ times second.
+The alternative $b$ obtains the ranks $r + 1$, $2$ and $1$, each $p + q$ times.
+Consider any alternative $c \in A \setminus \set{a, b}$.
+Its score is maximal when it comes first in $>_1$, first in $>_2$ and first in $>$, by convexity of the weights.
+In that case, $c$ is positioned at the ranks $1$, $3$ and $m$, each $p + q$ times.
+
+	Letting $s(x)$ denote the score of $x$ at $P$, we obtain $s(a) = q w_r + p w_{r + 2} + (p + q) w_1 + (p + q) w_2$, thus, $s(a) ≥ (p + q) w_m + (p + q) w_1 + (p + q) w_2$; $s(b) = (p + q) w_{r + 1} + (p + q) w_2 + (p + q) w_1$; and, $\forall c \in A \setminus \set{a, b}$,
+	$s(c) ≤ (p + q) w_1 + (p + q) w_3 + (p + q) w_m$.
+It follows that $a$ or $b$ maximize $s$ (as $s(a) ≥ s(c)$).
+We conclude by observing that $a \in f(P) ⇔ s(a) ≥ s(b) ⇔ q w_r + p w_{r + 2} ≥ (p + q) w_{r + 1} ⇔ w_r - w_{r + 1} ≥ (p / q) (w_{r + 1} - w_{r + 2})$, and similarly for $b \in f(P)$.
+\end{proof*}
+
 \end{document}
@@
 
-\appendix
-\import{preamble/}{appendix.tex}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2021-01-12 minimax.tex
t-shirts xps and example proposition 4

@@
 
+\begin{example*}
+	Suppose we want to ask the following question to the chair: $w_{2} - w_{3} ≥ 2 (w_{3} - w_{4})$.
+In other words, we want to relate the difference between the weights of the second and third positions with the double of the difference between the weights of the third and fourth positions.
+We can rewrite this inequality in the form $w_{2} + 2 w_{4} ≥ 3 w_{3}$, and we can translate the original question in one of the form "is $a$ better than $b$?" where $a$ is an alternative ranked once in second position and twice in fourth position, and $b$ is ranked three times in third position.
+In order to do so, we construct a profile $P$ such that $a$ and $b$ respect these constraints and all the other alternative are strictly worse than them.
+	\begin{center}
+		$
+		\begin{array}{ccccc}
+			\#\text{voters} \quad &w_1&w_2&w_3&w_4\\
+			\mathbf{1} \quad &c&a&b&d\\
+			\mathbf{2} \quad &d&c&b&a\\
+			\mathbf{3} \quad &a&b&c&d\\
+			\mathbf{3} \quad &b&a&d&c\\
+		\end{array}.
+		$
+	\end{center}
+	The score of the alternatives are $s(a)=3w_1+3w_2+w_2+2w_4$, $s(b)=3w_1+3w_2+3w_3$, $s(c)=w_1+2w_2+3w_3+3w_4$, $s(d)=2w_1+3w_3+4w_4$.
+Since the weights are convex $s(a)>s(c)$, $s(a)>s(d)$, $s(b)>s(c)$ and $s(b)>s(d)$.
+Therefore, if the committee picks $a$ in $P$, the answer to the original question is yes, the converse if $b$ is picked.
+\end{example*}
+
 At this stage, we are satisfied that a procedure exists to transform our abstract questions to questions about winners of a PSR.
@@
 			\addlegendimage{mark=pentagon*,cyan,mark size=2}
+			\addlegendimage{mark=halfcircle*,violet,mark size=2}
 			\addlegendimage{mark=*,pink,mark size=2}
@@
 			\addlegendentry{m=10, n=30}
+			\addplot[thick, mark=halfcircle*, mark size = {2}, mark indices = {400}, violet] table [x=k, y=tshirt]{data/normalizedLin.dat};
+			\addlegendentry{tshirts m11n30}
 			\addplot[thick, mark=*, mark size = {2}, mark indices = {400}, pink] table [x=k, y=courses]{data/normalizedLin.dat};

### 2021-01-12 minimax.tex
minor changes introduction

@@
 In many situations, such as in group recommender systems, the goal is to find a consensus choice.
-It is therefore natural to look at methods from social choice and see how they can be adapted for group decision-making in a computerized setting.
+%It is therefore natural to look at methods from social choice and see how they can be adapted for group decision-making in a computerized setting.
+Methods from social choice can be adapted for group decision-making in a computerized setting.
 
@@
 Our approach is evaluated experimentally in simulations where the both the voting rule and the agent's preferences are initially unknown to the system and incrementally revealed by answering questions.
-We compare the effectiveness of several different strategies  including strategies that proceed in phases, learning first as much as possible about the voting rule and then focus on eliciting agent's preferences, and as well strategies that interwind questions to chair and to the agents based on which is estimated to provide more information.
+We compare the effectiveness of several strategies  including strategies that proceed in phases, learning first as much as possible about the voting rule and then focus on eliciting agent's preferences, and as well strategies that interwind questions to chair and to the agents based on which is estimated to provide more information.
 %Our approach permits to compare experimentally strategies that question the chair, the agents, or both.
@@
 A classic paper is the one by \citet{Stein1994} that, considering scoring rules, identified dominance relations between alternatives; these relations allow to determine pairs of alternatives where the first is at least as good as the second no matter which weights are chosen among a generic class of weights (decreasing weighs or convex decreasing weights).
-
 More recent articles considered the problem of dealing with unspecified weights in positional scoring rules: \citet{Llamazares2013} proposed a method based on Data Envelopment Analysis (DEA), while \citet{Viappiani2018} proposed to aggregate the uncertainty in weights using criteria used in decision-making under uncertainty (such as minimax regret).

### 2021-01-12 cover letter/resubmission.tex
No abstract

@@
 \maketitle
-
-\begin{abstract}
-Social choice deals with the problem of determining a consensus choice from the preferences of different agents.
-In the classical setting, the voting rule is fixed beforehand and full information concerning the preferences of the agents is provided.
-This assumption of full preference information has recently been questioned by a number of researchers and
-	several methods for eliciting the preferences of the agents have been proposed.
-	%  are completely known have been proposed, as well as techniques that consider the opposite scenario.
-
-In this paper we argue that in many situations one should consider as well the voting rule to be 	partially specified.
-%	This article goes one step further by tackling one important new case, namely, when both the voting rule and the agents preferences are partially known.
-It also permits to obtain a progressively refined recommendation without requiring to achieve full knowledge of either sort of information.
-%This is useful because providing such information is often costly: the chair may find it hard to specify a rule completely; agents may need time to form reflective preferences.	
-	Focusing on positional scoring rules, we assume that the chair, while not able to give a precise definition of the rule, is capable of answering simple questions requiring to pick a winner from a specific example profile.
-In addition, we assume that the agent preferences have to be elicited as well and are acquired by asking comparison queries.
-	We propose a method for robust approximate winner determination and interactive elicitation based on minimax regret; we develop several strategies for choosing the questions to ask to  the chair and the agents in order to %acquire the most relevant information for
-converge quickly to a near-optimal alternative. Finally, we analyze these strategies in experiments %in order to validate our approach
- %focusing on settings 
- where the voting rule and the preferences are simultaneously elicited.
- %and obtain practical guidelines.
-\end{abstract}
 

### 2021-01-12 minimax.tex
position of floating environments at the top

@@
 and we can rewrite $\PMR$ as follows:
-
 \begin{align}
@@
 It is parameterized by $q_c$, a value indicating the number of questions that must be asked to the chair.
-The \strat{Two phases - ca} variant first asks $q_c$ questions to the chair, then $k - q_c$ questions to the agents, using in both cases Pessimistic to select the specific questions; whereas the \strat{Two phases - ac} variant starts with $k - q_c$ questions to the agents, then questions the chair.
+The \strat{Two phases-ca} variant first asks $q_c$ questions to the chair, then $k - q_c$ questions to the agents, using in both cases Pessimistic to select the specific questions; whereas the \strat{Two phases-ac} variant starts with $k - q_c$ questions to the agents, then questions the chair.
 %Note that when asking first only questions to the chair, if the obtained knowledge approximates well the scoring vector, then in the second part of the elicitation we fall into the more classical setting of incompleteness of preferences assuming a known voting rule.
@@
 \label{sec:experiments}
-%TODO
-%\begin{enumerate}
-%	\item Reach regret: $n/10$. Add considerations.
-%MMR and sd with systematically one decimal exactly
-%Page numbers
-%\end{enumerate}
 We  performed a number of numerical experiments in order to validate our approach and to test the performance of the different elicitation strategies.
@@
 
-\paragraph{Comparison of strategies}
-\begin{figure}[ht]
+\begin{figure}[t]
 	\caption{Average MMR in problems of size $(5, 10)$ after $k$ questions.}
@@
 \end{table}
-\begin{table}
+\begin{table}[t]
 	\caption{Average MMR in problems of size $(10, 20)$ and geometric weights after $k$ questions.}
@@
 \end{table}
+\paragraph{Comparison of strategies}
 Our first experiment concerns small size situations.
@@
 %\subsection{Absolute evaluation of Pessimistic strategy}
-\paragraph{In-depth evaluation of Pessimistic}
-\label{sec:lowRegret}
 \begin{table}
@@
 
+\paragraph{In-depth evaluation of Pessimistic}
+\label{sec:lowRegret}
 While in previous experiments we compared Pessimistic to the other strategies, in this set of experiments, we evaluate the Pessimistic strategy in absolute terms. 
@@
 %\subsection{Decrease in MMR values}
-\paragraph{Decrease in MMR values}
 
-\begin{figure}[ht]
+\begin{figure}[t]
 	\caption{Average MMR (normalized on the number of voters $n$) after $k$ questions with Pessimistic strategy for different problem sizes.}
@@
 
+\paragraph{Decrease in MMR values}
 We next wonder how fast the regret decreases, measured as a function of the number of questions asked.

### 2021-01-12 cover letter/resubmission.tex
Titling material
edit of cover letter

@@
 
-\title{Cover letter}
+\title{Resubmission file}
 \subtitle{Simultaneous Elicitation of Scoring Rule and Agent Preferences for Robust Winner Determination}
-\author{}
+\author{Submission ID: TODO}
 \date{}
@@
 
+\medskip
 We have submitted this article for the first time to IJCAI 2020 (TODO ID?).
-The reviewer’s evaluations of it were: from R1, Accept (good paper, I can argue for accepting it); from R2, Weak accept (marginally above the acceptance theshold, rejecting it would not be that bad); from R3, Weak reject (marginally below the acceptance threshold, accepting it would not be that bad); and from R4, Reject (Not good enough, I can argue for rejecting it).
-The strongest criticisms from the last two reviewers were, from R3, that we should improve presentation with a larger example and expand the discussion (R3 incorrectly thought that we had room to spare within the constraints imposed by IJCAI); and from R4, that our literature review omitted important related works; that the results in the paper were incremental in nature; and that it was almost impossible to find the main contribution or take away message from the paper.
-The metareview pointed out that “One might view the work as somewhat incremental, but there is some substantial solid work here”; but recommended rejection because of 1) the very brief discussion of the empirical evaluation and 2) the incomplete literature review.
-The metareviewer also commented that “after some further work on the paper there's a reasonable chance that it could be accepted for another high quality conference.”
+The submission was evaluated by four reviewers; the overall assessment (full reviews are included in Section \ref{sec:reviews-ijcai}) were:
+\begin{itemize}
+\item R1: Accept {\em (good paper, I can argue for accepting it)};
+\item R2: Weak accept {\em (marginally above the acceptance theshold, rejecting it would not be that bad)};
+\item R3: Weak reject {\em (marginally below the acceptance threshold, accepting it would not be that bad)}; and
+\item R4:  Reject {\em (Not good enough, I can argue for rejecting it)}.
+\end{itemize}
 
-We extended very significantly the literature review and the experimental section, also taking advantage of two supplementary pages, and submitted the resulting work to AAMAS 2021 (with submission ID 554).
-The evaluations were: from R1 and R2, poor (4, good attempt but too many concerns, so probably should be rejected); and from R3, good (7, probably should be accepted).
+%from R1, Accept (good paper, I can argue for accepting it); from R2, Weak accept (marginally above the acceptance theshold, rejecting it would not be that bad); from R3, Weak reject (marginally below the acceptance threshold, accepting it would not be that bad); and from R4, Reject (Not good enough, I can argue for rejecting it).
+The strongest criticisms from the last two reviewers (R3 and R4).
+According to R3 we should have improved the presentation with a larger example and expanded the discussion (R3 incorrectly thought that we had room to spare within the constraints imposed by IJCAI);  R4 found that our literature review omitted important related works, that the results in the paper were incremental in nature; and that the main contribution or take away message was not clearly stated in the paper.
+
+The metareview pointed out that {\em “One might view the work as somewhat incremental, but there is some substantial solid work here”}; but recommended rejection because of 1) the very brief discussion of the empirical evaluation and 2) the incomplete literature review.
+The metareviewer also commented that {\em “after some further work on the paper there's a reasonable chance that it could be accepted for another high quality conference.”}
+
+\medskip
+Following the IJCAI rejection we focus our work in extending the literature review and in improving the experimental section %(also taking advantage of the two additional pages), 
+and submitted the resulting work to AAMAS 2021 (with submission ID 554). 
+Our AAMAS submission received the following evaluations (full reviews are given in Section \ref{sec:reviews-aamas}):
+\begin{itemize}
+\item R1: {\em poor (4, good attempt but too many concerns, so probably should be rejected)};
+\item R2: {\em poor (4, good attempt but too many concerns, so probably should be rejected)}; and
+\item R3; {\em good (7, probably should be accepted)}
+\end{itemize}
+%from R1 and R2, poor (4, good attempt but too many concerns, so probably should be rejected); and from R3, good (7, probably should be accepted). 
 R1 considered our theoretical results as relatively simple extensions of the results of Lu and Boutilier and found the experimental results quite preliminary.
 About the first point, R1 stated to be unable to think about an example of a setting where our proposition would apply.
-(After rebuttal, R1 stated that the example we provided in our response was convincing.) 
+Notice that we took the opportunity of using the rebuttal to provide an application example and that, after rebuttal, R1 stated that the example we provided in our response was convincing.
+
 About experiments, R1 regretted that we use only impartial culture assumption; that we look at very small elections only; and that the way some of our conclusions are phrased make them appear more general than allowed by the experimental observations.
+
 R2 criticized the lack of theoretical guarantees for the proposed elicitation strategies, as well as the missing reasoning behind several of the experimental observations.
@@
 Finally, R3, similarly to R1, found unclear which sorts of situations would permit an application of our proposed approach.
-The metareview stated that the paper misses novelty and that hypotheses are missing from the experimental section and experiments should not be limited to the impartial culture assumption.
+
+The metareview stated that the paper misses novelty, that the experimental section should be improved and that experiments should not be limited to the impartial culture assumption.
 
@@
 \begin{itemize}
-	\item The introduction provides an example of a situation where our approach is applicable.
+	\item The introduction provides an example of a situation where our approach is applicable (this example was found convincing by AAMAS reviewers after rebuttal).
 	\item We better explain our motivation for asking questions that can be phrased as choices of winners out of a profile (which makes the answer “observable” in an econometric sense), and highlight the methodological novelty of this approach.
-	\item We integrated the Related Works section into the Introduction to save space, but kept all the references we added following the earlier criticisms about the missing references to the literature.
+	\item We integrated the Related Works section into the Introduction to save space, but kept all the references we added following the earlier criticisms (in the IJCAI submission) about the missing references to the literature.
 	\item We went beyond impartial culture by testing our heuristics on real data.
@@
 	\item TODO We better explain what results can be anticipated before presenting the experimental results.
+\commentOC{We just agreed we don’t specifically talk about this and don’t change anything because does not apply here.}
 	\item We changed the phrasing of some of our conclusions that were too general.
@@
 \section{Submission to IJCAI 2020} 
+\label{sec:reviews-ijcai}
 \subsection{Review 1}
@@
 \section{Submission to AAMAS-2021} 
+\label{sec:reviews-aamas}
 \subsection{Review 1}

### 2021-01-12 cover letter/resubmission.tex
table of contents, IDs, ijcai20 paper

@@
 \subtitle{Simultaneous Elicitation of Scoring Rule and Agent Preferences for Robust Winner Determination}
-\author{Submission ID: TODO}
+\author{Submission ID: 3177}
 \date{}
@@
 
+\tableofcontents
+
 \section{Summary of previous criticisms and our corrections}
@@
 \medskip
-We have submitted this article for the first time to IJCAI 2020 (TODO ID?).
+We have submitted this article for the first time to IJCAI 2020 (with submission ID 7094).
 The submission was evaluated by four reviewers; the overall assessment (full reviews are included in Section \ref{sec:reviews-ijcai}) were:
@@
 
-\section{Submission to AAMAS-2021} 
+\section{Rejected paper IJCAI 2020}
+You will find here below the version of this article that was submitted to IJCAI 2020.
+\includepdf[pages=-]{ijcai20_paper_7094.pdf}
+
+\section{Submission to AAMAS 2021} 
 \label{sec:reviews-aamas}
@@
 You will find here below the version of this article that was submitted to AAMAS 2021.
-%\includepdf[pages=-]{aamas21_paper_554.pdf}
+\includepdf[pages=-]{aamas21_paper_554.pdf}
 \end{document}

### 2021-01-12 minimax.tex
ID

@@
 
-\author{
-	Beatrice Napolitano$^1$\footnote{Contact Author}\and
-	Olivier Cailloux$^1$\and
-	Paolo Viappiani$^2$\\
-	\affiliations
-	$^1$Université Paris-Dauphine, Université PSL, CNRS, LAMSADE\\
-	$^2$LIP6, UMR 7606, CNRS and Sorbonne Universit\'e\\
-	\emails
-	\{beatrice.napolitano, olivier.cailloux\}@dauphine.fr,
-	paolo.viappiani@lip6.fr
-}
+\author{ID: 3177}
+
+%\author{
+%	Beatrice Napolitano$^1$\footnote{Contact Author}\and
+%	Olivier Cailloux$^1$\and
+%	Paolo Viappiani$^2$\\
+%	\affiliations
+%	$^1$Université Paris-Dauphine, Université PSL, CNRS, LAMSADE\\
+%	$^2$LIP6, UMR 7606, CNRS and Sorbonne Universit\'e\\
+%	\emails
+%	\{beatrice.napolitano, olivier.cailloux\}@dauphine.fr,
+%	paolo.viappiani@lip6.fr
+%}
 

### 2021-01-13 minimax.tex
shortening introduction

@@
 %This is useful because providing such information is often costly: the chair may find it hard to specify a rule completely; agents may need time to form reflective preferences.	
-	Focusing on positional scoring rules, we assume that the chair, while not able to give a precise definition of the rule, is capable of answering simple questions requiring to pick a winner from a specific example profile.
-In addition, we assume that the agent preferences have to be elicited as well and are acquired by asking comparison queries.
+	Focusing on positional scoring rules, we assume that the chair, while not able to give a precise definition of the rule, is capable of answering simple questions requiring to pick a winner from a concrete profile.
+In addition, we assume that the agent preferences also have to be elicited.
+%and are acquired by asking comparison queries.
 	We propose a method for robust approximate winner determination and interactive elicitation based on minimax regret; we develop several strategies for choosing the questions to ask to  the chair and the agents in order to %acquire the most relevant information for
@@
  %focusing on settings 
- where the voting rule and the preferences are simultaneously elicited.
+ where the  rule and the preferences are simultaneously elicited.
  %and obtain practical guidelines.
@@
 Aggregation of preference information is a central task in many computer systems (recommender systems, search engines, etc).
-In many situations, such as in group recommender systems, the goal is to find a consensus choice.
+In many situations, such as in group recommender systems, the goal is to find a consensus choice;
 %It is therefore natural to look at methods from social choice and see how they can be adapted for group decision-making in a computerized setting.
-Methods from social choice can be adapted for group decision-making in a computerized setting.
+social choice theory can provide foundations for such applications. %Methods from social choice can be adapted for group decision-making in a computerized setting.
 
@@
 In the context of social choice, several authors have been interested in obtaining information about winners with reduced assumptions about the knowledge of the agent preferences (assuming that the voting rule is known).
-One early work is  by \Citet{Conitzer2005} who studied the complexity of communication, using different voting rules, determining lower and upper bounds; they showed that, in the worst case, the agents should send their complete set of preference for several rules.
+One early work is  by \Citet{Conitzer2005} who studied the complexity of communication, using different voting rules; %determining lower and upper bounds;
+%they showed that, 
+in the worst case, the agents should send their complete set of preference for several rules. 
+\Citet{Konczak05} studied the computation of possible and necessary winners in the case of partial knowledge of agent preferences, for various voting rules; %and showed that the problem is hard in the general case.
+\citet{Xia2008} then showed that, while the identification of a necessary co-winner in scoring rules is polynomial,  the determination of possible co-winners is NP-hard; they also  proposed polynomial-time algorithms when using maximin and Bucklin.
+\citep{Walsh2007} showed that the general case remains computationally hard even when restricting to single-peaked preferences \citep{Walsh2007};  sufficient conditions that ensure tractability were then found \citep{Pini2007}.
 
-\Citet{Konczak05} studied the computation of possible and necessary winners in the case of partial knowledge of agent preferences, for various voting rules, and showed that the problem is hard in the general case.
-This work was then extended by \citet{Xia2008} who showed that, while the identification of a necessary co-winner in scoring rules is polynomial,  the determination of possible co-winners is NP-hard; they also  proposed polynomial-time algorithms when using maximin and Bucklin.
-In other papers it was showed that the general case remains computationally hard even when restricting to single-peaked preferences \citep{Walsh2007};  sufficient conditions that ensure tractability were then found \citep{Pini2007}.
-
-Thereafter, noticing that in many practical situations there would be too many possible winners but no necessary winners, the importance of proposing efficient elicitation strategies has been identified.
-Several works addressed the problem of  elicitation of agent preferences \citep{Naamani-Dery2015,Kalech2011,Lu2011,Pini2009,Benabbou2016,Dey2016,Dey2016_2} using a variety of approaches (minimax regret, Bayesian methods, etc.), and others \citep{Walsh2009,Conitzer2009}  analyzed when to stop the elicitation process.
+Since in many practical situations there would be too many possible winners but no necessary winners, %several authors proposed elicitation methods of agent preferences. 
+several works addressed the problem of  elicitation of agent preferences \citep{Naamani-Dery2015,Kalech2011,Lu2011,Pini2009,Benabbou2016,Dey2016,Dey2016_2}  using a variety of approaches (minimax regret, Bayesian methods, etc.), with the goal of converging to a necessary winners; \citep{Walsh2009,Conitzer2009}  analyzed when to stop the elicitation process.
 
 While most of the focus in the research community has been in dealing with incomplete agent preferences, 
-another line of research has dealt with scenarios where it is instead the voting rule that is partially defined, but the preferences are given. 
-A classic paper is the one by \citet{Stein1994} that, considering scoring rules, identified dominance relations between alternatives; these relations allow to determine pairs of alternatives where the first is at least as good as the second no matter which weights are chosen among a generic class of weights (decreasing weighs or convex decreasing weights).
-More recent articles considered the problem of dealing with unspecified weights in positional scoring rules: \citet{Llamazares2013} proposed a method based on Data Envelopment Analysis (DEA), while \citet{Viappiani2018} proposed to aggregate the uncertainty in weights using criteria used in decision-making under uncertainty (such as minimax regret).
-\Citet{Cailloux2014} are interested in elicitation of a different class of rules.
+another line of research \citep{Stein1994,Llamazares2013,Viappiani2018} has dealt with %scenarios where it is instead the voting rule that is partially defined. % but the preferences are given. 
+a  partially defined voting rule.
+%A classic paper is the one by \citet{Stein1994} that, considering scoring rules, identified dominance relations between alternatives; these relations allow to determine pairs of alternatives where the first is at least as good as the second no matter which weights are chosen among a generic class of weights (decreasing weighs or convex decreasing weights).
+%More recent articles considered the problem of dealing with unspecified weights in positional scoring rules: \citet{Llamazares2013} proposed a method based on Data Envelopment Analysis (DEA), while \citet{Viappiani2018} proposed to aggregate the uncertainty in weights using criteria used in decision-making under uncertainty (such as minimax regret).
+\Citet{Cailloux2014} provided an elicitation framework for a different class of rules.
 
-Finally, we mention works related to the manipulability of voting rules \citep{Elkind2012,Dey2018,Dey2018_2,Conitzer2011,Baumeister2019}, and studies of strategic behaviors, when agents learn incrementally about other agent preferences \citep{Endriss2016,Lev2019,Annemieke2012}.
+Finally, we mention works addressing the manipulability of voting rules \citep{Elkind2012,Dey2018,Dey2018_2,Conitzer2011,Baumeister2019}, and studies of strategic behaviors
+% when agents learn incrementally about other agent preferences
+ \citep{Endriss2016,Lev2019,Annemieke2012}.
 
@@
 
-As part of the contribution of this work, we publish an open-source library that allows to reproduce our experiments, and serve as a basis for further research (url not displayed for anonymity reasons).
+An open-source library, allowing to reproduce our experiments, will be made publicly available.\footnote{URL not displayed for anonymity reasons.}
+%and serve as a basis for further research
 

### 2021-01-15 minimax.tex
Integrated some display math. Poor reader.

@@
 Among the many possible social choice functions, we consider {\em positional scoring rules (PSR)}, which attach weights to positions according to the vector $(w_1, \ldots, w_m)$, also known as the {\em scoring vector}.
+Let $\alpha^{x}_r$ be the number of times that alternative $x$ was ranked in the $r$-th position.
 An alternative obtains a score that depends on the rank obtained in each of the preference orders:
@@
 \end{align}
-where $\alpha^{x}_r$ is the number of times that alternative $x$ was ranked in the $r$-th position.
 The winners are the alternatives with the highest score.
 
-In this work we assume fixed, but unknown to us, a profile $\profile^*$ representing the preferences $\pref_j^*$ of the agents, and a weight vector $\w^*$, representing the preferences of the chair.
-We want to reason about partial preference information concerning those objects.
+In this work we assume fixed, but unknown to us, a profile $\profile^*$ representing the preferences $\pref_j^*$ of the agents, and a weight vector $\w^*$ representing the preferences of the chair.
+We will reason about partial preference information concerning those objects.
 At a given time, our knowledge of agent $j$'s preference is encoded by a partial order over the alternatives, thus a transitive and asymmetric binary relation, denoted by $\ppref_j$. 
@@
 Therefore, the vector $(w_1,\ldots,w_m)$  is not known but we are given a set of constraints restraining the possible values that weights can take.
-We consider a decreasing sequence of weights:
-\begin{align}
-	1=w_{1} ≥ w_{2} ≥ \ldots ≥ w_{m}=0. \label{eq:monotone}
-\end{align}
-This is a natural assumption, as it is better to be ranked first than second, second than third, etc. 
-Without loss of generality, we consider that $w_1=1$ and $w_m=0$.
+We consider a decreasing sequence of weights $1 = w_1 ≥ w_2 ≥ … ≥ w_m = 0$, a natural assumption, as it is better to be ranked first than second, second than third, etc.
 
@@
 \label{sec:mmr}
-In this paper, we consider a setting where both the agent preferences and the preferences of the chair about the voting rule are incomplete.
+In this paper, we consider that both the agent preferences and the preferences of the chair about the voting rule are incomplete.
 As reviewed in \cref{sec:related}, some authors have considered possible and necessary winners assuming 
@@
 Notice that often there are no necessary winners and too many possible winners; it is therefore useful to declare a winner given partial information.
-As a decision criterion to determine a winner, we propose to use minimax regret. 
-Minimax regret \citep{Savage1954} is a decision criterion that has been used for robust optimization under data uncertainty \citep{Kouvelis1997} as well as in decision-making with uncertain utility values \citep{Salo2001,Boutilier2006}.
+As a decision criterion to determine a winner, we propose to use minimax regret \citep{Savage1954}. 
+This decision criterion has been used for robust optimization under data uncertainty \citep{Kouvelis1997} as well as in decision-making with uncertain utility values \citep{Salo2001,Boutilier2006}.
 In particular, \citet{Lu2011} have adopted minimax regret for winner determination in social choice where
@@
 We formalize the notion of minimax regret in multiple steps.
-First of all, $\Regret(x, \profile, \w)$ is the “regret” of selecting $x$ as a winner instead of choosing the optimal alternative under $\profile$ and $\w$:
-\begin{align} 
-	\Regret(x; \profile, \w) = \max_{y \in A} s(y; \profile,\w) - s(x; \profile, \w).
-\end{align}
+First of all, $\Regret(x, \profile, \w)$ is the “regret” of selecting $x$ as a winner instead of choosing the optimal alternative under $\profile$ and $\w$: $\Regret(x; \profile, \w) = \max_{y \in A} s(y; \profile,\w) - s(x; \profile, \w)$.
 The pairwise maximum regret $\PMR(x,y;\pprofile,W)$ of $x$ relative to $y$ given the partial profile $\pprofile$ and the set of weights $W$
-is the worst-case loss of choosing $x$ instead of $y$ under all possible realizations of the full profile {\em and} all possible instantiations of the weights:
-\begin{align}
-	\PMR(x,y; \pprofile, W) & = \max_{\w \in W} \max_{\profile \in C(\pprofile)} s(y; \profile,\w) - s(x; \profile,\w).
-\end{align}
-
+is the worst-case loss of choosing $x$ instead of $y$ under all possible realizations of the full profile {\em and} all possible instantiations of the weights: $\PMR(x,y; \pprofile, W) & = \max_{\w \in W} \max_{\profile \in C(\pprofile)} s(y; \profile,\w) - s(x; \profile,\w)$.
 The maximum regret $\MaxR(x;\pprofile,W)$ is the worst-case loss of $x$.
-That is the loss occurred as the result of an adversarial selection of the complete profile $\profile \in C(\pprofile)$ and of the scoring vector $\w \in W$ that together maximize the loss between $x$ and the true winner under $\profile$ and $\w$:
-\begin{align}
-	\MaxR(x; \pprofile, W) & = \max_{y \in A} \PMR(x,y; \pprofile, W)\\
-	& = \max_{\w \in W} \max_{\profile \in C(\profile)} \Regret(x; \profile, \w).
-\end{align}
-
-Finally,  $\MMR(\pprofile,W)$ is the value of minimax regret under $\pprofile$ and $W$, obtained when recommending a minimax optimal alternative $x^*_{\pprofile, W} \in A^*_{\pprofile, W}$:
-
-\begin{align}
-	\MMR(\pprofile,W) & = \min_{x \in A} \MaxR(x;\pprofile,W); \\
-	A^*_{\pprofile, W} & = \argmin_{x \in A} \MaxR(x;\pprofile,W).
-\end{align}
+That is the loss occurred as the result of an adversarial selection of the complete profile $\profile \in C(\pprofile)$ and of the scoring vector $\w \in W$ that together maximize the loss between $x$ and the true winner under $\profile$ and $\w$: $\MaxR(x; \pprofile, W) = \max_{y \in A} \PMR(x,y; \pprofile, W) = \max_{\w \in W} \max_{\profile \in C(\profile)} \Regret(x; \profile, \w)$.
+Finally,  $\MMR(\pprofile,W)$ is the value of minimax regret under $\pprofile$ and $W$, obtained when recommending a minimax optimal alternative $x^*_{\pprofile, W} \in A^*_{\pprofile, W}$: $\MMR(\pprofile,W) & = \min_{x \in A} \MaxR(x;\pprofile,W)$ and $A^*_{\pprofile, W} & = \argmin_{x \in A} \MaxR(x;\pprofile,W)$.
 By picking as consensus choice
@@
 Recall that, in the computation of $s(x; \profile, \w)$, $w_{v_j(x)}$ represents the score that $x$ obtains in the ranking $v_j$ (see \cref{eq:srule}).
-Since scoring rules are additively decomposable, we can consider separately the contribution of each agent to the total score. Thus, we can write the actual regret of choosing $x$ instead of $y$ as
-\[
-s(y; \profile,\w) - s(x; \profile, \w) = \sum_{j=1}^n w_{v_j(y)} - w_{v_j(x)},
-\]
-and we can rewrite $\PMR$ as follows:
-\begin{align}
-	& \PMR(x,y; \pprofile, W) = \max_{\w \in W} \max_{\profile \in C(\pprofile)} [ s(y; \profile,\w) - s(x; \profile,\w) ] \\
-	& =  \max_{\w \in W} \sum_{j=1}^{n} \max_{v_j \in C(\succ_j^p)} [w_{v_j(y)} - w_{v_j(x)}]. \\
-\end{align}
+Since scoring rules are additively decomposable, we can consider separately the contribution of each agent to the total score.
+Thus, we can write the actual regret of choosing $x$ instead of $y$ as $s(y; \profile,\w) - s(x; \profile, \w) = \sum_{j=1}^n w_{v_j(y)} - w_{v_j(x)}$, and we can rewrite $\PMR$ as $\PMR(x,y; \pprofile, W) = \max_{\w \in W} \max_{\profile \in C(\pprofile)} [ s(y; \profile,\w) - s(x; \profile,\w) ] =  \max_{\w \in W} \sum_{j=1}^{n} \max_{v_j \in C(\succ_j^p)} [w_{v_j(y)} - w_{v_j(x)}]$.
 Note that in general the inner max depends on the weights chosen by the outer max.
@@
 	\max_{\w} & \sum_{r=1}^m (\hat{\alpha}_{r}^{y} - \hat{\alpha}_{r}^{x}) w_{r}\\
-	\text{ s.t. } & \text{\cref{eq:monotone}} \text{ and } \text{\cref{eq:convexity}} \text{ and } \Co_W.
+	\text{ s.t. } & w_1 = 1, w_m = 0, \text{\cref{eq:convexity}} \text{ and } \Co_W.
 \end{align}
-Note that given our choice $w_{1}=1$ and $w_{m}=0$, there are only $m-2$ variables 
-(we leave $w_{1}$ and $w_{m}$ in the LP just for clarity of presentation).
+%Note that given our choice $w_{1}=1$ and $w_{m}=0$, there are only $m-2$ variables 
+%(we leave $w_{1}$ and $w_{m}$ in the LP just for clarity of presentation).
 
@@
 Such questions aim at refining our knowledge about the scoring rule; a response gives us a constraint on the weight vector $\w$.
-In particular, we want to obtain constraints of the type
-\begin{align}
-	w_{r} - w_{r+1} \geq \lambda (w_{r+1} - w_{r+2})
-\end{align}
-for $r \in \{1,\ldots,m-2\}$, relating the difference between the importance of ranks $r$ and $r+1$ with the difference between ranks $r+1$ and $r+2$.
+In particular, we want to obtain constraints of the type $w_{r} - w_{r+1} \geq \lambda (w_{r+1} - w_{r+2})$ for $r \in \{1,\ldots,m-2\}$, relating the difference between the importance of ranks $r$ and $r+1$ with the difference between ranks $r+1$ and $r+2$.
 

### 2021-01-15 minimax.tex
Shorter example

@@
 	Suppose we want to ask the following question to the chair: $w_{2} - w_{3} ≥ 2 (w_{3} - w_{4})$. 
-In other words, we want to relate the difference between the weights of the second and third positions with the double of the difference between the weights of the third and fourth positions.
-We can rewrite this inequality in the form $w_{2} + 2 w_{4} ≥ 3 w_{3}$, and we can translate the original question in one of the form "is $a$ better than $b$?" where $a$ is an alternative ranked once in second position and twice in fourth position, and $b$ is ranked three times in third position.
-In order to do so, we construct a profile $P$ such that $a$ and $b$ respect these constraints and all the other alternative are strictly worse than them.
+	We then show the following profile to the chair and ask who should win (each column is a preference of a voter).
 	\begin{center}
 		$
-		\begin{array}{ccccc}
-			\#\text{voters} \quad &w_1&w_2&w_3&w_4\\
-			\mathbf{1} \quad &c&a&b&d\\
-			\mathbf{2} \quad &d&c&b&a\\
-			\mathbf{3} \quad &a&b&c&d\\
-			\mathbf{3} \quad &b&a&d&c\\
+		\begin{array}{ccccccccc}
+			c&d&d&a&a&a&b&b&b\\
+			a&c&c&b&b&b&a&a&a\\
+			b&b&b&c&c&c&d&d&d\\
+			d&a&a&d&d&d&c&c&c\\
 		\end{array}.
@@
 	\end{center}
-	The score of the alternatives are $s(a)=3w_1+3w_2+w_2+2w_4$, $s(b)=3w_1+3w_2+3w_3$, $s(c)=w_1+2w_2+3w_3+3w_4$, $s(d)=2w_1+3w_3+4w_4$.
-Since the weights are convex $s(a)>s(c)$, $s(a)>s(d)$, $s(b)>s(c)$ and $s(b)>s(d)$.
-Therefore, if the committee picks $a$ in $P$, the answer to the original question is yes, the converse if $b$ is picked.
+	Both $a$ and $b$ have scores higher than $c$ and $d$ for all convex weights, thus either $a$ or $b$ will be picked under our hypothesis; and $s(a) ≥ s(b) ⇔ w_2 + 2 w_4 ≥ 3 w_3$.
 \end{example*}

### 2021-01-15 minimax.tex
Shorter about questioning approach

@@
 The pairwise maximum regret $\PMR(x,y;\pprofile,W)$ of $x$ relative to $y$ given the partial profile $\pprofile$ and the set of weights $W$
-is the worst-case loss of choosing $x$ instead of $y$ under all possible realizations of the full profile {\em and} all possible instantiations of the weights: $\PMR(x,y; \pprofile, W) & = \max_{\w \in W} \max_{\profile \in C(\pprofile)} s(y; \profile,\w) - s(x; \profile,\w)$.
+is the worst-case loss of choosing $x$ instead of $y$ under all possible realizations of the full profile {\em and} all possible instantiations of the weights: $\PMR(x,y; \pprofile, W) = \max_{\w \in W} \max_{\profile \in C(\pprofile)} s(y; \profile,\w) - s(x; \profile,\w)$.
 The maximum regret $\MaxR(x;\pprofile,W)$ is the worst-case loss of $x$.
 That is the loss occurred as the result of an adversarial selection of the complete profile $\profile \in C(\pprofile)$ and of the scoring vector $\w \in W$ that together maximize the loss between $x$ and the true winner under $\profile$ and $\w$: $\MaxR(x; \pprofile, W) = \max_{y \in A} \PMR(x,y; \pprofile, W) = \max_{\w \in W} \max_{\profile \in C(\profile)} \Regret(x; \profile, \w)$.
-Finally,  $\MMR(\pprofile,W)$ is the value of minimax regret under $\pprofile$ and $W$, obtained when recommending a minimax optimal alternative $x^*_{\pprofile, W} \in A^*_{\pprofile, W}$: $\MMR(\pprofile,W) & = \min_{x \in A} \MaxR(x;\pprofile,W)$ and $A^*_{\pprofile, W} & = \argmin_{x \in A} \MaxR(x;\pprofile,W)$.
+Finally,  $\MMR(\pprofile,W)$ is the value of minimax regret under $\pprofile$ and $W$, obtained when recommending a minimax optimal alternative $x^*_{\pprofile, W} \in A^*_{\pprofile, W}$: $\MMR(\pprofile,W) = \min_{x \in A} \MaxR(x;\pprofile,W)$ and $A^*_{\pprofile, W} = \argmin_{x \in A} \MaxR(x;\pprofile,W)$.
 By picking as consensus choice
@@
 \paragraph{Building concrete questions for the chair}
-As we assume that the weights constitute the utility components of the chair, it might be reasonable to assume that the chair is able to answer such abstract questions in our setting.
-However, it is important to make sure that a question can also, in principle, be asked in a more concrete way, in terms of winners of example profiles.
-This permits to test how the chair understands the question and to relate the preference of the chair to her choice behavior in the economic sense.
-
-Such questions have precise semantics whose understanding is shared by the chair.
-This way of asking questions is sufficiently natural that it has been used in experimental settings investigating the feeling of justice of individuals \citep{Giritligil2005}.
-To the best of our knowledge, the use of such questions to systematically guide an elicitation process is novel.
-
+The chair might be considered able to answer such abstract questions in our setting; but we consider it important to make sure that these questions can also be asked in a more concrete way, in terms of winners of example profiles: such questions have precise semantics whose understanding can be assumed to be shared by the chair, contrary to abstract questions about weights.
 Our approach is analogous to that of decision theorists with preference elicitation: a large stream of research considers more meaningful to ask direct choice questions ("please choose either a or b") than to question the decision maker about the shape of its utility function.
 The former are considered "observable": acts of choice are translated to preference statements.
+In the social choice context, this way of asking questions has been used in experimental settings investigating the feeling of justice of individuals \citep{Giritligil2005}, but, to the best of our knowledge, the use of such questions to systematically guide an elicitation process is novel.
 
-Furthermore this will be necessary for an ordinal extension of our work where the scores would not be considered as cardinal utilities.
 Thus, our task is to build a profile, given $\lambda$ and $r ≤ m-2$, in such a way that the set of (tied) winners picked by the chair reveals whether $w_{r} - w_{r+1} \geq \lambda (w_{r+1} - w_{r+2})$.
@@
 \end{example*}
-
-At this stage, we are satisfied that a procedure exists to transform our abstract questions to questions about winners of a PSR.
-Further studies would investigate, for example, what is lost in terms of elicitation efficiency when we are forced to restrain to realistic concrete questions, meaning, questions involving small profiles; or investigate the relationship between our understanding of scores as (cardinal) utility and (ordinal) scores as definition of a PSR.
 
@@
 To avoid the absorption property of the max, we adopt $\leximax$ as an aggregator.
-Pessimistic thus considers question $q_1$ to be better  than $q_2$ iff
-\begin{align}
-	R^{\max}_1 < R^{\max}_2 \text{ or } [R^{\max}_1 = R^{\max}_2 \text{ and } R^{\min}_1 < R^{\min}_2].
-\end{align}
+Pessimistic thus considers question $q_1$ to be better  than $q_2$ iff $R^{\max}_1 < R^{\max}_2 \text{ or } [R^{\max}_1 = R^{\max}_2 \text{ and } R^{\min}_1 < R^{\min}_2]$.
 %This comparison gives a way of picking questions among a set of possible questions, by picking one that minimizes this approximate measure of minimax regret {\em a posteriori}. 

### 2021-01-15 cover letter/resubmission.tex
Minor changes

@@
 %from R1, Accept (good paper, I can argue for accepting it); from R2, Weak accept (marginally above the acceptance theshold, rejecting it would not be that bad); from R3, Weak reject (marginally below the acceptance threshold, accepting it would not be that bad); and from R4, Reject (Not good enough, I can argue for rejecting it).
-The strongest criticisms from the last two reviewers (R3 and R4).
-According to R3 we should have improved the presentation with a larger example and expanded the discussion (R3 incorrectly thought that we had room to spare within the constraints imposed by IJCAI);  R4 found that our literature review omitted important related works, that the results in the paper were incremental in nature; and that the main contribution or take away message was not clearly stated in the paper.
+The strongest criticisms from the last two reviewers (R3 and R4) and, from R3, that we should have improved the presentation with a larger example and expanded the discussion (R3 incorrectly thought that we had room to spare within the constraints imposed by IJCAI);  R4 found that our literature review omitted important related works, that the results in the paper were incremental in nature; and that the main contribution or take away message was not clearly stated in the paper.
 
@@
 \medskip
-Following the IJCAI rejection we focus our work in extending the literature review and in improving the experimental section %(also taking advantage of the two additional pages), 
+Following the IJCAI rejection we extended the literature review and improved the experimental section %(also taking advantage of the two additional pages), 
 and submitted the resulting work to AAMAS 2021 (with submission ID 554). 
@@
 Notice that we took the opportunity of using the rebuttal to provide an application example and that, after rebuttal, R1 stated that the example we provided in our response was convincing.
-
 About experiments, R1 regretted that we use only impartial culture assumption; that we look at very small elections only; and that the way some of our conclusions are phrased make them appear more general than allowed by the experimental observations.
@@
 \begin{itemize}
-	\item The introduction provides an example of a situation where our approach is applicable (this example was found convincing by AAMAS reviewers after rebuttal).
+	\item The introduction provides an example of a situation where our approach is applicable (which was found convincing by an AAMAS reviewer after rebuttal).
 	\item We better explain our motivation for asking questions that can be phrased as choices of winners out of a profile (which makes the answer “observable” in an econometric sense), and highlight the methodological novelty of this approach.
@@
 The results show that the number of questions to be asked is much smaller with real data than with impartial culture, as expected.
-	\item TODO We better explain what results can be anticipated before presenting the experimental results.
-\commentOC{We just agreed we don’t specifically talk about this and don’t change anything because does not apply here.}
 	\item We changed the phrasing of some of our conclusions that were too general.

### 2021-01-15 minimax.tex
reduced figures and moved tables

@@
 		\begin{axis}[
-			y=10,
+			y=8,
 			xlabel=Number of Questions,
 			ylabel=Avg. Regret,
-			ytick={0,2,4,6,8,10,12},
+			ytick={0,2,4,6,8,10},
 			xtick distance=10,
@@
 			ymin=0,
-			ymax=12,
+			ymax=11,
 			xmin=0,
 			xmax=100,
-			yticklabels={0,2,4,6,8,10,12}]
-			\addlegendimage{mark=*,teal,mark size=2}
-			\addlegendimage{mark=triangle*,orange,mark size=2}
-			\addlegendimage{mark=square*,blue,mark size=2}
-			\addlegendimage{mark=diamond*,red,mark size=2}
+			yticklabels={0,2,4,6,8,10},
+			legend style={font=\scriptsize}]
+			\addlegendimage{mark=*,teal,mark size=1.5}
+			\addlegendimage{mark=triangle*,orange,mark size=1.5}
+			\addlegendimage{mark=square*,blue,mark size=1.5}
+			\addlegendimage{mark=diamond*,red,mark size=1.5}
 
@@
 \sisetup{table-number-alignment = center, table-figures-integer=2, table-figures-decimal=1, table-auto-round}
-\begin{table}
-	\caption{Average MMR in problems of size $(10, 20)$ after $k$ questions.}
-	\label{tab:biggerSize}
-	\begin{tabular}{S[table-figures-integer=3, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=1]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=1]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=1]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
-		\toprule
-		{k} & {Rnd.} & {sd} & {Pes.} & {sd} & {Eli.} & {sd} \\
-		\midrule
-		0 &20.0 & 0.0 & 20.0 & 0.0&  20.0 & 0.0 \\
-		50 & 19.82 & 0.04 &	15.59 &0.56	&17.38& 0.7\\
-		100 & 19.12	& 0.26&	11.91&	1.26 &15.23& 0.73\\
-		150 & 18.06	& 0.47&	8.92&	1.53 &13.38& 1.11\\
-		200 & 16.89	& 0.62&6.24&2.02&11.76& 1.03\\
-		250 & 15.63 & 0.84&	4.64&1.72&10.56& 0.89\\
-		300 & 14.72	& 0.94&	3.01& 1.35 &10.48& 0.87\\
-		350 & 13.41	& 1.15& 1.76& 0.95&10.48& 0.86\\
-		400 & 11.98	& 0.68&	0.62&0.56 &10.48& 0.86\\
-		\bottomrule
-	\end{tabular}
-\end{table}
 \begin{table}[t]
@@
 
-%\subsection{Absolute evaluation of Pessimistic strategy}
-\begin{table}
-	\caption{Number of questions needed by Pessimistic strategy to reach an MMR of $\frac{n}{10}$ (represented by $k_{\MMR}$), by size.}
-	\label{tab:lowRegret}
-	\begin{tabular}{S[table-figures-decimal=0]S[table-figures-decimal=0]SS[table-figures-integer=3, table-figures-decimal=0]}
-		\toprule
-		{m} & {n} & {$\frac{n}{10}$} & {$k_{\MMR}$} \\
-		\midrule
-		5 & 10 & 1 & 60 \\
-		5 & 15 & 1.5 & 80 \\
-		5 & 20 & 2 & 110 \\
-		10 & 20 & 2 & 340 \\
-		10 & 30 & 3 & 527 \\
-		15 & 30 & 3 & 951 \\
-		\bottomrule
-	\end{tabular}
-\end{table}
-
-\paragraph{In-depth evaluation of Pessimistic}
+\paragraph{Evaluation of Pessimistic Strategy}
 \label{sec:lowRegret}
@@
 \begin{figure}[t]
-	\caption{Average MMR (normalized on the number of voters $n$) after $k$ questions with Pessimistic strategy for different problem sizes.}
+	\caption{Average MMR (normalized by $n$) after $k$ questions with Pessimistic strategy for different data-sets.}
 	\label{fig:linearity}
@@
 		\begin{axis}[
-			y=100,
+			y=80,
 			legend columns=3,
@@
 			xmax=1000,
-			yticklabels={0,0.5,1}]
+			yticklabels={0,0.5,1},
+			legend style={font=\scriptsize}]
 
@@
 
-%\begin{figure}
-%	\caption{Average MMR after $k$ questions with Pessimistic strategy for different problem sizes.}
-%	\label{fig:linearity}
-%	\begin{tikzpicture}
-%		\pgfplotsset{
-%			every axis legend/.append style={
-%				at={(0.5,1.03)},
-%				anchor=south
-%			},
-%		}
-%		\begin{axis}[
-%			y=3.5,
-%			legend columns=3,
-%			xlabel=Number of Questions,
-%			ylabel=Avg. Regret,
-%			ytick={0,5,10,15,20,25,30},
-%			xtick distance=100,
-%			ytick distance=5,
-%			xtick pos=left,
-%			ymajorgrids=true,
-%			ytick style={draw=none},
-%			ymin=0,
-%			ymax=31,
-%			xmin=0,
-%			xmax=1000,
-%			yticklabels={0,5,10,15,20,25,30}]
-%			
-%			\addlegendimage{mark=triangle*,teal,mark size=2}
-%			\addlegendimage{mark=*,violet,mark size=2}
-%			\addlegendimage{mark=square*,green,mark size=2}
-%			\addlegendimage{mark=diamond*,red,mark size=2}
-%			\addlegendimage{mark=halfsquare left*,blue,mark size=2}
-%			\addlegendimage{mark=halfsquare right*,brown,mark size=2}
-%			\addlegendimage{mark=pentagon*,cyan,mark size=2}
-%			\addlegendimage{mark=halfsquare*,magenta,mark size=2}
-%			
-%			
-%			\addplot[thick, mark=triangle*, mark size = {2}, mark indices = {35}, teal] table [x=k, y=5.10]{data/linearity.dat};
-%			\addlegendentry{m=5, n=10}
-%			\addplot[thick, mark=*, mark size = {2}, mark indices = {45}, violet] table [x=k, y=5.15]{data/linearity.dat};
-%			\addlegendentry{m=5, n=15}
-%			\addplot[thick, mark=square*, mark size = {2}, mark indices = {90}, green] table [x=k, y=5.20]{data/linearity.dat};
-%			\addlegendentry{m=5, n=20}
-%			\addplot[thick, mark=diamond*, mark size = {2}, mark indices = {150}, red] table [x=k, y=10.20]{data/linearity.dat};
-%			\addlegendentry{m=10, n=20}
-%			\addplot[thick, mark=halfquare left*, mark size = {2}, mark indices = {60}, blue] table [x=k, y=14.9]{data/linearity.dat};
-%			\addlegendentry{m=14, n=9}
-%			\addplot[thick, mark=halfsquare right*, mark size = {2}, mark indices = {60}, brown] table [x=k, y=skate]{data/linearity.dat};
-%			\addlegendentry{skate m14n9}
-%			\addplot[thick, mark=pentagon*, mark size = {2}, mark indices = {300}, cyan] table [x=k, y=10.30]{data/linearity.dat};
-%			\addlegendentry{m=10, n=30}
-%			\addplot[thick, mark=halfsquare*, mark size = {2}, mark indices = {400}, magenta] table [x=k, y=15.30]{data/linearity.dat};
-%			\addlegendentry{m=15, n=30}
-%			
-%		\end{axis}
-%	\end{tikzpicture}
-%\end{figure}
-
-%\begin{figure}
-%	\caption{Average MMR after $k$ questions with Pessimistic strategy for different problem sizes.}
-%
-%	%\Description{Graph showing that the MMR decreases very approximately linearly, and is convex, as a function of the number of questions.}
-%	\includegraphics[width=.45\textwidth]{linearity.png}
-%\end{figure}
-
-\paragraph{Decrease in MMR values}
 We next wonder how fast the regret decreases, measured as a function of the number of questions asked.
@@
 \newpage
-
 \bibliographystyle{named}
@@
 
+\begin{table}[ht]
+	\caption{Number of questions needed by Pessimistic strategy to reach an MMR of $\frac{n}{10}$ (represented by $k_{\MMR}$), by size.}
+	\label{tab:lowRegret}
+	\begin{tabular}{S[table-figures-decimal=0]S[table-figures-decimal=0]SS[table-figures-integer=3, table-figures-decimal=0]}
+		\toprule
+		{m} & {n} & {$\frac{n}{10}$} & {$k_{\MMR}$} \\
+		\midrule
+		5 & 10 & 1 & 60 \\
+		5 & 15 & 1.5 & 80 \\
+		5 & 20 & 2 & 110 \\
+		10 & 20 & 2 & 340 \\
+		10 & 30 & 3 & 527 \\
+		15 & 30 & 3 & 951 \\
+		\bottomrule
+	\end{tabular}
+\end{table}
+
+\sisetup{table-number-alignment = center, table-figures-integer=2, table-figures-decimal=1, table-auto-round}
+\begin{table}[ht]
+	\caption{Average MMR in problems of size $(10, 20)$ after $k$ questions.}
+	\label{tab:biggerSize}
+	\begin{tabular}{S[table-figures-integer=3, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=1]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=1]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=1]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
+		\toprule
+		{k} & {Rnd.} & {sd} & {Pes.} & {sd} & {Eli.} & {sd} \\
+		\midrule
+		0 &20.0 & 0.0 & 20.0 & 0.0&  20.0 & 0.0 \\
+		50 & 19.82 & 0.04 &	15.59 &0.56	&17.38& 0.7\\
+		100 & 19.12	& 0.26&	11.91&	1.26 &15.23& 0.73\\
+		150 & 18.06	& 0.47&	8.92&	1.53 &13.38& 1.11\\
+		200 & 16.89	& 0.62&6.24&2.02&11.76& 1.03\\
+		250 & 15.63 & 0.84&	4.64&1.72&10.56& 0.89\\
+		300 & 14.72	& 0.94&	3.01& 1.35 &10.48& 0.87\\
+		350 & 13.41	& 1.15& 1.76& 0.95&10.48& 0.86\\
+		400 & 11.98	& 0.68&	0.62&0.56 &10.48& 0.86\\
+		\bottomrule
+	\end{tabular}
+\end{table}
+
 \end{document}

### 2021-01-16 minimax.tex
revision Sec 4 and 5

@@
 The goal is to obtain relevant information to reduce minimax regret as quickly as possible.
-As termination condition of elicitation, we can check whether minimax regret is lower than a threshold; or after having asked a given number of questions.
+The elicitation can be terminated either after a given number of questions, or when the minimax regret is lower than a threshold (or until it drops to zero if we wish optimality).
+
+%As termination condition of elicitation, we can check whether minimax regret is lower than a threshold; or after having asked a given number of questions.
 %if we wish optimality, we can perform elicitation until minimax regret drops to zero.
 
-The remainder of this section is structured as follows.
-First, we discuss the different types of questions that can be asked to the agents and to the chair, and the way responses are handled.
-Then, we describe different strategies to determine informative queries to ask next, with the goal of reducing $\MMR(\pprofile,W)$ quickly.
+%The remainder of this section is structured as follows.
+%First, we discuss the different types of questions that can be asked to the agents and to the chair, and the way responses are handled.
+%Then, we describe different strategies to determine informative queries to ask next, with the goal of reducing $\MMR(\pprofile,W)$ quickly.
 
@@
 We distinguish between questions asked to the agents and questions asked to the chair.
-As {\em questions asked to the agents} it is natural to consider comparison queries asking to compare two alternatives.
+As {\em questions asked to the agents} we consider comparison queries relating two alternatives.
 %Another common type of queries are {\em top-k}, asking to each agent her $k$ most preferred alternatives.
@@
 \paragraph{Building concrete questions for the chair}
-The chair might be considered able to answer such abstract questions in our setting; but we consider it important to make sure that these questions can also be asked in a more concrete way, in terms of winners of example profiles: such questions have precise semantics whose understanding can be assumed to be shared by the chair, contrary to abstract questions about weights.
-Our approach is analogous to that of decision theorists with preference elicitation: a large stream of research considers more meaningful to ask direct choice questions ("please choose either a or b") than to question the decision maker about the shape of its utility function.
+Even if the chair might be considered able to answer such abstract questions, we consider important to make sure that these questions can also be asked in a more concrete way: in terms of winners of example profiles.
+Such questions have precise semantics whose understanding can be assumed to be shared by the chair, contrary to abstract questions about weights.
+A large stream of research considers more meaningful to ask direct choice questions ("please choose either a or b") than to question the decision maker about the shape of its utility function.
 The former are considered "observable": acts of choice are translated to preference statements.
 In the social choice context, this way of asking questions has been used in experimental settings investigating the feeling of justice of individuals \citep{Giritligil2005}, but, to the best of our knowledge, the use of such questions to systematically guide an elicitation process is novel.
+Moreover, this way of questioning the chair is independent of the voting rule that is being elicited.
+Asking questions about weights only works when a scoring rule is being considered.
 
@@
 \end{proposition}
+See the proof of construction in \cref{proof:chairQuestions}.
 
@@
 If it opted for a question about weights, it draws one rank in $1 ≤ r ≤ m-2$ equiprobably, takes the middle of the interval of values for $\lambda$ that are still possible considering our knowledge so far, and asks whether $w_r - w_{r+1} ≥ \lambda (w_{r+1} - w_{r+2})$.
-The intervals are initialized to $[1, n]$: $\lambda≥1$ by convexity and we assume $\lambda≤n$ wlog, in fact for $\lambda≥n$, the rule coincides with Plurality.
+%The intervals are initialized to $[1, n]$: $\lambda≥1$ by convexity and we assume $\lambda≤n$ wlog, in fact for $\lambda≥n$, the rule coincides with Plurality.
 If it opted for a question to agents, it draws equiprobably among the agents whose preference is not known entirely; draws an alternative $a$ equiprobably among those involved in some incomparabilities in $\ppref_j$; and draws an alternative $b$ equiprobably among those incomparable with $a$ in $\ppref_j$.
@@
 The \strat{Pessimistic} strategy considers a set of $n + m$ candidate questions: one per agent, and one per rank.
-The candidate questions to the agents use the heuristic proposed by \citet{Lu2011}: for each agent $j$, if $x^*$ and $\bar{y}$ are incomparable in $\ppref_j$, the candidate question concerns the pair $(x^*, \bar{y})$, otherwise, the candidate question concerns the pair $(x^*, z)$ for some $z$ incomparable to $x^*$ (randomly chosen), or if none such $z$ exist, the pair $(\bar{y}, z)$ for some $z$ incomparable to $\bar{y}$, or, if both $x^*$ and $\bar{y}$ are comparable to every alternatives in $\ppref_j$, any incomparable pair is picked at random.
-To understand the rationale behind the heuristic, 
-recall that, as shown in the proof of \cref{claim:completion}, in order to increase $\PMR(x^{*},\bar{y})$, the adversary should place as many alternatives as possible above $x^{*}$ if $x^* \ppref_j \bar{y}$, and between $\bar{y}$ and $x^{*}$ if $\bar{y} \ppref_j x^*$.
-Responses to questions involving $x^*$ or $\bar{y}$ constrain the ability of the adversary to complete the profile in such manner, possibly reducing minimax regret.
+The candidate questions to the agents are chosen following the idea of \citet{Lu2011}: in order to increase $\PMR(x^{*},\bar{y})$, the adversary should place as many alternatives as possible above $x^{*}$ if $x^* \ppref_j \bar{y}$, and between $\bar{y}$ and $x^{*}$ if $\bar{y} \ppref_j x^*$.
+For each agent $j$, if $x^*$ and $\bar{y}$ are incomparable in $\ppref_j$, the candidate question concerns the pair $(x^*, \bar{y})$, otherwise, the candidate question concerns the pair $(x^*, z)$ for some $z$ incomparable to $x^*$ (randomly chosen), or if none such $z$ exist, the pair $(\bar{y}, z)$ for some $z$ incomparable to $\bar{y}$, or, if both $x^*$ and $\bar{y}$ are comparable to every alternatives in $\ppref_j$, any incomparable pair is picked at random.
+%Responses to questions involving $x^*$ or $\bar{y}$ constrain the ability of the adversary to complete the profile in such manner, possibly reducing minimax regret.
 The candidate questions to the chair are determined as in the Random strategy.
-
-The Pessimistic strategy then selects among these $n + m$ candidate questions one that leads to minimal regret in the worst case, considering both possible answers to the question, and with penalty terms depending on the kind of question.
-To define this comparison precisely, assume that a question $q_1$ has type $t_1$ (being “chair” or “agent”), and leads to the new knowledge states $(\pprofile_1, W_1)$ if answered positively and $(\pprofile'_1, W'_1)$ if the answer is negative.
-Define $R^{\max}_1 = \max\set{\MMR(\pprofile_1, W_1), \MMR(\pprofile'_1, W'_1)}$
-and $R^{\min}_1 = \min\set{\MMR(\pprofile_1, W_1), \MMR(\pprofile'_1, W'_1)} \epsilon_{t} + \epsilon'_{t}$.
-%If $(\pprofile_1, W_1) ≥ (\pprofile'_1, W'_1)$, define $\MMR^{\max} = \MMR(\pprofile_1, W_1)$ and $\MMR^{\min} = \MMR(\pprofile'_1, W'_1)$; otherwise, define $\MMR^{\max} = \MMR(\pprofile'_1, W'_1)$ and $\MMR^{\min} = \MMR(\pprofile_1, W_1)$.
-% and and $(\pprofile^\min_2, W^\min_2)$. numbering them so that $\MMR(\pprofile_1, W_1) ≥ \MMR(\pprofile_2, W_2)$. Then the badness of the question in the worst case is:
-The terms $\epsilon_t$ and $\epsilon'_{t}$ are real numbers associated to the type $t$ of question; these parameters are to be determined experimentally and are used to fine control the choice of the question type.
-Define similarly $t_2$, $R^{\max}_2$ and $R^{\min}_2$ for a question $q_2$.
-We are now faced with the problem of aggregating these values in order to compare the informative values of the candidate questions.
-We adopt a pessimistic approach, reported to perform better than optimistic aggregation \citep{Cailloux2014}, although our experiments in this context suggested a weak impact of that choice on the performance of the strategy.
-To avoid the absorption property of the max, we adopt $\leximax$ as an aggregator.
-Pessimistic thus considers question $q_1$ to be better  than $q_2$ iff $R^{\max}_1 < R^{\max}_2 \text{ or } [R^{\max}_1 = R^{\max}_2 \text{ and } R^{\min}_1 < R^{\min}_2]$.
-%This comparison gives a way of picking questions among a set of possible questions, by picking one that minimizes this approximate measure of minimax regret {\em a posteriori}. 
-%The motivation for using this operator lies in 
-In other words if the maximal {\em a posteriori} MMR of two questions are (nearly) equal, then it considers the (penalized) minimal MMR values, preferring the question with the lowest value.
-(Technically, instead of applying a pure lexicographic aggregation, which is very sensitive to small errors due to floating-point computations, we apply a weighted sum between the maximal and the penalized minimal MMR values, with a predominant weight given to the maximal one, several order of magnitudes higher than the weight given to the penalized minimal MMR.)
+The Pessimistic strategy then selects among these $n + m$ candidate questions one that leads to minimal regret in the worst case: for each question we compute the minimax regret for the two possible answers, considering a penalty terms depending on the kind of question, and choose the best according to (quasi-)$\leximax$.
+We provide more details in \cref{sec:appendix}.
 
 The \strat{Extended pessimistic} strategy uses the same criterion as the pessimistic strategy, but extending it to a bigger set of candidate questions, the same as those considered by the Random strategy.
-These candidate questions are then evaluated using the same operator as for the Pessimistic strategy, that is, we compute the minimax regret for the two possible answers, for each candidate question, and choose the best according to (quasi-)$\leximax$.
+These candidate questions are then evaluated using the same operator as for the Pessimistic strategy.
 We use this strategy to test whether Pessimistic performs well: depending on the quality of the heuristic of the Pessimistic strategy, it might perform nearly equally well, or perhaps even better, than Extended pessimistic, while being (much) faster.
@@
 Finally, the \strat{Elitist} strategy aims at uncovering as quickly as possible the top alternative of each agent. It asks $m - 1$ questions to each agent in turn. 
-Given an agent to query $j$, it asks about an alternative currently undominated in $\ppref_j$ and any alternative that it has not yet asked about for that agent, or equivalently, any alternative that is currently incomparable to this alternative.
+Given an agent to query $j$, it asks about an alternative currently undominated in $\ppref_j$ and any alternative that is currently incomparable to this alternative.
 This approach guarantees that the top alternative in the ranking of $j$ will be known after having asked exactly $m-1$ questions to $j$.
@@
 %Our experiments are described by topic here below.
-We start by describing the general protocol of experimentation. %use the following protocol, deviations are indicated below for each experiment.
-Having picked a problem size $(m, n)$, a number of questions $k$ and a strategy to test, we randomly generate an “oracle”, representing the true preferences of the agents (i.e.
+%We start by describing the general protocol of experimentation. %use the following protocol, deviations are indicated below for each experiment.
+We used both real data-sets and generated profiles.
+In the latter case, we pick a problem size $(m, n)$, a number of questions $k$ and a strategy to test, we then randomly generate an “oracle”, representing the true preferences of the agents (i.e.
 the linear orders) and the weights associated with the chair's scoring rule.
 The preferences are generated following an impartial culture assumption: the linear order of each agent is generated independently from the other ones and all have the same probability of appearing.
-IC is a quite challenging situation: as can be expected intuitively (and shown experimentally by \citet{Lu2011} in their setting), the number of questions to be asked decrease with less varied profiles.
-We want to focus on the most critical setting, as there is a wide variety of possible situations to test in such experiments.
-For generating the weights we first draw $m - 1$ numbers uniformly at random (in the interval $\intvl{0,1}$ representing weight ``differences''), normalize and sort them; 
-a sequence of convex decreasing weight is then obtained by a decumulative sum.
+IC is a quite challenging situation: as can be expected intuitively (and shown in \cref{fig:linearity}), the number of questions to be asked decrease with less varied profiles.
+The real preferences are downloaded from \textit{PrefLib: A Library for Preferences} \citep{PrefLib} and passed to the oracle.
+In particular, we used the following data-sets: \textit{T Shirt} (11 T-Shirt designs (m) voted by 30 members (n) of the Optimization Research Group at NICTA), \textit{AGH Course Selection} (9 courses (m) evaluated by 146 students (n) of the AGH University) and Skate (14 skaters (m) evaluated by 9 judges (n) at the Euros Pairs Short Program).
+%We want to focus on the most critical setting, as there is a wide variety of possible situations to test in such experiments.
+For both real and generated data-sets we generate the weights of the scoring rule.
+We first draw $m - 1$ numbers uniformly at random (in the interval $\intvl{0,1}$ representing weight ``differences''), normalize and sort them; a sequence of convex decreasing weight is then obtained by a decumulative sum.
 The penalty parameters for the Pessimistic and Extended pessimistic strategies are set to $\epsilon_{\text{chair}} = 1.1$, $\epsilon'_{\text{chair}} = 10^{-6}$, $\epsilon_{\text{agent}} = 1.0$ and $\epsilon'_{\text{agent}} = 0$.
 
-We start with empty knowledge ($\pprofile = (\emptyset, \emptyset, …), W = \W$) about the preference orderings of the agents or the weight differences favored by the chair.
-We obtain the first question to be asked using the strategy under test, as described above.
+We start with empty knowledge ($\pprofile = (\emptyset, \emptyset, …), W = \W$) about the preference orderings of the agents and the weight differences favored by the chair.
+We obtain the first question to be asked using the strategy under test.
 We then use the oracle to answer the question and update the system's knowledge, which is thus used to obtain the next question.
@@
 Notice that although they exhibit a close performance, Pessimistic performs consistently better, in the sense that the numbers are systematically in favor of Extended pessimistic when performing the experiment again.
-\Cref{tab:biggerSize} shows that these conclusions also hold for a problem of larger size ($m = 10, n = 20$), except that this table does not feature Extended pessimistic, which is too slow to be run repeatedly on such instance.
+In \cref{sec:appendix} we provide a problem of larger size.
 
@@
 We first wonder how many questions should be asked in order to reach a low regret level.
-Here, we consider a low level to be a tenth of the number of agents ($n/10$): such a regret is equivalent to the difference of score of an alternative $x$ that results from switching from a profile $P$ to a profile $P'$ where ten percent of the agents rank $x$ last instead of first.
-The results for various sizes are displayed in \cref{tab:lowRegret}. 
+We consider a low level to be a tenth of the number of agents: such a regret is equivalent to the difference of score of an alternative $x$ that results from switching from a profile $P$ to a profile $P'$ where ten percent of the agents rank $x$ last instead of first.
+The results for various sizes are displayed in \cref{sec:appendix}. 
 For the experiments we performed, we see that the number of questions required to reach a low regret level grows approximately linearly with the number of agents and grows less fast than the square of the number of alternatives.
@@
 These numbers have to be contrasted with the estimated number of questions required to elicit the full preference of an agent which are $6.6$ for $m=5$, $24.8$ for $m=10$ and $48.4$ for $m=15$.
-To obtain these data, we constrained the Pessimistic strategy to ask questions to the agents only, and ran it on a single agent problem, with various values for $m$.
+To obtain these data, we constrained Pessimistic strategy to ask questions to the agents only, and ran it on a single agent problem, with various values for $m$.
 
@@
 This is important practically because it may be impossible or undesirable to ask sufficient questions to reach a low regret level.
-Knowing the speed of decrease permits to know which trade-offs can be achieved between the quality of the resulting recommendation and the number of questions that participants have to answer.
+%Knowing the speed of decrease permits to know which trade-offs can be achieved between the quality of the resulting recommendation and the number of questions that participants have to answer. 
 \Cref{fig:linearity} shows graphically the decrease in MMR according to the number of questions asked for various problem sizes.
 We see that this function is convex, apart from the very first few questions, indicating %to users of our approach
-that, on average, halving the number of questions will only reduce the gain in regret by less than half. \commentBN{Reviewer: Halving the number of questions reduces the regret by more than 50\%.}
-
+that, on average, halving the number of questions will only reduce the gain in regret by less than half. %\commentBN{Reviewer: Halving the number of questions reduces the regret by more than 50\%.}
 At the start of the elicitation, the space of uncertainty is so large that the adversary can attain the maximum possible value of regret; multiple answers are needed to constrain her enough for the MMR to start decreasing.
@@
 
+In \cref{fig:linearity} we can also observe, as expected, that given a problem size the number of questions needed to reach a given MMR is lower when considering a real data-set than a IC generated profile.
+\commentBN{Add more?}
 % do less harm than halving the gain in regret, on average.
@@
 		100 & 2.03 & 1.56 & 1.88 & 1.02  \\
-		150 & 3.41 & 1.79 & 4.07 & 1.51 \\
+%		150 & 3.41 & 1.79 & 4.07 & 1.51 \\
 		200 & 4.61	& 1.35  & 6.53 & 2.0  \\
-		250 & 8.4 & 1.86 & 	7.69 & 1.24 \\
+%		250 & 8.4 & 1.86 & 	7.69 & 1.24 \\
 		300 &11.07 & 0.86& 11.87 & 1.25 \\
-		350 &15.06 & 0.68&15.59 & 0.6 \\
+%		350 &15.06 & 0.68&15.59 & 0.6 \\
 		400 &20.0 & 0.0 & 20.0 & 0.0 \\
@@
 
-We mention some directions for future works.
+%We mention some directions for future works.
 Further development of elicitation strategies, considering alternative heuristics, is an important direction. 
@@
 \section{Appendix}
+\label{sec:appendix}
+\newtheorem*{details*}{Strategy Details}
+
+\begin{details*}[Pessimistic]
+	Once having selected $n + m$ candidate questions, the Pessimistic strategy selects the one that leads to minimal regret in the worst case, considering both possible answers to the question, and with penalty terms depending on the kind of question.
+To define this comparison precisely, assume that a question $q_1$ has type $t_1$ (being “chair” or “agent”), and leads to the new knowledge states $(\pprofile_1, W_1)$ if answered positively and $(\pprofile'_1, W'_1)$ if the answer is negative.
+	Define $R^{\max}_1 = \max\set{\MMR(\pprofile_1, W_1), \MMR(\pprofile'_1, W'_1)}$
+	and $R^{\min}_1 = \min\set{\MMR(\pprofile_1, W_1), \MMR(\pprofile'_1, W'_1)} \epsilon_{t} + \epsilon'_{t}$.
+	%If $(\pprofile_1, W_1) ≥ (\pprofile'_1, W'_1)$, define $\MMR^{\max} = \MMR(\pprofile_1, W_1)$ and $\MMR^{\min} = \MMR(\pprofile'_1, W'_1)$; otherwise, define $\MMR^{\max} = \MMR(\pprofile'_1, W'_1)$ and $\MMR^{\min} = \MMR(\pprofile_1, W_1)$.
+	% and and $(\pprofile^\min_2, W^\min_2)$. numbering them so that $\MMR(\pprofile_1, W_1) ≥ \MMR(\pprofile_2, W_2)$. Then the badness of the question in the worst case is:
+	The terms $\epsilon_t$ and $\epsilon'_{t}$ are real numbers associated to the type $t$ of question; these parameters are to be determined experimentally and are used to fine control the choice of the question type.
+	Define similarly $t_2$, $R^{\max}_2$ and $R^{\min}_2$ for a question $q_2$.
+	We are now faced with the problem of aggregating these values in order to compare the informative values of the candidate questions.
+We adopt a pessimistic approach, reported to perform better than optimistic aggregation \citep{Cailloux2014}, although our experiments in this context suggested a weak impact of that choice on the performance of the strategy.
+	To avoid the absorption property of the max, we adopt $\leximax$ as an aggregator.
+	Pessimistic thus considers question $q_1$ to be better  than $q_2$ iff $R^{\max}_1 < R^{\max}_2 \text{ or } [R^{\max}_1 = R^{\max}_2 \text{ and } R^{\min}_1 < R^{\min}_2]$.
+	%This comparison gives a way of picking questions among a set of possible questions, by picking one that minimizes this approximate measure of minimax regret {\em a posteriori}. 
+	%The motivation for using this operator lies in 
+	In other words if the maximal {\em a posteriori} MMR of two questions are (nearly) equal, then it considers the (penalized) minimal MMR values, preferring the question with the lowest value.
+	(Technically, instead of applying a pure lexicographic aggregation, which is very sensitive to small errors due to floating-point computations, we apply a weighted sum between the maximal and the penalized minimal MMR values, with a predominant weight given to the maximal one, several order of magnitudes higher than the weight given to the penalized minimal MMR.)
+\end{details*}
+
 \begin{sketch*}[\cref{claim:completion}]
@@
 \begin{proof*}[\cref{prop:chairQuestions}]
+	\label{proof:chairQuestions}
 	Define a linear order $>_1$ over $A$ as placing $a$ at rank $r$, $b$ at rank $r + 1$, and the remaining alternatives arbitrarily. 
@@
 \end{proof*}
-
-\begin{table}[ht]
-	\caption{Number of questions needed by Pessimistic strategy to reach an MMR of $\frac{n}{10}$ (represented by $k_{\MMR}$), by size.}
-	\label{tab:lowRegret}
-	\begin{tabular}{S[table-figures-decimal=0]S[table-figures-decimal=0]SS[table-figures-integer=3, table-figures-decimal=0]}
-		\toprule
-		{m} & {n} & {$\frac{n}{10}$} & {$k_{\MMR}$} \\
-		\midrule
-		5 & 10 & 1 & 60 \\
-		5 & 15 & 1.5 & 80 \\
-		5 & 20 & 2 & 110 \\
-		10 & 20 & 2 & 340 \\
-		10 & 30 & 3 & 527 \\
-		15 & 30 & 3 & 951 \\
-		\bottomrule
-	\end{tabular}
-\end{table}
 
@@
 \end{table}
+\Cref{tab:biggerSize} shows that the conclusions of \cref{fig:smallSize} also hold for a problem of larger size ($m = 10, n = 20$), except that this table does not feature Extended pessimistic, which is too slow to be run repeatedly on such instance.
+
+\begin{table}[ht]
+	\caption{Number of questions needed by Pessimistic strategy to reach an MMR of $\frac{n}{10}$ (represented by $k_{\MMR}$), by size.}
+	\label{tab:lowRegret}
+	\begin{tabular}{S[table-figures-decimal=0]S[table-figures-decimal=0]SS[table-figures-integer=3, table-figures-decimal=0]}
+		\toprule
+		{m} & {n} & {$\frac{n}{10}$} & {$k_{\MMR}$} \\
+		\midrule
+		5 & 10 & 1 & 60 \\
+		5 & 15 & 1.5 & 80 \\
+		5 & 20 & 2 & 110 \\
+		10 & 20 & 2 & 340 \\
+		10 & 30 & 3 & 527 \\
+		15 & 30 & 3 & 951 \\
+		\bottomrule
+	\end{tabular}
+\end{table}
 

### 2021-01-17 minimax.tex
Some compression

@@
 		\hfuzz=2cm
-	%Reduces verbosity about the bad line breaks.
-		\hbadness 5000
+	%Reduces verbosity about the bad line breaks. TODO reduce
+		\hbadness 10000
 	%Reduces verbosity about the underful vboxes.
@@
 %This paper considers both sources of uncertainty at the same time, and proposes a method able to recommend a consensus choice without requiring full knowledge of either.
-In this paper we focus on positional scoring rules, that are a particularly common method used to aggregate rankings, and we assume that both the agent preferences and the social choice rule are partially specified.
+In this paper we focus on positional scoring rules, that are a particularly common method used to aggregate rankings. 
 We develop methods, based on the notion of minimax regret, for determining a robust ``winner'' under uncertainty of both the voting rule and the agent preferences.
@@
 We now introduce some basic concepts.
-We consider a set $A$ of $m$ alternatives (products, restaurants, movies, public projects, job candidates, etc.) and a set $\set{1, …, n}$ of agents.
+We consider a set $A$ of $m$ alternatives (products, restaurants, public projects, job candidates, etc.) and a set $N = \set{1, …, n}$ of agents.
 Each agent $j$ comes from an infinite set $\N$ of potential agents and is associated to her “real” preference order ${\pref_j}  \in \linors$ which is a linear order (a connected, transitive, asymmetric relation) over the alternatives.
-Following the social choice nomenclature, we call {\em profile} the association of a preference to each agent, considering a subset of agents from the set $\N$, and denote a profile by $(\pref_1,\ldots,\pref_n)$.
+A {\em profile} $(\pref_1,\ldots,\pref_n)$ associates to each agent a preference, considering a subset of agents from the set $\N$.
 A profile is equivalently represented by $\profile=(v_1,\ldots,v_n)$ where $v_j(i) \in \set{1, \ldots, m}$ denotes the rank (position) of alternative $i$ in the preference order $\pref_j$.
@@
 Let $V$ be the set of possible preference profiles (the union, for any integer $n$, of the $n$-fold Cartesian product of the linear orders over the alternatives).
-A social choice function $f : V \rightarrow \powersetz{A}$ associates a profile with a set of winners, where $\powersetz{A}$ represents the set of subsets of $A$ except for the empty set (sets are used for tied winners).
+A social choice function $f : V \rightarrow \powersetz{A}$ associates to each profile a set of winners, where $\powersetz{A}$ represents the set of subsets of $A$ except for the empty set (sets are used for tied winners).
 Among the many possible social choice functions, we consider {\em positional scoring rules (PSR)}, which attach weights to positions according to the vector $(w_1, \ldots, w_m)$, also known as the {\em scoring vector}.
@@
 
-In this work we assume fixed, but unknown to us, a profile $\profile^*$ representing the preferences $\pref_j^*$ of the agents, and a weight vector $\w^*$ representing the preferences of the chair.
-We will reason about partial preference information concerning those objects.
-At a given time, our knowledge of agent $j$'s preference is encoded by a partial order over the alternatives, thus a transitive and asymmetric binary relation, denoted by $\ppref_j$. 
-In this work we assume that preference information is truthful, i.e. $a \ppref_j b ⇒ a \pref_j^* b$.
+We assume fixed, but unknown to us, a profile $\profile^*$ representing the preferences $\pref_j^*$ of the agents, and a weight vector $\w^*$ representing the preferences of the chair. 
+At a given time, our knowledge of agent $j$'s preference is encoded by a partial order ${\ppref_j} \subseteq {\pref_j^*}$ over the alternatives, thus a transitive and asymmetric binary relation (we assume that preference information is truthful).
 %We use $\prefinc$ to denote incomparability, that is $a \prefinc_{j} b$ iff $a \nppref_j b \wedge b \nppref_j a$.
@@
 
-A completion of $\ppref_j$ is any linear order $\pref$ that extends $\ppref_j$ and we indicate with $C(\ppref_j) = \set{{\succ} \in \linors \suchthat {\ppref_j} \subseteq {\succ}}$ the set of possible completions of $\ppref_i$.
-Then $C(\pprofile)=C(\ppref_1)\times … \times C(\ppref_n)$ is the set of complete profiles extending $p$. Note that $\profile^* \in C(\pprofile)$.
+Let $C(\ppref_j) = \set{{\succ} \in \linors \suchthat {\ppref_j} \subseteq {\succ}}$ denote the set of possible completions of $\ppref_i$ and $C(\pprofile) = \prod_{j \in N} C(\ppref_j)$ the set of complete profiles extending $\pprofile$.
+Note that $\profile^* \in C(\pprofile)$.
 

### 2021-01-17 minimax.tex
Set of agents N and N*

@@
 We now introduce some basic concepts.
-We consider a set $A$ of $m$ alternatives (products, restaurants, public projects, job candidates, etc.) and a set $N = \set{1, …, n}$ of agents.
-Each agent $j$ comes from an infinite set $\N$ of potential agents and is associated to her “real” preference order ${\pref_j}  \in \linors$ which is a linear order (a connected, transitive, asymmetric relation) over the alternatives.
-A {\em profile} $(\pref_1,\ldots,\pref_n)$ associates to each agent a preference, considering a subset of agents from the set $\N$.
-A profile is equivalently represented by $\profile=(v_1,\ldots,v_n)$ where $v_j(i) \in \set{1, \ldots, m}$ denotes the rank (position) of alternative $i$ in the preference order $\pref_j$.
+We consider a set $A$ of $m$ alternatives (products, restaurants, public projects, job candidates, etc.) and an infinite set $\N$ of potential agents.
+A {\em profile} $(\pref_j, j \in N)$ considers a finite subset of agents $N \subset \N$ and associates to each agent a preference order ${\pref_j}  \in \linors$, a linear order over the alternatives.
+A profile is equivalently represented by $\profile=(v_j, j \in N)$ where $v_j(x) \in \set{1, \ldots, m}$ denotes the rank of alternative $x$ in the preference order $\pref_j$.
 
-Let $V$ be the set of possible preference profiles (the union, for any integer $n$, of the $n$-fold Cartesian product of the linear orders over the alternatives).
-A social choice function $f : V \rightarrow \powersetz{A}$ associates to each profile a set of winners, where $\powersetz{A}$ represents the set of subsets of $A$ except for the empty set (sets are used for tied winners).
+A social choice function $f : \cup_{\emptyset ≠ N \subset \N} \linors^N \rightarrow \powersetz{A}$ associates to each profile a set of (tied) winners, where $\powersetz{A}$ represents the set of subsets of $A$ except for the empty set.
 Among the many possible social choice functions, we consider {\em positional scoring rules (PSR)}, which attach weights to positions according to the vector $(w_1, \ldots, w_m)$, also known as the {\em scoring vector}.
 Let $\alpha^{x}_r$ be the number of times that alternative $x$ was ranked in the $r$-th position.
-An alternative obtains a score that depends on the rank obtained in each of the preference orders:
+Given $\profile$ and $\w$, an alternative $x \in A$ obtains the score
 \begin{align}
@@
 	s(x; \profile, \w) = \sum_{j=1}^{n} w_{v_j(x)}
-	= \sum_{r=1}^{m} \alpha^{x}_r w_r 
+	= \sum_{r=1}^{m} \alpha^{x}_r w_r\ .
 \end{align}

### 2021-01-17 minimax.tex
Some more compr

@@
 We now introduce some basic concepts.
-We consider a set $A$ of $m$ alternatives (products, restaurants, public projects, job candidates, etc.) and an infinite set $\N$ of potential agents.
+We consider a set $A$ of $m$ alternatives (products, restaurants, public projects, job candidates, etc.), an infinite set $\N$ of potential agents and a specific finite set of agents $N^* \subset \N$.
+
 A {\em profile} $(\pref_j, j \in N)$ considers a finite subset of agents $N \subset \N$ and associates to each agent a preference order ${\pref_j}  \in \linors$, a linear order over the alternatives.
 A profile is equivalently represented by $\profile=(v_j, j \in N)$ where $v_j(x) \in \set{1, \ldots, m}$ denotes the rank of alternative $x$ in the preference order $\pref_j$. 
-
 A social choice function $f : \cup_{\emptyset ≠ N \subset \N} \linors^N \rightarrow \powersetz{A}$ associates to each profile a set of (tied) winners, where $\powersetz{A}$ represents the set of subsets of $A$ except for the empty set.
-Among the many possible social choice functions, we consider {\em positional scoring rules (PSR)}, which attach weights to positions according to the vector $(w_1, \ldots, w_m)$, also known as the {\em scoring vector}.
+Among the many possible social choice functions, we consider convex {\em positional scoring rules (PSRs)}.
+A PSR $f^{\w}$ is parameterized by a \emph{scoring vector} $\w$ associating weights $w_r \in [0, 1]$ to positions, with $1 = w_1 ≥ w_2 ≥ … ≥ w_m = 0$.
 Let $\alpha^{x}_r$ be the number of times that alternative $x$ was ranked in the $r$-th position.
@@
 \end{align}
-The winners are the alternatives with the highest score.
+The winners $f^{\w}(\profile)$ are the alternatives with highest score.
 
-We assume fixed, but unknown to us, a profile $\profile^*$ representing the preferences $\pref_j^*$ of the agents, and a weight vector $\w^*$ representing the preferences of the chair. 
-At a given time, our knowledge of agent $j$'s preference is encoded by a partial order ${\ppref_j} \subseteq {\pref_j^*}$ over the alternatives, thus a transitive and asymmetric binary relation (we assume that preference information is truthful).
-%We use $\prefinc$ to denote incomparability, that is $a \prefinc_{j} b$ iff $a \nppref_j b \wedge b \nppref_j a$.
-An incomplete profile $\pprofile = (\ppref_1, \ldots, \ppref_n)$ maps each agent to a partial preference.
-
-Let $C(\ppref_j) = \set{{\succ} \in \linors \suchthat {\ppref_j} \subseteq {\succ}}$ denote the set of possible completions of $\ppref_i$ and $C(\pprofile) = \prod_{j \in N} C(\ppref_j)$ the set of complete profiles extending $\pprofile$.
-Note that $\profile^* \in C(\pprofile)$.
-
-We also assume that the weights of the scoring rule are only partially specified.
-Therefore, the vector $(w_1,\ldots,w_m)$  is not known but we are given a set of constraints restraining the possible values that weights can take.
-We consider a decreasing sequence of weights $1 = w_1 ≥ w_2 ≥ … ≥ w_m = 0$, a natural assumption, as it is better to be ranked first than second, second than third, etc.
-
-The weights of a scoring rule can model different preferences of the chair. 
-For instance, the weights can control the inclination to favor ``extreme'' alternatives (often at either the top or the bottom of the input rankings) at the expenses of ``moderate'' alternatives (that are more consistently in the middle part of the input rankings).
-
-An important class of scoring rule is the one composed of weights that represent a convex sequence \citep{Stein1994,Llamazares2016}, meaning that the difference between the weight of the first position and the weight of the second position is at least as large as the difference between the weights of the second and third positions, etc.
+An important class of PSRs is the one using convex weights \citep{Stein1994,Llamazares2016}, meaning that the difference between the weight of the first position and the weight of the second position is at least as large as the difference between the weights of the second and third positions, etc.
 \begin{equation} 
@@
 \end{equation}
-The constraint above is often used when aggregating rankings in sport competitions.
-We use $\W$ to denote the set of convex weight vectors. It is also a natural and common assumption: losing ranks at the top of the ranking is more damaging than losing ranks at the bottom.
+The constraint above is a natural and common assumption, often used when aggregating rankings in sport competitions: losing ranks at the top of the ranking is more damaging than losing ranks at the bottom.
+Let $\W$ denote the set of such convex weight vectors.
 
-In general it can be difficult to set the weights in an appropriate way.
-We assume that, in addition of basic requirements (monotonicity and convexity), the chair is able to specify additional preferences about how the social choice function should behave.
-In this work we assume that the preferences of the chair are encoded with linear constraints about the vector $\w$, relating the value of the weights of different positions, and the set of these constraints is denoted by $\Co_W$.
-Moreover, we use $\pw \subseteq \W$ to denote the set of weight vectors compatible with the preferences expressed by the chair about the scoring vector.
-Of course it may be difficult for real decision makers to state preferences about the voting rule in such an abstract way.
-We will show in \cref{sec:elicit} that the additional preferences we use can be elicited by 
-%asking questions about concrete profiles, for instance, by 
-showing a complete profile of a small synthetic election and asking who should be elected in this case.
+Let $\profile^* = (\pref_j^*, j \in N^*)$ and $\w^*$ denote the profile and weight vector, unknown to us, that represent the preferences of the agents in $N^*$ and of the chair.
+
+At a given time, our knowledge of agent $j$'s preference is encoded by a partial order ${\ppref_j} \subseteq {\pref_j^*}$ over the alternatives, a transitive and asymmetric relation (we assume that preference information is truthful).
+%We use $\prefinc$ to denote incomparability, that is $a \prefinc_{j} b$ iff $a \nppref_j b \wedge b \nppref_j a$.
+An incomplete profile $\pprofile = (\ppref_j, j \in N^*)$ maps each agent to a partial preference.
+Let $C(\ppref_j) = \set{{\succ} \in \linors \suchthat {\ppref_j} \subseteq {\succ}}$ denote the set of possible completions of $\ppref_i$ and $C(\pprofile) = \prod_{j \in N} C(\ppref_j)$ the set of complete profiles extending $\pprofile$.
+Note that $\profile^* \in C(\pprofile)$.
+
+The vector $\w^*$  is also unknown but we assume that the chair is able to specify additional preference information taking the form of linear constraints about $\w^*$.
+Let $\pw \subseteq \W$ denote the set of weight vectors compatible with the preferences expressed by the chair about the scoring vector.
+%Of course it may be difficult for real decision makers to state preferences about the voting rule in such an abstract way.
+We will show in \cref{sec:elicit} that the additional preferences we use can be elicited by showing a complete profile of a synthetic election and asking who should be elected in this case.
 
@@
 \label{sec:mmr}
-In this paper, we consider that both the agent preferences and the preferences of the chair about the voting rule are incomplete.
-As reviewed in \cref{sec:related}, some authors have considered possible and necessary winners assuming 
-either a partial profile or assuming an incompletely specified scoring rule.
-
-Notice that often there are no necessary winners and too many possible winners; it is therefore useful to declare a winner given partial information.
+It is desirable in an elicitation protocol such as ours to be able to stop before reaching full knowledge of the agent preferences or of the preferences of the chair about the voting rule.
+As, often, there are no necessary winners and too many possible winners, it is useful to declare a winner given partial information.
 As a decision criterion to determine a winner, we propose to use minimax regret \citep{Savage1954}. 
@@
 In particular, \citet{Lu2011} have adopted minimax regret for winner determination in social choice where
-the preferences of agents that are only partially known, while the social choice function is predetermined and known.
+the preferences of agents that are partially known, while the social choice function is known.
 
-In this work, we consider the simultaneous presence of uncertainty in agent preferences and in the weights of the scoring rule used as a social choice function.
-Using {\em maximum regret} to quantify the worst-case error, the alternatives that minimize this error are selected as tied winners, providing us with a form of robust optimization.
+We consider the simultaneous presence of incomplete knowledge in agent preferences and in the weights of the PSR.
+We use \emph{maximum regret} to quantify the worst-case error, and let the alternatives that minimize this quantity win, providing us with a form of robust optimization.
 Intuitively, the quality of a proposed alternative $a$ is how far $a$ is from the optimal one in the worst case, given the current knowledge.
@@
 We formalize the notion of minimax regret in multiple steps.
-First of all, $\Regret(x, \profile, \w)$ is the “regret” of selecting $x$ as a winner instead of choosing the optimal alternative under $\profile$ and $\w$: $\Regret(x; \profile, \w) = \max_{y \in A} s(y; \profile,\w) - s(x; \profile, \w)$.
-The pairwise maximum regret $\PMR(x,y;\pprofile,W)$ of $x$ relative to $y$ given the partial profile $\pprofile$ and the set of weights $W$
-is the worst-case loss of choosing $x$ instead of $y$ under all possible realizations of the full profile {\em and} all possible instantiations of the weights: $\PMR(x,y; \pprofile, W) = \max_{\w \in W} \max_{\profile \in C(\pprofile)} s(y; \profile,\w) - s(x; \profile,\w)$.
+First of all, $\Regret(x, \profile, \w) = \max_{y \in A} s(y; \profile,\w) - s(x; \profile, \w)$ is the “regret” of selecting $x$ as a winner instead of choosing the optimal alternative under $\profile$ and $\w$.
+The pairwise maximum regret $\PMR(x,y;\pprofile,W) = \max_{\w \in W} \max_{\profile \in C(\pprofile)} s(y; \profile,\w) - s(x; \profile,\w)$ of $x$ relative to $y$ given the partial profile $\pprofile$ and the set of weights $W$
+is the worst-case loss of choosing $x$ instead of $y$ under all possible realizations of the full profile {\em and} all possible instantiations of the weights.
 The maximum regret $\MaxR(x;\pprofile,W)$ is the worst-case loss of $x$.
@@
 The last proposition shows that PMR is linear in the weights.
-Recall that the preferences of the chair are encoded with linear constraints $\Co_{W}$.
+Recall that $\pw$ represents the weight vectors compatible with the preferences of the chair stated so far.
 The pairwise max regret $\PMR(x,y; \pprofile,W)$ can be obtained as the solution of the following linear program defined on the variables $w_1, …, w_m$, which represent the weights attached to different positions:
@@
 	\max_{\w} & \sum_{r=1}^m (\hat{\alpha}_{r}^{y} - \hat{\alpha}_{r}^{x}) w_{r}\\
-	\text{ s.t. } & w_1 = 1, w_m = 0, \text{\cref{eq:convexity}} \text{ and } \Co_W.
+	\text{ s.t. } & w_1 = 1, w_m = 0, \text{\cref{eq:convexity}} \text{ and } w \in \pw.
 \end{align}
@@
 
-An open-source library, allowing to reproduce our experiments, will be made publicly available.\footnote{URL not displayed for anonymity reasons.}
+As part of our contribution, a general open-source library, allowing to reproduce our experiments and perform many more, will be made publicly available (URL not displayed for ensuring anonymity).
 %and serve as a basis for further research

### 2021-01-17 minimax.tex
Six pages.

@@
 We consider the simultaneous presence of incomplete knowledge in agent preferences and in the weights of the PSR.
-We use \emph{maximum regret} to quantify the worst-case error, and let the alternatives that minimize this quantity win, providing us with a form of robust optimization.
+We use \emph{maximum regret} to quantify the worst-case error, and let the alternatives that minimize this quantity win, giving some robustness in face of ignorance.
 Intuitively, the quality of a proposed alternative $a$ is how far $a$ is from the optimal one in the worst case, given the current knowledge.
@@
 is the worst-case loss of choosing $x$ instead of $y$ under all possible realizations of the full profile {\em and} all possible instantiations of the weights.
-The maximum regret $\MaxR(x;\pprofile,W)$ is the worst-case loss of $x$.
-That is the loss occurred as the result of an adversarial selection of the complete profile $\profile \in C(\pprofile)$ and of the scoring vector $\w \in W$ that together maximize the loss between $x$ and the true winner under $\profile$ and $\w$: $\MaxR(x; \pprofile, W) = \max_{y \in A} \PMR(x,y; \pprofile, W) = \max_{\w \in W} \max_{\profile \in C(\profile)} \Regret(x; \profile, \w)$.
-Finally,  $\MMR(\pprofile,W)$ is the value of minimax regret under $\pprofile$ and $W$, obtained when recommending a minimax optimal alternative $x^*_{\pprofile, W} \in A^*_{\pprofile, W}$: $\MMR(\pprofile,W) = \min_{x \in A} \MaxR(x;\pprofile,W)$ and $A^*_{\pprofile, W} = \argmin_{x \in A} \MaxR(x;\pprofile,W)$.
-By picking as consensus choice
-an alternative associated with minimax regret, we can provide a recommendation that gives worst-case guarantees, giving some robustness in face of uncertainty (due to both not knowing the agent preferences and the weights used in the aggregation).
-In cases of ties in minimax regret, we can either decide to return all minimax alternatives $A^*_{\pprofile, W}$ as winners or to pick just one of them using some tie-breaking strategy.
+The maximum regret $\MaxR(x;\pprofile,W) = \max_{y \in A} \PMR(x,y; \pprofile, W) = \max_{\w \in W} \max_{\profile \in C(\profile)} \Regret(x; \profile, \w)$ is the worst-case loss of $x$.
+That is the loss occurred as the result of an adversarial selection of the complete profile $\profile \in C(\pprofile)$ and of the scoring vector $\w \in W$ that together maximize the loss between $x$ and the true winner under $\profile$ and $\w$.
+Finally,  $\MMR(\pprofile,W) = \min_{x \in A} \MaxR(x;\pprofile,W)$ is the value of minimax regret under $\pprofile$ and $W$, obtained when recommending a minimax optimal alternative $x^*_{\pprofile, W} \in A^*_{\pprofile, W} = \argmin_{x \in A} \MaxR(x;\pprofile,W)$.
+Picking as consensus choice an alternative associated with minimax regret provides a recommendation that gives worst-case guarantees. 
+In cases of ties in minimax regret, we can return all minimax alternatives $A^*_{\pprofile, W}$ as winners or pick one of them using some tie-breaking strategy.
 
-Observe that if $\MMR(\pprofile, W)\!=\!0$, then any $x^{*}_{\pprofile,W} \in A^*_{\pprofile, W}$ is a necessary co-winner; this means that for any valid completion of the profile and any feasible $w \in W$, $x^{*}_{\pprofile,W}$ obtains the highest score.
+Observe that if $\MMR(\pprofile, W)\!=\!0$, then any $x^{*}_{\pprofile,W} \in A^*_{\pprofile, W}$ is a necessary winner: any valid completion of the profile and choice of $w \in W$ gives to $x^{*}_{\pprofile,W}$ the highest score.
 
@@
 \paragraph{Computation of minimax regret}
-In order to compute pairwise maximum regret, and therefore minimax regret, we decompose the $\PMR$ into the contributions associated to each agent by adapting the reasoning from \citet{Lu2011}.
+In order to compute pairwise maximum regret, and therefore minimax regret, we decompose the PMR into the contributions associated to each agent by adapting the reasoning from \citet{Lu2011} \commentOC{Cite Conitzer}.
 The setting is however more challenging due to the presence of uncertainty in the weights.
@@
 Since scoring rules are additively decomposable, we can consider separately the contribution of each agent to the total score.
-Thus, we can write the actual regret of choosing $x$ instead of $y$ as $s(y; \profile,\w) - s(x; \profile, \w) = \sum_{j=1}^n w_{v_j(y)} - w_{v_j(x)}$, and we can rewrite $\PMR$ as $\PMR(x,y; \pprofile, W) = \max_{\w \in W} \max_{\profile \in C(\pprofile)} [ s(y; \profile,\w) - s(x; \profile,\w) ] =  \max_{\w \in W} \sum_{j=1}^{n} \max_{v_j \in C(\succ_j^p)} [w_{v_j(y)} - w_{v_j(x)}]$.
-Note that in general the inner max depends on the weights chosen by the outer max.
+Thus, we can write the actual regret of choosing $x$ instead of $y$ as $s(y; \profile,\w) - s(x; \profile, \w) = \sum_{j=1}^n w_{v_j(y)} - w_{v_j(x)}$, and we obtain $\PMR(x,y; \pprofile, W) =  \max_{\w \in W} \sum_{j=1}^{n} \max_{v_j \in C(\succ_j^p)} [w_{v_j(y)} - w_{v_j(x)}]$.
+%Note that in general the inner max depends on the weights chosen by the outer max.
 
-We are interested in computing $\PMR(x, y; \pprofile, W)$.
-This represents the “worst” difference of score, thus the difference of score between $y$ and $x$ under the worst case preferences compatible with $\pprofile$ and $W$, where the worst case is the one that maximizes this difference of score.
-We consider now a procedure for completing a partial profile that was first proposed by \citet{Lu2011} when considering %minimax regret with 
-a fixed weight vector.
-As we will show, this procedure can also be used when the weight vector is not completely known. Let us write $a \pprefeq_j b$ iff $a \ppref_j b \lor a = b$.
+The following propositions (with proofs in appendix) show that the procedure for completing a partial profile that was first proposed by \citet{Lu2011} when considering a fixed weight vector also applies in our setting.
+We write $a \pprefeq_j b$ iff $a \ppref_j b \lor a = b$ and adopt the canonical notation when considering a relation as a function, writing for example ${\pprefeq_j}(x)$ to designate $\set{y \suchthat x \pprefeq_j y}$.
 
@@
 
-Let ${\pprefeq_j}(x)$ designate the set of alternatives known to be considered by $j$ as less good than or equal to $x$, and ${\pprefinv_j}(y)$ be the set of alternatives known to be considered by $j$ as strictly better than $y$.
 \begin{proposition} \label{claim:rankPMR}
@@
 
-The proposition can also be understood by observing that in the case $(x \pprefeq_j y)$, $\beta$ is the number of alternatives incomparable with both $x$ and $y$.
 \begin{proposition}
@@
 $\hat{\alpha}_{r}^{x}$)  is the number of times $y$ (resp.
-$x$) is at rank $r$ in the complete profile $\hat{\profile}$ as determined in \cref{claim:rankPMR}.
+$x$) has rank $r$ in the complete profile $\hat{\profile}$ defined in \cref{claim:rankPMR}.
 %\ref{claim:completion}.
 \end{proposition}
+
+(\cref{claim:rankPMR} can be understood by observing that in the case $(x \pprefeq_j y)$, $\beta$ is the number of alternatives incomparable with both $x$ and $y$.)
 The last proposition shows that PMR is linear in the weights.
-Recall that $\pw$ represents the weight vectors compatible with the preferences of the chair stated so far.
-The pairwise max regret $\PMR(x,y; \pprofile,W)$ can be obtained as the solution of the following linear program defined on the variables $w_1, …, w_m$, which represent the weights attached to different positions:
+%Recall that $\pw$ represents the weight vectors compatible with the preferences of the chair stated so far.
+The pairwise max regret $\PMR(x,y; \pprofile,W)$ can thus be obtained by solving the following linear program defined on the variables $w_1, …, w_m$:
 \begin{align}
 	\max_{\w} & \sum_{r=1}^m (\hat{\alpha}_{r}^{y} - \hat{\alpha}_{r}^{x}) w_{r}\\
-	\text{ s.t. } & w_1 = 1, w_m = 0, \text{\cref{eq:convexity}} \text{ and } w \in \pw.
+	\text{ s.t. } & w_1 = 1 ≥ … ≥ w_m = 0, \text{\cref{eq:convexity}} \text{ and } \w \in \pw.
 \end{align}
@@
 
-The max regret $\MaxR(x; \pprofile, W)$ is determined by considering the pairwise regret of $x$ with all other alternatives in $A$.
-Optimal alternatives w.r.t. minimax regret are the ones with least max regret. 
-Observe that, whenever the $\PMR$ of an alternative $x$ (against some other alternative $y$) exceeds the best MR value found so far, we do not need to further evaluate $x$. 
-This idea can be exploited further by adopting a minimax-search tree \citep{Braziunas2012}.
+The max regret $\MaxR(x; \pprofile, W)$ is determined by considering the pairwise regret of $x$ with all other alternatives in $A$, and the recommended alternatives are the ones with least max regret.
+Observe that when the $\PMR$ of an alternative $x$ (against some other alternative $y$) exceeds the best MR value found so far, we do not need to further evaluate $x$. 
+This idea can be exploited using a minimax-search tree \citep{Braziunas2012}.
 

### 2021-01-17 cover letter/resubmission.tex
revision cover letter

@@
 \section{Summary of previous criticisms and our corrections}
-\commentOC{See \href{https://ijcai-21.org/cfp/}{CFP, Resubmissions}.}
-
 Dear editors and reviewers,
@@
 \item R1: Accept {\em (good paper, I can argue for accepting it)};
-\item R2: Weak accept {\em (marginally above the acceptance theshold, rejecting it would not be that bad)};
+\item R2: Weak accept {\em (marginally above the acceptance threshold, rejecting it would not be that bad)};
 \item R3: Weak reject {\em (marginally below the acceptance threshold, accepting it would not be that bad)}; and
@@
 
-%from R1, Accept (good paper, I can argue for accepting it); from R2, Weak accept (marginally above the acceptance theshold, rejecting it would not be that bad); from R3, Weak reject (marginally below the acceptance threshold, accepting it would not be that bad); and from R4, Reject (Not good enough, I can argue for rejecting it).
-The strongest criticisms from the last two reviewers (R3 and R4) and, from R3, that we should have improved the presentation with a larger example and expanded the discussion (R3 incorrectly thought that we had room to spare within the constraints imposed by IJCAI);  R4 found that our literature review omitted important related works, that the results in the paper were incremental in nature; and that the main contribution or take away message was not clearly stated in the paper.
+The strongest criticisms came from the last two reviewers (R3 and R4): R3 pointed out that we should have improved the presentation with a larger example and expanded the discussion (R3 incorrectly thought that the IJCAI page limit was 7 instead of 6, excluding the additional page for references);  R4 found that our literature review omitted important related works, that the results in the paper were incremental in nature and that the main contribution or take away message was not clearly stated in the paper.
 
@@
 \medskip
-Following the IJCAI rejection we extended the literature review and improved the experimental section %(also taking advantage of the two additional pages), 
-and submitted the resulting work to AAMAS 2021 (with submission ID 554). 
-Our AAMAS submission received the following evaluations (full reviews are given in Section \ref{sec:reviews-aamas}):
+\paragraph*{First improvements:}Following IJCAI rejection we reworked the paper trying to solve the issues mentioned by reviewers: we extended the literature review adding a new dedicated section; we improved the experimental section increasing the size of the experiments, adding a new strategy and describing thoroughly the results obtained.
+We also added more figures and tables with the idea of giving a more immediate understanding of the experimental results.
+%(also taking advantage of the two additional pages),
+
+We submitted the resulting work to AAMAS 2021 (with submission ID 554) receiving the following evaluations (full reviews are given in Section \ref{sec:reviews-aamas}):
 \begin{itemize}
@@
 	\item We changed the phrasing of some of our conclusions that were too general.
+	\item \commentBN{"Shouldn't we add that we removed proofs and tables?"}
 \end{itemize}

### 2021-01-18 minimax.tex
solved warning
Further reduction and small modifs

@@
 \usepackage{soul}
+\usepackage[hidelinks,hypertexnames=false]{hyperref}
 \usepackage{amsthm}
-\usepackage[hidelinks]{hyperref}
 
@@
 The goal is to obtain relevant information to reduce minimax regret as quickly as possible.
-The elicitation can be terminated either after a given number of questions, or when the minimax regret is lower than a threshold (or until it drops to zero if we wish optimality).
+The elicitation can be terminated either after a given number of questions, or when the minimax regret is lower than a threshold (or when it drops to zero if we wish optimality).
 
@@
 \paragraph{Building concrete questions for the chair}
-Even if the chair might be considered able to answer such abstract questions, we consider important to make sure that these questions can also be asked in a more concrete way: in terms of winners of example profiles.
+Even if the chair might be considered able to answer directly such abstract questions, we want to ensure that these questions can also, in principle, be asked in a more concrete way: in terms of winners of example profiles.
 Such questions have precise semantics whose understanding can be assumed to be shared by the chair, contrary to abstract questions about weights.
-A large stream of research considers more meaningful to ask direct choice questions ("please choose either a or b") than to question the decision maker about the shape of its utility function.
-The former are considered "observable": acts of choice are translated to preference statements.
-In the social choice context, this way of asking questions has been used in experimental settings investigating the feeling of justice of individuals \citep{Giritligil2005}, but, to the best of our knowledge, the use of such questions to systematically guide an elicitation process is novel.
-Moreover, this way of questioning the chair is independent of the voting rule that is being elicited.
-Asking questions about weights only works when a scoring rule is being considered.
+Moreover, this way of questioning the chair is independent of the voting rule that is being elicited. Asking questions about weights only works when a scoring rule is being considered.
+Asking who should win in specific profiles has been used in experimental settings investigating the feeling of justice of individuals \citep{Giritligil2005}, but, to the best of our knowledge, the use of such questions to systematically guide an elicitation process about voting rules is novel.
+This is similar to favor, in decision theory, direct choice questions ("please choose either a or b") compared to questioning the decision maker about the shape of her utility function.
+The former are considered “observable”: acts of choice are translated to preference statements \citep{colell_microeconomic_1995}.
 
@@
 \end{proposition}
-See the proof of construction in \cref{proof:chairQuestions}.
 
@@
 	Both $a$ and $b$ have scores higher than $c$ and $d$ for all convex weights, thus either $a$ or $b$ will be picked under our hypothesis; and $s(a) ≥ s(b) ⇔ w_2 + 2 w_4 ≥ 3 w_3$.
+	(\cref{proof:chairQuestions} presents the general method of constructing such profile.)
 \end{example*}
@@
 \paragraph{Elicitation strategies}
-We develop several elicitation strategies for simultaneous elicitation of agent preferences and of the scoring rule.
+We develop several strategies for simultaneous elicitation of agent preferences and of the PSR.
 While it is of course possible to first fully elicit the agent preferences and afterwards elicit weights, we want to investigate experimentally approaches that are able to recommend winning alternatives before obtaining complete knowledge of the profile or the rule.
 %Indeed, it can be beneficial to split efforts asking questions to the chair and to agents, depending on which is estimated to be more informative.
-We define here the various strategies we tested experimentally. A strategy tells us, given the current partial knowledge $(\pprofile, W)$, which question should be asked next.
+We define here the various strategies we tested experimentally. A strategy tells us, given the current partial knowledge $(\pprofile, W)$, which question to ask next.
 
 The \strat{Random} strategy gives a baseline for comparison and informs about the difficulty of an elicitation problem. 
-This strategy first chooses equiprobably whether it will ask a question about weights or a question about a preference ordering.
-If it opted for a question about weights, it draws one rank in $1 ≤ r ≤ m-2$ equiprobably, takes the middle of the interval of values for $\lambda$ that are still possible considering our knowledge so far, and asks whether $w_r - w_{r+1} ≥ \lambda (w_{r+1} - w_{r+2})$.
+It first chooses equiprobably whether to question the chair or the agents.
+In the first case, it draws one rank in $1 ≤ r ≤ m-2$ equiprobably, takes the middle of the interval of values for $\lambda$ that are still possible considering our knowledge so far, and asks whether $w_r - w_{r+1} ≥ \lambda (w_{r+1} - w_{r+2})$.
 %The intervals are initialized to $[1, n]$: $\lambda≥1$ by convexity and we assume $\lambda≤n$ wlog, in fact for $\lambda≥n$, the rule coincides with Plurality.
-If it opted for a question to agents, it draws equiprobably among the agents whose preference is not known entirely; draws an alternative $a$ equiprobably among those involved in some incomparabilities in $\ppref_j$; and draws an alternative $b$ equiprobably among those incomparable with $a$ in $\ppref_j$.
+In the second case, it draws equiprobably among the agents whose preference is not known entirely; draws an alternative $a$ equiprobably among those involved in some incomparabilities in $\ppref_j$; and draws an alternative $b$ equiprobably among those incomparable with $a$ in $\ppref_j$.
 
-Let $(x^{*},\bar{y}, \bar{\profile}, \bar{\w})$ be the current solution of the minimax regret, where $\bar{y}, \bar{\profile}, \bar{\w}$ are, respectively, the choice of $y$, the completion of the profile and the selection of weights for which $x^{*}$ is the minimax optimal alternative.
-The \strat{Pessimistic} strategy considers a set of $n + m$ candidate questions: one per agent, and one per rank.
-The candidate questions to the agents are chosen following the idea of \citet{Lu2011}: in order to increase $\PMR(x^{*},\bar{y})$, the adversary should place as many alternatives as possible above $x^{*}$ if $x^* \ppref_j \bar{y}$, and between $\bar{y}$ and $x^{*}$ if $\bar{y} \ppref_j x^*$.
-For each agent $j$, if $x^*$ and $\bar{y}$ are incomparable in $\ppref_j$, the candidate question concerns the pair $(x^*, \bar{y})$, otherwise, the candidate question concerns the pair $(x^*, z)$ for some $z$ incomparable to $x^*$ (randomly chosen), or if none such $z$ exist, the pair $(\bar{y}, z)$ for some $z$ incomparable to $\bar{y}$, or, if both $x^*$ and $\bar{y}$ are comparable to every alternatives in $\ppref_j$, any incomparable pair is picked at random.
-%Responses to questions involving $x^*$ or $\bar{y}$ constrain the ability of the adversary to complete the profile in such manner, possibly reducing minimax regret.
+Let $(x^{*},\bar{y}, \bar{\profile}, \bar{\w})$ be the current solution of the minimax regret, where $x^{*}$ is the minimax optimal alternative and $\bar{y}, \bar{\profile}, \bar{\w}$ the corresponding adversarial choices.
+The \strat{Pessimistic} strategy considers a set of $n + m$ candidate questions: one per agent, and one per rank \commentOC{Isn’t this $m-2$?}.
+The candidate questions to the agents are chosen by extending the idea of \citet{Lu2011}, that priviledge learning about the relationship of $x^*$ and $\bar{y}$ to the other alternatives if possible.
 The candidate questions to the chair are determined as in the Random strategy.
-The Pessimistic strategy then selects among these $n + m$ candidate questions one that leads to minimal regret in the worst case: for each question we compute the minimax regret for the two possible answers, considering a penalty terms depending on the kind of question, and choose the best according to (quasi-)$\leximax$.
-We provide more details in \cref{sec:appendix}.
+The Pessimistic strategy selects among these $n + m$ candidate questions one that leads to minimal regret in the worst case: for each question we compute the minimax regret for the two possible answers, considering a penalty terms depending on the kind of question, and choose the best according to (quasi-)$\leximax$.
+\Cref{sec:appendix} provides more details.
 
@@
 Given an agent to query $j$, it asks about an alternative currently undominated in $\ppref_j$ and any alternative that is currently incomparable to this alternative.
-This approach guarantees that the top alternative in the ranking of $j$ will be known after having asked exactly $m-1$ questions to $j$.
+Thus, the top alternative in the ranking of $j$ will be known after having asked exactly $m-1$ questions to $j$.
 After having asked $n (m-1)$ questions to the agents, it questions the chair only, using the same approach as the Pessimistic strategy.
@@
 \label{sec:experiments}
-We  performed a number of numerical experiments in order to validate our approach and to test the performance of the different elicitation strategies.
+We  performed a number of numerical experiments using both real data and generated profiles in order to validate our approach and to test the performance of the different elicitation strategies.
 %Our experiments are described by topic here below.
 %We start by describing the general protocol of experimentation. %use the following protocol, deviations are indicated below for each experiment.
-We used both real data-sets and generated profiles.
-In the latter case, we pick a problem size $(m, n)$, a number of questions $k$ and a strategy to test, we then randomly generate an “oracle”, representing the true preferences of the agents (i.e.
-the linear orders) and the weights associated with the chair's scoring rule.
-The preferences are generated following an impartial culture assumption: the linear order of each agent is generated independently from the other ones and all have the same probability of appearing.
-IC is a quite challenging situation: as can be expected intuitively (and shown in \cref{fig:linearity}), the number of questions to be asked decrease with less varied profiles.
-The real preferences are downloaded from \textit{PrefLib: A Library for Preferences} \citep{PrefLib} and passed to the oracle.
-In particular, we used the following data-sets: \textit{T Shirt} (11 T-Shirt designs (m) voted by 30 members (n) of the Optimization Research Group at NICTA), \textit{AGH Course Selection} (9 courses (m) evaluated by 146 students (n) of the AGH University) and Skate (14 skaters (m) evaluated by 9 judges (n) at the Euros Pairs Short Program).
-%We want to focus on the most critical setting, as there is a wide variety of possible situations to test in such experiments.
-For both real and generated data-sets we generate the weights of the scoring rule.
-We first draw $m - 1$ numbers uniformly at random (in the interval $\intvl{0,1}$ representing weight ``differences''), normalize and sort them; a sequence of convex decreasing weight is then obtained by a decumulative sum.
-The penalty parameters for the Pessimistic and Extended pessimistic strategies are set to $\epsilon_{\text{chair}} = 1.1$, $\epsilon'_{\text{chair}} = 10^{-6}$, $\epsilon_{\text{agent}} = 1.0$ and $\epsilon'_{\text{agent}} = 0$.
 
+Given a problem size $(m, n)$, a number of questions $k$ and a strategy to test, we first create an “oracle”, representing the true preferences of the agents (randomly generated or coming from real data) and the weights associated with the chair’s scoring rule (randomly generated).
 We start with empty knowledge ($\pprofile = (\emptyset, \emptyset, …), W = \W$) about the preference orderings of the agents and the weight differences favored by the chair.
@@
 The sizes of the considered scenarios are comparable to the ones used by \citet{Cailloux2014}.
+
+The oracle is built as follows. 
+For the real preferences, we used the following data sets from \href{https://www.preflib.org/}{PrefLib} \citep{PrefLib}.
+\textit{T Shirt}: $m = 11$ tee shirt designs voted by $n = 30$ members of the Optimization Research Group at NICTA \commentOC{refs for these data sets?}; \textit{AGH Course Selection}: $m = 9$ courses evaluated by $n = 146$ students of the AGH University; and \emph{Skate}: $m = 14$ skaters evaluated by $n = 9$ judges at the Euros Pairs Short Program.
+%We want to focus on the most critical setting, as there is a wide variety of possible situations to test in such experiments.
+For the generated preferences, we follow an Impartial Culture (IC) assumption: the linear order of each agent is drawn independently and all have the same probability of appearing.
+We adopt IC because it is a more challenging situation: as can be expected intuitively (and shown in \cref{fig:linearity}), the number of questions to be asked decrease with less varied profiles.
+To generate the weights of the scoring rule, we first draw $m - 1$ numbers uniformly at random (in the interval $\intvl{0,1}$ representing weight ``differences''), normalize and sort them; a sequence of convex decreasing weight is then obtained by a decumulative sum.
 
@@
 \begin{details*}[Pessimistic]
+	Given $j \in N^*$, if $x^*$ and $\bar{y}$ are incomparable in $\ppref_j$, the candidate question concerns the pair $(x^*, \bar{y})$, otherwise, the candidate question concerns the pair $(x^*, z)$ for some $z$ incomparable to $x^*$ (randomly chosen), or if none such $z$ exist, the pair $(\bar{y}, z)$ for some $z$ incomparable to $\bar{y}$, or, if both $x^*$ and $\bar{y}$ are comparable to every alternatives in $\ppref_j$, any incomparable pair is picked at random.
+%Responses to questions involving $x^*$ or $\bar{y}$ constrain the ability of the adversary to complete the profile in such manner, possibly reducing minimax regret.
 	Once having selected $n + m$ candidate questions, the Pessimistic strategy selects the one that leads to minimal regret in the worst case, considering both possible answers to the question, and with penalty terms depending on the kind of question.
@@
 	(Technically, instead of applying a pure lexicographic aggregation, which is very sensitive to small errors due to floating-point computations, we apply a weighted sum between the maximal and the penalized minimal MMR values, with a predominant weight given to the maximal one, several order of magnitudes higher than the weight given to the penalized minimal MMR.)
+
+The penalty parameters for the Pessimistic and Extended pessimistic strategies are set to $\epsilon_{\text{chair}} = 1.1$, $\epsilon'_{\text{chair}} = 10^{-6}$, $\epsilon_{\text{agent}} = 1.0$ and $\epsilon'_{\text{agent}} = 0$.
 \end{details*}

### 2021-01-18 minimax.tex
shorten introduction

--- 2021-01-17 minimax.tex
@@
 In many situations, such as in group recommender systems, the goal is to find a consensus choice;
-%It is therefore natural to look at methods from social choice and see how they can be adapted for group decision-making in a computerized setting.
-social choice theory can provide foundations for such applications. %Methods from social choice can be adapted for group decision-making in a computerized setting.
+social choice theory can provide foundations for such applications
 
-The traditional approach to social choice assumes that both the social choice function and the full preference orderings of the agents (voters) are expressed beforehand.
+%The traditional approach to social choice assumes that both the social choice function and the full preference orderings of the agents (voters) are expressed beforehand.
 These represent two strong hypothesis.
+The traditional approach to social choice assumes that 1) the social choice function and 2) the full preference orderings of the agents are expressed beforehand. These represent two strong hypothesis.
+
 Requiring agents to express full preference orderings can be prohibitively costly (in terms of cognitive and communication cost).
-This observation has motivated a number of recent works considering social choice with partial preference orders and incremental elicitation of agent preferences.
+This observation has motivated several works assuming partial preference orders; 
+%and incremental elicitation of agent preferences. 
+%In the context of social choice, several authors have been interested in obtaining information about winners with reduced assumptions about the knowledge of the agent preferences (assuming that the voting rule is known).
+one early work is  by \Citet{Conitzer2005} who studied the complexity of communication when using different voting rules. %determining lower and upper bounds;
+%they showed that, 
+%in the worst case, the agents should send their complete set of preference for several rules. 
+\Citet{Konczak05} studied the computation of possible and necessary winners for various voting rules; %and showed that the problem is hard in the general case.
+\citet{Xia2008} then showed that, while the identification of a necessary co-winner in scoring rules is polynomial,  the determination of possible co-winners is NP-hard;
+% they also  proposed polynomial-time algorithms when using maximin and Bucklin.
+additional complexity results were given by \citet{Walsh2007} and \citet{Pini2007}.
+%\citep{Walsh2007} showed that the general case remains computationally hard even when restricting to single-peaked preferences;  sufficient conditions that ensure tractability were then found \citep{Pini2007}.
 
-Furthermore, it is often difficult for non-expert users to formalize a voting rule on the basis of some generic preferences over a desired aggregation method.
+Since in many practical situations there would be too many possible winners but no necessary winners,  
+several works addressed the problem of  elicitation of agent preferences \citep{Naamani-Dery2015,Kalech2011,Lu2011,Pini2009,Benabbou2016,Dey2016,Dey2016_2}  using a variety of approaches (minimax regret, Bayesian methods, etc.) with the goal of converging to a necessary winner; \citep{Walsh2009,Conitzer2009}  analyzed when to stop the elicitation process.
+
+Furthermore, it is often difficult for non-experts to formalize a voting rule on the basis of some generic preferences over a desired aggregation method.
 Thus, the first hypothesis should also be relaxed.
+%While most of the focus in the research community has been in dealing with incomplete agent preferences, 
 Consider, as an example, a committee that is about to hire a new employee, whose performances are evaluated by several experts.
@@
 at each step of the elicitation ask a question either to one of the agents or to the chair (the person or organization supervising the voting process) and discuss several heuristics that determine queries that quickly reduce regret.
-Answers to questions are encoded in terms of constraints; questions to the agents are comparions between pairs of alternatives while
+Answers to questions are encoded in terms of constraints; questions to the agents are comparisons between pairs of alternatives while
 questions to the chair ask  to select who should be the winner in a synthetic profile.
-While previous works have considered either partial information about the agent preferences or a partially specified aggregation method, we do not know of any work considering both sources of uncertainty at the same time.
-Actually, very few works altogether have considered the problem of eliciting a voting rule by asking questions to the chair.
+
+While some previous works have considered partially specified aggregation methods \citep{Stein1994,Llamazares2013,Viappiani2018}, we do not know of any work considering both sources of uncertainty at the same time.
+%has dealt with %scenarios where it is instead the voting rule that is partially defined. % but the preferences are given. 
+%a  partially defined voting rule.
+%While previous works have considered either partial information about the agent preferences or a partially specified aggregation method, we do not know of any work considering both sources of uncertainty at the same time.
+Actually, very few works altogether have considered the problem of eliciting a voting rule by asking questions to the chair;  we are aware of the work of \Citet{Cailloux2014}, that assumes a different representation for the rule.
+%we mention the work of \Citet{Cailloux2014} considering elicitation the voting rule by assuming a specific representation.
+
+%A classic paper is the one by \citet{Stein1994} that, considering scoring rules, identified dominance relations between alternatives; these relations allow to determine pairs of alternatives where the first is at least as good as the second no matter which weights are chosen among a generic class of weights (decreasing weighs or convex decreasing weights).
+%More recent articles considered the problem of dealing with unspecified weights in positional scoring rules: \citet{Llamazares2013} proposed a method based on Data Envelopment Analysis (DEA), while \citet{Viappiani2018} proposed to aggregate the uncertainty in weights using criteria used in decision-making under uncertainty (such as minimax regret).
+% provided an elicitation framework for a different class of rules.
 
@@
 We compare the effectiveness of several strategies  including strategies that proceed in phases, learning first as much as possible about the voting rule and then focus on eliciting agent's preferences, and as well strategies that interwind questions to chair and to the agents based on which is estimated to provide more information.
-%Our approach permits to compare experimentally strategies that question the chair, the agents, or both.
-
-%A concrete application of our work might be a committee that is about to hire a new employee, whose performances are evaluated by several experts.
-The members of the committee may not have a voting rule in mind at the start of the process, and might not wish to agree on a specific voting rule, but they might be willing to answer enough questions about selecting winners out of specific profiles to determine their employee of choice.
-
-%We describe informally here a few of the conclusions stemming from these experiments, given a problem involving $m$ alternatives and $n$ agents.
-First, a good quality recommendation can be reached by asking what can be considered a reasonable number of questions to the chair and agents.
-For example, in a problem of size $m = 5$, $n = 10$, only $55$ questions in total are required to reach a good quality recommendation, which can be considered reasonable as these questions are to be dispatched over $10$ agents and the chair.
-%Second, the quality of the recommendation increases faster than linearly with the number of questions,  after an initial phase with almost no increase in quality, before slowing down and converging to an optimal recommendation.
-%Third, we experimentally find out that asking questions only to the agents performs similarly to asking questions both to the agents and the chair, although questions to the chair do have a positive value in terms of quality of the recommendation.
-%Knowing this permits to choose the questioning strategy wisely depending on the estimated cost of each kind of question, which depends on the application.
-
-%NOTE: the structure of the article is perhaps self evident...
-%The paper is organized as follows. \Cref{sec:related} reviews the works related to our objective and
-%\Cref{sec:background} provides the necessary background.
-In \cref{sec:mmr} we provide a method for robust winner determination using the minimax criterion.
-%, a method that selects a winner that minimizes the worst possible regret.
-%In Section \ref{sec:elicit} we provide an interactive elicitation protocol based on minimal regret;  Section \ref{sec:experiments} presents an experimental validation of our approach and some guidelines stemming from these simulations; and Section \ref{sec:conclusions} provides some final thoughts.
-
-\paragraph{Related Work}
-\label{sec:related}
-In the context of social choice, several authors have been interested in obtaining information about winners with reduced assumptions about the knowledge of the agent preferences (assuming that the voting rule is known).
-One early work is  by \Citet{Conitzer2005} who studied the complexity of communication, using different voting rules; %determining lower and upper bounds;
-%they showed that, 
-in the worst case, the agents should send their complete set of preference for several rules. 
-\Citet{Konczak05} studied the computation of possible and necessary winners in the case of partial knowledge of agent preferences, for various voting rules; %and showed that the problem is hard in the general case.
-\citet{Xia2008} then showed that, while the identification of a necessary co-winner in scoring rules is polynomial,  the determination of possible co-winners is NP-hard; they also  proposed polynomial-time algorithms when using maximin and Bucklin.
-\citep{Walsh2007} showed that the general case remains computationally hard even when restricting to single-peaked preferences \citep{Walsh2007};  sufficient conditions that ensure tractability were then found \citep{Pini2007}.
-
-Since in many practical situations there would be too many possible winners but no necessary winners, %several authors proposed elicitation methods of agent preferences. 
-several works addressed the problem of  elicitation of agent preferences \citep{Naamani-Dery2015,Kalech2011,Lu2011,Pini2009,Benabbou2016,Dey2016,Dey2016_2}  using a variety of approaches (minimax regret, Bayesian methods, etc.), with the goal of converging to a necessary winners; \citep{Walsh2009,Conitzer2009}  analyzed when to stop the elicitation process.
-
-While most of the focus in the research community has been in dealing with incomplete agent preferences, 
-another line of research \citep{Stein1994,Llamazares2013,Viappiani2018} has dealt with %scenarios where it is instead the voting rule that is partially defined. % but the preferences are given. 
-a  partially defined voting rule.
-%A classic paper is the one by \citet{Stein1994} that, considering scoring rules, identified dominance relations between alternatives; these relations allow to determine pairs of alternatives where the first is at least as good as the second no matter which weights are chosen among a generic class of weights (decreasing weighs or convex decreasing weights).
-%More recent articles considered the problem of dealing with unspecified weights in positional scoring rules: \citet{Llamazares2013} proposed a method based on Data Envelopment Analysis (DEA), while \citet{Viappiani2018} proposed to aggregate the uncertainty in weights using criteria used in decision-making under uncertainty (such as minimax regret).
-\Citet{Cailloux2014} provided an elicitation framework for a different class of rules.
 

### 2021-01-18 minimax.tex
Minor rewording

--- 2021-01-18 minimax.tex
@@
 \label{sec:experiments}
-We  performed a number of numerical experiments using both real data and generated profiles in order to validate our approach and to test the performance of the different elicitation strategies.
+We  performed a number of numerical experiments using both real data and generated profiles in order to validate our approach and test the performance of our elicitation strategies.
 %Our experiments are described by topic here below.
@@
 This is repeated until $k$ answers have been obtained, computing the resulting MMR values along the way for various values of $k$.
-We repeat this whole experiment a variable number of times indicated below, for a given $(m, n, k)$, and report the average resulting MMR and the standard deviation \textit{sd}.
+We repeat this whole experiment a variable number of times, for a given $(m, n, k)$, and report the average resulting MMR and standard deviation \textit{sd}.
 The sizes of the considered scenarios are comparable to the ones used by \citet{Cailloux2014}.
@@
 We also see that Pessimistic performs slightly better than Extended pessimistic, showing that Pessimistic chooses candidate questions wisely; this is good news since Pessimistic is much faster: it takes on average only $16$s for a complete elicitation session (for $m = 5$, $n = 10$ and $100$ questions), while Extended pessimistic takes $50$s.
-Notice that although they exhibit a close performance, Pessimistic performs consistently better, in the sense that the numbers are systematically in favor of Extended pessimistic when performing the experiment again.
-In \cref{sec:appendix} we provide a problem of larger size.
+Although their performance is close, Pessimistic performs systematically better in multiple runs of the experiment.
+\Cref{sec:appendix} provides a problem of larger size.
 
@@
 \label{sec:lowRegret}
-While in previous experiments we compared Pessimistic to the other strategies, in this set of experiments, we evaluate the Pessimistic strategy in absolute terms. 
+This set of experiments evaluate the Pessimistic strategy in absolute terms. 
 We first wonder how many questions should be asked in order to reach a low regret level.

### 2021-01-19 minimax.tex
Some comments

@@
 Given a problem size $(m, n)$, a number of questions $k$ and a strategy to test, we first create an “oracle”, representing the true preferences of the agents (randomly generated or coming from real data) and the weights associated with the chair’s scoring rule (randomly generated).
-We start with empty knowledge ($\pprofile = (\emptyset, \emptyset, …), W = \W$) about the preference orderings of the agents and the weight differences favored by the chair.
+We start with empty knowledge ($\pprofile = \emptyset, W = \W$) about the preference orderings of the agents and the weight differences favored by the chair.
 We obtain the first question to be asked using the strategy under test.
@@
 
-\begin{figure}[t]
+\begin{figure}
 	\caption{Average MMR in problems of size $(5, 10)$ after $k$ questions.}
@@
 \sisetup{table-number-alignment = center, table-figures-integer=2, table-figures-decimal=1, table-auto-round}
-\begin{table}[t]
+\begin{table}
 	\caption{Average MMR in problems of size $(10, 20)$ and geometric weights after $k$ questions.}
@@
 \label{sec:lowRegret}
-This set of experiments evaluate the Pessimistic strategy in absolute terms. 
+Our next set of experiments evaluate the Pessimistic strategy in absolute terms. 
 We first wonder how many questions should be asked in order to reach a low regret level.
 We consider a low level to be a tenth of the number of agents: such a regret is equivalent to the difference of score of an alternative $x$ that results from switching from a profile $P$ to a profile $P'$ where ten percent of the agents rank $x$ last instead of first.
-The results for various sizes are displayed in \cref{sec:appendix}. 
+The results for various sizes are displayed in \cref{sec:appendix} \commentOC{TODO}. 
 For the experiments we performed, we see that the number of questions required to reach a low regret level grows approximately linearly with the number of agents and grows less fast than the square of the number of alternatives.
@@
 These numbers have to be contrasted with the estimated number of questions required to elicit the full preference of an agent which are $6.6$ for $m=5$, $24.8$ for $m=10$ and $48.4$ for $m=15$.
-To obtain these data, we constrained Pessimistic strategy to ask questions to the agents only, and ran it on a single agent problem, with various values for $m$.
+To obtain these data, we constrained the Pessimistic strategy to ask questions to the agents only, and ran it on a single agent problem, with various values for $m$.
 
@@
 
-%\subsection{Decrease in MMR values}
-
-\begin{figure}[t]
+\begin{figure}
 	\caption{Average MMR (normalized by $n$) after $k$ questions with Pessimistic strategy for different data-sets.}
@@
 In \cref{fig:linearity} we can also observe, as expected, that given a problem size the number of questions needed to reach a given MMR is lower when considering a real data-set than a IC generated profile.
-\commentBN{Add more?}
+\commentBN{Add more?} \commentOC{Strange $m=14, n=9$; t-shirts; and comparison between ts and m10n30 is not clearly in favor of real data.
+I’d suppress the discussion about speed of reduction.}
 % do less harm than halving the gain in regret, on average.

### 2021-01-19 minimax.tex
No data-sets

@@
 \begin{figure}
-	\caption{Average MMR (normalized by $n$) after $k$ questions with Pessimistic strategy for different data-sets.}
+	\caption{Average MMR (normalized by $n$) after $k$ questions with Pessimistic strategy for different data sets.}
 	\label{fig:linearity}
@@
 
-In \cref{fig:linearity} we can also observe, as expected, that given a problem size the number of questions needed to reach a given MMR is lower when considering a real data-set than a IC generated profile.
+In \cref{fig:linearity} we can also observe, as expected, that given a problem size the number of questions needed to reach a given MMR is lower when considering a real data set than a IC generated profile.
 \commentBN{Add more?} \commentOC{Strange $m=14, n=9$; t-shirts; and comparison between ts and m10n30 is not clearly in favor of real data.

### 2021-01-19 minimax.tex
references, agreed changes and take away messages

@@
 \pgfplotsset{compat=1.16}
+
+\setlist[itemize]{noitemsep, topsep=0pt}
 
@@
 Our approach is evaluated experimentally in simulations where the both the voting rule and the agent's preferences are initially unknown to the system and incrementally revealed by answering questions.
-We compare the effectiveness of several strategies  including strategies that proceed in phases, learning first as much as possible about the voting rule and then focus on eliciting agent's preferences, and as well strategies that interwind questions to chair and to the agents based on which is estimated to provide more information.
+We compare the effectiveness of several strategies  including strategies that proceed in phases, learning first as much as possible about the voting rule and then focus on eliciting agent's preferences, and as well strategies that interwind \commentBN{Is it a real word?
+The dictionary corrects me with https://dictionary.cambridge.org/it/dizionario/inglese/intertwined} questions to chair and to the agents based on which is estimated to provide more information.
+In this work:
+\begin{itemize}
+	\item we provide a new mechanism for the elicitation of the voting rule which translate abstract questions about weights to direct choice questions about a profile;  
+	\item we show that, starting with zero knowledge, it is possible to reach a reasonable low regret level with a reasonable number of questions;
+	\item we present different elicitation strategies proving that it is possible to achieve good results without sacrificing computation time;
+	\item we show that for the class of rule considered, only few questions about the voting rule are enough to reach a low regret level;
+	\item we show that low degree of similarity among preference rankings (like in the case of impartial culture) is a more challenging setting than less varied profiles.
+\end{itemize}
 
@@
 \paragraph{Computation of minimax regret}
-In order to compute pairwise maximum regret, and therefore minimax regret, we decompose the PMR into the contributions associated to each agent by adapting the reasoning from \citet{Lu2011} \commentOC{Cite Conitzer}.
-The setting is however more challenging due to the presence of uncertainty in the weights.
+Given a voting rule and a partially specified profile, \citet{Xia2008} determine necessary winners by showing constructions that attempt to maximize the score difference between a proposed winner and a chosen alternative.
+This reasoning was later adopted by \citet{Lu2011} who used the considerations on the worse-case completions for computing the minimax regret.
+
+In order to compute pairwise maximum regret, and therefore minimax regret, we decompose the PMR into the contributions associated to each agent by adapting this same reasoning to our setting.
+The context is however more challenging due to the presence of uncertainty in the weights.
 
@@
 For the real preferences, we used the following data sets from \href{https://www.preflib.org/}{PrefLib} \citep{PrefLib}.
-\textit{T Shirt}: $m = 11$ tee shirt designs voted by $n = 30$ members of the Optimization Research Group at NICTA \commentOC{refs for these data sets?}; \textit{AGH Course Selection}: $m = 9$ courses evaluated by $n = 146$ students of the AGH University; and \emph{Skate}: $m = 14$ skaters evaluated by $n = 9$ judges at the Euros Pairs Short Program.
+\textit{T Shirt}: $m = 11$ tee shirt designs voted by $n = 30$ members of the Optimization Research Group at NICTA; \textit{AGH Course Selection}: $m = 9$ courses evaluated by $n = 146$ students of the AGH University; and \emph{Skate}: $m = 14$ skaters evaluated by $n = 9$ judges at the Euros Pairs Short Program.
 %We want to focus on the most critical setting, as there is a wide variety of possible situations to test in such experiments.
@@
 We consider a low level to be a tenth of the number of agents: such a regret is equivalent to the difference of score of an alternative $x$ that results from switching from a profile $P$ to a profile $P'$ where ten percent of the agents rank $x$ last instead of first.
-The results for various sizes are displayed in \cref{sec:appendix} \commentOC{TODO}. 
+The results for various sizes are displayed in \cref{tab:lowRegret}.
+
+\commentBN{Replace the following paragraph with real stats on the distribution of questions.}
 For the experiments we performed, we see that the number of questions required to reach a low regret level grows approximately linearly with the number of agents and grows less fast than the square of the number of alternatives.
@@
 To obtain these data, we constrained the Pessimistic strategy to ask questions to the agents only, and ran it on a single agent problem, with various values for $m$.
+
+\begin{table}[ht]
+	\caption{Number of questions needed by Pessimistic strategy to reach an MMR of $\frac{n}{10}$ (represented by $k_{\MMR}$), by size.}
+	\label{tab:lowRegret}
+	\begin{tabular}{S[table-figures-decimal=0]S[table-figures-decimal=0]SS[table-figures-integer=3, table-figures-decimal=0]}
+		\toprule
+		{m} & {n} & {$\frac{n}{10}$} & {$k_{\MMR}$} \\
+		\midrule
+		5 & 10 & 1 & 60 \\
+		5 & 15 & 1.5 & 80 \\
+		5 & 20 & 2 & 110 \\
+		10 & 20 & 2 & 340 \\
+		10 & 30 & 3 & 527 \\
+		15 & 30 & 3 & 951 \\
+		\bottomrule
+	\end{tabular}
+\end{table}
 
@@
 
-We next wonder how fast the regret decreases, measured as a function of the number of questions asked.
+%We next wonder how fast the regret decreases, measured as a function of the number of questions asked.
 This is important practically because it may be impossible or undesirable to ask sufficient questions to reach a low regret level.
-%Knowing the speed of decrease permits to know which trade-offs can be achieved between the quality of the resulting recommendation and the number of questions that participants have to answer. 
-\Cref{fig:linearity} shows graphically the decrease in MMR according to the number of questions asked for various problem sizes.
+%%Knowing the speed of decrease permits to know which trade-offs can be achieved between the quality of the resulting recommendation and the number of questions that participants have to answer. 
+%\Cref{fig:linearity} shows graphically the decrease in MMR according to the number of questions asked for various problem sizes.
 We see that this function is convex, apart from the very first few questions, indicating %to users of our approach
-that, on average, halving the number of questions will only reduce the gain in regret by less than half. %\commentBN{Reviewer: Halving the number of questions reduces the regret by more than 50\%.}
-At the start of the elicitation, the space of uncertainty is so large that the adversary can attain the maximum possible value of regret; multiple answers are needed to constrain her enough for the MMR to start decreasing.
+%that, on average, halving the number of questions will only reduce the gain in regret by less than half. %\commentBN{Reviewer: Halving the number of questions reduces the regret by more than 50\%.}
+%At the start of the elicitation, the space of uncertainty is so large that the adversary can attain the maximum possible value of regret; multiple answers are needed to constrain her enough for the MMR to start decreasing.
 When approaching optimality, the pace of MMR reduction decreases.
@@
 In \cref{fig:linearity} we can also observe, as expected, that given a problem size the number of questions needed to reach a given MMR is lower when considering a real data set than a IC generated profile.
-\commentBN{Add more?} \commentOC{Strange $m=14, n=9$; t-shirts; and comparison between ts and m10n30 is not clearly in favor of real data.
-I’d suppress the discussion about speed of reduction.}
+\commentBN{Add the following:}
+By looking at the data we observe that:
+\begin{itemize}
+	\item \textit{Skate} - the top-2 alternatives are the same for all voters, and 8 out of 9 voters rank the same alternative at position 3;
+	\item \textit{AGH} - all voters rank the same alternative at the top position, different group of voters share the same preference rankings;
+	\item \textit{T Shirt} - the alternatives are evenly distributed in the preference rankings.
+\end{itemize}
+The experiments suggest that high degree of similarity in the preference rankings helps reducing the regret faster.
 % do less harm than halving the gain in regret, on average.
@@
 \bibliographystyle{named}
-\bibliography{biblio}
+{\small \bibliography{biblio}}
 
@@
 
-\begin{table}[ht]
-	\caption{Number of questions needed by Pessimistic strategy to reach an MMR of $\frac{n}{10}$ (represented by $k_{\MMR}$), by size.}
-	\label{tab:lowRegret}
-	\begin{tabular}{S[table-figures-decimal=0]S[table-figures-decimal=0]SS[table-figures-integer=3, table-figures-decimal=0]}
-		\toprule
-		{m} & {n} & {$\frac{n}{10}$} & {$k_{\MMR}$} \\
-		\midrule
-		5 & 10 & 1 & 60 \\
-		5 & 15 & 1.5 & 80 \\
-		5 & 20 & 2 & 110 \\
-		10 & 20 & 2 & 340 \\
-		10 & 30 & 3 & 527 \\
-		15 & 30 & 3 & 951 \\
-		\bottomrule
-	\end{tabular}
-\end{table}
-
 \end{document}

### 2021-01-19 minimax.tex
Take-away (a must have, in periods of Covid).

@@
 
-Our approach is evaluated experimentally in simulations where the both the voting rule and the agent's preferences are initially unknown to the system and incrementally revealed by answering questions.
-We compare the effectiveness of several strategies  including strategies that proceed in phases, learning first as much as possible about the voting rule and then focus on eliciting agent's preferences, and as well strategies that interwind \commentBN{Is it a real word?
-The dictionary corrects me with https://dictionary.cambridge.org/it/dizionario/inglese/intertwined} questions to chair and to the agents based on which is estimated to provide more information.
+Let us also mention works addressing the manipulability of voting rules \citep{Elkind2012,Dey2018,Dey2018_2,Conitzer2011,Baumeister2019}, and studies of strategic behaviors
+% when agents learn incrementally about other agent preferences
+ \citep{Endriss2016,Lev2019,Annemieke2012}.
+
+Our approach is evaluated in simulations where both the voting rule and the agent's preferences are initially unknown to the system and incrementally revealed by answering questions.
+We compare the effectiveness of several strategies of choosing questions depending on the current knowledge.
 In this work:
 \begin{itemize}
-	\item we provide a new mechanism for the elicitation of the voting rule which translate abstract questions about weights to direct choice questions about a profile;  
-	\item we show that, starting with zero knowledge, it is possible to reach a reasonable low regret level with a reasonable number of questions;
-	\item we present different elicitation strategies proving that it is possible to achieve good results without sacrificing computation time;
-	\item we show that for the class of rule considered, only few questions about the voting rule are enough to reach a low regret level;
-	\item we show that low degree of similarity among preference rankings (like in the case of impartial culture) is a more challenging setting than less varied profiles.
+	\item we provide a novel mechanism for elicitating a voting rule by translating abstract questions about weights to direct choice questions about a profile;  
+	\item we show that in small problem sizes, starting with zero knowledge, it is possible to reach a low regret level with a reasonable number of questions;
+	\item we present elicitation strategies that achieve good results within reasonable computation time for small problem sizes;
+	\item we show that for the class of rule considered, asking a few questions about the voting rule suffice to reach a low regret level;
+	\item our experiments suggest that low degree of similarity among preference rankings (like in the case of impartial culture) is a more challenging setting than less varied profiles.
 \end{itemize}
-
-Finally, we mention works addressing the manipulability of voting rules \citep{Elkind2012,Dey2018,Dey2018_2,Conitzer2011,Baumeister2019}, and studies of strategic behaviors
-% when agents learn incrementally about other agent preferences
- \citep{Endriss2016,Lev2019,Annemieke2012}.
 

### 2021-01-19 minimax.tex
some wording

@@
 
-Let us also mention works addressing the manipulability of voting rules \citep{Elkind2012,Dey2018,Dey2018_2,Conitzer2011,Baumeister2019}, and studies of strategic behaviors
-% when agents learn incrementally about other agent preferences
- \citep{Endriss2016,Lev2019,Annemieke2012}.
+We also mention works addressing the manipulability of voting rules \citep{Elkind2012,Dey2018,Dey2018_2,Conitzer2011,Baumeister2019} and 
+strategic behaviors \citep{Endriss2016,Lev2019,Annemieke2012}.
 
 Our approach is evaluated in simulations where both the voting rule and the agent's preferences are initially unknown to the system and incrementally revealed by answering questions.
-We compare the effectiveness of several strategies of choosing questions depending on the current knowledge.
-In this work:
+We compare the effectiveness of several question strategies based on the current knowledge about the rule and preferences.
+To summarize:
 \begin{itemize}
-	\item we provide a novel mechanism for elicitating a voting rule by translating abstract questions about weights to direct choice questions about a profile;  
-	\item we show that in small problem sizes, starting with zero knowledge, it is possible to reach a low regret level with a reasonable number of questions;
+	\item we provide a novel mechanism for eliciting a voting rule by translating abstract questions about weights to a choice of an alternative given a concrete profile;  
+	\item we show that in small problem sizes, %starting with zero knowledge,
+	 it is possible to reach a low regret level with a reasonable number of questions;
 	\item we present elicitation strategies that achieve good results within reasonable computation time for small problem sizes;
 	\item we show that for the class of rule considered, asking a few questions about the voting rule suffice to reach a low regret level;
-	\item our experiments suggest that low degree of similarity among preference rankings (like in the case of impartial culture) is a more challenging setting than less varied profiles.
+	\item our experiments suggest that low degree of similarity among preferences %rankings 
+	(as in impartial culture) is a more challenging setting than less varied profiles.
 \end{itemize}
@@
 
-As part of our contribution, a general open-source library, allowing to reproduce our experiments and perform many more, will be made publicly available (URL not displayed for ensuring anonymity).
+As part of our contribution, a general open-source library, allowing to reproduce our experiments and perform many more, will be made publicly available.\footnote{URL not displayed for ensuring anonymity.}
 %and serve as a basis for further research

### 2021-01-19 minimax.tex
introduction and references size

@@
 These represent two strong hypothesis.
-The traditional approach to social choice assumes that 1) the social choice function and 2) the full preference orderings of the agents are expressed beforehand. These represent two strong hypothesis.
+The traditional approach to social choice assumes that 1) the full preference orderings of the agents and 2) the social choice function are expressed beforehand. These represent two strong hypothesis.
 
 Requiring agents to express full preference orderings can be prohibitively costly (in terms of cognitive and communication cost).
-This observation has motivated several works assuming partial preference orders; 
+This observation has motivated several works assuming partial preference orders: 
 %and incremental elicitation of agent preferences. 
 %In the context of social choice, several authors have been interested in obtaining information about winners with reduced assumptions about the knowledge of the agent preferences (assuming that the voting rule is known).
-one early work is  by \Citet{Conitzer2005} who studied the complexity of communication when using different voting rules. %determining lower and upper bounds;
+one early work is  by \Citet{Conitzer2005} who studied the complexity of communication when using different voting rules; %determining lower and upper bounds;
 %they showed that, 
@@
 
-Since in many practical situations there would be too many possible winners but no necessary winners,  
-several works addressed the problem of  elicitation of agent preferences \citep{Naamani-Dery2015,Kalech2011,Lu2011,Pini2009,Benabbou2016,Dey2016,Dey2016_2}  using a variety of approaches (minimax regret, Bayesian methods, etc.) with the goal of converging to a necessary winner; \citep{Walsh2009,Conitzer2009}  analyzed when to stop the elicitation process.
+Since in many practical situations there would be too many possible winners but no necessary winners, several works addressed the problem of agent preferences elicitation using a variety of approaches (minimax regret, Bayesian methods, etc.) with the goal of converging to a necessary winner \citep{Naamani-Dery2015,Kalech2011,Lu2011,Pini2009,Benabbou2016,Dey2016,Dey2016_2}.
+Among those, \citep{Walsh2009,Conitzer2009} analyzed when to stop the elicitation process.
 
-Furthermore, it is often difficult for non-experts to formalize a voting rule on the basis of some generic preferences over a desired aggregation method.
-Thus, the first hypothesis should also be relaxed.
+A second concern is the ability of the chair (the person or organization supervising the voting process) to provide a precise definition of the voting rule, suggesting the relaxation of the second hypothesis.
+Indeed, it is often difficult for non-experts to formalize a voting rule on the basis of some generic preferences over a desired aggregation method.
+%Thus, the first hypothesis should also be relaxed. 
 %While most of the focus in the research community has been in dealing with incomplete agent preferences, 
-Consider, as an example, a committee that is about to hire a new employee, whose performances are evaluated by several experts.
-The members of the committee may not have a voting rule in mind at the start of the process, and might not wish to agree on a specific voting rule, but they might be willing to answer a few questions requiring to select who should be the winner out of specific profiles.
+Consider, as an example, a chair that is about to hire a new employee, whose performances are evaluated by several experts.
+The members of the chair may not have a voting rule in mind at the start of the process, and might not wish to agree on a specific voting rule.
+However, they might be willing to answer a few questions requiring to select who should be the winner out of specific profiles.
 %The information provided can be used to   % to determine their employee of choice.
@@
 %This paper considers both sources of uncertainty at the same time, and proposes a method able to recommend a consensus choice without requiring full knowledge of either.
-In this paper we focus on positional scoring rules, that are a particularly common method used to aggregate rankings. 
+In this paper, we focus on positional scoring rules, that are a particularly common method used to aggregate rankings. 
 We develop methods, based on the notion of minimax regret, for determining a robust ``winner'' under uncertainty of both the voting rule and the agent preferences.
@@
 We provide incremental elicitation methods that 
-at each step of the elicitation ask a question either to one of the agents or to the chair (the person or organization supervising the voting process) and discuss several heuristics that determine queries that quickly reduce regret.
+at each step of the elicitation ask a question either to one of the agents or to the chair, and discuss several heuristics that determine queries that quickly reduce regret. 
 Answers to questions are encoded in terms of constraints; questions to the agents are comparisons between pairs of alternatives while
@@
 %While previous works have considered either partial information about the agent preferences or a partially specified aggregation method, we do not know of any work considering both sources of uncertainty at the same time.
-Actually, very few works altogether have considered the problem of eliciting a voting rule by asking questions to the chair;  we are aware of the work of \Citet{Cailloux2014}, that assumes a different representation for the rule.
+Actually, very few works altogether have considered the problem of eliciting a voting rule by asking questions to the chair.
+We mention the work of \Citet{Cailloux2014} that assumes a different representation for the rule.
 %we mention the work of \Citet{Cailloux2014} considering elicitation the voting rule by assuming a specific representation.
@@
 
-We also mention works addressing the manipulability of voting rules \citep{Elkind2012,Dey2018,Dey2018_2,Conitzer2011,Baumeister2019} and 
+Additionally, some works address the manipulability of voting rules \citep{Elkind2012,Dey2018,Dey2018_2,Conitzer2011,Baumeister2019} and 
 strategic behaviors \citep{Endriss2016,Lev2019,Annemieke2012}.
 
-Our approach is evaluated in simulations where both the voting rule and the agent's preferences are initially unknown to the system and incrementally revealed by answering questions.
-We compare the effectiveness of several question strategies based on the current knowledge about the rule and preferences.
-To summarize:
+Our approach is evaluated on small scale simulations where both the voting rule and the agent preferences are initially unknown to the system and incrementally revealed through questioning.
+We compare the effectiveness of several questioning strategies based on the current knowledge of the rule and preferences. To summarize our contributions:
 \begin{itemize}
 	\item we provide a novel mechanism for eliciting a voting rule by translating abstract questions about weights to a choice of an alternative given a concrete profile;  
-	\item we show that in small problem sizes, %starting with zero knowledge,
+	\item we show that %in small problem sizes, %starting with zero knowledge,
 	 it is possible to reach a low regret level with a reasonable number of questions;
-	\item we present elicitation strategies that achieve good results within reasonable computation time for small problem sizes;
+	\item we present elicitation strategies that achieve good results within reasonable computation time; %for small problem sizes;
 	\item we show that for the class of rule considered, asking a few questions about the voting rule suffice to reach a low regret level;
@@
 	Suppose we want to ask the following question to the chair: $w_{2} - w_{3} ≥ 2 (w_{3} - w_{4})$. 
-	We then show the following profile to the chair and ask who should win (each column is a preference of a voter).
+	We then show the following profile to the chair and ask who should win (each column is a preference of an agent).
 	\begin{center}
@@
 \begin{itemize}
-	\item \textit{Skate} - the top-2 alternatives are the same for all voters, and 8 out of 9 voters rank the same alternative at position 3;
-	\item \textit{AGH} - all voters rank the same alternative at the top position, different group of voters share the same preference rankings;
+	\item \textit{Skate} - the top-2 alternatives are the same for all agents, and 8 out of 9 agents rank the same alternative at position 3;
+	\item \textit{AGH} - all agents rank the same alternative at the top position, different group of agents share the same preference rankings;
 	\item \textit{T Shirt} - the alternatives are evenly distributed in the preference rankings.
@@
 \label{sec:conclusions}
-In this paper we have considered a social choice setting with partial information about the agent's preferences and a partially specified voting rule.
+In this paper we have considered a social choice setting with partial information about the agent preferences and a partially specified voting rule.
 In this setting, we have proposed the use of minimax regret both as a means of robust winner determination as well as a guide to the process of simultaneous elicitation of preferences and voting rule.
@@
 \bibliographystyle{named}
-{\small \bibliography{biblio}}
+%{\small \bibliography{biblio}}
+{\fontsize{9.7}{10.7}\selectfont \bibliography{biblio}}
 
@@
 
-	Define $P$ as the profile of $3 (p + q)$ voters containing $q$ times $>_1$, $p$ times $>_2$, and $>_3$ and $>_4$ each $p + q$ times.
+	Define $P$ as the profile of $3 (p + q)$ agents containing $q$ times $>_1$, $p$ times $>_2$, and $>_3$ and $>_4$ each $p + q$ times.
 	As a result, $a$ obtains the following ranks: $q$ times $r$, $p$ times $r + 2$, $p + q$ times first, and $p + q$ times second.

### 2021-01-19 minimax.tex
candidate questions

@@
 Let $(x^{*},\bar{y}, \bar{\profile}, \bar{\w})$ be the current solution of the minimax regret, where $x^{*}$ is the minimax optimal alternative and $\bar{y}, \bar{\profile}, \bar{\w}$ the corresponding adversarial choices.
-The \strat{Pessimistic} strategy considers a set of $n + m$ candidate questions: one per agent, and one per rank \commentOC{Isn’t this $m-2$?}.
+The \strat{Pessimistic} strategy considers a set of $n + (m-2)$ candidate questions: one per agent, and one per rank (excluding the first and the last one which are known).
 The candidate questions to the agents are chosen by extending the idea of \citet{Lu2011}, that priviledge learning about the relationship of $x^*$ and $\bar{y}$ to the other alternatives if possible.
 The candidate questions to the chair are determined as in the Random strategy.
-The Pessimistic strategy selects among these $n + m$ candidate questions one that leads to minimal regret in the worst case: for each question we compute the minimax regret for the two possible answers, considering a penalty terms depending on the kind of question, and choose the best according to (quasi-)$\leximax$.
+The Pessimistic strategy selects among these $n + m - 2$ candidate questions one that leads to minimal regret in the worst case: for each question we compute the minimax regret for the two possible answers, considering a penalty terms depending on the kind of question, and choose the best according to (quasi-)$\leximax$.
 \Cref{sec:appendix} provides more details.

### 2021-01-20 minimax.tex
full pass: several edits, reintroducing pessimistic

@@
 Our approach is evaluated on small scale simulations where both the voting rule and the agent preferences are initially unknown to the system and incrementally revealed through questioning.
-We compare the effectiveness of several questioning strategies based on the current knowledge of the rule and preferences. To summarize our contributions:
-\begin{itemize}
-	\item we provide a novel mechanism for eliciting a voting rule by translating abstract questions about weights to a choice of an alternative given a concrete profile;  
-	\item we show that %in small problem sizes, %starting with zero knowledge,
-	 it is possible to reach a low regret level with a reasonable number of questions;
-	\item we present elicitation strategies that achieve good results within reasonable computation time; %for small problem sizes;
-	\item we show that for the class of rule considered, asking a few questions about the voting rule suffice to reach a low regret level;
-	\item our experiments suggest that low degree of similarity among preferences %rankings 
-	(as in impartial culture) is a more challenging setting than less varied profiles.
-\end{itemize}
-
+We compare the effectiveness of several questioning strategies based on the current knowledge of the rule and preferences. 
 \section{Social choice with partial information}
@@
 A profile is equivalently represented by $\profile=(v_j, j \in N)$ where $v_j(x) \in \set{1, \ldots, m}$ denotes the rank of alternative $x$ in the preference order $\pref_j$. 
-A social choice function $f : \cup_{\emptyset ≠ N \subset \N} \linors^N \rightarrow \powersetz{A}$ associates to each profile a set of (tied) winners, where $\powersetz{A}$ represents the set of subsets of $A$ except for the empty set.
+A social choice function $f : \cup_{\emptyset ≠ N \subset \N} \linors^N \rightarrow \powersetz{A}$ associates to each profile a set of (tied) winners, where $\powersetz{A}$ is the powerset of $A$ excluding the empty set.
 Among the many possible social choice functions, we consider convex {\em positional scoring rules (PSRs)}.
@@
 \end{equation}
-The constraint above is a natural and common assumption, often used when aggregating rankings in sport competitions: losing ranks at the top of the ranking is more damaging than losing ranks at the bottom.
+The constraint above is a natural and common assumption, often used when aggregating rankings in sport competitions (such as F1 racing, alpine skiing world cup); losing ranks at the top  is more damaging than losing ranks at the bottom.
 Let $\W$ denote the set of such convex weight vectors.
@@
 In particular, \citet{Lu2011} have adopted minimax regret for winner determination in social choice where
-the preferences of agents that are partially known, while the social choice function is known.
+the preferences of agents are partially known, while the social choice function is known.
 
@@
 
-The maximum regret is considered by assuming that an adversary can both 1) extend the partial profile $\pprofile$ into a complete profile, and 2) instantiate the weights choosing among any weight vector in $\pw$, where $\pprofile$ and $\pw$ represent our knowledge so far.
+Given $\pprofile$ and $\pw$ (that represent the current knowledge about agent preferences and the PSR),
+the maximum regret is considered by assuming that an adversary can both 1) extend the partial profile $\pprofile$ into a complete profile, and 2) instantiate the weights choosing among any weight vector in $\pw$.
+%where $\pprofile$ and $\pw$ represent our knowledge so far.
 We formalize the notion of minimax regret in multiple steps.
@@
 Given a voting rule and a partially specified profile, \citet{Xia2008} determine necessary winners by showing constructions that attempt to maximize the score difference between a proposed winner and a chosen alternative.
-This reasoning was later adopted by \citet{Lu2011} who used the considerations on the worse-case completions for computing the minimax regret.
+This reasoning was later adopted by \citet{Lu2011} who used the considerations on the worst-case completions for computing the minimax regret.
 
@@
 \end{proposition}
-
-\begin{proposition}
+Note that in \cref{claim:rankPMR}, in the case $(x \pprefeq_j y)$, $\beta$ is the number of alternatives incomparable with both $x$ and $y$.
+\begin{proposition}\label{claim:PMR}
 	The $\PMR$ can be written as:
@@
 	\end{align}
-	where $\hat{\alpha}_{r}^{y}$ (resp.
-$\hat{\alpha}_{r}^{x}$)  is the number of times $y$ (resp.
-$x$) has rank $r$ in the complete profile $\hat{\profile}$ defined in \cref{claim:rankPMR}.
-%\ref{claim:completion}.
+	where $\hat{\alpha}_{r}^{y}$ (resp. $\hat{\alpha}_{r}^{x}$)  is the number of times $y$ (resp. $x$) has rank $r$ in the complete profile $\hat{\profile}$ defined in \cref{claim:rankPMR}. 
 \end{proposition}
-
-(\cref{claim:rankPMR} can be understood by observing that in the case $(x \pprefeq_j y)$, $\beta$ is the number of alternatives incomparable with both $x$ and $y$.)
-The last proposition shows that PMR is linear in the weights.
+%\cref{claim:rankPMR} can be understood by observing that in the case $(x \pprefeq_j y)$, $\beta$ is the number of alternatives incomparable with both $x$ and $y$.
+\cref{claim:PMR}  shows that PMR is linear in the weights.
 %Recall that $\pw$ represents the weight vectors compatible with the preferences of the chair stated so far.
@@
 %(we leave $w_{1}$ and $w_{m}$ in the LP just for clarity of presentation).
-
 The max regret $\MaxR(x; \pprofile, W)$ is determined by considering the pairwise regret of $x$ with all other alternatives in $A$, and the recommended alternatives are the ones with least max regret.
@@
 We develop several strategies for simultaneous elicitation of agent preferences and of the PSR.
-While it is of course possible to first fully elicit the agent preferences and afterwards elicit weights, we want to investigate experimentally approaches that are able to recommend winning alternatives before obtaining complete knowledge of the profile or the rule.
+While it is of course possible to first fully elicit the agent preferences and afterwards elicit weights, we want to investigate approaches that are able to recommend winning alternatives before obtaining complete knowledge of the profile or the rule.
 %Indeed, it can be beneficial to split efforts asking questions to the chair and to agents, depending on which is estimated to be more informative.
@@
 The candidate questions to the chair are determined as in the Random strategy.
-The Pessimistic strategy selects among these $n + m - 2$ candidate questions one that leads to minimal regret in the worst case: for each question we compute the minimax regret for the two possible answers, considering a penalty terms depending on the kind of question, and choose the best according to (quasi-)$\leximax$.
-\Cref{sec:appendix} provides more details.
+The strategy selects among these $n + m - 2$ candidate questions one that leads to minimal regret in the worst case: for each question we compute the minimax regret for the two possible answers, considering a penalty terms depending on the kind of question, and choose the best according to (quasi-)$\leximax$.
+%\Cref{sec:appendix} provides more details.
+
+	Given $j \in N^*$, if $x^*$ and $\bar{y}$ are incomparable in $\ppref_j$, the candidate question concerns the pair $(x^*, \bar{y})$, otherwise, %the candidate question
+	it concerns the pair $(x^*, z)$ for some $z$ incomparable to $x^*$ (randomly chosen), or if none such $z$ exist, the pair $(\bar{y}, z)$ for some $z$ incomparable to $\bar{y}$, or, if both $x^*$ and $\bar{y}$ are comparable to every alternatives in $\ppref_j$, any incomparable pair is picked at random.
+%Responses to questions involving $x^*$ or $\bar{y}$ constrain the ability of the adversary to complete the profile in such manner, possibly reducing minimax regret.
+	Once having selected $n + m - 2$ candidate questions, the Pessimistic strategy selects the one that leads to minimal regret in the worst case.
+	%, considering both possible answers to the question, and with penalty terms depending on the kind of question. To define this comparison precisely, 
+	Assume that a question $q_1$ has type $t_1$ (being “chair” or “agent”), and leads to the new knowledge states $(\pprofile_1, W_1)$ if answered positively and $(\pprofile'_1, W'_1)$ if the answer is negative.
+	Define $R^{\max}_1 = \max\set{\MMR(\pprofile_1, W_1), \MMR(\pprofile'_1, W'_1)}$
+	and $R^{\min}_1 = \min\set{\MMR(\pprofile_1, W_1), \MMR(\pprofile'_1, W'_1)} \epsilon_{t} + \epsilon'_{t}$.
+	%If $(\pprofile_1, W_1) ≥ (\pprofile'_1, W'_1)$, define $\MMR^{\max} = \MMR(\pprofile_1, W_1)$ and $\MMR^{\min} = \MMR(\pprofile'_1, W'_1)$; otherwise, define $\MMR^{\max} = \MMR(\pprofile'_1, W'_1)$ and $\MMR^{\min} = \MMR(\pprofile_1, W_1)$.
+	% and and $(\pprofile^\min_2, W^\min_2)$. numbering them so that $\MMR(\pprofile_1, W_1) ≥ \MMR(\pprofile_2, W_2)$. Then the badness of the question in the worst case is:
+	The terms $\epsilon_t$ and $\epsilon'_{t}$ are real numbers associated to the type $t$ of question; these parameters are determined experimentally and used to fine control the choice of the question type.
+	Define similarly $t_2$, $R^{\max}_2$ and $R^{\min}_2$ for  $q_2$.
+	%We are now faced with the problem of aggregating these values in order to compare the informative values of the candidate questions.
+\footnote{We adopt a pessimistic approach, reported to perform better than optimistic aggregation \citep{Cailloux2014}, although Our experiments in this context suggested a weak impact of that choice on the performance of the strategy.}
+	%To avoid the absorption property of the max, we adopt $\leximax$ as an aggregator.
+	Pessimistic considers question $q_1$ to be better  than $q_2$ iff $R^{\max}_1 < R^{\max}_2 \text{ or } [R^{\max}_1 = R^{\max}_2 \text{ and } R^{\min}_1 < R^{\min}_2]$.
+	%This comparison gives a way of picking questions among a set of possible questions, by picking one that minimizes this approximate measure of minimax regret {\em a posteriori}. 
+	%The motivation for using this operator lies in 
+	In other words if the maximal {\em a posteriori} MMR of two questions are (nearly) equal, then it considers the (penalized) minimal MMR values, preferring the question with the lowest value.\footnote{In our simulations the parameters for the Pessimistic and Extended pessimistic are set to $\epsilon_{\text{chair}} = 1.1$, $\epsilon'_{\text{chair}} = 10^{-6}$, $\epsilon_{\text{agent}} = 1.0$ and $\epsilon'_{\text{agent}} = 0$.}
+	%(Technically, instead of applying a pure lexicographic aggregation, which is very sensitive to small errors due to floating-point computations, we apply a weighted sum between the maximal and the penalized minimal MMR values, with a predominant weight given to the maximal one, several order of magnitudes higher than the weight given to the penalized minimal MMR.)
 
@@
 These candidate questions are then evaluated using the same operator as for the Pessimistic strategy.
-We use this strategy to test whether Pessimistic performs well: depending on the quality of the heuristic of the Pessimistic strategy, it might perform nearly equally well, or perhaps even better, than Extended pessimistic, while being (much) faster.
+%We use this strategy to test whether Pessimistic performs well: depending on the quality of the heuristic of the Pessimistic strategy, it might perform nearly equally well, or perhaps even better, than Extended pessimistic, while being (much) faster.
 Extended pessimistic is applicable only to small problem instances: its complexity is in $O(n^2 m^5)$, because we consider $O(m^2)$ questions for each agent and need for each question to compute MMR twice, whose complexity is $O(nm^3)$.
 
-The \strat{Two phases} strategy is developed in order to investigate the effect of varying the proportion of questions asked to agents and to the chair, and compare the performance of asking questions to the chair first or to the agents first.
-It is parameterized by $q_c$, a value indicating the number of questions that must be asked to the chair.
+The \strat{Two phases} strategy is developed in order to investigate the effect of varying the proportion of questions of the two types, %asked to agents and to the chair, %and to compare the performance
+when asking all questions to the chair at the beginning or at the end.
+%first or to the agents first. 
+It is parameterized by $q_c$,  the number of questions to be asked to the chair.
 The \strat{Two phases-ca} variant first asks $q_c$ questions to the chair, then $k - q_c$ questions to the agents, using in both cases Pessimistic to select the specific questions; whereas the \strat{Two phases-ac} variant starts with $k - q_c$ questions to the agents, then questions the chair.
@@
 
-Finally, the \strat{Elitist} strategy aims at uncovering as quickly as possible the top alternative of each agent. It asks $m - 1$ questions to each agent in turn. 
-Given an agent to query $j$, it asks about an alternative currently undominated in $\ppref_j$ and any alternative that is currently incomparable to this alternative.
-Thus, the top alternative in the ranking of $j$ will be known after having asked exactly $m-1$ questions to $j$.
-After having asked $n (m-1)$ questions to the agents, it questions the chair only, using the same approach as the Pessimistic strategy.
+Finally, the \strat{Elitist} strategy aims at uncovering as quickly as possible the top alternatives of all agents. 
+%It asks $m - 1$ questions to each agent in turn. 
+For any agent $j$, it asks to compare an alternative currently undominated in $\ppref_j$ with one that is currently incomparable.
+Thus, the top alternative for $j$ will be known after having asked exactly $m-1$ questions to $j$.
+After having asked $n (m-1)$ questions to the agents, it questions the chair only, using the same approach as Pessimistic.
 This strategy can be expected to perform well when the chair assigns a large weight to the first rank, as compared to the other ranks.
-It will be useful to further challenge the Pessimistic strategy, which is not specifically tailored to such a situation.
+It is used to further challenge Pessimistic, which is not specifically tailored to such a situation.
 
@@
 The oracle is built as follows. 
-For the real preferences, we used the following data sets from \href{https://www.preflib.org/}{PrefLib} \citep{PrefLib}.
-\textit{T Shirt}: $m = 11$ tee shirt designs voted by $n = 30$ members of the Optimization Research Group at NICTA; \textit{AGH Course Selection}: $m = 9$ courses evaluated by $n = 146$ students of the AGH University; and \emph{Skate}: $m = 14$ skaters evaluated by $n = 9$ judges at the Euros Pairs Short Program.
+For the real preferences, we used three datasets from \href{https://www.preflib.org/}{PrefLib} \citep{PrefLib}:\textit{T-Shirt} (researchers voted on tee shirt designs; $m \!=\! 11, n \!=\! 30$),
+\textit{Courses}  (students voted on courses; $m \!=\! 9, n \!=\! 146$)
+and \emph{Skate} (judges vote on skaters at the Euros Pairs Short Program; $m \!=\! 14, n \!=\! 9$).
+% tee shirt designs voted by 
+%$n \!=\! 30$ 
+%members of the Optimization Research Group at NICTA;
+% \textit{AGH Course Selection}: $m \!=\! 9$ courses evaluated by $n = 146$ students 
+%of the AGH University; 
+%and \emph{Skate}: $m \!=\! 14$ skaters evaluated by $n \!=\! 9$ judges at the Euros Pairs Short Program.
 %We want to focus on the most critical setting, as there is a wide variety of possible situations to test in such experiments.
-For the generated preferences, we follow an Impartial Culture (IC) assumption: the linear order of each agent is drawn independently and all have the same probability of appearing.
-We adopt IC because it is a more challenging situation: as can be expected intuitively (and shown in \cref{fig:linearity}), the number of questions to be asked decrease with less varied profiles.
-To generate the weights of the scoring rule, we first draw $m - 1$ numbers uniformly at random (in the interval $\intvl{0,1}$ representing weight ``differences''), normalize and sort them; a sequence of convex decreasing weight is then obtained by a decumulative sum.
+For the synthetic datasets, we follow an Impartial Culture (IC) assumption: the linear order of each agent is drawn i.i.d. uniformly.
+%independently and all have the same probability of appearing. 
+We believe IC to be a challenging situation and expect the number of questions to ask, in order to reach a certain level of regret, to decrease with less varied profiles.
+%We adopt IC because it is a more challenging situation: as can be expected intuitively , the number of questions to be asked decrease with less varied profiles. 
+To generate the weights of the scoring rule, we first draw $m \!-\!
+1$ numbers uniformly at random (in the interval $\intvl{0,1}$ representing weight ``differences''), normalize and sort them; a sequence of convex decreasing weight is then obtained by a decumulative sum.
 
@@
 \begin{table}
-	\caption{Average MMR in problems of size $(10, 20)$ and geometric weights after $k$ questions.}
+	\caption{Average MMR in problems of size $(10, 20)$ after $k$ questions assuming geometric weights.}
 	\label{tab:geometricWeights}
@@
 Our next set of experiments evaluate the Pessimistic strategy in absolute terms. 
-We first wonder how many questions should be asked in order to reach a low regret level.
-We consider a low level to be a tenth of the number of agents: such a regret is equivalent to the difference of score of an alternative $x$ that results from switching from a profile $P$ to a profile $P'$ where ten percent of the agents rank $x$ last instead of first.
+We first wonder how many questions should be asked in order to reach low regret. 
+For the scope of the experiment we consider a ``low level'' to be a tenth of the number of agents: such a regret is equivalent to the difference of score of an alternative $x$ that results from switching from a profile $P$ to a profile $P'$ where ten percent of the agents rank $x$ last instead of first.
 The results for various sizes are displayed in \cref{tab:lowRegret}.
@@
 \commentBN{Replace the following paragraph with real stats on the distribution of questions.}
-For the experiments we performed, we see that the number of questions required to reach a low regret level grows approximately linearly with the number of agents and grows less fast than the square of the number of alternatives.
+%For the experiments we performed, we see that the number of questions required to reach a low regret level grows approximately linearly with the number of agents and grows less fast than the square of the number of alternatives.
 Averaging these data by category of value for $m$, and assuming no questions get asked to the chair, we see that in order to reach a low regret level, each agent will have to answer $5.6$ questions for $m = 5$, $17.2$ questions for $m = 10$ and $27.1$ questions for $m = 15$.
@@
 
-In \cref{fig:linearity} we can also observe, as expected, that given a problem size the number of questions needed to reach a given MMR is lower when considering a real data set than a IC generated profile.
+In \cref{fig:linearity} we can also observe, as expected, that given a problem size the number of questions needed to reach a given MMR is lower when considering real datasets rather than a synthetic profile generated according to IC.
 \commentBN{Add the following:}
-By looking at the data we observe that:
-\begin{itemize}
-	\item \textit{Skate} - the top-2 alternatives are the same for all agents, and 8 out of 9 agents rank the same alternative at position 3;
-	\item \textit{AGH} - all agents rank the same alternative at the top position, different group of agents share the same preference rankings;
-	\item \textit{T Shirt} - the alternatives are evenly distributed in the preference rankings.
-\end{itemize}
-The experiments suggest that high degree of similarity in the preference rankings helps reducing the regret faster.
+Indeed, in the Skate dataset the top-2 alternatives are the same for all agents, and 8 out of 9 agents rank the same alternative at position 3; in Courses  all agents rank the same alternative at the top position,
+while in \textit{T-Shirt}  the alternatives are evenly distributed in the preference rankings.
+%By looking at the data we observe that:
+%\begin{itemize}
+%	\item \textit{Skate} - the top-2 alternatives are the same for all agents, and 8 out of 9 agents rank the same alternative at position 3;
+%	\item \textit{AGH} - all agents rank the same alternative at the top position, different group of agents share the same preference rankings;
+%	\item \textit{T Shirt} - the alternatives are evenly distributed in the preference rankings.
+%\end{itemize}
+%The experiments suggest that high degree of similarity in the preference rankings helps reducing the regret faster.
 % do less harm than halving the gain in regret, on average.
@@
 \end{table}
-
 The experiments so far let the strategy target its questions unrestrictively, leaving open the possibility of questioning either the chair or an agent at each step.
 One may wonder what is lost in terms of regret by asking different proportions of questions to the chair and the agents.
-Such restrictions may be useful because of (partial) unavailability of the chair, or because the estimated cognitive costs may differ sensibly, as these types of questions differ in nature.
+Such restrictions may be useful because of (partial) unavailability of the chair, or because the estimated cognitive costs may differ sensibly.
+%, as these types of questions differ in nature.
+
 \Cref{tab:twoP400} shows the MMR value reached in problems of size $m = 10, n = 20$ after $400$ questions, using the Two phases strategy, in the “ca” (chair then agents) and in the “ac” (agents then chair) variants.
-These numbers are to be compared with the MMR value reached after 400 questions with the Pessimistic strategy (displayed in \cref{fig:linearity}), which is $0.6$.
-The Pessimistic strategy asks on average $48$ questions to the chair in this setting.
+These numbers are to be compared with the MMR value reached after 400 questions with the Pessimistic strategy (displayed in \cref{fig:linearity}), which is $0.6$; the Pessimistic strategy asks on average $48$ questions to the chair in this setting.
+These numbers highlight that it is possible to obtain a good-quality recommendation while knowing only that the voting rule is a scoring rule and that the weights are convex, which is our basic hypothesis (corresponding to the line $q_c = 0$, where no question is asked to the chair).
 
-These numbers highlight that it is possible to obtain a good-quality recommendation while knowing only that the voting rule is a scoring rule and that the weights are convex, which is our basic hypothesis (corresponding to the line $q_c = 0$, where no question is asked to the chair).
+We summarize the main observation  from the experiments:
+\begin{itemize}
+%	\item we provide a novel mechanism for eliciting a voting rule by translating abstract questions about weights to a choice of an alternative given a concrete profile;  
+	\item we showed that with our elicitation method %in small problem sizes, %starting with zero knowledge,
+	 it is possible to reach low regret with a reasonable number of questions;
+	\item the elicitation strategies that we provide, in particular Pessimistic, achieve good results within reasonable computation time; %for small problem sizes;
+	\item we showed that for the class of rule considered, asking a few questions to the chair suffice to reach  low regret;
+	\item our experiments suggest that low degree of similarity among preferences %rankings 
+	(as in impartial culture) is a more challenging setting than less varied profiles.
+\end{itemize}
 
@@
 Second, elicitation could be extended to voting rules beyond scoring rules. 
-Finally, an important direction of extension aims at studying how to elicit preferences while restraining to concrete and easy questions.
+Finally, an important direction of research  aims at eliciting preferences while restraining to concrete and easy questions.
 % Acknowledgments: We thank the reviewers for comments helping to improve the paper.

### 2021-01-20 minimax.tex
new m14n9 data (and correction on T shirt dataset name)

@@
 The oracle is built as follows. 
-For the real preferences, we used three datasets from \href{https://www.preflib.org/}{PrefLib} \citep{PrefLib}:\textit{T-Shirt} (researchers voted on tee shirt designs; $m \!=\! 11, n \!=\! 30$),
+For the real preferences, we used three datasets from \href{https://www.preflib.org/}{PrefLib} \citep{PrefLib}:\textit{T Shirt} (researchers voted on T-shirt designs; $m \!=\! 11, n \!=\! 30$),
 \textit{Courses}  (students voted on courses; $m \!=\! 9, n \!=\! 146$)
@@
 			\addlegendentry{courses m9n146}
-			\addplot[thick, mark=halfsquare left*, mark size = {2}, mark indices = {200}, blue] table [x=k, y=14.9]{data/normalizedLin.dat};
+			%\addplot[thick, mark=halfsquare left*, mark size = {2}, mark indices = {200}, blue] table [x=k, y=14.9]{data/normalizedLin.dat};
+			\addplot[thick, mark=halfsquare left*, mark size = {2}, mark indices = {200}, blue] table [x=k, y=14.9]{data/m14n9.dat};
 			\addlegendentry{m=14, n=9}
@@
 Indeed, in the Skate dataset the top-2 alternatives are the same for all agents, and 8 out of 9 agents rank the same alternative at position 3; in Courses  all agents rank the same alternative at the top position,
-while in \textit{T-Shirt}  the alternatives are evenly distributed in the preference rankings.
+while in \textit{T Shirt}  the alternatives are evenly distributed in the preference rankings.
 %By looking at the data we observe that:

### 2021-01-20 minimax.tex
Cmt and citet

@@
 \section{Introduction}
+\commentOC{Remaining refs to appendix. Describe what is there. data set VS dataset.}
 Aggregation of preference information is a central task in many computer systems (recommender systems, search engines, etc).
@@
 Since in many practical situations there would be too many possible winners but no necessary winners, several works addressed the problem of agent preferences elicitation using a variety of approaches (minimax regret, Bayesian methods, etc.) with the goal of converging to a necessary winner \citep{Naamani-Dery2015,Kalech2011,Lu2011,Pini2009,Benabbou2016,Dey2016,Dey2016_2}.
-Among those, \citep{Walsh2009,Conitzer2009} analyzed when to stop the elicitation process.
+Among those, \citet{Walsh2009,Conitzer2009} analyzed when to stop the elicitation process.
 

### 2021-01-20 minimax.tex
Some todos
More precise ref

@@
 \section{Introduction}
-\commentOC{Remaining refs to appendix. Describe what is there. data set VS dataset.}
+\commentOC{Remaining refs to appendix. Describe what is there. data set VS dataset. Figure 2. Footnotes. Comments. Talk about small settings?}
 Aggregation of preference information is a central task in many computer systems (recommender systems, search engines, etc).
@@
 Such questions have precise semantics whose understanding can be assumed to be shared by the chair, contrary to abstract questions about weights.
-Moreover, this way of questioning the chair is independent of the voting rule that is being elicited. Asking questions about weights only works when a scoring rule is being considered.
+Moreover, this way of questioning the chair is independent of the voting rule that is being elicited. Questions about weights only make sense when considering PSRs.
 Asking who should win in specific profiles has been used in experimental settings investigating the feeling of justice of individuals \citep{Giritligil2005}, but, to the best of our knowledge, the use of such questions to systematically guide an elicitation process about voting rules is novel.
 This is similar to favor, in decision theory, direct choice questions ("please choose either a or b") compared to questioning the decision maker about the shape of her utility function.
-The former are considered “observable”: acts of choice are translated to preference statements \citep{colell_microeconomic_1995}.
+The former are considered “observable”: acts of choice are translated to preference statements \citep[Ch.\ 1]{colell_microeconomic_1995}.
 
@@
 
-\begin{table}[ht]
+\begin{table}
 	\caption{Number of questions needed by Pessimistic strategy to reach an MMR of $\frac{n}{10}$ (represented by $k_{\MMR}$), by size.}

### 2021-01-20 minimax.tex
Let LaTeX do the positioning
some wording, typos, plus comments

--- 2021-01-20 minimax.tex
@@
 \newcommand{\commentBN}[1]{\textcolor{red}{\small$\big[$BN: #1$\big]$}}
+\newcommand{\commentPV}[1]{\textcolor{brown}{\small$\big[$PV: #1$\big]$}}
 
@@
 \section{Introduction}
-\commentOC{Remaining refs to appendix. Describe what is there. data set VS dataset.}
+\commentOC{Remaining refs to appendix. Describe what is there. data set VS dataset. Figure 2. Footnotes. Comments. Talk about small settings?}
+\commentPV{If we have space (can save by formatting the itemize at the end of experiments as text), show Regret and PMR formulas as displaymath}
 Aggregation of preference information is a central task in many computer systems (recommender systems, search engines, etc).
@@
 
-Our approach is evaluated on small scale simulations where both the voting rule and the agent preferences are initially unknown to the system and incrementally revealed through questioning.
+Our approach is evaluated on simulations with synthetic and real datasets where both the voting rule and the agent preferences are initially unknown to the system and incrementally revealed through questioning.
 We compare the effectiveness of several questioning strategies based on the current knowledge of the rule and preferences. 
@@
 
-The following propositions (with proofs in appendix) show that the procedure for completing a partial profile that was first proposed by \citet{Lu2011} when considering a fixed weight vector also applies in our setting.
-We write $a \pprefeq_j b$ iff $a \ppref_j b \lor a = b$ and adopt the canonical notation when considering a relation as a function, writing for example ${\pprefeq_j}(x)$ to designate $\set{y \suchthat x \pprefeq_j y}$.
+The following propositions (proofs in appendix) show that the procedure for completing a partial profile,  proposed by \citet{Lu2011} when considering a fixed weight vector, also applies in our setting.
+We write $a \pprefeq_j b$ iff $a \ppref_j b \lor a = b$ and adopt the canonical notation when considering a relation as a function, writing ${\pprefeq_j}(x)$ to designate $\set{y \suchthat x \pprefeq_j y}$.
 
@@
 	%The motivation for using this operator lies in 
-	In other words if the maximal {\em a posteriori} MMR of two questions are (nearly) equal, then it considers the (penalized) minimal MMR values, preferring the question with the lowest value.\footnote{In our simulations the parameters for the Pessimistic and Extended pessimistic are set to $\epsilon_{\text{chair}} = 1.1$, $\epsilon'_{\text{chair}} = 10^{-6}$, $\epsilon_{\text{agent}} = 1.0$ and $\epsilon'_{\text{agent}} = 0$.}
+	In other words if the maximal {\em a posteriori} MMR of two questions are (nearly) equal, then it considers the (penalized) minimal MMR values, preferring the question with the lowest value.\footnote{In our tests
+	%the parameters for Pessimistic and Extended pessimistic are 
+	we set to $\epsilon_{\text{chair}} = 1.1$, $\epsilon'_{\text{chair}} = 10^{-6}$, $\epsilon_{\text{agent}} = 1.0$ and $\epsilon'_{\text{agent}} = 0$.}
 	%(Technically, instead of applying a pure lexicographic aggregation, which is very sensitive to small errors due to floating-point computations, we apply a weighted sum between the maximal and the penalized minimal MMR values, with a predominant weight given to the maximal one, several order of magnitudes higher than the weight given to the penalized minimal MMR.)
@@
 \Cref{sec:appendix} provides a problem of larger size.
+\commentPV{Check problem size displayed in the labels of the two table. The one in the appendix does not seem larger.}
 
@@
 while in \textit{T Shirt}  the alternatives are evenly distributed in the preference rankings.
+\commentPV{If are evenly distributed, then doesn't this goes against our argument?}
 %By looking at the data we observe that:
@@
 
-We summarize the main observation  from the experiments:
+We summarize the main observations from the experiments:
+\commentPV{We could save space by 'de-itemizing' this, i.e. by formatting as text with i) bla bla bla.... ii) .... iiii) ....}
 \begin{itemize}

### 2021-01-20 minimax.tex

@@
 \sisetup{table-number-alignment = center, table-figures-integer=2, table-figures-decimal=1, table-auto-round}
-\begin{table}[ht]
+\begin{table}
 	\caption{Average MMR in problems of size $(10, 20)$ after $k$ questions.}

### 2021-01-20 minimax.tex
new xps

@@
 			\addlegendentry{m=15, n=30}
+
+			\addplot[thick, mark=halfsquare left*, mark size = {2}, mark indices = {200}, orange] table [x=k, y=14.10]{data/new.dat};
+			\addlegendentry{m=14, n=10}
+			\addplot[thick, mark=halfsquare right*, mark size = {2}, mark indices = {60}, black] table [x=k, y=15.10]{data/new.dat};
+			\addlegendentry{m=15, n=10}
+			\addplot[thick, mark=halfsquare*, mark size = {2}, mark indices = {400}, yellow] table [x=k, y=15.9]{data/new.dat};
+			\addlegendentry{m=15, n=9}
 		\end{axis}
@@
 \end{figure}
+
+%\begin{table}
+%	\caption{Average number of questions asked to the chair (\textit{qstC}) and to the agents (\textit{qstV}) by Pessimistic strategy to reach zero regret on the data sets of \cref{fig:linearity}.}
+%	\label{tab:questions}
+%	\begin{tabular}{S[table-text-alignment=right] S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=1]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=1]}
+%		\toprule
+%		{data set} & {qstC} & {sd} & {qstV} & {sd} \\
+%		\midrule
+%		m5n10 &		8.4		& 2.67 		& 61		& 6.25\\
+%		m5n20 &		13.6	& 6.38		& 118.9		& 14.4\\
+%		m10n20 &	48.5	 & 6		& 362.4		& 47.6	\\
+%		m10n30 &	56.3	&	11.18	&598.1 		&75.19	\\
+%		m15n30 &	24.5	&8.77		&	775.5	&	8.77	\\
+%		m14n9 &		58.3	&33.66		&370.9		&40.54	\\
+%		m14n9-2 &	56.2	&34.11		&368.7		&	53.07 \\
+%		skate &	0		& 0			&103.3		&2.21	\\
+%		tshirt &	30.0	&	15.87	&	961.2	&	23.04	\\
+%		courses & 0		& 0		&950		&5.08	\\
+%		
+%		\bottomrule
+%	\end{tabular}
+%\end{table}
 

### 2021-01-20 minimax.tex
take away back to intro

@@
 We compare the effectiveness of several questioning strategies based on the current knowledge of the rule and preferences.
+\commentBN{on small sizes because we assume humans}
+\commentBN{remove bullets and restore PMR}
+\begin{itemize}
+	\item we provide a novel mechanism for eliciting a voting rule by translating abstract questions about weights to a choice of an alternative given a concrete profile;  
+	\item we showed that with our elicitation method %in small problem sizes, %starting with zero knowledge,
+	it is possible to reach low regret with a reasonable number of questions;
+	\item the elicitation strategies that we provide, in particular Pessimistic, achieve good results within reasonable computation time; %for small problem sizes;
+	\item we showed that for the class of rule considered, asking a few questions to the chair suffice to reach low regret;
+	\item our experiments suggest that low degree of similarity among preferences %rankings 
+	(as in impartial culture) is a more challenging setting than less varied profiles.
+\end{itemize}
+
 \section{Social choice with partial information}
@@
 \Cref{sec:appendix} provides a problem of larger size.
-\commentPV{Check problem size displayed in the labels of the two table. The one in the appendix does not seem larger.}
 
@@
 
-We summarize the main observations from the experiments:
-\commentPV{We could save space by 'de-itemizing' this, i.e. by formatting as text with i) bla bla bla.... ii) .... iiii) ....}
-\begin{itemize}
-%	\item we provide a novel mechanism for eliciting a voting rule by translating abstract questions about weights to a choice of an alternative given a concrete profile;  
-	\item we showed that with our elicitation method %in small problem sizes, %starting with zero knowledge,
-	 it is possible to reach low regret with a reasonable number of questions;
-	\item the elicitation strategies that we provide, in particular Pessimistic, achieve good results within reasonable computation time; %for small problem sizes;
-	\item we showed that for the class of rule considered, asking a few questions to the chair suffice to reach  low regret;
-	\item our experiments suggest that low degree of similarity among preferences %rankings 
-	(as in impartial culture) is a more challenging setting than less varied profiles.
-\end{itemize}
-
 \section{Conclusions}  
@@
 \newtheorem*{details*}{Strategy Details}
-
+\commentBN{delete all this}
 \begin{details*}[Pessimistic]

### 2021-01-20 minimax.tex
take away, footnotes, data set, restored xps, removed table appendix, new table questions, real dataset consideration, maybe something else idk anymore

--- 2021-01-20 minimax.tex
@@
 \section{Introduction}
-\commentOC{Remaining refs to appendix. Describe what is there. data set VS dataset. Figure 2. Footnotes. Comments. Talk about small settings?}
+\commentOC{Remaining refs to appendix. Describe what is there.}
 \commentPV{If we have space (can save by formatting the itemize at the end of experiments as text), show Regret and PMR formulas as displaymath}
@@
 %we mention the work of \Citet{Cailloux2014} considering elicitation the voting rule by assuming a specific representation.
-
 %A classic paper is the one by \citet{Stein1994} that, considering scoring rules, identified dominance relations between alternatives; these relations allow to determine pairs of alternatives where the first is at least as good as the second no matter which weights are chosen among a generic class of weights (decreasing weighs or convex decreasing weights).
@@
 % provided an elicitation framework for a different class of rules.
-
 Additionally, some works address the manipulability of voting rules \citep{Elkind2012,Dey2018,Dey2018_2,Conitzer2011,Baumeister2019} and 
@@
 Our approach is evaluated on simulations with synthetic and real datasets where both the voting rule and the agent preferences are initially unknown to the system and incrementally revealed through questioning.
+We assume the chair to be human, thus able to answer questions about a limited number of alternatives, so we focus on small scale social choice situations.
 We compare the effectiveness of several questioning strategies based on the current knowledge of the rule and preferences.
+To summarize our contributions: 1) we provide a novel mechanism for eliciting a voting rule by translating abstract questions about weights to a choice of an alternative given a concrete profile; 2) we show that with our elicitation method it is possible to reach low regret with a reasonable number of questions; 3) we present elicitation strategies that achieve good results within reasonable computation time; 4) we show that for the class of rule considered, asking a few questions to the chair suffice to reach low regret; 5) our experiments suggest that low degree of similarity among preferences (as in impartial culture) is a more challenging setting than less varied profiles.
+%\begin{itemize}
+%	\item we provide a novel mechanism for eliciting a voting rule by translating abstract questions about weights to a choice of an alternative given a concrete profile;  
+%	\item we showed that with our elicitation method %in small problem sizes, %starting with zero knowledge,
+%	it is possible to reach low regret with a reasonable number of questions;
+%	\item the elicitation strategies that we provide, in particular Pessimistic, achieve good results within reasonable computation time; %for small problem sizes;
+%	\item we showed that for the class of rule considered, asking a few questions to the chair suffice to reach low regret;
+%	\item our experiments suggest that low degree of similarity among preferences %rankings 
+%	(as in impartial culture) is a more challenging setting than less varied profiles.
+%\end{itemize}
+
 \section{Social choice with partial information}
@@
 	%The motivation for using this operator lies in 
-	In other words if the maximal {\em a posteriori} MMR of two questions are (nearly) equal, then it considers the (penalized) minimal MMR values, preferring the question with the lowest value.\footnote{In our tests
-	%the parameters for Pessimistic and Extended pessimistic are 
-	we set to $\epsilon_{\text{chair}} = 1.1$, $\epsilon'_{\text{chair}} = 10^{-6}$, $\epsilon_{\text{agent}} = 1.0$ and $\epsilon'_{\text{agent}} = 0$.}
+	In other words if the maximal {\em a posteriori} MMR of two questions are (nearly) equal, then it considers the (penalized) minimal MMR values, preferring the question with the lowest value.
 	%(Technically, instead of applying a pure lexicographic aggregation, which is very sensitive to small errors due to floating-point computations, we apply a weighted sum between the maximal and the penalized minimal MMR values, with a predominant weight given to the maximal one, several order of magnitudes higher than the weight given to the penalized minimal MMR.)
@@
 1$ numbers uniformly at random (in the interval $\intvl{0,1}$ representing weight ``differences''), normalize and sort them; a sequence of convex decreasing weight is then obtained by a decumulative sum.
+The penalty parameters for the Pessimistic and Extended pessimistic strategies are set to  $\epsilon_{\text{chair}} = 1.1$, $\epsilon'_{\text{chair}} = 10^{-6}$, $\epsilon_{\text{agent}} = 1.0$ and $\epsilon'_{\text{agent}} = 0$.
 
@@
 We see that asking random questions does not allow to reach a low regret level even after having asked 100 questions, whereas a low regret level ($\MMR$ = 1) is reached by Pessimistic before having asked 60 questions.
+This holds also for different problem sizes.
+For instance, for $m =10$, $n = 20$ and $400$ questions, Random strategy reaches an average regret (over 10 runs) of $12$ (±$ 0.7$) and Pessimistic $0.6$ (±$ 0.5$).
 We also see that Pessimistic performs slightly better than Extended pessimistic, showing that Pessimistic chooses candidate questions wisely; this is good news since Pessimistic is much faster: it takes on average only $16$s for a complete elicitation session (for $m = 5$, $n = 10$ and $100$ questions), while Extended pessimistic takes $50$s.
 Although their performance is close, Pessimistic performs systematically better in multiple runs of the experiment.
-\Cref{sec:appendix} provides a problem of larger size.
-\commentPV{Check problem size displayed in the labels of the two table. The one in the appendix does not seem larger.}
 
@@
 The results for various sizes are displayed in \cref{tab:lowRegret}. 
+\commentBN{Either we remove this consideration about n/10 together with \cref{tab:lowRegret}, and we present \cref{tab:questions}.
+Or we redo \cref{tab:questions} considering the questions needed to reach MMR=n/10 instead of the ones needed to reach 0.}
 
-\commentBN{Replace the following paragraph with real stats on the distribution of questions.}
 %For the experiments we performed, we see that the number of questions required to reach a low regret level grows approximately linearly with the number of agents and grows less fast than the square of the number of alternatives.
-Averaging these data by category of value for $m$, and assuming no questions get asked to the chair, we see that in order to reach a low regret level, each agent will have to answer $5.6$ questions for $m = 5$, $17.2$ questions for $m = 10$ and $27.1$ questions for $m = 15$.
+%Averaging these data by category of value for $m$, and assuming no questions get asked to the chair, we see that in order to reach a low regret level, each agent will have to answer $5.6$ questions for $m = 5$, $17.2$ questions for $m = 10$ and $27.1$ questions for $m = 15$.
 These numbers have to be contrasted with the estimated number of questions required to elicit the full preference of an agent which are $6.6$ for $m=5$, $24.8$ for $m=10$ and $48.4$ for $m=15$.
@@
 \begin{figure}
-	\caption{Average MMR (normalized by $n$) after $k$ questions with Pessimistic strategy for different data sets.}
+	\caption{Average MMR (normalized by $n$) after $k$ questions with Pessimistic strategy for different datasets.}
 	\label{fig:linearity}
@@
 			\addlegendentry{courses m9n146}
-			%\addplot[thick, mark=halfsquare left*, mark size = {2}, mark indices = {200}, blue] table [x=k, y=14.9]{data/normalizedLin.dat};
-			\addplot[thick, mark=halfsquare left*, mark size = {2}, mark indices = {200}, blue] table [x=k, y=14.9]{data/m14n9.dat};
+			\addplot[thick, mark=halfsquare left*, mark size = {2}, mark indices = {200}, blue] table [x=k, y=14.9]{data/normalizedLin.dat};
 			\addlegendentry{m=14, n=9}
@@
 When approaching optimality, the pace of MMR reduction decreases.
-
-In \cref{fig:linearity} we can also observe, as expected, that given a problem size the number of questions needed to reach a given MMR is lower when considering real datasets rather than a synthetic profile generated according to IC.
-\commentBN{Add the following:}
-Indeed, in the Skate dataset the top-2 alternatives are the same for all agents, and 8 out of 9 agents rank the same alternative at position 3; in Courses  all agents rank the same alternative at the top position,
-while in \textit{T Shirt}  the alternatives are evenly distributed in the preference rankings.
-\commentPV{If are evenly distributed, then doesn't this goes against our argument?}
-%By looking at the data we observe that:
-%\begin{itemize}
-%	\item \textit{Skate} - the top-2 alternatives are the same for all agents, and 8 out of 9 agents rank the same alternative at position 3;
-%	\item \textit{AGH} - all agents rank the same alternative at the top position, different group of agents share the same preference rankings;
-%	\item \textit{T Shirt} - the alternatives are evenly distributed in the preference rankings.
-%\end{itemize}
-%The experiments suggest that high degree of similarity in the preference rankings helps reducing the regret faster.
-% do less harm than halving the gain in regret, on average.
+\Cref{fig:linearity} shows graphically the decrease in MMR according to the number of questions asked for various problem sizes.
+In particular, we can observe, as we expected, that given a problem size, the less the profile is varied the more questions are needed to reach a given MMR.
+For instance, in the \textit{Skate} dataset the top-2 alternatives are the same for all agents, and 8 out of 9 agents rank the same alternative at position 3; in \textit{Courses} all agents rank the same alternative at the top position, while in \textit{T Shirt} the alternatives are evenly distributed in the preference rankings.
+If we compare \textit{Skate} with the same size generated problem (m=14, n=9) we see that the former performs much better than the latter, reaching zero regret after only $100$ questions, while the IC needs almost $500$ questions to reach the same result.
+But if we compare \textit{T Shirt} with the corresponding IC, \commentBN{Do we substitute m=10, n=30 with m=11, n=30 to make it same as T shirt?} we do not observe any important differences in terms of decrease of regret.
+This suggest that high degree of similarity in the preference rankings helps reducing the regret faster.
 
@@
 \paragraph{Comparison with Two Phase}
+
 \begin{table}
@@
 \end{table}
+
 The experiments so far let the strategy target its questions unrestrictively, leaving open the possibility of questioning either the chair or an agent at each step.
@@
 In this setting, we have proposed the use of minimax regret both as a means of robust winner determination as well as a guide to the process of simultaneous elicitation of preferences and voting rule.
-Our experimental results %on randomly generated and real world data sets 
+Our experimental results %on randomly generated and real world datasets 
 suggest that regret-based elicitation is effective and allows to quickly reduce worst-case regret significantly.
@@
 
-As part of our contribution, a general open-source library, allowing to reproduce our experiments and perform many more, will be made publicly available.\footnote{URL not displayed for ensuring anonymity.}
+As part of our contribution, a general open-source library, allowing to reproduce our experiments and perform many more, will be made publicly available. (URL not displayed for ensuring anonymity.)
 %and serve as a basis for further research
@@
 \newtheorem*{details*}{Strategy Details}
-
-\begin{details*}[Pessimistic]
-	Given $j \in N^*$, if $x^*$ and $\bar{y}$ are incomparable in $\ppref_j$, the candidate question concerns the pair $(x^*, \bar{y})$, otherwise, the candidate question concerns the pair $(x^*, z)$ for some $z$ incomparable to $x^*$ (randomly chosen), or if none such $z$ exist, the pair $(\bar{y}, z)$ for some $z$ incomparable to $\bar{y}$, or, if both $x^*$ and $\bar{y}$ are comparable to every alternatives in $\ppref_j$, any incomparable pair is picked at random.
-%Responses to questions involving $x^*$ or $\bar{y}$ constrain the ability of the adversary to complete the profile in such manner, possibly reducing minimax regret.
-	Once having selected $n + m$ candidate questions, the Pessimistic strategy selects the one that leads to minimal regret in the worst case, considering both possible answers to the question, and with penalty terms depending on the kind of question.
-To define this comparison precisely, assume that a question $q_1$ has type $t_1$ (being “chair” or “agent”), and leads to the new knowledge states $(\pprofile_1, W_1)$ if answered positively and $(\pprofile'_1, W'_1)$ if the answer is negative.
-	Define $R^{\max}_1 = \max\set{\MMR(\pprofile_1, W_1), \MMR(\pprofile'_1, W'_1)}$
-	and $R^{\min}_1 = \min\set{\MMR(\pprofile_1, W_1), \MMR(\pprofile'_1, W'_1)} \epsilon_{t} + \epsilon'_{t}$.
-	%If $(\pprofile_1, W_1) ≥ (\pprofile'_1, W'_1)$, define $\MMR^{\max} = \MMR(\pprofile_1, W_1)$ and $\MMR^{\min} = \MMR(\pprofile'_1, W'_1)$; otherwise, define $\MMR^{\max} = \MMR(\pprofile'_1, W'_1)$ and $\MMR^{\min} = \MMR(\pprofile_1, W_1)$.
-	% and and $(\pprofile^\min_2, W^\min_2)$. numbering them so that $\MMR(\pprofile_1, W_1) ≥ \MMR(\pprofile_2, W_2)$. Then the badness of the question in the worst case is:
-	The terms $\epsilon_t$ and $\epsilon'_{t}$ are real numbers associated to the type $t$ of question; these parameters are to be determined experimentally and are used to fine control the choice of the question type.
-	Define similarly $t_2$, $R^{\max}_2$ and $R^{\min}_2$ for a question $q_2$.
-	We are now faced with the problem of aggregating these values in order to compare the informative values of the candidate questions.
-We adopt a pessimistic approach, reported to perform better than optimistic aggregation \citep{Cailloux2014}, although our experiments in this context suggested a weak impact of that choice on the performance of the strategy.
-	To avoid the absorption property of the max, we adopt $\leximax$ as an aggregator.
-	Pessimistic thus considers question $q_1$ to be better  than $q_2$ iff $R^{\max}_1 < R^{\max}_2 \text{ or } [R^{\max}_1 = R^{\max}_2 \text{ and } R^{\min}_1 < R^{\min}_2]$.
-	%This comparison gives a way of picking questions among a set of possible questions, by picking one that minimizes this approximate measure of minimax regret {\em a posteriori}. 
-	%The motivation for using this operator lies in 
-	In other words if the maximal {\em a posteriori} MMR of two questions are (nearly) equal, then it considers the (penalized) minimal MMR values, preferring the question with the lowest value.
-	(Technically, instead of applying a pure lexicographic aggregation, which is very sensitive to small errors due to floating-point computations, we apply a weighted sum between the maximal and the penalized minimal MMR values, with a predominant weight given to the maximal one, several order of magnitudes higher than the weight given to the penalized minimal MMR.)
-
-The penalty parameters for the Pessimistic and Extended pessimistic strategies are set to $\epsilon_{\text{chair}} = 1.1$, $\epsilon'_{\text{chair}} = 10^{-6}$, $\epsilon_{\text{agent}} = 1.0$ and $\epsilon'_{\text{agent}} = 0$.
-\end{details*}
 
@@
 
-\sisetup{table-number-alignment = center, table-figures-integer=2, table-figures-decimal=1, table-auto-round}
 \begin{table}
-	\caption{Average MMR in problems of size $(10, 20)$ after $k$ questions.}
-	\label{tab:biggerSize}
-	\begin{tabular}{S[table-figures-integer=3, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=1]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=1]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=1]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
+	\caption{Average number of questions asked to the chair (\textit{qstC}) and to the agents (\textit{qstV}) by Pessimistic strategy to reach zero regret on the datasets of \cref{fig:linearity}.}
+	\label{tab:questions}
+	\begin{tabular}{cS[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=2]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=2]}
 		\toprule
-		{k} & {Rnd.} & {sd} & {Pes.} & {sd} & {Eli.} & {sd} \\
+		{dataset} & {qstC} & {sd} & {qstV} & {sd} \\
 		\midrule
-		0 &20.0 & 0.0 & 20.0 & 0.0&  20.0 & 0.0 \\
-		50 & 19.82 & 0.04 &	15.59 &0.56	&17.38& 0.7\\
-		100 & 19.12	& 0.26&	11.91&	1.26 &15.23& 0.73\\
-		150 & 18.06	& 0.47&	8.92&	1.53 &13.38& 1.11\\
-		200 & 16.89	& 0.62&6.24&2.02&11.76& 1.03\\
-		250 & 15.63 & 0.84&	4.64&1.72&10.56& 0.89\\
-		300 & 14.72	& 0.94&	3.01& 1.35 &10.48& 0.87\\
-		350 & 13.41	& 1.15& 1.76& 0.95&10.48& 0.86\\
-		400 & 11.98	& 0.68&	0.62&0.56 &10.48& 0.86\\
+		m5n10 	&	8.4		& 2.67 		& 61		& 6.25\\
+		m5n20 	&	13.6	& 6.38		& 118.9		& 14.4\\
+		m10n20 	&	48.5	& 6			& 362.4		& 47.6	\\
+		m10n30 	&	56.3	& 11.18		& 598.1 	& 75.19	\\
+		m15n30 	&	24.5	& 8.77		& 775.5		& 8.77	\\
+		m14n9 	&	58.3	& 33.66		& 370.9		& 40.54	\\
+		m14n9-2 &	56.2	& 34.11		& 368.7		& 53.07 \\
+		skate 	&	0		& 0			& 103.3		& 2.21	\\
+		tshirt  &	30.0	& 5.87		& 961.2		& 23.04	\\
+		courses & 0			& 0			& 950		& 5.08	\\
+
 		\bottomrule
@@
 \end{table}
-\Cref{tab:biggerSize} shows that the conclusions of \cref{fig:smallSize} also hold for a problem of larger size ($m = 10, n = 20$), except that this table does not feature Extended pessimistic, which is too slow to be run repeatedly on such instance.
 

### 2021-01-20 minimax.tex
Providing some (hopefully) (near) final touch

@@
 \section{Introduction}
-\commentOC{Remaining refs to appendix. Describe what is there.}
-\commentPV{If we have space (can save by formatting the itemize at the end of experiments as text), show Regret and PMR formulas as displaymath}
 Aggregation of preference information is a central task in many computer systems (recommender systems, search engines, etc).
 In many situations, such as in group recommender systems, the goal is to find a consensus choice;
-social choice theory can provide foundations for such applications
+social choice theory can provide foundations for such applications.
 
@@
 Since in many practical situations there would be too many possible winners but no necessary winners, several works addressed the problem of agent preferences elicitation using a variety of approaches (minimax regret, Bayesian methods, etc.) with the goal of converging to a necessary winner \citep{Naamani-Dery2015,Kalech2011,Lu2011,Pini2009,Benabbou2016,Dey2016,Dey2016_2}.
-Among those, \citet{Walsh2009,Conitzer2009} analyzed when to stop the elicitation process.
+Among those, \citet{Walsh2009} and \citet{Conitzer2009} analyzed when to stop the elicitation process.
 
@@
 %This paper considers both sources of uncertainty at the same time, and proposes a method able to recommend a consensus choice without requiring full knowledge of either.
-In this paper, we focus on positional scoring rules, that are a particularly common method used to aggregate rankings. 
+In this paper, we focus on positional scoring rules with convex weights, that are a particularly common method used to aggregate rankings. 
 We develop methods, based on the notion of minimax regret, for determining a robust ``winner'' under uncertainty of both the voting rule and the agent preferences.
@@
 We provide incremental elicitation methods that 
-at each step of the elicitation ask a question either to one of the agents or to the chair, and discuss several heuristics that determine queries that quickly reduce regret. 
-Answers to questions are encoded in terms of constraints; questions to the agents are comparisons between pairs of alternatives while
-questions to the chair ask  to select who should be the winner in a synthetic profile.
+at each step of the elicitation question either one of the agents or the chair, and we discuss several heuristics to choose questions that quickly reduce the regret. 
+Answers to questions are encoded as constraints; questions to the agents are comparisons between pairs of alternatives while
+questions to the chair ask to select a winner out of a synthetic profile.
 
@@
 
-The following propositions (proofs in appendix) show that the procedure for completing a partial profile,  proposed by \citet{Lu2011} when considering a fixed weight vector, also applies in our setting.
-We write $a \pprefeq_j b$ iff $a \ppref_j b \lor a = b$ and adopt the canonical notation when considering a relation as a function, writing ${\pprefeq_j}(x)$ to designate $\set{y \suchthat x \pprefeq_j y}$.
+The following propositions (with proofs in appendix) show that the procedure for completing a partial profile,  proposed by \citet{Lu2011} when considering a fixed weight vector, also applies in our setting.
+We write $a \pprefeq_j b$ iff $a \ppref_j b \lor a = b$ and adopt the canonical notation when considering a relation as a function, writing ${\pprefeq_j}(x)$ for $\set{y \suchthat x \pprefeq_j y}$.
 
@@
 Even if the chair might be considered able to answer directly such abstract questions, we want to ensure that these questions can also, in principle, be asked in a more concrete way: in terms of winners of example profiles.
-Such questions have precise semantics whose understanding can be assumed to be shared by the chair, contrary to abstract questions about weights.
+Such questions have clear semantics whose understanding can be assumed to be shared by the chair, contrary to abstract questions about weights.
 Moreover, this way of questioning the chair is independent of the voting rule that is being elicited. Questions about weights only make sense when considering PSRs.
 Asking who should win in specific profiles has been used in experimental settings investigating the feeling of justice of individuals \citep{Giritligil2005}, but, to the best of our knowledge, the use of such questions to systematically guide an elicitation process about voting rules is novel.
-This is similar to favor, in decision theory, direct choice questions ("please choose either a or b") compared to questioning the decision maker about the shape of her utility function.
+This is similar to favor, in decision theory, direct choice questions ("please choose either a or b") compared to, say, questioning the decision maker about the shape of her utility function.
 The former are considered “observable”: acts of choice are translated to preference statements \citep[Ch.\ 1]{colell_microeconomic_1995}.
@@
 The \strat{Pessimistic} strategy considers a set of $n + (m-2)$ candidate questions: one per agent, and one per rank (excluding the first and the last one which are known).
+
 The candidate questions to the agents are chosen by extending the idea of \citet{Lu2011}, that priviledge learning about the relationship of $x^*$ and $\bar{y}$ to the other alternatives if possible.
-The candidate questions to the chair are determined as in the Random strategy.
-The strategy selects among these $n + m - 2$ candidate questions one that leads to minimal regret in the worst case: for each question we compute the minimax regret for the two possible answers, considering a penalty terms depending on the kind of question, and choose the best according to (quasi-)$\leximax$.
-%\Cref{sec:appendix} provides more details.
-
 	Given $j \in N^*$, if $x^*$ and $\bar{y}$ are incomparable in $\ppref_j$, the candidate question concerns the pair $(x^*, \bar{y})$, otherwise, %the candidate question
@@
 %Responses to questions involving $x^*$ or $\bar{y}$ constrain the ability of the adversary to complete the profile in such manner, possibly reducing minimax regret.
+
+The candidate questions to the chair are determined as in the Random strategy.
+
 	Once having selected $n + m - 2$ candidate questions, the Pessimistic strategy selects the one that leads to minimal regret in the worst case.
@@
 	% and and $(\pprofile^\min_2, W^\min_2)$. numbering them so that $\MMR(\pprofile_1, W_1) ≥ \MMR(\pprofile_2, W_2)$. Then the badness of the question in the worst case is:
-	The terms $\epsilon_t$ and $\epsilon'_{t}$ are real numbers associated to the type $t$ of question; these parameters are determined experimentally and used to fine control the choice of the question type.
+	The terms $\epsilon_t$ and $\epsilon'_{t}$ are real numbers associated to the type $t$ of question; these parameters are used to fine tune the choice of the question type. 
 	Define similarly $t_2$, $R^{\max}_2$ and $R^{\min}_2$ for  $q_2$.
@@
 %We use this strategy to test whether Pessimistic performs well: depending on the quality of the heuristic of the Pessimistic strategy, it might perform nearly equally well, or perhaps even better, than Extended pessimistic, while being (much) faster.
-Extended pessimistic is applicable only to small problem instances: its complexity is in $O(n^2 m^5)$, because we consider $O(m^2)$ questions for each agent and need for each question to compute MMR twice, whose complexity is $O(nm^3)$.
+Extended pessimistic is applicable only to very small problem instances: its complexity is in $O(n^2 m^5)$, because we consider $O(m^2)$ questions for each agent and need for each question to compute MMR twice, whose complexity is $O(nm^3)$.
 
@@
 %We want to focus on the most critical setting, as there is a wide variety of possible situations to test in such experiments.
-For the synthetic datasets, we follow an Impartial Culture (IC) assumption: the linear order of each agent is drawn i.i.d. uniformly.
+For the synthetic datasets, we follow an Impartial Culture (IC) assumption: the linear order of each agent is drawn i.i.d.\ uniformly.
 %independently and all have the same probability of appearing. 
@@
 We see that asking random questions does not allow to reach a low regret level even after having asked 100 questions, whereas a low regret level ($\MMR$ = 1) is reached by Pessimistic before having asked 60 questions.
-This holds also for different problem sizes.
+This also holds for other problem sizes.
 For instance, for $m =10$, $n = 20$ and $400$ questions, Random strategy reaches an average regret (over 10 runs) of $12$ (±$ 0.7$) and Pessimistic $0.6$ (±$ 0.5$).
@@
 Our next set of experiments evaluate the Pessimistic strategy in absolute terms. 
-We first wonder how many questions should be asked in order to reach low regret. 
-For the scope of the experiment we consider a ``low level'' to be a tenth of the number of agents: such a regret is equivalent to the difference of score of an alternative $x$ that results from switching from a profile $P$ to a profile $P'$ where ten percent of the agents rank $x$ last instead of first.
+We first wonder how many questions should be asked in order to reach a low regret level, fixed at $n / 10$: such a regret is equivalent to the difference of score of an alternative $x$ that results from switching from a profile $P$ to a profile $P'$ where ten percent of the agents rank $x$ last instead of first.
 The results for various sizes are displayed in \cref{tab:lowRegret}. 
-\commentBN{Either we remove this consideration about n/10 together with \cref{tab:lowRegret}, and we present \cref{tab:questions}.
-Or we redo \cref{tab:questions} considering the questions needed to reach MMR=n/10 instead of the ones needed to reach 0.}
-
-%For the experiments we performed, we see that the number of questions required to reach a low regret level grows approximately linearly with the number of agents and grows less fast than the square of the number of alternatives.
-%Averaging these data by category of value for $m$, and assuming no questions get asked to the chair, we see that in order to reach a low regret level, each agent will have to answer $5.6$ questions for $m = 5$, $17.2$ questions for $m = 10$ and $27.1$ questions for $m = 15$.
-These numbers have to be contrasted with the estimated number of questions required to elicit the full preference of an agent which are $6.6$ for $m=5$, $24.8$ for $m=10$ and $48.4$ for $m=15$.
-To obtain these data, we constrained the Pessimistic strategy to ask questions to the agents only, and ran it on a single agent problem, with various values for $m$.
+Another interesting measure is the average number of questions asked to each participant before reaching zero regret.
+For example, in the case $m = 10, n = 20$, Pessimistic asks on average $49$ questions to the chair and $18$ questions to each agent (\cref{tab:questions} in \cref{sec:appendix} provides more data).
 
@@
 \end{table}
-
-%\begin{table}
-%	\caption{Number of questions needed by the Pessimistic strategy to elicit the complete preference of one agent.}
-%	\label{tab:fullProfile}
-%	\begin{tabular}{S[table-figures-decimal=0]S}
-%		\toprule
-%		{m} & {k} \\
-%		\midrule
-%		5 & 6.6\\
-%		10 & 24.8\\
-%		15 & 48.4\\
-%		\bottomrule
-%	\end{tabular}
-%\end{table}
 
@@
 
-%We next wonder how fast the regret decreases, measured as a function of the number of questions asked.
-This is important practically because it may be impossible or undesirable to ask sufficient questions to reach a low regret level.
-%%Knowing the speed of decrease permits to know which trade-offs can be achieved between the quality of the resulting recommendation and the number of questions that participants have to answer. 
-%\Cref{fig:linearity} shows graphically the decrease in MMR according to the number of questions asked for various problem sizes.
-We see that this function is convex, apart from the very first few questions, indicating %to users of our approach
-%that, on average, halving the number of questions will only reduce the gain in regret by less than half. %\commentBN{Reviewer: Halving the number of questions reduces the regret by more than 50\%.}
-%At the start of the elicitation, the space of uncertainty is so large that the adversary can attain the maximum possible value of regret; multiple answers are needed to constrain her enough for the MMR to start decreasing.
-When approaching optimality, the pace of MMR reduction decreases.
 \Cref{fig:linearity} shows graphically the decrease in MMR according to the number of questions asked for various problem sizes.
-In particular, we can observe, as we expected, that given a problem size, the less the profile is varied the more questions are needed to reach a given MMR.
-For instance, in the \textit{Skate} dataset the top-2 alternatives are the same for all agents, and 8 out of 9 agents rank the same alternative at position 3; in \textit{Courses} all agents rank the same alternative at the top position, while in \textit{T Shirt} the alternatives are evenly distributed in the preference rankings.
-If we compare \textit{Skate} with the same size generated problem (m=14, n=9) we see that the former performs much better than the latter, reaching zero regret after only $100$ questions, while the IC needs almost $500$ questions to reach the same result.
-But if we compare \textit{T Shirt} with the corresponding IC, \commentBN{Do we substitute m=10, n=30 with m=11, n=30 to make it same as T shirt?} we do not observe any important differences in terms of decrease of regret.
-This suggest that high degree of similarity in the preference rankings helps reducing the regret faster.
+In particular, this shows important differences between some real data sets and the problems generated using IC.
+In the \textit{Skate} problem, the value $\MMR = 1$ is reached after less than $100$ questions, while the IC case of the same size ($m = 14, n = 9$) requires more than $200$ questions to reach that value.
+But comparing \textit{T Shirt} with similar IC cases do not reveal any important differences in terms of decrease of regret.
+This can be explained by the high degree of similarity in the preference rankings of the \textit{Skate} problem, which helps reducing the regret faster: in that dataset the top-2 alternatives are the same for all agents, and 8 out of 9 agents rank the same alternative at position 3.
+By contrast, in \textit{T Shirt}, the alternatives are evenly distributed in the preference rankings.
+% in \textit{Courses} all agents rank the same alternative at the top position,
 
 %\subsection{Value of information comparison}
-\paragraph{Comparison with Two Phase}
+\paragraph{Comparison with Two Phases}
 
@@
 
+%TODO restore this (temporarily disabled to avoid warning). I suggest $q_c$ and $q_v$ instead of qstC and qstV.
 \begin{table}
@@
 \end{table}
-
 \end{document}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2021-01-20 appendix.tex
moved appendix and larger legend

--- 2021-01-20 minimax.tex
@@
 \usepackage{amsthm}
-
+\usepackage{xr}
+\externaldocument{minimax}
 %%% Load required packages here (note that many are included already).
@@
 \pgfplotsset{compat=1.16}
-
-\setlist[itemize]{noitemsep, topsep=0pt}
-
-\newcommand{\commentOC}[1]{\textcolor{blue}{\small$\big[$OC: #1$\big]$}}
-\newcommand{\commentBN}[1]{\textcolor{red}{\small$\big[$BN: #1$\big]$}}
-\newcommand{\commentPV}[1]{\textcolor{brown}{\small$\big[$PV: #1$\big]$}}
-
-\pdfinfo{
-	/TemplateVersion (IJCAI.2021.0)
-}
-
-%I find these settings useful in draft mode. Should be removed for final versions.
-	%Which line breaks are chosen: accept worse lines, therefore reducing risk of overfull lines. Default = 200.
-		\tolerance=2000
-	%Accept overfull hbox up to...
-		\hfuzz=2cm
-	%Reduces verbosity about the bad line breaks. TODO reduce
-		\hbadness 10000
-	%Reduces verbosity about the underful vboxes.
-		\vbadness=6000
-
-%%% Use this command to specify the title of your paper.
-
-\title{Simultaneous Elicitation of Scoring Rule and Agent Preferences for Robust Winner Determination}
-
-%%% Provide names, affiliations, and email addresses for all authors.
-
-\author{ID: 3177}
-
-%\author{
-%	Beatrice Napolitano$^1$\footnote{Contact Author}\and
-%	Olivier Cailloux$^1$\and
-%	Paolo Viappiani$^2$\\
-%	\affiliations
-%	$^1$Université Paris-Dauphine, Université PSL, CNRS, LAMSADE\\
-%	$^2$LIP6, UMR 7606, CNRS and Sorbonne Universit\'e\\
-%	\emails
-%	\{beatrice.napolitano, olivier.cailloux\}@dauphine.fr,
-%	paolo.viappiani@lip6.fr
-%}
-
-\newcommand{\BibTeX}{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em\TeX}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \begin{document}
 
-\maketitle
-
-\begin{abstract}
-Social choice deals with the problem of determining a consensus choice from the preferences of different agents.
-In the classical setting, the voting rule is fixed beforehand and full information concerning the preferences of the agents is provided.
-This assumption of full preference information has recently been questioned by a number of researchers and
-	several methods for eliciting the preferences of the agents have been proposed.
-	%  are completely known have been proposed, as well as techniques that consider the opposite scenario.
-
-In this paper we argue that in many situations one should consider as well the voting rule to be 	partially specified.
-%	This article goes one step further by tackling one important new case, namely, when both the voting rule and the agents preferences are partially known.
-It also permits to obtain a progressively refined recommendation without requiring to achieve full knowledge of either sort of information.
-%This is useful because providing such information is often costly: the chair may find it hard to specify a rule completely; agents may need time to form reflective preferences.	
-	Focusing on positional scoring rules, we assume that the chair, while not able to give a precise definition of the rule, is capable of answering simple questions requiring to pick a winner from a concrete profile.
-In addition, we assume that the agent preferences also have to be elicited.
-%and are acquired by asking comparison queries.
-	We propose a method for robust approximate winner determination and interactive elicitation based on minimax regret; we develop several strategies for choosing the questions to ask to  the chair and the agents in order to %acquire the most relevant information for
-converge quickly to a near-optimal alternative. Finally, we analyze these strategies in experiments %in order to validate our approach
- %focusing on settings 
- where the  rule and the preferences are simultaneously elicited.
- %and obtain practical guidelines.
-\end{abstract}
-
-\section{Introduction}
-Aggregation of preference information is a central task in many computer systems (recommender systems, search engines, etc).
-In many situations, such as in group recommender systems, the goal is to find a consensus choice;
-social choice theory can provide foundations for such applications.
-
-%The traditional approach to social choice assumes that both the social choice function and the full preference orderings of the agents (voters) are expressed beforehand.
-These represent two strong hypothesis.
-The traditional approach to social choice assumes that 1) the full preference orderings of the agents and 2) the social choice function are expressed beforehand. These represent two strong hypothesis.
-
-Requiring agents to express full preference orderings can be prohibitively costly (in terms of cognitive and communication cost).
-This observation has motivated several works assuming partial preference orders: 
-%and incremental elicitation of agent preferences. 
-%In the context of social choice, several authors have been interested in obtaining information about winners with reduced assumptions about the knowledge of the agent preferences (assuming that the voting rule is known).
-one early work is  by \Citet{Conitzer2005} who studied the complexity of communication when using different voting rules; %determining lower and upper bounds;
-%they showed that, 
-%in the worst case, the agents should send their complete set of preference for several rules. 
-\Citet{Konczak05} studied the computation of possible and necessary winners for various voting rules; %and showed that the problem is hard in the general case.
-\citet{Xia2008} then showed that, while the identification of a necessary co-winner in scoring rules is polynomial,  the determination of possible co-winners is NP-hard;
-% they also  proposed polynomial-time algorithms when using maximin and Bucklin.
-additional complexity results were given by \citet{Walsh2007} and \citet{Pini2007}.
-%\citep{Walsh2007} showed that the general case remains computationally hard even when restricting to single-peaked preferences;  sufficient conditions that ensure tractability were then found \citep{Pini2007}.
-
-Since in many practical situations there would be too many possible winners but no necessary winners, several works addressed the problem of agent preferences elicitation using a variety of approaches (minimax regret, Bayesian methods, etc.) with the goal of converging to a necessary winner \citep{Naamani-Dery2015,Kalech2011,Lu2011,Pini2009,Benabbou2016,Dey2016,Dey2016_2}.
-Among those, \citet{Walsh2009} and \citet{Conitzer2009} analyzed when to stop the elicitation process.
-
-A second concern is the ability of the chair (the person or organization supervising the voting process) to provide a precise definition of the voting rule, suggesting the relaxation of the second hypothesis.
-Indeed, it is often difficult for non-experts to formalize a voting rule on the basis of some generic preferences over a desired aggregation method.
-%Thus, the first hypothesis should also be relaxed. 
-%While most of the focus in the research community has been in dealing with incomplete agent preferences, 
-Consider, as an example, a chair that is about to hire a new employee, whose performances are evaluated by several experts.
-The members of the chair may not have a voting rule in mind at the start of the process, and might not wish to agree on a specific voting rule.
-However, they might be willing to answer a few questions requiring to select who should be the winner out of specific profiles.
-%The information provided can be used to   % to determine their employee of choice.
-
-%This paper considers both sources of uncertainty at the same time, and proposes a method able to recommend a consensus choice without requiring full knowledge of either.
-In this paper, we focus on positional scoring rules with convex weights, that are a particularly common method used to aggregate rankings. 
-We develop methods, based on the notion of minimax regret, for determining a robust ``winner'' under uncertainty of both the voting rule and the agent preferences.
-%alternative using positional scoring rules and 
-We provide incremental elicitation methods that 
-at each step of the elicitation question either one of the agents or the chair, and we discuss several heuristics to choose questions that quickly reduce the regret. 
-Answers to questions are encoded as constraints; questions to the agents are comparisons between pairs of alternatives while
-questions to the chair ask to select a winner out of a synthetic profile.
-
-While some previous works have considered partially specified aggregation methods \citep{Stein1994,Llamazares2013,Viappiani2018}, we do not know of any work considering both sources of uncertainty at the same time.
-%has dealt with %scenarios where it is instead the voting rule that is partially defined. % but the preferences are given. 
-%a  partially defined voting rule.
-%While previous works have considered either partial information about the agent preferences or a partially specified aggregation method, we do not know of any work considering both sources of uncertainty at the same time.
-Actually, very few works altogether have considered the problem of eliciting a voting rule by asking questions to the chair.
-We mention the work of \Citet{Cailloux2014} that assumes a different representation for the rule.
-%we mention the work of \Citet{Cailloux2014} considering elicitation the voting rule by assuming a specific representation.
-%A classic paper is the one by \citet{Stein1994} that, considering scoring rules, identified dominance relations between alternatives; these relations allow to determine pairs of alternatives where the first is at least as good as the second no matter which weights are chosen among a generic class of weights (decreasing weighs or convex decreasing weights).
-%More recent articles considered the problem of dealing with unspecified weights in positional scoring rules: \citet{Llamazares2013} proposed a method based on Data Envelopment Analysis (DEA), while \citet{Viappiani2018} proposed to aggregate the uncertainty in weights using criteria used in decision-making under uncertainty (such as minimax regret).
-% provided an elicitation framework for a different class of rules.
-Additionally, some works address the manipulability of voting rules \citep{Elkind2012,Dey2018,Dey2018_2,Conitzer2011,Baumeister2019} and 
-strategic behaviors \citep{Endriss2016,Lev2019,Annemieke2012}.
-
-Our approach is evaluated on simulations with synthetic and real datasets where both the voting rule and the agent preferences are initially unknown to the system and incrementally revealed through questioning.
-We assume the chair to be human, thus able to answer questions about a limited number of alternatives, so we focus on small scale social choice situations.
-We compare the effectiveness of several questioning strategies based on the current knowledge of the rule and preferences.
-To summarize our contributions: 1) we provide a novel mechanism for eliciting a voting rule by translating abstract questions about weights to a choice of an alternative given a concrete profile; 2) we show that with our elicitation method it is possible to reach low regret with a reasonable number of questions; 3) we present elicitation strategies that achieve good results within reasonable computation time; 4) we show that for the class of rule considered, asking a few questions to the chair suffice to reach low regret; 5) our experiments suggest that low degree of similarity among preferences (as in impartial culture) is a more challenging setting than less varied profiles.
-%\begin{itemize}
-%	\item we provide a novel mechanism for eliciting a voting rule by translating abstract questions about weights to a choice of an alternative given a concrete profile;  
-%	\item we showed that with our elicitation method %in small problem sizes, %starting with zero knowledge,
-%	it is possible to reach low regret with a reasonable number of questions;
-%	\item the elicitation strategies that we provide, in particular Pessimistic, achieve good results within reasonable computation time; %for small problem sizes;
-%	\item we showed that for the class of rule considered, asking a few questions to the chair suffice to reach low regret;
-%	\item our experiments suggest that low degree of similarity among preferences %rankings 
-%	(as in impartial culture) is a more challenging setting than less varied profiles.
-%\end{itemize}
-
-\section{Social choice with partial information}
-\label{sec:background}
-We now introduce some basic concepts.
-We consider a set $A$ of $m$ alternatives (products, restaurants, public projects, job candidates, etc.), an infinite set $\N$ of potential agents and a specific finite set of agents $N^* \subset \N$.
-
-A {\em profile} $(\pref_j, j \in N)$ considers a finite subset of agents $N \subset \N$ and associates to each agent a preference order ${\pref_j}  \in \linors$, a linear order over the alternatives.
-A profile is equivalently represented by $\profile=(v_j, j \in N)$ where $v_j(x) \in \set{1, \ldots, m}$ denotes the rank of alternative $x$ in the preference order $\pref_j$. 
-A social choice function $f : \cup_{\emptyset ≠ N \subset \N} \linors^N \rightarrow \powersetz{A}$ associates to each profile a set of (tied) winners, where $\powersetz{A}$ is the powerset of $A$ excluding the empty set.
-Among the many possible social choice functions, we consider convex {\em positional scoring rules (PSRs)}.
-A PSR $f^{\w}$ is parameterized by a \emph{scoring vector} $\w$ associating weights $w_r \in [0, 1]$ to positions, with $1 = w_1 ≥ w_2 ≥ … ≥ w_m = 0$.
-Let $\alpha^{x}_r$ be the number of times that alternative $x$ was ranked in the $r$-th position.
-Given $\profile$ and $\w$, an alternative $x \in A$ obtains the score
-\begin{align}
-	\label{eq:srule}
-	s(x; \profile, \w) = \sum_{j=1}^{n} w_{v_j(x)}
-	= \sum_{r=1}^{m} \alpha^{x}_r w_r\ .
-\end{align}
-The winners $f^{\w}(\profile)$ are the alternatives with highest score.
-
-An important class of PSRs is the one using convex weights \citep{Stein1994,Llamazares2016}, meaning that the difference between the weight of the first position and the weight of the second position is at least as large as the difference between the weights of the second and third positions, etc.
-\begin{equation} 
-	\label{eq:convexity}
-	\forall r \in \{1,\ldots,m-2\}: w_r - w_{r+1} \geq w_{r+1}-w_{r+2}.
-\end{equation}
-The constraint above is a natural and common assumption, often used when aggregating rankings in sport competitions (such as F1 racing, alpine skiing world cup); losing ranks at the top  is more damaging than losing ranks at the bottom.
-Let $\W$ denote the set of such convex weight vectors.
-
-Let $\profile^* = (\pref_j^*, j \in N^*)$ and $\w^*$ denote the profile and weight vector, unknown to us, that represent the preferences of the agents in $N^*$ and of the chair.
-
-At a given time, our knowledge of agent $j$'s preference is encoded by a partial order ${\ppref_j} \subseteq {\pref_j^*}$ over the alternatives, a transitive and asymmetric relation (we assume that preference information is truthful).
-%We use $\prefinc$ to denote incomparability, that is $a \prefinc_{j} b$ iff $a \nppref_j b \wedge b \nppref_j a$.
-An incomplete profile $\pprofile = (\ppref_j, j \in N^*)$ maps each agent to a partial preference.
-Let $C(\ppref_j) = \set{{\succ} \in \linors \suchthat {\ppref_j} \subseteq {\succ}}$ denote the set of possible completions of $\ppref_i$ and $C(\pprofile) = \prod_{j \in N} C(\ppref_j)$ the set of complete profiles extending $\pprofile$.
-Note that $\profile^* \in C(\pprofile)$.
-
-The vector $\w^*$  is also unknown but we assume that the chair is able to specify additional preference information taking the form of linear constraints about $\w^*$.
-Let $\pw \subseteq \W$ denote the set of weight vectors compatible with the preferences expressed by the chair about the scoring vector.
-%Of course it may be difficult for real decision makers to state preferences about the voting rule in such an abstract way.
-We will show in \cref{sec:elicit} that the additional preferences we use can be elicited by showing a complete profile of a synthetic election and asking who should be elected in this case.
-
-\section{Robust winner determination}
-\label{sec:mmr}
-It is desirable in an elicitation protocol such as ours to be able to stop before reaching full knowledge of the agent preferences or of the preferences of the chair about the voting rule.
-As, often, there are no necessary winners and too many possible winners, it is useful to declare a winner given partial information.
-As a decision criterion to determine a winner, we propose to use minimax regret \citep{Savage1954}. 
-This decision criterion has been used for robust optimization under data uncertainty \citep{Kouvelis1997} as well as in decision-making with uncertain utility values \citep{Salo2001,Boutilier2006}.
-In particular, \citet{Lu2011} have adopted minimax regret for winner determination in social choice where
-the preferences of agents are partially known, while the social choice function is known.
-
-We consider the simultaneous presence of incomplete knowledge in agent preferences and in the weights of the PSR.
-We use \emph{maximum regret} to quantify the worst-case error, and let the alternatives that minimize this quantity win, giving some robustness in face of ignorance.
-Intuitively, the quality of a proposed alternative $a$ is how far $a$ is from the optimal one in the worst case, given the current knowledge.
-
-Given $\pprofile$ and $\pw$ (that represent the current knowledge about agent preferences and the PSR),
-the maximum regret is considered by assuming that an adversary can both 1) extend the partial profile $\pprofile$ into a complete profile, and 2) instantiate the weights choosing among any weight vector in $\pw$.
-%where $\pprofile$ and $\pw$ represent our knowledge so far.
-We formalize the notion of minimax regret in multiple steps.
-First of all, $\Regret(x, \profile, \w) = \max_{y \in A} s(y; \profile,\w) - s(x; \profile, \w)$ is the “regret” of selecting $x$ as a winner instead of choosing the optimal alternative under $\profile$ and $\w$.
-The pairwise maximum regret $\PMR(x,y;\pprofile,W) = \max_{\w \in W} \max_{\profile \in C(\pprofile)} s(y; \profile,\w) - s(x; \profile,\w)$ of $x$ relative to $y$ given the partial profile $\pprofile$ and the set of weights $W$
-is the worst-case loss of choosing $x$ instead of $y$ under all possible realizations of the full profile {\em and} all possible instantiations of the weights.
-The maximum regret $\MaxR(x;\pprofile,W) = \max_{y \in A} \PMR(x,y; \pprofile, W) = \max_{\w \in W} \max_{\profile \in C(\profile)} \Regret(x; \profile, \w)$ is the worst-case loss of $x$.
-That is the loss occurred as the result of an adversarial selection of the complete profile $\profile \in C(\pprofile)$ and of the scoring vector $\w \in W$ that together maximize the loss between $x$ and the true winner under $\profile$ and $\w$.
-Finally,  $\MMR(\pprofile,W) = \min_{x \in A} \MaxR(x;\pprofile,W)$ is the value of minimax regret under $\pprofile$ and $W$, obtained when recommending a minimax optimal alternative $x^*_{\pprofile, W} \in A^*_{\pprofile, W} = \argmin_{x \in A} \MaxR(x;\pprofile,W)$.
-Picking as consensus choice an alternative associated with minimax regret provides a recommendation that gives worst-case guarantees. 
-In cases of ties in minimax regret, we can return all minimax alternatives $A^*_{\pprofile, W}$ as winners or pick one of them using some tie-breaking strategy.
-
-Observe that if $\MMR(\pprofile, W)\!=\!0$, then any $x^{*}_{\pprofile,W} \in A^*_{\pprofile, W}$ is a necessary winner: any valid completion of the profile and choice of $w \in W$ gives to $x^{*}_{\pprofile,W}$ the highest score.
-
-We note that our notion of regret gives some cardinal meaning to the scores: instead of just being used to select winners under the corresponding PSR, their differences are considered as representing the regret of the chair.
-
-% Add some general remarks about using minimax regret
-
-\paragraph{Computation of minimax regret}
-Given a voting rule and a partially specified profile, \citet{Xia2008} determine necessary winners by showing constructions that attempt to maximize the score difference between a proposed winner and a chosen alternative.
-This reasoning was later adopted by \citet{Lu2011} who used the considerations on the worst-case completions for computing the minimax regret.
-
-In order to compute pairwise maximum regret, and therefore minimax regret, we decompose the PMR into the contributions associated to each agent by adapting this same reasoning to our setting.
-The context is however more challenging due to the presence of uncertainty in the weights.
-
-Recall that, in the computation of $s(x; \profile, \w)$, $w_{v_j(x)}$ represents the score that $x$ obtains in the ranking $v_j$ (see \cref{eq:srule}).
-Since scoring rules are additively decomposable, we can consider separately the contribution of each agent to the total score.
-Thus, we can write the actual regret of choosing $x$ instead of $y$ as $s(y; \profile,\w) - s(x; \profile, \w) = \sum_{j=1}^n w_{v_j(y)} - w_{v_j(x)}$, and we obtain $\PMR(x,y; \pprofile, W) =  \max_{\w \in W} \sum_{j=1}^{n} \max_{v_j \in C(\succ_j^p)} [w_{v_j(y)} - w_{v_j(x)}]$.
-%Note that in general the inner max depends on the weights chosen by the outer max.
-
-The following propositions (with proofs in appendix) show that the procedure for completing a partial profile,  proposed by \citet{Lu2011} when considering a fixed weight vector, also applies in our setting.
-We write $a \pprefeq_j b$ iff $a \ppref_j b \lor a = b$ and adopt the canonical notation when considering a relation as a function, writing ${\pprefeq_j}(x)$ for $\set{y \suchthat x \pprefeq_j y}$.
-
-\begin{proposition} \label{claim:completion}
-	There exists a completion $\hat{\profile} \in C(\pprofile)$ of the profile $\profile$ such that $\PMR(x,y; \pprofile, W) = \max_{\w \in W} [ s(y; \hat{\profile}, \w) - s(x; \hat{\profile}, \w) ]$ and such that the linear order $\hat{v}_{j}$ of each agent $j$ satisfies:
-	\begin{align} 
-		\label{eq:complx}
-		a \pref_j x &⇔ ¬(x \pprefeq_j a)\\
-		\label{eq:comply}
-		y \pref_j a &⇔ ¬(a \pprefeq_j y) ∧ ¬((x \pprefeq_j y) ∧ ¬(x \pprefeq_j a)).
-	\end{align} 
-\end{proposition}
-
-\begin{proposition} \label{claim:rankPMR}
-	The rank of $x$ in the PMR-maximizing linear orders of agent $j$ is $\hat{v}_{j}(x) = 1+\card{A}-\card{{\pprefeq_j}(x)}$, and the rank of $y$ is $\hat{v}_{j}(y)=1+\card{{\pprefinv_j}(y)}+\card{\beta}$, where $\card{\beta} = \card{A \setminus ({\pprefeq_j}(x) \cup {\pprefinv_j}(y))}$ if $(x \pprefeq_j y)$ and $\card{\beta} = 0$ otherwise.
-\end{proposition}
-Note that in \cref{claim:rankPMR}, in the case $(x \pprefeq_j y)$, $\beta$ is the number of alternatives incomparable with both $x$ and $y$.
-\begin{proposition}\label{claim:PMR}
-	The $\PMR$ can be written as:
-	\begin{align} 
-		\PMR(x,y; \pprofile, W)  
-		& = \max_{w \in W} \sum_{j=1}^n w_{\hat{v}_j(y)} - w_{\hat{v}_j(x)} \\ 
-		& = \max_{w \in W} \sum_{r=1}^m (\hat{\alpha}_{r}^{y} - \hat{\alpha}_{r}^{x}) w_i. 
-	\end{align}
-	where $\hat{\alpha}_{r}^{y}$ (resp. $\hat{\alpha}_{r}^{x}$)  is the number of times $y$ (resp. $x$) has rank $r$ in the complete profile $\hat{\profile}$ defined in \cref{claim:rankPMR}. 
-\end{proposition}
-%\cref{claim:rankPMR} can be understood by observing that in the case $(x \pprefeq_j y)$, $\beta$ is the number of alternatives incomparable with both $x$ and $y$.
-\cref{claim:PMR}  shows that PMR is linear in the weights.
-%Recall that $\pw$ represents the weight vectors compatible with the preferences of the chair stated so far.
-The pairwise max regret $\PMR(x,y; \pprofile,W)$ can thus be obtained by solving the following linear program defined on the variables $w_1, …, w_m$:
-\begin{align}
-	\max_{\w} & \sum_{r=1}^m (\hat{\alpha}_{r}^{y} - \hat{\alpha}_{r}^{x}) w_{r}\\
-	\text{ s.t. } & w_1 = 1 ≥ … ≥ w_m = 0, \text{\cref{eq:convexity}} \text{ and } \w \in \pw.
-\end{align}
-%Note that given our choice $w_{1}=1$ and $w_{m}=0$, there are only $m-2$ variables 
-%(we leave $w_{1}$ and $w_{m}$ in the LP just for clarity of presentation).
-The max regret $\MaxR(x; \pprofile, W)$ is determined by considering the pairwise regret of $x$ with all other alternatives in $A$, and the recommended alternatives are the ones with least max regret.
-Observe that when the $\PMR$ of an alternative $x$ (against some other alternative $y$) exceeds the best MR value found so far, we do not need to further evaluate $x$. 
-This idea can be exploited using a minimax-search tree \citep{Braziunas2012}.
-
-\section{Interactive Elicitation} 
-\label{sec:elicit}
-We propose an incremental elicitation method based on minimax regret.
-At each step, the system may ask a question either to one of the agents about her preferences or to the chair about the voting rule. 
-The goal is to obtain relevant information to reduce minimax regret as quickly as possible.
-The elicitation can be terminated either after a given number of questions, or when the minimax regret is lower than a threshold (or when it drops to zero if we wish optimality).
-
-%As termination condition of elicitation, we can check whether minimax regret is lower than a threshold; or after having asked a given number of questions.
-%if we wish optimality, we can perform elicitation until minimax regret drops to zero.
-
-%The remainder of this section is structured as follows.
-%First, we discuss the different types of questions that can be asked to the agents and to the chair, and the way responses are handled.
-%Then, we describe different strategies to determine informative queries to ask next, with the goal of reducing $\MMR(\pprofile,W)$ quickly.
-
-\paragraph{Question types}
-We distinguish between questions asked to the agents and questions asked to the chair.
-As {\em questions asked to the agents} we consider comparison queries relating two alternatives.
-%Another common type of queries are {\em top-k}, asking to each agent her $k$ most preferred alternatives.
-The effect of a response to a question asked to an agent is the increase in our knowledge about the agent rankings, thus augmenting the partial profile $\pprofile$. 
-If agent $j$ answers a comparison query stating that alternative $a$ is preferred to $b$, then the partial order $\ppref_j$ is augmented with $a \ppref_j b$ and by transitive closure.
-
-A bit more discussion is needed about {\em questions asked to the chair}.
-Such questions aim at refining our knowledge about the scoring rule; a response gives us a constraint on the weight vector $\w$.
-In particular, we want to obtain constraints of the type $w_{r} - w_{r+1} \geq \lambda (w_{r+1} - w_{r+2})$ for $r \in \{1,\ldots,m-2\}$, relating the difference between the importance of ranks $r$ and $r+1$ with the difference between ranks $r+1$ and $r+2$.
-
-\paragraph{Building concrete questions for the chair}
-Even if the chair might be considered able to answer directly such abstract questions, we want to ensure that these questions can also, in principle, be asked in a more concrete way: in terms of winners of example profiles.
-Such questions have clear semantics whose understanding can be assumed to be shared by the chair, contrary to abstract questions about weights.
-Moreover, this way of questioning the chair is independent of the voting rule that is being elicited. Questions about weights only make sense when considering PSRs.
-Asking who should win in specific profiles has been used in experimental settings investigating the feeling of justice of individuals \citep{Giritligil2005}, but, to the best of our knowledge, the use of such questions to systematically guide an elicitation process about voting rules is novel.
-This is similar to favor, in decision theory, direct choice questions ("please choose either a or b") compared to, say, questioning the decision maker about the shape of her utility function.
-The former are considered “observable”: acts of choice are translated to preference statements \citep[Ch.\ 1]{colell_microeconomic_1995}.
-
-Thus, our task is to build a profile, given $\lambda$ and $r ≤ m-2$, in such a way that the set of (tied) winners picked by the chair reveals whether $w_{r} - w_{r+1} \geq \lambda (w_{r+1} - w_{r+2})$.
-\begin{proposition}\label{prop:chairQuestions}
-	Given a rational $\lambda = p/q > 1$ and a rank $r$ between $1$ and $m - 2$, there exists a profile $P$ such that, for any weight vector $\w \in \W$, $a \in f(P)$ iff $w_{r} - w_{r+1} ≥ \lambda (w_{r+1} - w_{r+2})$ and $b \in f(P)$ iff $w_{r} - w_{r+1} ≤ \lambda (w_{r+1} - w_{r+2})$, where $f$ is the PSR parameterized with $\w$.
-\end{proposition}
-
-\begin{example*}
-	Suppose we want to ask the following question to the chair: $w_{2} - w_{3} ≥ 2 (w_{3} - w_{4})$. 
-	We then show the following profile to the chair and ask who should win (each column is a preference of an agent).
-	\begin{center}
-		$
-		\begin{array}{ccccccccc}
-			c&d&d&a&a&a&b&b&b\\
-			a&c&c&b&b&b&a&a&a\\
-			b&b&b&c&c&c&d&d&d\\
-			d&a&a&d&d&d&c&c&c\\
-		\end{array}.
-		$
-	\end{center}
-	Both $a$ and $b$ have scores higher than $c$ and $d$ for all convex weights, thus either $a$ or $b$ will be picked under our hypothesis; and $s(a) ≥ s(b) ⇔ w_2 + 2 w_4 ≥ 3 w_3$.
-	(\cref{proof:chairQuestions} presents the general method of constructing such profile.)
-\end{example*}
-
-\paragraph{Elicitation strategies}
-We develop several strategies for simultaneous elicitation of agent preferences and of the PSR.
-While it is of course possible to first fully elicit the agent preferences and afterwards elicit weights, we want to investigate approaches that are able to recommend winning alternatives before obtaining complete knowledge of the profile or the rule.
-%Indeed, it can be beneficial to split efforts asking questions to the chair and to agents, depending on which is estimated to be more informative.
-We define here the various strategies we tested experimentally. A strategy tells us, given the current partial knowledge $(\pprofile, W)$, which question to ask next.
-
-The \strat{Random} strategy gives a baseline for comparison and informs about the difficulty of an elicitation problem. 
-It first chooses equiprobably whether to question the chair or the agents.
-In the first case, it draws one rank in $1 ≤ r ≤ m-2$ equiprobably, takes the middle of the interval of values for $\lambda$ that are still possible considering our knowledge so far, and asks whether $w_r - w_{r+1} ≥ \lambda (w_{r+1} - w_{r+2})$.
-%The intervals are initialized to $[1, n]$: $\lambda≥1$ by convexity and we assume $\lambda≤n$ wlog, in fact for $\lambda≥n$, the rule coincides with Plurality.
-In the second case, it draws equiprobably among the agents whose preference is not known entirely; draws an alternative $a$ equiprobably among those involved in some incomparabilities in $\ppref_j$; and draws an alternative $b$ equiprobably among those incomparable with $a$ in $\ppref_j$.
-
-Let $(x^{*},\bar{y}, \bar{\profile}, \bar{\w})$ be the current solution of the minimax regret, where $x^{*}$ is the minimax optimal alternative and $\bar{y}, \bar{\profile}, \bar{\w}$ the corresponding adversarial choices.
-The \strat{Pessimistic} strategy considers a set of $n + (m-2)$ candidate questions: one per agent, and one per rank (excluding the first and the last one which are known).
-
-The candidate questions to the agents are chosen by extending the idea of \citet{Lu2011}, that priviledge learning about the relationship of $x^*$ and $\bar{y}$ to the other alternatives if possible.
-	Given $j \in N^*$, if $x^*$ and $\bar{y}$ are incomparable in $\ppref_j$, the candidate question concerns the pair $(x^*, \bar{y})$, otherwise, %the candidate question
-	it concerns the pair $(x^*, z)$ for some $z$ incomparable to $x^*$ (randomly chosen), or if none such $z$ exist, the pair $(\bar{y}, z)$ for some $z$ incomparable to $\bar{y}$, or, if both $x^*$ and $\bar{y}$ are comparable to every alternatives in $\ppref_j$, any incomparable pair is picked at random.
-%Responses to questions involving $x^*$ or $\bar{y}$ constrain the ability of the adversary to complete the profile in such manner, possibly reducing minimax regret.
-
-The candidate questions to the chair are determined as in the Random strategy.
-
-	Once having selected $n + m - 2$ candidate questions, the Pessimistic strategy selects the one that leads to minimal regret in the worst case.
-	%, considering both possible answers to the question, and with penalty terms depending on the kind of question. To define this comparison precisely, 
-	Assume that a question $q_1$ has type $t_1$ (being “chair” or “agent”), and leads to the new knowledge states $(\pprofile_1, W_1)$ if answered positively and $(\pprofile'_1, W'_1)$ if the answer is negative.
-	Define $R^{\max}_1 = \max\set{\MMR(\pprofile_1, W_1), \MMR(\pprofile'_1, W'_1)}$
-	and $R^{\min}_1 = \min\set{\MMR(\pprofile_1, W_1), \MMR(\pprofile'_1, W'_1)} \epsilon_{t} + \epsilon'_{t}$.
-	%If $(\pprofile_1, W_1) ≥ (\pprofile'_1, W'_1)$, define $\MMR^{\max} = \MMR(\pprofile_1, W_1)$ and $\MMR^{\min} = \MMR(\pprofile'_1, W'_1)$; otherwise, define $\MMR^{\max} = \MMR(\pprofile'_1, W'_1)$ and $\MMR^{\min} = \MMR(\pprofile_1, W_1)$.
-	% and and $(\pprofile^\min_2, W^\min_2)$. numbering them so that $\MMR(\pprofile_1, W_1) ≥ \MMR(\pprofile_2, W_2)$. Then the badness of the question in the worst case is:
-	The terms $\epsilon_t$ and $\epsilon'_{t}$ are real numbers associated to the type $t$ of question; these parameters are used to fine tune the choice of the question type. 
-	Define similarly $t_2$, $R^{\max}_2$ and $R^{\min}_2$ for  $q_2$.
-	%We are now faced with the problem of aggregating these values in order to compare the informative values of the candidate questions.
-\footnote{We adopt a pessimistic approach, reported to perform better than optimistic aggregation \citep{Cailloux2014}, although Our experiments in this context suggested a weak impact of that choice on the performance of the strategy.}
-	%To avoid the absorption property of the max, we adopt $\leximax$ as an aggregator.
-	Pessimistic considers question $q_1$ to be better  than $q_2$ iff $R^{\max}_1 < R^{\max}_2 \text{ or } [R^{\max}_1 = R^{\max}_2 \text{ and } R^{\min}_1 < R^{\min}_2]$.
-	%This comparison gives a way of picking questions among a set of possible questions, by picking one that minimizes this approximate measure of minimax regret {\em a posteriori}. 
-	%The motivation for using this operator lies in 
-	In other words if the maximal {\em a posteriori} MMR of two questions are (nearly) equal, then it considers the (penalized) minimal MMR values, preferring the question with the lowest value.
-	%(Technically, instead of applying a pure lexicographic aggregation, which is very sensitive to small errors due to floating-point computations, we apply a weighted sum between the maximal and the penalized minimal MMR values, with a predominant weight given to the maximal one, several order of magnitudes higher than the weight given to the penalized minimal MMR.)
-
-The \strat{Extended pessimistic} strategy uses the same criterion as the pessimistic strategy, but extending it to a bigger set of candidate questions, the same as those considered by the Random strategy.
-These candidate questions are then evaluated using the same operator as for the Pessimistic strategy.
-%We use this strategy to test whether Pessimistic performs well: depending on the quality of the heuristic of the Pessimistic strategy, it might perform nearly equally well, or perhaps even better, than Extended pessimistic, while being (much) faster.
-Extended pessimistic is applicable only to very small problem instances: its complexity is in $O(n^2 m^5)$, because we consider $O(m^2)$ questions for each agent and need for each question to compute MMR twice, whose complexity is $O(nm^3)$.
-
-The \strat{Two phases} strategy is developed in order to investigate the effect of varying the proportion of questions of the two types, %asked to agents and to the chair, %and to compare the performance
-when asking all questions to the chair at the beginning or at the end.
-%first or to the agents first. 
-It is parameterized by $q_c$,  the number of questions to be asked to the chair.
-The \strat{Two phases-ca} variant first asks $q_c$ questions to the chair, then $k - q_c$ questions to the agents, using in both cases Pessimistic to select the specific questions; whereas the \strat{Two phases-ac} variant starts with $k - q_c$ questions to the agents, then questions the chair.
-%Note that when asking first only questions to the chair, if the obtained knowledge approximates well the scoring vector, then in the second part of the elicitation we fall into the more classical setting of incompleteness of preferences assuming a known voting rule.
-%And vice-versa when asking first questions to the agents, the second part of the elicitation is similar to the setting of incompletely specified scoring rule. 
-%This strategy also permits to simulate the current state of the art when considering incomplete preferences.
-By asking enough questions to the chair we can reduce our problem into a well studied one of incompleteness of preferences knowing the voting rule.
-Similarly, if we invert to whom ask questions first, we fall instead in an already studied case of uncertainty of the voting rule with a known complete profile.
-
-Finally, the \strat{Elitist} strategy aims at uncovering as quickly as possible the top alternatives of all agents. 
-%It asks $m - 1$ questions to each agent in turn. 
-For any agent $j$, it asks to compare an alternative currently undominated in $\ppref_j$ with one that is currently incomparable.
-Thus, the top alternative for $j$ will be known after having asked exactly $m-1$ questions to $j$.
-After having asked $n (m-1)$ questions to the agents, it questions the chair only, using the same approach as Pessimistic.
-This strategy can be expected to perform well when the chair assigns a large weight to the first rank, as compared to the other ranks.
-It is used to further challenge Pessimistic, which is not specifically tailored to such a situation.
-
-%\item {\em Volumetric} strategy: chooses an agent $i$ and a query that maximizes the number of new pairwise preferences revealed given the worst response.
-
-\section{Empirical Evaluation} 
-\label{sec:experiments}
-We  performed a number of numerical experiments using both real data and generated profiles in order to validate our approach and test the performance of our elicitation strategies.
-%Our experiments are described by topic here below.
-%We start by describing the general protocol of experimentation. %use the following protocol, deviations are indicated below for each experiment.
-
-Given a problem size $(m, n)$, a number of questions $k$ and a strategy to test, we first create an “oracle”, representing the true preferences of the agents (randomly generated or coming from real data) and the weights associated with the chair’s scoring rule (randomly generated).
-We start with empty knowledge ($\pprofile = \emptyset, W = \W$) about the preference orderings of the agents and the weight differences favored by the chair.
-We obtain the first question to be asked using the strategy under test.
-We then use the oracle to answer the question and update the system's knowledge, which is thus used to obtain the next question.
-This is repeated until $k$ answers have been obtained, computing the resulting MMR values along the way for various values of $k$.
-We repeat this whole experiment a variable number of times, for a given $(m, n, k)$, and report the average resulting MMR and standard deviation \textit{sd}.
-The sizes of the considered scenarios are comparable to the ones used by \citet{Cailloux2014}.
-
-The oracle is built as follows. 
-For the real preferences, we used three datasets from \href{https://www.preflib.org/}{PrefLib} \citep{PrefLib}:\textit{T Shirt} (researchers voted on T-shirt designs; $m \!=\! 11, n \!=\! 30$),
-\textit{Courses}  (students voted on courses; $m \!=\! 9, n \!=\! 146$)
-and \emph{Skate} (judges vote on skaters at the Euros Pairs Short Program; $m \!=\! 14, n \!=\! 9$).
-% tee shirt designs voted by 
-%$n \!=\! 30$ 
-%members of the Optimization Research Group at NICTA;
-% \textit{AGH Course Selection}: $m \!=\! 9$ courses evaluated by $n = 146$ students 
-%of the AGH University; 
-%and \emph{Skate}: $m \!=\! 14$ skaters evaluated by $n \!=\! 9$ judges at the Euros Pairs Short Program.
-%We want to focus on the most critical setting, as there is a wide variety of possible situations to test in such experiments.
-For the synthetic datasets, we follow an Impartial Culture (IC) assumption: the linear order of each agent is drawn i.i.d.\ uniformly.
-%independently and all have the same probability of appearing. 
-We believe IC to be a challenging situation and expect the number of questions to ask, in order to reach a certain level of regret, to decrease with less varied profiles.
-%We adopt IC because it is a more challenging situation: as can be expected intuitively , the number of questions to be asked decrease with less varied profiles. 
-To generate the weights of the scoring rule, we first draw $m \!-\!
-1$ numbers uniformly at random (in the interval $\intvl{0,1}$ representing weight ``differences''), normalize and sort them; a sequence of convex decreasing weight is then obtained by a decumulative sum.
-The penalty parameters for the Pessimistic and Extended pessimistic strategies are set to  $\epsilon_{\text{chair}} = 1.1$, $\epsilon'_{\text{chair}} = 10^{-6}$, $\epsilon_{\text{agent}} = 1.0$ and $\epsilon'_{\text{agent}} = 0$.
-
-\begin{figure}
-	\caption{Average MMR in problems of size $(5, 10)$ after $k$ questions.}
-	\label{fig:smallSize}
-	\begin{tikzpicture}
-		\begin{axis}[
-			y=8,
-			xlabel=Number of Questions,
-			ylabel=Avg. Regret,
-			ytick={0,2,4,6,8,10},
-			xtick distance=10,
-			ytick distance=2,
-			xtick pos=left,
-			ymajorgrids=true,
-			ytick style={draw=none},
-			ymin=0,
-			ymax=11,
-			xmin=0,
-			xmax=100,
-			yticklabels={0,2,4,6,8,10},
-			legend style={font=\scriptsize}]
-			\addlegendimage{mark=*,teal,mark size=1.5}
-			\addlegendimage{mark=triangle*,orange,mark size=1.5}
-			\addlegendimage{mark=square*,blue,mark size=1.5}
-			\addlegendimage{mark=diamond*,red,mark size=1.5}
-
-			\addplot[thick, mark=*, mark size = {2}, mark indices = {35}, teal] table [x=k, y=Pes.]{data/comparison.dat};
-			\addlegendentry{Pes.}
-			\addplot[thick, mark=triangle*, mark size = {2}, mark indices = {45}, orange] table [x=k, y=Ex.Pes.]{data/comparison.dat};
-			\addlegendentry{Ex.Pes.}
-			\addplot[thick, mark=square*, mark size = {2}, mark indices = {50}, blue] table [x=k, y=Eli.]{data/comparison.dat};
-			\addlegendentry{Eli.}
-			\addplot[thick, mark=diamond*, mark size = {2}, mark indices = {50}, red] table [x=k, y=Rnd.]{data/comparison.dat};
-			\addlegendentry{Rnd.}
-
-		\end{axis}
-	\end{tikzpicture}
-\end{figure}
-
-%\begin{figure}
-%	\caption{Average MMR in problems of size $(5, 10)$ after $k$ questions.}
-%	\label{fig:smallSize}
-%%	\Description{Graph showing that Pessimistic performs slightly better than Extended pessimistic, itself performing better than Elitist, itself performing much better than Random.}
-%	\includegraphics[width=.45\textwidth]{comparison.png}
-%\end{figure}
-\sisetup{table-number-alignment = center, table-figures-integer=2, table-figures-decimal=1, table-auto-round}
-\begin{table}
-	\caption{Average MMR in problems of size $(10, 20)$ after $k$ questions assuming geometric weights.}
-	\label{tab:geometricWeights}
-	\begin{tabular}{S[table-figures-integer=3, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=1]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=1]}
-		\toprule
-		{k} & {Pes.} & {sd} & {Eli.} & {sd} \\
-		\midrule
-		0	&20.0	&0.0	&20.0	&0.0\\
-		50	&15.96	&0.54	&17.26	&0.42\\
-		100	&12.48	&0.93	&15.6	&0.43\\
-		150	&9.58	&1.37	&13.94	&0.76\\
-		200	&7.43	&1.25	&10.95	&1.12\\
-		250	&5.26	&1.52	&6.6	&0.79\\
-		300	&3.47	&1.32	&6.57	&0.79\\
-		\bottomrule
-	\end{tabular}
-\end{table}
-\paragraph{Comparison of strategies}
-Our first experiment concerns small size situations.
-\Cref{fig:smallSize} compares some of our strategies in the case $m = 5, n = 10$ (variations around this size yield similar conclusions), where the results are averaged over $200$ runs.
-%(The figure also displays the performance of the Elitist strategy, to which we will come back.)
-We see that asking random questions does not allow to reach a low regret level even after having asked 100 questions, whereas a low regret level ($\MMR$ = 1) is reached by Pessimistic before having asked 60 questions.
-This also holds for other problem sizes.
-For instance, for $m =10$, $n = 20$ and $400$ questions, Random strategy reaches an average regret (over 10 runs) of $12$ (±$ 0.7$) and Pessimistic $0.6$ (±$ 0.5$).
-We also see that Pessimistic performs slightly better than Extended pessimistic, showing that Pessimistic chooses candidate questions wisely; this is good news since Pessimistic is much faster: it takes on average only $16$s for a complete elicitation session (for $m = 5$, $n = 10$ and $100$ questions), while Extended pessimistic takes $50$s.
-Although their performance is close, Pessimistic performs systematically better in multiple runs of the experiment.
-
-We also compared the Pessimistic strategy against Elitist in a situation specifically tailored to advantage Elitist.
-For that experiment specifically, instead of drawing the weights of the oracle randomly, we fix it to a “geometric” weight vector, such that $w_r - w_{r + 1} = 2(w_{r + 1} - w_{r + 2})$, for all $r ≤ m - 2$, so as to dramatically increase the importance of the weights associated to the top ranks.
-Even in that case, we see in \cref{tab:geometricWeights} that Pessimistic performs better than Elitist.
-
-\paragraph{Evaluation of Pessimistic Strategy}
-\label{sec:lowRegret}
-Our next set of experiments evaluate the Pessimistic strategy in absolute terms. 
-We first wonder how many questions should be asked in order to reach a low regret level, fixed at $n / 10$: such a regret is equivalent to the difference of score of an alternative $x$ that results from switching from a profile $P$ to a profile $P'$ where ten percent of the agents rank $x$ last instead of first.
-The results for various sizes are displayed in \cref{tab:lowRegret}. 
-Another interesting measure is the average number of questions asked to each participant before reaching zero regret.
-For example, in the case $m = 10, n = 20$, Pessimistic asks on average $49$ questions to the chair and $18$ questions to each agent (\cref{tab:questions} in \cref{sec:appendix} provides more data).
-
-\begin{table}
-	\caption{Number of questions needed by Pessimistic strategy to reach an MMR of $\frac{n}{10}$ (represented by $k_{\MMR}$), by size.}
-	\label{tab:lowRegret}
-	\begin{tabular}{S[table-figures-decimal=0]S[table-figures-decimal=0]SS[table-figures-integer=3, table-figures-decimal=0]}
-		\toprule
-		{m} & {n} & {$\frac{n}{10}$} & {$k_{\MMR}$} \\
-		\midrule
-		5 & 10 & 1 & 60 \\
-		5 & 15 & 1.5 & 80 \\
-		5 & 20 & 2 & 110 \\
-		10 & 20 & 2 & 340 \\
-		10 & 30 & 3 & 527 \\
-		15 & 30 & 3 & 951 \\
-		\bottomrule
-	\end{tabular}
-\end{table}
-
-\begin{figure}
-	\caption{Average MMR (normalized by $n$) after $k$ questions with Pessimistic strategy for different datasets.}
-	\label{fig:linearity}
-	\begin{tikzpicture}
-		\pgfplotsset{
-			every axis legend/.append style={
-				at={(0.5,1.1)},
-				anchor=south
-			},
-		}
-		\begin{axis}[
-			y=80,
-			legend columns=3,
-			xlabel=Number of Questions,
-			ylabel=MMR/n,
-			ytick={0,0.5,1},
-			xtick distance=100,
-			xtick pos=left,
-			ymajorgrids=true,
-			ytick style={draw=none},
-			ymin=0,
-			ymax=1,
-			xmin=0,
-			xmax=1000,
-			yticklabels={0,0.5,1},
-			legend style={font=\scriptsize}]
-
-			\addlegendimage{mark=triangle*,teal,mark size=2}
-%			\addlegendimage{mark=*,violet,mark size=2}
-			\addlegendimage{mark=square*,green,mark size=2}
-			\addlegendimage{mark=diamond*,red,mark size=2}
-			\addlegendimage{mark=pentagon*,cyan,mark size=2}
-			\addlegendimage{mark=halfcircle*,violet,mark size=2}
-			\addlegendimage{mark=*,pink,mark size=2}
-			\addlegendimage{mark=halfsquare left*,blue,mark size=2}
-			\addlegendimage{mark=halfsquare right*,brown,mark size=2}
-			\addlegendimage{mark=halfsquare*,magenta,mark size=2}
-
-			\addplot[thick, mark=triangle*, mark size = {2}, mark indices = {35}, teal] table [x=k, y=5.10]{data/normalizedLin.dat};
-			\addlegendentry{m=5, n=10}
-%			\addplot[thick, mark=*, mark size = {2}, mark indices = {45}, violet] table [x=k, y=5.15]{data/normalizedLin.dat};
-%			\addlegendentry{m=5, n=15}
-			\addplot[thick, mark=square*, mark size = {2}, mark indices = {90}, green] table [x=k, y=5.20]{data/normalizedLin.dat};
-			\addlegendentry{m=5, n=20}
-			\addplot[thick, mark=diamond*, mark size = {2}, mark indices = {150}, red] table [x=k, y=10.20]{data/normalizedLin.dat};
-			\addlegendentry{m=10, n=20}
-			\addplot[thick, mark=pentagon*, mark size = {2}, mark indices = {300}, cyan] table [x=k, y=10.30]{data/normalizedLin.dat};
-			\addlegendentry{m=10, n=30}
-			\addplot[thick, mark=halfcircle*, mark size = {2}, mark indices = {400}, violet] table [x=k, y=tshirt]{data/normalizedLin.dat};
-			\addlegendentry{tshirts m11n30}
-			\addplot[thick, mark=*, mark size = {2}, mark indices = {400}, pink] table [x=k, y=courses]{data/normalizedLin.dat};
-			\addlegendentry{courses m9n146}
-			\addplot[thick, mark=halfsquare left*, mark size = {2}, mark indices = {200}, blue] table [x=k, y=14.9]{data/normalizedLin.dat};
-			\addlegendentry{m=14, n=9}
-			\addplot[thick, mark=halfsquare right*, mark size = {2}, mark indices = {60}, brown] table [x=k, y=skate]{data/normalizedLin.dat};
-			\addlegendentry{skate m14n9}
-			\addplot[thick, mark=halfsquare*, mark size = {2}, mark indices = {400}, magenta] table [x=k, y=15.30]{data/normalizedLin.dat};
-			\addlegendentry{m=15, n=30}
-		\end{axis}
-	\end{tikzpicture}
-\end{figure}
-
-\Cref{fig:linearity} shows graphically the decrease in MMR according to the number of questions asked for various problem sizes.
-In particular, this shows important differences between some real data sets and the problems generated using IC.
-In the \textit{Skate} problem, the value $\MMR = 1$ is reached after less than $100$ questions, while the IC case of the same size ($m = 14, n = 9$) requires more than $200$ questions to reach that value.
-But comparing \textit{T Shirt} with similar IC cases do not reveal any important differences in terms of decrease of regret.
-This can be explained by the high degree of similarity in the preference rankings of the \textit{Skate} problem, which helps reducing the regret faster: in that dataset the top-2 alternatives are the same for all agents, and 8 out of 9 agents rank the same alternative at position 3.
-By contrast, in \textit{T Shirt}, the alternatives are evenly distributed in the preference rankings.
-% in \textit{Courses} all agents rank the same alternative at the top position,
-
-%\subsection{Value of information comparison}
-\paragraph{Comparison with Two Phases}
-
-\begin{table}
-	\caption{Average MMR in problems of size $(10, 20)$ after $400$ questions, among which $q_c$ to the chair.}
-	\label{tab:twoP400}
-	\begin{tabular}{S[table-figures-integer=3, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=1]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=1]}
-		\toprule
-		{$q_c$} & {2 ph.\ ca} & {sd} & {2 ph.\ ac} & {sd} \\
-		\midrule
-		0 & 0.66 & 0.67 & 0.65 & 0.65  \\
-		15 & 0.71 & 0.73 & 0.67	& 0.64 \\
-		30 & 0.62 & 0.5 & 0.8 & 0.62 \\
-		50 & 1.23 & 1.46 & 0.8 & 0.79 \\
-		100 & 2.03 & 1.56 & 1.88 & 1.02  \\
-%		150 & 3.41 & 1.79 & 4.07 & 1.51 \\
-		200 & 4.61	& 1.35  & 6.53 & 2.0  \\
-%		250 & 8.4 & 1.86 & 	7.69 & 1.24 \\
-		300 &11.07 & 0.86& 11.87 & 1.25 \\
-%		350 &15.06 & 0.68&15.59 & 0.6 \\
-		400 &20.0 & 0.0 & 20.0 & 0.0 \\
-		\bottomrule
-	\end{tabular}
-\end{table}
-
-The experiments so far let the strategy target its questions unrestrictively, leaving open the possibility of questioning either the chair or an agent at each step.
-One may wonder what is lost in terms of regret by asking different proportions of questions to the chair and the agents.
-Such restrictions may be useful because of (partial) unavailability of the chair, or because the estimated cognitive costs may differ sensibly.
-%, as these types of questions differ in nature.
-
-\Cref{tab:twoP400} shows the MMR value reached in problems of size $m = 10, n = 20$ after $400$ questions, using the Two phases strategy, in the “ca” (chair then agents) and in the “ac” (agents then chair) variants.
-These numbers are to be compared with the MMR value reached after 400 questions with the Pessimistic strategy (displayed in \cref{fig:linearity}), which is $0.6$; the Pessimistic strategy asks on average $48$ questions to the chair in this setting.
-These numbers highlight that it is possible to obtain a good-quality recommendation while knowing only that the voting rule is a scoring rule and that the weights are convex, which is our basic hypothesis (corresponding to the line $q_c = 0$, where no question is asked to the chair).
-
-\section{Conclusions}  
-\label{sec:conclusions}
-In this paper we have considered a social choice setting with partial information about the agent preferences and a partially specified voting rule.
-In this setting, we have proposed the use of minimax regret both as a means of robust winner determination as well as a guide to the process of simultaneous elicitation of preferences and voting rule.
-Our experimental results %on randomly generated and real world datasets 
-suggest that regret-based elicitation is effective and allows to quickly reduce worst-case regret significantly.
-They also show that, in our setting, good quality (low regret) recommendations can be achieved short of knowing the weights precisely or the profile completely.
-%regret, but they also show that starting with zero knowledge became a pretentious approach really quickly when increasing the size of the problem.
-Future works will therefore include the test of these strategies on partial specified profiles, ideally on real datasets.
-An other important direction is the extension to voting rules beyond scoring rules.
-%Regret-based elicitation allows to determine near-optimal winners using only few information about the agent preferences.
-
-As part of our contribution, a general open-source library, allowing to reproduce our experiments and perform many more, will be made publicly available. (URL not displayed for ensuring anonymity.)
-%and serve as a basis for further research
-
-%We mention some directions for future works.
-Further development of elicitation strategies, considering alternative heuristics, is an important direction. 
-Second, elicitation could be extended to voting rules beyond scoring rules. 
-Finally, an important direction of research  aims at eliciting preferences while restraining to concrete and easy questions.
-% Acknowledgments: We thank the reviewers for comments helping to improve the paper.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%% The acknowledgments section is defined using the "acks" environment
-%%% (rather than an unnumbered section). The use of this environment 
-%%% ensures the proper identification of the section in the article 
-%%% metadata as well as the consistent spelling of the heading.
-
-%\begin{acks}
-%If you wish to include any acknowledgments in your paper (e.g., to 
-%people or funding agencies), please do so using the `\texttt{acks}' 
-%environment. Note that the text of your acknowledgments will be omitted
-%if you compile your document with the `\texttt{anonymous}' option.
-%\end{acks}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%% The next two lines define, first, the bibliography style to be 
-%%% applied, and, second, the bibliography file to be used.
-%\bibliographystyle{abbrvnat} 
-%\bibliography{biblio}
-
-\newpage
-\bibliographystyle{named}
-%{\small \bibliography{biblio}}
-{\fontsize{9.7}{10.7}\selectfont \bibliography{biblio}}
-
-\newpage
 \appendix
@@
 \newtheorem*{details*}{Strategy Details}
-
+This appendix provides proofs for the propositions presented in the paper together with an additional table of experimental results.
 \begin{sketch*}[\cref{claim:completion}]
@@
 
-%TODO restore this (temporarily disabled to avoid warning). I suggest $q_c$ and $q_v$ instead of qstC and qstV.
-\begin{table}
-	\caption{Average number of questions asked to the chair (\textit{qstC}) and to the agents (\textit{qstV}) by Pessimistic strategy to reach zero regret on the datasets of \cref{fig:linearity}.}
+\begin{table}[ht]
+	\caption{Average number of questions asked to the chair ($q_{c}$) and to the agents (\textit{$q_{v}$}) by Pessimistic strategy to reach zero regret on the datasets of \cref{fig:linearity}.}
 	\label{tab:questions}
@@
 		\toprule
-		{dataset} & {qstC} & {sd} & {qstV} & {sd} \\
+		{dataset} & {$q_{c}$} & {sd} & {$q_{v}$} & {sd} \\
 		\midrule
@@
 		courses & 0			& 0			& 950		& 5.08	\\	
-
 		\bottomrule
@@
 \end{table}
+
 \end{document}

### 2021-01-20 minimax.tex
moved appendix and larger legend

@@
 \usepackage{amsthm}
-
+\usepackage{xr}
+\externaldocument{appendix}
 %%% Load required packages here (note that many are included already).
@@
 			yticklabels={0,0.5,1},
-			legend style={font=\scriptsize}]
+			legend style={font=\footnotesize}]
 
@@
 
-\newpage
-\appendix
-\section{Appendix}
-\label{sec:appendix}
-\newtheorem*{details*}{Strategy Details}
-
-\begin{sketch*}[\cref{claim:completion}]
-	Consider our knowledge $\pprefeq_j$ about the preference of the agent $j$. 
-	The adversary's goal is to make the score of $y$ as high as possible and the score of $x$ as low as possible. 
-	To do this, he should complete $\ppref_j$ to $\pref_j$ by putting above $x$ as many alternatives as he can, that is, all the alternatives except those that are known to be worse than $x$ (those $a$ such that $x \pprefeq_j a$); and similarly, he should put below $y$ all the alternatives he can.
-Two conditions must be excluded for $a$ to go below $y$.
-The alternatives such that $a \pprefeq_j y$ can’t be put below $y$.
-	Furthermore, the first objective must take priority over the second one: when an alternative should go above $x$ according to the first objective (because $¬(x \pprefeq_j a)$), and $x$ is known to be better than $y$ (thus $x \pprefeq_j y$), then $a$ should be put above $x$ (irrespective of whether $a \pprefeq_j y$), which will move both $x$ and $y$ one rank lower than if $a$ had been put below $y$.
-	This maximizes the adversary’s interests: because the weight vector is convex, the difference of scores will be lower when both alternatives are ranked lower (Equation \ref{eq:convexity}), and that difference of scores is in favor of $x$ when $x \ppref_j y$, thus to be minimized from the point of view of the adversary.
-\end{sketch*}
-
-\begin{proof*}[\cref{claim:rankPMR}]
-	The rank of $x$ is directly obtained from \cref{eq:complx}.
-The rank of $y$ is obtained by complementing \cref{eq:comply}, obtaining $a \prefeq_j y ⇔ (a \pprefeq_j y) ∨ ((x \pprefeq_j y) ∧ ¬(x \pprefeq_j a))$, and, observing that $a \pref_j y ⇔ a ≠ y ∧ a \prefeq_j y$, obtaining that $a \pref_j y$ if and only if
-	\begin{equation}
-		\label{eq:betteryinter}
-		(a \neq y) ∧ [(a \pprefeq_j y) ∨ ((x \pprefeq_j y) ∧ ¬(x \pprefeq_j a))],
-	\end{equation} 
-	or equivalently, if and only if
-	\begin{equation}
-		\label{eq:bettery}
-		%a \pref_j y ⇔ 
-		(a \ppref_j y) ∨ ((x \pprefeq_j y) ∧ ¬(x \pprefeq_j a)).
-	\end{equation} 
-	Indeed, \eqref{eq:betteryinter} $⇒$ \eqref{eq:bettery}, and \eqref{eq:bettery} $⇒$ \eqref{eq:betteryinter} because $(x \pprefeq_j y) ∧ ¬(x \pprefeq_j a) ⇒ a ≠ y$ (as when $a = y$, $(x \pprefeq_j y)$ and $¬(x \pprefeq_j a)$ are opposite claims).
-Suffices now to rewrite \cref{eq:bettery} to let the two disjuncts designate disjoint sets:
-	\begin{equation}
-		\label{eq:betteryfinal}
-		a \pref_j y ⇔ 
-		(a \ppref_j y) ∨ ((x \pprefeq_j y) ∧ ¬(x \pprefeq_j a) ∧ ¬(a \ppref_j y)).
-	\end{equation}
-\end{proof*}
-
-\begin{proof*}[\cref{prop:chairQuestions}]
-	\label{proof:chairQuestions}
-	Define a linear order $>_1$ over $A$ as placing $a$ at rank $r$, $b$ at rank $r + 1$, and the remaining alternatives arbitrarily. 
-	Define a linear order $>_2$ over $A$ as placing $a$ at rank $r + 2$, $b$ at rank $r + 1$, and the remaining alternatives arbitrarily.
-	Define an arbitrary linear ordering $>$ over $A \setminus \set{a, b}$. 
-	Define a linear order $>_3$ as placing $a$ first, $b$ second, and following the order of $>$ for the remaining positions.
-	Finally, define a linear order $>_4$ as placing $b$ first, $a$ second, and following the \emph{inverse} order of $>$ for the remaining positions.
-
-	Define $P$ as the profile of $3 (p + q)$ agents containing $q$ times $>_1$, $p$ times $>_2$, and $>_3$ and $>_4$ each $p + q$ times.
-	As a result, $a$ obtains the following ranks: $q$ times $r$, $p$ times $r + 2$, $p + q$ times first, and $p + q$ times second.
-The alternative $b$ obtains the ranks $r + 1$, $2$ and $1$, each $p + q$ times.
-Consider any alternative $c \in A \setminus \set{a, b}$.
-Its score is maximal when it comes first in $>_1$, first in $>_2$ and first in $>$, by convexity of the weights.
-In that case, $c$ is positioned at the ranks $1$, $3$ and $m$, each $p + q$ times.
-
-	Letting $s(x)$ denote the score of $x$ at $P$, we obtain $s(a) = q w_r + p w_{r + 2} + (p + q) w_1 + (p + q) w_2$, thus, $s(a) ≥ (p + q) w_m + (p + q) w_1 + (p + q) w_2$; $s(b) = (p + q) w_{r + 1} + (p + q) w_2 + (p + q) w_1$; and, $\forall c \in A \setminus \set{a, b}$,
-	$s(c) ≤ (p + q) w_1 + (p + q) w_3 + (p + q) w_m$.
-It follows that $a$ or $b$ maximize $s$ (as $s(a) ≥ s(c)$).
-We conclude by observing that $a \in f(P) ⇔ s(a) ≥ s(b) ⇔ q w_r + p w_{r + 2} ≥ (p + q) w_{r + 1} ⇔ w_r - w_{r + 1} ≥ (p / q) (w_{r + 1} - w_{r + 2})$, and similarly for $b \in f(P)$.
-\end{proof*}
-
-%TODO restore this (temporarily disabled to avoid warning). I suggest $q_c$ and $q_v$ instead of qstC and qstV.
-\begin{table}
-	\caption{Average number of questions asked to the chair (\textit{qstC}) and to the agents (\textit{qstV}) by Pessimistic strategy to reach zero regret on the datasets of \cref{fig:linearity}.}
-	\label{tab:questions}
-	\begin{tabular}{cS[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=2]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=2]}
-		\toprule
-		{dataset} & {qstC} & {sd} & {qstV} & {sd} \\
-		\midrule
-		m5n10 	&	8.4		& 2.67 		& 61		& 6.25\\
-		m5n20 	&	13.6	& 6.38		& 118.9		& 14.4\\
-		m10n20 	&	48.5	& 6			& 362.4		& 47.6	\\
-		m10n30 	&	56.3	& 11.18		& 598.1 	& 75.19	\\
-		m15n30 	&	24.5	& 8.77		& 775.5		& 8.77	\\
-		m14n9 	&	58.3	& 33.66		& 370.9		& 40.54	\\
-		m14n9-2 &	56.2	& 34.11		& 368.7		& 53.07 \\
-		skate 	&	0		& 0			& 103.3		& 2.21	\\
-		tshirt  &	30.0	& 5.87		& 961.2		& 23.04	\\
-		courses & 0			& 0			& 950		& 5.08	\\
-
-		\bottomrule
-	\end{tabular}
-\end{table}
 \end{document}

### 2021-01-20 minimax.tex
small edits

@@
 %(we leave $w_{1}$ and $w_{m}$ in the LP just for clarity of presentation).
-The max regret $\MaxR(x; \pprofile, W)$ is determined by considering the pairwise regret of $x$ with all other alternatives in $A$, and the recommended alternatives are the ones with least max regret.
+The max regret $\MaxR(x; \pprofile, W)$ is determined by computing the pairwise regret of $x$ with all other alternatives in $A$, and the recommended alternatives are the ones with least max regret. 
 Observe that when the $\PMR$ of an alternative $x$ (against some other alternative $y$) exceeds the best MR value found so far, we do not need to further evaluate $x$. 
@@
 The oracle is built as follows. 
-For the real preferences, we used three datasets from \href{https://www.preflib.org/}{PrefLib} \citep{PrefLib}:\textit{T Shirt} (researchers voted on T-shirt designs; $m \!=\! 11, n \!=\! 30$),
+For the real preferences, we used three datasets from \href{https://www.preflib.org/}{PrefLib} \citep{PrefLib}: \textit{T Shirt} (researchers voted on tee shirt designs; $m \!=\! 11, n \!=\! 30$),
 \textit{Courses}  (students voted on courses; $m \!=\! 9, n \!=\! 146$)
@@
 %(The figure also displays the performance of the Elitist strategy, to which we will come back.)
-We see that asking random questions does not allow to reach a low regret level even after having asked 100 questions, whereas a low regret level ($\MMR$ = 1) is reached by Pessimistic before having asked 60 questions.
+We see that asking random questions does not allow to reach a low regret level even after having asked 100 questions, whereas a low regret level ($\MMR \!=\!
+1$) is reached by Pessimistic before having asked 60 questions.
 This also holds for other problem sizes.
@@
 In particular, this shows important differences between some real data sets and the problems generated using IC.
-In the \textit{Skate} problem, the value $\MMR = 1$ is reached after less than $100$ questions, while the IC case of the same size ($m = 14, n = 9$) requires more than $200$ questions to reach that value.
+In the \textit{Skate} problem, the value $\MMR\!=\!1$ is reached after less than $100$ questions, while the IC case of the same size ($m = 14, n = 9$) requires more than $200$ questions to reach that value.
 But comparing \textit{T Shirt} with similar IC cases do not reveal any important differences in terms of decrease of regret.

### 2021-01-20 minimax.tex
some regret formulas in display mode

@@
 We formalize the notion of minimax regret in multiple steps.
-First of all, $\Regret(x, \profile, \w) = \max_{y \in A} s(y; \profile,\w) - s(x; \profile, \w)$ is the “regret” of selecting $x$ as a winner instead of choosing the optimal alternative under $\profile$ and $\w$.
-The pairwise maximum regret $\PMR(x,y;\pprofile,W) = \max_{\w \in W} \max_{\profile \in C(\pprofile)} s(y; \profile,\w) - s(x; \profile,\w)$ of $x$ relative to $y$ given the partial profile $\pprofile$ and the set of weights $W$
-is the worst-case loss of choosing $x$ instead of $y$ under all possible realizations of the full profile {\em and} all possible instantiations of the weights.
-The maximum regret $\MaxR(x;\pprofile,W) = \max_{y \in A} \PMR(x,y; \pprofile, W) = \max_{\w \in W} \max_{\profile \in C(\profile)} \Regret(x; \profile, \w)$ is the worst-case loss of $x$.
-That is the loss occurred as the result of an adversarial selection of the complete profile $\profile \in C(\pprofile)$ and of the scoring vector $\w \in W$ that together maximize the loss between $x$ and the true winner under $\profile$ and $\w$.
+First of all, $\Regret(x, \profile, \w)$
+is the “regret” of selecting $x$ as a winner instead of the optimal alternative under $\profile$ and $\w$:
+$$\Regret(x, \profile, \w) = \max_{y \in A} s(y; \profile,\w) - s(x; \profile, \w).$$
+ The {\em pairwise maximum regret} of $x$ relative to $y$ given the partial profile $\pprofile$ and the set of weights $W$ is the worst-case loss of choosing $x$ instead of $y$ under all possible realizations of the full profile {\em and} all possible instantiations of the weights:
+$$\PMR(x,y;\pprofile,W) = \max_{\w \in W} \max_{\profile \in C(\pprofile)} s(y; \profile,\w) - s(x; \profile,\w).$$
+The maximum regret %$\MaxR(x;\pprofile,W)$ 
+is the worst-case loss of $x$:
+\begin{align}
+\MaxR(x;\pprofile,W) & = \max_{y \in A} \PMR(x,y; \pprofile, W) \\ &= \max_{\w \in W} \max_{\profile \in C(\profile)} \Regret(x; \profile, \w).
+\end{align}
+$\MaxR(x;\pprofile,W)$ is the result of an adversarial selection of the complete profile $\profile \in C(\pprofile)$ and of the scoring vector $\w \in W$ that jointly maximize the loss between $x$ and the true winner under $\profile$ and $\w$.
 Finally,  $\MMR(\pprofile,W) = \min_{x \in A} \MaxR(x;\pprofile,W)$ is the value of minimax regret under $\pprofile$ and $W$, obtained when recommending a minimax optimal alternative $x^*_{\pprofile, W} \in A^*_{\pprofile, W} = \argmin_{x \in A} \MaxR(x;\pprofile,W)$.
 Picking as consensus choice an alternative associated with minimax regret provides a recommendation that gives worst-case guarantees. 
-In cases of ties in minimax regret, we can return all minimax alternatives $A^*_{\pprofile, W}$ as winners or pick one of them using some tie-breaking strategy.
+In cases of ties, %in minimax regret, 
+we can return all minimax alternatives $A^*_{\pprofile, W}$ as winners or pick one of them using some tie-breaking strategy.
 
@@
 		& = \max_{w \in W} \sum_{j=1}^n w_{\hat{v}_j(y)} - w_{\hat{v}_j(x)} \\ 
-		& = \max_{w \in W} \sum_{r=1}^m (\hat{\alpha}_{r}^{y} - \hat{\alpha}_{r}^{x}) w_i. 
+		& = \max_{w \in W} \sum_{r=1}^m (\hat{\alpha}_{r}^{y} - \hat{\alpha}_{r}^{x}) w_i 
 	\end{align}
@@
 
-The \strat{Random} strategy gives a baseline for comparison and informs about the difficulty of an elicitation problem. 
+The \strat{Random} strategy is used as a baseline. % and informs about the difficulty of an elicitation problem. 
 It first chooses equiprobably whether to question the chair or the agents.
@@
 %The intervals are initialized to $[1, n]$: $\lambda≥1$ by convexity and we assume $\lambda≤n$ wlog, in fact for $\lambda≥n$, the rule coincides with Plurality.
-In the second case, it draws equiprobably among the agents whose preference is not known entirely; draws an alternative $a$ equiprobably among those involved in some incomparabilities in $\ppref_j$; and draws an alternative $b$ equiprobably among those incomparable with $a$ in $\ppref_j$.
+In the second case, it draws equiprobably among the agents whose preference is not known entirely; it then draws an alternative $a$ among those involved in some incomparabilities in $\ppref_j$ and an alternative $b$ among those incomparable with $a$ in $\ppref_j$.
 
@@
 	%The motivation for using this operator lies in 
-	In other words if the maximal {\em a posteriori} MMR of two questions are (nearly) equal, then it considers the (penalized) minimal MMR values, preferring the question with the lowest value.
+	In other words if the maximal {\em a posteriori} MMR of two questions are (approximately) equal, then it considers the (penalized) minimal MMR values.
+%, preferring the question with the lowest value.
 	%(Technically, instead of applying a pure lexicographic aggregation, which is very sensitive to small errors due to floating-point computations, we apply a weighted sum between the maximal and the penalized minimal MMR values, with a predominant weight given to the maximal one, several order of magnitudes higher than the weight given to the penalized minimal MMR.)
@@
 Given a problem size $(m, n)$, a number of questions $k$ and a strategy to test, we first create an “oracle”, representing the true preferences of the agents (randomly generated or coming from real data) and the weights associated with the chair’s scoring rule (randomly generated).
-We start with empty knowledge ($\pprofile = \emptyset, W = \W$) about the preference orderings of the agents and the weight differences favored by the chair.
+We start with empty knowledge ($\pprofile = \emptyset, W = \W$) about the preference orderings of the agents and the weights %differences favored by
+of the chair.
 We obtain the first question to be asked using the strategy under test.
@@
 For instance, for $m =10$, $n = 20$ and $400$ questions, Random strategy reaches an average regret (over 10 runs) of $12$ (±$ 0.7$) and Pessimistic $0.6$ (±$ 0.5$).
-We also see that Pessimistic performs slightly better than Extended pessimistic, showing that Pessimistic chooses candidate questions wisely; this is good news since Pessimistic is much faster: it takes on average only $16$s for a complete elicitation session (for $m = 5$, $n = 10$ and $100$ questions), while Extended pessimistic takes $50$s.
+We notice that Pessimistic performs slightly better than Extended pessimistic, showing that Pessimistic chooses candidate questions wisely; this is good news since Pessimistic is much faster: it takes on average only $16$s for a complete elicitation session (for $m = 5$, $n = 10$ and $100$ questions), while Extended pessimistic takes $50$s.
 Although their performance is close, Pessimistic performs systematically better in multiple runs of the experiment.

### 2021-01-20 minimax.tex
very minor

@@
 $\MaxR(x;\pprofile,W)$ is the result of an adversarial selection of the complete profile $\profile \in C(\pprofile)$ and of the scoring vector $\w \in W$ that jointly maximize the loss between $x$ and the true winner under $\profile$ and $\w$.
-Finally,  $\MMR(\pprofile,W) = \min_{x \in A} \MaxR(x;\pprofile,W)$ is the value of minimax regret under $\pprofile$ and $W$, obtained when recommending a minimax optimal alternative $x^*_{\pprofile, W} \in A^*_{\pprofile, W} = \argmin_{x \in A} \MaxR(x;\pprofile,W)$.
+Finally,  $\MMR(\pprofile,W) = \min_{x \in A} \MaxR(x;\pprofile,W)$ is the value of {\em minimax regret} under $\pprofile$ and $W$, obtained when recommending a {\em minimax optimal} alternative $x^*_{\pprofile, W} \in A^*_{\pprofile, W} = \argmin_{x \in A} \MaxR(x;\pprofile,W)$.
 Picking as consensus choice an alternative associated with minimax regret provides a recommendation that gives worst-case guarantees. 

### 2021-01-21 appendix.tex
last changes

@@
 
-\appendix
-\section{Appendix}
+\section*{Appendix}
 \label{sec:appendix}
@@
 \begin{proof*}[\cref{claim:rankPMR}]
-	The rank of $x$ is directly obtained from \cref{eq:complx}.
-The rank of $y$ is obtained by complementing \cref{eq:comply}, obtaining $a \prefeq_j y ⇔ (a \pprefeq_j y) ∨ ((x \pprefeq_j y) ∧ ¬(x \pprefeq_j a))$, and, observing that $a \pref_j y ⇔ a ≠ y ∧ a \prefeq_j y$, obtaining that $a \pref_j y$ if and only if
+	The rank of $x$ is directly obtained from Eq.(\ref{eq:complx}).
+The rank of $y$ is obtained by complementing Eq.(\ref{eq:comply}), obtaining $a \prefeq_j y ⇔ (a \pprefeq_j y) ∨ ((x \pprefeq_j y) ∧ ¬(x \pprefeq_j a))$, and, observing that $a \pref_j y ⇔ a ≠ y ∧ a \prefeq_j y$, obtaining that $a \pref_j y$ if and only if
 	\begin{equation}

### 2021-01-21 minimax.tex
last changes

@@
 
-The following propositions (with proofs in appendix) show that the procedure for completing a partial profile,  proposed by \citet{Lu2011} when considering a fixed weight vector, also applies in our setting.
+The following propositions (with proofs in Appendix) show that the procedure for completing a partial profile,  proposed by \citet{Lu2011} when considering a fixed weight vector, also applies in our setting.
 We write $a \pprefeq_j b$ iff $a \ppref_j b \lor a = b$ and adopt the canonical notation when considering a relation as a function, writing ${\pprefeq_j}(x)$ for $\set{y \suchthat x \pprefeq_j y}$.
@@
 	There exists a completion $\hat{\profile} \in C(\pprofile)$ of the profile $\profile$ such that $\PMR(x,y; \pprofile, W) = \max_{\w \in W} [ s(y; \hat{\profile}, \w) - s(x; \hat{\profile}, \w) ]$ and such that the linear order $\hat{v}_{j}$ of each agent $j$ satisfies:
-	\begin{align} 
+	\begin{eqnarray}
 		\label{eq:complx}
-		a \pref_j x &⇔ ¬(x \pprefeq_j a)\\
+		a \pref_j x &⇔& \lnot(x \pprefeq_j a);\\
 		\label{eq:comply}
-		y \pref_j a &⇔ ¬(a \pprefeq_j y) ∧ ¬((x \pprefeq_j y) ∧ ¬(x \pprefeq_j a)).
-	\end{align} 
+		y \pref_j a &⇔& \lnot(a \pprefeq_j y) ∧ \lnot((x \pprefeq_j y) ∧ \lnot(x \pprefeq_j a)).
+	\end{eqnarray}
+%	\begin{align} 
+%		\label{eq:complx}
+%		a \pref_j x &⇔ ¬(x \pprefeq_j a)\\
+%		\label{eq:comply}
+%		y \pref_j a &⇔ ¬(a \pprefeq_j y) ∧ ¬((x \pprefeq_j y) ∧ ¬(x \pprefeq_j a)).
+%	\end{align} 
 \end{proposition}
@@
 	Both $a$ and $b$ have scores higher than $c$ and $d$ for all convex weights, thus either $a$ or $b$ will be picked under our hypothesis; and $s(a) ≥ s(b) ⇔ w_2 + 2 w_4 ≥ 3 w_3$.
-	(\cref{proof:chairQuestions} presents the general method of constructing such profile.)
+	(the proof in Appendix presents the general method of constructing such profile.)
 \end{example*}
@@
 Another interesting measure is the average number of questions asked to each participant before reaching zero regret.
-For example, in the case $m = 10, n = 20$, Pessimistic asks on average $49$ questions to the chair and $18$ questions to each agent (\cref{tab:questions} in \cref{sec:appendix} provides more data).
+For example, in the case $m = 10, n = 20$, Pessimistic asks on average $49$ questions to the chair and $18$ questions to each agent (\cref{tab:questions} in Appendix provides more data).
 
@@
 
-			\addlegendimage{mark=triangle*,teal,mark size=2}
 %			\addlegendimage{mark=*,violet,mark size=2}
-			\addlegendimage{mark=square*,green,mark size=2}
+			\addlegendimage{mark=halfsquare right*,brown,mark size=2}
 			\addlegendimage{mark=diamond*,red,mark size=2}
@@
 			\addlegendimage{mark=*,pink,mark size=2}
+			\addlegendimage{mark=triangle*,green,mark size=2}
 			\addlegendimage{mark=halfsquare left*,blue,mark size=2}
-			\addlegendimage{mark=halfsquare right*,brown,mark size=2}
+			\addlegendimage{mark=square*,teal,mark size=2}
 			\addlegendimage{mark=halfsquare*,magenta,mark size=2}
 
-			\addplot[thick, mark=triangle*, mark size = {2}, mark indices = {35}, teal] table [x=k, y=5.10]{data/normalizedLin.dat};
-			\addlegendentry{m=5, n=10}
+%			\addplot[thick, mark=triangle*, mark size = {2}, mark indices = {35}, teal] table [x=k, y=5.10]{data/normalizedLin.dat};
+%			\addlegendentry{m=5, n=10}
 %			\addplot[thick, mark=*, mark size = {2}, mark indices = {45}, violet] table [x=k, y=5.15]{data/normalizedLin.dat};
 %			\addlegendentry{m=5, n=15}
-			\addplot[thick, mark=square*, mark size = {2}, mark indices = {90}, green] table [x=k, y=5.20]{data/normalizedLin.dat};
+			\addplot[thick, mark=halfsquare right*, mark size = {2}, mark indices = {120}, brown] table [x=k, y=5.20]{data/normalizedLin.dat};
 			\addlegendentry{m=5, n=20}
@@
 			\addlegendentry{m=10, n=20}
-			\addplot[thick, mark=pentagon*, mark size = {2}, mark indices = {300}, cyan] table [x=k, y=10.30]{data/normalizedLin.dat};
-			\addlegendentry{m=10, n=30}
+%			\addplot[thick, mark=pentagon*, mark size = {2}, mark indices = {300}, cyan] table [x=k, y=10.30]{data/normalizedLin.dat};
+%			\addlegendentry{m=10, n=30}
+			\addplot[thick, mark=pentagon*, mark size = {2}, mark indices = {240}, cyan] table [x=k, y=11.30]{data/normalizedLin.dat};
+			\addlegendentry{m=11, n=30}
 			\addplot[thick, mark=halfcircle*, mark size = {2}, mark indices = {400}, violet] table [x=k, y=tshirt]{data/normalizedLin.dat};
@@
 			\addlegendentry{courses m9n146}
+			\addplot[thick, mark=triangle*, mark size = {2}, mark indices = {400}, green] table [x=k, y=9.146]{data/normalizedLin.dat};
+			\addlegendentry{m=9, n=146}
 			\addplot[thick, mark=halfsquare left*, mark size = {2}, mark indices = {200}, blue] table [x=k, y=14.9]{data/normalizedLin.dat};
 			\addlegendentry{m=14, n=9}
-			\addplot[thick, mark=halfsquare right*, mark size = {2}, mark indices = {60}, brown] table [x=k, y=skate]{data/normalizedLin.dat};
+			\addplot[thick, mark=square*, mark size = {2}, mark indices = {60}, teal] table [x=k, y=skate]{data/normalizedLin.dat};
 			\addlegendentry{skate m14n9}
@@
 
-The experiments so far let the strategy target its questions unrestrictively, leaving open the possibility of questioning either the chair or an agent at each step.
+The experiments so far let the strategy free to question either the chair or an agent at each step.
 One may wonder what is lost in terms of regret by asking different proportions of questions to the chair and the agents.
@@
 These numbers are to be compared with the MMR value reached after 400 questions with the Pessimistic strategy (displayed in \cref{fig:linearity}), which is $0.6$; the Pessimistic strategy asks on average $48$ questions to the chair in this setting.
-These numbers highlight that it is possible to obtain a good-quality recommendation while knowing only that the voting rule is a scoring rule and that the weights are convex, which is our basic hypothesis (corresponding to the line $q_c = 0$, where no question is asked to the chair).
+The line $q_c = 0$, where no question is asked to the chair, suggest that it is possible to obtain a good-quality recommendation while knowing only that the voting rule is a scoring rule with convex weights, which is our basic hypothesis.
+However, we observe that asking no questions to the chair does not permits to reach $\MMR\!=\!0$.
+The strategy, indeed, obtains full knowledge of the profile after an average of 500 questions to the voters but never reaches zero.
 
@@
 \label{sec:conclusions}
-In this paper we have considered a social choice setting with partial information about the agent preferences and a partially specified voting rule.
-In this setting, we have proposed the use of minimax regret both as a means of robust winner determination as well as a guide to the process of simultaneous elicitation of preferences and voting rule.
+In this paper we have considered a social choice setting with partial information about the agent preferences and voting rule.
+We have proposed the use of minimax regret both as a means of robust winner determination and as a guide to the process of simultaneous elicitation of preferences and voting rule.
 Our experimental results %on randomly generated and real world datasets 
 suggest that regret-based elicitation is effective and allows to quickly reduce worst-case regret significantly.
-They also show that, in our setting, good quality (low regret) recommendations can be achieved short of knowing the weights precisely or the profile completely.
+They also show that, in our setting, good quality (low regret) recommendations can be achieved short of having full knowledge of weights or profile.
 %regret, but they also show that starting with zero knowledge became a pretentious approach really quickly when increasing the size of the problem.
@@
 
-As part of our contribution, a general open-source library, allowing to reproduce our experiments and perform many more, will be made publicly available. (URL not displayed for ensuring anonymity.)
+As part of our contribution, an open-source library, to reproduce our experiments and perform many more, will be made publicly available. (URL not displayed for anonymity.)
 %and serve as a basis for further research
 
+Some directions for future works include developing new elicitation strategies, considering alternative heuristics; extending the elicitation to voting rules beyond scoring rules; eliciting preferences while restraining to concrete and easy questions.
+
 %We mention some directions for future works.
-Further development of elicitation strategies, considering alternative heuristics, is an important direction. 
-Second, elicitation could be extended to voting rules beyond scoring rules. 
-Finally, an important direction of research  aims at eliciting preferences while restraining to concrete and easy questions.
+%Further development of elicitation strategies, considering alternative heuristics, is an important direction. 
+%Second, elicitation could be extended to voting rules beyond scoring rules. 
+%Finally, an important direction of research  aims at eliciting preferences while restraining to concrete and easy questions.
 % Acknowledgments: We thank the reviewers for comments helping to improve the paper.

### 2021-01-21 minimax.tex
last last changes

@@
 
-The candidate questions to the agents are chosen by extending the idea of \citet{Lu2011}, that priviledge learning about the relationship of $x^*$ and $\bar{y}$ to the other alternatives if possible.
+The candidate questions to the agents are chosen by extending the idea of \citet{Lu2011}, that privilege learning about the relationship of $x^*$ and $\bar{y}$ to the other alternatives if possible.
 	Given $j \in N^*$, if $x^*$ and $\bar{y}$ are incomparable in $\ppref_j$, the candidate question concerns the pair $(x^*, \bar{y})$, otherwise, %the candidate question
@@
 For the real preferences, we used three datasets from \href{https://www.preflib.org/}{PrefLib} \citep{PrefLib}: \textit{T Shirt} (researchers voted on tee shirt designs; $m \!=\! 11, n \!=\! 30$),
-\textit{Courses}  (students voted on courses; $m \!=\! 9, n \!=\! 146$)
+\textit{Courses}  (students voted on courses; $m \!=\! 9, n \!=\! 146$; referred to as AGH on PrefLib)
 and \emph{Skate} (judges vote on skaters at the Euros Pairs Short Program; $m \!=\! 14, n \!=\! 9$).
@@
 Our next set of experiments evaluate the Pessimistic strategy in absolute terms. 
-We first wonder how many questions should be asked in order to reach a low regret level, fixed at $n / 10$: such a regret is equivalent to the difference of score of an alternative $x$ that results from switching from a profile $P$ to a profile $P'$ where ten percent of the agents rank $x$ last instead of first.
-The results for various sizes are displayed in \cref{tab:lowRegret}. 
+We first wonder how many questions should be asked in order to achieve low regret, fixed at $n / 10$: this is equivalent to the difference of score of an alternative $x$ that results from switching from a profile $P$ to a profile $P'$ where a tenth of the agents rank $x$ last instead of first.
+\cref{tab:lowRegret} shows results for various sizes. 
+%The results for various sizes are displayed in \cref{tab:lowRegret}. 
 Another interesting measure is the average number of questions asked to each participant before reaching zero regret.
@@
 
-\Cref{fig:linearity} shows graphically the decrease in MMR according to the number of questions asked for various problem sizes.
-In particular, this shows important differences between some real data sets and the problems generated using IC.
+\Cref{fig:linearity} shows the decrease in MMR according to the number of questions asked for various problem sizes.
+In particular, this shows important differences between some real datasets and the problems generated using IC.
 In the \textit{Skate} problem, the value $\MMR\!=\!1$ is reached after less than $100$ questions, while the IC case of the same size ($m = 14, n = 9$) requires more than $200$ questions to reach that value.
-But comparing \textit{T Shirt} with similar IC cases do not reveal any important differences in terms of decrease of regret.
-This can be explained by the high degree of similarity in the preference rankings of the \textit{Skate} problem, which helps reducing the regret faster: in that dataset the top-2 alternatives are the same for all agents, and 8 out of 9 agents rank the same alternative at position 3.
+This reasoning also applies to the \textit{Courses} dataset but not to the \textit{T Shirt} dataset.
+This can be explained by the high degree of similarity in the preference rankings of the \textit{Skate} and the \textit{Courses} problems, which helps reducing the regret faster.
+For example, in \textit{Skate} the top-2 alternatives are the same for all agents, and 8 out of 9 agents rank the same alternative at position 3.
 By contrast, in \textit{T Shirt}, the alternatives are evenly distributed in the preference rankings.
@@
 The line $q_c = 0$, where no question is asked to the chair, suggest that it is possible to obtain a good-quality recommendation while knowing only that the voting rule is a scoring rule with convex weights, which is our basic hypothesis.
-However, we observe that asking no questions to the chair does not permits to reach $\MMR\!=\!0$.
+However, we observe that asking no questions to the chair does not permit to reach $\MMR\!=\!0$.
 The strategy, indeed, obtains full knowledge of the profile after an average of 500 questions to the voters but never reaches zero.

### 2021-03-26 rebuttal/ijcai21-authors-response.tex
draft from drive

% IJCAI-21 Author's response

% Template file with author's reponse

\documentclass{article}
\pdfpagewidth=8.5in
\pdfpageheight=11in
\usepackage{ijcai21-authors-response}

\usepackage{times}
\usepackage{soul}
\usepackage{url}
\usepackage[hidelinks]{hyperref}
\usepackage[utf8]{inputenc}
\usepackage[small]{caption}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{booktabs}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{lipsum}
\urlstyle{same}

\newtheorem{example}{Example}
\newtheorem{theorem}{Theorem}

\begin{document}
\paragraph{Rebuttal to Reviewer $\#$2: factual error}
One of the weaknesses of the paper is indeed the fact that the method proposed here is not compared with others, neither in terms of computational efficiency, nor in terms of quality of the result. Only variants of the same methods are compared with each others

We believe it is erroneous to consider the lack of comparison a weakness. The simultaneous elicitation of both the voting rule and the agents preferences is a novel setting. To the best of our knowledge, there is no clear competitor from the state-of-the-art to compare with. However, please note that we designed all the strategies to challenge one another; in particular:
The Elitist Strategy has a very different approach than the Pessimistic Strategy to the point that it cannot be considered a variant. We compared these two strategies in a situation specifically tailored to advantage the Elitist Strategy.
The Experiment involving the Two Phases Strategy was designed to challenge our interleaving approach by comparing it with a more classical linear method: first elicit the rule and then the agent’s preferences or vice versa. The former coincides with the case of preferences elicitation, given the voting rule, investigated by Lu and Boutilier [2011].
We are not aware of any work that elicits the voting rule we could compare with —the work by Cailloux and Endriss [2014] does not consider scoring rules.

R2: “If an election is to be achieved, the voting rule has to be defined independently of the preferences of the voters. And probably not by the chairperson who may influence the result by choosing the weights.”
It is not true that any decision process involving preference aggregation requires a voting rule defined beforehand, nor that it is necessarily a bad idea to let a chair decide on the voting rule or influence the voting rule definition. The interest of considering incomplete knowledge in the voting rule has been advocated in a recent survey paper of a leading researchers in computational social choice [Lang 2020; section 2.5]. Jerôme’s paper also says that. HAH. The case of IJCAI aggregation process of reviews illustrates the point. The Introduction section of our article provides another example.

[Lang 2020] Jérôme Lang: Collective Decision Making under Incomplete Knowledge: Possible and Necessary Solutions. IJCAI 2020: 4885-4891

\paragraph{Rebuttal to Reviewer $\#$32: specific questions}
[If we have space we add that although the reviewer didn’t use the proper section, the questions were in the form provided in the FAQ “When to answer?”]

-Why would voters participate in a voting rule that is not public or common knowledge?
-I struggle to understand why a "third party elicits both votes and chair" setting might arise in practice. Can the authors give an example?
-Why is this easier than reflecting on the relative weights?
-If the chair can compute winners over and over for every elicitation for arbitrary size profiles, why wouldn't the chair just compute the real winner himself or herself, rather the delegate to the third party?

Other than the example we provided in the Introduction —that describes the hiring process of a new employee— we could consider the reviewing process of a conference where the best paper must be elected. This new example also responds to the concern regarding the lack of knowledge of the voting rule among the agents. In this context, the agents express their preferences on the papers they reviewed, but they are not aware of the voting rule the SPC member will apply when aggregating all the preferences. Nonetheless, reviewers are still willing to participate in the process. On the other hand, the SPC member may not have a specific voting rule in mind, and she will find it hard to provide a precise scoring vector if asked. This part addresses the argument on the relative weights. Imagine, for the sake of the example, that all the reviewers review all the papers and they rank them according to their preferences. How does the SPC select the best paper? Surely she could adopt the Borda count and pick the paper with the highest score, but this is not the most appealing method. Maybe the SPC strongly believes that being ranked once in the first position is “much more” valuable than being ranked two times second, but does not know exactly how much more (though she can judge example cases). This is similar to how the paper WeBuildAI (and the general literature in micro-economy) supposes that participants are able to compare pairs of matches, but does not assume that participants can explicit their utility functions. Specifying general algorithms is demanding, hence, we adapt a mechanism used in a real life experiment by Giritligil et al. [2005] in a novel way for the setting of elicitation of positioning scoring rules (PSRs).

There is also an important methodological argument for being able to phrase questions in terms of winners out of profiles. This is arguably the most fundamental and natural view of what a social choice function is: it chooses winners out of profiles. The rest, such as talking in terms of weights, is a synthetic, constructed, view about how a social choice function works. Different such constructions could lead to different appreciations and judgements by participants. For example, PSRs can also be described in terms of distance to ideal profiles ( On the role of distances in defining voting rules, E Elkind, P Faliszewski, AM Slinko, AAMAS 2010). There is no a priori reason to believe that questioning the chair in terms of this different parametric space would yield logically equivalent answers: research in experimental psychology shows that participants’ answers differ widely when changing the phrasing of preference-related questions (Lichtenstein, Slovic - The Construction of Preference, Cambridge University Press, 2006). To get out of such conundrums, we need a language considered “fundamental”. Questions of the form “In this profile, who should win?” arguably provides such a natural language.

Finally, the chair could delegate to a third party, by agreeing to let the principle of “min-max regret” decide instead of picking her favorite winner, for example, because the chair wants to satisfy a form of fairness which she thinks that algorithm satisfies. This is a classical assumption in political science. Note that the chair cannot compute the real winner as she ignores the profile.

-Is Figure 1 for the synthetic data? Please specify. Same question for Tables 2 and 3. In Figure 2, are the m=N,n=N lines the synthetic data?
-Why is Figure 2 shown for only Pessimistic, not all the approaches? Were all approaches tested on all data sets? Or were all approaches only tested on synthetic data?

Yes, when we do not specify the name of the dataset we mean data generated following the procedure described in Sec 5. Regarding the real datasets, we only tested the Pessimistic strategy for the following reasons:
Random was considered only as a baseline in the first experiment, which shows that Pessimistic performs much better; therefore we did not consider Random any further. 
Extended Pessimistic is computationally too consuming and it can be tested only on small instances; as explained in “Sec 4 - Elicitation strategies”; 
Elitist was designed with the only purpose of challenging our best strategy (Pessimistic) in extreme cases tailored to favor the Elitist. Testing this strategy in other settings does not yield interesting information;
Two Phase was designed to compare our interleaving approach to a more classical linear method: first elicit the rule and then the agents preferences or vice versa. We thought that the most challenging situation (Impartial Culture) was the best way to perform this test.

\paragraph{Rebuttal to Reviewer $\#$56: specific questions}

They seem to have a linear constraint question in mind which they then convert to a “what is the winner of this profile?” question. However I think the opposite may be more plausible. Having a profile for which you want to know the winner and then deduce the constraint.
-Can you clarify better the rationale behind the assumptions you make on questions to the chair?

PAOLO DRAFT: Indeed the question is asked by showing a profile and asking who should win; the response is encoded as a constraint and added to the system’s knowledge. Note that we want to ask an informative query: the elicitation strategy decides which question to be asked, and, if it is of the “chair” type, the strategy decides the linear constraint to check; this is then translated to a profile.

The usefulness in practice is not really clear. If the chair does not know the weight vector, he can’t answer the questions.
-You say that you assume the chair to be human, yet you think he will answer hundreds of questions..? Could you elaborate more on why you think this is reasonable?
Maybe the chair could be instead a black box PSR that let’s you test it for different outcomes…

PAOLO DRAFT: We assume the chair to be human and, as discussed in the paragraph “Building concrete questions for the chair“ on page 3, we view questions “what is the winner of this profile” to be easier to answer than directly asking the weights (in the same way as, for the problem of elicitation an utility function, one would ask comparison queries rather than asking directly utility values). 
Note that, in our experiments, we often plot the total number of questions in order to have a simple way to compare the total elicitation cost. But it is important to note,  queries are posed to different agents and to the chair, and that the number of questions each has to answer is usually not that big. In fact the number of questions asked to the chair using the Pessimistic strategy (as shown in the appendix) is often quite small  (e.g. zero in skate and "courses", 8.4 in m5n10, 13 in m5n20, 30 in tshirt,...), this is because the strategy does a good job of asking the question that gives more information, and often only “sparse” information about the voting rule is enough. Similarly, the average number of questions asked to a voter is also reasonable (e.g questions per agent 6.5 in courses, 6.1 in m5n10,  )
: X.X in Experiment YY, for instance. In Table 2, the (10,20) example shows that to reach a “low” regret -that we define as n/10- we need to ask 340 questions. This number should be divided among the voters and the chair, resulting in ~ 10 questions per voter, which we consider a reasonable amount. The fact that asking too many questions to the chair is not worth it isworth is also displayed in Table 3 in the main text.
Finally, note that the process could be terminated early: e.g. one could decide to stop after a fixed number of questions (even if regret is not zero) and to output as an “approximate winner” the alternative with lowest minimax regret value.
If the paper is accepted, we’ll stress the points above and include in the final version the Table with $\#$questions from the appendix.

\end{document}

### 2021-03-26 rebuttal/ijcai21-authors-response.tex
first changes

@@
 \paragraph{Rebuttal to Reviewer $\#$2: factual error}
-One of the weaknesses of the paper is indeed the fact that the method proposed here is not compared with others, neither in terms of computational efficiency, nor in terms of quality of the result.
-Only variants of the same methods are compared with each others
-
+\begin{itemize}
+	\item \textit{One of the weaknesses is that the method proposed is not compared with others.}
+\end{itemize}
 We believe it is erroneous to consider the lack of comparison a weakness.
@@
 To the best of our knowledge, there is no clear competitor from the state-of-the-art to compare with.
-However, please note that we designed all the strategies to challenge one another; in particular:
+However, please note that we designed all the strategies to challenge one another.
 The Elitist Strategy has a very different approach than the Pessimistic Strategy to the point that it cannot be considered a variant.
 We compared these two strategies in a situation specifically tailored to advantage the Elitist Strategy.
-The Experiment involving the Two Phases Strategy was designed to challenge our interleaving approach by comparing it with a more classical linear method: first elicit the rule and then the agent’s preferences or vice versa.
+The experiment involving the Two Phases Strategy was designed to challenge our interleaving approach by comparing it with a more classical linear method: first elicit the rule and then the agent’s preferences or vice versa.
 The former coincides with the case of preferences elicitation, given the voting rule, investigated by Lu and Boutilier [2011].
 We are not aware of any work that elicits the voting rule we could compare with —the work by Cailloux and Endriss [2014] does not consider scoring rules.
-
-R2: “If an election is to be achieved, the voting rule has to be defined independently of the preferences of the voters.
-And probably not by the chairperson who may influence the result by choosing the weights.”
-It is not true that any decision process involving preference aggregation requires a voting rule defined beforehand, nor that it is necessarily a bad idea to let a chair decide on the voting rule or influence the voting rule definition.
-The interest of considering incomplete knowledge in the voting rule has been advocated in a recent survey paper of a leading researchers in computational social choice [Lang 2020; section 2.5].
-Jerôme’s paper also says that.
-HAH.
+\begin{itemize}
+	\item \textit{The voting rule has to be defined independently of the voters preferences and not by the chairperson.}
+\end{itemize}
+It is not true that any decision process involving preference aggregation requires a voting rule defined beforehand, nor that it is necessarily a bad idea to let a chair decide on the voting rule.
+The interest of considering incomplete knowledge in the voting rule has been advocated in a recent survey paper of a leading researchers in Computational Social Choice [Lang 2020 \url{https://doi.org/10.24963/ijcai.2020/680}; section 2.5].
 The case of IJCAI aggregation process of reviews illustrates the point.
@@
 
-[Lang 2020] Jérôme Lang: Collective Decision Making under Incomplete Knowledge: Possible and Necessary Solutions. IJCAI 2020: 4885-4891
-
 \paragraph{Rebuttal to Reviewer $\#$32: specific questions}
-[If we have space we add that although the reviewer didn’t use the proper section, the questions were in the form provided in the FAQ “When to answer?”]
-
--Why would voters participate in a voting rule that is not public or common knowledge?
--I struggle to understand why a "third party elicits both votes and chair" setting might arise in practice. Can the authors give an example?
--Why is this easier than reflecting on the relative weights?
--If the chair can compute winners over and over for every elicitation for arbitrary size profiles, why wouldn't the chair just compute the real winner himself or herself, rather the delegate to the third party?
-
+[Although not in the proper section, the reviewer formulated the following questions in the format described by the FAQ “When to answer?”.]
+\begin{itemize}
+	\item \textit{I struggle to understand when the setting may occur in practice.
+Can the authors give an example?
+Why would voters participate in a voting rule that is not public or common knowledge?
+Why wouldn't the chair just compute the winner herself?}
+\end{itemize}
 Other than the example we provided in the Introduction —that describes the hiring process of a new employee— we could consider the reviewing process of a conference where the best paper must be elected.

### 2021-03-28 rebuttal/ijcai21-authors-response.tex
rebuttal one page

@@
 \begin{document}
-\paragraph{Rebuttal to Reviewer $\#$2: factual error}
-\begin{itemize}
-	\item \textit{One of the weaknesses is that the method proposed is not compared with others.}
-\end{itemize}
+	We thank the reviewers for their comments. We specify that the questions reported are not verbatim for lack of space. 
+\paragraph{Rebuttal to Reviewer $\#$2: factual error}.\\
+\textit{\textbf{One of the weaknesses is that the method proposed is not compared with others.}}
+
 We believe it is erroneous to consider the lack of comparison a weakness.
-The simultaneous elicitation of both the voting rule and the agents preferences is a novel setting.
-To the best of our knowledge, there is no clear competitor from the state-of-the-art to compare with.
+The simultaneous elicitation of both the voting rule and the agents preferences is a novel setting and, as far as we know, there is no clear competitor from the state-of-the-art to compare with.
 However, please note that we designed all the strategies to challenge one another.
-The Elitist Strategy has a very different approach than the Pessimistic Strategy to the point that it cannot be considered a variant.
-We compared these two strategies in a situation specifically tailored to advantage the Elitist Strategy.
-The experiment involving the Two Phases Strategy was designed to challenge our interleaving approach by comparing it with a more classical linear method: first elicit the rule and then the agent’s preferences or vice versa.
-The former coincides with the case of preferences elicitation, given the voting rule, investigated by Lu and Boutilier [2011].
-We are not aware of any work that elicits the voting rule we could compare with —the work by Cailloux and Endriss [2014] does not consider scoring rules.
-\begin{itemize}
-	\item \textit{The voting rule has to be defined independently of the voters preferences and not by the chairperson.}
-\end{itemize}
+$1)$ The Elitist has a very different approach than the Pessimistic to the point that it cannot be considered a variant.
+We compared these two strategies in a situation specifically tailored to advantage the Elitist.
+$2)$ The Two Phases was designed to challenge our interleaving approach by comparing it with a more classical linear method: first elicit the rule and then the agents preferences or vice versa.
+The former coincides with the method of Lu and Boutilier [2011] for preferences elicitation fixed the voting rule.
+We are not aware of any method that elicits the voting rule we could compare with —the work by Cailloux and Endriss [2014] does not consider PSRs.
+
+\textit{\textbf{The voting rule has to be defined independently of the voters preferences and not by the chairperson.}}
+
 It is not true that any decision process involving preference aggregation requires a voting rule defined beforehand, nor that it is necessarily a bad idea to let a chair decide on the voting rule.
-The interest of considering incomplete knowledge in the voting rule has been advocated in a recent survey paper of a leading researchers in Computational Social Choice [Lang 2020 \url{https://doi.org/10.24963/ijcai.2020/680}; section 2.5].
-The case of IJCAI aggregation process of reviews illustrates the point.
+The interest of considering incomplete knowledge in the voting rule has been advocated in a recent survey paper of a leading researcher in Computational Social Choice [Lang 2020, \url{https://doi.org/10.24963/ijcai.2020/680}].
+The case of IJCAI aggregation process of reviews illustrates the point: reviewers provide their preferences despite ignoring how these will be aggregated.
 The Introduction section of our article provides another example.
@@
 \paragraph{Rebuttal to Reviewer $\#$32: specific questions}
-[Although not in the proper section, the reviewer formulated the following questions in the format described by the FAQ “When to answer?”.]
-\begin{itemize}
-	\item \textit{I struggle to understand when the setting may occur in practice.
-Can the authors give an example?
-Why would voters participate in a voting rule that is not public or common knowledge?
-Why wouldn't the chair just compute the winner herself?}
-\end{itemize}
-Other than the example we provided in the Introduction —that describes the hiring process of a new employee— we could consider the reviewing process of a conference where the best paper must be elected.
-This new example also responds to the concern regarding the lack of knowledge of the voting rule among the agents.
-In this context, the agents express their preferences on the papers they reviewed, but they are not aware of the voting rule the SPC member will apply when aggregating all the preferences.
-Nonetheless, reviewers are still willing to participate in the process.
-On the other hand, the SPC member may not have a specific voting rule in mind, and she will find it hard to provide a precise scoring vector if asked.
-This part addresses the argument on the relative weights.
+.[Although not in the proper section, the reviewer formulated questions in the format described by the FAQ on when to answer.]
+
+\textit{\textbf{Can the authors give an example of when the setting may occur in practice?
+Why would voters participate without knowing the voting rule?
+Why selecting winners is easier than reflecting on weights or computing the winner herself?}}
+
+Other than the example we provided in the Introduction, we could consider the reviewing process of a conference where the best paper must be elected.
+In this context, the agents express their preferences on the papers they reviewed, but they are not aware of the voting rule the SPC member will apply when aggregating them.
+%Nonetheless, reviewers are still willing to participate in the process.
+Also, the SPC member may not have a specific voting rule in mind, and she will find it hard to provide a precise scoring vector if asked.
 Imagine, for the sake of the example, that all the reviewers review all the papers and they rank them according to their preferences.
-How does the SPC select the best paper?
-Surely she could adopt the Borda count and pick the paper with the highest score, but this is not the most appealing method.
-Maybe the SPC strongly believes that being ranked once in the first position is “much more” valuable than being ranked two times second, but does not know exactly how much more (though she can judge example cases).
+The SPC member could adopt the Borda count and pick the paper with the highest score, but this is not the most appealing method.
+Maybe she strongly believes that being ranked once in the first position is “much more” valuable than being ranked two times second, but does not know exactly how much more (though she can judge example cases).
 This is similar to how the paper WeBuildAI (and the general literature in micro-economy) supposes that participants are able to compare pairs of matches, but does not assume that participants can explicit their utility functions.
-Specifying general algorithms is demanding, hence, we adapt a mechanism used in a real life experiment by Giritligil et al.
+Methodologically, phrase questions in terms of winners out of profiles is arguably the most fundamental and natural view of what a social choice function is.
+The rest, such as talking in terms of weights, is a synthetic, constructed, view that could lead to different appreciations and judgments by participants.
+%For example, PSRs can also be described in terms of distance to ideal profiles ( On the role of distances in defining voting rules, E Elkind, P Faliszewski, AM Slinko, AAMAS 2010). 
+%There is no a priori reason to believe that questioning the chair in terms of this different parametric space would yield logically equivalent answers: 
+A research in experimental psychology shows that participants’ answers differ widely when changing the phrasing of preference-related questions [Lichtensteina, Slovic, 2012, \url{https://doi.org/10.1017/CBO9780511618031}].
+%(Lichtenstein, Slovic - The Construction of Preference, Cambridge University Press, 2006). 
+To get out of such conundrums, we need a language considered “fundamental”. Questions of the form “In this profile, who should win?” arguably provides such a natural language.
+%Specifying general algorithms is demanding, hence, we adapt a mechanism used in a real life experiment by Giritligil et al.
 [2005] in a novel way for the setting of elicitation of positioning scoring rules (PSRs).
 
-There is also an important methodological argument for being able to phrase questions in terms of winners out of profiles.
-This is arguably the most fundamental and natural view of what a social choice function is: it chooses winners out of profiles.
-The rest, such as talking in terms of weights, is a synthetic, constructed, view about how a social choice function works.
-Different such constructions could lead to different appreciations and judgements by participants.
-For example, PSRs can also be described in terms of distance to ideal profiles ( On the role of distances in defining voting rules, E Elkind, P Faliszewski, AM Slinko, AAMAS 2010).
-There is no a priori reason to believe that questioning the chair in terms of this different parametric space would yield logically equivalent answers: research in experimental psychology shows that participants’ answers differ widely when changing the phrasing of preference-related questions (Lichtenstein, Slovic - The Construction of Preference, Cambridge University Press, 2006).
-To get out of such conundrums, we need a language considered “fundamental”.
-Questions of the form “In this profile, who should win?” arguably provides such a natural language.
+%Finally, the chair could delegate to a third party, by agreeing to let the principle of “min-max regret” decide instead of picking her favorite winner, for example, because the chair wants to satisfy a form of fairness which she thinks that algorithm satisfies.
+This is a classical assumption in political science.
+%Note that the chair cannot compute the real winner as she ignores the profile.
 
-Finally, the chair could delegate to a third party, by agreeing to let the principle of “min-max regret” decide instead of picking her favorite winner, for example, because the chair wants to satisfy a form of fairness which she thinks that algorithm satisfies.
-This is a classical assumption in political science.
-Note that the chair cannot compute the real winner as she ignores the profile.
+\textit{\textbf{Is Figure 1 for the synthetic data? Please specify. Why is Figure 2 shown for only Pessimistic, not all the approaches?}}
 
--Is Figure 1 for the synthetic data? Please specify. Same question for Tables 2 and 3. In Figure 2, are the m=N,n=N lines the synthetic data?
--Why is Figure 2 shown for only Pessimistic, not all the approaches? Were all approaches tested on all data sets? Or were all approaches only tested on synthetic data?
+%-Is Figure 1 for the synthetic data? Please specify. Same question for Tables 2 and 3. In Figure 2, are the m=N,n=N lines the synthetic data?
+%-Why is Figure 2 shown for only Pessimistic, not all the approaches? Were all approaches tested on all data sets? Or were all approaches only tested on synthetic data?
+Yes, when we do not specify the name of the dataset we mean data generated following the procedure described in Sec 5.
+Regarding the real datasets, we only tested the Pessimistic strategy for the following reasons: $1)$ Random was considered only as a baseline in the first experiment, which shows that Pessimistic performs much better; $2)$ Extended Pessimistic is computationally too consuming and it can be tested only on small instances (as pointed out in Sec 4); $3)$ Elitist was designed with the only purpose of challenging our best strategy (Pessimistic) in extreme cases tailored to favor the former.
+Testing this strategy in other settings does not yield interesting information; $4)$ Two Phase was designed to compare our interleaving approach to a more classical linear method.
+We thought that the most challenging situation (Impartial Culture) was the best setting to perform this test.
 
-Yes, when we do not specify the name of the dataset we mean data generated following the procedure described in Sec 5.
-Regarding the real datasets, we only tested the Pessimistic strategy for the following reasons:
-Random was considered only as a baseline in the first experiment, which shows that Pessimistic performs much better; therefore we did not consider Random any further. 
-Extended Pessimistic is computationally too consuming and it can be tested only on small instances; as explained in “Sec 4 - Elicitation strategies”; 
-Elitist was designed with the only purpose of challenging our best strategy (Pessimistic) in extreme cases tailored to favor the Elitist.
-Testing this strategy in other settings does not yield interesting information;
-Two Phase was designed to compare our interleaving approach to a more classical linear method: first elicit the rule and then the agents preferences or vice versa.
-We thought that the most challenging situation (Impartial Culture) was the best way to perform this test.
+\paragraph{Rebuttal to Reviewer $\#$56: specific questions}.\\
+\textit{\textbf{Can you clarify better the rationale behind the assumptions you make on questions to the chair?}}
 
-\paragraph{Rebuttal to Reviewer $\#$56: specific questions}
+The question is asked by showing a profile and asking who should win; the response is encoded as a constraint and added to the system’s knowledge.
+Methodologically, phrase questions in terms of winners out of profiles is arguably the most fundamental and natural view of what a social choice function is (as pointed out in our response to reviewer $\#$32).
+We adapt a mechanism used in a real life experiment by Giritligil et al.
+[2005] in a novel way for the elicitation of PSRs.
+%Note that we want to ask an informative query: the elicitation strategy decides which question to be asked, and, if it is of the “chair” type, the strategy decides the linear constraint to check; this is then translated to a profile.
 
-They seem to have a linear constraint question in mind which they then convert to a “what is the winner of this profile?” question.
-However I think the opposite may be more plausible.
-Having a profile for which you want to know the winner and then deduce the constraint.
--Can you clarify better the rationale behind the assumptions you make on questions to the chair?
+\textit{\textbf{Could you elaborate on why you think is reasonable to assume the human chair will answer hundreds of questions?}}
 
-PAOLO DRAFT: Indeed the question is asked by showing a profile and asking who should win; the response is encoded as a constraint and added to the system’s knowledge.
-Note that we want to ask an informative query: the elicitation strategy decides which question to be asked, and, if it is of the “chair” type, the strategy decides the linear constraint to check; this is then translated to a profile.
-
-The usefulness in practice is not really clear. If the chair does not know the weight vector, he can’t answer the questions.
--You say that you assume the chair to be human, yet you think he will answer hundreds of questions..? Could you elaborate more on why you think this is reasonable?
-Maybe the chair could be instead a black box PSR that let’s you test it for different outcomes…
-
-PAOLO DRAFT: We assume the chair to be human and, as discussed in the paragraph “Building concrete questions for the chair“ on page 3, we view questions “what is the winner of this profile” to be easier to answer than directly asking the weights (in the same way as, for the problem of elicitation an utility function, one would ask comparison queries rather than asking directly utility values).
+%We assume the chair to be human and, as discussed in the paragraph “Building concrete questions for the chair“ on page 3, we view questions “what is the winner of this profile” to be easier to answer than directly asking the weights (in the same way as, for the problem of elicitation an utility function, one would ask comparison queries rather than asking directly utility values).
 Note that, in our experiments, we often plot the total number of questions in order to have a simple way to compare the total elicitation cost.
-But it is important to note,  queries are posed to different agents and to the chair, and that the number of questions each has to answer is usually not that big.
-In fact the number of questions asked to the chair using the Pessimistic strategy (as shown in the appendix) is often quite small  (e.g.
+Table 1 of Appendix shows that the number of questions posed to the chair (and each agent) is usually not that big.
+When the profile is quite homogeneous (see the lines corresponding to real datasets) this number is very low or even zero in case of clear winner.
+We also mention that the process could be terminated early: after a fixed number of questions (the “approximate winner” is the alternative with lowest regret); or after reaching a "low enough" regret.
+%In fact the number of questions asked to the chair using the Pessimistic strategy (as shown in the appendix) is often quite small  (e.g.
 zero in skate and "courses", 8.4 in m5n10, 13 in m5n20, 30 in tshirt,...), this is because the strategy does a good job of asking the question that gives more information, and often only “sparse” information about the voting rule is enough.
 Similarly, the average number of questions asked to a voter is also reasonable (e.g questions per agent 6.5 in courses, 6.1 in m5n10,  )
-: X.X in Experiment YY, for instance.
+%: X.X in Experiment YY, for instance.
 In Table 2, the (10,20) example shows that to reach a “low” regret -that we define as n/10- we need to ask 340 questions.
@@
 The fact that asking too many questions to the chair is not worth it isworth is also displayed in Table 3 in the main text.
-Finally, note that the process could be terminated early: e.g.
+%Finally, note that the process could be terminated early: e.g.
 one could decide to stop after a fixed number of questions (even if regret is not zero) and to output as an “approximate winner” the alternative with lowest minimax regret value.
-If the paper is accepted, we’ll stress the points above and include in the final version the Table with $\#$questions from the appendix.
+If the paper will be accepted, we will stress more this point and include the Appendix Table in the final version.
 

### 2021-03-28 rebuttal/ijcai21-authors-response.tex
Comments rebutt

@@
 
+\usepackage{color}
+
+\newcommand{\commentOC}[1]{\textcolor{blue}{\small$\big[$OC: #1$\big]$}}
+\newcommand{\commentBN}[1]{\textcolor{red}{\small$\big[$BN: #1$\big]$}}
+\newcommand{\commentPV}[1]{\textcolor{brown}{\small$\big[$PV: #1$\big]$}}
+
 \begin{document}
+%Working around the censorship.
+\addtocounter{pagecount}{-4}
+
 	We thank the reviewers for their comments. We specify that the questions reported are not verbatim for lack of space. 
@@
 
+\commentOC{I suggest to remove “factual error” and “specific questions” and rather directly go with the first question.}
 We believe it is erroneous to consider the lack of comparison a weakness.
@@
 This is similar to how the paper WeBuildAI (and the general literature in micro-economy) supposes that participants are able to compare pairs of matches, but does not assume that participants can explicit their utility functions.
-Methodologically, phrase questions in terms of winners out of profiles is arguably the most fundamental and natural view of what a social choice function is.
-The rest, such as talking in terms of weights, is a synthetic, constructed, view that could lead to different appreciations and judgments by participants.
-%For example, PSRs can also be described in terms of distance to ideal profiles ( On the role of distances in defining voting rules, E Elkind, P Faliszewski, AM Slinko, AAMAS 2010). 
+Methodologically speaking, phrasing questions in terms of winners out of profiles is arguably the most fundamental and natural view of what a social choice function is.
+Talking in terms of weights is a synthetic construction that could lead to different judgments by participants than other constructions.
+\commentOC{I find it important that the two next commented-out sentences be somehow included.}
+%For example, PSRs can also be described in terms of distance to ideal profiles ( On the role of distances in defining voting rules, Elkind et al., AAMAS 2010). 
 %There is no a priori reason to believe that questioning the chair in terms of this different parametric space would yield logically equivalent answers: 
-A research in experimental psychology shows that participants’ answers differ widely when changing the phrasing of preference-related questions [Lichtensteina, Slovic, 2012, \url{https://doi.org/10.1017/CBO9780511618031}].
+A research in experimental psychology shows that participants’ answers differ widely when changing the phrasing of preference-related questions [Lichtenstein \& Slovic, 2012, \href{https://doi.org/10.1017/CBO9780511618031}{doi: 10.1017/CBO9780511618031}].
 %(Lichtenstein, Slovic - The Construction of Preference, Cambridge University Press, 2006). 
@@
 Yes, when we do not specify the name of the dataset we mean data generated following the procedure described in Sec 5.
-Regarding the real datasets, we only tested the Pessimistic strategy for the following reasons: $1)$ Random was considered only as a baseline in the first experiment, which shows that Pessimistic performs much better; $2)$ Extended Pessimistic is computationally too consuming and it can be tested only on small instances (as pointed out in Sec 4); $3)$ Elitist was designed with the only purpose of challenging our best strategy (Pessimistic) in extreme cases tailored to favor the former.
+Regarding the real datasets, we only tested the Pessimistic strategy for the following reasons: $1)$ Random was considered only as a baseline in the first experiment, which shows that Pessimistic performs much better; $2)$ As pointed out in Sec 4, Extended Pessimistic is too computationally costly to run on larger instances; $3)$ Elitist was designed with the only purpose of challenging our best strategy (Pessimistic) in extreme cases tailored to favor the former.
 Testing this strategy in other settings does not yield interesting information; $4)$ Two Phase was designed to compare our interleaving approach to a more classical linear method.
 We thought that the most challenging situation (Impartial Culture) was the best setting to perform this test.
+\commentOC{What does the last sentence answer?}
 
@@
 The question is asked by showing a profile and asking who should win; the response is encoded as a constraint and added to the system’s knowledge.
-Methodologically, phrase questions in terms of winners out of profiles is arguably the most fundamental and natural view of what a social choice function is (as pointed out in our response to reviewer $\#$32).
+Phrasing questions in terms of winners out of profiles is arguably the most fundamental and natural view of what a social choice function is (as pointed out in our response to reviewer $\#$32).
 We adapt a mechanism used in a real life experiment by Giritligil et al.
@@
 Note that, in our experiments, we often plot the total number of questions in order to have a simple way to compare the total elicitation cost. 
-Table 1 of Appendix shows that the number of questions posed to the chair (and each agent) is usually not that big.
+\commentOC{I’d remove this first sentence and rephrase the next one.}
+Table 1 of Appendix shows that the number of questions posed to the chair (and each agent) is usually not that big.\commentOC{I suggest: is small or is usually small, and we have to phrase explicitly that the assumption in the question is wrong.}
 When the profile is quite homogeneous (see the lines corresponding to real datasets) this number is very low or even zero in case of clear winner.

### 2021-03-28 rebuttal/ijcai21-authors-response.tex
rebuttal comments

@@
 \newcommand{\commentOC}[1]{\textcolor{blue}{\small$\big[$OC: #1$\big]$}}
-\newcommand{\commentBN}[1]{\textcolor{red}{\small$\big[$BN: #1$\big]$}}
-\newcommand{\commentPV}[1]{\textcolor{brown}{\small$\big[$PV: #1$\big]$}}
+\newcommand{\commentBN}[1]{\textcolor{magenta}{\small$\big[$BN: #1$\big]$}}
+\newcommand{\commentPV}[1]{\textcolor{red}{\small$\big[$PV: #1$\big]$}}
 
@@
 
-\commentOC{I suggest to remove “factual error” and “specific questions” and rather directly go with the first question.}
+\commentOC{I suggest to remove “factual error” and “specific questions” and rather directly go with the first question.} \commentBN{I'm not against removing it but I thought it was better to specify why we are replying.
+In the FAQ for the AC there is a question 1) "What should I do if the authors have sent a response?" the answer is "You have to check whether the response really points out a factual error in a review or unethical issues.etc etc" 2)"Can reviewers ask specific questions to the authors, that they should answer during the response phase?" the answer is "In principle, No.
+etc etc".
+I'm afraid the AC won't send the respond to the reviewer if he feels we're just using it to contest his opinion.}
 We believe it is erroneous to consider the lack of comparison a weakness.
@@
 We compared these two strategies in a situation specifically tailored to advantage the Elitist.
-$2)$ The Two Phases was designed to challenge our interleaving approach by comparing it with a more classical linear method: first elicit the rule and then the agents preferences or vice versa.
+$2)$ The Two Phases was designed to challenge our interleaving approach by comparing it with a more classical linear \commentPV{I don't like calling "linear" the classic method of first eliciting the rule and then the agents.
+But I am unsure about an alternative, maybe "sequential"?} method: first elicit the rule and then the agents preferences or vice versa.
 The former coincides with the method of Lu and Boutilier [2011] for preferences elicitation fixed the voting rule.
@@
 Other than the example we provided in the Introduction, we could consider the reviewing process of a conference where the best paper must be elected.
-In this context, the agents express their preferences on the papers they reviewed, but they are not aware of the voting rule the SPC member will apply when aggregating them.
+In this context, the agents express their preferences on the papers they reviewed, but they are not aware of the voting rule the Program Chair will apply when aggregating them.
 %Nonetheless, reviewers are still willing to participate in the process.
-Also, the SPC member may not have a specific voting rule in mind, and she will find it hard to provide a precise scoring vector if asked.
+Also, the PC may not have a specific voting rule in mind, and she will find it hard to provide a precise scoring vector if asked.
 Imagine, for the sake of the example, that all the reviewers review all the papers and they rank them according to their preferences.
-The SPC member could adopt the Borda count and pick the paper with the highest score, but this is not the most appealing method.
+The PC member could adopt the Borda count and pick the paper with the highest score, but this is not the most appealing method.
 Maybe she strongly believes that being ranked once in the first position is “much more” valuable than being ranked two times second, but does not know exactly how much more (though she can judge example cases).
@@
 Regarding the real datasets, we only tested the Pessimistic strategy for the following reasons: $1)$ Random was considered only as a baseline in the first experiment, which shows that Pessimistic performs much better; $2)$ As pointed out in Sec 4, Extended Pessimistic is too computationally costly to run on larger instances; $3)$ Elitist was designed with the only purpose of challenging our best strategy (Pessimistic) in extreme cases tailored to favor the former.
-Testing this strategy in other settings does not yield interesting information; $4)$ Two Phase was designed to compare our interleaving approach to a more classical linear method.
+Testing this strategy in other settings does not yield interesting information; $4)$ Two Phases was designed to compare our interleaving approach to a more classical linear method.
 We thought that the most challenging situation (Impartial Culture) was the best setting to perform this test.
-\commentOC{What does the last sentence answer?}
+\commentOC{What does the last sentence answer?}\commentBN{To why we didn't test Two Phases with real datasets.}
 

### 2021-03-28 rebuttal/ijcai21-authors-response.tex
one more comment

@@
 Yes, when we do not specify the name of the dataset we mean data generated following the procedure described in Sec 5.
-Regarding the real datasets, we only tested the Pessimistic strategy for the following reasons: $1)$ Random was considered only as a baseline in the first experiment, which shows that Pessimistic performs much better; $2)$ As pointed out in Sec 4, Extended Pessimistic is too computationally costly to run on larger instances; $3)$ Elitist was designed with the only purpose of challenging our best strategy (Pessimistic) in extreme cases tailored to favor the former.
+Regarding the real datasets, we only tested the Pessimistic strategy for the following reasons: $1)$ Random was considered only as a baseline in the first experiment, which shows that Pessimistic performs much better; $2)$ As pointed out in Sec 4, Extended Pessimistic is too computationally costly to run on larger instances; \commentBN{I would keep the old phrasing to keep the same structure for all points (Extended Pessimistic ...
+as pointed out)} $3)$ Elitist was designed with the only purpose of challenging our best strategy (Pessimistic) in extreme cases tailored to favor the former.
 Testing this strategy in other settings does not yield interesting information; $4)$ Two Phases was designed to compare our interleaving approach to a more classical linear method.

### 2021-03-29 rebuttal/ijcai21-authors-response.tex
Rework first part

@@
 
-	We thank the reviewers for their comments. We specify that the questions reported are not verbatim for lack of space. 
-\paragraph{Rebuttal to Reviewer $\#$2: factual error}.\\
-\textit{\textbf{One of the weaknesses is that the method proposed is not compared with others.}}
+	We thank the reviewers for their comments. We specify that the questions reported are not verbatim for lack of space and focus on factual errors. 
+\paragraph{Review $\#$2: “the method proposed here is not compared with others”.}
+We believe it is erroneous to consider the lack of comparison a weakness.
+The simultaneous elicitation of both the voting rule and the agents preferences is a novel setting and, as far as we know, there is no competitor from the state-of-the-art to compare with.
+We are not aware of any method that elicits the voting rule we could compare with – the work by Cailloux and Endriss [2014] does not consider PSRs.
+Nevertheless, the Two Phases strategy was designed to challenge our interleaving approach by comparing it with a more classical sequential method, which (when first eliciting the rule and then the agents preferences) coincides with the method of Lu and Boutilier [2011] for preferences elicitation with a fixed voting rule.
 
-\commentOC{I suggest to remove “factual error” and “specific questions” and rather directly go with the first question.} \commentBN{I'm not against removing it but I thought it was better to specify why we are replying.
-In the FAQ for the AC there is a question 1) "What should I do if the authors have sent a response?" the answer is "You have to check whether the response really points out a factual error in a review or unethical issues.etc etc" 2)"Can reviewers ask specific questions to the authors, that they should answer during the response phase?" the answer is "In principle, No.
-etc etc".
-I'm afraid the AC won't send the respond to the reviewer if he feels we're just using it to contest his opinion.}
-We believe it is erroneous to consider the lack of comparison a weakness.
-The simultaneous elicitation of both the voting rule and the agents preferences is a novel setting and, as far as we know, there is no clear competitor from the state-of-the-art to compare with.
-However, please note that we designed all the strategies to challenge one another.
-$1)$ The Elitist has a very different approach than the Pessimistic to the point that it cannot be considered a variant.
-We compared these two strategies in a situation specifically tailored to advantage the Elitist.
-$2)$ The Two Phases was designed to challenge our interleaving approach by comparing it with a more classical linear \commentPV{I don't like calling "linear" the classic method of first eliciting the rule and then the agents.
-But I am unsure about an alternative, maybe "sequential"?} method: first elicit the rule and then the agents preferences or vice versa.
-The former coincides with the method of Lu and Boutilier [2011] for preferences elicitation fixed the voting rule.
-We are not aware of any method that elicits the voting rule we could compare with —the work by Cailloux and Endriss [2014] does not consider PSRs.
+\paragraph{Review $\#$2: “Only variants of the same methods are compared with each others”.}
+The Elitist strategy has a very different approach than the Pessimistic one, to the point that it cannot be considered a variant.
+They are compared in a situation specifically tailored to advantage the Elitist.
+\commentOC{Isn’t this a bit arguable that Elitist is very different rather than a variant?}
 
-\textit{\textbf{The voting rule has to be defined independently of the voters preferences and not by the chairperson.}}
-
+\paragraph{Review $\#$2: “the voting rule has to be defined independently of the preferences of the voters. And probably not by the chairpersonn who may influence the result by choosing the weights”.}
 It is not true that any decision process involving preference aggregation requires a voting rule defined beforehand, nor that it is necessarily a bad idea to let a chair decide on the voting rule.
-The interest of considering incomplete knowledge in the voting rule has been advocated in a recent survey paper of a leading researcher in Computational Social Choice [Lang 2020, \url{https://doi.org/10.24963/ijcai.2020/680}].
+The interest of considering incomplete knowledge in the voting rule has been advocated in a recent survey paper of a leading researcher in Computational Social Choice [Lang 2020, \href{https://doi.org/10.24963/ijcai.2020/680}{doi: 10.24963/ijcai.2020/680}].
 The case of IJCAI aggregation process of reviews illustrates the point: reviewers provide their preferences despite ignoring how these will be aggregated.
@@
 
-\paragraph{Rebuttal to Reviewer $\#$32: specific questions}
-.[Although not in the proper section, the reviewer formulated questions in the format described by the FAQ on when to answer.]
-
+\paragraph{Review $\#$32 suggests that it is hard to find “any real setting where a third party decides who wins a vote, not the chair.
+(…) Why would voters participate in a voting rule that is not public or common knowledge?
+(…) Why would the chair give up control of choosing the winner?”.}
 \textit{\textbf{Can the authors give an example of when the setting may occur in practice?
@@
 Why selecting winners is easier than reflecting on weights or computing the winner herself?}}
-
+It is not true that such setting is uncommon, on the contrary.
 Other than the example we provided in the Introduction, we could consider the reviewing process of a conference where the best paper must be elected.
 In this context, the agents express their preferences on the papers they reviewed, but they are not aware of the voting rule the Program Chair will apply when aggregating them.
-%Nonetheless, reviewers are still willing to participate in the process.
+Nonetheless, reviewers are still willing to participate in the process.
 Also, the PC may not have a specific voting rule in mind, and she will find it hard to provide a precise scoring vector if asked.

### 2021-03-29 rebuttal/ijcai21-authors-response.tex
Going on rebutting

@@
 	We thank the reviewers for their comments. We specify that the questions reported are not verbatim for lack of space and focus on factual errors. 
-\paragraph{Review $\#$2: “the method proposed here is not compared with others”.}
+\paragraph{Review $\#$2 writes as a weankess that “the method proposed here is not compared with others”.}
 We believe it is erroneous to consider the lack of comparison a weakness.
@@
 Nevertheless, the Two Phases strategy was designed to challenge our interleaving approach by comparing it with a more classical sequential method, which (when first eliciting the rule and then the agents preferences) coincides with the method of Lu and Boutilier [2011] for preferences elicitation with a fixed voting rule.
-
-\paragraph{Review $\#$2: “Only variants of the same methods are compared with each others”.}
+%\paragraph{Review $\#$2: “Only variants of the same methods are compared with each others”.}
+%\commentOC{Isn’t this a bit arguable that Elitist is very different rather than a variant?}
 The Elitist strategy has a very different approach than the Pessimistic one, to the point that it cannot be considered a variant.
 They are compared in a situation specifically tailored to advantage the Elitist.
-\commentOC{Isn’t this a bit arguable that Elitist is very different rather than a variant?}
 
@@
 (…) Why would voters participate in a voting rule that is not public or common knowledge?
-(…) Why would the chair give up control of choosing the winner?”.}
-\textit{\textbf{Can the authors give an example of when the setting may occur in practice?
-Why would voters participate without knowing the voting rule?
-Why selecting winners is easier than reflecting on weights or computing the winner herself?}}
+(…) If the chair can compute winners over and over for every elicitation for arbitrary size profiles, why wouldn't the chair just compute the real winner himself or herself, rather the delegate to the third party?
+(…) Why is this easier than reflecting on the relative weights?”}
 It is not true that such setting is uncommon, on the contrary.
@@
 Talking in terms of weights is a synthetic construction that could lead to different judgments by participants than other constructions.
-\commentOC{I find it important that the two next commented-out sentences be somehow included.}
-%For example, PSRs can also be described in terms of distance to ideal profiles ( On the role of distances in defining voting rules, Elkind et al., AAMAS 2010). 
-%There is no a priori reason to believe that questioning the chair in terms of this different parametric space would yield logically equivalent answers: 
-A research in experimental psychology shows that participants’ answers differ widely when changing the phrasing of preference-related questions [Lichtenstein \& Slovic, 2012, \href{https://doi.org/10.1017/CBO9780511618031}{doi: 10.1017/CBO9780511618031}].
-%(Lichtenstein, Slovic - The Construction of Preference, Cambridge University Press, 2006). 
+For example, PSRs can also be described in terms of distance to ideal profiles (On the role of distances in defining voting rules, Elkind et al., AAMAS 2010). 
+There is no a priori reason to believe that questioning the chair in terms of this different parametric space would yield logically equivalent answers: research in experimental psychology shows that participants’ answers differ widely when changing the phrasing of preference-related questions [Lichtenstein \& Slovic, 2012, \href{https://doi.org/10.1017/CBO9780511618031}{doi: 10.1017/CBO9780511618031}].
 To get out of such conundrums, we need a language considered “fundamental”. Questions of the form “In this profile, who should win?” arguably provides such a natural language.
+
+\paragraph{Review $\#$32: Why would the chair give up control of choosing the winner?”.}
+\textit{\textbf{}}
 %Specifying general algorithms is demanding, hence, we adapt a mechanism used in a real life experiment by Giritligil et al.

### 2021-03-29 rebuttal/ijcai21-authors-response.tex
Again!

@@
 	We thank the reviewers for their comments. We specify that the questions reported are not verbatim for lack of space and focus on factual errors. 
-\paragraph{Review $\#$2 writes as a weankess that “the method proposed here is not compared with others”.}
+\paragraph{Review $\#$2 writes as a weakness that “the method proposed here is not compared with others”.}
 We believe it is erroneous to consider the lack of comparison a weakness.
@@
 Also, the PC may not have a specific voting rule in mind, and she will find it hard to provide a precise scoring vector if asked.
-Imagine, for the sake of the example, that all the reviewers review all the papers and they rank them according to their preferences.
-The PC member could adopt the Borda count and pick the paper with the highest score, but this is not the most appealing method.
 Maybe she strongly believes that being ranked once in the first position is “much more” valuable than being ranked two times second, but does not know exactly how much more (though she can judge example cases).
 This is similar to how the paper WeBuildAI (and the general literature in micro-economy) supposes that participants are able to compare pairs of matches, but does not assume that participants can explicit their utility functions.
+
 Methodologically speaking, phrasing questions in terms of winners out of profiles is arguably the most fundamental and natural view of what a social choice function is.
@@
 
-\paragraph{Review $\#$32: Why would the chair give up control of choosing the winner?”.}
+Also, it is a classical assumption in political science that the chair could delegate to a third party, for example, because the chair wants to satisfy a form of fairness which she thinks that algorithm satisfies.
+In our case, this is done by agreeing to let the principle of “min-max regret” decide instead of picking her favorite winner.
+
+%\paragraph{Review $\#$32: Why would the chair give up control of choosing the winner?”.}
 \textit{\textbf{}}
@@
 
-%Finally, the chair could delegate to a third party, by agreeing to let the principle of “min-max regret” decide instead of picking her favorite winner, for example, because the chair wants to satisfy a form of fairness which she thinks that algorithm satisfies.
-This is a classical assumption in political science.
 %Note that the chair cannot compute the real winner as she ignores the profile.

### 2021-03-29 rebuttal/ijcai21-authors-response.tex
More

@@
 Yes, when we do not specify the name of the dataset we mean data generated following the procedure described in Sec 5.
-Regarding the real datasets, we only tested the Pessimistic strategy for the following reasons: $1)$ Random was considered only as a baseline in the first experiment, which shows that Pessimistic performs much better; $2)$ As pointed out in Sec 4, Extended Pessimistic is too computationally costly to run on larger instances; \commentBN{I would keep the old phrasing to keep the same structure for all points (Extended Pessimistic ...
-as pointed out)} $3)$ Elitist was designed with the only purpose of challenging our best strategy (Pessimistic) in extreme cases tailored to favor the former.
+Regarding the real datasets, we only tested the Pessimistic strategy for the following reasons: $1)$ Random was considered only as a baseline in the first experiment, which shows that Pessimistic performs much better; $2)$ Extended Pessimistic is too computationally costly to run on larger instances (as pointed out in Sec 4); $3)$ Elitist was designed with the only purpose of challenging our best strategy (Pessimistic) in extreme cases tailored to favor the former.
 Testing this strategy in other settings does not yield interesting information; $4)$ Two Phases was designed to compare our interleaving approach to a more classical linear method.
@@
 
-\paragraph{Rebuttal to Reviewer $\#$56: specific questions}.\\
-\textit{\textbf{Can you clarify better the rationale behind the assumptions you make on questions to the chair?}}
-
+\paragraph{Review $\#$56: Can you clarify better the rationale behind the assumptions you make on questions to the chair?}
 The question is asked by showing a profile and asking who should win; the response is encoded as a constraint and added to the system’s knowledge.
@@
 
-\textit{\textbf{Could you elaborate on why you think is reasonable to assume the human chair will answer hundreds of questions?}}
+\paragraph{Review $\#$56: “If the chair does not know the weight vector, he can’t answer the questions.”}
+This is untrue, as indicated above as a reply to Review \#32.
 
+\paragraph{Review $\#$56 writes that we “assume the human chair will answer hundreds of questions”. \commentOC{Beatrice, please check the exact quote.}}
 %We assume the chair to be human and, as discussed in the paragraph “Building concrete questions for the chair“ on page 3, we view questions “what is the winner of this profile” to be easier to answer than directly asking the weights (in the same way as, for the problem of elicitation an utility function, one would ask comparison queries rather than asking directly utility values).
-Note that, in our experiments, we often plot the total number of questions in order to have a simple way to compare the total elicitation cost. 
+We do not assume this. We plot the total number of questions in order to have a simple way to compare the total elicitation cost. 
 \commentOC{I’d remove this first sentence and rephrase the next one.}
-Table 1 of Appendix shows that the number of questions posed to the chair (and each agent) is usually not that big.\commentOC{I suggest: is small or is usually small, and we have to phrase explicitly that the assumption in the question is wrong.}
-When the profile is quite homogeneous (see the lines corresponding to real datasets) this number is very low or even zero in case of clear winner.
+Table 1 of Appendix shows that the number of questions posed to the chair (and each agent) is usually small.
+Our experiments also show efficiency decreases slowly when diminishing the number of questions to the chair and distributing them to the voters instead.
+%When the profile is quite homogeneous (see the lines corresponding to real datasets) this number is very low or even zero in case of clear winner.
 We also mention that the process could be terminated early: after a fixed number of questions (the “approximate winner” is the alternative with lowest regret); or after reaching a "low enough" regret.
@@
 one could decide to stop after a fixed number of questions (even if regret is not zero) and to output as an “approximate winner” the alternative with lowest minimax regret value.
-If the paper will be accepted, we will stress more this point and include the Appendix Table in the final version.
-
+%If the paper will be accepted, we will stress more this point and include the Appendix Table in the final version.
 \end{document}

### 2021-03-29 rebuttal/ijcai21-authors-response.tex
Last for now!

@@
 
-	We thank the reviewers for their comments. We specify that the questions reported are not verbatim for lack of space and focus on factual errors. 
+	We thank the reviewers for their comments. We focus on factual errors and on the “questions for the authors”.
+
 \paragraph{Review $\#$2 writes as a weakness that “the method proposed here is not compared with others”.}
@@
 
-\paragraph{Review $\#$56: Can you clarify better the rationale behind the assumptions you make on questions to the chair?}
+\paragraph{Review $\#$56: “If the chair does not know the weight vector, he can’t answer the questions.”}
+This is untrue, as indicated above as a reply to Review \#32.
+
+\paragraph{Review $\#$56: “Can you clarify better the rationale behind the assumptions you make on questions to the chair?”}
 The question is asked by showing a profile and asking who should win; the response is encoded as a constraint and added to the system’s knowledge.
@@
 
-\paragraph{Review $\#$56: “If the chair does not know the weight vector, he can’t answer the questions.”}
-This is untrue, as indicated above as a reply to Review \#32.
-
-\paragraph{Review $\#$56 writes that we “assume the human chair will answer hundreds of questions”. \commentOC{Beatrice, please check the exact quote.}}
+\paragraph{Review $\#$56: “You say that you assume the chair to be human, yet you think he will answer hundreds of questions..?”}
 %We assume the chair to be human and, as discussed in the paragraph “Building concrete questions for the chair“ on page 3, we view questions “what is the winner of this profile” to be easier to answer than directly asking the weights (in the same way as, for the problem of elicitation an utility function, one would ask comparison queries rather than asking directly utility values).
 We do not assume this. We plot the total number of questions in order to have a simple way to compare the total elicitation cost. 
-\commentOC{I’d remove this first sentence and rephrase the next one.}
 Table 1 of Appendix shows that the number of questions posed to the chair (and each agent) is usually small.
-Our experiments also show efficiency decreases slowly when diminishing the number of questions to the chair and distributing them to the voters instead.
+Our experiments also show that efficiency decreases only slowly when diminishing the number of questions to the chair and distributing them to the voters instead.
 %When the profile is quite homogeneous (see the lines corresponding to real datasets) this number is very low or even zero in case of clear winner.

### 2021-03-29 rebuttal/ijcai21-authors-response.tex
Full VS partial profiles
Phrasing
rebuttal comments

@@
 
-	We thank the reviewers for their comments. We focus on factual errors and on the “questions for the authors”.
+	We thank the reviewers for their comments.
+We focus on factual errors and on the “questions for the authors”.
+\commentBN{Maybe: "We focus on factual errors and only on the questions reported in “questions for the authors”", or "We focus on factual errors when not better specified." and we write a Q before the questions.}
 
@@
 %\commentOC{Isn’t this a bit arguable that Elitist is very different rather than a variant?}
-The Elitist strategy has a very different approach than the Pessimistic one, to the point that it cannot be considered a variant.
-They are compared in a situation specifically tailored to advantage the Elitist.
+The Elitist strategy has a very different approach than the Pessimistic one and does not use the regret to question the voters.
+It was conceived to challenge our best strategy (Pessimistic) in extreme cases tailored to favor Elitist.
+\commentBN{I removed "to the point that it cannot be considered a variant", it's arguable, maybe it's better to not focus on this.}
 
@@
 
+\commentBN{If we want to keep this we could summarize it as follows}
+Yes, when we do not specify the name of the dataset we mean data generated following the procedure described in Sec 5.
+We designed several strategies in order to challenge one another and select the best strategy in the worst case (Impartial Culture).
+Once this was found to be Pessimistic, we tested it on real dataset.
+
 \paragraph{Review $\#$56: “If the chair does not know the weight vector, he can’t answer the questions.”}

### 2021-03-29 rebuttal/ijcai21-authors-response.tex
rebuttal comments

--- 2021-03-29 rebuttal/ijcai21-authors-response.tex
@@
 
-	We thank the reviewers for their comments. We focus on factual errors and on the “questions for the authors”.
+	We thank the reviewers for their comments.
 
@@
 %\commentOC{Isn’t this a bit arguable that Elitist is very different rather than a variant?}
-The Elitist strategy has a very different approach than the Pessimistic one, to the point that it cannot be considered a variant.
-They are compared in a situation specifically tailored to advantage the Elitist.
+The Elitist strategy has a very different approach than the Pessimistic one and does not use the regret to question the voters.
+It was conceived to challenge our best strategy (Pessimistic) in extreme cases tailored to favor Elitist.
 
@@
 \paragraph{Review $\#$32 suggests that it is hard to find “any real setting where a third party decides who wins a vote, not the chair.
+(…) Can the authors give an example?
 (…) Why would voters participate in a voting rule that is not public or common knowledge?
@@
 In our case, this is done by agreeing to let the principle of “min-max regret” decide instead of picking her favorite winner.
+Note that we assume the chair can pick winners out of full profiles, but needs to delegate to the min-max algorithm for querying the voters and picking winners out of partial profiles.
 
@@
 %-Why is Figure 2 shown for only Pessimistic, not all the approaches? Were all approaches tested on all data sets? Or were all approaches only tested on synthetic data?
-Yes, when we do not specify the name of the dataset we mean data generated following the procedure described in Sec 5.
+%Yes, when we do not specify the name of the dataset we mean data generated following the procedure described in Sec 5.
 Regarding the real datasets, we only tested the Pessimistic strategy for the following reasons: $1)$ Random was considered only as a baseline in the first experiment, which shows that Pessimistic performs much better; $2)$ Extended Pessimistic is too computationally costly to run on larger instances (as pointed out in Sec 4); $3)$ Elitist was designed with the only purpose of challenging our best strategy (Pessimistic) in extreme cases tailored to favor the former.
@@
 \commentOC{What does the last sentence answer?}\commentBN{To why we didn't test Two Phases with real datasets.}
+%
+%\commentBN{If we want to keep this we could summarize it as follows}
+
+Yes, when we do not specify the name of the dataset we mean data generated following the procedure described in Sec 5.
+We designed several strategies in order to challenge one another and select the best strategy in the most challenging setting (Impartial Culture).
+Once this was found to be Pessimistic, we tested it on real dataset.
 

### 2021-03-29 rebuttal/ijcai21-authors-response.tex
rebuttal comments
final?

@@
 
-	We thank the reviewers for their comments.
+	We thank the reviewers for their comments. We address factual errors ($\#$2) and both factual errors and direct questions ($\#$32 and $\#$56).
 
@@
 %\paragraph{Review $\#$32: Why would the chair give up control of choosing the winner?”.}
-\textit{\textbf{}}
 %Specifying general algorithms is demanding, hence, we adapt a mechanism used in a real life experiment by Giritligil et al.
@@
 
-\textit{\textbf{Is Figure 1 for the synthetic data? Please specify. Why is Figure 2 shown for only Pessimistic, not all the approaches?}}
+%\paragraph{Review $\#$32 "Is Figure 1 for the synthetic data? Please specify. (…) Why is Figure 2 shown for only Pessimistic, not all the approaches?"}
 
@@
 
-Yes, when we do not specify the name of the dataset we mean data generated following the procedure described in Sec 5.
+%Yes, when we do not specify the name of the dataset we mean data generated following the procedure described in Sec 5.
 We designed several strategies in order to challenge one another and select the best strategy in the most challenging setting (Impartial Culture).

### 2021-03-29 rebuttal/ijcai21-authors-response.tex
final

@@
 
-	We thank the reviewers for their comments. We address factual errors ($\#$2) and both factual errors and direct questions ($\#$32 and $\#$56).
+	We thank the reviewers for their comments. We address factual errors (Review $\#$2) and both factual errors and direct questions (Reviews $\#$32 and $\#$56).
 
@@
 
-\paragraph{Review $\#$2: “the voting rule has to be defined independently of the preferences of the voters. And probably not by the chairpersonn who may influence the result by choosing the weights”.}
+\paragraph{Review $\#$2: “the voting rule has to be defined independently of the preferences of the voters. And probably not by the chairperson who may influence the result by choosing the weights”.}
 It is not true that any decision process involving preference aggregation requires a voting rule defined beforehand, nor that it is necessarily a bad idea to let a chair decide on the voting rule.
@@
 
-\paragraph{Review $\#$56: “You say that you assume the chair to be human, yet you think he will answer hundreds of questions..?”}
+\paragraph{Review $\#$56: “You say that you assume the chair (…) will answer hundreds of questions”}
 %We assume the chair to be human and, as discussed in the paragraph “Building concrete questions for the chair“ on page 3, we view questions “what is the winner of this profile” to be easier to answer than directly asking the weights (in the same way as, for the problem of elicitation an utility function, one would ask comparison queries rather than asking directly utility values).

### 2021-03-29 rebuttal/ijcai21-authors-response.tex
final final

--- 2021-03-29 rebuttal/ijcai21-authors-response.tex
@@
 
-\paragraph{Review $\#$56: “You say that you assume the chair to be human, yet you think he will answer hundreds of questions..?”}
+\paragraph{Review $\#$56: “You say that you assume the chair (…) will answer hundreds of questions..?”}
 %We assume the chair to be human and, as discussed in the paragraph “Building concrete questions for the chair“ on page 3, we view questions “what is the winner of this profile” to be easier to answer than directly asking the weights (in the same way as, for the problem of elicitation an utility function, one would ask comparison queries rather than asking directly utility values).
@@
 The fact that asking too many questions to the chair is not worth it isworth is also displayed in Table 3 in the main text.
-%Finally, note that the process could be terminated early: e.g.
-one could decide to stop after a fixed number of questions (even if regret is not zero) and to output as an “approximate winner” the alternative with lowest minimax regret value.
+Note that the process could be terminated early: one could decide to stop after a fixed number of questions is asked (even if regret is not zero) and to output as an “approximate winner” the alternative with lowest regret.
 %If the paper will be accepted, we will stress more this point and include the Appendix Table in the final version.

### 2021-04-30 minimax.tex
format ADT

@@
-\documentclass{article}
-\pdfpagewidth=8.5in
-\pdfpageheight=11in
-% The file ijcai21.sty is NOT the same than previous years'
-\usepackage{ijcai21}
+% This is samplepaper.tex, a sample chapter demonstrating the
+% LLNCS macro package for Springer Computer Science proceedings;
+% Version 2.20 of 2017/10/04
+%
+\documentclass[runningheads]{llncs}
+%
+\input{preamble/packages}
+\input{preamble/math}
+\usepackage{graphicx}
 \usepackage{times}
 \usepackage{soul}
-\usepackage[hidelinks,hypertexnames=false]{hyperref}
+%\usepackage[hidelinks,hypertexnames=false]{hyperref}
+\let\proof\relax
+\let\endproof\relax
 \usepackage{amsthm}
 \usepackage{xr}
-\externaldocument{appendix}
 %%% Load required packages here (note that many are included already).
-\input{preamble/packages}
-\input{preamble/math}
-%for appendix
-\usepackage{import}
+
 \usepackage{algorithm, algpseudocode}
@@
 
-\setlist[itemize]{noitemsep, topsep=0pt}
-
-\newcommand{\commentOC}[1]{\textcolor{blue}{\small$\big[$OC: #1$\big]$}}
-\newcommand{\commentBN}[1]{\textcolor{red}{\small$\big[$BN: #1$\big]$}}
-\newcommand{\commentPV}[1]{\textcolor{brown}{\small$\big[$PV: #1$\big]$}}
-
-\pdfinfo{
-	/TemplateVersion (IJCAI.2021.0)
-}
-
-%I find these settings useful in draft mode. Should be removed for final versions.
-	%Which line breaks are chosen: accept worse lines, therefore reducing risk of overfull lines. Default = 200.
-		\tolerance=2000
-	%Accept overfull hbox up to...
-		\hfuzz=2cm
-	%Reduces verbosity about the bad line breaks. TODO reduce
-		\hbadness 10000
-	%Reduces verbosity about the underful vboxes.
-		\vbadness=6000
-
-%%% Use this command to specify the title of your paper.
-
-\title{Simultaneous Elicitation of Scoring Rule and Agent Preferences for Robust Winner Determination}
-
-%%% Provide names, affiliations, and email addresses for all authors.
-
-\author{ID: 3177}
-
-%\author{
-%	Beatrice Napolitano$^1$\footnote{Contact Author}\and
-%	Olivier Cailloux$^1$\and
-%	Paolo Viappiani$^2$\\
-%	\affiliations
-%	$^1$Université Paris-Dauphine, Université PSL, CNRS, LAMSADE\\
-%	$^2$LIP6, UMR 7606, CNRS and Sorbonne Universit\'e\\
-%	\emails
-%	\{beatrice.napolitano, olivier.cailloux\}@dauphine.fr,
-%	paolo.viappiani@lip6.fr
-%}
-
-\newcommand{\BibTeX}{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em\TeX}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\usepackage[hypertexnames=false]{hyperref} 
+%\usepackage{cleveref}
+% Used for displaying a sample figure. If possible, figure files should
+% be included in EPS format.
+%
+% If you use the hyperref package, please uncomment the following line
+% to display URLs in blue roman font according to Springer's eBook style:
+% \renewcommand\UrlFont{\color{blue}\rmfamily}
 
 \begin{document}
+%
+\title{Simultaneous Elicitation of Scoring Rule and Agent Preferences for Robust Winner Determination}
+%
+\titlerunning{Simultaneous Elicitation of Scoring Rule and Agent Preferences}
+% If the paper title is too long for the running head, you can set
+% an abbreviated paper title here
+%
 
-\maketitle
+%\author{Submission 15}
+%\institute{}
 
+\author{Beatrice Napolitano\inst{1}\orcidID{0000-0002-3887-6206} \and
+Olivier Cailloux\inst{1}\and
+Paolo Viappiani\inst{2}}
+%
+\authorrunning{B. Napolitano et al.}
+% First names are abbreviated in the running head.
+% If there are more than two authors, 'et al.' is used.
+%
+\institute{Université Paris-Dauphine, Université PSL, CNRS, LAMSADE \and
+LIP6, UMR 7606, CNRS and Sorbonne Universit\'e \\
+\email{\{beatrice.napolitano, olivier.cailloux\}@dauphine.fr}\\
+%\url{http://www.springer.com/gp/computer-science/lncs} \and
+%ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
+\email{paolo.viappiani@lip6.fr}}
+
+\maketitle              % typeset the header of the contribution
+%
 \begin{abstract}
+%The abstract should briefly summarize the contents of the paper in
+%150--250 words.
+\begin{sloppypar}
 Social choice deals with the problem of determining a consensus choice from the preferences of different agents.
 In the classical setting, the voting rule is fixed beforehand and full information concerning the preferences of the agents is provided.
-This assumption of full preference information has recently been questioned by a number of researchers and
-	several methods for eliciting the preferences of the agents have been proposed.
-	%  are completely known have been proposed, as well as techniques that consider the opposite scenario.
-
+This assumption of full preference information has recently been questioned by a number of researchers and several methods for eliciting the preferences of the agents have been proposed.
 In this paper we argue that in many situations one should consider as well the voting rule to be partially specified.
-%	This article goes one step further by tackling one important new case, namely, when both the voting rule and the agents preferences are partially known.
-It also permits to obtain a progressively refined recommendation without requiring to achieve full knowledge of either sort of information.
-%This is useful because providing such information is often costly: the chair may find it hard to specify a rule completely; agents may need time to form reflective preferences.	
 Focusing on positional scoring rules, we assume that the chair, while not able to give a precise definition of the rule, is capable of answering simple questions requiring to pick a winner from a concrete profile.
 In addition, we assume that the agent preferences also have to be elicited.
-%and are acquired by asking comparison queries.
-	We propose a method for robust approximate winner determination and interactive elicitation based on minimax regret; we develop several strategies for choosing the questions to ask to  the chair and the agents in order to %acquire the most relevant information for
-converge quickly to a near-optimal alternative. Finally, we analyze these strategies in experiments %in order to validate our approach
- %focusing on settings 
- where the  rule and the preferences are simultaneously elicited.
- %and obtain practical guidelines.
+We propose a method for robust approximate winner determination and interactive elicitation based on minimax regret; we develop several strategies for choosing the questions to ask to the chair and the agents in order to converge quickly to a near-optimal alternative.
+Finally, we analyze these strategies in experiments where the rule and the preferences are simultaneously elicited.
+\end{sloppypar}
+\keywords{Uncertainty in AI \and Computational Social Choice \and Preference Elicitation.}
 \end{abstract}
-
+%
+%
+%
 \section{Introduction}
@@
 %In the context of social choice, several authors have been interested in obtaining information about winners with reduced assumptions about the knowledge of the agent preferences (assuming that the voting rule is known).
-one early work is  by \Citet{Conitzer2005} who studied the complexity of communication when using different voting rules; %determining lower and upper bounds;
+one early work is  by Conitzer and Sandholm \cite{Conitzer2005} who studied the complexity of communication when using different voting rules; %determining lower and upper bounds;
 %they showed that, 
 %in the worst case, the agents should send their complete set of preference for several rules. 
-\Citet{Konczak05} studied the computation of possible and necessary winners for various voting rules; %and showed that the problem is hard in the general case.
-\citet{Xia2008} then showed that, while the identification of a necessary co-winner in scoring rules is polynomial,  the determination of possible co-winners is NP-hard;
+Konczak and Lang \cite{Konczak05} studied the computation of possible and necessary winners for various voting rules; %and showed that the problem is hard in the general case.
+Xia and Conitzer \cite{Xia2008} then showed that, while the identification of a necessary co-winner in scoring rules is polynomial,  the determination of possible co-winners is NP-hard;
 % they also  proposed polynomial-time algorithms when using maximin and Bucklin.
-additional complexity results were given by \citet{Walsh2007} and \citet{Pini2007}.
-%\citep{Walsh2007} showed that the general case remains computationally hard even when restricting to single-peaked preferences;  sufficient conditions that ensure tractability were then found \citep{Pini2007}.
+additional complexity results were given by Walsh \cite{Walsh2007} and Pini et al. \cite{Pini2007}.
+%\cite{Walsh2007} showed that the general case remains computationally hard even when restricting to single-peaked preferences;  sufficient conditions that ensure tractability were then found \cite{Pini2007}.
 
-Since in many practical situations there would be too many possible winners but no necessary winners, several works addressed the problem of agent preferences elicitation using a variety of approaches (minimax regret, Bayesian methods, etc.) with the goal of converging to a necessary winner \citep{Naamani-Dery2015,Kalech2011,Lu2011,Pini2009,Benabbou2016,Dey2016,Dey2016_2}.
-Among those, \citet{Walsh2009} and \citet{Conitzer2009} analyzed when to stop the elicitation process.
+Since in many practical situations there would be too many possible winners but no necessary winners, several works addressed the problem of agent preferences elicitation using a variety of approaches (minimax regret, Bayesian methods, etc.) with the goal of converging to a necessary winner \cite{Naamani-Dery2015,Kalech2011,Lu2011,Pini2009,Benabbou2016,Dey2016,Dey2016_2}.
+Among those, Walsh \cite{Walsh2009} and Conitzer \cite{Conitzer2009} analyzed when to stop the elicitation process.
 
@@
 
-While some previous works have considered partially specified aggregation methods \citep{Stein1994,Llamazares2013,Viappiani2018}, we do not know of any work considering both sources of uncertainty at the same time.
+While some previous works have considered partially specified aggregation methods \cite{Stein1994,Llamazares2013,Viappiani2018}, we do not know of any work considering both sources of uncertainty at the same time.
 %has dealt with %scenarios where it is instead the voting rule that is partially defined. % but the preferences are given. 
@@
 Actually, very few works altogether have considered the problem of eliciting a voting rule by asking questions to the chair.
-We mention the work of \Citet{Cailloux2014} that assumes a different representation for the rule.
+We mention the work of Cailloux and Endriss \cite{Cailloux2014} that assumes a different representation for the rule.
 %we mention the work of \Citet{Cailloux2014} considering elicitation the voting rule by assuming a specific representation.
@@
 % provided an elicitation framework for a different class of rules.
-Additionally, some works address the manipulability of voting rules \citep{Elkind2012,Dey2018,Dey2018_2,Conitzer2011,Baumeister2019} and 
-strategic behaviors \citep{Endriss2016,Lev2019,Annemieke2012}.
+Additionally, some works address the manipulability of voting rules \cite{Elkind2012,Dey2018,Dey2018_2,Conitzer2011,Baumeister2019} and 
+strategic behaviors \cite{Endriss2016,Lev2019,Annemieke2012}.
 
@@
 
-An important class of PSRs is the one using convex weights \citep{Stein1994,Llamazares2016}, meaning that the difference between the weight of the first position and the weight of the second position is at least as large as the difference between the weights of the second and third positions, etc.
+An important class of PSRs is the one using convex weights \cite{Stein1994,Llamazares2016}, meaning that the difference between the weight of the first position and the weight of the second position is at least as large as the difference between the weights of the second and third positions, etc.
 \begin{equation} 
@@
 As, often, there are no necessary winners and too many possible winners, it is useful to declare a winner given partial information.
-As a decision criterion to determine a winner, we propose to use minimax regret \citep{Savage1954}. 
-This decision criterion has been used for robust optimization under data uncertainty \citep{Kouvelis1997} as well as in decision-making with uncertain utility values \citep{Salo2001,Boutilier2006}.
-In particular, \citet{Lu2011} have adopted minimax regret for winner determination in social choice where
+As a decision criterion to determine a winner, we propose to use minimax regret \cite{Savage1954}. 
+This decision criterion has been used for robust optimization under data uncertainty \cite{Kouvelis1997} as well as in decision-making with uncertain utility values \cite{Salo2001,Boutilier2006}.
+In particular, Lu and Boutilier \cite{Lu2011} have adopted minimax regret for winner determination in social choice where
 the preferences of agents are partially known, while the social choice function is known.
@@
 \paragraph{Computation of minimax regret}
-Given a voting rule and a partially specified profile, \citet{Xia2008} determine necessary winners by showing constructions that attempt to maximize the score difference between a proposed winner and a chosen alternative.
-This reasoning was later adopted by \citet{Lu2011} who used the considerations on the worst-case completions for computing the minimax regret.
+Given a voting rule and a partially specified profile, Xia and Conitzer \cite{Xia2008} determine necessary winners by showing constructions that attempt to maximize the score difference between a proposed winner and a chosen alternative.
+This reasoning was later adopted by Lu and Boutilier \cite{Lu2011} who used the considerations on the worst-case completions for computing the minimax regret.
 
@@
 Since scoring rules are additively decomposable, we can consider separately the contribution of each agent to the total score.
-Thus, we can write the actual regret of choosing $x$ instead of $y$ as $s(y; \profile,\w) - s(x; \profile, \w) = \sum_{j=1}^n w_{v_j(y)} - w_{v_j(x)}$, and we obtain $\PMR(x,y; \pprofile, W) =  \max_{\w \in W} \sum_{j=1}^{n} \max_{v_j \in C(\succ_j^p)} [w_{v_j(y)} - w_{v_j(x)}]$.
+Thus, we can write the actual regret of choosing $x$ instead of $y$ as $s(y; \profile,\w) - s(x; \profile, \w) = \sum_{j=1}^n w_{v_j(y)} - w_{v_j(x)}$, and we obtain \[\PMR(x,y; \pprofile, W) =  \max_{\w \in W} \sum_{j=1}^{n} \max_{v_j \in C(\succ_j^p)} [w_{v_j(y)} - w_{v_j(x)}].\]
 %Note that in general the inner max depends on the weights chosen by the outer max.
 
-The following propositions (with proofs in Appendix) show that the procedure for completing a partial profile,  proposed by \citet{Lu2011} when considering a fixed weight vector, also applies in our setting.
+The following propositions (with proofs in Appendix) show that the procedure for completing a partial profile,  proposed by Lu and Boutilier \cite{Lu2011} when considering a fixed weight vector, also applies in our setting.
 We write $a \pprefeq_j b$ iff $a \ppref_j b \lor a = b$ and adopt the canonical notation when considering a relation as a function, writing ${\pprefeq_j}(x)$ for $\set{y \suchthat x \pprefeq_j y}$.
@@
 \begin{proposition} \label{claim:completion}
-	There exists a completion $\hat{\profile} \in C(\pprofile)$ of the profile $\profile$ such that $\PMR(x,y; \pprofile, W) = \max_{\w \in W} [ s(y; \hat{\profile}, \w) - s(x; \hat{\profile}, \w) ]$ and such that the linear order $\hat{v}_{j}$ of each agent $j$ satisfies:
+	\begin{sloppypar}
+		There exists a completion $\hat{\profile} \in C(\pprofile)$ of the profile $\profile$ such that ${\PMR(x,y; \pprofile, W) = \max_{\w \in W} [ s(y; \hat{\profile}, \w) - s(x; \hat{\profile}, \w) ]}$ and such that the linear order $\hat{v}_{j}$ of each agent $j$ satisfies:
+	\end{sloppypar}
+
 	\begin{eqnarray}
@@
 \begin{proposition} \label{claim:rankPMR}
+	\begin{sloppypar}
 	The rank of $x$ in the PMR-maximizing linear orders of agent $j$ is $\hat{v}_{j}(x) = 1+\card{A}-\card{{\pprefeq_j}(x)}$, and the rank of $y$ is $\hat{v}_{j}(y)=1+\card{{\pprefinv_j}(y)}+\card{\beta}$, where $\card{\beta} = \card{A \setminus ({\pprefeq_j}(x) \cup {\pprefinv_j}(y))}$ if $(x \pprefeq_j y)$ and $\card{\beta} = 0$ otherwise.
+	\end{sloppypar}
 \end{proposition}
@@
 Observe that when the $\PMR$ of an alternative $x$ (against some other alternative $y$) exceeds the best MR value found so far, we do not need to further evaluate $x$. 
-This idea can be exploited using a minimax-search tree \citep{Braziunas2012}.
+This idea can be exploited using a minimax-search tree \cite{Braziunas2012}.
 
@@
 Moreover, this way of questioning the chair is independent of the voting rule that is being elicited. Questions about weights only make sense when considering PSRs.
-Asking who should win in specific profiles has been used in experimental settings investigating the feeling of justice of individuals \citep{Giritligil2005}, but, to the best of our knowledge, the use of such questions to systematically guide an elicitation process about voting rules is novel.
+Asking who should win in specific profiles has been used in experimental settings investigating the feeling of justice of individuals \cite{Giritligil2005}, but, to the best of our knowledge, the use of such questions to systematically guide an elicitation process about voting rules is novel.
 This is similar to favor, in decision theory, direct choice questions ("please choose either a or b") compared to, say, questioning the decision maker about the shape of her utility function.
-The former are considered “observable”: acts of choice are translated to preference statements \citep[Ch.\ 1]{colell_microeconomic_1995}.
+The former are considered “observable”: acts of choice are translated to preference statements \cite[Ch.\ 1]{colell_microeconomic_1995}.
 
@@
 
-\begin{example*}
+\begin{example}
 	Suppose we want to ask the following question to the chair: $w_{2} - w_{3} ≥ 2 (w_{3} - w_{4})$. 
@@
 	(the proof in Appendix presents the general method of constructing such profile.)
-\end{example*}
+\end{example}
 
@@
 
-The candidate questions to the agents are chosen by extending the idea of \citet{Lu2011}, that privilege learning about the relationship of $x^*$ and $\bar{y}$ to the other alternatives if possible.
+The candidate questions to the agents are chosen by extending the idea of Lu and Boutilier \cite{Lu2011}, that privilege learning about the relationship of $x^*$ and $\bar{y}$ to the other alternatives if possible.
 Given $j \in N^*$, if $x^*$ and $\bar{y}$ are incomparable in $\ppref_j$, the candidate question concerns the pair $(x^*, \bar{y})$, otherwise, %the candidate question
@@
 Assume that a question $q_1$ has type $t_1$ (being “chair” or “agent”), and leads to the new knowledge states $(\pprofile_1, W_1)$ if answered positively and $(\pprofile'_1, W'_1)$ if the answer is negative.
-	Define $R^{\max}_1 = \max\set{\MMR(\pprofile_1, W_1), \MMR(\pprofile'_1, W'_1)}$
-	and $R^{\min}_1 = \min\set{\MMR(\pprofile_1, W_1), \MMR(\pprofile'_1, W'_1)} \epsilon_{t} + \epsilon'_{t}$.
+Define \[R^{\max}_1 = \max\set{\MMR(\pprofile_1, W_1), \MMR(\pprofile'_1, W'_1)}\]
+and \[R^{\min}_1 = \min\set{\MMR(\pprofile_1, W_1), \MMR(\pprofile'_1, W'_1)} \epsilon_{t} + \epsilon'_{t}.\]
 %If $(\pprofile_1, W_1) ≥ (\pprofile'_1, W'_1)$, define $\MMR^{\max} = \MMR(\pprofile_1, W_1)$ and $\MMR^{\min} = \MMR(\pprofile'_1, W'_1)$; otherwise, define $\MMR^{\max} = \MMR(\pprofile'_1, W'_1)$ and $\MMR^{\min} = \MMR(\pprofile_1, W_1)$.
@@
 %We are now faced with the problem of aggregating these values in order to compare the informative values of the candidate questions.
-\footnote{We adopt a pessimistic approach, reported to perform better than optimistic aggregation \citep{Cailloux2014}, although Our experiments in this context suggested a weak impact of that choice on the performance of the strategy.}
+\footnote{We adopt a pessimistic approach, reported to perform better than optimistic aggregation \cite{Cailloux2014}, although Our experiments in this context suggested a weak impact of that choice on the performance of the strategy.}
 %To avoid the absorption property of the max, we adopt $\leximax$ as an aggregator.
@@
 %The motivation for using this operator lies in 
-	In other words if the maximal {\em a posteriori} MMR of two questions are (approximately) equal, then it considers the (penalized) minimal MMR values.
-%, preferring the question with the lowest value.
+In other words if the maximal {\em a posteriori} MMR of two questions are (approximately) equal, then it considers the (penalized) minimal MMR values. %, preferring the question with the lowest value.
 %(Technically, instead of applying a pure lexicographic aggregation, which is very sensitive to small errors due to floating-point computations, we apply a weighted sum between the maximal and the penalized minimal MMR values, with a predominant weight given to the maximal one, several order of magnitudes higher than the weight given to the penalized minimal MMR.)
@@
 We repeat this whole experiment a variable number of times, for a given $(m, n, k)$, and report the average resulting MMR and standard deviation \textit{sd}.
-The sizes of the considered scenarios are comparable to the ones used by \citet{Cailloux2014}.
+The sizes of the considered scenarios are comparable to the ones used by Cailloux and Endriss \cite{Cailloux2014}.
 
 The oracle is built as follows. 
-For the real preferences, we used three datasets from \href{https://www.preflib.org/}{PrefLib} \citep{PrefLib}: \textit{T Shirt} (researchers voted on tee shirt designs; $m \!=\! 11, n \!=\! 30$),
+For the real preferences, we used three datasets from \href{https://www.preflib.org/}{PrefLib} \cite{PrefLib}: \textit{T Shirt} (researchers voted on tee shirt designs; $m \!=\! 11, n \!=\! 30$),
 \textit{Courses}  (students voted on courses; $m \!=\! 9, n \!=\! 146$; referred to as AGH on PrefLib)
@@
 Another interesting measure is the average number of questions asked to each participant before reaching zero regret.
-For example, in the case $m = 10, n = 20$, Pessimistic asks on average $49$ questions to the chair and $18$ questions to each agent (\cref{tab:questions} in Appendix provides more data).
+For example, in the case $m = 10, n = 20$, Pessimistic asks on average $49$ questions to the chair and $18$ questions to each agent (\cref{tab:Numquestions} provides more data).
 
@@
 
+\begin{table}[ht]
+	\caption{Average number of questions asked to the chair ($q_{c}$) and to the agents (\textit{$q_{v}$}) by Pessimistic strategy to reach zero regret on the datasets of \cref{fig:linearity}.}
+	\label{tab:Numquestions}
+	\begin{tabular}{cS[table-number-alignment = right, table-figures-integer=4]@{ ± }S[table-number-alignment = left, table-figures-integer=2]S[table-number-alignment = right, table-figures-integer=4]@{ ± }S[table-number-alignment = left, table-figures-integer=2]}
+		\toprule
+		{dataset} & {$q_{c}$} & {sd} & {$q_{v}$} & {sd} \\
+		\midrule
+		m5n10 	&	8.4		& 2.67 		& 61		& 6.25\\
+		m5n20 	&	13.6	& 6.38		& 118.9		& 14.4\\
+		m10n20 	&	48.5	& 6			& 362.4		& 47.6	\\
+		m10n30 	&	56.3	& 11.18		& 598.1 	& 75.19	\\
+		m15n30 	&	24.5	& 8.77		& 775.5		& 8.77	\\
+		m14n9 	&	58.3	& 33.66		& 370.9		& 40.54	\\
+		m14n9-2 &	56.2	& 34.11		& 368.7		& 53.07 \\
+		skate 	&	0		& 0			& 103.3		& 2.21	\\
+		tshirt  &	30.0	& 5.87		& 961.2		& 23.04	\\
+		courses & 0			& 0			& 950		& 5.08	\\	
+		\bottomrule
+	\end{tabular}
+\end{table}
+
 \Cref{fig:linearity} shows the decrease in MMR according to the number of questions asked for various problem sizes.
@@
 Some directions for future works include developing new elicitation strategies, considering alternative heuristics; extending the elicitation to voting rules beyond scoring rules; eliciting preferences while restraining to concrete and easy questions.
-
-%We mention some directions for future works.
-%Further development of elicitation strategies, considering alternative heuristics, is an important direction. 
-%Second, elicitation could be extended to voting rules beyond scoring rules. 
-%Finally, an important direction of research  aims at eliciting preferences while restraining to concrete and easy questions.
-% Acknowledgments: We thank the reviewers for comments helping to improve the paper.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%% The acknowledgments section is defined using the "acks" environment
-%%% (rather than an unnumbered section). The use of this environment 
-%%% ensures the proper identification of the section in the article 
-%%% metadata as well as the consistent spelling of the heading.
-
-%\begin{acks}
-%If you wish to include any acknowledgments in your paper (e.g., to 
-%people or funding agencies), please do so using the `\texttt{acks}' 
-%environment. Note that the text of your acknowledgments will be omitted
-%if you compile your document with the `\texttt{anonymous}' option.
-%\end{acks}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%% The next two lines define, first, the bibliography style to be 
-%%% applied, and, second, the bibliography file to be used.
-%\bibliographystyle{abbrvnat} 
-%\bibliography{biblio}
-
-\newpage
-\bibliographystyle{named}
-%{\small \bibliography{biblio}}
-{\fontsize{9.7}{10.7}\selectfont \bibliography{biblio}}
+%
+% ---- Bibliography ----
+%
+% BibTeX users should specify bibliography style 'splncs04'.
+% References will then be sorted and formatted in the correct style.
+%
+\bibliographystyle{splncs04}
+\bibliography{biblio}
+%
 

### 2021-05-05 minimax.tex
todos done and updated

@@
 social choice theory can provide foundations for such applications.
-
 %The traditional approach to social choice assumes that both the social choice function and the full preference orderings of the agents (voters) are expressed beforehand.
 These represent two strong hypothesis.
-The traditional approach to social choice assumes that 1) the full preference orderings of the agents and 2) the social choice function are expressed beforehand. These represent two strong hypothesis.
-
+The traditional approach to social choice assumes that 1) the full preference orderings of the agents and 2) the social choice function are expressed beforehand. These represent two strong hypotheses.
 Requiring agents to express full preference orderings can be prohibitively costly (in terms of cognitive and communication cost).
@@
 We compare the effectiveness of several questioning strategies based on the current knowledge of the rule and preferences.
-To summarize our contributions: 1) we provide a novel mechanism for eliciting a voting rule by translating abstract questions about weights to a choice of an alternative given a concrete profile; 2) we show that with our elicitation method it is possible to reach low regret with a reasonable number of questions; 3) we present elicitation strategies that achieve good results within reasonable computation time; 4) we show that for the class of rule considered, asking a few questions to the chair suffice to reach low regret; 5) our experiments suggest that low degree of similarity among preferences (as in impartial culture) is a more challenging setting than less varied profiles.
+To summarize our contributions: 1) we provide a novel mechanism for eliciting a voting rule by translating abstract questions about weights to a choice of an alternative given a concrete profile; 2) we show that with our elicitation method it is possible to reach low regret with a reasonable number of questions; 3) we present elicitation strategies that achieve good results within reasonable computation time; 4) we show that for the class of rules considered, asking a few questions to the chair suffice to reach low regret; 5) our experiments suggest that low degree of similarity among preferences (as in impartial culture) is a more challenging setting than less varied profiles.
 %\begin{itemize}
@@
 %	\item the elicitation strategies that we provide, in particular Pessimistic, achieve good results within reasonable computation time; %for small problem sizes;
-%	\item we showed that for the class of rule considered, asking a few questions to the chair suffice to reach low regret;
+%	\item we showed that for the class of rules considered, asking a few questions to the chair suffice to reach low regret;
 %	\item our experiments suggest that low degree of similarity among preferences %rankings 
@@
 
-The following propositions (with proofs in Appendix) show that the procedure for completing a partial profile,  proposed by Lu and Boutilier \cite{Lu2011} when considering a fixed weight vector, also applies in our setting.
+The following propositions show that the procedure for completing a partial profile,  proposed by Lu and Boutilier \cite{Lu2011} when considering a fixed weight vector, also applies in our setting.
 We write $a \pprefeq_j b$ iff $a \ppref_j b \lor a = b$ and adopt the canonical notation when considering a relation as a function, writing ${\pprefeq_j}(x)$ for $\set{y \suchthat x \pprefeq_j y}$.
@@
 
+\begin{proof}[Proof Sketch]
+	Consider our knowledge $\pprefeq_j$ about the preference of the agent $j$. 
+	The adversary's goal is to make the score of $y$ as high as possible and the score of $x$ as low as possible. 
+	To do this, he should complete $\ppref_j$ to $\pref_j$ by putting above $x$ as many alternatives as he can, that is, all the alternatives except those that are known to be worse than $x$ (those $a$ such that $x \pprefeq_j a$); and similarly, he should put below $y$ all the alternatives he can.
+Two conditions must be excluded for $a$ to go below $y$.
+The alternatives such that $a \pprefeq_j y$ can’t be put below $y$.
+	Furthermore, the first objective must take priority over the second one: when an alternative should go above $x$ according to the first objective (because $¬(x \pprefeq_j a)$), and $x$ is known to be better than $y$ (thus $x \pprefeq_j y$), then $a$ should be put above $x$ (irrespective of whether $a \pprefeq_j y$), which will move both $x$ and $y$ one rank lower than if $a$ had been put below $y$.
+	This maximizes the adversary’s interests: because the weight vector is convex, the difference of scores will be lower when both alternatives are ranked lower (Equation \ref{eq:convexity}), and that difference of scores is in favor of $x$ when $x \ppref_j y$, thus to be minimized from the point of view of the adversary.
+\end{proof}
+
 \begin{proposition} \label{claim:rankPMR}
@@
 \end{proposition}
+
+\begin{proof}[Proof]
+	The rank of $x$ is directly obtained from Eq.(\ref{eq:complx}).
+The rank of $y$ is obtained by complementing Eq.(\ref{eq:comply}), obtaining $a \prefeq_j y ⇔ (a \pprefeq_j y) ∨ ((x \pprefeq_j y) ∧ ¬(x \pprefeq_j a))$, and, observing that $a \pref_j y ⇔ a ≠ y ∧ a \prefeq_j y$, obtaining that $a \pref_j y$ if and only if
+	\begin{equation}
+		\label{eq:betteryinter}
+		(a \neq y) ∧ [(a \pprefeq_j y) ∨ ((x \pprefeq_j y) ∧ ¬(x \pprefeq_j a))],
+	\end{equation} 
+	or equivalently, if and only if
+	\begin{equation}
+		\label{eq:bettery}
+		%a \pref_j y ⇔ 
+		(a \ppref_j y) ∨ ((x \pprefeq_j y) ∧ ¬(x \pprefeq_j a)).
+	\end{equation} 
+	Indeed, \eqref{eq:betteryinter} $⇒$ \eqref{eq:bettery}, and \eqref{eq:bettery} $⇒$ \eqref{eq:betteryinter} because $(x \pprefeq_j y) ∧ ¬(x \pprefeq_j a) ⇒ a ≠ y$ (as when $a = y$, $(x \pprefeq_j y)$ and $¬(x \pprefeq_j a)$ are opposite claims).
+Suffices now to rewrite \cref{eq:bettery} to let the two disjuncts designate disjoint sets:
+	\begin{equation}
+		\label{eq:betteryfinal}
+		a \pref_j y ⇔ 
+		(a \ppref_j y) ∨ ((x \pprefeq_j y) ∧ ¬(x \pprefeq_j a) ∧ ¬(a \ppref_j y)).
+	\end{equation}
+\end{proof}
+
 Note that in \cref{claim:rankPMR}, in the case $(x \pprefeq_j y)$, $\beta$ is the number of alternatives incomparable with both $x$ and $y$.
@@
 \end{proposition}
+
+\begin{proof}[Proof]
+	\label{proof:chairQuestions}
+	Define a linear order $>_1$ over $A$ as placing $a$ at rank $r$, $b$ at rank $r + 1$, and the remaining alternatives arbitrarily. 
+	Define a linear order $>_2$ over $A$ as placing $a$ at rank $r + 2$, $b$ at rank $r + 1$, and the remaining alternatives arbitrarily.
+	Define an arbitrary linear ordering $>$ over $A \setminus \set{a, b}$. 
+	Define a linear order $>_3$ as placing $a$ first, $b$ second, and following the order of $>$ for the remaining positions.
+	Finally, define a linear order $>_4$ as placing $b$ first, $a$ second, and following the \emph{inverse} order of $>$ for the remaining positions.
+
+	Define $P$ as the profile of $3 (p + q)$ agents containing $q$ times $>_1$, $p$ times $>_2$, and $>_3$ and $>_4$ each $p + q$ times.
+	As a result, $a$ obtains the following ranks: $q$ times $r$, $p$ times $r + 2$, $p + q$ times first, and $p + q$ times second.
+The alternative $b$ obtains the ranks $r + 1$, $2$ and $1$, each $p + q$ times.
+Consider any alternative $c \in A \setminus \set{a, b}$.
+Its score is maximal when it comes first in $>_1$, first in $>_2$ and first in $>$, by convexity of the weights.
+In that case, $c$ is positioned at the ranks $1$, $3$ and $m$, each $p + q$ times.
+
+	Letting $s(x)$ denote the score of $x$ at $P$, we obtain $s(a) = q w_r + p w_{r + 2} + (p + q) w_1 + (p + q) w_2$, thus, $s(a) ≥ (p + q) w_m + (p + q) w_1 + (p + q) w_2$; $s(b) = (p + q) w_{r + 1} + (p + q) w_2 + (p + q) w_1$; and, $\forall c \in A \setminus \set{a, b}$,
+	$s(c) ≤ (p + q) w_1 + (p + q) w_3 + (p + q) w_m$.
+It follows that $a$ or $b$ maximize $s$ (as $s(a) ≥ s(c)$).
+We conclude by observing that $a \in f(P) ⇔ s(a) ≥ s(b) ⇔ q w_r + p w_{r + 2} ≥ (p + q) w_{r + 1} ⇔ w_r - w_{r + 1} ≥ (p / q) (w_{r + 1} - w_{r + 2})$, and similarly for $b \in f(P)$.
+\end{proof}
 
@@
 
+\begin{figure}
+	\caption{Average MMR (normalized by $n$) after $k$ questions with Pessimistic strategy for different datasets. (20 runs)}
+	\label{fig:linearity2}
+	\begin{tikzpicture}
+		\pgfplotsset{
+			every axis legend/.append style={
+				at={(0.5,1.1)},
+				anchor=south
+			},
+		}
+		\begin{axis}[
+			y=80,
+			legend columns=3,
+			xlabel=Number of Questions,
+			ylabel=MMR/n,
+			ytick={0,0.5,1},
+			xtick distance=100,
+			xtick pos=left,
+			ymajorgrids=true,
+			ytick style={draw=none},
+			ymin=0,
+			ymax=1,
+			xmin=0,
+			xmax=1000,
+			yticklabels={0,0.5,1},
+			legend style={font=\footnotesize}]
+
+			%			\addlegendimage{mark=*,violet,mark size=2}
+			\addlegendimage{mark=halfsquare right*,brown,mark size=2}
+			\addlegendimage{mark=diamond*,red,mark size=2}
+			\addlegendimage{mark=pentagon*,cyan,mark size=2}
+			\addlegendimage{mark=halfcircle*,violet,mark size=2}
+			\addlegendimage{mark=*,pink,mark size=2}
+			\addlegendimage{mark=triangle*,green,mark size=2}
+			\addlegendimage{mark=halfsquare left*,blue,mark size=2}
+			\addlegendimage{mark=square*,teal,mark size=2}
+			\addlegendimage{mark=halfsquare*,magenta,mark size=2}
+
+			%			\addplot[thick, mark=triangle*, mark size = {2}, mark indices = {35}, teal] table [x=k, y=5.10]{data/normalizedLin.dat};
+			%			\addlegendentry{m=5, n=10}
+			%			\addplot[thick, mark=*, mark size = {2}, mark indices = {45}, violet] table [x=k, y=5.15]{data/normalizedLin.dat};
+			%			\addlegendentry{m=5, n=15}
+			\addplot[thick, mark=halfsquare right*, mark size = {2}, mark indices = {120}, brown] table [x=k, y=5.20]{data/linearity_redone.dat};
+			\addlegendentry{m=5, n=20}
+			\addplot[thick, mark=diamond*, mark size = {2}, mark indices = {150}, red] table [x=k, y=10.20]{data/linearity_redone.dat};
+			\addlegendentry{m=10, n=20}
+			%			\addplot[thick, mark=pentagon*, mark size = {2}, mark indices = {300}, cyan] table [x=k, y=10.30]{data/normalizedLin.dat};
+			%			\addlegendentry{m=10, n=30}
+			\addplot[thick, mark=pentagon*, mark size = {2}, mark indices = {240}, cyan] table [x=k, y=11.30]{data/linearity_redone.dat};
+			\addlegendentry{m=11, n=30}
+			\addplot[thick, mark=halfcircle*, mark size = {2}, mark indices = {400}, violet] table [x=k, y=tshirts]{data/linearity_redone.dat};
+			\addlegendentry{tshirts m11n30}
+			\addplot[thick, mark=*, mark size = {2}, mark indices = {400}, pink] table [x=k, y=courses]{data/linearity_redone.dat};
+			\addlegendentry{courses m9n146}
+			\addplot[thick, mark=triangle*, mark size = {2}, mark indices = {400}, green] table [x=k, y=9.146]{data/linearity_redone.dat};
+			\addlegendentry{m=9, n=146}
+			\addplot[thick, mark=halfsquare left*, mark size = {2}, mark indices = {200}, blue] table [x=k, y=14.9]{data/linearity_redone.dat};
+			\addlegendentry{m=14, n=9}
+			\addplot[thick, mark=square*, mark size = {2}, mark indices = {60}, teal] table [x=k, y=skate]{data/linearity_redone.dat};
+			\addlegendentry{skate m14n9}
+			\addplot[thick, mark=halfsquare*, mark size = {2}, mark indices = {400}, magenta] table [x=k, y=15.30]{data/linearity_redone.dat};
+			\addlegendentry{m=15, n=30}
+		\end{axis}
+	\end{tikzpicture}
+\end{figure}
+
 \begin{table}[ht]
@@
 
+\begin{table}
+	\caption{Average MMR in problems of size $(10, 20)$ after $400$ questions, among which $q_c$ to the chair. (20 runs redone with penalty)}
+	\label{tab:twoP4002}
+	\begin{tabular}{S[table-figures-integer=3, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=1]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=1]}
+		\toprule
+		{$q_c$} & {2 ph.\ ca} & {sd} & {2 ph.\ ac} & {sd} \\
+		\midrule
+		0 & 0.86 & 0.72 & 0.73 & 0.67 \\
+		15 & 0.92 & 0.82 & 0.93	& 0.96  \\
+		30 & 0.9 & 0.97 & 0.72	& 0.7 \\
+		50 & 1.36 & 1.29 & 1.38	& 1.17 \\
+		100 & 1.9 & 1.72 & 2.5	& 1.46  \\
+		150 & 4.4 & 2.09 & 4.23 & 1.53 \\
+		200 & 6.05	& 1.53  & 6.06 & 1.61 \\
+		250 & 8.27	& 1.54& 8.86 & 1.38 \\
+		300 &11.54	& 1.07& 11.82 &1.25 \\
+		350 &15.39	& 0.61 &15.54	&0.73 \\
+		400 &20.0 & 0.0 & 20.0 & 0.0 \\
+		\bottomrule
+	\end{tabular}
+\end{table}
+
 The experiments so far let the strategy free to question either the chair or an agent at each step.

### 2021-05-06 minimax.tex
small changes to save space

@@
 	\end{sloppypar}
-
+	\vspace{-0.5cm}
 	\begin{eqnarray}
@@
 	The adversary's goal is to make the score of $y$ as high as possible and the score of $x$ as low as possible. 
-	To do this, he should complete $\ppref_j$ to $\pref_j$ by putting above $x$ as many alternatives as he can, that is, all the alternatives except those that are known to be worse than $x$ (those $a$ such that $x \pprefeq_j a$); and similarly, he should put below $y$ all the alternatives he can.
+	To do this, he should complete $\ppref_j$ to $\pref_j$ by placing above $x$ as many alternatives as possible; that is, all the alternatives except those that are known to be worse than $x$ (those $a$ such that $x \pprefeq_j a$); and similarly, he should put below $y$ all the alternatives he can.
 Two conditions must be excluded for $a$ to go below $y$.
@@
 	Furthermore, the first objective must take priority over the second one: when an alternative should go above $x$ according to the first objective (because $¬(x \pprefeq_j a)$), and $x$ is known to be better than $y$ (thus $x \pprefeq_j y$), then $a$ should be put above $x$ (irrespective of whether $a \pprefeq_j y$), which will move both $x$ and $y$ one rank lower than if $a$ had been put below $y$.
-	This maximizes the adversary’s interests: because the weight vector is convex, the difference of scores will be lower when both alternatives are ranked lower (Equation \ref{eq:convexity}), and that difference of scores is in favor of $x$ when $x \ppref_j y$, thus to be minimized from the point of view of the adversary.
+	This maximizes the adversary’s interests: because the weight vector is convex, the score difference will be lower when both alternatives are ranked lower (Equation \ref{eq:convexity}), and that difference of scores is in favor of $x$ when $x \ppref_j y$, thus to be minimized from the the adversary's point of view.
 \end{proof}
@@
 	\end{equation}
+\vspace{-0.5cm}
 \end{proof}
@@
 	Define a linear order $>_1$ over $A$ as placing $a$ at rank $r$, $b$ at rank $r + 1$, and the remaining alternatives arbitrarily. 
-	Define a linear order $>_2$ over $A$ as placing $a$ at rank $r + 2$, $b$ at rank $r + 1$, and the remaining alternatives arbitrarily.
+	Define %a linear order 
+	$>_2$ over $A$ as placing $a$ at rank $r + 2$, $b$ at rank $r + 1$, and the remaining alternatives arbitrarily.
 	Define an arbitrary linear ordering $>$ over $A \setminus \set{a, b}$. 
@@
 %Indeed, it can be beneficial to split efforts asking questions to the chair and to agents, depending on which is estimated to be more informative.
-We define here the various strategies we tested experimentally. A strategy tells us, given the current partial knowledge $(\pprofile, W)$, which question to ask next.
+We define here various strategies; %we tested experimentally. 
+a strategy tells us, given the current partial knowledge $(\pprofile, W)$, which question to ask next.
 
@@
 \label{sec:experiments}
-We  performed a number of numerical experiments using both real data and generated profiles in order to validate our approach and test the performance of our elicitation strategies.
+We  performed a number of numerical experiments using both real data and randomly generated profiles in order to validate our approach and test the performance of our elicitation strategies.
 %Our experiments are described by topic here below.
@@
 %We adopt IC because it is a more challenging situation: as can be expected intuitively , the number of questions to be asked decrease with less varied profiles. 
-To generate the weights of the scoring rule, we first draw $m \!-\!
-1$ numbers uniformly at random (in the interval $\intvl{0,1}$ representing weight ``differences''), normalize and sort them; a sequence of convex decreasing weight is then obtained by a decumulative sum.
-The penalty parameters for the Pessimistic and Extended pessimistic strategies are set to  $\epsilon_{\text{chair}} = 1.1$, $\epsilon'_{\text{chair}} = 10^{-6}$, $\epsilon_{\text{agent}} = 1.0$ and $\epsilon'_{\text{agent}} = 0$.
+To generate the scoring rule weights, we first draw $m \!-\!
+1$ numbers uniformly at random (in the interval $\intvl{0,1}$ representing weight ``differences''), normalize and sort them; a sequence of convex decreasing weightx is then obtained by a decumulative sum.
+The penalty parameters for the Pessimistic and Extended pessimistic strategies are  $\epsilon_{\text{chair}} = 1.1$, $\epsilon'_{\text{chair}} = 10^{-6}$, $\epsilon_{\text{agent}} = 1.0$ and $\epsilon'_{\text{agent}} = 0$.
 

### 2021-05-10 minimax.tex
changes after meeting

@@
 \usepackage[hypertexnames=false]{hyperref}
+
+\NewDocumentCommand{\commentOC}{m}{\textcolor{blue}{\small$\big[$OC: #1$\big]$}}
+\NewDocumentCommand{\commentBN}{m}{\textcolor{magenta}{\small$\big[$BN: #1$\big]$}}
+\NewDocumentCommand{\commentPV}{m}{\textcolor{red}{\small$\big[$PV: #1$\big]$}}
+
+\theoremstyle{remark}
+\newtheorem*{example*}{Example}
+
 %\usepackage{cleveref}
@@
 
-%\author{Submission 15}
-%\institute{}
+\author{Submission 15}
+\institute{}
 
-\author{Beatrice Napolitano\inst{1}\orcidID{0000-0002-3887-6206} \and
-Olivier Cailloux\inst{1}\and
-Paolo Viappiani\inst{2}}
-%
-\authorrunning{B. Napolitano et al.}
-% First names are abbreviated in the running head.
-% If there are more than two authors, 'et al.' is used.
-%
-\institute{Université Paris-Dauphine, Université PSL, CNRS, LAMSADE \and
-LIP6, UMR 7606, CNRS and Sorbonne Universit\'e \\
-\email{\{beatrice.napolitano, olivier.cailloux\}@dauphine.fr}\\
-%\url{http://www.springer.com/gp/computer-science/lncs} \and
-%ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
-\email{paolo.viappiani@lip6.fr}}
+%\author{Beatrice Napolitano\inst{1}\orcidID{0000-0002-3887-6206} \and
+%Olivier Cailloux\inst{1}\and
+%Paolo Viappiani\inst{2}}
+%%
+%\authorrunning{B. Napolitano et al.}
+%% First names are abbreviated in the running head.
+%% If there are more than two authors, 'et al.' is used.
+%%
+%\institute{Université Paris-Dauphine, Université PSL, CNRS, LAMSADE \and
+%LIP6, UMR 7606, CNRS and Sorbonne Universit\'e \\
+%\email{beatrice.napolitano@dauphine.fr}}
 
 \maketitle              % typeset the header of the contribution
+\vspace{4em}
 %
@@
 %While most of the focus in the research community has been in dealing with incomplete agent preferences, 
+\commentBN{here are two examples of situations. (divide in two par)}
 Consider, as an example, a chair that is about to hire a new employee, whose performances are evaluated by several experts.
@@
 However, they might be willing to answer a few questions requiring to select who should be the winner out of specific profiles.
+
 %The information provided can be used to   % to determine their employee of choice.
@@
 We now introduce some basic concepts.
-We consider a set $A$ of $m$ alternatives (products, restaurants, public projects, job candidates, etc.), an infinite set $\N$ of potential agents and a specific finite set of agents $N^* \subset \N$.
+We consider a set $A$ of $m$ alternatives (products, restaurants, public projects, job candidates, etc.), an infinite set $\N$ of potential agents.
 
@@
 A profile is equivalently represented by $\profile=(v_j, j \in N)$ where $v_j(x) \in \set{1, \ldots, m}$ denotes the rank of alternative $x$ in the preference order $\pref_j$. 
-A social choice function $f : \cup_{\emptyset ≠ N \subset \N} \linors^N \rightarrow \powersetz{A}$ associates to each profile a set of (tied) winners, where $\powersetz{A}$ is the powerset of $A$ excluding the empty set.
+A social choice function $f : \cup_{\emptyset ≠ N \subset \N, N \text{finite}} \linors^N \rightarrow \powersetz{A}$ associates to each profile a set of (tied) winners, where $\powersetz{A}$ is the powerset of $A$ excluding the empty set.
 Among the many possible social choice functions, we consider convex {\em positional scoring rules (PSRs)}.
@@
 	\label{eq:srule}
-	s(x; \profile, \w) = \sum_{j=1}^{n} w_{v_j(x)}
+	s(x; \profile, \w) = \sum_{j\in N} w_{v_j(x)}
 	= \sum_{r=1}^{m} \alpha^{x}_r w_r\ .
@@
 
-Let $\profile^* = (\pref_j^*, j \in N^*)$ and $\w^*$ denote the profile and weight vector, unknown to us, that represent the preferences of the agents in $N^*$ and of the chair.
+Consider a specific finite set of agents $N^* \subset \N$, let $\profile^* = (\pref_j^*, j \in N^*)$ and $\w^*$ denote the profile and weight vector, unknown to us, that represent the preferences of the agents in $N^*$ and of the chair.
 
@@
 Since scoring rules are additively decomposable, we can consider separately the contribution of each agent to the total score.
-Thus, we can write the actual regret of choosing $x$ instead of $y$ as $s(y; \profile,\w) - s(x; \profile, \w) = \sum_{j=1}^n w_{v_j(y)} - w_{v_j(x)}$, and we obtain \[\PMR(x,y; \pprofile, W) =  \max_{\w \in W} \sum_{j=1}^{n} \max_{v_j \in C(\succ_j^p)} [w_{v_j(y)} - w_{v_j(x)}].\]
+Thus, we can write the actual regret of choosing $x$ instead of $y$ as $s(y; \profile,\w) - s(x; \profile, \w) = \sum_{j \in N} w_{v_j(y)} - w_{v_j(x)}$, and we obtain \[\PMR(x,y; \pprofile, W) =  \max_{\w \in W} \sum_{j \in N} \max_{v_j \in C(\succ_j^p)} [w_{v_j(y)} - w_{v_j(x)}].\]
 %Note that in general the inner max depends on the weights chosen by the outer max.
@@
 	\begin{sloppypar}
-		There exists a completion $\hat{\profile} \in C(\pprofile)$ of the profile $\profile$ such that ${\PMR(x,y; \pprofile, W) = \max_{\w \in W} [ s(y; \hat{\profile}, \w) - s(x; \hat{\profile}, \w) ]}$ and such that the linear order $\hat{v}_{j}$ of each agent $j$ satisfies:
+		There exists a completion $\hat{\profile} \in C(\pprofile)$ of the partial profile $\pprofile$ such that ${\PMR(x,y; \pprofile, W) = \max_{\w \in W} [ s(y; \hat{\profile}, \w) - s(x; \hat{\profile}, \w) ]}$ and such that the linear order $\hat{v}_{j}$ of each agent $j$ satisfies:
 	\end{sloppypar}
@@
 		\PMR(x,y; \pprofile, W)  
-		& = \max_{w \in W} \sum_{j=1}^n w_{\hat{v}_j(y)} - w_{\hat{v}_j(x)} \\ 
+		& = \max_{w \in W} \sum_{j \in N} w_{\hat{v}_j(y)} - w_{\hat{v}_j(x)} \\ 
 		& = \max_{w \in W} \sum_{r=1}^m (\hat{\alpha}_{r}^{y} - \hat{\alpha}_{r}^{x}) w_i 
@@
 
-\begin{example}
+\begin{example*}
 	Suppose we want to ask the following question to the chair: $w_{2} - w_{3} ≥ 2 (w_{3} - w_{4})$. 
@@
 	Both $a$ and $b$ have scores higher than $c$ and $d$ for all convex weights, thus either $a$ or $b$ will be picked under our hypothesis; and $s(a) ≥ s(b) ⇔ w_2 + 2 w_4 ≥ 3 w_3$.
-	(the proof in Appendix presents the general method of constructing such profile.)
-\end{example}
+	Note that we can compress this profile by grouping agents with the same preference orders.
+In the proof, in fact, we show how to construct a profile where only four linear orders are possible.
+Each column of the new profile represent now the preference of a group of agents:
+	\begin{center}
+		$
+		\begin{array}{cccc}
+			\mathbf{1}&\mathbf{2}&\mathbf{3}&\mathbf{3} \\
+			c&d&a&b\\
+			a&c&b&a\\
+			b&b&c&d\\
+			d&a&d&c\\
+		\end{array}.
+		$
+	\end{center} 
+\end{example*}
 
@@
 			%			\addlegendentry{m=5, n=15}
-			\addplot[thick, mark=halfsquare right*, mark size = {2}, mark indices = {120}, brown] table [x=k, y=5.20]{data/normalizedLin.dat};
-			\addlegendentry{m=5, n=20}
-			\addplot[thick, mark=diamond*, mark size = {2}, mark indices = {150}, red] table [x=k, y=10.20]{data/normalizedLin.dat};
-			\addlegendentry{m=10, n=20}
-			%			\addplot[thick, mark=pentagon*, mark size = {2}, mark indices = {300}, cyan] table [x=k, y=10.30]{data/normalizedLin.dat};
-			%			\addlegendentry{m=10, n=30}
-			\addplot[thick, mark=pentagon*, mark size = {2}, mark indices = {240}, cyan] table [x=k, y=11.30]{data/normalizedLin.dat};
-			\addlegendentry{m=11, n=30}
-			\addplot[thick, mark=halfcircle*, mark size = {2}, mark indices = {400}, violet] table [x=k, y=tshirt]{data/normalizedLin.dat};
-			\addlegendentry{tshirts m11n30}
-			\addplot[thick, mark=*, mark size = {2}, mark indices = {400}, pink] table [x=k, y=courses]{data/normalizedLin.dat};
-			\addlegendentry{courses m9n146}
-			\addplot[thick, mark=triangle*, mark size = {2}, mark indices = {400}, green] table [x=k, y=9.146]{data/normalizedLin.dat};
-			\addlegendentry{m=9, n=146}
-			\addplot[thick, mark=halfsquare left*, mark size = {2}, mark indices = {200}, blue] table [x=k, y=14.9]{data/normalizedLin.dat};
-			\addlegendentry{m=14, n=9}
-			\addplot[thick, mark=square*, mark size = {2}, mark indices = {60}, teal] table [x=k, y=skate]{data/normalizedLin.dat};
-			\addlegendentry{skate m14n9}
-			\addplot[thick, mark=halfsquare*, mark size = {2}, mark indices = {400}, magenta] table [x=k, y=15.30]{data/normalizedLin.dat};
-			\addlegendentry{m=15, n=30}
-		\end{axis}
-	\end{tikzpicture}
-\end{figure}
-
-\begin{figure}
-	\caption{Average MMR (normalized by $n$) after $k$ questions with Pessimistic strategy for different datasets. (20 runs)}
-	\label{fig:linearity2}
-	\begin{tikzpicture}
-		\pgfplotsset{
-			every axis legend/.append style={
-				at={(0.5,1.1)},
-				anchor=south
-			},
-		}
-		\begin{axis}[
-			y=80,
-			legend columns=3,
-			xlabel=Number of Questions,
-			ylabel=MMR/n,
-			ytick={0,0.5,1},
-			xtick distance=100,
-			xtick pos=left,
-			ymajorgrids=true,
-			ytick style={draw=none},
-			ymin=0,
-			ymax=1,
-			xmin=0,
-			xmax=1000,
-			yticklabels={0,0.5,1},
-			legend style={font=\footnotesize}]
-
-			%			\addlegendimage{mark=*,violet,mark size=2}
-			\addlegendimage{mark=halfsquare right*,brown,mark size=2}
-			\addlegendimage{mark=diamond*,red,mark size=2}
-			\addlegendimage{mark=pentagon*,cyan,mark size=2}
-			\addlegendimage{mark=halfcircle*,violet,mark size=2}
-			\addlegendimage{mark=*,pink,mark size=2}
-			\addlegendimage{mark=triangle*,green,mark size=2}
-			\addlegendimage{mark=halfsquare left*,blue,mark size=2}
-			\addlegendimage{mark=square*,teal,mark size=2}
-			\addlegendimage{mark=halfsquare*,magenta,mark size=2}
-
-			%			\addplot[thick, mark=triangle*, mark size = {2}, mark indices = {35}, teal] table [x=k, y=5.10]{data/normalizedLin.dat};
-			%			\addlegendentry{m=5, n=10}
-			%			\addplot[thick, mark=*, mark size = {2}, mark indices = {45}, violet] table [x=k, y=5.15]{data/normalizedLin.dat};
-			%			\addlegendentry{m=5, n=15}
 			\addplot[thick, mark=halfsquare right*, mark size = {2}, mark indices = {120}, brown] table [x=k, y=5.20]{data/linearity_redone.dat};
@@
 		\midrule
-		0 & 0.66 & 0.67 & 0.65 & 0.65  \\
-		15 & 0.71 & 0.73 & 0.67	& 0.64 \\
-		30 & 0.62 & 0.5 & 0.8 & 0.62 \\
-		50 & 1.23 & 1.46 & 0.8 & 0.79 \\
-		100 & 2.03 & 1.56 & 1.88 & 1.02  \\
-		%		150 & 3.41 & 1.79 & 4.07 & 1.51 \\
-		200 & 4.61	& 1.35  & 6.53 & 2.0  \\
-		%		250 & 8.4 & 1.86 & 	7.69 & 1.24 \\
-		300 &11.07 & 0.86& 11.87 & 1.25 \\
-		%		350 &15.06 & 0.68&15.59 & 0.6 \\
-		400 &20.0 & 0.0 & 20.0 & 0.0 \\
-		\bottomrule
-	\end{tabular}
-\end{table}
-
-\begin{table}
-	\caption{Average MMR in problems of size $(10, 20)$ after $400$ questions, among which $q_c$ to the chair. (20 runs redone with penalty)}
-	\label{tab:twoP4002}
-	\begin{tabular}{S[table-figures-integer=3, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=1]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=1]}
-		\toprule
-		{$q_c$} & {2 ph.\ ca} & {sd} & {2 ph.\ ac} & {sd} \\
-		\midrule
 		0 & 0.86 & 0.72 & 0.73 & 0.67 \\
@@
 		100 & 1.9 & 1.72 & 2.5	& 1.46  \\
-		150 & 4.4 & 2.09 & 4.23 & 1.53 \\
+		%150 & 4.4 & 2.09 & 4.23 & 1.53 \\
 		200 & 6.05	& 1.53  & 6.06 & 1.61 \\
-		250 & 8.27	& 1.54& 8.86 & 1.38 \\
+		%250 & 8.27	& 1.54& 8.86 & 1.38 \\
 		300 &11.54	& 1.07& 11.82 &1.25 \\
-		350 &15.39	& 0.61 &15.54	&0.73 \\
+		%350 &15.39	& 0.61 &15.54	&0.73 \\
 		400 &20.0 & 0.0 & 20.0 & 0.0 \\

### 2021-05-11 minimax.tex
PMR and MR formulas in just one line

@@
 \begin{align}
-	\MaxR(x;\pprofile,W) & = \max_{y \in A} \PMR(x,y; \pprofile, W) \\ &= \max_{\w \in W} \max_{\profile \in C(\profile)} \Regret(x; \profile, \w).
+	\MaxR(x;\pprofile,W) & = \max_{y \in A} \PMR(x,y; \pprofile, W) %\\ &
+	= \max_{\w \in W} \max_{\profile \in C(\profile)} \Regret(x; \profile, \w).
 \end{align}
@@
 
-Observe that if $\MMR(\pprofile, W)\!=\!0$, then any $x^{*}_{\pprofile,W} \in A^*_{\pprofile, W}$ is a necessary winner: any valid completion of the profile and choice of $w \in W$ gives to $x^{*}_{\pprofile,W}$ the highest score.
+Observe that if $\MMR(\pprofile, W)\!=\!0$, then any $x^{*}_{\pprofile,W} \in A^*_{\pprofile, W}$ is a necessary winner: any valid completion of $\pprofile$ and any choice of $w \in W$ gives to $x^{*}_{\pprofile,W}$ the highest score.
 
@@
 		\PMR(x,y; \pprofile, W)  
-		& = \max_{w \in W} \sum_{j \in N} w_{\hat{v}_j(y)} - w_{\hat{v}_j(x)} \\ 
-		& = \max_{w \in W} \sum_{r=1}^m (\hat{\alpha}_{r}^{y} - \hat{\alpha}_{r}^{x}) w_i 
+		& = \max_{w \in W} \sum_{j \in N} w_{\hat{v}_j(y)} - w_{\hat{v}_j(x)} %\\ &
+		 = \max_{w \in W} \sum_{r=1}^m (\hat{\alpha}_{r}^{y} - \hat{\alpha}_{r}^{x}) w_i 
 	\end{align}

### 2021-05-12 minimax.tex
changes Table 2, second ex in Introduction and minors

--- 2021-05-10 minimax.tex
@@
 %While most of the focus in the research community has been in dealing with incomplete agent preferences, 
-\commentBN{here are two examples of situations. (divide in two par)}
-Consider, as an example, a chair that is about to hire a new employee, whose performances are evaluated by several experts.
+Here we provide two examples of such situations.
+
+Consider, as a first example, a chair that is about to hire a new employee whose performances are evaluated by several experts.
 The members of the chair may not have a voting rule in mind at the start of the process, and might not wish to agree on a specific voting rule.
@@
 
+Consider, as a second example, the reviewing process of a conference where the best paper must be elected.
+The agents express their preferences on the papers they reviewed, but they are not aware of the voting rule the Program Chair will apply when aggregating them.
+Nonetheless, reviewers are still willing to participate in the process.
+Also, the PC may not have a specific voting rule in mind, and she will find it hard to provide a precise scoring vector if asked.
+Maybe she strongly believes that being ranked once in the first position is “much more” valuable than being ranked two times second, but does not know exactly how much more (though she can judge example cases).
 %The information provided can be used to   % to determine their employee of choice.
@@
 The former are considered “observable”: acts of choice are translated to preference statements \cite[Ch.\ 1]{colell_microeconomic_1995}.
+\commentBN{In the rebuttal we add: There is no a priori reason to believe that questioning the chair in terms of this different parametric space would yield logically equivalent answers: research in experimental psychology shows that participants’ answers differ widely when changing the phrasing of preference-related questions [Lichtenstein and Slovic,	2012, doi: 10.1017/CBO9780511618031].
+To get out of such conundrums, we need a language considered “fundamental”.
+Questions of the form “In this profile, who should win?” arguably provides such a natural language.}
 
@@
 	Suppose we want to ask the following question to the chair: $w_{2} - w_{3} ≥ 2 (w_{3} - w_{4})$. 
-	We then show the following profile to the chair and ask who should win (each column is a preference of an agent).
+	We show the following profile to the chair and ask who should win (each column is a preference of an agent).
 	\begin{center}
@@
 \label{sec:experiments}
-We  performed a number of numerical experiments using both real data and randomly generated profiles in order to validate our approach and test the performance of our elicitation strategies.
+We  performed several numerical experiments using both real data and randomly generated profiles in order to validate our approach and test the performance of our elicitation strategies.
 %Our experiments are described by topic here below.
@@
 \textit{Courses}  (students voted on courses; $m \!=\! 9, n \!=\! 146$; referred to as AGH on PrefLib)
-and \emph{Skate} (judges vote on skaters at the Euros Pairs Short Program; $m \!=\! 14, n \!=\! 9$).
+and \emph{Skate} (judges voted on skaters at the Euros Pairs Short Program; $m \!=\! 14, n \!=\! 9$).
 % tee shirt designs voted by 
@@
 We first wonder how many questions should be asked in order to achieve low regret, fixed at $n / 10$: this is equivalent to the difference of score of an alternative $x$ that results from switching from a profile $P$ to a profile $P'$ where a tenth of the agents rank $x$ last instead of first.
-\cref{tab:lowRegret} shows results for various sizes. 
-%The results for various sizes are displayed in \cref{tab:lowRegret}. 
 Another interesting measure is the average number of questions asked to each participant before reaching zero regret.
-For example, in the case $m = 10, n = 20$, Pessimistic asks on average $49$ questions to the chair and $18$ questions to each agent (\cref{tab:Numquestions} provides more data).
+The results for various sizes are displayed in \cref{tab:questions}.
+%For example, in the case $m = 10, n = 20$, Pessimistic asks on average $49$ questions to the chair and $18$ questions to each agent (\cref{tab:Numquestions} provides more data).
 
-\begin{table}
-	\caption{Number of questions needed by Pessimistic strategy to reach an MMR of $\frac{n}{10}$ (represented by $k_{\MMR}$), by size.}
-	\label{tab:lowRegret}
-	\begin{tabular}{S[table-figures-decimal=0]S[table-figures-decimal=0]SS[table-figures-integer=3, table-figures-decimal=0]}
-		\toprule
-		{m} & {n} & {$\frac{n}{10}$} & {$k_{\MMR}$} \\
-		\midrule
-		5 & 10 & 1 & 60 \\
-		5 & 15 & 1.5 & 80 \\
-		5 & 20 & 2 & 110 \\
-		10 & 20 & 2 & 340 \\
-		10 & 30 & 3 & 527 \\
-		15 & 30 & 3 & 951 \\
-		\bottomrule
-	\end{tabular}
-\end{table}
+%\begin{table}
+%	\caption{Number of questions needed by Pessimistic strategy to reach an MMR of $\frac{n}{10}$ (represented by $k_{\MMR}$), by size.}
+%	\label{tab:lowRegret}
+%	\begin{tabular}{S[table-figures-decimal=0]S[table-figures-decimal=0]SS[table-figures-integer=3, table-figures-decimal=0]}
+%		\toprule
+%		{m} & {n} & {$\frac{n}{10}$} & {$k_{\MMR}$} \\
+%		\midrule
+%		5 & 10 & 1 & 60 \\
+%		5 & 15 & 1.5 & 80 \\
+%		5 & 20 & 2 & 110 \\
+%		10 & 20 & 2 & 340 \\
+%		10 & 30 & 3 & 527 \\
+%		15 & 30 & 3 & 951 \\
+%		\bottomrule
+%	\end{tabular}
+%\end{table}
 
@@
 
+%\begin{table}[ht]
+%	\caption{Average number of questions asked to the chair ($q_{c}$) and to the agents (\textit{$q_{v}$}) by Pessimistic strategy to reach zero regret on the datasets of \cref{fig:linearity}.}
+%	\label{tab:Numquestions}
+%	\begin{tabular}{cS[table-number-alignment = right, table-figures-integer=4]@{ ± }S[table-number-alignment = left, table-figures-integer=2]S[table-number-alignment = right, table-figures-integer=4]@{ ± }S[table-number-alignment = left, table-figures-integer=2]}
+%		\toprule
+%		{dataset} & {$q_{c}$} & {sd} & {$q_{v}$} & {sd} \\
+%		\midrule
+%		m5n10 	&	8.4		& 2.67 		& 61		& 6.25\\
+%		m5n20 	&	13.6	& 6.38		& 118.9		& 14.4\\
+%		m10n20 	&	48.5	& 6			& 362.4		& 47.6	\\
+%		m10n30 	&	56.3	& 11.18		& 598.1 	& 75.19	\\
+%		m15n30 	&	24.5	& 8.77		& 775.5		& 8.77	\\
+%		m14n9 	&	58.3	& 33.66		& 370.9		& 40.54	\\
+%		m14n9-2 &	56.2	& 34.11		& 368.7		& 53.07 \\
+%		skate 	&	0		& 0			& 103.3		& 2.21	\\
+%		tshirt  &	30.0	& 5.87		& 961.2		& 23.04	\\
+%		courses & 0			& 0			& 950		& 5.08	\\	
+%		\bottomrule
+%	\end{tabular}
+%\end{table}
+
 \begin{table}[ht]
-	\caption{Average number of questions asked to the chair ($q_{c}$) and to the agents (\textit{$q_{v}$}) by Pessimistic strategy to reach zero regret on the datasets of \cref{fig:linearity}.}
-	\label{tab:Numquestions}
-	\begin{tabular}{cS[table-number-alignment = right, table-figures-integer=4]@{ ± }S[table-number-alignment = left, table-figures-integer=2]S[table-number-alignment = right, table-figures-integer=4]@{ ± }S[table-number-alignment = left, table-figures-integer=2]}
+	\caption{Analysis of the questions asked by Pessimistic strategy on the datasets of \cref{fig:linearity}.
+The column $q_{c TR}$ ($q_{c ZR}$) indicates the average number of questions asked to the chair to reach a threshold regret of $\frac{n}{10}$ (zero regret).
+The column $[Q1_{v} | M_{v} | Q3_{v}]_{TR}$ ($[Q1_{v} | M_{v} | Q3_{v}]_{ZR}$) represents the average of the quartiles of the questions asked to the voters to reach $\frac{n}{10}$ regret (zero regret).}
+	\label{tab:questions}
+	\begin{tabular}{cccS[table-number-alignment = right, table-figures-integer=2]@{ ± }S[table-number-alignment = left, table-figures-integer=2]cS[table-number-alignment = right, table-figures-integer=2]@{ ± }S[table-number-alignment = left, table-figures-integer=2]c}
 		\toprule
-		{dataset} & {$q_{c}$} & {sd} & {$q_{v}$} & {sd} \\
+		{dataset} & m & n &{$q_{c TR}$} & {sd} & {$[Q1_{v} | M_{v} | Q3_{v}]_{TR}$} & {$q_{c ZR}$} & {sd} & {$[Q1_{v} | M_{v} | Q3_{v}]_{ZR}$} \\
 		\midrule
-		m5n10 	&	8.4		& 2.67 		& 61		& 6.25\\
-		m5n20 	&	13.6	& 6.38		& 118.9		& 14.4\\
-		m10n20 	&	48.5	& 6			& 362.4		& 47.6	\\
-		m10n30 	&	56.3	& 11.18		& 598.1 	& 75.19	\\
-		m15n30 	&	24.5	& 8.77		& 775.5		& 8.77	\\
-		m14n9 	&	58.3	& 33.66		& 370.9		& 40.54	\\
-		m14n9-2 &	56.2	& 34.11		& 368.7		& 53.07 \\
-		skate 	&	0		& 0			& 103.3		& 2.21	\\
-		tshirt  &	30.0	& 5.87		& 961.2		& 23.04	\\
-		courses & 0			& 0			& 950		& 5.08	\\	
+		m5n20 & 5&20&0&0&[4.3 | 4.95 | 5.84 ]&5.25&9.59&[5.36 | 6.15 | 7.21]\\
+		m10n20&10&20&0&0&[13.85 | 16.1| 18.41]&31.95&26.62&[19.66 | 21.78 | 24.7]\\
+		m11n30&11&30&0&0&[16.55|19|22.26]&45.15&40.14&[23.07|25.7|28.89]\\
+		tshirts&11&30&0&0&[12.92 | 16.17 |19.3]&\textendash&\textendash&\textendash\\
+		courses&9&146&0&0&[6.35 |7 |7]&0&0&[6.8 | 7 |7]\\
+		%m9n146&9&146&0&0&[1.94 |8 |9.25]&999.3&0.47&0&0&[1.94|8|9.25]&999.3&0.47\\
+		m14n9&14&9&5.4&9.49&[30.3|33.45|36.65]&64.05&40.37&[37.55|40.5|44.3]\\
+		skate&14&9&0&0&[11.35|11.8|12.25]&0&0&[11.5|11.9|12.7] \\
+		m15n30&15&30&0&0&[24.95|29.5|33.68]&\textendash&\textendash&\textendash \\
+
 		\bottomrule
@@
 These numbers are to be compared with the MMR value reached after 400 questions with the Pessimistic strategy (displayed in \cref{fig:linearity}), which is $0.6$; the Pessimistic strategy asks on average $48$ questions to the chair in this setting.
+\commentBN{This is not true anymore, after 400 questions it reaches $0.9$ with 0 questions to the chair, after 500 questions it reaches $0.4$ with $11.05$ question to the chair ($\sigma=12.34$).
+The data in Table 2 is after 582 questions.}
 The line $q_c = 0$, where no question is asked to the chair, suggest that it is possible to obtain a good-quality recommendation while knowing only that the voting rule is a scoring rule with convex weights, which is our basic hypothesis.

### 2021-05-12 minimax.tex
Phrasing

@@
 \begin{align}
-	\MaxR(x;\pprofile,W) & = \max_{y \in A} \PMR(x,y; \pprofile, W) \\ &= \max_{\w \in W} \max_{\profile \in C(\profile)} \Regret(x; \profile, \w).
+	\MaxR(x;\pprofile,W) & = \max_{y \in A} \PMR(x,y; \pprofile, W) = \max_{\w \in W} \max_{\profile \in C(\profile)} \Regret(x; \profile, \w).
 \end{align}
@@
 Such questions have clear semantics whose understanding can be assumed to be shared by the chair, contrary to abstract questions about weights.
-Moreover, this way of questioning the chair is independent of the voting rule that is being elicited. Questions about weights only make sense when considering PSRs.
+Moreover, this way of questioning the chair is independent of the voting rule that is being elicited; whereas questions about weights only make sense when considering PSRs.
 Asking who should win in specific profiles has been used in experimental settings investigating the feeling of justice of individuals \cite{Giritligil2005}, but, to the best of our knowledge, the use of such questions to systematically guide an elicitation process about voting rules is novel.
@@
 The former are considered “observable”: acts of choice are translated to preference statements \cite[Ch.\ 1]{colell_microeconomic_1995}.
-\commentBN{In the rebuttal we add: There is no a priori reason to believe that questioning the chair in terms of this different parametric space would yield logically equivalent answers: research in experimental psychology shows that participants’ answers differ widely when changing the phrasing of preference-related questions [Lichtenstein and Slovic,	2012, doi: 10.1017/CBO9780511618031].
+
+Although questioning in terms of profiles and in terms of weights is logically equivalent in our setting, there is no a priori certainty that questioning the chair using different phrasing would yield logically equivalent answers: research in experimental psychology shows that participants’ answers differ widely when changing the phrasing of preference-related questions [Lichtenstein and Slovic,	2012, doi: 10.1017/CBO9780511618031].
 To get out of such conundrums, we need a language considered “fundamental”.
-Questions of the form “In this profile, who should win?” arguably provides such a natural language.}
+Questions of the form “In this profile, who should win?” arguably provides such a natural language.
 
@@
 	Suppose we want to ask the following question to the chair: $w_{2} - w_{3} ≥ 2 (w_{3} - w_{4})$. 
-	We show the following profile to the chair and ask who should win (each column is a preference of an agent).
+	We show the profile in Figure xx, left, to the chair and ask who should win (each column is a preference of an agent).
 	\begin{center}
@@
 	Both $a$ and $b$ have scores higher than $c$ and $d$ for all convex weights, thus either $a$ or $b$ will be picked under our hypothesis; and $s(a) ≥ s(b) ⇔ w_2 + 2 w_4 ≥ 3 w_3$.
-	Note that we can compress this profile by grouping agents with the same preference orders.
-In the proof, in fact, we show how to construct a profile where only four linear orders are possible.
-Each column of the new profile represent now the preference of a group of agents:
+	Figure xx, right, shows the same profile using a compressed view, the numbers in bold indicating the number of voters (agents?) having the preference in the corresponding column.
+As the proof shows, constructed profiles require only four different linear orders.
 	\begin{center}
@@
 
-As part of our contribution, an open-source library, to reproduce our experiments and perform many more, will be made publicly available. (URL not displayed for anonymity.)
+As part of our contribution, an open-source library, to reproduce our experiments and perform many more, will be made publicly available. (URL not displayed for reasons of anonymity.)
 %and serve as a basis for further research

### 2021-05-13 minimax.tex
combined F1, new Table3, Table 2 explained and formatted, ref olivier text

@@
 \newtheorem*{example*}{Example}
+\usepackage{caption}
+\usepackage{subcaption}
 
@@
 
-Since in many practical situations there would be too many possible winners but no necessary winners, several works addressed the problem of agent preferences elicitation using a variety of approaches (minimax regret, Bayesian methods, etc.) with the goal of converging to a necessary winner \cite{Naamani-Dery2015,Kalech2011,Lu2011,Pini2009,Benabbou2016,Dey2016,Dey2016_2}.
+Since in many practical situations there would be too many possible winners but no necessary winners, several works addressed the problem of agent preferences elicitation using a variety of approaches (minimax regret, Bayesian methods, etc.) with the goal of converging to a necessary winner \cite{Naamani-Dery2015,Kalech2011,Lu2011,Pini2009,Benabbou2016,Dey2016_2}.
 Among those, Walsh \cite{Walsh2009} and Conitzer \cite{Conitzer2009} analyzed when to stop the elicitation process.
@@
 % provided an elicitation framework for a different class of rules.
-Additionally, some works address the manipulability of voting rules \cite{Elkind2012,Dey2018,Dey2018_2,Conitzer2011,Baumeister2019} and 
+Additionally, some works address the manipulability of voting rules \cite{Elkind2012,Dey2018,Conitzer2011,Baumeister2019} and 
 strategic behaviors \cite{Endriss2016,Lev2019,Annemieke2012}.
@@
 		\PMR(x,y; \pprofile, W)  
-		& = \max_{w \in W} \sum_{j \in N} w_{\hat{v}_j(y)} - w_{\hat{v}_j(x)} \\ 
-		& = \max_{w \in W} \sum_{r=1}^m (\hat{\alpha}_{r}^{y} - \hat{\alpha}_{r}^{x}) w_i 
+		& = \max_{w \in W} \sum_{j \in N} w_{\hat{v}_j(y)} - w_{\hat{v}_j(x)} = \max_{w \in W} \sum_{r=1}^m (\hat{\alpha}_{r}^{y} - \hat{\alpha}_{r}^{x}) w_i 
 	\end{align}
@@
 
-Although questioning in terms of profiles and in terms of weights is logically equivalent in our setting, there is no a priori certainty that questioning the chair using different phrasing would yield logically equivalent answers: research in experimental psychology shows that participants’ answers differ widely when changing the phrasing of preference-related questions [Lichtenstein and Slovic,	2012, doi: 10.1017/CBO9780511618031].
+Although questioning in terms of profiles and in terms of weights is logically equivalent in our setting, there is no a priori certainty that questioning the chair using different phrasing would yield logically equivalent answers: research in experimental psychology shows that participants’ answers differ widely when changing the phrasing of preference-related questions \cite{Lichtenstein2006}.
 To get out of such conundrums, we need a language considered “fundamental”.
@@
 	Suppose we want to ask the following question to the chair: $w_{2} - w_{3} ≥ 2 (w_{3} - w_{4})$.
-	We show the profile in Figure xx, left, to the chair and ask who should win (each column is a preference of an agent).
+We show the profile in Figure \ref{fig:profileQstComm} to the chair and ask who should win (each column is a preference of an agent).	Both $a$ and $b$ have scores higher than $c$ and $d$ for all convex weights, thus either $a$ or $b$ will be picked under our hypothesis; and $s(a) ≥ s(b) ⇔ w_2 + 2 w_4 ≥ 3 w_3$.
+	Figure \ref{fig:profileQstCommCompact} shows the same profile using a compressed view, the numbers in bold indicating the number of agents having the preference in the corresponding column.
+As the proof shows, constructed profiles require only four different linear orders.
+	\begin{figure}
+		\centering
+		\begin{subfigure}[b]{0.49\textwidth}
 			\begin{center}
@@
 			\end{center}
-	Both $a$ and $b$ have scores higher than $c$ and $d$ for all convex weights, thus either $a$ or $b$ will be picked under our hypothesis; and $s(a) ≥ s(b) ⇔ w_2 + 2 w_4 ≥ 3 w_3$.
-	Figure xx, right, shows the same profile using a compressed view, the numbers in bold indicating the number of voters (agents?) having the preference in the corresponding column.
-As the proof shows, constructed profiles require only four different linear orders.
+			\caption{}
+			\label{fig:profileQstComm}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{0.49\textwidth}
 			\begin{center}
@@
 			\end{center}
+			\caption{}
+			\label{fig:profileQstCommCompact}
+		\end{subfigure}
+		\caption{Profile representing a question for the chair in extended (a) and compact (b) form.}
+	\end{figure}
 \end{example*}
@@
 The results for various sizes are displayed in \cref{tab:questions}.
+The notation $q_{c {\scriptscriptstyle \MMR}≤ x}$ indicates the number of questions asked to the committee to reach a threshold regret $x$, averaged on $20$ runs.
+We use a similar notation for the questions to the voters $q_{v {\scriptscriptstyle \MMR}≤ x}$, but in this case we display the quartiles ([Q1|M|Q3]) of the number of questions asked to the voters, averaged on $20$ runs.
+It is important to mention that we stop our computation at $1000$ questions, the empty cells in \cref{tab:questions} indicate, thus, that the Pessimistic strategy applied to that dataset did not reach zero regret in $1000$ questions.
 %For example, in the case $m = 10, n = 20$, Pessimistic asks on average $49$ questions to the chair and $18$ questions to each agent (\cref{tab:Numquestions} provides more data).
 
-%\begin{table}
-%	\caption{Number of questions needed by Pessimistic strategy to reach an MMR of $\frac{n}{10}$ (represented by $k_{\MMR}$), by size.}
-%	\label{tab:lowRegret}
-%	\begin{tabular}{S[table-figures-decimal=0]S[table-figures-decimal=0]SS[table-figures-integer=3, table-figures-decimal=0]}
-%		\toprule
-%		{m} & {n} & {$\frac{n}{10}$} & {$k_{\MMR}$} \\
-%		\midrule
-%		5 & 10 & 1 & 60 \\
-%		5 & 15 & 1.5 & 80 \\
-%		5 & 20 & 2 & 110 \\
-%		10 & 20 & 2 & 340 \\
-%		10 & 30 & 3 & 527 \\
-%		15 & 30 & 3 & 951 \\
-%		\bottomrule
-%	\end{tabular}
-%\end{table}
+\begin{table}[ht]
+	\caption{Analysis of the questions asked by Pessimistic strategy on the datasets of \cref{fig:linearity}.
+The column $q_{c \scriptscriptstyle{\MMR} ≤ n/10}$ ($q_{c \scriptscriptstyle{\MMR} = 0}$) indicates the average number of questions asked to the chair to reach a threshold regret of $\frac{n}{10}$ (zero regret).
+The column $q_{v \scriptscriptstyle{\MMR} ≤ n/10}$ ($q_{v \scriptscriptstyle{\MMR} = 0}$) represents the average of the quartiles of the questions asked to the voters to reach $\frac{n}{10}$ regret (zero regret).}
+	\label{tab:questions}
+	\begin{tabular}{cccS[table-number-alignment = right, table-figures-integer=2]@{ ± }S[table-number-alignment = left, table-figures-integer=2] S[table-figures-integer=3, table-figures-decimal=1]@{ | }S[table-figures-integer=2, table-figures-decimal=1]@{ | }S[table-figures-integer=2, table-figures-decimal=1]@{ ]} S[table-number-alignment = right, table-figures-integer=2]@{ ± }S[table-number-alignment = left, table-figures-integer=2]S[table-figures-integer=3, table-figures-decimal=1]@{ | }S[table-figures-integer=2, table-figures-decimal=1]@{ | }S[table-figures-integer=2, table-figures-decimal=1]@{ ]}}
+		\toprule
+		{dataset} & m & n &{$q_{c \scriptscriptstyle{\MMR} ≤ n/10}$} & {sd} & \multicolumn{3}{c}{$q_{v \scriptscriptstyle{\MMR} ≤ n/10}$} & {$q_{c \scriptscriptstyle{\MMR} = n/10}$} & {sd} & \multicolumn{3}{c}{$q_{v \scriptscriptstyle{\MMR} = 0}$} \\
+		\midrule
+		m5n20 & 5&20&0.0&0.0&[4.3 &4.95 & 5.84 &5.25&9.59&[ \ 5.36 & 6.15 & 7.21\\
+		m10n20&10&20&0.0&0.0&[13.85 & 16.1& 18.41&31.95&26.62&[19.66 & 21.78 & 24.7\\
+		m11n30&11&30&0.0&0.0&[16.55&19.0&22.26&45.15&40.14&[23.07&25.7&28.89\\
+		tshirts&11&30&0.0&0.0&[12.92 & 16.17 &19.3\\
+		courses&9&146&0.0&0.0&[6.35 &7.0 &7.0&0.0&0.0&[6.8 & 7.0 &7.0\\
+		%m9n146&9&146&0&0&[1.94 &8 &9.25&999.3&0.47&0&0&[1.94&8&9.25&999.3&0.47\\
+		m14n9&14&9&5.4&9.49&[30.3&33.45&36.65&64.05&40.37&[37.55&40.5&44.3\\
+		skate&14&9&0.0&0.0&[11.35&11.8&12.25&0.0&0.0&[11.5&11.9&12.7 \\
+		m15n30&15&30&0.0&0.0&[24.95&29.5&33.68&\multicolumn{2}{c}{---}&\multicolumn{3}{c}{---} \\
+
+		\bottomrule
+	\end{tabular}
+\end{table}
+
+\Cref{fig:linearity} shows the decrease in MMR according to the number of questions asked for various problem sizes.
+In particular, this shows important differences between some real datasets and the problems generated using IC.
+In the \textit{Skate} problem, the value $\MMR\!=\!1$ is reached after less than $100$ questions, while the IC case of the same size ($m = 14, n = 9$) requires more than $200$ questions to reach that value.
+This reasoning also applies to the \textit{Courses} dataset but not to the \textit{T Shirt} dataset.
+This can be explained by the high degree of similarity in the preference rankings of the \textit{Skate} and the \textit{Courses} problems, which helps reducing the regret faster.
+For example, in \textit{Skate} the top-2 alternatives are the same for all agents, and 8 out of 9 agents rank the same alternative at position 3.
+By contrast, in \textit{T Shirt}, the alternatives are evenly distributed in the preference rankings.
+% in \textit{Courses} all agents rank the same alternative at the top position,
 
@@
 
-			%			\addlegendimage{mark=*,violet,mark size=2}
 			\addlegendimage{mark=halfsquare right*,brown,mark size=2}
@@
 
-			%			\addplot[thick, mark=triangle*, mark size = {2}, mark indices = {35}, teal] table [x=k, y=5.10]{data/normalizedLin.dat};
-			%			\addlegendentry{m=5, n=10}
-			%			\addplot[thick, mark=*, mark size = {2}, mark indices = {45}, violet] table [x=k, y=5.15]{data/normalizedLin.dat};
-			%			\addlegendentry{m=5, n=15}
 			\addplot[thick, mark=halfsquare right*, mark size = {2}, mark indices = {120}, brown] table [x=k, y=5.20]{data/linearity_redone.dat};
@@
 			\addlegendentry{m=10, n=20}
-			%			\addplot[thick, mark=pentagon*, mark size = {2}, mark indices = {300}, cyan] table [x=k, y=10.30]{data/normalizedLin.dat};
-			%			\addlegendentry{m=10, n=30}
 			\addplot[thick, mark=pentagon*, mark size = {2}, mark indices = {240}, cyan] table [x=k, y=11.30]{data/linearity_redone.dat};
@@
 
-%\begin{table}[ht]
-%	\caption{Average number of questions asked to the chair ($q_{c}$) and to the agents (\textit{$q_{v}$}) by Pessimistic strategy to reach zero regret on the datasets of \cref{fig:linearity}.}
-%	\label{tab:Numquestions}
-%	\begin{tabular}{cS[table-number-alignment = right, table-figures-integer=4]@{ ± }S[table-number-alignment = left, table-figures-integer=2]S[table-number-alignment = right, table-figures-integer=4]@{ ± }S[table-number-alignment = left, table-figures-integer=2]}
+%\subsection{Value of information comparison}
+\paragraph{Comparison with Two Phases}
+
+%\begin{table}
+%	\caption{Average MMR in problems of size $(10, 20)$ after $400$ questions, among which $q_c$ to the chair.}
+%	\label{tab:twoP400}
+%	\begin{tabular}{S[table-figures-integer=3, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=1]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=1]}
 %		\toprule
-%		{dataset} & {$q_{c}$} & {sd} & {$q_{v}$} & {sd} \\
+%		{$q_c$} & {2 ph.\ ca} & {sd} & {2 ph.\ ac} & {sd} \\
 %		\midrule
-%		m5n10 	&	8.4		& 2.67 		& 61		& 6.25\\
-%		m5n20 	&	13.6	& 6.38		& 118.9		& 14.4\\
-%		m10n20 	&	48.5	& 6			& 362.4		& 47.6	\\
-%		m10n30 	&	56.3	& 11.18		& 598.1 	& 75.19	\\
-%		m15n30 	&	24.5	& 8.77		& 775.5		& 8.77	\\
-%		m14n9 	&	58.3	& 33.66		& 370.9		& 40.54	\\
-%		m14n9-2 &	56.2	& 34.11		& 368.7		& 53.07 \\
-%		skate 	&	0		& 0			& 103.3		& 2.21	\\
-%		tshirt  &	30.0	& 5.87		& 961.2		& 23.04	\\
-%		courses & 0			& 0			& 950		& 5.08	\\	
+%		0 & 0.86 & 0.72 & 0.73 & 0.67 \\
+%		15 & 0.92 & 0.82 & 0.93	& 0.96  \\
+%		30 & 0.9 & 0.97 & 0.72	& 0.7 \\
+%		50 & 1.36 & 1.29 & 1.38	& 1.17 \\
+%		100 & 1.9 & 1.72 & 2.5	& 1.46  \\
+%		%150 & 4.4 & 2.09 & 4.23 & 1.53 \\
+%		200 & 6.05	& 1.53  & 6.06 & 1.61 \\
+%		%250 & 8.27	& 1.54& 8.86 & 1.38 \\
+%		300 &11.54	& 1.07& 11.82 &1.25 \\
+%		%350 &15.39	& 0.61 &15.54	&0.73 \\
+%		400 &20.0 & 0.0 & 20.0 & 0.0 \\
 %		\bottomrule
@@
 
-\begin{table}[ht]
-	\caption{Analysis of the questions asked by Pessimistic strategy on the datasets of \cref{fig:linearity}.
-The column $q_{c TR}$ ($q_{c ZR}$) indicates the average number of questions asked to the chair to reach a threshold regret of $\frac{n}{10}$ (zero regret).
-The column $[Q1_{v} | M_{v} | Q3_{v}]_{TR}$ ($[Q1_{v} | M_{v} | Q3_{v}]_{ZR}$) represents the average of the quartiles of the questions asked to the voters to reach $\frac{n}{10}$ regret (zero regret).}
-	\label{tab:questions}
-	\begin{tabular}{cccS[table-number-alignment = right, table-figures-integer=2]@{ ± }S[table-number-alignment = left, table-figures-integer=2]cS[table-number-alignment = right, table-figures-integer=2]@{ ± }S[table-number-alignment = left, table-figures-integer=2]c}
-		\toprule
-		{dataset} & m & n &{$q_{c TR}$} & {sd} & {$[Q1_{v} | M_{v} | Q3_{v}]_{TR}$} & {$q_{c ZR}$} & {sd} & {$[Q1_{v} | M_{v} | Q3_{v}]_{ZR}$} \\
-		\midrule
-		m5n20 & 5&20&0&0&[4.3 | 4.95 | 5.84 ]&5.25&9.59&[5.36 | 6.15 | 7.21]\\
-		m10n20&10&20&0&0&[13.85 | 16.1| 18.41]&31.95&26.62&[19.66 | 21.78 | 24.7]\\
-		m11n30&11&30&0&0&[16.55|19|22.26]&45.15&40.14&[23.07|25.7|28.89]\\
-		tshirts&11&30&0&0&[12.92 | 16.17 |19.3]&\textendash&\textendash&\textendash\\
-		courses&9&146&0&0&[6.35 |7 |7]&0&0&[6.8 | 7 |7]\\
-		%m9n146&9&146&0&0&[1.94 |8 |9.25]&999.3&0.47&0&0&[1.94|8|9.25]&999.3&0.47\\
-		m14n9&14&9&5.4&9.49&[30.3|33.45|36.65]&64.05&40.37&[37.55|40.5|44.3]\\
-		skate&14&9&0&0&[11.35|11.8|12.25]&0&0&[11.5|11.9|12.7] \\
-		m15n30&15&30&0&0&[24.95|29.5|33.68]&\textendash&\textendash&\textendash \\
-
-		\bottomrule
-	\end{tabular}
-\end{table}
-
-\Cref{fig:linearity} shows the decrease in MMR according to the number of questions asked for various problem sizes.
-In particular, this shows important differences between some real datasets and the problems generated using IC.
-In the \textit{Skate} problem, the value $\MMR\!=\!1$ is reached after less than $100$ questions, while the IC case of the same size ($m = 14, n = 9$) requires more than $200$ questions to reach that value.
-This reasoning also applies to the \textit{Courses} dataset but not to the \textit{T Shirt} dataset.
-This can be explained by the high degree of similarity in the preference rankings of the \textit{Skate} and the \textit{Courses} problems, which helps reducing the regret faster.
-For example, in \textit{Skate} the top-2 alternatives are the same for all agents, and 8 out of 9 agents rank the same alternative at position 3.
-By contrast, in \textit{T Shirt}, the alternatives are evenly distributed in the preference rankings.
-% in \textit{Courses} all agents rank the same alternative at the top position,
-
-%\subsection{Value of information comparison}
-\paragraph{Comparison with Two Phases}
-
 \begin{table}
-	\caption{Average MMR in problems of size $(10, 20)$ after $400$ questions, among which $q_c$ to the chair.}
-	\label{tab:twoP400}
+	\caption{Average MMR in problems of size $(10, 20)$ after $500$ questions, among which $q_c$ to the chair.}
+	\label{tab:twoP500}
 	\begin{tabular}{S[table-figures-integer=3, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=1]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=1]}
@@
 		\midrule
-		0 & 0.86 & 0.72 & 0.73 & 0.67 \\
-		15 & 0.92 & 0.82 & 0.93	& 0.96  \\
-		30 & 0.9 & 0.97 & 0.72	& 0.7 \\
-		50 & 1.36 & 1.29 & 1.38	& 1.17 \\
-		100 & 1.9 & 1.72 & 2.5	& 1.46  \\
-		%150 & 4.4 & 2.09 & 4.23 & 1.53 \\
-		200 & 6.05	& 1.53  & 6.06 & 1.61 \\
-		%250 & 8.27	& 1.54& 8.86 & 1.38 \\
-		300 &11.54	& 1.07& 11.82 &1.25 \\
-		%350 &15.39	& 0.61 &15.54	&0.73 \\
-		400 &20.0 & 0.0 & 20.0 & 0.0 \\
+		0 & 0.78 & 0.38 & 0.73 & 0.67 \\
+		15 & 0.58 & 0.3 & 0.59	& 0.37  \\
+		30 & 0.29 & 0.31 & 0.55 & 0.19 \\
+		50 & 0.0 & 0.0 & 0.0 & 0.01 \\
+		100 &  &  & 	&   \\
+		200 & 	&   &  &  \\
+		300 &	& &  & \\
+		400 & &  &  &  \\
+		500 & &  &  &  \\
 		\bottomrule
@@
 
-\Cref{tab:twoP400} shows the MMR value reached in problems of size $m = 10, n = 20$ after $400$ questions, using the Two phases strategy, in the “ca” (chair then agents) and in the “ac” (agents then chair) variants.
-These numbers are to be compared with the MMR value reached after 400 questions with the Pessimistic strategy (displayed in \cref{fig:linearity}), which is $0.6$; the Pessimistic strategy asks on average $48$ questions to the chair in this setting.
+\Cref{tab:twoP500} shows the MMR value reached in problems of size $m = 10, n = 20$ after $500$ questions, using the Two phases strategy, in the “ca” (chair then agents) and in the “ac” (agents then chair) variants.
+These numbers are to be compared with the MMR value reached after 500 questions with the Pessimistic strategy (displayed in \cref{fig:linearity}), which is $0.6$; the Pessimistic strategy asks on average $48$ questions to the chair in this setting.
 \commentBN{This is not true anymore, after 400 questions it reaches $0.9$ with 0 questions to the chair, after 500 questions it reaches $0.4$ with $11.05$ question to the chair ($\sigma=12.34$).

### 2021-05-14 minimax.tex
test end-of-line
Normalize all the line endings
tried to add a space to check line-endings
Table 3, 3 runs (4 more ongoing)
clarification on my comment page13

@@
 It is important to mention that we stop our computation at $1000$ questions, the empty cells in \cref{tab:questions} indicate, thus, that the Pessimistic strategy applied to that dataset did not reach zero regret in $1000$ questions.
+
 %For example, in the case $m = 10, n = 20$, Pessimistic asks on average $49$ questions to the chair and $18$ questions to each agent (\cref{tab:Numquestions} provides more data).
@@
 		\midrule		
-		0 & 0.78 & 0.38 & 0.73 & 0.67 \\
-		15 & 0.58 & 0.3 & 0.59	& 0.37  \\
-		30 & 0.29 & 0.31 & 0.55 & 0.19 \\
-		50 & 0.0 & 0.0 & 0.0 & 0.01 \\
-		100 &  &  & 	&   \\
-		200 & 	&   &  &  \\
-		300 &	& &  & \\
-		400 & &  &  &  \\
-		500 & &  &  &  \\
+		0	&0.78&	0.38&	0.78&	0.38\\
+		15	&0.58&	0.3	&   0.63&   0.26\\
+		30	&0.29&  0.31&	0.4&    0.52\\
+		50	&0.0&	0.0&	0.0&	0.0\\
+		100	&0.21&	0.36&	0.07&	0.12\\
+		200	&2.84&	1.52&	1.72&	1.79\\
+		300	&6.02&	2.28&	6.79&	0.81\\
+		400	&10.95&	0.74&	12.8&	0.92\\
+		500	&20.0&	0.0&	20.0&	0.0\\
+
 		\bottomrule
@@
 These numbers are to be compared with the MMR value reached after 500 questions with the Pessimistic strategy (displayed in \cref{fig:linearity}), which is $0.6$; the Pessimistic strategy asks on average $48$ questions to the chair in this setting.
-\commentBN{This is not true anymore, after 400 questions it reaches $0.9$ with 0 questions to the chair, after 500 questions it reaches $0.4$ with $11.05$ question to the chair ($\sigma=12.34$).
-The data in Table 2 is after 582 questions.}
+\commentBN{This is not true anymore, after 400 questions it reaches $0.9$ with 0 questions to the chair, after 500 questions it reaches $0.47$ ($\sigma = 0.51$) with $11.05$ question to the chair ($\sigma=12.34$).
+The data in Table 2 is after 582 questions.}\commentBN{Even this comment is not entirely true.
+We should take the data after 500 questions on the same datasets as the one used in Table3.
+On the first 3 runs, after 500 questions the regret is $0.62$ ($\sigma = 0.42$) and the number of questions to the committee is $14.33$ ($\sigma = 13.58$).
+On the first 7 runs, after 500 questions the regret is $0.67$ ($\sigma = 0.45$) and the number of questions to the committee is $13.29$ ($\sigma = 13.11$).}
 The line $q_c = 0$, where no question is asked to the chair, suggest that it is possible to obtain a good-quality recommendation while knowing only that the voting rule is a scoring rule with convex weights, which is our basic hypothesis.

### 2021-05-14 minimax.tex
fit in 15 pages

@@
 % \renewcommand\UrlFont{\color{blue}\rmfamily}
+
+%\renewcommand{\UrlFont}{\ttfamily\scriptsize}
 
@@
 \begin{align}
-	\max_{\w} & \sum_{r=1}^m (\hat{\alpha}_{r}^{y} - \hat{\alpha}_{r}^{x}) w_{r}\\
-	\text{ s.t. } & w_1 = 1 ≥ … ≥ w_m = 0, \text{\cref{eq:convexity}} \text{ and } \w \in \pw.
+	\max_{\w} \sum_{r=1}^m (\hat{\alpha}_{r}^{y} - \hat{\alpha}_{r}^{x}) w_{r} \quad
+	\text{ s.t. } w_1 = 1 ≥ … ≥ w_m = 0, \text{\cref{eq:convexity}} \text{ and } \w \in \pw.
 \end{align}
@@
 We show the profile in Figure \ref{fig:profileQstComm} to the chair and ask who should win (each column is a preference of an agent).	Both $a$ and $b$ have scores higher than $c$ and $d$ for all convex weights, thus either $a$ or $b$ will be picked under our hypothesis; and $s(a) ≥ s(b) ⇔ w_2 + 2 w_4 ≥ 3 w_3$.
-	Figure \ref{fig:profileQstCommCompact} shows the same profile using a compressed view, the numbers in bold indicating the number of agents having the preference in the corresponding column.
+	Figure \ref{fig:profileQstCommCompact} represents the same profile using a compressed view, the numbers in bold indicating the number of agents having the preference in the corresponding column.
 As the proof shows, constructed profiles require only four different linear orders.
@@
 		\end{subfigure}
-		\caption{Profile representing a question for the chair in extended (a) and compact (b) form.}
+		\caption{Profile representing a question to the chair in extended (a) and compact (b) form.}
 	\end{figure}
@@
 To generate the scoring rule weights, we first draw $m \!-\!
-1$ numbers uniformly at random (in the interval $\intvl{0,1}$ representing weight ``differences''), normalize and sort them; a sequence of convex decreasing weightx is then obtained by a decumulative sum.
+1$ numbers uniformly at random (in the interval $\intvl{0,1}$ representing weight ``differences''), normalize and sort them; a sequence of convex decreasing weights is then obtained by a decumulative sum.
 The penalty parameters for the Pessimistic and Extended pessimistic strategies are  $\epsilon_{\text{chair}} = 1.1$, $\epsilon'_{\text{chair}} = 10^{-6}$, $\epsilon_{\text{agent}} = 1.0$ and $\epsilon'_{\text{agent}} = 0$.
-
-\begin{figure}
-	\caption{Average MMR in problems of size $(5, 10)$ after $k$ questions.}
+\sisetup{table-number-alignment = center, table-figures-integer=2, table-figures-decimal=1, table-auto-round}
+\begin{minipage}{\textwidth}
+	\vspace{0.4cm}
+	\begin{minipage}{\textwidth}
+		\centering
+		\captionof{figure}{Average MMR in problems of size $(5, 10)$ after $k$ questions.}
 		\label{fig:smallSize}
+		\scalebox{0.85}{
 		\begin{tikzpicture}
@@
 		\end{tikzpicture}
-\end{figure}
+		}
+	\end{minipage}
+	\vspace{0.2cm}
 
-%\begin{figure}
-%	\caption{Average MMR in problems of size $(5, 10)$ after $k$ questions.}
-%	\label{fig:smallSize}
-%%	\Description{Graph showing that Pessimistic performs slightly better than Extended pessimistic, itself performing better than Elitist, itself performing much better than Random.}
-%	\includegraphics[width=.45\textwidth]{comparison.png}
-%\end{figure}
-\sisetup{table-number-alignment = center, table-figures-integer=2, table-figures-decimal=1, table-auto-round}
-\begin{table}
-	\caption{Average MMR in problems of size $(10, 20)$ after $k$ questions assuming geometric weights.}
+	\begin{minipage}{\textwidth}
+		\centering
+		\captionof{table}{Average MMR in problems of size $(10, 20)$ after $k$ questions assuming geometric weights.}
 		\label{tab:geometricWeights}
+		\scalebox{0.85}{
 		\begin{tabular}{S[table-figures-integer=3, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=1]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=1]}
@@
 		\end{tabular}
-\end{table}
+		}
+	\end{minipage}
+	\vspace{0.4cm}
+\end{minipage}
+
 \paragraph{Comparison of strategies}
@@
 The results for various sizes are displayed in \cref{tab:questions}.
-The notation $q_{c {\scriptscriptstyle \MMR}≤ x}$ indicates the number of questions asked to the committee to reach a threshold regret $x$, averaged on $20$ runs.
+The notation $q_{c {\scriptscriptstyle \MMR}≤ x}$ indicates the number of questions asked to the chair to reach a threshold regret $x$, averaged on $20$ runs.
 We use a similar notation for the questions to the voters $q_{v {\scriptscriptstyle \MMR}≤ x}$, but in this case we display the quartiles ([Q1|M|Q3]) of the number of questions asked to the voters, averaged on $20$ runs.
 It is important to mention that we stop our computation at $1000$ questions, the empty cells in \cref{tab:questions} indicate, thus, that the Pessimistic strategy applied to that dataset did not reach zero regret in $1000$ questions.
-
 %For example, in the case $m = 10, n = 20$, Pessimistic asks on average $49$ questions to the chair and $18$ questions to each agent (\cref{tab:Numquestions} provides more data).
-
-\begin{table}[ht]
-	\caption{Analysis of the questions asked by Pessimistic strategy on the datasets of \cref{fig:linearity}.
-The column $q_{c \scriptscriptstyle{\MMR} ≤ n/10}$ ($q_{c \scriptscriptstyle{\MMR} = 0}$) indicates the average number of questions asked to the chair to reach a threshold regret of $\frac{n}{10}$ (zero regret).
-The column $q_{v \scriptscriptstyle{\MMR} ≤ n/10}$ ($q_{v \scriptscriptstyle{\MMR} = 0}$) represents the average of the quartiles of the questions asked to the voters to reach $\frac{n}{10}$ regret (zero regret).}
+\vspace{-0.6cm}
+\begin{table}
+	\caption{Questions asked by Pessimistic strategy on several datasets.
+The column $q_{c \scriptscriptstyle{\MMR} ≤ n/10}$ ($q_{c \scriptscriptstyle{\MMR} = 0}$) indicates the avg number of questions asked to the chair to reach a threshold regret of $\frac{n}{10}$ (zero regret).
+The column $q_{v \scriptscriptstyle{\MMR} ≤ n/10}$ ($q_{v \scriptscriptstyle{\MMR} = 0}$) represents the avg of the quartiles of the questions asked to the voters to reach $\frac{n}{10}$ regret (zero regret).}
 	\label{tab:questions}
@@
 
-\begin{figure}
-	\caption{Average MMR (normalized by $n$) after $k$ questions with Pessimistic strategy for different datasets.}
+\begin{minipage}{\textwidth}
+	\vspace{0.4cm}
+	\begin{minipage}{\textwidth}
+		\centering
+		\captionof{figure}{Average MMR (normalized by $n$) after $k$ questions with Pessimistic strategy for different datasets.}
 		\label{fig:linearity}
@@
 		\end{tikzpicture}
-\end{figure}
+	\end{minipage}
+	\vspace{0.2cm}
 
-%\subsection{Value of information comparison}
-\paragraph{Comparison with Two Phases}
-
-%\begin{table}
-%	\caption{Average MMR in problems of size $(10, 20)$ after $400$ questions, among which $q_c$ to the chair.}
-%	\label{tab:twoP400}
-%	\begin{tabular}{S[table-figures-integer=3, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=1]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=1]}
-%		\toprule
-%		{$q_c$} & {2 ph.\ ca} & {sd} & {2 ph.\ ac} & {sd} \\
-%		\midrule
-%		0 & 0.86 & 0.72 & 0.73 & 0.67 \\
-%		15 & 0.92 & 0.82 & 0.93	& 0.96  \\
-%		30 & 0.9 & 0.97 & 0.72	& 0.7 \\
-%		50 & 1.36 & 1.29 & 1.38	& 1.17 \\
-%		100 & 1.9 & 1.72 & 2.5	& 1.46  \\
-%		%150 & 4.4 & 2.09 & 4.23 & 1.53 \\
-%		200 & 6.05	& 1.53  & 6.06 & 1.61 \\
-%		%250 & 8.27	& 1.54& 8.86 & 1.38 \\
-%		300 &11.54	& 1.07& 11.82 &1.25 \\
-%		%350 &15.39	& 0.61 &15.54	&0.73 \\
-%		400 &20.0 & 0.0 & 20.0 & 0.0 \\
-%		\bottomrule
-%	\end{tabular}
-%\end{table}
-
-\begin{table}
-	\caption{Average MMR in problems of size $(10, 20)$ after $500$ questions, among which $q_c$ to the chair.}
+	\begin{minipage}{\textwidth}
+		\centering
+		\captionof{table}{Average MMR in problems of size $(10, 20)$ after $500$ questions, among which $q_c$ to the chair.}
 		\label{tab:twoP500}
+		\scalebox{0.85}{
 		\begin{tabular}{S[table-figures-integer=3, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=1]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=1]}
@@
 		\end{tabular}
-\end{table}
+		}
+	\end{minipage}
+	\vspace{0.4cm}
+\end{minipage}
+%\subsection{Value of information comparison}
+\paragraph{Comparison with Two Phases}
 
@@
 These numbers are to be compared with the MMR value reached after 500 questions with the Pessimistic strategy (displayed in \cref{fig:linearity}), which is $0.6$; the Pessimistic strategy asks on average $48$ questions to the chair in this setting.
-\commentBN{This is not true anymore, after 400 questions it reaches $0.9$ with 0 questions to the chair, after 500 questions it reaches $0.47$ ($\sigma = 0.51$) with $11.05$ question to the chair ($\sigma=12.34$).
+%\commentBN{This is not true anymore, after 400 questions it reaches $0.9$ with 0 questions to the chair, after 500 questions it reaches $0.47$ ($\sigma = 0.51$) with $11.05$ question to the chair ($\sigma=12.34$).
 The data in Table 2 is after 582 questions.}\commentBN{Even this comment is not entirely true.
 We should take the data after 500 questions on the same datasets as the one used in Table3.
-On the first 3 runs, after 500 questions the regret is $0.62$ ($\sigma = 0.42$) and the number of questions to the committee is $14.33$ ($\sigma = 13.58$).
-On the first 7 runs, after 500 questions the regret is $0.67$ ($\sigma = 0.45$) and the number of questions to the committee is $13.29$ ($\sigma = 13.11$).}
+On the first 3 runs, after 500 questions the regret is $0.62$ ($\sigma = 0.42$) and the number of questions to the chair is $14.33$ ($\sigma = 13.58$).
+On the first 7 runs, after 500 questions the regret is $0.67$ ($\sigma = 0.45$) and the number of questions to the chair is $13.29$ ($\sigma = 13.11$).}
 The line $q_c = 0$, where no question is asked to the chair, suggest that it is possible to obtain a good-quality recommendation while knowing only that the voting rule is a scoring rule with convex weights, which is our basic hypothesis.

### 2021-05-14 minimax.tex
correction xps in text

@@
 This also holds for other problem sizes.
-For instance, for $m =10$, $n = 20$ and $400$ questions, Random strategy reaches an average regret (over 10 runs) of $12$ (±$ 0.7$) and Pessimistic $0.6$ (±$ 0.5$).
+For instance, for $m =10$, $n = 20$ and $500$ questions, Random strategy reaches an average regret (over 20 runs) of $9.3$ (±$ 0.7$) and Pessimistic $0.5$ (±$ 0.5$).
 We notice that Pessimistic performs slightly better than Extended pessimistic, showing that Pessimistic chooses candidate questions wisely; this is good news since Pessimistic is much faster: it takes on average only $16$s for a complete elicitation session (for $m = 5$, $n = 10$ and $100$ questions), while Extended pessimistic takes $50$s.
@@
 We use a similar notation for the questions to the voters $q_{v {\scriptscriptstyle \MMR}≤ x}$, but in this case we display the quartiles ([Q1|M|Q3]) of the number of questions asked to the voters, averaged on $20$ runs.
-It is important to mention that we stop our computation at $1000$ questions, the empty cells in \cref{tab:questions} indicate, thus, that the Pessimistic strategy applied to that dataset did not reach zero regret in $1000$ questions.
+It is important to mention that we stop our computation at $1000$ questions, the empty cells in \cref{tab:questions} indicate, thus, that the Pessimistic strategy applied to the corresponding dataset did not reach zero regret after having asked $1000$ questions.
 %For example, in the case $m = 10, n = 20$, Pessimistic asks on average $49$ questions to the chair and $18$ questions to each agent (\cref{tab:Numquestions} provides more data).
@@
 		skate&14&9&0.0&0.0&[11.35&11.8&12.25&0.0&0.0&[11.5&11.9&12.7 \\
-		m15n30&15&30&0.0&0.0&[24.95&29.5&33.68&\multicolumn{2}{c}{---}&\multicolumn{3}{c}{---} \\
+		m15n30&15&30&0.0&0.0&[24.95&29.5&33.68 \\
 
@@
 \Cref{tab:twoP500} shows the MMR value reached in problems of size $m = 10, n = 20$ after $500$ questions, using the Two phases strategy, in the “ca” (chair then agents) and in the “ac” (agents then chair) variants.
-These numbers are to be compared with the MMR value reached after 500 questions with the Pessimistic strategy (displayed in \cref{fig:linearity}), which is $0.6$; the Pessimistic strategy asks on average $48$ questions to the chair in this setting.
+These numbers are to be compared with the MMR value reached after 500 questions with the Pessimistic strategy (displayed in \cref{fig:linearity}), which is $0.7$; the Pessimistic strategy asks on average $13$ (± $13$) questions to the chair in this setting.
 %\commentBN{This is not true anymore, after 400 questions it reaches $0.9$ with 0 questions to the chair, after 500 questions it reaches $0.47$ ($\sigma = 0.51$) with $11.05$ question to the chair ($\sigma=12.34$).

### 2021-05-14 minimax.tex
header table 2
Some minor rephrasings

--- 2021-05-14 minimax.tex
@@
 We now introduce some basic concepts.
-We consider a set $A$ of $m$ alternatives (products, restaurants, public projects, job candidates, etc.), an infinite set $\N$ of potential agents.
+We consider a set $A$ of $m$ alternatives (products, restaurants, public projects, job candidates, etc.) and an infinite set $\N$ of potential agents.
 
@@
 \end{equation}
-The constraint above is a natural and common assumption, often used when aggregating rankings in sport competitions (such as F1 racing, alpine skiing world cup); losing ranks at the top  is more damaging than losing ranks at the bottom.
+The constraint above is a natural and common assumption, often used when aggregating rankings in sport competitions (such as F1 racing, alpine skiing world cup): losing ranks at the top  is more damaging than losing ranks at the bottom.
 Let $\W$ denote the set of such convex weight vectors.
 
-Consider a specific finite set of agents $N^* \subset \N$, let $\profile^* = (\pref_j^*, j \in N^*)$ and $\w^*$ denote the profile and weight vector, unknown to us, that represent the preferences of the agents in $N^*$ and of the chair.
+We consider a specific finite set of agents $N^* \subset \N$ and let $\profile^* = (\pref_j^*, j \in N^*)$ and $\w^*$ denote the profile and weight vector, unknown to us, that represent the preferences of the agents in $N^*$ and of the chair.
 
@@
 		\PMR(x,y; \pprofile, W)  
-		& = \max_{w \in W} \sum_{j \in N} w_{\hat{v}_j(y)} - w_{\hat{v}_j(x)} = \max_{w \in W} \sum_{r=1}^m (\hat{\alpha}_{r}^{y} - \hat{\alpha}_{r}^{x}) w_i 
+		& = \max_{w \in W} \sum_{j \in N} w_{\hat{v}_j(y)} - w_{\hat{v}_j(x)} = \max_{w \in W} \sum_{r=1}^m (\hat{\alpha}_{r}^{y} - \hat{\alpha}_{r}^{x}) w_i,
 	\end{align}
@@
 	Suppose we want to ask the following question to the chair: $w_{2} - w_{3} ≥ 2 (w_{3} - w_{4})$.
-We show the profile in Figure \ref{fig:profileQstComm} to the chair and ask who should win (each column is a preference of an agent).	Both $a$ and $b$ have scores higher than $c$ and $d$ for all convex weights, thus either $a$ or $b$ will be picked under our hypothesis; and $s(a) ≥ s(b) ⇔ w_2 + 2 w_4 ≥ 3 w_3$.
+We show the profile in Figure \ref{fig:profileQstComm} to the chair and ask who should win (each column is the preference of one agent).
+	Both $a$ and $b$ have scores higher than $c$ and $d$ for all convex weights, thus either $a$ or $b$ will be picked under our hypothesis; and $s(a) ≥ s(b) ⇔ w_2 + 2 w_4 ≥ 3 w_3$.
 	Figure \ref{fig:profileQstCommCompact} represents the same profile using a compressed view, the numbers in bold indicating the number of agents having the preference in the corresponding column.
@@
 We first wonder how many questions should be asked in order to achieve low regret, fixed at $n / 10$: this is equivalent to the difference of score of an alternative $x$ that results from switching from a profile $P$ to a profile $P'$ where a tenth of the agents rank $x$ last instead of first.
+Table 2, first five columns, contain the result: it displays, for each dataset, the number of questions asked to the committee, and the quartiles of the number of questions asked to the voters, averaged over $20$ runs.
+It is interesting to note that about twenty or thirty questions per voter on average suffice to reach a low regret in those instances.
+We find also noteworthy that the Pessimistic strategy chooses to ask zero questions to the chair but still achieves low regret, in most of those instances.
+
 Another interesting measure is the average number of questions asked to each participant before reaching zero regret.
-The results for various sizes are displayed in \cref{tab:questions}.
-The notation $q_{c {\scriptscriptstyle \MMR}≤ x}$ indicates the number of questions asked to the chair to reach a threshold regret $x$, averaged on $20$ runs.
-We use a similar notation for the questions to the voters $q_{v {\scriptscriptstyle \MMR}≤ x}$, but in this case we display the quartiles ([Q1|M|Q3]) of the number of questions asked to the voters, averaged on $20$ runs.
+The results for various sizes are displayed in the last two columns of \cref{tab:questions}.
+
  It is important to mention that we stop our computation at $1000$ questions, the empty cells in \cref{tab:questions} indicate, thus, that the Pessimistic strategy applied to that dataset did not reach zero regret in $1000$ questions.
+\commentOC{Need to drop the explanation in Table 2 as this is now explained in the text; change qcMMR=n/10 to qcMMR=0, and add in the text the explanation about qxMMR=; change hyphens to blanks in the table,= I suppose.}
 %For example, in the case $m = 10, n = 20$, Pessimistic asks on average $49$ questions to the chair and $18$ questions to each agent (\cref{tab:Numquestions} provides more data).

### 2021-05-14 minimax.tex

@@
 		\toprule
-		{dataset} & m & n &{$q_{c \scriptscriptstyle{\MMR} ≤ n/10}$} & {sd} & \multicolumn{3}{c}{$q_{v \scriptscriptstyle{\MMR} ≤ n/10}$} & {$q_{c \scriptscriptstyle{\MMR} = n/10}$} & {sd} & \multicolumn{3}{c}{$q_{v \scriptscriptstyle{\MMR} = 0}$} \\
+		{dataset} & m & n &{$q_{c \scriptscriptstyle{\MMR} ≤ n/10}$} & {sd} & \multicolumn{3}{c}{$q_{v \scriptscriptstyle{\MMR} ≤ n/10}$} & {$q_{c \scriptscriptstyle{\MMR} = 0}$} & {sd} & \multicolumn{3}{c}{$q_{v \scriptscriptstyle{\MMR} = 0}$} \\
 		\midrule

### 2021-05-14 minimax.tex
Pess strat

@@
 The results for various sizes are displayed in the last two columns of \cref{tab:questions}.
+Here, we see that the Pessimistic strategy does choose to question the chair when reaching low enough regret values.
+The tshirts and m15n30 datasets did not reach zero regret in $1000$ questions.
 
-It is important to mention that we stop our computation at $1000$ questions, the empty cells in \cref{tab:questions} indicate, thus, that the Pessimistic strategy applied to that dataset did not reach zero regret in $1000$ questions.
-\commentOC{Need to drop the explanation in Table 2 as this is now explained in the text; change qcMMR=n/10 to qcMMR=0, and add in the text the explanation about qxMMR=; change hyphens to blanks in the table,= I suppose.}
+\commentOC{Need to drop the explanation in Table 2 as this is now explained in the text; change qcMMR=n/10 to qcMMR=0, and add in the text the explanation about qxMMR=; change hyphens to blanks in the table.}
 %For example, in the case $m = 10, n = 20$, Pessimistic asks on average $49$ questions to the chair and $18$ questions to each agent (\cref{tab:Numquestions} provides more data).

### 2021-05-14 minimax.tex
15 pages again

@@
 social choice theory can provide foundations for such applications.
-%The traditional approach to social choice assumes that both the social choice function and the full preference orderings of the agents (voters) are expressed beforehand.
+%The traditional approach to social choice assumes that both the social choice function and the full preference orderings of the agents (agents) are expressed beforehand.
 These represent two strong hypothesis.
@@
 We first wonder how many questions should be asked in order to achieve low regret, fixed at $n / 10$: this is equivalent to the difference of score of an alternative $x$ that results from switching from a profile $P$ to a profile $P'$ where a tenth of the agents rank $x$ last instead of first.
-Table 2, first five columns, contain the result: it displays, for each dataset, the number of questions asked to the committee, and the quartiles of the number of questions asked to the voters, averaged over $20$ runs.
-It is interesting to note that about twenty or thirty questions per voter on average suffice to reach a low regret in those instances.
+Table 2, first five columns, contain the result: it displays, for each dataset, the number of questions asked to the chair ($q_{c \scriptscriptstyle{\MMR} ≤ n/10}$), and the quartiles of the number of questions asked to the agents ($q_{a \scriptscriptstyle{\MMR} ≤ n/10}$), averaged over $20$ runs.
+It is interesting to note that about twenty or thirty questions per agent on average suffice to reach a low regret in those instances.
 We find also noteworthy that the Pessimistic strategy chooses to ask zero questions to the chair but still achieves low regret, in most of those instances.
 
-Another interesting measure is the average number of questions asked to each participant before reaching zero regret.
+Another interesting measure is the average number of questions asked to the chair ($q_{c \scriptscriptstyle{\MMR} = 0}$) and to the agents ($q_{a \scriptscriptstyle{\MMR} = 0}$) before reaching zero regret.
 The results for various sizes are displayed in the last two columns of \cref{tab:questions}.
@@
 The tshirts and m15n30 datasets did not reach zero regret in $1000$ questions.
-
-\commentOC{Need to drop the explanation in Table 2 as this is now explained in the text; change qcMMR=n/10 to qcMMR=0, and add in the text the explanation about qxMMR=; change hyphens to blanks in the table.}
 %For example, in the case $m = 10, n = 20$, Pessimistic asks on average $49$ questions to the chair and $18$ questions to each agent (\cref{tab:Numquestions} provides more data).
@@
 \begin{table}
-	\caption{Questions asked by Pessimistic strategy on several datasets.
-The column $q_{c \scriptscriptstyle{\MMR} ≤ n/10}$ ($q_{c \scriptscriptstyle{\MMR} = 0}$) indicates the avg number of questions asked to the chair to reach a threshold regret of $\frac{n}{10}$ (zero regret).
-The column $q_{v \scriptscriptstyle{\MMR} ≤ n/10}$ ($q_{v \scriptscriptstyle{\MMR} = 0}$) represents the avg of the quartiles of the questions asked to the voters to reach $\frac{n}{10}$ regret (zero regret).}
+	\caption{Questions asked by Pessimistic strategy on several datasets to reach $\frac{n}{10}$ regret, columns 4 and 5, and zero regret, last two columns.}
 	\label{tab:questions}
@@
 		\toprule
-		{dataset} & m & n &{$q_{c \scriptscriptstyle{\MMR} ≤ n/10}$} & {sd} & \multicolumn{3}{c}{$q_{v \scriptscriptstyle{\MMR} ≤ n/10}$} & {$q_{c \scriptscriptstyle{\MMR} = 0}$} & {sd} & \multicolumn{3}{c}{$q_{v \scriptscriptstyle{\MMR} = 0}$} \\
+		{dataset} & m & n &{$q_{c \scriptscriptstyle{\MMR} ≤ n/10}$} & {sd} & \multicolumn{3}{c}{$q_{a \scriptscriptstyle{\MMR} ≤ n/10}$} & {$q_{c \scriptscriptstyle{\MMR} = 0}$} & {sd} & \multicolumn{3}{c}{$q_{a \scriptscriptstyle{\MMR} = 0}$} \\
 		\midrule
@@
 However, we observe that asking no questions to the chair does not permit to reach $\MMR\!=\!0$.
-The strategy, indeed, obtains full knowledge of the profile after an average of 500 questions to the voters but never reaches zero.
+The strategy, indeed, obtains full knowledge of the profile after an average of 500 questions to the agents but never reaches zero.
 

### 2021-05-15 minimax.tex
Table 3
Slight rewording Fig 2

@@
 We first wonder how many questions should be asked in order to achieve low regret, fixed at $n / 10$: this is equivalent to the difference of score of an alternative $x$ that results from switching from a profile $P$ to a profile $P'$ where a tenth of the agents rank $x$ last instead of first.
-Table 2, first five columns, contain the result: it displays, for each dataset, the number of questions asked to the chair ($q_{c \scriptscriptstyle{\MMR} ≤ n/10}$), and the quartiles of the number of questions asked to the agents ($q_{a \scriptscriptstyle{\MMR} ≤ n/10}$), averaged over $20$ runs.
+\cref{tab:questions}, first five columns, contains the result: it displays, for each dataset, the number of questions asked to the chair ($q_{c \scriptscriptstyle{\MMR} ≤ n/10}$), and the quartiles of the number of questions asked to the agents ($q_{a \scriptscriptstyle{\MMR} ≤ n/10}$), averaged over $20$ runs.
 It is interesting to note that about twenty or thirty questions per agent on average suffice to reach a low regret in those instances.
@@
 			\midrule
-			0	&0.78&	0.38&	0.78&	0.38\\
-			15	&0.58&	0.3	&   0.63&   0.26\\
-			30	&0.29&  0.31&	0.4&    0.52\\
-			50	&0.0&	0.0&	0.0&	0.0\\
-			100	&0.21&	0.36&	0.07&	0.12\\
-			200	&2.84&	1.52&	1.72&	1.79\\
-			300	&6.02&	2.28&	6.79&	0.81\\
-			400	&10.95&	0.74&	12.8&	0.92\\
-			500	&20.0&	0.0&	20.0&	0.0\\
+
+			0	&	0.62	&	0.52	&	0.62	&	0.52	\\
+			15	&	0.515	&	0.48	&	0.54	&	0.46	\\
+			30	&	0.345	&	0.47	&	0.325	&	0.425	\\
+			50	&	0.045	&	0.09	&	0.03	&	0.065	\\
+			100	&	0.14	&	0.23	&	0.075	&	0.135	\\
+			200	&	2.305	&	1.36	&	2.145	&	1.845	\\
+			300	&	5.15	&	2.38	&	6.83	&	0.625	\\
+			400	&	10.905	&	0.89	&	12.245	&	0.99	\\
+			500	&	20.0	&	0.0	&	20.0	&	0.0	\\
 

### 2021-05-15 minimax.tex
new tshirts data
Table 2 new headers and no sd

@@
 We first wonder how many questions should be asked in order to achieve low regret, fixed at $n / 10$: this is equivalent to the difference of score of an alternative $x$ that results from switching from a profile $P$ to a profile $P'$ where a tenth of the agents rank $x$ last instead of first.
-\cref{tab:questions}, first five columns, contains the result: it displays, for each dataset, the number of questions asked to the chair ($q_{c \scriptscriptstyle{\MMR} ≤ n/10}$), and the quartiles of the number of questions asked to the agents ($q_{a \scriptscriptstyle{\MMR} ≤ n/10}$), averaged over $20$ runs.
+\cref{tab:questions}, first five columns, contains the result: it displays, for each dataset, the number of questions asked to the chair ($q_{c}^{\scriptscriptstyle{\MMR} ≤ n/10}$), and the quartiles of the number of questions asked to the agents ($q_{a}^{\scriptscriptstyle{\MMR} ≤ n/10}$), averaged over $20$ runs.
 It is interesting to note that about twenty or thirty questions per agent on average suffice to reach a low regret in those instances.
@@
 
-Another interesting measure is the average number of questions asked to the chair ($q_{c \scriptscriptstyle{\MMR} = 0}$) and to the agents ($q_{a \scriptscriptstyle{\MMR} = 0}$) before reaching zero regret.
+Another interesting measure is the average number of questions asked to the chair ($q_{c}^{\scriptscriptstyle{\MMR} = 0}$) and to the agents ($q_{a}^{\scriptscriptstyle{\MMR} = 0}$) before reaching zero regret.
 The results for various sizes are displayed in the last two columns of \cref{tab:questions}.
 Here, we see that the Pessimistic strategy does choose to question the chair when reaching low enough regret values.
-The tshirts and m15n30 datasets did not reach zero regret in $1000$ questions.
+The m15n30 dataset did not reach zero regret in $1000$ questions.
 %For example, in the case $m = 10, n = 20$, Pessimistic asks on average $49$ questions to the chair and $18$ questions to each agent (\cref{tab:Numquestions} provides more data).
@@
 	\label{tab:questions}
-	\begin{tabular}{cccS[table-number-alignment = right, table-figures-integer=2]@{ ± }S[table-number-alignment = left, table-figures-integer=2] S[table-figures-integer=3, table-figures-decimal=1]@{ | }S[table-figures-integer=2, table-figures-decimal=1]@{ | }S[table-figures-integer=2, table-figures-decimal=1]@{ ]} S[table-number-alignment = right, table-figures-integer=2]@{ ± }S[table-number-alignment = left, table-figures-integer=2]S[table-figures-integer=3, table-figures-decimal=1]@{ | }S[table-figures-integer=2, table-figures-decimal=1]@{ | }S[table-figures-integer=2, table-figures-decimal=1]@{ ]}}
+	\begin{tabular}{cccS[table-number-alignment = center, table-figures-integer=2] S[table-figures-integer=3, table-figures-decimal=1]@{ | }S[table-figures-integer=2, table-figures-decimal=1]@{ | }S[table-figures-integer=2, table-figures-decimal=1]@{ ]} S[table-number-alignment = center, table-figures-integer=2]S[table-figures-integer=3, table-figures-decimal=1]@{ | }S[table-figures-integer=2, table-figures-decimal=1]@{ | }S[table-figures-integer=2, table-figures-decimal=1]@{ ]}}
 		\toprule
-		{dataset} & m & n &{$q_{c \scriptscriptstyle{\MMR} ≤ n/10}$} & {sd} & \multicolumn{3}{c}{$q_{a \scriptscriptstyle{\MMR} ≤ n/10}$} & {$q_{c \scriptscriptstyle{\MMR} = 0}$} & {sd} & \multicolumn{3}{c}{$q_{a \scriptscriptstyle{\MMR} = 0}$} \\
+		{dataset} & m & n &{$q_{c}^{\scriptscriptstyle{\MMR} ≤ n/10}$} & \multicolumn{3}{c}{$q_{a}^{\scriptscriptstyle{\MMR} ≤ n/10}$} & {$q_{c}^{ \scriptscriptstyle{\MMR} = 0}$} & \multicolumn{3}{c}{$q_{a}^{ \scriptscriptstyle{\MMR} = 0}$} \\
 		\midrule
-		m5n20 & 5&20&0.0&0.0&[4.3 &4.95 & 5.84 &5.25&9.59&[ \ 5.36 & 6.15 & 7.21\\
-		m10n20&10&20&0.0&0.0&[13.85 & 16.1& 18.41&31.95&26.62&[19.66 & 21.78 & 24.7\\
-		m11n30&11&30&0.0&0.0&[16.55&19.0&22.26&45.15&40.14&[23.07&25.7&28.89\\
-		tshirts&11&30&0.0&0.0&[12.92 & 16.17 &19.3\\
-		courses&9&146&0.0&0.0&[6.35 &7.0 &7.0&0.0&0.0&[6.8 & 7.0 &7.0\\
+		m5n20 & 5&20&0.0&[4.3 &4.95 & 5.84 &5.25&[ \ 5.36 & 6.15 & 7.21\\
+		m10n20&10&20&0.0&[13.85 & 16.1& 18.41&31.95&[19.66 & 21.78 & 24.7\\
+		m11n30&11&30&0.0&[16.55&19.0&22.26&45.15&[23.07&25.7&28.89\\
+		tshirts&11&30&0.0&[12.92 & 16.17 &19.3& 44.8 &[28.0 &	31.5 &34.9\\
+		courses&9&146&0.0&[6.35 &7.0 &7.0&0.0&[6.8 & 7.0 &7.0\\
 		%m9n146&9&146&0&0&[1.94 &8 &9.25&999.3&0.47&0&0&[1.94&8&9.25&999.3&0.47\\
-		m14n9&14&9&5.4&9.49&[30.3&33.45&36.65&64.05&40.37&[37.55&40.5&44.3\\
-		skate&14&9&0.0&0.0&[11.35&11.8&12.25&0.0&0.0&[11.5&11.9&12.7 \\
-		m15n30&15&30&0.0&0.0&[24.95&29.5&33.68 \\
+		m14n9&14&9&5.4&[30.3&33.45&36.65&64.05&[37.55&40.5&44.3\\
+		skate&14&9&0.0&[11.35&11.8&12.25&0.0&[11.5&11.9&12.7 \\
+		m15n30&15&30&0.0&[24.95&29.5&33.68 \\
 

### 2021-05-28 minimax.tex
linearity with 20 runs of tshirts and courses

@@
 		m11n30&11&30&0.0&[16.55&19.0&22.26&45.15&[23.07&25.7&28.89\\
-		tshirts&11&30&0.0&[12.92 & 16.17 &19.3& 44.8 &[28.0 &	31.5 &34.9\\
-		courses&9&146&0.0&[6.35 &7.0 &7.0&0.0&[6.8 & 7.0 &7.0\\
+		tshirts&11&30&0.0&[13.08&16.6&19.58& 43.15 &[28.22&31.98 &35.62\\
+		courses&9&146&0.0&[6.03 &7.0 &7.0&0.0&[6.81 & 7.0 &7.0\\
 		%m9n146&9&146&0&0&[1.94 &8 &9.25&999.3&0.47&0&0&[1.94&8&9.25&999.3&0.47\\
 		m14n9&14&9&5.4&[30.3&33.45&36.65&64.05&[37.55&40.5&44.3\\
-		skate&14&9&0.0&[11.35&11.8&12.25&0.0&[11.5&11.9&12.7 \\
+		skate&14&9&0.0&[11.35&11.6&12.3&0.0&[11.5&11.8&12.75 \\
 		m15n30&15&30&0.0&[24.95&29.5&33.68 \\
@@
 
-				\addplot[thick, mark=halfsquare right*, mark size = {2}, mark indices = {120}, brown] table [x=k, y=5.20]{data/linearity_redone.dat};
+				\addplot[thick, mark=halfsquare right*, mark size = {2}, mark indices = {120}, brown] table [x=k, y=5.20]{data/linearity.dat};
 				\addlegendentry{m=5, n=20}
-				\addplot[thick, mark=diamond*, mark size = {2}, mark indices = {150}, red] table [x=k, y=10.20]{data/linearity_redone.dat};
+				\addplot[thick, mark=diamond*, mark size = {2}, mark indices = {150}, red] table [x=k, y=10.20]{data/linearity.dat};
 				\addlegendentry{m=10, n=20}
-				\addplot[thick, mark=pentagon*, mark size = {2}, mark indices = {240}, cyan] table [x=k, y=11.30]{data/linearity_redone.dat};
+				\addplot[thick, mark=pentagon*, mark size = {2}, mark indices = {240}, cyan] table [x=k, y=11.30]{data/linearity.dat};
 				\addlegendentry{m=11, n=30}
-				\addplot[thick, mark=halfcircle*, mark size = {2}, mark indices = {400}, violet] table [x=k, y=tshirts]{data/linearity_redone.dat};
+				\addplot[thick, mark=halfcircle*, mark size = {2}, mark indices = {400}, violet] table [x=k, y=tshirts]{data/linearity.dat};
 				\addlegendentry{tshirts m11n30}
-				\addplot[thick, mark=*, mark size = {2}, mark indices = {400}, pink] table [x=k, y=courses]{data/linearity_redone.dat};
+				\addplot[thick, mark=*, mark size = {2}, mark indices = {400}, pink] table [x=k, y=courses]{data/linearity.dat};
 				\addlegendentry{courses m9n146}
-				\addplot[thick, mark=triangle*, mark size = {2}, mark indices = {400}, green] table [x=k, y=9.146]{data/linearity_redone.dat};
+				\addplot[thick, mark=triangle*, mark size = {2}, mark indices = {400}, green] table [x=k, y=9.146]{data/linearity.dat};
 				\addlegendentry{m=9, n=146}
-				\addplot[thick, mark=halfsquare left*, mark size = {2}, mark indices = {200}, blue] table [x=k, y=14.9]{data/linearity_redone.dat};
+				\addplot[thick, mark=halfsquare left*, mark size = {2}, mark indices = {200}, blue] table [x=k, y=14.9]{data/linearity.dat};
 				\addlegendentry{m=14, n=9}
-				\addplot[thick, mark=square*, mark size = {2}, mark indices = {60}, teal] table [x=k, y=skate]{data/linearity_redone.dat};
+				\addplot[thick, mark=square*, mark size = {2}, mark indices = {60}, teal] table [x=k, y=skate]{data/linearity.dat};
 				\addlegendentry{skate m14n9}
-				\addplot[thick, mark=halfsquare*, mark size = {2}, mark indices = {400}, magenta] table [x=k, y=15.30]{data/linearity_redone.dat};
+				\addplot[thick, mark=halfsquare*, mark size = {2}, mark indices = {400}, magenta] table [x=k, y=15.30]{data/linearity.dat};
 				\addlegendentry{m=15, n=30}

### 2021-07-12 minimax.tex
Table Two Phases 20 runs + display names and URL

@@
 
-\author{Submission 15}
-\institute{}
+%\author{Submission 15}
+%\institute{}
 
-%\author{Beatrice Napolitano\inst{1}\orcidID{0000-0002-3887-6206} \and
-%Olivier Cailloux\inst{1}\and
-%Paolo Viappiani\inst{2}}
-%%
-%\authorrunning{B. Napolitano et al.}
-%% First names are abbreviated in the running head.
-%% If there are more than two authors, 'et al.' is used.
-%%
-%\institute{Université Paris-Dauphine, Université PSL, CNRS, LAMSADE \and
-%LIP6, UMR 7606, CNRS and Sorbonne Universit\'e \\
-%\email{beatrice.napolitano@dauphine.fr}}
+\author{Beatrice Napolitano\inst{1}\orcidID{0000-0002-3887-6206} \and
+Olivier Cailloux\inst{1}\and
+Paolo Viappiani\inst{2}}
+%
+\authorrunning{B. Napolitano et al.}
+% First names are abbreviated in the running head.
+% If there are more than two authors, 'et al.' is used.
+%
+\institute{Université Paris-Dauphine, Université PSL, CNRS, LAMSADE \and
+LIP6, UMR 7606, CNRS and Sorbonne Universit\'e \\
+\email{beatrice.napolitano@dauphine.fr}}
 
 \maketitle              % typeset the header of the contribution
-\vspace{4em}
 %
@@
 
-			0	&	0.62	&	0.52	&	0.62	&	0.52	\\
-			15	&	0.515	&	0.48	&	0.54	&	0.46	\\
-			30	&	0.345	&	0.47	&	0.325	&	0.425	\\
-			50	&	0.045	&	0.09	&	0.03	&	0.065	\\
-			100	&	0.14	&	0.23	&	0.075	&	0.135	\\
-			200	&	2.305	&	1.36	&	2.145	&	1.845	\\
-			300	&	5.15	&	2.38	&	6.83	&	0.625	\\
-			400	&	10.905	&	0.89	&	12.245	&	0.99	\\
+			0	&	0.59	&	0.59	&	0.59	&	0.59	\\
+			15	&	0.5		&	0.49	&	0.55	&	0.58	\\
+			30	&	0.32	&	0.45	&	0.36	&	0.46	\\
+			50	&	0.08	&	0.2 	&	0.14	&	0.27	\\
+			100	&	0.39	&	0.57	&	0.23	&	0.46	\\
+			200	&	2.13	&	1.59	&	2.38	&	1.23	\\
+			300	&	5.8 	&	1.65	&	6.65	&	1.46	\\
+			400	&	11.28	&	1.09	&	11.94	&	1.22	\\
 			500	&	20.0	&	0.0	&	20.0	&	0.0	\\
@@
 
-As part of our contribution, an open-source library, to reproduce our experiments and perform many more, will be made publicly available. (URL not displayed for reasons of anonymity.)
+As part of our contribution, we provide an open-source library \url{https://github.com/oliviercailloux/minimax}, to reproduce our experiments and perform many more.
+%will be made publicly available.(URL not displayed for reasons of anonymity.)
 %and serve as a basis for further research

### 2021-07-15 minimax.tex
clean version to submit

@@
 \documentclass[runningheads]{llncs}
-%
-\input{preamble/packages}
-\input{preamble/math}
+
+\input glyphtounicode
+\pdfgentounicode=1
+
+\usepackage[T1]{fontenc}
+\usepackage[utf8]{inputenc}
+\usepackage{siunitx}
+\usepackage{newunicodechar}
+\usepackage{textcomp}
+\usepackage{mathrsfs}
+\usepackage{centernot}
+\usepackage{xpatch}
+\usepackage{stmaryrd}\SetSymbolFont{stmry}{bold}{U}{stmry}{m}{n}
+\usepackage[ntheorem]{empheq}
+\usepackage{doi}
+\makeatletter
+\patchcmd{\@doi}{http://dx.doi.org}{https://doi.org}{}{}
+\makeatother
+\usepackage{fixmath}
+\usepackage{amsfonts}
+\usepackage{bm}
+\usepackage[capitalise]{cleveref}
+\usepackage{xcolor}
+
 \usepackage{graphicx}
@@
 \usepackage{soul}
-%\usepackage[hidelinks,hypertexnames=false]{hyperref}
 \let\proof\relax
@@
 \usepackage{amsthm}
-\usepackage{xr}
-%%% Load required packages here (note that many are included already).
-
+\input{preamble/math}
 \usepackage{algorithm, algpseudocode}
@@
 
-\usepackage[hypertexnames=false]{hyperref}
-
-\NewDocumentCommand{\commentOC}{m}{\textcolor{blue}{\small$\big[$OC: #1$\big]$}}
-\NewDocumentCommand{\commentBN}{m}{\textcolor{magenta}{\small$\big[$BN: #1$\big]$}}
-\NewDocumentCommand{\commentPV}{m}{\textcolor{red}{\small$\big[$PV: #1$\big]$}}
-
 \theoremstyle{remark}
 \newtheorem*{example*}{Example}
-\usepackage{caption}
 \usepackage{subcaption}
 
-%\usepackage{cleveref}
-% Used for displaying a sample figure. If possible, figure files should
-% be included in EPS format.
-%
-% If you use the hyperref package, please uncomment the following line
-% to display URLs in blue roman font according to Springer's eBook style:
-% \renewcommand\UrlFont{\color{blue}\rmfamily}
+\usepackage{hyperref}
 
-%\renewcommand{\UrlFont}{\ttfamily\scriptsize}
+\renewcommand{\UrlFont}{\ttfamily\footnotesize}
 
@@
 %
-
-%\author{Submission 15}
-%\institute{}
 
@@
 
-\maketitle              % typeset the header of the contribution
+\maketitle              
 %
@@
 social choice theory can provide foundations for such applications.
-%The traditional approach to social choice assumes that both the social choice function and the full preference orderings of the agents (agents) are expressed beforehand.
-These represent two strong hypothesis.
 The traditional approach to social choice assumes that 1) the full preference orderings of the agents and 2) the social choice function are expressed beforehand. These represent two strong hypotheses.
@@
 This observation has motivated several works assuming partial preference orders: 
-%and incremental elicitation of agent preferences. 
-%In the context of social choice, several authors have been interested in obtaining information about winners with reduced assumptions about the knowledge of the agent preferences (assuming that the voting rule is known).
-one early work is  by Conitzer and Sandholm \cite{Conitzer2005} who studied the complexity of communication when using different voting rules; %determining lower and upper bounds;
-%they showed that, 
-%in the worst case, the agents should send their complete set of preference for several rules. 
-Konczak and Lang \cite{Konczak05} studied the computation of possible and necessary winners for various voting rules; %and showed that the problem is hard in the general case.
+one early work is  by Conitzer and Sandholm \cite{Conitzer2005} who studied the complexity of communication when using different voting rules;
+Konczak and Lang \cite{Konczak05} studied the computation of possible and necessary winners for various voting rules;
 Xia and Conitzer \cite{Xia2008} then showed that, while the identification of a necessary co-winner in scoring rules is polynomial,  the determination of possible co-winners is NP-hard;
-% they also  proposed polynomial-time algorithms when using maximin and Bucklin.
 additional complexity results were given by Walsh \cite{Walsh2007} and Pini et al. \cite{Pini2007}.
-%\cite{Walsh2007} showed that the general case remains computationally hard even when restricting to single-peaked preferences;  sufficient conditions that ensure tractability were then found \cite{Pini2007}.
 
@@
 Indeed, it is often difficult for non-experts to formalize a voting rule on the basis of some generic preferences over a desired aggregation method.
-%Thus, the first hypothesis should also be relaxed. 
-%While most of the focus in the research community has been in dealing with incomplete agent preferences, 
 Here we provide two examples of such situations.
@@
 Maybe she strongly believes that being ranked once in the first position is “much more” valuable than being ranked two times second, but does not know exactly how much more (though she can judge example cases).
-%The information provided can be used to   % to determine their employee of choice.
 
-%This paper considers both sources of uncertainty at the same time, and proposes a method able to recommend a consensus choice without requiring full knowledge of either.
 In this paper, we focus on positional scoring rules with convex weights, that are a particularly common method used to aggregate rankings. 
 We develop methods, based on the notion of minimax regret, for determining a robust ``winner'' under uncertainty of both the voting rule and the agent preferences.
-%alternative using positional scoring rules and 
-We provide incremental elicitation methods that 
-at each step of the elicitation question either one of the agents or the chair, and we discuss several heuristics to choose questions that quickly reduce the regret. 
-Answers to questions are encoded as constraints; questions to the agents are comparisons between pairs of alternatives while
-questions to the chair ask to select a winner out of a synthetic profile.
+We provide incremental elicitation methods that at each step of the elicitation question either one of the agents or the chair, and we discuss several heuristics to choose questions that quickly reduce the regret.
+Answers to questions are encoded as constraints; questions to the agents are comparisons between pairs of alternatives while questions to the chair ask to select a winner out of a synthetic profile.
 
 While some previous works have considered partially specified aggregation methods \cite{Stein1994,Llamazares2013,Viappiani2018}, we do not know of any work considering both sources of uncertainty at the same time.
-%has dealt with %scenarios where it is instead the voting rule that is partially defined. % but the preferences are given. 
-%a  partially defined voting rule.
-%While previous works have considered either partial information about the agent preferences or a partially specified aggregation method, we do not know of any work considering both sources of uncertainty at the same time.
 Actually, very few works altogether have considered the problem of eliciting a voting rule by asking questions to the chair.
 We mention the work of Cailloux and Endriss \cite{Cailloux2014} that assumes a different representation for the rule.
-%we mention the work of \Citet{Cailloux2014} considering elicitation the voting rule by assuming a specific representation.
-%A classic paper is the one by \citet{Stein1994} that, considering scoring rules, identified dominance relations between alternatives; these relations allow to determine pairs of alternatives where the first is at least as good as the second no matter which weights are chosen among a generic class of weights (decreasing weighs or convex decreasing weights).
-%More recent articles considered the problem of dealing with unspecified weights in positional scoring rules: \citet{Llamazares2013} proposed a method based on Data Envelopment Analysis (DEA), while \citet{Viappiani2018} proposed to aggregate the uncertainty in weights using criteria used in decision-making under uncertainty (such as minimax regret).
-% provided an elicitation framework for a different class of rules.
-Additionally, some works address the manipulability of voting rules \cite{Elkind2012,Dey2018,Conitzer2011,Baumeister2019} and 
-strategic behaviors \cite{Endriss2016,Lev2019,Annemieke2012}.
+Additionally, some works address the manipulability of voting rules \cite{Elkind2012,Dey2018,Conitzer2011,Baumeister2019} and strategic behaviors \cite{Endriss2016,Lev2019,Annemieke2012}.
 
@@
 To summarize our contributions: 1) we provide a novel mechanism for eliciting a voting rule by translating abstract questions about weights to a choice of an alternative given a concrete profile; 2) we show that with our elicitation method it is possible to reach low regret with a reasonable number of questions; 3) we present elicitation strategies that achieve good results within reasonable computation time; 4) we show that for the class of rules considered, asking a few questions to the chair suffice to reach low regret; 5) our experiments suggest that low degree of similarity among preferences (as in impartial culture) is a more challenging setting than less varied profiles.
-%\begin{itemize}
-%	\item we provide a novel mechanism for eliciting a voting rule by translating abstract questions about weights to a choice of an alternative given a concrete profile;  
-%	\item we showed that with our elicitation method %in small problem sizes, %starting with zero knowledge,
-%	it is possible to reach low regret with a reasonable number of questions;
-%	\item the elicitation strategies that we provide, in particular Pessimistic, achieve good results within reasonable computation time; %for small problem sizes;
-%	\item we showed that for the class of rules considered, asking a few questions to the chair suffice to reach low regret;
-%	\item our experiments suggest that low degree of similarity among preferences %rankings 
-%	(as in impartial culture) is a more challenging setting than less varied profiles.
-%\end{itemize}
 
@@
 At a given time, our knowledge of agent $j$'s preference is encoded by a partial order ${\ppref_j} \subseteq {\pref_j^*}$ over the alternatives, a transitive and asymmetric relation (we assume that preference information is truthful).
-%We use $\prefinc$ to denote incomparability, that is $a \prefinc_{j} b$ iff $a \nppref_j b \wedge b \nppref_j a$.
 An incomplete profile $\pprofile = (\ppref_j, j \in N^*)$ maps each agent to a partial preference.
@@
 Let $\pw \subseteq \W$ denote the set of weight vectors compatible with the preferences expressed by the chair about the scoring vector.
-%Of course it may be difficult for real decision makers to state preferences about the voting rule in such an abstract way.
 We will show in \cref{sec:elicit} that the additional preferences we use can be elicited by showing a complete profile of a synthetic election and asking who should be elected in this case.
@@
 the maximum regret is considered by assuming that an adversary can both 1) extend the partial profile $\pprofile$ into a complete profile, and 2) instantiate the weights choosing among any weight vector in $\pw$.
-%where $\pprofile$ and $\pw$ represent our knowledge so far.
 We formalize the notion of minimax regret in multiple steps.
@@
 $$\PMR(x,y;\pprofile,W) = \max_{\w \in W} \max_{\profile \in C(\pprofile)} s(y; \profile,\w) - s(x; \profile,\w).$$
-The maximum regret %$\MaxR(x;\pprofile,W)$ 
-is the worst-case loss of $x$:
+The maximum regret is the worst-case loss of $x$:
 \begin{align}
@@
 Picking as consensus choice an alternative associated with minimax regret provides a recommendation that gives worst-case guarantees. 
-In cases of ties, %in minimax regret, 
-we can return all minimax alternatives $A^*_{\pprofile, W}$ as winners or pick one of them using some tie-breaking strategy.
+In cases of ties, we can return all minimax alternatives $A^*_{\pprofile, W}$ as winners or pick one of them using some tie-breaking strategy.
 
@@
 We note that our notion of regret gives some cardinal meaning to the scores: instead of just being used to select winners under the corresponding PSR, their differences are considered as representing the regret of the chair.
-
-% Add some general remarks about using minimax regret
 
@@
 Thus, we can write the actual regret of choosing $x$ instead of $y$ as $s(y; \profile,\w) - s(x; \profile, \w) = \sum_{j \in N} w_{v_j(y)} - w_{v_j(x)}$, and we obtain \[\PMR(x,y; \pprofile, W) =  \max_{\w \in W} \sum_{j \in N} \max_{v_j \in C(\succ_j^p)} [w_{v_j(y)} - w_{v_j(x)}].\]
-%Note that in general the inner max depends on the weights chosen by the outer max.
 
@@
 	\end{eqnarray}
-	%	\begin{align} 
-	%		\label{eq:complx}
-	%		a \pref_j x &⇔ ¬(x \pprefeq_j a)\\
-	%		\label{eq:comply}
-	%		y \pref_j a &⇔ ¬(a \pprefeq_j y) ∧ ¬((x \pprefeq_j y) ∧ ¬(x \pprefeq_j a)).
-	%	\end{align} 
 \end{proposition}
@@
 \end{proposition}
-%\cref{claim:rankPMR} can be understood by observing that in the case $(x \pprefeq_j y)$, $\beta$ is the number of alternatives incomparable with both $x$ and $y$.
+
 \cref{claim:PMR}  shows that PMR is linear in the weights.
-%Recall that $\pw$ represents the weight vectors compatible with the preferences of the chair stated so far.
 The pairwise max regret $\PMR(x,y; \pprofile,W)$ can thus be obtained by solving the following linear program defined on the variables $w_1, …, w_m$:
@@
 \end{align}
-%Note that given our choice $w_{1}=1$ and $w_{m}=0$, there are only $m-2$ variables 
-%(we leave $w_{1}$ and $w_{m}$ in the LP just for clarity of presentation).
 The max regret $\MaxR(x; \pprofile, W)$ is determined by computing the pairwise regret of $x$ with all other alternatives in $A$, and the recommended alternatives are the ones with least max regret. 
@@
 
-%As termination condition of elicitation, we can check whether minimax regret is lower than a threshold; or after having asked a given number of questions.
-%if we wish optimality, we can perform elicitation until minimax regret drops to zero.
-
-%The remainder of this section is structured as follows.
-%First, we discuss the different types of questions that can be asked to the agents and to the chair, and the way responses are handled.
-%Then, we describe different strategies to determine informative queries to ask next, with the goal of reducing $\MMR(\pprofile,W)$ quickly.
-
 \paragraph{Question types}
@@
 As {\em questions asked to the agents} we consider comparison queries relating two alternatives.
-%Another common type of queries are {\em top-k}, asking to each agent her $k$ most preferred alternatives.
 The effect of a response to a question asked to an agent is the increase in our knowledge about the agent rankings, thus augmenting the partial profile $\pprofile$. 
@@
 	Define a linear order $>_1$ over $A$ as placing $a$ at rank $r$, $b$ at rank $r + 1$, and the remaining alternatives arbitrarily. 
-	Define %a linear order 
-	$>_2$ over $A$ as placing $a$ at rank $r + 2$, $b$ at rank $r + 1$, and the remaining alternatives arbitrarily.
+	Define $>_2$ over $A$ as placing $a$ at rank $r + 2$, $b$ at rank $r + 1$, and the remaining alternatives arbitrarily.
 	Define an arbitrary linear ordering $>$ over $A \setminus \set{a, b}$. 
@@
 		\centering
+		\caption{Profile representing a question to the chair in extended (a) and compact (b) form.}
 		\begin{subfigure}[b]{0.49\textwidth}
@@
 					d&a&a&d&d&d&c&c&c\\
-				\end{array}.
+				\end{array}
 				$
@@
 					d&a&d&c\\
-				\end{array}.
+				\end{array}
 				$
@@
 		\end{subfigure}
-		\caption{Profile representing a question to the chair in extended (a) and compact (b) form.}
 	\end{figure}
@@
 While it is of course possible to first fully elicit the agent preferences and afterwards elicit weights, we want to investigate approaches that are able to recommend winning alternatives before obtaining complete knowledge of the profile or the rule.
-%Indeed, it can be beneficial to split efforts asking questions to the chair and to agents, depending on which is estimated to be more informative.
-We define here various strategies; %we tested experimentally. 
-a strategy tells us, given the current partial knowledge $(\pprofile, W)$, which question to ask next.
+We define here various strategies; a strategy tells us, given the current partial knowledge $(\pprofile, W)$, which question to ask next.
 
-The \strat{Random} strategy is used as a baseline. % and informs about the difficulty of an elicitation problem. 
+The \strat{Random} strategy is used as a baseline.
 It first chooses equiprobably whether to question the chair or the agents.
 In the first case, it draws one rank in $1 ≤ r ≤ m-2$ equiprobably, takes the middle of the interval of values for $\lambda$ that are still possible considering our knowledge so far, and asks whether $w_r - w_{r+1} ≥ \lambda (w_{r+1} - w_{r+2})$.
-%The intervals are initialized to $[1, n]$: $\lambda≥1$ by convexity and we assume $\lambda≤n$ wlog, in fact for $\lambda≥n$, the rule coincides with Plurality.
 In the second case, it draws equiprobably among the agents whose preference is not known entirely; it then draws an alternative $a$ among those involved in some incomparabilities in $\ppref_j$ and an alternative $b$ among those incomparable with $a$ in $\ppref_j$.
@@
 it concerns the pair $(x^*, z)$ for some $z$ incomparable to $x^*$ (randomly chosen), or if none such $z$ exist, the pair $(\bar{y}, z)$ for some $z$ incomparable to $\bar{y}$, or, if both $x^*$ and $\bar{y}$ are comparable to every alternatives in $\ppref_j$, any incomparable pair is picked at random.
-%Responses to questions involving $x^*$ or $\bar{y}$ constrain the ability of the adversary to complete the profile in such manner, possibly reducing minimax regret.
 
@@
 Once having selected $n + m - 2$ candidate questions, the Pessimistic strategy selects the one that leads to minimal regret in the worst case.
-%, considering both possible answers to the question, and with penalty terms depending on the kind of question. To define this comparison precisely, 
 Assume that a question $q_1$ has type $t_1$ (being “chair” or “agent”), and leads to the new knowledge states $(\pprofile_1, W_1)$ if answered positively and $(\pprofile'_1, W'_1)$ if the answer is negative.
@@
 and \[R^{\min}_1 = \min\set{\MMR(\pprofile_1, W_1), \MMR(\pprofile'_1, W'_1)} \epsilon_{t} + \epsilon'_{t}.\]
-%If $(\pprofile_1, W_1) ≥ (\pprofile'_1, W'_1)$, define $\MMR^{\max} = \MMR(\pprofile_1, W_1)$ and $\MMR^{\min} = \MMR(\pprofile'_1, W'_1)$; otherwise, define $\MMR^{\max} = \MMR(\pprofile'_1, W'_1)$ and $\MMR^{\min} = \MMR(\pprofile_1, W_1)$.
-% and and $(\pprofile^\min_2, W^\min_2)$. numbering them so that $\MMR(\pprofile_1, W_1) ≥ \MMR(\pprofile_2, W_2)$. Then the badness of the question in the worst case is:
 The terms $\epsilon_t$ and $\epsilon'_{t}$ are real numbers associated to the type $t$ of question; these parameters are used to fine tune the choice of the question type. 
 Define similarly $t_2$, $R^{\max}_2$ and $R^{\min}_2$ for  $q_2$.
-%We are now faced with the problem of aggregating these values in order to compare the informative values of the candidate questions.
-\footnote{We adopt a pessimistic approach, reported to perform better than optimistic aggregation \cite{Cailloux2014}, although Our experiments in this context suggested a weak impact of that choice on the performance of the strategy.}
-%To avoid the absorption property of the max, we adopt $\leximax$ as an aggregator.
 Pessimistic considers question $q_1$ to be better  than $q_2$ iff $R^{\max}_1 < R^{\max}_2 \text{ or } [R^{\max}_1 = R^{\max}_2 \text{ and } R^{\min}_1 < R^{\min}_2]$.
-%This comparison gives a way of picking questions among a set of possible questions, by picking one that minimizes this approximate measure of minimax regret {\em a posteriori}. 
-%The motivation for using this operator lies in 
-In other words if the maximal {\em a posteriori} MMR of two questions are (approximately) equal, then it considers the (penalized) minimal MMR values. %, preferring the question with the lowest value.
-%(Technically, instead of applying a pure lexicographic aggregation, which is very sensitive to small errors due to floating-point computations, we apply a weighted sum between the maximal and the penalized minimal MMR values, with a predominant weight given to the maximal one, several order of magnitudes higher than the weight given to the penalized minimal MMR.)
+In other words if the maximal {\em a posteriori} MMR of two questions are (approximately) equal, then it considers the (penalized) minimal MMR values.
 
@@
 These candidate questions are then evaluated using the same operator as for the Pessimistic strategy.
-%We use this strategy to test whether Pessimistic performs well: depending on the quality of the heuristic of the Pessimistic strategy, it might perform nearly equally well, or perhaps even better, than Extended pessimistic, while being (much) faster.
 Extended pessimistic is applicable only to very small problem instances: its complexity is in $O(n^2 m^5)$, because we consider $O(m^2)$ questions for each agent and need for each question to compute MMR twice, whose complexity is $O(nm^3)$.
 
-The \strat{Two phases} strategy is developed in order to investigate the effect of varying the proportion of questions of the two types, %asked to agents and to the chair, %and to compare the performance
-when asking all questions to the chair at the beginning or at the end.
-%first or to the agents first. 
+The \strat{Two phases} strategy is developed in order to investigate the effect of varying the proportion of questions of the two types, when asking all questions to the chair at the beginning or at the end.
 It is parameterized by $q_c$,  the number of questions to be asked to the chair.
 The \strat{Two phases-ca} variant first asks $q_c$ questions to the chair, then $k - q_c$ questions to the agents, using in both cases Pessimistic to select the specific questions; whereas the \strat{Two phases-ac} variant starts with $k - q_c$ questions to the agents, then questions the chair.
-%Note that when asking first only questions to the chair, if the obtained knowledge approximates well the scoring vector, then in the second part of the elicitation we fall into the more classical setting of incompleteness of preferences assuming a known voting rule.
-%And vice-versa when asking first questions to the agents, the second part of the elicitation is similar to the setting of incompletely specified scoring rule. 
-%This strategy also permits to simulate the current state of the art when considering incomplete preferences.
-By asking enough questions to the chair we can reduce our problem into a well studied one of incompleteness of preferences knowing the voting rule.
-Similarly, if we invert to whom ask questions first, we fall instead in an already studied case of uncertainty of the voting rule with a known complete profile.
 
 Finally, the \strat{Elitist} strategy aims at uncovering as quickly as possible the top alternatives of all agents. 
-%It asks $m - 1$ questions to each agent in turn. 
 For any agent $j$, it asks to compare an alternative currently undominated in $\ppref_j$ with one that is currently incomparable.
@@
 
-%\item {\em Volumetric} strategy: chooses an agent $i$ and a query that maximizes the number of new pairwise preferences revealed given the worst response.
-
 \section{Empirical Evaluation} 
@@
 We  performed several numerical experiments using both real data and randomly generated profiles in order to validate our approach and test the performance of our elicitation strategies.
-%Our experiments are described by topic here below.
-%We start by describing the general protocol of experimentation. %use the following protocol, deviations are indicated below for each experiment.
 
 Given a problem size $(m, n)$, a number of questions $k$ and a strategy to test, we first create an “oracle”, representing the true preferences of the agents (randomly generated or coming from real data) and the weights associated with the chair’s scoring rule (randomly generated).
-We start with empty knowledge ($\pprofile = \emptyset, W = \W$) about the preference orderings of the agents and the weights %differences favored by
-of the chair.
+We start with empty knowledge ($\pprofile = \emptyset, W = \W$) about the preference orderings of the agents and the weights of the chair.
 We obtain the first question to be asked using the strategy under test.
@@
 and \emph{Skate} (judges voted on skaters at the Euros Pairs Short Program; $m \!=\! 14, n \!=\! 9$).
-% tee shirt designs voted by 
-%$n \!=\! 30$ 
-%members of the Optimization Research Group at NICTA;
-% \textit{AGH Course Selection}: $m \!=\! 9$ courses evaluated by $n = 146$ students 
-%of the AGH University; 
-%and \emph{Skate}: $m \!=\! 14$ skaters evaluated by $n \!=\! 9$ judges at the Euros Pairs Short Program.
-%We want to focus on the most critical setting, as there is a wide variety of possible situations to test in such experiments.
 For the synthetic datasets, we follow an Impartial Culture (IC) assumption: the linear order of each agent is drawn i.i.d.\ uniformly.
-%independently and all have the same probability of appearing. 
 We believe IC to be a challenging situation and expect the number of questions to ask, in order to reach a certain level of regret, to decrease with less varied profiles.
-%We adopt IC because it is a more challenging situation: as can be expected intuitively , the number of questions to be asked decrease with less varied profiles. 
 To generate the scoring rule weights, we first draw $m \!-\!
@@
 \sisetup{table-number-alignment = center, table-figures-integer=2, table-figures-decimal=1, table-auto-round}
+\noindent
 \begin{minipage}{\textwidth}
@@
 		\centering
-		\captionof{figure}{Average MMR in problems of size $(5, 10)$ after $k$ questions.}
+		\captionsetup{type=figure}
+		\caption{Average MMR in problems of size $(5, 10)$ after $k$ questions.}
 		\label{fig:smallSize}
@@
 		\centering
-		\captionof{table}{Average MMR in problems of size $(10, 20)$ after $k$ questions assuming geometric weights.}
+		\captionsetup{type=table}
+		\caption{Average MMR in problems of size $(10, 20)$ after $k$ questions assuming geometric weights.}
 		\label{tab:geometricWeights}
@@
 \Cref{fig:smallSize} compares some of our strategies in the case $m = 5, n = 10$ (variations around this size yield similar conclusions), where the results are averaged over $200$ runs.
-%(The figure also displays the performance of the Elitist strategy, to which we will come back.)
 We see that asking random questions does not allow to reach a low regret level even after having asked 100 questions, whereas a low regret level ($\MMR \!=\!
@@
 The m15n30 dataset did not reach zero regret in $1000$ questions.
-%For example, in the case $m = 10, n = 20$, Pessimistic asks on average $49$ questions to the chair and $18$ questions to each agent (\cref{tab:Numquestions} provides more data).
+
 \vspace{-0.6cm}
 \begin{table}
+	\centering
 	\caption{Questions asked by Pessimistic strategy on several datasets to reach $\frac{n}{10}$ regret, columns 4 and 5, and zero regret, last two columns.}
 	\label{tab:questions}
-	\begin{tabular}{cccS[table-number-alignment = center, table-figures-integer=2] S[table-figures-integer=3, table-figures-decimal=1]@{ | }S[table-figures-integer=2, table-figures-decimal=1]@{ | }S[table-figures-integer=2, table-figures-decimal=1]@{ ]} S[table-number-alignment = center, table-figures-integer=2]S[table-figures-integer=3, table-figures-decimal=1]@{ | }S[table-figures-integer=2, table-figures-decimal=1]@{ | }S[table-figures-integer=2, table-figures-decimal=1]@{ ]}}
+	\begin{tabular}{p{1.5cm}S[table-number-alignment = center, table-figures-integer=2]S[table-number-alignment = center, table-figures-integer=3]S[table-number-alignment = center, table-figures-integer=2,table-column-width=5em]p{0.5em}@{}S[table-figures-integer=2, table-figures-decimal=1]@{ | }S[table-figures-integer=2, table-figures-decimal=1]@{ | }S[table-figures-integer=2, table-figures-decimal=1]@{ ]} S[table-number-alignment = center, table-figures-integer=2, table-figures-decimal=1,table-column-width=5em]p{0.5em}@{}S[table-figures-integer=2, table-figures-decimal=1]@{ | }S[table-figures-integer=2, table-figures-decimal=1]@{ | }S[table-figures-integer=2, table-figures-decimal=1]@{ ]}}
 		\toprule
-		{dataset} & m & n &{$q_{c}^{\scriptscriptstyle{\MMR} ≤ n/10}$} & \multicolumn{3}{c}{$q_{a}^{\scriptscriptstyle{\MMR} ≤ n/10}$} & {$q_{c}^{ \scriptscriptstyle{\MMR} = 0}$} & \multicolumn{3}{c}{$q_{a}^{ \scriptscriptstyle{\MMR} = 0}$} \\
+		{dataset} & m & n &{$q_{c}^{\scriptscriptstyle{\MMR} ≤ n/10}$} & \multicolumn{4}{c}{$q_{a}^{\scriptscriptstyle{\MMR} ≤ n/10}$} & {$q_{c}^{ \scriptscriptstyle{\MMR} = 0}$} & \multicolumn{4}{c}{$q_{a}^{ \scriptscriptstyle{\MMR} = 0}$} \\
 		\midrule
-		m5n20 & 5&20&0.0&[4.3 &4.95 & 5.84 &5.25&[ \ 5.36 & 6.15 & 7.21\\
-		m10n20&10&20&0.0&[13.85 & 16.1& 18.41&31.95&[19.66 & 21.78 & 24.7\\
-		m11n30&11&30&0.0&[16.55&19.0&22.26&45.15&[23.07&25.7&28.89\\
-		tshirts&11&30&0.0&[13.08&16.6&19.58& 43.15 &[28.22&31.98 &35.62\\
-		courses&9&146&0.0&[6.03 &7.0 &7.0&0.0&[6.81 & 7.0 &7.0\\
+		m5n20 & 5&20&0.0&[&4.3 &4.95 & 5.84 &5.25&[& 5.36 & 6.15 & 7.21\\
+		m10n20&10&20&0.0&[&13.85 & 16.1& 18.41&31.95&[&19.66 & 21.78 & 24.7\\
+		m11n30&11&30&0.0&[&16.55&19.0&22.26&45.15&[&23.07&25.7&28.89\\
+		tshirts&11&30&0.0&[&13.08&16.6&19.58& 43.15 &[&28.22&31.98 &35.62\\
+		courses&9&146&0.0&[&6.03 &7.0 &7.0&0.0&[&6.81 & 7.0 &7.0\\
 		%m9n146&9&146&0&0&[1.94 &8 &9.25&999.3&0.47&0&0&[1.94&8&9.25&999.3&0.47\\
-		m14n9&14&9&5.4&[30.3&33.45&36.65&64.05&[37.55&40.5&44.3\\
-		skate&14&9&0.0&[11.35&11.6&12.3&0.0&[11.5&11.8&12.75 \\
-		m15n30&15&30&0.0&[24.95&29.5&33.68 \\
+		m14n9&14&9&5.4&[&30.3&33.45&36.65&64.05&[&37.55&40.5&44.3\\
+		skate&14&9&0.0&[&11.35&11.6&12.3&0.0&[&11.5&11.8&12.75 \\
+		m15n30&15&30&0.0&[&24.95&29.5&33.68 \\
 
@@
 By contrast, in \textit{T Shirt}, the alternatives are evenly distributed in the preference rankings.
-% in \textit{Courses} all agents rank the same alternative at the top position,
-
-\begin{minipage}{\textwidth}
+\noindent
+\begin{minipage}{\linewidth}
 	\vspace{0.4cm}
-	\begin{minipage}{\textwidth}
+	\begin{minipage}{\linewidth}
 		\centering
-		\captionof{figure}{Average MMR (normalized by $n$) after $k$ questions with Pessimistic strategy for different datasets.}
+		\captionsetup{type=figure}
+		\caption{Average MMR (normalized by $n$) after $k$ questions with Pessimistic strategy for different datasets.}
 		\label{fig:linearity}
@@
 
-	\begin{minipage}{\textwidth}
+	\begin{minipage}{\linewidth}
 		\centering
-		\captionof{table}{Average MMR in problems of size $(10, 20)$ after $500$ questions, among which $q_c$ to the chair.}
+		\captionsetup{type=table}
+		\caption{Average MMR in problems of size $(10, 20)$ after $500$ questions, among which $q_c$ to the chair.}
 		\label{tab:twoP500}
@@
 \end{minipage}
-%\subsection{Value of information comparison}
+
 \paragraph{Comparison with Two Phases}
@@
 Such restrictions may be useful because of (partial) unavailability of the chair, or because the estimated cognitive costs may differ sensibly.
-%, as these types of questions differ in nature.
 
@@
 These numbers are to be compared with the MMR value reached after 500 questions with the Pessimistic strategy (displayed in \cref{fig:linearity}), which is $0.7$; the Pessimistic strategy asks on average $13$ (± $13$) questions to the chair in this setting.
-%\commentBN{This is not true anymore, after 400 questions it reaches $0.9$ with 0 questions to the chair, after 500 questions it reaches $0.47$ ($\sigma = 0.51$) with $11.05$ question to the chair ($\sigma=12.34$).
-The data in Table 2 is after 582 questions.}\commentBN{Even this comment is not entirely true.
-We should take the data after 500 questions on the same datasets as the one used in Table3.
-On the first 3 runs, after 500 questions the regret is $0.62$ ($\sigma = 0.42$) and the number of questions to the chair is $14.33$ ($\sigma = 13.58$).
-On the first 7 runs, after 500 questions the regret is $0.67$ ($\sigma = 0.45$) and the number of questions to the chair is $13.29$ ($\sigma = 13.11$).}
 The line $q_c = 0$, where no question is asked to the chair, suggest that it is possible to obtain a good-quality recommendation while knowing only that the voting rule is a scoring rule with convex weights, which is our basic hypothesis.
@@
 We have proposed the use of minimax regret both as a means of robust winner determination and as a guide to the process of simultaneous elicitation of preferences and voting rule.
-Our experimental results %on randomly generated and real world datasets 
-suggest that regret-based elicitation is effective and allows to quickly reduce worst-case regret significantly.
+Our experimental results suggest that regret-based elicitation is effective and allows to quickly reduce worst-case regret significantly.
 They also show that, in our setting, good quality (low regret) recommendations can be achieved short of having full knowledge of weights or profile.
-%regret, but they also show that starting with zero knowledge became a pretentious approach really quickly when increasing the size of the problem.
-Future works will therefore include the test of these strategies on partial specified profiles, ideally on real datasets.
-An other important direction is the extension to voting rules beyond scoring rules.
-%Regret-based elicitation allows to determine near-optimal winners using only few information about the agent preferences.
 
-As part of our contribution, we provide an open-source library \url{https://github.com/oliviercailloux/minimax}, to reproduce our experiments and perform many more.
-%will be made publicly available.(URL not displayed for reasons of anonymity.)
-%and serve as a basis for further research
+As part of our contribution, we provide an open-source library that can be found at \url{https://github.com/oliviercailloux/minimax}, to reproduce our experiments and perform many more.
 
 Some directions for future works include developing new elicitation strategies, considering alternative heuristics; extending the elicitation to voting rules beyond scoring rules; eliciting preferences while restraining to concrete and easy questions.
-%
-% ---- Bibliography ----
-%
-% BibTeX users should specify bibliography style 'splncs04'.
-% References will then be sorted and formatted in the correct style.
-%
+
 \bibliographystyle{splncs04}
 \bibliography{biblio}
-%
 
